### 2024-03-22 introduction.tex
new

%======================================================================
\chapter{Introduction}
%======================================================================

Quantitative risk management is a key component of modern financial systems, ensuring the stability and resilience of markets, institutions, and portfolios against an array of risks. In the era of complex financial products, such as option portfolios and variable annuity contracts, traditional risk assessment methods often fall short in accurately capturing the multifaceted nature of market, credit, and operational risks. This is where advanced simulation techniques, particularly nested simulation procedures, become indispensable.

### 2024-03-22 uw-ethesis-frontpgs.tex
new

% T I T L E   P A G E
% -------------------
% Last updated June 14, 2017, by Stephen Carr, IST-Client Services
% The title page is counted as page `i' but we need to suppress the
% page number. Also, we don't want any headers or footers.
\pagestyle{empty}
\pagenumbering{roman}

% The contents of the title page are specified in the "titlepage"
% environment.
\begin{titlepage}
        \begin{center}
        \vspace*{1.0cm}

        \Huge
        {\bf Efficient Nested Simulation of Tail Risk Measures with Machine Learning Proxies }

        \vspace*{1.0cm}

        \normalsize
        by \\

        \vspace*{1.0cm}

        \Large
        Xintong Li \\

        \vspace*{3.0cm}

        \normalsize
        A thesis \\
        presented to the University of Waterloo \\ 
        in fulfillment of the \\
        thesis requirement for the degree of \\
        Doctor of Philosophy \\
        in \\
        Actuarial Science \\

        \vspace*{2.0cm}

        Waterloo, Ontario, Canada, 2022 \\

        \vspace*{1.0cm}

        \copyright\ Xintong Li, 2022 \\
        \end{center}
\end{titlepage}

% The rest of the front pages should contain no headers and be numbered using Roman numerals starting with `ii'
\pagestyle{plain}
\setcounter{page}{2}

\cleardoublepage % Ends the current page and causes all figures and tables that have so far appeared in the input to be printed.
% In a two-sided printing style, it also makes the next page a right-hand (odd-numbered) page, producing a blank page if necessary.

% E X A M I N I N G   C O M M I T T E E (Required for Ph.D. theses only)
% Remove or comment out the lines below to remove this page
\begin{center}\textbf{Examining Committee Membership}\end{center}
  \noindent
The following served on the Examining Committee for this thesis. The decision of the Examining Committee is by majority vote.
  \bigskip

%   \noindent
% \begin{tabbing}
% Internal-External Member: \=  \kill % using longest text to define tab length
% External Examiner: \>  John Smith \\ 
% \> Professor, Dept. of Philosophy of XX, University of ABC \\
% \end{tabbing} 
%   \bigskip

  \noindent
\begin{tabbing}
Internal-External Member: \=  \kill % using longest text to define tab length
Supervisor(s): \> Mingbin Feng \\
\> Assistant Professor, Dept. of Statistics and Actuarial Science\\
\> University of Waterloo \\[1cm]
\> Tony S. Wirjanto \\
\> Professor, Dept. of Statistics and Actuarial Science \\
\> University of Waterloo \\
\end{tabbing}
  \bigskip

  \noindent
  \begin{tabbing}
Internal-External Member: \=  \kill % using longest text to define tab length
Internal Member: \> Mary R. Hardy \\
\> Professor, Dept. of Statistics and Actuarial Science \\
\> University of Waterloo\\[1cm]
\> Chengguo Weng \\
\> Professor, Dept. of Statistics and Actuarial Science \\
\> University of Waterloo \\
\end{tabbing}
  \bigskip

%   \noindent
% \begin{tabbing}
% Internal-External Member: \=  \kill % using longest text to define tab length
% Internal-External Member: \> John Smith \\
% \> Professor, Dept. of XX, University of ABC \\
% \end{tabbing}
%   \bigskip

%   \noindent
% \begin{tabbing}
% Internal-External Member: \=  \kill % using longest text to define tab length
% Other Member(s): \> John Smith \\
% \> Professor, Dept. of XX, University of ABC \\
% \end{tabbing}

\cleardoublepage

% D E C L A R A T I O N   P A G E
% -------------------------------
  % The following is a sample Delaration Page as provided by the GSO
  % December 13th, 2006.  It is designed for an electronic thesis.
  \noindent
I hereby declare that I am the sole author of this thesis. This is a true copy of the thesis, including any required final revisions, as accepted by my examiners.

  \bigskip

  \noindent
I understand that my thesis may be made electronically available to the public.

\cleardoublepage

% A B S T R A C T
% ---------------

\begin{center}\textbf{Abstract}\end{center}

Nested simulation procedures are commonly required for estimating tail risk measures for complex financial contracts or portfolios. 
In a standard nested simulation procedure, an outer simulation simulates $M$ risk scenarios under a real-world measure to reflect real-world uncertainties in portfolio values in different risk scenarios. 
For each outer scenario, inner simulation estimates the corresponding portfolio loss based on $N$ sample paths simulated under a risk-neutral measure according to  the risk-neutral pricing theory. 
This standard procedure is computationally expensive. 
For example, the simulation budget, i.e., the total number of inner sample paths in all outer scenarios, is a common way to measure the computation required for a simulation procedure. For the standard nested simulation procedure, the simulation budget is $\Gamma = MN$.
To alleviate computational burden of the standard procedure, many studies proposed to replace the inner simulation with alternative such as regression, kernel smoothing, likelihood ratio method, kernel ridge regression, etc. 
We refer to these alternatives as proxies. 
The above proxies have been demonstrated to have superior performance than the standard procedure in different examples.

The three parts of the thesis have different research focuses but serve one common theme.
Chapter 2 compares four existing nested simulation methods on their theoretical convergence properties and practical performance. 
Extensive numerical experiments are conducted for fair comparisons of proxy models on their practical performance in different angles. 
Proxies in chapter 2 fail to perform for high dimensional scenarios. 
In chapter 3, machine learning proxies are considered to model variable annuity contract losses.
Numerical experiments show that, for scenarios with temporal structure, time-series machine learning models are better proxies than generic machine learning models. 
The machine learning proxies are applied in a 2-stage nested simulation design. 
Experiments show that machine learning proxies outperform payoff-specific proxies.
Chapter 4 proposes direction for future research. In the 2-stage design, inner simulation in the second stage is still costly. 
We propose replacing stage 2 with machine learning proxy predictions. 
We test the accuracy, sensitivity, and resilience of such proposal.

\cleardoublepage

% A C K N O W L E D G E M E N T S
% -------------------------------

\begin{center}\textbf{Acknowledgements}\end{center}

I would like to thank Professor Ben Feng and Professor Tony Wirjanto for they valuable support. They have patiently helped me through my journey as a Ph.D. student.  
\cleardoublepage

% T A B L E   O F   C O N T E N T S
% ---------------------------------
\renewcommand\contentsname{Table of Contents}
\tableofcontents
\cleardoublepage
\phantomsection    % allows hyperref to link to the correct page

% L I S T   O F   T A B L E S
% ---------------------------
\addcontentsline{toc}{chapter}{List of Tables}
\listoftables
\cleardoublepage
\phantomsection		% allows hyperref to link to the correct page

% L I S T   O F   F I G U R E S
% -----------------------------
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures
\cleardoublepage
\phantomsection		% allows hyperref to link to the correct page

% GLOSSARIES (Lists of definitions, abbreviations, symbols, etc. provided by the glossaries-extra package)
% -----------------------------
\printglossaries
\cleardoublepage
\phantomsection		% allows hyperref to link to the correct page

% Change page numbering back to Arabic numerals
\pagenumbering{arabic}

### 2024-03-23 project1/nsSurvey.tex
new

%======================================================================
\chapter{Nested Simulation Procedures in Financial Engineering: A Selected Review}
%======================================================================

\section{Introduction}

Nested simulation procedures, also known as stochastic on stochastic simulation, are commonly used in financial engineering to estimate risk measures for portfolios of complex financial derivatives. 
The term \textit{nested} is referred to a nested estimation problem, in which the estimation of the risk measure requires two levels of Monte Carlo (MC) simulations.
In a typical nested simulation procedure, an outer level simulation model generates underlying risk factors, which is referred to as the \textit{outer scenarios}.
For each outer scenario, an inner level simulation model generates scenario-wise samples of the portfolio losses, which is referred to as the \textit{inner replications}.

The nested simulation procedure is computationally expensive due to its nested structure. 
Given a fixed computational budget, the nested simulation procedure has to make a trade-off between the number of outer scenarios and the number of inner replications.
~\cite{gordy2010nested} are the first to analyze and propose the optimal budget allocation of a standard nested simulation procedure. 
The term \textit{standard} refers to using a standard Monte Carlo estimator, the sample mean of the inner replication to estimate a scenario-wise portfolio loss for an outer scenario.
~\cite{gordy2010nested} investigate the optimal budget allocation for a standard nested simulation procedure with respect to the mean squared error (MSE) of the estimated risk measure.

The standard nested simulation procedure is computationally expensive with a somewhat wasteful use of the simulation budget, as only the inner replications from the same outer scenario are used in estimating the scenario-wise portfolio loss for that outer scenario. 
Subsequent research efforts have been made to improve the efficiency of nested simulation procedures by using the inner replications from other outer scenarios. 
This is referred to as pooling. 
Different methods pool in different ways, either by a trained proxy model or by pre-defined likelihood ratio weights.
~\cite{broadie2015risk} propose a regression-based nested simulation procedure, which uses a trained regression proxy model to estimate the scenario-wise portfolio loss for an outer scenario by pooling the inner replications from all outer scenarios.
For risk measures in certain forms,~\cite{broadie2015risk} show that it is optimal to allocate all simulation budget to the outer level simulation, and the inner replication should be kept to a minimum of $1$.
Similarly,~\cite{hong2017kernel},~\cite{feng2020optimal}, and~\cite{zhang2022sample} propose to use a kernel smoothing model, a likelihood ratio model, and a kernel ridge regression model as proxies to pool the inner replications from all outer scenarios.
Another line of research is the multi-level Monte Carlo (MLMC) method analyzed in~\cite{giles2019multilevel}, which is a variance reduction technique that uses a hierarchy of approximations to the risk measure of interest.

This paper presents a survey study of some popular nested simulation procedures. 
Many procedures are proposed in the literature, but they are not directly comparable due to different error metrics, different assumptions, and different numerical examples.
Within a common analytical framework, we first summarize and compare their asymptotic rate of convergence.
Their asymptotic convergence results are closely examined for their assumptions that guarantee the convergence.
Furthermore, our study finds that different studies have used different examples in their numerical experiments, which introduces unfair advantages for certain simulation procedures over others. 
A fair comparison among popular methods is therefore urgently needed in the literature. 
Our numerical experiment is the first of its kind to subject back all the aforementioned simulation procedures to a complete and unbiased comparison. 
Extensive numerical experiments are conducted to show, in practical examples, how well the finite-sample performance of a method matches its theoretical convergence behavior. 
With our numerical examples, we compare the nested simulation procedures for different payoff complexity, problem dimensions, and risk measures.

The rest of the paper is organized as follows.
% Section~\ref{sec:problem-formulation} introduces the nested simulation procedure and the standard Monte Carlo estimator.
% Section~\ref{sec:asymptotic-convergence} provides new theoretical results on the convergence of existing nested simulation procedures.
% Section~\ref{sec:convergence-orders} summarizes the asymptotic convergence orders and the critical assumptions of nested simulation procedures in the literature.
% Section~\ref{sec:numerical-experiments} presents the numerical experiments and the comparisons of different nested simulation procedures with respect to different risk measures, problem dimensions, and payoff complexities.
% Section~\ref{sec:computational-complexity} discusses the computational complexity of different nested simulation procedures.
% Section~\ref{sec:conclusion} concludes the paper.

\section{Problem Formulation} \label{sec:problem-formulation}

In a nested estimation problem, we are interested in the quantity

$$\rho(g(X)), $$

where $X \in \Omega$. 
$g(X)$ can't be directly evaluated, but it is the output of

$$ g(X) = \mathbb{E}\left[ Y|X=x \right]\vert_{x=X} $$

Some common risk measures are in the nested expectation form, in which 
$$\rho(g(X)) = \mathbb{E}\left[ h(g(X)) \right]$$

where $h(\cdot)$ is a known function. 
Forms of $h$ include the following:
\begin{itemize}
    \item 	Smooth functions, e.g., a quadratic tracking error with benchmark $b$: $h(t) = (t - b)^2$
    \item 	Lipschitz continuous functions, e.g., a mean excess loss over threshold $u$: $h(t) = \max\{t - u, 0\}$. Here, $h$ is a hockey-stick function.
    \item 	Indicator functions, e.g., probability of a large loss over a threshold $u$: $h(t) = \mathbb{I}_{\{t \geqslant u\}}$
\end{itemize}

Other risk measures of interest that are not in the nested expectation form are the value at risk (VaR) and the conditional value at risk (CVaR). 
The $\alpha$-VaR of $g(X)$ is defined as
$$
    \mbox{VaR}_\alpha(g(X)) = q_\alpha = \inf \left\{ q: \Pr(g(X)\leq q) \geq \alpha \right\}.
$$
The $\alpha$-CVaR of $g(X)$ is defined as
$$
    \mbox{VaR}_\alpha(g(X)) =\frac{1}{1-\alpha} \int_{\alpha}^{1} q_v dv. 
$$

\subsection{The Standard Nested Simulation Procedure}

The standard nested simulation procedure first simulates $M$ independent and identically distributed (iid) outer scenarios $X_1, \dots, X_M$ from $F_X$, the distribution of $X$.
For each $X_i$, again simulate $Y_{ij}$, $j = 1, \dots, N$ from $F_{Y|X_i}$, the conditional distribution of $Y$ given $X_i$. Given scenario $i$, the $Y_{ij}$ are conditionally iid. Let $\Gamma = M \cdot N$ denote the total simulation budget, $f_X(x)$ denote the density of $X$, and $\mathbf{X} = (X_1, \dots, X_M)$ denote the vector of outer scenarios.

The standard nested simulation procedure estimates $g(X_i)$ with a standard Monte Carlo estimator

$$\hat{g}_N(X_i) = \frac{1}{N} \sum_{j=1}^N Y_{ij}; ~~~ Y_{ij} \sim F_{Y|X_i} $$

Let $(\hat{g}_N(\mathbf{X}))_{[1]}, \dots, (\hat{g}_N(\mathbf{X}))_{[M]}$ be the order statistics of $\hat{g}_N(X_1), \dots \hat{g}_N(X_M)$. 
The standard nested simulation estimators for different forms of $\rho$ are as follows:

\begin{enumerate}
    \item   Nested expectation form:
            $$\hat{\rho}_{M, N} = \frac{1}{M} \sum_{i=1}^M h(\hat{g}_N(X_i)) = \frac{1}{M} \sum_{i=1}^M h(\bar{Y}_{N, i}); ~~~ X_i \sim F_X$$
    \item   Value at risk (VaR):
            $$\hat{\rho}_{M, N} = (\hat{g}_N(\mathbf{X}))_{\lceil \alpha M \rceil}$$
    \item   Conditional value at risk (CVaR):
            $$\hat{\rho}_{M, N} = (\hat{g}_N(\mathbf{X}))_{\lceil \alpha M \rceil} + \frac{1}{(1-\alpha) M} \sum_{i=1}^M \max \{\hat{g}_N(X_i) - (\hat{g}_N(\mathbf{X}))_{\lceil \alpha M \rceil}, 0 \}$$
\end{enumerate}

~\cite{gordy2010nested} analyze the optimal budget allocation of the standard nested simulation procedure with respect to the MSE of the estimator $\hat{\rho}_{M, N}$.

\subsection{Supervised Learning Models}

In supervised learning, $g(\cdot)$ can be approximated by $\hat{g}^{\text{SL}}_{M, N}(\cdot)$, which is based on a chosen function family $\mathcal{G}$ and observations from the standard nested simulation procedure.
Consider the observation pairs $(X_i, \hat{g}_N(X_i))$ for $i \in \{1, \dots, M\}$ as training data, we can use supervised learning to approximate $g(\cdot)$ by $\hat{g}^{\text{SL}}_{M, N}(\cdot)$ and to pool the inner replications from all outer scenarios.
Using the $M$ \textit{training} samples, a supervised learning-based nested simulation procedure estimates  $\rho$ by

\begin{enumerate}
    \item   Nested expectation form:
            $$\hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = \frac{1}{M} \sum_{i=1}^M h(\hat{g}^{\text{SL}}_{M, N}(X_i)); ~~~ X_i \sim F_X$$
    \item   VaR:
            $$\hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = (\hat{g}^{\text{SL}}_{M, N}(\mathbf{X}))_{\lceil \alpha M \rceil}$$
    \item   CVaR:
            $$\hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = (\hat{g}^{\text{SL}}_{M, N}(\mathbf{X}))_{\lceil \alpha M \rceil} + \frac{1}{(1-\alpha) M} \sum_{i=1}^M \max \{\hat{g}^{\text{SL}}_{M, N}(X_i) - (\hat{g}^{\text{SL}}_{M, N}(\mathbf{X}))_{\lceil \alpha M \rceil}, 0 \}$$
\end{enumerate}
where $(\hat{g}_{M, N}(\mathbf{X}))_{\lceil \alpha M \rceil}$ is the $\lceil \alpha M \rceil$-th order statistic of $\hat{g}^{\text{SL}}_{M, N}(X_1), \dots, \hat{g}_{M, N}(X_M)$.
Similarly, with $M'$ \textit{test} samples of $X$, namely $\tilde{\mathbf{X}} = \tilde{X}_1, \dots, \tilde{X}_{M'}$, an estimator is given by

\begin{enumerate}
    \item   Nested expectation form:
            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = \frac{1}{M} \sum_{i=1}^M h(\hat{g}^{\text{SL}}_{M, N}(\tilde{X}_i)); ~~~ \tilde{X}_i \sim F_X.$$
    \item   VaR:
            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = (\hat{g}^{\text{SL}}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M \rceil}.$$
    \item   CVaR:
            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = (\hat{g}^{\text{SL}}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M \rceil} + \frac{1}{(1-\alpha) M} \sum_{i=1}^M \max \{\hat{g}^{\text{SL}}_{M, N}(\tilde{X}_i) - (\hat{g}^{\text{SL}}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M \rceil}, 0 \}, $$
            where $(\hat{g}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M \rceil}$ is the $\lceil \alpha M \rceil$-th order statistic of $\hat{g}^{\text{SL}}_{M, N}(\tilde{X}_1), \dots, \hat{g}_{M, N}(\tilde{X}_M)$. 
            Note that $\hat{g}^{\text{SL}}_{M, N}(\cdot)$ is derived from the training samples $(X_1, \hat{g}_N(X_1)), \dots, (X_M, \hat{g}_N(X_M))$.
\end{enumerate}

Existing literature on nested simulation procedures has proposed different methods to approximate the true function $g(\cdot)$ with supervised learning algorithms. 
Methods that include theoretical convergence results are regression~\citep{broadie2015risk}, kernel smoothing~\citep{hong2017kernel}, and kernel ridge regression~\citep{wang2022smooth}.
Their estimators of $g(\cdot)$ are given by $\hat{g}^{\text{REG}}_{M, N}(\cdot)$, $\hat{g}^{\text{KS}}_{M, N}(\cdot)$, and $\hat{g}^{\text{KRR}}_{M, N}(\cdot)$, respectively.

\begin{itemize}
    \item   Regression:
            $$\hat{g}^{\text{REG}}_{M, N}(X) = \Phi(X) \hat{\beta},$$
            where $\Phi$ is a chosen basis, and $\hat{\beta}$ is estimated from the training samples.
    \item   Kernel smoothing:
            $$\hat{g}^{\text{KS}}_{M, N}(X) = \frac{\sum_{i=1}^M \bar{Y}_{N, i} K_w(X - X_i)}{\sum_{i=1}^M K_w(X - X_i)}, $$
            where $K_w$ is the kernel function with bandwidth $w$.
    \item   Kernel ridge regression:
            $$\hat{g}^{\text{KRR}}_{M, N}(X) = \argmin_{g \in \mathcal{N}_{\Psi}(\Omega)} \left( \frac{1}{M} \sum_{i=1}^M (\hat{g}_N(X_i) - g(X_i))^2 + \lambda \|g\|_{\mathcal{N}_{\Psi}(\Omega)}^2\right),$$
            where $\mathcal{N}_{\Psi}(\Omega)$ is the reproducing kernel Hilbert space (RKHS) with kernel $\Psi$ defined domain $\Omega$, and $\lambda$ is the regularization parameter as in ridge regression. 
            More specifically, $\Phi$ is a Mat\'ern kernel with smoothness parameter $\nu$ and length scale parameter $\ell$.
\end{itemize}

\subsection{Likelihood Ratio Method}

Instead of using a supervised learning model,~\cite{zhang2022sample} uses the likelihood ratio weights to pool the inner replications from all outer scenarios.
This method is also referred to as importance sampling.
Here, we restrict our attention to problems in the nested expectation form whose outer scenarios characterize the stochasticity of the inner simulation model. 
Specifically,
$$ Y = Y(H, X), $$
where $H$ is a random variable whose distribution is specified by the outer scenarios $X$. 
We denote the conditional distribution of $H|X$ by $f_{H|X}$. 
For a specific scenario $X_i$, we write $f_{H|X}(\cdot |X_i)$. 
To reconcile with previously established notations, we note that inner simulation outputs $Y_{ij}$ can be written as
$$ Y_{ij} = Y(H_{ij}, X_i), $$
where $H_{ij} \sim f_{H|X}(\cdot |X_i)$.
Suppose that one can generate random variable H from some sampling
distribution $f_H$. Then, the likelihood ratio estimator of $\rho$ is given by
$$\hat{\rho}^{\text{LR}}_{M,N} = \frac{1}{M} \sum_{i=1}^M h(\hat{g}^{\text{LR}}_N(X_i)), $$ where the inner replications are pooled by the likelihood ratio weights with
$$\hat{g}^{\text{LR}}_N(X_i) = \frac{1}{N} \sum_{j=1}^N Y(H_j, X_i) \frac{f_{H|X}(H_{j}|X_i)}{f_H(H_{ij})}, \;\;\; H_j \sim f_H, \;\;\; i=1, \dots, M.$$

\subsection{Multi-level Monte Carlo}

The multi-level Monte Carlo (MLMC) method is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest, and it uses the difference between the approximations to reduce the variance of the estimator.
A MLMC approach is particularly useful when the quantity of interest is expensive to evaluate, and the standard Monte Carlo estimator has a high variance.
Instead of pooling from the inner samples, a MLMC-based nested simulation procedure estimates $\rho$ with a multi-level Monte Carlo estimator:

\begin{equation*}
    \hat{\rho}^{\text{MLMC}}_\Gamma = \sum_{\ell=0}^{L} \left( \frac{1}{M_{\ell}} \sum_{i=1}^{M_{\ell}} h(\hat{g}_{N_{\ell}}(X_{i, \ell})) - \frac{1}{M_{\ell-1}} \sum_{i=1}^{M_{\ell-1}} h(\hat{g}_{N_{\ell-1}}(X_{i, \ell-1})) \right), ~~~ X_{i, \ell} \sim F_X,
\end{equation*}

where $\hat{g}_N(\cdot) = 0$, $L$ is the number of levels, $M_{\ell}$ is the number of outer scenarios at level $\ell$, and $N_{\ell}$ is the number of inner replications at level $\ell$.
Applying the analysis of~\cite{giles2015multilevel} in a nested simulation context,~\cite{giles2019multilevel} show that the MLMC method can achieve a similar level of accuracy as the standard nested simulation procedure with a lower total computational budget.
The simulation budget $\Gamma$ is the sum of the computational budget at each level, that is, $\Gamma = \sum_{\ell=0}^{L} M_{\ell} \cdot N_{\ell}$.

\subsection{Problem Statement}

For all nested simulation procedures we are interested in the order of convergence of estimators in terms of the total simulation budget $\Gamma$.
The convergence rate of an estimator is measured by the MSE of the estimator $\hat{\rho}_{M, N}$ about the true value $\rho$.

\begin{align}
    & \text{MSE}(\hat{\rho}_{M, N}) = \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] \nonumber \\
    & \text{subject to} ~~~ M \cdot N = \Gamma, 
\end{align}

where $\Gamma = M \cdot N$ is the total simulation budget\footnote{For a MLMC-based nested simulation procedure, the total simulation budget $\Gamma$ is the sum of the computational budget at all levels.}. 
For a given nested simulation procedure, we are interested in the optimal budget allocation that minimizes the MSE of the estimator $\hat{\rho}_{M, N}$.

### 2024-03-23 project2/nnMetamodels.tex
new

%======================================================================
\chapter{Cutting Through the Noise: Using Deep Neural Network Metamodels for High Dimensional Nested Simulation}
%======================================================================

\section{Introduction}

Deep neural networks~\citep{hastie2009elements,lecun2015deep} have attracted attentions of researchers and practitioners due to their success in solving real-world supervised learning tasks such as AlphaGo~\citep{silver2016mastering} and ChatGPT~\citep{chatgpt}.
Since the first artificial neural network model~\citep{mcculloch1943logical} and the first algorithm for training a perceptron~\citep{rosenblatt1958perceptron}, especially after the introduction of backpropagation~\citep{rumelhart1985learning} and the growth of high-performance computing, the field of artificial neural network and deep learning in general has grown rapidly.
Two specialized neural network architectures that are relevant to our study are recurrent neural networks (RNNs)~\citep{williams1989learning,sutskever2014sequence} and long-short-term memory (LSTM)~\citep{hochreiter1997long,chung2014empirical}, as we need to train metamodels\footnote{In the field of actuarial science, a metamodel is commonly referred to as a proxy model.} that take sequential observations as input.
Despite their success, deep neural network models are often criticized for their lack of transparency and interpretability, which hinders their adoption in financial and actuarial applications.
Enormous research efforts are spent to test and improve the robustness of deep neural network models with carefully designed noise injection methods.
~\cite{poole2014analyzing} show that injecting synthetic noise before and after hidden unit activations during training improves the performance of autoencoders.
~\cite{neelakantan2015adding} improve learning for deep neural networks by injecting synthetic noise to the gradients during backpropagations.
A branch of research has been devoted to understanding the resilience of neural network models to noise in training labels.
For example,~\cite{luo2016understanding} show that adding synthetic label noise to the convolutional neural network (CNN) can improve its ability to capture global features. 
~\cite{srivastava2014dropout} quantify the error tolerance by injecting synthetic label noise with a custom Boltzmann machine hardware.
~\cite{szegedy2013intriguing} find that neural networks are vulnerable to adversarial examples, and~\cite{goodfellow2014explaining} design an efficient method to generate such noisy examples to exploit the vulnerability to adversarial perturbations.
~\cite{carlini2017towards} design targeted attacks to training labels to test the robustness of neural networks. 
Instead of using synthetic noise, ~\cite{jiang2020beyond} inject real-world label noise and examine noise tolerance of neural networks with controlled noise levels.
The aforementioned studies use real-world data, as is typically the case for many neural network studies, where noise is already present in the training labels before any noise injection.
Users of real-world data have little control over the noise level of the original training labels and usually examine the effect of noisy data by injecting noise, but it is unclear whether a neural network model trained on noisy data actually learns the real, i.e., noiseless, feature-label relationship.
Due to their lack of transparency and interpretability, the adoption of deep neural networks in financial and actuarial applications has been received by regulators with some skepticism.

The contributions of our study are two-fold:
\begin{enumerate}
    \item We study what deep neural networks learn from noisy data by training them using simulated data based on well-designed simulation experiments.
    This is a novel way to study the effect of noisy data and error tolerance of neural network models as one can \textit{reduce noise} in the data by increasing the number of replications in a simulation model.
    This new way of studying neural network models can provide more direct evidence on their transparency and interpretability.  
    \item We propose two generic nested simulation procedures that uses deep neural networks as metamodels to improve its efficiency while maintaining transparency. 
    In essence, a pilot stage simulation is used to generate a large number of noisy data, which are then used to train a metamodel.
    Depending on the application, a trained metamodel can serve two purposes: (1) to identify a set of tail scenarios, and (2) to estimate risk measures directly.
    The first procedure uses a metamodel to identify a set of potential tail scenarios on which computations are performed in the second stage, while the second procedure uses metamodel predictions to estimate risk measures directly.
    Our numerical results show that deep neural network metamodels can identify the tail scenarios accurately and so the proposed procedures can estimate tail risk measures with similar accuracy while, at the same time, using less simulation budget.
\end{enumerate}

We are curious about fundamental questions like ``What do deep neural networks learn from noisy data?'' and ``How well do neural networks learn from noisy data?''.
Data-driven answers to these questions prevail in the existing literature.
In supervised learning, deep neural networks are believed to learn from the given data about the feature-label relationship to predict new labels for unseen features.
Cross validation using to assess a subset, i.e., the validation set, of the original data, is a common way to access the quality of learning.
Generalization error on the test labels is another popular assessment metric.
But the test set is also a subset of the original data.
In this study, we revisit these questions in a simulation context and propose an alternative approach to answer them.
Instead of relying solely on real-data (splitting it into multiple subsets), we propose using stochastic simulation outputs as training labels for deep neural network models.
By controlling the simulation design parameters, such as the number of independent replications, we can control the quality (and also the quantity) of the training labels fed into the neural networks.
In such a controlled environment, we obtain more clear-cut answers to the above fundamental questions.

In nested simulation, a simulation model is used to generate a large number of outer scenarios, and each scenario is then used as an input to another simulation model.
Borrowing terminologies from machine learning research, we can view a set of simulated outer scenarios and the estimated hedging errors for those scenarios as the \textit{features} and (noisy) \textit{labels}.
One can train supervised learning models using these simulated features and labels.
They are then used to replace the time-consuming inner simulations by the trained model.
We refer to the trained supervised learning models as \textit{metamodels} of the inner simulation, which is also known as the \textit{surrogate models}.
Metamodeling is a popular approach to reduce the computational burden of simulation-based applications by replacing the time-consuming simulation with a metamodel.
The metamodel is trained using a set of simulated data, and it is used to predict the simulation output for new inputs.
The study of metamodeling is an active research area in the simulation literature, and using deep neural networks as metamodels is a relatively new development.
~\cite{fonseca2003simulation} provide general guidelines for simulation metamodeling with neural networks,~\cite{lieu2022adaptive} use deep neural networks as metamodels of a simulation model for structural reliability analysis, and~\cite{salle2014efficient} show that neural network metamodels help achieve higher prediction accuracy that other metamodels in approximating agent-based simulation models.
A popular metamodel in nested simulation procedures is stochastic kriging.
~\cite{liu2010stochastic} use stochastic kriging as a metamodel of Monte Carlo simulations to estimate the Conditional Value-at-Risk (CVaR) of a portfolio of derivative securities, and~\cite{gan2015valuation} use stochastic kriging for an efficient valuation of large portfolios of variable annuity (VA) contracts.
Other studies, such as ~\cite{broadie2015risk},~\cite{hong2017kernel}, and~\cite{zhang2022sample} use regression, kernel smoothing, and the likelihood ratio method, respectively.
Our study has three key distinctions over the existing ones:
\begin{enumerate}
    \item  our metamodel has high-dimensional inputs. In machine learning terminology, the features are high-dimensional vectors.
    To estimate the hedging error of a typical VA contract, the number of features is in the order of hundreds, which is at least one order of magnitude larger than the number of features in the aforementioned studies,
    \item  for estimating tail risk measures, our metamodel is only used for tail scenario identification but is \textit{not} used in the estimation of the tail risk measures.
    This is a feature designed particularly to convince regulators that the losses used in estimating the risk measure are based on a transparent inner simulation model rather than on some black-box metamodels, and
    \item  using simulation models as data generators, we can decrease the noise level and get arbitrarily close to the true labels by increasing the number of replications in the simulation model.
    This design allows a systematic study of the effect of noisy training labels on the performance of neural network models in predicting the noiseless labels.
\end{enumerate}

The rest of this article is organized as follows: 
% Section~\ref{sec:problem-formulation} presents the problem settings for tail risk measures and dynamic hedging of VAs. 
% Section~\ref{sec:metamodel2Stage} proposes an efficient two-stage nested simulation procedure that uses deep neural networks as metamodels to help reduce simulation budget by only performing computations on identified tail scenarios. 
% Section~\ref{sec:metamodel1Stage} proposes a one-stage nested simulation procedure that estimates risk measures directly with metamodel predictions.
% Section~\ref{sec:numerical} demonstrates the efficiency of deep learning proxies and examines error tolerance of two LSTM metamodels with different numbers of trainable parameters. 
% Practical suggestions are provided for the choice of suitable metamodels and simulation settings.

\section{Problem Formulation} \label{p2:problem-formulation}

In this section we present notations, problem settings, and a simulation model for risk estimation for hedging errors of variable annuities.
A main goal of the section is to showcase the complexity of the simulation model, which we use as a data generator to train deep neural network metamodels (Section~\ref{sec:metamodel2Stage} and Section~\ref{sec:metamodel1Stage}).
For readers who are interested in the examination of a neural network metamodel, it is sufficient to understand that our simulation model generates data with 240 features and 1 real-value label and our metamodels are generally applicable to any simulation model that generates data with similar characteristics.

\subsection{Tail Risk Measures: VaR and CVaR}
Measuring and monitoring risks, particularly tail risks, are important risk management tasks for financial institutions like banks and insurance companies.
Two most popular tail risk measures are Value-at-Risk (VaR) and Conditional Value-at-Risk (CVaR)~\citep{rockafellar2002conditional}. Other names of CVaR include Conditional Tail Expectation (CTE), Tail Value-at-Risk (TailVaR), and Expected Shortfall (ES).

Consider a loss random variable $L$ whose losses and gains lie in the right and left tails, respectively, of its distribution.
For a given confidence level $\alpha\in [0,1]$, the $\alpha$-VaR is defined as the $\alpha$-quantile of $L$:
$
    \VaR_\alpha = q_\alpha = \inf \left\{ q: \Pr(L\leq q) \geq \alpha \right\}.
$
The $\alpha$-CVaR of $L$ is defined as
$
    \CVaR_\alpha =\frac{1}{1-\alpha} \int_{v=\alpha}^{1} q_v dv.
$
Tail risk measures like VaR and CVaR are widely used for setting regulatory and economic capital, which is the amount of capital a financial institution holds to cover its risk.
For example, European insurers set regulatory capital at $99.5\%$-VaR according to Solvency II~\cite{eiopa2014underlying}.
In Canada, the regulatory capital requirement for VAs is set based on CVaRs as prescribed in~\cite{osfi2017life}.

Let $L_1,L_2,\ldots,L_M$ be $M$ independent and identically distributed (i.i.d.) simulated losses of $L$ and let $L_{(1)}\leq L_{(2)}\leq \ldots\leq L_{(M)}$ be the corresponding ordered losses.
For a given confidence level $\alpha$ (assume that $\alpha M$ is an integer for simplicity), $\alpha$-VaR can be estimated by the sample quantile $\widehat{\VaR}_\alpha = L_{(\alpha M)}$. Also, $\alpha$-CVaR can be estimated by
\begin{equation*}
    \widehat{\CVaR}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}L_{(i)} = \frac{1}{(1-\alpha)M} \sum_{i \in \tail_{(1-\alpha )M}}L_{i},
\end{equation*}
where we define a \textit{true tail scenario set} of size $k$ as $\tail_{k} = \{i: L_i > L_{(M-k)}\}$.
In this study, the loss random variable of interest is the hedging error for VA.

\subsection{Simulation Model for Variable Annuity Payouts}\label{subsec:VApayout}

Variable annuity contracts offer different types of guarantees.
Generally speaking, a portion of the VA premium is invested in a sub-account whose return is linked to some stock indices.

Two relevant types of guarantees in our studies are:
\begin{itemize}[noitemsep]
    \item \textbf{Guaranteed Minimum Maturity Benefit (GMMB)}: A GMMB contract pays a maturity benefit equal to the greater of the sub-account value and a fixed guarantee value.
    The guarantee value is often set as a percentage, e.g., 75\% or 100\%, of the initial premium.

    \item \textbf{Guaranteed Minimum Withdrawal Benefit (GMWB)}: A GMWB contract guarantees the minimum amount of periodic withdrawal the policyholder can take from the sub-account until maturity, even if the sub-account value reduces to zero.
    The minimum withdrawal benefit is typically a fixed percentage of the guarantee value.
    The guarantee value will decrease if the withdrawal exceeds the guaranteed minimum. The GMWB is typically offered with an accumulation period, during which no withdrawals are made but a GMDB is usually offered. Additional features offered with the GMWB include roll-up, ratchet, and reset~\citep{geneva2013variable}.
\end{itemize}
For a comprehensive review of other types of VA contracts such as Guaranteed Minimum Death Benefit (GMDB), Guaranteed Minimum Accumulation Benefit (GMAB) and Guaranteed Lifetime Withdrawal Benefit (GLWB), we refer readers to~\cite{hardy2003investment}.
Next we present a summary of dynamic hedging for VA contracts.
We refer readers to~\cite{dang2021efficient} for detailed modeling of insurer liabilities in different VA contracts and Greek estimation.

Consider a generic VA contract with maturity $T>0$ periods, e.g., $T=240$ months.
Denote the policyholder's (random) time of death by $\tau>0$.
Then the contract expires at $T'=\min\{T,\tau\}$, i.e., the earlier of the contract maturity and the death of the policyholder.
Let $S_t$, $F_t$, and $G_t$ be the indexed stock price, the subaccount value and the guarantee value, respectively, at time $t=1,2,\ldots,T$.
Evolution of the subaccount value and the guarantee value of a VA contract affect the contract payout.
Note that the policyholder's (random) time of death also affects the timing of the benefit payout for certain types of VA such as GMDB, but this is not considered in our study for simplicity.
For clarity, we use $F_t$ and $F_{t_+}$ to denote the sub-account value just before and just after the withdrawal at time $t$, if any.
Let $\eta_g$ be the gross rate of management fee that is deducted from the fund value at each period and let $\eta_n < \eta_g$ be the net rate of management fee income to the insurer.
The difference between the gross management fee and the net management fee income represents the incurred investment expenses.

At the inception of the contract, i.e., $t=0$, we assume that the whole premium is invested in the stock index and the guarantee base is set to the sub-account value:
\begin{equation*}
    S_0=F_0=G_0.
\end{equation*}
At each time $t=1,\ldots,T$, the following events take place in the following order:
\begin{enumerate}
    \item The sub-account value changes according to the growth of the underlying stock and the (gross) management fee is deducted. That is, 
        \begin{equation*}
            F_t = F_{(t-1)_+}\cdot\frac{S_{t}}{S_{t-1}}\cdot(1-\eta_g),
        \end{equation*} 
    where $(x)^+=\max\{x,0\}$ and $F_{(t-1)_+}$ will be defined later. The insurer's income at time $t$ is the net management fee, i.e., $F_t\eta_n$.

    \item The guarantee value ratchets up (ratcheting is a common feature in GMWB) if the sub-account value exceeds the previous guarantee value, i.e., 
        \begin{equation*}
            G_t = \max\{G_{t-1},F_t\}.
        \end{equation*}

    \item The withdrawal is made (for GMWB) and is deducted from the sub-account value, i.e., 
        \begin{equation*}
            F_{t_+} = (F_t - I_t)^+,
        \end{equation*} 
    where $I_t = \gamma G_t$. A GMMB can be modeled with $\gamma = 0$.
\end{enumerate}

We see from the above modeling steps that the status of a generic VA contract is summarized by a triplet $(S_t,F_t,G_t)$ whose evolution is driven by the stochasticity of $S_t$.
In practice, the simulation model may also incorporate additional complications like mortality, lapse, and excess withdrawal, etc.

At any time $t=1,\ldots,T$, the insurer's liability in a VA contract is the present value of all payments, net of the fee income.
For example, suppose that the per-period risk-free rate is $r$, then
the insurer's time-$t$ liability for a GMMB contract is $V_t = e^{-r(T-t)}\cdot (G_T - F_T)^+ - \sum_{s=t+1}^{T} e^{-r(T-s)} F_s \eta_n$.
Also, the insurer's time-$t$ liability for a GMWB contract is $V_t = \sum_{s=t+1}^{T} e^{-r(T-s)} [(I_s - F_s)^+- \eta_n F_s] $.

For example, consider the time-$t$ liability $V_t$ of a GMWB:
Suppose that given the stock sample path, e.g., an outer path $S_1,\ldots,S_t$, one can simulate future stock prices $\Stilde_{t+1},\ldots,\Stilde_{T}$, e.g., inner sample paths, based on some asset model such as a Black-Scholes model.
The tilde symbol ($\sim$) over a quantity denotes its association with the inner simulation.
Given the time~$t$ state $(S_t,F_t,G_t)$, following~\cite{cathcart2015calculating} the sensitivity of $V_t$ with respect to $S_t$ can be estimated by a pathwise estimator~\citep{glasserman2004monte}:
\begin{equation}\label{eq:delta}
    \Delta_t(\Stilde_{t+1},\ldots,\Stilde_{T} | S_t) = \frac{\partial V_t}{\partial S_t} = \sum_{s=t+1}^{T} e^{-r(T-s)} \left[\bm{1}\{\Itilde_s > \Ftilde_s\}\cdot \left( \frac{\partial \Itilde_s}{ \partial S_t} - \frac{\partial \Ftilde_s}{ \partial S_t}\right)- \eta_n \frac{\partial \Ftilde_s}{ \partial S_t}\right], \quad t=0,\ldots,T-1,
\end{equation}
where $\bm{1}\{\cdot\}$ is an indicator function and
\begin{align*}
    \frac{\partial \Ftilde_s}{ \partial S_t} &= \bm{1}\{\Itilde_{s-1} < \Ftilde_{s-1}\}\cdot\left( \frac{\partial \Ftilde_{s-1}}{ \partial S_t} - \frac{\partial \Itilde_{s-1}}{ \partial S_t}\right) \cdot \frac{\Stilde_s}{\Stilde_{s-1}}\cdot (1-\eta_g),\\
    \frac{\partial \Gtilde_s}{ \partial S_t} &= \bm{1}\{\Gtilde_{s-1} < \Ftilde_{s}\}\cdot\frac{\partial \Ftilde_{s}}{ \partial S_t} + \bm{1}\{\Gtilde_{s-1} \geq \Ftilde_{s}\}\cdot\frac{\partial \Gtilde_{s-1}}{ \partial S_t},\\
    \frac{\partial \Itilde_s}{ \partial S_t} &= \gamma \frac{\partial \Gtilde_s}{ \partial S_t}.
\end{align*}
The recursion is initialized with $(\Stilde_t,\Ftilde_t,\Gtilde_t) = (S_t,F_t,G_t)$, $\frac{\partial \Ftilde_s}{ \partial S_t} = \frac{\Ftilde_t}{S_t}$, and $\frac{\partial \Gtilde_s}{ \partial S_t} = \frac{\partial \Itilde_s}{ \partial S_t} = 0$.

\subsection{Dynamic Hedging for Variable Annuities}\label{subsec:dynamicHedge}

Below we provide a scheme used to perform a multi-period nested simulation in estimating (profit and loss) P\&L for one outer scenario.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.85\textwidth]{./project2/figures/sns.pdf}
    \caption{Illustration of multi-period nested simulation that estimates the P\&L for one outer scenario.}
    \label{fig:illustration}
\end{figure}

Insurers commonly use dynamic hedging to mitigate a market risk exposure in VA contract's embedded options.
In a dynamic hedging program, a hedge portfolio is set up and periodically rebalanced for a portfolio of VA contracts using stocks, bonds, futures, and other derivatives.
For simplicity, in this study we consider delta hedging for a generic VA liability using one stock and one bond.
The metamodeling procedures in Section~\ref{sec:metamodel2Stage} and Section~\ref{sec:metamodel1Stage} can be trivially adapted to more general hedging strategies.

Consider a generic VA contract whose delta hedge portfolio at any time~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at time $T$.
The value of the hedge portfolio at time~$(t-1)$ is:
\begin{equation*}
    H_{t-1} = \Delta_{t-1} S_{t-1} + B_{t-1},
\end{equation*}
where $S_t$ is the underlying stock price and any time $t>0$.
This hedge portfolio is brought forward to the next rebalancing time~$t$, when its value becomes:
\begin{equation*}
    H_{t}^{bf} = \Delta_{t-1} S_{t} + B_{t-1}e^{r}.
\end{equation*}
Therefore, the time~$t$ hedging error, i.e., the cash flow incurred by the insurer due to rebalancing at time~$t$, is
\begin{equation}\label{eq:hedgingerror}
    HE_t = H_t - H^{bf}_t, \quad t=1,\ldots, T-1.
\end{equation}
The P\&L of the VA contract includes the cost of the initial hedge ($H_0$), the hedging errors~\eqref{eq:hedgingerror}, the unwinding of the hedge at maturity ($H^{bf}_T$), and the unhedged liability ($V_0$).
Mathematically, the present value of these cash flows is given by
\begin{equation}\label{eq:lossrv}
L = H_0 + \sum_{t=1}^{T-1} e^{-rt} HE_t - e^{-rT} H^{bf}_T + V_0 = \sum_{t=0}^{T-1}\Delta_t (e^{-rt}S_t - e^{-r(t+1)}S_{t+1}) + V_0,
\end{equation}
where the second equality holds by a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$.

In~\eqref{eq:lossrv}, $\Delta_t$ and $V_0$ are determined by using a risk-neutral measure $\mathbb{Q}$ while the distribution of $L$ is under a real-world measure $\mathbb{P}$.
If $\Delta_t$ and $V_0$ cannot be calculated analytically, a nested simulation is required to estimate the tail risk measure of $L$.
Recall from Section~\ref{subsec:VApayout} that the stock sample path, regardless of the inner or outer simulation or a combination of both, determines the evolution of the triplet $(S_t,F_t,G_t)$.
Specifically, the outer scenarios $\bS^{(i)} = (S_{1}^{(i)},\ldots,S_{T}^{(i)})$, $i=1,\ldots,M$ are generated under $\mathbb{P}$.
At each time~$t=1,\ldots,T-1$ of a given outer scenario $\bS^{(i)}$, inner sample paths $\bStilde_{t}^{(j)} = (\Stilde_{t+1}^{(j)},\ldots,\Stilde_{T}^{(j)})$, $j=1,\ldots,N$ are generated under $\mathbb{Q}$ to estimate $\Delta_t^{(i)}$, $i=1,\ldots,M$.
Also, $V_0^{(i)}$, $i=1,\ldots,M$ are estimated under $\mathbb{Q}$ via inner simulations at time $0$.
Recall from Section~\ref{subsec:VApayout} that the stock's sample path, regardless of inner or outer simulation or a combination of both, determines the evolution of the triplet $(S_t,F_t,G_t)$.
For GMWB, a standard nested simulation procedure to estimate the $\alpha$-CVaR of $L$ is described in Algorithm~\ref{alg:standardProcedure}.

% For example, for GMWB, a standard nested simulation procedure to estimate the $\alpha$-CVaR of $L$ is as follows:
% \begin{enumerate}
%     \item For $i=1,\ldots,M$, simulate outer scenarios $\bS^{(i)} = (S_{1}^{(i)},\ldots,S_{T}^{(i)})$ under the real-world measure $\mathbb{P}$.
%     Figure~\ref{fig:illustration} illustrates the inner simulation experiments needed for an outer scenario.

%     \item For $t=0$, simulate time-$0$ inner paths $\bStilde_{0}^{(j)} = (\Stilde_{1}^{(j)},\Stilde_{2}^{(j)},\ldots,\Stilde_{T}^{(j)})$, $j=1,\ldots,N$ under $\mathbb{Q}$ {and} then estimate $V_0$ by $\Vhat_0 = \sum_{s=1}^{T} e^{-r(T-s)} [(I_s - F_s)^+- \eta_n F_s]$ and estimate $\Deltahat_0 = \Delta_0(\Stilde_{1}^{(j)},\ldots,\Stilde_{T}^{(j)} | S_0)$ based on~\eqref{eq:delta}.
%     Note that $S_0$ is known, so these inner paths do not depend on any outer scenario.
%     The same $\Vhat_0$ and $\Deltahat_0$ are used in all scenarios.

%     \item Given each scenario $\bS^{(i)}$, the following inner simulation is needed to estimate the corresponding loss $\Lhat_i$ for that scenario.
%     \begin{enumerate}
%         \item At each time~$t=1,\ldots,T-1$, simulate inner paths $\bStilde_{t}^{(ij)} = (\Stilde_{t+1}^{(ij)},\ldots,\Stilde_{T}^{(ij)})$, $j=1,\ldots,N$ under $\mathbb{Q}$ {and} then estimate $\Delta_t$ by $\Deltahat_t^{(i)} = \Delta_t(\Stilde_{t+1}^{(ij)},\ldots,\Stilde_{T}^{(ij)} | \bm{S}_t^{(i)})$ based on~\eqref{eq:delta}.

%         \item Use scenarios $\bS^{(i)}$ and $\Vhat_0$ and $\Deltahat_t^{(i)}$ to calculate losses $\Lhat_i^{MC}$, $t=0,\ldots,T-1$, based on~\eqref{eq:lossrv}. Then sort them as $\Lhat^{MC}_{(1)}\leq \Lhat^{MC}_{(2)} \leq \cdots\leq \Lhat^{MC}_{(M)}$.
%     \end{enumerate}

%     \item Estimate $\alpha$-CVaR of $L$ by $\widehat{\CVaR}^{MC}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}\Lhat_{(i)}^{MC} = \frac{1}{(1-\alpha)M} \sum_{i \in \widehat{\tail}_{(1-\alpha )M}^{MC}}\Lhat_{i}^{MC}$
%     where $\widehat{\tail}_{k}^{MC}$ denotes a \textit{Monte Carlo tail scenario set} associated with the largest $k$ estimated losses.
% \end{enumerate}

\begin{algorithm} 
\caption{Standard Nested Simulation Procedure for Estimating CVaR for GMWB Hedging Losses}
\begin{algorithmic}[1] \label{alg:standardProcedure}
    \STATE  For $i=1,\ldots,M$, simulate outer scenarios $\bS^{(i)} = (S_{1}^{(i)},\ldots,S_{T}^{(i)})$ under the real-world measure $\mathbb{P}$.
    \STATE  For $t=0$, simulate time-$0$ inner paths $\bStilde_{0}^{(j)} = (\Stilde_{1}^{(j)},\Stilde_{2}^{(j)},\ldots,\Stilde_{T}^{(j)})$, $j=1,\ldots,N$ under $\mathbb{Q}$, then estimate $V_0$ by $\Vhat_0 = \sum_{s=1}^{T} e^{-r(T-s)} [(I_s - F_s)^+- \eta_n F_s]$ and $\Deltahat_0 = \Delta_0(\Stilde_{1}^{(j)},\ldots,\Stilde_{T}^{(j)} | S_0)$.
    \STATE  Given each scenario $\bS^{(i)}$:
    \begin{enumerate}[label=\alph*., itemsep=0pt, parsep=0pt, topsep=0pt]
        \item   At each time~$t=1,\ldots,T-1$, simulate inner paths $\bStilde_{t}^{(ij)} = (\Stilde_{t+1}^{(ij)},\ldots,\Stilde_{T}^{(ij)})$, $j=1,\ldots,N$ under $\mathbb{Q}$, then estimate $\Delta_t$ by $\Deltahat_t^{(i)} = \Delta_t(\Stilde_{t+1}^{(ij)},\ldots,\Stilde_{T}^{(ij)} | \bm{S}_t^{(i)})$.
        \item   Use scenarios $\bS^{(i)}$ and $\Vhat_0$ and $\Deltahat_t^{(i)}$ to calculate losses $\Lhat_i^{MC}$, $t=0,\ldots,T-1$, then sort them as $\Lhat^{MC}_{(1)}\leq \Lhat^{MC}_{(2)} \leq \cdots\leq \Lhat^{MC}_{(M)}$.
    \end{enumerate}
    \STATE  Estimate $\alpha$-CVaR of $L$ by $\widehat{\CVaR}^{MC}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}\Lhat_{(i)}^{MC} = \frac{1}{(1-\alpha)M} \sum_{i \in \widehat{\tail}_{(1-\alpha )M}^{MC}}\Lhat_{i}^{MC}$.
\end{algorithmic}
\end{algorithm}

We refer to the collection of experiments needed conditional on one scenario $\bS^{(i)}$ to estimate $L_i$, that is, all upward arrows in Figure~\ref{fig:illustration}, as one inner simulation experiment.
We make four observations:
\begin{itemize}
    \item   each inner simulation is time-consuming, as it includes $T$ simulation experiments, one at each time $t=0,\ldots,T-1$,
    \item   after running inner simulations for $M$ scenarios, we obtain simulated data, that is, feature-label pairs, $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$; the feature vector $\bS$ is $T$ dimensional,
    \item   $\Lhat_i^{MC}$ is a standard Monte Carlo estimator of the true loss for scenario $\bS^{(i)}$. It is an unbiased estimator and its variance is inversely proportional to the number of inner replications $N$. 
    As $N$ approaches infinity, $\Lhat_i^{MC}$ converges to the true loss $L_i$, and
    \item   most importantly, when estimating tail risk measures such as $\alpha$-CVaR, only a small number of estimated losses, that is, those associated with the set of tail scenarios $\widehat{\tail}_{k}$ are used in the estimator.
\end{itemize}

\section{Two-Stage Nested Simulation with Metamodels} \label{sec:metamodel2Stage}

Based on the three observations above and inspired by~\cite{dang2020efficient}, we propose a two-stage nested simulation procedure which uses a deep neural network metamodel to identify potential tail scenarios.
We present our proposed procedure as a competitor to the standard procedure with $M$ outer scenarios and $N$ inner replications for each outer scenario, as described in Section~\ref{subsec:dynamicHedge}.
We propose a two-stage procedure with a neural network metamodel that aims to produce a CVaR estimate that's as accurate as that of the standard procedure, but uses fewer computations as than latter.

% \begin{itemize}
%     \item[I.] \textbf{Train a neural network metamodel using simulation data.}
%     \begin{itemize}[leftmargin=0pt]
%         \item Use a fraction of the total simulation budget to run Steps 1, 2, and 3 in the standard procedure with the same number of outer scenarios, $M$, but a much smaller number of inner replications, i.e., $N'\ll N$, in each scenario.
%         Then obtain $M$ simulated samples, i.e., feature-label pairs, $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$.
%         Note that $N'$ may be 10 times or even 100 times smaller than $N$, so the loss estimates $\Lhat_i$ are expected to have larger variance, i.e., more noisy, than the standard procedure's loss estimates.

%         \item Use the simulated data, $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$ to train a neural network.
%         We refer to the trained model as a \textit{metamodel} as denote it by $\Lhat^{PD}(\bS)$.
%         Denote the predicted losses for the outer scenarios by $\Lhat^{PD}_i = \Lhat^{PD}(\bS^{(i)})$, $i=1,\ldots,M$.

%         \item Sort the predicted losses $\Lhat^{PD}_{(1)}\leq \Lhat^{PD}_{(2)} \leq \cdots\leq \Lhat^{PD}_{(M)}$ to identify a \textit{predicted tail scenario set} associated with the largest predicted losses, i.e., $\widehat{\tail}_{m}^{PD}:=\{i: \Lhat^{PD}_i > \Lhat^{PD}_{(M-m)}\}$.
%         The number of predicted tail scenarios, $m$, is a user's choice and will be discussed later.
%     \end{itemize}
%         \item[II.] \textbf{Concentrate simulation on predicted tail scenarios.}
%         \begin{itemize}[leftmargin=0pt]

%         \item Run Steps 2 and 3 of the standard procedure with the same number of inner replications, $N$, but only on the predicted tail scenarios, i.e., scenarios associated with $\widehat{\tail}_{m}^{PD}$.
%         Denote the standard procedure's estimated losses and sorted losses by $\Lhat^{ML}_i$ and $\Lhat^{ML}_{(i)}$, respectively, $i=1,\ldots,m$.

%         \item Estimate the $\alpha$-CVaR of $L$ by $\widehat{\CVaR}^{ML}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}\Lhat_{(i)}^{ML} = \frac{1}{(1-\alpha)M} \sum_{i \in \widehat{\tail}_{(1-\alpha )M}^{ML}}\Lhat_{i}^{ML}$
%         where $\widehat{\tail}_{k}^{ML}$ denotes a \textit{predicted tail scenario set} associated with the largest $k$ estimated losses.
%     \end{itemize}
%     \end{itemize}

\begin{algorithm}
\caption{Two-Stage Metamodeling Nested Simulation Procedure for Estimating CVaR}
\begin{algorithmic}[1] \label{alg:twoStageProcedure}
    \STATE \textbf{Train a neural network metamodel using simulation data:}
    \begin{enumerate} [label=\alph*., itemsep=0pt, parsep=0pt, topsep=0pt]
        \item Use a fraction of the total simulation budget to run Steps 1, 2, and 3 in the standard procedure, i.e., Algorithm~\ref{alg:standardProcedure}, with the same number of outer scenarios, $M$, but a much smaller number of inner replications, $N' \ll N$, in each scenario. Obtain $M$ simulated samples (feature-label pairs), $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$. Note that $N'$ may be much smaller than $N$, so $\Lhat_i$ are expected to have larger variance.
        \item Use the simulated data, $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$ to train a neural network. Refer to the trained model as a metamodel and denote it by $\Lhat^{PD}(\bS)$. Denote the predicted losses for the outer scenarios by $\Lhat^{PD}_i = \Lhat^{PD}(\bS^{(i)})$, $i=1,\ldots,M$.
        \item Sort the predicted losses $\Lhat^{PD}_{(1)}\leq \Lhat^{PD}_{(2)} \leq \cdots\leq \Lhat^{PD}_{(M)}$ to identify a predicted tail scenario set, $\widehat{\tail}_{m}^{PD}$, associated with the largest predicted losses. The number of predicted tail scenarios, $m$, is a user's choice.
    \end{enumerate}
    \STATE \textbf{Concentrate simulation on predicted tail scenarios:}
    \begin{enumerate} [label=\alph*., itemsep=0pt, parsep=0pt, topsep=0pt]
        \item Run Steps 2 and 3 of Algorithm~\ref{alg:standardProcedure} with the same number of inner replications, $N$, but only on the predicted tail scenarios, i.e., scenarios in $\widehat{\tail}_{m}^{PD}$. Denote the standard procedure's estimated losses and sorted losses by $\Lhat^{ML}_i$ and $\Lhat^{ML}_{(i)}$, respectively, $i=1,\ldots,m$.
        \item Estimate the $\alpha$-CVaR of $L$ by $\widehat{\CVaR}^{ML}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}\Lhat_{(i)}^{ML} = \frac{1}{(1-\alpha)M} \sum_{i \in \widehat{\tail}_{(1-\alpha )M}^{ML}}\Lhat_{i}^{ML}$, where $\widehat{\tail}_{k}^{ML}$ denotes a predicted tail scenario set associated with the largest $k$ estimated losses.
    \end{enumerate}
\end{algorithmic}
\end{algorithm}

Similar to~\cite{dang2020efficient}, the proposed two-stage procedure in Algorithm ~\ref{alg:twoStageProcedure} uses the metamodel predictions to identify the predicted tail scenario set in Stage 1.
However, different from their fixed-budget simulation design, we attempt to achieve a target accuracy.
Specifically, in Stage 2 we propose using a standard procedure with the same number of inner replications, $N$, as a competing simulation procedure (or a benchmark).
There are two different experiment designs for nested simulation procedures: fixed-budget design and fixed-accuracy design.
In a fixed-budget design, the simulation budget is fixed and the goal is to achieve the highest accuracy possible within the budget.
Let $\Gamma = MN$ be the simulation budget for the standard procedure, where each scenario receives $\frac{\Gamma}{M}$ inner replications.
In the proposed two-stage procedure, suppose Stage 2 uses 1\% of the simulation budget, $\alpha = 95\%$, and $m=(1-\alpha)M$, then $99\%$ of the simulation budget is concentrated on $5\% M$ predicted tail scenarios in Stage 2.
In other words, each predicted tail scenario receives $\frac{99\% \Gamma}{5\% M}$ inner replications, almost 20 times more than that in the standard procedure.
This budget concentration is expected to improve the estimation accuracy of the two-stage procedure compared to a standard procedure with the same budget. 
If the metamodel is accurate in predicting true tail scenarios, then the two-stage procedure is expected to achieve higher accuracy than the standard procedure with the same budget.
However, we believe that the goal of designing an efficient simulation procedure is to solve practical problems faster, so a target-accuracy design is more suitable, which refers to obtaining a similar level of accuracy as the standard procedure but with much less simulation budget.
One other reason for this fixed-accuracy design is to investigate whether deep neural network metamodels trained with much noisier labels can identify true tail scenarios with similar accuracy as the standard procedure.
The size of the predicted tail scenario set in Stage 1, $m$, is an important experiment design parameter that affects the correct identification of true tail scenarios and ultimately affects the estimation accuracy for CVaR.
Clearly, there is a lower bound $m \geq (1-\alpha)M$ because the $\alpha$-CVaR is estimated by the average of $(1-\alpha)M$ largest losses at the end of Stage 2.
For ease of reference, we call the additional percentage of predicted tail scenarios above this lower bound, i.e., $\epsilon = \frac{m - (1-\alpha)M}{M}$, as a \textit{safety margin}.
On one hand, large $\epsilon$ is not desirable because it increases computations in Stage 2.
On the other hand, $\epsilon$ should be set reasonably large so more true tail scenarios are included in the the predicted tail scenario set $\widehat{\tail}_{m}^{PD}$ and are ultimately included in $\widehat{\tail}_{(1-\alpha )M}$ at the end of Stage 2.
The selection of $m$ is highly dependent on the choice of the metamodel.
Due to the simulation errors and approximation error in the metamodel in Stage 1, we do not expect perfect match between the true tail scenario set $\tail_{k}$ and the predicted tail scenario set $\widehat{\tail}_{k}^{PD}$ for any size $k$.
This means that we should not set $m$ at its lower bound: Some safety margin $\epsilon M$ should be added to the predicted tail scenario set, i.e., $m = (1-\alpha )M + \epsilon M$, to increase the likelihood that $\tail_{k} \subseteq \widehat{\tail}_{m}^{PD}$ and that the true tail scenarios are included in estimating $\alpha$-CVaR at the end of Stage 2.
The choice of safety margin $\epsilon$ is not trivial, and it should be set based on the metamodel's accuracy in identifying true tail scenarios.
In the numerical experiments, we examine the relationship between the safety margin and the correct identification of true tail scenarios for different metamodels.

\section{Single-Stage Nested Simulation with Neural Network Metamodels} \label{sec:metamodel1Stage}

In our exploratory experiment with the two-stage procedure, we observe that a suitable metamodel trained with noisy labels is accurate enough to identify true tail scenarios with a relatively small safety margin.
This observation motivates us to propose a single-stage procedure that uses the identical neural network metamodel, not for the purpose of differentiating between tail and non-tail scenarios, but rater to estimate the CVaR directly using the predicted losses.

\begin{algorithm}
\caption{Single-Stage Metamodeling Nested Simulation Procedure for Estimating CVaR}
\begin{algorithmic}[1] \label{alg:oneStageProcedure}
    \STATE Run Step 1 of Algorithm~\ref{alg:twoStageProcedure}, and denote the predicted losses by
    $\Lhat^{PD}_i = \Lhat^{PD}(\bS^{(i)})$, $i=1,\ldots,M$.
    \STATE Sort the predicted losses $\Lhat^{PD}_{(1)}\leq \Lhat^{PD}_{(2)} \leq \cdots\leq \Lhat^{PD}_{(M)}$ to identify the largest predicted losses. 
    \STATE Directly estimate the risk measure (e.g., $\alpha$-CVaR) of $L$ using the metamodel predictions: Calculate $\widehat{\CVaR}^{PD}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}\Lhat^{PD}_{(i)}$.
\end{algorithmic}
\end{algorithm}

The single-stage procedure has three major advantages over the two-stage procedure:
(1) the single-stage procedure is expected to be more efficient than the two-stage procedure because it does not require the running the standard procedure in Stage 2, 
(2) the safety margin $\epsilon$ is not needed in the single-stage procedure, and
(3) most importantly, the single-stage procedure is not limited to just estimating tail risk measures and can be extended to provide a broader assessment of risk. 
It can be naturally adapted to estimate risk measures that require the knowing of the entire loss distribution, such as the standard deviation or the squared tracking error.
In our numerical experiments, we will compare the single-stage procedure to the two-stage procedure and the standard procedure in estimating the $\alpha$-CVaR of the hedging losses for GMWB, and we will also examine the single-stage procedure's performance in estimating the standard deviation of the hedging losses.

\section{Numerical Results} \label{sec:numerical}

We conduct a series of simulation experiments to (1) demonstrate the efficiency of the proposed metamodeling procedures and (2) examine the error tolerance to noisy training data in deep learning models.
The problem settings in our experiments are identical to those in~\cite{dang2020efficient}:
we consider estimating the $95\%$ CVaR of the hedging loss of a GMWB contract, which is one of the most complex VA contracts in the market.
The VA contracts have a 20-year maturity and are delta-hedged with monthly rebalancing, i.e., $T=240$ rebalancing periods.
The gross and net management fees are $\eta_g = 0.2\%$ and $\eta_n=0.1\%$, respectively.
The withdrawal rate for GMWB is $0.375\%$ per month.
% To make our examples more realistic, the VAs are also subject to dynamic lapse as specified in Section~4.3 of~\cite{dang2020efficient}.
The risk-free rate is 0.2\% per period and the underlying asset $S_t$ is modeled by a regime-switching geometric Brownian motion with parameters specified in Table~2 of~\cite{dang2020efficient}.

To compare the numerical performances of different simulation procedures, we create a benchmark dataset with a large-scale nested simulation: We first simulate $M=100\!,\!000$ outer scenarios, i.e., $240$-periods stock paths $\bS^{(1)},\ldots,\bS^{(M)}$ under $\mathbb{P}$ and used these outer scenarios in all further experiments.
Note that the 5\% tail scenario set includes $5\!,\!000$ scenarios.
As the hedging losses for these scenarios cannot be calculated analytically, we run inner simulations with a large number of replications, $N=100\!,\!000$, conditional on each of the $M$ scenarios.
We denote these losses by $L_1,\ldots,L_M$ and will refer to them as \textit{true losses}.
We also use these true losses to estimate $\widehat{\CVaR}_{95\%}$ and denote the corresponding \textit{true tail scenario set} by $\tail_{5000}$.
Lastly, we refer to the set of feature-label pairs $\{(\bS^{(i)}, L_i): i=1,\ldots,M\}$ as a \textit{true dataset}.
Note that the feature vector $\bS$ is a 240-dimension stock path.

We compare our two-stage procedure to a standard nested simulation procedure that runs $N=1\!,\!000$ inner replications for each of the $M=100\!,\!000$ outer scenarios.
In Stage 1 of the proposed procedure, we first run inner simulations with $N'=100$ inner replications for each of the $M=100\!,\!000$ outer scenarios.
So, Stage 1's simulation budget is $10\%$ of the standard procedure's.
The resulting feature-label pairs $\{(\bS^{(i)}, \Lhat_i): i=1,\ldots,M\}$ is used for training different  metamodels.
Specifically, following the convention in machine learning research, we split this dataset into three parts: The training, validation, and test sets have $90\!,\!000$, $5\!,\!000$, and $5\!,\!000$ data points (90\%, 5\%, and 5\% of the dataset), respectively.
At the end of Stage 1, $m$ predicted tail scenarios, are identified by the trained metamodels.
In Stage 2, $N=1\!,\!000$ inner replications are run for all predicted tail scenarios.
Stage 2's simulation budget is $\frac{m}{M}$ of the standard procedure's.
In short, the two-stage procedure uses $15\% - 30\%$ of the standard procedure's budget for a safety margin between $0\% - 15\%$.

Five metamodels are considered in this experiment: multiple linear regression (MLR), quadratic polynomial regression (QPR) without interaction terms, feed-forward neural network (FNN), recurrent neural network (RNN), and long short-term memory (LSTM) network.
MLR and QPR are considered as extensions of regression metamodels in the nested simulation literature.
FNN is a generic neural network while RNN and LSTM are specialized models to accommodate the sequential structure of our time-series features.
A $\tanh$ activation function is used for RNN and LSTM layers, and a Rectified Linear Unit (ReLU) activation function is used for the fully-connected layers.
All neural network metamodels are trained by the Adam optimizer~\citep{kingma2014adam} with an initial learning rate of $0.001$ and an exponential learning rate decay schedule.
FNN is trained with a dropout rate of 20\%.
RNN and LSTM are trained with a dropout rate of 10\%.
The architectures and training settings are typical choices in the deep learning literature.
The training labels are normalized to have zero mean and unit standard deviation.
The architectures and the numbers of trainable parameters are shown in the first two columns of Table~\ref{tab:gmwb_arch}.
We see that the three deep neural network metamodels' have orders of magnitudes more trainable parameters than the two regression models.
In machine-learning terminologies, the three deep neural network models have much higher \textit{model capacities}.

\begin{table}[ht!]
    \small
    \centering
    \begin{tabular}{lccccc}
    \toprule
    \textbf{Model} & \textbf{\makecell{Layer size}} & \textbf{\makecell{\# parameters}} & \textbf{Training error} & \textbf{Test error} & \textbf{True error}\\
    \midrule
    MLR & N/A & $241$ & $0.707 (\pm 0.000)$ & $0.877 (\pm 0.001)$ & $0.694 (\pm 0.000)$ \\
    QPR & N/A & $481$ & $0.544 (\pm 0.000)$ & $0.636 (\pm 0.001)$ & $0.531 (\pm 0.000)$ \\
    FNN & $240, 128, 16$ & $35\!,\!009$ & $0.118 (\pm 0.001)$ & $0.247 (\pm 0.002)$ & $0.113 (\pm 0.001)$ \\
    RNN & $(240, 32), (240, 4), 32$ & $32\!,\!021$ & $0.132 (\pm 0.008)$ & $0.137 (\pm 0.008)$ & $0.119 (\pm 0.008)$ \\
    LSTM & $(240, 32), (240, 4), 32$ & $35\!,\!729$ & $0.075 (\pm 0.004)$ & $0.079 (\pm 0.005)$ & $0.063 (\pm 0.004)$ \\
    RNN$^*$\footnotemark & $(240, 32), (240, 4), 32$ & $32\!,\!021$ & $0.109 (\pm 0.005)$ & $0.128 (\pm 0.005)$ & $0.109 (\pm 0.005)$ \\
    \bottomrule
    \end{tabular}
    \caption{Architectures and MSEs of metamodels for GMWB inner simulation model.}
    \label{tab:gmwb_arch}
\end{table}

\footnotetext{Results of the well-trained RNN, where the ones suffers from the vanishing gradient issue are removed from the averages.}

For each metamodel, 50 independent macro replications are run\footnote{Each macro replication includes simulating a noisy dataset, separating it into training and test data, fitting a metamodel, and making predictions}.
The last three columns in Table~\ref{tab:gmwb_arch} display the average squared errors between the predicted losses and the losses (labels) in different datasets.
The half lengths of their 95\% confidence interval of these quantities are also reported in parentheses.
We first observe that the two regression metamodels' errors are larger than those of three deep neural network models.
This is because model capacities of the regression metamodels are too low to learn the complex dynamic hedging simulation model.
There are also differences among the three deep neural neetwork models.
The FNN is a generic neural network, its test error is larger than the training error, which is a sign of over-fitting and poor generalization.
In contrast, RNN and LSTM networks have recurrent strucutures and are designed to capture temporal relationship in the high-dimensional feature.
As a result, they have lower training errors, i.e., they fit the data better, and have lower testing error, i.e., they generalize better.
Notably, the true errors for the deep neural network metamodels are lower than the test errors.
Comparing the two metamodels with recurrent structures, A LSTM network overcomes two key drawbacks of a crude RNN.
\begin{enumerate}
    \item It avoids the vanishing gradient problem during training, which makes the LSTM easier to than the RNN. Figure~\ref{fig:QQ_RNN} shows the quantile-quantile (QQ) plots between the \textbf{training} labels and the RNN predictions for two macro replications, where training of the latter is hindered by the vanishing gradient problem\footnote{A well-trained RNN stops early at around 300 training epochs, while an ill-trained RNN uses up all 1000 training epochs.}. As a result, the half length of the 95\% confidence interval of the RNN's training error is much larger than all other metamodels. The last row of Table~\ref{tab:gmwb_arch} shows the average squared errors of the good RNN metamodels that are successfully trained. Removing the RNN metamodels that are ill-trained, the average squared errors of the RNN metamodels are lower than those of the FNN, but the half lengths of their 95\% confidence intervals are larger than those of the FNN. This suggests that the RNN is more sensitive to noise in stochastic gradient descent than the FNN.
    \item A LSTM introduces three gates that regulate the flow of information. These gates decide what information should be kept or discarded. This makes a LSTM more capcable of learning long-term dependencies. Since the feature in our dynamic hedging problem is a 240-dimensional time series, a LSTM is more suitable than a crude RNN.
\end{enumerate}

\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{./project2/figures/qqPlots/rnnGood.png}
        \caption{A good RNN metamodel}
    \end{subfigure}\hfill
    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{./project2/figures/qqPlots/rnnBad.png}
        \caption{A bad RNN metamodel}
        \label{subfig:badRNN}
    \end{subfigure}
    \caption{QQ-plots between true labels (x-axis) and predicted losses (y-axis) for the RNN metamodel.} 
    \label{fig:QQ_RNN}
\end{figure}

Recall that all three data sets are generated from the same simulation model, but the true data set is less noisy than the training and test data.
Part of the training error is due to simulation noise, and this noise is lower in the true error.
We observe that the two regression metamodels not only generalize to the test data poorly but also generalize to the true data poorly.
In contrast, the deep neural network metamodels generalize better to the true data than to the test data.
Figure~\ref{fig:QQ_REG} and Figure~\ref{fig:QQ_NN} shows the QQ plots between the \textbf{true} labels and the predicted losses for the regression metamodels and the neural network metamodels, respectively.

\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{./project2/figures/qqPlots/mlrLN.png}
        \caption{MLR metamodel}
    \end{subfigure}\hfill
    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{./project2/figures/qqPlots/qprLN.png}
        \caption{QPR metamodel}
    \end{subfigure}
    \caption{QQ-plots between true losses (x-axis) and predicted losses (y-axis) for regression metamodels.} 
    \label{fig:QQ_REG}
\end{figure}

Compared with the MSE table in Table~\ref{tab:gmwb_arch} that summarizes the overall fit, QQ plots offer a close look at the metamodels' performance on different parts of the loss distribution.
Figure~\ref{fig:QQ_REG} show that the regression metamodels' predictions are far from the true losses, especially on the tails.
Between the two regression metamodels, the QPR metamodel has a slightly better fit for larger losses.
Nevertheless, both regression metamodels have poor fits to the true data, and their fit on the tail is particularly undesirable.
The poor fit on the tail hinders the regression metamodels' ability to identify true tail scenarios and ultimately leads to poor CVaR estimates.
Adding the quadratic terms, our QPR metamodel is considered as a natural extension of the MLR.
Attempts to further improve the regression metamodels by adding interaction terms or higher-order terms do not improve the fit.
Having 240 features, feature engineering for regression metamodels is not a trivial task and is highly dependent on the simulation model. 
As a result, the regression metamodels are not flexible enough to capture the complex feature-label relationship in the dynamic hedging simulation model.

\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{./project2/figures/qqPlots/fnnLN.png}
        \caption{FNN metamodel}
    \end{subfigure}\hfill
    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{./project2/figures/qqPlots/lstmLoCapLN.png}
        \caption{LSTM metamodel}
    \end{subfigure}
    \caption{QQ-plots between true losses (x-axis) and predicted losses (y-axis) for neural network metamodels.} 
    \label{fig:QQ_NN}
\end{figure}

In Figure~\ref{fig:QQ_NN}, we illustrate the fit of the neural network metamodels.
The FNN has a better fit than the regression metamodels, but it still has a poor fit on the tails.
We observe that the LSTM metamodels' QQ-plots closely follow that 45-degree line.
Again, these metamodels are trained on noisy data, so the good fit to the true data should not be taken for granted.
This implies that these models indeed learn the true feature-label relationship in the dynamic hedging simulation model (i.e., true loss labels) even though they are trained on noisy observations (e.g., training labels) of the model.

From a unique analytical standpoint, our numerical study offers a methodical exploration into the robustness of deep neural network models against noise in training labels. 
By employing the standard nested simulation procedure in Algorithm~\ref{alg:standardProcedure} as a data generator, we gain the ability to manipulate the noise level through adjusting the number of inner replications while keeping the same simulation procedure.
As a result, this approach provides a controlled environment to examine the impact of label noise on neural network model.
It allows us to generate our true dataset that approximates the true hedging losses with a high degree of precision, and, as a result, it enables us to explore the crucial question of whether deep learning models are capable of learning the true feature-label relationship from noisy training labels.
Our numerical results in Table~\ref{tab:gmwb_arch} and the QQ plots provide direct evidence that deep neural network models are indeed able to cut through the noise in the training labels and learn the true feature-label relationship.
The LSTM metamodels' ability to learn the true feature-label relationship is crucial for the two-stage procedure to identify true tail scenarios and produce accurate CVaR estimates.

\subsection{Two-Stage Procedure} \label{subsec:twoStageProcedure}

In our proposed two-stage procedure, the metamodel is used to identify the predicted tail scenario set, on which the standard nested simulation procedure is run in Stage 2 to estimate the $95\%$-CVaR.
An accurate identification of the true tail scenarios is crucial.
In a two-stage procedure, metamodels' overall prediction errors measured by the MSEs in Table~\ref{tab:gmwb_arch} are not the determining factor, but their ability to effectively rank the scenarios by their \textbf{true} losses is most critical in producing accurate CVaR estimates.

\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{./project2/figures/tailMatches/regLN.png}
        \caption{Regression metamodels}
    \end{subfigure}\hfill
    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{./project2/figures/tailMatches/nnLN.png}
        \caption{Neural network metamodel}
    \end{subfigure}
    \caption{Percentage of correctly identified true tail scenarios by different metamodels.}
    \label{fig:tailMatches}
\end{figure}

Figure~\ref{fig:tailMatches} depicts the average percentage of correctly identified true tail scenarios\footnote{Each quantity is averaged over 50 macro replications.}  by different metamodels for different safety margins.
The percentage of tail matches of the traditional regression metamodels are significantly lower than the ones of the neural networks.
We see that a poor metamodel like the QPR identifies less than 40\% of the true tail scenario without any safety margin.
In contrast, a good metamodel like the LSTM identifies more than 75\% of the true tail scenarios without any safety margin and more than the QPR metamodel does with 15\% of safety margin\footnote{The metamodel in~\cite{dang2020efficient} identifies 100\% of the true tail scenarios on with a 10\% safety margin for a GMAB contract.
The GMAB contract is simpler than the GMWB contract, and the true tail scenarios are easier to identify. 
For a GMAB, our LSTM metamodel identifies 100\% of the true tail scenarios with a 2.5\% safety margin}.
The RNN metamodel suffers from the vanishing gradient problem during training. 
For some macro replications (as shown in Figure~\ref{subfig:badRNN}), the RNN metamodels' predictions are far from the true losses, especially on the tails.
The FNN metamodel has a better fit than the regression metamodels, but it does not have the same level of accuracy as the LSTM metamodel, which is a specialized network to capture the sequential structure of our time-series features.
For comparison, the horizontal dotted line shows the percentage of correctly identified true tails for the standard nested simulation procedure.
A good metamodel should be able to identify a similar percentage of true tail scenarios as the standard procedure does with a reasonable safety margin.
Otherwise, the two-stage procedure will offer no computational advantage in simulation budget over the standard procedure.
The LSTM metamodel can reaches similar percentage with a 5\% safety margin.
This indicates that the LSTM metamodel should be able to reach the same level of accuracy as the standard procedure with only 20\% of the simulation budget.

\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{./project2/figures/CVaR/allLN.png}
        \caption{Safety margin 0\% - 15\%.}
        \label{subfig:AllSafetyMargin}
    \end{subfigure}
    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{./project2/figures/CVaR/zoomedLN.png}
        \caption{Safety margin 7.5\% - 15\%.}
        \label{subfig:ZoomedSafetyMargin}
    \end{subfigure}
    \caption{Average 95\%-CVaR estimates by different procedures. Right figure is a zoomed-in version of left figure.} 
    \label{fig:CVaR95}
\end{figure}

Lastly, we return to our original goal of estimating the 95\%-CVaR of the dynamic hedging error.
Figure~\ref{fig:CVaR95} shows the 95\%-CVaR estimates for all five metamodels with different safety margins, averaged over 50 macro replications.
Figure~\ref{subfig:ZoomedSafetyMargin} is a zoomed version of Figure~\ref{subfig:AllSafetyMargin}.
Because the safety margin only affects the two-stage procedure, the true 95\%-CVaR and the one estimated by the standard procedure are horizontal (solid and dotted, respectively) lines in Figure~\ref{fig:CVaR95}.
We observe that, with reasonable safety margins, the two-stage procedures with a LSTM metamodel consistently produce estimates that are as accurate as the standard procedure's estimate.
The amount of computational savings is substantial.
The LSTM is particularly superior to other metamodels as it accurately identifies the true tail scenarios and produces highly accurate CVaR estimates with small safety margins.
By concentrating the simulation budget on the predicted tail scenarios, the two-stage procedure with the LSTM metamodel is able to achieve a similar accuracy as the standard procedure with a much smaller simulation budget.
As the percentage of correctly identified tails approaches 100\%, the two-stage procedure's CVaR estimates does not converge to the true value but to the standard procedure's estimate.
This is because the two-stage procedure's CVaR estimates are based on the standard procedure's estimates on the predicted tail scenarios, and the standard procedure's estimates themselves are also noisy.

\subsection{Noise Tolerance of Deep Neural Network Metamodels}

For financial and actuarial applications, regulators and practitioners are often concerned about the robustness of deep neural network models to noise in training labels, which hinders the adoption of these models in practice.
Since the true relationship is unknown in real-world applications, most deep learning literature illustrates the impact of noise by artificially injecting noise into real-world datasets, which is already noisy before the injection.
In our numerical experiments, we are able to use Monte Carlo simulation generate a true dataset that approximates the true hedging losses with a high degree of precision, and, as a result, we are able to explore the crucial question of whether deep learning models are capable of learning the true feature-label relationship from noisy training labels.
In this section, we treat the standard nested simulation procedure as a data generator and examine the noise tolerance of LSTM metamodels by varying the numbers of outer scenarios ($M$) and inner replications ($N$) used to generate the training data.
The number of outer scenarios corresponds to the number of feature-label pairs in the training dataset, and the number of inner replications controls the noise level in the training labels.
Recall that we use the standard nested simulation procedure with $N=100$ inner replications in our previous experiments, and we will refer to the resulting training dataset as the \textit{low-noise dataset}.
We also generate a \textit{medium-noise dataset} and a \textit{high-noise dataset} by running the standard nested simulation procedure with $N=10$ and $N=1$ inner replications, respectively.
By altering the data quantity and quality, we conduct a sensitivity analysis on the LSTM metamodels' noise tolerance.
We study the impact of noisy data on two LSTM metamodels with different model capacities, i.e., different numbers of trainable parameters.
The two LSTM metamodels has the same number of layers, but their numbers of hidden units in each layer are different.
More specfically, the high-capacity LSTM metamodel has $128$ and $16$ hidden units in the first and second LSTM layers, respectively, while the low-capacity LSTM metamodel has $32$ and $4$.

\begin{table}[ht!]
    \small
    \centering
    \begin{tabular}{lccccc}
        \toprule
        \textbf{Model}      & \textbf{Noise level of training labels}   & \textbf{Training error}   & \textbf{Test error}   & \textbf{True error}\\
        \midrule
        LSTM                & $N=100$                                   & $0.075 (\pm0.004)$        & $0.079(\pm0.005)$     & $0.063 (\pm0.004)$ \\ 
        High-capacity LSTM  & $N=100$                                   & $0.068 (\pm0.004)$        & $0.102(\pm0.006)$     & $0.060 (\pm0.004)$ \\
        LSTM                & $N=10$                                    & $0.195 (\pm0.001)$        & $0.193(\pm0.001)$     & $0.070 (\pm0.001)$ \\
        High-capacity LSTM  & $N=10$                                    & $0.157 (\pm0.002)$        & $0.199(\pm0.002)$     & $0.065 (\pm0.001)$ \\
        LSTM                & $N=1$                                     & ?$1.366 (\pm0.006)$        & ?$0.781(\pm0.005)$     & $0.129 (\pm0.002)$ \\
        High-capacityLSTM   & $N=1$                                     & ?$1.354 (\pm0.006)$        & ?$0.795(\pm0.005)$     & $0.149 (\pm0.002)$ \\
        \bottomrule
    \end{tabular}
    \caption{MSEs of LSTM metamodels.}
    \label{tab:lstm_arch}
\end{table}

Table~\ref{tab:lstm_arch} shows the average squared errors and the half widths of their 95\% confidence intervals between the metamodel predictions and the labels in the training dataset and the true dataset.
The test errors are included as a practical measure of the metamodels' generalization ability.
For this particular experiment, we are more interested in the true errors, which measure the metamodels' ability to learn the true feature-label relationship from the low-noise, medium-noise, and high-noise datasets.
We first observe that all the true errors are lower than the training errors, indicating that the LSTM metamodels generalize well to predicting the true losses.
Both LSTM metamodels are able to learn the true feature-label relationship from the low-noise and medium-noise datasets.
However, when the noise level is high, the high-capacity LSTM metamodel has extremely high training error and true error.
It also has wide confidence intervals, which is an indication that the high-capacity LSTM metamodel is starting to overfit to the noise in the training labels.
In contrast, the LSTM metamodel is more robust to label noise and is able to learn the true feature-label relationship better from the high-noise dataset.
In practice, since the true relationship is unknown, the true error is not available.
The test error approximates the true error and is directly observable.
The test errors of the LSTM metamodels are consistent with their true errors, which suggests that generalization ability of a metamodel can indeed be inferred from its test error.

Another way to read Table~\ref{tab:lstm_arch} is to compare the errors of two metamodels for the same noise level.
Comparing the LSTM with the high-capacity LSTM on each noise level, we observe that the high-capacity LSTM has lower training errors and true errors than the LSTM on both the low-noise and medium-noise datasets.
However, when the noise level is high, the high-capacity LSTM has lower training errors but higher true errors than the LSTM.
In our numerical example, only the highest level of noise moves one towards choosing the LSTM over the high-capacity LSTM.
In most cases, a high-capacity metamodel is better.
Nevertheless, in extreme circumstances when the noise level is too high, using a high capacity metamodel leads to severe overfitting and poor generalization.
Hence, domain knowledge about the right architecture for the task and knowledge about the noise level in the training labels are beneficial for choosing the right metamodel.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=\textwidth]{./project2/figures/qqPlots/lstmAll.png}
    \caption{QQ-plots between true losses (x-axis) and predicted losses (y-axis) for two LSTM metamodels.} 
    \label{fig:QQ_All}
\end{figure}

With more details, the QQ-plots depicted in Figure~\ref{fig:QQ_All} illustrates the fit of the two LSTM metamodels when different noise levels are present in the training labels.
They are arranged in a 2-by-3 grid, where the two rows correspond to the two LSTM metamodels, and the three columns correspond to the three noise levels.
The Pearson correlation coefficient between the true losses and the predicted losses is labeled in each subplot.
The sparsity of the plot increases as we move from left to right, indicating that the noise level in the training labels increases.
There are two key findings.
\begin{enumerate}
    \item   Compared to that of the regular LSTM, the metamodel predictions of high-capacity LSTM align more closely with the true losses when trained on the low-noise dataset.
    This is expected because the high-capacity LSTM has more trainable parameters and is able to learn more complex relationships better when the noise level is low.
    \item   When the noise level is medium or high, the high-capacity LSTM is more affected than the regular LSTM.
    This is because the high-capacity LSTM has more trainable parameters and is more prone to over-fitting to the noise in the training labels.
    In contrast, the regular LSTM is more robust to label noise.
\end{enumerate}

To further test the sensitivity of a LSTM metamodel and provide a more comprehensive picture of the noise tolerance of deep neural network models, we conduct a sensitivity analysis on the noise tolerance of the regular LSTM metamodel by varying the numbers of outer scenarios ($M$) and inner replications ($N$) used to generate the training data.
The number of outer scenarios corresponds to the number of feature-label pairs (i.e., data size) of the training dataset, and the number of inner replications controls the noise level in the training labels.

\begin{table}[ht!]
    \small
    \centering
    \begin{tabular}{lccccc}
        \toprule
                          & $N=1\!,\!000$ & $N=100$       & $N=10$        & $N=1$ \\
        \midrule
        $M = 100$         & $0.158$ & $0.167$ & $0.229$ & $1.139$ \\
        $M = 1\!,\!000$   & $0.127$ & $0.123$ & $0.173$ & $0.559$ \\
        $M = 10\!,\!000$  & $0.097$ & $0.099$ & $0.115$ & $0.283$ \\
        $M = 100\!,\!000$ & $0.063$ & $0.063$ & $0.068$ & $0.126$ \\
        \bottomrule
    \end{tabular}
    \caption{MSE between regular LSTM predicted losses and true losses.}
    \label{tab:lstm_sens}
\end{table}

\begin{table}[ht!]
    \small
    \centering
    \begin{tabular}{lccccc}
        \toprule
                          & $N=1\!,\!000$ & $N=100$       & $N=10$        & $N=1$ \\
        \midrule
        $M = 100$         & $0.087$ & ?$0.131$ & $0.408$ & ?$0.764$ \\
        $M = 1\!,\!000$   & $0.087$ & ?$0.156$ & $0.367$ & ?$0.878$ \\
        $M = 10\!,\!000$  & $0.063$ & $0.064$ & $0.147$ & $0.351$ \\
        $M = 100\!,\!000$ & $0.038$ & $0.060$ & $0.065$ & $0.149$ \\
        \bottomrule
    \end{tabular}
    \caption{MSE between high-capacity LSTM predicted losses and true losses.}
    \label{tab:hicaplstm_sens}
\end{table}

Table~\ref{tab:lstm_sens} and~\ref{tab:hicaplstm_sens} show the average squared errors between the LSTM predictions and the true losses for various combinations of $M$ and $N$.
The 4th row of Table~\ref{tab:lstm_sens} shows the performance of the regular LSTM metamodel trained with $M=100\!,000$ samples with different noise levels.
We observe that an increasing $N$ reduces the MSE, but the reduction is not significant for a regular LSTM when $N$ is larger than $10$.
For the high-capacity LSTM, the MSE is significantly reduced when $N$ is increased from $1$ to $100$, but the reduction is not significant when $N$ is increased from $100$ to $1\!,000$.
Another way to interpret the results in Table~\ref{tab:lstm_sens} is to compare the MSEs for the same budget of $\Gamma = M \times N$. 
Entries on the same diagonal represents the same simulation budget.
For most budgets, the MSEs are also the lowest when $N = 10$.
The results in Table~\ref{tab:lstm_sens} suggest that the performance of the LSTM metamodel is more sensitive to the number of outer scenarios than the number of inner replications.
Treating the neural network as an advanced regression metamodel, we find this pheonomenon to be consistent with the results in~\cite{broadie2015risk}, where the authors show that the performance of a regression-based nested simulation procedure is more affected by the number of outer scenarios.

To further investigate the LSTM metamodels' sensitivity to data quantity and quality, we report the Spearman rank correlation coefficients Table~\ref{tab:lstm_corr}, which measure the ability to rank the scenarios by their true losses.
It is an appropriate measure of the metamodel's performance in the two-stage procedure, where the metamodel is used to identify the predicted tail scenario set, on which extensive simulations are run in stage 2 to estimate the $95\%$-CVaR.
The Pearson correlation coefficients are also included in the parentheses to illustrate the linear correlation between the predicted losses and the true losses.
They measure the metamodel's overall prediction accuracy.
The p-values of all quantities are less than $10^{-5}$, indicating that the correlations are statistically significant.

\begin{table}[ht!]
    \small
    \centering
    \begin{tabular}{lccccc}
        \toprule
                          & $N=1\!,\!000$ & $N=100$       & $N=10$        & $N=1$ \\
        \midrule
        $M = 100$         & 0.937 (0.941) & 0.896 (0.903) & 0.875 (0.915) & 0.638 (0.881) \\
        $M = 1\!,\!000$   & 0.922 (0.927) & 0.886 (0.891) & 0.899 (0.908) & 0.722 (0.768) \\
        $M = 10\!,\!000$  & 0.947 (0.948) & 0.908 (0.905) & 0.937 (0.900) & 0.845 (0.630) \\
        $M = 100\!,\!000$ & 0.965 (0.966) & 0.927 (0.922) & 0.963 (0.909) & 0.935 (0.640) \\
        \bottomrule
    \end{tabular}
    \caption{Spearman (and Pearson) correlation coefficients between regular LSTM predicted losses and true losses.}
    \label{tab:lstm_corr}
\end{table}

Consistent with the results in Table~\ref{tab:lstm_sens}, the Pearson and Spearman correlation of the LSTM metamodel predictions with the true losses is sensitive to the number of outer scenarios, especially at higher noise levels.
Notably, the Spearman correlation coefficients are not significantly different from the Pearson correlation coefficients for any $N$ larger than $10$.
In our numerical experiments, the regular LSTM metamodel is trained on $M = 100\!,000$ samples from the low noise training dataset ($N=100$), the total simulation budget is $\Gamma = 10\!,000\!,000$.
The corresponding Spearman correlation coefficient is 0.927, which is very close to the Pearson correlation coefficient of 0.922.
This is a strong evidence that the LSTM metamodel is not only able to effectively rank the scenarios by their true losses, but also able to make accurate loss predictions.
Instead of using the LSTM metamodel only for ranking in a two-stage procedure, LSTM's ability to cut through a moderate level of noise in training labels encourages us to use its predictions to estimate the CVaR directly.

% We proceed to examine the impact of noise on the LSTM metamodels' performance in predicting the true tail scenarios.
% The effect of training label noise is more pronounced for the high-capacity LSTM than for the regular LSTM.
% For both LSTM metamodels, the Spearman correlation coefficients are not significantly different from the Pearson correlation coefficients, which is significantly different from the two-stage procedure in~\cite{dang2020efficient}.
% This difference is due to the fact that the two-stage procedure in~\cite{dang2020efficient} uses a simplified asset model (i.e., a Black Scholes model) as a proxy simulation model for the regime-switching model. 
% The two models are significantly different, but the ranking of the scenarios by their losses is similar.
% For our two-stage procedure, the only difference between the simulation models in Stage 1 and Stage 2 is the number of inner replications.
% The ability for the LSTM metamodels to cut through the noise in training labels and learn the true feature-label relationship offers more accurate loss estimates (i.e., high Pearson correlations), which leads to more accurate rankings (i.e., high Spearman correlations).

\subsection{Single-Stage Procedure}

The accuracy and robustness of the LSTM metamodels motivate us to propose a single-stage procedure that uses the metamodel predictions to estimate the CVaR directly.
Instead of relying on the standard nested simulation procedure in Stage 2, the single-stage procedure is more efficient and extends to estimating other risk measures that require knowledge of the entire loss distribution.
In this section, we compare the single-stage procedure to the two-stage procedure and the standard procedure in estimating the $95\%$-CVaR of the hedging losses for GMWB.
% , and we also examine the single-stage procedure's performance in estimating the standard deviation of the hedging losses. 
In our numerical experiments, the results for the single-stage procedure is obtained with the same metamodels as in the two-stage procedure.
The only difference from Section~\ref{subsec:twoStageProcedure} is that the metamodels predictions are used to estimate the risk measures directly.

\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{./project2/figures/singleStage/CVaRmediumNoise.png}
        \caption{With medium noise training labels ($N=10$)}
    \end{subfigure}
    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{./project2/figures/singleStage/CVaRhighNoise.png}
        \caption{With high noise training labels ($N=1$)}
    \end{subfigure}
    \caption{CVaR estimates of the single-stage procedure with metamodels.}
    \label{fig:CVaRsingleStage}
\end{figure}

Figure~\ref{fig:CVaRsingleStage} shows the boxplots of the 95\%-CVaR estimates of the single-stage procedure with different metamodels and compares them to the two-stage procedure and the standard procedure.
The two-stage procedure uses the same simulation budget as the single-stage procedure in Stage 1 with extra budget for extensive inner simulation on the predicted tail scenarios in Stage 2.
The metamodel with the best performance in the two-stage procedure is chosen, and the safety margin is set to 0\%.
The standard procedure shown in Figure~\ref{fig:CVaRsingleStage} uses the noisy loss labels in the training dataset to estimate the CVaR directly, which uses the same simulation budget as the single-stage procedure.
We observe that the single-stage procedures with the LSTM metamodels consistently produce CVaR estimates that are closer to the true value than the standard procedure's estimate, especially when the noise level is high in the training labels.
It is another strong evidence that the LSTM metamodel is able to cut through the noise in the noisy training labels and make accurate loss predictions that lead to accurate CVaR estimates.
The difference in performance among the metamodels is more pronounced in the single-stage procedure than in the two-stage procedure.
Trained using low noise and medium noise labels, high-capacity LSTM metamodel consistently produces CVaR estimates that are closer to the true value than the regular LSTM, while the other metamodels produce even worse estimates.
Since we are using the metamodel predictions to estimate the CVaR directly without any safety margin, the metamodel's overall prediction accuracy becomes more important.
In other words, the single-stage procedure is more sensitive to the metamodel's ability to make accurate loss predictions than the two-stage procedure.
Previously, a generic FNN metamodel performs well in the two-stage procedure. 
However, results in Figure~\ref{fig:CVaRsingleStage} suggest that the FNN metamodel should not be used in the single-stage procedure.

A single-stage procedure with a high-capcity LSTM metamodel is particularly superior to the two-stage procedure, as it is able to achieve a similar accuracy as the standard procedure with a much smaller simulation budget.
Note that the single-stage procedure does not require a safety margin.
By avoiding the calibration of the safety margin, it is more straight-forward to implement and is more efficient than the two-stage procedure.
For a two-stage procedure with a 0\% safety margin, the extra computational cost is from the extensive inner simulation in Stage 2.
On 4 20-core Intel Xeon Gold 6230 processors, Stage 2 of the two-stage procedure takes 30 minutes to run with parallel processing, while the 95\% confidence interval of training time of the high-capacity LSTM metamodel is $(19.64 \pm 0.94)$ minutes on a Nvidia RTX 3060 Ti GPU.
While the accuracy of the two-stage procedure is highly dependent on the safety margin, increasing the safety margin introduces extra computational cost.
Therefore, while achieving a higher accuracy in estimating the CVaR, the single-stage procedure requires only $60\%$ computation time of the two-stage procedure.

\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{./project2/figures/singleStage/MSEConvergence_lstmLoCap.png}
        \caption{regular LSTM}
        \label{subfig:convLoCap}
    \end{subfigure}
    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{./project2/figures/singleStage/MSEConvergence_lstmHiCap.png}
        \caption{high-capacity LSTM}
        \label{subfig:convHiCap}
    \end{subfigure}
    \caption{Empirical convergence of CVaR for the single-stage procedure with LSTM metamodels.} 
    \label{fig:gammaConvergence}
\end{figure}

To further investigate the single-stage procedure's performance, we conduct a convergence analysis on the LSTM metamodels.
Figure~\ref{fig:gammaConvergence} shows the log-log plots of the relative root mean square errors (RRMSE) between the LSTM metamodel CVaR predictions and the true CVaR against the total simulation budget $\Gamma$.
For each budget $\Gamma$, the metamodels are trained for different combinations of $M$ and $N$, and the metamodel with the best RRMSE is plotted.
While numerical results suggests that the CVaR estimator of the single-stage procedure with LSTM metamodels may have better accuracy than the two-stage procedure and the standard procedure when the number of outer scenarios is further increased, we found it difficult to compare their performance due to insufficient computational resources.
For $\Gamma \leq 100\!,000$, the number of outer scenarios is fixed at $M = 100\!,000$, and only the number of inner replications is varied.
Instead, we try to analyze the effect of the number of outer scenarios and the number of inner replications separately by fixing one and varying the other.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=\textwidth]{./project2/figures/singleStage/MSEConvergence_lstmLoCap_MN.png}
    \caption{Empirical convergence of the single-stage procedure with a LSTM metamodel.} 
    \label{fig:mnConvergence}
\end{figure}

Figure~\ref{fig:mnConvergence} shows the log-log plots of the RRMSE between the LSTM metamodel CVaR predictions and the true CVaR against the simulation budget.
The left figure shows the empirical convergence of the RRMSE for increasing inner replications with a fixed number of outer scenarios ($M=100\!,\!000$), and the right figure shows the empirical convergence of the RRMSE for increasing outer scenarios with a fixed number of inner replications ($N=10$).
Due to computational constraints, we are not able to run the two-stage procedure and the standard procedure with a higher $M$ or $N$, therefore the comparison between the single-stage procedure is only available up to $M = 100\!,000$ and $N = 1\!,000$.
We observe that the RRMSE decreases as the simulation budget increases, and the rate of convergence is higher when the quantity of the data increases.
For an LSTM metamodel, increasing the data quality of the training labels has diminishing returns, which is consistent with the results in Figure~\ref{fig:mnConvergence}.
For an increasing number of inner replications with fixed number of outer scenarios, the RRMSE cease to decrease after reaching $N = 100$. 
More specfically, when the quality of the training labels is fixed at $N = 10$, the CVaR estimator of single-stage procedure with a LSTM metamodel converge roughly in the order of $\mathcal{O}(M^{\frac{2}{3}})$.
Hence, in practice, we suggest to run the single-stage procedure with a moderate number of inner replications and a large number of outer scenarios to achieve a high level of accuracy with a reasonable computational cost.

\section{Conclusion} \label{sec:conclusion}
The proposed nested simulation procedures with deep neural network metamodels result in substantial computational savings in estimating CVaR of the hedging loss of a VA contract from accurately predicting the hedging losses and identifying the tail scenarios.
When new outer scenarios are generated, a trained LSTM metamodel can distinguish between tail and non-tail scenarios and make accurate predictions without the need to run new inner simulations.
Our novel experiment design allows us to examine the impact of label noise on deep neural network models.
We find that a deep neural network with a suitable architecture is able to cut through the noise in training labels and learn the true complex dynamic hedging model.
By showcasing the resilience of these models, our study aims to influence regulatory bodies towards recognizing the value and applicability of deep learning metamodels in financial risk management, and it provides informed suggestions and guidance for the incorporation and oversight of advanced deep learning metamodel in Monte Carlo Simulation in financial applications.
Our findings are particularly insightful in this context.
In our numerical experiments, a LSTM metamodel is resilient to a high level of noise in training labels and is able to make accurate predictions. 
This is a promising evidence that deep neural network metamodels can be used to improve the efficiency of Monte Carlo simulation for quantitative risk management tasks that require a computational-expensive simulation procedure.
We propose two nested simulation procedures that use deep neural network metamodels to estimate risk measures of the hedging loss of a VA contract.
For estimating tail risk measures, our two-stage procedure is designed to address regulatory concerns by avoiding the direct use of metamodel predictions but instead use them to identify the potential tail scenarios.
An extensive inner simulation is performed to achieve a high level of accuracy on the predicted tail scenarios.
However, the safety margin in the two-stage procedure is a user's choice and is not easy to determine before running extensive numerical experiments.
Our single-stage procedure uses the metamodel predictions to estimate the risk measure directly.
It is more efficient and can be extended to estimate risk measures that require knowledge of the entire loss distribution.
Our numerical experiments demonstrate that the proposed single-stage procedure with deep neural network metamodels result in further computational savings over our two-stage procedure. 
Furthermore, our numerical results provide evidences for adopting deep neural network metamodels in Monte Carlo simulation for risk management tasks.
Through our systematic study of the noise tolerance of deep neural network metamodels, we address regulatory concerns by showing that a LSTM metamodel is resilient to a high level of noise in training labels and is able to make accurate predictions.
A possible future research direction is to apply deep neural network metamodels in other financial risk management tasks that requires complex nested simulation with high-dimensional outer scenarios.
Another future research direction is to investigate the impact of label noise on other deep learning models, such as convolutional neural networks and transformer models, and to compare their performance with LSTM metamodels in nested simulation procedures. 
From a practical standpoint, the choice of a suitable deep neural network architecture is crucial for the success of a deep learning metamodel in nested simulation procedures.
We find that a LSTM metamodel is the most suitable for our dynamic hedging simulation model with time series features, but the optimal network architecture may vary for different simulation models.
Exploring deep neural network metamodels in other complex risk management tasks presents a promising avenue for research, especially as these tasks often involve complex, high-dimensional scenarios where traditional methods are insufficient. 
The versatility of neural networks could unlock new insights across a broad spectrum of financial and actuarial applications.

### 2024-03-23 uw-ethesis-frontpgs.tex
new

@@
 
-Nested simulation procedures are commonly required for estimating tail risk measures for complex financial contracts or portfolios. 
-In a standard nested simulation procedure, an outer simulation simulates $M$ risk scenarios under a real-world measure to reflect real-world uncertainties in portfolio values in different risk scenarios.
-For each outer scenario, inner simulation estimates the corresponding portfolio loss based on $N$ sample paths simulated under a risk-neutral measure according to  the risk-neutral pricing theory. 
-This standard procedure is computationally expensive. 
-For example, the simulation budget, i.e., the total number of inner sample paths in all outer scenarios, is a common way to measure the computation required for a simulation procedure.
-For the standard nested simulation procedure, the simulation budget is $\Gamma = MN$.
-To alleviate computational burden of the standard procedure, many studies proposed to replace the inner simulation with alternative such as regression, kernel smoothing, likelihood ratio method, kernel ridge regression, etc.
-We refer to these alternatives as proxies. 
-The above proxies have been demonstrated to have superior performance than the standard procedure in different examples.
-
-The three parts of the thesis have different research focuses but serve one common theme.
-Chapter 2 compares four existing nested simulation methods on their theoretical convergence properties and practical performance. 
-Extensive numerical experiments are conducted for fair comparisons of proxy models on their practical performance in different angles. 
-Proxies in chapter 2 fail to perform for high dimensional scenarios. 
-In chapter 3, machine learning proxies are considered to model variable annuity contract losses.
-Numerical experiments show that, for scenarios with temporal structure, time-series machine learning models are better proxies than generic machine learning models. 
-The machine learning proxies are applied in a 2-stage nested simulation design. 
-Experiments show that machine learning proxies outperform payoff-specific proxies.
-Chapter 4 proposes direction for future research. In the 2-stage design, inner simulation in the second stage is still costly. 
-We propose replacing stage 2 with machine learning proxy predictions. 
-We test the accuracy, sensitivity, and resilience of such proposal.
-
+In the task of estimating risk measures for portfolios of complex financial derivatives, nested simulation procedures are commonly required but often computationally expensive. 
+Tremendous efforts have been made to improve the efficiency of nested simulation procedures by approximating the inner simulation model with a proxy model. 
+In this study, we review the literature on nested simulation procedures in financial engineering and establish fair comparisons of different proxy models using the same set of numerical examples. 
+Our study shows interesting findings on the performance of different proxy models and provides useful insights for practitioners to choose proxy models for nested simulation procedures.
 \cleardoublepage

### 2024-03-24 project2/nnMetamodels.tex
new

@@
 Given the time~$t$ state $(S_t,F_t,G_t)$, following~\cite{cathcart2015calculating} the sensitivity of $V_t$ with respect to $S_t$ can be estimated by a pathwise estimator~\citep{glasserman2004monte}:
-\begin{equation}\label{eq:delta}
-    \Delta_t(\Stilde_{t+1},\ldots,\Stilde_{T} | S_t) = \frac{\partial V_t}{\partial S_t} = \sum_{s=t+1}^{T} e^{-r(T-s)} \left[\bm{1}\{\Itilde_s > \Ftilde_s\}\cdot \left( \frac{\partial \Itilde_s}{ \partial S_t} - \frac{\partial \Ftilde_s}{ \partial S_t}\right)- \eta_n \frac{\partial \Ftilde_s}{ \partial S_t}\right], \quad t=0,\ldots,T-1,
-\end{equation}
+\begin{align}\label{eq:delta}
+    \Delta_t(\Stilde_{t+1},\ldots,\Stilde_{T} | S_t) = \frac{\partial V_t}{\partial S_t} = \sum_{s=t+1}^{T} e^{-r(T-s)} \left[\bm{1}\{\Itilde_s > \Ftilde_s\} \cdot \left( \frac{\partial \Itilde_s}{ \partial S_t} - \frac{\partial \Ftilde_s}{ \partial S_t}\right)- \eta_n \frac{\partial \Ftilde_s}{ \partial S_t}\right], \nonumber \\
+    t=0,\ldots,T-1,
+\end{align}
 where $\bm{1}\{\cdot\}$ is an indicator function and
@@
     \toprule
-    \textbf{Model} & \textbf{\makecell{Layer size}} & \textbf{\makecell{\# parameters}} & \textbf{Training error} & \textbf{Test error} & \textbf{True error}\\
+    \textbf{Model} & \textbf{\makecell{Layer size}} & \textbf{\makecell{Capacity}} & \textbf{Training error} & \textbf{Test error} & \textbf{True error}\\
     \midrule
@@
         \toprule
-        \textbf{Model}      & \textbf{Noise level of training labels}   & \textbf{Training error}   & \textbf{Test error}   & \textbf{True error}\\
+        \textbf{Model}      & \textbf{Noise level}   & \textbf{Training error}   & \textbf{Test error}   & \textbf{True error}\\
         \midrule
@@
         \includegraphics[width=\textwidth]{./project2/figures/singleStage/CVaRmediumNoise.png}
-        \caption{With medium noise training labels ($N=10$)}
+        \caption{Medium noise training labels ($N=10$)}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{./project2/figures/singleStage/CVaRhighNoise.png}
-        \caption{With high noise training labels ($N=1$)}
+        \caption{High noise training labels ($N=1$)}
     \end{subfigure}
@@
 The left figure shows the empirical convergence of the RRMSE for increasing inner replications with a fixed number of outer scenarios ($M=100\!,\!000$), and the right figure shows the empirical convergence of the RRMSE for increasing outer scenarios with a fixed number of inner replications ($N=10$).
-Due to computational constraints, we are not able to run the two-stage procedure and the standard procedure with a higher $M$ or $N$, therefore the comparison between the single-stage procedure is only available up to $M = 100\!,000$ and $N = 1\!,000$.
+Due to computational constraints, we are not able to run the two-stage procedure and the standard procedure with more outer scenarios or more inner replications, therefore the comparison between the single-stage procedure is only available up to $M = 100\!,000$ and $N = 1\!,000$.
 We observe that the RRMSE decreases as the simulation budget increases, and the rate of convergence is higher when the quantity of the data increases.

### 2024-03-24 project2/nnMetamodels.tex
new

@@
 The rest of this article is organized as follows: 
-% Section~\ref{sec:problem-formulation} presents the problem settings for tail risk measures and dynamic hedging of VAs. 
-% Section~\ref{sec:metamodel2Stage} proposes an efficient two-stage nested simulation procedure that uses deep neural networks as metamodels to help reduce simulation budget by only performing computations on identified tail scenarios.
-% Section~\ref{sec:metamodel1Stage} proposes a one-stage nested simulation procedure that estimates risk measures directly with metamodel predictions.
-% Section~\ref{sec:numerical} demonstrates the efficiency of deep learning proxies and examines error tolerance of two LSTM metamodels with different numbers of trainable parameters. 
+% Section~\ref{sec2:problem-formulation} presents the problem settings for tail risk measures and dynamic hedging of VAs. 
+% Section~\ref{sec2:metamodel2Stage} proposes an efficient two-stage nested simulation procedure that uses deep neural networks as metamodels to help reduce simulation budget by only performing computations on identified tail scenarios.
+% Section~\ref{sec2:metamodel1Stage} proposes a one-stage nested simulation procedure that estimates risk measures directly with metamodel predictions.
+% Section~\ref{sec2:numerical} demonstrates the efficiency of deep learning proxies and examines error tolerance of two LSTM metamodels with different numbers of trainable parameters. 
 % Practical suggestions are provided for the choice of suitable metamodels and simulation settings.
 
-\section{Problem Formulation} \label{p2:problem-formulation}
+\section{Problem Formulation} \label{sec2:problem-formulation}
 
 In this section we present notations, problem settings, and a simulation model for risk estimation for hedging errors of variable annuities.
-A main goal of the section is to showcase the complexity of the simulation model, which we use as a data generator to train deep neural network metamodels (Section~\ref{sec:metamodel2Stage} and Section~\ref{sec:metamodel1Stage}).
+A main goal of the section is to showcase the complexity of the simulation model, which we use as a data generator to train deep neural network metamodels (Section~\ref{sec2:metamodel2Stage} and Section~\ref{sec2:metamodel1Stage}).
 For readers who are interested in the examination of a neural network metamodel, it is sufficient to understand that our simulation model generates data with 240 features and 1 real-value label and our metamodels are generally applicable to any simulation model that generates data with similar characteristics.
@@
 Given the time~$t$ state $(S_t,F_t,G_t)$, following~\cite{cathcart2015calculating} the sensitivity of $V_t$ with respect to $S_t$ can be estimated by a pathwise estimator~\citep{glasserman2004monte}:
-\begin{align}\label{eq:delta}
+\begin{align}\label{eq2:delta}
     \Delta_t(\Stilde_{t+1},\ldots,\Stilde_{T} | S_t) = \frac{\partial V_t}{\partial S_t} = \sum_{s=t+1}^{T} e^{-r(T-s)} \left[\bm{1}\{\Itilde_s > \Ftilde_s\} \cdot \left( \frac{\partial \Itilde_s}{ \partial S_t} - \frac{\partial \Ftilde_s}{ \partial S_t}\right)- \eta_n \frac{\partial \Ftilde_s}{ \partial S_t}\right], \nonumber \\
@@
     \caption{Illustration of multi-period nested simulation that estimates the P\&L for one outer scenario.}
-    \label{fig:illustration}
+    \label{fig2:illustration}
 \end{figure}
@@
 For simplicity, in this study we consider delta hedging for a generic VA liability using one stock and one bond.
-The metamodeling procedures in Section~\ref{sec:metamodel2Stage} and Section~\ref{sec:metamodel1Stage} can be trivially adapted to more general hedging strategies.
+The metamodeling procedures in Section~\ref{sec2:metamodel2Stage} and Section~\ref{sec2:metamodel1Stage} can be trivially adapted to more general hedging strategies.
 
@@
 Therefore, the time~$t$ hedging error, i.e., the cash flow incurred by the insurer due to rebalancing at time~$t$, is
-\begin{equation}\label{eq:hedgingerror}
+\begin{equation}\label{eq2:hedgingerror}
     HE_t = H_t - H^{bf}_t, \quad t=1,\ldots, T-1.
 \end{equation}
-The P\&L of the VA contract includes the cost of the initial hedge ($H_0$), the hedging errors~\eqref{eq:hedgingerror}, the unwinding of the hedge at maturity ($H^{bf}_T$), and the unhedged liability ($V_0$).
+The P\&L of the VA contract includes the cost of the initial hedge ($H_0$), the hedging errors~\eqref{eq2:hedgingerror}, the unwinding of the hedge at maturity ($H^{bf}_T$), and the unhedged liability ($V_0$).
 Mathematically, the present value of these cash flows is given by
-\begin{equation}\label{eq:lossrv}
+\begin{equation}\label{eq2:lossrv}
 L = H_0 + \sum_{t=1}^{T-1} e^{-rt} HE_t - e^{-rT} H^{bf}_T + V_0 = \sum_{t=0}^{T-1}\Delta_t (e^{-rt}S_t - e^{-r(t+1)}S_{t+1}) + V_0,
@@
 
-In~\eqref{eq:lossrv}, $\Delta_t$ and $V_0$ are determined by using a risk-neutral measure $\mathbb{Q}$ while the distribution of $L$ is under a real-world measure $\mathbb{P}$.
+In~\eqref{eq2:lossrv}, $\Delta_t$ and $V_0$ are determined by using a risk-neutral measure $\mathbb{Q}$ while the distribution of $L$ is under a real-world measure $\mathbb{P}$.
 If $\Delta_t$ and $V_0$ cannot be calculated analytically, a nested simulation is required to estimate the tail risk measure of $L$.
@@
 Recall from Section~\ref{subsec:VApayout} that the stock's sample path, regardless of inner or outer simulation or a combination of both, determines the evolution of the triplet $(S_t,F_t,G_t)$.
-For GMWB, a standard nested simulation procedure to estimate the $\alpha$-CVaR of $L$ is described in Algorithm~\ref{alg:standardProcedure}.
+For GMWB, a standard nested simulation procedure to estimate the $\alpha$-CVaR of $L$ is described in Algorithm~\ref{alg2:standardProcedure}.
 
@@
 %     \item For $i=1,\ldots,M$, simulate outer scenarios $\bS^{(i)} = (S_{1}^{(i)},\ldots,S_{T}^{(i)})$ under the real-world measure $\mathbb{P}$.
-%     Figure~\ref{fig:illustration} illustrates the inner simulation experiments needed for an outer scenario.
+%     Figure~\ref{fig2:illustration} illustrates the inner simulation experiments needed for an outer scenario.
 
-%     \item For $t=0$, simulate time-$0$ inner paths $\bStilde_{0}^{(j)} = (\Stilde_{1}^{(j)},\Stilde_{2}^{(j)},\ldots,\Stilde_{T}^{(j)})$, $j=1,\ldots,N$ under $\mathbb{Q}$ {and} then estimate $V_0$ by $\Vhat_0 = \sum_{s=1}^{T} e^{-r(T-s)} [(I_s - F_s)^+- \eta_n F_s]$ and estimate $\Deltahat_0 = \Delta_0(\Stilde_{1}^{(j)},\ldots,\Stilde_{T}^{(j)} | S_0)$ based on~\eqref{eq:delta}.
+%     \item For $t=0$, simulate time-$0$ inner paths $\bStilde_{0}^{(j)} = (\Stilde_{1}^{(j)},\Stilde_{2}^{(j)},\ldots,\Stilde_{T}^{(j)})$, $j=1,\ldots,N$ under $\mathbb{Q}$ {and} then estimate $V_0$ by $\Vhat_0 = \sum_{s=1}^{T} e^{-r(T-s)} [(I_s - F_s)^+- \eta_n F_s]$ and estimate $\Deltahat_0 = \Delta_0(\Stilde_{1}^{(j)},\ldots,\Stilde_{T}^{(j)} | S_0)$ based on~\eqref{eq2:delta}.
 %     Note that $S_0$ is known, so these inner paths do not depend on any outer scenario.
@@
 %     \begin{enumerate}
-%         \item At each time~$t=1,\ldots,T-1$, simulate inner paths $\bStilde_{t}^{(ij)} = (\Stilde_{t+1}^{(ij)},\ldots,\Stilde_{T}^{(ij)})$, $j=1,\ldots,N$ under $\mathbb{Q}$ {and} then estimate $\Delta_t$ by $\Deltahat_t^{(i)} = \Delta_t(\Stilde_{t+1}^{(ij)},\ldots,\Stilde_{T}^{(ij)} | \bm{S}_t^{(i)})$ based on~\eqref{eq:delta}.
+%         \item At each time~$t=1,\ldots,T-1$, simulate inner paths $\bStilde_{t}^{(ij)} = (\Stilde_{t+1}^{(ij)},\ldots,\Stilde_{T}^{(ij)})$, $j=1,\ldots,N$ under $\mathbb{Q}$ {and} then estimate $\Delta_t$ by $\Deltahat_t^{(i)} = \Delta_t(\Stilde_{t+1}^{(ij)},\ldots,\Stilde_{T}^{(ij)} | \bm{S}_t^{(i)})$ based on~\eqref{eq2:delta}.
 
-%         \item Use scenarios $\bS^{(i)}$ and $\Vhat_0$ and $\Deltahat_t^{(i)}$ to calculate losses $\Lhat_i^{MC}$, $t=0,\ldots,T-1$, based on~\eqref{eq:lossrv}.
+%         \item Use scenarios $\bS^{(i)}$ and $\Vhat_0$ and $\Deltahat_t^{(i)}$ to calculate losses $\Lhat_i^{MC}$, $t=0,\ldots,T-1$, based on~\eqref{eq2:lossrv}.
 Then sort them as $\Lhat^{MC}_{(1)}\leq \Lhat^{MC}_{(2)} \leq \cdots\leq \Lhat^{MC}_{(M)}$.
@@
 \caption{Standard Nested Simulation Procedure for Estimating CVaR for GMWB Hedging Losses}
-\begin{algorithmic}[1] \label{alg:standardProcedure}
+\begin{algorithmic}[1] \label{alg2:standardProcedure}
     \STATE  For $i=1,\ldots,M$, simulate outer scenarios $\bS^{(i)} = (S_{1}^{(i)},\ldots,S_{T}^{(i)})$ under the real-world measure $\mathbb{P}$.
@@
 
-We refer to the collection of experiments needed conditional on one scenario $\bS^{(i)}$ to estimate $L_i$, that is, all upward arrows in Figure~\ref{fig:illustration}, as one inner simulation experiment.
+We refer to the collection of experiments needed conditional on one scenario $\bS^{(i)}$ to estimate $L_i$, that is, all upward arrows in Figure~\ref{fig2:illustration}, as one inner simulation experiment.
 We make four observations:
@@
 
-\section{Two-Stage Nested Simulation with Metamodels} \label{sec:metamodel2Stage}
+\section{Two-Stage Nested Simulation with Metamodels} \label{sec2:metamodel2Stage}
 
@@
 \caption{Two-Stage Metamodeling Nested Simulation Procedure for Estimating CVaR}
-\begin{algorithmic}[1] \label{alg:twoStageProcedure}
+\begin{algorithmic}[1] \label{alg2:twoStageProcedure}
     \STATE \textbf{Train a neural network metamodel using simulation data:}
     \begin{enumerate} [label=\alph*., itemsep=0pt, parsep=0pt, topsep=0pt]
-        \item Use a fraction of the total simulation budget to run Steps 1, 2, and 3 in the standard procedure, i.e., Algorithm~\ref{alg:standardProcedure}, with the same number of outer scenarios, $M$, but a much smaller number of inner replications, $N' \ll N$, in each scenario.
+        \item Use a fraction of the total simulation budget to run Steps 1, 2, and 3 in the standard procedure, i.e., Algorithm~\ref{alg2:standardProcedure}, with the same number of outer scenarios, $M$, but a much smaller number of inner replications, $N' \ll N$, in each scenario.
 Obtain $M$ simulated samples (feature-label pairs), $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$.
@@
     \begin{enumerate} [label=\alph*., itemsep=0pt, parsep=0pt, topsep=0pt]
-        \item Run Steps 2 and 3 of Algorithm~\ref{alg:standardProcedure} with the same number of inner replications, $N$, but only on the predicted tail scenarios, i.e., scenarios in $\widehat{\tail}_{m}^{PD}$.
+        \item Run Steps 2 and 3 of Algorithm~\ref{alg2:standardProcedure} with the same number of inner replications, $N$, but only on the predicted tail scenarios, i.e., scenarios in $\widehat{\tail}_{m}^{PD}$.
 Denote the standard procedure's estimated losses and sorted losses by $\Lhat^{ML}_i$ and $\Lhat^{ML}_{(i)}$, respectively, $i=1,\ldots,m$.
@@
 
-Similar to~\cite{dang2020efficient}, the proposed two-stage procedure in Algorithm ~\ref{alg:twoStageProcedure} uses the metamodel predictions to identify the predicted tail scenario set in Stage 1.
+Similar to~\cite{dang2020efficient}, the proposed two-stage procedure in Algorithm ~\ref{alg2:twoStageProcedure} uses the metamodel predictions to identify the predicted tail scenario set in Stage 1.
 However, different from their fixed-budget simulation design, we attempt to achieve a target accuracy.
@@
 
-\section{Single-Stage Nested Simulation with Neural Network Metamodels} \label{sec:metamodel1Stage}
+\section{Single-Stage Nested Simulation with Neural Network Metamodels} \label{sec2:metamodel1Stage}
 
@@
 \caption{Single-Stage Metamodeling Nested Simulation Procedure for Estimating CVaR}
-\begin{algorithmic}[1] \label{alg:oneStageProcedure}
-    \STATE Run Step 1 of Algorithm~\ref{alg:twoStageProcedure}, and denote the predicted losses by
+\begin{algorithmic}[1] \label{alg2:oneStageProcedure}
+    \STATE Run Step 1 of Algorithm~\ref{alg2:twoStageProcedure}, and denote the predicted losses by
     $\Lhat^{PD}_i = \Lhat^{PD}(\bS^{(i)})$, $i=1,\ldots,M$.
@@
 
-\section{Numerical Results} \label{sec:numerical}
+\section{Numerical Results} \label{sec2:numerical}
 
@@
     \item It avoids the vanishing gradient problem during training, which makes the LSTM easier to than the RNN.
-Figure~\ref{fig:QQ_RNN} shows the quantile-quantile (QQ) plots between the \textbf{training} labels and the RNN predictions for two macro replications, where training of the latter is hindered by the vanishing gradient problem\footnote{A well-trained RNN stops early at around 300 training epochs, while an ill-trained RNN uses up all 1000 training epochs.}.
+Figure~\ref{fig2:QQ_RNN} shows the quantile-quantile (QQ) plots between the \textbf{training} labels and the RNN predictions for two macro replications, where training of the latter is hindered by the vanishing gradient problem\footnote{A well-trained RNN stops early at around 300 training epochs, while an ill-trained RNN uses up all 1000 training epochs.}.
 As a result, the half length of the 95\% confidence interval of the RNN's training error is much larger than all other metamodels.
@@
         \caption{A bad RNN metamodel}
-        \label{subfig:badRNN}
+        \label{subfig2:badRNN}
     \end{subfigure}
     \caption{QQ-plots between true labels (x-axis) and predicted losses (y-axis) for the RNN metamodel.} 
-    \label{fig:QQ_RNN}
+    \label{fig2:QQ_RNN}
 \end{figure}
@@
 In contrast, the deep neural network metamodels generalize better to the true data than to the test data.
-Figure~\ref{fig:QQ_REG} and Figure~\ref{fig:QQ_NN} shows the QQ plots between the \textbf{true} labels and the predicted losses for the regression metamodels and the neural network metamodels, respectively.
+Figure~\ref{fig2:QQ_REG} and Figure~\ref{fig2:QQ_NN} shows the QQ plots between the \textbf{true} labels and the predicted losses for the regression metamodels and the neural network metamodels, respectively.
 
@@
     \caption{QQ-plots between true losses (x-axis) and predicted losses (y-axis) for regression metamodels.} 
-    \label{fig:QQ_REG}
+    \label{fig2:QQ_REG}
 \end{figure}
@@
 Compared with the MSE table in Table~\ref{tab:gmwb_arch} that summarizes the overall fit, QQ plots offer a close look at the metamodels' performance on different parts of the loss distribution.
-Figure~\ref{fig:QQ_REG} show that the regression metamodels' predictions are far from the true losses, especially on the tails.
+Figure~\ref{fig2:QQ_REG} show that the regression metamodels' predictions are far from the true losses, especially on the tails.
 Between the two regression metamodels, the QPR metamodel has a slightly better fit for larger losses.
@@
     \caption{QQ-plots between true losses (x-axis) and predicted losses (y-axis) for neural network metamodels.} 
-    \label{fig:QQ_NN}
+    \label{fig2:QQ_NN}
 \end{figure}
 
-In Figure~\ref{fig:QQ_NN}, we illustrate the fit of the neural network metamodels.
+In Figure~\ref{fig2:QQ_NN}, we illustrate the fit of the neural network metamodels.
 The FNN has a better fit than the regression metamodels, but it still has a poor fit on the tails.
@@
 From a unique analytical standpoint, our numerical study offers a methodical exploration into the robustness of deep neural network models against noise in training labels. 
-By employing the standard nested simulation procedure in Algorithm~\ref{alg:standardProcedure} as a data generator, we gain the ability to manipulate the noise level through adjusting the number of inner replications while keeping the same simulation procedure.
+By employing the standard nested simulation procedure in Algorithm~\ref{alg2:standardProcedure} as a data generator, we gain the ability to manipulate the noise level through adjusting the number of inner replications while keeping the same simulation procedure.
 As a result, this approach provides a controlled environment to examine the impact of label noise on neural network model.
@@
     \caption{Percentage of correctly identified true tail scenarios by different metamodels.}
-    \label{fig:tailMatches}
+    \label{fig2:tailMatches}
 \end{figure}
 
-Figure~\ref{fig:tailMatches} depicts the average percentage of correctly identified true tail scenarios\footnote{Each quantity is averaged over 50 macro replications.}  by different metamodels for different safety margins.
+Figure~\ref{fig2:tailMatches} depicts the average percentage of correctly identified true tail scenarios\footnote{Each quantity is averaged over 50 macro replications.}  by different metamodels for different safety margins.
 The percentage of tail matches of the traditional regression metamodels are significantly lower than the ones of the neural networks.
@@
 The RNN metamodel suffers from the vanishing gradient problem during training. 
-For some macro replications (as shown in Figure~\ref{subfig:badRNN}), the RNN metamodels' predictions are far from the true losses, especially on the tails.
+For some macro replications (as shown in Figure~\ref{subfig2:badRNN}), the RNN metamodels' predictions are far from the true losses, especially on the tails.
 The FNN metamodel has a better fit than the regression metamodels, but it does not have the same level of accuracy as the LSTM metamodel, which is a specialized network to capture the sequential structure of our time-series features.
@@
         \caption{Safety margin 0\% - 15\%.}
-        \label{subfig:AllSafetyMargin}
+        \label{subfig2:AllSafetyMargin}
     \end{subfigure}
@@
         \caption{Safety margin 7.5\% - 15\%.}
-        \label{subfig:ZoomedSafetyMargin}
+        \label{subfig2:ZoomedSafetyMargin}
     \end{subfigure}
     \caption{Average 95\%-CVaR estimates by different procedures. Right figure is a zoomed-in version of left figure.} 
-    \label{fig:CVaR95}
+    \label{fig2:CVaR95}
 \end{figure}
@@
 Lastly, we return to our original goal of estimating the 95\%-CVaR of the dynamic hedging error.
-Figure~\ref{fig:CVaR95} shows the 95\%-CVaR estimates for all five metamodels with different safety margins, averaged over 50 macro replications.
-Figure~\ref{subfig:ZoomedSafetyMargin} is a zoomed version of Figure~\ref{subfig:AllSafetyMargin}.
-Because the safety margin only affects the two-stage procedure, the true 95\%-CVaR and the one estimated by the standard procedure are horizontal (solid and dotted, respectively) lines in Figure~\ref{fig:CVaR95}.
+Figure~\ref{fig2:CVaR95} shows the 95\%-CVaR estimates for all five metamodels with different safety margins, averaged over 50 macro replications.
+Figure~\ref{subfig2:ZoomedSafetyMargin} is a zoomed version of Figure~\ref{subfig2:AllSafetyMargin}.
+Because the safety margin only affects the two-stage procedure, the true 95\%-CVaR and the one estimated by the standard procedure are horizontal (solid and dotted, respectively) lines in Figure~\ref{fig2:CVaR95}.
 We observe that, with reasonable safety margins, the two-stage procedures with a LSTM metamodel consistently produce estimates that are as accurate as the standard procedure's estimate.
@@
         High-capacity LSTM  & $N=10$                 & $0.157 (\pm0.002)$        & $0.199(\pm0.002)$     & $0.065 (\pm0.001)$ \\
-        LSTM                & $N=1$                                     & ?$1.366 (\pm0.006)$        & ?$0.781(\pm0.005)$     & $0.129 (\pm0.002)$ \\
-        High-capacityLSTM   & $N=1$                                     & ?$1.354 (\pm0.006)$        & ?$0.795(\pm0.005)$     & $0.149 (\pm0.002)$ \\
+        LSTM                & $N=1$                  & $1.366 (\pm0.006)$        & $0.781(\pm0.005)$     & $0.129 (\pm0.002)$ \\
+        High-capacityLSTM   & $N=1$                  & $1.354 (\pm0.006)$        & $0.795(\pm0.005)$     & $0.149 (\pm0.002)$ \\
         \bottomrule
@@
     \caption{QQ-plots between true losses (x-axis) and predicted losses (y-axis) for two LSTM metamodels.} 
-    \label{fig:QQ_All}
+    \label{fig2:QQ_All}
 \end{figure}
 
-With more details, the QQ-plots depicted in Figure~\ref{fig:QQ_All} illustrates the fit of the two LSTM metamodels when different noise levels are present in the training labels.
+With more details, the QQ-plots depicted in Figure~\ref{fig2:QQ_All} illustrates the fit of the two LSTM metamodels when different noise levels are present in the training labels.
 They are arranged in a 2-by-3 grid, where the two rows correspond to the two LSTM metamodels, and the three columns correspond to the three noise levels.
@@
         \midrule
-        $M = 100$         & $0.087$ & ?$0.131$ & $0.408$ & ?$0.764$ \\
-        $M = 1\!,\!000$   & $0.087$ & ?$0.156$ & $0.367$ & ?$0.878$ \\
+        $M = 100$         & $0.087$ & $0.131$ & $0.408$ & $0.764$ \\
+        $M = 1\!,\!000$   & $0.087$ & $0.156$ & $0.367$ & $0.878$ \\
         $M = 10\!,\!000$  & $0.063$ & $0.064$ & $0.147$ & $0.351$ \\
@@
 Table~\ref{tab:lstm_sens} and~\ref{tab:hicaplstm_sens} show the average squared errors between the LSTM predictions and the true losses for various combinations of $M$ and $N$.
-The 4th row of Table~\ref{tab:lstm_sens} shows the performance of the regular LSTM metamodel trained with $M=100\!,000$ samples with different noise levels.
+The last rows of Table~\ref{tab:lstm_sens} and Table~\ref{tab:hicaplstm_sens} show the performance of the regular and high capacity LSTM metamodels trained with $M=100\!,000$ training labels with different noise levels.
 We observe that an increasing $N$ reduces the MSE, but the reduction is not significant for a regular LSTM when $N$ is larger than $10$.
@@
     \caption{CVaR estimates of the single-stage procedure with metamodels.}
-    \label{fig:CVaRsingleStage}
+    \label{fig2:CVaRsingleStage}
 \end{figure}
 
-Figure~\ref{fig:CVaRsingleStage} shows the boxplots of the 95\%-CVaR estimates of the single-stage procedure with different metamodels and compares them to the two-stage procedure and the standard procedure.
+Figure~\ref{fig2:CVaRsingleStage} shows the boxplots of the 95\%-CVaR estimates of the single-stage procedure with different metamodels and compares them to the two-stage procedure and the standard procedure.
 The two-stage procedure uses the same simulation budget as the single-stage procedure in Stage 1 with extra budget for extensive inner simulation on the predicted tail scenarios in Stage 2.
 The metamodel with the best performance in the two-stage procedure is chosen, and the safety margin is set to 0\%.
-The standard procedure shown in Figure~\ref{fig:CVaRsingleStage} uses the noisy loss labels in the training dataset to estimate the CVaR directly, which uses the same simulation budget as the single-stage procedure.
+The standard procedure shown in Figure~\ref{fig2:CVaRsingleStage} uses the noisy loss labels in the training dataset to estimate the CVaR directly, which uses the same simulation budget as the single-stage procedure.
 We observe that the single-stage procedures with the LSTM metamodels consistently produce CVaR estimates that are closer to the true value than the standard procedure's estimate, especially when the noise level is high in the training labels.
@@
 Previously, a generic FNN metamodel performs well in the two-stage procedure. 
-However, results in Figure~\ref{fig:CVaRsingleStage} suggest that the FNN metamodel should not be used in the single-stage procedure.
+However, results in Figure~\ref{fig2:CVaRsingleStage} suggest that the FNN metamodel should not be used in the single-stage procedure.
 
@@
         \caption{regular LSTM}
-        \label{subfig:convLoCap}
+        \label{subfig2:convLoCap}
     \end{subfigure}
@@
         \caption{high-capacity LSTM}
-        \label{subfig:convHiCap}
+        \label{subfig2:convHiCap}
     \end{subfigure}
     \caption{Empirical convergence of CVaR for the single-stage procedure with LSTM metamodels.} 
-    \label{fig:gammaConvergence}
+    \label{fig2:gammaConvergence}
 \end{figure}
@@
 To further investigate the single-stage procedure's performance, we conduct a convergence analysis on the LSTM metamodels.
-Figure~\ref{fig:gammaConvergence} shows the log-log plots of the relative root mean square errors (RRMSE) between the LSTM metamodel CVaR predictions and the true CVaR against the total simulation budget $\Gamma$.
+Figure~\ref{fig2:gammaConvergence} shows the log-log plots of the relative root mean square errors (RRMSE) between the LSTM metamodel CVaR predictions and the true CVaR against the total simulation budget $\Gamma$.
 For each budget $\Gamma$, the metamodels are trained for different combinations of $M$ and $N$, and the metamodel with the best RRMSE is plotted.
@@
     \caption{Empirical convergence of the single-stage procedure with a LSTM metamodel.} 
-    \label{fig:mnConvergence}
+    \label{fig2:mnConvergence}
 \end{figure}
 
-Figure~\ref{fig:mnConvergence} shows the log-log plots of the RRMSE between the LSTM metamodel CVaR predictions and the true CVaR against the simulation budget.
+Figure~\ref{fig2:mnConvergence} shows the log-log plots of the RRMSE between the LSTM metamodel CVaR predictions and the true CVaR against the simulation budget.
 The left figure shows the empirical convergence of the RRMSE for increasing inner replications with a fixed number of outer scenarios ($M=100\!,\!000$), and the right figure shows the empirical convergence of the RRMSE for increasing outer scenarios with a fixed number of inner replications ($N=10$).
@@
 We observe that the RRMSE decreases as the simulation budget increases, and the rate of convergence is higher when the quantity of the data increases.
-For an LSTM metamodel, increasing the data quality of the training labels has diminishing returns, which is consistent with the results in Figure~\ref{fig:mnConvergence}.
+For an LSTM metamodel, increasing the data quality of the training labels has diminishing returns, which is consistent with the results in Figure~\ref{fig2:mnConvergence}.
 For an increasing number of inner replications with fixed number of outer scenarios, the RRMSE cease to decrease after reaching $N = 100$. 
@@
 
-\section{Conclusion} \label{sec:conclusion}
+\section{Conclusion} \label{sec2:conclusion}
 The proposed nested simulation procedures with deep neural network metamodels result in substantial computational savings in estimating CVaR of the hedging loss of a VA contract from accurately predicting the hedging losses and identifying the tail scenarios.

### 2024-04-04 project1/nsSurvey.tex
new

@@
 
-Nested simulation procedures, also known as stochastic on stochastic simulation, are commonly used in financial engineering to estimate risk measures for portfolios of complex financial derivatives. 
+Nested simulation procedures are commonly used in financial engineering to estimate risk measures for portfolios of complex financial derivatives. 
 The term \textit{nested} is referred to a nested estimation problem, in which the estimation of the risk measure requires two levels of Monte Carlo (MC) simulations.
@@
 For risk measures in certain forms,~\cite{broadie2015risk} show that it is optimal to allocate all simulation budget to the outer level simulation, and the inner replication should be kept to a minimum of $1$.
-Similarly,~\cite{hong2017kernel},~\cite{feng2020optimal}, and~\cite{zhang2022sample} propose to use a kernel smoothing model, a likelihood ratio model, and a kernel ridge regression model as proxies to pool the inner replications from all outer scenarios.
-Another line of research is the multi-level Monte Carlo (MLMC) method analyzed in~\cite{giles2019multilevel}, which is a variance reduction technique that uses a hierarchy of approximations to the risk measure of interest.
+Similarly,~\cite{hong2017kernel},~\cite{feng2020optimal}, and~\cite{zhang2022sample} use a kernel smoothing model, a likelihood ratio model, and a kernel ridge regression model as proxies to pool the inner replications from all outer scenarios.
+In simulation studies, this approach of using a model of a simulation model is known as metamodeling, and the models of a simulation model are also referred to as metamodels~\citep{barton1998simulation}.
+Another line of research is the multi-level Monte Carlo (MLMC) method analyzed in~\cite{giles2019multilevel}, which is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest.
 
@@
 Their asymptotic convergence results are closely examined for their assumptions that guarantee the convergence.
-Furthermore, our study finds that different studies have used different examples in their numerical experiments, which introduces unfair advantages for certain simulation procedures over others. 
+Furthermore, our study finds that different studies propose different examples in their numerical experiments, which introduces unfair advantages for certain simulation procedures over others. 
 A fair comparison among popular methods is therefore urgently needed in the literature. 
@@
 The rest of the paper is organized as follows.
-% Section~\ref{sec:problem-formulation} introduces the nested simulation procedure and the standard Monte Carlo estimator.
-% Section~\ref{sec:asymptotic-convergence} provides new theoretical results on the convergence of existing nested simulation procedures.
-% Section~\ref{sec:convergence-orders} summarizes the asymptotic convergence orders and the critical assumptions of nested simulation procedures in the literature.
-% Section~\ref{sec:numerical-experiments} presents the numerical experiments and the comparisons of different nested simulation procedures with respect to different risk measures, problem dimensions, and payoff complexities.
-% Section~\ref{sec:computational-complexity} discusses the computational complexity of different nested simulation procedures.
-% Section~\ref{sec:conclusion} concludes the paper.
+Section~\ref{sec1:problem-formulation} introduces the nested simulation procedure and the standard Monte Carlo estimator.
+Section~\ref{sec1:asymptotic-convergence} provides new theoretical results on the convergence of existing nested simulation procedures.
+Section~\ref{sec1:convergence-orders} summarizes the asymptotic convergence orders and the critical assumptions of nested simulation procedures in the literature.
+Section~\ref{sec1:numerical-experiments} presents the numerical experiments and the comparisons of different nested simulation procedures with respect to different risk measures, problem dimensions, and payoff complexities.
+Section~\ref{sec1:computational-complexity} discusses the computational complexity of different nested simulation procedures.
+Section~\ref{sec1:conclusion} concludes the paper.
 
-\section{Problem Formulation} \label{sec:problem-formulation}
+\section{Problem Formulation} \label{sec1:problem-formulation}
 
@@
 
+\subsection{Multi-level Monte Carlo}
+
+The multi-level Monte Carlo (MLMC) method is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest, and it uses the difference between the approximations to reduce the variance of the estimator.
+The MLMC method is particularly useful when the quantity of interest is expensive to evaluate, and the standard Monte Carlo estimator has a high variance.
+The MLMC method estimates $\rho$ with a multi-level Monte Carlo estimator:
+
+\begin{equation*}
+    \hat{\rho}^{\text{MLMC}}_\Gamma = \sum_{\ell=0}^{L} \left( \frac{1}{M_{\ell}} \sum_{i=1}^{M_{\ell}} h(\hat{g}_{N_{\ell}}(X_{i, \ell})) - \frac{1}{M_{\ell-1}} \sum_{i=1}^{M_{\ell-1}} h(\hat{g}_{N_{\ell-1}}(X_{i, \ell-1})) \right), ~~~ X_{i, \ell} \sim F_X,
+\end{equation*}
+
+where $\hat{g}_N(\cdot) = 0$, $L$ is the number of levels, $M_{\ell}$ is the number of outer scenarios at level $\ell$, and $N_{\ell}$ is the number of inner replications at level $\ell$.
+Applying the analysis of~\cite{giles2015multilevel} in a nested simulation context,~\cite{giles2019multilevel} show that the MLMC method can achieve a similar level of accuracy as the standard nested simulation procedure with a lower total computational budget.
+The simulation budget $\Gamma$ is the sum of the computational budget at each level, that is, $\Gamma = \sum_{\ell=0}^{L} M_{\ell} \cdot N_{\ell}$.
+
 \subsection{Supervised Learning Models}
@@
 Consider the observation pairs $(X_i, \hat{g}_N(X_i))$ for $i \in \{1, \dots, M\}$ as training data, we can use supervised learning to approximate $g(\cdot)$ by $\hat{g}^{\text{SL}}_{M, N}(\cdot)$ and to pool the inner replications from all outer scenarios.
-Using the $M$ \textit{training} samples, a supervised learning-based nested simulation procedure estimates  $\rho$ by
+Using the $M$ \textit{training} samples, a nested Monte Carlo estimator of $\rho$ is given by
 
@@
     \item   Nested expectation form:
-            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = \frac{1}{M} \sum_{i=1}^M h(\hat{g}^{\text{SL}}_{M, N}(\tilde{X}_i)); ~~~ \tilde{X}_i \sim F_X.$$
+            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = \frac{1}{M'} \sum_{i=1}^{M'} h(\hat{g}^{\text{SL}}_{M, N}(\tilde{X}_i)); ~~~ \tilde{X}_i \sim F_X.$$
     \item   VaR:
-            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = (\hat{g}^{\text{SL}}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M \rceil}.$$
+            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = (\hat{g}^{\text{SL}}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M' \rceil}.$$
     \item   CVaR:
-            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = (\hat{g}^{\text{SL}}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M \rceil} + \frac{1}{(1-\alpha) M} \sum_{i=1}^M \max \{\hat{g}^{\text{SL}}_{M, N}(\tilde{X}_i) - (\hat{g}^{\text{SL}}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M \rceil}, 0 \}, $$
-            where $(\hat{g}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M \rceil}$ is the $\lceil \alpha M \rceil$-th order statistic of $\hat{g}^{\text{SL}}_{M, N}(\tilde{X}_1), \dots, \hat{g}_{M, N}(\tilde{X}_M)$.
+            \begin{align*}
+                \hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} & = (\hat{g}^{\text{SL}}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M' \rceil}  \\
+                & + \frac{1}{(1-\alpha) M'} \sum_{i=1}^{M'} \max \{\hat{g}^{\text{SL}}_{M, N}(\tilde{X}_i) - (\hat{g}^{\text{SL}}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M' \rceil}, 0 \}, 
+            \end{align*}
+\end{enumerate}
+where $(\hat{g}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M' \rceil}$ is the $\lceil \alpha M' \rceil$-th order statistic of $\hat{g}^{\text{SL}}_{M, N}(\tilde{X}_1), \dots, \hat{g}_{M, N}(\tilde{X}_{M'})$.
 Note that $\hat{g}^{\text{SL}}_{M, N}(\cdot)$ is derived from the training samples $(X_1, \hat{g}_N(X_1)), \dots, (X_M, \hat{g}_N(X_M))$.
-\end{enumerate}
+
+We are interested in minimizing the MSE of the supervised learning-based nested simulation estimator with supervised learning $\hat{\rho}^{\text{SL}, \text{Train}}_{M, N}$ and $\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'}$ subject to the total simulation budget $\Gamma$.
+
+\begin{align}
+    & \min_{M, N}  & \text{MSE}(\hat{\rho}^{\text{SL}}_{M, N}) = \mathbb{E} \left[ \left( \hat{\rho}^{\text{SL}}_{M, N} - \rho \right)^2 \right] \nonumber \\
+    & \text{subject to} & M \cdot N = \Gamma 
+\end{align}
 
@@
 
-Instead of using a supervised learning model,~\cite{zhang2022sample} uses the likelihood ratio weights to pool the inner replications from all outer scenarios.
-This method is also referred to as importance sampling.
+Instead of using a supervised learning model as proxy,~\cite{zhang2022sample} uses the likelihood ratio weights to pool the inner replications from all outer scenarios.
 Here, we restrict our attention to problems in the nested expectation form whose outer scenarios characterize the stochasticity of the inner simulation model. 
@@
 
-\subsection{Multi-level Monte Carlo}
-
-The multi-level Monte Carlo (MLMC) method is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest, and it uses the difference between the approximations to reduce the variance of the estimator.
-A MLMC approach is particularly useful when the quantity of interest is expensive to evaluate, and the standard Monte Carlo estimator has a high variance.
-Instead of pooling from the inner samples, a MLMC-based nested simulation procedure estimates $\rho$ with a multi-level Monte Carlo estimator:
-
-\begin{equation*}
-    \hat{\rho}^{\text{MLMC}}_\Gamma = \sum_{\ell=0}^{L} \left( \frac{1}{M_{\ell}} \sum_{i=1}^{M_{\ell}} h(\hat{g}_{N_{\ell}}(X_{i, \ell})) - \frac{1}{M_{\ell-1}} \sum_{i=1}^{M_{\ell-1}} h(\hat{g}_{N_{\ell-1}}(X_{i, \ell-1})) \right), ~~~ X_{i, \ell} \sim F_X,
-\end{equation*}
-
-where $\hat{g}_N(\cdot) = 0$, $L$ is the number of levels, $M_{\ell}$ is the number of outer scenarios at level $\ell$, and $N_{\ell}$ is the number of inner replications at level $\ell$.
-Applying the analysis of~\cite{giles2015multilevel} in a nested simulation context,~\cite{giles2019multilevel} show that the MLMC method can achieve a similar level of accuracy as the standard nested simulation procedure with a lower total computational budget.
-The simulation budget $\Gamma$ is the sum of the computational budget at each level, that is, $\Gamma = \sum_{\ell=0}^{L} M_{\ell} \cdot N_{\ell}$.
-
-\subsection{Problem Statement}
-
-For all nested simulation procedures we are interested in the order of convergence of estimators in terms of the total simulation budget $\Gamma$.
-The convergence rate of an estimator is measured by the MSE of the estimator $\hat{\rho}_{M, N}$ about the true value $\rho$.
+With a total simulation budget $\Gamma$, we are interested in the order of convergence of estimators for all nested simulation procedures, which is measured by their MSE about the risk measure $\rho$.
 
 \begin{align}
-    & \text{MSE}(\hat{\rho}_{M, N}) = \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] \nonumber \\
+    & \min ~~~ \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] \nonumber \\
     & \text{subject to} ~~~ M \cdot N = \Gamma, 
@@
 
-where $\Gamma = M \cdot N$ is the total simulation budget\footnote{For a MLMC-based nested simulation procedure, the total simulation budget $\Gamma$ is the sum of the computational budget at all levels.}.
-For a given nested simulation procedure, we are interested in the optimal budget allocation that minimizes the MSE of the estimator $\hat{\rho}_{M, N}$.
+where $\Gamma$ is the total simulation budget for all nested simulation procedures considered in this study.
+A special case is the MLMC method, where the total simulation budget $\Gamma$ is the sum of the computational budget at all levels.
+
+\section{Asymptotic Analysis} \label{sec1:asymptotic-convergence}
+In this section, we summarize the existing asymptotic convergence results of the nested simulation procedures in the literature, and we compare their critical assumptions that guarantee the convergence.
+
+\begin{table}[ht]
+    \centering
+    \footnotesize
+    \begin{tabular}{|l|c|c|c|c|c|}
+    \hline
+    \textbf{Estimator for} $g(X)$ & \textbf{Smooth} $h$ & \textbf{Lipschitz}(\textbf{hockey-stick} $h$) & \textbf{Indicator} $h$ & \textbf{VaR} & \textbf{CVaR} \\
+    \hline
+    Standard Monte Carlo & $\star$ & $\star$($\checkmark$) & $\checkmark$ & $\checkmark$ & $\times$ \\
+    \hline
+    Multi-level Monte Carlo & $\times$ & $\times$($\times$) & $\checkmark$ & $\times$ & $\times$ \\
+    \hline
+    Regression & $\checkmark$ & $\checkmark$($\checkmark$) & $\times$ & $\times$ & $\times$ \\
+    \hline
+    Kernel smoothing & $\checkmark$ & $\times$($\checkmark$) & $\checkmark$ & $\times$ & $\times$ \\
+    \hline
+    Kernel ridge regression & $\Diamond$ & $\times$($\Diamond$) & $\Diamond$ & $\Diamond$ & $\Diamond$ \\
+    \hline
+    Likelihood ratio & $\checkmark$ & $\times$($\checkmark$) & $\checkmark$ & $\times$ & $\times$ \\
+    \hline
+    \end{tabular}
+    \caption{Existing asymptotic convergence results of nested simulation procedures for MSE}
+    \label{tab1:asymConv-mse}
+\end{table}
+
+Table~\ref{tab1:asymConv-mse} summarizes the existing asymptotic convergence results of nested simulation procedures for MSE in the literature.
+A $\checkmark$ indicates there exists an asymptotic convergence result for the corresponding estimator,
+a $\times$ indicates there does not exist an asymptotic convergence result, 
+a $\star$ indicates an asymptotic result is not available in the literature but is provided in this study, and
+a $\Diamond$ indicates the asymptotic convergence result exists in the literature but in a weaker form.
+~\cite{gordy2010nested} provide the asymptotic convergence results for the standard nested simulation procedure with hockey-stick $h$, indicator $h$ and VaR.
+Their CVaR analysis is incomplete as the VaR is assumed to be known but not estimated in the convergence proof.
+When the VaR is known, the CVaR analysis reduces to the nested expectation form with $h$ being a hockey-stick function.
+~\cite{giles2019multilevel} provide the asymptotic convergence results for the MLMC method with an indicator $h$.
+~\cite{broadie2015risk} provide the asymptotic convergence results for the regression-based nested simulation procedure with smooth $h$ and Lipschitz continuous $h$.
+The Lipschitz continuous family includes the hockey-stick function as a special case, thus the convergence result for the hockey-stick function is implied.
+~\cite{hong2017kernel} and~\cite{zhang2022sample} provide the asymptotic convergence results with the nested expectation form for the kernel smoothing-based procedure and likelihood ratio-based nested simulation procedure, respectively.
+The convergence results for a Lipschitz continuous $h$ cannot be directly inferred from the analysis for a hockey-stick function.
+
+While most of the literature focuses on the MSE of the estimator of $\rho$,~\cite{wang2022smooth} analyze the asymptotic convergence of the estimator of $\rho$ in terms of the absolute error.
+Let $\hat{\rho}$ be the estimator of $\rho$. Its absolute error about $\rho$ is defined as
+
+$$
+\mbox{Absolute Error}\left(\hat{\rho}\right) = \left| \hat{\rho} - \rho \right|.
+$$
+
+In~\cite{wang2022smooth}, the authors of the KRR-based nested simulation procedures claim to have bridged the gap between the cubic and square root convergence rates of nested simulation procedures.
+However, they analyze convergence in probabilistic order, and it is only applicable in terms of the absolute error.
+Instead of showing the convergence of the KRR-based estimator in terms of MSE as in~\cite{gordy2010nested}, we show the connections between the convergence in MSE and the convergence in probabilistic order for absolute error.
+Our findings in Section~\ref{sec1:connection-mse-absolute-error} show that the analysis of ~\cite{wang2022smooth} indeed bridges the gap, but only in terms of the absolute error.
+
+\subsection{Connections between Convergence in MSE and Absolute Error} \label{sec1:connection-mse-absolute-error}
+
+This section establishes the connections between the convergence in MSE and the convergence in probabilistic order for absolute error in the context of nested simulation procedures.
+In order to show the connections between the convergence in MSE and the convergence in probabilistic order for absolute error, we first need to state the definition for a sequence of random variables to converge in those two forms.
+
+\begin{definition}
+    Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
+    We write $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-k} \right)$, that is, $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $k$ if 
+    $$
+        \exists C \limsup_{M} \frac{\mathbb{E} \left[\left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-k}} \leq C
+    $$
+\end{definition}
+
+\begin{definition}
+    Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
+    We write $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-k})$, that is $\hat{\rho}_{\Gamma}$ converges in probabilistic order $k$ to $\rho$ if for large enough $\Gamma$,
+    $$
+        \forall \epsilon > 0 \exists C \mathbb{P} \left( \left| \hat{\rho}_{\Gamma} - \rho \right| \geq C \Gamma^{-k} \right) \leq \epsilon 
+    $$
+\end{definition}
+
+We start by showing the convergence in probabilistic order from the convergence in MSE.
+Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-k} \right)$.
+Then, from the definition of convergence in MSE, there exists a constant $C$ such that 
+$$
+    \limsup_{M} \frac{\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-k}} \leq C.
+$$
+Hence, there exists some $\Gamma$ such that for all $\gamma \geq \Gamma$,
+$$
+\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \right] \leq C\gamma^{-k}.
+$$
+The convergence in probabilistic order can be shown by separating the expectation into two parts: tail and non-tail.
+$$
+\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| \leq d\gamma^s\}} \right] + \mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\}} \right] \leq C\gamma^{-k}.
+$$
+The first term is always positive, and the second term can be bounded from below by the indicator function.
+\begin{align*}
+\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\}} \right] 
+& \geq \mathbb{E} \left[ d^2 \gamma^{2s} \cdot \mathbb{I}\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\} \right] \\
+& = d^2 \gamma^{2s} \cdot \mathbb{E} \left[ \mathbb{I}\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \} \right] \\
+& = d^2 \gamma^{2s} \cdot \mathbb{P} \left(|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \right)
+\end{align*}
+
+Combining bounds on the two terms, we have
+
+$$
+    d^2 \gamma^{2s} \mathbb{P} \left(|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \right) \leq C \gamma^{-k}.
+$$
+
+Let $s = -\frac{k}{2}$. Arranging the terms, we have
+
+$$
+    \mathbb{P} \left( |\hat{\rho}_{\gamma} - \rho| > d\gamma^{-\frac{k}{2}} \right) \leq \frac{C}{d^2}
+$$
+
+Hence, for all $\epsilon >0$, there exist $C^* = \sqrt{\frac{C}{\epsilon}}$ such that for all $\gamma \geq \Gamma$,
+
+$$
+    \mathbb{P} \left( |\hat{\rho}_{\gamma} - \rho| > C^*\gamma^{-\frac{k}{2}} \right) \leq \epsilon
+$$
+
+In essence, the above is the definition of convergence in probabilistic order, that is,
+
+$$
+    \left| \hat{\rho}_{\gamma} - \rho \right| = \mathcal{O}_\mathbb{P} \left( \Gamma^{-\frac{k}{2}} \right)
+$$
+
+\begin{theorem} \label{thm1:convergence-mse-prob}
+    Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
+    If $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $k$, then $\hat{\rho}_{\Gamma}$ converges in probabilistic order to $\rho$ in order $\frac{k}{2}$.
+\end{theorem}
+
+To the best of our knowledge, Theorem~\ref{thm1:convergence-mse-prob} has not been explicitly stated in the literature.
+It is the first result that shows the connections between the convergence in MSE and the convergence in probabilistic order for absolute error in the context of nested simulation.
+Theorem~\ref{thm1:convergence-mse-prob} is a general result that can be applied to any nested simulation procedure that converges in MSE to $\rho$ in order $k$.
+If the estimator converges in MSE to $\rho$ in order $k$, then it converges in probabilistic order to $\rho$ in order $\frac{k}{2}$.
+
+While the convergence in MSE implies the convergence in probabilistic order, the converse is not necessarily true.
+Similarly, the above argument is applied in reverse.
+Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-k})$.
+The MSE of $\hat{\rho}_{\Gamma}$ can be separated into the same two parts.
+
+$$
+    \mathbb{E}\left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| \leq d\Gamma^{-2k}\}} \right] + \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^{-2k}\}} \right],
+$$
+where the first term can be bounded from above.
+
+\begin{align*}
+    \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s\}} \right] 
+    & \leq d^2 \Gamma^{-2k} \cdot \mathbb{E} \left[ \mathbb{I}\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s \} \right] \\
+    & = d^2 \Gamma^{-2k} \cdot \mathbb{P} \left(|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s \right) \leq d^2 \Gamma^{-2k} 
+\end{align*}
+However, the second term is not always bounded. 
+If the random variable $\hat{\rho}_{\Gamma}$ admits a density function $f$, then the second term can be further decomposed.
+
+\begin{align*}
+    \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^{-2k}\}} \right] 
+    & = \int_{-\infty}^{-d\Gamma^{-2k}} (x - \rho)^2 f(x) dx + \int_{d\Gamma^{-2k}}^{\infty} (x - \rho)^2 f(x) dx 
+\end{align*}
+Hence, $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $2k$ if and only if both integrals converge in order higher than $2k$. 
+The above argument shows that the convergence in probabilistic order does not necessarily imply the convergence in MSE.
+The convergence in probabilistic order is a weaker form of convergence than the convergence in MSE.
+
+\subsection{Asymptotic Analysis for the Standard Nested Simulation Procedure}
+In~\cite{gordy2010nested}, the authors analyze the asymptotic convergence of the standard nested simulation procedure in terms of MSE. 
+The analysis is complete for the nested expectation form where $h$ is either an indicator function or a hockey-stick function and VaR. 
+For the nested expectation form where $h$ is a smooth function or a Lipschitz continuous function, the analysis is incomplete.
+In this section, we fill in the holes in the analysis of~\cite{gordy2010nested}.
+
+\begin{assumption} \label{as1:sns}
+    $h(g(X))$ has finite second moment, i.e., $\mathbb{E} \left[ \left( h(g(X)) \right)^2 \right] < \infty$.
+\end{assumption}
+
+\begin{assumption} \label{as1:sns-noise}
+    $\hat{g}_N(X) = g(X) + \bar{Z}_N(X)$, where the simulation noise $\bar{Z}_N(X)$ has zero mean and variance $\nu(X) / N$, where the conditional variance $\nu(X)$ is bounded, i.e., there exists $C_{\nu, 1} > 0$ such that $\nu(x) \leq C_{\nu, 1}$ for all $x \in \mathbb{R}$.
+\end{assumption}
+
+Let $\rho_M = \frac{1}{M} \sum_{i=1}^M h(g(X_i))$ be the nested Monte Carlo estimator with the true function $g$.
+The MSE of the standard procedure can be decomposed into two terms.
+
+\begin{align} \label{eq1:mse-sns}
+    & \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] \nonumber \\
+    & \leq 2 \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho_M \right)^2 \right] 
+            + 2  \mathbb{E} \left[ \left(\rho_M - \rho \right)^2 \right]  \nonumber \\
+    & = 2 \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{g}_{N}(X_i) \right) -  \frac{1}{M} \sum_{i=1}^M h\left(g(X_i) \right)  \right)^2\right] \nonumber \\
+    & ~~~~ + 2  \mathbb{E} \left[ \left(\frac{1}{M} \sum_{i=1}^M h\left(g(X_i) \right) - \mathbb{E}\left[ h(g(X))\right] \right)^2 \right]  \nonumber \\
+    & = 2 \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{g}_{N}(X_i) \right) -  h\left(g(X_i) \right)  \right)^2\right] + \frac{2}{M} \text{Var}(h(g(X))) \nonumber \\
+    & = 2 \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{g}_{N}(X_i) \right) -  h\left(g(X_i) \right)  \right)^2\right] + \mathcal{O}(M^{-1}),
+\end{align}
+where the last equality follows from Assumption~\ref{as1:sns}.
+The analysis of the first term is different for smooth and Lipschitz continuous $h$. 
+We will analyze them separately.
+
+\subsubsection*{A Smooth Function $h$}
+\begin{assumption} \label{as1:sns-smooth}
+    The function $h$ has bounded first and second order derivative, i.e., there exists $C_1 > 0$ such that $|h'(x)| \leq C_1$ for all $x \in \mathbb{R}$, and there exists $C_2 > 0$ such that $|h''(x)| \leq C_2$ for all $x \in \mathbb{R}$.
+\end{assumption}
+Assumption~\ref{as1:sns-smooth} is similar to the smoothness assumption in~\cite{wang2022smooth}.
+Since $h$ is a smooth function, Taylor expansion can be applied to the first term in Equation~\ref{eq1:mse-sns}.
+
+\begin{align} \label{eq1:taylor-sns}
+    & \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{g}_{N}(X_i) \right) -  h\left(g(X_i) \right)  \right)^2\right] \nonumber \\
+    & = \mathbb{E} \left[ \left( \frac{1}{M} \sum_{i=1}^M h'\left( g(X_i) \right) \left( \hat{g}_{N}(X_i) - g(X_i) \right) +  \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{g}_{N}(X_i) - g(X_i) \right)^2 \right)^2\right] \nonumber \\
+    & \leq 2 \underbrace{\mathbb{E} \left[ \left( \frac{1}{M} \sum_{i=1}^M h'\left( g(X_i) \right) \left( \hat{g}_{ N}(X_i) - g(X_i) \right) \right)^2\right]}_{S_1} \nonumber \\
+    & ~~~~ + 2 \underbrace{\mathbb{E} \left[ \left( \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{g}_{N}(X_i) - g(X_i) \right)^2 \right)^2\right]}_{S_2}
+\end{align}
+where the last inequality is due to $2ab \leq a^2 + b^2$ for any $a, b \in \mathbb{R}$. 
+For different methods of nested estimation, each of the two terms on the right-hand side of Equation~\ref{eq1:taylor-sns} can be analyzed separately.
+We start with the first term $S_1$.
+
+\begin{align} \label{eq1:s1-sns}
+    S_1 
+    & = \mathbb{E} \left[ \left(\frac{1}{M} \sum_{i=1}^M h'\left( g(X_i) \right) \left( \hat{g}_{N}(X_i) - g(X_i) \right) \right)^2 \right] \nonumber \\
+    & = \mathbb{E} \left[ \left(\frac{1}{M} \sum_{i=1}^M h'\left( g(X_i) \right) \bar{Z}_N(X_i) \right)^2 \right] \nonumber \\
+    & \leq C_1^2 \mathbb{E} \left[ \left(\frac{1}{M} \sum_{i=1}^M \bar{Z}_N(X_i) \right)^2 \right] \nonumber \\
+    & = C_1^2 \mathbb{E} \left[ \frac{1}{M^2} \sum_{i=1}^M \sum_{j=1}^M \bar{Z}_N(X_i) \bar{Z}_N(X_j) \right] \nonumber \\
+    & = C_1^2 \mathbb{E} \left[ \frac{1}{M^2} \sum_{i=1}^M \bar{Z}_N^2(X_i) + \frac{1}{M^2} \sum_{i=1}^M \sum_{j \neq i}^M \bar{Z}_N(X_i) \bar{Z}_N(X_j) \right] \nonumber \\
+    & \leq  \frac{C_1^2 C_{\nu, 1}}{MN} = \mathcal{O}(M^{-1} N^{-1})
+\end{align}
+where the last inequality in Equation~\ref{eq1:s1-sns} is due to Assumption~\ref{as1:sns-noise}, independence of $X_i$ and $X_j$ for $i \neq j$, and the fact that $\mathbb{E} \left[ \bar{Z}_N(X) \right] = 0$.
+It remains to analyze the second term $S_2$, where Assumption \ref{as1:sns-noise-var} is necessary to ensure the existence of the fourth moment of the simulation noise and the convergence of the second term.
+
+\begin{assumption} \label{as1:sns-noise-var}
+    The fourth moment of simulation noise $\bar{Z}_N(X)$ follows $\mathbb{E} \left[ \left( \bar{Z}_N(X) \right)^4 \right] = \nu_2(X) / N^2$, where $\nu_2(X)$ is bounded, i.e., there exists $C_{\nu,2} > 0$ such that $\nu_2(X) \leq C_{\nu,2}$ for all $x \in \mathbb{R}$.
+\end{assumption}
+
+\begin{align} \label{eq1:s2-sns}
+    S_2 & = \mathbb{E} \left[ \left( \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{g}^{\text{SL}}_{M, N}(X_i) - g(X_i) \right)^2 \right)^2\right] \nonumber \\
+    & = \mathbb{E} \left[ \left(\frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \bar{Z}^2_N(X_i) \right)^2 \right] \nonumber \\
+    & \leq C_2^2 \mathbb{E} \left[ \left(\frac{1}{2M} \sum_{i=1}^M \bar{Z}^2_N(X_i) \right)^2 \right] \nonumber \\
+    & = C_2^2 \mathbb{E} \left[ \frac{1}{2M^2} \sum_{i=1}^M \sum_{j=1}^M \bar{Z}^2_N(X_i) \bar{Z}^2_N(X_j) \right] \nonumber \\
+    & = C_2^2 \mathbb{E} \left[ \frac{1}{2M^2} \sum_{i=1}^M \bar{Z}_N^4(X_i) + \frac{1}{2M^2} \sum_{i=1}^M \sum_{j \neq i}^M \bar{Z}_N^2(X_i) \bar{Z}_N^2(X_j) \right] \nonumber \\
+    & \leq  C_2^2 \left(\frac{ C_{\nu, 2} M}{2M^2N^2} + \frac{C_{\nu,1}^2M(M-1)}{2M^2N^2}\right) = \mathcal{O}(N^{-2})
+\end{align}
+where the second inequality is due to Assumption~\ref{as1:sns-smooth}, and the last inequality follows from Assumption~\ref{as1:sns-noise-var} and the fact that $\hat{g}_{N}(X)$ is a standard Monte Carlo estimator of $g(X)$.
+Combining Equation~\ref{eq1:mse-sns},~\ref{eq1:taylor-sns},~\ref{eq1:s1-sns}, and~\ref{eq1:s2-sns}, we have
+
+\begin{equation} \label{eq1:mse-sns-smooth}
+    \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(M^{-1}) + \mathcal{O}(N^{-2})
+\end{equation}
+Setting $M = \mathcal{O}(\Gamma^{2/3})$ and $N = \mathcal{O}(\Gamma^{1/3})$, we provide the same rate of convergence as obtained for other risk measures in~\cite{gordy2010nested}.
+As shown in Section~\ref{sec1:connection-mse-absolute-error}, the convergence in MSE automatically implies the convergence in probabilistic order.
+
+\begin{theorem} \label{thm1:sns-smooth}
+    Let $h$ be a smooth function. 
+    MSE of the standard nested simulation procedure converges in order $\Gamma^{2/3}$, that is,
+    $$\mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(\Gamma^{-2/3}).$$
+\end{theorem}
+The proof techniques used in deriving Theorem~\ref{thm1:sns-smooth} is completely different from the one used in~\cite{gordy2010nested}.
+The analysis in~\cite{gordy2010nested} is based on the differentiablity of the joint density of $Y$ and the average inner simulation noise, which is difficult to verify in practice.
+Instead, we use the Taylor expansion of the smooth function $h$ to analyze the convergence of the standard nested simulation procedure.
+The critical assumption in our derivation is Assumption~\ref{as1:sns-noise-var}, which is necessary to ensure the existence of the fourth moment of the simulation noise and the convergence of $S_2$, the second order term in the Taylor expansion.
+Assumption~\ref{as1:sns-noise-var} is a moment condition that is easier to verify in practice than conditions on the joint density.
+As stated in Theorem~\ref{thm1:convergence-mse-prob}, the convergence in MSE automatically implies the convergence in probabilistic order.
+
+\begin{corollary}
+    Let $h$ be a smooth function. 
+    The absolute error of the standard nested simulation procedure converges in probabilistic order $\Gamma^{-1/3}$, that is,
+    $$\left| \hat{\rho}_{M, N} - \rho \right| = \mathcal{O}_\mathbb{P}(\Gamma^{-1/3}).$$
+\end{corollary}
+
+\subsubsection*{A Lipschitz Continuous Function $h$}
+We proceed to analyze the convergence for a Lipschitz continuous function $h$.
+For the CVaR analysis in~\cite{gordy2010nested}, the authors assume the knowing of the corresponding VaR.
+Hence, the analysis of CVaR is not complete.
+Instead, the quantity that is being analyzed is instead the mean excess loss, which corresponds to $h$ being a hockey-stick function and belongs to the family of the Lipschitz continuous functions. 
+Here we present the convergence analysis for the whole family of the Lipschitz continuous functions, which includes the hockey-stick function as a special case.
+
+\begin{assumption} \label{as1:sns-lip}
+    The function $h$ is Lipschitz continuous. Hence, $|h(x_1) - h(x_2) \leq K|x_1 - x_2|$ for some constant $K< \infty$.
+\end{assumption}
+Assumption~\ref{as1:sns-lip} is a standard assumption for analysis involving Lipschitz continuous functions, and it is also used in~\cite{broadie2015risk}.
+For the Lipschitz continuous case, the first term in Equation~\ref{eq1:mse-sns} is analyzed differently.
+
+\begin{align}
+    \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{g}_{N}(X_i) \right) -  h\left(g(X_i) \right)  \right)^2\right]    
+    & \leq \mathbb{E} \left[ \left( h\left( \hat{g}_{N}(X) \right) -  h\left(g(X) \right)  \right)^2\right]  \nonumber \\
+    & \leq K^2 \mathbb{E} \left[ \left( \hat{g}_{N}(X) -  g(X)  \right)^2\right] \nonumber \\
+    & = K^2 \mathbb{E} \left[ \left( \bar{Z}_{N}(X) \right)^2\right] = \mathcal{O}(N^{-1})
+\end{align}
+where the first inequality follows from Cauchy-Schwarz inequality, the second equality follows from Assumption~\ref{as1:sns-lip}, and the last equality follows from Assumption~\ref{as1:sns-noise}.
+
+\begin{equation}
+    \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(M^{-1}) + \mathcal{O}(N^{-1})
+\end{equation}
+Setting $M = \mathcal{O}(\Gamma^{1/2})$ and $N = \mathcal{O}(\Gamma^{1/2})$, we provide a looser bound than the one obtained for hockey-stick $h$.
+
+\begin{theorem}
+    Let $h$ be a Lipschitz continuous function. 
+    MSE of the standard nested simulation procedure converges in order $\Gamma^{1/2}$, that is,
+    $$\mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(\Gamma^{-1/2}).$$
+\end{theorem}
+
+Immediately from Theorem~\ref{thm1:convergence-mse-prob}, the convergence in MSE automatically implies the convergence in probabilistic order.
+
+\begin{corollary}
+    Let $h$ be a Lipschitz continuous function. The absolute error of the standard nested simulation procedure converges in probabilistic order $\Gamma^{-1/4}$, that is,
+    $$\left| \hat{\rho}_{M, N} - \rho \right| = \mathcal{O}_\mathbb{P}(\Gamma^{-1/4}).$$
+\end{corollary}
+
+\subsection{Asymptotic Analysis of a kNN-based Nested Simulation Procedure for a Smooth Function}
+
+In~\cite{hong2017kernel}, the authors analyze the asymptotic convergence in terms of MSE for a kernel smoothing-based nested simulation procedure.
+The analysis is complete for the nested expectation form where $h$ is either a smooth function, an indicator function, or a hockey-stick function.
+The kernel function of interest in the asymptotic analysis is the Nadaraya-Watson kernel.
+Nevertheless, the numerical results are derived based on a kNN-based nested simulation procedure.
+In this section, we attempt to fill in the holes in the analysis of~\cite{hong2017kernel} by providing the asymptotic convergence of a kNN-based nested simulation procedure for smooth $h$ in the nested expectation form.
+Surprisingly, the asymptotic convergence rate of the kNN-based nested simulation procedure is noticeably different from the result obtained in~\cite{hong2017kernel}.
+
+A kNN regression is a non-parametric method that estimates the conditional expectation of $Y$ given $X$ by averaging the $Y$ values of the $k$ nearest neighbors of $X$.
+Without loss of generality, we assume that $\{(X_i, \bar{Y}_{n, i}), i = 1, \dots, M\}$ are independent and identically distributed (i.i.d.) observations of $(X, Y)$ from the standard nested simulation procedure with an inner simulation budget of $n$, where $X_i$ is the $i^{\text{th}}$ of the outer scenario $X \in \Omega \subset \mathbb{R}^d$, and $\bar{Y}_{n, i}$ is the estimate of $Y|X_i$ with an inner simulation budget of $n$.
+Let $f_{XY}(x, y)$ be the joint density of random vector $(X, Y)$, and $f_X(x) = \int f_{XY}(x, y) dy$ be the marginal density of $X$.
+Let $k$ be a sequence of positive integers $k = k(M)$ such that 
+\begin{align*}
+    k                   & \rightarrow \infty \\
+    \frac{k}{M}         & \rightarrow 0, ~~~ \text{as} ~ M \rightarrow \infty. \\
+    \frac{\log(M)}{k}   & \rightarrow 0, ~~~ \text{as} ~ k \rightarrow \infty.
+\end{align*}
+A kNN-based nested simulation procedure with model parameter $k$ estimates the risk measure $\rho = \mathbb{E} \left[ h(g(X)) \right]$ with
+
+\begin{align*}
+\hat{\rho}^{\text{kNN}, \text{Test}}_{M, n, M'} 
+& = \frac{1}{M'} \sum_{i=1}^{M'} h(\hat{g}^{\text{kNN}}_{M, n}(\tilde{X}_i)); ~~~ \tilde{X}_i \sim F_X, \\
+\hat{g}^{\text{kNN}}_{M, n}(x) 
+& = \frac{\frac{1}{M R_k^d} \sum_{i=1}^M K\left(\frac{x - X_i}{R_k}\right) \bar{Y}_{n, i}}{\frac{1}{M R_k^d} \sum_{i=1}^M K\left(\frac{x - X_i}{R_k}\right)}
+\end{align*}
+
+where $R_k$ is the Euclidean distance between $X_i$ and its $k^{\text{th}}$ nearest neighbor, and $K(\cdot)$ is the kernel function satisfying
+
+\begin{align*}
+    \int K(u) du & = 1, \\
+    K(u) &= 0 ~~~ ~\text{for}~ \|u\| \geq 1,
+\end{align*}
+
+where $\|\cdot\|$ is the Euclidean norm.
+For a kNN estimator trained with $M$ i.i.d. observations, denote $B_M(x)$ and $V_M(x)$ as its bias and variance at point $x$, respectively.
+
+\begin{assumption} \label{as1:knn}
+    $f_X$ is bounded and continuously differentiable up to second order in a neighborhood of $x$ with $f_X(x) > 0$, $f_X$, $\mathbb{E} \left[ Y^2| X = x \right] < \infty$, and the kernel function $K$ satisfies
+    \begin{align*}
+        \int \|u\|^2  |K(u)| du & < \infty, \\
+        \int \nu_\alpha K(u) du & = 0, ~~~ \text{for}~ \alpha = 1, \dots, d.
+    \end{align*}
+    Suppose $\mathbb{P}(\|x - X\| > r) = \mathcal{O}(r^{-\alpha})$ for some $\alpha > 0$ as $r \rightarrow \infty$.
+\end{assumption}
+
+The following lemma from~\cite{mack1981local} characterizes the pointwise convergence of the kNN estimator in terms of its bias and variance at point $x$.
+
+\begin{lemma}
+    Assume the random vector $(X, Y)$ and the kernel function $K$ satisfies Assumption~\ref{as1:knn}. Then the bias and variance of the kNN estimator at point $x$ are given by
+    \begin{align*}
+        B_M(x) & = A_{\text{kNN}}(x) \cdot \left( \left( \frac{k}{M} \right)^\frac{2}{d} + o \left( \frac{k}{M} \right)^\frac{2}{d} \right) + B_{\text{kNN}} \cdot \left(\frac{1}{k} + o\left(\frac{1}{k}\right)\right), \\
+        V_M(x) & = \frac{C_{kNN} \cdot \text{Var}[Y| X = x]}{k} \int K^2(u) du + o\left(\frac{1}{k}\right).
+    \end{align*}
+\end{lemma}
+
+Let $h$ be a smooth function, i.e., Assumption~\ref{as1:sns-smooth} holds.
+The bias of the estimator of $\rho$ for a kNN-based nested simulation procedure is analyzed following Taylor expansion.
+\begin{align} \label{eq1:bias-knn}
+    & \mathbb{E} \left[ h(\hat{g}^{\text{kNN}}_{M, n}(X)) - h(g(X)) \right] \nonumber \\
+    & = \mathbb{E} \left[ h'(g(X)) \left( \hat{g}^{\text{kNN}}_{M, n}(X) - g(X) \right) + \frac{1}{2} h''(z) \left( \hat{g}^{\text{kNN}}_{M, n}(X) - g(X) \right)^2 \right] 
+\end{align}
+where the bias is decomposed into two terms, and $z$ is between $\hat{g}^{\text{kNN}}_{M, n}(X)$ and $g(X)$.
+The first term in Equation~\ref{eq1:bias-knn} is 
+\begin{align} \label{eq1:bias-knn-1}
+    & ~~~~ \mathbb{E} \left[ h'(g(X)) \left( \hat{g}^{\text{kNN}}_{M, n}(X) - g(X) \right) \right]  \nonumber \\
+    & = \mathbb{E} \left[ h'(g(X)) \mathbb{E}\left[ \hat{g}^{\text{kNN}}_{M, n}(X) - g(X) |X\right] \right] \nonumber \\
+    & = \int_{\Omega} h'(g(x)) B_M(x) f_X(x) dx \nonumber \\
+    & = \int_{\Omega} h'(g(x)) \left( A_{\text{kNN}}(x) \left(\frac{k}{M}\right)^{2/d} \left(1+o_x(1)\right) + B_{\text{kNN}} \cdot \left(\frac{1}{k} + o_x\left(\frac{1}{k}\right)\right) \right) f_X(x) dx \nonumber \\
+    & = \left(\frac{k}{M}\right)^{2/d} \mathbb{E} \left[ h'(g(X)) A_{\text{kNN}}(X) \right] (1+ o(1)) + \frac{B_{\text{kNN}}}{k} \mathbb{E} \left[ h'(g(X)) \right] (1+ o(1)).
+\end{align}
+
+The second term in Equation~\ref{eq1:bias-knn} is 
+\begin{align} \label{eq1:bias-knn-2}
+    & ~~~~ \mathbb{E} \left[ h''(z) \left( \hat{g}^{\text{kNN}}_{M, n}(X) - g(X) \right)^2 \right]  \nonumber \\
+    & = \int_{\Omega} h''(g(z)) \left(B_M^2(X) + V_M(x)\right) f_X(x) dx \nonumber \\
+    & \leq C_2 \int_{\Omega} \left( \frac{C_{\text{kNN}} \cdot \text{Var}[Y| X = x]}{k} \int K^2(u) du + o\left(\frac{1}{k}\right) \right) f_X(x) dx \nonumber \\
+    & + C_2 \int_{\Omega} \left( A_{\text{kNN}}(x) \left(\frac{k}{M}\right)^{2/d} \left(1+o_x(1)\right) + B_{\text{kNN}} \cdot \left(\frac{1}{k} + o_x\left(\frac{1}{k}\right)\right) \right)^2 f_X(x) dx
+\end{align}
+
+where the second term in Equation~\ref{eq1:bias-knn-2} is of higher order than Equation~\ref{eq1:bias-knn-1}, and it is negligible since $kM^{-1} \rightarrow 0$ as $M \rightarrow \infty$ and $k \rightarrow \infty$,
+The first term in Equation~\ref{eq1:bias-knn-2} is $\mathcal{O}\left(\frac{1}{k}\right)$.
+Set $k = \mathcal{O}(M^{\frac{2}{2+d}})$ and $M = \mathcal{O}(\Gamma)$, the bias of the kNN-based nested simulation procedure converges in the order of $\Gamma^{-\frac{2}{2+d}}$.
+
+\begin{definition} \label{def:knn-smooth-bias}
+    Let $h$ be a smooth function. 
+    The bias of the kNN-based nested simulation procedure converges in the order of $\Gamma^{-\frac{2}{2+d}}$, that is,
+    $$ \mathbb{E} \left[ h(\hat{g}^{\text{kNN}}_{M, n}(X)) - h(g(X)) \right]  = \mathcal{O}(\Gamma^{-\frac{2}{2+d}}).$$
+\end{definition}
+
+Definition~\ref{def:knn-smooth-bias} is obtained by matching the orders of the bias terms in Equation~\ref{eq1:bias-knn-1} and~\ref{eq1:bias-knn-2}.
+It is the tightest bound that can be obtained for the convergence of the kNN-based nested simulation procedure with a smooth function $h$.
+The variance is left for future work.
+It implies that the kNN-based nested simulation procedure converges at most in the order of $\Gamma^{-\frac{2}{3}}$ for $d = 1$ and has slower convergence than the standard procedure for $d \geq 2$.
+Asymptotically, it has slower convergence than the result obtained in~\cite{hong2017kernel} for the Nadaraya-Watson kernel.
+This discrepancy underscores the critical importance of aligning theoretical analysis with numerical illustrations.
+The slower convergence rate observed with the kNN approach not only challenges the robustness of empirical findings derived under differing assumptions but also signals a cautionary note for practitioners.
+This alignment is crucial for ensuring the reliability and validity of conclusions drawn from such procedures, especially in the context of risk management and financial decision-making.
+
+\section{Convergence Orders and Critical Assumptions of Nested Simulation Procedures}
+\label{sec1:convergence-orders}
+
+In this section, we summarize the convergence orders and the critical assumptions of the nested simulation procedures.
+The results are summarized in~\ref{tab1:asymConv-order}, where the orders of convergence are presented in the order of the total simulation budget $\Gamma$.
+
+\begin{table}[ht]
+    \centering
+    \tiny
+    \begin{tabular}{|l|c|c|c|c|c|}
+    \hline
+    \textbf{Estimator for} $g(X)$ & \textbf{Smooth} $h$ & \textbf{Lipschitz} / \textbf{hockey-stick} $h$ & \textbf{Indicator} $h$ & \textbf{VaR} & \textbf{CVaR} \\
+    \hline
+    Standard Monte Carlo & $\mathcal{O}(\Gamma^{-2/3})$ & $\mathcal{O}(\Gamma^{-1/2})$ / $\mathcal{O}(\Gamma^{-2/3})$ & $\mathcal{O}(\Gamma^{-2/3})$ & $\mathcal{O}(\Gamma^{-2/3})$ & $\times$ \\
+    \hline
+    Multi-level MC & $\times$ & $\times$ / $\times$ & $\mathcal{O}(\Gamma^{-1}|\log(\Gamma)|
+    )$ & $\times$ & $\times$ \\
+    \hline
+    Regression & $\mathcal{O}(\Gamma^{-1})$ & $\mathcal{O}(\Gamma^{-1})$/$\mathcal{O}(\Gamma^{-1})$ & $\times$ & $\times$ & $\times$ \\
+    \hline
+    Kernel smoothing & $\mathcal{O}(\Gamma^{-\min\{1, \frac{4}{d+2}\}})$ & $\times$ / $\mathcal{O}(\Gamma^{-\min\{1, \frac{4}{d+2}\}})$ & $\mathcal{O}(\Gamma^{-\min\{1, \frac{4}{d+2}\}})$ & $\times$ & $\times$ \\
+    \hline
+    Kernel ridge regression & $\mathcal{O}(\Gamma^{-1})$ & $\times$ / $\mathcal{O}(\Gamma^{-1})$ & $\mathcal{O}(\Gamma^{-1})$ & $\mathcal{O}(\Gamma^{-1})$ & $\mathcal{O}(\Gamma^{-1})$ \\
+    \hline
+    Likelihood ratio & $\mathcal{O}(\Gamma^{-1})$ & $\times$ / $\mathcal{O}(\Gamma^{-1})$ & $\mathcal{O}(\Gamma^{-1})$ & $\times$ & $\times$ \\
+    \hline
+    \end{tabular}
+    \caption{Asymptotic rate of convergence of nested simulation procedures in MSE}
+    \label{tab1:asymConv-order}
+\end{table}
+
+The asymptotic convergence rate of the nested simulation procedures is highly dependent on the assumptions on the random variable $X$, $Y$, and the inner simulation noise.
+As more advanced supervised learning techniques are used to estimate the function $g$, a more restrictive set of assumptions is required to ensure the asymptotic convergence of the inner estimators.
+In this section, we summarize the pivotal assumptions regarding the random variables and the inner simulation noise for all nested simulation procedures. 
+They are presented in an order reflecting their relative ease in satisfying the assumptions.
+
+\subsection{Standard Assumptions}
+~\cite{gordy2010nested} and~\cite{broadie2015risk} assume that the inner simulation noise has zero mean and variance that is inversely proportional to the inner simulation budget $N$, i.e., Assumption~\ref{as1:sns-noise}.
+The analysis in~\cite{gordy2010nested} further requires assumptions on $f_{Y,\tilde{Z}_N}(y,z_N)$, the joint density of random variable $Y$ and the normalized inner simulation noise $\tilde{Z}_N := \sqrt{N} \cdot\bar{Z}_N(X)$.
+
+\subsection{Assumptions on Joint Density}
+
+\begin{assumption} \label{as1:sns-joint-density}
+    The joint density $f_{Y,\tilde{Z}_N}(y,z_N)$ and its partial derivatives 
+    $\frac{\partial f_{Y,\tilde{Z}_N}(y,z_N)}{\partial y}$ and $\frac{\partial^2 f_{Y,\tilde{Z}_N}(y,z)}{\partial y^2}$ exist.
+\end{assumption}
+
+\begin{assumption} \label{as1:sns-joint-density-bound}
+    For $N \geq 1$, there exist non-negative functions $p_{0, N}(\cdot)$, $p_{1, N}(\cdot)$, and $p_{2, N}(\cdot)$ such that for all $y$ and $z$,
+    \begin{align*}
+        f_{Y,\tilde{Z}_N}(y,z) & \leq p_{0, N}(z) \\
+        \left| \frac{\partial f_{Y,\tilde{Z}_N}(y,z)}{\partial y} \right| & \leq p_{1, N}(z) \\
+        \left| \frac{\partial^2 f_{Y,\tilde{Z}_N}(y,z)}{\partial y^2} \right| & \leq p_{2, N}(z).
+    \end{align*}
+    In addition, 
+    \begin{equation}
+        \sup_N \int_{-\infty}^{\infty} |z|^r p_{i, N}(z) dz < \infty
+    \end{equation}
+    for $i = 0, 1, 2$ and $r \in [0, 4]$.
+\end{assumption}
+
+Assumption~\ref{as1:sns-joint-density} and~\ref{as1:sns-joint-density-bound} are necessary for the Taylor expansion up to the second order on the joint density $f_{Y,\tilde{Z}_N}(y,z_N)$, and they can easily be satisfied by perturbing $Y$ and $\tilde{Z}_N$ with a zero-mean normal random variable with a small variance.
+However, Assumption~\ref{as1:sns-joint-density-bound} is hard to be verified in practice.
+Since~\cite{broadie2015risk} only analyze the nested expectation case with smooth and Lipschitz continuous function $h$, the regression-based nested simulation procedure does not require Assumption~\ref{as1:sns-joint-density} and~\ref{as1:sns-joint-density-bound} for the convergence analysis.
+In our analysis of the standard nested simulation procedure for smooth $h$ in the nested expectation form, we make additional assumptions on the fourth moment of the inner simulation noise, i.e., Assumption~\ref{as1:sns-smooth}, so the second-order term in the Taylor expansion can be bounded.
+
+\subsection{Assumptions for the Multi-level Monte Carlo Procedure}
+In addition to Assumption~\ref{as1:sns-joint-density-bound}, the multi-level Monte Carlo procedure requires assumptions on the random variable $Q:= \frac{|\mathbb{E} \left[ Y | X \right]|}{\text{Var}[Y|X]}$.
+
+\begin{assumption} \label{as1:mlmc-q}
+    $f_Q$, the density of $Q$ exists, and there exist positive constants $q_0$ such that $f_Q(q) \leq q_0$ for all $q \in [0, q_0]$.
+\end{assumption}
+
+Assumption~\ref{as1:mlmc-q} ensures that the conditional expectation of $Y$ given $X$ is not concentrated around zero, as ~\cite{giles2019multilevel} show the asymptotic convergence of the multi-level Monte Carlo procedure only when $\rho$ is in the nested expectation form with $h$ being an indicator function, i.e., $h(x) = \mathbb{I}_{\{x \geq 0\}}$.
+
+\subsection{Assumptions for the Likelihood Ratio-Based Procedure}
+In addition to Assumption~\ref{as1:sns-joint-density-bound}, the likelihood ratio-based nested simulation procedure requires assumptions on the marginal density of $H$, the random variable that characterizes the stochasticity of the inner simulation model.
+More specifically, for the likelihood ratio-based nested simulation procedure, the random variable $H$ is introduced to represent the inner simulation noise, and $Y$ can be directly expressed as a function of $H$ and $X$, i.e., $Y = Y(H, X)$.
+Instead of simulating $Y$ directly, the random variable $H$ is simulated from the conditional distribution $f_{H|X}(y|x)$, and $Y$ is then obtained by evaluating $Y(H, X)$.
+
+\begin{assumption} \label{as1:likelihood-ratio-marginal-density}
+    The marginal density $f_H(y)$ of $H$ exists. $f_H(y)$ can be sampled from and evaluated, and $Y(y, x) f_{H|X}(y|x) = 0$ whenever $f_H(x) = 0$. 
+\end{assumption}
+
+Furthermore, the likelihood ratio-based nested simulation procedure requires the samples of $H$ to be independent with the outer scenario $X$.
+
+\begin{assumption} \label{as1:likelihood-ratio-independence}
+    The inner sample $H \sim f_H(y)$ is independent of $X$. Samples $\{X_i, i=1,\ldots,M\}$ and $\{H_i, i=1,\ldots,N\}$ are i.i.d. samples from $f_X(x)$ and $f_H(y)$, respectively.
+\end{assumption}
+
+Assumption~\ref{as1:likelihood-ratio-independence} is necessary for $\hat{g}^{\text{LR}}_N(X_i)$ to be an unbiased and strongly consistent estimator of $g(X_i)$, which is a necessary condition for the convergence of $\hat{\rho}^{\text{LR}}_{M,N}$, the likelihood ratio-based nested simulation estimator of $\rho$.
+Assumption~\ref{as1:likelihood-ratio-marginal-density} and Assumption~\ref{as1:likelihood-ratio-independence} are likely to be satisfied in practice, as one can simulate $H$ separately from $X$ and evaluate $Y(H, X)$ for each pair of $(H, X)$.
+
+\subsection{Assumptions for the Kernel-Based Procedure}
+For the kernel-based nested simulation procedure,~\cite{hong2017kernel} simplifies the analysis by assuming that for each $X_i$, the inner simulation budget $N$ is fixed together with the variance of the inner simulation noise $\bar{Z}_N(X_i)$.
+In essence, this fixed variance design treats the $(X_i, \bar{Y}_{N, i})$ as independent and identically distributed observations of $(X, Y)$, and the kernel-based nested simulation procedure is analyzed as a nonparametric regression problem.
+Regularity conditions on $f_X(x)$, the density of $X$, and the conditional second moment of $Y$ are assumed to ensure the convergence of $\hat{g}^{\text{KS}}_{M, N}(X)$, the kernel smoothing estimator of $g(X)$.
+
+\begin{assumption}
+    $f_X(x)$ and $\mathbb{E} \left[ Y^2 | X = x \right]$ exist, $f(x) > 0$, and $f(x)$ is thrice continuously differentiable at $x$ with bounded third-order derivative.
+\end{assumption}
+
+Further assumptions are made on the kernel function $K_w$ and the bandwidth $w$ to ensure the convergence of the kernel smoothing estimator $\hat{g}^{\text{KS}}_{M, N}(X)$.
+% A similar set of assumptions is made in~\cite{jennen1988unifying} for the convergence analysis of a kernel smoothing estimator with kernel functions of higher orders.
+
+\subsection{Assumptions for the KRR-Based Procedure}
+For the KRR-based nested simulation procedure, the convergence is guaranteed only when $\bar{Z}_N(X)$ is the sum of $N$ i.i.d. zero-mean sub-Gaussian random variables.
+The sub-Gaussian assumption imposes a stronger condition on the inner simulation noise than all the other nested simulation procedures.
+The inner simulation noise is assumed to have lighter tails than the normal distribution, while examples of random variables that satisfy the sub-Gaussian assumption are hard to find.
+In addition, the following assumptions are made on $\Omega$, the domain of the outer scenario $X$:
+
+\begin{assumption} \label{as1:krr-domain}
+    $\Omega$ is a bounded subset of $\mathbb{R}^d$, and $f_X(x)$ is bounded above and below away from zero.
+\end{assumption}
+
+Assumption~\ref{as1:krr-domain} rules out the possibility of the outer scenario $X$ being a normal random variable, which is a common assumption in the literature.
+Furthermore, the convergence analysis of the KRR-based nested simulation procedure is shown in terms of the absolute error rather than the standard metric of MSE, which is due to the complexity of the KRR method itself.
+
+\section{Finite-Sample Experiments} \label{sec1:numerical-experiments}
+The theoretical framework has allowed the comparison of the asymptotic convergence behavior for different nested simulation procedures.
+However, a simulation budget in practice is almost always finite.
+In this section, we conduct a series of numerical experiments to compare the empirical convergence of the nested simulation procedures for different risk measures, option types, and asset dimensions.
+Numerical experiments are conducted on portfolios that consist of options on $d$ underlying assets, whose dynamics follow a multidimensional geometric Brownian motion with $0.3$ pairwise correlation.
+6 nested simulation procedures are considered, namely the standard nested simulation procedure, the multi-level Monte Carlo procedure, the regression-based, kernel smoothing-based, likelihood ratio-based, and kernel ridge regression-based nested simulation procedures.
+For the standard nested simulation procedure, the bootstrap-based budget allocation strategy from~\cite{zhang2021bootstrap} is implemented to estimate the optimal values of outer and inner simulation budgets.
+For the regression proxy, the Laguerre polynomials up to degree $3$ are used as the basis functions.
+The kNN proxy is implemented for the kernel smoothing-based procedure, and a cross-validation with grid search is used to find the optimal number of neighbors.
+The KRR proxy is implemented with a Mat\'ern kernel, and the smoothness, the length scale, and the regularization hyperparameters are found by a cross-validation with Bayesian search~\citep{frazier2018bayesian}.
+The procedures are compared for 5 types of risk measures, namely a quadratic tracking error, a mean excess loss over threshold $u$, a probability of a large loss over threshold $u$, th VaR, and the CVaR, where the threshold $u$ is set to be the 90\% VaR.
+The procedures are compared for different portfolios.
+\begin{itemize}
+    \item   Portfolio 1 considers $d$ assets.
+    The portfolio contains 3 European call options written on each asset with strikes $90$, $100$, and $110$, respectively. 
+    \item   Portfolio 2 considers $d$ assets.
+    The portfolio contains 3 geometric Asian options written on each asset with strikes $90$, $100$, and $110$, respectively. 
+    \item   Portfolio 3 considers $d$ assets.
+    The portfolio contains 3 up-and-out barrier call options written on each asset with strikes $90$, $100$, and $110$, respectively. They have a barrier level of $120$.
+    \item   Portfolio 4 considers $d$ assets.
+    The portfolio contains 3 down-and-out barrier call options written on each asset with strikes $90$, $100$, and $110$, respectively. They have a barrier level of $90$.
+    \item   Portfolio 5 contains 1 asset.
+    The portfolio longs 2 down-and-out barrier put options and shorts 1 barrier down-and-out put option. 
+\end{itemize}
+Except for portfolio 5, 5 different asset dimensions are considered, i.e., $d = 1, 2, 5, 10, 20$, while we only consider $d=1$ for portfolio 5. 
+525 experimental settings that arise from an exhaustive combination of the above simulation procedures, risk measures, portfolios, and asset dimensions are generated.
+For each of the scenarios, the estimation of the risk measure is repeated 1000 times to obtain the empirical MSE of the corresponding estimator under a range of simulation budgets.
+The total simulation budget $\Gamma$ ranges from $10,000$ to $10,240,000$ in a geometric progression with a common ratio of $2$.
+The empirical convergence results of each estimator are measured and recorded to illustrate their empirical behavior under different risk measures, option types, and asset dimensions.
+We start by examining the empirical convergence results for the most basic case, i.e., the quadratic tracking error risk measure for European call options on Portfolio 1 with $d = 1$.
+
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.7\textwidth]{./project1/figures/figure1.png}
+    \caption{Empirical convergence of nested simulation procedures for quadratic tracking error on Portfolio 1 with $d=1$}
+    \label{fig1:compareAll} 
+\end{figure}
+In Figure~\ref{fig1:compareAll}, the MSEs of the nested simulation procedures are plotted against the total simulation budget $\Gamma$ in a log-log scale, where each point represents the average MSE of the corresponding estimator over 1000 replications.
+The MSEs of the nested simulation procedures are fitted with a regression line, and the slope of the fitted line is reported as the first number in the legend.
+The second number in the legend is the corresponding asymptotic rate of convergence obtained from the theoretical analysis.
+The slope of the fitted line can be regarded as the empirical rate of convergence of the corresponding procedure.
+By comparing the empirical rates of convergence with the asymptotic rates, we can observe that the empirical rates of convergence of the standard, the kernel smoothing-based, the regression-based, the likelihood ratio-based, and the KRR-based procedures all closely match their asymptotic rates.
+Due to the computational complexity of the likelihood ratio-based and the KRR-based procedures, their MSEs are not reported for $\Gamma$ larger than $16,000$ and $64,000$, respectively.
+Due to the difficulty of fixing $\Gamma$ for the multi-level Monte Carlo procedure, the empirical rate of convergence of the multi-level Monte Carlo procedure is not reported here, but a detailed analysis of the empirical convergence of the multi-level Monte Carlo procedure is provided in Section~\ref{sec1:empirical-mlmc}.
+In the following sections, we examine the empirical convergence of the nested simulation procedures in a similar manner as in Figure~\ref{fig1:compareAll}.
+With a more detailed analysis of different risk measures, option types, and asset dimensions, we aim to provide a comprehensive understanding of the convergence behavior of the nested simulation procedures in practice.
+
+\subsection{Sensitivity to the Asset Dimension} \label{sec1:sensitivity-dimension}
+In portfolio risk management, the asset dimension is a critical factor that determines the complexity of the portfolio and the computational cost of the risk measure estimation.
+The theoretical analyses in Section~\ref{sec1:convergence-orders} suggest that the asymptotic rate of convergence of the nested simulation procedures, except for the kernel smoothing-based procedure, is independent of the asset dimension.
+However, the empirical convergence behavior of the nested simulation procedures could be sensitive to the asset dimension.
+In this section, we examine the empirical convergence of the nested simulation procedures for different asset dimensions.
+
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure2a.png}
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure2b.png}
+    \caption{Empirical convergence of nested simulation procedures for quadratic tracking error on Portfolio 1 with different asset dimensions}
+    \label{fig1:assetDimension} 
+\end{figure}
+
+In Figure~\ref{fig1:assetDimension}, the empirical convergence of the nested simulation procedures for a quadratic tracking error on Portfolio 1 is illustrated for different asset dimensions, i.e., $d = 2$ and $d = 20$.
+The empirical rates of convergence of the standard, the KRR-based, and the likelihood ratio-based procedures closely match their asymptotic rates for both asset dimensions, and they are independent of the asset dimension.
+On the other hand, the empirical rates of convergence of the kernel smoothing-based and regression-based procedures are higher than their asymptotic rates for both asset dimensions.
+They are sensitive to the asset dimension but in different ways.
+The empirical rate of convergence of the kernel smoothing-based procedure decreases as the asset dimension increases.
+This phenomenon is consistent with the theoretical analysis in Section~\ref{sec1:asymptotic-convergence}, where the asymptotic rate of convergence of the kernel smoothing-based procedure is shown to be sensitive to the asset dimension.
+However, the empirical rate is still higher than its asymptotic rate for $d = 2$ and $d = 20$.
+The empirical rates of convergence of the regression-based procedure is higher than its asymptotic rates for both asset dimensions, and the empirical rate is higher for $d = 20$ than for $d = 2$.
+
+\subsection{Empirical Convergence of Parametric Regression Procedures} \label{sec1:regression-convergence}
+
+For both the regression-based and the kernel smoothing-based procedures, the reason for the higher empirical rates can be explained by having poor proxy estimators for smaller simulation budgets.
+For lower simulation budgets, the proxy estimators of the true inner simulation are poor, and the MSEs of the regression-based and kernel smoothing-based procedures are dominated by the model error of the proxy estimators.
+In other words, they have not reached their asymptotic regimes yet.
+Due to computation constraints, we are not able to conduct experiments for kernel smoothing-based nested simulation procedures for higher budget levels, but we are able to conduct additional experiments for the regression-based nested simulation procedure.
+In our previous numerical experiments, the empirical rate of convergence of the regression procedure is observed to be much larger than its asymptotic rate of convergence.
+For dimensions larger than 10, the MSE of the regression procedure decreases quickly in the beginning, and it stabilizes after a certain budget level.
+In~\ref{fig1:reg_lb} illustrates the empirical convergence of the regression-based procedure in more detail at higher simulation budgets, where the asymptotic level of convergence is reached for $d = 20$.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.7\textwidth]{./project1/figures/figure3.png}
+    \caption{Empirical convergence of regression procedure for European call options and $d=20$}
+    \label{fig1:reg_lb} 
+\end{figure}
+
+The left part of Figure \ref{fig1:reg_lb} contains the MSEs of the regression procedure for budget sizes that are smaller than $10,000$. 
+Slopes of the fitted lines on the left correspond to the empirical rate of convergence of the regression procedure for budget levels between $1,000$ and $10,000$.
+To investigate the convergence behavior for higher budget levels, we conduct additional experiments for the European call option with dimension $20$. 
+The additional experiments are summarized on the right of Figure \ref{fig1:reg_lb}.
+After reaching a certain budget level, i.e., $\Gamma = 1,000,000$, the empirical rate of convergence for the regression-based nested simulation procedure approaches its asymptotic rate. 
+For nested simulation procedures whose proxy models are biased, the proxy estimators of the true inner simulation are poor, especially for smaller budget sizes. 
+We are able to clearly observe this phenomenon for the regression proxy, and it can be explained by dividing the MSE into proxy bias and simulation variance.
+For small budget sizes, the improvement of the bias of the regression proxy dominates the improvement of simulation variance. 
+Performing poorly for extremely low simulation budgets, the regression proxy improves significantly. 
+As the simulation budget gets higher, the improvement of the regression proxy becomes negligible compared with that of the simulation variance. 
+The regression proxy ceases to improve after reaching a certain level ($\Gamma = 100\!,\!000$ in our case), and the improvement of simulation variance dominates.
+
+\subsection{Empirical Convergence of Kernel Smoothing-Based Procedures} \label{sec1:kernel-smoothing-convergence}
+
+The kernel smoothing proxy is a nonparametric regression procedure.
+According to the theoretical analysis in Section~\ref{sec1:asymptotic-convergence}, the asymptotic rate of convergence of the kernel smoothing-based nested simulation procedure is highly dependent on the dimension of the asset.
+
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure4a.png}
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure4b.png}
+    \caption{Empirical convergence of kernel smoothing procedure for different values of $d$}
+    \label{fig1:kernel_d} 
+\end{figure}
+
+In Figure~\ref{fig1:kernel_d}, the empirical convergence of the kernel smoothing-based nested simulation procedure for quadratic tracking error is illustrated for different asset dimensions, i.e., $d = 1, 2, 5, 10$.
+The observation finds that the kernel smoothing-based nested simulation procedure is extremely sensitive to the asset dimension and the payoff structure.
+While the asset dimension is expected to be a critical factor as shown in the theoretical analysis, the payoff structure is an unexpected factor that affects the empirical convergence of the kernel smoothing-based nested simulation procedure.
+For a portfolio with geometric Asian options, the payoff complexity is higher than that of a portfolio with European call options.
+The empirical rate of convergence of the kernel smoothing-based procedure is significantly lower for the portfolio with geometric Asian options than for the portfolio with European call options.
+For geometric Asian options, the empirical rates of convergence are even lower than the asymptotic rates for all asset dimensions.
+
+Due to the computational cost of the kernel smoothing-based nested simulation procedure, we are not able to conduct experiments for higher budget levels.
+However, we are able to conduct additional experiments to examine the effects of cross-validation on the empirical convergence of the kernel smoothing-based procedure.
+Another phenomenon that is observed in Figure~\ref{fig1:kernel_d} is that the empirical rate of convergence of the kernel smoothing-based procedure does not decrease monotonically as the simulation budget increases.
+This is likely due to the fact that the kernel smoothing-based procedure, as a nonparametric regression procedure, is highly dependent on the cross-validation of the proxy hyperparameters.
+For the kernel smoothing-based procedure, the kNN proxy is implemented. 
+Hence, the proxy hyperparameter is the number of nearest neighbors $k$.
+In our numerical experiment, cross-validation is conducted once to select the optimal value of $k$ for each simulation budget, and the selected value of $k$ is fixed for all $1,000$ replications.
+Therefore, a poor selection of the optimal value of $k$ can lead to a poor proxy estimator, and the MSE of the kernel smoothing-based procedure will be dominated by the model error of the proxy estimator.
+
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure5a.png}
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure5b.png}
+    \caption{Cross-validation for the kernel smoothing-based procedure with $\Gamma=100,000$}
+    \label{fig1:kernel_cv} 
+\end{figure}
+
+In Figure~\ref{fig1:kernel_cv}, the empirical convergence of the kernel smoothing-based nested simulation procedure for the probability of large loss is illustrated for different values of $k$ with $\Gamma = 100,000$.
+The observation is that the value of optimal $k$ estimated by cross-validation is highly variable across different replications.
+For the two replications where $k = 80$ is selected as the optimal value of $k$, the estimated risk measures for the kernel smoothing-based procedure are $0.1187$ and $0.1189$, which are significantly higher than the estimated risk measures for the other replications and far from the true risk measure of $0.1$.
+This observation suggests that the empirical convergence of the kernel smoothing-based nested simulation procedure is highly dependent on the cross-validation of the proxy hyperparameters.
+
+\subsection{Sensitivity to the Option Types and Risk Measures} \label{sec1:sensitivity-option-type}
+
+In our previous numerical experiments, we have examined the empirical convergence behavior of the nested simulation procedures for European call options, which is the most basic option type.
+To examine the sensitivity of the empirical convergence behavior to the option type, we consider path-dependent options, namely geometric Asian options and barrier options.
+
+\begin{figure}[ht!] 
+    \centering
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure6a.png}
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure6b.png}
+    \caption{Empirical convergence of nested simulation procedures for quadratic tracking error on different portfolios with $d=20$}
+    \label{fig1:1x03} 
+\end{figure}
+
+In Figure~\ref{fig1:1x03}, the empirical convergence of the nested simulation procedures for the quadratic tracking errors of Portfolio 1 and Portfolio 4 is illustrated for $d = 20$.
+The empirical rates of standard, likelihood ratio-based, and KRR-based nested simulation procedures closely ensemble their asymptotic rates for path-dependent options.
+The empirical rate of convergence of the regression-based and kernel smoothing-based procedures is much higher than their asymptotic rates for barrier options, with reasons explained in Section~\ref{sec1:regression-convergence}.
+
+\begin{figure}[ht!] 
+    \centering
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure7a.png}
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure7b.png}
+    \caption{Empirical convergence of nested simulation procedures for a W-shaped payoff}
+    \label{fig1:5503} 
+\end{figure}
+
+In~\cite{broadie2015risk}, the authors propose a numerical example where the payoff has a W-shape with respect to the underlying asset price.
+We have incorporated this example as Portfolio 5.
+In Figure~\ref{fig1:5503}, the empirical convergence of the nested simulation procedures for quadratic tracking error and mean excess loss on Portfolio 5 is illustrated for $d = 1$.
+For all procedures, we observe a similar convergence behavior as in other path-dependent options.
+The MSEs of the kernel smoothing-based and KRR-based procedures do not decrease monotonically as the simulation budget increases, as observed and analyzed in Section~\ref{sec1:kernel-smoothing-convergence}.
+
+\begin{figure}[ht!] 
+    \centering
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure8a.png}
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure8b.png}
+    \caption{Empirical convergence of nested simulation procedures for different risk measures on Portfolio 1 with $d=20$}
+    \label{fig1:110x}
+\end{figure}
+
+Figure~\ref{fig1:110x} illustrates similar observations for sensitivity to different risk measures.
+A change in the risk measure of interest does not affect the empirical convergence behavior of all nested simulation procedures.
+From the empirical convergence results, we observe that the empirical rates of convergence of the regression-based nested simulation procedure are the highest among all nested simulation procedures for all risk measures and option types.
+Furthermore, the regression-based procedure is stable across different payoff structures and risk measures. 
+Its MSEs decrease quickly in the beginning, and after reaching a certain budget level, the rate of decrease stabilizes to match its asymptotic rate of convergence.
+
+\subsection{Sensitivity to level for VaR and CVaR} \label{sec1:sensitivity-level}
+
+The level of VaR and CVaR is a critical factor that determines the complexity of the risk measure estimation.
+In our previous numerical experiments, the level of VaR and CVaR is set to be the 90\% quantile of the distribution of the inner simulation noise.
+In this section, we examine the empirical convergence of the regression-based nested simulation procedures for different levels of VaR and CVaR, i.e., $80\%$, $90\%$, $95\%$, $99\%$, and $99.6\%$.
+
+\begin{figure}[ht!] 
+    \centering
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure9a.png}
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure9b.png}
+    \caption{Empirical convergence of regression-based procedures for different levels of VaR and CVaR for Up and Out Barrier Call Options}
+    \label{fig1:sens_level}
+\end{figure}
+
+In Figure~\ref{fig1:sens_level}, the empirical convergence of the regression-based nested simulation procedure for different levels of VaR and CVaR is illustrated for up-and-out barrier call options.
+The empirical rates of convergence of the regression-based nested simulation procedure are independent of the level of VaR and CVaR.
+
+\subsection{Sensitivity to the Asset Model} \label{sec1:sensitivity-assetModel}
+
+Our previous numerical experiments have been conducted under the assumption that the underlying asset dynamics follow a multidimensional geometric Brownian motion with $0.3$ pairwise correlation.
+To examine the sensitivity of the empirical convergence behavior to the asset model, we consider a stochastic volatility model, i.e., a Heston model.
+
+\begin{figure}[ht!] 
+    \centering
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure10a.png}
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure10b.png}
+    \caption{Empirical convergence of regression-based nested simulation procedures for different asset models}
+    \label{fig1:sens_model}
+\end{figure}
+
+In Figure~\ref{fig1:sens_model}, the empirical convergence results of the regression-based nested simulation procedure for a quadratic tracking error and a 90\%-CVaR are illustrated for different asset models, i.e., a geometric Brownian motion and a Heston model.
+The empirical rates of convergence of the regression-based nested simulation procedure are observed to be independent of the asset model.
+
+\subsection{Empirical Convergence of Multi-level Monte Carlo} \label{sec1:empirical-mlmc}
+
+The multi-level Monte Carlo procedure is a variance reduction technique that is designed to reduce the computational cost of nested simulation procedures.
+The theoretical analysis in~\cite{giles2019multilevel} shows that the multi-level Monte Carlo procedure has a faster empirical rate of convergence than the standard nested simulation procedure when the risk measure of interest is the probability of a large loss over a threshold $u$, i.e., the nested expectation case with $h$ being an indicator function.
+
+\begin{table}[ht]
+    \centering
+    \begin{tabular}{rrrrrr}
+    \toprule
+    \textbf{Level} & \textbf{Bias} & \textbf{Variance} & \textbf{MSE} & $\Gamma$ & \textbf{MSE of SNS} \\ 
+    \hline\hline
+    0 & 0.118  & 0.104  & 0.1364 & 6400     & 0.1660    \\
+    1 & 0.102  & 0.0916 & 0.1020 & 27600    & 0.1305    \\
+    2 & 0.0870 & 0.0794 & 0.0870 & 76600    & 0.0954    \\
+    3 & 0.0815 & 0.0746 & 0.0812 & 175600   & 0.0744    \\
+    4 & 0.0893 & 0.0805 & 0.0884 & 348100   & 0.0460    \\
+    5 & 0.0750 & 0.0694 & 0.0750 & 640000   & 0.0366    \\
+    \bottomrule
+    \end{tabular}
+    \caption{MSEs of the multi-level Monte Carlo procedure for different levels}
+    \label{tab1:mlmc-mse}
+\end{table}
+
+Instead of using a figure, we provide a summary of the empirical convergence results of the multi-level Monte Carlo procedure with a decomposition table of the MSEs in Table~\ref{tab1:mlmc-mse}.
+The MSEs of the multi-level Monte Carlo procedure are decomposed into the bias and the variance of the estimator.
+The MSEs of the standard nested simulation procedure with a similar total simulation budget are also provided for comparison.
+Since the multi-level Monte Carlo procedure is designed with a fixed number of outer simulation paths, the benefit of the multi-level Monte Carlo procedure is minimal when the total simulation budget is large.
+More specifically, when $\Gamma$ is large, the standard nested simulation procedure with a bootstrap-based budget allocation strategy benefits from having a larger number of outer simulation paths, and the MSE of the standard nested simulation procedure is lower than that of the multi-level Monte Carlo procedure with a fixed number of outer simulation paths.
+
+\section{Computational Complexity} \label{sec1:computational-complexity}
+Compared to the standard procedure, proxy-based nested simulation procedures often have faster empirical rates of convergence.
+The faster convergence benefits from the pooling of inner samples through the proxy models. 
+However, pooling itself comes with computational costs, which are usually ignored in most numerical comparisons. 
+This section summarizes the algorithmic complexity and illustrate the computational time of different nested simulation procedures.
+The findings can provide some further guidance on the choice of a proper nested simulation procedure given a nested estimation problem.
+Define basic operations to be basic mathematical operators, that is, arithmetic with individual elements has complexity $\mathcal{O}(1)$.
+
+\begin{table}[ht]
+    \centering  
+    \small
+    \begin{tabular}{llll}
+    \hline
+    \textbf{Procedures}      & \textbf{Training cost}                    &  \textbf{Prediction cost}    & \textbf{Total additional cost} \\ \hline \hline
+    Standard procedure       &  $0$                                      &  $\mathcal{O}(M)$            & $\mathcal{O}(M)$ \\ 
+    Regression               &  $\mathcal{O}(p^2M) + \mathcal{O}(p^3)$   &  $\mathcal{O}(pM)$           & $\mathcal{O}(p^2M) + \mathcal{O}(p^3)$ \\
+    Kernel smoothing         &  $\mathcal{O}(M\log(M))$                  &  $\mathcal{O}(k\log(M))$     & $\mathcal{O}(M\log(M))$ \\
+    Kernel ridge regression  &  $\mathcal{O}(M^3)$                       &  $\mathcal{O}(M^2)$          & $\mathcal{O}(M^3)$ \\
+    Likelihood ratio         &  $0$                                      &  $\mathcal{O}(M^2)$          & $\mathcal{O}(M^2)$ \\
+    \hline
+    \end{tabular} 
+    \caption{Additional computational costs of nested simulation procedures aside from simulation}
+    \label{tab1:complexity}
+\end{table}
+
+Table~\ref{tab1:complexity} shows the algorithmic complexity of the nested simulation procedures.
+For a $d$-dimensional nested estimation problem, the simulation cost for all procedures is $\mathcal{O}(dMN)$.
+The simulation cost is omitted from Table~\ref{tab1:complexity}, as all methods are given the same simulation budget.
+Given $M$ outer samples and the corresponding $M$ inner sample averages, the algorithmic complexity of the additional operations does not involve $N$ thus can be written in terms of $M$ only.
+The training cost includes the cost of fitting the proxy model and the cost of cross-validation for nonparametric regression proxies.
+For the standard procedure, the training cost is $0$ due to the absence of proxy models. 
+Its prediction cost $\mathcal{O}(M)$ comes from the evaluation of the function $h$ for $M$ samples.
+For the regression-based procedure, a linear regression model is fitted with $p$ predictors.
+In practice, $p$ is usually much smaller than $M$ and does not grow with the simulation budget $\Gamma$.
+However, it is dependent on the complexity of the payoff function.
+Estimating the coefficients of the regression model involves multiplying the design matrix by its transpose and inverting the resulting matrix, which has complexity $\mathcal{O}(p^2M)$ and $\mathcal{O}(p^3)$, respectively.
+For a review in the complexity of matrix inversion, see~\cite{stothers2010complexity}.
+The matrix inversion has complexity $\mathcal{O}(p^3)$ using Gauss-Jordan elimination, but in practice, the complexity can be reduced to $\mathcal{O}(p^{2.807})$ by~\cite{strassen1969gaussian} and $\mathcal{O}(p^{2.376})$ by~\cite{coppersmith1987matrix}.
+The prediction cost of the regression-based procedure is $\mathcal{O}(pM)$, which comes from the multiplication of the design matrix by the estimated coefficients.
+For the kernel smoothing-based procedure, the kNN proxy is implemented.
+In practice, the K-D tree algorithm~\citep{bentley1975multidimensional} is often implemented for efficient nearest neighbor search.
+During training, a tree is constructed to store the distance, which has complexity $\mathcal{O}(M\log(M))$.
+The prediction cost of the kernel smoothing-based procedure is $\mathcal{O}(kM\log(M))$, which comes from a query of the K-D tree for $k$ nearest neighbors for $M$ samples.
+Conversely, An inefficient algorithm calculates the distance matrix during training and a block sort algorithm to find the $k$ nearest neighbors, which results in a complexity of $\mathcal{O}(M^2)$ and $\mathcal{O}(M^2\log(M))$, respectively.
+A practical implementation of block sort is provided in~\cite{kim2008ratio}.
+Hence, an efficient implementation of the kNN proxy is crucial for the kernel smoothing-based procedure.
+For the likelihood ratio-based procedure, the training cost is $0$ as no training is required.
+The prediction cost of the likelihood ratio-based procedure is $\mathcal{O}(M^2)$, which comes from the calculation of the likelihood weights for $M$ samples.
+For the KRR-based procedure, the main training cost comes from inverting an $M \times M$ kernel matrix~\citep{scholkopf2002learning}, which has complexity $\mathcal{O}(M^3)$ using Gauss-Jordan elimination.
+Similar to the regression-based procedure, this complexity can be reduced to $\mathcal{O}(M^{2.376})$.
+The prediction cost of the KRR-based procedure is $\mathcal{O}(M^2)$, which comes from the multiplication of the kernel matrix by the estimated coefficients.
+Among the proxy-based procedures, regression is the most efficient as $p$ is usually much smaller than $M$. 
+Kernel smoothing and KRR are kernel-based proxies, and they are more expensive due to distance calculation and cross-validation of hyperparameters. 
+The kNN proxy has only 1 hyperparameter $k$, while the KRR proxy requires 3 hyperparameters, namely the smoothness hyperparameter $\nu$, scale hyperparameter $\ell$, and the regularization hyperparameter $\lambda$.
+Calculating the likelihood ratio weights is inevitable for the likelihood ratio-based procedure. 
+While a k-fold cross-validation is used to estimate the hyperparameter for kNN, the KRR requires Bayesian optimization~\citep{shahriari2015taking} to estimate the hyperparameters due to having a high-dimensional search space.
+The likelihood ratio-based procedure requires no training, but the cost of calculating the likelihood weights is $\mathcal{O}(M^2)$.
+Comparing the algorithmic complexity of the nested simulation procedures, the regression-based procedure is the most efficient among the proxy-based procedures.
+For a fixed $p$, the total additional cost of a regression-based procedure is $\mathcal{O}(M)$, which is the same as the standard procedure's.
+
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure11a.png}
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure11b.png}
+    \caption{Total computational cost for different procedures with $d=10$}
+    \label{fig1:tcc}
+\end{figure}
+
+In our finite-sample experiments, we have observed that the actual computational cost to be significantly different from the theoretical complexity, as not only the order of complexity but also the constant factors can affect the computational cost.
+In Figure~\ref{fig1:tcc}, the total computational time of different nested simulation procedures for European call options and geometric Asian options with $d = 10$ is illustrated in a log-log scale.
+The $x$-axis shows the total simulation budget $\Gamma$, and the $y$-axis is the total computational time for 1 replication of the numerical experiment, in seconds.
+All procedures are implemented on a machine with an AMD Ryzen 9 7900X processor with 32GB of RAM.
+8 cores are used for parallel computing, and the total computational time is the sum of the simulation time, the training time, and the prediction time.
+The regression and kernel smoothing-based procedures are the most efficient among the proxy-based procedures.
+Since the regression-based procedure has a higher empirical rate of convergence, it is preferred over the kNN.
+The likelihood ratio-based and KRR-based procedures are the most computationally expensive among all procedures.
+They are demanding in terms of memory.
+For budgets larger than $10^5$, the likelihood ratio-based procedure becomes impractical as storage of the likelihood weights becomes a bottleneck.
+The KRR-based procedure suffers from both cross-validation and inverting a kernel matrix of size $M \times M$.
+To separate the total computational time into different attributes, we provide a detailed analysis of the total computational time in the remainder of this section.
+
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure12a.png}
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure12b.png}
+    \caption{Computational cost for implementing nested simulation procedures with $d=10$, excluding simulation time}
+    \label{fig1:c_model}
+\end{figure}
+
+Figure~\ref{fig1:c_model} illustrates the computational time of implementing different nested simulation procedures for the portfolio of geometric Asian options with $d = 10$, excluding the simulation time.
+The simulation time is omitted as it is the same for all procedures.
+The remainder can be decomposed into two parts: hyperparameter tuning and model implementation.
+The hyperparameter tuning cost is the cost of estimating the optimal hyperparameters for the proxy models, and the model implementation cost is the cost of fitting the proxy models and generating predictions from the trained proxies.
+For each procedure, each point in Figure~\ref{fig1:c_model} represents the average computational time for a given simulation budget $\Gamma$.
+A regression model is fitted to each model respectively, and its slope is reported as the growth rate of the computational time with respect to $\Gamma$.
+The total computational time of the standard procedure is mostly attributed to finding the optimal $M$ and $N$ using the bootstrap-based budget allocation strategy from~\cite{zhang2021bootstrap}.
+This cost does not grow with the simulation budget $\Gamma$, as its slope is close to $0$.
+The regression-based procedure does not require hyperparameter tuning, and its total computational time is mainly attributed to the model implementation.
+The slope of the regression line is close to $1$, resembling the its algorithmic complexity in Table~\ref{tab1:complexity}.
+The kernel smoothing-based and KRR-based procedure requires cross-validation to estimate the optimal hyperparameters.
+In our implementaion of kNN, the cross-validation is conducted using a grid search with a search space whose cardinality does not grow with the simulation budget $\Gamma$.
+However, the cross-validation cost of the kernel smoothing-based procedure grows with the simulation budget $\Gamma$ as more samples are involved.
+The KRR-based procedure requires Bayesian optimization to estimate the optimal hyperparameters, and the cardinality of the search space grows with the simulation budget $\Gamma$.
+The empirical cost of the KRR-based procedure does not resemble its algorithmic complexity in Table~\ref{tab1:complexity}.
+The efficient implementation of KRR is an active area of research, and the computational cost of KRR can be reduced by using a low-rank approximation of the kernel matrix, e.g., the Nystr\"om method~\citep{nystrom1930praktische}.
+Our observation for KRR implementation time is in line with the findings in~\cite{scikit-learn}, where the cost of KRR is reported quickly increasing with the number of samples.
+The likelihood ratio-based procedure requires no hyperparameter tuning, and its total computational time is mainly attributed to the likelihood weight calculation, which is $\mathcal{O}(M^2)$. 
+In summary, for a large simulation budget, the regression-based procedure is the most efficient among all proxy-based procedures in terms of computational time.
+
+\section{Conclusion} \label{sec1:conclusion}
+In the task of estimating risk measures for portfolios of complex financial derivatives, nested simulation procedures are commonly required but often computationally expensive. 
+Tremendous efforts have been made to improve the efficiency of nested simulation procedures by approximating the inner simulation model with a proxy model. 
+In this study, we review the literature on nested simulation procedures in financial engineering and establish fair comparisons of different proxy models using the same set of numerical examples. 
+Asymptotic properties of estimators for different nested simulation procedures are influenced by their corresponding proxy models.
+To show an asymptotic convergence result, a more complex proxy model requires a more stringent set of assumptions on the distribution of the outer scenario and the inner simulation noise.
+With extensive numerical experiments, we have found the finite-sample performance of a procedure can deviate from its theory. 
+In theory, supervised learning-based nested simulation procedures often provide higher rates of convergence, but they come at the computational expense of model training and generating predictions from the trained models.
+The likelihood ratio-based procedure requires no training, but it is computationally expensive to compute and store the likelihood weights.
+As a result, the total computational budget is not necessarily the same as the simulation budget, which is usually a limiting factor for practical applications.
+A kernel-based procedure, e.g., kNN and KRR, requires cross-validation, and its empirical performance depends heavily the choice of hyperparameters.
+A kNN-based procedure is sensitive to the asset dimension and the problem complexity.
+A KRR-based procedure is computationally expensive, and its cost grows quickly with the simulation budget.
+For kernel-based procedures, the computational cost is heavily dependent on the efficient implementation of the associated algorithms.
+For a nested estimation problem with a given computational budget, we suggest the use of the regression-based simulation procedure when the budget size is moderate. 
+It is efficient to implement, and it exhibits fast empirical convergence in estimating risk measures for option portfolios.

### 2024-04-04 project2/nnMetamodels.tex
new

@@
 
-Consider a generic VA contract whose delta hedge portfolio at any time~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at time $T$.
+Consider a VA contract whose delta hedge portfolio at any time~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at time $T$.
 The value of the hedge portfolio at time~$(t-1)$ is:
@@
 Denote the standard procedure's estimated losses and sorted losses by $\Lhat^{ML}_i$ and $\Lhat^{ML}_{(i)}$, respectively, $i=1,\ldots,m$.
-        \item Estimate the $\alpha$-CVaR of $L$ by $\widehat{\CVaR}^{ML}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}\Lhat_{(i)}^{ML} = \frac{1}{(1-\alpha)M} \sum_{i \in \widehat{\tail}_{(1-\alpha )M}^{ML}}\Lhat_{i}^{ML}$, where $\widehat{\tail}_{k}^{ML}$ denotes a predicted tail scenario set associated with the largest $k$ estimated losses.
+        \item Estimate the $\alpha$-CVaR of $L$ by 
+        $$\widehat{\CVaR}^{ML}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}\Lhat_{(i)}^{ML} = \frac{1}{(1-\alpha)M} \sum_{i \in \widehat{\tail}_{(1-\alpha )M}^{ML}}\Lhat_{i}^{ML},$$ 
+        where $\widehat{\tail}_{k}^{ML}$ denotes a predicted tail scenario set associated with the largest $k$ estimated losses.
     \end{enumerate}
@@
 \begin{table}[ht!]
-    \small
     \centering
+    \footnotesize
     \begin{tabular}{lccccc}

### 2024-04-04 project3/tlHedging.tex
new

\chapter{Efficient Transfer of Knowledge for Deep Hedging of Variable Annuities}

\section{Introduction}

Reinforcement Learning (RL) is a branch of machine learning that focuses on training algorithms, known as agents, to make a sequence of decisions. 
The agent learns to achieve a goal in an uncertain, potentially complex environment by trial and error, using feedback from its own actions and experiences. 
Unlike supervised learning, where training data is labeled with the correct answers, in RL, an agent is provided with rewards or punishments as signals for its actions.

The core of RL revolves around the concept of the agent interacting with its environment over time, aiming to maximize the cumulative reward. 
This process involves observing the state of the environment, selecting and performing actions, and receiving rewards or penalties in response to those actions. 
The agent's objective is to learn a mapping from states to actions that maximizes this cumulative reward, which is often referred to as a policy. 
One of the fundamental frameworks for modeling RL problems is the Markov Decision Process (MDP). 
An MDP provides a mathematical formulation of the decision-making process, characterized by states, actions, rewards, and transition probabilities. Solving an MDP involves finding a policy that maximizes some function of the expected rewards, typically the expected cumulative reward over time.

Reinforcement learning algorithms can be broadly categorized into two types: model-based and model-free approaches. 
Model-based methods utilize a model of the environment to simulate the outcomes of actions, enabling planning and decision-making with fewer interactions with the environment. 
Conversely, model-free methods learn directly from interactions with the environment, without relying on a model, making them more straightforward but often less efficient in terms of sample usage.

A compelling application of RL is in the hedging of financial derivatives, a domain where the complexity and uncertainty of financial markets make traditional static models inadequate.
Financial derivatives are contracts whose value is derived from an underlying asset, and hedging is the practice of making investments to reduce the risk of adverse price movements.
RL's adaptability and learning capabilities offer a promising solution to dynamically adjust hedging strategies in response to market movements.
This approach, particularly with model-free algorithms, has the potential to enhance risk management practices by developing strategies that can adapt in real-time to changing market conditions.

In this paper, we propose a transfer learning approach to improve the risk management of variable annuities (VAs) by learning a hedging strategy utilizing previous experiences from other financial products.
VAs are popular retirement products that combine investment and insurance features, offering policyholders the potential for investment growth and the protection of a guaranteed minimum death benefit or income benefit.
Due to the complexity of the products and the dynamic nature of the financial markets, the task of hedging VAs is particularly challenging.
We aim to leverage the knowledge from the hedging strategies of financial derivatives to construct hedging strategies for VAs, thereby improving the risk management of these products.
The rest of the paper is organized as follows: Section~\ref{sec:vaHedging} presents the problem formulation for hedging variable annuity with a deep neural network, Section~\ref{sec:tlHedging} presents the background knowledge for transfer learning, and Section~\ref{sec:numerical} states the plans for ongoing numerical experiments.

\section{Dynamic Hedging of Variable Annuities} \label{sec:vaHedging}

\subsection{Variable Annuities}
Variable annuity contracts offer different types of guarantees.
Generally speaking, a portion of the VA premium is invested in a sub-account whose return is linked to some stock indices.

Two relevant types of guarantees in our studies are:
\begin{itemize}[noitemsep]
    \item \textbf{Guaranteed Minimum Maturity Benefit (GMMB)}: A GMMB contract pays a maturity benefit equal to the greater of the sub-account value and a fixed guarantee value.
    The guarantee value is often set as a percentage, e.g., 75\% or 100\%, of the initial premium.

    \item \textbf{Guaranteed Minimum Withdrawal Benefit (GMWB)}: A GMWB contract guarantees the minimum amount of periodic withdrawal the policyholder can take from the sub-account until maturity, even if the sub-account value reduces to zero.
    The minimum withdrawal benefit is typically a fixed percentage of the guarantee value.
    The guarantee value will decrease if the withdrawal exceeds the guaranteed minimum. The GMWB is typically offered with an accumulation period, during which no withdrawals are made but a GMDB is usually offered. Additional features offered with the GMWB include roll-up, ratchet, and reset~\citep{geneva2013variable}.
\end{itemize}
For a comprehensive review of other types of VA contracts such as Guaranteed Minimum Death Benefit (GMDB), Guaranteed Minimum Accumulation Benefit (GMAB) and Guaranteed Lifetime Withdrawal Benefit (GLWB), we refer readers to~\cite{hardy2003investment}.
Next we present a summary of dynamic hedging for VA contracts.
We refer readers to~\cite{dang2021efficient} for detailed modeling of insurer liabilities in different VA contracts and Greek estimation.

Consider a generic VA contract with maturity $T>0$ periods, e.g., $T=240$ months.
Denote the policyholder's (random) time of death by $\tau>0$.
Then the contract expires at $T'=\min\{T,\tau\}$, i.e., the earlier of the contract maturity and the death of the policyholder.
Let $S_t$, $F_t$, and $G_t$ be the indexed stock price, the subaccount value and the guarantee value, respectively, at time $t=1,2,\ldots,T$.
Evolution of the subaccount value and the guarantee value of a VA contract affect the contract payout.
Note that the policyholder's (random) time of death also affects the timing of the benefit payout for certain types of VA such as GMDB, but this is not considered in our study for simplicity.
For clarity, we use $F_t$ and $F_{t_+}$ to denote the sub-account value just before and just after the withdrawal at time $t$, if any.
Let $\eta_g$ be the gross rate of management fee that is deducted from the fund value at each period and let $\eta_n < \eta_g$ be the net rate of management fee income to the insurer.
The difference between the gross management fee and the net management fee income represents the incurred investment expenses.

At the inception of the contract, i.e., $t=0$, we assume that the whole premium is invested in the stock index and the guarantee base is set to the sub-account value:
\begin{equation*}
    S_0=F_0=G_0.
\end{equation*}
At each time $t=1,\ldots,T$, the following events take place in the following order:
\begin{enumerate}
    \item The sub-account value changes according to the growth of the underlying stock and the (gross) management fee is deducted. That is, 
        \begin{equation*}
            F_t = F_{(t-1)_+}\cdot\frac{S_{t}}{S_{t-1}}\cdot(1-\eta_g),
        \end{equation*} 
    where $(x)^+=\max\{x,0\}$ and $F_{(t-1)_+}$ will be defined later. The insurer's income at time $t$ is the net management fee, i.e., $F_t\eta_n$.

    \item The guarantee value ratchets up (ratcheting is a common feature in GMWB) if the sub-account value exceeds the previous guarantee value, i.e., 
        \begin{equation*}
            G_t = \max\{G_{t-1},F_t\}.
        \end{equation*}

    \item The withdrawal is made (for GMWB) and is deducted from the sub-account value, i.e., 
        \begin{equation*}
            F_{t_+} = (F_t - I_t)^+,
        \end{equation*} 
    where $I_t = \gamma G_t$. A GMMB can be modeled with $\gamma = 0$.
\end{enumerate}

We see from the above modeling steps that the status of a generic VA contract is summarized by a triplet $(S_t,F_t,G_t)$ whose evolution is driven by the stochasticity of $S_t$.
In practice, the simulation model may also incorporate additional complications like mortality, lapse, and excess withdrawal, etc.

At any time $t=1,\ldots,T$, the insurer's liability in a VA contract is the present value of all payments, net of the fee income.
For example, suppose that the per-period risk-free rate is $r$, then
the insurer's time-$t$ liability for a GMMB contract is $L_t = e^{-r(T-t)}\cdot (G_T - F_T)^+ - \sum_{s=t+1}^{T} e^{-r(T-s)} F_s \eta_n$.
Also, the insurer's time-$t$ liability for a GMWB contract is $L_t = \sum_{s=t+1}^{T} e^{-r(T-s)} [(I_s - F_s)^+- \eta_n F_s] $.

For example, consider the time-$t$ liability $L_t$ of a GMWB:
Suppose that given the stock sample path, e.g., an outer path $S_1,\ldots,S_t$, one can simulate future stock prices $\Stilde_{t+1},\ldots,\Stilde_{T}$, e.g., inner sample paths, based on some asset model such as a Black-Scholes model.
The tilde symbol ($\sim$) over a quantity denotes its association with the inner simulation.
Given the time~$t$ state $(S_t,F_t,G_t)$, following~\cite{cathcart2015calculating} the sensitivity of $L_t$ with respect to $S_t$ can be estimated by a pathwise estimator~\citep{glasserman2004monte}:
\begin{equation}\label{eq:delta}
    \Delta_t(\Stilde_{t+1},\ldots,\Stilde_{T} | S_t) = \frac{\partial L_t}{\partial S_t} = \sum_{s=t+1}^{T} e^{-r(T-s)} \left[\bm{1}\{\Itilde_s > \Ftilde_s\}\cdot \left( \frac{\partial \Itilde_s}{ \partial S_t} - \frac{\partial \Ftilde_s}{ \partial S_t}\right)- \eta_n \frac{\partial \Ftilde_s}{ \partial S_t}\right], \quad t=0,\ldots,T-1,
\end{equation}
where $\bm{1}\{\cdot\}$ is an indicator function and
\begin{align*}
    \frac{\partial \Ftilde_s}{ \partial S_t} &= \bm{1}\{\Itilde_{s-1} < \Ftilde_{s-1}\}\cdot\left( \frac{\partial \Ftilde_{s-1}}{ \partial S_t} - \frac{\partial \Itilde_{s-1}}{ \partial S_t}\right) \cdot \frac{\Stilde_s}{\Stilde_{s-1}}\cdot (1-\eta_g),\\
    \frac{\partial \Gtilde_s}{ \partial S_t} &= \bm{1}\{\Gtilde_{s-1} < \Ftilde_{s}\}\cdot\frac{\partial \Ftilde_{s}}{ \partial S_t} + \bm{1}\{\Gtilde_{s-1} \geq \Ftilde_{s}\}\cdot\frac{\partial \Gtilde_{s-1}}{ \partial S_t},\\
    \frac{\partial \Itilde_s}{ \partial S_t} &= \gamma \frac{\partial \Gtilde_s}{ \partial S_t}.
\end{align*}
The recursion is initialized with $(\Stilde_t,\Ftilde_t,\Gtilde_t) = (S_t,F_t,G_t)$, $\frac{\partial \Ftilde_s}{ \partial S_t} = \frac{\Ftilde_t}{S_t}$, and $\frac{\partial \Gtilde_s}{ \partial S_t} = \frac{\partial \Itilde_s}{ \partial S_t} = 0$.

\subsection{Markov Decision Process (MDP) for Hedging VAs}
A Markov Decision Process (MDP) provides a mathematical framework for solving sequential decision-making tasks in situations where outcomes are partly random and partly under the control of an agent. 
In the context of hedging VAs, an MDP can be used to model the decision-making process of an insurer who aims to minimize the liability of the VA by dynamically adjusting the hedging portfolio based on the current state of the VA and the financial markets.
An MDP is defined by the tuple $\mathcal{M} = (\mu_0, \mathcal{S}, \mathcal{A}, \mathcal{P}, \mathcal{R}, \gamma)$, where:

\begin{itemize}
    \item $\mu_0$ is the initial states.
    \item $\mathcal{S}$ is a finite set of states.
    \item $\mathcal{A}$ is a finite set of actions.
    \item $\mathcal{P}$ is a state transition probability distribution, where $\mathcal{P}(s'|s, a)$ represents the probability of transitioning from state $s$ to state $s'$ due to action $a$.
    \item $\mathcal{R}$ is a reward distribution, $\mathcal{R}(s, a, s')$ is the reward received after transitioning from state $s$ to state $s'$ due to action $a$.
    \item $\gamma$ is a discount factor, $\gamma \in [0,1]$,  which models the present value of future rewards.
\end{itemize}

The objective in an MDP is to find a policy, $\pi: \mathcal{S} \rightarrow \mathcal{A}$, that maximizes the cumulative reward over time, often referred to as the value function for a policy $\pi$ at state $s$:

\begin{equation} \label{eq:V_pi}
    V^{\pi}_{\mathcal{M}}(s) = \mathbb{E}_{s_0 \sim \mu_0, a_i \sim \pi(\cdot|s_i), s_{i+1} \sim \mathcal{P}(\cdot|s, a)} \left[ \sum_{t=0}^{\infty} \gamma^t R_{t+1} |\pi, s \right],
\end{equation}

where $R_{t+1} = \mathcal{R}(s_i, a_i, s_{i+1})$ is the reward received by the agent after taking action $a_i$ in state $s_i$ and transitioning to state $s_{i+1}$, and the expectation is taken over the possible sequences of states and rewards that follow from the policy $\pi$.
In the context of hedging VAs, the initial states $\mu_0$ specifies the initial value of the VA and the market specifications. 
The state space $\mathcal{S}$ represent the information available to the agent, such as current value of the underlying asset ($S_t$), the current subaccount value ($F_t$), and the guarantee value ($G_t$), as well as other relevant contract specifications.
The action space $\mathcal{A}$ represent the hedging decisions, such as the hedging portfolio weights.
The state transition probability distribution $\mathcal{P}$ and the reward function $\mathcal{R}$ are derived from the dynamics of the VA and the market specifications. Instead of having an infinite time horizon, the final reward is obtained at the maturity of the VA contract. Hence, $R_{t} = 0$ for all $t > T$.
The discount factor $\gamma$ models the present value of future rewards and is conveniently inherited from the risk-free rate.

Considering the task of hedging a GMWB contract, the hedging strategy aims to minimize the insurer's liability $L_t$ at each time $t=1,\ldots,T$ by dynamically adjusting the hedging portfolio based on the current state of the VA and the financial markets. The objective is to find a policy $\pi$ that minimizes the expected liability over time, i.e.,

\begin{equation}
    \min_{\pi} \mathbb{E}[\sum_{t=1}^{T} \gamma^t L_t | \pi, s_0],
\end{equation}

where it can be conveniently rewritten as the value function $V^{\pi}_{\mathcal{M}}(s)$ in Equation~\ref{eq:V_pi} by setting the reward function $R_{t} = -L_t$ and the discount factor $\gamma = \frac{1}{1+r}$. 
Other value functions can be used to optimize over a risk measure on the cumulative liability, such as the Value-at-Risk (VaR) or the Conditional Value-at-Risk (CVaR).
Denote the risk measure as $\rho_{\alpha}$, where $\alpha$ is the confidence level, then the value function can be set as

\begin{equation}
    V^{\pi}_{\mathcal{M}}(s) = \rho_{\alpha}(\sum_{t=1}^{T} \gamma^t L_t | \pi, s_0).
\end{equation}

\subsection{Deep Hedging Approaches}

Deep hedging is a reinforcement learning approach that leverages deep learning models to optimize hedging strategies for financial derivatives.
In deep hedging, the objective is to minimize the hedging error or a risk measure over a set of paths of the underlying asset, which involves training the DNNs using backpropagation and optimization algorithms to find the hedging strategy that maximizing the value function.

\begin{enumerate}
    \item \textbf{Value Function:} Specify a value function that quantifies the hedging performance. 
    This could include minimizing the expected liability, the CVaR, or the variance of portfolio returns.
    \item \textbf{Training and Optimization:} Using historical data or simulated data generated from the specified market model, train the DNN using backpropagation and optimization algorithms to find the hedging strategy that maximizes the value function.
    \item \textbf{Implementation and Adjustment:} Implement the learned hedging strategy in real-time trading, with periodic adjustments based on new market information and continuous learning to adapt to changing market dynamics. This is often referred to as online learning.
\end{enumerate}

Depending on the specific market model and the hedging objective, deep hedging can be categorized into model-based and model-free approaches.
Model-based deep hedging trains a deep neural network (DNN) to learn optimal hedging actions by maximizing a value function that reflects the hedging error or risk measure, such as the variance of the hedging portfolio's final value or tail risk measures like the CVaR.
The DNN processes sequential market data and outputs a policy that determines the hedging actions based on the current state of the market.
In the context of deep hedging, the policy $\pi = \phi(\mathcal{I})$ is defined by the parameter $\phi$ of a DNN, and the information $\mathcal{I}$ is the training data during the learning process.
~\cite{buehler2019deep} is the first paper to propose a model-based deep hedging approach for hedging financial derivatives with a focus on minimizing CVaR.
A more recent paper by~\cite{imaki2021no} proposes a new network architecture for model-based deep hedging that can be trained more efficiently.
A typical setup for a model-based deep hedging strategy includes:

\begin{enumerate}[label=\arabic*a.]
    \setcounter{enumi}{3}
    \item \textbf{Market Model Specification:} Define the underlying asset price dynamics and the risk factors affecting the financial instruments. Common models include geometric Brownian motion for stock prices or more complex models accounting for jumps or stochastic volatility.~\cite{glasserman2004monte} provides detailed discussions on simulating asset prices under various models.
    \item \textbf{Deep Neural Network Design:} Design a DNN architecture capable of processing sequential market data and making hedging decisions. The network outputs a policy by receiving inputs that include historical prices, option strikes, and other relevant financial indicators.~\cite{buehler2019deep} uses a feedforward neural network (FNN), where its input layer receives the current state of the market, and its output layer produces the hedging weights.
\end{enumerate}

Conversely, model-free deep hedging approaches directly learn from historical market data without making explicit assumptions about asset price dynamics. 
Instead, the value functions are learned directly from the data, and the hedging strategies are derived from the learned value functions.
A typical setup for a model-free deep hedging strategy includes:

\begin{enumerate}[label=\arabic*b.]
    \setcounter{enumi}{3}
    \item \textbf{Market Model Specification:} No explicit model assumptions are made about the underlying asset price dynamics. Instead, the deep learning model learns the value function and hedging strategies directly from historical market or simulation data.
    \item \textbf{Deep Neural Network Design:} Design two DNNs: a value network and a policy network. The value network learns the value function, while the policy network learns the optimal hedging actions based on the approximated value function.
\end{enumerate}

A model-free approach does not require explicit model assumptions about asset price dynamics, making it more flexible and adaptable to different market conditions and more robust to model misspecification.

\subsection{Value-based and Policy-based Deep Reinforcement Learning}

Model-free deep reinforcement learning algorithms can be broadly categorized into two types: value-based and policy-based approaches.

\begin{enumerate}
    \item \textbf{Value-based Deep Reinforcement Learning:} Value-based approaches learn the value function directly from the data and derive the policy from the learned value function. 
    The value function is learned by training a DNN to approximate the value function, which quantifies the expected cumulative reward over time. 
    The policy is then derived from the learned value function by selecting the action that maximizes the value function at each state. 
    ~\cite{mnih2015human} is the first paper to demonstrate the effectiveness of value-based deep reinforcement learning in training agents to play Atari games.
    To update the value function, the DNN is trained to minimize the difference between the current value function and the target value function, which is updated based on the maximum expected reward from the previous iteration.
    When trained to approximate the value function, the DNN benefits from the use of experience replay buffers, which is proposed by~\cite{lin1992self} to store and sample historical transitions and uniformly sampled during training to enhance the sample efficiency and stability of the learning process.
    ~\cite{kolm2019dynamic} uses a value-based deep reinforcement learning approach to hedge European options under the Black-Scholes framework.

    \item \textbf{Policy-based Deep Reinforcement Learning:}
    In valued-based approaches, the value function is updated iteratively with the maximum expected reward of all possible actions, which can be computationally expensive for continuous action spaces.
    To overcome this difficulty, a policy-based approach estimates the value function before realization of the final payoff of the hedging portfolio, which is particularly useful for hedging long-term financial derivatives or VA contracts.
    Two types of policy-based approaches prevail in the literature: actor-critic and policy gradient methods.

    An actor-critic method designs an actor network and a critic network to learn the value function and the policy simultaneously.
    The actor network learns the policy by directly outputting the action based on the current state, while the critic network learns the value of an action by approximating the expected cumulative reward over time following the actor's policy.
    A popular actor-critic algorithm is the Deep Deterministic Policy Gradient (DDPG) algorithm proposed by~\cite{lillicrap2015continuous}, which is implemented by~\cite{xu2022delta} in hedging financial derivatives in S\&P 500 and DJIA index options.

    A policy gradient method uses policy gradient theorem to update the policy by performing gradient ascent with respect to the policy parameters.
    Representative algorithms include the Proximal Policy Optimization (PPO) algorithm proposed by~\cite{schulman2017proximal} and the Trust Region Policy Optimization (TRPO) algorithm proposed by~\cite{schulman2015trust}.
    The most relevant paper to our study is~\cite{chong2023pseudo}, which uses the PPO algorithm to hedge GMMB with a GMDB rider under the Black-Scholes framework.
\end{enumerate}

\section{Transfer Learning for Risk Management of Variable Annuities} \label{sec:tlHedging}

Transfer learning is a machine learning technique that leverages knowledge from one domain to improve learning in another domain.
In the context of deep reinforcement learning, transfer learning can be used to improve the risk management of VAs in five ways:
\begin{enumerate}
    \item   \textbf{Transferring to VA products}: Knowledge can be transferred from the hedging strategies of financial derivatives to constructing hedging strategies for VAs.
    VAs are complex insurance products with unique features, which makes it challenging to develop effective hedging strategies.
    However, the payoff structures of VAs are similar to those of financial derivatives, such as European options, which have been extensively studied in the literature.
    By leveraging the knowledge from the hedging strategies of financial derivatives, we can improve the risk management of VAs.
    \item   \textbf{Transferring to new VA products}: Knowledge can be transferred from the hedging strategies of one VA product to another VA product.
    Different VA products have different features and payoff structures, which makes it challenging to develop hedging strategies for new VA products.
    However, experience from hedging one VA product can be transferred to develop hedging strategies for new VA products, especially when the new VA product is similar to the existing ones.
    \item   \textbf{Transferring to new asset models}: Knowledge can be transferred from the hedging strategies of one asset model to another asset model.
    A stochastic volatility model is a more realistic model for asset prices than the Black-Scholes model, but it is more challenging to develop hedging strategies for VAs under such a model.
    \item  \textbf{Transferring to new model specifications}: Model misspecification is a common issue in financial modeling, and training on data simulated with misspecified parameters can lead to suboptimal hedging strategies.
    If only the misspecified model is similar to the correct model, then we can leverage the knowledge from the misspecified model to improve the hedging strategies under the correct model, since the only difference between the two models is the parameter values. 
    \item   \textbf{Transferring to the real world}: Knowledge can be transferred from simulated data to real-world data.
    In practice, it is challenging to obtain real-world data for VAs, but we can leverage simulated data to develop hedging strategies for VAs.
    If the simulated data is representative of the real-world data, then the hedging strategies developed from the simulated data can be transferred to the real world.

\end{enumerate}

Given a set of source domains $\bm{\mathcal{M}}_s= \{ \mathcal{M}_s| \mathcal{M}_s \in \bm{\mathcal{M}}_s\}$ and a target domain $\mathcal{M}_t$, transfer learning aims to improve the learning on the target domain.
While utilizing the interior information $\mathcal{I}_t$ from the target domain, the exterior information $\mathcal{I}_s$ from the source domains is also leveraged to improve the learning on the target domain.

\begin{equation}
    \pi^* = \arg \max_\pi \mathbb{E}_{s \sim \mu_0, a \sim \pi} \left[V_{\mathcal{M}}^\pi (s, a) \right], 
\end{equation}

where $\pi = \phi(\mathcal{I}_s \sim \bm{\mathcal{M}}_s, \mathcal{I}_t \sim \mathcal{M}_t)$ is policy learned from target domain based on information from both the source domains and the target domain.
A regular reinforcement without transfer learning is a special case where $\mathcal{I}_s = \emptyset$ and $\pi = \phi(\mathcal{I}_t \sim \mathcal{M}_t)$.

In the context of deep hedging, various research has been conducted to improve the hedging strategies on real-world data by leveraging knowledge from simulated data.
Most of the research uses the offline-online learning approach, where the hedging strategies are first trained with simulation data, but updated in real-time based on new market information and continuous learning to adapt to changing market dynamics.
The most relevant paper to our study is~\cite{xiao2021optimal}, which use policy gradient algorithms to train hedging strategies for European options with simulation data from Heston model and then updated in real-time hedging S\&P 500 index options.
To the best of our knowledge, no research has been conducted to improve the hedging strategies with the state-of-the-art transfer learning techniques.
This section introduces some transfer learning techniques that are relevant to our task of hedging VAs.

\subsection{Reward Shaping}

In the context of hedging VAs using deep reinforcement learning and transfer learning, reward shaping becomes a crucial technique. 
It involves modifying the reward function in the target domain to incorporate additional guidance, which often leads to more efficient learning and better performance.
This technique can be particularly useful for managing the complex risks associated with VAs, as it can guide the learning process towards strategies that are more effective in hedging these products.

One way to implement reward shaping in this context is by introducing auxiliary rewards that reflect the performance of hedging strategies learned from the source domains.
Reward shaping learns an auxiliary reward function $\mathcal{R}_s: \mathcal{S} \times \mathcal{A} \times \mathcal{S} \rightarrow \mathbb{R}$ from the source domains.
The auxiliary reward function is then used to shape the reward function in the target domain, $\mathcal{R}'_t = \mathcal{R}_t + \mathcal{R}_s$, by incorporating the insights gained from the source domains.

Some popular reward shaping techniques include potential-based reward shaping~\citep{ng1999policy}, potential based state-action advice~\citep{wiewiora2003principled}, dynamic value function advice~\citep{harutyunyan2015expressing}.

\subsection{Policy Transfer}

The most straightforward approach to transfer learning is to directly transfer the policy learned from the source domains to the target domain via policy distillation.
Policy distillation is a technique that transfers the knowledge from a teacher policy to a student policy by training the student policy to mimic the teacher policy up to a certain extent.
The teacher policy is learned from the source domains, and the student policy learns the hedging strategies in the target domain while guided by the teacher policy.
In the Distral algorithm~\citep{teh2017distral}, the student policy maximizes a multi-task objective:
$\max_{\phi} \sum_{i=1}^K \mathcal{J}(\pi_\phi, \pi_{E_i})$, where

\begin{equation}
    \mathcal{J}(\pi_\phi, \pi_{E_i}) = \sum_{t=0}^\infty \mathbb{E}_{s_t \sim \mu_0^t, a_t \sim \pi_\phi} \left[ \gamma^t R_{t+1} + \frac{\alpha}{\beta} \log \pi_{\phi}(a_t|s_t) - \frac{1}{\beta}log \pi_{E_i}(a_t|s_t) \right],
\end{equation}

where a set of $K$ teacher policies $\pi_{E_i}$ are learned from the source domains, and the student policy $\pi_\phi$ is learned on the target domain. $\alpha$ and $\beta$ are hyperparameters that control the trade-off between mimicking the teacher policies and exploring the target domain.

\subsection{Representation Transfer}

Representation transfer is a technique that transfers the knowledge based on the following critical assumption:

\begin{assumption}
    The state space $\mathcal{S}$, the action space $\mathcal{A}$, and the reward function $\mathcal{R}$ can be disentangled into orthogonal subspaces, which are task-invariant such that knowledge can be transferred between domains on the universal subspaces.
\end{assumption}

A suitable representation transfer technique for our task of hedging VAs is modular networks~\citep{andreas2017modular}, which decomposes a policy $\pi$ into two sub-modules $g$ and $f$, i.e.,

\begin{equation}
    \pi = \phi(s_{market}, s_{guarantee}) = f(g(s_{market}), s_{guarantee}),
\end{equation}

~\cite{zhang2018decoupling} uses modular networks to transfer knowledge of physics models from previous tasks to new tasks in a simulated environment.
In the context of hedging VAs, $g$ is the module that processes the market information, and $f$ is the module that processes the guarantee information.
The core idea behind modular networks is that the market information can be applied for hedging strategies across different VA products, while the guarantee information is specific to each VA product.
Hence, knowledge can be transferred from the source domains to the target domain by transferring the market module $g$.

\subsection{Evaluation Metrics}

The metrics discussed for evaluating transfer learning approaches focus on two key aspects: mastery and generalization. 
Mastery assesses the agent's final performance level in the target domain, indicating how effectively it has learned a specific task from previous knowledge. 
Some common metrics for evaluating mastery include:

\begin{itemize}
    \item \textbf{Asymptotic performance:} the final reward of the agent in the target domain.
    \item \textbf{Transfer ratio:} the ratio of the agent's performance in the target domain with and without transfer learning.
\end{itemize}

Generalization, on the other hand, refers to the agent's ability to quickly adapt its learned knowledge to the target domain.

\begin{itemize}
    \item \textbf{Jumpstart performance:} the initial reward of the agent in the target domain.
    \item \textbf{Accumulated reward:} the total area under the reward curve over time in the target domain.
    \item \textbf{Time to threshold:} the time it takes for the agent to reach a certain performance threshold in the target domain.
    \item \textbf{Performance with fixed epochs:} the agent's performance in the target domain after a fixed number of epochs.
\end{itemize}

\section{Plans for Ongoing Numerical Experiments} \label{sec:numerical}

As we aim to enhance the risk management strategies for variable annuities (VAs) through the application of transfer learning, our next step involves conducting a series of numerical experiments. These experiments are crucial for validating the theoretical frameworks and methodologies developed so far. Our plan includes:

\begin{enumerate}
    \item \textbf{Simulation setup:} Designing a simulation environment that closely mirrors real-world market dynamics and VA contract specifics. 
    This setup will include various asset models, including the Black-Scholes and stochastic volatility models, to test the adaptability of transferred hedging strategies across different market conditions.
    \item \textbf{Baseline model comparison:} Establishing a set of baseline hedging strategies against which we can compare the performance of our transfer learning-enhanced strategies. 
    This will likely involve traditional delta hedging techniques and possibly other reinforcement learning approches that have not utilized transfer learning.
    \item \textbf{Transfer learning implementation:} Applying the transfer learning methodologies discussed, including reward shaping, policy transfer, and/or representation transfer to the task of hedging VAs. 
    The transfer can happen between different VA products, different asset models, different model specifications, and between simulated and real-world data.
    \item \textbf{Performance evaluation:} Utilizing the evaluation metrics outlined in the previous sections to assess mastery and generalization of the transfer learning strategies. 
    Key metrics will include asymptotic performance, transfer ratio, jumpstart performance, and time to threshold.
    \item \textbf{Sensitivity analysis:} Conducting sensitivity analyses to understand how changes in market conditions, contract specifics, and model parameters affect the performance of our transfer learning strategies. This will help in identifying the robustness and limitations of our approach.
    \item \textbf{Hedging in real-world:} If accessible, applying the trained models to real-world data to further validate their practical applicability and performance in real-world market conditions.
\end{enumerate}

Through these numerical experiments, we aim to demonstrate the efficacy of transfer learning in improving the hedging of VAs in a variety of market conditions and contract specifics. 
We expect that our transfer learning-enhanced strategies will outperform traditional hedging techniques and possibly other machine learning approaches that have not utilized transfer learning. 
This will provide strong evidence for the potential of transfer learning in improving risk management strategies for VAs and other complex financial products in a dynamic market environment.

\subsection{Initial Numerical Experiments}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.8\textwidth]{./project3/figures/Figure_1.png}
    \caption{Initial numerical experiments for GMMB}
    \label{fig3:GMMB}
\end{figure}

\newpage
\footnotesize 
\bibliographystyle{plainnat}
\bibliography{refP3}

\end{document}

### 2024-04-04 introduction.tex
new

@@
 Quantitative risk management is a key component of modern financial systems, ensuring the stability and resilience of markets, institutions, and portfolios against an array of risks. 
-In the era of complex financial products, such as option portfolios and variable annuity contracts, traditional risk assessment methods often fall short in accurately capturing the multifaceted nature of market, credit, and operational risks.
-This is where advanced simulation techniques, particularly nested simulation procedures, become indispensable.
+For complex financial products, such as option portfolios and variable annuity contracts, traditional risk assessment methods often fall short in accurately capturing the multifaceted nature of market, credit, and operational risks.
+This is where advanced Monte Carlo simulation techniques, particularly nested simulation procedures, become indispensable.
+In constract to finite-difference methods, a Monte Carlo simulation scheme is more flexible and can be easily adapted to model complex financial products with multiple sources of risk.

### 2024-04-04 project1/nsSurvey.tex
new

@@
 It is efficient to implement, and it exhibits fast empirical convergence in estimating risk measures for option portfolios. 
+However, we have only examined the performance for option portfolios in this study, where finding a suitable set of basis functions for regression is relatively easy.
+For payoff functions with high complexity or high dimensionality, the regression-based procedure may not be the best choice.
+In practice, a variable annuity contract is often high-dimensional in time with a complex payoff structure, and it is a challenging problem for nested simulation procedures.
+In such cases, a neural network-based procedure may be more suitable, as it is a data-driven algorithm that finds a suitable set of basis functions automatically.
+In Chapter~\ref{ch2}, we will examine the performance of regression-based and neural network-based nested simulation procedures for estimating risk measures for variable annuities.

### 2024-04-04 project3/tlHedging.tex
new

@@
 We aim to leverage the knowledge from the hedging strategies of financial derivatives to construct hedging strategies for VAs, thereby improving the risk management of these products.
-The rest of the paper is organized as follows: Section~\ref{sec:vaHedging} presents the problem formulation for hedging variable annuity with a deep neural network, Section~\ref{sec:tlHedging} presents the background knowledge for transfer learning, and Section~\ref{sec:numerical} states the plans for ongoing numerical experiments.
+The rest of the paper is organized as follows: Section~\ref{sec3:vaHedging} presents the problem formulation for hedging variable annuity with a deep neural network, Section~\ref{sec3:tlHedging} presents the background knowledge for transfer learning, and Section~\ref{sec3:numerical} states the plans for ongoing numerical experiments.
 
-\section{Dynamic Hedging of Variable Annuities} \label{sec:vaHedging}
-
-\subsection{Variable Annuities}
-Variable annuity contracts offer different types of guarantees.
-Generally speaking, a portion of the VA premium is invested in a sub-account whose return is linked to some stock indices.
-
-Two relevant types of guarantees in our studies are:
-\begin{itemize}[noitemsep]
-    \item \textbf{Guaranteed Minimum Maturity Benefit (GMMB)}: A GMMB contract pays a maturity benefit equal to the greater of the sub-account value and a fixed guarantee value.
-    The guarantee value is often set as a percentage, e.g., 75\% or 100\%, of the initial premium.
-
-    \item \textbf{Guaranteed Minimum Withdrawal Benefit (GMWB)}: A GMWB contract guarantees the minimum amount of periodic withdrawal the policyholder can take from the sub-account until maturity, even if the sub-account value reduces to zero.
-    The minimum withdrawal benefit is typically a fixed percentage of the guarantee value.
-    The guarantee value will decrease if the withdrawal exceeds the guaranteed minimum.
-The GMWB is typically offered with an accumulation period, during which no withdrawals are made but a GMDB is usually offered.
-Additional features offered with the GMWB include roll-up, ratchet, and reset~\citep{geneva2013variable}.
-\end{itemize}
-For a comprehensive review of other types of VA contracts such as Guaranteed Minimum Death Benefit (GMDB), Guaranteed Minimum Accumulation Benefit (GMAB) and Guaranteed Lifetime Withdrawal Benefit (GLWB), we refer readers to~\cite{hardy2003investment}.
-Next we present a summary of dynamic hedging for VA contracts.
-We refer readers to~\cite{dang2021efficient} for detailed modeling of insurer liabilities in different VA contracts and Greek estimation.
-
-Consider a generic VA contract with maturity $T>0$ periods, e.g., $T=240$ months.
-Denote the policyholder's (random) time of death by $\tau>0$.
-Then the contract expires at $T'=\min\{T,\tau\}$, i.e., the earlier of the contract maturity and the death of the policyholder.
-Let $S_t$, $F_t$, and $G_t$ be the indexed stock price, the subaccount value and the guarantee value, respectively, at time $t=1,2,\ldots,T$.
-Evolution of the subaccount value and the guarantee value of a VA contract affect the contract payout.
-Note that the policyholder's (random) time of death also affects the timing of the benefit payout for certain types of VA such as GMDB, but this is not considered in our study for simplicity.
-For clarity, we use $F_t$ and $F_{t_+}$ to denote the sub-account value just before and just after the withdrawal at time $t$, if any.
-Let $\eta_g$ be the gross rate of management fee that is deducted from the fund value at each period and let $\eta_n < \eta_g$ be the net rate of management fee income to the insurer.
-The difference between the gross management fee and the net management fee income represents the incurred investment expenses.
-
-At the inception of the contract, i.e., $t=0$, we assume that the whole premium is invested in the stock index and the guarantee base is set to the sub-account value:
-\begin{equation*}
-    S_0=F_0=G_0.
-\end{equation*}
-At each time $t=1,\ldots,T$, the following events take place in the following order:
-\begin{enumerate}
-    \item The sub-account value changes according to the growth of the underlying stock and the (gross) management fee is deducted. That is, 
-        \begin{equation*}
-            F_t = F_{(t-1)_+}\cdot\frac{S_{t}}{S_{t-1}}\cdot(1-\eta_g),
-        \end{equation*} 
-    where $(x)^+=\max\{x,0\}$ and $F_{(t-1)_+}$ will be defined later. The insurer's income at time $t$ is the net management fee, i.e., $F_t\eta_n$.
-
-    \item The guarantee value ratchets up (ratcheting is a common feature in GMWB) if the sub-account value exceeds the previous guarantee value, i.e., 
-        \begin{equation*}
-            G_t = \max\{G_{t-1},F_t\}.
-        \end{equation*}
-
-    \item The withdrawal is made (for GMWB) and is deducted from the sub-account value, i.e., 
-        \begin{equation*}
-            F_{t_+} = (F_t - I_t)^+,
-        \end{equation*} 
-    where $I_t = \gamma G_t$. A GMMB can be modeled with $\gamma = 0$.
-\end{enumerate}
-
-We see from the above modeling steps that the status of a generic VA contract is summarized by a triplet $(S_t,F_t,G_t)$ whose evolution is driven by the stochasticity of $S_t$.
-In practice, the simulation model may also incorporate additional complications like mortality, lapse, and excess withdrawal, etc.
-
-At any time $t=1,\ldots,T$, the insurer's liability in a VA contract is the present value of all payments, net of the fee income.
-For example, suppose that the per-period risk-free rate is $r$, then
-the insurer's time-$t$ liability for a GMMB contract is $L_t = e^{-r(T-t)}\cdot (G_T - F_T)^+ - \sum_{s=t+1}^{T} e^{-r(T-s)} F_s \eta_n$.
-Also, the insurer's time-$t$ liability for a GMWB contract is $L_t = \sum_{s=t+1}^{T} e^{-r(T-s)} [(I_s - F_s)^+- \eta_n F_s] $.
-
-For example, consider the time-$t$ liability $L_t$ of a GMWB:
-Suppose that given the stock sample path, e.g., an outer path $S_1,\ldots,S_t$, one can simulate future stock prices $\Stilde_{t+1},\ldots,\Stilde_{T}$, e.g., inner sample paths, based on some asset model such as a Black-Scholes model.
-The tilde symbol ($\sim$) over a quantity denotes its association with the inner simulation.
-Given the time~$t$ state $(S_t,F_t,G_t)$, following~\cite{cathcart2015calculating} the sensitivity of $L_t$ with respect to $S_t$ can be estimated by a pathwise estimator~\citep{glasserman2004monte}:
-\begin{equation}\label{eq:delta}
-    \Delta_t(\Stilde_{t+1},\ldots,\Stilde_{T} | S_t) = \frac{\partial L_t}{\partial S_t} = \sum_{s=t+1}^{T} e^{-r(T-s)} \left[\bm{1}\{\Itilde_s > \Ftilde_s\}\cdot \left( \frac{\partial \Itilde_s}{ \partial S_t} - \frac{\partial \Ftilde_s}{ \partial S_t}\right)- \eta_n \frac{\partial \Ftilde_s}{ \partial S_t}\right], \quad t=0,\ldots,T-1,
-\end{equation}
-where $\bm{1}\{\cdot\}$ is an indicator function and
-\begin{align*}
-    \frac{\partial \Ftilde_s}{ \partial S_t} &= \bm{1}\{\Itilde_{s-1} < \Ftilde_{s-1}\}\cdot\left( \frac{\partial \Ftilde_{s-1}}{ \partial S_t} - \frac{\partial \Itilde_{s-1}}{ \partial S_t}\right) \cdot \frac{\Stilde_s}{\Stilde_{s-1}}\cdot (1-\eta_g),\\
-    \frac{\partial \Gtilde_s}{ \partial S_t} &= \bm{1}\{\Gtilde_{s-1} < \Ftilde_{s}\}\cdot\frac{\partial \Ftilde_{s}}{ \partial S_t} + \bm{1}\{\Gtilde_{s-1} \geq \Ftilde_{s}\}\cdot\frac{\partial \Gtilde_{s-1}}{ \partial S_t},\\
-    \frac{\partial \Itilde_s}{ \partial S_t} &= \gamma \frac{\partial \Gtilde_s}{ \partial S_t}.
-\end{align*}
-The recursion is initialized with $(\Stilde_t,\Ftilde_t,\Gtilde_t) = (S_t,F_t,G_t)$, $\frac{\partial \Ftilde_s}{ \partial S_t} = \frac{\Ftilde_t}{S_t}$, and $\frac{\partial \Gtilde_s}{ \partial S_t} = \frac{\partial \Itilde_s}{ \partial S_t} = 0$.
+\section{Dynamic Hedging of Variable Annuities} \label{sec3:vaHedging}
 
@@
 
-\begin{equation} \label{eq:V_pi}
+\begin{equation} \label{eq3:V_pi}
     V^{\pi}_{\mathcal{M}}(s) = \mathbb{E}_{s_0 \sim \mu_0, a_i \sim \pi(\cdot|s_i), s_{i+1} \sim \mathcal{P}(\cdot|s, a)} \left[ \sum_{t=0}^{\infty} \gamma^t R_{t+1} |\pi, s \right],
@@
 
-where it can be conveniently rewritten as the value function $V^{\pi}_{\mathcal{M}}(s)$ in Equation~\ref{eq:V_pi} by setting the reward function $R_{t} = -L_t$ and the discount factor $\gamma = \frac{1}{1+r}$.
+where it can be conveniently rewritten as the value function $V^{\pi}_{\mathcal{M}}(s)$ in Equation~\ref{eq3:V_pi} by setting the reward function $R_{t} = -L_t$ and the discount factor $\gamma = \frac{1}{1+r}$.
 Other value functions can be used to optimize over a risk measure on the cumulative liability, such as the Value-at-Risk (VaR) or the Conditional Value-at-Risk (CVaR).
@@
 
-\section{Transfer Learning for Risk Management of Variable Annuities} \label{sec:tlHedging}
+\section{Transfer Learning for Risk Management of Variable Annuities} \label{sec3:tlHedging}
 
@@
 
-\section{Plans for Ongoing Numerical Experiments} \label{sec:numerical}
+\section{Plans for Ongoing Numerical Experiments} \label{sec3:numerical}
 
@@
 \end{figure}
-
-\newpage
-\footnotesize 
-\bibliographystyle{plainnat}
-\bibliography{refP3}
-
-\end{document}

### 2024-04-11 project1/nsSurvey.tex
new

@@
 
-$$\rho(g(X)), $$
-
-where $X \in \Omega$. 
-$g(X)$ can't be directly evaluated, but it is the output of
-
-$$ g(X) = \mathbb{E}\left[ Y|X=x \right]\vert_{x=X} $$
+$$\rho(L) = \rho(L(X))$$
+
+where $X \in \mathcal{X} \subset \mathbb{R}^d$, and $L = L(X)$ is a random variable whose distribution is characterized by $X$.
+$L(X)$ can't be directly evaluated, but it is the output of
+
+$$ L(X) = \mathbb{E}\left[ Y|X=x \right]\vert_{x=X} $$
 
 Some common risk measures are in the nested expectation form, in which 
-$$\rho(g(X)) = \mathbb{E}\left[ h(g(X)) \right]$$
-
-where $h(\cdot)$ is a known function. 
-Forms of $h$ include the following:
-\begin{itemize}
-    \item 	Smooth functions, e.g., a quadratic tracking error with benchmark $b$: $h(t) = (t - b)^2$
-    \item 	Lipschitz continuous functions, e.g., a mean excess loss over threshold $u$: $h(t) = \max\{t - u, 0\}$. Here, $h$ is a hockey-stick function.
-    \item 	Indicator functions, e.g., probability of a large loss over a threshold $u$: $h(t) = \mathbb{I}_{\{t \geqslant u\}}$
-\end{itemize}
+$$\rho(L) = \mathbb{E}\left[ h(L) \right]$$
+
+where $h: \mathbb{R} \rightarrow \mathbb{R}$ is a known function. 
+Common forms of $h$ includes smooth functions, Lipschitz continuous functions, and indicator functions.
+The nested expectation form is a general form that covers many risk measures of interest in financial engineering by varying the function $h$.
+
+\begin{definition} \label{def1:smooth}
+    A function $h: \mathbb{R} \rightarrow \mathbb{R}$ is smooth if it is continuously differentiable up to the $n$-th order for some $n \in \mathbb{N}$, 
+    and its $n$-th and $(n-m)$-th derivatives are bounded for some $m \in \mathbb{N}$ and $m < n$.
+\end{definition}
+
+A quadratic tracking error with a benchmark $b$ falls into this category, in which $h(t) = (t - b)^2$.
+In the context of nested simulation, different procedures require different versions of Definition~\ref{def1:smooth} to specify the smoothness of $h$ for their convergence analysis.
+Table~\ref{tab1:smoothness} summarizes the smoothness assumption of $h$ for different nested simulation procedures in the literature.
+
+\begin{table}[ht!]
+    \centering
+    \begin{tabular}{lcc}
+    \toprule
+    \textbf{Nested Simulation Procedures} & $n$ & $m$ \\
+    \midrule
+    Regression & $2$ & $0$ \\
+    Kernel smoothing & $3$ & $1$ \\
+    Kernel ridge regression & $2$ & $1$ \\
+    Likelihood ratio & $2$ & $1$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Smoothness assumption of $h$ for different nested simulation procedures}
+    \label{tab1:smoothness}
+\end{table}
+
+\begin{definition} \label{def1:lipschitz}
+    A function $h: \mathbb{R} \rightarrow \mathbb{R}$ is Lipschitz continuous with Lipschitz constant $K$ if for all $t_1, t_2 \in \mathbb{R}$, 
+    $$|h(t_1) - h(t_2)| \leq K|t_1 - t_2|.$$
+\end{definition}
+
+A mean excess loss over a threshold $u$ is defined by setting $h(t) = \max\{t - u, 0\}$, which is a special case of a Lipschitz continuous function.
+
+\begin{definition} \label{def1:indicator}
+    A function $h: \mathbb{R} \rightarrow \mathbb{R}$ is an indicator function if 
+    $$h(t) = \mathbb{I}_{\{t \geq u\}}$$
+    for some $u \in \mathbb{R}$.
+\end{definition}
+
+The probability of a large loss over a threshold $u$ is obtained by setting $h(t) = \mathbb{I}_{\{t \geq u\}}$.
 
 Other risk measures of interest that are not in the nested expectation form are the value at risk (VaR) and the conditional value at risk (CVaR). 
-The $\alpha$-VaR of $g(X)$ is defined as
-$$
-    \mbox{VaR}_\alpha(g(X)) = q_\alpha = \inf \left\{ q: \Pr(g(X)\leq q) \geq \alpha \right\}.
-$$
-The $\alpha$-CVaR of $g(X)$ is defined as
-$$
-    \mbox{VaR}_\alpha(g(X)) =\frac{1}{1-\alpha} \int_{\alpha}^{1} q_v dv. 
+The $\alpha$-VaR of $L$ is defined as
+$$
+    \mbox{VaR}_\alpha(L) = q_\alpha = \inf \left\{ q: \Pr(L\leq q) \geq \alpha \right\}.
+$$
+The $\alpha$-CVaR of $L$ is defined as
+$$
+    \mbox{CVaR}_\alpha(L) =\frac{1}{1-\alpha} \int_{\alpha}^{1} q_v dv. 
 $$
@@
 
-The standard nested simulation procedure estimates $g(X_i)$ with a standard Monte Carlo estimator
-
-$$\hat{g}_N(X_i) = \frac{1}{N} \sum_{j=1}^N Y_{ij}; ~~~ Y_{ij} \sim F_{Y|X_i} $$
-
-Let $(\hat{g}_N(\mathbf{X}))_{[1]}, \dots, (\hat{g}_N(\mathbf{X}))_{[M]}$ be the order statistics of $\hat{g}_N(X_1), \dots \hat{g}_N(X_M)$. 
+The standard nested simulation procedure estimates $L_i = L(X_i)$ with a standard Monte Carlo estimator
+
+$$\hat{L}_{N, i} = \frac{1}{N} \sum_{j=1}^N Y_{ij}; ~~~ Y_{ij} \sim F_{Y|X_i} $$
+
+Let $\hat{L}_{(i)}, \dots, \hat{L}_{(M)}$ be the order statistics of $\hat{L}_{N, 1}, \dots \hat{L}_{N, M}$. 
 The standard nested simulation estimators for different forms of $\rho$ are as follows:
@@
     \item   Nested expectation form:
-            $$\hat{\rho}_{M, N} = \frac{1}{M} \sum_{i=1}^M h(\hat{g}_N(X_i)) = \frac{1}{M} \sum_{i=1}^M h(\bar{Y}_{N, i}); ~~~ X_i \sim F_X$$
+            $$\hat{\rho}_{M, N} = \frac{1}{M} \sum_{i=1}^M h(\hat{L}_{N, i}) = \frac{1}{M} \sum_{i=1}^M h(\bar{Y}_{N, i}); ~~~ X_i \sim F_X$$
     \item   Value at risk (VaR):
-            $$\hat{\rho}_{M, N} = (\hat{g}_N(\mathbf{X}))_{\lceil \alpha M \rceil}$$
+            $$\hat{\rho}_{M, N} = \hat{L}_{(\lceil \alpha M \rceil)}$$
     \item   Conditional value at risk (CVaR):
-            $$\hat{\rho}_{M, N} = (\hat{g}_N(\mathbf{X}))_{\lceil \alpha M \rceil} + \frac{1}{(1-\alpha) M} \sum_{i=1}^M \max \{\hat{g}_N(X_i) - (\hat{g}_N(\mathbf{X}))_{\lceil \alpha M \rceil}, 0 \}$$
+            $$\hat{\rho}_{M, N} = \hat{L}_{(\lceil \alpha M \rceil)} + \frac{1}{(1-\alpha) M} \sum_{i=1}^M \max \{\hat{L}_{N, i} - \hat{L}_{(\lceil \alpha M \rceil)}, 0 \}$$
 \end{enumerate}
 
-~\cite{gordy2010nested} analyze the optimal budget allocation of the standard nested simulation procedure with respect to the MSE of the estimator $\hat{\rho}_{M, N}$.
+~\cite{gordy2010nested} analyze the optimal budget allocation of the standard nested simulation procedure with respect to the MSE of the estimator $\hat{\rho}_{M, N}$ for hockey-stick $h$, indicator $h$, and VaR.
 
@@
 \begin{equation*}
-    \hat{\rho}^{\text{MLMC}}_\Gamma = \sum_{\ell=0}^{L} \left( \frac{1}{M_{\ell}} \sum_{i=1}^{M_{\ell}} h(\hat{g}_{N_{\ell}}(X_{i, \ell})) - \frac{1}{M_{\ell-1}} \sum_{i=1}^{M_{\ell-1}} h(\hat{g}_{N_{\ell-1}}(X_{i, \ell-1})) \right), ~~~ X_{i, \ell} \sim F_X,
+    \hat{\rho}^{\text{MLMC}}_\Gamma = \sum_{\upsilon=0}^{\Upsilon} \left( \frac{1}{M_{\upsilon}} \sum_{i=1}^{M_{\upsilon}} h(\hat{L}_{N_{\upsilon}}(X_{i, \upsilon})) - \frac{1}{M_{\upsilon-1}} \sum_{i=1}^{M_{\upsilon-1}} h(\hat{L}_{N_{\upsilon-1}}(X_{i, \upsilon-1})) \right), ~~~ X_{i, \upsilon} \sim F_X,
 \end{equation*}
 
-where $\hat{g}_N(\cdot) = 0$, $L$ is the number of levels, $M_{\ell}$ is the number of outer scenarios at level $\ell$, and $N_{\ell}$ is the number of inner replications at level $\ell$.
+where $\hat{L}_{N_{-1}}(\cdot) = 0$, $\Upsilon$ is the number of levels, $M_{\upsilon}$ is the number of outer scenarios at level $\upsilon$, and $N_{\upsilon}$ is the number of inner replications at level $\upsilon$.
 Applying the analysis of~\cite{giles2015multilevel} in a nested simulation context,~\cite{giles2019multilevel} show that the MLMC method can achieve a similar level of accuracy as the standard nested simulation procedure with a lower total computational budget.
-The simulation budget $\Gamma$ is the sum of the computational budget at each level, that is, $\Gamma = \sum_{\ell=0}^{L} M_{\ell} \cdot N_{\ell}$.
+The simulation budget $\Gamma$ is the sum of the computational budget at each level, that is, $\Gamma = \sum_{\upsilon=0}^{\Upsilon} M_{\upsilon} \cdot N_{\upsilon}$.
 
@@
 
-In supervised learning, $g(\cdot)$ can be approximated by $\hat{g}^{\text{SL}}_{M, N}(\cdot)$, which is based on a chosen function family $\mathcal{G}$ and observations from the standard nested simulation procedure.
-Consider the observation pairs $(X_i, \hat{g}_N(X_i))$ for $i \in \{1, \dots, M\}$ as training data, we can use supervised learning to approximate $g(\cdot)$ by $\hat{g}^{\text{SL}}_{M, N}(\cdot)$ and to pool the inner replications from all outer scenarios.
+Supervised learning-based nested simulation procedures treat the estimation of $L(\cdot)$ as a supervised learning problem. 
+In supervised learning, $L(\cdot)$ can be approximated by $\hat{L}^{\text{SL}}_{M, N}(\cdot)$, which is based on a chosen function family and observations from the standard nested simulation procedure.
+Consider the observation pairs $(X_i, \hat{L}_{N, i})$ for $i \in \{1, \dots, M\}$ as training data, we can use supervised learning to approximate $L_i$ by $\hat{L}_{M, N}^{\text{SL}}(X_i)$ and to pool the inner replications from all outer scenarios.
+More specifically, $\hat{L}^{\text{SL}}_{M, N}(\cdot)$ denotes the supervised learning model trained on $(X_i, \hat{L}_{N, i})$ for $i \in \{1, \dots, M\}$, which is the simulation output of the standard nested simulation procedure with $M$ outer scenarios and $N$ inner replications.
 Using the $M$ \textit{training} samples, a nested Monte Carlo estimator of $\rho$ is given by
@@
     \item   Nested expectation form:
-            $$\hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = \frac{1}{M} \sum_{i=1}^M h(\hat{g}^{\text{SL}}_{M, N}(X_i)); ~~~ X_i \sim F_X$$
+            $$\hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = \frac{1}{M} \sum_{i=1}^M h(\hat{L}^{\text{SL}}_{M, N}(X_i)); ~~~ X_i \sim F_X$$
     \item   VaR:
-            $$\hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = (\hat{g}^{\text{SL}}_{M, N}(\mathbf{X}))_{\lceil \alpha M \rceil}$$
+            $$\hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = \hat{L}^{\text{SL}}_{(\lceil \alpha M \rceil)}$$
     \item   CVaR:
-            $$\hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = (\hat{g}^{\text{SL}}_{M, N}(\mathbf{X}))_{\lceil \alpha M \rceil} + \frac{1}{(1-\alpha) M} \sum_{i=1}^M \max \{\hat{g}^{\text{SL}}_{M, N}(X_i) - (\hat{g}^{\text{SL}}_{M, N}(\mathbf{X}))_{\lceil \alpha M \rceil}, 0 \}$$
+            $$\hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = \hat{L}^{\text{SL}}_{(\lceil \alpha M \rceil)} + \frac{1}{(1-\alpha) M} \sum_{i=1}^M \max \{\hat{L}^{\text{SL}}_{M, N}(X_i) - \hat{L}^{\text{SL}}_{(\lceil \alpha M \rceil)}, 0 \}$$
 \end{enumerate}
-where $(\hat{g}_{M, N}(\mathbf{X}))_{\lceil \alpha M \rceil}$ is the $\lceil \alpha M \rceil$-th order statistic of $\hat{g}^{\text{SL}}_{M, N}(X_1), \dots, \hat{g}_{M, N}(X_M)$.
-Similarly, with $M'$ \textit{test} samples of $X$, namely $\tilde{\mathbf{X}} = \tilde{X}_1, \dots, \tilde{X}_{M'}$, an estimator is given by
+where $\hat{L}_{(\lceil \alpha M \rceil)}$ is the $\lceil \alpha M \rceil$-th order statistic of $\hat{L}^{\text{SL}}_{M, N}(X_1), \dots, \hat{L}_{M, N}(X_M)$.
+
+After a supervised learning model is trained, it can be used to make predictions for all $X \in \mathcal{X}$.
+Instead of using the same training samples to estimate the risk measure, we can use predictions of a new set of $M'$ \textit{test} samples of $X$, namely $\tilde{\mathbf{X}} = \tilde{X}_1, \dots, \tilde{X}_{M'}$.
+The resulting supervised learning-based estimator of $\rho^{\text{SL}, \text{Test}}$ is given by
 
@@
     \item   Nested expectation form:
-            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = \frac{1}{M'} \sum_{i=1}^{M'} h(\hat{g}^{\text{SL}}_{M, N}(\tilde{X}_i)); ~~~ \tilde{X}_i \sim F_X.$$
+            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = \frac{1}{M'} \sum_{i=1}^{M'} h(\hat{L}^{\text{SL}}_{M, N}(\tilde{X}_i)); ~~~ \tilde{X}_i \sim F_X.$$
     \item   VaR:
-            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = (\hat{g}^{\text{SL}}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M' \rceil}.$$
+            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = \hat{L}^{\text{SL}}_{(\lceil \alpha M' \rceil)}.$$
     \item   CVaR:
-            \begin{align*}
-                \hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} & = (\hat{g}^{\text{SL}}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M' \rceil}  \\
-                & + \frac{1}{(1-\alpha) M'} \sum_{i=1}^{M'} \max \{\hat{g}^{\text{SL}}_{M, N}(\tilde{X}_i) - (\hat{g}^{\text{SL}}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M' \rceil}, 0 \}, 
-            \end{align*}
+            \begin{equation*}
+                \hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} 
+                = \hat{L}^{\text{SL}}_{(\lceil \alpha M' \rceil)} 
+                + \frac{1}{(1-\alpha) M'} \sum_{i=1}^{M'} \max \{\hat{L}^{\text{SL}}_{M, N}(\tilde{X}_i) - \hat{L}^{\text{SL}}_{(\lceil \alpha M' \rceil)}, 0 \}, 
+            \end{equation*}
 \end{enumerate}
-where $(\hat{g}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M' \rceil}$ is the $\lceil \alpha M' \rceil$-th order statistic of $\hat{g}^{\text{SL}}_{M, N}(\tilde{X}_1), \dots, \hat{g}_{M, N}(\tilde{X}_{M'})$.
-Note that $\hat{g}^{\text{SL}}_{M, N}(\cdot)$ is derived from the training samples $(X_1, \hat{g}_N(X_1)), \dots, (X_M, \hat{g}_N(X_M))$.
-
-We are interested in minimizing the MSE of the supervised learning-based nested simulation estimator with supervised learning $\hat{\rho}^{\text{SL}, \text{Train}}_{M, N}$ and $\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'}$ subject to the total simulation budget $\Gamma$.
+where $\hat{L}^{\text{SL}}_{(\lceil \alpha M' \rceil)}$ is the $\lceil \alpha M' \rceil$-th order statistic of $\hat{L}^{\text{SL}}_{M, N}(\tilde{X}_1), \dots, \hat{L}^{\text{SL}}_{M, N}(\tilde{X}_{M'})$.
+Note that $\hat{L}^{\text{SL}}_{M, N}(\cdot)$ is the model preditions of a supervised learning model trained on the training samples $(X_1, \hat{L}_{N, 1}), \dots, (X_M, \hat{L}_{N, M})$.
+
+We are interested in minimizing the MSE of the supervised learning-based nested simulation estimator with supervised learning $\hat{\rho}^{\text{SL}, \text{Train}}_{M, N}$ and $\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'}$ subject to the total simulation budget $\Gamma$, and we are interested in the order of convergence of the estimator for all nested simulation procedures when the total simulation budget $\Gamma$ approaches infinity.
 
@@
 
-Existing literature on nested simulation procedures has proposed different methods to approximate the true function $g(\cdot)$ with supervised learning algorithms. 
+Existing literature on nested simulation procedures has proposed different methods to approximate the true function $L(\cdot)$ with supervised learning models. 
 Methods that include theoretical convergence results are regression~\citep{broadie2015risk}, kernel smoothing~\citep{hong2017kernel}, and kernel ridge regression~\citep{wang2022smooth}.
-Their estimators of $g(\cdot)$ are given by $\hat{g}^{\text{REG}}_{M, N}(\cdot)$, $\hat{g}^{\text{KS}}_{M, N}(\cdot)$, and $\hat{g}^{\text{KRR}}_{M, N}(\cdot)$, respectively.
+Their estimators of $L(\cdot)$ are given by $\hat{L}^{\text{REG}}_{M, N}(\cdot)$, $\hat{L}^{\text{KS}}_{M, N}(\cdot)$, and $\hat{L}^{\text{KRR}}_{M, N}(\cdot)$, respectively.
 
@@
     \item   Regression:
-            $$\hat{g}^{\text{REG}}_{M, N}(X) = \Phi(X) \hat{\beta},$$
+            $$\hat{L}^{\text{REG}}_{M, N}(X) = \Phi(X) \hat{\beta},$$
             where $\Phi$ is a chosen basis, and $\hat{\beta}$ is estimated from the training samples.
     \item   Kernel smoothing:
-            $$\hat{g}^{\text{KS}}_{M, N}(X) = \frac{\sum_{i=1}^M \bar{Y}_{N, i} K_w(X - X_i)}{\sum_{i=1}^M K_w(X - X_i)}, $$
+            $$\hat{L}^{\text{KS}}_{M, N}(X) = \frac{\sum_{i=1}^M \bar{Y}_{N, i} K_w(X - X_i)}{\sum_{i=1}^M K_w(X - X_i)}, $$
             where $K_w$ is the kernel function with bandwidth $w$.
     \item   Kernel ridge regression:
-            $$\hat{g}^{\text{KRR}}_{M, N}(X) = \argmin_{g \in \mathcal{N}_{\Psi}(\Omega)} \left( \frac{1}{M} \sum_{i=1}^M (\hat{g}_N(X_i) - g(X_i))^2 + \lambda \|g\|_{\mathcal{N}_{\Psi}(\Omega)}^2\right),$$
+            $$\hat{L}^{\text{KRR}}_{M, N}(X) = \argmin_{g \in \mathcal{N}_{\Psi}(\Omega)} \left( \frac{1}{M} \sum_{i=1}^M (\hat{L}_{N, i} - L_i)^2 + \lambda \|L\|_{\mathcal{N}_{\Psi}(\Omega)}^2\right),$$
             where $\mathcal{N}_{\Psi}(\Omega)$ is the reproducing kernel Hilbert space (RKHS) with kernel $\Psi$ defined domain $\Omega$, and $\lambda$ is the regularization parameter as in ridge regression.
-            More specifically, $\Phi$ is a Mat\'ern kernel with smoothness parameter $\nu$ and length scale parameter $\ell$.
+            More specifically, $\Phi$ is a Mat\'ern kernel with smoothness parameter $\nu$ and length scale parameter $\upsilon$.
 \end{itemize}
 
+These supervised learning models approximates the inner simulation model $L(\cdot)$ with a function $\hat{L}^{\text{SL}}_{M, N}(\cdot)$, and they are used to pool the inner replications from all outer scenarios to estimate the risk measure $\rho$.
+In simulation literature, using models to approximate simulation is often referred to as the metamodeling approach, or it is referred to as a proxy model in the financial engineering literature.
+Supervised learning models are broadly classified into regression and classification models depending on whether the traget variable $L$ is continuous or discrete.
+In our context, the target variable $L$ is continuous, and the supervised learning models refer to regression models.
+Regression models can be further categorized into parametric and non-parametric regression.
+Among our interested supervised learning models, regression is a parametric regression model, while kernel smoothing and kernel ridge regression are non-parametric regression model.
+
 \subsection{Likelihood Ratio Method}
 
-Instead of using a supervised learning model as proxy,~\cite{zhang2022sample} uses the likelihood ratio weights to pool the inner replications from all outer scenarios.
+Instead of using a supervised learning model as a proxy,~\cite{zhang2022sample} uses the likelihood ratio weights to pool the inner replications from all outer scenarios.
 Here, we restrict our attention to problems in the nested expectation form whose outer scenarios characterize the stochasticity of the inner simulation model. 
@@
 distribution $f_H$. Then, the likelihood ratio estimator of $\rho$ is given by
-$$\hat{\rho}^{\text{LR}}_{M,N} = \frac{1}{M} \sum_{i=1}^M h(\hat{g}^{\text{LR}}_N(X_i)), $$ where the inner replications are pooled by the likelihood ratio weights with
-$$\hat{g}^{\text{LR}}_N(X_i) = \frac{1}{N} \sum_{j=1}^N Y(H_j, X_i) \frac{f_{H|X}(H_{j}|X_i)}{f_H(H_{ij})}, \;\;\; H_j \sim f_H, \;\;\; i=1, \dots, M.$$
-
-With a total simulation budget $\Gamma$, we are interested in the order of convergence of estimators for all nested simulation procedures, which is measured by their MSE about the risk measure $\rho$.
+$$\hat{\rho}^{\text{LR}}_{M,N} = \frac{1}{M} \sum_{i=1}^M h(\hat{L}^{\text{LR}}_{N, i}), $$ where the inner replications are pooled by the likelihood ratio weights with
+$$\hat{L}^{\text{LR}}_{N, i} = \frac{1}{N} \sum_{j=1}^N Y(H_j, X_i) \frac{f_{H|X}(H_{j}|X_i)}{f_H(H_{ij})}, \;\;\; H_j \sim f_H, \;\;\; i=1, \dots, M.$$
+
+\subsection{Problem Statement}
+
+With a total simulation budget $\Gamma$, we are interested in the orders of convergence of estimators for all nested simulation procedures, which are measured by their MSE about the risk measure $\rho$.
 
@@
 
-where $\Gamma$ is the total simulation budget for all nested simulation procedures considered in this study.
-A special case is the MLMC method, where the total simulation budget $\Gamma$ is the sum of the computational budget at all levels.
+where $\Gamma$ is the total simulation budget for a nested simulation procedure.
+A special case is the MLMC method, where the total simulation budget $\Gamma$ is the sum of the simulation budgets at all levels.
 
@@
 Instead of showing the convergence of the KRR-based estimator in terms of MSE as in~\cite{gordy2010nested}, we show the connections between the convergence in MSE and the convergence in probabilistic order for absolute error.
-Our findings in Section~\ref{sec1:connection-mse-absolute-error} show that the analysis of ~\cite{wang2022smooth} indeed bridges the gap, but only in terms of the absolute error.
+Our findings in Section~\ref{sec1:connection-mse-absolute-error} show that the analysis of ~\cite{wang2022smooth} indeed bridges the gap, but only in terms of convergence in probabilistic order for the absolute error.
 
@@
     Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
-    We write $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-k} \right)$, that is, $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $k$ if 
-    $$
-        \exists C \limsup_{M} \frac{\mathbb{E} \left[\left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-k}} \leq C
+    We write $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-\xi} \right)$, that is, $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $\xi$ if
+    $$
+        \exists C \limsup_{M} \frac{\mathbb{E} \left[\left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-\xi}} \leq C
     $$
@@
     Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
-    We write $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-k})$, that is $\hat{\rho}_{\Gamma}$ converges in probabilistic order $k$ to $\rho$ if for large enough $\Gamma$,
-    $$
-        \forall \epsilon > 0 \exists C \mathbb{P} \left( \left| \hat{\rho}_{\Gamma} - \rho \right| \geq C \Gamma^{-k} \right) \leq \epsilon 
+    We write $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-\xi})$, that is $\hat{\rho}_{\Gamma}$ converges in probabilistic order $\xi$ to $\rho$ if for a sufficiently large $\Gamma$,
+    $$
+        \forall \epsilon > 0 \exists C \mathbb{P} \left( \left| \hat{\rho}_{\Gamma} - \rho \right| \geq C \Gamma^{-\xi} \right) \leq \epsilon 
     $$
@@
 We start by showing the convergence in probabilistic order from the convergence in MSE.
-Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-k} \right)$.
+Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-\xi} \right)$.
 Then, from the definition of convergence in MSE, there exists a constant $C$ such that 
 $$
-    \limsup_{M} \frac{\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-k}} \leq C.
+    \limsup_{M} \frac{\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-\xi}} \leq C.
 $$
@@
 $$
-\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \right] \leq C\gamma^{-k}.
+\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \right] \leq C\gamma^{-\xi}.
 $$
@@
 $$
-\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| \leq d\gamma^s\}} \right] + \mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\}} \right] \leq C\gamma^{-k}.
+\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| \leq d\gamma^s\}} \right] + \mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\}} \right] \leq C\gamma^{-\xi}.
 $$
@@
 $$
-    d^2 \gamma^{2s} \mathbb{P} \left(|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \right) \leq C \gamma^{-k}.
-$$
-
-Let $s = -\frac{k}{2}$. Arranging the terms, we have
-
-$$
-    \mathbb{P} \left( |\hat{\rho}_{\gamma} - \rho| > d\gamma^{-\frac{k}{2}} \right) \leq \frac{C}{d^2}
+    d^2 \gamma^{2s} \mathbb{P} \left(|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \right) \leq C \gamma^{-\xi}.
+$$
+
+Let $s = -\frac{\xi}{2}$. Arranging the terms, we have
+
+$$
+    \mathbb{P} \left( |\hat{\rho}_{\gamma} - \rho| > d\gamma^{-\frac{\xi}{2}} \right) \leq \frac{C}{d^2}
 $$
@@
 $$
-    \mathbb{P} \left( |\hat{\rho}_{\gamma} - \rho| > C^*\gamma^{-\frac{k}{2}} \right) \leq \epsilon
+    \mathbb{P} \left( |\hat{\rho}_{\gamma} - \rho| > C^*\gamma^{-\frac{\xi}{2}} \right) \leq \epsilon
 $$
@@
 $$
-    \left| \hat{\rho}_{\gamma} - \rho \right| = \mathcal{O}_\mathbb{P} \left( \Gamma^{-\frac{k}{2}} \right)
+    \left| \hat{\rho}_{\gamma} - \rho \right| = \mathcal{O}_\mathbb{P} \left( \Gamma^{-\frac{\xi}{2}} \right)
 $$
@@
     Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
-    If $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $k$, then $\hat{\rho}_{\Gamma}$ converges in probabilistic order to $\rho$ in order $\frac{k}{2}$.
+    If $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $\xi$, then $\hat{\rho}_{\Gamma}$ converges in probabilistic order to $\rho$ in order $\frac{\xi}{2}$.
 \end{theorem}
@@
 It is the first result that shows the connections between the convergence in MSE and the convergence in probabilistic order for absolute error in the context of nested simulation.
-Theorem~\ref{thm1:convergence-mse-prob} is a general result that can be applied to any nested simulation procedure that converges in MSE to $\rho$ in order $k$.
-If the estimator converges in MSE to $\rho$ in order $k$, then it converges in probabilistic order to $\rho$ in order $\frac{k}{2}$.
+Theorem~\ref{thm1:convergence-mse-prob} is a general result that can be applied to any nested simulation procedure that converges in MSE to $\rho$ in order $\xi$.
+If the estimator converges in MSE to $\rho$ in order $\xi$, then it converges in probabilistic order to $\rho$ in order $\frac{\xi}{2}$.
 
@@
 Similarly, the above argument is applied in reverse.
-Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-k})$.
+Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-\xi})$.
 The MSE of $\hat{\rho}_{\Gamma}$ can be separated into the same two parts.
@@
 $$
-    \mathbb{E}\left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| \leq d\Gamma^{-2k}\}} \right] + \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^{-2k}\}} \right],
+    \mathbb{E}\left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| \leq d\Gamma^{-2\xi}\}} \right] + \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^{-2\xi}\}} \right],
 $$
@@
     \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s\}} \right] 
-    & \leq d^2 \Gamma^{-2k} \cdot \mathbb{E} \left[ \mathbb{I}\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s \} \right] \\
-    & = d^2 \Gamma^{-2k} \cdot \mathbb{P} \left(|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s \right) \leq d^2 \Gamma^{-2k} 
+    & \leq d^2 \Gamma^{-2\xi} \cdot \mathbb{E} \left[ \mathbb{I}\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s \} \right] \\
+    & = d^2 \Gamma^{-2\xi} \cdot \mathbb{P} \left(|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s \right) \leq d^2 \Gamma^{-2\xi} 
 \end{align*}
@@
 \begin{align*}
-    \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^{-2k}\}} \right] 
-    & = \int_{-\infty}^{-d\Gamma^{-2k}} (x - \rho)^2 f(x) dx + \int_{d\Gamma^{-2k}}^{\infty} (x - \rho)^2 f(x) dx 
+    \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^{-2\xi}\}} \right] 
+    & = \int_{-\infty}^{-d\Gamma^{-2k}} (x - \rho)^2 f(x) dx + \int_{d\Gamma^{-2\xi}}^{\infty} (x - \rho)^2 f(x) dx 
 \end{align*}
-Hence, $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $2k$ if and only if both integrals converge in order higher than $2k$. 
+Hence, $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $2\xi$ if and only if both integrals converge in order higher than $2\xi$. 
 The above argument shows that the convergence in probabilistic order does not necessarily imply the convergence in MSE.
-The convergence in probabilistic order is a weaker form of convergence than the convergence in MSE.
+Hence, the converse of Theorem~\ref{thm1:convergence-mse-prob} is not necessarily true, and the convergence in probabilistic order is a weaker form of convergence than the convergence in MSE.
+The immediate implication is that the results in~\cite{wang2022smooth}, which show the convergence in probabilistic order for the absolute error, is not necessarily equivalent to the convergence in MSE.
 
@@
 \begin{assumption} \label{as1:sns}
-    $h(g(X))$ has finite second moment, i.e., $\mathbb{E} \left[ \left( h(g(X)) \right)^2 \right] < \infty$.
-\end{assumption}
+    $h(L)$ has finite second moment, i.e., $\mathbb{E} \left[ \left( h(L) \right)^2 \right] < \infty$.
+\end{assumption}
+
+Assumption~\ref{as1:sns} is a standard assumption in the literature~\citep{hong2017kernel} for the analysis of nested simulation procedures to analyze the convergence of the variance of $\hat{\rho}_{M, N}$.
 
 \begin{assumption} \label{as1:sns-noise}
-    $\hat{g}_N(X) = g(X) + \bar{Z}_N(X)$, where the simulation noise $\bar{Z}_N(X)$ has zero mean and variance $\nu(X) / N$, where the conditional variance $\nu(X)$ is bounded, i.e., there exists $C_{\nu, 1} > 0$ such that $\nu(x) \leq C_{\nu, 1}$ for all $x \in \mathbb{R}$.
-\end{assumption}
-
-Let $\rho_M = \frac{1}{M} \sum_{i=1}^M h(g(X_i))$ be the nested Monte Carlo estimator with the true function $g$.
-The MSE of the standard procedure can be decomposed into two terms.
+    $\hat{L}_N(X) = L(X) + \bar{Z}_N(X)$, where the simulation noise $\bar{Z}_N(X)$ has zero mean and variance $\nu(X) / N$, where the conditional variance $\nu(X)$ is bounded, i.e., 
+    $$
+        \sup_{x \in \mathcal{X}} \nu(x) \leq C_{\nu, 1} < \infty.
+    $$
+\end{assumption}
+
+For simplicity, we denote $\hat{L}_N(X)$ as $\hat{L}_N$.
+Let $\rho_M = \frac{1}{M} \sum_{i=1}^M h(L_i)$ be the nested Monte Carlo estimator with the true function $g$.
+The MSE of the standard nested simulation procedure can be decomposed into two terms.
 
@@
 \begin{assumption} \label{as1:sns-smooth}
-    The function $h$ has bounded first and second order derivative, i.e., there exists $C_1 > 0$ such that $|h'(x)| \leq C_1$ for all $x \in \mathbb{R}$, and there exists $C_2 > 0$ such that $|h''(x)| \leq C_2$ for all $x \in \mathbb{R}$.
+    The function $h$ has bounded first and second order derivative, i.e.,
+    \begin{align*}
+        \sup_{x \in \mathcal{X}} |h'(x)|  & \leq C_{h, 1} < \infty, \\
+        \sup_{x \in \mathcal{X}} |h''(x)| & \leq C_{h, 2} < \infty.
+    \end{align*}
 \end{assumption}
@@
 \begin{align} \label{eq1:s2-sns}
-    S_2 & = \mathbb{E} \left[ \left( \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{g}^{\text{SL}}_{M, N}(X_i) - g(X_i) \right)^2 \right)^2\right] \nonumber \\
+    S_2 & = \mathbb{E} \left[ \left( \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{L}^{\text{SL}}_{M, N}(X_i) - g(X_i) \right)^2 \right)^2\right] \nonumber \\
     & = \mathbb{E} \left[ \left(\frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \bar{Z}^2_N(X_i) \right)^2 \right] \nonumber \\
@@
 \begin{assumption} \label{as1:sns-lip}
-    The function $h$ is Lipschitz continuous. Hence, $|h(x_1) - h(x_2) \leq K|x_1 - x_2|$ for some constant $K< \infty$.
+    The function $h$ is Lipschitz continuous. Hence, $|h(x_1) - h(x_2)| \leq K|x_1 - x_2|$ for some constant $K< \infty$.
 \end{assumption}
@@
 Kernel smoothing and KRR are kernel-based proxies, and they are more expensive due to distance calculation and cross-validation of hyperparameters. 
-The kNN proxy has only 1 hyperparameter $k$, while the KRR proxy requires 3 hyperparameters, namely the smoothness hyperparameter $\nu$, scale hyperparameter $\ell$, and the regularization hyperparameter $\lambda$.
+The kNN proxy has only 1 hyperparameter $k$, while the KRR proxy requires 3 hyperparameters, namely the smoothness hyperparameter $\nu$, scale hyperparameter $\upsilon$, and the regularization hyperparameter $\lambda$.
 Calculating the likelihood ratio weights is inevitable for the likelihood ratio-based procedure. 

### 2024-04-12 project1/nsSurvey.tex
new

@@
     \item   Kernel smoothing:
-            $$\hat{L}^{\text{KS}}_{M, N}(X) = \frac{\sum_{i=1}^M \bar{Y}_{N, i} K_w(X - X_i)}{\sum_{i=1}^M K_w(X - X_i)}, $$
+            $$\hat{L}^{\text{KS}}_{M, N}(X) = \frac{\sum_{i=1}^M \hat{L}_{N, i} K_w(X - X_i)}{\sum_{i=1}^M K_w(X - X_i)}, $$
             where $K_w$ is the kernel function with bandwidth $w$.
+
+            In~\cite{hong2017kernel}, the k-nearest neighbor (KNN) method is also implemented as a kernel smoothing method, but the convergence analysis is not provided.
+
+    \item   kNN~\citep{mack1981local}:
+            \begin{equation*}
+            \hat{L}^{\text{kNN}}_{M, N}(x) 
+            = \frac{\frac{1}{M R_M^d} \sum_{i=1}^M \hat{L}_{N, i} K\left(\frac{x - X_i}{R_M}\right)}{\frac{1}{M R_M^d} \sum_{i=1}^M K\left(\frac{x - X_i}{R_M}\right)}
+            \end{equation*}
+            where $R_k$ is the Euclidean distance between $X_i$ and its $k$-th nearest neighbor, and $K:\mathbb{R}^d \rightarrow \mathbb{R}$ is a bounded, nonnegative kernel function satisfying 
+            \begin{align*}
+                \int K(u) du & = 1, \\
+                K(u) &= 0 ~~~ ~\text{for}~ \|u\| \geq 1,
+            \end{align*}
+            where $\|\cdot\|$ is the Euclidean norm, and  $k$ is the number of nearest neighbors to consider.
+
     \item   Kernel ridge regression:
@@
     \hline
-    \textbf{Estimator for} $g(X)$ & \textbf{Smooth} $h$ & \textbf{Lipschitz}(\textbf{hockey-stick} $h$) & \textbf{Indicator} $h$ & \textbf{VaR} & \textbf{CVaR} \\
+    \textbf{Estimator for} $L$ & \textbf{Smooth} $h$ & \textbf{Lipschitz}(\textbf{hockey-stick} $h$) & \textbf{Indicator} $h$ & \textbf{VaR} & \textbf{CVaR} \\
     \hline
@@
 For the nested expectation form where $h$ is a smooth function or a Lipschitz continuous function, the analysis is incomplete.
-In this section, we fill in the holes in the analysis of~\cite{gordy2010nested}.
+In this section, we fill in the holes for the analysis of~\cite{gordy2010nested}.
 
@@
 
-For simplicity, we denote $\hat{L}_N(X)$ as $\hat{L}_N$.
+For simplicity, we abbreviate $\hat{L}_N(X)$ as $\hat{L}_N$, $\bar{Z}_N(X)$ as $\bar{Z}_N$, and $\bar{Z}_{N, i}$ as $\bar{Z}_{N, i}$.
 Let $\rho_M = \frac{1}{M} \sum_{i=1}^M h(L_i)$ be the nested Monte Carlo estimator with the true function $g$.
-The MSE of the standard nested simulation procedure can be decomposed into two terms.
+The MSE of the standard nested simulation procedure can be decomposed into two ways.
 
@@
             + 2  \mathbb{E} \left[ \left(\rho_M - \rho \right)^2 \right]  \nonumber \\
-    & = 2 \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{g}_{N}(X_i) \right) -  \frac{1}{M} \sum_{i=1}^M h\left(g(X_i) \right)  \right)^2\right] \nonumber \\
-    & ~~~~ + 2  \mathbb{E} \left[ \left(\frac{1}{M} \sum_{i=1}^M h\left(g(X_i) \right) - \mathbb{E}\left[ h(g(X))\right] \right)^2 \right]  \nonumber \\
-    & = 2 \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{g}_{N}(X_i) \right) -  h\left(g(X_i) \right)  \right)^2\right] + \frac{2}{M} \text{Var}(h(g(X))) \nonumber \\
-    & = 2 \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{g}_{N}(X_i) \right) -  h\left(g(X_i) \right)  \right)^2\right] + \mathcal{O}(M^{-1}),
-\end{align}
-where the last equality follows from Assumption~\ref{as1:sns}.
+    & = 2 \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) -  \frac{1}{M} \sum_{i=1}^M h\left(L_i \right)  \right)^2\right] \nonumber \\
+    & ~~~~ + 2  \mathbb{E} \left[ \left(\frac{1}{M} \sum_{i=1}^M h\left(L_i \right) - \mathbb{E}\left[ h(L)\right] \right)^2 \right]  \nonumber \\
+    & = 2 \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) -  h\left(L_i \right)  \right)^2\right] + \frac{2}{M} \text{Var}(h(L)) \nonumber \\
+    & = 2 \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) -  h\left(L_i \right)  \right)^2\right] + \mathcal{O}(M^{-1}),
+\end{align}
+
+In~\ref{eq1:mse-sns}, the last equality follows from Assumption~\ref{as1:sns}.
 The analysis of the first term is different for smooth and Lipschitz continuous $h$. 
 We will analyze them separately.
+
+Another way to decompose the MSE is the bias-variance decomposition as in~\cite{gordy2010nested}.
+
+\begin{align} \label{eq1:mse-sns2}
+    \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] 
+    & = \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \mathbb{E} \left[ \hat{\rho}_{M, N} \right] \right)^2 \right] + \left( \mathbb{E} \left[ \hat{\rho}_{M, N} \right] - \rho \right)^2 \nonumber \\
+    & = \text{Var}(\hat{\rho}_{M, N}) + \text{Bias}^2(\hat{\rho}_{M, N})
+\end{align}
+
+where $\text{Var}(\hat{\rho}_{M, N})$ is the variance of the estimator and $\text{Bias}(\hat{\rho}_{M, N})$ is the bias of the estimator about $\rho$.
+For a smooth function $h$, both ways of decomposing the MSE lead to the same order of convergence.
+However, for a Lipschitz continuous function $h$, Equation~\ref{eq1:mse-sns2} leads to a stronger order of convergence than Equation~\ref{eq1:mse-sns}.
+In the following, we analyze the convergence of the standard nested simulation procedure for smooth and Lipschitz continuous $h$ using following both decompositions.
+Their critical assumptions and convergence results are summarized and compared.
 
@@
 \begin{align} \label{eq1:taylor-sns}
-    & \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{g}_{N}(X_i) \right) -  h\left(g(X_i) \right)  \right)^2\right] \nonumber \\
-    & = \mathbb{E} \left[ \left( \frac{1}{M} \sum_{i=1}^M h'\left( g(X_i) \right) \left( \hat{g}_{N}(X_i) - g(X_i) \right) +  \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{g}_{N}(X_i) - g(X_i) \right)^2 \right)^2\right] \nonumber \\
-    & \leq 2 \underbrace{\mathbb{E} \left[ \left( \frac{1}{M} \sum_{i=1}^M h'\left( g(X_i) \right) \left( \hat{g}_{ N}(X_i) - g(X_i) \right) \right)^2\right]}_{S_1} \nonumber \\
-    & ~~~~ + 2 \underbrace{\mathbb{E} \left[ \left( \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{g}_{N}(X_i) - g(X_i) \right)^2 \right)^2\right]}_{S_2}
+    & \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) -  h\left(L_i \right)  \right)^2\right] \nonumber \\
+    & = \mathbb{E} \left[ \left( \frac{1}{M} \sum_{i=1}^M h'\left( L_i \right) \left( \hat{L}_{N, i} - L_i \right) +  \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{L}_{N, i} - L_i \right)^2 \right)^2\right] \nonumber \\
+    & \leq 2 \underbrace{\mathbb{E} \left[ \left( \frac{1}{M} \sum_{i=1}^M h'\left( L_i \right) \left( \hat{L}_{N, i}- L_i \right) \right)^2\right]}_{S_1} \nonumber \\
+    & ~~~~ + 2 \underbrace{\mathbb{E} \left[ \left( \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{L}_{N, i} - L_i \right)^2 \right)^2\right]}_{S_2}
 \end{align}
 where the last inequality is due to $2ab \leq a^2 + b^2$ for any $a, b \in \mathbb{R}$. 
-For different methods of nested estimation, each of the two terms on the right-hand side of Equation~\ref{eq1:taylor-sns} can be analyzed separately.
+The two terms on the right-hand side of Equation~\ref{eq1:taylor-sns} are analyzed separately.
 We start with the first term $S_1$.
@@
     S_1 
-    & = \mathbb{E} \left[ \left(\frac{1}{M} \sum_{i=1}^M h'\left( g(X_i) \right) \left( \hat{g}_{N}(X_i) - g(X_i) \right) \right)^2 \right] \nonumber \\
-    & = \mathbb{E} \left[ \left(\frac{1}{M} \sum_{i=1}^M h'\left( g(X_i) \right) \bar{Z}_N(X_i) \right)^2 \right] \nonumber \\
-    & \leq C_1^2 \mathbb{E} \left[ \left(\frac{1}{M} \sum_{i=1}^M \bar{Z}_N(X_i) \right)^2 \right] \nonumber \\
-    & = C_1^2 \mathbb{E} \left[ \frac{1}{M^2} \sum_{i=1}^M \sum_{j=1}^M \bar{Z}_N(X_i) \bar{Z}_N(X_j) \right] \nonumber \\
-    & = C_1^2 \mathbb{E} \left[ \frac{1}{M^2} \sum_{i=1}^M \bar{Z}_N^2(X_i) + \frac{1}{M^2} \sum_{i=1}^M \sum_{j \neq i}^M \bar{Z}_N(X_i) \bar{Z}_N(X_j) \right] \nonumber \\
+    & = \mathbb{E} \left[ \left(\frac{1}{M} \sum_{i=1}^M h'\left( L_i \right) \left( \hat{L}_{N, i} - L_i \right) \right)^2 \right] \nonumber \\
+    & = \mathbb{E} \left[ \left(\frac{1}{M} \sum_{i=1}^M h'\left( L_i \right) \bar{Z}_{N, i} \right)^2 \right] \nonumber \\
+    & \leq C_1^2 \mathbb{E} \left[ \left(\frac{1}{M} \sum_{i=1}^M \bar{Z}_{N, i} \right)^2 \right] \nonumber \\
+    & = C_1^2 \mathbb{E} \left[ \frac{1}{M^2} \sum_{i=1}^M \sum_{j=1}^M \bar{Z}_{N, i} \bar{Z}_{N, j} \right] \nonumber \\
+    & = C_1^2 \mathbb{E} \left[ \frac{1}{M^2} \sum_{i=1}^M \bar{Z}_{N, i}^2 + \frac{1}{M^2} \sum_{i=1}^M \sum_{j \neq i}^M \bar{Z}_{N, i} \bar{Z}_{N, j} \right] \nonumber \\
     & \leq  \frac{C_1^2 C_{\nu, 1}}{MN} = \mathcal{O}(M^{-1} N^{-1})
 \end{align}
-where the last inequality in Equation~\ref{eq1:s1-sns} is due to Assumption~\ref{as1:sns-noise}, independence of $X_i$ and $X_j$ for $i \neq j$, and the fact that $\mathbb{E} \left[ \bar{Z}_N(X) \right] = 0$.
+where the last inequality in Equation~\ref{eq1:s1-sns} is due to Assumption~\ref{as1:sns-noise}, independence of $X_i$ and $X_j$ for $i \neq j$, and the fact that the inner simulation noise has zero mean, i.e., $\mathbb{E} \left[ \bar{Z}_N \right] = 0$.
 It remains to analyze the second term $S_2$, where Assumption \ref{as1:sns-noise-var} is necessary to ensure the existence of the fourth moment of the simulation noise and the convergence of the second term.
@@
 \begin{align} \label{eq1:s2-sns}
-    S_2 & = \mathbb{E} \left[ \left( \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{L}^{\text{SL}}_{M, N}(X_i) - g(X_i) \right)^2 \right)^2\right] \nonumber \\
-    & = \mathbb{E} \left[ \left(\frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \bar{Z}^2_N(X_i) \right)^2 \right] \nonumber \\
-    & \leq C_2^2 \mathbb{E} \left[ \left(\frac{1}{2M} \sum_{i=1}^M \bar{Z}^2_N(X_i) \right)^2 \right] \nonumber \\
-    & = C_2^2 \mathbb{E} \left[ \frac{1}{2M^2} \sum_{i=1}^M \sum_{j=1}^M \bar{Z}^2_N(X_i) \bar{Z}^2_N(X_j) \right] \nonumber \\
-    & = C_2^2 \mathbb{E} \left[ \frac{1}{2M^2} \sum_{i=1}^M \bar{Z}_N^4(X_i) + \frac{1}{2M^2} \sum_{i=1}^M \sum_{j \neq i}^M \bar{Z}_N^2(X_i) \bar{Z}_N^2(X_j) \right] \nonumber \\
+    S_2 & = \mathbb{E} \left[ \left( \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{L}^{\text{SL}}_{M, N}(X_i) - L_i \right)^2 \right)^2\right] \nonumber \\
+    & = \mathbb{E} \left[ \left(\frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \bar{Z}_{N, i}^2 \right)^2 \right] \nonumber \\
+    & \leq C_2^2 \mathbb{E} \left[ \left(\frac{1}{2M} \sum_{i=1}^M \bar{Z}_{N, i}^2 \right)^2 \right] \nonumber \\
+    & = C_2^2 \mathbb{E} \left[ \frac{1}{2M^2} \sum_{i=1}^M \sum_{j=1}^M \bar{Z}_{N, i}^2 \bar{Z}_{N, j}^2 \right] \nonumber \\
+    & = C_2^2 \mathbb{E} \left[ \frac{1}{2M^2} \sum_{i=1}^M \bar{Z}_{N, i}^4 + \frac{1}{2M^2} \sum_{i=1}^M \sum_{j \neq i}^M \bar{Z}_N^2(X_i) \bar{Z}_N^2(X_j) \right] \nonumber \\
     & \leq  C_2^2 \left(\frac{ C_{\nu, 2} M}{2M^2N^2} + \frac{C_{\nu,1}^2M(M-1)}{2M^2N^2}\right) = \mathcal{O}(N^{-2})
 \end{align}
-where the second inequality is due to Assumption~\ref{as1:sns-smooth}, and the last inequality follows from Assumption~\ref{as1:sns-noise-var} and the fact that $\hat{g}_{N}(X)$ is a standard Monte Carlo estimator of $g(X)$.
+where the second inequality is due to Assumption~\ref{as1:sns-smooth}, and the last inequality follows from Assumption~\ref{as1:sns-noise-var} and the fact that $\hat{L}_N$ is a standard Monte Carlo estimator of $L$.
 Combining Equation~\ref{eq1:mse-sns},~\ref{eq1:taylor-sns},~\ref{eq1:s1-sns}, and~\ref{eq1:s2-sns}, we have
@@
 Setting $M = \mathcal{O}(\Gamma^{2/3})$ and $N = \mathcal{O}(\Gamma^{1/3})$, we provide the same rate of convergence as obtained for other risk measures in~\cite{gordy2010nested}.
-As shown in Section~\ref{sec1:connection-mse-absolute-error}, the convergence in MSE automatically implies the convergence in probabilistic order.
+However, we observe that Equation~\ref{eq1:s1-sns} converges in the order of $\mathcal{O}(M^{-1}N^{-1})$.
+The cross term here is potentially problematic \textcolor{red}{(Why?)}, as setting $N$ as a negative power of $M$ may result in Equation~\ref{eq1:s1-sns} to be divergent.
+
+In order to avoid the cross term, we proceed to follow the bias-variance decomposition in Equation~\ref{eq1:mse-sns2}.
+
+\begin{align} \label{eq1:bias-sns-smooth}
+    \text{Bias}(\hat{\rho}_{M, N})
+    & = \mathbb{E} \left[ \hat{\rho}_{M, N} \right] - \rho \nonumber \\
+    & = \mathbb{E} \left[ \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) \right] - \mathbb{E} \left[ h\left(L \right) \right]  \nonumber \\
+    & = \mathbb{E} \left[ h\left( \hat{L}_N \right) - h\left( L \right) \right] \nonumber \\
+    & = \mathbb{E} \left[h'\left( L \right) \left( \hat{L}_N - L \right) + \frac{1}{2} h''\left( z \right) \left( \hat{L}_N - L \right)^2 \right]
+\end{align}
+
+where the last equality follows from the Taylor expansion of the smooth function $h$.
+The first and second order Taylor expansion terms are analyzed separately in Equation~\ref{eq1:bias-sns-smooth-Taylor1} and Equation~\ref{eq1:bias-sns-smooth-Taylor2}.
+
+\begin{align} \label{eq1:bias-sns-smooth-Taylor1}
+    \mathbb{E} \left[ h'\left( L \right) \left( \hat{L}_N - L \right) \right]
+    & = \mathbb{E} \left[ h'\left( L \right) \left( \hat{L}_N - L \right) \right] \nonumber \\
+    & = \mathbb{E} \left[ \mathbb{E} \left[ h'\left( L \right) \left( \hat{L}_N - L \right)  | X \right] \right] \nonumber \\
+    & = \mathbb{E} \left[ h'\left( L \right) \mathbb{E} \left[ \hat{L}_N - L  | X \right] \right] = 0
+\end{align}
+
+\begin{align} \label{eq1:bias-sns-smooth-Taylor2}
+    \mathbb{E} \left[ h''\left( z \right) \left( \hat{L}_N - L \right)^2 \right]
+    & \leq \mathbb{E} \left[ |h''\left( z \right)| \left( \hat{L}_N - L \right)^2 \right] \nonumber \\
+    & \leq C_{h,2} \mathbb{E} \left[ \left( \hat{L}_N - L \right)^2 \right] \nonumber \\
+    & = C_{h,2} \text{Var}(\hat{L}_N) = \mathcal{O}\left( N^{-1} \right)
+\end{align}
+
+It remains to analyze the variance term in Equation~\ref{eq1:mse-sns2}.
+
+\begin{equation} \label{eq1:var-sns-smooth}
+    \text{Var}(\hat{\rho}_{M, N}) = \frac{1}{M} \text{Var}(h(\hat{L}_N)) = \mathcal{O}(M^{-1})
+\end{equation}
+
+Equation~\ref{eq1:var-sns-smooth} directly follows from Assumption~\ref{as1:sns} and the fact that $\hat{L}_N$ is a standard Monte Carlo estimator of $L$.
+Combining Equation~\ref{eq1:bias-sns-smooth-Taylor1},~\ref{eq1:bias-sns-smooth-Taylor2}, and~\ref{eq1:var-sns-smooth}, we are able to show the convergence order of the standard nested simulation procedure for a smooth function $h$ without the cross term as in Equation~\ref{eq1:s1-sns}.
 
@@
 \end{theorem}
+
 The proof techniques used in deriving Theorem~\ref{thm1:sns-smooth} is completely different from the one used in~\cite{gordy2010nested}.
@@
 \begin{align}
-    \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{g}_{N}(X_i) \right) -  h\left(g(X_i) \right)  \right)^2\right]    
-    & \leq \mathbb{E} \left[ \left( h\left( \hat{g}_{N}(X) \right) -  h\left(g(X) \right)  \right)^2\right]  \nonumber \\
-    & \leq K^2 \mathbb{E} \left[ \left( \hat{g}_{N}(X) -  g(X)  \right)^2\right] \nonumber \\
+    \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) -  h\left(L_i \right)  \right)^2\right]    
+    & \leq \mathbb{E} \left[ \left( h\left( \hat{L}_N \right) -  h\left(L \right)  \right)^2\right]  \nonumber \\
+    & \leq K^2 \mathbb{E} \left[ \left( \hat{L}_N -  L  \right)^2\right] \nonumber \\
     & = K^2 \mathbb{E} \left[ \left( \bar{Z}_{N}(X) \right)^2\right] = \mathcal{O}(N^{-1})
@@
 Setting $M = \mathcal{O}(\Gamma^{1/2})$ and $N = \mathcal{O}(\Gamma^{1/2})$, we provide a looser bound than the one obtained for hockey-stick $h$.
+This bound can be strengthened by using the bias-variance decomposition in Equation~\ref{eq1:mse-sns2}.
+
+\begin{align} \label{eq1:bias-sns-lip}
+    \text{Bias}(\hat{\rho}_{M, N})
+    & = \mathbb{E} \left[ \hat{\rho}_{M, N} \right] - \rho \nonumber \\
+    & = \mathbb{E} \left[ \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) \right] - \mathbb{E} \left[ h\left(L \right) \right]  \nonumber \\
+    & = \mathbb{E} \left[ h\left( \hat{L}_N \right) - h\left( L \right) \right] \nonumber \\
+    & \leq \mathbb{E} \left[ |h\left( \hat{L}_N \right) - h\left( L \right) | \right] \nonumber \\
+    & \leq K \mathbb{E} \left[ |\hat{L}_N - L| \right] \nonumber \\
+    & = K \mathbb{E} \left[ |\bar{Z}_N| \right] \nonumber \\
+    & \leq K \sqrt{\mathbb{E} \left[ \left( \bar{Z}_N \right)^2 \right]} = \mathcal{O}(N^{-1})
+\end{align}
+
+The variance term in Equation~\ref{eq1:mse-sns2} for Lipschitz continuous $h$ is identical to the one in Equation~\ref{eq1:var-sns-smooth}.
+Hence, the convergence order of the standard nested simulation procedure for Lipschitz continuous $h$ is the same as the one for smooth $h$.
+
+\begin{equation}
+    \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(M^{-1}) + \mathcal{O}(N^{-2})
+\end{equation}
+
+Setting $M = \mathcal{O}(\Gamma^{2/3})$ and $N = \mathcal{O}(\Gamma^{1/3})$, we provide the same rate of convergence as obtained for other risk measures in~\cite{gordy2010nested}.
 
@@
     Let $h$ be a Lipschitz continuous function. 
-    MSE of the standard nested simulation procedure converges in order $\Gamma^{1/2}$, that is,
-    $$\mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(\Gamma^{-1/2}).$$
+    MSE of the standard nested simulation procedure converges in order $\Gamma^{2/3}$, that is,
+    $$\mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(\Gamma^{-2/3}).$$
 \end{theorem}
@@
 \begin{corollary}
-    Let $h$ be a Lipschitz continuous function. The absolute error of the standard nested simulation procedure converges in probabilistic order $\Gamma^{-1/4}$, that is,
-    $$\left| \hat{\rho}_{M, N} - \rho \right| = \mathcal{O}_\mathbb{P}(\Gamma^{-1/4}).$$
+    Let $h$ be a Lipschitz continuous function. The absolute error of the standard nested simulation procedure converges in probabilistic order $\Gamma^{-1/3}$, that is,
+    $$\left| \hat{\rho}_{M, N} - \rho \right| = \mathcal{O}_\mathbb{P}(\Gamma^{-1/3}).$$
 \end{corollary}
@@
 \end{align*}
-A kNN-based nested simulation procedure with model parameter $k$ estimates the risk measure $\rho = \mathbb{E} \left[ h(g(X)) \right]$ with
-
-\begin{align*}
-\hat{\rho}^{\text{kNN}, \text{Test}}_{M, n, M'} 
-& = \frac{1}{M'} \sum_{i=1}^{M'} h(\hat{g}^{\text{kNN}}_{M, n}(\tilde{X}_i)); ~~~ \tilde{X}_i \sim F_X, \\
-\hat{g}^{\text{kNN}}_{M, n}(x) 
-& = \frac{\frac{1}{M R_k^d} \sum_{i=1}^M K\left(\frac{x - X_i}{R_k}\right) \bar{Y}_{n, i}}{\frac{1}{M R_k^d} \sum_{i=1}^M K\left(\frac{x - X_i}{R_k}\right)}
-\end{align*}
-
-where $R_k$ is the Euclidean distance between $X_i$ and its $k^{\text{th}}$ nearest neighbor, and $K(\cdot)$ is the kernel function satisfying
-
+A kNN-based nested simulation procedure with model parameter $k$ estimates the risk measure $\rho = \mathbb{E} \left[ h(L) \right]$ with
+
+\begin{equation*}
+    \hat{L}^{\text{kNN}}_{M, N}(x) 
+    = \frac{\frac{1}{M R_M^d} \sum_{i=1}^M \hat{L}_{N, i} K\left(\frac{x - X_i}{R_M}\right)}{\frac{1}{M R_M^d} \sum_{i=1}^M K\left(\frac{x - X_i}{R_M}\right)}
+    \end{equation*}
+    where $R_k$ is the Euclidean distance between $X_i$ and its $k$-th nearest neighbor, and $K:\mathbb{R}^d \rightarrow \mathbb{R}$ is a bounded, nonnegative kernel function satisfying 
     \begin{align*}
@@
     \end{align*}
-
-where $\|\cdot\|$ is the Euclidean norm.
+where $\|\cdot\|$ is the Euclidean norm, and $k$ is the number of nearest neighbors to consider.
 For a kNN estimator trained with $M$ i.i.d. observations, denote $B_M(x)$ and $V_M(x)$ as its bias and variance at point $x$, respectively.
@@
 \begin{align} \label{eq1:bias-knn}
-    & \mathbb{E} \left[ h(\hat{g}^{\text{kNN}}_{M, n}(X)) - h(g(X)) \right] \nonumber \\
-    & = \mathbb{E} \left[ h'(g(X)) \left( \hat{g}^{\text{kNN}}_{M, n}(X) - g(X) \right) + \frac{1}{2} h''(z) \left( \hat{g}^{\text{kNN}}_{M, n}(X) - g(X) \right)^2 \right] 
-\end{align}
-where the bias is decomposed into two terms, and $z$ is between $\hat{g}^{\text{kNN}}_{M, n}(X)$ and $g(X)$.
+    & \mathbb{E} \left[ h(\hat{L}^{\text{kNN}}_{M, n}(X)) - h(L) \right] \nonumber \\
+    & = \mathbb{E} \left[ h'(L) \left( \hat{L}^{\text{kNN}}_{M, n}(X) - L \right) + \frac{1}{2} h''(z) \left( \hat{L}^{\text{kNN}}_{M, n}(X) - L \right)^2 \right] 
+\end{align}
+where the bias is decomposed into two terms, and $z$ is between $\hat{L}^{\text{kNN}}_{M, n}(X)$ and $L$.
 The first term in Equation~\ref{eq1:bias-knn} is 
 \begin{align} \label{eq1:bias-knn-1}
-    & ~~~~ \mathbb{E} \left[ h'(g(X)) \left( \hat{g}^{\text{kNN}}_{M, n}(X) - g(X) \right) \right]  \nonumber \\
-    & = \mathbb{E} \left[ h'(g(X)) \mathbb{E}\left[ \hat{g}^{\text{kNN}}_{M, n}(X) - g(X) |X\right] \right] \nonumber \\
-    & = \int_{\Omega} h'(g(x)) B_M(x) f_X(x) dx \nonumber \\
-    & = \int_{\Omega} h'(g(x)) \left( A_{\text{kNN}}(x) \left(\frac{k}{M}\right)^{2/d} \left(1+o_x(1)\right) + B_{\text{kNN}} \cdot \left(\frac{1}{k} + o_x\left(\frac{1}{k}\right)\right) \right) f_X(x) dx \nonumber \\
-    & = \left(\frac{k}{M}\right)^{2/d} \mathbb{E} \left[ h'(g(X)) A_{\text{kNN}}(X) \right] (1+ o(1)) + \frac{B_{\text{kNN}}}{k} \mathbb{E} \left[ h'(g(X)) \right] (1+ o(1)).
+    & ~~~~ \mathbb{E} \left[ h'(L) \left( \hat{L}^{\text{kNN}}_{M, n}(X) - L \right) \right]  \nonumber \\
+    & = \mathbb{E} \left[ h'(L) \mathbb{E}\left[ \hat{L}^{\text{kNN}}_{M, n}(X) - L |X\right] \right] \nonumber \\
+    & = \int_{\Omega} h'(L) B_M(x) f_X(x) dx \nonumber \\
+    & = \int_{\Omega} h'(L) \left( A_{\text{kNN}}(x) \left(\frac{k}{M}\right)^{2/d} \left(1+o_x(1)\right) + B_{\text{kNN}} \cdot \left(\frac{1}{k} + o_x\left(\frac{1}{k}\right)\right) \right) f_X(x) dx \nonumber \\
+    & = \left(\frac{k}{M}\right)^{2/d} \mathbb{E} \left[ h'(L) A_{\text{kNN}}(X) \right] (1+ o(1)) + \frac{B_{\text{kNN}}}{k} \mathbb{E} \left[ h'(L) \right] (1+ o(1)).
 \end{align}
@@
 \begin{align} \label{eq1:bias-knn-2}
-    & ~~~~ \mathbb{E} \left[ h''(z) \left( \hat{g}^{\text{kNN}}_{M, n}(X) - g(X) \right)^2 \right]  \nonumber \\
-    & = \int_{\Omega} h''(g(z)) \left(B_M^2(X) + V_M(x)\right) f_X(x) dx \nonumber \\
+    & ~~~~ \mathbb{E} \left[ h''(z) \left( \hat{L}^{\text{kNN}}_{M, n}(X) - L \right)^2 \right]  \nonumber \\
+    & = \int_{\Omega} h''(z) \left(B_M^2(X) + V_M(x)\right) f_X(x) dx \nonumber \\
     & \leq C_2 \int_{\Omega} \left( \frac{C_{\text{kNN}} \cdot \text{Var}[Y| X = x]}{k} \int K^2(u) du + o\left(\frac{1}{k}\right) \right) f_X(x) dx \nonumber \\
@@
     The bias of the kNN-based nested simulation procedure converges in the order of $\Gamma^{-\frac{2}{2+d}}$, that is,
-    $$ \mathbb{E} \left[ h(\hat{g}^{\text{kNN}}_{M, n}(X)) - h(g(X)) \right]  = \mathcal{O}(\Gamma^{-\frac{2}{2+d}}).$$
+    $$ \mathbb{E} \left[ h(\hat{L}^{\text{kNN}}_{M, n}(X)) - h(L) \right]  = \mathcal{O}(\Gamma^{-\frac{2}{2+d}}).$$
 \end{definition}
@@
     \hline
-    \textbf{Estimator for} $g(X)$ & \textbf{Smooth} $h$ & \textbf{Lipschitz} / \textbf{hockey-stick} $h$ & \textbf{Indicator} $h$ & \textbf{VaR} & \textbf{CVaR} \\
+    \textbf{Estimator for} $L$ & \textbf{Smooth} $h$ & \textbf{Lipschitz} / \textbf{hockey-stick} $h$ & \textbf{Indicator} $h$ & \textbf{VaR} & \textbf{CVaR} \\
     \hline
@@
 
-Assumption~\ref{as1:likelihood-ratio-independence} is necessary for $\hat{g}^{\text{LR}}_N(X_i)$ to be an unbiased and strongly consistent estimator of $g(X_i)$, which is a necessary condition for the convergence of $\hat{\rho}^{\text{LR}}_{M,N}$, the likelihood ratio-based nested simulation estimator of $\rho$.
+Assumption~\ref{as1:likelihood-ratio-independence} is necessary for $\hat{L}^{\text{LR}}_N(X_i)$ to be an unbiased and strongly consistent estimator of $L_i$, which is a necessary condition for the convergence of $\hat{\rho}^{\text{LR}}_{M,N}$, the likelihood ratio-based nested simulation estimator of $\rho$.
 Assumption~\ref{as1:likelihood-ratio-marginal-density} and Assumption~\ref{as1:likelihood-ratio-independence} are likely to be satisfied in practice, as one can simulate $H$ separately from $X$ and evaluate $Y(H, X)$ for each pair of $(H, X)$.
@@
 \subsection{Assumptions for the Kernel-Based Procedure}
-For the kernel-based nested simulation procedure,~\cite{hong2017kernel} simplifies the analysis by assuming that for each $X_i$, the inner simulation budget $N$ is fixed together with the variance of the inner simulation noise $\bar{Z}_N(X_i)$.
+For the kernel-based nested simulation procedure,~\cite{hong2017kernel} simplifies the analysis by assuming that for each $X_i$, the inner simulation budget $N$ is fixed together with the variance of the inner simulation noise $\bar{Z}_{N, i}$.
 In essence, this fixed variance design treats the $(X_i, \bar{Y}_{N, i})$ as independent and identically distributed observations of $(X, Y)$, and the kernel-based nested simulation procedure is analyzed as a nonparametric regression problem.
-Regularity conditions on $f_X(x)$, the density of $X$, and the conditional second moment of $Y$ are assumed to ensure the convergence of $\hat{g}^{\text{KS}}_{M, N}(X)$, the kernel smoothing estimator of $g(X)$.
+Regularity conditions on $f_X(x)$, the density of $X$, and the conditional second moment of $Y$ are assumed to ensure the convergence of $\hat{L}^{\text{KS}}_{M, N}(X)$, the kernel smoothing estimator of $L$.
 
@@
 
-Further assumptions are made on the kernel function $K_w$ and the bandwidth $w$ to ensure the convergence of the kernel smoothing estimator $\hat{g}^{\text{KS}}_{M, N}(X)$.
+Further assumptions are made on the kernel function $K_w$ and the bandwidth $w$ to ensure the convergence of the kernel smoothing estimator $\hat{L}^{\text{KS}}_{M, N}(X)$.
 % A similar set of assumptions is made in~\cite{jennen1988unifying} for the convergence analysis of a kernel smoothing estimator with kernel functions of higher orders.

### 2024-04-12 introduction.tex
new intro

--- 2024-03-22 introduction.tex
@@
 
-Quantitative risk management is a key component of modern financial systems, ensuring the stability and resilience of markets, institutions, and portfolios against an array of risks.
-In the era of complex financial products, such as option portfolios and variable annuity contracts, traditional risk assessment methods often fall short in accurately capturing the multifaceted nature of market, credit, and operational risks.
-This is where advanced simulation techniques, particularly nested simulation procedures, become indispensable.
+% Quantitative risk management is a key component of modern financial systems, ensuring the stability and resilience of markets, institutions, and portfolios against an array of risks. 
+% For complex financial products, such as option portfolios and variable annuity contracts, traditional risk assessment methods often fall short in accurately capturing the multifaceted nature of market, credit, and operational risks.
+% This is where advanced Monte Carlo simulation techniques, particularly nested simulation procedures, become indispensable.
+% In constract to finite-difference methods, a Monte Carlo simulation scheme is more flexible and can be easily adapted to model complex financial products with multiple sources of risk.
+
+The realm of financial risk management is in a constant state of evolution, driven by the rapid advancement of financial technologies and the increasing complexity of financial products.
+Traditional risk management techniques, which often rely on linear assumptions and static models, are increasingly inadequate for addressing the multifaceted and dynamic risks associated with modern financial instruments like variable annuities and derivatives portfolios.
+This thesis introduces cutting-edge machine learning approaches to enhance risk estimation and management, offering substantial improvements over conventional methods such as nested simulations.
+
+Financial markets today are characterized by high volatility and intricate dependencies, influenced by global economic factors and interlinked financial systems.
+In such an environment, the ability to accurately estimate and hedge against potential risks is paramount.
+Traditional risk assessment methods, including standard nested simulations, often lack the flexibility and scalability required to handle the stochastic nature of modern financial markets.
+They also tend to be computationally intensive and can fail to capture extreme events, leading to substantial misestimations of risk and inadequate hedging strategies.
+
+Recognizing these challenges, this research focuses on the application of machine learning models as metamodels within nested simulations.
+Machine learning offers the potential to automate and improve the accuracy of risk predictions, adapt to new patterns in data, and handle high-dimensional spaces efficiently.
+The adaptive nature of these models allows for better handling of the non-linear and time-varying patterns typical of financial markets, thus providing a more robust framework for risk assessment and decision-making.
+
+The thesis is structured into three main sections, each addressing a different aspect of risk management through the lens of machine learning: The first section provides a comprehensive review of existing nested simulation techniques and introduces the concept of using machine learning models as metamodels.
+It compares various machine learning approaches, such as neural networks and ensemble methods, to traditional models, assessing their efficacy and efficiency in simulating tail risks.
+This comparison is foundational, setting the stage for the subsequent application of specific machine learning techniques to complex financial risk estimation tasks.
+
+The second section details the implementation of Long Short-Term Memory (LSTM) networks to enhance the efficiency and accuracy of nested simulations in estimating the tail risk of variable annuities.
+By leveraging LSTMs, the research demonstrates significant improvements in computational speed and prediction accuracy.
+The ability of LSTM networks to process sequences of data and remember long-term dependencies makes them particularly suited for modeling the sequential risks associated with financial instruments over time.
+
+The final section explores a novel approach to hedging variable annuities using a combination of Proximal Policy Optimization (PPO) and LSTM networks.
+This model-free reinforcement learning strategy adapts to changes in market conditions in real-time, providing a flexible and powerful tool for managing financial risks.
+The use of PPO, known for its stability and effectiveness in various control tasks, underscores the innovative aspect of this research, pushing the boundaries of how machine learning can be utilized in financial risk management.
+
+This research aims not only to demonstrate the practical applications of machine learning in financial risk management but also to contribute to the theoretical advancement of risk management strategies.
+By bridging the gap between traditional financial models and modern machine learning techniques, this thesis provides valuable insights that could influence future practices and research in the field.
+The findings could have significant implications for both financial theorists and practitioners, pointing the way toward more resilient and adaptive financial systems.

### 2024-04-12 introduction.tex
new

--- 2024-04-04 introduction.tex
@@
 This is where advanced Monte Carlo simulation techniques, particularly nested simulation procedures, become indispensable.
-In constract to finite-difference methods, a Monte Carlo simulation scheme is more flexible and can be easily adapted to model complex financial products with multiple sources of risk.
+In contrast to finite-difference methods, a Monte Carlo simulation scheme is more flexible and can be easily adapted to model complex financial and actuarial products.
+
+% For insurance contracts with embedded financial options, such as variable annuities, the valuation and risk management process is particularly challenging due to the presence of multiple sources of risk.
+% In such an environment, the ability to accurately estimate and hedge against potential risks is crucial.
+% Traditional risk assessment methods, including standard nested simulations, often lack the scalability required to handle the stochastic nature of modern financial markets. 
+% They also tend to be computationally intensive and can fail to capture extreme events, leading to substantial misestimations of risk and inadequate hedging strategies.
+
+% Recognizing these challenges, this research focuses on the application of machine learning models as metamodels within nested simulations.
+Machine learning offers the potential to automate and improve the accuracy of risk predictions, adapt to new patterns in data, and handle high-dimensional spaces efficiently.
+The adaptive nature of these models allows for better handling of the non-linear and time-varying patterns typical of financial markets, thus providing a more robust framework for risk assessment and decision-making.
+
+% The thesis is structured into three main sections, each addressing a different aspect of risk management through the lens of machine learning: The first section provides a comprehensive review of existing nested simulation techniques and introduces the concept of using machine learning models as metamodels.
+It compares various machine learning approaches, such as neural networks and ensemble methods, to traditional models, assessing their efficacy and efficiency in simulating tail risks.
+This comparison is foundational, setting the stage for the subsequent application of specific machine learning techniques to complex financial risk estimation tasks.
+
+% The second section details the implementation of Long Short-Term Memory (LSTM) networks to enhance the efficiency and accuracy of nested simulations in estimating the tail risk of variable annuities.
+By leveraging LSTMs, the research demonstrates significant improvements in computational speed and prediction accuracy.
+The ability of LSTM networks to process sequences of data and remember long-term dependencies makes them particularly suited for modeling the sequential risks associated with financial instruments over time.
+
+% The final section explores a novel approach to hedging variable annuities using a combination of Proximal Policy Optimization (PPO) and LSTM networks.
+This model-free reinforcement learning strategy adapts to changes in market conditions in real-time, providing a flexible and powerful tool for managing financial risks.
+The use of PPO, known for its stability and effectiveness in various control tasks, underscores the innovative aspect of this research, pushing the boundaries of how machine learning can be utilized in financial risk management.
+
+% This research aims not only to demonstrate the practical applications of machine learning in financial risk management but also to contribute to the theoretical advancement of risk management strategies.
+By bridging the gap between traditional financial models and modern machine learning techniques, this thesis provides valuable insights that could influence future practices and research in the field.
+The findings could have significant implications for both financial theorists and practitioners, pointing the way toward more resilient and adaptive financial systems.

### 2024-04-12 uw-ethesis-frontpgs.tex
new intro
new abstract

@@
         \Huge
-        {\bf Efficient Nested Simulation of Tail Risk Measures with Machine Learning Proxies }
+        {\bf Resilient Machine Learning Approaches to Risk Evaluation and Hedging in Financial Portfolios and Variable Annuities}
 
@@
 
-In the task of estimating risk measures for portfolios of complex financial derivatives, nested simulation procedures are commonly required but often computationally expensive. 
-Tremendous efforts have been made to improve the efficiency of nested simulation procedures by approximating the inner simulation model with a proxy model. 
-In this study, we review the literature on nested simulation procedures in financial engineering and establish fair comparisons of different proxy models using the same set of numerical examples. 
-Our study shows interesting findings on the performance of different proxy models and provides useful insights for practitioners to choose proxy models for nested simulation procedures.
+Quantitative risk management of modern financial derivatives and actuarial products is intricate and often requires modelling the underlying stochasticity with Monte Carlo simulations.
+A simulation scheme is flexible, and it can easily adapt to changes in model assumptions and market conditions.
+However, as multiple sources of risk are considered for long time horizons, such simulation schemes become expensive to implement. 
+Tremendous research effort is dedicated in the design of computationally efficient machine learning-based procedures that mitigate the computational burden of a standard simulation procedure.
+In machine learning, model flexibility comes at the expense of model resilience, which is especially crucial for risk management tasks.
+This study considers the management of tail risk for complex financial and actuarial products with resilient machine learning-based nested simulation procedures and reinforcement learning-based hedging policies.
+Our approaches offer significant improvements over a standard simulation procedures and illustrate a resilient machine learning model is built by accounting for problem complexity and data structure, quality, and quantity.
+
 \cleardoublepage
@@
 
-I would like to thank Professor Ben Feng and Professor Tony Wirjanto for they valuable support. They have patiently helped me through my journey as a Ph.D. student.  
+I would like to thank Professor Mingbin Feng and Professor Tony Wirjanto for their valuable support. They have patiently helped me through my journey as a Ph.D. student.  
 \cleardoublepage

### 2024-04-14 introduction.tex
small changes to intro

@@
 Quantitative risk management is a key component of modern financial systems, ensuring the stability and resilience of markets, institutions, and portfolios against an array of risks. 
-For complex financial products, such as option portfolios and variable annuity contracts, traditional risk assessment methods often fall short in accurately capturing the multifaceted nature of market, credit, and operational risks.
+For financial products like option portfolios and variable annuity contracts, traditional risk assessment methods often fall short in accurately capturing the complex dynamics of the underlying risk factors.
 This is where advanced Monte Carlo simulation techniques, particularly nested simulation procedures, become indispensable.
-In contrast to finite-difference methods, a Monte Carlo simulation scheme is more flexible and can be easily adapted to model complex financial and actuarial products.
+In contrast to finite-difference methods, a Monte Carlo simulation scheme is more flexible and can be easily adapted to model complex dynamics with a rule-based design.
 

### 2024-04-14 introduction.tex
new

@@
 This is where advanced Monte Carlo simulation techniques, particularly nested simulation procedures, become indispensable.
-In contrast to finite-difference methods, a Monte Carlo simulation scheme is more flexible and can be easily adapted to model complex dynamics with a rule-based design.
-
-% For insurance contracts with embedded financial options, such as variable annuities, the valuation and risk management process is particularly challenging due to the presence of multiple sources of risk.
-% In such an environment, the ability to accurately estimate and hedge against potential risks is crucial.
-% Traditional risk assessment methods, including standard nested simulations, often lack the scalability required to handle the stochastic nature of modern financial markets. 
-% They also tend to be computationally intensive and can fail to capture extreme events, leading to substantial misestimations of risk and inadequate hedging strategies.
-
-% Recognizing these challenges, this research focuses on the application of machine learning models as metamodels within nested simulations.
-Machine learning offers the potential to automate and improve the accuracy of risk predictions, adapt to new patterns in data, and handle high-dimensional spaces efficiently.
-The adaptive nature of these models allows for better handling of the non-linear and time-varying patterns typical of financial markets, thus providing a more robust framework for risk assessment and decision-making.
-
-% The thesis is structured into three main sections, each addressing a different aspect of risk management through the lens of machine learning: The first section provides a comprehensive review of existing nested simulation techniques and introduces the concept of using machine learning models as metamodels.
-It compares various machine learning approaches, such as neural networks and ensemble methods, to traditional models, assessing their efficacy and efficiency in simulating tail risks.
-This comparison is foundational, setting the stage for the subsequent application of specific machine learning techniques to complex financial risk estimation tasks.
-
-% The second section details the implementation of Long Short-Term Memory (LSTM) networks to enhance the efficiency and accuracy of nested simulations in estimating the tail risk of variable annuities.
-By leveraging LSTMs, the research demonstrates significant improvements in computational speed and prediction accuracy.
-The ability of LSTM networks to process sequences of data and remember long-term dependencies makes them particularly suited for modeling the sequential risks associated with financial instruments over time.
-
-% The final section explores a novel approach to hedging variable annuities using a combination of Proximal Policy Optimization (PPO) and LSTM networks.
-This model-free reinforcement learning strategy adapts to changes in market conditions in real-time, providing a flexible and powerful tool for managing financial risks.
-The use of PPO, known for its stability and effectiveness in various control tasks, underscores the innovative aspect of this research, pushing the boundaries of how machine learning can be utilized in financial risk management.
-
-% This research aims not only to demonstrate the practical applications of machine learning in financial risk management but also to contribute to the theoretical advancement of risk management strategies.
-By bridging the gap between traditional financial models and modern machine learning techniques, this thesis provides valuable insights that could influence future practices and research in the field.
-The findings could have significant implications for both financial theorists and practitioners, pointing the way toward more resilient and adaptive financial systems.
+In contrast to finite-difference methods, a Monte Carlo simulation scheme is more flexible and can be easily adapted to model tail risk with a rule-based design.
+In this thesis, we focus on building and analyzing nested simulation procedures for risk management applications of financial derivatives and insurance products.

### 2024-04-15 introduction.tex
new

@@
 In this thesis, we focus on building and analyzing nested simulation procedures for risk management applications of financial derivatives and insurance products.
+Nested simulation, also known as nested stochastic modeling and stochastic-on-stochastic modeling, becomes necessary when stochastic simulation of a parameter of interest is contingent on another quantity to be determined stochastically.
+In the context of financial engineering, nested simulation is used to model the risk of a financial product whose payoff depends on a set of underlying risk factors.
+A nested simulation procedure consists of two levels of simulation: the outer level simulates the underlying risk factors, while the inner level estimates the conditional mean of the payoff for a given risk factor with another Monte Carlo simulation.

### 2024-04-16 introduction.tex
new

--- 2024-04-14 introduction.tex
@@
 In this thesis, we focus on building and analyzing nested simulation procedures for risk management applications of financial derivatives and insurance products.
+Nested simulation, also known as nested stochastic modeling and stochastic-on-stochastic modeling, becomes necessary when stochastic simulation of a parameter of interest is contingent on another quantity to be determined stochastically.
+In the context of financial engineering, nested simulation is used to model the tail risk of a contract whose payoff depends on a set of underlying risk factors.
+For example, estimating the value of an exotic option at a risk horizon requires simulation given a realization of the underlying assets upto that horizon.
+A standard nested simulation procedure consists of two levels of simulation: the outer level simulates the underlying risk factors, while the inner level estimates the value of interest with the inner sample mean from another level of Monte Carlo simulation.
+The nested structure allows for accurate estimation given sufficient computational resources, but it also introduces additional complexity in the simulation design and implementation.
+% ~\cite{gordy2010nested} investigate the standard nested simulation method for estimating tail risk measures of financial portfolios and provide an optimal resource allocation strategy for nested simulation.

### 2024-04-18 project3/tlHedging.tex
new

@@
-\chapter{Efficient Transfer of Knowledge for Deep Hedging of Variable Annuities}
+\chapter{Model-Free Deep Hedging of Variable Annuities}
 
@@
 
-In this paper, we propose a transfer learning approach to improve the risk management of variable annuities (VAs) by learning a hedging strategy utilizing previous experiences from other financial products.
+In this paper, we propose a model-free RL algorithm to improve the risk management of variable annuities (VAs) by learning a hedging strategy from past experience.
 VAs are popular retirement products that combine investment and insurance features, offering policyholders the potential for investment growth and the protection of a guaranteed minimum death benefit or income benefit.
 Due to the complexity of the products and the dynamic nature of the financial markets, the task of hedging VAs is particularly challenging.
-We aim to leverage the knowledge from the hedging strategies of financial derivatives to construct hedging strategies for VAs, thereby improving the risk management of these products.
-The rest of the paper is organized as follows: Section~\ref{sec3:vaHedging} presents the problem formulation for hedging variable annuity with a deep neural network, Section~\ref{sec3:tlHedging} presents the background knowledge for transfer learning, and Section~\ref{sec3:numerical} states the plans for ongoing numerical experiments.
+Our model-free RL approach aims to learn an optimal hedging policy for VAs without relying on a predefined model of the underlying asset dynamics.
+By leveraging the flexibility and adaptability of RL algorithms, we aim to develop a dynamic hedging strategy that can effectively manage the risks associated with VAs in a changing market environment.
+
+The rest of the paper is organized as follows: Section~\ref{sec3:vaHedging} presents the problem formulation for hedging variable annuity with a deep neural network,
 
 \section{Dynamic Hedging of Variable Annuities} \label{sec3:vaHedging}
-
-\subsection{Markov Decision Process (MDP) for Hedging VAs}
-A Markov Decision Process (MDP) provides a mathematical framework for solving sequential decision-making tasks in situations where outcomes are partly random and partly under the control of an agent. 
-In the context of hedging VAs, an MDP can be used to model the decision-making process of an insurer who aims to minimize the liability of the VA by dynamically adjusting the hedging portfolio based on the current state of the VA and the financial markets.
-An MDP is defined by the tuple $\mathcal{M} = (\mu_0, \mathcal{S}, \mathcal{A}, \mathcal{P}, \mathcal{R}, \gamma)$, where:
-
-\begin{itemize}
-    \item $\mu_0$ is the initial states.
-    \item $\mathcal{S}$ is a finite set of states.
-    \item $\mathcal{A}$ is a finite set of actions.
-    \item $\mathcal{P}$ is a state transition probability distribution, where $\mathcal{P}(s'|s, a)$ represents the probability of transitioning from state $s$ to state $s'$ due to action $a$.
-    \item $\mathcal{R}$ is a reward distribution, $\mathcal{R}(s, a, s')$ is the reward received after transitioning from state $s$ to state $s'$ due to action $a$.
-    \item $\gamma$ is a discount factor, $\gamma \in [0,1]$,  which models the present value of future rewards.
-\end{itemize}
-
-The objective in an MDP is to find a policy, $\pi: \mathcal{S} \rightarrow \mathcal{A}$, that maximizes the cumulative reward over time, often referred to as the value function for a policy $\pi$ at state $s$:
-
-\begin{equation} \label{eq3:V_pi}
-    V^{\pi}_{\mathcal{M}}(s) = \mathbb{E}_{s_0 \sim \mu_0, a_i \sim \pi(\cdot|s_i), s_{i+1} \sim \mathcal{P}(\cdot|s, a)} \left[ \sum_{t=0}^{\infty} \gamma^t R_{t+1} |\pi, s \right],
-\end{equation}
-
-where $R_{t+1} = \mathcal{R}(s_i, a_i, s_{i+1})$ is the reward received by the agent after taking action $a_i$ in state $s_i$ and transitioning to state $s_{i+1}$, and the expectation is taken over the possible sequences of states and rewards that follow from the policy $\pi$.
-In the context of hedging VAs, the initial states $\mu_0$ specifies the initial value of the VA and the market specifications. 
-The state space $\mathcal{S}$ represent the information available to the agent, such as current value of the underlying asset ($S_t$), the current subaccount value ($F_t$), and the guarantee value ($G_t$), as well as other relevant contract specifications.
-The action space $\mathcal{A}$ represent the hedging decisions, such as the hedging portfolio weights.
-The state transition probability distribution $\mathcal{P}$ and the reward function $\mathcal{R}$ are derived from the dynamics of the VA and the market specifications.
-Instead of having an infinite time horizon, the final reward is obtained at the maturity of the VA contract.
-Hence, $R_{t} = 0$ for all $t > T$.
-The discount factor $\gamma$ models the present value of future rewards and is conveniently inherited from the risk-free rate.
-
-Considering the task of hedging a GMWB contract, the hedging strategy aims to minimize the insurer's liability $L_t$ at each time $t=1,\ldots,T$ by dynamically adjusting the hedging portfolio based on the current state of the VA and the financial markets.
-The objective is to find a policy $\pi$ that minimizes the expected liability over time, i.e.,
-
-\begin{equation}
-    \min_{\pi} \mathbb{E}[\sum_{t=1}^{T} \gamma^t L_t | \pi, s_0],
-\end{equation}
-
-where it can be conveniently rewritten as the value function $V^{\pi}_{\mathcal{M}}(s)$ in Equation~\ref{eq3:V_pi} by setting the reward function $R_{t} = -L_t$ and the discount factor $\gamma = \frac{1}{1+r}$.
-Other value functions can be used to optimize over a risk measure on the cumulative liability, such as the Value-at-Risk (VaR) or the Conditional Value-at-Risk (CVaR).
-Denote the risk measure as $\rho_{\alpha}$, where $\alpha$ is the confidence level, then the value function can be set as
-
-\begin{equation}
-    V^{\pi}_{\mathcal{M}}(s) = \rho_{\alpha}(\sum_{t=1}^{T} \gamma^t L_t | \pi, s_0).
-\end{equation}
 
@@
 ~\cite{buehler2019deep} is the first paper to propose a model-based deep hedging approach for hedging financial derivatives with a focus on minimizing CVaR.
-A more recent paper by~\cite{imaki2021no} proposes a new network architecture for model-based deep hedging that can be trained more efficiently.
+~\cite{carbonneau2021deep} extends the model-based approach to hedging long-term financial derivatives and compares the performance of deep hedging strategies trained with different reward functions.
+A more recent paper by~\cite{imaki2021no} proposes a new network architecture for model-based deep hedging that can be trained more efficiently by implementing a no-tranaction band.
 A typical setup for a model-based deep hedging strategy includes:
@@
 \end{enumerate}
+
+In summary, model-based deep hedging approaches rely on explicit market models to learn the optimal hedging strategies.
+It requires the knowing of the underlying asset price dynamics and the risk factors affecting the financial instruments, which may limit its flexibility and robustness to model misspecification.
+~\cite{chong2023pseudo} specifically discuss the effect of model misspecification on the performance of model-based deep hedging strategies for hedging variable annuities with a guaranteed minimum death benefit (GMDB) rider under the Black-Scholes framework.
 
@@
     A policy gradient method uses policy gradient theorem to update the policy by performing gradient ascent with respect to the policy parameters.
-    Representative algorithms include the Proximal Policy Optimization (PPO) algorithm proposed by~\cite{schulman2017proximal} and the Trust Region Policy Optimization (TRPO) algorithm proposed by~\cite{schulman2015trust}.
+    Representative algorithms include the Trust Region Policy Optimization (TRPO) algorithm proposed by~\cite{schulman2015trust} and the Proximal Policy Optimization (PPO) algorithm proposed by~\cite{schulman2017proximal}.
+
     The most relevant paper to our study is~\cite{chong2023pseudo}, which uses the PPO algorithm to hedge GMMB with a GMDB rider under the Black-Scholes framework.
-\end{enumerate}
-
-\section{Transfer Learning for Risk Management of Variable Annuities} \label{sec3:tlHedging}
-
-Transfer learning is a machine learning technique that leverages knowledge from one domain to improve learning in another domain.
-In the context of deep reinforcement learning, transfer learning can be used to improve the risk management of VAs in five ways:
-\begin{enumerate}
-    \item   \textbf{Transferring to VA products}: Knowledge can be transferred from the hedging strategies of financial derivatives to constructing hedging strategies for VAs.
-    VAs are complex insurance products with unique features, which makes it challenging to develop effective hedging strategies.
-    However, the payoff structures of VAs are similar to those of financial derivatives, such as European options, which have been extensively studied in the literature.
-    By leveraging the knowledge from the hedging strategies of financial derivatives, we can improve the risk management of VAs.
-    \item   \textbf{Transferring to new VA products}: Knowledge can be transferred from the hedging strategies of one VA product to another VA product.
-    Different VA products have different features and payoff structures, which makes it challenging to develop hedging strategies for new VA products.
-    However, experience from hedging one VA product can be transferred to develop hedging strategies for new VA products, especially when the new VA product is similar to the existing ones.
-    \item   \textbf{Transferring to new asset models}: Knowledge can be transferred from the hedging strategies of one asset model to another asset model.
-    A stochastic volatility model is a more realistic model for asset prices than the Black-Scholes model, but it is more challenging to develop hedging strategies for VAs under such a model.
-    \item  \textbf{Transferring to new model specifications}: Model misspecification is a common issue in financial modeling, and training on data simulated with misspecified parameters can lead to suboptimal hedging strategies.
-    If only the misspecified model is similar to the correct model, then we can leverage the knowledge from the misspecified model to improve the hedging strategies under the correct model, since the only difference between the two models is the parameter values.
-    \item   \textbf{Transferring to the real world}: Knowledge can be transferred from simulated data to real-world data.
-    In practice, it is challenging to obtain real-world data for VAs, but we can leverage simulated data to develop hedging strategies for VAs.
-    If the simulated data is representative of the real-world data, then the hedging strategies developed from the simulated data can be transferred to the real world.
+    However,~\cite{chong2023pseudo} implement the PPO algorithm with the knowing of the underlying asset model and the risk factors affecting the mortality rate, while our study focuses on the model-free deep reinforcement learning approach to hedge VAs without explicit model assumptions.
 
@@
 
-Given a set of source domains $\bm{\mathcal{M}}_s= \{ \mathcal{M}_s| \mathcal{M}_s \in \bm{\mathcal{M}}_s\}$ and a target domain $\mathcal{M}_t$, transfer learning aims to improve the learning on the target domain.
-While utilizing the interior information $\mathcal{I}_t$ from the target domain, the exterior information $\mathcal{I}_s$ from the source domains is also leveraged to improve the learning on the target domain.
+\section{Proximal Policy Optimization for Hedging Variable Annuities}
+
+PPO is a policy gradient method that aims to optimize the policy by performing gradient ascent with respect to the policy parameters.
+Originally proposed by~\cite{schulman2017proximal} and inspired by TRPO, PPO aims to address the limitation of a crude policy gradient method by introducing a clipped surrogate objective function that prevents large policy updates and ensures more stable training.
+While TRPO uses a hard coded constraint on the policy update to ensure that the new policy does not deviate too far from the old policy, PPO uses a clipped surrogate objective function that penalizes a high Kullback–Leibler (KL) divergence between the new and old policies.
+This allows for more significant policy updates while maintaining the stability of the training process.
+
+The PPO algorithm consists of two main components: the policy network and the value network.
+The policy network learns the policy by outputting the action based on the current state, while the value network learns the value function by approximating the expected cumulative reward over time following the policy.
+The policy network is updated by performing gradient ascent with respect to the policy parameters, while the value network is updated by minimizing the mean squared error between the predicted value and the target value.
+
+The PPO algorithm is particularly well-suited for continuous action spaces and has been successfully applied to a wide range of reinforcement learning tasks, including robotic control, game playing, and financial trading.
+In the context of hedging VAs, PPO can be used to learn an optimal hedging policy by maximizing a reward function that reflects the hedging performance.
+
+\subsection{Markov Decision Process (MDP) for Hedging VAs}
+A Markov Decision Process (MDP) provides a mathematical framework for solving sequential decision-making tasks in situations where outcomes are partly random and partly under the control of an agent. 
+In the context of hedging VAs, an MDP can be used to model the decision-making process of an insurer who aims to minimize the liability of the VA by dynamically adjusting the hedging portfolio based on the current state of the VA and the financial markets.
+In this section, we reformulate the hedging problem of VAs from Section~\ref{subsec:VApayout} as an MDP and define the key components of the MDP.
+An MDP is defined by the tuple $\mathcal{M} = (\mu_0, \mathcal{S}, \mathcal{A}, \mathcal{P}, \mathcal{R}, \gamma)$, where:
+
+\begin{itemize}
+    \item $\mu_0$ is the initial states.
+    \item $\mathcal{S}$ is a finite set of states.
+    \item $\mathcal{A}$ is a finite set of actions.
+    \item $\mathcal{P}$ is a state transition probability distribution, where $\mathcal{P}(s'|s, a)$ represents the probability of transitioning from state $s$ to state $s'$ due to action $a$.
+    \item $\mathcal{R}$ is a reward distribution, $\mathcal{R}(s, a, s')$ is the reward received after transitioning from state $s$ to state $s'$ due to action $a$.
+    \item $\gamma$ is a discount factor, $\gamma \in [0,1]$,  which models the present value of future rewards.
+\end{itemize}
+
+The objective in an MDP is to find a policy, $\pi: \mathcal{S} \rightarrow \mathcal{A}$, that maximizes the cumulative reward over time, often referred to as the value function for a policy $\pi$ at state $s$:
+
+\begin{equation} \label{eq3:V_pi}
+    V^{\pi}_{\mathcal{M}}(s) = \mathbb{E}_{s_0 \sim \mu_0, a_i \sim \pi(\cdot|s_i), s_{i+1} \sim \mathcal{P}(\cdot|s, a)} \left[ \sum_{t=0}^{\infty} \gamma^t R_{t+1} |\pi, s \right],
+\end{equation}
+
+where $R_{t+1} = \mathcal{R}(s_i, a_i, s_{i+1})$ is the reward received by the agent after taking action $a_i$ in state $s_i$ and transitioning to state $s_{i+1}$, and the expectation is taken over the possible sequences of states and rewards that follow from the policy $\pi$.
+
+In the context of hedging VAs, the initial states $\mu_0$ specifies the initial value of the VA and the market specifications. 
+The state space $\mathcal{S}$ represent the information available to the agent, such as current value of the underlying asset ($S_t$), the current subaccount value ($F_t$), and the guarantee value ($G_t$), as well as other relevant contract specifications.
+The action space $\mathcal{A}$ represent the hedging decisions, such as the hedging portfolio weights.
+The state transition probability distribution $\mathcal{P}$ and the reward function $\mathcal{R}$ are derived from the dynamics of the VA and the market specifications.
+Instead of having an infinite time horizon, the final reward is obtained at the maturity of the VA contract.
+Hence, $R_{t} = 0$ for all $t > T$.
+The discount factor $\gamma$ models the present value of future rewards and is conveniently inherited from the risk-free rate.
+
+Considering the task of hedging a GMWB contract, the hedging strategy aims to minimize the insurer's liability $L_t$ at each time $t=1,\ldots,T$ by dynamically adjusting the hedging portfolio based on the current state of the VA and the financial markets.
+The objective is to find a policy $\pi$ that minimizes the expected liability over time, i.e.,
 
 \begin{equation}
-    \pi^* = \arg \max_\pi \mathbb{E}_{s \sim \mu_0, a \sim \pi} \left[V_{\mathcal{M}}^\pi (s, a) \right], 
+    \min_{\pi} \mathbb{E}[\sum_{t=1}^{T} \gamma^t L_t | \pi, s_0],
 \end{equation}
 
-where $\pi = \phi(\mathcal{I}_s \sim \bm{\mathcal{M}}_s, \mathcal{I}_t \sim \mathcal{M}_t)$ is policy learned from target domain based on information from both the source domains and the target domain.
-A regular reinforcement without transfer learning is a special case where $\mathcal{I}_s = \emptyset$ and $\pi = \phi(\mathcal{I}_t \sim \mathcal{M}_t)$.
-
-In the context of deep hedging, various research has been conducted to improve the hedging strategies on real-world data by leveraging knowledge from simulated data.
-Most of the research uses the offline-online learning approach, where the hedging strategies are first trained with simulation data, but updated in real-time based on new market information and continuous learning to adapt to changing market dynamics.
-The most relevant paper to our study is~\cite{xiao2021optimal}, which use policy gradient algorithms to train hedging strategies for European options with simulation data from Heston model and then updated in real-time hedging S\&P 500 index options.
-To the best of our knowledge, no research has been conducted to improve the hedging strategies with the state-of-the-art transfer learning techniques.
-This section introduces some transfer learning techniques that are relevant to our task of hedging VAs.
-
-\subsection{Reward Shaping}
-
-In the context of hedging VAs using deep reinforcement learning and transfer learning, reward shaping becomes a crucial technique. 
-It involves modifying the reward function in the target domain to incorporate additional guidance, which often leads to more efficient learning and better performance.
-This technique can be particularly useful for managing the complex risks associated with VAs, as it can guide the learning process towards strategies that are more effective in hedging these products.
-
-One way to implement reward shaping in this context is by introducing auxiliary rewards that reflect the performance of hedging strategies learned from the source domains.
-Reward shaping learns an auxiliary reward function $\mathcal{R}_s: \mathcal{S} \times \mathcal{A} \times \mathcal{S} \rightarrow \mathbb{R}$ from the source domains.
-The auxiliary reward function is then used to shape the reward function in the target domain, $\mathcal{R}'_t = \mathcal{R}_t + \mathcal{R}_s$, by incorporating the insights gained from the source domains.
-
-Some popular reward shaping techniques include potential-based reward shaping~\citep{ng1999policy}, potential based state-action advice~\citep{wiewiora2003principled}, dynamic value function advice~\citep{harutyunyan2015expressing}.
-
-\subsection{Policy Transfer}
-
-The most straightforward approach to transfer learning is to directly transfer the policy learned from the source domains to the target domain via policy distillation.
-Policy distillation is a technique that transfers the knowledge from a teacher policy to a student policy by training the student policy to mimic the teacher policy up to a certain extent.
-The teacher policy is learned from the source domains, and the student policy learns the hedging strategies in the target domain while guided by the teacher policy.
-In the Distral algorithm~\citep{teh2017distral}, the student policy maximizes a multi-task objective:
-$\max_{\phi} \sum_{i=1}^K \mathcal{J}(\pi_\phi, \pi_{E_i})$, where
+where it can be conveniently rewritten as the value function $V^{\pi}_{\mathcal{M}}(s)$ in Equation~\ref{eq3:V_pi} by setting the reward function $R_{t} = -L_t$ and the discount factor $\gamma = \frac{1}{1+r}$.
+Other value functions can be used to optimize over a risk measure on the cumulative liability, such as the Value-at-Risk (VaR) or the Conditional Value-at-Risk (CVaR).
+Denote the risk measure as $\rho_{\alpha}$, where $\alpha$ is the confidence level, then the value function can be set as
 
 \begin{equation}
-    \mathcal{J}(\pi_\phi, \pi_{E_i}) = \sum_{t=0}^\infty \mathbb{E}_{s_t \sim \mu_0^t, a_t \sim \pi_\phi} \left[ \gamma^t R_{t+1} + \frac{\alpha}{\beta} \log \pi_{\phi}(a_t|s_t) - \frac{1}{\beta}log \pi_{E_i}(a_t|s_t) \right],
+    V^{\pi}_{\mathcal{M}}(s) = \rho_{\alpha}(\sum_{t=1}^{T} \gamma^t L_t | \pi, s_0).
 \end{equation}
-
-where a set of $K$ teacher policies $\pi_{E_i}$ are learned from the source domains, and the student policy $\pi_\phi$ is learned on the target domain.
-$\alpha$ and $\beta$ are hyperparameters that control the trade-off between mimicking the teacher policies and exploring the target domain.
-
-\subsection{Representation Transfer}
-
-Representation transfer is a technique that transfers the knowledge based on the following critical assumption:
-
-\begin{assumption}
-    The state space $\mathcal{S}$, the action space $\mathcal{A}$, and the reward function $\mathcal{R}$ can be disentangled into orthogonal subspaces, which are task-invariant such that knowledge can be transferred between domains on the universal subspaces.
-\end{assumption}
-
-A suitable representation transfer technique for our task of hedging VAs is modular networks~\citep{andreas2017modular}, which decomposes a policy $\pi$ into two sub-modules $g$ and $f$, i.e.,
-
-\begin{equation}
-    \pi = \phi(s_{market}, s_{guarantee}) = f(g(s_{market}), s_{guarantee}),
-\end{equation}
-
-~\cite{zhang2018decoupling} uses modular networks to transfer knowledge of physics models from previous tasks to new tasks in a simulated environment.
-In the context of hedging VAs, $g$ is the module that processes the market information, and $f$ is the module that processes the guarantee information.
-The core idea behind modular networks is that the market information can be applied for hedging strategies across different VA products, while the guarantee information is specific to each VA product.
-Hence, knowledge can be transferred from the source domains to the target domain by transferring the market module $g$.
-
-\subsection{Evaluation Metrics}
-
-The metrics discussed for evaluating transfer learning approaches focus on two key aspects: mastery and generalization. 
-Mastery assesses the agent's final performance level in the target domain, indicating how effectively it has learned a specific task from previous knowledge. 
-Some common metrics for evaluating mastery include:
-
-\begin{itemize}
-    \item \textbf{Asymptotic performance:} the final reward of the agent in the target domain.
-    \item \textbf{Transfer ratio:} the ratio of the agent's performance in the target domain with and without transfer learning.
-\end{itemize}
-
-Generalization, on the other hand, refers to the agent's ability to quickly adapt its learned knowledge to the target domain.
-
-\begin{itemize}
-    \item \textbf{Jumpstart performance:} the initial reward of the agent in the target domain.
-    \item \textbf{Accumulated reward:} the total area under the reward curve over time in the target domain.
-    \item \textbf{Time to threshold:} the time it takes for the agent to reach a certain performance threshold in the target domain.
-    \item \textbf{Performance with fixed epochs:} the agent's performance in the target domain after a fixed number of epochs.
-\end{itemize}
-
-\section{Plans for Ongoing Numerical Experiments} \label{sec3:numerical}
-
-As we aim to enhance the risk management strategies for variable annuities (VAs) through the application of transfer learning, our next step involves conducting a series of numerical experiments.
-These experiments are crucial for validating the theoretical frameworks and methodologies developed so far.
-Our plan includes:
-
-\begin{enumerate}
-    \item \textbf{Simulation setup:} Designing a simulation environment that closely mirrors real-world market dynamics and VA contract specifics. 
-    This setup will include various asset models, including the Black-Scholes and stochastic volatility models, to test the adaptability of transferred hedging strategies across different market conditions.
-    \item \textbf{Baseline model comparison:} Establishing a set of baseline hedging strategies against which we can compare the performance of our transfer learning-enhanced strategies. 
-    This will likely involve traditional delta hedging techniques and possibly other reinforcement learning approches that have not utilized transfer learning.
-    \item \textbf{Transfer learning implementation:} Applying the transfer learning methodologies discussed, including reward shaping, policy transfer, and/or representation transfer to the task of hedging VAs.
-    The transfer can happen between different VA products, different asset models, different model specifications, and between simulated and real-world data.
-    \item \textbf{Performance evaluation:} Utilizing the evaluation metrics outlined in the previous sections to assess mastery and generalization of the transfer learning strategies. 
-    Key metrics will include asymptotic performance, transfer ratio, jumpstart performance, and time to threshold.
-    \item \textbf{Sensitivity analysis:} Conducting sensitivity analyses to understand how changes in market conditions, contract specifics, and model parameters affect the performance of our transfer learning strategies.
-This will help in identifying the robustness and limitations of our approach.
-    \item \textbf{Hedging in real-world:} If accessible, applying the trained models to real-world data to further validate their practical applicability and performance in real-world market conditions.
-\end{enumerate}
-
-Through these numerical experiments, we aim to demonstrate the efficacy of transfer learning in improving the hedging of VAs in a variety of market conditions and contract specifics. 
-We expect that our transfer learning-enhanced strategies will outperform traditional hedging techniques and possibly other machine learning approaches that have not utilized transfer learning. 
-This will provide strong evidence for the potential of transfer learning in improving risk management strategies for VAs and other complex financial products in a dynamic market environment.
-
-\subsection{Initial Numerical Experiments}
-
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{./project3/figures/Figure_1.png}
-    \caption{Initial numerical experiments for GMMB}
-    \label{fig3:GMMB}
-\end{figure}

### 2024-04-18 project3/tlHedging.tex
new

@@
 
+\subsection{Simulation Model for Variable Annuities Hedging}
+
+Consider a generic VA contract with maturity $T>0$ periods, e.g., $T=240$ months.
+Denote the policyholder's (random) time of death by $\tau>0$.
+Then the contract expires at $T'=\min\{T,\tau\}$, i.e., the earlier of the contract maturity and the death of the policyholder.
+Let $S_t$, $F_t$, and $G_t$ be the indexed stock price, the subaccount value and the guarantee value, respectively, at time $t=1,2,\ldots,T$.
+Evolution of the subaccount value and the guarantee value of a VA contract affect the contract payout.
+Note that the policyholder's (random) time of death also affects the timing of the benefit payout for certain types of VA such as GMDB, but this is not considered in our study for simplicity.
+For clarity, we use $F_t$ and $F_{t_+}$ to denote the sub-account value just before and just after the withdrawal at time $t$, if any.
+Let $\eta_g$ be the gross rate of management fee that is deducted from the fund value at each period and let $\eta_n < \eta_g$ be the net rate of management fee income to the insurer.
+The difference between the gross management fee and the net management fee income represents the incurred investment expenses.
+
+At the inception of the contract, i.e., $t=0$, we assume that the whole premium is invested in the stock index and the guarantee base is set to the sub-account value:
+\begin{equation*}
+    S_0=F_0=G_0.
+\end{equation*}
+At each time $t=1,\ldots,T$, the following events take place in the following order:
+\begin{enumerate}
+    \item The sub-account value changes according to the growth of the underlying stock and the (gross) management fee is deducted. That is, 
+        \begin{equation*}
+            F_t = F_{(t-1)_+}\cdot\frac{S_{t}}{S_{t-1}}\cdot(1-\eta_g),
+        \end{equation*} 
+    where $(x)^+=\max\{x,0\}$ and $F_{(t-1)_+}$ will be defined later. The insurer's income at time $t$ is the net management fee, i.e., $F_t\eta_n$.
+
+    \item The guarantee value ratchets up (ratcheting is a common feature in GMWB) if the sub-account value exceeds the previous guarantee value, i.e., 
+        \begin{equation*}
+            G_t = \max\{G_{t-1},F_t\}.
+        \end{equation*}
+
+    \item The withdrawal is made (for GMWB) and is deducted from the sub-account value, i.e., 
+        \begin{equation*}
+            F_{t_+} = (F_t - I_t)^+,
+        \end{equation*} 
+    where $I_t = \gamma G_t$. A GMMB can be modeled with $\gamma = 0$.
+\end{enumerate}
+
+Consider a VA contract whose delta hedge portfolio at any time~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at time $T$.
+The value of the hedge portfolio at time~$(t-1)$ is:
+\begin{equation*}
+    H_{t-1} = \Delta_{t-1} S_{t-1} + B_{t-1},
+\end{equation*}
+where $S_t$ is the underlying stock price and any time $t>0$.
+This hedge portfolio is brought forward to the next rebalancing time~$t$, when its value becomes:
+\begin{equation*}
+    H_{t}^{bf} = \Delta_{t-1} S_{t} + B_{t-1}e^{r}.
+\end{equation*}
+Therefore, the time~$t$ hedging error, i.e., the cash flow incurred by the insurer due to rebalancing at time~$t$, is
+\begin{equation}
+    HE_t = H_t - H^{bf}_t, \quad t=1,\ldots, T-1.
+\end{equation}
+The P\&L of the VA contract includes the cost of the initial hedge ($H_0$), the hedging errors~\eqref{eq2:hedgingerror}, the unwinding of the hedge at maturity ($H^{bf}_T$), and the contract payout $P_t$ at time~$t\in \{0,\ldots,T\}$.
+Mathematically, the present value of these cash flows is given by
+\begin{align}
+L   & = H_0 - e^{-rT} H^{bf}_T + \sum_{t=1}^{T-1} e^{-rt} HE_t  + \sum_{t=1}^T e^{-rt} P_t \\ 
+    & = H_0 - e^{-rT} H^{bf}_T + \sum_{t=1}^{T-1} e^{-rt} \Delta_{t-1} (S_{t-1} - S_{t}) + B_{t-1}(1-e^{r}) + \sum_{t=1}^T e^{-rt} P_t \nonumber \\
+    & = \sum_{t=1}^T e^{-rt} \left( \Delta_{t-1} (S_{t-1} - e^{-r} S_t) + P_t \right) \label{eq3:lossrv}
+\end{align}
+where the last equality holds by a rearrangement of terms and a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$.
+It is worth noting that the formulation Equation~\ref{eq3:lossrv} differ from the traditional loss reserve calculation in Equation~\ref{eq2:lossrv} as the later includes $V_0$, the unhedged liability at time $t=0$.
+Since we are interested in a model-free deep reinforcement learning approach to hedging VAs, the insurer does not have explicit knowledge of the underlying asset price dynamics or the future mortality rates when the contract is first issued.
+Therefore, the insurer must learn an optimal hedging policy from historical market data without relying on a predefined model to estimate $V_0$.
+
 \subsection{Markov Decision Process (MDP) for Hedging VAs}
+
 A Markov Decision Process (MDP) provides a mathematical framework for solving sequential decision-making tasks in situations where outcomes are partly random and partly under the control of an agent. 
@@
 
-In the context of hedging VAs, the initial states $\mu_0$ specifies the initial value of the VA and the market specifications. 
-The state space $\mathcal{S}$ represent the information available to the agent, such as current value of the underlying asset ($S_t$), the current subaccount value ($F_t$), and the guarantee value ($G_t$), as well as other relevant contract specifications.
-The action space $\mathcal{A}$ represent the hedging decisions, such as the hedging portfolio weights.
-The state transition probability distribution $\mathcal{P}$ and the reward function $\mathcal{R}$ are derived from the dynamics of the VA and the market specifications.
-Instead of having an infinite time horizon, the final reward is obtained at the maturity of the VA contract.
-Hence, $R_{t} = 0$ for all $t > T$.
-The discount factor $\gamma$ models the present value of future rewards and is conveniently inherited from the risk-free rate.
-
-Considering the task of hedging a GMWB contract, the hedging strategy aims to minimize the insurer's liability $L_t$ at each time $t=1,\ldots,T$ by dynamically adjusting the hedging portfolio based on the current state of the VA and the financial markets.
-The objective is to find a policy $\pi$ that minimizes the expected liability over time, i.e.,
+In the context of hedging VAs, the state space $\mathcal{S}$ represents the information available to the agent: the current value of the underlying asset ($S_t$), the current subaccount value ($F_t$), the guarantee value ($G_t$), the time to maturity ($\tau = T-t$), and the previous hedging weight ($\Delta_{t-1}$).
+Let $\mathbf{S}_t = (S_t, F_t, G_t, \tau, \Delta_{t-1}) \in \mathcal{S} $ denote the state vector at time $t$.
+That is,
+$$
+    (S_t, F_t, G_t, \tau, \Delta_{t-1})  \in \mathbb{R}^+ \times \mathbb{R}^+ \times \mathbb{R}^+ \times \mathbb{N} \times \mathbb{R}.
+$$
+The action space $\mathcal{A}$ only contains the hedging portfolio weights ($\Delta_t$).
+$$
+    \Delta_t \in \mathbb{R}.
+$$
+The initial states $\mu_0 = (S_0, F_0, G_0, T, 0)$ specifies the initial values of the underlying asset, the subaccount value, the guarantee value, and the time to maturity. 
+The previous hedging weight $\Delta_{t-1}$ at $t=0$ is set to zero as no prior hedging has been done.
+The state transition probability distribution $\mathcal{P}$ is conveniently inherited from the dynamics of the VA in Section~\ref{subsec:VApayout}, and the reward function $\mathcal{R}$ and discount factor $\gamma$ are derived from Equation~\ref{eq2:lossrv}.
+\begin{align*}
+    R_{t+1} = -\Delta_t (S_t - e^{-r}S_{t+1}) + P_{t+1}, \quad & t \in \{0,\ldots,T-1\}, \\
+    & \gamma  = e^{-r},
+\end{align*}
+where the discount factor $\gamma$ models the present value of future rewards and is conveniently inherited from the risk-free rate $r$. 
+Hence, the objective of the insurer is to find a policy $\pi$ that minimizes the expected liability over time by dynamically adjusting the hedging portfolio based on the current state of the VA and the financial markets, which is equivalent to finding the policy that maximizes the value function at each state $s$.
 
 \begin{equation}
-    \min_{\pi} \mathbb{E}[\sum_{t=1}^{T} \gamma^t L_t | \pi, s_0],
+    V^{\pi}_{\mathcal{M}}(s) = \mathbb{E}\left[\sum_{t=0}^{T} \gamma^t R_{t+1} | \pi, s\right],
 \end{equation}
-
-where it can be conveniently rewritten as the value function $V^{\pi}_{\mathcal{M}}(s)$ in Equation~\ref{eq3:V_pi} by setting the reward function $R_{t} = -L_t$ and the discount factor $\gamma = \frac{1}{1+r}$.
-Other value functions can be used to optimize over a risk measure on the cumulative liability, such as the Value-at-Risk (VaR) or the Conditional Value-at-Risk (CVaR).
-Denote the risk measure as $\rho_{\alpha}$, where $\alpha$ is the confidence level, then the value function can be set as
-
-\begin{equation}
-    V^{\pi}_{\mathcal{M}}(s) = \rho_{\alpha}(\sum_{t=1}^{T} \gamma^t L_t | \pi, s_0).
-\end{equation}
+where the expectation is taken over the possible sequences of states and rewards that follow from the policy $\pi$.

### 2024-04-18 project3/tlHedging.tex
new

@@
     Representative algorithms include the Trust Region Policy Optimization (TRPO) algorithm proposed by~\cite{schulman2015trust} and the Proximal Policy Optimization (PPO) algorithm proposed by~\cite{schulman2017proximal}.
-
+    ~\cite{du2020deep} show that the PPO algorithm is more sample efficient and stable than the value-based approaches in training agents to hedge financial derivatives.
     The most relevant paper to our study is~\cite{chong2023pseudo}, which uses the PPO algorithm to hedge GMMB with a GMDB rider under the Black-Scholes framework.
@@
 The PPO algorithm consists of two main components: the policy network and the value network.
-The policy network learns the policy by outputting the action based on the current state, while the value network learns the value function by approximating the expected cumulative reward over time following the policy.
+The policy network learns the policy by outputting the action based on the current state, while the value network learns the value function (and an advantage function) by approximating the expected cumulative reward over time following the policy.
 The policy network is updated by performing gradient ascent with respect to the policy parameters, while the value network is updated by minimizing the mean squared error between the predicted value and the target value.
@@
 \begin{enumerate}
+    \item The dynamic lapse rate $q_t$ is applied to the contract, i.e., $q$ of the policyholders leave the contract at time $t$.
+        \begin{equation*}
+            q_t = q_t^B \cdot \text{clip} (M_q (\frac{G_{t-1}}{F_{t-1}} - D_q), L_q, U_q),
+        \end{equation*}
+    where $q_t^B$ is the base lapse rate, $\text{clip}(x, a, b)$ is a function that clips the value of $x$ to be within the range $[a, b]$, and $M_q$, $D_q$, $L_q$, and $U_q$ are the model parameters taken from National Association of Insurance Commissioners’(NAIC) Valuation Manual 21~\citep{naic2021}.
     \item The sub-account value changes according to the growth of the underlying stock and the (gross) management fee is deducted. That is, 
         \begin{equation*}
-            F_t = F_{(t-1)_+}\cdot\frac{S_{t}}{S_{t-1}}\cdot(1-\eta_g),
+            F_t = F_{(t-1)_+}\cdot\frac{S_{t}}{S_{t-1}}\cdot(1-\eta_g)\cdot(1-q_t),
         \end{equation*} 
@@
         \begin{equation*}
-            G_t = \max\{G_{t-1},F_t\}.
+            G_t = \max\{G_{t-1}\cdot(1-q_t),F_t\}.
         \end{equation*} 
+    A GMDB can be modeled with $G_t = G_{t-1}\cdot(1-q_t)$.
 
@@
 where the last equality holds by a rearrangement of terms and a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$.
+For a GMMB contract, the payoff at time~$t$ is $P_t$ is defined as
+\begin{equation} \label{eq3:gmmb_payout}
+    P_t = 
+    \begin{cases}
+        \max\{G_T - F_T, 0\} & \text{if } t = T, \\
+        0 & \text{otherwise}.
+    \end{cases}
+\end{equation}
 It is worth noting that the formulation Equation~\ref{eq3:lossrv} differ from the traditional loss reserve calculation in Equation~\ref{eq2:lossrv} as the later includes $V_0$, the unhedged liability at time $t=0$.
@@
 
-\subsection{Markov Decision Process (MDP) for Hedging VAs}
+\subsection{Markov Decision Process}
 
@@
 
-The objective in an MDP is to find a policy, $\pi: \mathcal{S} \rightarrow \mathcal{A}$, that maximizes the cumulative reward over time, often referred to as the value function for a policy $\pi$ at state $s$:
+The objective in an MDP is to find a policy, $\pi: \mathcal{S} \rightarrow \mathbb{P}(\mathcal{A})$, that maximizes the cumulative reward over time, often referred to as the state value function for a policy $\pi$ at state $s$:
 
 \begin{equation} \label{eq3:V_pi}
-    V^{\pi}_{\mathcal{M}}(s) = \mathbb{E}_{s_0 \sim \mu_0, a_i \sim \pi(\cdot|s_i), s_{i+1} \sim \mathcal{P}(\cdot|s, a)} \left[ \sum_{t=0}^{\infty} \gamma^t R_{t+1} |\pi, s \right],
+    V^{\pi}_{\mathcal{M}}(s_t) = \mathbb{E}_{s_{t+1}, a_{t}} \left[ \sum_{t=0}^{\infty} \gamma^t R_{t+1} |\pi, s_t \right],
 \end{equation}
 
-where $R_{t+1} = \mathcal{R}(s_i, a_i, s_{i+1})$ is the reward received by the agent after taking action $a_i$ in state $s_i$ and transitioning to state $s_{i+1}$, and the expectation is taken over the possible sequences of states and rewards that follow from the policy $\pi$.
+where $R_{t+1} = \mathcal{R}(s_t, a_t, s_{t+1})$ is the reward received by the agent after taking action $a_t$ in state $s_t$ and transitioning to state $s_{t+1}$, and the expectation is taken over the possible sequences of states and rewards that follow from the policy $\pi$.
+The state-action value function, $Q^{\pi}_{\mathcal{M}}(s_t, a_t)$, is defined as the expected cumulative reward starting from state $s_t$, taking action $a_t$, and following policy $\pi$ thereafter:
 
-In the context of hedging VAs, the state space $\mathcal{S}$ represents the information available to the agent: the current value of the underlying asset ($S_t$), the current subaccount value ($F_t$), the guarantee value ($G_t$), the time to maturity ($\tau = T-t$), and the previous hedging weight ($\Delta_{t-1}$).
+\begin{equation} \label{eq3:Q_pi}
+    Q^{\pi}_{\mathcal{M}}(s_t, a_t) = \mathbb{E}_{s_{t+1}, a_{t+1}} \left[ \sum_{t=0}^{\infty} \gamma^t R_{t+1} |\pi, s_t, a_t \right],
+\end{equation}
+
+Based on Equations~\ref{eq3:V_pi} and~\ref{eq3:Q_pi}, the advantage function, $A^{\pi}_{\mathcal{M}}(s_t, a_t)$, is defined as the difference between the state-action value function and the state value function:
+
+\begin{equation} \label{eq3:A_pi}
+    A^{\pi}_{\mathcal{M}}(s_t, a_t) = Q^{\pi}_{\mathcal{M}}(s_t, a_t) - V^{\pi}_{\mathcal{M}}(s_t).
+\end{equation}
+
+The advantage function quantifies the advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi$.
+
+\subsection{Model-Free PPO for Hedging Variable Annuities}
+
+The state space $\mathcal{S}$ represents the information available to the agent: the current value of the underlying asset ($S_t$), the current subaccount value ($F_t$), the guarantee value ($G_t$), the time to maturity ($\tau = T-t$), and the previous hedging weight ($\Delta_{t-1}$).
 Let $\mathbf{S}_t = (S_t, F_t, G_t, \tau, \Delta_{t-1}) \in \mathcal{S} $ denote the state vector at time $t$.
@@
 where the discount factor $\gamma$ models the present value of future rewards and is conveniently inherited from the risk-free rate $r$. 
-Hence, the objective of the insurer is to find a policy $\pi$ that minimizes the expected liability over time by dynamically adjusting the hedging portfolio based on the current state of the VA and the financial markets, which is equivalent to finding the policy that maximizes the value function at each state $s$.
+For a GMMB contract, the reward function $P_t$ defined in Equation~\ref{eq3:gmmb_payout} indicates that the payout is only made at the end of the contract, i.e., $t=T$, which makes it challenging to learn the optimal hedging policy without iterating through the entire contract period.
+Nevertheless, the objective of the insurer is to find a policy $\pi$ that minimizes the expected liability over time by dynamically adjusting the hedging portfolio based on the current state of the VA and the financial markets, which is equivalent to finding the policy that maximizes the value function at each state $s$.
 
 \begin{equation}
-    V^{\pi}_{\mathcal{M}}(s) = \mathbb{E}\left[\sum_{t=0}^{T} \gamma^t R_{t+1} | \pi, s\right],
+    V^{\pi_{\theta}}(s_t) = \mathbb{E}\left[\sum_{t=0}^{T} \gamma^t R_{t+1} | \pi_{\theta}, s_t\right],
 \end{equation}
-where the expectation is taken over the possible sequences of states and rewards that follow from the policy $\pi$.
+where the expectation is taken over the possible sequences of states, and rewards that follow from the policy $\pi$.
+The action-value function $Q^{\pi_{\theta}}$ and the advantage function $A^{\pi_{\theta}}$ are similarly defined as in Equations~\ref{eq3:Q_pi} and~\ref{eq3:A_pi}, respectively.
+
+In a model-free PPO approach of reinforcement learning, the agent estimates the advantage function $A^{\pi_{\theta}}$ by learning the value function with a deep neural network.
+Denote the estimator of the andvantage function at time $t$ by $\hat{A}_{\pi_{\theta}}(s_t, a_t)$.
+The policy $\pi_\theta$ is also parameterized by a deep neural network with parameters $\theta$, and the policy is updated by performing gradient ascent with respect to the policy parameters to maximize an objective function that reflects the advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi$, i.e., the objective function involves the estimator $\hat{A}_{\pi}(s_t, a_t)$.
+\begin{align}
+    \max_{\theta} \mathbb{E}\left[ \min \left\{ r_t(\theta)\hat{A}^{\pi_{\theta}}(s_t, a_t), \text{clip}(r_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(s_t, a_t)  \right\} \right] \\
+    r_t(\theta) = \frac{\pi_{\theta}(a_t|s_t)}{\pi_{\theta_{old}}(a_t|s_t)} 
+\end{align}
+
+where $\theta_{old}$ denotes the policy parameters at the previous iteration, $\epsilon$ is a hyperparameter that controls the size of the policy update, and $\text{clip}(x, a, b)$ is a function that clips the value of $x$ to be within the range $[a, b]$.
+The policy is updated by performing gradient ascent with respect to the policy parameters $\theta$ to maximize the objective function, which is estimated by sampling from the environment and computing the empirical average of the objective function over the sampled trajectories.
+The first component in the objective function, $r_t(\theta) \hat{A}^{\pi_{\theta}}(s_t, a_t)$, is a surrogate objective function that approximates the advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi_{\theta_{old}}$, and the second component, $\text{clip}(r_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(s_t, a_t)$, is a clipped surrogate objective function that prevents large policy updates and ensures more stable training.
+The TRPO algorithm proposed by~\cite{schulman2015trust} uses a similar clipped surrogate objective function to ensure that the policy update does not deviate too far from the old policy, but PPO simplifies the optimization problem by using a clipped surrogate objective function instead of a hard-coded constraint on the policy update.
+Compared to TRPO, PPO is more computationally efficient and easier to implement, making it a popular choice for training deep reinforcement learning agents.
+For a in-depth discussion on the implementation details of both TRPO and PPO, we refer the reader to~\cite{engstrom2020implementation}.
+
+In a model-free reinforcement learning approach, the agent learns the optimal policy by iteratively updating the policy and the value function based on the observed states, actions, and rewards.
+In our context of hedging VAs, the agent does not have explicit knowledge of the underlying asset price dynamics or the future mortality rates, so the future payoff of the VA is uncertain and must be learned from interactions with the environment.
+This uncertainty results in the formulation of the hedging problem as in Equation~\ref{eq3:lossrv} instead of the traditional loss reserve calculation in Equation~\ref{eq2:lossrv}, where the initial liability $V_0$ can be estimated by simulating from a known financial (and actuarial) model.
+The model-free PPO algorithm allows the agent to learn an optimal hedging policy from past observations without relying on a predefined model, making it a suitable approach for hedging VAs in a dynamic and uncertain market environment.
+
+\section{Numerical Experiment}
+
+More specifically, our implementation of the PPO uses a generalized advantage estimation~\citep{schulman2015high} to estimate the advantage function.
+
+\section{Transfer Learning for Hedging Variable Annuities}
+
+Transfer learning is a machine learning technique that leverages knowledge gained from one task to improve performance on another related task.
+In the context of reinforcement learning, transfer learning can be used to transfer knowledge learned from one environment to another, allowing the agent to learn more efficiently and effectively in the new environment.
+In this section, we explore the potential of transfer learning for hedging VAs by transferring knowledge learned from a related financial derivative, such as a European option, to improve the performance of the hedging policy for VAs.

### 2024-04-18 project3/tlHedging.tex
new

@@
 
-\subsection{Simulation Model for Variable Annuities Hedging}
+\subsection{Simulation Model for Variable Annuities Hedging} \label{subsec:VASimulation}
 
@@
         \end{equation*} 
-    where $I_t = \gamma G_t$. A GMMB can be modeled with $\gamma = 0$.
+    where $I_t = \xi G_t$. A GMMB can be modeled with $\xi = 0$.
 \end{enumerate}
@@
 \begin{align}
-L   & = H_0 - e^{-rT} H^{bf}_T + \sum_{t=1}^{T-1} e^{-rt} HE_t  + \sum_{t=1}^T e^{-rt} P_t \\ 
-    & = H_0 - e^{-rT} H^{bf}_T + \sum_{t=1}^{T-1} e^{-rt} \Delta_{t-1} (S_{t-1} - S_{t}) + B_{t-1}(1-e^{r}) + \sum_{t=1}^T e^{-rt} P_t \nonumber \\
-    & = \sum_{t=1}^T e^{-rt} \left( \Delta_{t-1} (S_{t-1} - e^{-r} S_t) + P_t \right) \label{eq3:lossrv}
+L   & = H_0 - e^{-rT} H^{bf}_T + \sum_{t=1}^{T-1} e^{-rt} HE_t  + \sum_{t=1}^T e^{-rt} P_t + \sum_{t=1}^T e^{-rt} C_t  \\ 
+    & = H_0 - e^{-rT} H^{bf}_T + \sum_{t=1}^{T-1} e^{-rt} \Delta_{t-1} (S_{t-1} - S_{t}) + B_{t-1}(1-e^{r}) + \sum_{t=1}^T e^{-rt} (P_t + C_t) \nonumber \\
+    & = \sum_{t=1}^T e^{-rt} \left( \Delta_{t-1} (S_{t-1} - e^{-r} S_t) + C_t \right) \label{eq3:lossrv}
 \end{align}
-where the last equality holds by a rearrangement of terms and a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$.
+where the last equality holds by a rearrangement of terms and a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$, and $C_t := C \cdot S_{t-1} \cdot (|\Delta_{t-1}| + 0.01 \Delta_{t-1}^2)$ is the tranaction cost at time $t$, which follows from the quadratic transaction cost model used in~\cite{garleanu2013dynamic}.
+
 For a GMMB contract, the payoff at time~$t$ is $P_t$ is defined as
@@
 The state transition probability distribution $\mathcal{P}$ is conveniently inherited from the dynamics of the VA in Section~\ref{subsec:VApayout}, and the reward function $\mathcal{R}$ and discount factor $\gamma$ are derived from Equation~\ref{eq2:lossrv}.
-\begin{align*}
-    R_{t+1} = -\Delta_t (S_t - e^{-r}S_{t+1}) + P_{t+1}, \quad & t \in \{0,\ldots,T-1\}, \\
-    & \gamma  = e^{-r},
-\end{align*}
+\begin{align} \label{eq3:rewardTrading}
+    R_{t+1}^{\text{Trade}} = -\Delta_t (S_t - e^{-r}S_{t+1}) + P_{t+1} + C_{t+1}, \quad & t \in \{0,\ldots,T-1\}, \\
+    & \gamma  = e^{-r}, \nonumber
+\end{align}
 where the discount factor $\gamma$ models the present value of future rewards and is conveniently inherited from the risk-free rate $r$. 
 For a GMMB contract, the reward function $P_t$ defined in Equation~\ref{eq3:gmmb_payout} indicates that the payout is only made at the end of the contract, i.e., $t=T$, which makes it challenging to learn the optimal hedging policy without iterating through the entire contract period.
-Nevertheless, the objective of the insurer is to find a policy $\pi$ that minimizes the expected liability over time by dynamically adjusting the hedging portfolio based on the current state of the VA and the financial markets, which is equivalent to finding the policy that maximizes the value function at each state $s$.
+Equation~\ref{eq3:rewardTrading} allows the agent to receive rewards at each time step, which enables the agent to learn the optimal hedging policy that maximizes the cumulative reward over time.
+However, the reward function in Equation~\ref{eq3:rewardTrading} may not be suitable for hedging, as it does not directly reflect the hedging performance and encourages the agent to take actions that maximize the reward without considering downside risk.
+To address this issue, we propose a new reward function that reflects the hedging performance and encourages the agent to learn a hedging policy that aims to maximize the expected reward with quadratic penalty.
 
+\begin{equation} \label{eq3:rewardHedging}
+    R_{t+1}^{\text{Hedge}} = R_{t+1}^{\text{Trade}} - \frac{\lambda}{2}(R_{t+1}^{\text{Trade}})^2, \quad t \in \{0,\ldots,T-1\},
+\end{equation}
+
+The objective of an insurer is to find a policy $\pi$ that maximize the expected reward () over time by dynamically adjusting the hedging portfolio based on the current state of the VA and the financial markets, which is equivalent to finding the policy that maximizes the value function at each state $s$.
 \begin{equation}
@@
 The action-value function $Q^{\pi_{\theta}}$ and the advantage function $A^{\pi_{\theta}}$ are similarly defined as in Equations~\ref{eq3:Q_pi} and~\ref{eq3:A_pi}, respectively.
+However,
 
-In a model-free PPO approach of reinforcement learning, the agent estimates the advantage function $A^{\pi_{\theta}}$ by learning the value function with a deep neural network.
 Denote the estimator of the andvantage function at time $t$ by $\hat{A}_{\pi_{\theta}}(s_t, a_t)$.
+In a model-free PPO approach of reinforcement learning, the agent estimates the advantage function $A^{\pi_{\theta}}$ by learning the value function with a deep neural network with parameters $\phi$, i.e.,
+\begin{equation}
+    \hat{A}_{\pi_{\theta}}(s_t, a_t) = V_{\phi}(s_t) - Q_{\phi}(s_t, a_t).
+\end{equation}
 The policy $\pi_\theta$ is also parameterized by a deep neural network with parameters $\theta$, and the policy is updated by performing gradient ascent with respect to the policy parameters to maximize an objective function that reflects the advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi$, i.e., the objective function involves the estimator $\hat{A}_{\pi}(s_t, a_t)$.
@@
 
+\begin{algorithm} 
+    \caption{PPO for Hedging Variable Annuities} 
+    \begin{algorithmic}[1] \label{alg3:ppoHedging}
+        \STATE  Initialize policy parameters $\theta_0$ and value function parameters $\phi_0$.
+        \STATE  \textbf{For} {iteration $k=0, 1,2,\ldots$} \textbf{do}
+        \STATE  \quad Collect a set of trajectories $\mathcal{D}_k$ by sampling from the environment with policy $\pi_{\theta_{k}}$.
+        \STATE  \quad Compute the rewards $\hat{R}_t$ for each trajectory in $\mathcal{D}_k$.
+        \STATE  \quad Estimates the advantage function with $\hat{A}_{\pi_{\theta_k}}(s_t, a_t)$ using value function $V_{\phi_k}$.
+        \STATE  \quad Update the policy parameters $\theta_{k+1}$ by 
+        \begin{equation*}
+            \max_{\theta} \mathbb{E}\left[ \min \left\{ r_t(\theta)\hat{A}^{\pi_{\theta}}(s_t, a_t), \text{clip}(r_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(s_t, a_t)  \right\} \right]
+        \end{equation*}
+        \STATE  \quad Update the value function parameters $\phi_{k+1}$ by minimizing the mean squared error between the predicted value and the actual collected reward.
+        \begin{equation*}
+            \phi_{k+1} = \arg \min_{\phi} \frac{1}{|\mathcal{D}_k|T} \sum_{\mathcal{\kappa} \in \mathcal{D}_k} \sum_{t=0}^{T} \left( V_{\phi}(s_t) - \hat{R}_t \right)^2
+        \end{equation*}
+        \STATE  \textbf{End For}
+    \end{algorithmic}
+\end{algorithm}
+
 In a model-free reinforcement learning approach, the agent learns the optimal policy by iteratively updating the policy and the value function based on the observed states, actions, and rewards.
@@
 
+In this section, we present a numerical experiment to demonstrate the effectiveness of the model-free PPO algorithm for hedging VAs with transaction costs.
+We consider a VA contract with a maturity of $T=240$ months and a guaranteed minimum maturity benefit (GMMB) rider with a simulation environment described in Section~\ref{subsec:VASimulation}.
+The simulation enviornment is implemented in Python using the OpenAI Gym framework~\citep{brockman2016openai} and PyTorch library~\citep{paszke2019pytorch}.
+The environment is designed to simulate the dynamics of the VA contract and provide the agent with the current state of the VA with the contract specifications and the financial market information described in Table~\ref{tab3:hyperparameters}.
+
+\begin{table}[ht!]
+    \centering
+    \begin{tabular}{ll} 
+        \toprule
+        Hyperparameter & Value \\
+        \midrule
+        $|\mathcal{D}_k|$   & 64        \\
+        $\epsilon$          & 0.2       \\
+        Learning rate       & 0.0003    \\
+        $r$                 & 0.002     \\
+        $S_0$               & 1000      \\
+        $\mu$               & 0.00375   \\
+        $\sigma$            & 0.0457627 \\
+        $T$                 & 240       \\
+        \bottomrule
+    \end{tabular}
+    \caption{PPO Hyperparameters and GMMB Contract Specifications} 
+    \label{tab3:hyperparameters}
+\end{table}
+
+The underlying asset price $S_t$ is modeled as a geometric Brownian motion with a drift rate $\mu$ and a volatility $\sigma$.
+The weights of the value network and the policy network are initialized with orthogonal initialization~\citep{engstrom2020implementation} with scaling $\sqrt{2}$ and the bias terms set to zero.
+The value network and the policy network are implemented as fully connected neural networks with two hidden layers of 64 units each and $\tanh$ activation functions.
+They are trained using the Adam optimizer with a learning rate of $0.0003$ and a batch size automatically adjusted to the number of trajectories in the collected dataset.
+At each timestep, the observations are normalized and cliped between $-10$ and $10$ before being fed into the neural networks to stabilize the training process.
+For PPO, we follow the suggestions in~\cite{schulman2017proximal} and set the clipping hyperparameter $\epsilon$ to $0.2$ to prevent large policy updates. 
 More specifically, our implementation of the PPO uses a generalized advantage estimation~\citep{schulman2015high} to estimate the advantage function.
+The agent interacts with the environment for $10^6$ episodes, and the policy and value networks are updated every $64$ episodes and evaluated every $1000$ episodes.
+The performance of the agent is evaluated based on the average reward over an independent test set of $10^5$ episodes, and the results are compared with the benchmark hedging strategy, delta hedging.
 
@@
 In this section, we explore the potential of transfer learning for hedging VAs by transferring knowledge learned from a related financial derivative, such as a European option, to improve the performance of the hedging policy for VAs.
+
+In the context of deep reinforcement learning, transfer learning can be used to improve the risk management of VAs in five ways:
+\begin{enumerate}
+    \item   \textbf{Transferring to VA products}: Knowledge can be transferred from the hedging strategies of financial derivatives to constructing hedging strategies for VAs.
+    VAs are complex insurance products with unique features, which makes it challenging to develop effective hedging strategies.
+    However, the payoff structures of VAs are similar to those of financial derivatives, such as European options, which have been extensively studied in the literature.
+    By leveraging the knowledge from the hedging strategies of financial derivatives, we can improve the risk management of VAs.
+    \item   \textbf{Transferring to new VA products}: Knowledge can be transferred from the hedging strategies of one VA product to another VA product.
+    Different VA products have different features and payoff structures, which makes it challenging to develop hedging strategies for new VA products.
+    However, experience from hedging one VA product can be transferred to develop hedging strategies for new VA products, especially when the new VA product is similar to the existing ones.
+    \item   \textbf{Transferring to new asset models}: Knowledge can be transferred from the hedging strategies of one asset model to another asset model.
+    A stochastic volatility model is a more realistic model for asset prices than the Black-Scholes model, but it is more challenging to develop hedging strategies for VAs under such a model.
+    \item  \textbf{Transferring to new model specifications}: Model misspecification is a common issue in financial modeling, and training on data simulated with misspecified parameters can lead to suboptimal hedging strategies.
+    If only the misspecified model is similar to the correct model, then we can leverage the knowledge from the misspecified model to improve the hedging strategies under the correct model, since the only difference between the two models is the parameter values.
+    \item   \textbf{Transferring to the real world}: Knowledge can be transferred from simulated data to real-world data.
+    In practice, it is challenging to obtain real-world data for VAs, but we can leverage simulated data to develop hedging strategies for VAs.
+    If the simulated data is representative of the real-world data, then the hedging strategies developed from the simulated data can be transferred to the real world.
+\end{enumerate}
+Given a set of source domains $\bm{\mathcal{M}}_s= \{ \mathcal{M}_s| \mathcal{M}_s \in \bm{\mathcal{M}}_s\}$ and a target domain $\mathcal{M}_t$, transfer learning aims to improve the learning on the target domain.
+While utilizing the interior information $\mathcal{I}_t$ from the target domain, the exterior information $\mathcal{I}_s$ from the source domains is also leveraged to improve the learning on the target domain.
+\begin{equation}
+    \pi^* = \arg \max_\pi \mathbb{E}_{s \sim \mu_0, a \sim \pi} \left[V_{\mathcal{M}}^\pi (s, a) \right], 
+\end{equation}
+where $\pi = \phi(\mathcal{I}_s \sim \bm{\mathcal{M}}_s, \mathcal{I}_t \sim \mathcal{M}_t)$ is policy learned from target domain based on information from both the source domains and the target domain.
+A regular reinforcement without transfer learning is a special case where $\mathcal{I}_s = \emptyset$ and $\pi = \phi(\mathcal{I}_t \sim \mathcal{M}_t)$.
+In the context of deep hedging, various research has been conducted to improve the hedging strategies on real-world data by leveraging knowledge from simulated data.
+Most of the research uses the offline-online learning approach, where the hedging strategies are first trained with simulation data, but updated in real-time based on new market information and continuous learning to adapt to changing market dynamics.
+The most relevant paper to our study is~\cite{xiao2021optimal}, which use policy gradient algorithms to train hedging strategies for European options with simulation data from Heston model and then updated in real-time hedging S\&P 500 index options.
+
+\subsection{Evaluation Metrics}
+The metrics discussed for evaluating transfer learning approaches focus on two key aspects: mastery and generalization. 
+Mastery assesses the agent's final performance level in the target domain, indicating how effectively it has learned a specific task from previous knowledge. 
+Some common metrics for evaluating mastery include:
+\begin{itemize}
+    \item \textbf{Asymptotic performance:} the final reward of the agent in the target domain.
+    \item \textbf{Transfer ratio:} the ratio of the agent's performance in the target domain with and without transfer learning.
+\end{itemize}
+Generalization, on the other hand, refers to the agent's ability to quickly adapt its learned knowledge to the target domain.
+\begin{itemize}
+    \item \textbf{Jumpstart performance:} the initial reward of the agent in the target domain.
+    \item \textbf{Accumulated reward:} the total area under the reward curve over time in the target domain.
+    \item \textbf{Time to threshold:} the time it takes for the agent to reach a certain performance threshold in the target domain.
+    \item \textbf{Performance with fixed epochs:} the agent's performance in the target domain after a fixed number of epochs.
+\end{itemize}

### 2024-04-18 project3/tlHedging.tex
new

@@
 The agent interacts with the environment for $10^6$ episodes, and the policy and value networks are updated every $64$ episodes and evaluated every $1000$ episodes.
-The performance of the agent is evaluated based on the average reward over an independent test set of $10^5$ episodes, and the results are compared with the benchmark hedging strategy, delta hedging.
+The performance of the agent is evaluated based on the average reward over an independent test set of $10^4$ episodes, and the results are compared with the benchmark hedging strategy, delta hedging.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\textwidth]{./project3/figures/loss_distribution.png}
+    \caption{Performance of PPO for Hedging GMMB Contracts on GBM Asset Model} 
+    \label{fig3:ppo_hedging}
+\end{figure}
+
+Figure~\ref{fig3:ppo_hedging} shows the performance of the PPO algorithm for hedging GMMB contracts on a geometric Brownian motion (GBM) asset model.
+The figure shows the distribution of the hedging errors incurred by the agent over the $10^4$ test episodes.
+The hedging errors are calculated as the difference between the actual cash flow incurred by the agent due to rebalancing and the expected cash flow based on the optimal hedging policy.
+The results show that the PPO algorithm is able to learn an optimal hedging policy that minimizes the hedging errors, and it surpasses the benchmark delta hedging strategy in terms of hedging performance.
 

### 2024-05-03 project2/nnMetamodels.tex
new

@@
 \chapter{Cutting Through the Noise: Using Deep Neural Network Metamodels for High Dimensional Nested Simulation}
+\label{ch2}
 %======================================================================
@@
 
-Deep neural networks~\citep{hastie2009elements,lecun2015deep} have attracted attentions of researchers and practitioners due to their success in solving real-world supervised learning tasks such as AlphaGo~\citep{silver2016mastering} and ChatGPT~\citep{chatgpt}.
+Deep neural networks~\citep{hastie2009elements,lecun2015deep} have attracted attentions of researchers and practitioners due to their success in solving real-world machine learning tasks such as AlphaGo~\citep{silver2016mastering} and ChatGPT~\citep{chatgpt}.
 Since the first artificial neural network model~\citep{mcculloch1943logical} and the first algorithm for training a perceptron~\citep{rosenblatt1958perceptron}, especially after the introduction of backpropagation~\citep{rumelhart1985learning} and the growth of high-performance computing, the field of artificial neural network and deep learning in general has grown rapidly.

### 2024-05-03 project3/draft.tex
new

\chapter{Model-Free Deep Hedging of Variable Annuities}

\section{Introduction}

Reinforcement Learning (RL) is a branch of machine learning that focuses on training algorithms, known as agents, to make a sequence of decisions. 
The agent learns to achieve a goal in an uncertain, potentially complex environment by trial and error, using feedback from its own actions and experiences. 
Unlike supervised learning, where training data is labeled with the correct answers, in RL, an agent is provided with rewards or punishments as signals for its actions.

The core of RL revolves around the concept of the agent interacting with its environment over time, aiming to maximize the cumulative reward. 
This process involves observing the state of the environment, selecting and performing actions, and receiving rewards or penalties in response to those actions. 
The agent's objective is to learn a mapping from states to actions that maximizes this cumulative reward, which is often referred to as a policy. 
One of the fundamental frameworks for modeling RL problems is the Markov Decision Process (MDP). 
An MDP provides a mathematical formulation of the decision-making process, characterized by states, actions, rewards, and transition probabilities. 
Solving an MDP involves finding a policy that maximizes some function of the expected rewards, typically the expected cumulative reward over time.

RL algorithms can be broadly categorized into two types: model-based RL and model-free RL. 
Model-based RL utilize a model of the environment to simulate the outcomes of actions, enabling planning and decision-making with fewer interactions with the environment. 
The biggest drawback of model-based RL is model bias. 
In practice, the ground-true model is usually not available.
By using a model, an RL agent can exploit the model bias, which leads to suboptimal performance in the real environment.
Conversely, model-free RL learn directly from interactions with the environment.
Without relying on a model, model-free RL algorithms are more straightforward implement and tune.

A compelling application of RL is dynamic hedging, where the complexity and uncertainty of financial markets make traditional static models inadequate.
RL's adaptability and learning capabilities offer a promising solution to dynamically adjust hedging strategies in response to market movements and assumptions changes.
In particular, model-free RL has the potential to enhance risk management practices by developing robust strategies that can adapt in real-time.

In this paper, we propose a model-free RL algorithm to improve the risk management of variable annuities (VAs).
VAs are popular insurance products that add investment features to an insurance contract.
Hedging VAs is particularly challenging due to multiple sources of risk.
Our model-free RL approach aims to learn a hedging policy without directly accessing models of the underlying risk factors.
By interacting with an enviornment, the hedging policy can effectively manage the risks of VAs in a changing market environment.

The rest of the paper is organized as follows:

\section{Review of Reinforcement Learning}

\subsection{Markov Decision Process}

An MDP is defined by the tuple $\mathcal{M} = (\mathcal{S}, \mathcal{A}, \mathcal{P}, \mathcal{R}, \gamma)$, where:

\begin{itemize}
    \item $\mathcal{S}$ is a finite set of states.
    \item $\mathcal{A}$ is a finite set of actions.
    \item $\mathcal{P}$ is a state transition probability distribution, where $\mathcal{P}(s_{t}|s_{t-1}, a_{t-1})$ represents the probability of transitioning from state $s_t$ to state $s_{t-1}$ due to action $a_{t-1}$.
    \item $\mathcal{R}$ is a reward distribution, $\mathcal{R}(s, a, s')$ is the reward received after transitioning from state $s$ to state $s'$ due to action $a$.
    \item $\gamma$ is a discount factor, $\gamma \in [0,1]$,  which models the present value of future rewards.
\end{itemize}

The objective in an MDP is to find a policy, $\pi: \mathcal{S} \rightarrow \mathbb{P}(\mathcal{A})$, that maximizes the cumulative reward over time.
A Markov Decision Process (MDP) provides a mathematical framework for solving sequential decision-making tasks in an enviornment where outcomes are partly random and partly under the control of a hedging agent. 
For hedging VAs, the asset dynamics and the mortality model are not controlled by the agent, but the agent controls the cumulative reward by deciding on the hedging weights.
In this section, we reformulate the hedging enviornment of VAs from Section~\ref{subsec:VApayout} as an MDP and define the key components of the MDP.

\textbf{Hedging Environment of Variable Annuities} \label{subsec:VASimulation}

Consider a generic VA contract with maturity $T>0$ periods, e.g., $T=240$ months.
Then the contract expires at $T'=\min\{T,\tau\}$, i.e., the earlier of the contract maturity and the death of the policyholder.
Let $S_t$, $F_t$, and $G_t$ be the indexed stock price, the subaccount value and the guarantee value, respectively, at time $t=1,2,\ldots,T$.
Evolution of the subaccount value and the guarantee value of a VA contract affect the contract payout.
For clarity, we use $F_t$ and $F_{t_+}$ to denote the sub-account value just before and just after the withdrawal at time $t$, if any.
Let $\eta_g$ be the gross rate of management fee that is deducted from the fund value at each period and let $\eta_n < \eta_g$ be the net rate of management fee income to the insurer.
The difference between the gross management fee and the net management fee income represents the incurred investment expenses.

At the inception of the contract, i.e., $t=0$, we assume that the whole premium is invested in the stock index and the guarantee base is set to the sub-account value:
\begin{equation*}
    S_0=F_0=G_0.
\end{equation*}
At each time $t=1,\ldots,T$, the following events take place in the following order:
\begin{enumerate}
    \item The dynamic lapse rate $q_t$ is applied to the contract, i.e., $q$ of the policyholders leave the contract at time $t$.
        \begin{equation} \label{eq3:lapse}
            q_t = q_t^B \cdot \text{clip} (M_q (\frac{G_{t-1}}{F_{t-1}} - D_q), L_q, U_q),
        \end{equation}
    where $q_t^B$ is the base lapse rate, $\text{clip}(x, a, b)$ is a function that clips the value of $x$ to be within the range $[a, b]$, and $M_q$, $D_q$, $L_q$, and $U_q$ are the model parameters taken from National Association of Insurance Commissioners’ (NAIC) Valuation Manual 21~\citep{naic2021}.
    \item The sub-account value changes according to the growth of the underlying stock and the (gross) management fee is deducted. That is, 
        \begin{equation} \label{eq3:subaccount}
            F_t = F_{(t-1)_+}\cdot\frac{S_{t}}{S_{t-1}}\cdot(1-\eta_g)\cdot(1-q_t),
        \end{equation} 
    where $(x)^+=\max\{x,0\}$ and $F_{(t-1)_+}$ will be defined later. The insurer's income at time $t$ is the net management fee, i.e., $F_t\eta_n$.

    \item The guarantee value ratchets up (ratcheting is a common feature in GMWB) if the sub-account value exceeds the previous guarantee value, i.e., 
        \begin{equation} \label{eq3:guarantee}
            G_t = \max\{G_{t-1}\cdot(1-q_t),F_t\}.
        \end{equation} 
    A GMMB can be modeled with $G_t = G_{t-1}\cdot(1-q_t)$.

    \item The withdrawal is made (for GMWB) and is deducted from the sub-account value, i.e., 
        \begin{equation} \label{eq3:withdrawal}
            F_{t_+} = (F_t - I_t)^+,
        \end{equation} 
    where $I_t = \xi G_t$. A GMMB can be modeled with $\xi = 0$.
\end{enumerate}

Consider a VA contract whose delta hedge portfolio at any time~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at time $T$.
The value of the hedge portfolio at time~$(t-1)$ is:
\begin{equation*}
    H_{t-1} = \Delta_{t-1} S_{t-1} + B_{t-1},
\end{equation*}
where $S_t$ is the underlying stock price and any time $t>0$.
This hedge portfolio is brought forward to the next rebalancing time~$t$, when its value becomes:
\begin{equation*}
    H_{t}^{bf} = \Delta_{t-1} S_{t} + B_{t-1}e^{r}.
\end{equation*}
Therefore, the time~$t$ hedging error, i.e., the cash flow incurred by the insurer due to rebalancing at time~$t$, is
\begin{equation}
    HE_t = H_t - H^{bf}_t, \quad t=1,\ldots, T-1.
\end{equation}
The P\&L of the VA contract includes the cost of the initial hedge ($H_0$), the hedging errors~\eqref{eq2:hedgingerror}, the unwinding of the hedge at maturity ($H^{bf}_T$), and the contract payout at time~$t\in \{0,\ldots,T\}$.
Mathematically, the present value of the liability for a GMMB contract is 
\begin{align} \label{eq3:lossGMMB}
L   & = H_0 - e^{-rT} H^{bf}_T + \sum_{t=1}^{T-1} e^{-rt} HE_t + \sum_{t=1}^T e^{-rt} C_t - \sum_{t=1}^T e^{-rt} F_t\eta_n + e^{-rT} (G_t - F_t)^+ nonumber \\ 
    & = e^{-rT} (G_T - F_{T^+})^+ + \sum_{t=1}^T e^{-rt}  \left( \Delta_{t-1} (S_{t-1} - e^{-r} S_t) + C_t - F_t\eta_n \right) \label{eq3:lossrv}
\end{align}
where the equality holds by a rearrangement of terms and a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$, and $C_t := C \cdot S_{t-1} \cdot (|\Delta_{t-1}| + 0.01 \Delta_{t-1}^2)$ is the tranaction cost at time $t$~\cite{garleanu2013dynamic}.
Hence, the present liability consist of the hedging errors, the transaction costs, the net management fees, and the contract payouts.
Similarly, the present value of the liability for a GMWB contract is
\begin{equation} \label{eq3:lossGMWB}
L = \sum_{t=1}^T e^{-rt}  \left( \Delta_{t-1} (S_{t-1} - e^{-r} S_t) + C_t - F_t\eta_n \right)
\end{equation}
The GMWB payout is implicitly included in $F_t\eta_n$.
The discrete-time hedging problem of VAs can be conveniently formulated as an MDP, where the states, actions, transition probabilities, policies, and rewards are defined as follows.

\textbf{State Space}

The state space $\mathcal{S}$ represents all the information needed to characterize the hedging environment.
In a VA hedging problem, $\mathbf{s}_t$, the information available to a hedging agent at each time $t$ is 
$$\mathbf{s}_t := (S_t, F_t, G_t, \tau, \Delta_{t-1}) \in \mathcal{S}.$$
where $\tau$ is the remaining time to maturity and $\Delta_{t-1}$ is the previous hedging weight.
The hedging environment is partially observed, e.g., the agent does not have access to the contract specifications.
It has to learn a representation of the relevant information from the observed state $\mathbf{s}_t$.

\textbf{Action Space}

The action space $\mathcal{A}$ represents the set of actions that the agent can take at each time $t$.
In a VA hedging problem, the action space only includes the hedging weight $\Delta_t$.

\textbf{Policy}
A policy $\pi$ determines the best action to take in a given state, i.e.,
$$a_t \sim \pi(\cdot|\mathbf{s}_t).$$
In a VA hedging problem the policy outputs the hedging weight $\Delta_t$ given the observed state $\mathbf{s}_t$.

\textbf{Transition Probabilities}
The transition probabilities $\mathcal{P}$ represent the probability of transitioning from one state to another from taking an action.
In our setup, the transition probabilities are fully determined by Equation~\ref{eq3:lapse}, Equation~\ref{eq3:subaccount}, Equation~\ref{eq3:guarantee}, and Equation~\ref{eq3:withdrawal}.
Let $\mathcal{P}(\mathbf{s}_{t+1}|\mathbf{s}_t, a_t)$ be the probability of transitioning from state $\mathbf{s}_t$ to state $\mathbf{s}_{t+1}$ due to action $a_t$.
Aside from the previous hedging weight $\Delta_{t-1}$, the transition probabilities are independent of the actions.

\textbf{Reward and Discount Factor}
The reward function $\mathcal{R}$ and discount factor $\gamma$ in a typical RL problem are defined as follows:
\begin{align}
    \mathcal{R} & = \sum_{t=0}^{T-1} \gamma^t R_t \\
    \gamma      & = e^{-r}, \nonumber
\end{align}
where $R_t$ is the term reward received by the agent at time $t$, and the discount factor $\gamma$ is conveniently inherited from the risk-free rate $r$. 
In hedging, the term reward $R_t$ should be drived from Equation~\ref{eq3:lossGMMB} and Equation~\ref{eq3:lossGMWB} to represent the performance of the hedging policy, i.e., how closely the hedging portfolio tracks the liability.
For GMWB, we propose a term reward formulation that encourages the agent to maximize the expected reward with low hedging errors and transaction costs:
\begin{equation} \label{eq3:rewardGMWB}
    R_t = F_{t-1}\eta_n - \Delta_{t-1} |S_{t-1} - e^{-r}S_{t}| - C_{t-1}, \quad t \in \{1,\ldots,T \}
\end{equation}
The reward function of GMWB directly links to the time-$t$ loss of a GMWB contract as in Equation~\ref{eq3:lossGMWB}.
The GMMB loss consists of an additional payoff at maturity $T$, thus its term reward is formulated as:
\begin{equation} \label{eq3:rewardGMMB}
    R_t = 
    \begin{cases}
    F_{t-1}\eta_n - \Delta_{t-1} |S_{t-1} - e^{-r}S_{t}| - C_{t-1},                         & t\in \{1,\ldots,T-1 \} \\
    F_{t-1}\eta_n - \Delta_{t-1} |S_{t-1} - e^{-r}S_{t}| - C_{t-1} + (G_T - F_{T^+})^+      & t = T
    \end{cases}
\end{equation}
It is worth noting that learning to hedge GMWB is easier for an RL agent due to the absense of reward at maturity (long-term feedback).

\subsection{From AlphaZero to Deep Hedging}
Deep reinforcement learning first attacted attentions when AlphaGo~\citep{silver2016mastering} surpasses human in playing Go. 
Soon after, AlphaZero~\citep{silver2016mastering} emerged as an RL algorithm that improves over self-plays.
It quickly extended beyond Go to other games like Chess and Shogi.
In essence, the AlphaZero agent use a neural network to paramaterize the policy and the value function.
The neural network takes the current state of the game as input and outputs the probability distribution of the next move and a value of the current state.
\begin{equation}
    (\mathbf{\pi}, v) = f_{\theta}(s), \quad L(\theta) = (z - v)^2 - \mathbf{p}^T \log \mathbf{\pi} + c||\theta||^2,
\end{equation}
where $f_{\theta}$ is the neural network with parameters $\theta$, $s$ is the current state of the game, $\pi$ is the policy, $v$ is the value of the current state, and $c$ is a regularization parameter.
$\mathbf{p}$ and $z$ are the probability distribution of the next move and the outcome of the game, respectively.
They are induced by a planning algorithm, i.e., Monte Carlo Tree Search (MCTS).
The neural network $f_{\theta}$ is trained with a stochastic gradient descent algorithm to minimize $L$.
$L$ has three components.
The last term penalizes large neural network weights.
Its first two terms measure the similarity between $f_{\theta}(s)$, the learned policy and value function, with the action and game outcome planned by the MCTS.
A planning algorithm like the MCTS has to be present due to the large search space in the game of Go.

\subsection{Model-Based and Model Free RL}

\section{Problem Formulation}

\section{Numerical Experiments}

\section{Conclusion}

### 2024-05-03 project3/draft.tex
new

@@
 \begin{align} \label{eq3:lossGMMB}
-L   & = H_0 - e^{-rT} H^{bf}_T + \sum_{t=1}^{T-1} e^{-rt} HE_t + \sum_{t=1}^T e^{-rt} C_t - \sum_{t=1}^T e^{-rt} F_t\eta_n + e^{-rT} (G_t - F_t)^+ nonumber \\ 
-    & = e^{-rT} (G_T - F_{T^+})^+ + \sum_{t=1}^T e^{-rt}  \left( \Delta_{t-1} (S_{t-1} - e^{-r} S_t) + C_t - F_t\eta_n \right) \label{eq3:lossrv}
+L   & = H_0 - e^{-rT} H^{bf}_T + \sum_{t=1}^{T-1} e^{-rt} HE_t + \sum_{t=1}^T e^{-rt} C_t(\Delta_{t-1}) - \sum_{t=1}^T e^{-rt} F_t\eta_n + e^{-rT} (G_t - F_t)^+  \nonumber \\ 
+    & = e^{-rT} (G_T - F_{T^+})^+ + \sum_{t=1}^T e^{-rt}  \left( \Delta_{t-1} (S_{t-1} - e^{-r} S_t) + C_t(\Delta_{t-1}) - F_t\eta_n \right) 
 \end{align}
-where the equality holds by a rearrangement of terms and a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$, and $C_t := C \cdot S_{t-1} \cdot (|\Delta_{t-1}| + 0.01 \Delta_{t-1}^2)$ is the tranaction cost at time $t$~\cite{garleanu2013dynamic}.
+where the equality holds by a rearrangement of terms and a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$, and $C_t(\Delta_{t-1}) := C \cdot S_{t-1} \cdot (|\Delta_{t-1}| + 0.01 \Delta_{t-1}^2)$ is the tranaction cost at time $t$~\cite{garleanu2013dynamic}.
 Hence, the present liability consist of the hedging errors, the transaction costs, the net management fees, and the contract payouts.
@@
 The GMWB payout is implicitly included in $F_t\eta_n$.
+Both Equation~\ref{eq3:lossGMMB} and Equation~\ref{eq3:lossGMWB} neglect the transaction cost to liquidate the hedge portfolio at maturity.
 The discrete-time hedging problem of VAs can be conveniently formulated as an MDP, where the states, actions, transition probabilities, policies, and rewards are defined as follows.
@@
 \textbf{Policy}
+
 A policy $\pi$ determines the best action to take in a given state, i.e.,
 $$a_t \sim \pi(\cdot|\mathbf{s}_t).$$
-In a VA hedging problem the policy outputs the hedging weight $\Delta_t$ given the observed state $\mathbf{s}_t$.
+In a VA hedging problem the policy outputs the hedging weight $a_t = \Delta_t$ given the observed state $\mathbf{s}_t$.
+In the following sections, we will refer to $\Delta_t$ as the policy.
 
 \textbf{Transition Probabilities}
+
 The transition probabilities $\mathcal{P}$ represent the probability of transitioning from one state to another from taking an action.
@@
 Let $\mathcal{P}(\mathbf{s}_{t+1}|\mathbf{s}_t, a_t)$ be the probability of transitioning from state $\mathbf{s}_t$ to state $\mathbf{s}_{t+1}$ due to action $a_t$.
-Aside from the previous hedging weight $\Delta_{t-1}$, the transition probabilities are independent of the actions.
+Aside from the previous hedging weight $\Delta_{t-1}$, the transition probabilities are independent from the actions.
+Paths simulated from the transition probabilities are called trajectories (or episodes) of the MDP.
 
@@
 \begin{align}
-    \mathcal{R} & = \sum_{t=0}^{T-1} \gamma^t R_t \\
+    \mathcal{R} & = \sum_{t=1}^{T-1} \gamma^t R_t \\
     \gamma      & = e^{-r}, \nonumber
@@
 \begin{equation} \label{eq3:rewardGMWB}
-    R_t = F_{t-1}\eta_n - \Delta_{t-1} |S_{t-1} - e^{-r}S_{t}| - C_{t-1}, \quad t \in \{1,\ldots,T \}
+    R_t = F_{t-1}\eta_n - \Delta_{t-1} |S_{t-1} - e^{-r}S_{t}| - C_{t-1}(\Delta_{t-1}), \quad t \in \{1,\ldots,T \}
 \end{equation}
@@
     \begin{cases}
-    F_{t-1}\eta_n - \Delta_{t-1} |S_{t-1} - e^{-r}S_{t}| - C_{t-1},                         & t\in \{1,\ldots,T-1 \} \\
-    F_{t-1}\eta_n - \Delta_{t-1} |S_{t-1} - e^{-r}S_{t}| - C_{t-1} + (G_T - F_{T^+})^+      & t = T
+    F_{t-1}\eta_n - \Delta_{t-1} |S_{t-1} - e^{-r}S_{t}| - C_{t-1}(\Delta_{t-1}),                         & t\in \{1,\ldots,T-1 \} \\
+    F_{t-1}\eta_n - \Delta_{t-1} |S_{t-1} - e^{-r}S_{t}| - C_{t-1}(\Delta_{t-1}) + (G_T - F_{T^+})^+      & t = T
     \end{cases}
@@
 
-\subsection{From AlphaZero to Deep Hedging}
+\subsection{Model-Based RL: From AlphaZero to Deep Hedging}
 Deep reinforcement learning first attacted attentions when AlphaGo~\citep{silver2016mastering} surpasses human in playing Go. 
-Soon after, AlphaZero~\citep{silver2016mastering} emerged as an RL algorithm that improves over self-plays.
+Soon after, AlphaZero~\citep{silver2016mastering} emerged as a model-based RL algorithm that improves over self-plays.
 It quickly extended beyond Go to other games like Chess and Shogi.
@@
 \begin{equation}
-    (\mathbf{\pi}, v) = f_{\theta}(s), \quad L(\theta) = (z - v)^2 - \mathbf{p}^T \log \mathbf{\pi} + c||\theta||^2,
+    (\mathbf{\pi}, v) = f_{\theta}(s), \quad L(\theta) = - \mathbf{\pi}^{\intercal} \log(\mathbf{p}) + (z - v)^2  + c||\theta||^2,
 \end{equation}
@@
 They are induced by a planning algorithm, i.e., Monte Carlo Tree Search (MCTS).
+Since it is infeasible to efficiently simulate trajectories in the game of Go, a planning algorithm is necessary to generate expected outcomes.
 The neural network $f_{\theta}$ is trained with a stochastic gradient descent algorithm to minimize $L$.
@@
 Its first two terms measure the similarity between $f_{\theta}(s)$, the learned policy and value function, with the action and game outcome planned by the MCTS.
-A planning algorithm like the MCTS has to be present due to the large search space in the game of Go.
 
-\subsection{Model-Based and Model Free RL}
+In a typical hedging problem, the transition probabilities are independent from the hedging weights, i.e., the actions.
+This simplifies the training of the neural network as complete trajectories can be simulated without the need of a planning algorithm.
+More specifically, at any time $t$, the neural network can directly learn the policy from simulated trajectories upto maturity.
+The knowing of the model prior to maturity and the ability to move back in time makes an RL algorithm model-based~\citep{moerland2023model}.
+
+Let $(\tilde{\mathbf{s}}_0, \tilde{\Delta}_0, \tilde{\mathbf{s}}_1, \tilde{\Delta}_1, \ldots, \tilde{s}_T)$ and $\tilde{\mathcal{R}} = (R_1, \ldots, R_t)$ be a trajectory and the hedging reward of the MDP, respectively.
+The neural network $f_{\theta}$ takes the previous state and hedging weight as input and outputs the hedging weight at the current state.
+\begin{equation}
+    \mathbf{\Delta} = f_{\theta}(\mathbf{s}_0, \ldots, \mathbf{s}_T), \quad L(\theta) = \rho(L) = \rho(-\mathcal{R}) = \rho(- \sum_{t=0}^{T} \gamma^t R_t),
+\end{equation}
+where $\rho(L)$ is a convex risk measure of the total present liability $L$. 
+A common choice of $\rho$ is a CVaR.
+In practice, the neural network $f_{\theta}$ is trained to minimize the empirical CVaR over a batch of trajectories.
+
+\subsection{Model-Free RL}
 
@@
 
+All numerical experiments are run using~\cite{paszke2019pytorch}.
+
 \section{Conclusion}

### 2024-05-04 project3/draft.tex
new

@@
 This simplifies the training of the neural network as complete trajectories can be simulated without the need of a planning algorithm.
-More specifically, at any time $t$, the neural network can directly learn the policy from simulated trajectories upto maturity.
-The knowing of the model prior to maturity and the ability to move back in time makes an RL algorithm model-based~\citep{moerland2023model}.
+In contrast to AlphaZero, deep hedging~\citep{buehler2019deep} uses $f_{\theta}$ for planning, as opposed to the MCTS.
+More specifically, at any time $t$, the neural network $f_{\theta}$ serves as a model that predict possible future rewards before they are actually observed.
+This is known as model-based RL. 
+Using a model allows for planning, i.e., decision-making take place using future situations that have not been experienced by the agent.
 

### 2024-05-05 project3/draft.tex
new

@@
 Its first two terms measure the similarity between $f_{\theta}(s)$, the learned policy and value function, with the action and game outcome planned by the MCTS.
+The neural network is trained to predict the outcome of the game and the next move before they are actually observed.
+This is known as model-based RL~\citep{sutton2018reinforcement}.
+Using a model allows for planning, i.e., decision-making take place using future situations that have not been experienced by the agent.
 
 In a typical hedging problem, the transition probabilities are independent from the hedging weights, i.e., the actions.
-This simplifies the training of the neural network as complete trajectories can be simulated without the need of a planning algorithm.
-In contrast to AlphaZero, deep hedging~\citep{buehler2019deep} uses $f_{\theta}$ for planning, as opposed to the MCTS.
+This simplifies the planning of the neural network as complete trajectories can be simulated without the need of a planning algorithm.
+In contrast to AlphaZero, deep hedging~\citep{buehler2019deep} only uses $f_{\theta}$ for planning.
 More specifically, at any time $t$, the neural network $f_{\theta}$ serves as a model that predict possible future rewards before they are actually observed.
-This is known as model-based RL. 
-Using a model allows for planning, i.e., decision-making take place using future situations that have not been experienced by the agent.
-
 Let $(\tilde{\mathbf{s}}_0, \tilde{\Delta}_0, \tilde{\mathbf{s}}_1, \tilde{\Delta}_1, \ldots, \tilde{s}_T)$ and $\tilde{\mathcal{R}} = (R_1, \ldots, R_t)$ be a trajectory and the hedging reward of the MDP, respectively.

### 2024-05-05 project3/draft.tex
new

@@
 In particular, model-free RL has the potential to enhance risk management practices by developing robust strategies that can adapt in real-time.
+Some popular RL algorithms include Proximal Policy Optimization (PPO), Deep Q-Networks (DQN), and Actor-Critic methods.
 
@@
 
-\section{Review of Reinforcement Learning}
+\section{Literature Review of Reinforcement Learning}
 
@@
 The neural network $f_{\theta}$ takes the previous state and hedging weight as input and outputs the hedging weight at the current state.
-\begin{equation}
+\begin{equation} \label{eq3:deephedging}
     \mathbf{\Delta} = f_{\theta}(\mathbf{s}_0, \ldots, \mathbf{s}_T), \quad L(\theta) = \rho(L) = \rho(-\mathcal{R}) = \rho(- \sum_{t=0}^{T} \gamma^t R_t),
@@
 In practice, the neural network $f_{\theta}$ is trained to minimize the empirical CVaR over a batch of trajectories.
+It serves as a model of the hedging environment which plans according to model predictions.
+~\cite{xu2020variable} propose a deep hedging algorithm for VAs that falls into this category of model-based RL.
+A cost function is defined to minimize the expected shortfall of the total present liability.
+~\cite{carbonneau2021deep} extends the model-based approach to hedging long-term financial derivatives and compares the performance of deep hedging strategies trained with different cost functions.
+In Equation~\ref{eq3:deephedging}, the state space of the MDP contains the previous hedging weight.
+A more recent paper by~\cite{imaki2021no} proposes a new network architecture that removes the previous hedging weight from the state space by introducing a no-transaction band.
+It allows for a more efficient training of the neural network by removing the semi-recurrent problem structure.
+Despite the success of model-based RL in hedging, most studies focus on hedging different types of contracts on classical asset models, e.g., Black-Scholes model and Heston model.
+Motivated by the seminal work by~\cite{gatheral2022volatility}, there are a many subsequent works focusing on roughening the classical stochastic volatility models. 
+In the rough volatility models, the latent volatility process is modelled by a stochastic process that is rougher than the sample paths of diffusion process. 
+Among these rough volatility models, notable examples are rough Heston model and the rough Bergomi model. 
+Model-based RL struggles in a rough volatility model due to difficulties in designing a suitable cost function.~\cite{horvath2021deep} shows that a CVaR-based cost function can lead to suboptimal hedging performance in a discretized rough Bergomi model.
+The risk measure $\rho$ needs to be redesigned to account for jump risks, and it is still an open question.
+In summary, model-based RL algorithms like deep hedging do not depend on the asset model, i.e., they are \textbf{model-independent}.
+However, they are not model-free as designing a suitable cost function is necessary but challenging.
+In contrast, a model-free approach does not require a explicit design for different asset dynamics, making it more flexible and adaptable to different market conditions and more robust to model misspecification.
 
-\subsection{Model-Free RL}
+\subsection{Model-Free RL: Hedging VAs with PPO}
+
+Model-free RL algorithms learn directly from interactions with the environment.
+Predominantly, they can be categorized into two types: value-based RL and policy-based RL.
+Value-based approaches learn the value function directly from the data and derive the policy from the learned value function. 
+The value function is learned by training a DNN to approximate the value function, which quantifies the expected cumulative reward over time. 
+The policy is then derived from the learned value function by selecting the action that maximizes the value function at each state. 
+~\cite{mnih2015human} is the first paper to demonstrate the effectiveness of value-based deep reinforcement learning in training agents to play Atari games.
+To update the value function, the DNN is trained to minimize the difference between the current value function and the target value function, which is updated based on the maximum expected reward from the previous iteration.
+When trained to approximate the value function, the DNN benefits from the use of experience replay buffers, which is proposed by~\cite{lin1992self} to store and sample historical transitions and uniformly sampled during training to enhance the sample efficiency and stability of the learning process.
+~\cite{kolm2019dynamic} uses a value-based deep reinforcement learning approach to hedge European options under the Black-Scholes framework.
+
+In valued-based approaches, the value function is updated iteratively with the maximum expected reward of all possible actions, which can be computationally expensive for continuous action spaces.
+To overcome this difficulty, a policy-based approach estimates the value function before realization of the final payoff of the hedging portfolio, which is particularly useful for hedging long-term financial derivatives or VA contracts.
+Two types of policy-based approaches prevail in the literature: actor-critic and policy gradient methods.
+
+An actor-critic method designs an actor network and a critic network to learn the value function and the policy simultaneously.
+The actor network learns the policy by directly outputting the action based on the current state, while the critic network learns the value of an action by approximating the expected cumulative reward over time following the actor's policy.
+A popular actor-critic algorithm is the Deep Deterministic Policy Gradient (DDPG) algorithm proposed by~\cite{lillicrap2015continuous}, which is implemented by~\cite{xu2022delta} in hedging financial derivatives in S\&P 500 and DJIA index options.
+
+A policy gradient method uses policy gradient theorem to update the policy by performing gradient ascent with respect to the policy parameters.
+Representative algorithms include the Trust Region Policy Optimization (TRPO) algorithm proposed by~\cite{schulman2015trust} and the Proximal Policy Optimization (PPO) algorithm proposed by~\cite{schulman2017proximal}.
+~\cite{du2020deep} show that the PPO algorithm is more sample efficient and stable than the value-based approaches in training agents to hedge financial derivatives.
+The most relevant paper to our study is~\cite{chong2023pseudo}, which uses the PPO algorithm to hedge GMMB with a GMDB rider under the Black-Scholes framework.
+However, information of the underlying risk factors is leaked to the agent, which makes their study pseudo-model-free.
+To further improve the risk management of VAs under rough volatility models, we propose a model-free deep reinforcement learning approach to hedge VAs without explicit or implicit knowledge of the underlying risk factors.
 
 \section{Problem Formulation}
+
+The objective of an insurer is to find a policy $\pi$ that maximize the expected reward over time by dynamically adjusting the hedging portfolio based on the current state of the VA and the financial markets, which is equivalent to finding the policy that maximizes the value function at each state $s$.
+\begin{equation}
+    V^{\pi_{\theta}}(s_t) = \mathbb{E}\left[\sum_{t=0}^{T} \gamma^t R_{t+1} | \pi_{\theta}, s_t\right],
+\end{equation}
+where the expectation is taken over the possible sequences of states, and rewards that follow from the policy $\pi$.
+The action-value function $Q^{\pi_{\theta}}$ and the advantage function $A^{\pi_{\theta}}$ are similarly defined as in Equations~\ref{eq3:Q_pi} and~\ref{eq3:A_pi}, respectively.
+However,
+
+Denote the estimator of the andvantage function at time $t$ by $\hat{A}_{\pi_{\theta}}(s_t, a_t)$.
+In a model-free PPO approach of reinforcement learning, the agent estimates the advantage function $A^{\pi_{\theta}}$ by learning the value function with a deep neural network with parameters $\phi$, i.e.,
+\begin{equation}
+    \hat{A}_{\pi_{\theta}}(s_t, a_t) = V_{\phi}(s_t) - Q_{\phi}(s_t, a_t).
+\end{equation}
+The policy $\pi_\theta$ is also parameterized by a deep neural network with parameters $\theta$, and the policy is updated by performing gradient ascent with respect to the policy parameters to maximize an objective function that reflects the advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi$, i.e., the objective function involves the estimator $\hat{A}_{\pi}(s_t, a_t)$.
+\begin{align}
+    \max_{\theta} \mathbb{E}\left[ \min \left\{ r_t(\theta)\hat{A}^{\pi_{\theta}}(s_t, a_t), \text{clip}(r_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(s_t, a_t)  \right\} \right] \\
+    r_t(\theta) = \frac{\pi_{\theta}(a_t|s_t)}{\pi_{\theta_{old}}(a_t|s_t)} 
+\end{align}
+
+where $\theta_{old}$ denotes the policy parameters at the previous iteration, $\epsilon$ is a hyperparameter that controls the size of the policy update, and $\text{clip}(x, a, b)$ is a function that clips the value of $x$ to be within the range $[a, b]$.
+The policy is updated by performing gradient ascent with respect to the policy parameters $\theta$ to maximize the objective function, which is estimated by sampling from the environment and computing the empirical average of the objective function over the sampled trajectories.
+The first component in the objective function, $r_t(\theta) \hat{A}^{\pi_{\theta}}(s_t, a_t)$, is a surrogate objective function that approximates the advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi_{\theta_{old}}$, and the second component, $\text{clip}(r_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(s_t, a_t)$, is a clipped surrogate objective function that prevents large policy updates and ensures more stable training.
+The TRPO algorithm proposed by~\cite{schulman2015trust} uses a similar clipped surrogate objective function to ensure that the policy update does not deviate too far from the old policy, but PPO simplifies the optimization problem by using a clipped surrogate objective function instead of a hard-coded constraint on the policy update.
+Compared to TRPO, PPO is more computationally efficient and easier to implement, making it a popular choice for training deep reinforcement learning agents.
+For a in-depth discussion on the implementation details of both TRPO and PPO, we refer the reader to~\cite{engstrom2020implementation}.
+
+\begin{algorithm} 
+    \caption{PPO for Hedging Variable Annuities} 
+    \begin{algorithmic}[1] \label{alg3:ppoHedging}
+        \STATE  Initialize policy parameters $\theta_0$ and value function parameters $\phi_0$.
+        \STATE  \textbf{For} {iteration $k=0, 1,2,\ldots$} \textbf{do}
+        \STATE  \quad Collect a set of trajectories $\mathcal{D}_k$ by sampling from the environment with policy $\pi_{\theta_{k}}$.
+        \STATE  \quad Compute the rewards $\hat{R}_t$ for each trajectory in $\mathcal{D}_k$.
+        \STATE  \quad Estimates the advantage function with $\hat{A}_{\pi_{\theta_k}}(s_t, a_t)$ using value function $V_{\phi_k}$.
+        \STATE  \quad Update the policy parameters $\theta_{k+1}$ by 
+        \begin{equation*}
+            \max_{\theta} \mathbb{E}\left[ \min \left\{ r_t(\theta)\hat{A}^{\pi_{\theta}}(s_t, a_t), \text{clip}(r_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(s_t, a_t)  \right\} \right]
+        \end{equation*}
+        \STATE  \quad Update the value function parameters $\phi_{k+1}$ by minimizing the mean squared error between the predicted value and the actual collected reward.
+        \begin{equation*}
+            \phi_{k+1} = \arg \min_{\phi} \frac{1}{|\mathcal{D}_k|T} \sum_{\mathcal{\kappa} \in \mathcal{D}_k} \sum_{t=0}^{T} \left( V_{\phi}(s_t) - \hat{R}_t \right)^2
+        \end{equation*}
+        \STATE  \textbf{End For}
+    \end{algorithmic}
+\end{algorithm}
+
+In a model-free reinforcement learning approach, the agent learns the optimal policy by iteratively updating the policy and the value function based on the observed states, actions, and rewards.
+In our context of hedging VAs, the agent does not have explicit knowledge of the underlying asset price dynamics or the future mortality rates, so the future payoff of the VA is uncertain and must be learned from interactions with the environment.
 

### 2024-05-05 project3/tlHedging.tex
new

@@
 
-The objective of an insurer is to find a policy $\pi$ that maximize the expected reward () over time by dynamically adjusting the hedging portfolio based on the current state of the VA and the financial markets, which is equivalent to finding the policy that maximizes the value function at each state $s$.
+The objective of an insurer is to find a policy $\pi$ that maximize the expected reward over time by dynamically adjusting the hedging portfolio based on the current state of the VA and the financial markets, which is equivalent to finding the policy that maximizes the value function at each state $s$.
 \begin{equation}

### 2024-05-05 project3/draft.tex
new

@@
 In particular, model-free RL has the potential to enhance risk management practices by developing robust strategies that can adapt in real-time.
-Some popular RL algorithms include Proximal Policy Optimization (PPO), Deep Q-Networks (DQN), and Actor-Critic methods.
+Some popular RL algorithms include Proximal Policy Optimization (PPO), Deep Q-Networks (DQN), and Deep Deterministic Policy Gradient (DDPG).
 
@@
 
-\subsection{Model-Free RL: Hedging VAs with PPO}
+\subsection{Model-Free RL for Hedging}
 
@@
 
-\section{Problem Formulation}
+\section{Hedging VAs with a PPO Agent}
+In a hedging problem, an insurer aims to find a policy $\pi_\theta$ that maximize the expected reward over time by dynamically adjusting the hedging portfolio based on the current state of the VA and the financial markets, which is equivalent to finding the policy that maximizes the value function at each state $s$.
 
-The objective of an insurer is to find a policy $\pi$ that maximize the expected reward over time by dynamically adjusting the hedging portfolio based on the current state of the VA and the financial markets, which is equivalent to finding the policy that maximizes the value function at each state $s$.
-\begin{equation}
-    V^{\pi_{\theta}}(s_t) = \mathbb{E}\left[\sum_{t=0}^{T} \gamma^t R_{t+1} | \pi_{\theta}, s_t\right],
+\begin{equation} \label{eq3:V_pi}
+    V^{\pi_\theta}(s_t) = \mathbb{E}_{s_{t+1}, a_{t}} \left[ \sum_{t=0}^{\infty} \gamma^t R_{t+1} |\pi_\theta, s_t \right],
 \end{equation}
-where the expectation is taken over the possible sequences of states, and rewards that follow from the policy $\pi$.
-The action-value function $Q^{\pi_{\theta}}$ and the advantage function $A^{\pi_{\theta}}$ are similarly defined as in Equations~\ref{eq3:Q_pi} and~\ref{eq3:A_pi}, respectively.
-However,
+
+where $R_{t+1}$ is the reward received by the agent after taking action $a_t$ in state $s_t$ and transitioning to state $s_{t+1}$, and the expectation is taken over the possible sequences of states and rewards that follow from the policy $\pi$.
+The state-action value function, $Q^{\pi_\theta}(s_t, a_t)$, is defined as the expected cumulative reward starting from state $s_t$, taking action $a_t$, and following policy $\pi$ thereafter:
+
+\begin{equation} \label{eq3:Q_pi}
+    Q^{\pi_\theta}(s_t, a_t) = \mathbb{E}_{s_{t+1}, a_{t+1}} \left[ \sum_{t=0}^{\infty} \gamma^t R_{t+1} |\pi, s_t, a_t \right],
+\end{equation}
+
+Based on Equations~\ref{eq3:V_pi} and~\ref{eq3:Q_pi}, the advantage function, $A^{\pi}(s_t, a_t)$, is defined as the difference between the state-action value function and the state value function:
+
+\begin{equation} \label{eq3:A_pi}
+    A^{\pi_\theta}(s_t, a_t) = Q^{\pi}(s_t, a_t) - V^{\pi}(s_t).
+\end{equation}
+
+In a model-free PPO approach of reinforcement learning, the agent estimates the advantage function $A^{\pi}$ by learning the value function with a deep neural network with parameters $\phi$.
 
@@
 \begin{equation}
-    \hat{A}_{\pi_{\theta}}(s_t, a_t) = V_{\phi}(s_t) - Q_{\phi}(s_t, a_t).
+    \hat{A}^{\pi_{\theta}}(s_t, a_t) = V_{\phi}(s_t) - Q_{\phi}(s_t, a_t).
 \end{equation}
@@
 
-In a model-free reinforcement learning approach, the agent learns the optimal policy by iteratively updating the policy and the value function based on the observed states, actions, and rewards.
-In our context of hedging VAs, the agent does not have explicit knowledge of the underlying asset price dynamics or the future mortality rates, so the future payoff of the VA is uncertain and must be learned from interactions with the environment.
+In a model-free reinforcement learning approach, the agent is a trial-and-error learner that interacts with the environment to learn the optimal policy by iteratively updating the policy and the value function based on the observed states, actions, and rewards.
+For hedging VAs, the agent does not have access to a planning algorithm or a model of the underlying risk factors, and it must learn the optimal policy by directly interacting with the environment.
 
@@
 
-All numerical experiments are run using~\cite{paszke2019pytorch}.
+We present a numerical experiment to demonstrate the effectiveness of the model-free PPO algorithm for hedging VAs with transaction costs.
+We consider a VA contract with a maturity of $T=240$ months and a guaranteed minimum maturity benefit (GMMB) rider with a simulation environment described in Section~\ref{subsec:VASimulation}.
+The simulation enviornment is implemented in Python using the OpenAI Gym framework~\citep{brockman2016openai}, and the neural networks are programmed using the PyTorch library~\citep{paszke2019pytorch}.
+The environment is designed to simulate the dynamics of the VA contract and provide the agent with the current state of the VA with the contract specifications and the financial market information described in Table~\ref{tab3:hyperparameters}.
+
+\begin{table}[ht!]
+    \centering
+    \begin{tabular}{ll} 
+        \toprule
+        Hyperparameter & Value \\
+        \midrule
+        $|\mathcal{D}_k|$   & 64        \\
+        $\epsilon$          & 0.2       \\
+        Learning rate       & 0.0003    \\
+        $r$                 & 0.002     \\
+        $S_0$               & 1000      \\
+        $\mu$               & 0.00375   \\
+        $\sigma$            & 0.0457627 \\
+        $T$                 & 240       \\
+        \bottomrule
+    \end{tabular}
+    \caption{PPO Hyperparameters and GMMB Contract Specifications} 
+    \label{tab3:hyperparameters}
+\end{table}
+
+The underlying asset price $S_t$ is modeled as a geometric Brownian motion with a drift rate $\mu$ and a volatility $\sigma$.
+The weights of the value network and the policy network are initialized with orthogonal initialization~\citep{engstrom2020implementation} with scaling $\sqrt{2}$ and the bias terms set to zero.
+The value network and the policy network are implemented as fully connected neural networks with two hidden layers of 64 units each and $\tanh$ activation functions.
+They are trained using the Adam optimizer with a learning rate of $0.0003$ and a batch size automatically adjusted to the number of trajectories in the collected dataset.
+At each timestep, the observations are normalized and cliped between $-10$ and $10$ before being fed into the neural networks to stabilize the training process.
+For PPO, we follow the suggestions in~\cite{schulman2017proximal} and set the clipping hyperparameter $\epsilon$ to $0.2$ to prevent large policy updates. 
+More specifically, our implementation of the PPO uses a generalized advantage estimation~\citep{schulman2015high} to estimate the advantage function.
+The agent interacts with the environment for $10^6$ episodes, and the policy and value networks are updated every $64$ episodes and evaluated every $1000$ episodes.
+The performance of the agent is evaluated based on the average reward over an independent test set of $10^4$ episodes, and the results are compared with the benchmark hedging strategy, delta hedging.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\textwidth]{./project3/figures/loss_distribution.png}
+    \caption{Performance of PPO for Hedging GMMB Contracts on GBM Asset Model} 
+    \label{fig3:ppo_hedging}
+\end{figure}
+
+Figure~\ref{fig3:ppo_hedging} shows the performance of the PPO algorithm for hedging GMMB contracts on a geometric Brownian motion (GBM) asset model.
+The figure shows the distribution of the hedging errors incurred by the agent over the $10^4$ test episodes.
+The hedging errors are calculated as the difference between the actual cash flow incurred by the agent due to rebalancing and the expected cash flow based on the optimal hedging policy.
+The results show that the PPO algorithm is able to learn an optimal hedging policy that minimizes the hedging errors, and it surpasses the benchmark delta hedging strategy in terms of hedging performance.
 

### 2024-05-05 project3/tlHedging.tex
new

@@
 We consider a VA contract with a maturity of $T=240$ months and a guaranteed minimum maturity benefit (GMMB) rider with a simulation environment described in Section~\ref{subsec:VASimulation}.
-The simulation enviornment is implemented in Python using the OpenAI Gym framework~\citep{brockman2016openai} and PyTorch library~\citep{paszke2019pytorch}.
+The simulation enviornment is implemented in Python using the OpenAI Gym framework~\citep{brockman2016openai}, and the neural networks are programmed using the PyTorch library~\citep{paszke2019pytorch}.
 The environment is designed to simulate the dynamics of the VA contract and provide the agent with the current state of the VA with the contract specifications and the financial market information described in Table~\ref{tab3:hyperparameters}.

### 2024-05-06 project3/draft.tex
new

@@
 
-\section{Literature Review of Reinforcement Learning}
-
-\subsection{Markov Decision Process}
+\section{Markov Decision Process}
 
@@
 
-\textbf{Hedging Environment of Variable Annuities} \label{subsec:VASimulation}
+\subsection{Hedging Environment of Variable Annuities} \label{subsec:VASimulation}
 
@@
 
-\textbf{State Space}
+\subsection{State Space}
 
@@
 
-\textbf{Action Space}
+\subsection{Action Space}
 
@@
 
-\textbf{Policy}
+\subsection{Policy}
 
@@
 
-\textbf{Transition Probabilities}
+\subsection{Transition Probabilities}
 
@@
 
-\textbf{Reward and Discount Factor}
+\subsection{Reward and Discount Factor}
 The reward function $\mathcal{R}$ and discount factor $\gamma$ in a typical RL problem are defined as follows:
@@
 It is worth noting that learning to hedge GMWB is easier for an RL agent due to the absense of reward at maturity (long-term feedback).
+
+\subsection{Value Function and Advantage Function}
+
+This section introduces some critical concepts in RL, i.e., the value function and the advantage function.
+They are essential for understanding the performance of the hedging policy and the learning process of the RL agent.
+
+A value function quantifies the expected cumulative reward over time.
+The state value function, $V^{\pi}(s_t)$, is defined as the expected cumulative reward starting from state $s_t$ and following policy $\pi$ thereafter:
+
+\begin{equation} \label{eq3:V_pi}
+    V^{\pi}(s_t) = \mathbb{E} \left[ \sum_{t=0}^{\infty} \gamma^t R_t |\pi, s_t \right],
+\end{equation}
+
+where $R_t$ is the reward received by the agent after taking action $a_t$ in state $s_t$ and transitioning to state $s_{t+1}$, and the expectation is taken over the possible sequences of states and rewards that follow from the policy $\pi$.
+The state-action value function, $Q^{\pi}(s_t, a_t)$, is defined as the expected cumulative reward starting from state $s_t$, taking action $a_t$, and following policy $\pi$ thereafter:
+
+\begin{equation} \label{eq3:Q_pi}
+    Q^{\pi}(s_t, a_t) = \mathbb{E} \left[ \sum_{t=0}^{\infty} \gamma^t R_t |\pi, s_t, a_t \right],
+\end{equation}
+
+Based on Equations~\ref{eq3:V_pi} and~\ref{eq3:Q_pi}, the advantage function, $A^{\pi}(s_t, a_t)$, is defined as the difference between the state-action value function and the state value function:
+
+\begin{equation} \label{eq3:A_pi}
+    A^{\pi}(s_t, a_t) = Q^{\pi}(s_t, a_t) - V^{\pi}(s_t).
+\end{equation}
+
+The advantage function quantifies the advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi$.
+
+\section{Model-Based and Model-Free RL}
 
@@
 In summary, model-based RL algorithms like deep hedging do not depend on the asset model, i.e., they are \textbf{model-independent}.
-However, they are not model-free as designing a suitable cost function is necessary but challenging.
+However, they are not \textbf{model-free}.
+For example, deep hedging builds its own model of the hedging environment to plan the hedging strategy ahead of time using a neural network.
+Designing a suitable cost function for such a network is necessary but challenging.
 In contrast, a model-free approach does not require a explicit design for different asset dynamics, making it more flexible and adaptable to different market conditions and more robust to model misspecification.
@@
 
-Model-free RL algorithms learn directly from interactions with the environment.
-Predominantly, they can be categorized into two types: value-based RL and policy-based RL.
+In a model-free reinforcement learning approach, the agent is a trial-and-error learner that interacts with the environment to learn the optimal policy by iteratively updating the policy and the value function based on the observed states, actions, and rewards.
+For hedging VAs, the agent does not have access to a planning algorithm or a model of the underlying risk factors, and it must learn the optimal policy by directly interacting with the environment.
+Boardly speaking, model-free RL can be categorized into two types: value-based RL and policy-based RL.
 Value-based approaches learn the value function directly from the data and derive the policy from the learned value function. 
@@
 \section{Hedging VAs with a PPO Agent}
-In a hedging problem, an insurer aims to find a policy $\pi_\theta$ that maximize the expected reward over time by dynamically adjusting the hedging portfolio based on the current state of the VA and the financial markets, which is equivalent to finding the policy that maximizes the value function at each state $s$.
-
-\begin{equation} \label{eq3:V_pi}
-    V^{\pi_\theta}(s_t) = \mathbb{E}_{s_{t+1}, a_{t}} \left[ \sum_{t=0}^{\infty} \gamma^t R_{t+1} |\pi_\theta, s_t \right],
-\end{equation}
-
-where $R_{t+1}$ is the reward received by the agent after taking action $a_t$ in state $s_t$ and transitioning to state $s_{t+1}$, and the expectation is taken over the possible sequences of states and rewards that follow from the policy $\pi$.
-The state-action value function, $Q^{\pi_\theta}(s_t, a_t)$, is defined as the expected cumulative reward starting from state $s_t$, taking action $a_t$, and following policy $\pi$ thereafter:
-
-\begin{equation} \label{eq3:Q_pi}
-    Q^{\pi_\theta}(s_t, a_t) = \mathbb{E}_{s_{t+1}, a_{t+1}} \left[ \sum_{t=0}^{\infty} \gamma^t R_{t+1} |\pi, s_t, a_t \right],
-\end{equation}
-
-Based on Equations~\ref{eq3:V_pi} and~\ref{eq3:Q_pi}, the advantage function, $A^{\pi}(s_t, a_t)$, is defined as the difference between the state-action value function and the state value function:
-
-\begin{equation} \label{eq3:A_pi}
-    A^{\pi_\theta}(s_t, a_t) = Q^{\pi}(s_t, a_t) - V^{\pi}(s_t).
-\end{equation}
-
-In a model-free PPO approach of reinforcement learning, the agent estimates the advantage function $A^{\pi}$ by learning the value function with a deep neural network with parameters $\phi$.
-
-Denote the estimator of the andvantage function at time $t$ by $\hat{A}_{\pi_{\theta}}(s_t, a_t)$.
-In a model-free PPO approach of reinforcement learning, the agent estimates the advantage function $A^{\pi_{\theta}}$ by learning the value function with a deep neural network with parameters $\phi$, i.e.,
-\begin{equation}
-    \hat{A}^{\pi_{\theta}}(s_t, a_t) = V_{\phi}(s_t) - Q_{\phi}(s_t, a_t).
-\end{equation}
-The policy $\pi_\theta$ is also parameterized by a deep neural network with parameters $\theta$, and the policy is updated by performing gradient ascent with respect to the policy parameters to maximize an objective function that reflects the advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi$, i.e., the objective function involves the estimator $\hat{A}_{\pi}(s_t, a_t)$.
+In a hedging problem, an insurer aims to find a policy $\pi$ that maximize the expected reward over time.
+In a policy-based RL approach like the PPO, both the policy and the value function are parameterized by deep neural networks.
+We denote the policy by $\pi_{\theta}$ and the value function by $V_{\phi}$, where $\theta$ and $\phi$ are the parameters of the value network and the policy network, respectively.
+The policy is updated according to an objective function that reflects the advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi$.
 \begin{align}
-    \max_{\theta} \mathbb{E}\left[ \min \left\{ r_t(\theta)\hat{A}^{\pi_{\theta}}(s_t, a_t), \text{clip}(r_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(s_t, a_t)  \right\} \right] \\
-    r_t(\theta) = \frac{\pi_{\theta}(a_t|s_t)}{\pi_{\theta_{old}}(a_t|s_t)} 
+    \max_{\theta} \mathbb{E}\left[ \min \left\{ \Lambda_t(\theta)\hat{A}^{\pi_{\theta}}(s_t, a_t), \text{clip}(\Lambda_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(s_t, a_t)  \right\} \right] \\
+    \Lambda_t(\theta) = \frac{\pi_{\theta}(a_t|s_t)}{\pi_{\theta_{old}}(a_t|s_t)} 
 \end{align}
 
-where $\theta_{old}$ denotes the policy parameters at the previous iteration, $\epsilon$ is a hyperparameter that controls the size of the policy update, and $\text{clip}(x, a, b)$ is a function that clips the value of $x$ to be within the range $[a, b]$.
+where $\theta_{old}$ denotes the policy parameters at the previous iteration, $\epsilon$ is a hyperparameter that controls the size of the policy update, $\text{clip}(x, a, b)$ is a function that clips the value of $x$ to be within the range $[a, b]$, and $\hat{A}^{\pi_{\theta}}(s_t, a_t)$ is the estimated advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi_{\theta_{old}}$.
+In our implementation, the advantage function is estimated following the GAE method proposed by~\cite{schulman2015high}.
 The policy is updated by performing gradient ascent with respect to the policy parameters $\theta$ to maximize the objective function, which is estimated by sampling from the environment and computing the empirical average of the objective function over the sampled trajectories.
-The first component in the objective function, $r_t(\theta) \hat{A}^{\pi_{\theta}}(s_t, a_t)$, is a surrogate objective function that approximates the advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi_{\theta_{old}}$, and the second component, $\text{clip}(r_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(s_t, a_t)$, is a clipped surrogate objective function that prevents large policy updates and ensures more stable training.
+The first component in the objective function, $\Lambda_t(\theta) \hat{A}^{\pi_{\theta}}(s_t, a_t)$, is a surrogate objective function that approximates the advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi_{\theta_{old}}$, and the second component, $\text{clip}(\Lambda_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(s_t, a_t)$, is a clipped surrogate objective function that prevents large policy updates and ensures more stable training.
 The TRPO algorithm proposed by~\cite{schulman2015trust} uses a similar clipped surrogate objective function to ensure that the policy update does not deviate too far from the old policy, but PPO simplifies the optimization problem by using a clipped surrogate objective function instead of a hard-coded constraint on the policy update.
@@
         \begin{equation*}
-            \max_{\theta} \mathbb{E}\left[ \min \left\{ r_t(\theta)\hat{A}^{\pi_{\theta}}(s_t, a_t), \text{clip}(r_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(s_t, a_t)  \right\} \right]
+            \max_{\theta} \mathbb{E}\left[ \min \left\{ \Lambda_t(\theta)\hat{A}^{\pi_{\theta}}(s_t, a_t), \text{clip}(\Lambda_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(s_t, a_t)  \right\} \right]
         \end{equation*}
@@
 \end{algorithm}
-
-In a model-free reinforcement learning approach, the agent is a trial-and-error learner that interacts with the environment to learn the optimal policy by iteratively updating the policy and the value function based on the observed states, actions, and rewards.
-For hedging VAs, the agent does not have access to a planning algorithm or a model of the underlying risk factors, and it must learn the optimal policy by directly interacting with the environment.
 
@@
         Learning rate       & 0.0003    \\
-        $r$                 & 0.002     \\
         $S_0$               & 1000      \\
@@
         $\sigma$            & 0.0457627 \\
+        $r$                 & 0.002     \\
         $T$                 & 240       \\

### 2024-05-06 project3/draft.tex
new

@@
 
+Algorithm~\ref{alg3:ppoHedging} outlines the PPO algorithm for training an agent to hedge VAs.
+At each iteration $k$, the agent collects a set of trajectories $\mathcal{D}_k$ by interacting with the environment (Section~\ref{subsec:VASimulation}) with the current policy $\pi_{\theta_k}$.
+The agent then computes the rewards $\hat{R}_t$ for each trajectory in $\mathcal{D}_k$ and estimates the advantage function with $\hat{A}_{\pi_{\theta_k}}(s_t, a_t)$ using the value function $V_{\phi_k}$.
+The policy parameters $\theta_{k+1}$ are updated by performing gradient ascent with respect to the policy parameters to maximize the clipped surrogate objective function.
+The value function parameters $\phi_{k+1}$ are updated by minimizing the mean squared error between the predicted value and the actual collected reward.
+The agent iterates this process until convergence to learn an optimal policy for hedging VAs.
+
 \section{Numerical Experiments}

### 2024-05-06 project3/draft.tex
new

@@
 Among these rough volatility models, notable examples are rough Heston model and the rough Bergomi model. 
-Model-based RL struggles in a rough volatility model due to difficulties in designing a suitable cost function.~\cite{horvath2021deep} shows that a CVaR-based cost function can lead to suboptimal hedging performance in a discretized rough Bergomi model.
-The risk measure $\rho$ needs to be redesigned to account for jump risks, and it is still an open question.
+Model-based RL struggles in a rough volatility model due to difficulties in designing a suitable cost function.~\cite{horvath2021deep} shows that a standard implementation of deep hedging can lead to suboptimal hedging performance in a discretized rough Bergomi model.
+The CVaR-based cost function needs to be redesigned to account for jump risks, and it is still an open question.
 In summary, model-based RL algorithms like deep hedging do not depend on the asset model, i.e., they are \textbf{model-independent}.
@@
 
-where $\theta_{old}$ denotes the policy parameters at the previous iteration, $\epsilon$ is a hyperparameter that controls the size of the policy update, $\text{clip}(x, a, b)$ is a function that clips the value of $x$ to be within the range $[a, b]$, and $\hat{A}^{\pi_{\theta}}(s_t, a_t)$ is the estimated advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi_{\theta_{old}}$.
+where $\theta_{old}$ denotes the policy parameters at the previous iteration, $\epsilon$ is a clip range hyperparameter that controls the size of the policy update, $\text{clip}(x, a, b)$ is a function that clips the value of $x$ to be within the range $[a, b]$, and $\hat{A}^{\pi_{\theta}}(s_t, a_t)$ is the estimated advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi_{\theta_{old}}$.
 In our implementation, the advantage function is estimated following the GAE method proposed by~\cite{schulman2015high}.
@@
 \begin{algorithm} 
-    \caption{PPO for Hedging Variable Annuities} 
+    \caption{PPO for Hedging Variable Annuities (Not Yet Done)} 
     \begin{algorithmic}[1] \label{alg3:ppoHedging}
@@
         \STATE  \quad Compute the rewards $\hat{R}_t$ for each trajectory in $\mathcal{D}_k$.
-        \STATE  \quad Estimates the advantage function with $\hat{A}_{\pi_{\theta_k}}(s_t, a_t)$ using value function $V_{\phi_k}$.
+        \STATE  \quad Estimates the advantage function with $\hat{A}_{\pi_{\theta_k}}(\mathbf{s}_t, a_t)$ using value function $V_{\phi_k}$.
         \STATE  \quad Update the policy parameters $\theta_{k+1}$ by 
         \begin{equation*}
-            \max_{\theta} \mathbb{E}\left[ \min \left\{ \Lambda_t(\theta)\hat{A}^{\pi_{\theta}}(s_t, a_t), \text{clip}(\Lambda_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(s_t, a_t)  \right\} \right]
+            \max_{\theta} \mathbb{E}\left[ \min \left\{ \Lambda_t(\theta)\hat{A}^{\pi_{\theta}}(\mathbf{s}_t, a_t), \text{clip}(\Lambda_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(\mathbf{s}_t, a_t)  \right\} \right]
         \end{equation*}
@@
         \begin{equation*}
-            \phi_{k+1} = \arg \min_{\phi} \frac{1}{|\mathcal{D}_k|T} \sum_{\mathcal{\kappa} \in \mathcal{D}_k} \sum_{t=0}^{T} \left( V_{\phi}(s_t) - \hat{R}_t \right)^2
+            \phi_{k+1} = \arg \min_{\phi} \frac{1}{|\mathcal{D}_k|T} \sum_{\mathcal{\kappa} \in \mathcal{D}_k} \sum_{t=0}^{T} \left( V_{\phi}(\mathbf{s}_t) - \hat{R}_t \right)^2
         \end{equation*}
@@
 The agent iterates this process until convergence to learn an optimal policy for hedging VAs.
+
+\subsection{Accounting for Non-Markovian Dynamics}
+
+In the context of hedging VAs, the state space is partially observed.
+The agent does not have access to the contract specifications and the underlying risk factors.
+Furthermore, a rough volatility model introduces non-Markovian dynamics, i.e., the future state of the system depends on the entire history of the system.
+To address the non-Markovian dynamics, an LSTM component is added to the state representation $\mathbf{s}_t$ to capture the temporal dependencies in the data.
+This approach is known as recurrent PPO~\citep{ni2021recurrent}.
+Let $h_t$ be the hidden state of the LSTM at time $t$.
+The state representation $\mathbf{s}_t$ with recurrent PPO is defined as:
+\begin{equation}
+    \mathbf{s}_t = (S_t, F_t, G_t, \tau, \Delta_{t-1}, h_t)
+\end{equation}
+Instead of following the standard PPO algorithm, the agent uses the recurrent PPO algorithm to learn an optimal policy for hedging VAs.
+
+\begin{algorithm} 
+    \caption{Recurrent PPO for Hedging Variable Annuities} 
+    \begin{algorithmic}[1] \label{alg3:ppoHedging-rnn}
+        \STATE  Initialize policy parameters $\theta_0$ and value function parameters $\phi_0$.
+        \STATE  \textbf{For} {iteration $k=0, 1,2,\ldots$} \textbf{do}
+        \STATE  \quad Collect a set of trajectories $\mathcal{D}_k$ by sampling from the environment with policy $\pi_{\theta_{k}}$.
+        \STATE  \quad Compute the rewards $\hat{R}_t$ for each trajectory in $\mathcal{D}_k$.
+        \STATE  \quad Estimates the advantage function with $\hat{A}_{\pi_{\theta_k}}(\mathbf{s}_t, a_t)$ using value function $V_{\phi_k}$.
+        \STATE  \quad Update the policy parameters $\theta_{k+1}$ by 
+        \begin{equation*}
+            \max_{\theta} \mathbb{E}\left[ \min \left\{ \Lambda_t(\theta)\hat{A}^{\pi_{\theta}}(\mathbf{s}_t, a_t), \text{clip}(\Lambda_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(\mathbf{s}_t, a_t)  \right\} \right]
+        \end{equation*}
+        \STATE  \quad Update the value function parameters $\phi_{k+1}$ by minimizing the mean squared error between the predicted value and the actual collected reward.
+        \begin{equation*}
+            \phi_{k+1} = \arg \min_{\phi} \frac{1}{|\mathcal{D}_k|T} \sum_{\mathcal{\kappa} \in \mathcal{D}_k} \sum_{t=0}^{T} \left( V_{\phi}(\mathbf{s}_t) - \hat{R}_t \right)^2
+        \end{equation*}
+        \STATE  \textbf{End For}
+    \end{algorithmic}
+\end{algorithm}
 

### 2024-05-06 project3/draft.tex
new

@@
 \begin{algorithm} 
-    \caption{PPO for Hedging Variable Annuities (Not Yet Done)} 
+    \caption{PPO for Hedging Variable Annuities} 
     \begin{algorithmic}[1] \label{alg3:ppoHedging}
@@
 \begin{algorithm} 
-    \caption{Recurrent PPO for Hedging Variable Annuities} 
+    \caption{Recurrent PPO for Hedging Variable Annuities (Not Yet Done)} 
     \begin{algorithmic}[1] \label{alg3:ppoHedging-rnn}
@@
 \end{algorithm}
+
+Algorithm~\ref{alg3:ppoHedging-rnn} outlines the recurrent PPO algorithm for training an agent to hedge VAs with non-Markovian dynamics.
 

### 2024-05-06 project3/draft.tex
new

@@
 The state representation $\mathbf{s}_t$ with recurrent PPO is defined as:
-\begin{equation}
+\begin{equation} \label{eq3:stateRNN}
     \mathbf{s}_t = (S_t, F_t, G_t, \tau, \Delta_{t-1}, h_t)
 \end{equation}
+The policy and reward function remain the same but with the new state representation in Equation~\ref{eq3:stateRNN}.
 Instead of following the standard PPO algorithm, the agent uses the recurrent PPO algorithm to learn an optimal policy for hedging VAs.

### 2024-05-15 project3/draft.tex
new

@@
 Let $h_t$ be the hidden state of the LSTM at time $t$.
-The state representation $\mathbf{s}_t$ with recurrent PPO is defined as:
+The state representation $\mathbf{s}_t$ is fed into the LSTM at each time step to update the hidden state $h_t$.
 \begin{equation} \label{eq3:stateRNN}
-    \mathbf{s}_t = (S_t, F_t, G_t, \tau, \Delta_{t-1}, h_t)
+    \mathbf{s}_t = (S_t, F_t, G_t, \tau, \Delta_{t-1}), \quad h_t = \text{LSTM}(\mathbf{s}_t, h_{t-1})
 \end{equation}
+
+\begin{figure}[ht!]
+    \centering
+    \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{./project3/tikz/ppo_diagram.pdf}
+        \caption{regular PPO}
+        \label{subfig3:architecturePPO}
+    \end{subfigure}
+    \hspace{1cm}
+    \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{./project3/tikz/recurrentppo_diagram.pdf}
+        \caption{Recurrent PPO with LSTM}
+        \label{subfig3:architectureLSTMPPO}
+    \end{subfigure}
+    \caption{PPO Network Architectures} 
+    \label{fig3:architecturePPO}
+\end{figure}
+
 The policy and reward function remain the same but with the new state representation in Equation~\ref{eq3:stateRNN}.
@@
 
+Figure~\ref{fig3:architecturePPO} illustrates the network architecture of the standard PPO and the recurrent PPO with LSTM, and Algorithm~\ref{alg3:ppoHedging-rnn} outlines the recurrent PPO algorithm and for training an agent to hedge VAs with non-Markovian dynamics.
+The recurrent PPO algorithm is similar to the standard PPO algorithm, but it includes an LSTM component to capture the temporal dependencies in the data.
+However, the sequantial nature of the LSTM is not suitable for parallel computation, which slows down the training process.
+
 \begin{algorithm}
-    \caption{Recurrent PPO for Hedging Variable Annuities (Not Yet Done)} 
+    \caption{Recurrent PPO with LSTM for Hedging Variable Annuities} 
     \begin{algorithmic}[1] \label{alg3:ppoHedging-rnn}
         \STATE  Initialize policy parameters $\theta_0$ and value function parameters $\phi_0$.
+        \STATE  Initialize the LSTM layers with random weights, and set the hidden state $h_0$ to zeros.
         \STATE  \textbf{For} {iteration $k=0, 1,2,\ldots$} \textbf{do}
         \STATE  \quad Collect a set of trajectories $\mathcal{D}_k$ by sampling from the environment with policy $\pi_{\theta_{k}}$.
+        \STATE  \quad Reset the LSTM hidden state $h_0$ to zeros at the beginning of each trajectory.
         \STATE  \quad Compute the rewards $\hat{R}_t$ for each trajectory in $\mathcal{D}_k$.
@@
 \end{algorithm}
-
-Algorithm~\ref{alg3:ppoHedging-rnn} outlines the recurrent PPO algorithm for training an agent to hedge VAs with non-Markovian dynamics.
 

### 2024-05-15 project3/tikz/ppo_diagram.tex
new

\documentclass{standalone}
\usepackage{tikz}
\usetikzlibrary{positioning, shapes.geometric, arrows.meta}

\begin{document}
\begin{tikzpicture}[
    node distance=2cm and 3cm,
    every node/.style={align=center},
    block/.style={rectangle, draw, text width=5em, text centered, rounded corners, minimum height=3em},
    line/.style={draw, -{Latex[scale=1.5]}}
]

% Nodes
\node[block] (input) {State Vector $\mathbf{s}_t$};
\node[block, below=of input] (fc_layer) {Fully Connected Layer};
\node[block, below left=of fc_layer] (policy_hidden) {Policy Network $\theta$};
\node[block, below right=of fc_layer] (value_hidden) {Value Network $\phi$};
\node[block, below=of policy_hidden] (policy_output) {Policy $\pi_\theta$};
\node[block, below=of value_hidden] (value_output) {Value $V_\phi$};

% Arrows
\path[line] (input) -- (fc_layer) node[midway, left] {};
\path[line] (fc_layer) -- (policy_hidden) node[midway, left] {};
\path[line] (fc_layer) -- (value_hidden) node[midway, right] {};
\path[line] (policy_hidden) -- (policy_output) node[midway, left] {};
\path[line] (value_hidden) -- (value_output) node[midway, right] {};

\end{tikzpicture}
\end{document}

### 2024-05-15 project3/tikz/recurrentppo_diagram.tex
new

\documentclass{standalone}
\usepackage{tikz}
\usetikzlibrary{positioning, shapes.geometric, arrows.meta}

\begin{document}
\begin{tikzpicture}[
    node distance=1cm and 3cm,  % Reduced vertical spacing, keep horizontal spacing
    every node/.style={align=center},
    block/.style={rectangle, draw, text width=5em, text centered, rounded corners, minimum height=2em},
    line/.style={draw, -{Latex[scale=1.5]}}
]

% Nodes
\node[block] (input) {State Vector $\mathbf{s}_t$};
\node[block, below=of input, yshift=0cm] (lstm_layer) {LSTM Layer};
\node[block, below=of lstm_layer, yshift=0cm] (fc_layer) {Fully Connected Layer};
\node[block, below left=of fc_layer, xshift=1cm, yshift=0cm] (policy_hidden) {Policy Network $\theta$};
\node[block, below right=of fc_layer, xshift=-1cm, yshift=0cm] (value_hidden) {Value Network $\phi$};
\node[block, below=of policy_hidden, yshift=0cm] (policy_output) {Policy $\pi_\theta$};
\node[block, below=of value_hidden, yshift=0cm] (value_output) {Value $V_\phi$};

% Arrows
\path[line] (input) -- (lstm_layer) node[midway, left] {};
\path[line] (lstm_layer) -- (fc_layer) node[midway, left] {};
\path[line] (fc_layer) -- (policy_hidden) node[midway, left] {};
\path[line] (fc_layer) -- (value_hidden) node[midway, right] {};
\path[line] (policy_hidden) -- (policy_output) node[midway, left] {};
\path[line] (value_hidden) -- (value_output) node[midway, right] {};

\end{tikzpicture}
\end{document}

### 2024-05-15 project3/draft.tex
new

@@
 Its first two terms measure the similarity between $f_{\theta}(s)$, the learned policy and value function, with the action and game outcome planned by the MCTS.
-The neural network is trained to predict the outcome of the game and the next move before they are actually observed.
+The neural network is trained to fit the planned outcomes of the game.
+It stores a global solution that predicts the outcome of the game and the next move before they are actually observed.
 This is known as model-based RL~\citep{sutton2018reinforcement}.
@@
 In a typical hedging problem, the transition probabilities are independent from the hedging weights, i.e., the actions.
-This simplifies the planning of the neural network as complete trajectories can be simulated without the need of a planning algorithm.
-In contrast to AlphaZero, deep hedging~\citep{buehler2019deep} only uses $f_{\theta}$ for planning.
-More specifically, at any time $t$, the neural network $f_{\theta}$ serves as a model that predict possible future rewards before they are actually observed.
+This simplifies the planning as complete trajectories can be simulated without the need of a planning algorithm.
+In contrast to AlphaZero, deep hedging~\citep{buehler2019deep} uses the model itself to simulate the complete trajectories following the transition probabilities of the MDP.
 Let $(\tilde{\mathbf{s}}_0, \tilde{\Delta}_0, \tilde{\mathbf{s}}_1, \tilde{\Delta}_1, \ldots, \tilde{s}_T)$ and $\tilde{\mathcal{R}} = (R_1, \ldots, R_t)$ be a trajectory and the hedging reward of the MDP, respectively.
-The neural network $f_{\theta}$ takes the previous state and hedging weight as input and outputs the hedging weight at the current state.
+The neural network $f_{\theta}$ stores a global solution, i.e., it takes the previous state and hedging weight as input and outputs the hedging weight at the current state.
 \begin{equation} \label{eq3:deephedging}
-    \mathbf{\Delta} = f_{\theta}(\mathbf{s}_0, \ldots, \mathbf{s}_T), \quad L(\theta) = \rho(L) = \rho(-\mathcal{R}) = \rho(- \sum_{t=0}^{T} \gamma^t R_t),
+    \mathbf{\Delta}_t = f_{\theta}(\mathbf{s}_t), \quad L(\theta) = \rho(L) = \rho(-\mathcal{R}) = \rho(- \sum_{t=0}^{T} \gamma^t R_t),
 \end{equation}
 where $\rho(L)$ is a convex risk measure of the total present liability $L$. 
+The risk measure $\rho$ serves as a model of the MDP that 
 A common choice of $\rho$ is a CVaR.
 In practice, the neural network $f_{\theta}$ is trained to minimize the empirical CVaR over a batch of trajectories.
-It serves as a model of the hedging environment which plans according to model predictions.
-~\cite{xu2020variable} propose a deep hedging algorithm for VAs that falls into this category of model-based RL.
+In other words, planning is done through $\rho$, which measures the performance of a hedging policy over a batch of complete trajectories.
+The ability to know the future outcomes of the hedging policy before they are actually observed and the use of a risk measure to guide the training of the neural network are the key features of model-based RL.
+For hedging VAs,~\cite{xu2020variable} propose a deep hedging algorithm that falls into this category of model-based RL.
 A cost function is defined to minimize the expected shortfall of the total present liability.
@@
 For hedging VAs, the agent does not have access to a planning algorithm or a model of the underlying risk factors, and it must learn the optimal policy by directly interacting with the environment.
+Figure~\ref{fig3:RLMethods} illustrates the critical difference between model-based and model-free RL methods.
+
+\begin{figure}[ht!]
+    \centering
+    \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{./project3/tikz/modelBased.pdf}
+        \caption{Model-based RL (Deep Hedging)}
+        \label{subfig3:mbRL}
+    \end{subfigure}
+    \hspace{1cm}
+    \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{./project3/tikz/modelFree.pdf}
+        \caption{Model-free RL}
+        \label{subfig3:mfRL}
+    \end{subfigure}
+    \caption{Model-based and Model-free RL Methods}
+    \label{fig3:RLMethods}
+\end{figure}
+
 Boardly speaking, model-free RL can be categorized into two types: value-based RL and policy-based RL.
@@
 \end{equation}
+The difference between a feedforward neural network (FNN) and a LSTM network is illustrated in Figure~\ref{fig3:nn}.
 
@@
     \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{./project3/tikz/ppo_diagram.pdf}
-        \caption{regular PPO}
-        \label{subfig3:architecturePPO}
+        \includegraphics[width=\textwidth]{./project3/tikz/fnn.pdf}
+        \caption{FNN}
+        \label{subfig3:fnn}
     \end{subfigure}
@@
     \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{./project3/tikz/recurrentppo_diagram.pdf}
-        \caption{Recurrent PPO with LSTM}
-        \label{subfig3:architectureLSTMPPO}
+        \includegraphics[width=\textwidth]{./project3/tikz/lstm.pdf}
+        \caption{LSTM}
+        \label{subfig3:lstm}
     \end{subfigure}
-    \caption{PPO Network Architectures} 
-    \label{fig3:architecturePPO}
+    \caption{Neural Network Architectures}
+    \label{fig3:nn}
 \end{figure}
 
-The policy and reward function remain the same but with the new state representation in Equation~\ref{eq3:stateRNN}.
+In a LSTM, the cell state $c_t$ stores a representation of historical information up to time $t$.
+It is updated at each time step by a forget gate $f_t$, an input gate $i_t$, and an output gate $o_t$.
+
+In a recurrent PPO with LSTM, the policy and reward function remain the same but with the new state representation in Equation~\ref{eq3:stateRNN}.
 Instead of following the standard PPO algorithm, the agent uses the recurrent PPO algorithm to learn an optimal policy for hedging VAs.
-
 Figure~\ref{fig3:architecturePPO} illustrates the network architecture of the standard PPO and the recurrent PPO with LSTM, and Algorithm~\ref{alg3:ppoHedging-rnn} outlines the recurrent PPO algorithm and for training an agent to hedge VAs with non-Markovian dynamics.
-The recurrent PPO algorithm is similar to the standard PPO algorithm, but it includes an LSTM component to capture the temporal dependencies in the data.
-However, the sequantial nature of the LSTM is not suitable for parallel computation, which slows down the training process.
 
@@
 
+\begin{figure}[ht!]
+    \centering
+    \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{./project3/tikz/ppo_diagram.pdf}
+        \caption{regular PPO}
+        \label{subfig3:architecturePPO}
+    \end{subfigure}
+    \hspace{1cm}
+    \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{./project3/tikz/recurrentppo_diagram.pdf}
+        \caption{Recurrent PPO with LSTM}
+        \label{subfig3:architectureLSTMPPO}
+    \end{subfigure}
+    \caption{PPO Network Architectures} 
+    \label{fig3:architecturePPO}
+\end{figure}
+
+The recurrent PPO algorithm is similar to the standard PPO algorithm, but it includes an LSTM component to capture the temporal dependencies in the data.
+However, the sequantial nature of the LSTM is not suitable for parallel computation, which slows down the training process.
+
 \section{Numerical Experiments}
@@
         \midrule
-        $|\mathcal{D}_k|$   & 64        \\
+        $|\mathcal{D}_k|$   & 16        \\
         $\epsilon$          & 0.2       \\
-        Learning rate       & 0.0003    \\
+        Learning rate       & 0.0001    \\
         $S_0$               & 1000      \\

### 2024-05-15 project3/tikz/fnn.tex
new

\documentclass{standalone}
\usepackage{tikz}
\usetikzlibrary{positioning}

\begin{document}

\begin{tikzpicture}[scale=1, every node/.style={transform shape}]
    % Input layer
    \foreach \i in {1,2,3}
        \node[circle, draw, minimum size=6mm, inner sep=0pt] (I-\i) at (0, -\i*1.5 -1) {};
    \node[draw=none] (I-4) at (0, -6) {\vdots};
    \node[circle, draw, minimum size=6mm, inner sep=0pt] (I-5) at (0, -7.5) {};
    \node[below=0.5cm of I-5, draw=none] (ILabel) {Input};

    % Hidden layer
    \foreach \i in {1,2,3,4}
        \node[circle, draw, minimum size=6mm, inner sep=0pt] (H-\i) at (3, -\i*1.5 -0.5) {};
    \node[draw=none] (H-5) at (3, -7.5) {\vdots};
    \node[circle, draw, minimum size=6mm, inner sep=0pt] (H-6) at (3, -9) {};
    \node[below=0.5cm of H-6, draw=none] (HLabel) {Hidden};

    % Output layer
    \node[circle, draw, minimum size=6mm, inner sep=0pt] (O-1) at (6, -4.5) {};
    \node[below=3cm of O-1, draw=none] (OLabel) {Output};

    % Connect layers
    \foreach \i in {1,2,3,5}
        \foreach \j in {1,2,3,4,6}
            \draw[->] (I-\i) -- (H-\j);

    \foreach \i in {1,2,3,4,6}
        \draw[->] (H-\i) -- (O-1);

    % Add margins using transparent nodes
    \node[draw=none] (margin-top) at (0, -1) {};
    \node[draw=none] (margin-bottom) at (0, -10.5) {};
\end{tikzpicture}

\end{document}

### 2024-05-15 project3/tikz/modelBased.tex
new

\documentclass[tikz,border=10pt]{standalone}
\usepackage{tikz}
\usetikzlibrary{positioning, arrows.meta}

\begin{document}

\begin{tikzpicture}[>=Stealth, node distance=1cm and 2cm, every node/.style={draw, rectangle, minimum height=2em, minimum width=3em, text centered}]
    % Nodes
    \node (model) {Model};
    \node (planning) [below left=of model] {Planning};
    \node (policy) [below right=of model] {Policy/Value};
    \node (act) [below=2cm of model] {Act};
    \node (data) [below=1cm of act] {Data};

    % Arrows
    \draw[->] (planning) -- (policy);
    \draw[->] (policy) -- (planning);
    \draw[->] (planning) -- (act);
    \draw[->] (data) -- (policy);
    \draw[->] (model) -- (planning);
    \draw[->] (act) -- (data);

\end{tikzpicture}

\end{document}

### 2024-05-16 project3/draft.tex
new

@@
 \begin{align} \label{eq3:lossGMMB}
-L   & = H_0 - e^{-rT} H^{bf}_T + \sum_{t=1}^{T-1} e^{-rt} HE_t + \sum_{t=1}^T e^{-rt} C_t(\Delta_{t-1}) - \sum_{t=1}^T e^{-rt} F_t\eta_n + e^{-rT} (G_t - F_t)^+  \nonumber \\ 
-    & = e^{-rT} (G_T - F_{T^+})^+ + \sum_{t=1}^T e^{-rt}  \left( \Delta_{t-1} (S_{t-1} - e^{-r} S_t) + C_t(\Delta_{t-1}) - F_t\eta_n \right) 
+L   & = H_0 - e^{-rT} H^{bf}_T + \sum_{t=1}^{T-1} e^{-rt} HE_t + \sum_{t=1}^T e^{-rt} C_t - \sum_{t=1}^T e^{-rt} F_t\eta_n + e^{-rT} (G_t - F_t)^+  \nonumber \\ 
+    & = e^{-rT} (G_T - F_{T^+})^+ + \sum_{t=1}^T e^{-rt}  \left( \Delta_{t-1} (S_{t-1} - e^{-r} S_t) + C_t - F_t\eta_n \right) 
 \end{align}
-where the equality holds by a rearrangement of terms and a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$, and $C_t(\Delta_{t-1}) := C \cdot S_{t-1} \cdot (|\Delta_{t-1}| + 0.01 \Delta_{t-1}^2)$ is the tranaction cost at time $t$~\cite{garleanu2013dynamic}.
+where the equality holds by a rearrangement of terms and a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$, and $C_t := C \cdot S_{t-1} \cdot |\Delta_t - \Delta_{t-1}|$ is the tranaction cost at time $t$~\citep{garleanu2013dynamic}.
 Hence, the present liability consist of the hedging errors, the transaction costs, the net management fees, and the contract payouts.
@@
 
-The underlying asset price $S_t$ is modeled as a geometric Brownian motion with a drift rate $\mu$ and a volatility $\sigma$.
+The underlying asset price $S_t$ is modeled as a geometric Brownian motion (GBM) with a drift rate $\mu$ and a volatility $\sigma$.
 The weights of the value network and the policy network are initialized with orthogonal initialization~\citep{engstrom2020implementation} with scaling $\sqrt{2}$ and the bias terms set to zero.
-The value network and the policy network are implemented as fully connected neural networks with two hidden layers of 64 units each and $\tanh$ activation functions.
-They are trained using the Adam optimizer with a learning rate of $0.0003$ and a batch size automatically adjusted to the number of trajectories in the collected dataset.
+The value network and the policy network are implemented as fully connected neural networks with two hidden layers of 16 units each and $\tanh$ activation functions.
+They are trained using the Adam optimizer with a learning rate of $0.0001$ and a batch size automatically adjusted to the number of trajectories in the collected dataset.
 At each timestep, the observations are normalized and cliped between $-10$ and $10$ before being fed into the neural networks to stabilize the training process.
@@
 More specifically, our implementation of the PPO uses a generalized advantage estimation~\citep{schulman2015high} to estimate the advantage function.
-The agent interacts with the environment for $10^6$ episodes, and the policy and value networks are updated every $64$ episodes and evaluated every $1000$ episodes.
+The agent interacts with the environment for $10^5$ episodes, and the policy and value networks are evaluated every $1000$ episodes.
 The performance of the agent is evaluated based on the average reward over an independent test set of $10^4$ episodes, and the results are compared with the benchmark hedging strategy, delta hedging.
@@
 
-Figure~\ref{fig3:ppo_hedging} shows the performance of the PPO algorithm for hedging GMMB contracts on a geometric Brownian motion (GBM) asset model.
+Figure~\ref{fig3:ppo_hedging} shows the performance of the PPO algorithm for hedging GMMB contracts on a GBM asset model.
 The figure shows the distribution of the hedging errors incurred by the agent over the $10^4$ test episodes.

### 2024-05-16 project3/tikz/fnn.tex
new

@@
 
-\begin{tikzpicture}[scale=1, every node/.style={transform shape}]
+\begin{tikzpicture}[scale=1, 
+    font=\sf \scriptsize, every node/.style={transform shape}]
     % Input layer
@@
     \foreach \i in {1,2,3,4}
-        \node[circle, draw, minimum size=6mm, inner sep=0pt] (H-\i) at (3, -\i*1.5 -0.5) {};
-    \node[draw=none] (H-5) at (3, -7.5) {\vdots};
-    \node[circle, draw, minimum size=6mm, inner sep=0pt] (H-6) at (3, -9) {};
+        \node[circle, draw, minimum size=6mm, inner sep=0pt] (H-\i) at (5, -\i*1.5 -0.5) {}; % Adjusted x-coordinate to 5
+    \node[draw=none] (H-5) at (5, -7.5) {\vdots}; % Adjusted x-coordinate to 5
+    \node[circle, draw, minimum size=6mm, inner sep=0pt] (H-6) at (5, -9) {}; % Adjusted x-coordinate to 5
     \node[below=0.5cm of H-6, draw=none] (HLabel) {Hidden};
@@
     % Output layer
-    \node[circle, draw, minimum size=6mm, inner sep=0pt] (O-1) at (6, -4.5) {};
+    \node[circle, draw, minimum size=6mm, inner sep=0pt] (O-1) at (10, -4.5) {}; % Adjusted x-coordinate to 10
     \node[below=3cm of O-1, draw=none] (OLabel) {Output};

### 2024-05-16 project3/draft.tex
w

@@
 It allows for a more efficient training of the neural network by removing the semi-recurrent problem structure.
+
 Despite the success of model-based RL in hedging, most studies focus on hedging different types of contracts on classical asset models, e.g., Black-Scholes model and Heston model.
@@
 However, they are not \textbf{model-free}.
-For example, deep hedging builds its own model of the hedging environment to plan the hedging strategy ahead of time using a neural network.
-Designing a suitable cost function for such a network is necessary but challenging.
+For example, deep hedging builds its own model of the hedging environment to plan the hedging strategy ahead of time using a neural network and a risk measure.
+Designing a suitable risk measure for such a network is necessary but challenging.
 In contrast, a model-free approach does not require a explicit design for different asset dynamics, making it more flexible and adaptable to different market conditions and more robust to model misspecification.
@@
 \end{figure}
+
+A model-based RL uses a model of the environment that enables decision-making with future situations that have not been experienced by the agent.
+However, the model bias can lead to suboptimal performance in the real environment.
+In contrast, a model-free RL learns directly from the environment without relying on a model, which makes it more flexible and robust to model misspecification.
+Model-free RL algorithms gain its popularity in robotics tasks, where transition probabilities in the environment are unknown and can be affected by the agent's actions.
+In the context of hedging, existing studies use transaction costs as a function of the hedging weights, which makes the transition probabilities independent on the actions.
+However, the trade size can affect the asset price in a real environment~\citep{hasbrouck1991measuring}, which makes the model-free approach a promising direction for hedging VAs in the real market.
 
@@
 The agent interacts with the environment for $10^5$ episodes, and the policy and value networks are evaluated every $1000$ episodes.
-The performance of the agent is evaluated based on the average reward over an independent test set of $10^4$ episodes, and the results are compared with the benchmark hedging strategy, delta hedging.
+The performance of the agent is evaluated based on the average reward over an independent test set of $10^3$ episodes, and the results are compared with the benchmark hedging strategy, delta hedging.
 
-\begin{figure}
+\begin{figure}[ht!]
     \centering
-    \includegraphics[width=0.8\textwidth]{./project3/figures/loss_distribution.png}
-    \caption{Performance of PPO for Hedging GMMB Contracts on GBM Asset Model} 
-    \label{fig3:ppo_hedging}
+    \includegraphics[width=\textwidth]{./project3/figures/PPO_DH.png}
+    \caption{Hedging performance of recurrent PPO and deep hedging}
+    \label{fig3:ppo_dh}
 \end{figure}
 
-Figure~\ref{fig3:ppo_hedging} shows the performance of the PPO algorithm for hedging GMMB contracts on a GBM asset model.
-The figure shows the distribution of the hedging errors incurred by the agent over the $10^4$ test episodes.
-The hedging errors are calculated as the difference between the actual cash flow incurred by the agent due to rebalancing and the expected cash flow based on the optimal hedging policy.
-The results show that the PPO algorithm is able to learn an optimal hedging policy that minimizes the hedging errors, and it surpasses the benchmark delta hedging strategy in terms of hedging performance.
+This experiment compares the hedging performance of the recurrent PPO agent with LSTM and the deep hedging algorithm proposed by~\cite{buehler2019deep} for hedging VAs with a GMMB rider.
+The experiment is conducted with the same simulation budget.
+
+\begin{figure}[ht!]
+    \centering
+    \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/PPOs_GBM.png}
+        \caption{GBM}
+    \end{subfigure}
+    \hspace{1cm}
+    \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/PPOs_GBMRS.png}
+        \caption{Regime-switching GBM}
+    \end{subfigure}
+    \caption{Hedging performance of standard PPO and recurrent PPO} 
+    \label{fig3:ppo_result}
+\end{figure}
+
+Figure~\ref{fig3:ppo_result} illustrates the hedging performance of the standard PPO and the recurrent PPO with LSTM for hedging VAs with transaction costs $C=0.005$.
+The figures show the distributions of the hedging errors incurred by the agents over the $10^3$ test episodes for the GBM and the regime-switching GBM asset models.
+For both asset models, the recurrent PPO outperforms the standard PPO in terms of hedging performance.
+For the regime-switching GBM, the 95\%-VaR of hedging errors of the recurrent PPO and the standard PPO are $136.24$ and $147.14$, respectively.
+The hedging errors of the recurrent PPO are more concentrated around zero, indicating that historical information captured by the LSTM component helps the agent make better hedging decisions even in the enviornment is Markovian.
+
+\begin{figure}[ht!]
+    \centering
+    \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/PPO_cost_001.png}
+        \caption{$C = 0.001$}
+    \end{subfigure}
+    \hspace{1cm}
+    \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/PPO_cost_02.png}
+        \caption{$C = 0.02$}
+    \end{subfigure}
+    \caption{Hedging performance of recurrent PPO and delta hedging with different transaction costs} 
+    \label{fig3:ppo_cost}
+\end{figure}
+
+Figure~\ref{fig3:ppo_cost} shows the hedging performance of the recurrent PPO agent and the delta hedging strategy with different transaction costs when the asset model is a GBM.
+The experiment is conducted with transaction costs of $C=0.001$ and $C=0.02$.
+The delta hedging strategy is implemented with the Black-Scholes delta.
+When the transaction cost is low, the delta hedging strategy outperforms the recurrent PPO agent.
+However, as the transaction cost increases, delta hedging becomes less effective, and the recurrent PPO agent is able to learn from the environment and adapt its hedging strategy to minimize the hedging errors.
+
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=\textwidth]{./project3/figures/PPO_anchor.png}
+    \caption{Hedging performance of recurrent PPO with or without anchor}
+    \label{fig3:ppo_anchor}
+\end{figure}
+
+Figure~\ref{fig3:ppo_anchor} illustrates the hedging performance of the recurrent PPO agent with and without the model information of the underlying asset model and the current value of the liability.
+The experiment is conducted for the GBM asset model with transaction costs of $C=0.005$.
+The results show that the agent with the model information does not outperform the agent without the model information.
+
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=\textwidth]{./project3/figures/PPO_GMWB.png}
+    \caption{Hedging performance of recurrent PPO with GMWB}
+    \label{fig3:ppo_GMWB}
+\end{figure}
+
+Figure~\ref{fig3:ppo_GMWB} illustrates the hedging performance of the recurrent PPO agent for hedging VAs with a GMWB rider.
+The experiment is conducted with the same hyperparameters as the experiment with the GMMB rider.
+Unlike the GMMB rider, the PPO agent struggles to learn an optimal hedging strategy for the VA with a GMWB rider.
+The hedging errors of the PPO agent are more dispersed, indicating that more training episodes are needed to achieve a satisfactory hedging performance.
+The results suggest that the GMWB rider introduces additional complexity to the hedging problem, and the model-free RL algorithm is not sample efficient.
 

### 2024-09-26 conclusion.tex
new

\chapter{Conclusion} \label{chap:conclusion}

In this thesis, we have discussed the use of nested simulation procedures for risk management applications of financial derivatives and insurance products.

### 2024-09-26 introduction.tex
new

@@
 Quantitative risk management is a key component of modern financial systems, ensuring the stability and resilience of markets, institutions, and portfolios against an array of risks. 
-For financial products like option portfolios and variable annuity contracts, traditional risk assessment methods often fall short in accurately capturing the complex dynamics of the underlying risk factors.
+For financial products like option portfolios and variable annuity (VA) contracts, traditional risk assessment methods often fall short in accurately capturing the complex dynamics of the underlying risk factors.
+VA contracts are a popular type of complex insurance product that is linked to the performance of underlying assets, providing a guaranteed minimum income benefit to the policyholder.
 This is where advanced Monte Carlo simulation techniques, particularly nested simulation procedures, become indispensable.
 In contrast to finite-difference methods, a Monte Carlo simulation scheme is more flexible and can be easily adapted to model tail risk with a rule-based design.
+~\cite{glasserman2004monte} provide a comprehensive overview of nested simulation methods in financial engineering and risk management applications.
 In this thesis, we focus on building and analyzing nested simulation procedures for risk management applications of financial derivatives and insurance products.
@@
 For example, estimating the value of an exotic option at a risk horizon requires simulation given a realization of the underlying assets upto that horizon.
-A standard nested simulation procedure consists of two levels of simulation: the outer level simulates the underlying risk factors, while the inner level estimates the value of interest with the inner sample mean from another level of Monte Carlo simulation.
+A standard nested simulation procedure consists of two levels of simulation: the outer-level simulation generates the underlying risk factors, while the inner-level simulation estimates the value of interest with the inner sample mean from another level of Monte Carlo simulation.
 The nested structure allows for accurate estimation given sufficient computational resources, but it also introduces additional complexity in the simulation design and implementation.
-% ~\cite{gordy2010nested} investigate the standard nested simulation method for estimating tail risk measures of financial portfolios and provide an optimal resource allocation strategy for nested simulation.
+Furthermore, in real-world applications, the computational burden of nested simulation can be prohibitive due to its nested structure.
+The number of inner simulations required to achieve a desired level of accuracy for each outer scenario can be prohibitively large.
+Metamodeling techniques that approximate the inner simulation model can be used to reduce the computational burden of nested simulation.
+Metamodels are statistical models that approximate the output of a complex simulation model as a function of its input parameters.
+In this thesis, we focus on metamodels of the inner simulation models in nested simulation procedures for risk management applications of financial derivatives and VA contracts.
+Two interesting problems that requires nested simulation are considered in this thesis: (1) estimating the risk of a portfolio of financial options and (2) dynamic hedging of VA contracts with a delta hedging strategy.
+The risk management of VAs is a challenging problem due to the complex interactions between the policyholder's behavior, the financial market dynamics, and the insurer's risk management strategies.
+% Moreover, the risk management of VAs is further complicated by transaction costs, which often makes delta hedging strategies insufficient. 
+% This thesis discusses a particular extension of using deep reinforcement learning to dynamically hedge VA contracts with transaction costs.
+
+This thesis consists of four chapters.
+Chapter \ref{chap:project1} summarizes theoretical convergence results of several state-of-the-art single-period nested simulation procedures under the same analytical framework.
+Numerical experiments are conducted to test their empirical convergence behavior under finite budget sizes.
+Chapter \ref{chap:project2} proposes the use of neural network models as proxies for a two-stage multi-period nested simulation procedure on VA contracts. 
+In our numerical experiment, the best neural network proxy surpasses the state-of-the-art proxy model in tail identification, and it leads to substantial computational savings. 
+Chapter \ref{chap:project3} conducts sensitivity testing on the neural network proxy.
+We argue that for estimating tail risk measures of VA contact losses, the inner simulation can be replaced entirely by a suitable proxy model.
+Eliminating the inner simulation can lead to more substantial computational savings without affecting estimation quality. 
+In the case of requiring extensive inner simulations for regulatory purposes, effective budget allocations can help achieve higher estimator quality with the same computational budget.
+Chapter \ref{chap:conclusion} concludes the thesis and discusses potential future research directions.
+
+\section{Metamodeling for Monte Carlo Simulation Scheme}
+
+\section{Machine Learning for Risk Management Applications}
+
+Machine learning (ML) algorithms are essential tools for identifying complex patterns and relationships in data. 
+In particular, they are well-suited for handling non-linearities and large-scale data structures, which are challenging for traditional statistical methods. 
+In the context of risk management, ML algorithms have been widely used for predicting financial time series, estimating risk measures, and optimizing trading strategies.
+ML algorithms can be broadly categorized into supervised learning, unsupervised learning, and reinforcement learning.
+This section focuses on three widely used supervised learning models and two reinforcement learning algorithms that are relevant to risk management applications.
+
+\subsection{Supervised Learning Models}
+
+Supervised learning is a fundamental approach in machine learning where the algorithm learns a mapping from inputs to outputs based on example input-output pairs \cite{galton1886regression}. 
+In this paradigm, a model is trained on a labeled dataset, which means that each training example is associated with an output label or value. 
+The goal is to learn a general rule that maps inputs (also known as features) to outputs (also known as target), enabling the model to make accurate predictions on new, unseen data.
+
+\begin{itemize} 
+    \item \textbf{Classification}: The output variable is categorical, and the task is to assign inputs to one of several predefined categories. 
+    Common use in finance and actuarial applications are fraud detection and credit scoring.
+    \item \textbf{Regression}: The output variable is continuous, and the task is to predict a real-valued number. 
+    Examples in actuarial applications include predicting claim amounts, reserve estimates, and asset prices.
+\end{itemize}
+
+This thesis focuses on regression models for risk management applications, where the goal is to predict a continuous target variable based on one or more input features.
+Given a dataset of $n$ observations $\{(x_1, y_1), (x_2, y_2), \ldots, (x_n, y_n)\}$, where $x_i \in \mathbb{R}^d$ is the $d$-dimensional input feature vector and $y_i \in \mathbb{R}$ is the target variable, a supervised learning algorithm aims to learn a function $f: \mathbb{R}^d \rightarrow \mathbb{R}$ that best predicts the target variable $y$ given the input features $x$.
+
+Linear regression, kernel regression, neural network algorithms all fall under the supervised learning category and are widely used in risk management applications.
+Nevertheless, all supervised learning models can be evaluated on a similar set of metrics.
+The learning process involves minimizing a loss function $l(f(x),y)$ over the training data, which quantifies the difference between the predicted outputs and the true outputs. 
+A common loss function for regression problems is the mean squared error (MSE):
+
+\begin{equation}
+    \text{MSE} = \frac{1}{n} \sum_{i=1}^{n} (f(x_i) - y_i)^2.
+\end{equation}
+
+In most risk management applications, a critical task of users of supervised learning models is to design a suitable loss function that aligns with the objectives of the problem.
+Another important consideration is the choice of a suitable supervised learning algorithm.
+The choice may vary based on the complexity of the relationship, the interpretability of the model, and the computational resources available.
+In the following sections, we discuss three widely used supervised learning models in risk management applications: traditional regression and two neural network architectures.
+
+\subsection{Regression Models}
+
+Regression models are the most common supervised learning algorithms used in risk management applications.
+A regression model predicts a continuous target variable based on one or more input features.
+Linear regression is a simple and interpretable model that attempts to predict a target variable as a linear combination of input features. 
+It assumes a linear relationship between the dependent variable and one or more independent variables. 
+This method has been thoroughly explored in statistical literature, with \citet{bishop2006pattern} providing an extensive treatment of regression techniques in the broader context of machine learning.
+It is known as parametric regression because it assumes a specific functional form for the input-output relationship with a finite set of parameters~\citep{seber2012linear}.
+General form of a parametric regression model is given by:
+\begin{equation}
+    y = \beta_0 + \sum_{j=1}^{p} \beta_j \phi_j(x) + \epsilon,
+\end{equation}
+where $\epsilon$ is the error term, $p$ is the number of features, $\beta_0, \beta_1, \ldots, \beta_p$ are the trainable regression coefficients, and $\phi_j(x)$ are basis functions that transfrom the input $x$ to allow for non-linear modeling.
+Basis functions can be any functions of $x$ that are chosen to capture the underlying structure of the data.
+Common choices include polynomial basis functions: $\phi_j(x) = x^j$ and Laguerre basis functions: $\phi_j(x) = e^{-x/2} L_j(x)$, where $L_j(x)$ are the Laguerre polynomials that are solutions to the Laguerre differential equation~\citep{szeg1939orthogonal}.
+The training of parametric regression refers to the process of estimating the regression coefficients $\beta_0, \beta_1, \ldots, \beta_p$ that minimize the loss function.
+For a MSE loss, the optimal regression coefficients can be obtained by solving the normal equations.
+Parametric regression is a powerful tool for modeling linear relationships where the basis functions are known from expert knowledge for explicit feature engineering techniques~\citep{hastie2009elements}.
+These techniques utilize predefined functional forms to model the relationship between independent variables and the dependent variable. 
+However, when data exhibits complex, non-linear relationships, linear models fall short. 
+While these methods are straightforward and interpretable, they impose strong assumptions about the underlying data structure.
+Often, expert knowledge is required to select the appropriate basis functions, which can limit the flexibility of the model.
+Extensions like polynomial regression and generalized linear models (GLMs) have been introduced to capture non-linearity, though these models can still be limited in capturing highly complex patterns.
+To overcome these limitations, non-parametric methods such as kernel regression \citep{hastie2009elements} are often employed. 
+Kernel regression estimates the function $f(x)$ by averaging the target variable over a local neighborhood of the input $x$.
+The kernel regression with the Nadaraya-Watson estimator is given by:
+\begin{equation}
+    \hat{f}(x) = \frac{\sum_{i=1}^{n} K\left(\frac{x-x_i}{h}\right) y_i}{\sum_{i=1}^{n} K\left(\frac{x-x_i}{h}\right)},
+\end{equation}
+where $K(\cdot)$ is the kernel function, which assigns weights to the data points based on their distance to the input $x$, and $h$ is the bandwidth parameter that controls the smoothness of the estimated function.
+The objective is to estimate the function $f(x)$ directly from the data without imposing a specific form, hence, when the true relationship between variables is complex or unknown.
+However, they come with several drawbacks that limit their effectiveness, especially in high-dimensional settings or when dealing with large datasets. 
+One of the most significant drawbacks of non-parametric regression is the \textbf{curse of dimensionality} \cite{bellman1966dynamic}. 
+As the number of features increases, the volume of the input space grows exponentially, making the data sparse and leading to overfitting.
+In addition, the computational cost of non-parametric methods often grows rapidly with the number of dimensions, making them impractical for high-dimensional data. 
+These limitations have motivated the adoption of neural networks, which can address many of the challenges associated with non-parametric approaches.
+
+\subsection{Neural Network Architectures}
+
+The progression from traditional regression methods to neural network architectures has been driven by the need to model increasingly complex and high-dimensional data.
+The limitations of parametric and non-parametric regression models in capturing complex patterns have led to the rise of neural networks as a powerful tool for learning non-linear relationships in data.
+Neural networks have emerged as powerful tools capable of overcoming many limitations of traditional regression methods. 
+They can learn complex, non-linear relationships in data without the need for explicit feature engineering.
+The most crude form of a neural network is the feedforward neural network, which consists of an input layer, one or more hidden layers, and an output layer.
+
+\subsection{Reinforcement Learning}
+Reinforcement learning (RL) is a machine learning technique that learns a policy by interacting with an environment and receiving feedback in the form of rewards.
+In a dynamic heding problem, the policy is a trading strategy that minimizes the risk of the hedged portfolio, the environment contains the financial market dynamics and the contract terms, and the rewards are the negative hedging errors or a risk measure of the hedging portfolio.

### 2024-09-26 project1/nsSurvey.tex
new

@@
 %======================================================================
-\chapter{Nested Simulation Procedures in Financial Engineering: A Selected Review}
+\chapter{Nested Simulation Procedures in Financial Engineering: A Selected Review} \label{chap:project1}
 %======================================================================
@@
 ~\cite{gordy2010nested} are the first to analyze and propose the optimal budget allocation of a standard nested simulation procedure. 
-The term \textit{standard} refers to using a standard Monte Carlo estimator, the sample mean of the inner replication to estimate a scenario-wise portfolio loss for an outer scenario.
-~\cite{gordy2010nested} investigate the optimal budget allocation for a standard nested simulation procedure with respect to the mean squared error (MSE) of the estimated risk measure.
+The term \textit{standard} refers to using a standard MC estimator, the sample mean of the inner replication to estimate a scenario-wise portfolio loss for an outer scenario.
+~\cite{gordy2010nested} investigate the optimal budget allocation for a standard nested simulation procedure with respect to the MSE of the estimated risk measure.
 
@@
 This is referred to as pooling. 
-Different methods pool in different ways, either by a trained proxy model or by pre-defined likelihood ratio weights.
-~\cite{broadie2015risk} propose a regression-based nested simulation procedure, which uses a trained regression proxy model to estimate the scenario-wise portfolio loss for an outer scenario by pooling the inner replications from all outer scenarios.
+Different methods pool in different ways, either by a trained metamodel or by pre-defined likelihood ratio weights.
+~\cite{broadie2015risk} propose a regression-based nested simulation procedure, which uses a trained regression metamodel to estimate the scenario-wise portfolio loss for an outer scenario by pooling the inner replications from all outer scenarios.
 For risk measures in certain forms,~\cite{broadie2015risk} show that it is optimal to allocate all simulation budget to the outer level simulation, and the inner replication should be kept to a minimum of $1$.
-Similarly,~\cite{hong2017kernel},~\cite{feng2020optimal}, and~\cite{zhang2022sample} use a kernel smoothing model, a likelihood ratio model, and a kernel ridge regression model as proxies to pool the inner replications from all outer scenarios.
+Similarly,~\cite{hong2017kernel},~\cite{feng2020optimal}, and~\cite{zhang2022sample} use a kernel smoothing model, a likelihood ratio model, and a kernel ridge regression (KRR) model as metamodels to pool the inner replications from all outer scenarios.
 In simulation studies, this approach of using a model of a simulation model is known as metamodeling, and the models of a simulation model are also referred to as metamodels~\citep{barton1998simulation}.
@@
 Their asymptotic convergence results are closely examined for their assumptions that guarantee the convergence.
-Furthermore, our study finds that different studies propose different examples in their numerical experiments, which introduces unfair advantages for certain simulation procedures over others. 
+Furthermore, the existing literature chooses different performance metrics to evaluate the asymptotic convergence of nested simulation procedures.
+In this chapter, we discuss the asymptotic convergence of nested simulation procedures in terms of the MSE of the estimator, and we provide a comprehensive comparison of their convergence rates and critical assumptions.
+We also discuss the connection between the MSE and the absolute error of the estimator in the context of nested simulation procedures.
+
+In terms of finite-sample performance, this chapter shows that different studies propose different examples in their numerical experiments, which introduces unfair advantages for certain simulation procedures over others.
 A fair comparison among popular methods is therefore urgently needed in the literature. 
@@
 With our numerical examples, we compare the nested simulation procedures for different payoff complexity, problem dimensions, and risk measures. 
+This chapter also provides a discussion on the computational complexity of different nested simulation procedures, including additional computational costs for training metamodels and pooling inner replications.
 
 The rest of the paper is organized as follows.
-Section~\ref{sec1:problem-formulation} introduces the nested simulation procedure and the standard Monte Carlo estimator.
+Section~\ref{sec1:problem-formulation} introduces the nested simulation procedure and the standard MC estimator.
 Section~\ref{sec1:asymptotic-convergence} provides new theoretical results on the convergence of existing nested simulation procedures.
@@
 
-where $h: \mathbb{R} \rightarrow \mathbb{R}$ is a known function. 
+where $h: \mathbb{R} \rightarrow \mathbb{R}$ is a known nonlinear function. 
 Common forms of $h$ includes smooth functions, Lipschitz continuous functions, and indicator functions.
@@
     A function $h: \mathbb{R} \rightarrow \mathbb{R}$ is smooth if it is continuously differentiable up to the $n$-th order for some $n \in \mathbb{N}$, 
-    and its $n$-th and $(n-m)$-th derivatives are bounded for some $m \in \mathbb{N}$ and $m < n$.
+    and its $n$-th and $m$-th derivatives are bounded for some $m \in \mathbb{N}$ and $m < n$.
 \end{definition}
@@
     \midrule
-    Regression & $2$ & $0$ \\
-    Kernel smoothing & $3$ & $1$ \\
+    Regression & $2$ & $2$ \\
+    Kernel smoothing & $3$ & $2$ \\
     Kernel ridge regression & $2$ & $1$ \\
@@
 
-Other risk measures of interest that are not in the nested expectation form are the value at risk (VaR) and the conditional value at risk (CVaR). 
+Other risk measures of interest that are not in the nested expectation form are the value at risk (VaR) and the conditional value at risk(CVaR)~\citep{hardy2022quantitative}. 
 The $\alpha$-VaR of $L$ is defined as
-$$
+\begin{equation} \label{eq1:var}
     \mbox{VaR}_\alpha(L) = q_\alpha = \inf \left\{ q: \Pr(L\leq q) \geq \alpha \right\}.
-$$
+\end{equation}
+
 The $\alpha$-CVaR of $L$ is defined as
-$$
+\begin{equation} \label{eq1:cvar}
     \mbox{CVaR}_\alpha(L) =\frac{1}{1-\alpha} \int_{\alpha}^{1} q_v dv. 
-$$
+\end{equation}
+Other names of CVaR include Conditional Tail Expectation (CTE), Tail Value-at-Risk (TailVaR), and Expected Shortfall (ES).
 
@@
 
-The standard nested simulation procedure estimates $L_i = L(X_i)$ with a standard Monte Carlo estimator
+The standard nested simulation procedure estimates $L_i = L(X_i)$ with a standard MC estimator
 
@@
             $$\hat{\rho}_{M, N} = \hat{L}_{(\lceil \alpha M \rceil)}$$
-    \item   Conditional value at risk (CVaR):
-            $$\hat{\rho}_{M, N} = \hat{L}_{(\lceil \alpha M \rceil)} + \frac{1}{(1-\alpha) M} \sum_{i=1}^M \max \{\hat{L}_{N, i} - \hat{L}_{(\lceil \alpha M \rceil)}, 0 \}$$
+    \item   CVaR:
+            \begin{equation} \label{eq1:cvar-hat}
+                \hat{\rho}_{M, N} = \hat{L}_{(\lceil \alpha M \rceil)} + \frac{1}{(1-\alpha) M} \sum_{i=1}^M \max \{\hat{L}_{N, i} - \hat{L}_{(\lceil \alpha M \rceil)}, 0 \}
+            \end{equation}
 \end{enumerate}
@@
 
-The multi-level Monte Carlo (MLMC) method is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest, and it uses the difference between the approximations to reduce the variance of the estimator.
-The MLMC method is particularly useful when the quantity of interest is expensive to evaluate, and the standard Monte Carlo estimator has a high variance.
-The MLMC method estimates $\rho$ with a multi-level Monte Carlo estimator:
+The MLMC method is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest, and it uses the difference between the approximations to reduce the variance of the estimator.
+The MLMC method is particularly useful when the quantity of interest is expensive to evaluate, and the standard MC estimator has a high variance.
+The MLMC method estimates $\rho$ with a MLMC estimator:
 
@@
 
-\subsection{Supervised Learning Models}
-
-Supervised learning-based nested simulation procedures treat the estimation of $L(\cdot)$ as a supervised learning problem. 
-In supervised learning, $L(\cdot)$ can be approximated by $\hat{L}^{\text{SL}}_{M, N}(\cdot)$, which is based on a chosen function family and observations from the standard nested simulation procedure.
+\subsection{Supervised Learning Metamodels}
+
+Supervised learning-based nested simulation procedures treat the inner simulation model $L(\cdot)$ as a black-box function, and they approximate $L(\cdot)$ with supervised learning metamodels.
+In this metamodeling approach, $L(\cdot)$ can be approximated by $\hat{L}^{\text{SL}}_{M, N}(\cdot)$, which is based on a chosen function family and observations from the standard nested simulation procedure.
 Consider the observation pairs $(X_i, \hat{L}_{N, i})$ for $i \in \{1, \dots, M\}$ as training data, we can use supervised learning to approximate $L_i$ by $\hat{L}_{M, N}^{\text{SL}}(X_i)$ and to pool the inner replications from all outer scenarios.
 More specifically, $\hat{L}^{\text{SL}}_{M, N}(\cdot)$ denotes the supervised learning model trained on $(X_i, \hat{L}_{N, i})$ for $i \in \{1, \dots, M\}$, which is the simulation output of the standard nested simulation procedure with $M$ outer scenarios and $N$ inner replications.
-Using the $M$ \textit{training} samples, a nested Monte Carlo estimator of $\rho$ is given by
+To evaluate the convergence of the supervised learning-based nested simulation procedure, we consider the convergence behavior of the supervised learning model $h(\hat{L}^{\text{SL}}_{M, N}(\cdot))$ to the true risk measure $\rho = h(L(\cdot))$.
+More specifically, we want to study the quantity
+\begin{equation} \label{eq1:sl-E}
+    \mathbb{E} \left[ h(\hat{L}^{\text{SL}}_{M, N}(X))   \right] - \rho; ~~~ X \sim F_X.
+\end{equation}
+
+However, studying the expectation in Equation~\ref{eq1:sl-E} is unrealistic, as in practice the risk measure $\rho$ is estimated with a finite number of samples.
+Using the $M$ \textit{training} samples, a supervised learning-based nested MC estimator of $\rho$ is given by
 
@@
     \item   Nested expectation form:
-            $$\hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = \frac{1}{M} \sum_{i=1}^M h(\hat{L}^{\text{SL}}_{M, N}(X_i)); ~~~ X_i \sim F_X$$
+            \begin{equation} \label{eq1:sl-train}
+                \hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = \frac{1}{M} \sum_{i=1}^M h(\hat{L}^{\text{SL}}_{M, N}(X_i)); ~~~ X_i \sim F_X
+            \end{equation}
     \item   VaR:
@@
 
-After a supervised learning model is trained, it can be used to make predictions for all $X \in \mathcal{X}$.
-Instead of using the same training samples to estimate the risk measure, we can use predictions of a new set of $M'$ \textit{test} samples of $X$, namely $\tilde{\mathbf{X}} = \tilde{X}_1, \dots, \tilde{X}_{M'}$.
+After a supervised learning metamodel is trained, it can be used to make predictions for all $X \in \mathcal{X}$.
+Instead of using the same training samples to estimate the risk measure, we can use metamodel predictions for a new set of $M'$ \textit{test} samples of $X$, namely $\tilde{\mathbf{X}} = \tilde{X}_1, \dots, \tilde{X}_{M'}$.
 The resulting supervised learning-based estimator of $\rho^{\text{SL}, \text{Test}}$ is given by
@@
     \item   Nested expectation form:
-            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = \frac{1}{M'} \sum_{i=1}^{M'} h(\hat{L}^{\text{SL}}_{M, N}(\tilde{X}_i)); ~~~ \tilde{X}_i \sim F_X.$$
+            \begin{equation} \label{eq1:sl-test}
+            \hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = \frac{1}{M'} \sum_{i=1}^{M'} h(\hat{L}^{\text{SL}}_{M, N}(\tilde{X}_i)); ~~~ \tilde{X}_i \sim F_X.
+            \end{equation}
     \item   VaR:
@@
 
-Existing literature on nested simulation procedures has proposed different methods to approximate the true function $L(\cdot)$ with supervised learning models. 
-Methods that include theoretical convergence results are regression~\citep{broadie2015risk}, kernel smoothing~\citep{hong2017kernel}, and kernel ridge regression~\citep{wang2022smooth}.
+For the more complex metamodels, the convergence analysis of their MSEs is more challenging.
+More specifically, the KRR-based nested simulation~\citep{wang2022smooth} provides a convergence analysis in terms of absolute error (AE).
+\begin{align} \label{eq1:ae}
+    & \min_{M, N}  & \text{AE}(\hat{\rho}^{\text{SL}}_{M, N}) = \mathbb{E} \left[ \left| \hat{\rho}^{\text{KRR}}_{M, N} - \rho \right| \right] \nonumber \\
+    & \text{subject to} & M \cdot N = \Gamma 
+\end{align}
+
+The absolute error is a less stringent error metric than the MSE. 
+Section~\ref{sec1:connection-mse-absolute-error} discusses the connection between the MSE and the absolute error of the estimator in the context of nested simulation procedures.
+
+Existing literature on nested simulation procedures has proposed different metamodels to approximate the true function $L(\cdot)$ with supervised learning models. 
+In this study, we focus on the metamodeling approaches that include theoretical convergence results.
+Methods that include theoretical convergence results are regression~\citep{broadie2015risk}, kernel smoothing~\citep{hong2017kernel}, and KRR~\citep{wang2022smooth}.
 Their estimators of $L(\cdot)$ are given by $\hat{L}^{\text{REG}}_{M, N}(\cdot)$, $\hat{L}^{\text{KS}}_{M, N}(\cdot)$, and $\hat{L}^{\text{KRR}}_{M, N}(\cdot)$, respectively.
@@
     \item   Regression:
-            $$\hat{L}^{\text{REG}}_{M, N}(X) = \Phi(X) \hat{\beta},$$
-            where $\Phi$ is a chosen basis, and $\hat{\beta}$ is estimated from the training samples.
+            $$\hat{L}^{\text{REG}}_{M, N}(X) = \Phi(X) \hat{\beta}^{\text{REG}},$$
+            where $\Phi$ is a chosen basis, and $\hat{\beta}^{\text{REG}}$ is estimated from the training samples.
+            In~\cite{broadie2015risk}, the convergence analysis is performed on the expection Equation~\ref{eq1:sl-E} and for smooth and Lipschitz continuous $h$. 
+            Connections between the expectation and the MSE are discussed in the Appendix.
     \item   Kernel smoothing:
@@
             where $K_w$ is the kernel function with bandwidth $w$.
-
-            In~\cite{hong2017kernel}, the k-nearest neighbor (KNN) method is also implemented as a kernel smoothing method, but the convergence analysis is not provided.
+            ~\cite{nadaraya1964estimating} and ~\cite{watson1964smooth} originally proposed this kernel smoothing method for nonparametric regression, and it is widely known in the literature as Nadaraya-Watson kernel regression.
+            ~\cite{hong2017kernel} provides convergence analysis for metamodel predictions of the training samples (Equation~\ref{eq1:sl-train}), and the convergence analysis is provided for smooth, hockey-stick, and indicator $h$.
 
@@
             where $\|\cdot\|$ is the Euclidean norm, and  $k$ is the number of nearest neighbors to consider.
-
-    \item   Kernel ridge regression:
+            The k-nearest neighbor (KNN) method is implemented as a metamodel for numerical experiments in~\cite{hong2017kernel}, but the convergence analysis is not provided.
+
+    \item   KRR:
             $$\hat{L}^{\text{KRR}}_{M, N}(X) = \argmin_{g \in \mathcal{N}_{\Psi}(\Omega)} \left( \frac{1}{M} \sum_{i=1}^M (\hat{L}_{N, i} - L_i)^2 + \lambda \|L\|_{\mathcal{N}_{\Psi}(\Omega)}^2\right),$$
@@
             More specifically, $\Phi$ is a Mat\'ern kernel with smoothness parameter $\nu$ and length scale parameter $\upsilon$.
+            ~\cite{wang2022smooth} provides convergence analysis for the absolute error (Equation~\ref{eq1:ae}), and the convergence analysis is provided for smooth, Lipschitz continuous, and indicator $h$, VaR, and CVaR.
 \end{itemize}
 
-These supervised learning models approximates the inner simulation model $L(\cdot)$ with a function $\hat{L}^{\text{SL}}_{M, N}(\cdot)$, and they are used to pool the inner replications from all outer scenarios to estimate the risk measure $\rho$.
-In simulation literature, using models to approximate simulation is often referred to as the metamodeling approach, or it is referred to as a proxy model in the financial engineering literature.
-Supervised learning models are broadly classified into regression and classification models depending on whether the traget variable $L$ is continuous or discrete.
+These supervised learning metamodels approximate the inner simulation model $L(\cdot)$ with functions in the form of $\hat{L}^{\text{SL}}_{M, N}(\cdot)$, and the metamodels are used to pool the inner replications from all outer scenarios to estimate the risk measure $\rho$.
+In simulation literature, using models to approximate simulation is often referred to as the metamodeling approach, or it is referred to as a metamodel in the financial engineering literature.
+Supervised learning models are broadly classified into regression and classification models depending on whether the traget variable is continuous or discrete.
 In our context, the target variable $L$ is continuous, and the supervised learning models refer to regression models.
@@
 Among our interested supervised learning models, regression is a parametric regression model, while kernel smoothing and kernel ridge regression are non-parametric regression model.
+Their asymptotic convergence results are summarized in Table~\ref{tab1:asymConv-mse}, and Section~\ref{sec1:regression-convergence} and Section~\ref{sec1:kernel-smoothing-convergence} compare their finite-sample performance with numerical experiments.
 
@@
 
-Instead of using a supervised learning model as a proxy,~\cite{zhang2022sample} uses the likelihood ratio weights to pool the inner replications from all outer scenarios.
+Instead of using a supervised learning model as a metamodel,~\cite{zhang2022sample} uses the likelihood ratio weights to pool the inner replications from all outer scenarios.
 Here, we restrict our attention to problems in the nested expectation form whose outer scenarios characterize the stochasticity of the inner simulation model. 
@@
 $$\hat{L}^{\text{LR}}_{N, i} = \frac{1}{N} \sum_{j=1}^N Y(H_j, X_i) \frac{f_{H|X}(H_{j}|X_i)}{f_H(H_{ij})}, \;\;\; H_j \sim f_H, \;\;\; i=1, \dots, M.$$
+In Section~\ref{sec1:sensitivity-option-type}, we implement the likelihood ratio method and share its fast convergence in finite-sample experiments despite the costly computation of the likelihood ratio weights (Section~\ref{sec1:computational-complexity}).
 
@@
     \hline
-    Standard Monte Carlo & $\star$ & $\star$($\checkmark$) & $\checkmark$ & $\checkmark$ & $\times$ \\
-    \hline
-    Multi-level Monte Carlo & $\times$ & $\times$($\times$) & $\checkmark$ & $\times$ & $\times$ \\
+    Standard MC & $\star$ & $\star$($\checkmark$) & $\checkmark$ & $\checkmark$ & $\times$ \\
+    \hline
+    Multi-level MC & $\times$ & $\times$($\times$) & $\checkmark$ & $\times$ & $\times$ \\
     \hline
@@
 For simplicity, we abbreviate $\hat{L}_N(X)$ as $\hat{L}_N$, $\bar{Z}_N(X)$ as $\bar{Z}_N$, and $\bar{Z}_{N, i}$ as $\bar{Z}_{N, i}$.
-Let $\rho_M = \frac{1}{M} \sum_{i=1}^M h(L_i)$ be the nested Monte Carlo estimator with the true function $g$.
+Let $\rho_M = \frac{1}{M} \sum_{i=1}^M h(L_i)$ be the nested MC estimator with the true function $g$.
 The MSE of the standard nested simulation procedure can be decomposed into two ways.
@@
 \end{align}
-where the second inequality is due to Assumption~\ref{as1:sns-smooth}, and the last inequality follows from Assumption~\ref{as1:sns-noise-var} and the fact that $\hat{L}_N$ is a standard Monte Carlo estimator of $L$.
+where the second inequality is due to Assumption~\ref{as1:sns-smooth}, and the last inequality follows from Assumption~\ref{as1:sns-noise-var} and the fact that $\hat{L}_N$ is a standard MC estimator of $L$.
 Combining Equation~\ref{eq1:mse-sns},~\ref{eq1:taylor-sns},~\ref{eq1:s1-sns}, and~\ref{eq1:s2-sns}, we have
@@
 
-Equation~\ref{eq1:var-sns-smooth} directly follows from Assumption~\ref{as1:sns} and the fact that $\hat{L}_N$ is a standard Monte Carlo estimator of $L$.
+Equation~\ref{eq1:var-sns-smooth} directly follows from Assumption~\ref{as1:sns} and the fact that $\hat{L}_N$ is a standard MC estimator of $L$.
 Combining Equation~\ref{eq1:bias-sns-smooth-Taylor1},~\ref{eq1:bias-sns-smooth-Taylor2}, and~\ref{eq1:var-sns-smooth}, we are able to show the convergence order of the standard nested simulation procedure for a smooth function $h$ without the cross term as in Equation~\ref{eq1:s1-sns}.
@@
 
-A kNN regression is a non-parametric method that estimates the conditional expectation of $Y$ given $X$ by averaging the $Y$ values of the $k$ nearest neighbors of $X$.
+A kNN regression can be used as a non-parametric metamodel that estimates the conditional expectation of $Y$ given $X$ by averaging the $Y$ values of the $k$ nearest neighbors of $X$.
 Without loss of generality, we assume that $\{(X_i, \bar{Y}_{n, i}), i = 1, \dots, M\}$ are independent and identically distributed (i.i.d.) observations of $(X, Y)$ from the standard nested simulation procedure with an inner simulation budget of $n$, where $X_i$ is the $i^{\text{th}}$ of the outer scenario $X \in \Omega \subset \mathbb{R}^d$, and $\bar{Y}_{n, i}$ is the estimate of $Y|X_i$ with an inner simulation budget of $n$.
@@
     \hline
-    Standard Monte Carlo & $\mathcal{O}(\Gamma^{-2/3})$ & $\mathcal{O}(\Gamma^{-1/2})$ / $\mathcal{O}(\Gamma^{-2/3})$ & $\mathcal{O}(\Gamma^{-2/3})$ & $\mathcal{O}(\Gamma^{-2/3})$ & $\times$ \\
+    Standard MC & $\mathcal{O}(\Gamma^{-2/3})$ & $\mathcal{O}(\Gamma^{-1/2})$ / $\mathcal{O}(\Gamma^{-2/3})$ & $\mathcal{O}(\Gamma^{-2/3})$ & $\mathcal{O}(\Gamma^{-2/3})$ & $\times$ \\
     \hline
@@
 
-\subsection{Assumptions for the Multi-level Monte Carlo Procedure}
-In addition to Assumption~\ref{as1:sns-joint-density-bound}, the multi-level Monte Carlo procedure requires assumptions on the random variable $Q:= \frac{|\mathbb{E} \left[ Y | X \right]|}{\text{Var}[Y|X]}$.
+\subsection{Assumptions for the MLMC Procedure}
+In addition to Assumption~\ref{as1:sns-joint-density-bound}, the MLMC procedure requires assumptions on the random variable $Q:= \frac{|\mathbb{E} \left[ Y | X \right]|}{\text{Var}[Y|X]}$.
 
@@
 
-Assumption~\ref{as1:mlmc-q} ensures that the conditional expectation of $Y$ given $X$ is not concentrated around zero, as ~\cite{giles2019multilevel} show the asymptotic convergence of the multi-level Monte Carlo procedure only when $\rho$ is in the nested expectation form with $h$ being an indicator function, i.e., $h(x) = \mathbb{I}_{\{x \geq 0\}}$.
+Assumption~\ref{as1:mlmc-q} ensures that the conditional expectation of $Y$ given $X$ is not concentrated around zero, as ~\cite{giles2019multilevel} show the asymptotic convergence of the MLMC procedure only when $\rho$ is in the nested expectation form with $h$ being an indicator function, i.e., $h(x) = \mathbb{I}_{\{x \geq 0\}}$.
 
@@
 Further assumptions are made on the kernel function $K_w$ and the bandwidth $w$ to ensure the convergence of the kernel smoothing estimator $\hat{L}^{\text{KS}}_{M, N}(X)$.
-% A similar set of assumptions is made in~\cite{jennen1988unifying} for the convergence analysis of a kernel smoothing estimator with kernel functions of higher orders.
+A similar set of assumptions is made in~\cite{jennen1988unifying} for the convergence analysis of a kernel smoothing estimator with kernel functions of higher orders.
 
@@
 Assumption~\ref{as1:krr-domain} rules out the possibility of the outer scenario $X$ being a normal random variable, which is a common assumption in the literature.
-Furthermore, the convergence analysis of the KRR-based nested simulation procedure is shown in terms of the absolute error rather than the standard metric of MSE, which is due to the complexity of the KRR method itself.
+Furthermore, the convergence analysis of the KRR-based nested simulation procedure is shown in terms of the absolute error rather than the standard metric of MSE, which is due to the complexity of the KRR metatmodel.
 
@@
 Numerical experiments are conducted on portfolios that consist of options on $d$ underlying assets, whose dynamics follow a multidimensional geometric Brownian motion with $0.3$ pairwise correlation.
-6 nested simulation procedures are considered, namely the standard nested simulation procedure, the multi-level Monte Carlo procedure, the regression-based, kernel smoothing-based, likelihood ratio-based, and kernel ridge regression-based nested simulation procedures.
+6 nested simulation procedures are considered, namely the standard nested simulation procedure, the MLMC procedure, the regression-based, kernel smoothing-based, likelihood ratio-based, and kernel ridge regression-based nested simulation procedures.
 For the standard nested simulation procedure, the bootstrap-based budget allocation strategy from~\cite{zhang2021bootstrap} is implemented to estimate the optimal values of outer and inner simulation budgets.
-For the regression proxy, the Laguerre polynomials up to degree $3$ are used as the basis functions.
-The kNN proxy is implemented for the kernel smoothing-based procedure, and a cross-validation with grid search is used to find the optimal number of neighbors.
-The KRR proxy is implemented with a Mat\'ern kernel, and the smoothness, the length scale, and the regularization hyperparameters are found by a cross-validation with Bayesian search~\citep{frazier2018bayesian}.
+For the regression metamodel, the Laguerre polynomials up to degree $3$ are used as the basis functions.
+The kNN metamodel is implemented for the kernel smoothing-based procedure, and a cross-validation with grid search is used to find the optimal number of neighbors.
+The KRR metamodel is implemented with a Mat\'ern kernel, and the smoothness, the length scale, and the regularization hyperparameters are found by a cross-validation with Bayesian search~\citep{frazier2018bayesian}.
 The procedures are compared for 5 types of risk measures, namely a quadratic tracking error, a mean excess loss over threshold $u$, a probability of a large loss over threshold $u$, th VaR, and the CVaR, where the threshold $u$ is set to be the 90\% VaR.
@@
 Due to the computational complexity of the likelihood ratio-based and the KRR-based procedures, their MSEs are not reported for $\Gamma$ larger than $16,000$ and $64,000$, respectively.
-Due to the difficulty of fixing $\Gamma$ for the multi-level Monte Carlo procedure, the empirical rate of convergence of the multi-level Monte Carlo procedure is not reported here, but a detailed analysis of the empirical convergence of the multi-level Monte Carlo procedure is provided in Section~\ref{sec1:empirical-mlmc}.
+Due to the difficulty of fixing $\Gamma$ for the MLMC procedure, the empirical rate of convergence of the MLMC procedure is not reported here, but a detailed analysis of the empirical convergence of the MLMC procedure is provided in Section~\ref{sec1:empirical-mlmc}.
 In the following sections, we examine the empirical convergence of the nested simulation procedures in a similar manner as in Figure~\ref{fig1:compareAll}.
@@
 
-For both the regression-based and the kernel smoothing-based procedures, the reason for the higher empirical rates can be explained by having poor proxy estimators for smaller simulation budgets.
-For lower simulation budgets, the proxy estimators of the true inner simulation are poor, and the MSEs of the regression-based and kernel smoothing-based procedures are dominated by the model error of the proxy estimators.
+For both the regression-based and the kernel smoothing-based procedures, the reason for the higher empirical rates can be explained by having poor metamodels for smaller simulation budgets.
+For lower simulation budgets, the trained metamodels of the true inner simulation are poor, and the MSEs of the regression-based and kernel smoothing-based procedures are dominated by the model error of the metamodels.
 In other words, they have not reached their asymptotic regimes yet.
@@
 In our previous numerical experiments, the empirical rate of convergence of the regression procedure is observed to be much larger than its asymptotic rate of convergence.
-For dimensions larger than 10, the MSE of the regression procedure decreases quickly in the beginning, and it stabilizes after a certain budget level.
+For dimensions larger than $10$, the MSE of the regression procedure decreases quickly in the beginning, and it stabilizes after a certain budget level.
 In~\ref{fig1:reg_lb} illustrates the empirical convergence of the regression-based procedure in more detail at higher simulation budgets, where the asymptotic level of convergence is reached for $d = 20$.
@@
 
-The left part of Figure \ref{fig1:reg_lb} contains the MSEs of the regression procedure for budget sizes that are smaller than $10,000$. 
-Slopes of the fitted lines on the left correspond to the empirical rate of convergence of the regression procedure for budget levels between $1,000$ and $10,000$.
+The left part of Figure \ref{fig1:reg_lb} contains the MSEs of the regression procedure for budget sizes that are smaller than $10^3$. 
+Slopes of the fitted lines on the left correspond to the empirical rate of convergence of the regression procedure for budget levels between $10^3$ and $10^4$.
 To investigate the convergence behavior for higher budget levels, we conduct additional experiments for the European call option with dimension $20$. 
 The additional experiments are summarized on the right of Figure \ref{fig1:reg_lb}.
-After reaching a certain budget level, i.e., $\Gamma = 1,000,000$, the empirical rate of convergence for the regression-based nested simulation procedure approaches its asymptotic rate. 
-For nested simulation procedures whose proxy models are biased, the proxy estimators of the true inner simulation are poor, especially for smaller budget sizes. 
-We are able to clearly observe this phenomenon for the regression proxy, and it can be explained by dividing the MSE into proxy bias and simulation variance.
-For small budget sizes, the improvement of the bias of the regression proxy dominates the improvement of simulation variance. 
-Performing poorly for extremely low simulation budgets, the regression proxy improves significantly. 
-As the simulation budget gets higher, the improvement of the regression proxy becomes negligible compared with that of the simulation variance. 
-The regression proxy ceases to improve after reaching a certain level ($\Gamma = 100\!,\!000$ in our case), and the improvement of simulation variance dominates.
+After reaching a certain budget level, i.e., $\Gamma = 10^6$, the empirical rate of convergence for the regression-based nested simulation procedure approaches its asymptotic rate. 
+For nested simulation procedures with biased metamodeling, the metamodel estimates of the true inner simulation are poor, especially for smaller budget sizes. 
+We are able to clearly observe this phenomenon for the regression metamodel, and it can be explained by dividing the MSE into metamodeling bias and simulation variance.
+For small budget sizes, the improvement in the bias of the regression metamodel dominates the improvement in simulation variance. 
+Performing poorly for extremely low simulation budgets, the regression metamodel improves significantly as the simulation budget increases.
+As the simulation budget gets higher, the improvement of the regression bias becomes negligible compared with that of the simulation variance. 
+The regression metamodel ceases to improve after reaching a certain level ($\Gamma = 10^6$ in our case), and the improvement of simulation variance dominates.
+Due to high computational costs, we are not able to conduct experiments for higher budget levels, but we expect the MSE of the regression-based nested simulation procedure to stabilize after $\Gamma = 10^6$, and the empirical rate of convergence to approach its asymptotic rate.
 
@@
 
-The kernel smoothing proxy is a nonparametric regression procedure.
+Kernel smoothing is a nonparametric regression metamodel.
 According to the theoretical analysis in Section~\ref{sec1:asymptotic-convergence}, the asymptotic rate of convergence of the kernel smoothing-based nested simulation procedure is highly dependent on the dimension of the asset.
+In this section, we use a kNN metamodel for the kernel smoothing-based nested simulation procedure, and we examine its empirical convergence for different asset dimensions.
 
@@
 Another phenomenon that is observed in Figure~\ref{fig1:kernel_d} is that the empirical rate of convergence of the kernel smoothing-based procedure does not decrease monotonically as the simulation budget increases.
-This is likely due to the fact that the kernel smoothing-based procedure, as a nonparametric regression procedure, is highly dependent on the cross-validation of the proxy hyperparameters.
-For the kernel smoothing-based procedure, the kNN proxy is implemented. 
-Hence, the proxy hyperparameter is the number of nearest neighbors $k$.
+This is likely due to the fact that the kernel smoothing-based procedure, as a nonparametric regression procedure, is highly dependent on the cross-validation of the hyperparameters of the metamodel.
+For the kernel smoothing-based procedure, the kNN metamodel is implemented. 
+Hence, the hyperparameter of interest is the number of nearest neighbors $k$.
 In our numerical experiment, cross-validation is conducted once to select the optimal value of $k$ for each simulation budget, and the selected value of $k$ is fixed for all $1,000$ replications.
-Therefore, a poor selection of the optimal value of $k$ can lead to a poor proxy estimator, and the MSE of the kernel smoothing-based procedure will be dominated by the model error of the proxy estimator.
+Therefore, a suboptimal selection of the optimal value of $k$ can lead to a poor metamodel estimate, and the MSE of the kRR-based procedure will be dominated by the model error of the metamodel.
 
@@
 The observation is that the value of optimal $k$ estimated by cross-validation is highly variable across different replications.
-For the two replications where $k = 80$ is selected as the optimal value of $k$, the estimated risk measures for the kernel smoothing-based procedure are $0.1187$ and $0.1189$, which are significantly higher than the estimated risk measures for the other replications and far from the true risk measure of $0.1$.
-This observation suggests that the empirical convergence of the kernel smoothing-based nested simulation procedure is highly dependent on the cross-validation of the proxy hyperparameters.
+For $d = 2$, the optimal value of $k$ is estimated to be between $120$ to $220$ for most replications, and the estimated risk measures are close to the true risk measure of $0.1$.
+For the two replications where $k = 80$ is estimated as the optimal value of $k$, the resulting estimates of risk measures are $0.1187$ and $0.1189$, which are significantly higher than the estimated risk measures for the other replications and far from the true risk measure of $0.1$.
+This observation suggests that the empirical convergence of the kernel smoothing-based nested simulation procedure is highly dependent on the cross-validation of the hyperparameters of the metamodel.
 
@@
 In Figure~\ref{fig1:sens_level}, the empirical convergence of the regression-based nested simulation procedure for different levels of VaR and CVaR is illustrated for up-and-out barrier call options.
-The empirical rates of convergence of the regression-based nested simulation procedure are independent of the level of VaR and CVaR.
+The empirical rates of convergence of the regression-based nested simulation procedure are not sensitive to the level of VaR and CVaR.
 
@@
 In Figure~\ref{fig1:sens_model}, the empirical convergence results of the regression-based nested simulation procedure for a quadratic tracking error and a 90\%-CVaR are illustrated for different asset models, i.e., a geometric Brownian motion and a Heston model.
-The empirical rates of convergence of the regression-based nested simulation procedure are observed to be independent of the asset model.
-
-\subsection{Empirical Convergence of Multi-level Monte Carlo} \label{sec1:empirical-mlmc}
-
-The multi-level Monte Carlo procedure is a variance reduction technique that is designed to reduce the computational cost of nested simulation procedures.
-The theoretical analysis in~\cite{giles2019multilevel} shows that the multi-level Monte Carlo procedure has a faster empirical rate of convergence than the standard nested simulation procedure when the risk measure of interest is the probability of a large loss over a threshold $u$, i.e., the nested expectation case with $h$ being an indicator function.
+The empirical rates of convergence of the regression-based nested simulation procedure are observed to be insensitive to the asset model.
+
+\subsection{Sensitivity to the regression basis} \label{sec1:sensitivity-basis}
+
+In our previous numerical experiments, the regression-based nested simulation procedure is implemented with Laguerre polynomials up to degree $3$ as the basis functions.
+To examine the sensitivity of the empirical convergence behavior to the regression basis, we consider different basis functions, i.e., regular polynomial regression up to degree $3$.
+
+\begin{figure}[ht!] 
+    \centering
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure13a.png}
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure13b.png}
+    \caption{Empirical convergence of regression-based nested simulation procedures for different regression bases}
+    \label{fig1:sens_basis}
+\end{figure}
+
+In Figure~\ref{fig1:sens_basis}, the empirical convergence results of the regression-based nested simulation procedure for a quadratic tracking error and a 90\%-CVaR are illustrated for different regression bases, i.e., Laguerre polynomials and regular polynomials up to degree $3$.
+The empirical rates of convergence of the regression-based nested simulation procedure are observed to be insensitive to the chosen regression basis.
+In summary, the empirical convergence behavior of the regression-based nested simulation procedure is stable across different risk measures, option types, asset dimensions, levels of VaR and CVaR, asset models, and regression bases.
+With a limited total budget, the regression-based nested simulation procedure is the most robust and stable among all nested simulation procedures.
+
+\subsection{Empirical Convergence of MLMC} \label{sec1:empirical-mlmc}
+
+The MLMC procedure is a variance reduction technique that is designed to reduce the computational cost of nested simulation procedures.
+The theoretical analysis in~\cite{giles2019multilevel} shows that the MLMC procedure has a faster empirical rate of convergence than the standard nested simulation procedure when the risk measure of interest is the probability of a large loss over a threshold $u$, i.e., the nested expectation case with $h$ being an indicator function.
 
@@
     \end{tabular}
-    \caption{MSEs of the multi-level Monte Carlo procedure for different levels}
+    \caption{MSEs of the MLMC procedure for different levels}
     \label{tab1:mlmc-mse}
@@
 
-Instead of using a figure, we provide a summary of the empirical convergence results of the multi-level Monte Carlo procedure with a decomposition table of the MSEs in Table~\ref{tab1:mlmc-mse}.
-The MSEs of the multi-level Monte Carlo procedure are decomposed into the bias and the variance of the estimator.
+Instead of using a figure, we provide a summary of the empirical convergence results of the MLMC procedure with a decomposition table of the MSEs in Table~\ref{tab1:mlmc-mse}.
+The MSEs of the MLMC procedure are decomposed into the bias and the variance of the estimator.
 The MSEs of the standard nested simulation procedure with a similar total simulation budget are also provided for comparison.
-Since the multi-level Monte Carlo procedure is designed with a fixed number of outer simulation paths, the benefit of the multi-level Monte Carlo procedure is minimal when the total simulation budget is large.
-More specifically, when $\Gamma$ is large, the standard nested simulation procedure with a bootstrap-based budget allocation strategy benefits from having a larger number of outer simulation paths, and the MSE of the standard nested simulation procedure is lower than that of the multi-level Monte Carlo procedure with a fixed number of outer simulation paths.
+Since the MLMC procedure is designed with a fixed number of outer simulation paths, the benefit of the MLMC procedure is minimal when the total simulation budget is large.
+More specifically, when $\Gamma$ is large, the standard nested simulation procedure with a bootstrap-based budget allocation strategy benefits from having a larger number of outer simulation paths, and the MSE of the standard nested simulation procedure is lower than that of the MLMC procedure with a fixed number of outer simulation paths.
 
 \section{Computational Complexity} \label{sec1:computational-complexity}
-Compared to the standard procedure, proxy-based nested simulation procedures often have faster empirical rates of convergence.
-The faster convergence benefits from the pooling of inner samples through the proxy models. 
+Compared to the standard procedure, metamodel-based nested simulation procedures often have faster empirical rates of convergence.
+Their faster convergence benefits from the pooling of inner samples through the metamodels. 
 However, pooling itself comes with computational costs, which are usually ignored in most numerical comparisons. 
@@
 For a $d$-dimensional nested estimation problem, the simulation cost for all procedures is $\mathcal{O}(dMN)$.
-The simulation cost is omitted from Table~\ref{tab1:complexity}, as all methods are given the same simulation budget.
+The simulation cost is omitted from Table~\ref{tab1:complexity}, as all procedures are given the same simulation budget.
 Given $M$ outer samples and the corresponding $M$ inner sample averages, the algorithmic complexity of the additional operations does not involve $N$ thus can be written in terms of $M$ only.
-The training cost includes the cost of fitting the proxy model and the cost of cross-validation for nonparametric regression proxies.
-For the standard procedure, the training cost is $0$ due to the absence of proxy models. 
+The training cost includes the cost of fitting the metamodel and the cost of cross-validation for nonparametric regression metamodels.
+For the standard procedure, the training cost is $0$ due to the absence of a metamodel. 
 Its prediction cost $\mathcal{O}(M)$ comes from the evaluation of the function $h$ for $M$ samples.
@@
 The prediction cost of the regression-based procedure is $\mathcal{O}(pM)$, which comes from the multiplication of the design matrix by the estimated coefficients.
-For the kernel smoothing-based procedure, the kNN proxy is implemented.
+For the kernel smoothing-based procedure, the kNN metamodel is implemented.
 In practice, the K-D tree algorithm~\citep{bentley1975multidimensional} is often implemented for efficient nearest neighbor search.
@@
 A practical implementation of block sort is provided in~\cite{kim2008ratio}.
-Hence, an efficient implementation of the kNN proxy is crucial for the kernel smoothing-based procedure.
+Hence, an efficient implementation of the kNN metamodel is crucial for the kernel smoothing-based procedure.
 For the likelihood ratio-based procedure, the training cost is $0$ as no training is required.
@@
 The prediction cost of the KRR-based procedure is $\mathcal{O}(M^2)$, which comes from the multiplication of the kernel matrix by the estimated coefficients.
-Among the proxy-based procedures, regression is the most efficient as $p$ is usually much smaller than $M$. 
-Kernel smoothing and KRR are kernel-based proxies, and they are more expensive due to distance calculation and cross-validation of hyperparameters. 
-The kNN proxy has only 1 hyperparameter $k$, while the KRR proxy requires 3 hyperparameters, namely the smoothness hyperparameter $\nu$, scale hyperparameter $\upsilon$, and the regularization hyperparameter $\lambda$.
+Among the metamodel-based procedures, regression is the most efficient as $p$ is usually much smaller than $M$. 
+Kernel smoothing and KRR are kernel-based metamodels, and they are more computaional expensive due to distance calculations and cross-validations of hyperparameters. 
+The kNN metamodel has only 1 hyperparameter $k$, while the KRR metamodel requires 3 hyperparameters, namely the smoothness hyperparameter $\nu$, scale hyperparameter $\upsilon$, and the regularization hyperparameter $\lambda$.
 Calculating the likelihood ratio weights is inevitable for the likelihood ratio-based procedure. 
@@
 The likelihood ratio-based procedure requires no training, but the cost of calculating the likelihood weights is $\mathcal{O}(M^2)$.
-Comparing the algorithmic complexity of the nested simulation procedures, the regression-based procedure is the most efficient among the proxy-based procedures.
+Comparing the algorithmic complexity of the nested simulation procedures, the regression-based procedure is the most efficient among the metamodel-based procedures.
 For a fixed $p$, the total additional cost of a regression-based procedure is $\mathcal{O}(M)$, which is the same as the standard procedure's.
@@
 8 cores are used for parallel computing, and the total computational time is the sum of the simulation time, the training time, and the prediction time.
-The regression and kernel smoothing-based procedures are the most efficient among the proxy-based procedures.
+The regression and kernel smoothing-based procedures are the most efficient among the metamodel-based procedures.
 Since the regression-based procedure has a higher empirical rate of convergence, it is preferred over the kNN.
@@
 The remainder can be decomposed into two parts: hyperparameter tuning and model implementation.
-The hyperparameter tuning cost is the cost of estimating the optimal hyperparameters for the proxy models, and the model implementation cost is the cost of fitting the proxy models and generating predictions from the trained proxies.
+The hyperparameter tuning cost is the cost of estimating the optimal hyperparameters for the metamodels, and the model implementation cost is the cost of fitting the metamodels and generating predictions from the trained metamodels.
 For each procedure, each point in Figure~\ref{fig1:c_model} represents the average computational time for a given simulation budget $\Gamma$.
-A regression model is fitted to each model respectively, and its slope is reported as the growth rate of the computational time with respect to $\Gamma$.
+A regression model is fitted to each model respectively, and its slope can be viewed as the growth rate of the computational time with respect to $\Gamma$.
 The total computational time of the standard procedure is mostly attributed to finding the optimal $M$ and $N$ using the bootstrap-based budget allocation strategy from~\cite{zhang2021bootstrap}.
@@
 The likelihood ratio-based procedure requires no hyperparameter tuning, and its total computational time is mainly attributed to the likelihood weight calculation, which is $\mathcal{O}(M^2)$. 
-In summary, for a large simulation budget, the regression-based procedure is the most efficient among all proxy-based procedures in terms of computational time.
+In summary, for a large simulation budget, the regression-based procedure is the most efficient among all metamodel-based procedures in terms of computational time.
 
@@
 In the task of estimating risk measures for portfolios of complex financial derivatives, nested simulation procedures are commonly required but often computationally expensive. 
-Tremendous efforts have been made to improve the efficiency of nested simulation procedures by approximating the inner simulation model with a proxy model. 
-In this study, we review the literature on nested simulation procedures in financial engineering and establish fair comparisons of different proxy models using the same set of numerical examples. 
-Asymptotic properties of estimators for different nested simulation procedures are influenced by their corresponding proxy models.
-To show an asymptotic convergence result, a more complex proxy model requires a more stringent set of assumptions on the distribution of the outer scenario and the inner simulation noise.
+Tremendous efforts have been made to improve the efficiency of nested simulation procedures by approximating the inner simulation model with a metamodels. 
+In this study, we review the literature on nested simulation procedures in financial engineering and establish fair comparisons of different metamodels using the same set of numerical examples. 
+Asymptotic properties of estimators for different nested simulation procedures are influenced by their corresponding metamodels.
+To show an asymptotic convergence result, a more complex metamodels requires a more stringent set of assumptions on the distribution of the outer scenario and the inner simulation noise.
 With extensive numerical experiments, we have found the finite-sample performance of a procedure can deviate from its theory. 
@@
 In such cases, a neural network-based procedure may be more suitable, as it is a data-driven algorithm that finds a suitable set of basis functions automatically.
-In Chapter~\ref{ch2}, we will examine the performance of regression-based and neural network-based nested simulation procedures for estimating risk measures for variable annuities.
+In Chapter~\ref{chap:project2}, we will examine the performance of regression-based and neural network-based nested simulation procedures for estimating risk measures for variable annuities.

### 2024-09-26 project2/nnMetamodels.tex
new

@@
 \chapter{Cutting Through the Noise: Using Deep Neural Network Metamodels for High Dimensional Nested Simulation}
-\label{ch2}
+\label{chap:project2}
 %======================================================================
@@
 Measuring and monitoring risks, particularly tail risks, are important risk management tasks for financial institutions like banks and insurance companies.
-Two most popular tail risk measures are Value-at-Risk (VaR) and Conditional Value-at-Risk (CVaR)~\citep{rockafellar2002conditional}.
-Other names of CVaR include Conditional Tail Expectation (CTE), Tail Value-at-Risk (TailVaR), and Expected Shortfall (ES).
+Two most popular tail risk measures are VaR and CVaR~\citep{hardy2022quantitative, rockafellar2002conditional}.
 
 Consider a loss random variable $L$ whose losses and gains lie in the right and left tails, respectively, of its distribution.
-For a given confidence level $\alpha\in [0,1]$, the $\alpha$-VaR is defined as the $\alpha$-quantile of $L$:
-$
-    \VaR_\alpha = q_\alpha = \inf \left\{ q: \Pr(L\leq q) \geq \alpha \right\}.
-$
-The $\alpha$-CVaR of $L$ is defined as
-$
-    \CVaR_\alpha =\frac{1}{1-\alpha} \int_{v=\alpha}^{1} q_v dv.
-$
+For a given confidence level $\alpha\in [0,1]$, the $\alpha$-VaR and $\alpha$-CVaR are defined in Equation~\eqref{eq1:var} and Equation~\eqref{eq1:cvar}, respectively.
 Tail risk measures like VaR and CVaR are widely used for setting regulatory and economic capital, which is the amount of capital a financial institution holds to cover its risk.
@@
 Also, $\alpha$-CVaR can be estimated by
-\begin{equation*}
-    \widehat{\CVaR}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}L_{(i)} = \frac{1}{(1-\alpha)M} \sum_{i \in \tail_{(1-\alpha )M}}L_{i},
-\end{equation*}
-where we define a \textit{true tail scenario set} of size $k$ as $\tail_{k} = \{i: L_i > L_{(M-k)}\}$.
+\begin{equation} \label{eq2:cvar-hat}
+    \widehat{\CVaR}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}L_{(i)} = \frac{1}{(1-\alpha)M} \sum_{i \in \tail_{(1-\alpha )M}}L_{i}.
+\end{equation}
+Equation \eqref{eq2:cvar-hat} is the same as \eqref{eq1:cvar-hat} except we define a \textit{true tail scenario set} of size $k$ as $\tail_{k} = \{i: L_i > L_{(M-k)}\}$.
 In this study, the loss random variable of interest is the hedging error for VA.
@@
 This is because model capacities of the regression metamodels are too low to learn the complex dynamic hedging simulation model.
-There are also differences among the three deep neural neetwork models.
+All neural network metamodels have high model capcities comparing with the number of data points in the training set, i.e., $90\!,\!000$.
+This is not a huge concern for the deep neural networks.
+In neural network literature, the number of trainable parameters is often much larger than the number of data points in the training set.
+AlexNet~\citep{krizhevsky2012imagenet}, a well-known convolutional neural network, has 60 million parameters and is trained on the ImageNet dataset with 1.2 million images.
+Other examples include generative pre-trained transformer models like BERT~\citep{devlin2018bert} and GPT-3~\citep{brown2020language}, which have billions of parameters and are trained on large-scale text corpora.
+The reason for not overfitting is still an open question in deep learning research.
+One possible explanation is that the optimization surface of deep neural networks is highly non-convex and has many local minima.
+As a result, given a good initialization, the optimization algorithm is likely to find a solution that generalizes well to unseen data.
+
+There are also differences among the three deep neural network models due to having different architectures.
 The FNN is a generic neural network, its test error is larger than the training error, which is a sign of over-fitting and poor generalization.
@@
 Notably, the true errors for the deep neural network metamodels are lower than the test errors.
+This is a sign of the metamodels' ability to learn the true feature-label relationship with noisy training labels. 
+Section~\ref{subsec2:noiseTolerance} investigates this phenomenon in more details.
+
 Comparing the two metamodels with recurrent structures, A LSTM network overcomes two key drawbacks of a crude RNN.
@@
     \item A LSTM introduces three gates that regulate the flow of information. 
-These gates decide what information should be kept or discarded.
-This makes a LSTM more capcable of learning long-term dependencies.
+    These gates decide what information should be kept or discarded. This makes a LSTM more capcable of learning long-term dependencies. 
     Since the feature in our dynamic hedging problem is a 240-dimensional time series, a LSTM is more suitable than a crude RNN.
+    The network architecture serves as a prior knowledge that guides the optimization algorithm to find a solution that generalizes well to unseen data, and it significantly impact the metamodel's performance.
+    It is important to choose a suitable architecture with a pre-set capacity that is large enough to learn the true feature-label relationship.
 \end{enumerate}
@@
 
-Compared with the MSE table in Table~\ref{tab:gmwb_arch} that summarizes the overall fit, QQ plots offer a close look at the metamodels' performance on different parts of the loss distribution.
+Comparing with the MSE table in Table~\ref{tab:gmwb_arch} that summarizes the overall fit, QQ plots offer a closer look at the metamodels' performance on different parts of the loss distribution.
 Figure~\ref{fig2:QQ_REG} show that the regression metamodels' predictions are far from the true losses, especially on the tails.
@@
 
-\subsection{Noise Tolerance of Deep Neural Network Metamodels}
+\subsection{Noise Tolerance of Deep Neural Network Metamodels} \label{subsec2:noiseTolerance}
 
@@
 
+The maximum number of data points in the training dataset is set to $M = 100\!,000$.
+The training dataset is split into training and test sets with a 90\%-10\% ratio.
+The true labels are generated by running the standard nested simulation procedure with $N=100\!,000$ inner replications for each of the $100\!,000$ outer scenarios.
+The reason for using a maximum of $100\!,000$ data points is precisely due to the computational cost of running the standard nested simulation procedure.
+For consistency, the LSTM metamodels are trained with the same architecture and training settings as in the previous experiments.
+
 \begin{table}[ht!]
@@
         High-capacity LSTM  & $N=100$                & $0.068 (\pm0.004)$        & $0.102(\pm0.006)$     & $0.060 (\pm0.004)$ \\
+        Difference          & $N=100$                & $-0.007$                  & $0.023$               & $-0.003$ \\
+        \hline
         LSTM                & $N=10$                 & $0.195 (\pm0.001)$        & $0.193(\pm0.001)$     & $0.070 (\pm0.001)$ \\
         High-capacity LSTM  & $N=10$                 & $0.157 (\pm0.002)$        & $0.199(\pm0.002)$     & $0.065 (\pm0.001)$ \\
+        Difference          & $N=10$                 & $-0.038$                  & $0.006$               & $-0.005$ \\
+        \hline
         LSTM                & $N=1$                  & $1.366 (\pm0.006)$        & $0.781(\pm0.005)$     & $0.129 (\pm0.002)$ \\
         High-capacityLSTM   & $N=1$                  & $1.354 (\pm0.006)$        & $0.795(\pm0.005)$     & $0.149 (\pm0.002)$ \\
+        Difference          & $N=1$                  & $-0.012$                  & $0.014$               & \textcolor{red}{$0.020$} \\
         \bottomrule
@@
 
-Table~\ref{tab:lstm_arch} shows the average squared errors and the half widths of their 95\% confidence intervals between the metamodel predictions and the labels in the training dataset and the true dataset.
+The first two rows of Table~\ref{tab:lstm_arch} shows the average squared errors and the half widths of their 95\% confidence intervals between the metamodel predictions and the labels in the training dataset and the true dataset.
 The test errors are included as a practical measure of the metamodels' generalization ability.
@@
 Both LSTM metamodels are able to learn the true feature-label relationship from the low-noise and medium-noise datasets.
-However, when the noise level is high, the high-capacity LSTM metamodel has extremely high training error and true error.
-It also has wide confidence intervals, which is an indication that the high-capacity LSTM metamodel is starting to overfit to the noise in the training labels.
+However, when the noise level is high, both LSTM metamodels have high true error.
+The diffences in the errors between the LSTM metamodels are also reported in the last rows of Table~\ref{tab:lstm_arch}.
+A positive difference indicates that the high-capacity LSTM has higher errors than the LSTM.
+We observe that both LSTM metamodels have similar errors on the low-noise and medium-noise datasets.
+However, when the noise level is high, the high-capacity LSTM has higher errors than the regular LSTM.
+This is because the high-capacity LSTM has more trainable parameters and is more prone to over-fitting to the noise in the training labels.
 In contrast, the LSTM metamodel is more robust to label noise and is able to learn the true feature-label relationship better from the high-noise dataset.
-In practice, since the true relationship is unknown, the true error is not available.
+In practice, since the true relationship is unknown, the true error is not readily available.
 The test error approximates the true error and is directly observable.
-The test errors of the LSTM metamodels are consistent with their true errors, which suggests that generalization ability of a metamodel can indeed be inferred from its test error.
+The difference in test errors of the LSTM metamodels are inconsistent with the differences in true errors.
+Therefore, test errors are not reliable indicators of the metamodels' noise tolerance.
+For practical applications that utilize nerual networks as metamodels, we recommend not simulating the test scenarios.
+Instead, we recommend simulating the true contract losses on a few tail and non-tail training scenarios to evaluate the metamodels' noise tolerance.
 
-Another way to read Table~\ref{tab:lstm_arch} is to compare the errors of two metamodels for the same noise level.
-Comparing the LSTM with the high-capacity LSTM on each noise level, we observe that the high-capacity LSTM has lower training errors and true errors than the LSTM on both the low-noise and medium-noise datasets.
-However, when the noise level is high, the high-capacity LSTM has lower training errors but higher true errors than the LSTM.
-In our numerical example, only the highest level of noise moves one towards choosing the LSTM over the high-capacity LSTM.
+In summary, our numerical experiments demonstrate that both LSTM metamodels are capable of learning the true inner simulation model from noisy training labels.
 In most cases, a high-capacity metamodel is better.
@@
 
-With more details, the QQ-plots depicted in Figure~\ref{fig2:QQ_All} illustrates the fit of the two LSTM metamodels when different noise levels are present in the training labels.
-They are arranged in a 2-by-3 grid, where the two rows correspond to the two LSTM metamodels, and the three columns correspond to the three noise levels.
+In more details, the QQ-plots depicted in Figure~\ref{fig2:QQ_All} illustrates the fit of the two LSTM metamodels when different noise levels are present in the training labels.
+They are arranged in a 2-by-3 grid, where the two rows correspond to the two LSTM metamodels with different model capacities, and the three columns correspond to the increasing noise levels.
 The Pearson correlation coefficient between the true losses and the predicted losses is labeled in each subplot.
@@
 To further test the sensitivity of a LSTM metamodel and provide a more comprehensive picture of the noise tolerance of deep neural network models, we conduct a sensitivity analysis on the noise tolerance of the regular LSTM metamodel by varying the numbers of outer scenarios ($M$) and inner replications ($N$) used to generate the training data.
-The number of outer scenarios corresponds to the number of feature-label pairs (i.e., data size) of the training dataset, and the number of inner replications controls the noise level in the training labels.
+The number of outer scenarios corresponds to the number of data points in the training dataset, and the number of inner replications controls the noise level in the training labels.
 
@@
         \toprule
-                          & $N=1\!,\!000$ & $N=100$       & $N=10$        & $N=1$ \\
+                            & $N=1$ & $N=10$  & $N=100$ & $N=1\!,\!000$\\
         \midrule
-        $M = 100$         & $0.158$ & $0.167$ & $0.229$ & $1.139$ \\
-        $M = 1\!,\!000$   & $0.127$ & $0.123$ & $0.173$ & $0.559$ \\
-        $M = 10\!,\!000$  & $0.097$ & $0.099$ & $0.115$ & $0.283$ \\
-        $M = 100\!,\!000$ & $0.063$ & $0.063$ & $0.068$ & $0.126$ \\
+        $M = 100$           & $1.139$ & $0.229$ & $0.167$ & $0.158$ \\
+        $M = 1\!,\!000$     & $0.559$ & $0.173$ & $0.123$ & $0.127$ \\
+        $M = 10\!,\!000$    & $0.283$ & $0.115$ & $0.099$ & $0.097$ \\
+        $M = 100\!,\!000$   & $0.126$ & $0.068$ & $0.063$ & $0.063$ \\
         \bottomrule
@@
     \caption{MSE between regular LSTM predicted losses and true losses.}
-    \label{tab:lstm_sens}
+    \label{tab2:lstm_sens}
 \end{table}
@@
         \toprule
-                          & $N=1\!,\!000$ & $N=100$       & $N=10$        & $N=1$ \\
+                          & $N=1$ & $N=10$  & $N=100$ & $N=1\!,\!000$\\
         \midrule
-        $M = 100$         & $0.087$ & $0.131$ & $0.408$ & $0.764$ \\
-        $M = 1\!,\!000$   & $0.087$ & $0.156$ & $0.367$ & $0.878$ \\
-        $M = 10\!,\!000$  & $0.063$ & $0.064$ & $0.147$ & $0.351$ \\
-        $M = 100\!,\!000$ & $0.038$ & $0.060$ & $0.065$ & $0.149$ \\
+        $M = 100$           & $0.764$ & $0.408$ & $0.131$ & $0.087$ \\
+        $M = 1\!,\!000$     & $0.878$ & $0.367$ & $0.156$ & $0.087$ \\
+        $M = 10\!,\!000$    & $0.351$ & $0.147$ & $0.064$ & $0.063$ \\
+        $M = 100\!,\!000$   & $0.149$ & $0.065$ & $0.060$ & $0.038$ \\
         \bottomrule
@@
     \caption{MSE between high-capacity LSTM predicted losses and true losses.}
-    \label{tab:hicaplstm_sens}
+    \label{tab2:hicaplstm_sens}
 \end{table}
 
-Table~\ref{tab:lstm_sens} and~\ref{tab:hicaplstm_sens} show the average squared errors between the LSTM predictions and the true losses for various combinations of $M$ and $N$.
-The last rows of Table~\ref{tab:lstm_sens} and Table~\ref{tab:hicaplstm_sens} show the performance of the regular and high capacity LSTM metamodels trained with $M=100\!,000$ training labels with different noise levels.
+Table~\ref{tab2:lstm_sens} and~\ref{tab2:hicaplstm_sens} show the average squared errors between the LSTM predictions and the true losses for increasing $M$ and $N$.
+The last rows of Table~\ref{tab2:lstm_sens} and Table~\ref{tab2:hicaplstm_sens} show the performance of the regular and high capacity LSTM metamodels trained with $M=100\!,000$ training labels with different noise levels.
 We observe that an increasing $N$ reduces the MSE, but the reduction is not significant for a regular LSTM when $N$ is larger than $10$.
 For the high-capacity LSTM, the MSE is significantly reduced when $N$ is increased from $1$ to $100$, but the reduction is not significant when $N$ is increased from $100$ to $1\!,000$.
-Another way to interpret the results in Table~\ref{tab:lstm_sens} is to compare the MSEs for the same budget of $\Gamma = M \times N$. 
+Another way to interpret the results in Table~\ref{tab2:lstm_sens} is to compare the MSEs for the same budget of $\Gamma = M \times N$. 
 Entries on the same diagonal represents the same simulation budget.
 For most budgets, the MSEs are also the lowest when $N = 10$.
-The results in Table~\ref{tab:lstm_sens} suggest that the performance of the LSTM metamodel is more sensitive to the number of outer scenarios than the number of inner replications.
+The results in Table~\ref{tab2:lstm_sens} suggest that the performance of the LSTM metamodel is more sensitive to the number of outer scenarios than the number of inner replications.
 Treating the neural network as an advanced regression metamodel, we find this pheonomenon to be consistent with the results in~\cite{broadie2015risk}, where the authors show that the performance of a regression-based nested simulation procedure is more affected by the number of outer scenarios.
+The last row in Table~\ref{tab2:lstm_sens} and ~\ref{tab2:hicaplstm_sens} show that the high-capacity LSTM metamodel is relatively insensitive to the number of inner replications.
+To make the most efficient use of a fixed simulation budget, the number of inner replication should be set constant around $N=10$ while increasing the number of outer scenarios to the maximum.
 
-To further investigate the LSTM metamodels' sensitivity to data quantity and quality, we report the Spearman rank correlation coefficients Table~\ref{tab:lstm_corr}, which measure the ability to rank the scenarios by their true losses.
+To further investigate the LSTM metamodels' sensitivity to data quantity and quality ($M$ and $N$, respectively), we report the Spearman rank correlation coefficients Table~\ref{tab2:lstm_corr}, which measure the ability to rank the scenarios by their true losses.
 It is an appropriate measure of the metamodel's performance in the two-stage procedure, where the metamodel is used to identify the predicted tail scenario set, on which extensive simulations are run in stage 2 to estimate the $95\%$-CVaR.
@@
         \toprule
-                          & $N=1\!,\!000$ & $N=100$       & $N=10$        & $N=1$ \\
+                          & $N=1$        & $N=10$        & $N=100$       & $N=1\!,\!000$ \\
         \midrule
-        $M = 100$         & 0.937 (0.941) & 0.896 (0.903) & 0.875 (0.915) & 0.638 (0.881) \\
-        $M = 1\!,\!000$   & 0.922 (0.927) & 0.886 (0.891) & 0.899 (0.908) & 0.722 (0.768) \\
-        $M = 10\!,\!000$  & 0.947 (0.948) & 0.908 (0.905) & 0.937 (0.900) & 0.845 (0.630) \\
-        $M = 100\!,\!000$ & 0.965 (0.966) & 0.927 (0.922) & 0.963 (0.909) & 0.935 (0.640) \\
+        $M = 100$         & 0.638 (0.881) & 0.875 (0.915) & 0.896 (0.903) & 0.937 (0.941) \\
+        $M = 1\!,\!000$   & 0.722 (0.768) & 0.899 (0.908) & 0.886 (0.891) & 0.922 (0.927) \\
+        $M = 10\!,\!000$  & 0.845 (0.630) & 0.937 (0.900) & 0.908 (0.905) & 0.947 (0.948) \\
+        $M = 100\!,\!000$ & 0.935 (0.640) & 0.963 (0.909) & 0.927 (0.922) & 0.965 (0.966) \\
         \bottomrule
     \end{tabular}
-    \caption{Spearman (and Pearson) correlation coefficients between regular LSTM predicted losses and true losses.}
-    \label{tab:lstm_corr}
+    \caption{Spearman (and Pearson) correlation coefficients between high-capacity LSTM predicted losses and true losses.}
+    \label{tab2:lstm_corr}
 \end{table}
 
-Consistent with the results in Table~\ref{tab:lstm_sens}, the Pearson and Spearman correlation of the LSTM metamodel predictions with the true losses is sensitive to the number of outer scenarios, especially at higher noise levels.
-Notably, the Spearman correlation coefficients are not significantly different from the Pearson correlation coefficients for any $N$ larger than $10$.
-In our numerical experiments, the regular LSTM metamodel is trained on $M = 100\!,000$ samples from the low noise training dataset ($N=100$), the total simulation budget is $\Gamma = 10\!,000\!,000$.
-The corresponding Spearman correlation coefficient is 0.927, which is very close to the Pearson correlation coefficient of 0.922.
+Consistent with the results in Table~\ref{tab2:lstm_sens}, the Spearman correlation of the LSTM metamodel predictions with the true losses is insensitive to the number of inner replications, especially when $M$ is large.
+The Pearson correlation coefficients are significantly lower for $N=1$ than the other $N$ values.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.6\textwidth]{./project2/figures/cor_heatmap.png}
+    \caption{Difference between Spearman and Pearson correlation coefficients for high-capacity LSTM metamodel.}
+    \label{fig2:cor-heatmap}
+\end{figure}
+
+Figure~\ref{fig2:cor-heatmap} shows the difference between the Spearman and Pearson correlation coefficients for the high-capacity LSTM metamodel.
+The heatmap is generated by subtracting the Pearson correlation coefficients from the Spearman correlation.
+We observe that Spearman correlation coefficients are not significantly different from the Pearson correlation coefficients for any $N$ larger than $10$. 
 This is a strong evidence that the LSTM metamodel is not only able to effectively rank the scenarios by their true losses, but also able to make accurate loss predictions.
 Instead of using the LSTM metamodel only for ranking in a two-stage procedure, LSTM's ability to cut through a moderate level of noise in training labels encourages us to use its predictions to estimate the CVaR directly.
-
-% We proceed to examine the impact of noise on the LSTM metamodels' performance in predicting the true tail scenarios.
-% The effect of training label noise is more pronounced for the high-capacity LSTM than for the regular LSTM.
-% For both LSTM metamodels, the Spearman correlation coefficients are not significantly different from the Pearson correlation coefficients, which is significantly different from the two-stage procedure in~\cite{dang2020efficient}.
-% This difference is due to the fact that the two-stage procedure in~\cite{dang2020efficient} uses a simplified asset model (i.e., a Black Scholes model) as a proxy simulation model for the regime-switching model.
-% The two models are significantly different, but the ranking of the scenarios by their losses is similar.
-% For our two-stage procedure, the only difference between the simulation models in Stage 1 and Stage 2 is the number of inner replications.
-% The ability for the LSTM metamodels to cut through the noise in training labels and learn the true feature-label relationship offers more accurate loss estimates (i.e., high Pearson correlations), which leads to more accurate rankings (i.e., high Spearman correlations).
 
@@
 In our numerical experiments, the results for the single-stage procedure is obtained with the same metamodels as in the two-stage procedure.
-The only difference from Section~\ref{subsec:twoStageProcedure} is that the metamodels predictions are used to estimate the risk measures directly.
+The only difference from Section~\ref{subsec:twoStageProcedure} is that the metamodel predictions are used to estimate the risk measures directly.
 
@@
 However, the safety margin in the two-stage procedure is a user's choice and is not easy to determine before running extensive numerical experiments.
+
 Our single-stage procedure uses the metamodel predictions to estimate the risk measure directly.
@@
 The versatility of neural networks could unlock new insights across a broad spectrum of financial and actuarial applications.
+
+In this chapter, we have demonstrated the potential of deep neural network metamodels in nested simulation procedures for delta hedging of variable annuity contracts and have shown that they can be used to estimate risk measures with high accuracy and efficiency.
+We have assumed a zero transaction cost model for our monthly rebalancing.
+In practice, transaction costs can be significant and can affect the hedging strategy.
+In the next chapter, we will extend our study to include transaction costs in the hedging strategy and investigate the impact of transaction costs on the hedging performance and the risk measures of the hedging error.
+We will also explore the use of deep neural network models as reinforcement learning agents to optimize the hedging strategy by directly interacting with the financial market and maximize the hedging performance.

### 2024-09-26 project3/draft.tex
new

@@
-\chapter{Model-Free Deep Hedging of Variable Annuities}
+\chapter{Model-Free Deep Hedging of Variable Annuities} \label{chap:project3}
 
@@
 
-Reinforcement Learning (RL) is a branch of machine learning that focuses on training algorithms, known as agents, to make a sequence of decisions. 
-The agent learns to achieve a goal in an uncertain, potentially complex environment by trial and error, using feedback from its own actions and experiences. 
-Unlike supervised learning, where training data is labeled with the correct answers, in RL, an agent is provided with rewards or punishments as signals for its actions.
+In the evolving landscape of financial markets, insurance products such as variable annuities (VAs) have gained significant interest due to their ability to provide both investment growth and guaranteed benefits.
+Managing the risks associated with these products, especially in volatile market conditions, is a complex task that demands sophisticated financial modeling techniques. 
+Reinforcement Learning (RL) has emerged as a powerful tool for addressing such complexities.
+With the recent advancement in deep learning, deep neural network (DNN) architectures have been successfully applied to RL problems, leading to the development of deep reinforcement learning (DRL) algorithms.
+These algorithms have demonstrated remarkable success decision-making tasks that must be optimized over time. 
+In the context of managing VAs, DRL has shown promise in optimizing hedging strategies where long-term financial and policyholder decisions interact dynamically with changing market conditions.
 
-The core of RL revolves around the concept of the agent interacting with its environment over time, aiming to maximize the cumulative reward. 
-This process involves observing the state of the environment, selecting and performing actions, and receiving rewards or penalties in response to those actions. 
-The agent's objective is to learn a mapping from states to actions that maximizes this cumulative reward, which is often referred to as a policy. 
-One of the fundamental frameworks for modeling RL problems is the Markov Decision Process (MDP). 
-An MDP provides a mathematical formulation of the decision-making process, characterized by states, actions, rewards, and transition probabilities. 
-Solving an MDP involves finding a policy that maximizes some function of the expected rewards, typically the expected cumulative reward over time.
+Reinforcement learning is a branch of machine learning in which an agent learns to make sequential decisions by interacting with its environment. 
+Through trial and error, the agent receives feedback in the form of rewards or penalties, allowing it to learn an optimal policy for achieving long-term goals. 
+In financial and actuarial contexts, RL has been applied to portfolio optimization, asset allocation, and risk management. 
+In a dynamic hedging problem, the agent is referred to as the decision-maker that tries to minimize financial risks over time horizon by adjusting the hedging portfolio based on the current environment, which is the current state of the financial markets and actuarial assumptions.
+By intergrating deep neural network, DRL extends this framework by enabling the agent to handle high-dimensional and complex environments. 
+DRL has shown particular promise in finance because of its ability to process vast amounts of financial data and discover intricate patterns in market dynamics.
+Despite their success, DRL faces practical limitations when applied to real-world financial markets.
+Its most significant drawback is the requirement for extensive data and computational resources.
+Training a DRL agent from scratch requires a large dataset along with considerable computational time for exploration and learning.
+This is especially problematic for variable annuities, which are long-term insurance products that are sensitive to market fluctuations and underlying actuarial assumptions.
+Given that financial markets are highly dynamic, frequent retraining to account for new market regimes becomes necessary, which can lead to prohibitively high costs and computational inefficiency.
+Moreover, using historical data leads to overfitting to the past. 
+An overfitting model can lead to suboptimal hedging strategies that perform poorly in changing market conditions.
 
-RL algorithms can be broadly categorized into two types: model-based RL and model-free RL. 
-Model-based RL utilize a model of the environment to simulate the outcomes of actions, enabling planning and decision-making with fewer interactions with the environment. 
-The biggest drawback of model-based RL is model bias. 
-In practice, the ground-true model is usually not available.
-By using a model, an RL agent can exploit the model bias, which leads to suboptimal performance in the real environment.
-Conversely, model-free RL learn directly from interactions with the environment.
-Without relying on a model, model-free RL algorithms are more straightforward implement and tune.
-
-A compelling application of RL is dynamic hedging, where the complexity and uncertainty of financial markets make traditional static models inadequate.
-RL's adaptability and learning capabilities offer a promising solution to dynamically adjust hedging strategies in response to market movements and assumptions changes.
-In particular, model-free RL has the potential to enhance risk management practices by developing robust strategies that can adapt in real-time.
-Some popular RL algorithms include Proximal Policy Optimization (PPO), Deep Q-Networks (DQN), and Deep Deterministic Policy Gradient (DDPG).
-
-In this paper, we propose a model-free RL algorithm to improve the risk management of variable annuities (VAs).
-VAs are popular insurance products that add investment features to an insurance contract.
-Hedging VAs is particularly challenging due to multiple sources of risk.
-Our model-free RL approach aims to learn a hedging policy without directly accessing models of the underlying risk factors.
-By interacting with an enviornment, the hedging policy can effectively manage the risks of VAs in a changing market environment.
+Transfer learning (TL) offers a compelling solution to the challenges posed by existing DRL approaches. 
+The core idea of TL is to leverage knowledge from previously solved tasks and apply that knowledge to new but related tasks.
+In the context of financial modeling, this means that instead of training an RL agent from scratch every time underlying assumptions change, the model can utilize the knowledge gained from past market environments to accelerate the learning process under the new environment.
+TL in financial markets is particularly advantageous for addressing the data scarcity problem. 
+By transferring existing knowledge from similar environments, TL improves model performance in situations where historical data is limited or noisy. 
+This allows models using TL to be both more accurate and computationally efficient. 
+Additionally, TL enhances the robustness of models by allowing continuous learning. 
+Instead of retraining a deep RL model from scratch when market conditions shift, TL enables the reuse of pre-trained models, facilitating faster adaptation to new environments while avoiding overfitting to past conditions.
+In the risk management of variable annuities, transfer learning enables quicker adaptation to changing financial and actuarial assumptions by reusing information obtained from another set of related assumptions, such as the management of similar financial instruments or different market regimes.
+A DRL agent equipped with transfer learning can adjust its strategies in response to new market data, making the model more adaptive and responsive without the need for costly retraining.
+More specifically, a DRL agent trained to manage variable annuities for a GMMB contract can apply its learned strategies to a GMWB contract with the same financial assumptions. 
+A DRL agent trained for a VA product on a Black-Scholes asset model can transfer its knowledge to the training of a similar product on a stochastic volatility model.
+This approach significantly reduces the computational costs associated with the training of new VA products with different assumptions and improves the generalization of the model to unseen market conditions.
+By integrating transfer learning with existing DRL frameworks, we can eliminate the inefficiencies of training models from scratch, provide faster adaptability to new market conditions, and enhance the scalability and computational efficiency of financial models.
+This approach offers a more robust and practical solution for managing variable annuities in dynamic and volatile financial markets.
 
@@
 
-\section{Markov Decision Process}
+\section{Markov Decision Process for Hedging VAs}
 
@@
 \end{equation}
-It is worth noting that learning to hedge GMWB is easier for an RL agent due to the absense of reward at maturity (long-term feedback).
 
@@
 
-\section{Model-Based and Model-Free RL}
+\section{Exising RL Algorithms and Their Limitations}
 
@@
 
+In the context of deep hedging, various research has been conducted to improve the hedging strategies on real-world data by leveraging knowledge from simulated data.
+Most of the research uses the offline-online learning approach, where the hedging strategies are first trained with simulation data, but updated in real-time based on new market information and continuous learning to adapt to changing market dynamics.
+The most relevant paper to our study is~\cite{xiao2021optimal}, which use policy gradient algorithms to train hedging strategies for European options with simulation data from Heston model and then updated in real-time hedging S\&P 500 index options.
+To the best of our knowledge, no research has been conducted to improve the hedging strategies with the state-of-the-art transfer learning techniques.
+This section introduces some transfer learning techniques that are relevant to our task of hedging VAs.
+
+\subsection{Reward Shaping}
+
+In the context of hedging VAs using deep reinforcement learning and transfer learning, reward shaping becomes a crucial technique. 
+It involves modifying the reward function in the target domain to incorporate additional guidance, which often leads to more efficient learning and better performance.
+This technique can be particularly useful for managing the complex risks associated with VAs, as it can guide the learning process towards strategies that are more effective in hedging these products.
+
+One way to implement reward shaping in this context is by introducing auxiliary rewards that reflect the performance of hedging strategies learned from the source domains.
+Reward shaping learns an auxiliary reward function $\mathcal{R}_s: \mathcal{S} \times \mathcal{A} \times \mathcal{S} \rightarrow \mathbb{R}$ from the source domains.
+The auxiliary reward function is then used to shape the reward function in the target domain, $\mathcal{R}'_t = \mathcal{R}_t + \mathcal{R}_s$, by incorporating the insights gained from the source domains.
+
+Some popular reward shaping techniques include potential-based reward shaping~\citep{ng1999policy}, potential based state-action advice~\citep{wiewiora2003principled}, dynamic value function advice~\citep{harutyunyan2015expressing}.
+
+\subsection{Policy Transfer}
+
+The most straightforward approach to transfer learning is to directly transfer the policy learned from the source domains to the target domain via policy distillation.
+Policy distillation is a technique that transfers the knowledge from a teacher policy to a student policy by training the student policy to mimic the teacher policy up to a certain extent.
+The teacher policy is learned from the source domains, and the student policy learns the hedging strategies in the target domain while guided by the teacher policy.
+In the Distral algorithm~\citep{teh2017distral}, the student policy maximizes a multi-task objective:
+$\max_{\phi} \sum_{i=1}^K \mathcal{J}(\pi_\phi, \pi_{E_i})$, where
+
+\begin{equation}
+    \mathcal{J}(\pi_\phi, \pi_{E_i}) = \sum_{t=0}^\infty \mathbb{E}_{s_t \sim \mu_0^t, a_t \sim \pi_\phi} \left[ \gamma^t R_{t+1} + \frac{\alpha}{\beta} \log \pi_{\phi}(a_t|s_t) - \frac{1}{\beta}log \pi_{E_i}(a_t|s_t) \right],
+\end{equation}
+
+where a set of $K$ teacher policies $\pi_{E_i}$ are learned from the source domains, and the student policy $\pi_\phi$ is learned on the target domain.
+$\alpha$ and $\beta$ are hyperparameters that control the trade-off between mimicking the teacher policies and exploring the target domain.
+
+\subsection{Evaluation Metrics}
+
+The metrics discussed for evaluating transfer learning approaches focus on two key aspects: mastery and generalization. 
+Mastery assesses the agent's final performance level in the target domain, indicating how effectively it has learned a specific task from previous knowledge. 
+Some common metrics for evaluating mastery include:
+
+\begin{itemize}
+    \item \textbf{Asymptotic performance:} the final reward of the agent in the target domain.
+    \item \textbf{Transfer ratio:} the ratio of the agent's performance in the target domain with and without transfer learning.
+\end{itemize}
+
+Generalization, on the other hand, refers to the agent's ability to quickly adapt its learned knowledge to the target domain.
+
+\begin{itemize}
+    \item \textbf{Jumpstart performance:} the initial reward of the agent in the target domain.
+    \item \textbf{Accumulated reward:} the total area under the reward curve over time in the target domain.
+    \item \textbf{Time to threshold:} the time it takes for the agent to reach a certain performance threshold in the target domain.
+    \item \textbf{Performance with fixed epochs:} the agent's performance in the target domain after a fixed number of epochs.
+\end{itemize}
+
 \section{Numerical Experiments}

### 2024-09-27 conclusion.tex
new

@@
 In this thesis, we have discussed the use of nested simulation procedures for risk management applications of financial derivatives and insurance products.
+We have shown that the nested simulation framework can be used to efficiently estimate the risk measures of complex financial products, such as variable annuities, by combining machine learning-based metamodels with nested simulations.
+
+In this thesis, we have explored the application of nested simulation procedures in the risk management of financial derivatives and insurance products, with a particular focus on variable annuity contracts featuring Guaranteed Minimum Maturity Benefits and Guaranteed Minimum Withdrawal Benefits.
+Recognizing the computational challenges inherent in the standard nested simulation procedure, especially when estimating tail risk measures for complex financial products, we proposed an innovative approach that integrates machine learning-based metamodels into the nested simulation framework.
+
+Our primary contribution lies in the development and implementation of long short-term memory networks as metamodels for the inner simulations within the nested simulation procedure. 
+By employing LSTMs, we effectively approximated the contract losses associated with dynamic hedging strategies under various market scenarios.
+This approach significantly reduced computational complexity while maintaining high levels of accuracy in risk estimation.
+The LSTM metamodels captured the temporal dependencies and nonlinear relationships present in financial time series data, enabling efficient estimation of tail risk measures.
+
+Through extensive numerical experiments and sensitivity analysis, we demonstrated that our LSTM-based nested simulation procedure provides accurate and computationally efficient estimates of the tail risk associated with VA contracts.
+The results showed that the metamodels could effectively replace the computationally intensive inner simulations, reducing the overall runtime without compromising the precision of risk assessments.
+This efficiency gain is particularly valuable for insurers and financial institutions that require timely and accurate risk evaluations to meet regulatory requirements and make informed risk management decisions.
+
+Additionally, we investigated the adaptability of our approach to changing market conditions and different VA contract features. 
+By incorporating transfer learning techniques, we enabled rapid adaptation of the LSTM metamodels to new contracts and evolving market dynamics. 
+This aspect of our research highlights the potential for machine learning models to not only improve computational efficiency but also enhance the flexibility and responsiveness of risk management practices in the face of market volatility.
+
+The thesis is an attempt to bridge the gap between traditional simulation schemes and modern machine learning techniques in the context of financial risk management.
+By bridging advanced machine learning techniques with financial risk management practices, this thesis contributes to the development of more efficient, adaptable, and robust methodologies that are essential in the rapidly evolving landscape of quantitative finance and actuarial science.

### 2024-09-27 futureWork/rlHedging.tex
new

--- 2024-09-26 project3/draft.tex
@@
-\chapter{Model-Free Deep Hedging of Variable Annuities} \label{chap:project3}
+\chapter{Future Work: Deep Hedging Variable Annuities with Transfer Learning} \label{chap:futureWork}
 
-\section{Introduction}
-
-In the evolving landscape of financial markets, insurance products such as variable annuities (VAs) have gained significant interest due to their ability to provide both investment growth and guaranteed benefits.
+In the evolving landscape of financial markets, insurance products such as VAs have gained significant interest due to their ability to provide both investment growth and guaranteed benefits. 
 Managing the risks associated with these products, especially in volatile market conditions, is a complex task that demands sophisticated financial modeling techniques. 
 Reinforcement Learning (RL) has emerged as a powerful tool for addressing such complexities.
-With the recent advancement in deep learning, deep neural network (DNN) architectures have been successfully applied to RL problems, leading to the development of deep reinforcement learning (DRL) algorithms.
+With the recent advancement in deep learning, DNN architectures have been successfully applied to RL problems, leading to the development of deep reinforcement learning (DRL) algorithms.
 These algorithms have demonstrated remarkable success decision-making tasks that must be optimized over time. 
@@
 Transfer learning (TL) offers a compelling solution to the challenges posed by existing DRL approaches. 
-The core idea of TL is to leverage knowledge from previously solved tasks and apply that knowledge to new but related tasks.
-In the context of financial modeling, this means that instead of training an RL agent from scratch every time underlying assumptions change, the model can utilize the knowledge gained from past market environments to accelerate the learning process under the new environment.
+Similar to the TL framework proposed in Chapter~\ref{chap:project3}, TL can also be applied to DRL to accelerate the training.
+In the context of financial modeling, instead of training an RL agent from scratch every time underlying assumptions change, the model can utilize the knowledge gained from past market environments to accelerate the learning process under the new environment.
 TL in financial markets is particularly advantageous for addressing the data scarcity problem. 
@@
 
-The rest of the paper is organized as follows:
+The rest of the chapter is organized as follows: 
+% Section~\ref{sec:MDP} introduces the mathematical formulation for hedging VAs and defines the key components of the framework.
+% Section~\ref{sec:RLAlgorithms} provides an overview of existing RL algorithms and their limitations in the context of hedging VAs.
+% Section~\ref{sec:PPO} introduces the proximal policy optimization algorithm and its application to the hedging of VAs.
+% Section~\ref{sec:TL} presents the transfer learning framework for accelerating the training of DRL agents in the dynamic hedging of VAs.
+% Section~\ref{sec:experiments} presents the experimental setup and results, comparing the performance of transfer learning with training from scratch.
+% Finally, Section~\ref{sec:FutureDirections} concludes the chapter and discusses future research directions.
 
-\section{Markov Decision Process for Hedging VAs}
+\section{Markov Decision Process for Hedging VAs} \label{sec:MDP}
 
-An MDP is defined by the tuple $\mathcal{M} = (\mathcal{S}, \mathcal{A}, \mathcal{P}, \mathcal{R}, \gamma)$, where:
+A Markov Decision Process (MDP) provides a mathematical framework for modeling decision-making in stochastic environments over time. 
+By formulating the VA hedging problem as an MDP, we can utilize RLalgorithms to learn optimal hedging policies directly from data.
+AnMDP is defined by the tuple $\mathcal{M} = (\mathcal{S}, \mathcal{A}, \mathcal{P}, \mathcal{R}, \gamma)$, where:
 
@@
 The objective in an MDP is to find a policy, $\pi: \mathcal{S} \rightarrow \mathbb{P}(\mathcal{A})$, that maximizes the cumulative reward over time.
-A Markov Decision Process (MDP) provides a mathematical framework for solving sequential decision-making tasks in an enviornment where outcomes are partly random and partly under the control of a hedging agent.
+A MDP provides a mathematical framework for solving sequential decision-making tasks in an enviornment where outcomes are partly random and partly under the control of a hedging agent. 
 For hedging VAs, the asset dynamics and the mortality model are not controlled by the agent, but the agent controls the cumulative reward by deciding on the hedging weights.
@@
 
-\section{Exising RL Algorithms and Their Limitations}
+\section{Exising RL Algorithms and Their Limitations} \label{sec:RLAlgorithms}
 
@@
 This simplifies the planning as complete trajectories can be simulated without the need of a planning algorithm.
-In contrast to AlphaZero, deep hedging~\citep{buehler2019deep} uses the model itself to simulate the complete trajectories following the transition probabilities of the MDP.
-Let $(\tilde{\mathbf{s}}_0, \tilde{\Delta}_0, \tilde{\mathbf{s}}_1, \tilde{\Delta}_1, \ldots, \tilde{s}_T)$ and $\tilde{\mathcal{R}} = (R_1, \ldots, R_t)$ be a trajectory and the hedging reward of the MDP, respectively.
-The neural network $f_{\theta}$ stores a global solution, i.e., it takes the previous state and hedging weight as input and outputs the hedging weight at the current state.
-\begin{equation} \label{eq3:deephedging}
-    \mathbf{\Delta}_t = f_{\theta}(\mathbf{s}_t), \quad L(\theta) = \rho(L) = \rho(-\mathcal{R}) = \rho(- \sum_{t=0}^{T} \gamma^t R_t),
-\end{equation}
-where $\rho(L)$ is a convex risk measure of the total present liability $L$. 
-The risk measure $\rho$ serves as a model of the MDP that 
+In contrast to AlphaZero, deep hedging~\citep{buehler2019deep} uses monte carlo simulations to generate sample paths of asset dynamics.
+These simulations are conducted based on predefined stochastic asset models. 
+The parameters and structure of these models are specified in advance, dictating the behavior of the simulated asset prices.
+
 A common choice of $\rho$ is a CVaR.
@@
 In other words, planning is done through $\rho$, which measures the performance of a hedging policy over a batch of complete trajectories.
+The neural network, representing the hedging policy, is trained using the data generated from these simulations. 
+The objective is to learn a strategy that minimizes a tail risk measure of the total present liability.
+Consequently, the learned policy is inherently tailored to the characteristics of the model used in the simulations.
 The ability to know the future outcomes of the hedging policy before they are actually observed and the use of a risk measure to guide the training of the neural network are the key features of model-based RL.
+These models describe how asset prices evolve over time, and more importantly, they are used to predict future states based on current information.
+While model-based approaches can be powerful when the model accurately reflects reality, they are susceptible to model risk, i.e., the risk that the chosen model is incorrect or incomplete. 
+It can lead to suboptimal hedging strategies if the real market deviates from the model assumptions.
+
 For hedging VAs,~\cite{xu2020variable} propose a deep hedging algorithm that falls into this category of model-based RL.
@@
 ~\cite{carbonneau2021deep} extends the model-based approach to hedging long-term financial derivatives and compares the performance of deep hedging strategies trained with different cost functions.
-In Equation~\ref{eq3:deephedging}, the state space of the MDP contains the previous hedging weight.
+In deep hedging~\citep{buehler2019deep} the state space of the MDP contains the previous hedging weight.
 A more recent paper by~\cite{imaki2021no} proposes a new network architecture that removes the previous hedging weight from the state space by introducing a no-transaction band.
@@
 Model-based RL struggles in a rough volatility model due to difficulties in designing a suitable cost function.~\cite{horvath2021deep} shows that a standard implementation of deep hedging can lead to suboptimal hedging performance in a discretized rough Bergomi model.
-The CVaR-based cost function needs to be redesigned to account for jump risks, and it is still an open question.
-In summary, model-based RL algorithms like deep hedging do not depend on the asset model, i.e., they are \textbf{model-independent}.
-However, they are not \textbf{model-free}.
-For example, deep hedging builds its own model of the hedging environment to plan the hedging strategy ahead of time using a neural network and a risk measure.
-Designing a suitable risk measure for such a network is necessary but challenging.
+
 In contrast, a model-free approach does not require a explicit design for different asset dynamics, making it more flexible and adaptable to different market conditions and more robust to model misspecification.
@@
 In a model-free reinforcement learning approach, the agent is a trial-and-error learner that interacts with the environment to learn the optimal policy by iteratively updating the policy and the value function based on the observed states, actions, and rewards.
-For hedging VAs, the agent does not have access to a planning algorithm or a model of the underlying risk factors, and it must learn the optimal policy by directly interacting with the environment.
-Figure~\ref{fig3:RLMethods} illustrates the critical difference between model-based and model-free RL methods.
+For hedging VAs, the agent does not have access to a planning algorithm or the underlying stochastic asset model, and it must learn the optimal policy by directly interacting with the environment.
 
-\begin{figure}[ht!]
-    \centering
-    \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{./project3/tikz/modelBased.pdf}
-        \caption{Model-based RL (Deep Hedging)}
-        \label{subfig3:mbRL}
-    \end{subfigure}
-    \hspace{1cm}
-    \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{./project3/tikz/modelFree.pdf}
-        \caption{Model-free RL}
-        \label{subfig3:mfRL}
-    \end{subfigure}
-    \caption{Model-based and Model-free RL Methods}
-    \label{fig3:RLMethods}
-\end{figure}
-
-A model-based RL uses a model of the environment that enables decision-making with future situations that have not been experienced by the agent.
-However, the model bias can lead to suboptimal performance in the real environment.
-In contrast, a model-free RL learns directly from the environment without relying on a model, which makes it more flexible and robust to model misspecification.
 Model-free RL algorithms gain its popularity in robotics tasks, where transition probabilities in the environment are unknown and can be affected by the agent's actions.
@@
 A policy gradient method uses policy gradient theorem to update the policy by performing gradient ascent with respect to the policy parameters.
+
+\begin{algorithm}[H] \label{alg:REINFORCE}
+    \caption{Vanilla Policy Gradient (REINFORCE)}
+    \begin{algorithmic}[1]
+    \STATE \textbf{Initialize} policy parameters $\theta$ arbitrarily.
+    \STATE  \textbf{For} {iteration $k=0, 1,2,\ldots$} \textbf{do}
+        \STATE \quad  Collect a set of $\mathcal{D}_k$ by sampling from the enviornment with policy $\pi_\theta$.
+        \STATE  \quad Compute the rewards $R_t$ for each trajectory in $\mathcal{D}_k$ for $t=0,1,\ldots,T$.
+        \STATE  \quad Update the policy parameters $\theta_{k+1}$ by 
+        \begin{equation*}
+            \theta_{k+1} = \theta_k + \alpha \frac{1}{|\mathcal{D}_k|T} \sum_{\mathcal{\kappa} \in \mathcal{D}_k} \sum_{t=0}^{T} \nabla_\theta \log \pi_\theta(a_t | s_t) R_t
+        \end{equation*}
+    \STATE  \textbf{End For}
+    \end{algorithmic}
+\end{algorithm}
+
+Algorithm~\ref{alg:REINFORCE} shows the REINFORCE algorithm~\citep{sutton1999policy}, a classic policy gradient method that updates the policy by performing gradient ascent with respect to the policy parameters.
+When training on real-world data, deep hedging of~\cite{buehler2019deep} effectively becomes a model-free policy gradient methods. 
+The policy is updated by performing gradient ascent with respect to the policy parameters to maximize the expected reward over time, where the reward function is designed to be the negative of a tail risk measure of the total present liability.
+
 Representative algorithms include the Trust Region Policy Optimization (TRPO) algorithm proposed by~\cite{schulman2015trust} and the Proximal Policy Optimization (PPO) algorithm proposed by~\cite{schulman2017proximal}.
@@
 
-\section{Hedging VAs with a PPO Agent}
+\section{Hedging VAs with a PPO Agent} \label{sec:PPO}
 In a hedging problem, an insurer aims to find a policy $\pi$ that maximize the expected reward over time.
@@
 \end{equation}
-The difference between a feedforward neural network (FNN) and a LSTM network is illustrated in Figure~\ref{fig3:nn}.
-
-\begin{figure}[ht!]
-    \centering
-    \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{./project3/tikz/fnn.pdf}
-        \caption{FNN}
-        \label{subfig3:fnn}
-    \end{subfigure}
-    \hspace{1cm}
-    \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{./project3/tikz/lstm.pdf}
-        \caption{LSTM}
-        \label{subfig3:lstm}
-    \end{subfigure}
-    \caption{Neural Network Architectures}
-    \label{fig3:nn}
-\end{figure}
 
@@
     \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{./project3/tikz/ppo_diagram.pdf}
+        \includegraphics[width=\textwidth]{./futureWork/tikz/ppo_diagram.pdf}
         \caption{regular PPO}
@@
     \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{./project3/tikz/recurrentppo_diagram.pdf}
+        \includegraphics[width=\textwidth]{./futureWork/tikz/recurrentppo_diagram.pdf}
         \caption{Recurrent PPO with LSTM}
@@
 However, the sequantial nature of the LSTM is not suitable for parallel computation, which slows down the training process.
+
+\section{Transfer Learning for Hedging VAs} \label{sec:TransferLearning}
 
@@
 Some common metrics for evaluating mastery include:
-
-\begin{itemize}
-    \item \textbf{Asymptotic performance:} the final reward of the agent in the target domain.
-    \item \textbf{Transfer ratio:} the ratio of the agent's performance in the target domain with and without transfer learning.
-\end{itemize}
-
 Generalization, on the other hand, refers to the agent's ability to quickly adapt its learned knowledge to the target domain.
+In the context of risk management, generalization is more important than mastery, as the agent must be able to quickly adapt to changing market conditions and new financial products.
+Some common metrics for evaluating generalization include:
 
@@
 
-\section{Numerical Experiments}
+\section{Numerical Experiments} \label{sec:Experiments}
 
 We present a numerical experiment to demonstrate the effectiveness of the model-free PPO algorithm for hedging VAs with transaction costs.
-We consider a VA contract with a maturity of $T=240$ months and a guaranteed minimum maturity benefit (GMMB) rider with a simulation environment described in Section~\ref{subsec:VASimulation}.
+We consider a VA contract with a maturity of $T=240$ months and a GMMB rider with a simulation environment described in Section~\ref{subsec:VASimulation}.
 The simulation enviornment is implemented in Python using the OpenAI Gym framework~\citep{brockman2016openai}, and the neural networks are programmed using the PyTorch library~\citep{paszke2019pytorch}.
@@
 The underlying asset price $S_t$ is modeled as a geometric Brownian motion (GBM) with a drift rate $\mu$ and a volatility $\sigma$.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.9\textwidth]{./futureWork/figures/CVaR_histories.png}
+    \caption{Hedging performance of deep hedging with transfer learning}
+    \label{fig3:dh-transfers}
+\end{figure}
+
+Figure~\ref{fig3:dh-transfers} illustrates the hedging performance of the deep hedging algorithm with transfer learning for hedging VAs with a GMMB rider.
+The first deep hedging agent is directly trained on the Heston asset model, and the second deep hedging agent is trained with transfer learning from the GBM model.
+The figure plot the 95\%-CVaR of hedging errors against training epochs for both agents.
+The deep hedging agent with transfer learning outperforms the deep hedging agent trained on the Heston model in both mastery and generalization.
+The agent with transfer learning achieves a lower loss in the target domain and adapts more quickly to the new environment, indicating that the agent has learned a more robust hedging strategy that can be effectively applied to a more complex environment.
+
+For the PPO agent, we use a regular PPO and a recurrent PPO with an LSTM component to capture the temporal dependencies in the data.
 The weights of the value network and the policy network are initialized with orthogonal initialization~\citep{engstrom2020implementation} with scaling $\sqrt{2}$ and the bias terms set to zero.
@@
     \centering
-    \includegraphics[width=\textwidth]{./project3/figures/PPO_DH.png}
+    \includegraphics[width=0.5\textwidth]{./futureWork/figures/PPO_DH.png}
     \caption{Hedging performance of recurrent PPO and deep hedging}
@@
     \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{./project3/figures/PPOs_GBM.png}
+        \includegraphics[width=\textwidth]{./futureWork/figures/PPOs_GBM.png}
         \caption{GBM}
@@
     \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{./project3/figures/PPOs_GBMRS.png}
+        \includegraphics[width=\textwidth]{./futureWork/figures/PPOs_GBMRS.png}
         \caption{Regime-switching GBM}
@@
     \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{./project3/figures/PPO_cost_001.png}
+        \includegraphics[width=\textwidth]{./futureWork/figures/PPO_cost_001.png}
         \caption{$C = 0.001$}
@@
     \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{./project3/figures/PPO_cost_02.png}
+        \includegraphics[width=\textwidth]{./futureWork/figures/PPO_cost_02.png}
         \caption{$C = 0.02$}
@@
     \centering
-    \includegraphics[width=\textwidth]{./project3/figures/PPO_anchor.png}
+    \includegraphics[width=\textwidth]{./futureWork/figures/PPO_anchor.png}
     \caption{Hedging performance of recurrent PPO with or without anchor}
@@
     \centering
-    \includegraphics[width=\textwidth]{./project3/figures/PPO_GMWB.png}
+    \includegraphics[width=\textwidth]{./futureWork/figures/PPO_GMWB.png}
     \caption{Hedging performance of recurrent PPO with GMWB}
@@
 
-\section{Conclusion}
+\section{Future Directions} \label{sec:FutureDirections}
+
+The proposed future work of this thesis aims to investigate how transfer learning can be effectively integrated into the training of PPO agents for dynamic hedging of VA contracts. 
+The primary goal is to enhance the adaptability and efficiency of hedging strategies in response to new VA products and changing market conditions.
+
+The first objective is to establish a systematic approach for transferring policies learned by PPO agents from source tasks to target tasks in the context of dynamic hedging. 
+Source tasks may involve hedging a GMMB under a specific market model, while target tasks could entail hedging a GMWB under a different market model.
+
+To achieve this, the research will explore methodologies such as policy distillation, where knowledge from a pre-trained "teacher" policy is transferred to a "student" policy~\citep{rusu2015policy}.
+Policy distillation has been effective in compressing and transferring knowledge between networks, improving learning efficiency in RL settings.
+Another avenue is the use of pre-trained model initialization, wherein the policy network trained on the source task initializes the policy for the target task. 
+This method leverages the shared underlying structures between tasks, potentially accelerating convergence and improving performance 
+The framework will also consider feature representation transfer, aiming to reuse learned representations of market dynamics and policyholder behaviors between tasks. 
+By capturing common patterns across different contracts and market models, the PPO agent can more effectively generalize to new scenarios~\citep{bengio2012deep}.
+
+By addressing these objectives, the research aims to advance the field of financial risk management through the development of adaptive and efficient hedging strategies for variable annuities.
+The integration of transfer learning into PPO agents has the potential to significantly reduce computational costs and improve the robustness of hedging policies in dynamic market environments.

### 2024-09-27 introduction.tex
new

@@
 
-\section{Metamodeling for Monte Carlo Simulation Scheme}
+\section{Managing Risk of Variable Annuity with Nested Simulation}
+
+VA contracts are index-linked insurance products that offer policyholders the potential for capital appreciation through exposure to equity markets while providing guarantees that protect against downside risk.
+These products have gained significant interest as they address the needs of individuals seeking both wealth accumulation and financial security, especially in the context of retirement planning.
+The most interesting feature of VAs is embedded guarantees that ensure a specified minimum benefit regardless of market performance.
+Two VA contracts that are most relevant to this thesis are Guaranteed Minimum Maturity Benefit (GMMB) and the Guaranteed Minimum Withdrawal Benefit (GMWB). 
+The GMMB guarantees that at the maturity of the contract, the policyholder will receive no less than the initial investment or a predetermined minimum amount. 
+The GMWB allows policyholders to withdraw a specified percentage of their benefit base each period during the contract horizon~\citep{hardy2003investment}.
+While these guarantees enhance the attractiveness of VAs to consumers by offering protection against market downturns and ensuring income stability, they introduce substantial financial risks to insurers.
+The embedded options within GMMBs and GMWBs expose insurers to market risk, longevity risk, and policyholder behavior risk. 
+Effective management of these risks is crucial for insurers to maintain solvency and meet regulatory capital requirements.
+
+One of the primary risk management strategies employed by insurers to mitigate the financial risks associated with VAs is dynamic hedging. 
+Dynamic hedging involves frequently adjusting a portfolio of financial instruments to offset changes in the value of the guarantees due to market movements~\citep{hull2016options}. 
+This strategy aims to neutralize the sensitivity of the insurer's liability to market fluctuations by constructing a hedging portfolio that replicates the cash flows of the guarantees.
+However, dynamic hedging introduces complexity in estimating the insurer's overall risk exposure, especially concerning extreme market events or tail risks.
+Estimating tail risk in the context of dynamic hedging of VAs is challenging, as it requires the stochastic modeling of the financial market and the accurate loss estimation of the hedging portfolio under various market scenarios.
+Nested simulation has emerged as a robust method for estimating risk measures in such complex settings~\citep{gordy2010nested}.
+In nested simulation, an outer simulation generates a set of market scenarios over the contract horizon, while an inner simulation estimates the contract loss in each scenario.
+By combining the results of the inner simulations across the outer scenarios, nested simulation provides an accurate estimate of the tail risk of the VA contract.
+
+Despite its robustness, nested simulation is computationally intensive, often requiring significant computational resources and time. 
+Each scenario in the outer simulation requires numerous inner simulations to accurately estmate contract loss. 
+This computational burden poses practical limitations, especially when high precision in tail risk estimation is required.
+To address this challenge, metamodeling techniques can be employed to approximate the inner simulation model and reduce the computational cost of nested simulation.
+
+\section{Metamodeling for Monte Carlo Simulation}
+
+Metamodeling, also known as surrogate modeling, is a technique used to approximate complex simulation models with simpler, computationally efficient models. 
+In the context of Monte Carlo simulations, metamodels are models of models that aim to reduce computational costs by creating an approximate model that can quickly predict simulation outputs based on input variables~\citep{kleijnen2018design}.
+This section introduces metamodeling for Monte Carlo simulation, elaborates on its methodologies, and highlights its importance in practical applications.
+
+Monte Carlo simulations are widely used for modeling and analyzing complex systems that are probabilistic in nature. 
+These simulations often require a significant amount of computational resources, especially when high accuracy or numerous iterations are necessary~\citep{glasserman2004monte}. 
+Metamodeling addresses this challenge by constructing an approximate model (metamodel) that emulates the behavior of the original simulation model with much less computational effort.
+The metamodel serves as a predictive model that maps input variables to output responses. 
+Learning from a set of simulation runs, the metamodel can generalize and predict outputs for new inputs without running the full simulation.
+Metamodeling is particularly useful when the simulation model is computationally expensive. 
+By replacing the simulation model with a metamodel, the computational cost of evaluating the model can be significantly reduced, enabling faster analysis and decision-making.
+
+The process of metamodeling generally involves:
+
+\begin{enumerate} 
+    \item \textbf{Design of Experiments}: Selecting input combinations to run the original simulation and collect data. 
+    \item \textbf{Building the Metamodel}: Using the collected data to train a surrogate model that approximates the simulation. 
+    \item \textbf{Validation}: Assessing the metamodel's accuracy and generalization capability.
+    \item \textbf{Application}: Using the metamodel to predict simulation outputs for new input combinations.
+\end{enumerate}
+
+The development of advanced machine learning algorithms, particularly deep learning techniques, has significantly enhanced metamodeling approaches for Monte Carlo simulations, especially in high-dimensional and complex problem settings.
+Example use cases for machine learning include~\cite{jin2020deep}, ~\cite{tang2020deep}, and~\cite{rosen2012metamodeling}.
+These methods offer powerful tools for capturing intricate patterns and nonlinear relationships that traditional metamodeling techniques might struggle to model effectively.
+In the following sections, we discuss machine learning algorithms in the context of metamodeling for Monte Carlo simulations and their applications in risk management.
 
@@
 This thesis focuses on regression models for risk management applications, where the goal is to predict a continuous target variable based on one or more input features.
-Given a dataset of $n$ observations $\{(x_1, y_1), (x_2, y_2), \ldots, (x_n, y_n)\}$, where $x_i \in \mathbb{R}^d$ is the $d$-dimensional input feature vector and $y_i \in \mathbb{R}$ is the target variable, a supervised learning algorithm aims to learn a function $f: \mathbb{R}^d \rightarrow \mathbb{R}$ that best predicts the target variable $y$ given the input features $x$.
+Given a dataset of $n$ observations $\{(x_1, y_1), (x_2, y_2), \ldots, (x_n, y_n)\}$, where $x_i \in \mathbb{R}^d$ is the $d$-dimensional input feature vector and $y_i \in \mathbb{R}$ is the target variable, a supervised learning algorithm aims to learn a function $f(;\theta): \mathbb{R}^d \rightarrow \mathbb{R}$ that best predicts the target variable $y$ given the input features $x$ with a set of function parameters $\theta$.
 
@@
 Nevertheless, all supervised learning models can be evaluated on a similar set of metrics.
-The learning process involves minimizing a loss function $l(f(x),y)$ over the training data, which quantifies the difference between the predicted outputs and the true outputs. 
+The learning process involves minimizing a loss function $l(f(x; \theta),y)$ over the training data, which quantifies the difference between the predicted outputs and the true outputs. 
 A common loss function for regression problems is the mean squared error (MSE):
@@
 \begin{equation}
-    \text{MSE} = \frac{1}{n} \sum_{i=1}^{n} (f(x_i) - y_i)^2.
+    \text{MSE} = \frac{1}{n} \sum_{i=1}^{n} (f(x_i;\theta) - y_i)^2.
 \end{equation}
@@
 General form of a parametric regression model is given by:
-\begin{equation}
-    y = \beta_0 + \sum_{j=1}^{p} \beta_j \phi_j(x) + \epsilon,
+\begin{equation} \label{eq:regression}
+    f(x; \theta) = \beta_0 + \sum_{j=1}^{p} \beta_j \phi_j(x),
 \end{equation}
-where $\epsilon$ is the error term, $p$ is the number of features, $\beta_0, \beta_1, \ldots, \beta_p$ are the trainable regression coefficients, and $\phi_j(x)$ are basis functions that transfrom the input $x$ to allow for non-linear modeling.
+where $p$ is the number of features, $\beta_0, \beta_1, \ldots, \beta_p$ are the trainable regression coefficients, and $\phi_j(x)$ are basis functions that transfrom the input $x$ to allow for non-linear modeling.
 Basis functions can be any functions of $x$ that are chosen to capture the underlying structure of the data.
@@
 To overcome these limitations, non-parametric methods such as kernel regression \citep{hastie2009elements} are often employed. 
-Kernel regression estimates the function $f(x)$ by averaging the target variable over a local neighborhood of the input $x$.
+Kernel regression estimates the relationship by averaging the target variable over a local neighborhood of the input $x$.
 The kernel regression with the Nadaraya-Watson estimator is given by:
 \begin{equation}
-    \hat{f}(x) = \frac{\sum_{i=1}^{n} K\left(\frac{x-x_i}{h}\right) y_i}{\sum_{i=1}^{n} K\left(\frac{x-x_i}{h}\right)},
+    f(x; \theta) = \frac{\sum_{i=1}^{n} K\left(\frac{x-x_i}{h}\right) y_i}{\sum_{i=1}^{n} K\left(\frac{x-x_i}{h}\right)},
 \end{equation}
 where $K(\cdot)$ is the kernel function, which assigns weights to the data points based on their distance to the input $x$, and $h$ is the bandwidth parameter that controls the smoothness of the estimated function.
-The objective is to estimate the function $f(x)$ directly from the data without imposing a specific form, hence, when the true relationship between variables is complex or unknown.
+The objective is to estimate the feature-label relationship directly from the data without imposing a specific form, hence, when the true relationship between variables is complex or unknown.
 However, they come with several drawbacks that limit their effectiveness, especially in high-dimensional settings or when dealing with large datasets. 
-One of the most significant drawbacks of non-parametric regression is the \textbf{curse of dimensionality} \cite{bellman1966dynamic}. 
+One of the most significant drawbacks of non-parametric regression is the curse of dimensionality \cite{bellman1966dynamic}. 
 As the number of features increases, the volume of the input space grows exponentially, making the data sparse and leading to overfitting.
-In addition, the computational cost of non-parametric methods often grows rapidly with the number of dimensions, making them impractical for high-dimensional data. 
+In addition, the computational cost of non-parametric methods, including cross validation and distance calculation, often grows rapidly with the number of dimensions.
+It makes them impractical for modeling high-dimensional large-scale datasets. 
 These limitations have motivated the adoption of neural networks, which can address many of the challenges associated with non-parametric approaches.
@@
 They can learn complex, non-linear relationships in data without the need for explicit feature engineering.
-The most crude form of a neural network is the feedforward neural network, which consists of an input layer, one or more hidden layers, and an output layer.
+The most crude form of a neural network is the feedforward neural network, which consists of an input layer, one or more hidden layers, and an output layer~\citep{goodfellow2016}.
 
-\subsection{Reinforcement Learning}
-Reinforcement learning (RL) is a machine learning technique that learns a policy by interacting with an environment and receiving feedback in the form of rewards.
-In a dynamic heding problem, the policy is a trading strategy that minimizes the risk of the hedged portfolio, the environment contains the financial market dynamics and the contract terms, and the rewards are the negative hedging errors or a risk measure of the hedging portfolio.
+\begin{figure}[ht!]
+    \centering
+    \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{./project3/tikz/fnn.pdf}
+        \caption{FNN}
+        \label{subfig:fnn}
+    \end{subfigure}
+    \hspace{1cm}
+    \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{./project3/tikz/lstm.pdf}
+        \caption{LSTM}
+        \label{subfig:lstm}
+    \end{subfigure}
+    \caption{Neural Network Architectures}
+    \label{fig:nn}
+\end{figure}
+
+Figure~\ref{subfig:fnn} shows a feedforward neural network (FNN) architecture with one hidden layer.
+The input layer receives the input features, which are then passed through the hidden layer(s) to the output layer.
+Each layer consists of multiple neurons, which apply a non-linear activation function to the weighted sum of the inputs.
+
+\begin{equation}
+    f(x; \theta) = f^{(k)}(f^{(k-1)} \cdots (f^{(2)}(f^{(1)}(x;\theta^{(1)});\theta^{(2)} )\cdots ;\theta^{(k-1)});\theta^{(k)}),
+\end{equation}
+
+where $\theta = (\theta^{(1)}, \theta^{(2)}, \ldots, \theta^{(k)})$ are the trainable parameters of the neural network, $f^{(i)}$ is the $i$-th layer of the neural network, $x$ is the input feature vector, $f^{(1)}(x;\theta^{(1)}) = x$, $f^{(k)}$ is the output layer, $k$ is the number of layers, and $f^{(i)}$ is the output of the $i$-th layer.
+To move from layer $i-1$ to layer $i$,
+
+\begin{equation} \label{eq:neural}
+    f^{(i)}(z;\theta^{(i)}) = a^{(i)}(\beta_0^{(i)} + \sum_{j=1}^{p_i} \beta_j^{(i)} z),
+\end{equation}
+
+where $a^{(i)}$ are the nonlinear activation functions, $\theta^{(i)} = (\beta_0^{(i)}, \dots, \beta_p^{(i)})$ are the trainable parameters of the $i$-th layer, and $p_i$ is the number of neurons in the previous layer.
+Equation~\ref{eq:neural} represents a single neuron in a neural network, which applies a linear transformation to the input followed by a non-linear activation function. 
+The linear transformation is similar to the linear regression model in Equation~\ref{eq:regression}, but the non-linear activation function allows the neural network to model complex, non-linear relationships in the data.
+The FNN is tuned by adjusting the trainable parameters $\theta$ while fixing the activation functions $a^{(i)}$.
+A typical choice for the activation function is the rectified linear unit (ReLU), which is defined as $a(z) = \max(0, z)$.
+
+The key advantage of feedforward neural networks (FNNs) lies in their ability to perform automatic feature engineering without direct human intervention. 
+Unlike traditional machine learning models that require manual selection and transformation of input features, neural networks learn to extract and compose features through their hidden layers during the training process.
+Each hidden layer in the network captures higher-level abstractions of the input data by transforming the outputs of the previous layer through nonlinear activation functions~\citep{lecun2015deep}.
+Each layer builds upon the representations learned by the previous layer, enabling the network to capture multiple levels of abstraction.
+This characteristic is crucial for modeling complex datasets with intricate patterns and relationships~\citep{bengio2013representation}.
+
+The last layer of the neural network, known as the output layer, typically performs a linear transformation of the features extracted by the preceding hidden layers. 
+With $a^{k}(z) = z$, the last layer is same as a linear regression with its inputs as transformed, high-level features learned by the hidden layers.
+By viewing the output layer as performing linear regression on the features learned by the network, we can draw parallels between neural networks and traditional regression models. 
+The main difference is that, in neural networks, the input features to the regression model are learned automatically rather than being manually specified.
+
+The most famous theorem in neural network theory is the universal approximation theorem~\citep{hornik1989multilayer}.
+It states that given appropriate activation functions $a$, a feedforward neural network with a single hidden layer containing a finite number of neurons can approximate any continuous function on a compact subset of $\mathbb{R}^n$ to arbitrary accuracy.
+Despite this theoretical guarantee for single-layer neural networks, in practice, deep neural networks (DNN) with multiple hidden layers have been shown to be more effective at capturing complex patterns and relationships in data~\citep{lecun2015deep}.
+Examples include AlexNet~\citep{krizhevsky2012imagenet}, VGG~\citep{simonyan2014very}, and ResNet~\citep{he2016deep}, which have achieved state-of-the-art performance on image classification tasks.
+In this thesis, we focus on the application of deep neural networks, specifically long short-term memory (LSTM) networks, as metamodels for nested simulation procedures in risk management applications.
+
+\subsection{Long Short-Term Memory Networks}
+
+Building upon the capabilities of FNNs, we recognize that while FNNs are successful at capturing complex, nonlinear relationships through automatic feature learning, they are inherently limited when it comes to modeling sequential data or time-dependent patterns.
+This independence assumption limits their effectiveness in modeling financial time series, where temporal dependencies play a critical role. 
+The stylized facts of financial time series, such as volatility clustering, fat tails, and autocorrelation, are challenging to capture with traditional feedforward neural networks due to the absence of memory in the model~\citep{cont2001empirical}.
+
+To overcome the limitations of FNNs in handling sequential data, recurrent neural networks (RNNs) were introduced.
+In an RNN, the hidden state at each time step is a function of both the current input and the hidden state from the previous time step~\citep{elman1990finding}:
+
+\begin{equation}
+    h_t = f(x_t, h_{t-1}; \theta),
+\end{equation}
+
+where $h_t$ is the hidden state at time $t$, $x_t$ is the input at time $t$, $h_{t-1}$ is the hidden state at time $t-1$, and $f$ is the recurrent function parameterized by $\theta$.
+This architecture enables RNNs to capture temporal dependencies by maintaining a dynamic internal state that reflects the memory of past inputs.
+However, traditional RNNs suffer from the vanishing and explodeing gradient problem, which hinders their ability to capture long-term dependencies that often present in financial time series~\citep{bengio1994learning}.
+During training, gradients propagated backward through time can either diminish exponentially (vanishing gradients) or grow uncontrollably (exploding gradients).
+This limitation is particularly problematic in modeling long-term financial contracts and insurance guarantees, where patterns may span over extended periods.
+
+To address these issues, a long short-term memory (LSTM) network was developed by \citet{hochreiter1997long}.
+It is a specialized form of RNNs designed to capture long-term dependencies more effectively with the help of RNN memory cells and gating mechanisms.
+
+\begin{align*}
+    i_t &= a(W_i x_t + U_i h_{t-1} + b_i), \\
+    f_t &= a(W_f x_t + U_f h_{t-1} + b_f), \\
+    o_t &= a(W_o x_t + U_o h_{t-1} + b_o), \\
+    g_t &= a(W_g x_t + U_g h_{t-1} + b_g), \\
+    c_t &= f_t \odot c_{t-1} + i_t \odot g_t, \\
+    h_t &= o_t \odot \tanh(c_t),
+\end{align*}
+
+where $i_t, f_t, o_t, g_t, c_t, h_t$ are the input gate, forget gate, output gate, cell input, cell state, and hidden state at time $t$, respectively.
+$W_i$, $W_f$, $W_o$, $W_g$, $U_i$, $U_f$, $U_o$, $U_g$ are the weight matrices, and $b_i$, $b_f$, $b_o$, $b_g$ are the bias vectors.
+$a$ is the activation function, typically the sigmoid function, and $\odot$ denotes element-wise multiplication.
+
+\begin{equation*}
+    a(z) = \frac{1}{1 + e^{-z}}.
+\end{equation*}
+
+Figure~\ref{subfig:lstm} shows the architecture of an LSTM network.
+The gating mechanisms in LSTMs effectively mitigate the vanishing and exploding gradient problem by regulating the flow of information through the network.
+The input gate $i_t$ controls the flow of information into the cell state $c_t$, the forget gate $f_t$ regulates the retention of information in the cell state, and the output gate $o_t$ determines the information passed to the hidden state $h_t$.
+The cell input $g_t$ is used to update the cell state based on the input $x_t$ and the previous hidden state $h_{t-1}$.
+The cell state $c_t$ acts as a memory unit that stores information over time, while the hidden state $h_t$ captures the relevant information for the current time step.
+By incorporating memory cells and gating mechanisms, LSTMs can effectively model long-term dependencies in sequential data in finance and actuarial applications.
+
+This thesis aims to explore the application and noise tolerance of LSTM networks in metamodeling for nested simulation procedures in risk management.
+We investigate the performance of LSTM networks in approximating the inner simulation model in a two-stage nested simulation procedure for index-linked insurance contracts.
+By leveraging the memory and sequential modeling capabilities of LSTMs, we aim to improve the accuracy and efficiency of nested simulation procedures for risk management applications.
+
+\subsection{Transfer Learning}
+
+% \subsection{Reinforcement Learning}
+% Reinforcement learning (RL) is a machine learning technique that learns a policy by interacting with an environment and receiving feedback in the form of rewards.
+% In a dynamic heding problem, the policy is a trading strategy that minimizes the risk of the hedged portfolio, the environment contains the financial market dynamics and the contract terms, and the rewards are the negative hedging errors or a risk measure of the hedging portfolio.

### 2024-09-27 project3/draft.tex
new

--- 2024-05-16 project3/draft.tex
@@
-\chapter{Model-Free Deep Hedging of Variable Annuities}
+\chapter{Transfer Learning for Rapid Adaptation of Deep Neural Network Metamodels in Dynamic Hedging of Variable Annuities} \label{chap:project3}
 
@@
 
-Reinforcement Learning (RL) is a branch of machine learning that focuses on training algorithms, known as agents, to make a sequence of decisions. 
-The agent learns to achieve a goal in an uncertain, potentially complex environment by trial and error, using feedback from its own actions and experiences. 
-Unlike supervised learning, where training data is labeled with the correct answers, in RL, an agent is provided with rewards or punishments as signals for its actions.
+In the evolving landscape of financial markets, insurance products such as VAs have gained significant interest due to their ability to provide both investment growth and guaranteed benefits. 
+Managing the risks associated with these products, especially in volatile market conditions, is a complex task that demands sophisticated financial modeling techniques. 
+Traditional machine learning models often struggle to capture the intricate nonlinear relationships and temporal dependencies inherent in financial data.
+To address the computational burden, metamodeling techniques have been proposed, where a simpler model approximates the outcomes of the more complex simulation. 
+In particular, deep neural networks (DNNs), and specifically LSTM networks, have been employed as metamodels to predict the outcomes of the inner simulations efficiently
+Chapter~\ref{chap:project2} introduces a nested simulation framework for dynamic hedging of VAs, where the inner simulation is approximated by an LSTM metamodel.
+It shows that crude RNN and LSTMs are well-suited for metamodeling Monte Carlo simulation of financial time series and can capture the long-term dependencies in the data.
 
-The core of RL revolves around the concept of the agent interacting with its environment over time, aiming to maximize the cumulative reward. 
-This process involves observing the state of the environment, selecting and performing actions, and receiving rewards or penalties in response to those actions. 
-The agent's objective is to learn a mapping from states to actions that maximizes this cumulative reward, which is often referred to as a policy. 
-One of the fundamental frameworks for modeling RL problems is the Markov Decision Process (MDP). 
-An MDP provides a mathematical formulation of the decision-making process, characterized by states, actions, rewards, and transition probabilities. 
-Solving an MDP involves finding a policy that maximizes some function of the expected rewards, typically the expected cumulative reward over time.
+Despite the advantages of using DNN metamodels, a significant challenge arises when market conditions change or new VA contracts with different features are introduced. 
+Retraining neural network metamodels from scratch in response to every change is computationally inefficient and time-consuming.
+Moreover, financial markets are inherently dynamic, with frequent shifts in volatility, interest rates, and other risk factors~\citep{cont2001empirical}.
+Therefore, it is essential to develop methods that can rapidly adapt existing metamodels to new conditions without incurring the full computational cost of retraining.
+Transfer Learning offers a compelling solution to this problem by enabling the reuse of a pre-trained model on a new but related task~\citep{pan2009survey}.
+In the context of DNNs, transfer learning involves leveraging the knowledge acquired during training on one dataset to improve learning performance on a different dataset~\citep{yosinski2014transferable}.
+This approach can significantly reduce training time and computational resources while enhancing model generalization.
+Instead of starting from scratch, a new DNN metamodel can be built on top of the pre-trained model and fine-tuned on the new data, allowing it to adapt quickly to changing market conditions and new VA contracts.
 
-RL algorithms can be broadly categorized into two types: model-based RL and model-free RL. 
-Model-based RL utilize a model of the environment to simulate the outcomes of actions, enabling planning and decision-making with fewer interactions with the environment. 
-The biggest drawback of model-based RL is model bias. 
-In practice, the ground-true model is usually not available.
-By using a model, an RL agent can exploit the model bias, which leads to suboptimal performance in the real environment.
-Conversely, model-free RL learn directly from interactions with the environment.
-Without relying on a model, model-free RL algorithms are more straightforward implement and tune.
+In this chapter, we explore the application of transfer learning to the dynamic hedging of VAs using RNN and LSTM metamodels.
+We propose a novel transfer learning framework that accelerates the training of DNN metamodels for nested simulation in a dynamic hedging problem.
+Our approach involves pre-training an LSTM network on a large dataset of VA simulations and then fine-tuning it on a smaller dataset of new VA contracts.
+We evaluate the performance of the transfer learning framework on a real-world dataset of VA contracts and compare it with training the LSTM network from scratch.
 
-A compelling application of RL is dynamic hedging, where the complexity and uncertainty of financial markets make traditional static models inadequate.
-RL's adaptability and learning capabilities offer a promising solution to dynamically adjust hedging strategies in response to market movements and assumptions changes.
-In particular, model-free RL has the potential to enhance risk management practices by developing robust strategies that can adapt in real-time.
-Some popular RL algorithms include Proximal Policy Optimization (PPO), Deep Q-Networks (DQN), and Deep Deterministic Policy Gradient (DDPG).
+The rest of this chapter is organized as follows.
+Section~\ref{sec3:background} provides an overview of the dynamic hedging problem for VAs and the use of LSTM networks as metamodels in a nested simulation procedure.
+Section~\ref{sec3:transfer_learning} introduces the transfer learning framework for rapid adaptation of LSTM metamodels in dynamic hedging.
+Section~\ref{sec3:experiments} presents the experimental setup and results, comparing the performance of transfer learning with training from scratch.
+Finally, Section~\ref{sec3:conclusion} concludes the chapter and discusses future research directions.
 
-In this paper, we propose a model-free RL algorithm to improve the risk management of variable annuities (VAs).
-VAs are popular insurance products that add investment features to an insurance contract.
-Hedging VAs is particularly challenging due to multiple sources of risk.
-Our model-free RL approach aims to learn a hedging policy without directly accessing models of the underlying risk factors.
-By interacting with an enviornment, the hedging policy can effectively manage the risks of VAs in a changing market environment.
+\section{Background} \label{sec3:background}
 
-The rest of the paper is organized as follows:
+\section{Transfer Learning for Rapid Adaptation of LSTM Metamodels} \label{sec3:transfer_learning}
 
-\section{Markov Decision Process}
+\section{Numerical Experiments} \label{sec3:experiments}
 
-An MDP is defined by the tuple $\mathcal{M} = (\mathcal{S}, \mathcal{A}, \mathcal{P}, \mathcal{R}, \gamma)$, where:
-
-\begin{itemize}
-    \item $\mathcal{S}$ is a finite set of states.
-    \item $\mathcal{A}$ is a finite set of actions.
-    \item $\mathcal{P}$ is a state transition probability distribution, where $\mathcal{P}(s_{t}|s_{t-1}, a_{t-1})$ represents the probability of transitioning from state $s_t$ to state $s_{t-1}$ due to action $a_{t-1}$.
-    \item $\mathcal{R}$ is a reward distribution, $\mathcal{R}(s, a, s')$ is the reward received after transitioning from state $s$ to state $s'$ due to action $a$.
-    \item $\gamma$ is a discount factor, $\gamma \in [0,1]$,  which models the present value of future rewards.
-\end{itemize}
-
-The objective in an MDP is to find a policy, $\pi: \mathcal{S} \rightarrow \mathbb{P}(\mathcal{A})$, that maximizes the cumulative reward over time.
-A Markov Decision Process (MDP) provides a mathematical framework for solving sequential decision-making tasks in an enviornment where outcomes are partly random and partly under the control of a hedging agent.
-For hedging VAs, the asset dynamics and the mortality model are not controlled by the agent, but the agent controls the cumulative reward by deciding on the hedging weights.
-In this section, we reformulate the hedging enviornment of VAs from Section~\ref{subsec:VApayout} as an MDP and define the key components of the MDP.
-
-\subsection{Hedging Environment of Variable Annuities} \label{subsec:VASimulation}
-
-Consider a generic VA contract with maturity $T>0$ periods, e.g., $T=240$ months.
-Then the contract expires at $T'=\min\{T,\tau\}$, i.e., the earlier of the contract maturity and the death of the policyholder.
-Let $S_t$, $F_t$, and $G_t$ be the indexed stock price, the subaccount value and the guarantee value, respectively, at time $t=1,2,\ldots,T$.
-Evolution of the subaccount value and the guarantee value of a VA contract affect the contract payout.
-For clarity, we use $F_t$ and $F_{t_+}$ to denote the sub-account value just before and just after the withdrawal at time $t$, if any.
-Let $\eta_g$ be the gross rate of management fee that is deducted from the fund value at each period and let $\eta_n < \eta_g$ be the net rate of management fee income to the insurer.
-The difference between the gross management fee and the net management fee income represents the incurred investment expenses.
-
-At the inception of the contract, i.e., $t=0$, we assume that the whole premium is invested in the stock index and the guarantee base is set to the sub-account value:
-\begin{equation*}
-    S_0=F_0=G_0.
-\end{equation*}
-At each time $t=1,\ldots,T$, the following events take place in the following order:
-\begin{enumerate}
-    \item The dynamic lapse rate $q_t$ is applied to the contract, i.e., $q$ of the policyholders leave the contract at time $t$.
-        \begin{equation} \label{eq3:lapse}
-            q_t = q_t^B \cdot \text{clip} (M_q (\frac{G_{t-1}}{F_{t-1}} - D_q), L_q, U_q),
-        \end{equation}
-    where $q_t^B$ is the base lapse rate, $\text{clip}(x, a, b)$ is a function that clips the value of $x$ to be within the range $[a, b]$, and $M_q$, $D_q$, $L_q$, and $U_q$ are the model parameters taken from National Association of Insurance Commissioners’ (NAIC) Valuation Manual 21~\citep{naic2021}.
-    \item The sub-account value changes according to the growth of the underlying stock and the (gross) management fee is deducted. That is, 
-        \begin{equation} \label{eq3:subaccount}
-            F_t = F_{(t-1)_+}\cdot\frac{S_{t}}{S_{t-1}}\cdot(1-\eta_g)\cdot(1-q_t),
-        \end{equation} 
-    where $(x)^+=\max\{x,0\}$ and $F_{(t-1)_+}$ will be defined later. The insurer's income at time $t$ is the net management fee, i.e., $F_t\eta_n$.
-
-    \item The guarantee value ratchets up (ratcheting is a common feature in GMWB) if the sub-account value exceeds the previous guarantee value, i.e., 
-        \begin{equation} \label{eq3:guarantee}
-            G_t = \max\{G_{t-1}\cdot(1-q_t),F_t\}.
-        \end{equation} 
-    A GMMB can be modeled with $G_t = G_{t-1}\cdot(1-q_t)$.
-
-    \item The withdrawal is made (for GMWB) and is deducted from the sub-account value, i.e., 
-        \begin{equation} \label{eq3:withdrawal}
-            F_{t_+} = (F_t - I_t)^+,
-        \end{equation} 
-    where $I_t = \xi G_t$. A GMMB can be modeled with $\xi = 0$.
-\end{enumerate}
-
-Consider a VA contract whose delta hedge portfolio at any time~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at time $T$.
-The value of the hedge portfolio at time~$(t-1)$ is:
-\begin{equation*}
-    H_{t-1} = \Delta_{t-1} S_{t-1} + B_{t-1},
-\end{equation*}
-where $S_t$ is the underlying stock price and any time $t>0$.
-This hedge portfolio is brought forward to the next rebalancing time~$t$, when its value becomes:
-\begin{equation*}
-    H_{t}^{bf} = \Delta_{t-1} S_{t} + B_{t-1}e^{r}.
-\end{equation*}
-Therefore, the time~$t$ hedging error, i.e., the cash flow incurred by the insurer due to rebalancing at time~$t$, is
-\begin{equation}
-    HE_t = H_t - H^{bf}_t, \quad t=1,\ldots, T-1.
-\end{equation}
-The P\&L of the VA contract includes the cost of the initial hedge ($H_0$), the hedging errors~\eqref{eq2:hedgingerror}, the unwinding of the hedge at maturity ($H^{bf}_T$), and the contract payout at time~$t\in \{0,\ldots,T\}$.
-Mathematically, the present value of the liability for a GMMB contract is 
-\begin{align} \label{eq3:lossGMMB}
-L   & = H_0 - e^{-rT} H^{bf}_T + \sum_{t=1}^{T-1} e^{-rt} HE_t + \sum_{t=1}^T e^{-rt} C_t - \sum_{t=1}^T e^{-rt} F_t\eta_n + e^{-rT} (G_t - F_t)^+  \nonumber \\ 
-    & = e^{-rT} (G_T - F_{T^+})^+ + \sum_{t=1}^T e^{-rt}  \left( \Delta_{t-1} (S_{t-1} - e^{-r} S_t) + C_t - F_t\eta_n \right) 
-\end{align}
-where the equality holds by a rearrangement of terms and a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$, and $C_t := C \cdot S_{t-1} \cdot |\Delta_t - \Delta_{t-1}|$ is the tranaction cost at time $t$~\citep{garleanu2013dynamic}.
-Hence, the present liability consist of the hedging errors, the transaction costs, the net management fees, and the contract payouts.
-Similarly, the present value of the liability for a GMWB contract is
-\begin{equation} \label{eq3:lossGMWB}
-L = \sum_{t=1}^T e^{-rt}  \left( \Delta_{t-1} (S_{t-1} - e^{-r} S_t) + C_t - F_t\eta_n \right)
-\end{equation}
-The GMWB payout is implicitly included in $F_t\eta_n$.
-Both Equation~\ref{eq3:lossGMMB} and Equation~\ref{eq3:lossGMWB} neglect the transaction cost to liquidate the hedge portfolio at maturity.
-The discrete-time hedging problem of VAs can be conveniently formulated as an MDP, where the states, actions, transition probabilities, policies, and rewards are defined as follows.
-
-\subsection{State Space}
-
-The state space $\mathcal{S}$ represents all the information needed to characterize the hedging environment.
-In a VA hedging problem, $\mathbf{s}_t$, the information available to a hedging agent at each time $t$ is 
-$$\mathbf{s}_t := (S_t, F_t, G_t, \tau, \Delta_{t-1}) \in \mathcal{S}.$$
-where $\tau$ is the remaining time to maturity and $\Delta_{t-1}$ is the previous hedging weight.
-The hedging environment is partially observed, e.g., the agent does not have access to the contract specifications.
-It has to learn a representation of the relevant information from the observed state $\mathbf{s}_t$.
-
-\subsection{Action Space}
-
-The action space $\mathcal{A}$ represents the set of actions that the agent can take at each time $t$.
-In a VA hedging problem, the action space only includes the hedging weight $\Delta_t$.
-
-\subsection{Policy}
-
-A policy $\pi$ determines the best action to take in a given state, i.e.,
-$$a_t \sim \pi(\cdot|\mathbf{s}_t).$$
-In a VA hedging problem the policy outputs the hedging weight $a_t = \Delta_t$ given the observed state $\mathbf{s}_t$.
-In the following sections, we will refer to $\Delta_t$ as the policy.
-
-\subsection{Transition Probabilities}
-
-The transition probabilities $\mathcal{P}$ represent the probability of transitioning from one state to another from taking an action.
-In our setup, the transition probabilities are fully determined by Equation~\ref{eq3:lapse}, Equation~\ref{eq3:subaccount}, Equation~\ref{eq3:guarantee}, and Equation~\ref{eq3:withdrawal}.
-Let $\mathcal{P}(\mathbf{s}_{t+1}|\mathbf{s}_t, a_t)$ be the probability of transitioning from state $\mathbf{s}_t$ to state $\mathbf{s}_{t+1}$ due to action $a_t$.
-Aside from the previous hedging weight $\Delta_{t-1}$, the transition probabilities are independent from the actions.
-Paths simulated from the transition probabilities are called trajectories (or episodes) of the MDP.
-
-\subsection{Reward and Discount Factor}
-The reward function $\mathcal{R}$ and discount factor $\gamma$ in a typical RL problem are defined as follows:
-\begin{align}
-    \mathcal{R} & = \sum_{t=1}^{T-1} \gamma^t R_t \\
-    \gamma      & = e^{-r}, \nonumber
-\end{align}
-where $R_t$ is the term reward received by the agent at time $t$, and the discount factor $\gamma$ is conveniently inherited from the risk-free rate $r$. 
-In hedging, the term reward $R_t$ should be drived from Equation~\ref{eq3:lossGMMB} and Equation~\ref{eq3:lossGMWB} to represent the performance of the hedging policy, i.e., how closely the hedging portfolio tracks the liability.
-For GMWB, we propose a term reward formulation that encourages the agent to maximize the expected reward with low hedging errors and transaction costs:
-\begin{equation} \label{eq3:rewardGMWB}
-    R_t = F_{t-1}\eta_n - \Delta_{t-1} |S_{t-1} - e^{-r}S_{t}| - C_{t-1}(\Delta_{t-1}), \quad t \in \{1,\ldots,T \}
-\end{equation}
-The reward function of GMWB directly links to the time-$t$ loss of a GMWB contract as in Equation~\ref{eq3:lossGMWB}.
-The GMMB loss consists of an additional payoff at maturity $T$, thus its term reward is formulated as:
-\begin{equation} \label{eq3:rewardGMMB}
-    R_t = 
-    \begin{cases}
-    F_{t-1}\eta_n - \Delta_{t-1} |S_{t-1} - e^{-r}S_{t}| - C_{t-1}(\Delta_{t-1}),                         & t\in \{1,\ldots,T-1 \} \\
-    F_{t-1}\eta_n - \Delta_{t-1} |S_{t-1} - e^{-r}S_{t}| - C_{t-1}(\Delta_{t-1}) + (G_T - F_{T^+})^+      & t = T
-    \end{cases}
-\end{equation}
-It is worth noting that learning to hedge GMWB is easier for an RL agent due to the absense of reward at maturity (long-term feedback).
-
-\subsection{Value Function and Advantage Function}
-
-This section introduces some critical concepts in RL, i.e., the value function and the advantage function.
-They are essential for understanding the performance of the hedging policy and the learning process of the RL agent.
-
-A value function quantifies the expected cumulative reward over time.
-The state value function, $V^{\pi}(s_t)$, is defined as the expected cumulative reward starting from state $s_t$ and following policy $\pi$ thereafter:
-
-\begin{equation} \label{eq3:V_pi}
-    V^{\pi}(s_t) = \mathbb{E} \left[ \sum_{t=0}^{\infty} \gamma^t R_t |\pi, s_t \right],
-\end{equation}
-
-where $R_t$ is the reward received by the agent after taking action $a_t$ in state $s_t$ and transitioning to state $s_{t+1}$, and the expectation is taken over the possible sequences of states and rewards that follow from the policy $\pi$.
-The state-action value function, $Q^{\pi}(s_t, a_t)$, is defined as the expected cumulative reward starting from state $s_t$, taking action $a_t$, and following policy $\pi$ thereafter:
-
-\begin{equation} \label{eq3:Q_pi}
-    Q^{\pi}(s_t, a_t) = \mathbb{E} \left[ \sum_{t=0}^{\infty} \gamma^t R_t |\pi, s_t, a_t \right],
-\end{equation}
-
-Based on Equations~\ref{eq3:V_pi} and~\ref{eq3:Q_pi}, the advantage function, $A^{\pi}(s_t, a_t)$, is defined as the difference between the state-action value function and the state value function:
-
-\begin{equation} \label{eq3:A_pi}
-    A^{\pi}(s_t, a_t) = Q^{\pi}(s_t, a_t) - V^{\pi}(s_t).
-\end{equation}
-
-The advantage function quantifies the advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi$.
-
-\section{Model-Based and Model-Free RL}
-
-\subsection{Model-Based RL: From AlphaZero to Deep Hedging}
-Deep reinforcement learning first attacted attentions when AlphaGo~\citep{silver2016mastering} surpasses human in playing Go. 
-Soon after, AlphaZero~\citep{silver2016mastering} emerged as a model-based RL algorithm that improves over self-plays.
-It quickly extended beyond Go to other games like Chess and Shogi.
-In essence, the AlphaZero agent use a neural network to paramaterize the policy and the value function.
-The neural network takes the current state of the game as input and outputs the probability distribution of the next move and a value of the current state.
-\begin{equation}
-    (\mathbf{\pi}, v) = f_{\theta}(s), \quad L(\theta) = - \mathbf{\pi}^{\intercal} \log(\mathbf{p}) + (z - v)^2  + c||\theta||^2,
-\end{equation}
-where $f_{\theta}$ is the neural network with parameters $\theta$, $s$ is the current state of the game, $\pi$ is the policy, $v$ is the value of the current state, and $c$ is a regularization parameter.
-$\mathbf{p}$ and $z$ are the probability distribution of the next move and the outcome of the game, respectively.
-They are induced by a planning algorithm, i.e., Monte Carlo Tree Search (MCTS).
-Since it is infeasible to efficiently simulate trajectories in the game of Go, a planning algorithm is necessary to generate expected outcomes.
-The neural network $f_{\theta}$ is trained with a stochastic gradient descent algorithm to minimize $L$.
-$L$ has three components.
-The last term penalizes large neural network weights.
-Its first two terms measure the similarity between $f_{\theta}(s)$, the learned policy and value function, with the action and game outcome planned by the MCTS.
-The neural network is trained to fit the planned outcomes of the game.
-It stores a global solution that predicts the outcome of the game and the next move before they are actually observed.
-This is known as model-based RL~\citep{sutton2018reinforcement}.
-Using a model allows for planning, i.e., decision-making take place using future situations that have not been experienced by the agent.
-
-In a typical hedging problem, the transition probabilities are independent from the hedging weights, i.e., the actions.
-This simplifies the planning as complete trajectories can be simulated without the need of a planning algorithm.
-In contrast to AlphaZero, deep hedging~\citep{buehler2019deep} uses the model itself to simulate the complete trajectories following the transition probabilities of the MDP.
-Let $(\tilde{\mathbf{s}}_0, \tilde{\Delta}_0, \tilde{\mathbf{s}}_1, \tilde{\Delta}_1, \ldots, \tilde{s}_T)$ and $\tilde{\mathcal{R}} = (R_1, \ldots, R_t)$ be a trajectory and the hedging reward of the MDP, respectively.
-The neural network $f_{\theta}$ stores a global solution, i.e., it takes the previous state and hedging weight as input and outputs the hedging weight at the current state.
-\begin{equation} \label{eq3:deephedging}
-    \mathbf{\Delta}_t = f_{\theta}(\mathbf{s}_t), \quad L(\theta) = \rho(L) = \rho(-\mathcal{R}) = \rho(- \sum_{t=0}^{T} \gamma^t R_t),
-\end{equation}
-where $\rho(L)$ is a convex risk measure of the total present liability $L$. 
-The risk measure $\rho$ serves as a model of the MDP that 
-A common choice of $\rho$ is a CVaR.
-In practice, the neural network $f_{\theta}$ is trained to minimize the empirical CVaR over a batch of trajectories.
-In other words, planning is done through $\rho$, which measures the performance of a hedging policy over a batch of complete trajectories.
-The ability to know the future outcomes of the hedging policy before they are actually observed and the use of a risk measure to guide the training of the neural network are the key features of model-based RL.
-For hedging VAs,~\cite{xu2020variable} propose a deep hedging algorithm that falls into this category of model-based RL.
-A cost function is defined to minimize the expected shortfall of the total present liability.
-~\cite{carbonneau2021deep} extends the model-based approach to hedging long-term financial derivatives and compares the performance of deep hedging strategies trained with different cost functions.
-In Equation~\ref{eq3:deephedging}, the state space of the MDP contains the previous hedging weight.
-A more recent paper by~\cite{imaki2021no} proposes a new network architecture that removes the previous hedging weight from the state space by introducing a no-transaction band.
-It allows for a more efficient training of the neural network by removing the semi-recurrent problem structure.
-Despite the success of model-based RL in hedging, most studies focus on hedging different types of contracts on classical asset models, e.g., Black-Scholes model and Heston model.
-Motivated by the seminal work by~\cite{gatheral2022volatility}, there are a many subsequent works focusing on roughening the classical stochastic volatility models. 
-In the rough volatility models, the latent volatility process is modelled by a stochastic process that is rougher than the sample paths of diffusion process. 
-Among these rough volatility models, notable examples are rough Heston model and the rough Bergomi model. 
-Model-based RL struggles in a rough volatility model due to difficulties in designing a suitable cost function.~\cite{horvath2021deep} shows that a standard implementation of deep hedging can lead to suboptimal hedging performance in a discretized rough Bergomi model.
-The CVaR-based cost function needs to be redesigned to account for jump risks, and it is still an open question.
-In summary, model-based RL algorithms like deep hedging do not depend on the asset model, i.e., they are \textbf{model-independent}.
-However, they are not \textbf{model-free}.
-For example, deep hedging builds its own model of the hedging environment to plan the hedging strategy ahead of time using a neural network.
-Designing a suitable cost function for such a network is necessary but challenging.
-In contrast, a model-free approach does not require a explicit design for different asset dynamics, making it more flexible and adaptable to different market conditions and more robust to model misspecification.
-
-\subsection{Model-Free RL for Hedging}
-
-In a model-free reinforcement learning approach, the agent is a trial-and-error learner that interacts with the environment to learn the optimal policy by iteratively updating the policy and the value function based on the observed states, actions, and rewards.
-For hedging VAs, the agent does not have access to a planning algorithm or a model of the underlying risk factors, and it must learn the optimal policy by directly interacting with the environment.
-Figure~\ref{fig3:RLMethods} illustrates the critical difference between model-based and model-free RL methods.
-
-\begin{figure}[ht!]
-    \centering
-    \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{./project3/tikz/modelBased.pdf}
-        \caption{Model-based RL (Deep Hedging)}
-        \label{subfig3:mbRL}
-    \end{subfigure}
-    \hspace{1cm}
-    \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{./project3/tikz/modelFree.pdf}
-        \caption{Model-free RL}
-        \label{subfig3:mfRL}
-    \end{subfigure}
-    \caption{Model-based and Model-free RL Methods}
-    \label{fig3:RLMethods}
-\end{figure}
-
-Boardly speaking, model-free RL can be categorized into two types: value-based RL and policy-based RL.
-Value-based approaches learn the value function directly from the data and derive the policy from the learned value function. 
-The value function is learned by training a DNN to approximate the value function, which quantifies the expected cumulative reward over time. 
-The policy is then derived from the learned value function by selecting the action that maximizes the value function at each state. 
-~\cite{mnih2015human} is the first paper to demonstrate the effectiveness of value-based deep reinforcement learning in training agents to play Atari games.
-To update the value function, the DNN is trained to minimize the difference between the current value function and the target value function, which is updated based on the maximum expected reward from the previous iteration.
-When trained to approximate the value function, the DNN benefits from the use of experience replay buffers, which is proposed by~\cite{lin1992self} to store and sample historical transitions and uniformly sampled during training to enhance the sample efficiency and stability of the learning process.
-~\cite{kolm2019dynamic} uses a value-based deep reinforcement learning approach to hedge European options under the Black-Scholes framework.
-
-In valued-based approaches, the value function is updated iteratively with the maximum expected reward of all possible actions, which can be computationally expensive for continuous action spaces.
-To overcome this difficulty, a policy-based approach estimates the value function before realization of the final payoff of the hedging portfolio, which is particularly useful for hedging long-term financial derivatives or VA contracts.
-Two types of policy-based approaches prevail in the literature: actor-critic and policy gradient methods.
-
-An actor-critic method designs an actor network and a critic network to learn the value function and the policy simultaneously.
-The actor network learns the policy by directly outputting the action based on the current state, while the critic network learns the value of an action by approximating the expected cumulative reward over time following the actor's policy.
-A popular actor-critic algorithm is the Deep Deterministic Policy Gradient (DDPG) algorithm proposed by~\cite{lillicrap2015continuous}, which is implemented by~\cite{xu2022delta} in hedging financial derivatives in S\&P 500 and DJIA index options.
-
-A policy gradient method uses policy gradient theorem to update the policy by performing gradient ascent with respect to the policy parameters.
-Representative algorithms include the Trust Region Policy Optimization (TRPO) algorithm proposed by~\cite{schulman2015trust} and the Proximal Policy Optimization (PPO) algorithm proposed by~\cite{schulman2017proximal}.
-~\cite{du2020deep} show that the PPO algorithm is more sample efficient and stable than the value-based approaches in training agents to hedge financial derivatives.
-The most relevant paper to our study is~\cite{chong2023pseudo}, which uses the PPO algorithm to hedge GMMB with a GMDB rider under the Black-Scholes framework.
-However, information of the underlying risk factors is leaked to the agent, which makes their study pseudo-model-free.
-To further improve the risk management of VAs under rough volatility models, we propose a model-free deep reinforcement learning approach to hedge VAs without explicit or implicit knowledge of the underlying risk factors.
-
-\section{Hedging VAs with a PPO Agent}
-In a hedging problem, an insurer aims to find a policy $\pi$ that maximize the expected reward over time.
-In a policy-based RL approach like the PPO, both the policy and the value function are parameterized by deep neural networks.
-We denote the policy by $\pi_{\theta}$ and the value function by $V_{\phi}$, where $\theta$ and $\phi$ are the parameters of the value network and the policy network, respectively.
-The policy is updated according to an objective function that reflects the advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi$.
-\begin{align}
-    \max_{\theta} \mathbb{E}\left[ \min \left\{ \Lambda_t(\theta)\hat{A}^{\pi_{\theta}}(s_t, a_t), \text{clip}(\Lambda_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(s_t, a_t)  \right\} \right] \\
-    \Lambda_t(\theta) = \frac{\pi_{\theta}(a_t|s_t)}{\pi_{\theta_{old}}(a_t|s_t)} 
-\end{align}
-
-where $\theta_{old}$ denotes the policy parameters at the previous iteration, $\epsilon$ is a clip range hyperparameter that controls the size of the policy update, $\text{clip}(x, a, b)$ is a function that clips the value of $x$ to be within the range $[a, b]$, and $\hat{A}^{\pi_{\theta}}(s_t, a_t)$ is the estimated advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi_{\theta_{old}}$.
-In our implementation, the advantage function is estimated following the GAE method proposed by~\cite{schulman2015high}.
-The policy is updated by performing gradient ascent with respect to the policy parameters $\theta$ to maximize the objective function, which is estimated by sampling from the environment and computing the empirical average of the objective function over the sampled trajectories.
-The first component in the objective function, $\Lambda_t(\theta) \hat{A}^{\pi_{\theta}}(s_t, a_t)$, is a surrogate objective function that approximates the advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi_{\theta_{old}}$, and the second component, $\text{clip}(\Lambda_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(s_t, a_t)$, is a clipped surrogate objective function that prevents large policy updates and ensures more stable training.
-The TRPO algorithm proposed by~\cite{schulman2015trust} uses a similar clipped surrogate objective function to ensure that the policy update does not deviate too far from the old policy, but PPO simplifies the optimization problem by using a clipped surrogate objective function instead of a hard-coded constraint on the policy update.
-Compared to TRPO, PPO is more computationally efficient and easier to implement, making it a popular choice for training deep reinforcement learning agents.
-For a in-depth discussion on the implementation details of both TRPO and PPO, we refer the reader to~\cite{engstrom2020implementation}.
-
-\begin{algorithm} 
-    \caption{PPO for Hedging Variable Annuities} 
-    \begin{algorithmic}[1] \label{alg3:ppoHedging}
-        \STATE  Initialize policy parameters $\theta_0$ and value function parameters $\phi_0$.
-        \STATE  \textbf{For} {iteration $k=0, 1,2,\ldots$} \textbf{do}
-        \STATE  \quad Collect a set of trajectories $\mathcal{D}_k$ by sampling from the environment with policy $\pi_{\theta_{k}}$.
-        \STATE  \quad Compute the rewards $\hat{R}_t$ for each trajectory in $\mathcal{D}_k$.
-        \STATE  \quad Estimates the advantage function with $\hat{A}_{\pi_{\theta_k}}(\mathbf{s}_t, a_t)$ using value function $V_{\phi_k}$.
-        \STATE  \quad Update the policy parameters $\theta_{k+1}$ by 
-        \begin{equation*}
-            \max_{\theta} \mathbb{E}\left[ \min \left\{ \Lambda_t(\theta)\hat{A}^{\pi_{\theta}}(\mathbf{s}_t, a_t), \text{clip}(\Lambda_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(\mathbf{s}_t, a_t)  \right\} \right]
-        \end{equation*}
-        \STATE  \quad Update the value function parameters $\phi_{k+1}$ by minimizing the mean squared error between the predicted value and the actual collected reward.
-        \begin{equation*}
-            \phi_{k+1} = \arg \min_{\phi} \frac{1}{|\mathcal{D}_k|T} \sum_{\mathcal{\kappa} \in \mathcal{D}_k} \sum_{t=0}^{T} \left( V_{\phi}(\mathbf{s}_t) - \hat{R}_t \right)^2
-        \end{equation*}
-        \STATE  \textbf{End For}
-    \end{algorithmic}
-\end{algorithm}
-
-Algorithm~\ref{alg3:ppoHedging} outlines the PPO algorithm for training an agent to hedge VAs.
-At each iteration $k$, the agent collects a set of trajectories $\mathcal{D}_k$ by interacting with the environment (Section~\ref{subsec:VASimulation}) with the current policy $\pi_{\theta_k}$.
-The agent then computes the rewards $\hat{R}_t$ for each trajectory in $\mathcal{D}_k$ and estimates the advantage function with $\hat{A}_{\pi_{\theta_k}}(s_t, a_t)$ using the value function $V_{\phi_k}$.
-The policy parameters $\theta_{k+1}$ are updated by performing gradient ascent with respect to the policy parameters to maximize the clipped surrogate objective function.
-The value function parameters $\phi_{k+1}$ are updated by minimizing the mean squared error between the predicted value and the actual collected reward.
-The agent iterates this process until convergence to learn an optimal policy for hedging VAs.
-
-\subsection{Accounting for Non-Markovian Dynamics}
-
-In the context of hedging VAs, the state space is partially observed.
-The agent does not have access to the contract specifications and the underlying risk factors.
-Furthermore, a rough volatility model introduces non-Markovian dynamics, i.e., the future state of the system depends on the entire history of the system.
-To address the non-Markovian dynamics, an LSTM component is added to the state representation $\mathbf{s}_t$ to capture the temporal dependencies in the data.
-This approach is known as recurrent PPO~\citep{ni2021recurrent}.
-Let $h_t$ be the hidden state of the LSTM at time $t$.
-The state representation $\mathbf{s}_t$ is fed into the LSTM at each time step to update the hidden state $h_t$.
-\begin{equation} \label{eq3:stateRNN}
-    \mathbf{s}_t = (S_t, F_t, G_t, \tau, \Delta_{t-1}), \quad h_t = \text{LSTM}(\mathbf{s}_t, h_{t-1})
-\end{equation}
-The difference between a feedforward neural network (FNN) and a LSTM network is illustrated in Figure~\ref{fig3:nn}.
-
-\begin{figure}[ht!]
-    \centering
-    \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{./project3/tikz/fnn.pdf}
-        \caption{FNN}
-        \label{subfig3:fnn}
-    \end{subfigure}
-    \hspace{1cm}
-    \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{./project3/tikz/lstm.pdf}
-        \caption{LSTM}
-        \label{subfig3:lstm}
-    \end{subfigure}
-    \caption{Neural Network Architectures}
-    \label{fig3:nn}
-\end{figure}
-
-In a LSTM, the cell state $c_t$ stores a representation of historical information up to time $t$.
-It is updated at each time step by a forget gate $f_t$, an input gate $i_t$, and an output gate $o_t$.
-
-In a recurrent PPO with LSTM, the policy and reward function remain the same but with the new state representation in Equation~\ref{eq3:stateRNN}.
-Instead of following the standard PPO algorithm, the agent uses the recurrent PPO algorithm to learn an optimal policy for hedging VAs.
-Figure~\ref{fig3:architecturePPO} illustrates the network architecture of the standard PPO and the recurrent PPO with LSTM, and Algorithm~\ref{alg3:ppoHedging-rnn} outlines the recurrent PPO algorithm and for training an agent to hedge VAs with non-Markovian dynamics.
-
-\begin{algorithm}
-    \caption{Recurrent PPO with LSTM for Hedging Variable Annuities} 
-    \begin{algorithmic}[1] \label{alg3:ppoHedging-rnn}
-        \STATE  Initialize policy parameters $\theta_0$ and value function parameters $\phi_0$.
-        \STATE  Initialize the LSTM layers with random weights, and set the hidden state $h_0$ to zeros.
-        \STATE  \textbf{For} {iteration $k=0, 1,2,\ldots$} \textbf{do}
-        \STATE  \quad Collect a set of trajectories $\mathcal{D}_k$ by sampling from the environment with policy $\pi_{\theta_{k}}$.
-        \STATE  \quad Reset the LSTM hidden state $h_0$ to zeros at the beginning of each trajectory.
-        \STATE  \quad Compute the rewards $\hat{R}_t$ for each trajectory in $\mathcal{D}_k$.
-        \STATE  \quad Estimates the advantage function with $\hat{A}_{\pi_{\theta_k}}(\mathbf{s}_t, a_t)$ using value function $V_{\phi_k}$.
-        \STATE  \quad Update the policy parameters $\theta_{k+1}$ by 
-        \begin{equation*}
-            \max_{\theta} \mathbb{E}\left[ \min \left\{ \Lambda_t(\theta)\hat{A}^{\pi_{\theta}}(\mathbf{s}_t, a_t), \text{clip}(\Lambda_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(\mathbf{s}_t, a_t)  \right\} \right]
-        \end{equation*}
-        \STATE  \quad Update the value function parameters $\phi_{k+1}$ by minimizing the mean squared error between the predicted value and the actual collected reward.
-        \begin{equation*}
-            \phi_{k+1} = \arg \min_{\phi} \frac{1}{|\mathcal{D}_k|T} \sum_{\mathcal{\kappa} \in \mathcal{D}_k} \sum_{t=0}^{T} \left( V_{\phi}(\mathbf{s}_t) - \hat{R}_t \right)^2
-        \end{equation*}
-        \STATE  \textbf{End For}
-    \end{algorithmic}
-\end{algorithm}
-
-\begin{figure}[ht!]
-    \centering
-    \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{./project3/tikz/ppo_diagram.pdf}
-        \caption{regular PPO}
-        \label{subfig3:architecturePPO}
-    \end{subfigure}
-    \hspace{1cm}
-    \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{./project3/tikz/recurrentppo_diagram.pdf}
-        \caption{Recurrent PPO with LSTM}
-        \label{subfig3:architectureLSTMPPO}
-    \end{subfigure}
-    \caption{PPO Network Architectures} 
-    \label{fig3:architecturePPO}
-\end{figure}
-
-The recurrent PPO algorithm is similar to the standard PPO algorithm, but it includes an LSTM component to capture the temporal dependencies in the data.
-However, the sequantial nature of the LSTM is not suitable for parallel computation, which slows down the training process.
-
-\section{Numerical Experiments}
-
-We present a numerical experiment to demonstrate the effectiveness of the model-free PPO algorithm for hedging VAs with transaction costs.
-We consider a VA contract with a maturity of $T=240$ months and a guaranteed minimum maturity benefit (GMMB) rider with a simulation environment described in Section~\ref{subsec:VASimulation}.
-The simulation enviornment is implemented in Python using the OpenAI Gym framework~\citep{brockman2016openai}, and the neural networks are programmed using the PyTorch library~\citep{paszke2019pytorch}.
-The environment is designed to simulate the dynamics of the VA contract and provide the agent with the current state of the VA with the contract specifications and the financial market information described in Table~\ref{tab3:hyperparameters}.
-
-\begin{table}[ht!]
-    \centering
-    \begin{tabular}{ll} 
-        \toprule
-        Hyperparameter      & Value \\
-        \midrule
-        $|\mathcal{D}_k|$   & 16        \\
-        $\epsilon$          & 0.2       \\
-        Learning rate       & 0.0001    \\
-        $S_0$               & 1000      \\
-        $\mu$               & 0.00375   \\
-        $\sigma$            & 0.0457627 \\
-        $r$                 & 0.002     \\
-        $T$                 & 240       \\
-        \bottomrule
-    \end{tabular}
-    \caption{PPO Hyperparameters and GMMB Contract Specifications} 
-    \label{tab3:hyperparameters}
-\end{table}
-
-The underlying asset price $S_t$ is modeled as a geometric Brownian motion (GBM) with a drift rate $\mu$ and a volatility $\sigma$.
-The weights of the value network and the policy network are initialized with orthogonal initialization~\citep{engstrom2020implementation} with scaling $\sqrt{2}$ and the bias terms set to zero.
-The value network and the policy network are implemented as fully connected neural networks with two hidden layers of 16 units each and $\tanh$ activation functions.
-They are trained using the Adam optimizer with a learning rate of $0.0001$ and a batch size automatically adjusted to the number of trajectories in the collected dataset.
-At each timestep, the observations are normalized and cliped between $-10$ and $10$ before being fed into the neural networks to stabilize the training process.
-For PPO, we follow the suggestions in~\cite{schulman2017proximal} and set the clipping hyperparameter $\epsilon$ to $0.2$ to prevent large policy updates. 
-More specifically, our implementation of the PPO uses a generalized advantage estimation~\citep{schulman2015high} to estimate the advantage function.
-The agent interacts with the environment for $10^5$ episodes, and the policy and value networks are evaluated every $1000$ episodes.
-The performance of the agent is evaluated based on the average reward over an independent test set of $10^4$ episodes, and the results are compared with the benchmark hedging strategy, delta hedging.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\textwidth]{./project3/figures/loss_distribution.png}
-    \caption{Performance of PPO for Hedging GMMB Contracts on GBM Asset Model} 
-    \label{fig3:ppo_hedging}
-\end{figure}
-
-Figure~\ref{fig3:ppo_hedging} shows the performance of the PPO algorithm for hedging GMMB contracts on a GBM asset model.
-The figure shows the distribution of the hedging errors incurred by the agent over the $10^4$ test episodes.
-The hedging errors are calculated as the difference between the actual cash flow incurred by the agent due to rebalancing and the expected cash flow based on the optimal hedging policy.
-The results show that the PPO algorithm is able to learn an optimal hedging policy that minimizes the hedging errors, and it surpasses the benchmark delta hedging strategy in terms of hedging performance.
-
-\section{Conclusion}
+\section{Conclusion} \label{sec3:conclusion}

### 2024-09-27 uw-ethesis-frontpgs.tex
small changes to intro
new

@@
 
-        Waterloo, Ontario, Canada, 2022 \\
+        Waterloo, Ontario, Canada, 2024 \\
 
@@
 
-        \copyright\ Xintong Li, 2022 \\
+        \copyright\ Xintong Li, 2024 \\
         \end{center}
@@
 In machine learning, model flexibility comes at the expense of model resilience, which is especially crucial for risk management tasks.
-This study considers the management of tail risk for complex financial and actuarial products with resilient machine learning-based nested simulation procedures and reinforcement learning-based hedging policies.
+This study considers the management of tail risk for complex financial and actuarial products with resilient machine learning-based nested simulation procedures.
+We propose a novel metamodeling approach that integrates deep neural networks within the nested simulation framework for efficient risk estimation.
 Our approaches offer significant improvements over a standard simulation procedures and illustrate a resilient machine learning model is built by accounting for problem complexity and data structure, quality, and quantity.
+To further enhance adaptability to new VA contracts and changing market conditions, the thesis introduces transfer learning techniques. 
+By reusing and fine-tuning pre-trained metamodels, the approach accelerates the adaptation process to different contract features and evolving market dynamics without the need for retraining models from scratch.
+Transfer learning improves computational efficiency ando enhances the robustness and flexibility neural network metamodels in dynamic hedging of variable annuities.
+
+Extensive numerical experiments demonstrate that the proposed method achieves substantial improvements in computational efficiency, reducing simulation times by orders of magnitude compared to standard nested simulation procedures.
+The results indicate that the deep neural network metamodels with transfer learning can quickly adapt to new market scenarios and contract specifications.
+The findings of this research contribute to the advancement of risk management practices for complex actuarial products and financial derivatives.
+By leveraging advanced machine learning techniques, the thesis offers a practical and scalable solution for insurers to perform timely and accurate risk assessments.
+The integration of LSTM metamodels and transfer learning into the nested simulation framework represents a significant step toward more efficient, adaptable, and robust methodologies in actuarial science and quantitative finance.
 

### 2024-09-28 project3/draft.tex
new

@@
 In this chapter, we explore the application of transfer learning to the dynamic hedging of VAs using RNN and LSTM metamodels.
-We propose a novel transfer learning framework that accelerates the training of DNN metamodels for nested simulation in a dynamic hedging problem.
+We propose a novel transfer learning framework that accelerates the training of DNN metamodels for nested simulatiogn in a dynamic hedging problem.
 Our approach involves pre-training an LSTM network on a large dataset of VA simulations and then fine-tuning it on a smaller dataset of new VA contracts.
@@
 
-\section{Background} \label{sec3:background}
+\section{Transfer Learning in Metamodeling} \label{sec3:background}
 
-\section{Transfer Learning for Rapid Adaptation of LSTM Metamodels} \label{sec3:transfer_learning}
+Transfer learning (TL) is a machine learning paradigm where knowledge acquired from a source task is utilized to improve learning performance on a related target task.
+We refer readers to \cite{pan2009survey} for a comprehensive survey of transfer learning techniques and applications.
+In the context of DNNs metamodeling-based simulation procedures for hedging VAs, TL involves pre-training a neural network where the simulation budget is abundant and then fine-tuning it on a smaller dataset of new contracts or market conditions.
+Written on the same underlying asset, different VA contracts may share common features or exhibit similar patterns, especially temporal dependencies in the underlying financial time series.
+Similarly, two VAs with the same features but based on different underlying assets may have some shared characteristics that can be leveraged to improve the learning performance of the metamodel.
+By transferring knowledge from a pre-trained model to a new but related task, TL can significantly reduce the computational cost of training the metamodel on the target task.
+
+LSTM networks are well-suited for modeling sequential data due to their ability to capture long-term dependencies.
+For the application of VA risk management using metamodel-based nested simulation, LSTM networks approximate the inner simulation, i.e., the mapping from market scenarios to the scenario-wise contract losses.
+In Chapter~\ref{chap:project2}, we treat metamodeling as a supervised learning problem and demonstrated that LSTM networks can effectively model this complex relationships with extensive training on a large dataset of VA simulations.
+The total computational cost originates from two sources: running the standard nested simulation procedure to generate the training data and training the LSTM network on the generate dataset.
+Given a new of VA contract, the above process needs to be repeated to adapt the LSTM metamodel to the new contract.
+For a DNN with a large number of parameters, retraining the LSTM network from scratch can be computationally expensive.
+TL offers an alternative approach to keep the previous knowledge as a foundation, thus accelerates the adaptation of the LSTM metamodel to new conditions.
+Computational savings come in two forms: (1) less training time is required to fine-tune the pre-trained model on the new dataset, and (2) fewer data points are needed to achieve a good LSTM metamodel, which is particularly beneficial when the standard nested simulation procedure is costly.
+
+In supervised learning, a \textbf{domain} $\mathcal{D}$ comprises a feature space $\mathcal{X}$ and a marginal probability distribution $F$.
+Correspondingly, a \textbf{task} $\mathcal{T}$ consists of a label space $\mathcal{Y}$ and a predictive function $f: \mathcal{X} \rightarrow \mathcal{Y}$ that maps input features to output labels.
+
+A typical TL framework for supervised learning consists of the following:
+\begin{itemize}
+    \item   \textbf{source domain}: $\mathcal{D}_{\text{So}} = \{\mathcal{X}_{\text{So}}, F_{\text{So}}(X)\}$
+    \item   \textbf{source task}: $\mathcal{T}_{\text{So}} = \{\mathcal{Y}_{\text{So}}, f_{\text{So}}(\cdot)\}$
+    \item   \textbf{target domain}: $\mathcal{D}_{\text{Ta}} = \{\mathcal{X}_{\text{Ta}}, F_{\text{Ta}}(x)\}$
+    \item   \textbf{target task}: $\mathcal{T}_{\text{Ta}} = \{\mathcal{Y}_{\text{Ta}}, f_{\text{Ta}}(\cdot)\}$
+\end{itemize}
+
+where $\mathcal{X}_{\text{So}}$ and $\mathcal{X}_{\text{Ta}}$ include input features derived from the outer simulation of two different VA contracts or market conditions, and $F_{\text{So}}(X)$ and $F_{\text{Ta}}(x)$ are the marginal probability distributions of the source and target domains, respectively.
+In our numerical experiments, the dataset is generated by running the standard nested simulation procedure in Algorithm~\ref{alg2:standardProcedure} for a large number of VA contracts.
+The input features $X$ are the risk factors, and the output labels $L$ are the contract losses at each time step.
+We keep the number of features to be $240$ for both source and target domains as in Section~\ref{sec2:numerical}.
+The predictive function $f_{\text{So}}$ and $f_{\text{Ta}}$ are trained to estimate outputs $L_{\text{So}}$ and $L_{\text{Ta}}$ such as contract losses in inner simulations under the source and target tasks, respectively.
+Transfer learning seeks to improve the learning of the target predictive function $f_{\text{Ta}}(\cdot)$ in $\mathcal{D}_{\text{Ta}}$ by leveraging the previous training on $\mathcal{D}_{\text{So}}$ and $f_{\text{So}}(\cdot)$, particularly when $\mathcal{D}_{\text{So}} \neq \mathcal{D}_{\text{Ta}}$ or $\mathcal{T}_{\text{So}} \neq \mathcal{T}_{\text{Ta}}$.
+In Chapter~\ref{chap:project2}, $\mathcal{D}_{\text{So}} = \mathcal{D}_{\text{Ta}}$ and $\mathcal{T}_{\text{So}} = \mathcal{T}_{\text{Ta}}$.
+
+In our TL setting, both the source and target tasks involve learning a mapping from the risk factors to the VA contract losses.
+For the source task, we have a dataset $\mathcal{D}_{\text{So}} = { (X_{\text{So}}^{(i)}, L_{\text{So}}^{(i)}) }{i=1}^{M_{\text{So}}}$, where $M_{\text{So}}$ is the number of training samples, i.e., the number of outer simulation paths used to generate the dataset with a standard nested simulation procedure.
+$X_{\text{So}}^{(i)} \in \mathcal{X}_{\text{So}}$ and $L_{\text{So}}^{(i)} \in \mathcal{Y}_{\text{So}}$.
+
+The ultimate objective is to learn a metamodel $f_{\text{Ta}}$ that predicts the VA contract losses $L_{\text{So}}$ from the scenarios $X_{\text{Ta}}$ in the form of a financial time series.
+TL starts by training a metamodel $f_{\text{So}}$ on the source domain $\mathcal{D}_{\text{So}}$.
+$f_{\text{So}}$ is approximated by an LSTM network $f_{\text{So}}(\cdot ; \theta_{\text{So}})$, and the parameters of the LSTM network, $\theta_{\text{So}}$ are learned by minimizing a MSE loss function on the source domain.
+Then the pre-trained parameters $\theta_{\text{So}}$ to inform the learning of $f_{\text{Ta}}(\cdot ; \theta_{\text{Ta}})$ on the target domain $\mathcal{D}_{\text{Ta}}$.
+The training on the target domain should encourage similarity between $\theta_{\text{So}}$ and $\theta_{\text{Ta}}$ to facilitate the transfer of knowledge.
+
+The most common TL techniques for supervised learning include fine-tuning, layer freezing, and multi-task learning. 
+These techniques can be categorized based on how they leverage pre-trained metamodels and how they encourage the similarity between $f_{\text{So}}(\cdot ; \theta_{\text{So}})$ and $f_{\text{Ta}}(\cdot ; \theta_{\text{Ta}})$.
+
+\subsection{Fine-tuning}
+
+Fine-tuning is a commonly used TL technique that uses the \textbf{same neural network architecture} for both the source and target tasks.
+We first train the source LSTM metamodel $f_{\text{So}}(\cdot; \theta_{\text{So}})$ on $\mathcal{D}_{\text{So}}$, capturing temporal dependencies and patterns relevant to the source task. 
+For the target task, we initialize $\theta_{\text{Ta}} = \theta_{\text{So}}$ and proceed to fine-tune the entire network on $\mathcal{D}_{\text{Ta}}$ using a smaller learning rate. 
+This algorithm assumes that the learned sequential representations are beneficial for the target task.
+Only minor adjustments are needed to adapt the metamodel to the new task, and the training process is accelerated by the pre-trained parameters.
+
+\subsection{Layer Freezing}
+
+In layer freezing, we partition the model parameters into frozen layers $\theta_1$ and trainable layers $\theta_2$, such that $\theta = [\theta_1; \theta_2]$. 
+% This approach leverages the general feature representations captured by the frozen layers, adapting only the task-specific layers to the target domain~\citep{howard2018universal}.
+
+\subsection{Multi-task Learning}
+
+\section{Rapid Adaptation of LSTM Metamodels} \label{sec3:transfer_learning}
 

### 2024-09-29 project3/draft.tex
new

@@
 For the target task, we initialize $\theta_{\text{Ta}} = \theta_{\text{So}}$ and proceed to fine-tune the entire network on $\mathcal{D}_{\text{Ta}}$ using a smaller learning rate.
-This algorithm assumes that the learned sequential representations are beneficial for the target task.
+
+\begin{algorithm}[ht!]
+\caption{Fine-tuning Metamodel for a Target Task}
+\begin{algorithmic}[1] \label{alg3:fineTuning}
+    \STATE \textbf{Input:} source dataset $\mathcal{D}_{\text{So}} = \{(X_{\text{So}}^{(i)}, L_{\text{So}}^{(i)})\}_{i=1}^{M_{\text{So}}}$ , target dataset $\mathcal{D}_{\text{Ta}} = \{(X_{\text{Ta}}^{(i)}, L_{\text{Ta}}^{(i)})\}_{i=1}^{M_{\text{Ta}}}$, learning rate $\alpha_{\text{So}}$ and smaller learning rate $\alpha_{\text{Ta}}$.
+
+    \STATE Train a LSTM metamodel $f_{\text{So}}(\cdot; \theta_{\text{So}})$ on $\mathcal{D}_{\text{So}}$:
+    \begin{equation}
+        \theta_{\text{So}} = \min_{\theta} \frac{1}{M_{\text{So}}} \sum_{i=1}^{M_{\text{So}}} \left( f_{\text{So}}(X_{\text{So}}^{(i)}; \theta) - L_{\text{So}}^{(i)} \right)^2
+    \end{equation}
+
+    \STATE Initialize the target metamodel parameters $\theta_{\text{Ta}}$ using the pre-trained metamodel parameters:
+    \[
+    \theta_{\text{Ta}} \gets \theta_{\text{So}}
+    \]
+
+    \STATE Fine-tune the entire LSTM model $f_{\text{Ta}}(\cdot; \theta_{\text{Ta}})$ on the target dataset $\mathcal{D}_{\text{Ta}}$ using a smaller learning rate $\alpha_{\text{Ta}}$:
+    \begin{equation}
+        \theta_{\text{Ta}} = \min_{\theta} \frac{1}{M_{\text{Ta}}} \sum_{i=1}^{M_{\text{Ta}}} \left( f_{\text{Ta}}(X_{\text{Ta}}^{(i)}; \theta) - L_{\text{Ta}}^{(i)} \right)^2
+    \end{equation}
+
+    \STATE \textbf{Output:} Final adapted LSTM metamodel $f_{\text{Ta}}(\cdot; \theta_{\text{Ta}})$ for the target task
+\end{algorithmic}
+\end{algorithm}
+
+Algorithm~\ref{alg3:fineTuning} assumes that the learned sequential representations are beneficial for the target task.
 Only minor adjustments are needed to adapt the metamodel to the new task, and the training process is accelerated by the pre-trained parameters.
+Fine-tuning is particularly useful when the nested simulation procedures for the two VA contracts are closely related.
+Only minor adjustments are needed to adapt the LSTM metamodel to the new domain.
 
@@
 
-In layer freezing, we partition the model parameters into frozen layers $\theta_1$ and trainable layers $\theta_2$, such that $\theta = [\theta_1; \theta_2]$. 
-% This approach leverages the general feature representations captured by the frozen layers, adapting only the task-specific layers to the target domain~\citep{howard2018universal}.
+In a layer freezing approach, we partition the model parameters into frozen parameters $\theta_0$ and trainable parameters $\theta_1$, such that $\theta = [\theta_0, \theta_1]$. 
+Typically, $\theta_0$ are parameters of the lower layers, and $\theta_1$ are parameters of the higher layers that include the output layer.
+The intuition behind layer freezing is that the lower layers capture general features that are transferable across tasks, while the higher layers are more task-specific.
+
+\begin{algorithm}[ht!]
+    \caption{Layer Freezing for Metamodel Transfer}
+    \begin{algorithmic}[1] \label{alg3:layerFreezing}
+        \STATE \textbf{Input:} source dataset $\mathcal{D}_{\text{So}} = \{(X_{\text{So}}^{(i)}, L_{\text{So}}^{(i)})\}_{i=1}^{M_{\text{So}}}$, target dataset $\mathcal{D}_{\text{Ta}} = \{(X_{\text{Ta}}^{(i)}, L_{\text{Ta}}^{(i)})\}_{i=1}^{M_{\text{Ta}}}$, learning rates $\alpha_{\text{So}}$ and $\alpha_{\text{Ta}}$, frozen parameters $\theta_0$, trainable parameters $\theta_1$.
+
+        \STATE Train LSTM model $f_{\text{So}}(\cdot; \theta_{\text{So}})$ on $\mathcal{D}_{\text{So}}$:
+        \begin{equation}
+            \theta_{\text{So}} = [\theta_0, \theta_1] = \min_{\theta} \frac{1}{M_{\text{So}}} \sum_{i=1}^{M_{\text{So}}} \left( f_{\text{So}}(X_{\text{So}}^{(i)}; \theta) - L_{\text{So}}^{(i)} \right)^2
+        \end{equation}
+
+        \STATE Initialize the target model parameters $\theta_{\text{Ta}} = [\theta_0, \theta_1]$ using the pre-trained source model parameters $\theta_{\text{So}}$:
+        \[
+        \theta_{\text{Ta}} \gets \theta_{\text{So}} = [\theta_0, \theta_1]
+        \]
+
+        \STATE Freeze the parameters of the shared layers $\theta_0$:
+
+        \STATE Fine-tune the trainable higher layers $\theta_1$ on the target dataset $\mathcal{D}_{\text{Ta}}$ using Algorithm~\ref{alg3:fineTuning}:
+        \begin{equation}
+            \theta_{\text{Ta}} = \min_{\theta_1} \frac{1}{M_{\text{Ta}}} \sum_{i=1}^{M_{\text{Ta}}} \left( f_{\text{Ta}}(X_{\text{Ta}}^{(i)}; [\theta_0, \theta_1]) - L_{\text{Ta}}^{(i)} \right)^2
+        \end{equation}
+
+        \STATE \textbf{Output:} Final adapted LSTM metamodel $f_{\text{Ta}}(\cdot; [\theta_0, \theta_1])$ for the target task
+    \end{algorithmic}
+    \end{algorithm}
 
@@
 
-\section{Rapid Adaptation of LSTM Metamodels} \label{sec3:transfer_learning}
+Multi-task learning~\citep{caruana1997multitask} refers to a machine learning paradigm where a single model is trained simultaneously on multiple related tasks.
+Shared representations are learned across tasks, which can improve learning efficiency and predictive performance on each individual task with limited data.
+In contrast to fine-tuning and layer freezing, multi-task learning aims to leverage learned knowledge from multiple tasks, and all tasks are trained simultaneously.
+
+Let $\{\mathcal{T}_k\}_{k=1}^K$ represent a set of $K$ related tasks, each corresponding to a metamodeling task for a different standard nested simulation procedure.
+For each task $\mathcal{T}_k$, we have a dataset $\mathcal{D}_k = { (X_k^{(i)}, L_k^{(i)}) }{i=1}^{M_k}$, where $M_k$ is the number of training samples for task $k$.
+$X_k^{(i)}$ and $L_k^{(i)}$ are the features and contract loss labels for task $k$, respectively.
+
+For our metamodeling implementation in Chapter~\ref{chap:project2}, we consider a multi-task learning framework where the LSTM layers are shared across multiple tasks, and each task has its own fully connected layer for prediction.
+The network parameters are divided into shared parameters $\theta_0$ (LSTM layers) and task-specific parameters $\theta_k$ (fully connected layers for task $k$). 
+As opposed to layer freezing, all parameters are trainable.
+The objective function for multi-task learning is the sum of the loss functions of all tasks:
+
+\begin{equation} 
+    \min_{\theta_0, \theta_1, \dots, \theta_K} = \sum_{k=1}^K \frac{1}{M_k} \sum_{i=1}^{M_k} \left( f_i(X_k^{(i)}; \theta_0, \theta_1, \dots, \theta_K) - L_k^{(i)} \right)^2,
+\end{equation}
+
+where MSE loss function is used as the error metric, and $f_i(\cdot; \theta_0, \theta_1, \dots, \theta_K)$ is the output of the network for task $k$.
+In essence, multi-task learning uses a multi-head architecture, where each task has its own output head, but the shared LSTM layers learn a common representation across tasks.
+Transfer occurs through the shared LSTM layers $\theta_0$. 
+These layers learn representations of temporal patterns and dependencies common to all tasks, effectively \textbf{pooling} information from multiple simulation schemes. 
+The task-specific fully connected layers $[\theta_1, \dots, \theta_K]$ allow each task to capture unique characteristics not shared with other tasks.
+
+\begin{algorithm}
+    \caption{Multi-task Learning Framework for LSTM Metamodels}
+    \begin{algorithmic}[1] \label{alg3:multiTaskLearning}
+        \STATE \textbf{Input:} learning rate $\alpha$, set of $K$ tasks $\{\mathcal{T}_k\}_{k=1}^K$ with datasets $\mathcal{D}_k = \{(X_k^{(i)}, L_k^{(i)})\}_{i=1}^{M_k}$, task-specific parameters $\theta_k$ for each task $k$, and shared parameters $\theta_0$.
+
+        \STATE Train the multi-head LSTM metamodel on all $K$ tasks simultaneously:
+        \begin{equation}
+            \min_{\theta_0, \{\theta_k\}_{k=1}^K} \sum_{k=1}^K \frac{1}{M_k} \sum_{i=1}^{M_k} \left( f_i(X_k^{(i)}; \theta_0, \theta_k) - L_k^{(i)} \right)^2
+        \end{equation}
+
+        \STATE Update both the shared parameters $\theta_0$ and task-specific parameters $\{\theta_k\}_{k=1}^K$ simultaneously using backpropagation and gradient descent with learning rate $\alpha$.
+
+        \STATE \textbf{Output:} Trained multi-task LSTM metamodel $f(\cdot; \theta_0, \{\theta_k\}_{k=1}^K)$ for all $K$ tasks
+    \end{algorithmic}
+\end{algorithm}
+
+Algorithm~\ref{alg3:multiTaskLearning} outlines the multi-task learning framework for LSTM metamodels for nested simulation procedures.
+In Chapter~\ref{chap:project1} and Chapter~\ref{chap:project2}, we demonstrate that pooling using a metamodel can improve the computation efficiency and estimator accuracy in nested simulation procedures.
+Here, pooling happens at a higher level, where information from multiple metamodels are shared to improve the learning performance on individual tasks.
+
+Choosing appropriate simulation schemes is crucial for the success of multi-task learning.
+The tasks should be related to ensure that the shared layers can capture common features beneficial across tasks.
+Criteria for selecting simulation schemes include:
+
+\begin{itemize} 
+    \item   \textbf{Similarity in contract specifications:} 
+            simulations involving VA contracts with similar features are likely to share underlying risk factors and policyholder behaviors. 
+    \item   \textbf{Similarity in underlying assets:} 
+            datasets simulated under different but related asset models can provide diverse information that enrich the shared representations.
+            Datasets simulated under extreme market conditions can help the shared layers learn to hedge against tail risks.
+    \item   \textbf{Temporal Dynamics:} 
+            VA contracts with comparable maturity and rebalance frequency can help the shared layers learn temporal dependencies consistent across tasks. 
+\end{itemize}
+
+Suppose we aim to develop an LSTM metamodel for a GMWB contract under a stochastic volatility asset model, but we have limited data for this simulation scheme. 
+For multi-task learning, we can select related nested simulation simulation procedures with relatively abundant data, such as:
+
+\begin{itemize} 
+    \item GMMB contracts under stochastic volatility models. 
+    \item GMWB contracts under the Black-Scholes model. 
+    \item GMWB contracts under stochastic volatility models with different parameters.
+\end{itemize}
+
+These tasks share similarities in contract features and market dynamics, enabling the shared LSTM layers to learn relevant temporal patterns applicable to the target task.
+Furthermore, if a new but similar task is introduced, fine-tuning, layer freezing, and multi-task learning can be combined to leverage the pre-trained model effectively.
+More specfically, the shared layers can be frozen, and the task-specific layers for a similar task in the training set can be fine-tuned on the new task.
+This shared knowledge helps the model generalize better on a target task, as the LSTM layers have been exposed to a wider variety of patterns and dynamics.
+
+\subsection{Rapid Adaptation of LSTM Metamodels} \label{sec3:transfer_learning}
+
+In this section, we propose a transfer learning framework for rapid adaptation of LSTM metamodels in dynamic hedging of VAs.
+The goal is to leverage the knowledge acquired during training on a large dataset of VA simulations to improve the learning performance on a smaller dataset of new VA contracts.
+
+\begin{algorithm}
+    \caption{Transfer Learning Framework for LSTM Metamodels: Combining Fine-tuning, Layer Freezing, and Multi-task Learning}
+    \begin{algorithmic}[1] \label{alg3:combined}
+        \STATE \textbf{Input:} Set of $K$ tasks $\{\mathcal{T}_k\}_{k=1}^K$, with datasets $\mathcal{D}_k = \{(X_k^{(i)}, L_k^{(i)})\}_{i=1}^{M_k}$ for each task $k$, target dataset $\mathcal{D}_{\text{Ta}}$, learning rate $\alpha_{\text{So}}$ and $\alpha_{\text{Ta}}$, shared parameters $\theta_0$, task-specific parameters $\theta_k$ for each task $k$.
+
+        \STATE \textbf{Multi-task learning:} define shared LSTM layers $\theta_0$ and task-specific fully connected layers $\theta_k$ for each task $k$.
+The LSTM layers are shared across all tasks $\{\mathcal{T}_k\}_{k=1}^K$.
+
+        \STATE Train the multi-task LSTM metamodel on all $K$ tasks simultaneously:
+        \begin{equation}
+            \min_{\theta_0, \{\theta_k\}_{k=1}^K} \sum_{k=1}^K \frac{1}{M_k} \sum_{i=1}^{M_k} \left( f_i(X_k^{(i)}; \theta_0, \theta_k) - L_k^{(i)} \right)^2
+        \end{equation}
+
+        \STATE \textbf{Layer freezing:} once the multi-task metamodel is trained, freeze the parameters of the shared LSTM layers $\theta_0$.
+
+        \STATE \textbf{Fine-tuning:}  based on task similarity, initialize the target task model parameters $\theta_{\text{Ta}}$ using parameters $\theta_k$ from task $k$.
+        \[
+        \theta_{\text{Ta}} \gets \theta_k 
+        \]
+
+        \STATE Fine-tune only $\theta_{\text{Ta}}$ on the new target dataset $\mathcal{D}_{\text{Ta}}$ using a smaller learning rate $\alpha_{\text{Ta}}$:
+        \begin{equation}
+            \min_{\theta_{\text{Ta}}} \frac{1}{M_{\text{Ta}}} \sum_{i=1}^{M_{\text{Ta}}} \left( f_{\text{Ta}}(X_{\text{Ta}}^{(i)}; \theta_0, \theta_{\text{Ta}}) - L_{\text{Ta}}^{(i)} \right)^2
+        \end{equation}
+
+        \STATE \textbf{Output:} Final adapted LSTM metamodel $f_{\text{Ta}}(\cdot; \theta_0, \theta_{\text{Ta}})$ for the new VA contracts in the target task.
+    \end{algorithmic}
+    \end{algorithm}
+
+Algorithm~\ref{alg3:combined} combines the strengths of Multi-task learning, layer freezing, and fine-tuning to accelerate the training of LSTM metamodels.
+
+\begin{itemize}
+    \item \textbf{Multi-task learning} allows the shared LSTM layers to pool information across related tasks, learning generalizable representations of temporal dependencies.
+    \item \textbf{Layer freezing} ensures that shared features learned from source tasks are retained when adapting to a new task, reducing the risk of overfitting to the target simulation data.
+    \item \textbf{Fine-tuning} enables the task-specific layers to adapt quickly to the new task with minimal simulation cost, leveraging the pre-trained shared layers.
+\end{itemize}
+
+The combination of these techniques aims to significantly reduce the computational cost of training LSTM metamodels for a new but related VA contract.
 
@@
 
+In this section, we evaluate the performance of the transfer learning framework for rapid adaptation of LSTM metamodels in dynamic hedging of VAs.
+The low noise dataset generated by the standard nested simulation procedure in Section~\ref{sec2:numerical} is used to train the source LSTM metamodels.
+We consider two target tasks: one with the same contract but different underlying asset model and another with different contracts but the same asset model.
+
 \section{Conclusion} \label{sec3:conclusion}
+
+Multi-task learning offers a robust framework for transferring knowledge across related simulation schemes in LSTM metamodeling for nested simulations. 
+By sharing representations through the LSTM layers, the model can learn more generalizable features, enhancing performance on tasks with limited data. 
+Careful selection of simulation schemes and thoughtful design of the network architecture are essential to maximize the benefits of MTL while mitigating potential challenges.

### 2024-10-01 project3/draft.tex
new

@@
 Transfer learning (TL) is a machine learning paradigm where knowledge acquired from a source task is utilized to improve learning performance on a related target task.
-We refer readers to \cite{pan2009survey} for a comprehensive survey of transfer learning techniques and applications.
+We refer readers to \cite{pan2009survey} for a comprehensive survey of TL techniques and applications.
 In the context of DNNs metamodeling-based simulation procedures for hedging VAs, TL involves pre-training a neural network where the simulation budget is abundant and then fine-tuning it on a smaller dataset of new contracts or market conditions.
@@
 The predictive function $f_{\text{So}}$ and $f_{\text{Ta}}$ are trained to estimate outputs $L_{\text{So}}$ and $L_{\text{Ta}}$ such as contract losses in inner simulations under the source and target tasks, respectively.
-Transfer learning seeks to improve the learning of the target predictive function $f_{\text{Ta}}(\cdot)$ in $\mathcal{D}_{\text{Ta}}$ by leveraging the previous training on $\mathcal{D}_{\text{So}}$ and $f_{\text{So}}(\cdot)$, particularly when $\mathcal{D}_{\text{So}} \neq \mathcal{D}_{\text{Ta}}$ or $\mathcal{T}_{\text{So}} \neq \mathcal{T}_{\text{Ta}}$.
+TL seeks to improve the learning of the target predictive function $f_{\text{Ta}}(\cdot)$ in $\mathcal{D}_{\text{Ta}}$ by leveraging the previous training on $\mathcal{D}_{\text{So}}$ and $f_{\text{So}}(\cdot)$, particularly when $\mathcal{D}_{\text{So}} \neq \mathcal{D}_{\text{Ta}}$ or $\mathcal{T}_{\text{So}} \neq \mathcal{T}_{\text{Ta}}$.
 In Chapter~\ref{chap:project2}, $\mathcal{D}_{\text{So}} = \mathcal{D}_{\text{Ta}}$ and $\mathcal{T}_{\text{So}} = \mathcal{T}_{\text{Ta}}$.
@@
 
-        \STATE Fine-tune the trainable higher layers $\theta_1$ on the target dataset $\mathcal{D}_{\text{Ta}}$ using Algorithm~\ref{alg3:fineTuning}:
+        \STATE Fine-tune the trainable layers $\theta_1$ on the target dataset $\mathcal{D}_{\text{Ta}}$ using Algorithm~\ref{alg3:fineTuning}:
         \begin{equation}
@@
 
-In this section, we propose a transfer learning framework for rapid adaptation of LSTM metamodels in dynamic hedging of VAs.
+In this section, we propose a TL framework for rapid adaptation of LSTM metamodels in dynamic hedging of VAs.
 The goal is to leverage the knowledge acquired during training on a large dataset of VA simulations to improve the learning performance on a smaller dataset of new VA contracts.
@@
         \end{equation}
+
+        \STATE For a related task of hedging a new VA contract, combine fine-tuning and layer freezing:
 
@@
 
-In this section, we evaluate the performance of the transfer learning framework for rapid adaptation of LSTM metamodels in dynamic hedging of VAs.
+In this section, we evaluate the performance of the TL framework for rapid adaptation of LSTM metamodels in dynamic hedging of VAs.
 The low noise dataset generated by the standard nested simulation procedure in Section~\ref{sec2:numerical} is used to train the source LSTM metamodels.
 We consider two target tasks: one with the same contract but different underlying asset model and another with different contracts but the same asset model.
+
+Serveral datasets generated by related standard nested simulation procedures are considered as source and target tasks.
+VA contract losses are simulated under geometric Brownian motion (GBM) and regime-switching GBM (RS-GBM) asset models.
+The contracts include GMMB and GMWB contracts with no lapse, static lapse, and dynamic lapse features.
+The source dataset is generated by running the standard nested simulation procedure for 50,000 VA contracts, while each target task consists of 2,000 new sample paths.
+
+\begin{enumerate}
+    \item   GMMB contracts under RS-GBM asset model with no lapse.
+    \item   GMMB contracts under RS-GBM asset model with static lapse.
+    \item   GMMB contracts under RS-GBM asset model with dynamic lapse.
+    \item   GMWB contracts under RS-GBM asset model with dynamic lapse.
+\end{enumerate}
+
+From the first task to the last task, the complexity of the simulation schemes increases, and the LSTM metamodels need to adapt to the new conditions.
+Similar to Chapter~\ref{chap:project2}, the true contract losses for all scenarios are approximated by the standard nested simulation procedures with 100,000 inner replications. 
+The training datasets are generated on the same scenarios with 100 inner replications.
+These datasets are referred to as the \textbf{true dataset} and the \textbf{training dataset}, respectively in Section~\ref{sec2:numerical}.
+Hyperparameters, dropout rates, and network architectures for the LSTM metamodels are the same as the LSTM metamodel in Section~\ref{sec2:numerical}. 
+Due to limited computational resources, macro replications are not feasible for the tranfer learning experiments.
+
+\subsection{Fine-Tuning and Layer Freezing}
+
+\begin{figure}[ht!]
+    \centering
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/figure1a.png}
+        \caption{Extensive Training on Target Task} 
+        \label{subfig3-1:extensive}
+    \end{subfigure}\hfill
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/figure1b.png}
+        \caption{Without TL}
+        \label{subfig3-1:without}
+    \end{subfigure}
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/figure1c.png}
+        \caption{With Fine-tuning}
+        \label{subfig3-1:fineTuning}
+    \end{subfigure}\hfill
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/figure1d.png}
+        \caption{With Layer Freezing}
+        \label{subfig3-1:layerFreezing}
+    \end{subfigure}
+    \caption{Metamodel performance on RS-GBM GMMB with static lapse}
+    \label{fig3:figure1}
+\end{figure}
+
+We first compare the performance of fine-tuning and layer freezing on the target tasks.
+Figure~\ref{fig3:figure1} compares the performance of LSTM metamodels on the target tasks with and without TL.
+The learning history of the LSTM metamodels is shown for the target task of metamodeling GMMB contract losses on RS-GBM with static lapse.
+The source task is GMMB contracts on RS-GBM with no lapse, and the target task is the same simulation scheme but with static lapse.
+Figure~\ref{subfig3-1:extensive} demonstrates the performance of the LSTM metamodel trained extensively on the target task using $M_{\text{TA}} = 50,\!000$ samples, which serves as the benchmark for this study.
+The metamodel achieves a low validation error due to the availability of a large dataset.
+In contrast, Figure~\ref{subfig3-1:without} presents the results of training without TL, where $M_{\text{So}} = 50,\!000$, and $M_{\text{TA}} = 2,\!000$.
+This approach leads to highly unstable training dynamics, with substantial fluctuations in the validation error.
+Learning without transfer leads poor generalization and extreme overfitting. 
+Often, the training data is limited for a new VA contract, and such instability is particularly problematic for quick adaptation of LSTM metamodels.
+Figure~\ref{subfig3-1:fineTuning} shows the results of fine-tuning a pretrained metamodel on RS-GBM with no lapse.
+Fine-tuning offers noticeable improvements over training without TL by reducing the instability and lowering the validation error. 
+However, despite these improvements, fine-tuning may not fully mitigate the challenges of training with a small dataset.
+The fine-tuned metamodel still exhibits some fluctuations in the validation error, indicating that the model may not generalize well to new conditions.
+Figure~\ref{subfig3-1:layerFreezing} presents the results of layer freezing on the same target task.
+Layer freezing offers a more stable training process compared to fine-tuning, with a lower validation error and reduced fluctuations during its training.
+The underlying reason is that the LSTM layers are critical for capturing general feature representations that are transferable across tasks, and freezing these layers helps prevent overfitting to the target task.
+Layer freezing effectively retains useful information from the source task, while allowing the model to adapt to the new conditions in a data-efficient manner.
+
+\subsection{Transfer to VAs with Dynamic Lapse}
+
+\begin{figure}[ht!]
+    \centering
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/figure2a.png}
+        \caption{Fine-tuning from No Lapse} 
+        \label{subfig3-2:fromNolapse}
+    \end{subfigure}\hfill
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/figure2b.png}
+        \caption{Fine-tuning from Static Lapse}
+        \label{subfig3-2:fromLapse}
+    \end{subfigure}
+    \caption{Fine-tuned Metamodel performance on RS-GBM GMMB with dynamic lapse}
+    \label{fig3:figure2}
+\end{figure}
+
+We further investigate the performance of fine-tuning on the target task of metamodeling GMMB contract losses on RS-GBM with dynamic lapse. 
+The source tasks used for pretraining are GMMB contracts on RS-GBM with no lapse and static lapse, respectively. 
+Figure~\ref{fig3:figure2} displays the learning curves of the LSTM metamodels fine-tuned from these two distinct source tasks.
+We observe that the performance of the fine-tuned metamodel is highly dependent on the similarity between the source and target tasks.
+Fine-tuning from a source task with static lapse results in faster convergence and lower validation error.
+The metamodel trained on the GMMB with static lapse captures some features that are beneficial for the GMMB with dynamic lapse, which leads to a more stable training process.
+In Figure~\ref{subfig3-2:fromNolapse}, the metamodel needs to learn the effect of (1) whether lapse is present and (2) whether the lapse is dynamic.
+This learning process is more challenging.
+
+The observed improvement in transferability when fine-tuning from a static lapse source task highlights the importance of selecting appropriate source tasks in TL. 
+When the source task diverges significantly from the target task, the transferred metamodel may struggle to adapt to the new conditions given the limited amount of of training data.
+
+\begin{figure}[ht!]
+    \centering
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/figure3a.png}
+        \caption{Freezing LSTM Layers} 
+        \label{subfig3-3:freezeLSTM}
+    \end{subfigure}\hfill
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/figure3b.png}
+        \caption{Freezing the Fully Connected Layer}
+        \label{subfig3-3:freezeFC}
+    \end{subfigure}
+    \caption{Layer Freezing on RS-GBM GMMB with dynamic lapse}
+    \label{fig3:figure3}
+\end{figure}
+
+Figure~\ref{fig3:figure3} continues the investigation of layer freezing in the task of metamodeling GMMB contract losses on RS-GBM with dynamic lapse. 
+When transferring knowledge from the GMMB model with static lapse, the primary adaptation for the target task involves learning the impact of dynamic lapse.
+Freezing the LSTM layers and fine-tuning only the fully connected layer results in a higher validation error, which suggests a tendency of overfitting.
+This indicates that the fully connected layer struggles to adapt to the changes in the temporal dynamics introduced by dynamic lapse.
+In contrast, freezing the fully connected layer and fine-tuning the LSTM layers leads to a lower validation error and better generalization. 
+This can be attributed to the fact that the LSTM layers are responsible for capturing the temporal dependencies associated with dynamic lapse, while the fully connected layer remains less sensitive to shifts in the financial time series.
+
+This experiment emphasizes the importance of choosing which layers to freeze based on the nature of the source and target tasks. 
+In this case, the temporal structure of the data requires the LSTM layers to be flexible in learning new patterns related to dynamic lapse, while the fully connected layer can retain its original functionality.
+
+\subsection{Transfer Knowledge to Other Contract Types}
+
+When transferring knowledge from one VA contract type to another, the LSTM metamodel needs to adapt to different contract features and time series dynamics.
+We consider the task of metamodeling GMWB contract losses on RS-GBM with dynamic lapse, with the source tasks being GMMB contracts on RS-GBM also with dynamic lapse.
+Figure~\ref{fig3:figure4} illustrates the learning curves of the LSTM metamodels fine-tuned from the GMMB contracts to the GMWB contracts.
+
+\begin{figure}[ht!]
+    \centering
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/figure4a.png}
+        \caption{Extensive Training on Target Task} 
+        \label{subfig3-4:extensive}
+    \end{subfigure}\hfill
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/figure4b.png}
+        \caption{Without TL}
+        \label{subfig3-4:without}
+    \end{subfigure}
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/figure4c.png}
+        \caption{With Fine-tuning}
+        \label{subfig3-4:fineTuning}
+    \end{subfigure}\hfill
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/figure4d.png}
+        \caption{With Layer Freezing}
+        \label{subfig3-4:layerFreezing}
+    \end{subfigure}
+    \caption{TL performance on RS-GBM GMWB with dynamic lapse}
+    \label{fig3:figure4}
+\end{figure}
+
+Figure~\ref{subfig3-4:extensive} presents the performance of an extensively trained LSTM metamodel on the target task using 50,000 samples, serving as a benchmark of best metamodel performance. 
+The extensively trained metamodel achieves a low validation error and demonstrates stable convergence due to having enough training samples. 
+In contrast, Figure~\ref{subfig3-4:without} shows the results of training the metamodel on the target task without TL, using only 2,000 samples.
+The limited data leads to unstable training dynamics, with significant fluctuations in the validation error, indicating poor generalization and a tendency to overfit.
+
+When applying fine-tuning from the GMMB source task, as depicted in Figure~\ref{subfig3-4:fineTuning}, the metamodel exhibits improved performance compared to training without TL. 
+Fine-tuning results in a lower validation error and more stable convergence. 
+Despite the differences between GMMB and GMWB contracts, there is still valuable information that can be transferred. 
+Both the LSTM layers and the fully connected layers capture general temporal patterns and feature representations that are beneficial for the target task. 
+Fine-tuning allows the metamodel to adjust all layers, facilitating better adaptation to the complexities introduced by the GMWB contracts.
+
+However, when employing layer freezing, as shown in Figure~\ref{subfig3-4:layerFreezing}, the metamodel's performance deteriorates.
+Freezing the layers trained on the GMMB contracts does not allow the metamodel to sufficiently adapt to the complexities of the GMWB contracts. 
+The GMWB contracts are inherently more complex than GMMB contracts due to the guaranteed withdrawal benefits at each time step.
+The complexity introduce significant changes in the time series dynamics that the metamodel needs to capture.
+Freezing the LSTM layers or the fully connected layer hinders the metamodel's ability to learn these new patterns, and it leads to poor generalization and unstable error curves.
+
+The failure of layer freezing in this context indicates that the difference between the source and target tasks is too substantial for this method to be effective. 
+While layer freezing can be advantageous when the source and target tasks are closely related, it may hinder performance when the tasks diverge significantly.
+In such circumstances, fine-tuning provides a better approach by allowing the metamodel to leverage transferable knowledge while adapting to the new task's specific requirements. 
+Fine-tuning enables both the LSTM and fully connected layers to update their weights, capturing the complex dynamics of the GMWB contracts more effectively.
+
+These results highlight the importance of selecting appropriate TL strategies based on the similarity between the source and target tasks. 
+Even when the source and target contracts are substantially different, TL via fine-tuning can still offer performance improvements over training from scratch. 
+The ability to transfer general feature representations underscores the value of TL in dynamic hedging of VAs. 
+It enables more efficient training of metamodels and reduces computational burden for hedging new VA products. 
+Therefore, it is still worthwhile to transfer information from GMMB contracts when developing metamodels for more complex VA contracts given limited simulation data.
 

### 2024-10-01 project3/draft.tex
new

@@
 
-\section{Transfer Learning in Metamodeling} \label{sec3:background}
+\section{Transfer Learning in Financial Metamodeling} \label{sec3:background}
 
 Transfer learning (TL) is a machine learning paradigm where knowledge acquired from a source task is utilized to improve learning performance on a related target task.
-We refer readers to \cite{pan2009survey} for a comprehensive survey of TL techniques and applications.
-In the context of DNNs metamodeling-based simulation procedures for hedging VAs, TL involves pre-training a neural network where the simulation budget is abundant and then fine-tuning it on a smaller dataset of new contracts or market conditions.
+One of the primary applications of TL in finance is asset price prediction. 
+Traditional models, such as autoregressive integrated moving average (ARIMA) and generalized autoregressive conditional heteroskedasticity (GARCH), have been widely used in time series modeling.
+However, these models often struggle to capture the complex patterns and nonlinear relationships in financial data.
+DNNs like RNN and LSTM networks have demonstrated significant improvements in modeling temporal dependencies. 
+However, training these models from scratch requires extensive data, which may not always be available for specific assets or under certain market conditions.
+TL offers a solution to this problem by leveraging knowledge from related assets or tasks to improve the learning performance of DNNs on the target task.
+In algorithmic trading,~\cite{jeong2019improving} used TL to enhance the performance of a reinforcement learning agent by preventing overfitting from insufficient market data.
+TL techniques have also been applied in building fraud detection systems. 
+Financial fraud often exhibits subtle and evolving patterns, making it challenging to develop robust detection models.
+By transferring previous knowledge from detected fraud cases, models can adapt to detect new fraud schemes more effectively~\citep{lebichot2021transfer}.
+\cite{yan2024comprehensive} conduct a comprehensive survey study of current TL techniques in financial applications, and they find almost all applications of TL only employ parameter transfer, where the pre-trained model is fine-tuned on the target task.
+Our multi-task learning framework in Section~\ref{sec3:transfer_learning} extends beyond parameter transfer to shared representation learning across multiple tasks.
+
+Regarding nested simulation of VAs,~\cite{cheng2019fast} is the most relevant study to our work, where they proposed a TL framework for fast valuation of large portfolios of VAs.
+Instead of using stochastic kriging~\citep{gan2015valuation}, they employed a pre-trained DNN to select the best representative scenarios from a large portfolio of VAs.
+In our work, we focus on the application of TL to accelerate the training of LSTM metamodels for nested simulation in dynamic hedging of VAs.
+The fine-tuned LSTM metamodels can be readily adapted to the two-stage procedure and the single-stage procedure in Chapter~\ref{chap:project2} to predict the contract losses under different market scenarios.
+
+In our context of DNNs metamodeling-based simulation procedures for hedging VAs, TL involves pre-training a neural network where the simulation budget is abundant and then fine-tuning it on a smaller dataset of new contracts or market conditions.
 Written on the same underlying asset, different VA contracts may share common features or exhibit similar patterns, especially temporal dependencies in the underlying financial time series.
@@
 The metamodel achieves a low validation error due to the availability of a large dataset.
-In contrast, Figure~\ref{subfig3-1:without} presents the results of training without TL, where $M_{\text{So}} = 50,\!000$, and $M_{\text{TA}} = 2,\!000$.
+In contrast, Figure~\ref{subfig3-1:without} presents the results of training without TL, where $M_{\text{So}} = 50,\!000$, and $M_{\text{TA}} = 2,\!000$ samples.
 This approach leads to highly unstable training dynamics, with substantial fluctuations in the validation error.
@@
 The extensively trained metamodel achieves a low validation error and demonstrates stable convergence due to having enough training samples. 
-In contrast, Figure~\ref{subfig3-4:without} shows the results of training the metamodel on the target task without TL, using only 2,000 samples.
+In contrast, Figure~\ref{subfig3-4:without} shows the results of training the metamodel on the target task without TL, using only $M_{\text{TA}} = 2,\!000$ samples.
 The limited data leads to unstable training dynamics, with significant fluctuations in the validation error, indicating poor generalization and a tendency to overfit.
@@
 
-These results highlight the importance of selecting appropriate TL strategies based on the similarity between the source and target tasks. 
+\begin{table}[ht!]
+    \centering
+    \begin{tabular}{lllll}
+    \toprule
+    \textbf{Source} & \textbf{Extensive} & \textbf{Fine-tuning} & \textbf{Layer Freezing} & \textbf{Without TL} \\
+    \midrule
+    No Lapse & N/A & 0.4894 & 0.3361 & N/A \\
+    Static Lapse & N/A & 0.0794 & 0.0763 & N/A \\
+    Dynamic Lapse & 0.0587 &  N/A &  N/A & 0.2950 \\
+    \bottomrule
+    \end{tabular}
+    \caption{Comparison of different TL methods across various source tasks.}
+    \label{tab3:transfer_learning_results}
+\end{table}
+
+Table~\ref{tab3:transfer_learning_results} summarizes the MSEs of the LSTM metamodels trained using different TL methods across various source tasks.
+The last row shows the performance of training without TL on the target task.
+The results demonstrate the effectiveness of fine-tuning and layer freezing in transferring knowledge from different source tasks to the target task, and it is consistent with the observations from the learning curves.
+These numerical results highlight the importance of selecting appropriate TL strategies based on the similarity between the source and target tasks. 
 Even when the source and target contracts are substantially different, TL via fine-tuning can still offer performance improvements over training from scratch. 
@@
 It enables more efficient training of metamodels and reduces computational burden for hedging new VA products. 
-Therefore, it is still worthwhile to transfer information from GMMB contracts when developing metamodels for more complex VA contracts given limited simulation data.
+Therefore, it is still worthwhile to transfer information from GMMB contracts when developing metamodels for more complex VA contracts with limited simulation data.
+
+\subsection{Multi-task Learning}
 

### 2024-10-01 project3/draft.tex
new

@@
 
-Table~\ref{tab3:transfer_learning_results} summarizes the MSEs of the LSTM metamodels trained using different TL methods across various source tasks.
+Table~\ref{tab3:transfer_learning_results} summarizes the true MSEs of the LSTM metamodels trained using different TL methods across various source tasks.
+The calculations are based on the metamodel predictions and the approximate true contract losses with $100,\!000$ inner replications.
 The last row shows the performance of training without TL on the target task.

### 2024-10-03 project3/draft.tex
new

@@
 
-        \STATE Train the multi-head LSTM metamodel on all $K$ tasks simultaneously:
-        \begin{equation}
+        \STATE Train the multi-head LSTM metamodel on all $K$ tasks simultaneously by minimizing the multi-task loss function:
+        \begin{equation} \label{eq3:multiTaskLoss}
             \min_{\theta_0, \{\theta_k\}_{k=1}^K} \sum_{k=1}^K \frac{1}{M_k} \sum_{i=1}^{M_k} \left( f_i(X_k^{(i)}; \theta_0, \theta_k) - L_k^{(i)} \right)^2
@@
 Here, pooling happens at a higher level, where information from multiple metamodels are shared to improve the learning performance on individual tasks.
+The multi-task loss function encourages the shared LSTM layers to learn generalizable representations of temporal dependencies that are beneficial across all tasks.
 
@@
 
+Multi-task learning enables the LSTM metamodels to learn shared representations across related VA contracts.
+In this section, we examine the performance of multitask learning applied to two types of VAs, GMMB and GMWB with dynamic lapse rates.
+The simulation datasets contrain $2,\!000$ samples for each contract type, and the LSTM metamodels are trained using multi-task learning. 
+The metamodels are simultaneously trained to minimize the multi-task MSE loss function in Equation~\ref{eq3:multiTaskLoss}.
+We use individual task training as a baseline for comparison, where the LSTM metamodels are trained separately on the GMMB and GMWB contracts.
+The objective is to assess how multitask learning can improve the training efficiency and performance of both products compared to individual task training.
+
+% Below is a digram of the multi-task learning framework from mtl.pdf (tikz)
+\begin{figure}[ht!]
+    \includegraphics[width=\textwidth]{./project3/tikz/mtl.pdf}
+    \caption{Multi-task Learning Framework for VA Contracts}
+    \label{fig3:mtl}
+\end{figure}
+
+Figure~\ref{fig3:mtl} illustrates our multi-task learning framework for GMMB and GMWB contracts with dynamic lapse rates.
+The outer simulation paths for both contracts are the same, which are generated from the same nested simulation procedure with $100$ inner replications.
+The LSTM metamodels are trained simultaneously on both contracts.
+The LSTM layers are shared, and each contract has its own separate fully connected layers for contract loss predictions.
+
+\begin{figure}[ht!]
+    \centering
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/figure5a.png}
+        \caption{Multi-task training history} 
+        \label{subfig3-5:multiTask}
+    \end{subfigure}\hfill
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/figure5b.png}
+        \caption{Task performance with multitask training}
+        \label{subfig3-5:fineTuning}
+    \end{subfigure}
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/figure5c.png}
+        \caption{GMMB individual task training} 
+    \label{subfig3-5:gmmb_individual}
+    \end{subfigure}\hfill
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/figure5d.png}
+        \caption{GMWB individual task training}
+        \label{subfig3-5:gmwb_individual}
+    \end{subfigure}
+    \caption{Multi-task Learning on RS-GBM GMMB and GMWB with dynamic lapse}
+    \label{fig3:figure5}
+\end{figure}
+
+Figure~\ref{fig3:figure5} comopares the learning curves for the training of GMMB and GMWB, with and without multitask learning.
+The comparison between multitask learning (Figure~\ref{subfig3-5:multiTask} and~\ref{subfig3-5:fineTuning}) and individual task training ((Figure~\ref{subfig3-5:gmmb_individual} and~\ref{subfig3-5:gmwb_individual})) demonstrates the benefit of multi-task learning for both products.
+In the case of GMMB, multitask learning allows the model to achieve faster convergence while reducing overfitting.
+For GMWB, the multi-task learning framework helps to stablize the training process.
+The shared LSTM layers in the multitask model are able to capture common temporal patterns and dynamics, which benefits both GMMB and GMWB when training samples is scarce.
+Similar to pooling in Chapter~\ref{chap:project1} but on a higher level, multi-task learning enables the LSTM metamodels to leverage shared representations across related VA contracts.
+
 \section{Conclusion} \label{sec3:conclusion}

### 2024-10-03 project3/tikz/mtl.tex
new

\documentclass[tikz,border=10pt]{standalone}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows.meta, positioning}

\tikzstyle{input} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black]
\tikzstyle{block} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=blue!30]
\tikzstyle{output} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=orange!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

\begin{document}
\begin{tikzpicture}[node distance=2cm]

    % Input layers
    \node (input1) [input] {Outer Simulation Paths};

    % Shared LSTM layers
    \node (lstm1) [block, right of=input1, xshift=2.5cm] {Shared LSTM Layer 1};
    \node (lstm2) [block, right of=lstm1, xshift=2.5cm] {Shared LSTM Layer 2};

    % Task-specific dense layers (Task 1)
    \node (dense1) [block, right of=lstm2, xshift=2.5cm, yshift=0.8cm, fill=green!30] {Task 1 Dense Layer};
    \node (output1) [output, right of=dense1, xshift=2.5cm] {Task 1 Output};

    % Task-specific dense layers (Task 2)
    \node (dense2) [block, right of=lstm2, xshift=2.5cm, yshift=-0.8cm, fill=yellow!30] {Task 2 Dense Layer};
    \node (output2) [output, right of=dense2, xshift=2.5cm] {Task 2 Output};

    % Arrows
    \draw [arrow] (input1) -- (lstm1);

    \draw [arrow] (lstm1) -- (lstm2);

    \draw [arrow] (lstm2.east) -- ++(0.5,0) |- (dense1.west);
    \draw [arrow] (lstm2.east) -- ++(0.5,0) |- (dense2.west);

    \draw [arrow] (dense1) -- (output1);
    \draw [arrow] (dense2) -- (output2);

\end{tikzpicture}
\end{document}

### 2024-10-10 project3/draft.tex
new

@@
 In our TL setting, both the source and target tasks involve learning a mapping from the risk factors to the VA contract losses.
-For the source task, we have a dataset $\mathcal{D}_{\text{So}} = { (X_{\text{So}}^{(i)}, L_{\text{So}}^{(i)}) }{i=1}^{M_{\text{So}}}$, where $M_{\text{So}}$ is the number of training samples, i.e., the number of outer simulation paths used to generate the dataset with a standard nested simulation procedure.
+For the source task, we have a dataset $\mathcal{D}_{\text{So}} = { (X_{\text{So}}^{(i)}, L_{\text{So}}^{(i)}) }_{i=1}^{M_{\text{So}}}$, where $M_{\text{So}}$ is the number of training samples, i.e., the number of outer simulation paths used to generate the dataset with a standard nested simulation procedure.
 $X_{\text{So}}^{(i)} \in \mathcal{X}_{\text{So}}$ and $L_{\text{So}}^{(i)} \in \mathcal{Y}_{\text{So}}$.
@@
 The low noise dataset generated by the standard nested simulation procedure in Section~\ref{sec2:numerical} is used to train the source LSTM metamodels.
-We consider two target tasks: one with the same contract but different underlying asset model and another with different contracts but the same asset model.
+We consider TL to two types of target tasks: (1) the same contract but different underlying asset model, and (2) different contracts but the same asset model.
+Similar to Section~\ref{sec2:numerical}, we use the standard nested simulation procedure to generate the dataset for the source and target tasks.
+Serveral VA datasets generated with the standard nested simulation procedures under geometric Brownian motion (GBM) and regime-switching GBM (RS-GBM) asset models.
 
-Serveral datasets generated by related standard nested simulation procedures are considered as source and target tasks.
-VA contract losses are simulated under geometric Brownian motion (GBM) and regime-switching GBM (RS-GBM) asset models.
-The contracts include GMMB and GMWB contracts with no lapse, static lapse, and dynamic lapse features.
-The source dataset is generated by running the standard nested simulation procedure for 50,000 VA contracts, while each target task consists of 2,000 new sample paths.
+\begin{table}[ht!] 
+    \centering
+    \begin{tabular}{lcccc} 
+    \toprule
+    \textbf{Contract} & \textbf{Asset Model} & \textbf{Lapse} & \textbf{$M_{\text{So}}$}  & \textbf{$M_{\text{Ta}}$}\\
+    \midrule
+    GMMB & GBM & No lapse & 50,000 & N/A \\
+    GMMB & RS-GBM & No lapse & 50,000 & 2,000 \\
+    GMMB & RS-GBM & Static lapse & 50,000 & 2,000 \\
+    GMMB & RS-GBM & Dynamic lapse & 50,000 & 2,000 \\
+    GMWB & RS-GBM & Dynamic lapse & N/A & 2,000 \\
+    \bottomrule
+    \end{tabular}
+    \caption{VA Contracts for Transfer Learning Experiments}
+    \label{tab3:contracts}
+\end{table}
 
-\begin{enumerate}
-    \item   GMMB contracts under RS-GBM asset model with no lapse.
-    \item   GMMB contracts under RS-GBM asset model with static lapse.
-    \item   GMMB contracts under RS-GBM asset model with dynamic lapse.
-    \item   GMWB contracts under RS-GBM asset model with dynamic lapse.
-\end{enumerate}
+Table~\ref{tab3:contracts} lists the VA contracts used in the TL experiments.
+These contracts include GMMB and GMWB contracts with no lapse, static lapse, and dynamic lapse features.
+Before transferred to the target task, a LSTM metamodel is trained on a source dataset with $M_{\text{So}} = 50,\!000$ samples generated with $N_{\text{So}} = 100$ inner replications\footnotemark.
+\footnotetext{The GMMB contract on the GBM asset model is an exception, where scenario-wise contract losses can be computed analytically.}
+The pre-trained LSTM metamodel is then adapted to a target task that is different from the source task.
+The training dataset for the target task has $M_{\text{Ta}} = 2,\!000$ samples generated with $N_{\text{Ta}} = 100$ inner replications.
+During the training on both the source and target tasks, $10\%$ of the data is split into a validation dataset to monitor the training process and prevent overfitting using early stopping.
+The complexity of the simulation schemes increases from the first task to the last task, and the LSTM metamodels need to adapt to the new conditions with limited training data on the target tasks.
 
-From the first task to the last task, the complexity of the simulation schemes increases, and the LSTM metamodels need to adapt to the new conditions.
-Similar to Chapter~\ref{chap:project2}, the true contract losses for all scenarios are approximated by the standard nested simulation procedures with 100,000 inner replications. 
-The training datasets are generated on the same scenarios with 100 inner replications.
-These datasets are referred to as the \textbf{true dataset} and the \textbf{training dataset}, respectively in Section~\ref{sec2:numerical}.
-Hyperparameters, dropout rates, and network architectures for the LSTM metamodels are the same as the LSTM metamodel in Section~\ref{sec2:numerical}. 
-Due to limited computational resources, macro replications are not feasible for the tranfer learning experiments.
+All LSTM metamodels are evaluated based on their training history graphs for the target task, which plot training and validation MSE against the number of training epochs.
+The training history graphs visualize the learning curves of the LSTM metamodels, which provide insights into stability and convergence behavior the metamodels.
+We measure the generalization performance of the LSTM metamodels using the true MSE, which quantifies the accuracy of the LSTM metamodels in approximating the true inner simulation model of VA contracts.
+The true MSE is computed by comparing the metamodel predictions with the true contract losses, which are approximated by the standard nested simulation procedure with $100,\!000$ inner replications.
+Hyperparameters and network architectures for the LSTM metamodels are kept the same as the LSTM metamodel in Section~\ref{sec2:numerical}. 
+Due to limited computational resources, macro replications are not feasible for the TL experiments.
 
-\subsection{Fine-Tuning and Layer Freezing}
+\subsection{Learning Lapse Features}
 
@@
 
-We first compare the performance of fine-tuning and layer freezing on the target tasks.
+We first examine the performance of fine-tuning and layer freezing in adapting LSTM metamodels to new VA contracts with lapse features.
 Figure~\ref{fig3:figure1} compares the performance of LSTM metamodels on the target tasks with and without TL.
-The learning history of the LSTM metamodels is shown for the target task of metamodeling GMMB contract losses on RS-GBM with static lapse.
-The source task is GMMB contracts on RS-GBM with no lapse, and the target task is the same simulation scheme but with static lapse.
-Figure~\ref{subfig3-1:extensive} demonstrates the performance of the LSTM metamodel trained extensively on the target task using $M_{\text{TA}} = 50,\!000$ samples, which serves as the benchmark for this study.
-The metamodel achieves a low validation error due to the availability of a large dataset.
-In contrast, Figure~\ref{subfig3-1:without} presents the results of training without TL, where $M_{\text{So}} = 50,\!000$, and $M_{\text{TA}} = 2,\!000$ samples.
-This approach leads to highly unstable training dynamics, with substantial fluctuations in the validation error.
-Learning without transfer leads poor generalization and extreme overfitting. 
+Learning histories of the LSTM metamodels is shown for the target task of metamodeling GMMB contract losses on the RS-GBM asset model with static lapse.
+The source task is hedging a GMMB contract on RS-GBM with no lapse, and the target task is hedging the same GMMB contract but with static lapse.
+The simulation data for the target task is generated with the same nested simulation simulation procedure as the source task, except for the lapse feature.
+Figure~\ref{subfig3-1:extensive} demonstrates the performance of the LSTM metamodel trained extensively only on the target task using $M_{\text{TA}} = 50,\!000$ samples, which serves as a benchmark for this study.
+The metamodel achieves a low validation MSE due to the availability of a large dataset.
+In contrast, Figure~\ref{subfig3-1:without} presents the results of training directly on the target task without pre-training on the source task.
+With $M_{\text{TA}} = 2,\!000$ samples, the LSTM metamodel struggles to learn the temporal dependencies and patterns in the target task.
+It leads to highly unstable training dynamics, with substantial fluctuations in the validation MSE.
+Learning without knowledge transfer leads poor generalization and extreme overfitting. 
 Often, the training data is limited for a new VA contract, and such instability is particularly problematic for quick adaptation of LSTM metamodels.
+TL techniques like fine-tuning and layer freezing can help mitigate these challenges.
 Figure~\ref{subfig3-1:fineTuning} shows the results of fine-tuning a pretrained metamodel on RS-GBM with no lapse.
-Fine-tuning offers noticeable improvements over training without TL by reducing the instability and lowering the validation error. 
-However, despite these improvements, fine-tuning may not fully mitigate the challenges of training with a small dataset.
-The fine-tuned metamodel still exhibits some fluctuations in the validation error, indicating that the model may not generalize well to new conditions.
-Figure~\ref{subfig3-1:layerFreezing} presents the results of layer freezing on the same target task.
+Fine-tuning offers a noticeable improvement over training without TL by reducing the instability in the validation MSE. 
+However, despite this improvement, fine-tuning may not fully mitigate the challenges of training with a small dataset.
+The fine-tuned metamodel struggles to achieve a low validation MSE.
+Lowering the learning rate does not help the fine-tuned metamodel converge, and the validation MSE remains high after increasing the number of training epochs.
+It indicates that fine-tuning may not be sufficient for limited training data.
+Figure~\ref{subfig3-1:layerFreezing} presents the performance of layer freezing on the same target task.
 Layer freezing offers a more stable training process compared to fine-tuning, with a lower validation error and reduced fluctuations during its training.
-The underlying reason is that the LSTM layers are critical for capturing general feature representations that are transferable across tasks, and freezing these layers helps prevent overfitting to the target task.
-Layer freezing effectively retains useful information from the source task, while allowing the model to adapt to the new conditions in a data-efficient manner.
+The LSTM layers are critical for capturing general feature representations that are transferable across tasks, and freezing these layers helps prevent overfitting to the target task.
+In addition, the layer freezing approch tunes fewer neural network parameters than crude fine-tuning.
+It allows the transferred metamodelmodel to only focus on learning the lapse features without excessively adjusting the general temporal representations learned from the source task.
+This reduction in trainable parameters also accelerates the convergence process, and it leads to a more stable and efficient training on the target task.
 
@@
 Freezing the LSTM layers and fine-tuning only the fully connected layer results in a higher validation error, which suggests a tendency of overfitting.
-This indicates that the fully connected layer struggles to adapt to the changes in the temporal dynamics introduced by dynamic lapse.
+This indicates that the fully connected layer struggles to adapt to the changes in the temporal dynamics introduced by dynamic lapse, which can be viewed as another source of randomness in the time series.
 In contrast, freezing the fully connected layer and fine-tuning the LSTM layers leads to a lower validation error and better generalization. 
-This can be attributed to the fact that the LSTM layers are responsible for capturing the temporal dependencies associated with dynamic lapse, while the fully connected layer remains less sensitive to shifts in the financial time series.
+This can be attributed to the fact that the LSTM layers are responsible for capturing the temporal dependencies associated with dynamic lapse, and the fully connected layer predicts the contract losses based on these learned features.
 
 This experiment emphasizes the importance of choosing which layers to freeze based on the nature of the source and target tasks. 
-In this case, the temporal structure of the data requires the LSTM layers to be flexible in learning new patterns related to dynamic lapse, while the fully connected layer can retain its original functionality.
+In the case of learning dynamic lapse features, freezing the LSTM layers is not beneficial as they need to adapt to the new temporal patterns.
 
-\subsection{Transfer Knowledge to Other Contract Types}
+\begin{table}[ht!]
+    \centering
+    \begin{tabular}{lllll}
+    \toprule
+    \textbf{Source} & \textbf{Extensive} & \textbf{Fine-tuning} & \textbf{Layer Freezing} & \textbf{Without TL} \\
+    \midrule
+    No Lapse GMMB & N/A & 0.4894 & 0.3361 & N/A \\
+    Static Lapse GMMB & N/A & 0.0794 & 0.0763 & N/A \\
+    Dynamic Lapse GMMB & 0.0587 &  N/A &  N/A & 0.2950 \\
+    \bottomrule
+    \end{tabular}
+    \caption{Comparison of different TL methods on GMMB contracts}
+    \label{tab3:transfer_learning_results}
+\end{table}
+
+Table~\ref{tab3:transfer_learning_results} summarizes the true MSEs of the LSTM metamodels trained using different TL methods across various source tasks.
+The calculations are based on the metamodel predictions and the true contract losses approximated with $100,\!000$ inner replications.
+The first two rows show the performance of transferring knowledge from GMMB contracts with no lapse and static lapse to the target task of GMMB with dynamic lapse.
+The last row shows the performance of training without TL on the target task.
+The results demonstrate the effectiveness of fine-tuning and layer freezing in transferring knowledge from a related source tasks to the target task. 
+When transferring from a source task with static lapse to a target task with dynamic lapse, the MSEs achieved are $0.0794$ for fine-tuning and $0.0763$ for layer freezing.
+The benchmark MSE of $0.0587$, obtained from extensive training on the GMMB dynamic lapse task with much more samples.
+While TL from static lapse GMMB do not reach this level of accuracy due to the limited data in the target task, they significantly outperform training without TL. 
+This indicates that the models pre-trained on a static lapse setting are effective in capturing relevant features that are transferable to the dynamic lapse scenario.
+
+However, when the source task is less similar to the target task, the benefits of TL are less pronounced.
+The MSEs in this case are higher, with fine-tuning resulting in $0.4894$ and layer freezing achieving $0.3361$.
+This suggests that the divergence between the source and target tasks can lead to negative transfer.
+These results highlight the importance of selecting source tasks that share significant similarities with the target task to maximize the effectiveness of TL. 
+When the source and target contracts are substantially different, the pre-trained metamodels may struggle to adapt to the new conditions, as they may not have learned features relevant to the target task.
+
+\subsection{Transfer Knowledge to other Contract Types}
 
 When transferring knowledge from one VA contract type to another, the LSTM metamodel needs to adapt to different contract features and time series dynamics.
-We consider the task of metamodeling GMWB contract losses on RS-GBM with dynamic lapse, with the source tasks being GMMB contracts on RS-GBM also with dynamic lapse.
-Figure~\ref{fig3:figure4} illustrates the learning curves of the LSTM metamodels fine-tuned from the GMMB contracts to the GMWB contracts.
+We consider the task of metamodeling GMWB contract losses on RS-GBM asset model with dynamic lapse, with the source tasks being a GMMB contract on RS-GBM also with dynamic lapse.
+Figure~\ref{fig3:figure4} illustrates the learning history of transferring pre-trained LSTM metamodels from the GMMB contracts to the GMWB contracts.
 
@@
 The extensively trained metamodel achieves a low validation error and demonstrates stable convergence due to having enough training samples. 
-In contrast, Figure~\ref{subfig3-4:without} shows the results of training the metamodel on the target task without TL, using only $M_{\text{TA}} = 2,\!000$ samples.
-The limited data leads to unstable training dynamics, with significant fluctuations in the validation error, indicating poor generalization and a tendency to overfit.
+In contrast, Figure~\ref{subfig3-4:without} shows the results of training the metamodel directly on the target task with $2,\!000$ training samples. 
+Fewer training samples and no prior knowledge leads to unstable training dynamics. 
+The validation MSE fluctuates significantly.
 
-When applying fine-tuning from the GMMB source task, as depicted in Figure~\ref{subfig3-4:fineTuning}, the metamodel exhibits improved performance compared to training without TL. 
+When applying fine-tuning from the GMMB source task (Figure~\ref{subfig3-4:fineTuning}), the metamodel exhibits improved performance compared to training without TL. 
 Fine-tuning results in a lower validation error and more stable convergence.
@@
 Both the LSTM layers and the fully connected layers capture general temporal patterns and feature representations that are beneficial for the target task. 
-Fine-tuning allows the metamodel to adjust all layers, facilitating better adaptation to the complexities introduced by the GMWB contracts.
+Fine-tuning allows the metamodel to adjust all its neural network layers. 
+It allows better adaptation to the complexities introduced by the GMWB contract.
 
-However, when employing layer freezing, as shown in Figure~\ref{subfig3-4:layerFreezing}, the metamodel's performance deteriorates.
-Freezing the layers trained on the GMMB contracts does not allow the metamodel to sufficiently adapt to the complexities of the GMWB contracts. 
-The GMWB contracts are inherently more complex than GMMB contracts due to the guaranteed withdrawal benefits at each time step.
+However, when employing layer freezing (Figure~\ref{subfig3-4:layerFreezing}), the metamodel's performance deteriorates.
+Freezing some layers trained on the GMMB contracts does not allow the metamodel to sufficiently adapt to the complexities of the GMWB contracts. 
+The GMWB contracts are inherently more complex than GMMB contracts due to the guaranteed withdrawal benefits at each time step, and the contract features are significantly different.
 The complexity introduce significant changes in the time series dynamics that the metamodel needs to capture.
@@
 
-The failure of layer freezing in this context indicates that the difference between the source and target tasks is too substantial for this method to be effective. 
+\begin{table}[ht!]
+    \centering
+    \begin{tabular}{lrr}
+        \toprule
+        \textbf{Model} & \textbf{Training MSE} & \textbf{True MSE} \\
+        \midrule
+        Without TL & 0.3588 & 0.4188 \\
+        Fine Tuning & 0.1690 & 0.1780 \\
+        Layer Freezing & 0.1828 & 0.2295 \\
+        Extensive Training & 0.0853 & 0.0726 \\
+        \bottomrule
+    \end{tabular}
+    \caption{Comparison of different TL methods on GMWB contracts}
+    \label{tab3:transfer_learning_results_gmwb}
+\end{table}
+
+Table~\ref{tab3:transfer_learning_results_gmwb} summarizes the true MSEs of the LSTM metamodels on the GMWB contracts.
+The suboptimal performance of layer freezing in this context indicates that the difference between the source and target tasks is too substantial for this method to be effective. 
 While layer freezing can be advantageous when the source and target tasks are closely related, it may hinder performance when the tasks diverge significantly.
@@
 Fine-tuning enables both the LSTM and fully connected layers to update their weights, capturing the complex dynamics of the GMWB contracts more effectively.
-
-\begin{table}[ht!]
-    \centering
-    \begin{tabular}{lllll}
-    \toprule
-    \textbf{Source} & \textbf{Extensive} & \textbf{Fine-tuning} & \textbf{Layer Freezing} & \textbf{Without TL} \\
-    \midrule
-    No Lapse & N/A & 0.4894 & 0.3361 & N/A \\
-    Static Lapse & N/A & 0.0794 & 0.0763 & N/A \\
-    Dynamic Lapse & 0.0587 &  N/A &  N/A & 0.2950 \\
-    \bottomrule
-    \end{tabular}
-    \caption{Comparison of different TL methods across various source tasks.}
-    \label{tab3:transfer_learning_results}
-\end{table}
-
-Table~\ref{tab3:transfer_learning_results} summarizes the true MSEs of the LSTM metamodels trained using different TL methods across various source tasks.
-The calculations are based on the metamodel predictions and the approximate true contract losses with $100,\!000$ inner replications.
-The last row shows the performance of training without TL on the target task.
-The results demonstrate the effectiveness of fine-tuning and layer freezing in transferring knowledge from different source tasks to the target task, and it is consistent with the observations from the learning curves.
-These numerical results highlight the importance of selecting appropriate TL strategies based on the similarity between the source and target tasks. 
-Even when the source and target contracts are substantially different, TL via fine-tuning can still offer performance improvements over training from scratch. 
-The ability to transfer general feature representations underscores the value of TL in dynamic hedging of VAs. 
-It enables more efficient training of metamodels and reduces computational burden for hedging new VA products. 
-Therefore, it is still worthwhile to transfer information from GMMB contracts when developing metamodels for more complex VA contracts with limited simulation data.
+This is particularly beneficial when developing metamodels for complex VA contracts with limited simulation data. 
+For instance, transferring information from GMMB contracts can still be valuable when modeling GMWB contracts.
+Both contracts share some common contract features and temporal patterns, which allows a pre-trained LSTM metamodel to capture generalizable features that provide a solid foundation for the target task.
 
@@
 The simulation datasets contrain $2,\!000$ samples for each contract type, and the LSTM metamodels are trained using multi-task learning. 
-The metamodels are simultaneously trained to minimize the multi-task MSE loss function in Equation~\ref{eq3:multiTaskLoss}.
+In our experiments, Algorithm~\ref{alg3:multiTaskLearning} is used to train the LSTM metamodels simultaneously to minimize the multi-task MSE loss function in Equation~\ref{eq3:multiTaskLoss}.
 We use individual task training as a baseline for comparison, where the LSTM metamodels are trained separately on the GMMB and GMWB contracts.
@@
 
-Figure~\ref{fig3:figure5} comopares the learning curves for the training of GMMB and GMWB, with and without multitask learning.
+Figure~\ref{fig3:figure5} compares the learning curves for the training of GMMB and GMWB, with and without multitask learning.
 The comparison between multitask learning (Figure~\ref{subfig3-5:multiTask} and~\ref{subfig3-5:fineTuning}) and individual task training ((Figure~\ref{subfig3-5:gmmb_individual} and~\ref{subfig3-5:gmwb_individual})) demonstrates the benefit of multi-task learning for both products.
@@
 
+% \begin{figure}[ht!]
+%     \centering
+%     \begin{subfigure}{0.48\textwidth}
+%         \includegraphics[width=\textwidth]{./project3/figures/figure5a.png}
+%         \caption{Multi-task training history} 
+%         \label{subfig3-6:multiTask}
+%     \end{subfigure}\hfill
+%     \begin{subfigure}{0.48\textwidth}
+%         \includegraphics[width=\textwidth]{./project3/figures/figure5b.png}
+%         \caption{Task performance with multitask training}
+%         \label{subfig3-6:fineTuning}
+%     \end{subfigure}    
+%     \label{fig3:figure6}
+% \end{figure}
+
+Even when data is abundant, multi-task learning can improve the training efficiency and predictive performance of LSTM metamodels for nested simulations.
+The shared LSTM layers learn generalizable features that are beneficial across different VA contracts.
+% Figure~\ref{fig3:figure6} demonstrates the performance of multi-task learning on GMMB and GMWB contracts with dynamic lapse rates.
+
 \section{Conclusion} \label{sec3:conclusion}
 
+In this chapter, we introduced a transfer learning framework to accelerate the training of LSTM metamodels for dynamic hedging of variable annuity contracts.
+Traditional nested simulation procedures for VA risk management are computationally intensive.
+LSTM metamodels offer a data-driven approach to approximate the true contract losses, which can significantly reduce the computational cost of hedging a single VA contract.
+However, training LSTM metamodels on new VA contracts can be challenging due to the limited availability of simulation data.
+Our proposed framework leverages pre-trained LSTM networks and transfer learning techniques to adapt quickly metamodels to new but related VA contracts with minimal additional simulation cost.
+Fine-tuning a pre-trained LSTM metamodel on a new target task with limited data significantly improved training stability and predictive accuracy compared to training from scratch. 
+Layer freezing further enhanced performance by retaining transferable temporal representations learned from the source task. 
+However, the success of these methods depends on the similarity between the source and target tasks. 
+When the tasks were closely related, freezing some neural network layers yields substantial benefits. 
+Conversely, when the source and target tasks diverged significantly, fine-tuning the entire network is more effective.
+
 Multi-task learning offers a robust framework for transferring knowledge across related simulation schemes in LSTM metamodeling for nested simulations. 
-By sharing representations through the LSTM layers, the model can learn more generalizable features, enhancing performance on tasks with limited data. 
-Careful selection of simulation schemes and thoughtful design of the network architecture are essential to maximize the benefits of MTL while mitigating potential challenges.
+By sharing representations through the LSTM layers, the model can learn more generalizable features that are beneficial across different VA contracts. 
+The multi-task approach was particularly beneficial when training data for individual tasks was scarce, as it effectively pooled information across tasks to enhance learning efficiency and predictive performance.
+Furthermore, a metamodel trained with multi-task learning can serve as a pre-trained model. 
+It is adaptable to various VA contracts and asset models, and it is a versatile tool for practical applications in dynamic hedging of VAs.
+
+The integration of transfer learning into LSTM metamodeling represents a significant advancement in robust risk management associated with variable annuity contracts.
+By effectively leveraging existing knowledge, financial institutions can maintain accurate and responsive risk management practices in a rapidly changing market environment. 
+The methodologies presented in this chapter not only contribute to the field of actuarial science but also open the door for broader applications of transfer learning in financial modeling and risk assessment.

### 2024-10-10 project1/nsSurvey.tex
Updates from Overleaf

--- 2024-04-12 project1/nsSurvey.tex
@@
 Setting $M = \mathcal{O}(\Gamma^{1/2})$ and $N = \mathcal{O}(\Gamma^{1/2})$, we provide a looser bound than the one obtained for hockey-stick $h$.
-This bound can be strengthened by using the bias-variance decomposition in Equation~\ref{eq1:mse-sns2}.
+Using the bias-variance decomposition in Equation~\ref{eq1:mse-sns2},
 
@@
     & = K \mathbb{E} \left[ |\bar{Z}_N| \right] \nonumber \\
-    & \leq K \sqrt{\mathbb{E} \left[ \left( \bar{Z}_N \right)^2 \right]} = \mathcal{O}(N^{-1})
+    & \leq K \sqrt{\mathbb{E} \left[ \left( \bar{Z}_N \right)^2 \right]} = \mathcal{O}(N^{-1/2})
 \end{align}
@@
 The variance term in Equation~\ref{eq1:mse-sns2} for Lipschitz continuous $h$ is identical to the one in Equation~\ref{eq1:var-sns-smooth}.
-Hence, the convergence order of the standard nested simulation procedure for Lipschitz continuous $h$ is the same as the one for smooth $h$.
 
 \begin{equation}
-    \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(M^{-1}) + \mathcal{O}(N^{-2})
+    \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(M^{-1}) + \mathcal{O}(N^{-1})
 \end{equation}
@@
     MSE of the standard nested simulation procedure converges in order $\Gamma^{2/3}$, that is,
-    $$\mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(\Gamma^{-2/3}).$$
+    $$\mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(\Gamma^{-1/2}).$$
 \end{theorem}
@@
     Let $h$ be a Lipschitz continuous function. The absolute error of the standard nested simulation procedure converges in probabilistic order $\Gamma^{-1/3}$, that is,
-    $$\left| \hat{\rho}_{M, N} - \rho \right| = \mathcal{O}_\mathbb{P}(\Gamma^{-1/3}).$$
+    $$\left| \hat{\rho}_{M, N} - \rho \right| = \mathcal{O}_\mathbb{P}(\Gamma^{-1/4}).$$
 \end{corollary}

### 2024-10-10 conclusion.tex
new

@@
 \chapter{Conclusion} \label{chap:conclusion}
-
-In this thesis, we have discussed the use of nested simulation procedures for risk management applications of financial derivatives and insurance products.
-We have shown that the nested simulation framework can be used to efficiently estimate the risk measures of complex financial products, such as variable annuities, by combining machine learning-based metamodels with nested simulations.
 
@@
 Recognizing the computational challenges inherent in the standard nested simulation procedure, especially when estimating tail risk measures for complex financial products, we proposed an innovative approach that integrates machine learning-based metamodels into the nested simulation framework.
+We have shown that the nested simulation framework can be used to efficiently estimate the risk measures of complex financial products, such as variable annuities, by combining machine learning-based metamodels with nested simulations.
 
@@
 
-Additionally, we investigated the adaptability of our approach to changing market conditions and different VA contract features. 
+Additionally, we investigated the feasibility of our approach to changing market conditions and different VA contract features. 
 By incorporating transfer learning techniques, we enabled rapid adaptation of the LSTM metamodels to new contracts and evolving market dynamics. 

### 2024-10-11 project3/draft.tex
new

@@
 
+\begin{figure}[ht!]
+    \centering
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/figure4_1.png}
+        \caption{Tail scenarios identification} 
+        \label{subfig3-4-1:tail}
+    \end{subfigure}\hfill
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{./project3/figures/figure4_2.png}
+        \caption{$95\%$-CVaR prediction}
+        \label{subfig3-4-2:CVaR}
+    \end{subfigure}
+    \caption{TL performance on RS-GBM GMWB with dynamic lapse}
+    \label{fig3:figure4-1}
+\end{figure}
+
+Figure~\ref{fig3:figure4-1} illustrates the performance of the two-stage procedure with TL for GMWB contracts with dynamic lapse in predicting the tail scenarios and the $95\%$-CVaR.
+The graph provides a visual representation of how different TL approaches compare to training from scratch and the standard nested simulation procedure.
+Fine-tuning consistently outperforms both layer freezing and training from scratch across different simulation budgets, particularly in predicting tail scenarios and estimating the 95\%-CVaR. 
+This finding is consistent with the training history and MSEs in Figure~\ref{fig3:figure4} and Table~\ref{tab3:transfer_learning_results_gmwb}, respectively.
+It's important to note that while these results are promising, they also highlight the complexity of modeling GMWB contracts with dynamic lapse. 
+The fact that fine-tuning outperforms layer freezing suggests that there are significant differences in the tail behavior of GMMB and GMWB contracts, particularly when dynamic lapse is considered. 
+This underscores the need for careful model selection and validation when applying TL techniques to different VA products.
+
 \subsection{Multi-task Learning}
@@
 
-% Below is a digram of the multi-task learning framework from mtl.pdf (tikz)
 \begin{figure}[ht!]
@@
 The shared LSTM layers in the multitask model are able to capture common temporal patterns and dynamics, which benefits both GMMB and GMWB when training samples is scarce.
-Similar to pooling in Chapter~\ref{chap:project1} but on a higher level, multi-task learning enables the LSTM metamodels to leverage shared representations across related VA contracts.
+Similar to pooling in Chapter~\ref{chap:project1} and~\ref{chap:project2} but on a higher level, multi-task learning enables the LSTM metamodels to leverage shared representations across related VA contracts.
 
@@
 
-Even when data is abundant, multi-task learning can improve the training efficiency and predictive performance of LSTM metamodels for nested simulations.
-The shared LSTM layers learn generalizable features that are beneficial across different VA contracts.
+% Even when data is abundant, multi-task learning can improve the training efficiency and predictive performance of LSTM metamodels for nested simulations.
+% The shared LSTM layers learn generalizable features that are beneficial across different VA contracts.
 % Figure~\ref{fig3:figure6} demonstrates the performance of multi-task learning on GMMB and GMWB contracts with dynamic lapse rates.
@@
 By effectively leveraging existing knowledge, financial institutions can maintain accurate and responsive risk management practices in a rapidly changing market environment. 
-The methodologies presented in this chapter not only contribute to the field of actuarial science but also open the door for broader applications of transfer learning in financial modeling and risk assessment.
+The methodologies presented in this chapter attempt to make a significant contribution to the broader applications of transfer learning in financial modeling and risk assessment.

### 2024-10-11 project3/draft.tex
new

@@
 \begin{itemize} 
-    \item GMMB contracts under stochastic volatility models. 
-    \item GMWB contracts under the Black-Scholes model. 
-    \item GMWB contracts under stochastic volatility models with different parameters.
+    \item GMMB contracts under a stochastic volatility asset model. 
+    \item GMWB contracts under a Black-Scholes asset model. 
+    \item GMWB contracts under a stochastic volatility model with different simulation parameters.
 \end{itemize}

### 2024-10-25 introduction.tex
new

@@
 
-VA contracts are index-linked insurance products that offer policyholders the potential for capital appreciation through exposure to equity markets while providing guarantees that protect against downside risk.
+VA contracts are index-linked insurance products that offer policyholders the upside potential of equity markets while providing guarantees that protect against downside risk.
 These products have gained significant interest as they address the needs of individuals seeking both wealth accumulation and financial security, especially in the context of retirement planning.
@@
 
-\subsection{Regression Models}
+\subsection{Parametric Regression Models}
 
@@
 where $\theta = (\theta^{(1)}, \theta^{(2)}, \ldots, \theta^{(k)})$ are the trainable parameters of the neural network, $f^{(i)}$ is the $i$-th layer of the neural network, $x$ is the input feature vector, $f^{(1)}(x;\theta^{(1)}) = x$, $f^{(k)}$ is the output layer, $k$ is the number of layers, and $f^{(i)}$ is the output of the $i$-th layer.
-To move from layer $i-1$ to layer $i$,
+To move from a lower layer to a higher layer, i.e., from layer $i-1$ to layer $i$,
 
@@
 By leveraging the memory and sequential modeling capabilities of LSTMs, we aim to improve the accuracy and efficiency of nested simulation procedures for risk management applications.
-
-\subsection{Transfer Learning}
-
-% \subsection{Reinforcement Learning}
-% Reinforcement learning (RL) is a machine learning technique that learns a policy by interacting with an environment and receiving feedback in the form of rewards.
-% In a dynamic heding problem, the policy is a trading strategy that minimizes the risk of the hedged portfolio, the environment contains the financial market dynamics and the contract terms, and the rewards are the negative hedging errors or a risk measure of the hedging portfolio.

### 2024-10-25 project2/nnMetamodels.tex
new

@@
 
-To compare the numerical performances of different simulation procedures, we create a benchmark dataset with a large-scale nested simulation: We first simulate $M=100\!,\!000$ outer scenarios, i.e., $240$-periods stock paths $\bS^{(1)},\ldots,\bS^{(M)}$ under $\mathbb{P}$ and used these outer scenarios in all further experiments.
+To compare the numerical performances of different simulation procedures, we create a benchmark dataset with a large-scale nested simulation: We first simulate $M=\num{100000}$ outer scenarios, i.e., $240$-periods stock paths $\bS^{(1)},\ldots,\bS^{(M)}$ under $\mathbb{P}$ and used these outer scenarios in all further experiments.
 Note that the 5\% tail scenario set includes $5\!,\!000$ scenarios.
-As the hedging losses for these scenarios cannot be calculated analytically, we run inner simulations with a large number of replications, $N=100\!,\!000$, conditional on each of the $M$ scenarios.
+As the hedging losses for these scenarios cannot be calculated analytically, we run inner simulations with a large number of replications, $N=\num{100000}$, conditional on each of the $M$ scenarios.
 We denote these losses by $L_1,\ldots,L_M$ and will refer to them as \textit{true losses}.
@@
 
-We compare our two-stage procedure to a standard nested simulation procedure that runs $N=1\!,\!000$ inner replications for each of the $M=100\!,\!000$ outer scenarios.
-In Stage 1 of the proposed procedure, we first run inner simulations with $N'=100$ inner replications for each of the $M=100\!,\!000$ outer scenarios.
+We compare our two-stage procedure to a standard nested simulation procedure that runs $N=\num{1000}$ inner replications for each of the $M=\num{100000}$ outer scenarios.
+In Stage 1 of the proposed procedure, we first run inner simulations with $N'=100$ inner replications for each of the $M=\num{100000}$ outer scenarios.
 So, Stage 1's simulation budget is $10\%$ of the standard procedure's.
@@
 At the end of Stage 1, $m$ predicted tail scenarios, are identified by the trained metamodels.
-In Stage 2, $N=1\!,\!000$ inner replications are run for all predicted tail scenarios.
+In Stage 2, $N=\num{1000}$ inner replications are run for all predicted tail scenarios.
 Stage 2's simulation budget is $\frac{m}{M}$ of the standard procedure's.
@@
     \midrule
-    MLR & N/A & $241$ & $0.707 (\pm 0.000)$ & $0.877 (\pm 0.001)$ & $0.694 (\pm 0.000)$ \\
+    MLR & N/A & $241$ & $0.707 (\pm 3.6 \times 10^{-4})$ & $0.877 (\pm 0.001)$ & $0.694 (\pm 0.000)$ \\
     QPR & N/A & $481$ & $0.544 (\pm 0.000)$ & $0.636 (\pm 0.001)$ & $0.531 (\pm 0.000)$ \\
@@
 
-The maximum number of data points in the training dataset is set to $M = 100\!,000$.
+The maximum number of data points in the training dataset is set to $M = \num{100000}$.
 The training dataset is split into training and test sets with a 90\%-10\% ratio.
-The true labels are generated by running the standard nested simulation procedure with $N=100\!,000$ inner replications for each of the $100\!,000$ outer scenarios.
-The reason for using a maximum of $100\!,000$ data points is precisely due to the computational cost of running the standard nested simulation procedure.
+The true labels are generated by running the standard nested simulation procedure with $N=\num{100000}$ inner replications for each of the $\num{100000}$ outer scenarios.
+The reason for using a maximum of $\num{100000}$ data points is precisely due to the computational cost of running the standard nested simulation procedure.
 For consistency, the LSTM metamodels are trained with the same architecture and training settings as in the previous experiments.
@@
         LSTM                & $N=1$                  & $1.366 (\pm0.006)$        & $0.781(\pm0.005)$     & $0.129 (\pm0.002)$ \\
-        High-capacityLSTM   & $N=1$                  & $1.354 (\pm0.006)$        & $0.795(\pm0.005)$     & $0.149 (\pm0.002)$ \\
+        High-capacity LSTM  & $N=1$                  & $1.354 (\pm0.006)$        & $0.795(\pm0.005)$     & $0.149 (\pm0.002)$ \\
         Difference          & $N=1$                  & $-0.012$                  & $0.014$               & \textcolor{red}{$0.020$} \\
@@
         \toprule
-                            & $N=1$ & $N=10$  & $N=100$ & $N=1\!,\!000$\\
+                            & $N=1$ & $N=10$  & $N=100$ & $N=\num{1000}$\\
         \midrule
         $M = 100$           & $1.139$ & $0.229$ & $0.167$ & $0.158$ \\
-        $M = 1\!,\!000$     & $0.559$ & $0.173$ & $0.123$ & $0.127$ \\
-        $M = 10\!,\!000$    & $0.283$ & $0.115$ & $0.099$ & $0.097$ \\
-        $M = 100\!,\!000$   & $0.126$ & $0.068$ & $0.063$ & $0.063$ \\
+        $M = \num{1000}$     & $0.559$ & $0.173$ & $0.123$ & $0.127$ \\
+        $M = \num{10000}$    & $0.283$ & $0.115$ & $0.099$ & $0.097$ \\
+        $M = \num{100000}$   & $0.126$ & $0.068$ & $0.063$ & $0.063$ \\
         \bottomrule
@@
         \toprule
-                          & $N=1$ & $N=10$  & $N=100$ & $N=1\!,\!000$\\
+                          & $N=1$ & $N=10$  & $N=100$ & $N=\num{1000}$\\
         \midrule
         $M = 100$           & $0.764$ & $0.408$ & $0.131$ & $0.087$ \\
-        $M = 1\!,\!000$     & $0.878$ & $0.367$ & $0.156$ & $0.087$ \\
-        $M = 10\!,\!000$    & $0.351$ & $0.147$ & $0.064$ & $0.063$ \\
-        $M = 100\!,\!000$   & $0.149$ & $0.065$ & $0.060$ & $0.038$ \\
+        $M = \num{1000}$     & $0.878$ & $0.367$ & $0.156$ & $0.087$ \\
+        $M = \num{10000}$    & $0.351$ & $0.147$ & $0.064$ & $0.063$ \\
+        $M = \num{100000}$   & $0.149$ & $0.065$ & $0.060$ & $0.038$ \\
         \bottomrule
@@
 Table~\ref{tab2:lstm_sens} and~\ref{tab2:hicaplstm_sens} show the average squared errors between the LSTM predictions and the true losses for increasing $M$ and $N$.
-The last rows of Table~\ref{tab2:lstm_sens} and Table~\ref{tab2:hicaplstm_sens} show the performance of the regular and high capacity LSTM metamodels trained with $M=100\!,000$ training labels with different noise levels.
+The last rows of Table~\ref{tab2:lstm_sens} and Table~\ref{tab2:hicaplstm_sens} show the performance of the regular and high capacity LSTM metamodels trained with $M=\num{100000}$ training labels with different noise levels.
 We observe that an increasing $N$ reduces the MSE, but the reduction is not significant for a regular LSTM when $N$ is larger than $10$.
-For the high-capacity LSTM, the MSE is significantly reduced when $N$ is increased from $1$ to $100$, but the reduction is not significant when $N$ is increased from $100$ to $1\!,000$.
+For the high-capacity LSTM, the MSE is significantly reduced when $N$ is increased from $1$ to $100$, but the reduction is not significant when $N$ is increased from $100$ to $\num{1000}$.
 Another way to interpret the results in Table~\ref{tab2:lstm_sens} is to compare the MSEs for the same budget of $\Gamma = M \times N$. 
@@
         \toprule
-                          & $N=1$        & $N=10$        & $N=100$       & $N=1\!,\!000$ \\
+                          & $N=1$        & $N=10$        & $N=100$       & $N=\num{1000}$ \\
         \midrule
         $M = 100$         & 0.638 (0.881) & 0.875 (0.915) & 0.896 (0.903) & 0.937 (0.941) \\
-        $M = 1\!,\!000$   & 0.722 (0.768) & 0.899 (0.908) & 0.886 (0.891) & 0.922 (0.927) \\
-        $M = 10\!,\!000$  & 0.845 (0.630) & 0.937 (0.900) & 0.908 (0.905) & 0.947 (0.948) \\
-        $M = 100\!,\!000$ & 0.935 (0.640) & 0.963 (0.909) & 0.927 (0.922) & 0.965 (0.966) \\
+        $M = \num{1000}$   & 0.722 (0.768) & 0.899 (0.908) & 0.886 (0.891) & 0.922 (0.927) \\
+        $M = \num{10000}$  & 0.845 (0.630) & 0.937 (0.900) & 0.908 (0.905) & 0.947 (0.948) \\
+        $M = \num{100000}$ & 0.935 (0.640) & 0.963 (0.909) & 0.927 (0.922) & 0.965 (0.966) \\
         \bottomrule
@@
 While numerical results suggests that the CVaR estimator of the single-stage procedure with LSTM metamodels may have better accuracy than the two-stage procedure and the standard procedure when the number of outer scenarios is further increased, we found it difficult to compare their performance due to insufficient computational resources.
-For $\Gamma \leq 100\!,000$, the number of outer scenarios is fixed at $M = 100\!,000$, and only the number of inner replications is varied.
+For $\Gamma \leq \num{100000}$, the number of outer scenarios is fixed at $M = \num{100000}$, and only the number of inner replications is varied.
 Instead, we try to analyze the effect of the number of outer scenarios and the number of inner replications separately by fixing one and varying the other.
@@
 Figure~\ref{fig2:mnConvergence} shows the log-log plots of the RRMSE between the LSTM metamodel CVaR predictions and the true CVaR against the simulation budget.
-The left figure shows the empirical convergence of the RRMSE for increasing inner replications with a fixed number of outer scenarios ($M=100\!,\!000$), and the right figure shows the empirical convergence of the RRMSE for increasing outer scenarios with a fixed number of inner replications ($N=10$).
-Due to computational constraints, we are not able to run the two-stage procedure and the standard procedure with more outer scenarios or more inner replications, therefore the comparison between the single-stage procedure is only available up to $M = 100\!,000$ and $N = 1\!,000$.
+The left figure shows the empirical convergence of the RRMSE for increasing inner replications with a fixed number of outer scenarios ($M=\num{100000}$), and the right figure shows the empirical convergence of the RRMSE for increasing outer scenarios with a fixed number of inner replications ($N=10$).
+Due to computational constraints, we are not able to run the two-stage procedure and the standard procedure with more outer scenarios or more inner replications, therefore the comparison between the single-stage procedure is only available up to $M = \num{100000}$ and $N = \num{1000}$.
 We observe that the RRMSE decreases as the simulation budget increases, and the rate of convergence is higher when the quantity of the data increases.
@@
 More specfically, when the quality of the training labels is fixed at $N = 10$, the CVaR estimator of single-stage procedure with a LSTM metamodel converge roughly in the order of $\mathcal{O}(M^{\frac{2}{3}})$.
+This observation resonates with the convergence rate of a regression-based nested simulation procedure in~\cite{broadie2015risk}.
 Hence, in practice, we suggest to run the single-stage procedure with a moderate number of inner replications and a large number of outer scenarios to achieve a high level of accuracy with a reasonable computational cost.

### 2024-10-29 introduction.tex
new

@@
 Numerical experiments are conducted to test their empirical convergence behavior under finite budget sizes.
-Chapter \ref{chap:project2} proposes the use of neural network models as proxies for a two-stage multi-period nested simulation procedure on VA contracts. 
-In our numerical experiment, the best neural network proxy surpasses the state-of-the-art proxy model in tail identification, and it leads to substantial computational savings. 
-Chapter \ref{chap:project3} conducts sensitivity testing on the neural network proxy.
-We argue that for estimating tail risk measures of VA contact losses, the inner simulation can be replaced entirely by a suitable proxy model.
+Chapter~\ref{chap:project2} proposes the use of neural network models as proxies for a two-stage multi-period nested simulation procedure on VA contracts. 
+In our numerical experiment, the best neural network metamodel surpasses the state-of-the-art proxy models in tail identification, and it leads to substantial computational savings. 
+Chapter~\ref{chap:project2} also conducts sensitivity testing on the neural network metamodel.
+We argue that for estimating tail risk measures of VA contact losses, the inner simulation can be replaced entirely by a suitable metamodel.
 Eliminating the inner simulation can lead to more substantial computational savings without affecting estimation quality. 
 In the case of requiring extensive inner simulations for regulatory purposes, effective budget allocations can help achieve higher estimator quality with the same computational budget.
+Chapter~\ref{chap:project3} uses transfer learning techniques for quick adaptation of the neural network metamodel to new VA contracts with different contract specifications.
 Chapter \ref{chap:conclusion} concludes the thesis and discusses potential future research directions.

### 2024-10-29 introduction.tex
new

@@
 
-\subsection{Neural Network Architectures}
+\subsection{Feedforward Neural Networks}
 
@@
 They can learn complex, non-linear relationships in data without the need for explicit feature engineering.
-The most crude form of a neural network is the feedforward neural network, which consists of an input layer, one or more hidden layers, and an output layer~\citep{goodfellow2016}.
+The most crude form of a neural network is the feedforward neural network (FFN), which consists of an input layer, one or more hidden layers, and an output layer~\citep{goodfellow2016}.
 
@@
 The FNN is tuned by adjusting the trainable parameters $\theta$ while fixing the activation functions $a^{(i)}$.
-A typical choice for the activation function is the rectified linear unit (ReLU), which is defined as $a(z) = \max(0, z)$.
+A typical choice for the activation function is the rectified linear unit (ReLU), which is defined as $a(z) = \max(0, z)$~\citep{nair2010rectified}.
+The choice of activation function also plays a crucial role in the training of neural networks.
+While sigmoid and hyperbolic tangent functions were popular in early neural networks, ReLU has become the default activation function for deep networks due to its ability to mitigate the vanishing gradient problem and promote sparse activations~\citep{lecun2015deep}.
 
@@
 In this thesis, we focus on the application of deep neural networks, specifically long short-term memory (LSTM) networks, as metamodels for nested simulation procedures in risk management applications.
+
+\subsection{Training and Evaluation of Neural Networks}
+
+The training of neural networks involves adjusting the trainable parameters of the network to minimize the loss function.
+The loss function is typically the mean squared error (MSE) between the predicted outputs and the true outputs.
+The training process aims to find the optimal parameters that minimize the loss function.
+The most common approach is to use gradient descent methods with backpropagation, which is an efficient method for computing the gradients of the loss function with respect to the trainable parameters.
+Backpropagation computes the gradients by propagating the error derivatives backward through the network layers.
+This process allows the network to adjust the parameters in the direction of minimizing the loss function.
+The training process is typically performed over a number of epochs, where each epoch is one complete pass through the training dataset.
+
+However, the training of neural networks is non-convex, and the optimization problem is challenging.
+Stochastic gradient descent (SGD) is a popular optimization algorithm for training neural networks.
+It updates the parameters using a single or a small batch of training examples at a time, which makes it much faster than the crude gradient descent.
+However, SGD may oscillate and converge slowly, especially in non-convex problems~\citep{bengio2016}.
+To address these issues, various adaptive learning rate methods have been proposed.
+The most popular approach is Adam, which adjusts the learning rate during training to improve convergence speed and stability~\citep{kingma2014adam}.
+
+Another common technique to improve the training of neural networks is regularization to prevent overfitting.
+One effective regularization method is \textit{dropout}, which randomly sets a fraction of neurons to zero during each training iteration~\citep{srivastava2014dropout}.
+This prevents neurons from co-adapting too much, encourages redundancy, and leads to a more robust model that generalizes better to unseen data.
+\textit{Early stopping} is another yet regularization method that involves monitoring the model's performance on a validation set and stopping training when the performance no longer improves~\citep{prechelt2002early}.
+This helps prevent overfitting by halting training before the model begins to overfit to noise in the data.
 
@@
 
+The advancements in neural network optimization techniques, architectures, and training methodologies have significantly enhanced their usefulness in risk management applications.
+By effectively modeling complex, non-linear relationships and temporal dependencies, neural networks serve as powerful tools for addressing the computational challenges in estimating risk measures and developing effective risk mitigation strategies.
 This thesis aims to explore the application and noise tolerance of LSTM networks in metamodeling for nested simulation procedures in risk management.

### 2024-10-31 introduction.tex
new

@@
 
-Quantitative risk management is a key component of modern financial systems, ensuring the stability and resilience of markets, institutions, and portfolios against an array of risks. 
+Quantitative risk management is a key component of modern financial systems.
+Successful risk management practice ensures the stability and resilience against a variety of risks.
 For financial products like option portfolios and variable annuity (VA) contracts, traditional risk assessment methods often fall short in accurately capturing the complex dynamics of the underlying risk factors.
-VA contracts are a popular type of complex insurance product that is linked to the performance of underlying assets, providing a guaranteed minimum income benefit to the policyholder.
-This is where advanced Monte Carlo simulation techniques, particularly nested simulation procedures, become indispensable.
+VA contracts are a popular type of complex insurance product that is linked to the performance of underlying assets.
+It provides a guaranteed minimum income benefit to the policyholder regardless of the performance of the underlying assets.
+Advanced Monte Carlo simulation techniques, particularly nested simulation procedures, become indispensable for risk assessment of such products.
 In contrast to finite-difference methods, a Monte Carlo simulation scheme is more flexible and can be easily adapted to model tail risk with a rule-based design.
-~\cite{glasserman2004monte} provide a comprehensive overview of nested simulation methods in financial engineering and risk management applications.
+~\cite{glasserman2004monte} provide a comprehensive overview of Monte Carlo simulation methods in financial engineering and risk management applications.
 In this thesis, we focus on building and analyzing nested simulation procedures for risk management applications of financial derivatives and insurance products.
@@
 A standard nested simulation procedure consists of two levels of simulation: the outer-level simulation generates the underlying risk factors, while the inner-level simulation estimates the value of interest with the inner sample mean from another level of Monte Carlo simulation.
-The nested structure allows for accurate estimation given sufficient computational resources, but it also introduces additional complexity in the simulation design and implementation.
-Furthermore, in real-world applications, the computational burden of nested simulation can be prohibitive due to its nested structure.
-The number of inner simulations required to achieve a desired level of accuracy for each outer scenario can be prohibitively large.
+This nested structure allows for accurate estimation given sufficient computational resources, but it also introduces additional complexity in the simulation design and implementation.
+Furthermore, in real-world applications, the computational burden of nested simulation can be prohibitive.
+The number of inner simulations required to achieve a desired level of accuracy for each outer scenario can be infeasibly large.
 Metamodeling techniques that approximate the inner simulation model can be used to reduce the computational burden of nested simulation.
@@
 In this thesis, we focus on metamodels of the inner simulation models in nested simulation procedures for risk management applications of financial derivatives and VA contracts.
-Two interesting problems that requires nested simulation are considered in this thesis: (1) estimating the risk of a portfolio of financial options and (2) dynamic hedging of VA contracts with a delta hedging strategy.
+Two interesting problems that requires nested simulation are considered in this thesis:  
+\begin{itemize}
+    \item estimating the risk of a portfolio of financial options and 
+    \item dynamic hedging of VA contracts with a delta hedging strategy.
+\end{itemize}
 The risk management of VAs is a challenging problem due to the complex interactions between the policyholder's behavior, the financial market dynamics, and the insurer's risk management strategies.
-% Moreover, the risk management of VAs is further complicated by transaction costs, which often makes delta hedging strategies insufficient. 
-% This thesis discusses a particular extension of using deep reinforcement learning to dynamically hedge VA contracts with transaction costs.
-
+We focus mainly on the estimation of tail risk measures of VA contract losses using metamodel-based nested simulation procedures.
 This thesis consists of four chapters. 
@@
 Numerical experiments are conducted to test their empirical convergence behavior under finite budget sizes.
-Chapter~\ref{chap:project2} proposes the use of neural network models as proxies for a two-stage multi-period nested simulation procedure on VA contracts. 
-In our numerical experiment, the best neural network metamodel surpasses the state-of-the-art proxy models in tail identification, and it leads to substantial computational savings. 
+Chapter~\ref{chap:project2} proposes the use of neural network models as metamodels for a two-stage multi-period nested simulation procedure on VA contracts. 
+In our numerical experiment, the best neural network metamodel surpasses the state-of-the-art metamodels in tail identification, and it leads to substantial computational savings. 
 Chapter~\ref{chap:project2} also conducts sensitivity testing on the neural network metamodel. 
@@
 In the case of requiring extensive inner simulations for regulatory purposes, effective budget allocations can help achieve higher estimator quality with the same computational budget.
-Chapter~\ref{chap:project3} uses transfer learning techniques for quick adaptation of the neural network metamodel to new VA contracts with different contract specifications.
+In practice, underlying assumptions of the simulation model are subject to change, and new VA contracts are issued with different contract specifications.
+Simulation budgets are often scarce for new conditions.
+Chapter~\ref{chap:project3} uses transfer learning techniques for quick adaptation of the neural network metamodel to new market conditions and new VA contracts.
+Our numerical experiments shows that an intelligent use of transfer learning can lead to significantly better metamodels than those trained from scratch.
+Chapter~\ref{chap:futureWork} discusses the application of deep reinforcement learning in the dynamic hedging of VA contracts.
 Chapter \ref{chap:conclusion} concludes the thesis and discusses potential future research directions.
@@
 This strategy aims to neutralize the sensitivity of the insurer's liability to market fluctuations by constructing a hedging portfolio that replicates the cash flows of the guarantees.
-However, dynamic hedging introduces complexity in estimating the insurer's overall risk exposure, especially concerning extreme market events or tail risks.
-Estimating tail risk in the context of dynamic hedging of VAs is challenging, as it requires the stochastic modeling of the financial market and the accurate loss estimation of the hedging portfolio under various market scenarios.
+However, dynamic hedging introduces complexity in estimating the insurer's overall risk exposure.
+One of such examples is the estimation of tail risk measures of a VA contract.
+It requires the stochastic modeling of the financial market and the accurate loss estimation of the hedging portfolio under different market scenarios.
 Nested simulation has emerged as a robust method for estimating risk measures in such complex settings~\citep{gordy2010nested}.
@@
 Metamodeling is particularly useful when the simulation model is computationally expensive. 
-By replacing the simulation model with a metamodel, the computational cost of evaluating the model can be significantly reduced, enabling faster analysis and decision-making.
+By replacing the simulation model with a metamodel, the computational cost of evaluating the model can be significantly reduced. 
+This allows for faster convergence of simulation-based estimators.
 
@@
     \item \textbf{Design of Experiments}: Selecting input combinations to run the original simulation and collect data. 
-    \item \textbf{Building the Metamodel}: Using the collected data to train a surrogate model that approximates the simulation. 
+    \item \textbf{Building the Metamodel}: Using the collected data to train a metamodel that approximates the simulation model. 
     \item \textbf{Validation}: Assessing the metamodel's accuracy and generalization capability.
@@
 
-The development of advanced machine learning algorithms, particularly deep learning techniques, has significantly enhanced metamodeling approaches for Monte Carlo simulations, especially in high-dimensional and complex problem settings.
+The development of advanced machine learning models and deep learning techniques has significantly enhanced metamodeling approaches for Monte Carlo simulations, especially in high-dimensional and complex problem settings.
 Example use cases for machine learning include~\cite{jin2020deep}, ~\cite{tang2020deep}, and~\cite{rosen2012metamodeling}.
@@
     \item \textbf{Regression}: The output variable is continuous, and the task is to predict a real-valued number. 
-    Examples in actuarial applications include predicting claim amounts, reserve estimates, and asset prices.
+    Examples in actuarial applications include predicting claim amounts, reserve estimates, asset pricing, and estimating tail risk measures of loss distributions.
 \end{itemize}
@@
 This thesis focuses on regression models for risk management applications, where the goal is to predict a continuous target variable based on one or more input features.
-Given a dataset of $n$ observations $\{(x_1, y_1), (x_2, y_2), \ldots, (x_n, y_n)\}$, where $x_i \in \mathbb{R}^d$ is the $d$-dimensional input feature vector and $y_i \in \mathbb{R}$ is the target variable, a supervised learning algorithm aims to learn a function $f(;\theta): \mathbb{R}^d \rightarrow \mathbb{R}$ that best predicts the target variable $y$ given the input features $x$ with a set of function parameters $\theta$.
+Given a dataset of $n$ observations $\{(x_1, y_1), (x_2, y_2), \ldots, (x_n, y_n)\}$, where $x_i \in \mathbb{R}^d$ is the $d$-dimensional input feature vector, and $y_i \in \mathbb{R}$ is the target variable, a supervised learning algorithm aims to learn a function $f(;\theta): \mathbb{R}^d \rightarrow \mathbb{R}$ that best predicts the target variable $y$ given the input features $x$ with a set of function parameters $\theta$.
 
-Linear regression, kernel regression, neural network algorithms all fall under the supervised learning category and are widely used in risk management applications.
-Nevertheless, all supervised learning models can be evaluated on a similar set of metrics.
-The learning process involves minimizing a loss function $l(f(x; \theta),y)$ over the training data, which quantifies the difference between the predicted outputs and the true outputs. 
+Linear regression, kernel regression, and neural networks all fall under the supervised learning category and are widely used in risk management applications.
+Despite the differences in their functional forms, all supervised learning models can be evaluated on a similar set of metrics.
+The learning process is referred to as training, which involves minimizing a loss function $l(f(x; \theta),y)$ over the training data, which quantifies the difference between the predicted labels and the training labels.
 A common loss function for regression problems is the mean squared error (MSE):
 
-\begin{equation}
+\begin{equation} \label{eq:mse}
     \text{MSE} = \frac{1}{n} \sum_{i=1}^{n} (f(x_i;\theta) - y_i)^2.
@@
 The choice may vary based on the complexity of the relationship, the interpretability of the model, and the computational resources available.
-In the following sections, we discuss three widely used supervised learning models in risk management applications: traditional regression and two neural network architectures.
+In the following sections, we discuss four widely used supervised learning techniques in risk management applications: parametric regression, kernel regression, and two neural network architectures.
 
@@
 Linear regression is a simple and interpretable model that attempts to predict a target variable as a linear combination of input features. 
-It assumes a linear relationship between the dependent variable and one or more independent variables. 
-This method has been thoroughly explored in statistical literature, with \citet{bishop2006pattern} providing an extensive treatment of regression techniques in the broader context of machine learning.
+It assumes a linear relationship between the target output and one or more input features. 
+This method has been thoroughly explored in statistical literature. 
+\citet{bishop2006pattern} provide an extensive treatment of regression techniques in the broader context of machine learning.
 It is known as parametric regression because it assumes a specific functional form for the input-output relationship with a finite set of parameters~\citep{seber2012linear}.
@@
 Often, expert knowledge is required to select the appropriate basis functions, which can limit the flexibility of the model.
-Extensions like polynomial regression and generalized linear models (GLMs) have been introduced to capture non-linearity, though these models can still be limited in capturing highly complex patterns.
-To overcome these limitations, non-parametric methods such as kernel regression \citep{hastie2009elements} are often employed. 
-Kernel regression estimates the relationship by averaging the target variable over a local neighborhood of the input $x$.
+Extensions like polynomial regression and generalized linear models (GLMs) have been introduced to capture non-linearity.
+Nevertheless, these models can still be limited in capturing highly complex patterns.
+
+\subsection{Non-Parametric Regression Models}
+To overcome some limitations of parametric regression, non-parametric methods such as kernel regression~\citep{hastie2009elements} are often employed. 
+Kernel regression estimates the relationship by averaging the values of the target variable over a local neighborhood of the input $x$.
 The kernel regression with the Nadaraya-Watson estimator is given by:
@@
 where $K(\cdot)$ is the kernel function, which assigns weights to the data points based on their distance to the input $x$, and $h$ is the bandwidth parameter that controls the smoothness of the estimated function.
-The objective is to estimate the feature-label relationship directly from the data without imposing a specific form, hence, when the true relationship between variables is complex or unknown.
-However, they come with several drawbacks that limit their effectiveness, especially in high-dimensional settings or when dealing with large datasets. 
+The objective is to estimate the feature-label relationship directly from the data without imposing a specific form.
+However, they come with several drawbacks that limit their effectiveness, especially in high-dimensional settings or for large datasets. 
 One of the most significant drawbacks of non-parametric regression is the curse of dimensionality \cite{bellman1966dynamic}. 
-As the number of features increases, the volume of the input space grows exponentially, making the data sparse and leading to overfitting.
-In addition, the computational cost of non-parametric methods, including cross validation and distance calculation, often grows rapidly with the number of dimensions.
-It makes them impractical for modeling high-dimensional large-scale datasets. 
-These limitations have motivated the adoption of neural networks, which can address many of the challenges associated with non-parametric approaches.
+As the number of features increases, the volume of the input space grows exponentially.
+Data points become sparse and the model may overfit to noise in the data.
+In addition, the computational cost associated with non-parametric methods often grows rapidly with the number of dimensions.
+Cross validation and distance calculation are two computationally expensive operations that are often required for non-parametric regression.
+These drawbacks make non-parametric regression impractical for modeling high-dimensional large-scale datasets.
 
@@
 
-The progression from traditional regression methods to neural network architectures has been driven by the need to model increasingly complex and high-dimensional data.
-The limitations of parametric and non-parametric regression models in capturing complex patterns have led to the rise of neural networks as a powerful tool for learning non-linear relationships in data.
+The progression from traditional parametric and non-parametric regression methods to neural network architectures has been driven by the need to model increasingly complex and high-dimensional data.
 Neural networks have emerged as powerful tools capable of overcoming many limitations of traditional regression methods. 
 They can learn complex, non-linear relationships in data without the need for explicit feature engineering.
-The most crude form of a neural network is the feedforward neural network (FFN), which consists of an input layer, one or more hidden layers, and an output layer~\citep{goodfellow2016}.
+The most crude form of a neural network is the feedforward neural network (FNN), which consists of an input layer, one or more hidden layers, and an output layer~\citep{goodfellow2016}.
 
@@
 The key advantage of feedforward neural networks (FNNs) lies in their ability to perform automatic feature engineering without direct human intervention. 
-Unlike traditional machine learning models that require manual selection and transformation of input features, neural networks learn to extract and compose features through their hidden layers during the training process.
+Unlike traditional machine learning models that require manual selection and transformation of input features, neural networks learn to extract and compose features through their hidden layers during the training.
 Each hidden layer in the network captures higher-level abstractions of the input data by transforming the outputs of the previous layer through nonlinear activation functions~\citep{lecun2015deep}.
@@
 The last layer of the neural network, known as the output layer, typically performs a linear transformation of the features extracted by the preceding hidden layers. 
-With $a^{k}(z) = z$, the last layer is same as a linear regression with its inputs as transformed, high-level features learned by the hidden layers.
-By viewing the output layer as performing linear regression on the features learned by the network, we can draw parallels between neural networks and traditional regression models. 
+With $a^{k}(z) = z$, the last layer is equivalent to a linear regression with its inputs as transformed, high-level features learned by the hidden layers.
+We can draw parallels between neural networks and traditional regression models. 
 The main difference is that, in neural networks, the input features to the regression model are learned automatically rather than being manually specified.
 
-The most famous theorem in neural network theory is the universal approximation theorem~\citep{hornik1989multilayer}.
+The most well-known theorem in neural network theory is the universal approximation theorem~\citep{hornik1989multilayer}.
 It states that given appropriate activation functions $a$, a feedforward neural network with a single hidden layer containing a finite number of neurons can approximate any continuous function on a compact subset of $\mathbb{R}^n$ to arbitrary accuracy.
@@
 The training of neural networks involves adjusting the trainable parameters of the network to minimize the loss function.
-The loss function is typically the mean squared error (MSE) between the predicted outputs and the true outputs.
+The loss function is typically the MSE between the predicted labels and the training labels.
 The training process aims to find the optimal parameters that minimize the loss function.
@@
 Another common technique to improve the training of neural networks is regularization to prevent overfitting.
-One effective regularization method is \textit{dropout}, which randomly sets a fraction of neurons to zero during each training iteration~\citep{srivastava2014dropout}.
+One effective regularization method is dropout, which randomly sets a fraction of neurons to zero during each training iteration~\citep{srivastava2014dropout}.
 This prevents neurons from co-adapting too much, encourages redundancy, and leads to a more robust model that generalizes better to unseen data.
-\textit{Early stopping} is another yet regularization method that involves monitoring the model's performance on a validation set and stopping training when the performance no longer improves~\citep{prechelt2002early}.
-This helps prevent overfitting by halting training before the model begins to overfit to noise in the data.
+Early stopping is another regularization method that is relevant to our study.
+It involves monitoring the model's performance on a validation set and stopping training when the performance no longer improves~\citep{prechelt2002early}.
+This helps prevent overfitting by stopping training before the model begins to overfit to noise in the data.
+
+In simulation studies, the noise in the data can be controlled by the sample size.
 

### 2024-10-31 project1/nsSurvey.tex
new

@@
 
-This paper presents a survey study of some popular nested simulation procedures. 
+This paper presents a survey study of some popular nested simulation procedures with both asymptotic convergence analysis and numerical experiments.
 Many procedures are proposed in the literature, but they are not directly comparable due to different error metrics, different assumptions, and different numerical examples.
@@
 Furthermore, the existing literature chooses different performance metrics to evaluate the asymptotic convergence of nested simulation procedures.
-In this chapter, we discuss the asymptotic convergence of nested simulation procedures in terms of the MSE of the estimator, and we provide a comprehensive comparison of their convergence rates and critical assumptions.
+In this chapter, we discuss the asymptotic convergence of the nested simulation procedures in terms of the MSE of the estimator, and we provide a comprehensive comparison of their convergence rates and critical assumptions.
 We also discuss the connection between the MSE and the absolute error of the estimator in the context of nested simulation procedures.
@@
 
-The absolute error is a less stringent error metric than the MSE. 
-Section~\ref{sec1:connection-mse-absolute-error} discusses the connection between the MSE and the absolute error of the estimator in the context of nested simulation procedures.
+AE is a less stringent error metric than the MSE. 
+Section~\ref{sec1:connection-mse-absolute-error} discusses the connection between the MSE and the AE of the estimator in the context of nested simulation procedures.
 
@@
             More specifically, $\Phi$ is a Mat\'ern kernel with smoothness parameter $\nu$ and length scale parameter $\upsilon$.
-            ~\cite{wang2022smooth} provides convergence analysis for the absolute error (Equation~\ref{eq1:ae}), and the convergence analysis is provided for smooth, Lipschitz continuous, and indicator $h$, VaR, and CVaR.
+            ~\cite{wang2022smooth} provides convergence analysis for the AE (Equation~\ref{eq1:ae}), and the convergence analysis is provided for smooth, Lipschitz continuous, and indicator $h$, VaR, and CVaR.
 \end{itemize}
@@
 
-While most of the literature focuses on the MSE of the estimator of $\rho$,~\cite{wang2022smooth} analyze the asymptotic convergence of the estimator of $\rho$ in terms of the absolute error.
-Let $\hat{\rho}$ be the estimator of $\rho$. Its absolute error about $\rho$ is defined as
-
-$$
-\mbox{Absolute Error}\left(\hat{\rho}\right) = \left| \hat{\rho} - \rho \right|.
+While most of the literature focuses on the MSE of the estimator of $\rho$,~\cite{wang2022smooth} analyze the asymptotic convergence of the estimator of $\rho$ in terms of AE.
+Let $\hat{\rho}$ be the estimator of $\rho$. Its AE about $\rho$ is defined as
+
+$$
+\mbox{AE}\left(\hat{\rho}\right) = \left| \hat{\rho} - \rho \right|.
 $$
@@
 In~\cite{wang2022smooth}, the authors of the KRR-based nested simulation procedures claim to have bridged the gap between the cubic and square root convergence rates of nested simulation procedures.
-However, they analyze convergence in probabilistic order, and it is only applicable in terms of the absolute error.
-Instead of showing the convergence of the KRR-based estimator in terms of MSE as in~\cite{gordy2010nested}, we show the connections between the convergence in MSE and the convergence in probabilistic order for absolute error.
-Our findings in Section~\ref{sec1:connection-mse-absolute-error} show that the analysis of ~\cite{wang2022smooth} indeed bridges the gap, but only in terms of convergence in probabilistic order for the absolute error.
-
-\subsection{Connections between Convergence in MSE and Absolute Error} \label{sec1:connection-mse-absolute-error}
-
-This section establishes the connections between the convergence in MSE and the convergence in probabilistic order for absolute error in the context of nested simulation procedures.
-In order to show the connections between the convergence in MSE and the convergence in probabilistic order for absolute error, we first need to state the definition for a sequence of random variables to converge in those two forms.
+However, they analyze convergence in probabilistic order, and it is only applicable in terms of AE.
+Instead of showing the convergence of the KRR-based estimator in terms of MSE as in~\cite{gordy2010nested}, we show the connections between the convergence in MSE and the convergence in probabilistic order for AE.
+Our findings in Section~\ref{sec1:connection-mse-absolute-error} show that the analysis of ~\cite{wang2022smooth} indeed bridges the gap, but only in terms of convergence in probabilistic order for AE.
+
+\subsection{Connections between Convergence in MSE and AE} \label{sec1:connection-mse-absolute-error}
+
+This section establishes the connections between the convergence in MSE and the convergence in probabilistic order for AE in the context of nested simulation procedures.
+In order to show the connections between the convergence in MSE and the convergence in probabilistic order for AE, we first need to state the definition for a sequence of random variables to converge in those two forms.
 
@@
 To the best of our knowledge, Theorem~\ref{thm1:convergence-mse-prob} has not been explicitly stated in the literature.
-It is the first result that shows the connections between the convergence in MSE and the convergence in probabilistic order for absolute error in the context of nested simulation.
+It is the first result that shows the connections between the convergence in MSE and the convergence in probabilistic order for AE in the context of nested simulation.
 Theorem~\ref{thm1:convergence-mse-prob} is a general result that can be applied to any nested simulation procedure that converges in MSE to $\rho$ in order $\xi$.
@@
 Hence, the converse of Theorem~\ref{thm1:convergence-mse-prob} is not necessarily true, and the convergence in probabilistic order is a weaker form of convergence than the convergence in MSE.
-The immediate implication is that the results in~\cite{wang2022smooth}, which show the convergence in probabilistic order for the absolute error, is not necessarily equivalent to the convergence in MSE.
+The immediate implication is that the results in~\cite{wang2022smooth}, which show the convergence in probabilistic order for the AE, is not necessarily equivalent to the convergence in MSE.
 
@@
     Let $h$ be a smooth function. 
-    The absolute error of the standard nested simulation procedure converges in probabilistic order $\Gamma^{-1/3}$, that is,
+    The AE of the standard nested simulation procedure converges in probabilistic order $\Gamma^{-1/3}$, that is,
     $$\left| \hat{\rho}_{M, N} - \rho \right| = \mathcal{O}_\mathbb{P}(\Gamma^{-1/3}).$$
@@
 \begin{corollary}
-    Let $h$ be a Lipschitz continuous function. The absolute error of the standard nested simulation procedure converges in probabilistic order $\Gamma^{-1/3}$, that is,
+    Let $h$ be a Lipschitz continuous function. AE of the standard nested simulation procedure converges in probabilistic order $\Gamma^{-1/3}$, that is,
     $$\left| \hat{\rho}_{M, N} - \rho \right| = \mathcal{O}_\mathbb{P}(\Gamma^{-1/4}).$$
@@
 Assumption~\ref{as1:krr-domain} rules out the possibility of the outer scenario $X$ being a normal random variable, which is a common assumption in the literature.
-Furthermore, the convergence analysis of the KRR-based nested simulation procedure is shown in terms of the absolute error rather than the standard metric of MSE, which is due to the complexity of the KRR metatmodel.
+Furthermore, the convergence analysis of the KRR-based nested simulation procedure is shown in terms of AE rather than in MSE, which is due to the complexity of the KRR metatmodel.
 

### 2024-10-31 project2/nnMetamodels.tex
new

@@
 
-Deep neural networks~\citep{hastie2009elements,lecun2015deep} have attracted attentions of researchers and practitioners due to their success in solving real-world machine learning tasks such as AlphaGo~\citep{silver2016mastering} and ChatGPT~\citep{chatgpt}.
+Deep neural networks (DNNs) have attracted attentions of researchers and practitioners due to their success~\citep{hastie2009elements,lecun2015deep} in solving real-world machine learning tasks such as AlphaGo~\citep{silver2016mastering} and ChatGPT~\citep{chatgpt}.
 Since the first artificial neural network model~\citep{mcculloch1943logical} and the first algorithm for training a perceptron~\citep{rosenblatt1958perceptron}, especially after the introduction of backpropagation~\citep{rumelhart1985learning} and the growth of high-performance computing, the field of artificial neural network and deep learning in general has grown rapidly.
-Two specialized neural network architectures that are relevant to our study are recurrent neural networks (RNNs)~\citep{williams1989learning,sutskever2014sequence} and long-short-term memory (LSTM)~\citep{hochreiter1997long,chung2014empirical}, as we need to train metamodels\footnote{In the field of actuarial science, a metamodel is commonly referred to as a proxy model.} that take sequential observations as input.
-Despite their success, deep neural network models are often criticized for their lack of transparency and interpretability, which hinders their adoption in financial and actuarial applications.
-Enormous research efforts are spent to test and improve the robustness of deep neural network models with carefully designed noise injection methods.
+Two specialized neural network architectures that are relevant to our study are recurrent neural networks (RNNs)~\citep{williams1989learning,sutskever2014sequence} and long-short-term memory (LSTM)~\citep{hochreiter1997long,chung2014empirical}, as In the field of actuarial science, a metamodel is commonly referred to as a proxy model.
+Despite their success, DNN models are often criticized for their lack of transparency and interpretability, which hinders their adoption in financial and actuarial applications.
+Enormous research efforts are spent to test and improve the robustness of DNN models with carefully designed noise injection methods.
 ~\cite{poole2014analyzing} show that injecting synthetic noise before and after hidden unit activations during training improves the performance of autoencoders.
-~\cite{neelakantan2015adding} improve learning for deep neural networks by injecting synthetic noise to the gradients during backpropagations.
+~\cite{neelakantan2015adding} improve learning for DNNs by injecting synthetic noise to the gradients during backpropagations.
 A branch of research has been devoted to understanding the resilience of neural network models to noise in training labels.
@@
 Users of real-world data have little control over the noise level of the original training labels and usually examine the effect of noisy data by injecting noise, but it is unclear whether a neural network model trained on noisy data actually learns the real, i.e., noiseless, feature-label relationship.
-Due to their lack of transparency and interpretability, the adoption of deep neural networks in financial and actuarial applications has been received by regulators with some skepticism.
+Due to their lack of transparency and interpretability, the adoption of DNNs in financial and actuarial applications has been received by regulators with some skepticism.
 
@@
 \begin{enumerate}
-    \item We study what deep neural networks learn from noisy data by training them using simulated data based on well-designed simulation experiments.
+    \item We study what DNNs learn from noisy data by training them using simulated data based on well-designed simulation experiments.
     This is a novel way to study the effect of noisy data and error tolerance of neural network models as one can \textit{reduce noise} in the data by increasing the number of replications in a simulation model.
     This new way of studying neural network models can provide more direct evidence on their transparency and interpretability.  
-    \item We propose two generic nested simulation procedures that uses deep neural networks as metamodels to improve its efficiency while maintaining transparency. 
+    \item We propose two generic nested simulation procedures that uses DNNs as metamodels to improve its efficiency while maintaining transparency. 
     In essence, a pilot stage simulation is used to generate a large number of noisy data, which are then used to train a metamodel.
-    Depending on the application, a trained metamodel can serve two purposes: (1) to identify a set of tail scenarios, and (2) to estimate risk measures directly.
+    Depending on the application, a trained metamodel can serve two purposes: 
+    \begin{itemize}
+        \item to identify a set of tail scenarios, and 
+        \item to estimate risk measures directly.
+    \end{itemize}
     The first procedure uses a metamodel to identify a set of potential tail scenarios on which computations are performed in the second stage, while the second procedure uses metamodel predictions to estimate risk measures directly.
-    Our numerical results show that deep neural network metamodels can identify the tail scenarios accurately and so the proposed procedures can estimate tail risk measures with similar accuracy while, at the same time, using less simulation budget.
+    Our numerical results show that DNN metamodels can identify the tail scenarios accurately and so the proposed procedures can estimate tail risk measures with similar accuracy while, at the same time, using less simulation budget.
 \end{enumerate}
 
-We are curious about fundamental questions like ``What do deep neural networks learn from noisy data?'' and ``How well do neural networks learn from noisy data?''.
+We are curious about fundamental questions like ``What do DNNs learn from noisy data?'' and ``How well do neural networks learn from noisy data?''.
 Data-driven answers to these questions prevail in the existing literature.
-In supervised learning, deep neural networks are believed to learn from the given data about the feature-label relationship to predict new labels for unseen features.
+In supervised learning, DNNs are believed to learn from the given data about the feature-label relationship to predict new labels for unseen features.
 Cross validation using to assess a subset, i.e., the validation set, of the original data, is a common way to access the quality of learning.
@@
 In this study, we revisit these questions in a simulation context and propose an alternative approach to answer them.
-Instead of relying solely on real-data (splitting it into multiple subsets), we propose using stochastic simulation outputs as training labels for deep neural network models.
-By controlling the simulation design parameters, such as the number of independent replications, we can control the quality (and also the quantity) of the training labels fed into the neural networks.
+Instead of relying solely on real-data (splitting it into multiple subsets), we propose using stochastic simulation outputs as training labels for DNNs.
+By controlling the simulation design parameters, such as the number of independent replications, we can control the quality and also the quantity of the training labels fed into the neural networks.
 In such a controlled environment, we obtain more clear-cut answers to the above fundamental questions.
 
-In nested simulation, a simulation model is used to generate a large number of outer scenarios, and each scenario is then used as an input to another simulation model.
-Borrowing terminologies from machine learning research, we can view a set of simulated outer scenarios and the estimated hedging errors for those scenarios as the \textit{features} and (noisy) \textit{labels}.
+In nested simulation, a simulation model is used to generate a large number of outer scenarios, and each scenario is then used as an input to another simulation model, referred to as the inner simulation model.
+Borrowing terminologies from machine learning research, we can view a set of simulated outer scenarios and the estimated hedging errors for those scenarios as the \textit{features} and noisy \textit{labels}.
+The noise level of the labels can be controlled by the number of inner replications in the inner simulation model.
 One can train supervised learning models using these simulated features and labels.
 They are then used to replace the time-consuming inner simulations by the trained model.
-We refer to the trained supervised learning models as \textit{metamodels} of the inner simulation, which is also known as the \textit{surrogate models}.
+We refer to the trained supervised learning models as \textit{metamodels} of the inner simulation, which is also known as the \textit{surrogate models} in simulation literature.
 Metamodeling is a popular approach to reduce the computational burden of simulation-based applications by replacing the time-consuming simulation with a metamodel.
 The metamodel is trained using a set of simulated data, and it is used to predict the simulation output for new inputs.
-The study of metamodeling is an active research area in the simulation literature, and using deep neural networks as metamodels is a relatively new development.
-~\cite{fonseca2003simulation} provide general guidelines for simulation metamodeling with neural networks,~\cite{lieu2022adaptive} use deep neural networks as metamodels of a simulation model for structural reliability analysis, and~\cite{salle2014efficient} show that neural network metamodels help achieve higher prediction accuracy that other metamodels in approximating agent-based simulation models.
+The study of metamodeling is an active research area in the simulation literature, and using DNNs as metamodels is a relatively new development.
+~\cite{fonseca2003simulation} provide general guidelines for simulation metamodeling with neural networks,~\cite{lieu2022adaptive} use DNNs as metamodels of a simulation model for structural reliability analysis, and~\cite{salle2014efficient} show that neural network metamodels help achieve higher prediction accuracy that other metamodels in approximating agent-based simulation models.
 A popular metamodel in nested simulation procedures is stochastic kriging.
@@
     \item  using simulation models as data generators, we can decrease the noise level and get arbitrarily close to the true labels by increasing the number of replications in the simulation model.
-    This design allows a systematic study of the effect of noisy training labels on the performance of neural network models in predicting the noiseless labels.
+    This design allows a systematic study of the effect of noisy training labels on the performance of DNN models in predicting the noiseless labels.
 \end{enumerate}
 
-The rest of this article is organized as follows: 
-% Section~\ref{sec2:problem-formulation} presents the problem settings for tail risk measures and dynamic hedging of VAs. 
-% Section~\ref{sec2:metamodel2Stage} proposes an efficient two-stage nested simulation procedure that uses deep neural networks as metamodels to help reduce simulation budget by only performing computations on identified tail scenarios.
-% Section~\ref{sec2:metamodel1Stage} proposes a one-stage nested simulation procedure that estimates risk measures directly with metamodel predictions.
-% Section~\ref{sec2:numerical} demonstrates the efficiency of deep learning proxies and examines error tolerance of two LSTM metamodels with different numbers of trainable parameters. 
-% Practical suggestions are provided for the choice of suitable metamodels and simulation settings.
+In this chapter, DNN metamodels and DNN models are used almost interchangeably despite one distinction.
+\begin{itemize}
+    \item The discussion of \textit{DNN metamodels} focus more on the aspect of \textit{estimating} the inner simulation.
+    \item Tthe discussion of \textit{DNN models} focus more on \textit{studying the DNN} using simulation data.
+\end{itemize}
+
+The rest of this chapter is organized as follows: 
+Section~\ref{sec2:problem-formulation} presents the problem settings for tail risk measures and dynamic hedging of VAs. 
+Section~\ref{sec2:metamodel2Stage} proposes an efficient two-stage nested simulation procedure that uses DNNs as metamodels to help reduce simulation budget by only performing computations on identified tail scenarios.
+Section~\ref{sec2:metamodel1Stage} proposes a one-stage nested simulation procedure that estimates risk measures directly with metamodel predictions.
+Section~\ref{sec2:numerical} demonstrates the efficiency of DNN metamodels and examines error tolerance of two LSTM metamodels with different numbers of trainable parameters. 
+Practical suggestions are provided for the choice of suitable metamodels and simulation settings.
 
@@
 In this section we present notations, problem settings, and a simulation model for risk estimation for hedging errors of variable annuities.
-A main goal of the section is to showcase the complexity of the simulation model, which we use as a data generator to train deep neural network metamodels (Section~\ref{sec2:metamodel2Stage} and Section~\ref{sec2:metamodel1Stage}).
+A main goal of the section is to showcase the complexity of the simulation model, which we use as a data generator to train DNN metamodels (Section~\ref{sec2:metamodel2Stage} and Section~\ref{sec2:metamodel1Stage}).
 For readers who are interested in the examination of a neural network metamodel, it is sufficient to understand that our simulation model generates data with 240 features and 1 real-value label and our metamodels are generally applicable to any simulation model that generates data with similar characteristics.
@@
 
-Based on the three observations above and inspired by~\cite{dang2020efficient}, we propose a two-stage nested simulation procedure which uses a deep neural network metamodel to identify potential tail scenarios.
+Based on the three observations above and inspired by~\cite{dang2020efficient}, we propose a two-stage nested simulation procedure which uses a DNN metamodel to identify potential tail scenarios.
 We present our proposed procedure as a competitor to the standard procedure with $M$ outer scenarios and $N$ inner replications for each outer scenario, as described in Section~\ref{subsec:dynamicHedge}.
@@
 However, we believe that the goal of designing an efficient simulation procedure is to solve practical problems faster, so a target-accuracy design is more suitable, which refers to obtaining a similar level of accuracy as the standard procedure but with much less simulation budget.
-One other reason for this fixed-accuracy design is to investigate whether deep neural network metamodels trained with much noisier labels can identify true tail scenarios with similar accuracy as the standard procedure.
+One other reason for this fixed-accuracy design is to investigate whether DNN metamodels trained with much noisier labels can identify true tail scenarios with similar accuracy as the standard procedure.
 The size of the predicted tail scenario set in Stage 1, $m$, is an important experiment design parameter that affects the correct identification of true tail scenarios and ultimately affects the estimation accuracy for CVaR.
@@
 The withdrawal rate for GMWB is $0.375\%$ per month.
-% To make our examples more realistic, the VAs are also subject to dynamic lapse as specified in Section~4.3 of~\cite{dang2020efficient}.
-The risk-free rate is 0.2\% per period and the underlying asset $S_t$ is modeled by a regime-switching geometric Brownian motion with parameters specified in Table~2 of~\cite{dang2020efficient}.
+To make our examples more realistic, the VAs are also subject to a dynamic lapse model with the following key features:
+\begin{enumerate}
+    \item When a policyholder lapses, both the fund value ($F$) and guarantee value ($G$) are reduced proportionally.
+    \item The monthly lapse rate from time $t$ to $t + 1$, denoted as ${}_{\frac{1}{12}}q^l_{x+\frac{t}{12}}$, is given by:
+    \begin{equation}
+        {}_{\frac{1}{12}}q^l_{x+\frac{t}{12}} = \min\left\{1, \max\left\{0.5, 1 - 1.25 \times \left(\frac{G_t}{F_t} - 1.1\right)\right\} \times {}_{\frac{1}{12}}q^{base}_{x+\frac{t}{12}}\right\}
+    \end{equation}
+    where ${}_{\frac{1}{12}}q^{base}_{x+\frac{t}{12}}$ is the base monthly mortality rate for a policyholder aged $x + \frac{t}{12}$ at month $t$.
+    where the base monthly lapse rate is defined as:
+    \begin{equation}
+        {}_{\frac{1}{12}}q^{base}_{x+\frac{t}{12}} = 
+        \begin{cases}
+            0.00417 & \text{if } t < 84 \\
+            0.00833 & \text{if } t \geq 84
+        \end{cases}
+    \end{equation}
+\end{enumerate}
+
+The risk-free rate is 0.2\% per period and the underlying asset $S_t$ is modeled by a regime-switching geometric Brownian motion with parameters specified in Table~\ref{tab:regime_params}.
+
+\begin{table}[ht]
+    \centering
+    \begin{tabular}{lc}
+        \toprule
+        \textbf{Parameter}  & \textbf{Monthly Value} \\
+        \midrule
+        Risk-free rate & 0.002 \\
+        Mean return for regime 1  & 0.0085 \\
+        Mean return for regime 2   & -0.0200 \\
+        Standard deviation for regime 1  & 0.035 \\
+        Standard deviation for regime 2  & 0.080 \\
+        Transition probability from regime 1  & 0.04 \\
+        Transition probability from regime 2  & 0.20 \\
+        \bottomrule
+    \end{tabular}
+    \caption{Real-world parameters for the regime-switching model (monthly rates)}
+    \label{tab:regime_params}
+\end{table}
 
 To compare the numerical performances of different simulation procedures, we create a benchmark dataset with a large-scale nested simulation: We first simulate $M=\num{100000}$ outer scenarios, i.e., $240$-periods stock paths $\bS^{(1)},\ldots,\bS^{(M)}$ under $\mathbb{P}$ and used these outer scenarios in all further experiments.
-Note that the 5\% tail scenario set includes $5\!,\!000$ scenarios.
+Note that the 5\% tail scenario set includes $\num{5000}$ scenarios.
 As the hedging losses for these scenarios cannot be calculated analytically, we run inner simulations with a large number of replications, $N=\num{100000}$, conditional on each of the $M$ scenarios.
@@
 The resulting feature-label pairs $\{(\bS^{(i)}, \Lhat_i): i=1,\ldots,M\}$ is used for training different  metamodels.
-Specifically, following the convention in machine learning research, we split this dataset into three parts: The training, validation, and test sets have $90\!,\!000$, $5\!,\!000$, and $5\!,\!000$ data points (90\%, 5\%, and 5\% of the dataset), respectively.
+Specifically, following the convention in machine learning research, we split this dataset into three parts: The training, validation, and test sets have $\num{90000}$, $\num{5000}$, and $\num{5000}$ data points (90\%, 5\%, and 5\% of the dataset), respectively.
 At the end of Stage 1, $m$ predicted tail scenarios, are identified by the trained metamodels.
@@
 The architectures and the numbers of trainable parameters are shown in the first two columns of Table~\ref{tab:gmwb_arch}.
-We see that the three deep neural network metamodels' have orders of magnitudes more trainable parameters than the two regression models.
-In machine-learning terminologies, the three deep neural network models have much higher \textit{model capacities}.
+We see that the three DNN metamodels' have orders of magnitudes more trainable parameters than the two regression models.
+In machine-learning terminologies, the three DNN models have much higher \textit{model capacities}.
 
@@
     QPR & N/A & $481$ & $0.544 (\pm 0.000)$ & $0.636 (\pm 0.001)$ & $0.531 (\pm 0.000)$ \\
-    FNN & $240, 128, 16$ & $35\!,\!009$ & $0.118 (\pm 0.001)$ & $0.247 (\pm 0.002)$ & $0.113 (\pm 0.001)$ \\
-    RNN & $(240, 32), (240, 4), 32$ & $32\!,\!021$ & $0.132 (\pm 0.008)$ & $0.137 (\pm 0.008)$ & $0.119 (\pm 0.008)$ \\
-    LSTM & $(240, 32), (240, 4), 32$ & $35\!,\!729$ & $0.075 (\pm 0.004)$ & $0.079 (\pm 0.005)$ & $0.063 (\pm 0.004)$ \\
-    RNN$^*$\footnotemark & $(240, 32), (240, 4), 32$ & $32\!,\!021$ & $0.109 (\pm 0.005)$ & $0.128 (\pm 0.005)$ & $0.109 (\pm 0.005)$ \\
+    FNN & $240, 128, 16$ & $\num{35009}$ & $0.118 (\pm 0.001)$ & $0.247 (\pm 0.002)$ & $0.113 (\pm 0.001)$ \\
+    RNN & $(240, 32), (240, 4), 32$ & $\num{32021}$ & $0.132 (\pm 0.008)$ & $0.137 (\pm 0.008)$ & $0.119 (\pm 0.008)$ \\
+    LSTM & $(240, 32), (240, 4), 32$ & $\num{35729}$ & $0.075 (\pm 0.004)$ & $0.079 (\pm 0.005)$ & $0.063 (\pm 0.004)$ \\
+    RNN$^*$\footnotemark & $(240, 32), (240, 4), 32$ & $\num{32021}$ & $0.109 (\pm 0.005)$ & $0.128 (\pm 0.005)$ & $0.109 (\pm 0.005)$ \\
     \bottomrule
@@
 The half lengths of their 95\% confidence interval of these quantities are also reported in parentheses.
-We first observe that the two regression metamodels' errors are larger than those of three deep neural network models.
+We first observe that the two regression metamodels' errors are larger than those of three DNN models.
 This is because model capacities of the regression metamodels are too low to learn the complex dynamic hedging simulation model.
-All neural network metamodels have high model capcities comparing with the number of data points in the training set, i.e., $90\!,\!000$.
-This is not a huge concern for the deep neural networks.
+All neural network metamodels have high model capcities comparing with the number of data points in the training set, i.e., $\num{90000}$.
+This is not a huge concern for the DNNs.
 In neural network literature, the number of trainable parameters is often much larger than the number of data points in the training set.
@@
 The reason for not overfitting is still an open question in deep learning research.
-One possible explanation is that the optimization surface of deep neural networks is highly non-convex and has many local minima.
+One possible explanation is that the optimization surface of DNNs is highly non-convex and has many local minima.
 As a result, given a good initialization, the optimization algorithm is likely to find a solution that generalizes well to unseen data.
 
-There are also differences among the three deep neural network models due to having different architectures.
+There are also differences among the three DNN models due to having different architectures.
 The FNN is a generic neural network, its test error is larger than the training error, which is a sign of over-fitting and poor generalization.
@@
 As a result, they have lower training errors, i.e., they fit the data better, and have lower testing error, i.e., they generalize better.
-Notably, the true errors for the deep neural network metamodels are lower than the test errors.
+Notably, the true errors for the DNN metamodels are lower than the test errors.
 This is a sign of the metamodels' ability to learn the true feature-label relationship with noisy training labels. 
@@
 We observe that the two regression metamodels not only generalize to the test data poorly but also generalize to the true data poorly.
-In contrast, the deep neural network metamodels generalize better to the true data than to the test data.
+In contrast, the DNN metamodels generalize better to the true data than to the test data.
 Figure~\ref{fig2:QQ_REG} and Figure~\ref{fig2:QQ_NN} shows the QQ plots between the \textbf{true} labels and the predicted losses for the regression metamodels and the neural network metamodels, respectively.
@@
 
-From a unique analytical standpoint, our numerical study offers a methodical exploration into the robustness of deep neural network models against noise in training labels. 
+From a unique analytical standpoint, our numerical study offers a methodical exploration into the robustness of DNN models against noise in training labels. 
 By employing the standard nested simulation procedure in Algorithm~\ref{alg2:standardProcedure} as a data generator, we gain the ability to manipulate the noise level through adjusting the number of inner replications while keeping the same simulation procedure.
@@
 It allows us to generate our true dataset that approximates the true hedging losses with a high degree of precision, and, as a result, it enables us to explore the crucial question of whether deep learning models are capable of learning the true feature-label relationship from noisy training labels.
-Our numerical results in Table~\ref{tab:gmwb_arch} and the QQ plots provide direct evidence that deep neural network models are indeed able to cut through the noise in the training labels and learn the true feature-label relationship.
+Our numerical results in Table~\ref{tab:gmwb_arch} and the QQ plots provide direct evidence that DNN models are indeed able to cut through the noise in the training labels and learn the true feature-label relationship.
 The LSTM metamodels' ability to learn the true feature-label relationship is crucial for the two-stage procedure to identify true tail scenarios and produce accurate CVaR estimates.
@@
 
-\subsection{Noise Tolerance of Deep Neural Network Metamodels} \label{subsec2:noiseTolerance}
+\subsection{Noise Tolerance of DNN Metamodels} \label{subsec2:noiseTolerance}
 
-For financial and actuarial applications, regulators and practitioners are often concerned about the robustness of deep neural network models to noise in training labels, which hinders the adoption of these models in practice.
+For financial and actuarial applications, regulators and practitioners are often concerned about the robustness of DNN models to noise in training labels, which hinders the adoption of these models in practice.
 Since the true relationship is unknown in real-world applications, most deep learning literature illustrates the impact of noise by artificially injecting noise into real-world datasets, which is already noisy before the injection.
@@
 
-To further test the sensitivity of a LSTM metamodel and provide a more comprehensive picture of the noise tolerance of deep neural network models, we conduct a sensitivity analysis on the noise tolerance of the regular LSTM metamodel by varying the numbers of outer scenarios ($M$) and inner replications ($N$) used to generate the training data.
+To further test the sensitivity of a LSTM metamodel and provide a more comprehensive picture of the noise tolerance of DNN models, we conduct a sensitivity analysis on the noise tolerance of the regular LSTM metamodel by varying the numbers of outer scenarios ($M$) and inner replications ($N$) used to generate the training data.
 The number of outer scenarios corresponds to the number of data points in the training dataset, and the number of inner replications controls the noise level in the training labels.
@@
 \section{Conclusion} \label{sec2:conclusion}
-The proposed nested simulation procedures with deep neural network metamodels result in substantial computational savings in estimating CVaR of the hedging loss of a VA contract from accurately predicting the hedging losses and identifying the tail scenarios.
+The proposed nested simulation procedures with DNN metamodels result in substantial computational savings in estimating CVaR of the hedging loss of a VA contract from accurately predicting the hedging losses and identifying the tail scenarios.
 When new outer scenarios are generated, a trained LSTM metamodel can distinguish between tail and non-tail scenarios and make accurate predictions without the need to run new inner simulations.
-Our novel experiment design allows us to examine the impact of label noise on deep neural network models.
-We find that a deep neural network with a suitable architecture is able to cut through the noise in training labels and learn the true complex dynamic hedging model.
+Our novel experiment design allows us to examine the impact of label noise on DNN models.
+We find that a DNN with a suitable architecture is able to cut through the noise in training labels and learn the true complex dynamic hedging model.
 By showcasing the resilience of these models, our study aims to influence regulatory bodies towards recognizing the value and applicability of deep learning metamodels in financial risk management, and it provides informed suggestions and guidance for the incorporation and oversight of advanced deep learning metamodel in Monte Carlo Simulation in financial applications.
@@
 In our numerical experiments, a LSTM metamodel is resilient to a high level of noise in training labels and is able to make accurate predictions. 
-This is a promising evidence that deep neural network metamodels can be used to improve the efficiency of Monte Carlo simulation for quantitative risk management tasks that require a computational-expensive simulation procedure.
-We propose two nested simulation procedures that use deep neural network metamodels to estimate risk measures of the hedging loss of a VA contract.
+This is a promising evidence that DNN metamodels can be used to improve the efficiency of Monte Carlo simulation for quantitative risk management tasks that require a computational-expensive simulation procedure.
+We propose two nested simulation procedures that use DNN metamodels to estimate risk measures of the hedging loss of a VA contract.
 For estimating tail risk measures, our two-stage procedure is designed to address regulatory concerns by avoiding the direct use of metamodel predictions but instead use them to identify the potential tail scenarios.
@@
 It is more efficient and can be extended to estimate risk measures that require knowledge of the entire loss distribution.
-Our numerical experiments demonstrate that the proposed single-stage procedure with deep neural network metamodels result in further computational savings over our two-stage procedure. 
-Furthermore, our numerical results provide evidences for adopting deep neural network metamodels in Monte Carlo simulation for risk management tasks.
-Through our systematic study of the noise tolerance of deep neural network metamodels, we address regulatory concerns by showing that a LSTM metamodel is resilient to a high level of noise in training labels and is able to make accurate predictions.
-A possible future research direction is to apply deep neural network metamodels in other financial risk management tasks that requires complex nested simulation with high-dimensional outer scenarios.
+Our numerical experiments demonstrate that the proposed single-stage procedure with DNN metamodels result in further computational savings over our two-stage procedure. 
+Furthermore, our numerical results provide evidences for adopting DNN metamodels in Monte Carlo simulation for risk management tasks.
+Through our systematic study of the noise tolerance of DNN metamodels, we address regulatory concerns by showing that a LSTM metamodel is resilient to a high level of noise in training labels and is able to make accurate predictions.
+A possible future research direction is to apply DNN metamodels in other financial risk management tasks that requires complex nested simulation with high-dimensional outer scenarios.
 Another future research direction is to investigate the impact of label noise on other deep learning models, such as convolutional neural networks and transformer models, and to compare their performance with LSTM metamodels in nested simulation procedures.
-From a practical standpoint, the choice of a suitable deep neural network architecture is crucial for the success of a deep learning metamodel in nested simulation procedures.
+From a practical standpoint, the choice of a suitable DNN architecture is crucial for the success of a deep learning metamodel in nested simulation procedures.
 We find that a LSTM metamodel is the most suitable for our dynamic hedging simulation model with time series features, but the optimal network architecture may vary for different simulation models.
-Exploring deep neural network metamodels in other complex risk management tasks presents a promising avenue for research, especially as these tasks often involve complex, high-dimensional scenarios where traditional methods are insufficient.
+Exploring DNN metamodels in other complex risk management tasks presents a promising avenue for research, especially as these tasks often involve complex, high-dimensional scenarios where traditional methods are insufficient.
 The versatility of neural networks could unlock new insights across a broad spectrum of financial and actuarial applications.
 
-In this chapter, we have demonstrated the potential of deep neural network metamodels in nested simulation procedures for delta hedging of variable annuity contracts and have shown that they can be used to estimate risk measures with high accuracy and efficiency.
+In this chapter, we have demonstrated the potential of DNN metamodels in nested simulation procedures for delta hedging of variable annuity contracts and have shown that they can be used to estimate risk measures with high accuracy and efficiency.
 We have assumed a zero transaction cost model for our monthly rebalancing.
@@
 In the next chapter, we will extend our study to include transaction costs in the hedging strategy and investigate the impact of transaction costs on the hedging performance and the risk measures of the hedging error.
-We will also explore the use of deep neural network models as reinforcement learning agents to optimize the hedging strategy by directly interacting with the financial market and maximize the hedging performance.
+We will also explore the use of DNN models as reinforcement learning agents to optimize the hedging strategy by directly interacting with the financial market and maximize the hedging performance.

### 2024-10-31 project3/draft.tex
new

@@
     \centering
-    \begin{tabular}{lrr}
+    \begin{tabular}{lrrr}
         \toprule
-        \textbf{Model} & \textbf{Training MSE} & \textbf{True MSE} \\
+        \textbf{Model} & \textbf{Training Samples} & \textbf{Training MSE} & \textbf{True MSE} \\
         \midrule
-        Without TL & 0.3588 & 0.4188 \\
-        Fine Tuning & 0.1690 & 0.1780 \\
-        Layer Freezing & 0.1828 & 0.2295 \\
-        Extensive Training & 0.0853 & 0.0726 \\
+        Without TL & 2,000 & 0.3588 & 0.4188 \\
+        Fine Tuning & 2,000 & 0.1690 & 0.1780 \\
+        Layer Freezing & 2,000 & 0.1828 & 0.2295 \\
+        Extensive Training & 50,000 & 0.0853 & 0.0726 \\
         \bottomrule
     \end{tabular}
-    \caption{Comparison of different TL methods on GMWB contracts}
+    \caption{Comparison of different TL methods to GMWB contracts}
     \label{tab3:transfer_learning_results_gmwb}
@@
 Table~\ref{tab3:transfer_learning_results_gmwb} summarizes the true MSEs of the LSTM metamodels on the GMWB contracts.
+The TL methods are compared to training from scratch.
 The suboptimal performance of layer freezing in this context indicates that the difference between the source and target tasks is too substantial for this method to be effective. 

### 2024-11-01 project1/nsSurvey.tex
new

@@
 This is referred to as pooling. 
-Different methods pool in different ways, either by a trained metamodel or by pre-defined likelihood ratio weights.
+Different methods pool in different ways, either by a trained supervised learning metamodel or by pre-defined likelihood ratio weights.
 ~\cite{broadie2015risk} propose a regression-based nested simulation procedure, which uses a trained regression metamodel to estimate the scenario-wise portfolio loss for an outer scenario by pooling the inner replications from all outer scenarios.
@@
 
-This paper presents a survey study of some popular nested simulation procedures with both asymptotic convergence analysis and numerical experiments.
-Many procedures are proposed in the literature, but they are not directly comparable due to different error metrics, different assumptions, and different numerical examples.
+This paper presents a survey study of some popular nested simulation procedures that have both asymptotic convergence analysis and finite-sample performance evaluation.
+Many procedures are proposed in the literature, but they are not directly comparable due to having different error metrics, different assumptions, and different numerical examples.
 Within a common analytical framework, we first summarize and compare their asymptotic rate of convergence.
@@
 Furthermore, the existing literature chooses different performance metrics to evaluate the asymptotic convergence of nested simulation procedures.
-In this chapter, we discuss the asymptotic convergence of the nested simulation procedures in terms of the MSE of the estimator, and we provide a comprehensive comparison of their convergence rates and critical assumptions.
+In this chapter, we discuss the asymptotic convergence in terms of MSE of the estimator, and we provide a comprehensive comparison of their convergence rates and critical assumptions.
 We also discuss the connection between the MSE and the absolute error of the estimator in the context of nested simulation procedures.
 
-In terms of finite-sample performance, this chapter shows that different studies propose different examples in their numerical experiments, which introduces unfair advantages for certain simulation procedures over others.
+In terms of finite-sample performance, different studies propose different examples in their numerical experiments, which introduces unfair advantages for certain simulation procedures over others. 
 A fair comparison among popular methods is therefore urgently needed in the literature. 
-Our numerical experiment is the first of its kind to subject back all the aforementioned simulation procedures to a complete and unbiased comparison. 
+Our numerical experiment in this chapter is the first of its kind to subject back all the aforementioned simulation procedures to a complete and unbiased comparison. 
 Extensive numerical experiments are conducted to show, in practical examples, how well the finite-sample performance of a method matches its theoretical convergence behavior. 
 With our numerical examples, we compare the nested simulation procedures for different payoff complexity, problem dimensions, and risk measures. 
-This chapter also provides a discussion on the computational complexity of different nested simulation procedures, including additional computational costs for training metamodels and pooling inner replications.
+This chapter also provides a discussion on the computational complexity of different nested simulation procedures, including additional computational costs for training supervised learning metamodels and pooling inner replications.
 
@@
 Section~\ref{sec1:computational-complexity} discusses the computational complexity of different nested simulation procedures.
-Section~\ref{sec1:conclusion} concludes the paper.
+Section~\ref{sec1:conclusion} concludes this chapter.
 
@@
 
-In a nested estimation problem, we are interested in the quantity
+In a nested estimation problem, we are interested in estimating the quantity
 
@@
 where $h: \mathbb{R} \rightarrow \mathbb{R}$ is a known nonlinear function. 
-Common forms of $h$ includes smooth functions, Lipschitz continuous functions, and indicator functions.
 The nested expectation form is a general form that covers many risk measures of interest in financial engineering by varying the function $h$.
+Common forms of $h$ in the literature include smooth functions, Lipschitz continuous functions, and indicator functions.
 
@@
 A quadratic tracking error with a benchmark $b$ falls into this category, in which $h(t) = (t - b)^2$.
-In the context of nested simulation, different procedures require different versions of Definition~\ref{def1:smooth} to specify the smoothness of $h$ for their convergence analysis.
+In the context of nested estimation for smooth $h$, different procedures require different versions of Definition~\ref{def1:smooth} to specify the smoothness for their convergence analysis.
 Table~\ref{tab1:smoothness} summarizes the smoothness assumption of $h$ for different nested simulation procedures in the literature.
@@
     \midrule
-    Regression & $2$ & $2$ \\
+    Regression & $2$ & not required \\
     Kernel smoothing & $3$ & $2$ \\
@@
 
+The regression-based nested simulation procedure has the least stringent smoothness assumption.
+In general, a more complex metamodel requires a higher-order smoothness for $h$ for its convergence analysis.
+Despite being more advanced than kernel smoothing, the KRR-based procedure requires a less stringent smoothness assumption on $h$.
+It is counterintuitive that a more complex metamodel requires a less stringent smoothness assumption.
+This phenomenon is due to the fact that the convergence analysis for the KRR-based nested simulation procedure is shown in terms of absolute error, which is a less stringent error metric than MSE.
+Section~\ref{sec1:connection-mse-absolute-error} discusses the connection between the MSE and the AE of the estimator in the context of nested simulation procedures.
+In Table~\ref{tab1:smoothness}, the standard nested simulation procedure is the only procedure without asymptotic convergence analysis for smooth $h$.
+Section~\ref{sec1:sns} fills this gap by providing the asymptotic convergence analysis for the standard nested simulation procedure in terms of MSE.
+
 \begin{definition} \label{def1:lipschitz}
@@
 A mean excess loss over a threshold $u$ is defined by setting $h(t) = \max\{t - u, 0\}$, which is a special case of a Lipschitz continuous function.
+The regression-based nested simulation procedure is the only procedure that performs theoretical analysis for Lipschitz continuous $h$.
+The other procedures only provide convergence analysis for the special case, mean excess loss over a threshold $u$.
 
@@
 Other names of CVaR include Conditional Tail Expectation (CTE), Tail Value-at-Risk (TailVaR), and Expected Shortfall (ES).
+
+The rest of this section reviews the existing nested simulation procedures in the literature.
+We unify their notations and provide a comprehensive comparison of how inner replications are generated and pooled for different procedures.
 
@@
 The simulation budget $\Gamma$ is the sum of the computational budget at each level, that is, $\Gamma = \sum_{\upsilon=0}^{\Upsilon} M_{\upsilon} \cdot N_{\upsilon}$.
+Neither the standard nested simulation procedure nor the MLMC method involves pooling the inner replications from all outer scenarios.
+Pooling enhances sample efficiency, and it is a key feature that distinguishes the more advanced nested simulation procedures from the standard procedure.
 
@@
 
-We are interested in minimizing the MSE of the supervised learning-based nested simulation estimator with supervised learning $\hat{\rho}^{\text{SL}, \text{Train}}_{M, N}$ and $\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'}$ subject to the total simulation budget $\Gamma$, and we are interested in the order of convergence of the estimator for all nested simulation procedures when the total simulation budget $\Gamma$ approaches infinity.
-
-\begin{align}
-    & \min_{M, N}  & \text{MSE}(\hat{\rho}^{\text{SL}}_{M, N}) = \mathbb{E} \left[ \left( \hat{\rho}^{\text{SL}}_{M, N} - \rho \right)^2 \right] \nonumber \\
-    & \text{subject to} & M \cdot N = \Gamma 
-\end{align}
-
-For the more complex metamodels, the convergence analysis of their MSEs is more challenging.
-More specifically, the KRR-based nested simulation~\citep{wang2022smooth} provides a convergence analysis in terms of absolute error (AE).
-\begin{align} \label{eq1:ae}
-    & \min_{M, N}  & \text{AE}(\hat{\rho}^{\text{SL}}_{M, N}) = \mathbb{E} \left[ \left| \hat{\rho}^{\text{KRR}}_{M, N} - \rho \right| \right] \nonumber \\
-    & \text{subject to} & M \cdot N = \Gamma 
-\end{align}
-
-AE is a less stringent error metric than the MSE. 
-Section~\ref{sec1:connection-mse-absolute-error} discusses the connection between the MSE and the AE of the estimator in the context of nested simulation procedures.
-
-Existing literature on nested simulation procedures has proposed different metamodels to approximate the true function $L(\cdot)$ with supervised learning models. 
+Existing literature on nested simulation procedures has proposed different supervised learning metamodels to approximate the true function $L(\cdot)$.
 In this study, we focus on the metamodeling approaches that include theoretical convergence results.
@@
 Among our interested supervised learning models, regression is a parametric regression model, while kernel smoothing and kernel ridge regression are non-parametric regression model.
-Their asymptotic convergence results are summarized in Table~\ref{tab1:asymConv-mse}, and Section~\ref{sec1:regression-convergence} and Section~\ref{sec1:kernel-smoothing-convergence} compare their finite-sample performance with numerical experiments.
+
+We are interested in minimizing the MSE of the supervised learning-based nested simulation estimator with supervised learning $\hat{\rho}^{\text{SL}, \text{Train}}_{M, N}$ and $\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'}$ subject to the total simulation budget $\Gamma$, and we are interested in the order of convergence of the estimator for all nested simulation procedures when the total simulation budget $\Gamma$ approaches infinity.
+
+\begin{align}
+    & \min_{M, N}  & \text{MSE}(\hat{\rho}^{\text{SL}}_{M, N}) = \mathbb{E} \left[ \left( \hat{\rho}^{\text{SL}}_{M, N} - \rho \right)^2 \right] \nonumber \\
+    & \text{subject to} & M \cdot N = \Gamma 
+\end{align}
+
+For the more complex metamodels, the convergence analysis of their MSEs is more challenging.
+More specifically, the KRR-based nested simulation~\citep{wang2022smooth} provides a convergence analysis in terms of absolute error (AE).
+\begin{align} \label{eq1:ae}
+    & \min_{M, N}  & \text{AE}(\hat{\rho}^{\text{SL}}_{M, N}) = \mathbb{E} \left[ \left| \hat{\rho}^{\text{KRR}}_{M, N} - \rho \right| \right] \nonumber \\
+    & \text{subject to} & M \cdot N = \Gamma 
+\end{align}
+Section~\ref{sec1:connection-mse-absolute-error} draws the connection between the MSE and the AE of the estimator in the context of nested simulation procedures.
 
@@
 \section{Asymptotic Analysis} \label{sec1:asymptotic-convergence}
-In this section, we summarize the existing asymptotic convergence results of the nested simulation procedures in the literature, and we compare their critical assumptions that guarantee the convergence.
+In the first part of this section, we summarize the existing asymptotic convergence results of the nested simulation procedures in the literature, and we compare their critical assumptions that guarantee the convergence.
+The remaining of this section aims to fill the gap in the literature by
+\begin{itemize}
+    \item providing the asymptotic convergence results for the standard nested simulation procedure, 
+    \item showing the connections between the convergence in MSE and the convergence in probabilistic order for AE in the context of nested simulation procedures, and
+    \item illustrating the asymptotic rate of convergence of a kNN-based nested simulation procedure.
+\end{itemize}
 
@@
 
-\subsection{Asymptotic Analysis for the Standard Nested Simulation Procedure}
+\subsection{Asymptotic Analysis for the Standard Nested Simulation Procedure} \label{sec1:sns}
 In~\cite{gordy2010nested}, the authors analyze the asymptotic convergence of the standard nested simulation procedure in terms of MSE. 
@@
 For the standard nested simulation procedure, the bootstrap-based budget allocation strategy from~\cite{zhang2021bootstrap} is implemented to estimate the optimal values of outer and inner simulation budgets.
-For the regression metamodel, the Laguerre polynomials up to degree $3$ are used as the basis functions.
+For the regression metamodel, the Laguerre polynomials up to degree $3$ are used as the default basis functions.
 The kNN metamodel is implemented for the kernel smoothing-based procedure, and a cross-validation with grid search is used to find the optimal number of neighbors.
 The KRR metamodel is implemented with a Mat\'ern kernel, and the smoothness, the length scale, and the regularization hyperparameters are found by a cross-validation with Bayesian search~\citep{frazier2018bayesian}.
-The procedures are compared for 5 types of risk measures, namely a quadratic tracking error, a mean excess loss over threshold $u$, a probability of a large loss over threshold $u$, th VaR, and the CVaR, where the threshold $u$ is set to be the 90\% VaR.
-The procedures are compared for different portfolios.
+The procedures are compared for 5 types of risk measures:
 \begin{itemize}
-    \item   Portfolio 1 considers $d$ assets.
+    \item a quadratic tracking error,
+    \item a mean excess loss over a threshold $u$,
+    \item a probability of a large loss over a threshold $u$,
+    \item the VaR, and
+    \item the CVaR,
+\end{itemize}
+where the threshold $u$ for the mean excess loss and the probability of a large loss is set to be the 90\% VaR.
+The procedures are compared for different portfolios consisting of different types of options:
+\begin{itemize}
+    \item   Portfolio 1 consists of $d$ assets.
     The portfolio contains 3 European call options written on each asset with strikes $90$, $100$, and $110$, respectively. 
-    \item   Portfolio 2 considers $d$ assets.
+    \item   Portfolio 2 consists of $d$ assets.
     The portfolio contains 3 geometric Asian options written on each asset with strikes $90$, $100$, and $110$, respectively. 
-    \item   Portfolio 3 considers $d$ assets.
+    \item   Portfolio 3 consists of $d$ assets.
     The portfolio contains 3 up-and-out barrier call options written on each asset with strikes $90$, $100$, and $110$, respectively. They have a barrier level of $120$.
@@
 \end{itemize}
-Except for portfolio 5, 5 different asset dimensions are considered, i.e., $d = 1, 2, 5, 10, 20$, while we only consider $d=1$ for portfolio 5. 
+Except for portfolio 5, 5 different asset dimensions are considered, i.e., $d = 1, 2, 5, 10, 20$.
 525 experimental settings that arise from an exhaustive combination of the above simulation procedures, risk measures, portfolios, and asset dimensions are generated.
-For each of the scenarios, the estimation of the risk measure is repeated 1000 times to obtain the empirical MSE of the corresponding estimator under a range of simulation budgets.
-The total simulation budget $\Gamma$ ranges from $10,000$ to $10,240,000$ in a geometric progression with a common ratio of $2$.
+For each of the scenarios, the estimation of the risk measure is repeated \num{1000} times to obtain the empirical MSE of the corresponding estimator under a range of simulation budgets.
+The total simulation budget $\Gamma$ ranges from $\num{10000}$ to $\num{10240000}$ in a geometric progression with a common ratio of $2$.
 The empirical convergence results of each estimator are measured and recorded to illustrate their empirical behavior under different risk measures, option types, and asset dimensions.
@@
 \end{figure}
-In Figure~\ref{fig1:compareAll}, the MSEs of the nested simulation procedures are plotted against the total simulation budget $\Gamma$ in a log-log scale, where each point represents the average MSE of the corresponding estimator over 1000 replications.
-The MSEs of the nested simulation procedures are fitted with a regression line, and the slope of the fitted line is reported as the first number in the legend.
-The second number in the legend is the corresponding asymptotic rate of convergence obtained from the theoretical analysis.
-The slope of the fitted line can be regarded as the empirical rate of convergence of the corresponding procedure.
-By comparing the empirical rates of convergence with the asymptotic rates, we can observe that the empirical rates of convergence of the standard, the kernel smoothing-based, the regression-based, the likelihood ratio-based, and the KRR-based procedures all closely match their asymptotic rates.
-Due to the computational complexity of the likelihood ratio-based and the KRR-based procedures, their MSEs are not reported for $\Gamma$ larger than $16,000$ and $64,000$, respectively.
+In Figure~\ref{fig1:compareAll}, the MSEs of the nested simulation procedures are plotted against the total simulation budget $\Gamma$ in a log-log scale, where each point represents the average MSE of the corresponding estimator over \num{1000} macro replications of the same experiment.
 Due to the difficulty of fixing $\Gamma$ for the MLMC procedure, the empirical rate of convergence of the MLMC procedure is not reported here, but a detailed analysis of the empirical convergence of the MLMC procedure is provided in Section~\ref{sec1:empirical-mlmc}.
+
+The MSEs of the nested simulation procedures are fitted with a regression line, and the slope of the fitted line is reported as the empirical rate of convergence of the corresponding procedure.
+The second number in the legend is the asymptotic rate of convergence obtained from the theoretical analysis.
+By comparing the empirical rates of convergence with the asymptotic rates, we can observe that the empirical rates of all procedures closely match their asymptotic rates.
+
+Except for the standard nested simulation procedure, the empirical rates of convergence of the other procedures are close to $\Gamma^{-1}$.
+Pooling of inner simulation samples across different outer scenarios is the key reason for their higher empirical rates of convergence.
+However, pooling also introduces additional computational cost that is not reflected in the simulation budget $\Gamma$.
+Due to the computational complexity of the likelihood ratio-based and the KRR-based procedures, their MSEs are not reported for $\Gamma$ larger than $\num{16000}$ and $\num{64000}$, respectively.
+Detailed discussion of the additional computational cost of pooling is provided in Section~\ref{sec1:computational-complexity}.
+
 In the following sections, we examine the empirical convergence of the nested simulation procedures in a similar manner as in Figure~\ref{fig1:compareAll}.
@@
 In portfolio risk management, the asset dimension is a critical factor that determines the complexity of the portfolio and the computational cost of the risk measure estimation.
-The theoretical analyses in Section~\ref{sec1:convergence-orders} suggest that the asymptotic rate of convergence of the nested simulation procedures, except for the kernel smoothing-based procedure, is independent of the asset dimension.
-However, the empirical convergence behavior of the nested simulation procedures could be sensitive to the asset dimension.
-In this section, we examine the empirical convergence of the nested simulation procedures for different asset dimensions.
+The theoretical analyses in Section~\ref{sec1:convergence-orders} suggest that the asymptotic rate of convergence of the nested simulation procedures, except for the kernel smoothing-based procedure, is independent from the asset dimension.
+However, in practice, their empirical convergence behavior could be different.
+In this section, we examine the sensitivity of the empirical convergence of the nested simulation procedures to the asset dimension.
 
@@
 In Figure~\ref{fig1:assetDimension}, the empirical convergence of the nested simulation procedures for a quadratic tracking error on Portfolio 1 is illustrated for different asset dimensions, i.e., $d = 2$ and $d = 20$.
-The empirical rates of convergence of the standard, the KRR-based, and the likelihood ratio-based procedures closely match their asymptotic rates for both asset dimensions, and they are independent of the asset dimension.
+The empirical rates of convergence of the standard, the KRR-based, and the likelihood ratio-based procedures closely match their asymptotic rates for both asset dimensions, and they are insensitive to an increase in the asset dimension.
 On the other hand, the empirical rates of convergence of the kernel smoothing-based and regression-based procedures are higher than their asymptotic rates for both asset dimensions.
@@
 Hence, the hyperparameter of interest is the number of nearest neighbors $k$.
-In our numerical experiment, cross-validation is conducted once to select the optimal value of $k$ for each simulation budget, and the selected value of $k$ is fixed for all $1,000$ replications.
+In our numerical experiment, cross-validation is conducted once to select the optimal value of $k$ for each simulation budget, and the selected value of $k$ is fixed for all $\num{1000}$ replications.
 Therefore, a suboptimal selection of the optimal value of $k$ can lead to a poor metamodel estimate, and the MSE of the kRR-based procedure will be dominated by the model error of the metamodel.
@@
     \includegraphics[width=0.48\textwidth]{./project1/figures/figure5b.png}
-    \caption{Cross-validation for the kernel smoothing-based procedure with $\Gamma=100,000$}
+    \caption{Cross-validation for the kernel smoothing-based procedure with $\Gamma=\num{100000}$}
     \label{fig1:kernel_cv} 
@@
 
-In Figure~\ref{fig1:kernel_cv}, the empirical convergence of the kernel smoothing-based nested simulation procedure for the probability of large loss is illustrated for different values of $k$ with $\Gamma = 100,000$.
+In Figure~\ref{fig1:kernel_cv}, the empirical convergence of the kernel smoothing-based nested simulation procedure for the probability of large loss is illustrated for different values of $k$ with $\Gamma = \num{100000}$.
 The observation is that the value of optimal $k$ estimated by cross-validation is highly variable across different replications.

### 2024-11-01 project1/nsSurvey.tex
new

@@
     \item   Regression:
-            $$\hat{L}^{\text{REG}}_{M, N}(X) = \Phi(X) \hat{\beta}^{\text{REG}},$$
-            where $\Phi$ is a chosen basis, and $\hat{\beta}^{\text{REG}}$ is estimated from the training samples.
+            $$\hat{L}^{\text{REG}}_{M, N}(X) = \Phi(X) \hat{\beta},$$
+            where $\Phi$ is a chosen basis, and $\hat{\beta}$ is estimated from the training samples.
             In~\cite{broadie2015risk}, the convergence analysis is performed on the expection Equation~\ref{eq1:sl-E} and for smooth and Lipschitz continuous $h$. 
@@
 
-The MSEs of the nested simulation procedures are fitted with a regression line, and the slope of the fitted line is reported as the empirical rate of convergence of the corresponding procedure.
-The second number in the legend is the asymptotic rate of convergence obtained from the theoretical analysis.
-By comparing the empirical rates of convergence with the asymptotic rates, we can observe that the empirical rates of all procedures closely match their asymptotic rates.
-
-Except for the standard nested simulation procedure, the empirical rates of convergence of the other procedures are close to $\Gamma^{-1}$.
-Pooling of inner simulation samples across different outer scenarios is the key reason for their higher empirical rates of convergence.
+A regression line is fitted to the MSEs of each nested simulation procedure against the simulation budget $\Gamma$ in a log-log scale, and the slope of the fitted line is reported.
+The slopes of the fitted lines can be interpreted as the empirical rates of convergence.
+Alongside in the parentheses are the asymptotic rates of convergence obtained by the theoretical analysis in Section~\ref{sec1:asymptotic-convergence}.
+By comparing the empirical rates of convergence with the asymptotic rates, we can observe how well the empirical rates of convergence match their asymptotic rates.
+In the case illustrated in Figure~\ref{fig1:compareAll}, the empirical rates of all procedures closely match their asymptotic rates.
+
+Except for the standard nested simulation procedure, the empirical rates of convergence of the other procedures are close to $\Gamma^{-1}$, i.e., all of them achieve similar finite-sample performance that is better than the standard procedure.
+Pooling of inner simulation samples across different outer scenarios is the key reason behind their higher empirical rates of convergence.
 However, pooling also introduces additional computational cost that is not reflected in the simulation budget $\Gamma$.
@@
 In the following sections, we examine the empirical convergence of the nested simulation procedures in a similar manner as in Figure~\ref{fig1:compareAll}.
-With a more detailed analysis of different risk measures, option types, and asset dimensions, we aim to provide a comprehensive understanding of the convergence behavior of the nested simulation procedures in practice.
+With a more detailed analysis of different risk measures, option types, and asset dimensions, we aim to provide a comprehensive understanding and comparison of the convergence behavior of the nested simulation procedures in practice.
 
@@
 However, in practice, their empirical convergence behavior could be different.
-In this section, we examine the sensitivity of the empirical convergence of the nested simulation procedures to the asset dimension.
+In this section, we examine the sensitivity to the asset dimension of the empirical convergence of the nested simulation procedures.
 
@@
 The empirical rates of convergence of the standard, the KRR-based, and the likelihood ratio-based procedures closely match their asymptotic rates for both asset dimensions, and they are insensitive to an increase in the asset dimension.
-On the other hand, the empirical rates of convergence of the kernel smoothing-based and regression-based procedures are higher than their asymptotic rates for both asset dimensions.
-They are sensitive to the asset dimension but in different ways.
-The empirical rate of convergence of the kernel smoothing-based procedure decreases as the asset dimension increases.
-This phenomenon is consistent with the theoretical analysis in Section~\ref{sec1:asymptotic-convergence}, where the asymptotic rate of convergence of the kernel smoothing-based procedure is shown to be sensitive to the asset dimension.
-However, the empirical rate is still higher than its asymptotic rate for $d = 2$ and $d = 20$.
-The empirical rates of convergence of the regression-based procedure is higher than its asymptotic rates for both asset dimensions, and the empirical rate is higher for $d = 20$ than for $d = 2$.
-
-\subsection{Empirical Convergence of Parametric Regression Procedures} \label{sec1:regression-convergence}
-
-For both the regression-based and the kernel smoothing-based procedures, the reason for the higher empirical rates can be explained by having poor metamodels for smaller simulation budgets.
-For lower simulation budgets, the trained metamodels of the true inner simulation are poor, and the MSEs of the regression-based and kernel smoothing-based procedures are dominated by the model error of the metamodels.
-In other words, they have not reached their asymptotic regimes yet.
-Due to computation constraints, we are not able to conduct experiments for kernel smoothing-based nested simulation procedures for higher budget levels, but we are able to conduct additional experiments for the regression-based nested simulation procedure.
-In our previous numerical experiments, the empirical rate of convergence of the regression procedure is observed to be much larger than its asymptotic rate of convergence.
-For dimensions larger than $10$, the MSE of the regression procedure decreases quickly in the beginning, and it stabilizes after a certain budget level.
-In~\ref{fig1:reg_lb} illustrates the empirical convergence of the regression-based procedure in more detail at higher simulation budgets, where the asymptotic level of convergence is reached for $d = 20$.
-
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.7\textwidth]{./project1/figures/figure3.png}
-    \caption{Empirical convergence of regression procedure for European call options and $d=20$}
-    \label{fig1:reg_lb} 
-\end{figure}
-
-The left part of Figure \ref{fig1:reg_lb} contains the MSEs of the regression procedure for budget sizes that are smaller than $10^3$. 
-Slopes of the fitted lines on the left correspond to the empirical rate of convergence of the regression procedure for budget levels between $10^3$ and $10^4$.
-To investigate the convergence behavior for higher budget levels, we conduct additional experiments for the European call option with dimension $20$. 
-The additional experiments are summarized on the right of Figure \ref{fig1:reg_lb}.
-After reaching a certain budget level, i.e., $\Gamma = 10^6$, the empirical rate of convergence for the regression-based nested simulation procedure approaches its asymptotic rate. 
-For nested simulation procedures with biased metamodeling, the metamodel estimates of the true inner simulation are poor, especially for smaller budget sizes. 
-We are able to clearly observe this phenomenon for the regression metamodel, and it can be explained by dividing the MSE into metamodeling bias and simulation variance.
-For small budget sizes, the improvement in the bias of the regression metamodel dominates the improvement in simulation variance. 
-Performing poorly for extremely low simulation budgets, the regression metamodel improves significantly as the simulation budget increases.
-As the simulation budget gets higher, the improvement of the regression bias becomes negligible compared with that of the simulation variance. 
-The regression metamodel ceases to improve after reaching a certain level ($\Gamma = 10^6$ in our case), and the improvement of simulation variance dominates.
-Due to high computational costs, we are not able to conduct experiments for higher budget levels, but we expect the MSE of the regression-based nested simulation procedure to stabilize after $\Gamma = 10^6$, and the empirical rate of convergence to approach its asymptotic rate.
+Conversely, both the kernel smoothing-based and regression-based procedures are greatly affected by the asset dimension.
+Their sensitivities to the asset dimension differ in finite-sample experiments:
+\begin{itemize}    
+    \item For the kernel smoothing-based procedure, the empirical rate of convergence decreases as the asset dimension increases. 
+    This observation aligns with the theoretical analysis in Section~\ref{sec1:asymptotic-convergence}, which demonstrates that the asymptotic rate of convergence of the kernel smoothing-based procedure is sensitive to the asset dimension.
+    Nevertheless, even for $d = 2$ and $d = 20$, the empirical rate remains higher than its asymptotic rate.
+    \item For the regression-based procedure, the asymptotic rate is not affected by the asset dimension, but the empirical rates of convergence are higher than the asymptotic rates for both asset dimensions, and the empirical rate is higher for $d = 20$ than for $d = 2$.
+\end{itemize}
+In the following sections, we provide detailed explanations for the discrepancy between their empirical rates of convergence and their asymptotic rates.
 
@@
 Kernel smoothing is a nonparametric regression metamodel.
-According to the theoretical analysis in Section~\ref{sec1:asymptotic-convergence}, the asymptotic rate of convergence of the kernel smoothing-based nested simulation procedure is highly dependent on the dimension of the asset.
+According to the theoretical analysis in Section~\ref{sec1:asymptotic-convergence}, the asymptotic rate of convergence of the kernel smoothing-based nested simulation procedure is highly dependent on the asset dimension $d$.
 In this section, we use a kNN metamodel for the kernel smoothing-based nested simulation procedure, and we examine its empirical convergence for different asset dimensions.
@@
 For the two replications where $k = 80$ is estimated as the optimal value of $k$, the resulting estimates of risk measures are $0.1187$ and $0.1189$, which are significantly higher than the estimated risk measures for the other replications and far from the true risk measure of $0.1$.
-This observation suggests that the empirical convergence of the kernel smoothing-based nested simulation procedure is highly dependent on the cross-validation of the hyperparameters of the metamodel.
+This observation suggests that the empirical convergence of the kernel smoothing-based nested simulation procedure is highly sensitive to the cross-validation of the hyperparameters of the metamodel.
+A KRR-based nested simulation procedure suffers from the same problem.
+
+\subsection{Empirical Convergence of Parametric Regression Procedures} \label{sec1:regression-convergence}
+
+For both the regression-based and kernel smoothing-based procedures, the observed higher empirical rates of convergence can be explained by the poor performance of their metamodels at low simulation budgets.
+When simulation budgets are low, the metamodels trained to approximate the true inner simulation are inadequate.
+The MSEs for these procedures are dominated by the model errors of the metamodels.
+In other words, they have not yet reached their asymptotic convergence regimes.
+
+Due to computation constraints, we are not able to conduct experiments for kernel smoothing-based nested simulation procedures for higher budget levels, but we are able to conduct additional experiments for the regression-based nested simulation procedure.
+In our previous numerical experiments, the empirical rate of convergence of the regression procedure is observed to be much larger than its asymptotic rate of convergence.
+For dimensions larger than $10$, the MSE of the regression procedure decreases quickly in the beginning, and its rate of decrease stabilizes after a certain budget level.
+In~\ref{fig1:reg_lb} illustrates the empirical convergence of the regression-based procedure in more detail at higher simulation budgets, where the asymptotic level of convergence is reached for $d = 20$.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.7\textwidth]{./project1/figures/figure3.png}
+    \caption{Empirical convergence of regression procedure for European call options and $d=20$}
+    \label{fig1:reg_lb} 
+\end{figure}
+
+The left part of Figure \ref{fig1:reg_lb} contains the MSEs of the regression procedure for budget sizes that are smaller than $10^3$. 
+Slopes of the fitted lines on the left correspond to the empirical rate of convergence of the regression procedure for budget levels between $10^3$ and $10^4$.
+To investigate the convergence behavior for higher budget levels, we conduct additional experiments for the European call option with dimension $20$. 
+The additional experiments are summarized on the right side of Figure \ref{fig1:reg_lb}.
+After reaching a certain budget level, i.e., $\Gamma = 10^6$ in our case, the empirical rate of convergence for the regression-based nested simulation procedure approaches its asymptotic rate. 
+For nested simulation procedures with a biased metamodel, the metamodel estimates of the true inner simulation are poor, especially for smaller budget sizes. 
+We are able to clearly observe this phenomenon for the regression metamodel, and it can be explained by dividing the MSE into metamodeling bias and simulation variance.
+\begin{itemize}
+    \item For small budget sizes, the improvement in the bias of the regression metamodel dominates the improvement in simulation variance. 
+    Performing poorly for extremely low simulation budgets, the regression metamodel improves significantly as the simulation budget increases.
+    \item As the simulation budget gets higher, the improvement of the regression bias becomes negligible compared with that of the simulation variance. 
+    The regression metamodel ceases to improve after reaching a certain level ($\Gamma = 10^6$ in our case), and the improvement of simulation variance dominates.
+\end{itemize}
+Due to high computational costs, we are not able to conduct experiments for even higher budget levels, but we expect the MSE of the regression-based nested simulation procedure to stabilize after $\Gamma = 10^6$, and the empirical rate of convergence to approach its asymptotic rate.
+In the context of nested simulation procedures, a parametric regression metamodel has several advantages over a nonparametric regression metamodel.
+\begin{itemize}
+    \item Parametric regression achieves a good empirical convergence behavior for a moderate simulation budget.
+    \item Parametric regression is insensitive to changes in the asset dimension.
+    \item Parametric regression is easier to implement.
+    It does not require cross-validation to select the hyperparameters of the metamodel.
+\end{itemize}
+However, parametric regression suffers from the model misspecification risk.
+More specifically, selecting a wrong regression basis can lead to a poor metamodel estimate, where the MSE of the nested simulation procedure is dominated by the model error of the metamodel~\citep{broadie2015risk}.
+
+In our previous numerical experiments, the regression-based nested simulation procedure is implemented with Laguerre polynomials up to degree $3$ as the basis functions.
+It is a standard choice in the literature.
+To examine the sensitivity of the empirical convergence behavior to the regression basis, we consider different basis functions, i.e., regular polynomial regression up to degree $3$.
+
+\begin{figure}[ht!] 
+    \centering
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure13a.png}
+    \includegraphics[width=0.48\textwidth]{./project1/figures/figure13b.png}
+    \caption{Empirical convergence of regression-based nested simulation procedures for different regression bases}
+    \label{fig1:sens_basis}
+\end{figure}
+
+In Figure~\ref{fig1:sens_basis}, the empirical convergence results of the regression-based nested simulation procedure for a quadratic tracking error and a 90\%-CVaR are illustrated for the two different regression bases.
+The empirical rates of convergence of the regression-based nested simulation procedure are observed to be insensitive to the chosen regression basis.
 
@@
 
-\subsection{Sensitivity to the regression basis} \label{sec1:sensitivity-basis}
-
-In our previous numerical experiments, the regression-based nested simulation procedure is implemented with Laguerre polynomials up to degree $3$ as the basis functions.
-To examine the sensitivity of the empirical convergence behavior to the regression basis, we consider different basis functions, i.e., regular polynomial regression up to degree $3$.
-
-\begin{figure}[ht!] 
-    \centering
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure13a.png}
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure13b.png}
-    \caption{Empirical convergence of regression-based nested simulation procedures for different regression bases}
-    \label{fig1:sens_basis}
-\end{figure}
-
-In Figure~\ref{fig1:sens_basis}, the empirical convergence results of the regression-based nested simulation procedure for a quadratic tracking error and a 90\%-CVaR are illustrated for different regression bases, i.e., Laguerre polynomials and regular polynomials up to degree $3$.
-The empirical rates of convergence of the regression-based nested simulation procedure are observed to be insensitive to the chosen regression basis.
-In summary, the empirical convergence behavior of the regression-based nested simulation procedure is stable across different risk measures, option types, asset dimensions, levels of VaR and CVaR, asset models, and regression bases.
+In summary, we find the empirical convergence behavior of the regression-based nested simulation procedure to be stable across different risk measures, option types, asset dimensions, levels of VaR and CVaR, asset models, and regression bases.
 With a limited total budget, the regression-based nested simulation procedure is the most robust and stable among all nested simulation procedures.

### 2024-11-01 project2/nnMetamodels.tex
new

@@
     \end{tabular}
-    \caption{Spearman (and Pearson) correlation coefficients between high-capacity LSTM predicted losses and true losses.}
+    \caption{Spearman (Pearson) correlation coefficients of high-capacity LSTM predictions.}
     \label{tab2:lstm_corr}
@@
     \includegraphics[width=0.6\textwidth]{./project2/figures/cor_heatmap.png}
-    \caption{Difference between Spearman and Pearson correlation coefficients for high-capacity LSTM metamodel.}
+    \caption{Difference between Spearman and Pearson correlations for high-capacity LSTM metamodel.}
     \label{fig2:cor-heatmap}

### 2024-11-01 project3/draft.tex
new

@@
     \toprule
-    \textbf{Source} & \textbf{Extensive} & \textbf{Fine-tuning} & \textbf{Layer Freezing} & \textbf{Without TL} \\
+    \textbf{Lapse Type} & \textbf{Extensive} & \textbf{Fine-tuning} & \textbf{Layer Freezing} & \textbf{Without TL} \\
     \midrule
-    No Lapse GMMB & N/A & 0.4894 & 0.3361 & N/A \\
-    Static Lapse GMMB & N/A & 0.0794 & 0.0763 & N/A \\
-    Dynamic Lapse GMMB & 0.0587 &  N/A &  N/A & 0.2950 \\
+    No Lapse & N/A & 0.4894 & 0.3361 & N/A \\
+    Static Lapse & N/A & 0.0794 & 0.0763 & N/A \\
+    Dynamic Lapse & 0.0587 &  N/A &  N/A & 0.2950 \\
     \bottomrule

### 2024-11-01 project1/nsSurvey.tex
new

@@
 Numerical experiments are conducted on portfolios that consist of options on $d$ underlying assets, whose dynamics follow a multidimensional geometric Brownian motion with $0.3$ pairwise correlation.
-6 nested simulation procedures are considered, namely the standard nested simulation procedure, the MLMC procedure, the regression-based, kernel smoothing-based, likelihood ratio-based, and kernel ridge regression-based nested simulation procedures.
+
+A total of 6 nested simulation procedures are considered, namely the standard nested simulation procedure, the MLMC procedure, the regression-based, kernel smoothing-based, likelihood ratio-based, and kernel ridge regression-based nested simulation procedures.
 For the standard nested simulation procedure, the bootstrap-based budget allocation strategy from~\cite{zhang2021bootstrap} is implemented to estimate the optimal values of outer and inner simulation budgets.
@@
 The KRR metamodel is implemented with a Mat\'ern kernel, and the smoothness, the length scale, and the regularization hyperparameters are found by a cross-validation with Bayesian search~\citep{frazier2018bayesian}.
+Due to budget constraints, the hyperparameters of the nonparametric regression metamodel are tuned and used across all macro replications of the same experiment.
+
 The procedures are compared for 5 types of risk measures:
@@
 A KRR-based nested simulation procedure suffers from the same problem. 
+The fluctuation in Figure~\ref{fig1:kernel_d} is likely due to poor cross-validation of the hyperparameters of the metamodel.
 
@@
 
-In our previous numerical experiments, we have examined the empirical convergence behavior of the nested simulation procedures for European call options, which is the most basic option type.
-To examine the sensitivity of the empirical convergence behavior to the option type, we consider path-dependent options, namely geometric Asian options and barrier options.
+In our previous numerical experiments, we have examined the empirical convergence behavior of the nested simulation procedures for European call options, which only depends on the asset price at maturity.
+To examine the sensitivity of the empirical convergence behavior to the option type, we consider path-dependent options, i.e., geometric Asian options and barrier options.
 
@@
 The empirical rates of standard, likelihood ratio-based, and KRR-based nested simulation procedures closely ensemble their asymptotic rates for path-dependent options.
-The empirical rate of convergence of the regression-based and kernel smoothing-based procedures is much higher than their asymptotic rates for barrier options, with reasons explained in Section~\ref{sec1:regression-convergence}.
+The empirical rate of convergence of the regression-based and kernel smoothing-based procedures is much higher than their asymptotic rates for barrier options. 
+The reasons are explained in Section~\ref{sec1:regression-convergence} and Section~\ref{sec1:kernel-smoothing-convergence}.
 
@@
 
-In~\cite{broadie2015risk}, the authors propose a numerical example where the payoff has a W-shape with respect to the underlying asset price.
+In~\cite{broadie2015risk}, the authors propose a numerical example where the payoff has a W-shape with respect to the asset price at maturity.
 We have incorporated this example as Portfolio 5.
@@
 For all procedures, we observe a similar convergence behavior as in other path-dependent options.
-The MSEs of the kernel smoothing-based and KRR-based procedures do not decrease monotonically as the simulation budget increases, as observed and analyzed in Section~\ref{sec1:kernel-smoothing-convergence}.
+The MSEs of the kernel smoothing-based and KRR-based procedures do not decrease monotonically as the simulation budget increases.
+This fluctuating behavior is observed and analyzed in Section~\ref{sec1:kernel-smoothing-convergence}.
 
@@
 Furthermore, the regression-based procedure is stable across different payoff structures and risk measures. 
-Its MSEs decrease quickly in the beginning, and after reaching a certain budget level, the rate of decrease stabilizes to match its asymptotic rate of convergence.
+Its MSEs decrease quickly in the beginning, and after reaching a certain level of $\Gamma$, the rate of decrease stabilizes to match its asymptotic rate of convergence.
+Parametric regression is the most attractive metamodel for nested simulation procedures due to its fast empirical convergence behavior, stability across different payoff structures and risk measures, and ease of implementation.
+The following sections focus on the regression-based nested simulation procedure for the rest of the numerical experiments.
 
@@
 The level of VaR and CVaR is a critical factor that determines the complexity of the risk measure estimation.
-In our previous numerical experiments, the level of VaR and CVaR is set to be the 90\% quantile of the distribution of the inner simulation noise.
-In this section, we examine the empirical convergence of the regression-based nested simulation procedures for different levels of VaR and CVaR, i.e., $80\%$, $90\%$, $95\%$, $99\%$, and $99.6\%$.
+In our previous numerical experiments, the level of VaR and CVaR is set to be the $90\%$ quantile of the distribution of the inner simulation noise.
+In this section, we examine the empirical convergence of the regression-based nested simulation procedures for other levels of VaR and CVaR, i.e., $80\%$, $95\%$, $99\%$, and $99.6\%$.
 

### 2024-11-01 project1/nsSurvey.tex
new

@@
 
-Instead of using a figure, we provide a summary of the empirical convergence results of the MLMC procedure with a decomposition table of the MSEs in Table~\ref{tab1:mlmc-mse}.
+We provide a summary of the empirical convergence results of the MLMC procedure with a decomposition table of the MSEs in Table~\ref{tab1:mlmc-mse}.
 The MSEs of the MLMC procedure are decomposed into the bias and the variance of the estimator.
@@
 The training cost includes the cost of fitting the metamodel and the cost of cross-validation for nonparametric regression metamodels.
-For the standard procedure, the training cost is $0$ due to the absence of a metamodel. 
-Its prediction cost $\mathcal{O}(M)$ comes from the evaluation of the function $h$ for $M$ samples.
+
+For the standard procedure, 
+\begin{itemize}
+    \item the training cost is $0$ due to the absence of a metamodel. 
+    \item Its prediction cost $\mathcal{O}(M)$ comes from the evaluation of the function $h$ for $M$ samples.
+\end{itemize}
 For the regression-based procedure, a linear regression model is fitted with $p$ predictors.
-In practice, $p$ is usually much smaller than $M$ and does not grow with the simulation budget $\Gamma$.
-However, it is dependent on the complexity of the payoff function.
+\begin{itemize}
+    \item The training cost is $\mathcal{O}(p^2M) + \mathcal{O}(p^3)$.
           Estimating the coefficients of the regression model involves multiplying the design matrix by its transpose and inverting the resulting matrix, which has complexity $\mathcal{O}(p^2M)$ and $\mathcal{O}(p^3)$, respectively.
@@
           The matrix inversion has complexity $\mathcal{O}(p^3)$ using Gauss-Jordan elimination, but in practice, the complexity can be reduced to $\mathcal{O}(p^{2.807})$ by~\cite{strassen1969gaussian} and $\mathcal{O}(p^{2.376})$ by~\cite{coppersmith1987matrix}.
-The prediction cost of the regression-based procedure is $\mathcal{O}(pM)$, which comes from the multiplication of the design matrix by the estimated coefficients.
+          In practice, $p$ is usually much smaller than $M$ and does not grow with the simulation budget $\Gamma$.
+          $p$ is fixed by the basis function, which is selected based on the complexity of the payoff function.
+    \item The prediction cost of the regression-based procedure is $\mathcal{O}(pM)$, which comes from the multiplication of the design matrix by the estimated coefficients.
+\end{itemize}
 For the kernel smoothing-based procedure, the kNN metamodel is implemented. 
 In practice, the K-D tree algorithm~\citep{bentley1975multidimensional} is often implemented for efficient nearest neighbor search.
-During training, a tree is constructed to store the distance, which has complexity $\mathcal{O}(M\log(M))$.
-The prediction cost of the kernel smoothing-based procedure is $\mathcal{O}(kM\log(M))$, which comes from a query of the K-D tree for $k$ nearest neighbors for $M$ samples.
+\begin{itemize}
+    \item During training, a tree is constructed to store the distance, which has complexity $\mathcal{O}(M\log(M))$.
+    \item The prediction cost of the kernel smoothing-based procedure is $\mathcal{O}(kM\log(M))$, which comes from a query of the K-D tree for $k$ nearest neighbors for $M$ samples.
     Conversely, An inefficient algorithm calculates the distance matrix during training and a block sort algorithm to find the $k$ nearest neighbors, which results in a complexity of $\mathcal{O}(M^2)$ and $\mathcal{O}(M^2\log(M))$, respectively.
@@
     Hence, an efficient implementation of the kNN metamodel is crucial for the kernel smoothing-based procedure.
-For the likelihood ratio-based procedure, the training cost is $0$ as no training is required.
-The prediction cost of the likelihood ratio-based procedure is $\mathcal{O}(M^2)$, which comes from the calculation of the likelihood weights for $M$ samples.
-For the KRR-based procedure, the main training cost comes from inverting an $M \times M$ kernel matrix~\citep{scholkopf2002learning}, which has complexity $\mathcal{O}(M^3)$ using Gauss-Jordan elimination.
+\end{itemize}
+For the likelihood ratio-based procedure, 
+\begin{itemize}
+    \item the training cost is $0$ as no training is required.
+    \item The prediction cost of the likelihood ratio-based procedure is $\mathcal{O}(M^2)$, which comes from the calculation of the likelihood weights for $M$ samples.
+\end{itemize}
+For the KRR-based procedure, 
+\begin{itemize}
+    \item the main training cost comes from inverting an $M \times M$ kernel matrix~\citep{scholkopf2002learning}, which has complexity $\mathcal{O}(M^3)$ using Gauss-Jordan elimination.
           Similar to the regression-based procedure, this complexity can be reduced to $\mathcal{O}(M^{2.376})$.
-The prediction cost of the KRR-based procedure is $\mathcal{O}(M^2)$, which comes from the multiplication of the kernel matrix by the estimated coefficients.
-Among the metamodel-based procedures, regression is the most efficient as $p$ is usually much smaller than $M$. 
+    \item The prediction cost of the KRR-based procedure is $\mathcal{O}(M^2)$, which comes from the multiplication of the kernel matrix by the estimated coefficients.
+\end{itemize}
+Among the metamodel-based procedures, parametric regression is the most efficient.
+In regression, the number of features is usually much less than the number of data points, i.e., $p<M$. 
 Kernel smoothing and KRR are kernel-based metamodels, and they are more computaional expensive due to distance calculations and cross-validations of hyperparameters. 

### 2024-11-02 project1/nsSurvey.tex
new

@@
 
-In our finite-sample experiments, we have observed that the actual computational cost to be significantly different from the theoretical complexity, as not only the order of complexity but also the constant factors can affect the computational cost.
-In Figure~\ref{fig1:tcc}, the total computational time of different nested simulation procedures for European call options and geometric Asian options with $d = 10$ is illustrated in a log-log scale.
+The cost associated with pooling makes a significant impact on the overall computaional complexity of a metamodel-based nested simulation procedure.
+In our finite-sample experiments, we have indeed observed that the actual computational cost to deviate significantly from the simulation cost.
+In Figure~\ref{fig1:tcc}, the total actual computational time of different nested simulation procedures for European call options and geometric Asian options with $d = 10$ is illustrated in a log-log scale.
 The $x$-axis shows the total simulation budget $\Gamma$, and the $y$-axis is the total computational time for 1 replication of the numerical experiment, in seconds.
@@
 The likelihood ratio-based and KRR-based procedures are the most computationally expensive among all procedures.
-They are demanding in terms of memory.
+They are also demanding in terms of memory.
 For budgets larger than $10^5$, the likelihood ratio-based procedure becomes impractical as storage of the likelihood weights becomes a bottleneck.
@@
 
-Figure~\ref{fig1:c_model} illustrates the computational time of implementing different nested simulation procedures for the portfolio of geometric Asian options with $d = 10$, excluding the simulation time.
+Figure~\ref{fig1:c_model} illustrates the computational time of implementing different nested simulation procedures for the portfolio of geometric Asian options with $d = 10$.
 The simulation time is omitted as it is the same for all procedures.
-The remainder can be decomposed into two parts: hyperparameter tuning and model implementation.
+The remaining computations can be decomposed into two parts: hyperparameter tuning and model implementation.
 The hyperparameter tuning cost is the cost of estimating the optimal hyperparameters for the metamodels, and the model implementation cost is the cost of fitting the metamodels and generating predictions from the trained metamodels.

### 2024-11-02 project1/nsSurvey.tex
new

@@
 A regression model is fitted to each model respectively, and its slope can be viewed as the growth rate of the computational time with respect to $\Gamma$.
-The total computational time of the standard procedure is mostly attributed to finding the optimal $M$ and $N$ using the bootstrap-based budget allocation strategy from~\cite{zhang2021bootstrap}.
+\begin{itemize}
+    \item The total computational time of the standard procedure is mostly attributed to finding the optimal $M$ and $N$ using the bootstrap-based budget allocation strategy from~\cite{zhang2021bootstrap}.
     This cost does not grow with the simulation budget $\Gamma$, as its slope is close to $0$.
-The regression-based procedure does not require hyperparameter tuning, and its total computational time is mainly attributed to the model implementation.
+    \item The regression-based procedure does not require hyperparameter tuning, and its total computational time is mainly attributed to the model implementation.
     The slope of the regression line is close to $1$, resembling the its algorithmic complexity in Table~\ref{tab1:complexity}.
-The kernel smoothing-based and KRR-based procedure requires cross-validation to estimate the optimal hyperparameters.
+    \item The kernel smoothing-based and KRR-based procedure requires cross-validation to estimate the optimal hyperparameters. 
     In our implementaion of kNN, the cross-validation is conducted using a grid search with a search space whose cardinality does not grow with the simulation budget $\Gamma$.
     However, the cross-validation cost of the kernel smoothing-based procedure grows with the simulation budget $\Gamma$ as more samples are involved.
-The KRR-based procedure requires Bayesian optimization to estimate the optimal hyperparameters, and the cardinality of the search space grows with the simulation budget $\Gamma$.
+    The KRR-based procedure requires Bayesian optimization to estimate the optimal hyperparameters, and the cardinality of the search space also grows with the simulation budget $\Gamma$.
     The empirical cost of the KRR-based procedure does not resemble its algorithmic complexity in Table~\ref{tab1:complexity}.
@@
     Our observation for KRR implementation time is in line with the findings in~\cite{scikit-learn}, where the cost of KRR is reported quickly increasing with the number of samples.
-The likelihood ratio-based procedure requires no hyperparameter tuning, and its total computational time is mainly attributed to the likelihood weight calculation, which is $\mathcal{O}(M^2)$. 
+    \item The likelihood ratio-based procedure requires no hyperparameter tuning, and its total computational time is mainly attributed to the likelihood weight calculation, which is $\mathcal{O}(M^2)$.
+\end{itemize}
 In summary, for a large simulation budget, the regression-based procedure is the most efficient among all metamodel-based procedures in terms of computational time.
-
-\section{Conclusion} \label{sec1:conclusion}
+For moderate simulation budgets, the regression-based procedure should be the preferred choice.
+
+\section{Conclusion and Extensions} \label{sec1:conclusion}
 In the task of estimating risk measures for portfolios of complex financial derivatives, nested simulation procedures are commonly required but often computationally expensive. 
@@
 However, we have only examined the performance for option portfolios in this study, where finding a suitable set of basis functions for regression is relatively easy.
-For payoff functions with high complexity or high dimensionality, the regression-based procedure may not be the best choice.
 In practice, a variable annuity contract is often high-dimensional in time with a complex payoff structure, and it is a challenging problem for nested simulation procedures.
+The time dependence in the feature space leads to multi-collinearity, and the regression-based procedure may not be the best choice.
 In such cases, a neural network-based procedure may be more suitable, as it is a data-driven algorithm that finds a suitable set of basis functions automatically.
-In Chapter~\ref{chap:project2}, we will examine the performance of regression-based and neural network-based nested simulation procedures for estimating risk measures for variable annuities.
+In Chapter~\ref{chap:project2}, we examine the performance of regression-based and neural network-based nested simulation procedures for estimating risk measures for variable annuities.

### 2024-11-02 project2/nnMetamodels.tex
new

@@
 In supervised learning, DNNs are believed to learn from the given data about the feature-label relationship to predict new labels for unseen features.
-Cross validation using to assess a subset, i.e., the validation set, of the original data, is a common way to access the quality of learning.
+Cross-validation using to assess a subset, i.e., the validation set, of the original data, is a common way to access the quality of learning.
 Generalization error on the test labels is another popular assessment metric.
-But the test set is also a subset of the original data.
+However, the test set is also a subset of the original data.
 In this study, we revisit these questions in a simulation context and propose an alternative approach to answer them.
-Instead of relying solely on real-data (splitting it into multiple subsets), we propose using stochastic simulation outputs as training labels for DNNs.
+Instead of relying solely on real-data and splitting it into multiple subsets, we propose using stochastic simulation outputs as training labels for DNNs.
 By controlling the simulation design parameters, such as the number of independent replications, we can control the quality and also the quantity of the training labels fed into the neural networks.
@@
 A popular metamodel in nested simulation procedures is stochastic kriging.
-~\cite{liu2010stochastic} use stochastic kriging as a metamodel of Monte Carlo simulations to estimate the Conditional Value-at-Risk (CVaR) of a portfolio of derivative securities, and~\cite{gan2015valuation} use stochastic kriging for an efficient valuation of large portfolios of variable annuity (VA) contracts.
+~\cite{liu2010stochastic} use stochastic kriging as a metamodel of Monte Carlo simulations to estimate the CVaR of a portfolio of derivative securities, and~\cite{gan2015valuation} use stochastic kriging for an efficient valuation of large portfolios of variable annuity (VA) contracts.
 Other studies, such as ~\cite{broadie2015risk},~\cite{hong2017kernel}, and~\cite{zhang2022sample} use regression, kernel smoothing, and the likelihood ratio method, respectively.
@@
 
-In this section we present notations, problem settings, and a simulation model for risk estimation for hedging errors of variable annuities.
+In this section we present notations, problem settings, and a simulation model for risk estimation for hedging errors of VAs.
 A main goal of the section is to showcase the complexity of the simulation model, which we use as a data generator to train DNN metamodels (Section~\ref{sec2:metamodel2Stage} and Section~\ref{sec2:metamodel1Stage}).
@@
 
-Variable annuity contracts offer different types of guarantees.
+VA contracts offer different types of guarantees.
 Generally speaking, a portion of the VA premium is invested in a sub-account whose return is linked to some stock indices.
@@
 Denote the policyholder's (random) time of death by $\tau>0$.
-Then the contract expires at $T'=\min\{T,\tau\}$, i.e., the earlier of the contract maturity and the death of the policyholder.
+The contract expires at $T'=\min\{T,\tau\}$, i.e., the earlier of the contract maturity and the death of the policyholder.
 Let $S_t$, $F_t$, and $G_t$ be the indexed stock price, the subaccount value and the guarantee value, respectively, at time $t=1,2,\ldots,T$.
@@
 For GMWB, a standard nested simulation procedure to estimate the $\alpha$-CVaR of $L$ is described in Algorithm~\ref{alg2:standardProcedure}.
-
-% For example, for GMWB, a standard nested simulation procedure to estimate the $\alpha$-CVaR of $L$ is as follows:
-% \begin{enumerate}
-%     \item For $i=1,\ldots,M$, simulate outer scenarios $\bS^{(i)} = (S_{1}^{(i)},\ldots,S_{T}^{(i)})$ under the real-world measure $\mathbb{P}$.
-%     Figure~\ref{fig2:illustration} illustrates the inner simulation experiments needed for an outer scenario.
-
-%     \item For $t=0$, simulate time-$0$ inner paths $\bStilde_{0}^{(j)} = (\Stilde_{1}^{(j)},\Stilde_{2}^{(j)},\ldots,\Stilde_{T}^{(j)})$, $j=1,\ldots,N$ under $\mathbb{Q}$ {and} then estimate $V_0$ by $\Vhat_0 = \sum_{s=1}^{T} e^{-r(T-s)} [(I_s - F_s)^+- \eta_n F_s]$ and estimate $\Deltahat_0 = \Delta_0(\Stilde_{1}^{(j)},\ldots,\Stilde_{T}^{(j)} | S_0)$ based on~\eqref{eq2:delta}.
-%     Note that $S_0$ is known, so these inner paths do not depend on any outer scenario.
-%     The same $\Vhat_0$ and $\Deltahat_0$ are used in all scenarios.
-
-%     \item Given each scenario $\bS^{(i)}$, the following inner simulation is needed to estimate the corresponding loss $\Lhat_i$ for that scenario.
-%     \begin{enumerate}
-%         \item At each time~$t=1,\ldots,T-1$, simulate inner paths $\bStilde_{t}^{(ij)} = (\Stilde_{t+1}^{(ij)},\ldots,\Stilde_{T}^{(ij)})$, $j=1,\ldots,N$ under $\mathbb{Q}$ {and} then estimate $\Delta_t$ by $\Deltahat_t^{(i)} = \Delta_t(\Stilde_{t+1}^{(ij)},\ldots,\Stilde_{T}^{(ij)} | \bm{S}_t^{(i)})$ based on~\eqref{eq2:delta}.
-
-%         \item Use scenarios $\bS^{(i)}$ and $\Vhat_0$ and $\Deltahat_t^{(i)}$ to calculate losses $\Lhat_i^{MC}$, $t=0,\ldots,T-1$, based on~\eqref{eq2:lossrv}.
-Then sort them as $\Lhat^{MC}_{(1)}\leq \Lhat^{MC}_{(2)} \leq \cdots\leq \Lhat^{MC}_{(M)}$.
-%     \end{enumerate}
-
-%     \item Estimate $\alpha$-CVaR of $L$ by $\widehat{\CVaR}^{MC}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}\Lhat_{(i)}^{MC} = \frac{1}{(1-\alpha)M} \sum_{i \in \widehat{\tail}_{(1-\alpha )M}^{MC}}\Lhat_{i}^{MC}$
-%     where $\widehat{\tail}_{k}^{MC}$ denotes a \textit{Monte Carlo tail scenario set} associated with the largest $k$ estimated losses.
-% \end{enumerate}
 

### 2024-11-02 project2/nnMetamodels.tex
new

@@
 
-We refer to the collection of experiments needed conditional on one scenario $\bS^{(i)}$ to estimate $L_i$, that is, all upward arrows in Figure~\ref{fig2:illustration}, as one inner simulation experiment.
+We refer to the collection of experiments needed conditional on one scenario $\bS^{(i)}$ to estimate $L_i$, that is, all upward arrows in Figure~\ref{fig2:illustration}, as one inner simulation.
 We make four observations:
 \begin{itemize}
-    \item   each inner simulation is time-consuming, as it includes $T$ simulation experiments, one at each time $t=0,\ldots,T-1$,
-    \item   after running inner simulations for $M$ scenarios, we obtain simulated data, that is, feature-label pairs, $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$; the feature vector $\bS$ is $T$ dimensional,
+    \item   Each inner simulation is time-consuming, as it includes $T$ simulation experiments: one at each time $t=0,\ldots,T-1$,
+    \item   After running inner simulations for $M$ scenarios, we obtain simulated dataas feature-label pairs, $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$; the feature vector $\bS$ is $T$ dimensional.
     \item   $\Lhat_i^{MC}$ is a standard Monte Carlo estimator of the true loss for scenario $\bS^{(i)}$. 
@@
     As $N$ approaches infinity, $\Lhat_i^{MC}$ converges to the true loss $L_i$, and
-    \item   most importantly, when estimating tail risk measures such as $\alpha$-CVaR, only a small number of estimated losses, that is, those associated with the set of tail scenarios $\widehat{\tail}_{k}$ are used in the estimator.
+    \item   Most importantly, when estimating tail risk measures such as $\alpha$-CVaR, only a small number of estimated losses, that is, those associated with the set of tail scenarios $\widehat{\tail}_{k}$ are used in the estimator.
 \end{itemize}
@@
 We propose a two-stage procedure with a neural network metamodel that aims to produce a CVaR estimate that's as accurate as that of the standard procedure, but uses fewer computations as than latter.
-
-% \begin{itemize}
-%     \item[I.] \textbf{Train a neural network metamodel using simulation data.}
-%     \begin{itemize}[leftmargin=0pt]
-%         \item Use a fraction of the total simulation budget to run Steps 1, 2, and 3 in the standard procedure with the same number of outer scenarios, $M$, but a much smaller number of inner replications, i.e., $N'\ll N$, in each scenario.
-%         Then obtain $M$ simulated samples, i.e., feature-label pairs, $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$.
-%         Note that $N'$ may be 10 times or even 100 times smaller than $N$, so the loss estimates $\Lhat_i$ are expected to have larger variance, i.e., more noisy, than the standard procedure's loss estimates.
-
-%         \item Use the simulated data, $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$ to train a neural network.
-%         We refer to the trained model as a \textit{metamodel} as denote it by $\Lhat^{PD}(\bS)$.
-%         Denote the predicted losses for the outer scenarios by $\Lhat^{PD}_i = \Lhat^{PD}(\bS^{(i)})$, $i=1,\ldots,M$.
-
-%         \item Sort the predicted losses $\Lhat^{PD}_{(1)}\leq \Lhat^{PD}_{(2)} \leq \cdots\leq \Lhat^{PD}_{(M)}$ to identify a \textit{predicted tail scenario set} associated with the largest predicted losses, i.e., $\widehat{\tail}_{m}^{PD}:=\{i: \Lhat^{PD}_i > \Lhat^{PD}_{(M-m)}\}$.
-%         The number of predicted tail scenarios, $m$, is a user's choice and will be discussed later.
-%     \end{itemize}
-%         \item[II.] \textbf{Concentrate simulation on predicted tail scenarios.}
-%         \begin{itemize}[leftmargin=0pt]
-
-%         \item Run Steps 2 and 3 of the standard procedure with the same number of inner replications, $N$, but only on the predicted tail scenarios, i.e., scenarios associated with $\widehat{\tail}_{m}^{PD}$.
-%         Denote the standard procedure's estimated losses and sorted losses by $\Lhat^{ML}_i$ and $\Lhat^{ML}_{(i)}$, respectively, $i=1,\ldots,m$.
-
-%         \item Estimate the $\alpha$-CVaR of $L$ by $\widehat{\CVaR}^{ML}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}\Lhat_{(i)}^{ML} = \frac{1}{(1-\alpha)M} \sum_{i \in \widehat{\tail}_{(1-\alpha )M}^{ML}}\Lhat_{i}^{ML}$
-%         where $\widehat{\tail}_{k}^{ML}$ denotes a \textit{predicted tail scenario set} associated with the largest $k$ estimated losses.
-%     \end{itemize}
-%     \end{itemize}
 
@@
 However, different from their fixed-budget simulation design, we attempt to achieve a target accuracy.
-Specifically, in Stage 2 we propose using a standard procedure with the same number of inner replications, $N$, as a competing simulation procedure (or a benchmark).
-There are two different experiment designs for nested simulation procedures: fixed-budget design and fixed-accuracy design.
+Specifically, in Stage 2 we propose using a standard procedure with the same number of inner replications, $N$, as a benchmark procedure.
+There are two different types of experiment designs for nested simulation procedures: fixed-budget design and fixed-accuracy design.
 In a fixed-budget design, the simulation budget is fixed and the goal is to achieve the highest accuracy possible within the budget.
@@
 This budget concentration is expected to improve the estimation accuracy of the two-stage procedure compared to a standard procedure with the same budget. 
-If the metamodel is accurate in predicting true tail scenarios, then the two-stage procedure is expected to achieve higher accuracy than the standard procedure with the same budget.
+If the metamodel is accurate in predicting true tail scenarios, the two-stage procedure is expected to achieve higher accuracy than the standard procedure with the same budget.
 However, we believe that the goal of designing an efficient simulation procedure is to solve practical problems faster, so a target-accuracy design is more suitable, which refers to obtaining a similar level of accuracy as the standard procedure but with much less simulation budget.
@@
 The single-stage procedure has three major advantages over the two-stage procedure:
-(1) the single-stage procedure is expected to be more efficient than the two-stage procedure because it does not require the running the standard procedure in Stage 2, 
-(2) the safety margin $\epsilon$ is not needed in the single-stage procedure, and
-(3) most importantly, the single-stage procedure is not limited to just estimating tail risk measures and can be extended to provide a broader assessment of risk. 
+\begin{enumerate}
+    \item The single-stage procedure is expected to be more efficient than the two-stage procedure because it does not require the running the standard procedure in Stage 2.
+    \item The safety margin $\epsilon$ is not needed in the single-stage procedure.
+    The safety margin is difficult to determine because it depends on the metamodel's accuracy in identifying true tail scenarios.
+    The single-stage procedure does not need a safety margin because it directly estimates the risk measure using the predicted losses.
+    \item Most importantly, the single-stage procedure is not limited to just estimating tail risk measures and can be extended to provide a broader assessment of risk. 
     It can be naturally adapted to estimate risk measures that require the knowing of the entire loss distribution, such as the standard deviation or the squared tracking error.
-In our numerical experiments, we will compare the single-stage procedure to the two-stage procedure and the standard procedure in estimating the $\alpha$-CVaR of the hedging losses for GMWB, and we will also examine the single-stage procedure's performance in estimating the standard deviation of the hedging losses.
+    In our numerical experiments, we will compare the single-stage procedure to the two-stage procedure and the standard procedure in estimating the $\alpha$-CVaR for a larger range of $\alpha$.
+\end{enumerate}
 
@@
 
-We conduct a series of simulation experiments to (1) demonstrate the efficiency of the proposed metamodeling procedures and (2) examine the error tolerance to noisy training data in deep learning models.
+We conduct a series of simulation experiments to 
+\begin{enumerate}
+    \item demonstrate the efficiency of the proposed metamodeling procedures, and
+    \item examine the error tolerance to noisy training data in deep learning models.
+\end{enumerate}
 The problem settings in our experiments are identical to those in~\cite{dang2020efficient}:
@@
 
-For each metamodel, 50 independent macro replications are run\footnote{Each macro replication includes simulating a noisy dataset, separating it into training and test data, fitting a metamodel, and making predictions}.
+For each metamodel, 50 independent macro replications are run.
+Each macro replication involves simulating a noisy dataset, separating it into training and test data, fitting a metamodel, and making predictions.
 The last three columns in Table~\ref{tab:gmwb_arch} display the average squared errors between the predicted losses and the losses (labels) in different datasets.

### 2024-11-03 project2/nnMetamodels.tex
new

@@
 
-There are also differences among the three DNN models due to having different architectures.
+There are significant differences among the three DNN models due to having different architectures.
 The FNN is a generic neural network, its test error is larger than the training error, which is a sign of over-fitting and poor generalization.
 In contrast, RNN and LSTM networks have recurrent strucutures and are designed to capture temporal relationship in the high-dimensional feature.
-As a result, they have lower training errors, i.e., they fit the data better, and have lower testing error, i.e., they generalize better.
-Notably, the true errors for the DNN metamodels are lower than the test errors.
+As a result, they have lower training errors, i.e., they fit the data better, and have lower test errors, i.e., they generalize better.
+Notably, the true errors for the DNN metamodels are lower than the training errors.
 This is a sign of the metamodels' ability to learn the true feature-label relationship with noisy training labels. 
-Section~\ref{subsec2:noiseTolerance} investigates this phenomenon in more details.
+Section~\ref{subsec2:noiseTolerance} investigates this phenomenon in greater details.
 

### 2024-11-03 project1/nsSurvey.tex
new

@@
 
-A total of 6 nested simulation procedures are considered, namely the standard nested simulation procedure, the MLMC procedure, the regression-based, kernel smoothing-based, likelihood ratio-based, and kernel ridge regression-based nested simulation procedures.
+A total of 5 nested simulation procedures are considered, namely the standard nested simulation procedure, the regression-based, kernel smoothing-based, likelihood ratio-based, and kernel ridge regression-based nested simulation procedures.
 For the standard nested simulation procedure, the bootstrap-based budget allocation strategy from~\cite{zhang2021bootstrap} is implemented to estimate the optimal values of outer and inner simulation budgets.
@@
 Except for portfolio 5, 5 different asset dimensions are considered, i.e., $d = 1, 2, 5, 10, 20$.
-525 experimental settings that arise from an exhaustive combination of the above simulation procedures, risk measures, portfolios, and asset dimensions are generated.
-For each of the scenarios, the estimation of the risk measure is repeated \num{1000} times to obtain the empirical MSE of the corresponding estimator under a range of simulation budgets.
+525 experiment settings that arise from an exhaustive combination of the above simulation procedures, risk measures, portfolios, and asset dimensions are generated.
+For each experiment setting, the estimation of the risk measure is repeated \num{1000} times to obtain the empirical MSE of the corresponding estimator under a range of simulation budgets.
 The total simulation budget $\Gamma$ ranges from $\num{10000}$ to $\num{10240000}$ in a geometric progression with a common ratio of $2$.

### 2024-11-03 project2/nnMetamodels.tex
new

@@
     \item It avoids the vanishing gradient problem during training, which makes the LSTM easier to than the RNN.
-Figure~\ref{fig2:QQ_RNN} shows the quantile-quantile (QQ) plots between the \textbf{training} labels and the RNN predictions for two macro replications, where training of the latter is hindered by the vanishing gradient problem\footnote{A well-trained RNN stops early at around 300 training epochs, while an ill-trained RNN uses up all 1000 training epochs.}.
+Figure~\ref{fig2:QQ_RNN} shows the quantile-quantile (QQ) plots between the \textbf{training} labels and the RNN predictions for two macro replications, where training of the latter is hindered by the vanishing gradient problem.
     As a result, the half length of the 95\% confidence interval of the RNN's training error is much larger than all other metamodels.

### 2024-11-03 project3/draft.tex
new

@@
 In the evolving landscape of financial markets, insurance products such as VAs have gained significant interest due to their ability to provide both investment growth and guaranteed benefits. 
-Managing the risks associated with these products, especially in volatile market conditions, is a complex task that demands sophisticated financial modeling techniques. 
+Managing the risks associated with these products, especially in volatile market conditions, is a complex task that demands sophisticated financial modeling techniques like nested simulation.
+A standard nested simulation procedure involves running a large number of simulations to generate a dataset of scenario-wise contract losses.
+To address the computational burden, metamodeling techniques have been proposed, where a surrogate model approximates the outcomes of a more complex simulation. 
 Traditional machine learning models often struggle to capture the intricate nonlinear relationships and temporal dependencies inherent in financial data.
-To address the computational burden, metamodeling techniques have been proposed, where a simpler model approximates the outcomes of the more complex simulation. 
-In particular, deep neural networks (DNNs), and specifically LSTM networks, have been employed as metamodels to predict the outcomes of the inner simulations efficiently
+In particular, DNNs, and specifically LSTM networks, have been employed as metamodels to predict the outcomes of the inner simulations efficiently
 Chapter~\ref{chap:project2} introduces a nested simulation framework for dynamic hedging of VAs, where the inner simulation is approximated by an LSTM metamodel.
-It shows that crude RNN and LSTMs are well-suited for metamodeling Monte Carlo simulation of financial time series and can capture the long-term dependencies in the data.
+It shows that crude RNN and LSTMs are well-suited for metamodeling Monte Carlo simulation of financial time series and can capture the long-term dependencies in the simulation dataset.
 
@@
 Retraining neural network metamodels from scratch in response to every change is computationally inefficient and time-consuming.
-Moreover, financial markets are inherently dynamic, with frequent shifts in volatility, interest rates, and other risk factors~\citep{cont2001empirical}.
+Moreover, financial markets are inherently dynamic with frequent shifts in volatility, interest rates, and other risk factors~\citep{cont2001empirical}.
 Therefore, it is essential to develop methods that can rapidly adapt existing metamodels to new conditions without incurring the full computational cost of retraining.
-Transfer Learning offers a compelling solution to this problem by enabling the reuse of a pre-trained model on a new but related task~\citep{pan2009survey}.
-In the context of DNNs, transfer learning involves leveraging the knowledge acquired during training on one dataset to improve learning performance on a different dataset~\citep{yosinski2014transferable}.
+Transfer Learning (TL) offers a compelling solution to this problem by enabling the reuse of a pre-trained model on a new but related task~\citep{pan2009survey}.
+In the context of DNNs, TL involves leveraging the knowledge acquired during training on one dataset to improve learning performance on a different dataset~\citep{yosinski2014transferable}.
 This approach can significantly reduce training time and computational resources while enhancing model generalization.
@@
 
-In this chapter, we explore the application of transfer learning to the dynamic hedging of VAs using RNN and LSTM metamodels.
-We propose a novel transfer learning framework that accelerates the training of DNN metamodels for nested simulatiogn in a dynamic hedging problem.
+In this chapter, we explore the application of TL to the dynamic hedging of VAs using RNN and LSTM metamodels.
+We propose a novel TL framework that accelerates the training of DNN metamodels for nested simulation procecedures in dynamic hedging.
+This setting is particularly relevant for hedging problems, as insurance companies often underwrite new contracts under changing market conditions and actuarial assumptions.
+Fast adaptation of metamodels is necessarily for metamodel-based nested simulation procedures.
 Our approach involves pre-training an LSTM network on a large dataset of VA simulations and then fine-tuning it on a smaller dataset of new VA contracts.
-We evaluate the performance of the transfer learning framework on a real-world dataset of VA contracts and compare it with training the LSTM network from scratch.
+We evaluate the performance of the TL framework on a real-world dataset of VA contracts and compare it with training a LSTM metamodel from scratch.
 
@@
 Section~\ref{sec3:background} provides an overview of the dynamic hedging problem for VAs and the use of LSTM networks as metamodels in a nested simulation procedure.
-Section~\ref{sec3:transfer_learning} introduces the transfer learning framework for rapid adaptation of LSTM metamodels in dynamic hedging.
-Section~\ref{sec3:experiments} presents the experimental setup and results, comparing the performance of transfer learning with training from scratch.
+Section~\ref{sec3:transfer_learning} introduces the TL framework for rapid adaptation of LSTM metamodels in dynamic hedging.
+Section~\ref{sec3:experiments} presents the experimental setup and results, comparing the performance of TL with training from scratch.
 Finally, Section~\ref{sec3:conclusion} concludes the chapter and discusses future research directions.
@@
 
-Transfer learning (TL) is a machine learning paradigm where knowledge acquired from a source task is utilized to improve learning performance on a related target task.
+TL is a machine learning paradigm where knowledge acquired from a source task is utilized to improve learning performance on a related target task.
 One of the primary applications of TL in finance is asset price prediction. 
@@
 The low noise dataset generated by the standard nested simulation procedure in Section~\ref{sec2:numerical} is used to train the source LSTM metamodels.
-We consider TL to two types of target tasks: (1) the same contract but different underlying asset model, and (2) different contracts but the same asset model.
+We consider TL to two types of target tasks: 
+\begin{itemize}
+    \item the same contract but different underlying asset model, and
+    \item different contracts but the same asset model.
+\end{itemize}  
 Similar to Section~\ref{sec2:numerical}, we use the standard nested simulation procedure to generate the dataset for the source and target tasks.

### 2024-11-03 project2/nnMetamodels.tex
new

@@
 Let $\Gamma = MN$ be the simulation budget for the standard procedure, where each scenario receives $\frac{\Gamma}{M}$ inner replications.
-In the proposed two-stage procedure, suppose Stage 2 uses 1\% of the simulation budget, $\alpha = 95\%$, and $m=(1-\alpha)M$, then $99\%$ of the simulation budget is concentrated on $5\% M$ predicted tail scenarios in Stage 2.
+In the proposed two-stage procedure, suppose Stage 2 uses $1\%$ of the simulation budget, $\alpha = 95\%$, and $m=(1-\alpha)M$, then $99\%$ of the simulation budget is concentrated on $5\% M$ predicted tail scenarios in Stage 2.
 In other words, each predicted tail scenario receives $\frac{99\% \Gamma}{5\% M}$ inner replications, almost 20 times more than that in the standard procedure.
@@
 
-Figure~\ref{fig2:tailMatches} depicts the average percentage of correctly identified true tail scenarios\footnote{Each quantity is averaged over 50 macro replications.}  by different metamodels for different safety margins.
+Figure~\ref{fig2:tailMatches} depicts the average percentage of correctly identified true tail scenarios by different metamodels for different safety margins.
+Each quantity is averaged over 50 macro replications.
 The percentage of tail matches of the traditional regression metamodels are significantly lower than the ones of the neural networks.
 We see that a poor metamodel like the QPR identifies less than 40\% of the true tail scenario without any safety margin.
-In contrast, a good metamodel like the LSTM identifies more than 75\% of the true tail scenarios without any safety margin and more than the QPR metamodel does with 15\% of safety margin\footnote{The metamodel in~\cite{dang2020efficient} identifies 100\% of the true tail scenarios on with a 10\% safety margin for a GMAB contract.
+In contrast, a well-suited metamodel like the LSTM identifies more than 75\% of the true tail scenarios without any safety margin and more than the QPR metamodel does with 15\% of safety margin\footnote{The metamodel in~\cite{dang2020efficient} identifies 100\% of the true tail scenarios on with a 10\% safety margin for a GMAB contract.
 The GMAB contract is simpler than the GMWB contract, and the true tail scenarios are easier to identify. 

### 2024-11-03 project3/draft.tex
new

@@
 In contrast, Figure~\ref{subfig3-1:without} presents the results of training directly on the target task without pre-training on the source task.
-With $M_{\text{TA}} = 2,\!000$ samples, the LSTM metamodel struggles to learn the temporal dependencies and patterns in the target task.
-It leads to highly unstable training dynamics, with substantial fluctuations in the validation MSE.
+With only $M_{\text{TA}} = 2,\!000$ samples, the LSTM metamodel struggles to learn the temporal dependencies and patterns in the target task.
+It leads to highly unstable training dynamics with substantial fluctuations in the validation MSE.
 Learning without knowledge transfer leads poor generalization and extreme overfitting. 

### 2024-11-03 project2/nnMetamodels.tex
new

@@
 Since the first artificial neural network model~\citep{mcculloch1943logical} and the first algorithm for training a perceptron~\citep{rosenblatt1958perceptron}, especially after the introduction of backpropagation~\citep{rumelhart1985learning} and the growth of high-performance computing, the field of artificial neural network and deep learning in general has grown rapidly.
-Two specialized neural network architectures that are relevant to our study are recurrent neural networks (RNNs)~\citep{williams1989learning,sutskever2014sequence} and long-short-term memory (LSTM)~\citep{hochreiter1997long,chung2014empirical}, as In the field of actuarial science, a metamodel is commonly referred to as a proxy model.
+Two specialized neural network architectures that are relevant to our study are RNN~\citep{williams1989learning,sutskever2014sequence} and LSTM~\citep{hochreiter1997long,chung2014empirical}, as In the field of actuarial science, a metamodel is commonly referred to as a proxy model.
 Despite their success, DNN models are often criticized for their lack of transparency and interpretability, which hinders their adoption in financial and actuarial applications.
@@
 
-Five metamodels are considered in this experiment: multiple linear regression (MLR), quadratic polynomial regression (QPR) without interaction terms, feed-forward neural network (FNN), recurrent neural network (RNN), and long short-term memory (LSTM) network.
+Five metamodels are considered in this experiment: multiple linear regression (MLR), quadratic polynomial regression (QPR) without interaction terms, FNN, RNN, and LSTM network.
 MLR and QPR are considered as extensions of regression metamodels in the nested simulation literature.
 FNN is a generic neural network while RNN and LSTM are specialized models to accommodate the sequential structure of our time-series features.
-A $\tanh$ activation function is used for RNN and LSTM layers, and a Rectified Linear Unit (ReLU) activation function is used for the fully-connected layers.
+A $\tanh$ activation function is used for RNN and LSTM layers, and a ReLU activation function is used for the fully-connected layers.
 All neural network metamodels are trained by the Adam optimizer~\citep{kingma2014adam} with an initial learning rate of $0.001$ and an exponential learning rate decay schedule.
@@
 We see that the three DNN metamodels' have orders of magnitudes more trainable parameters than the two regression models.
-In machine-learning terminologies, the three DNN models have much higher \textit{model capacities}.
+In machine learning terminologies, the three DNN models have much higher \textit{model capacities}.
 
@@
     \midrule
-    MLR & N/A & $241$ & $0.707 (\pm 3.6 \times 10^{-4})$ & $0.877 (\pm 0.001)$ & $0.694 (\pm 0.000)$ \\
-    QPR & N/A & $481$ & $0.544 (\pm 0.000)$ & $0.636 (\pm 0.001)$ & $0.531 (\pm 0.000)$ \\
+    MLR & $\num{241}$ & $\num{241}$ & $0.707 (\pm 3.6 \times 10^{-4})$ & $0.877 (\pm 0.001)$ & $0.694 (\pm 0.000)$ \\
+    QPR & $\num{481}$ & $\num{481}$ & $0.544 (\pm 0.000)$ & $0.636 (\pm 0.001)$ & $0.531 (\pm 0.000)$ \\
     FNN & $240, 128, 16$ & $\num{35009}$ & $0.118 (\pm 0.001)$ & $0.247 (\pm 0.002)$ & $0.113 (\pm 0.001)$ \\
@@
 
-\footnotetext{Results of the well-trained RNN, where the ones suffers from the vanishing gradient issue are removed from the averages.}
+\footnotetext{Results of the well-trained RNN, where the ones suffers from the vanishing and exploding gradient issue are removed from the averages.}
 
-For each metamodel, 50 independent macro replications are run.
+For each metamodel, 100 independent macro replications are run.
 Each macro replication involves simulating a noisy dataset, separating it into training and test data, fitting a metamodel, and making predictions.
@@
 Figure~\ref{fig2:tailMatches} depicts the average percentage of correctly identified true tail scenarios by different metamodels for different safety margins.
-Each quantity is averaged over 50 macro replications.
+Each quantity is averaged over 100 macro replications.
 The percentage of tail matches of the traditional regression metamodels are significantly lower than the ones of the neural networks.

### 2024-11-03 project3/draft.tex
new

@@
 The metamodel trained on the GMMB with static lapse captures some features that are beneficial for the GMMB with dynamic lapse, which leads to a more stable training process.
-In Figure~\ref{subfig3-2:fromNolapse}, the metamodel needs to learn the effect of (1) whether lapse is present and (2) whether the lapse is dynamic.
+In Figure~\ref{subfig3-2:fromNolapse}, the metamodel needs to learn the effect of 
+\begin{itemize}
+    \item whether lapse is present and
+    \item whether the lapse is dynamic.
+\end{itemize}
 This learning process is more challenging.

### 2024-11-05 project2/nnMetamodels.tex
new

@@
 All neural network metamodels are trained by the Adam optimizer~\citep{kingma2014adam} with an initial learning rate of $0.001$ and an exponential learning rate decay schedule.
-FNN is trained with a dropout rate of 20\%.
-RNN and LSTM are trained with a dropout rate of 10\%.
+FNN is trained with a dropout rate of $20\%$.
+RNN and LSTM are trained with a dropout rate of $10\%$.
 The architectures and training settings are typical choices in the deep learning literature.
 The training labels are normalized to have zero mean and unit standard deviation.
-The architectures and the numbers of trainable parameters are shown in the first two columns of Table~\ref{tab:gmwb_arch}.
-We see that the three DNN metamodels' have orders of magnitudes more trainable parameters than the two regression models.
+The architectures and the numbers of trainable parameters are recorded in the first two columns of Table~\ref{tab:gmwb_arch}.
+We observe that the three DNN metamodels have orders of magnitudes more trainable parameters than the two traditional regression metamodels.
 In machine learning terminologies, the three DNN models have much higher \textit{model capacities}.
@@
 
-For each metamodel, 100 independent macro replications are run.
-Each macro replication involves simulating a noisy dataset, separating it into training and test data, fitting a metamodel, and making predictions.
+For each metamodel, \num{100} independent macro replications are run.
+Each macro replication involves simulating a noisy dataset, randomly separating it into training and test data, fitting a metamodel, and making predictions.
 The last three columns in Table~\ref{tab:gmwb_arch} display the average squared errors between the predicted losses and the losses (labels) in different datasets.
-The half lengths of their 95\% confidence interval of these quantities are also reported in parentheses.
+Training error, test error, and true error are the average squared errors between the predicted losses and the training labels, test labels, and true labels, respectively.
+The half lengths of their 95\% confidence intervals are also reported (in parentheses).
 We first observe that the two regression metamodels' errors are larger than those of three DNN models.
-This is because model capacities of the regression metamodels are too low to learn the complex dynamic hedging simulation model.
+This is because model capacities of the regression metamodels are too low to learn the training dataset.
+Succesful learning of the training dataset is a necessary condition for a metamodel to learn the dynamic hedging simulation model.
 All neural network metamodels have high model capcities comparing with the number of data points in the training set, i.e., $\num{90000}$.
@@
 In neural network literature, the number of trainable parameters is often much larger than the number of data points in the training set.
-AlexNet~\citep{krizhevsky2012imagenet}, a well-known convolutional neural network, has 60 million parameters and is trained on the ImageNet dataset with 1.2 million images.
-Other examples include generative pre-trained transformer models like BERT~\citep{devlin2018bert} and GPT-3~\citep{brown2020language}, which have billions of parameters and are trained on large-scale text corpora.
+AlexNet~\citep{krizhevsky2012imagenet}, a well-known convolutional neural network, has $60$ million trained parameters and is trained on the ImageNet dataset with only $1.2$ million sample images.
+Other examples include generative pre-trained transformer models like BERT~\citep{devlin2018bert} and GPT-3~\citep{brown2020language}, which have billions of trainable parameters and are trained on large-scale text corpora.
 The reason for not overfitting is still an open question in deep learning research.
-One possible explanation is that the optimization surface of DNNs is highly non-convex and has many local minima.
-As a result, given a good initialization, the optimization algorithm is likely to find a solution that generalizes well to unseen data.
+One of the explanations in the literature is that the optimization surface of DNNs is highly non-convex and has many local minima.
+Given a good initialization, the optimization algorithm is likely to find a solution that generalizes well to unseen data.
 
-There are significant differences among the three DNN models due to having different architectures.
-The FNN is a generic neural network, its test error is larger than the training error, which is a sign of over-fitting and poor generalization.
+There are significant differences among the three DNN models due to having different neural network architectures.
+The FNN is a generic neural network, its test error is much greater than the training error, which is a sign of over-fitting and poor generalization.
 In contrast, RNN and LSTM networks have recurrent strucutures and are designed to capture temporal relationship in the high-dimensional feature.
@@
     \item A LSTM introduces three gates that regulate the flow of information. 
-    These gates decide what information should be kept or discarded. This makes a LSTM more capcable of learning long-term dependencies. 
+    These gates decide what information should be kept or discarded. 
+    This makes a LSTM more capcable of learning long-term dependencies. 
     Since the feature in our dynamic hedging problem is a 240-dimensional time series, a LSTM is more suitable than a crude RNN.
-    The network architecture serves as a prior knowledge that guides the optimization algorithm to find a solution that generalizes well to unseen data, and it significantly impact the metamodel's performance.
+\end{enumerate}
+In summary, the network architecture serves as a prior knowledge that guides the optimization algorithm to find a solution that generalizes well to unseen data, and it significantly impact the metamodel's performance.
 It is important to choose a suitable architecture with a pre-set capacity that is large enough to learn the true feature-label relationship.
-\end{enumerate}
 
@@
 
-Recall that all three data sets are generated from the same simulation model, but the true data set is less noisy than the training and test data.
+Recall that all three data sets are generated from the same simulation model, but the true labels are less noisy than the training and test labels.
 Part of the training error is due to simulation noise, and this noise is lower in the true error.
-We observe that the two regression metamodels not only generalize to the test data poorly but also generalize to the true data poorly.
-In contrast, the DNN metamodels generalize better to the true data than to the test data.
+We observe that the two regression metamodels not only generalize to the test labels poorly but also generalize to the true labels poorly.
+In contrast, the DNN metamodels generalize better to the true labels than to the test labels.
+The test labels contain more simulation noise than the true labels.
+This is a sign of the regression metamodels' inability to learn the true feature-label relationship rather than merely over-fitting to the simulation noise.
+In practical applications, the true labels are not available.
+However, analyzing the quality of fit on the true labels in a simulation environment offers a unique opportunity to understand the metamodels' true ability of learning.
 Figure~\ref{fig2:QQ_REG} and Figure~\ref{fig2:QQ_NN} shows the QQ plots between the \textbf{true} labels and the predicted losses for the regression metamodels and the neural network metamodels, respectively.
@@
 Attempts to further improve the regression metamodels by adding interaction terms or higher-order terms do not improve the fit.
-Having 240 features, feature engineering for regression metamodels is not a trivial task and is highly dependent on the simulation model. 
-As a result, the regression metamodels are not flexible enough to capture the complex feature-label relationship in the dynamic hedging simulation model.
+With 240 features, feature engineering (i.e, variable selection) for regression metamodels is not a trivial task and is highly dependent on the simulation model. 
+As a result, the attempts to improve the traditional regression metamodels are not successful.
+The regression metamodels are not flexible enough to capture the complex feature-label relationship in the dynamic hedging simulation model.
 

### 2024-11-05 project2/nnMetamodels.tex
new

@@
 Section~\ref{sec2:metamodel2Stage} proposes an efficient two-stage nested simulation procedure that uses DNNs as metamodels to help reduce simulation budget by only performing computations on identified tail scenarios.
-Section~\ref{sec2:metamodel1Stage} proposes a one-stage nested simulation procedure that estimates risk measures directly with metamodel predictions.
+Section~\ref{sec2:metamodel1Stage} proposes a single-stage nested simulation procedure that estimates risk measures directly with metamodel predictions.
 Section~\ref{sec2:numerical} demonstrates the efficiency of DNN metamodels and examines error tolerance of two LSTM metamodels with different numbers of trainable parameters. 
@@
 
-Similar to~\cite{dang2020efficient}, the proposed two-stage procedure in Algorithm ~\ref{alg2:twoStageProcedure} uses the metamodel predictions to identify the predicted tail scenario set in Stage 1.
+Similar to~\cite{dang2020efficient}, the proposed two-stage procedure in Algorithm ~\ref{alg2:twoStageProcedure} uses the metamodel predictions to identify the predicted tail scenario set in stage 1.
 However, different from their fixed-budget simulation design, we attempt to achieve a target accuracy.
-Specifically, in Stage 2 we propose using a standard procedure with the same number of inner replications, $N$, as a benchmark procedure.
+Specifically, in stage 2 we propose using a standard procedure with the same number of inner replications, $N$, as a benchmark procedure.
 There are two different types of experiment designs for nested simulation procedures: fixed-budget design and fixed-accuracy design.
@@
 Let $\Gamma = MN$ be the simulation budget for the standard procedure, where each scenario receives $\frac{\Gamma}{M}$ inner replications.
-In the proposed two-stage procedure, suppose Stage 2 uses $1\%$ of the simulation budget, $\alpha = 95\%$, and $m=(1-\alpha)M$, then $99\%$ of the simulation budget is concentrated on $5\% M$ predicted tail scenarios in Stage 2.
+In the proposed two-stage procedure, suppose stage 2 uses $1\%$ of the simulation budget, $\alpha = 95\%$, and $m=(1-\alpha)M$, then $99\%$ of the simulation budget is concentrated on $5\% M$ predicted tail scenarios in stage 2.
 In other words, each predicted tail scenario receives $\frac{99\% \Gamma}{5\% M}$ inner replications, almost 20 times more than that in the standard procedure.
@@
 One other reason for this fixed-accuracy design is to investigate whether DNN metamodels trained with much noisier labels can identify true tail scenarios with similar accuracy as the standard procedure.
-The size of the predicted tail scenario set in Stage 1, $m$, is an important experiment design parameter that affects the correct identification of true tail scenarios and ultimately affects the estimation accuracy for CVaR.
-Clearly, there is a lower bound $m \geq (1-\alpha)M$ because the $\alpha$-CVaR is estimated by the average of $(1-\alpha)M$ largest losses at the end of Stage 2.
+The size of the predicted tail scenario set in stage 1, $m$, is an important experiment design parameter that affects the correct identification of true tail scenarios and ultimately affects the estimation accuracy for CVaR.
+Clearly, there is a lower bound $m \geq (1-\alpha)M$ because the $\alpha$-CVaR is estimated by the average of $(1-\alpha)M$ largest losses at the end of stage 2.
 For ease of reference, we call the additional percentage of predicted tail scenarios above this lower bound, i.e., $\epsilon = \frac{m - (1-\alpha)M}{M}$, as a \textit{safety margin}.
-On one hand, large $\epsilon$ is not desirable because it increases computations in Stage 2.
-On the other hand, $\epsilon$ should be set reasonably large so more true tail scenarios are included in the the predicted tail scenario set $\widehat{\tail}_{m}^{PD}$ and are ultimately included in $\widehat{\tail}_{(1-\alpha )M}$ at the end of Stage 2.
+On one hand, large $\epsilon$ is not desirable because it increases computations in stage 2.
+On the other hand, $\epsilon$ should be set reasonably large so more true tail scenarios are included in the the predicted tail scenario set $\widehat{\tail}_{m}^{PD}$ and are ultimately included in $\widehat{\tail}_{(1-\alpha )M}$ at the end of stage 2.
 The selection of $m$ is highly dependent on the choice of the metamodel.
-Due to the simulation errors and approximation error in the metamodel in Stage 1, we do not expect perfect match between the true tail scenario set $\tail_{k}$ and the predicted tail scenario set $\widehat{\tail}_{k}^{PD}$ for any size $k$.
-This means that we should not set $m$ at its lower bound: Some safety margin $\epsilon M$ should be added to the predicted tail scenario set, i.e., $m = (1-\alpha )M + \epsilon M$, to increase the likelihood that $\tail_{k} \subseteq \widehat{\tail}_{m}^{PD}$ and that the true tail scenarios are included in estimating $\alpha$-CVaR at the end of Stage 2.
+Due to the simulation errors and approximation error in the metamodel in stage 1, we do not expect perfect match between the true tail scenario set $\tail_{k}$ and the predicted tail scenario set $\widehat{\tail}_{k}^{PD}$ for any size $k$.
+This means that we should not set $m$ at its lower bound: Some safety margin $\epsilon M$ should be added to the predicted tail scenario set, i.e., $m = (1-\alpha )M + \epsilon M$, to increase the likelihood that $\tail_{k} \subseteq \widehat{\tail}_{m}^{PD}$ and that the true tail scenarios are included in estimating $\alpha$-CVaR at the end of stage 2.
 The choice of safety margin $\epsilon$ is not trivial, and it should be set based on the metamodel's accuracy in identifying true tail scenarios.
@@
 \begin{enumerate}
-    \item The single-stage procedure is expected to be more efficient than the two-stage procedure because it does not require the running the standard procedure in Stage 2.
+    \item The single-stage procedure is expected to be more efficient than the two-stage procedure because it does not require the running the standard procedure in stage 2.
     \item The safety margin $\epsilon$ is not needed in the single-stage procedure.
@@
 In Stage 1 of the proposed procedure, we first run inner simulations with $N'=100$ inner replications for each of the $M=\num{100000}$ outer scenarios.
-So, Stage 1's simulation budget is $10\%$ of the standard procedure's.
+So, stage 1's simulation budget is $10\%$ of the standard procedure's.
 The resulting feature-label pairs $\{(\bS^{(i)}, \Lhat_i): i=1,\ldots,M\}$ is used for training different  metamodels.
 Specifically, following the convention in machine learning research, we split this dataset into three parts: The training, validation, and test sets have $\num{90000}$, $\num{5000}$, and $\num{5000}$ data points (90\%, 5\%, and 5\% of the dataset), respectively.
-At the end of Stage 1, $m$ predicted tail scenarios, are identified by the trained metamodels.
-In Stage 2, $N=\num{1000}$ inner replications are run for all predicted tail scenarios.
+At the end of stage 1, $m$ predicted tail scenarios, are identified by the trained metamodels.
+In stage 2, $N=\num{1000}$ inner replications are run for all predicted tail scenarios.
 Stage 2's simulation budget is $\frac{m}{M}$ of the standard procedure's.
@@
 In summary, the network architecture serves as a prior knowledge that guides the optimization algorithm to find a solution that generalizes well to unseen data, and it significantly impact the metamodel's performance.
-It is important to choose a suitable architecture with a pre-set capacity that is large enough to learn the true feature-label relationship.
+It is important to choose a \textit{suitable} architecture with a pre-set capacity that is large enough to learn the true feature-label relationship.
 
@@
 
-Recall that all three data sets are generated from the same simulation model, but the true labels are less noisy than the training and test labels.
+Recall that all three datasets are generated from the same simulation model, but the true labels contain much less simulation noise than the training and test labels.
 Part of the training error is due to simulation noise, and this noise is lower in the true error.
@@
 Between the two regression metamodels, the QPR metamodel has a slightly better fit for larger losses.
-Nevertheless, both regression metamodels have poor fits to the true data, and their fit on the tail is particularly undesirable.
+Nevertheless, the predictions of both regression metamodels are far from the true labels, and their fit on the tail is particularly undesirable.
 The poor fit on the tail hinders the regression metamodels' ability to identify true tail scenarios and ultimately leads to poor CVaR estimates.
@@
 Attempts to further improve the regression metamodels by adding interaction terms or higher-order terms do not improve the fit.
-With 240 features, feature engineering (i.e, variable selection) for regression metamodels is not a trivial task and is highly dependent on the simulation model. 
-As a result, the attempts to improve the traditional regression metamodels are not successful.
+With 240 features, feature engineering (i.e., variable selection) for regression metamodels is not a trivial task and is highly dependent on the simulation procedure. 
+As a result, our attempts to improve the traditional regression metamodels are not successful.
 The regression metamodels are not flexible enough to capture the complex feature-label relationship in the dynamic hedging simulation model.
@@
 By employing the standard nested simulation procedure in Algorithm~\ref{alg2:standardProcedure} as a data generator, we gain the ability to manipulate the noise level through adjusting the number of inner replications while keeping the same simulation procedure.
-As a result, this approach provides a controlled environment to examine the impact of label noise on neural network model.
+This approach provides a controlled environment to examine the impact of label noise on neural network models.
 It allows us to generate our true dataset that approximates the true hedging losses with a high degree of precision, and, as a result, it enables us to explore the crucial question of whether deep learning models are capable of learning the true feature-label relationship from noisy training labels.
@@
 
-In our proposed two-stage procedure, the metamodel is used to identify the predicted tail scenario set, on which the standard nested simulation procedure is run in Stage 2 to estimate the $95\%$-CVaR.
+In our proposed two-stage procedure, the metamodel is used to identify the predicted tail scenario set, on which the standard nested simulation procedure is run in stage 2 to estimate the $95\%$-CVaR.
 An accurate identification of the true tail scenarios is crucial.
@@
 
-Figure~\ref{fig2:tailMatches} depicts the average percentage of correctly identified true tail scenarios by different metamodels for different safety margins.
-Each quantity is averaged over 100 macro replications.
-The percentage of tail matches of the traditional regression metamodels are significantly lower than the ones of the neural networks.
+Figure~\ref{fig2:tailMatches} depicts the average percentage of correctly identified true tail scenarios by different metamodels for increasing safety margins.
+Each quantity is averaged over $100$ macro replications.
+For a fixed safety margin, the percentage of tail matches of the traditional regression metamodels are significantly lower than the ones of the neural networks.
 We see that a poor metamodel like the QPR identifies less than 40\% of the true tail scenario without any safety margin.
-In contrast, a well-suited metamodel like the LSTM identifies more than 75\% of the true tail scenarios without any safety margin and more than the QPR metamodel does with 15\% of safety margin\footnote{The metamodel in~\cite{dang2020efficient} identifies 100\% of the true tail scenarios on with a 10\% safety margin for a GMAB contract.
+In contrast, a well-suited metamodel like the LSTM identifies more than 75\% of the true tail scenarios without any safety margin and more than the QPR metamodel does with 15\% of safety margin\footnote{The metamodel in~\cite{dang2020efficient} identifies 100\% of the true tail scenarios on with a $10\%$ safety margin for a GMAB contract.
 The GMAB contract is simpler than the GMWB contract, and the true tail scenarios are easier to identify. 
-For a GMAB, our LSTM metamodel identifies 100\% of the true tail scenarios with a 2.5\% safety margin}.
+For a GMAB, our LSTM metamodel identifies $100\%$ of the true tail scenarios with a $2.5\%$ safety margin}.
 The RNN metamodel suffers from the vanishing gradient problem during training. 
@@
 Lastly, we return to our original goal of estimating the 95\%-CVaR of the dynamic hedging error.
-Figure~\ref{fig2:CVaR95} shows the 95\%-CVaR estimates for all five metamodels with different safety margins, averaged over 50 macro replications.
+Figure~\ref{fig2:CVaR95} shows the 95\%-CVaR estimates for all five metamodels with different safety margins, averaged over 100 macro replications.
 Figure~\ref{subfig2:ZoomedSafetyMargin} is a zoomed version of Figure~\ref{subfig2:AllSafetyMargin}.
@@
 By concentrating the simulation budget on the predicted tail scenarios, the two-stage procedure with the LSTM metamodel is able to achieve a similar accuracy as the standard procedure with a much smaller simulation budget.
-As the percentage of correctly identified tails approaches 100\%, the two-stage procedure's CVaR estimates does not converge to the true value but to the standard procedure's estimate.
+As the percentage of correctly identified tails approaches $100\%$, the two-stage procedure's CVaR estimates does not converge to the true CVaR but to the standard procedure's estimate.
 This is because the two-stage procedure's CVaR estimates are based on the standard procedure's estimates on the predicted tail scenarios, and the standard procedure's estimates themselves are also noisy.
@@
 \begin{enumerate}
-    \item   Compared to that of the regular LSTM, the metamodel predictions of high-capacity LSTM align more closely with the true losses when trained on the low-noise dataset.
+    \item   When trained on the low-noise dataset, the metamodel predictions of high-capacity LSTM align more closely with the true labels than the regular LSTM.
     This is expected because the high-capacity LSTM has more trainable parameters and is able to learn more complex relationships better when the noise level is low.
@@
 
-To further test the sensitivity of a LSTM metamodel and provide a more comprehensive picture of the noise tolerance of DNN models, we conduct a sensitivity analysis on the noise tolerance of the regular LSTM metamodel by varying the numbers of outer scenarios ($M$) and inner replications ($N$) used to generate the training data.
+To further test the sensitivity of a LSTM metamodel and provide a more comprehensive view of the noise tolerance of DNN models, we conduct a sensitivity analysis on the noise tolerance of the regular LSTM metamodel by varying the numbers of outer scenarios ($M$) and inner replications ($N$) used to generate the training dataset.
 The number of outer scenarios corresponds to the number of data points in the training dataset, and the number of inner replications controls the noise level in the training labels.
@@
         \toprule
-                            & $N=1$ & $N=10$  & $N=100$ & $N=\num{1000}$\\
+                            & $N=\num{1}$ & $N=\num{10}$  & $N=\num{100}$ & $N=\num{1000}$\\
         \midrule
-        $M = 100$           & $1.139$ & $0.229$ & $0.167$ & $0.158$ \\
+        $M = \num{100}$      & $1.139$ & $0.229$ & $0.167$ & $0.158$ \\
         $M = \num{1000}$     & $0.559$ & $0.173$ & $0.123$ & $0.127$ \\
@@
         \toprule
-                          & $N=1$ & $N=10$  & $N=100$ & $N=\num{1000}$\\
+                          & $N=\num{1}$ & $N=\num{10}$  & $N=\num{100}$ & $N=\num{1000}$\\
         \midrule
-        $M = 100$           & $0.764$ & $0.408$ & $0.131$ & $0.087$ \\
+        $M = \num{100}$      & $0.764$ & $0.408$ & $0.131$ & $0.087$ \\
         $M = \num{1000}$     & $0.878$ & $0.367$ & $0.156$ & $0.087$ \\
@@
 The last rows of Table~\ref{tab2:lstm_sens} and Table~\ref{tab2:hicaplstm_sens} show the performance of the regular and high capacity LSTM metamodels trained with $M=\num{100000}$ training labels with different noise levels.
-We observe that an increasing $N$ reduces the MSE, but the reduction is not significant for a regular LSTM when $N$ is larger than $10$.
-For the high-capacity LSTM, the MSE is significantly reduced when $N$ is increased from $1$ to $100$, but the reduction is not significant when $N$ is increased from $100$ to $\num{1000}$.
+We observe that an increasing $N$ reduces the MSE, but the reduction is not significant for a regular LSTM when $N$ is larger than $\num{10}$.
+For the high-capacity LSTM, the MSE is significantly reduced when $N$ is increased from $\num{1}$ to $\num{100}$, but the reduction is not significant when $N$ is increased from $\num{100}$ to $\num{1000}$.
 Another way to interpret the results in Table~\ref{tab2:lstm_sens} is to compare the MSEs for the same budget of $\Gamma = M \times N$. 
@@
 The accuracy and robustness of the LSTM metamodels motivate us to propose a single-stage procedure that uses the metamodel predictions to estimate the CVaR directly. 
-Instead of relying on the standard nested simulation procedure in Stage 2, the single-stage procedure is more efficient and extends to estimating other risk measures that require knowledge of the entire loss distribution.
+Instead of relying on the standard nested simulation procedure in stage 2, the single-stage procedure is more efficient and extends to estimating other risk measures that require knowledge of the entire loss distribution.
 In this section, we compare the single-stage procedure to the two-stage procedure and the standard procedure in estimating the $95\%$-CVaR of the hedging losses for GMWB.
@@
 Figure~\ref{fig2:CVaRsingleStage} shows the boxplots of the 95\%-CVaR estimates of the single-stage procedure with different metamodels and compares them to the two-stage procedure and the standard procedure.
-The two-stage procedure uses the same simulation budget as the single-stage procedure in Stage 1 with extra budget for extensive inner simulation on the predicted tail scenarios in Stage 2.
+The two-stage procedure uses the same simulation budget as the single-stage procedure in stage 1 with extra budget for extensive inner simulation on the predicted tail scenarios in stage 2.
 The metamodel with the best performance in the two-stage procedure is chosen, and the safety margin is set to 0\%.
@@
 By avoiding the calibration of the safety margin, it is more straight-forward to implement and is more efficient than the two-stage procedure.
-For a two-stage procedure with a 0\% safety margin, the extra computational cost is from the extensive inner simulation in Stage 2.
-On 4 20-core Intel Xeon Gold 6230 processors, Stage 2 of the two-stage procedure takes 30 minutes to run with parallel processing, while the 95\% confidence interval of training time of the high-capacity LSTM metamodel is $(19.64 \pm 0.94)$ minutes on a Nvidia RTX 3060 Ti GPU.
+For a two-stage procedure with a 0\% safety margin, the extra computational cost is from the extensive inner simulation in stage 2.
+On 4 20-core Intel Xeon Gold 6230 processors, stage 2 of the two-stage procedure takes 30 minutes to run with parallel processing, while the 95\% confidence interval of training time of the high-capacity LSTM metamodel is $(19.64 \pm 0.94)$ minutes on a Nvidia RTX 3060 Ti GPU.
 While the accuracy of the two-stage procedure is highly dependent on the safety margin, increasing the safety margin introduces extra computational cost.

### 2024-11-09 introduction.tex
new

@@
 
-The training of neural networks involves adjusting the trainable parameters of the network to minimize the loss function.
-The loss function is typically the MSE between the predicted labels and the training labels.
-The training process aims to find the optimal parameters that minimize the loss function.
+The training of neural networks involves adjusting the trainable parameters of the network to minimize the loss function, which quantifies the error between the predictions and labels.
+The training process aims to find the optimal parameters that minimize this error.
 The most common approach is to use gradient descent methods with backpropagation, which is an efficient method for computing the gradients of the loss function with respect to the trainable parameters.
@@
 To address these issues, various adaptive learning rate methods have been proposed.
-The most popular approach is Adam, which adjusts the learning rate during training to improve convergence speed and stability~\citep{kingma2014adam}.
+The most popular approach is Adam, which is a SGD algorithm that adjusts the learning rate during training to improve convergence speed and stability~\citep{kingma2014adam}.
 
@@
 It involves monitoring the model's performance on a validation set and stopping training when the performance no longer improves~\citep{prechelt2002early}.
-This helps prevent overfitting by stopping training before the model begins to overfit to noise in the data.
+This helps prevent over-fitting by stopping training before the model begins to fit to noise in the data.
 
-In simulation studies, the noise in the data can be controlled by the sample size.
+Evaluation of the performance of a neural network is challenging due to the absence of analytical tools.
+Existing machine learning literature addresses this challenge by splitting the data into three parts: training set, validation set, and test set.
+The training set is used to train the model, the validation set is used to tune the model hyper-parameters, and the test set is used to evaluate how well the model generalizes to unseen data.
+The test set is not used during training and is only used for evaluation.
+
+Under-fitting occurs when the training error is high, which means that the neural network fails to capture the underlying patterns in the training data.
+Over-fitting occurs when the neural network fits to noise in the training data and cannot generalize to unseen data.
+In machine learning literature, over-fitting is often quantified as the gap between the training error and the test error~\citep{bishop2006pattern}.
+During training, as the test dataset is not used, this quantity is estimated using the validation set.
+If the validation error is high compared to the training error, the model is likely over-fitting to the training data.
 
@@
 This independence assumption limits their effectiveness in modeling financial time series, where temporal dependencies play a critical role. 
-The stylized facts of financial time series, such as volatility clustering, fat tails, and autocorrelation, are challenging to capture with traditional feedforward neural networks due to the absence of memory in the model~\citep{cont2001empirical}.
+The stylized facts of financial time series, such as volatility clustering, fat tails, and autocorrelation, are challenging to capture with traditional FNNs due to the absence of memory in the model~\citep{cont2001empirical}.
 
-To overcome the limitations of FNNs in handling sequential data, recurrent neural networks (RNNs) were introduced.
-In an RNN, the hidden state at each time step is a function of both the current input and the hidden state from the previous time step~\citep{elman1990finding}:
+To overcome the limitations of FNNs in handling sequential input, recurrent neural networks (RNNs) were introduced.
+In a RNN, the hidden state at each time step is a function of both the current input and the hidden state from the previous time period~\citep{elman1990finding}:
 
@@
 Figure~\ref{subfig:lstm} shows the architecture of an LSTM network.
-The gating mechanisms in LSTMs effectively mitigate the vanishing and exploding gradient problem by regulating the flow of information through the network.
+The gating mechanisms in LSTM networks effectively mitigate the vanishing and exploding gradient problem by regulating the flow of information through the network.
 The input gate $i_t$ controls the flow of information into the cell state $c_t$, the forget gate $f_t$ regulates the retention of information in the cell state, and the output gate $o_t$ determines the information passed to the hidden state $h_t$.

### 2024-11-09 project2/nnMetamodels.tex
new

@@
     \end{itemize}
-    The first procedure uses a metamodel to identify a set of potential tail scenarios on which computations are performed in the second stage, while the second procedure uses metamodel predictions to estimate risk measures directly.
+    The first procedure uses a metamodel to identify a set of potential tail scenarios on which computations are performed in stage 2, while the second procedure uses metamodel predictions to estimate risk measures directly.
     Our numerical results show that DNN metamodels can identify the tail scenarios accurately and so the proposed procedures can estimate tail risk measures with similar accuracy while, at the same time, using less simulation budget.
@@
 
-Similar to~\cite{dang2020efficient}, the proposed two-stage procedure in Algorithm ~\ref{alg2:twoStageProcedure} uses the metamodel predictions to identify the predicted tail scenario set in stage 1.
+Similar to~\cite{dang2020efficient}, the proposed two-stage procedure in Algorithm~\ref{alg2:twoStageProcedure} uses the metamodel predictions to identify the predicted tail scenario set in stage 1.
 However, different from their fixed-budget simulation design, we attempt to achieve a target accuracy.
@@
     It can be naturally adapted to estimate risk measures that require the knowing of the entire loss distribution, such as the standard deviation or the squared tracking error.
-    In our numerical experiments, we will compare the single-stage procedure to the two-stage procedure and the standard procedure in estimating the $\alpha$-CVaR for a larger range of $\alpha$.
+    Even for CVaR, the two-stage procedure become less attactive for an increased level.
+    In our numerical experiments, we will compare the single-stage procedure to the two-stage procedure and the standard procedure in estimating the $\alpha$-CVaR for a lower $\alpha$.
 \end{enumerate}
@@
 The withdrawal rate for GMWB is $0.375\%$ per month.
-To make our examples more realistic, the VAs are also subject to a dynamic lapse model with the following key features:
+To make our examples more realistic, the VAs are also subject to a dynamic lapse model with the following key features~\citep{naic2021}:
 \begin{enumerate}
@@
 
-The risk-free rate is 0.2\% per period and the underlying asset $S_t$ is modeled by a regime-switching geometric Brownian motion with parameters specified in Table~\ref{tab:regime_params}.
+The risk-free rate is $0.2\%$ per month and the underlying asset $S_t$ is modeled by a regime-switching geometric Brownian motion with parameters specified in Table~\ref{tab:regime_params}.
 
@@
         \midrule
-        Risk-free rate & 0.002 \\
-        Mean return for regime 1  & 0.0085 \\
-        Mean return for regime 2   & -0.0200 \\
-        Standard deviation for regime 1  & 0.035 \\
-        Standard deviation for regime 2  & 0.080 \\
-        Transition probability from regime 1  & 0.04 \\
-        Transition probability from regime 2  & 0.20 \\
+        Risk-free rate & $0.002$ \\
+        Mean return for regime 1  & $0.0085$ \\
+        Mean return for regime 2   & $-0.0200$ \\
+        Standard deviation for regime 1  & $0.035$ \\
+        Standard deviation for regime 2  & $0.080$ \\
+        Transition probability from regime 1  & $0.04$ \\
+        Transition probability from regime 2  & $0.20$ \\
         \bottomrule
@@
 To compare the numerical performances of different simulation procedures, we create a benchmark dataset with a large-scale nested simulation: We first simulate $M=\num{100000}$ outer scenarios, i.e., $240$-periods stock paths $\bS^{(1)},\ldots,\bS^{(M)}$ under $\mathbb{P}$ and used these outer scenarios in all further experiments.
-Note that the 5\% tail scenario set includes $\num{5000}$ scenarios.
+Note that the $5\%$ tail scenario set includes $\num{5000}$ scenarios.
 As the hedging losses for these scenarios cannot be calculated analytically, we run inner simulations with a large number of replications, $N=\num{100000}$, conditional on each of the $M$ scenarios.
@@
 
-We compare our two-stage procedure to a standard nested simulation procedure that runs $N=\num{1000}$ inner replications for each of the $M=\num{100000}$ outer scenarios.
-In Stage 1 of the proposed procedure, we first run inner simulations with $N'=100$ inner replications for each of the $M=\num{100000}$ outer scenarios.
+We compare our two-stage procedure to a benchmark standard nested simulation procedure that runs $N=\num{1000}$ inner replications for each of the $M=\num{100000}$ outer scenarios.
+In stage 1 of the proposed procedure, we first run inner simulations with $N'=100$ inner replications for each of the $M=\num{100000}$ outer scenarios.
 So, stage 1's simulation budget is $10\%$ of the standard procedure's.
 The resulting feature-label pairs $\{(\bS^{(i)}, \Lhat_i): i=1,\ldots,M\}$ is used for training different  metamodels.
-Specifically, following the convention in machine learning research, we split this dataset into three parts: The training, validation, and test sets have $\num{90000}$, $\num{5000}$, and $\num{5000}$ data points (90\%, 5\%, and 5\% of the dataset), respectively.
+Specifically, following the convention in machine learning literature, we split this dataset into three parts: The training, validation, and test sets have $\num{90000}$, $\num{5000}$, and $\num{5000}$ data points ($90\%$, $5\%$, and $5\%$ of the dataset), respectively.
 At the end of stage 1, $m$ predicted tail scenarios, are identified by the trained metamodels.
 In stage 2, $N=\num{1000}$ inner replications are run for all predicted tail scenarios.
-Stage 2's simulation budget is $\frac{m}{M}$ of the standard procedure's.
-In short, the two-stage procedure uses $15\% - 30\%$ of the standard procedure's budget for a safety margin between $0\% - 15\%$.
+This is the same number of replications as the benchmark standard procedure.
+Stage 2's simulation budget is $\frac{m}{M}$ of the benchmark standard procedure's.
+In short, the two-stage procedure uses $15\% - 30\%$ of the benchmark procedure's budget for a safety margin between $0\% - 15\%$.
 
 Five metamodels are considered in this experiment: multiple linear regression (MLR), quadratic polynomial regression (QPR) without interaction terms, FNN, RNN, and LSTM network.
-MLR and QPR are considered as extensions of regression metamodels in the nested simulation literature.
+MLR and QPR are two common metamodels in the simulation literature, and their implemention is straightfoward in our simulation setting.
 FNN is a generic neural network while RNN and LSTM are specialized models to accommodate the sequential structure of our time-series features.
@@
 In machine learning terminologies, the three DNN models have much higher \textit{model capacities}.
+From another point of view, MLR and QPR are two neural networks with no hidden layers. 
+For a traditional regression model, the numbers of neurons in its input layer equals to the cardinality of its regression bases.
+Treating regression metamodels as shallow neural networks allows for direct comparisons with DNNs.
 
@@
     \midrule
-    MLR & $\num{241}$ & $\num{241}$ & $0.707 (\pm 3.6 \times 10^{-4})$ & $0.877 (\pm 0.001)$ & $0.694 (\pm 0.000)$ \\
-    QPR & $\num{481}$ & $\num{481}$ & $0.544 (\pm 0.000)$ & $0.636 (\pm 0.001)$ & $0.531 (\pm 0.000)$ \\
+    MLR & $\num{240}$ & $\num{241}$ & $0.707 (\pm 3.6 \times 10^{-4})$ & $0.877 (\pm 0.001)$ & $0.694 (\pm 0.000)$ \\
+    QPR & $\num{480}$ & $\num{481}$ & $0.544 (\pm 0.000)$ & $0.636 (\pm 0.001)$ & $0.531 (\pm 0.000)$ \\
     FNN & $240, 128, 16$ & $\num{35009}$ & $0.118 (\pm 0.001)$ & $0.247 (\pm 0.002)$ & $0.113 (\pm 0.001)$ \\
@@
 
-\footnotetext{Results of the well-trained RNN, where the ones suffers from the vanishing and exploding gradient issue are removed from the averages.}
+\footnotetext{This row summarizes the results of the well-trained RNN, where the ones suffers from the vanishing and exploding gradient issue are removed from the averages.}
 
@@
 Each macro replication involves simulating a noisy dataset, randomly separating it into training and test data, fitting a metamodel, and making predictions.
-The last three columns in Table~\ref{tab:gmwb_arch} display the average squared errors between the predicted losses and the losses (labels) in different datasets.
-Training error, test error, and true error are the average squared errors between the predicted losses and the training labels, test labels, and true labels, respectively.
-The half lengths of their 95\% confidence intervals are also reported (in parentheses).
-We first observe that the two regression metamodels' errors are larger than those of three DNN models.
-This is because model capacities of the regression metamodels are too low to learn the training dataset.
-Succesful learning of the training dataset is a necessary condition for a metamodel to learn the dynamic hedging simulation model.
+The last three columns in Table~\ref{tab:gmwb_arch} display the average squared errors between the metamodel predictions and the loss labels for different datasets.
+Training error, test error, and true error are the average squared errors between the metamodel predictions and the training labels, test labels, and true labels, respectively.
+The half lengths of their $95\%$ confidence bands are also reported in parentheses.
+We first observe that the two regression metamodels have high training errors.
+This is a sign of under-fitting.
+Model capacities of the regression metamodels are too low to learn the training dataset.
+A successful learning on the training dataset is a necessary condition for a metamodel to generalize to the true simulation model.
 All neural network metamodels have high model capcities comparing with the number of data points in the training set, i.e., $\num{90000}$.
-This is not a huge concern for the DNNs.
-In neural network literature, the number of trainable parameters is often much larger than the number of data points in the training set.
-AlexNet~\citep{krizhevsky2012imagenet}, a well-known convolutional neural network, has $60$ million trained parameters and is trained on the ImageNet dataset with only $1.2$ million sample images.
+Empirically, this is not a huge concern for the DNNs.
+In neural network literature, the number of trainable parameters is often much larger than the number of training samples.
+AlexNet~\citep{krizhevsky2012imagenet}, a well-known convolutional neural network, has $\num{60}$ million trained parameters and is trained on the ImageNet dataset with only $1.2$ million sample images.
 Other examples include generative pre-trained transformer models like BERT~\citep{devlin2018bert} and GPT-3~\citep{brown2020language}, which have billions of trainable parameters and are trained on large-scale text corpora.
-The reason for not overfitting is still an open question in deep learning research.
+The reason for not over-fitting when the number of trainable parameters is much larger than the number of training samples is still an open question in deep learning research.
 One of the explanations in the literature is that the optimization surface of DNNs is highly non-convex and has many local minima.
@@
 There are significant differences among the three DNN models due to having different neural network architectures.
+Their model capacities are intentionally set to be similar to each other for a fair comparison.
 The FNN is a generic neural network, its test error is much greater than the training error, which is a sign of over-fitting and poor generalization.
@@
 \begin{enumerate}
-    \item It avoids the vanishing gradient problem during training, which makes the LSTM easier to than the RNN.
+    \item It avoids the vanishing gradient problem during training, which makes the LSTM network easier to than the RNN.
 Figure~\ref{fig2:QQ_RNN} shows the quantile-quantile (QQ) plots between the \textbf{training} labels and the RNN predictions for two macro replications, where training of the latter is hindered by the vanishing gradient problem.
-    As a result, the half length of the 95\% confidence interval of the RNN's training error is much larger than all other metamodels.
+    As a result, the half length of the $95\%$ confidence band of the RNN's training error is much larger than all other metamodels.
 The last row of Table~\ref{tab:gmwb_arch} shows the average squared errors of the good RNN metamodels that are successfully trained.
-    Removing the RNN metamodels that are ill-trained, the average squared errors of the RNN metamodels are lower than those of the FNN, but the half lengths of their 95\% confidence intervals are larger than those of the FNN.
+    Removing the RNN metamodels that are ill-trained, the average squared errors of the RNN metamodels are lower than those of the FNN, but the half lengths of their $95\%$ confidence bands are larger than those of the FNN.
     This suggests that the RNN is more sensitive to noise in stochastic gradient descent than the FNN.
@@
     These gates decide what information should be kept or discarded. 
-    This makes a LSTM more capcable of learning long-term dependencies. 
-    Since the feature in our dynamic hedging problem is a 240-dimensional time series, a LSTM is more suitable than a crude RNN.
+    This makes a LSTM network more capcable of learning long-term dependencies. 
+    Since the feature in our dynamic hedging problem is a 240-dimensional time series, a LSTM network is more suitable than a crude RNN.
 \end{enumerate}
-In summary, the network architecture serves as a prior knowledge that guides the optimization algorithm to find a solution that generalizes well to unseen data, and it significantly impact the metamodel's performance.
-It is important to choose a \textit{suitable} architecture with a pre-set capacity that is large enough to learn the true feature-label relationship.
+In summary, the network depth ensures successful learning of the training dataset, and the network architecture serves as a prior knowledge that guides the optimization algorithm to find a solution that generalizes well to unseen data.
+They are both crucial for the metamodels' performance.
+It is important to choose a \textit{suitable} architecture with a pre-set capacity that is large enough to learn the training dataset and generalize to the true feature-label relationship.
 
@@
 Recall that all three datasets are generated from the same simulation model, but the true labels contain much less simulation noise than the training and test labels.
-Part of the training error is due to simulation noise, and this noise is lower in the true error.
-We observe that the two regression metamodels not only generalize to the test labels poorly but also generalize to the true labels poorly.
-In contrast, the DNN metamodels generalize better to the true labels than to the test labels.
+Part of the training error is from the simulation noise, and this noise is much less reflected in the true error.
+We observe that the two regression metamodels is under-fitting with high training errors. 
+They also have low test and true errors, which indicates poor generalization.
+In contrast, the DNN metamodels have lower errors.
+More specifically, they generalize better to the true labels than to the test labels.
 The test labels contain more simulation noise than the true labels.
-This is a sign of the regression metamodels' inability to learn the true feature-label relationship rather than merely over-fitting to the simulation noise.
+This is a sign of the regression metamodels' inability to learn the true feature-label relationship rather than merely over-fitting to the simulation noise in the training labels.
 In practical applications, the true labels are not available.
@@
 Attempts to further improve the regression metamodels by adding interaction terms or higher-order terms do not improve the fit.
-With 240 features, feature engineering (i.e., variable selection) for regression metamodels is not a trivial task and is highly dependent on the simulation procedure. 
+Feature engineering (i.e., variable selection) for regression metamodels is not a trivial task and is highly dependent on the simulation procedure. 
+Having $240$ time-series features further complicates this issue.
 As a result, our attempts to improve the traditional regression metamodels are not successful.
@@
 We see that a poor metamodel like the QPR identifies less than 40\% of the true tail scenario without any safety margin.
-In contrast, a well-suited metamodel like the LSTM identifies more than 75\% of the true tail scenarios without any safety margin and more than the QPR metamodel does with 15\% of safety margin\footnote{The metamodel in~\cite{dang2020efficient} identifies 100\% of the true tail scenarios on with a $10\%$ safety margin for a GMAB contract.
+In contrast, a well-suited metamodel like the LSTM identifies more than 75\% of the true tail scenarios without any safety margin and more than the QPR metamodel does with $15\%$ of safety margin\footnote{The metamodel in~\cite{dang2020efficient} identifies $100\%$ of the true tail scenarios on with a $10\%$ safety margin for a GMAB contract.
 The GMAB contract is simpler than the GMWB contract, and the true tail scenarios are easier to identify. 
@@
     \end{subfigure}
-    \caption{Average 95\%-CVaR estimates by different procedures. Right figure is a zoomed-in version of left figure.} 
+    \caption{Average $95\%$-CVaR estimates by different procedures. Right figure is a zoomed-in version of left figure.} 
     \label{fig2:CVaR95}
@@
 
-Lastly, we return to our original goal of estimating the 95\%-CVaR of the dynamic hedging error.
-Figure~\ref{fig2:CVaR95} shows the 95\%-CVaR estimates for all five metamodels with different safety margins, averaged over 100 macro replications.
+Lastly, we return to our original goal of estimating the $95\%$-CVaR of the dynamic hedging error.
+Figure~\ref{fig2:CVaR95} shows the $95\%$-CVaR estimates for all five metamodels with different safety margins, averaged over $100$ macro replications.
 Figure~\ref{subfig2:ZoomedSafetyMargin} is a zoomed version of Figure~\ref{subfig2:AllSafetyMargin}.
@@
 In our numerical experiments, we are able to use Monte Carlo simulation generate a true dataset that approximates the true hedging losses with a high degree of precision, and, as a result, we are able to explore the crucial question of whether deep learning models are capable of learning the true feature-label relationship from noisy training labels.
-In this section, we treat the standard nested simulation procedure as a data generator and examine the noise tolerance of LSTM metamodels by varying the numbers of outer scenarios ($M$) and inner replications ($N$) used to generate the training data.
+In this section, we treat the standard nested simulation procedure as a data generator and examine the noise tolerance of LSTM metamodels by varying the numbers of outer scenarios ($M$) and inner replications ($N$) used to generate the training samples.
 The number of outer scenarios corresponds to the number of feature-label pairs in the training dataset, and the number of inner replications controls the noise level in the training labels.
@@
 
-The maximum number of data points in the training dataset is set to $M = \num{100000}$.
-The training dataset is split into training and test sets with a 90\%-10\% ratio.
+The maximum number of training samples is set to $M = \num{100000}$.
+The training samples are split into training and test sets with a $90\%$-$10\%$ ratio.
 The true labels are generated by running the standard nested simulation procedure with $N=\num{100000}$ inner replications for each of the $\num{100000}$ outer scenarios.
@@
 
-The first two rows of Table~\ref{tab:lstm_arch} shows the average squared errors and the half widths of their 95\% confidence intervals between the metamodel predictions and the labels in the training dataset and the true dataset.
+The first two rows of Table~\ref{tab:lstm_arch} shows the average squared errors and the half widths of their $95\%$ confidence intervals between the metamodel predictions and the labels in the training dataset and the true dataset.
 The test errors are included as a practical measure of the metamodels' generalization ability.
@@
 In most cases, a high-capacity metamodel is better.
-Nevertheless, in extreme circumstances when the noise level is too high, using a high capacity metamodel leads to severe overfitting and poor generalization.
+Nevertheless, in extreme circumstances when the noise level is too high, using a high capacity metamodel leads to severe over-fitting and poor generalization.
 Hence, domain knowledge about the right architecture for the task and knowledge about the noise level in the training labels are beneficial for choosing the right metamodel.
@@
 They measure the metamodel's overall prediction accuracy.
-The p-values of all quantities are less than $10^{-5}$, indicating that the correlations are statistically significant.
 
@@
         \toprule
-                          & $N=1$        & $N=10$        & $N=100$       & $N=\num{1000}$ \\
+                          & $N=\num{1}$        & $N=\num{10}$        & $N=\num{100}$       & $N=\num{1000}$ \\
         \midrule
-        $M = 100$         & 0.638 (0.881) & 0.875 (0.915) & 0.896 (0.903) & 0.937 (0.941) \\
+        $M = \num{100}$         & 0.638 (0.881) & 0.875 (0.915) & 0.896 (0.903) & 0.937 (0.941) \\
         $M = \num{1000}$   & 0.722 (0.768) & 0.899 (0.908) & 0.886 (0.891) & 0.922 (0.927) \\
@@
 Consistent with the results in Table~\ref{tab2:lstm_sens}, the Spearman correlation of the LSTM metamodel predictions with the true losses is insensitive to the number of inner replications, especially when $M$ is large.
-The Pearson correlation coefficients are significantly lower for $N=1$ than the other $N$ values.
+The Pearson correlation coefficients are significantly lower for $N=\num{1}$ than the other $N$ values.
 
@@
 The heatmap is generated by subtracting the Pearson correlation coefficients from the Spearman correlation.
-We observe that Spearman correlation coefficients are not significantly different from the Pearson correlation coefficients for any $N$ larger than $10$. 
+We observe that Spearman correlation coefficients are not significantly different from the Pearson correlation coefficients for any $N$ larger than $\num{10}$. 
 This is a strong evidence that the LSTM metamodel is not only able to effectively rank the scenarios by their true losses, but also able to make accurate loss predictions.
@@
 The two-stage procedure uses the same simulation budget as the single-stage procedure in stage 1 with extra budget for extensive inner simulation on the predicted tail scenarios in stage 2.
-The metamodel with the best performance in the two-stage procedure is chosen, and the safety margin is set to 0\%.
+The metamodel with the best performance in the two-stage procedure is chosen, and the safety margin is set to $0\%$.
 The standard procedure shown in Figure~\ref{fig2:CVaRsingleStage} uses the noisy loss labels in the training dataset to estimate the CVaR directly, which uses the same simulation budget as the single-stage procedure.
@@
 By avoiding the calibration of the safety margin, it is more straight-forward to implement and is more efficient than the two-stage procedure.
-For a two-stage procedure with a 0\% safety margin, the extra computational cost is from the extensive inner simulation in stage 2.
-On 4 20-core Intel Xeon Gold 6230 processors, stage 2 of the two-stage procedure takes 30 minutes to run with parallel processing, while the 95\% confidence interval of training time of the high-capacity LSTM metamodel is $(19.64 \pm 0.94)$ minutes on a Nvidia RTX 3060 Ti GPU.
+For a two-stage procedure with a $0\%$ safety margin, the extra computational cost is from the extensive inner simulation in stage 2.
+On $4$ $20$-core Intel Xeon Gold $\num{6230}$ processors, stage 2 of the two-stage procedure takes $30$ minutes to run with parallel processing, while the $95\%$ confidence interval of training time of the high-capacity LSTM metamodel is $(19.64 \pm 0.94)$ minutes on a Nvidia RTX $\num{3060}$ Ti GPU.
 While the accuracy of the two-stage procedure is highly dependent on the safety margin, increasing the safety margin introduces extra computational cost.
@@
 Figure~\ref{fig2:mnConvergence} shows the log-log plots of the RRMSE between the LSTM metamodel CVaR predictions and the true CVaR against the simulation budget.
-The left figure shows the empirical convergence of the RRMSE for increasing inner replications with a fixed number of outer scenarios ($M=\num{100000}$), and the right figure shows the empirical convergence of the RRMSE for increasing outer scenarios with a fixed number of inner replications ($N=10$).
+The left figure shows the empirical convergence of the RRMSE for increasing inner replications with a fixed number of outer scenarios ($M=\num{100000}$), and the right figure shows the empirical convergence of the RRMSE for increasing outer scenarios with a fixed number of inner replications ($N=\num{10}$).
 Due to computational constraints, we are not able to run the two-stage procedure and the standard procedure with more outer scenarios or more inner replications, therefore the comparison between the single-stage procedure is only available up to $M = \num{100000}$ and $N = \num{1000}$.
@@
 For an LSTM metamodel, increasing the data quality of the training labels has diminishing returns, which is consistent with the results in Figure~\ref{fig2:mnConvergence}.
-For an increasing number of inner replications with fixed number of outer scenarios, the RRMSE cease to decrease after reaching $N = 100$. 
-More specfically, when the quality of the training labels is fixed at $N = 10$, the CVaR estimator of single-stage procedure with a LSTM metamodel converge roughly in the order of $\mathcal{O}(M^{\frac{2}{3}})$.
+For an increasing number of inner replications with fixed number of outer scenarios, the RRMSE cease to decrease after reaching $N = \num{100}$. 
+More specfically, when the quality of the training labels is fixed at $N = \num{10}$, the CVaR estimator of single-stage procedure with a LSTM metamodel converge roughly in the order of $\mathcal{O}(M^{\frac{2}{3}})$.
 This observation resonates with the convergence rate of a regression-based nested simulation procedure in~\cite{broadie2015risk}.
@@
 Furthermore, our numerical results provide evidences for adopting DNN metamodels in Monte Carlo simulation for risk management tasks.
-Through our systematic study of the noise tolerance of DNN metamodels, we address regulatory concerns by showing that a LSTM metamodel is resilient to a high level of noise in training labels and is able to make accurate predictions.
+Through our systematic empirical study of the noise tolerance of DNN metamodels, we address regulatory concerns by showing that a LSTM metamodel is resilient to a high level of noise in training labels and is able to make accurate predictions.
 A possible future research direction is to apply DNN metamodels in other financial risk management tasks that requires complex nested simulation with high-dimensional outer scenarios.
@@
 
-In this chapter, we have demonstrated the potential of DNN metamodels in nested simulation procedures for delta hedging of variable annuity contracts and have shown that they can be used to estimate risk measures with high accuracy and efficiency.
-We have assumed a zero transaction cost model for our monthly rebalancing.
-In practice, transaction costs can be significant and can affect the hedging strategy.
-In the next chapter, we will extend our study to include transaction costs in the hedging strategy and investigate the impact of transaction costs on the hedging performance and the risk measures of the hedging error.
-We will also explore the use of DNN models as reinforcement learning agents to optimize the hedging strategy by directly interacting with the financial market and maximize the hedging performance.
+In this chapter, we have demonstrated the potential of DNN metamodels to estimate risk measures with high accuracy and efficiency when simulation data is abundant.
+In practice, simulation data is often scarce for new market conditions and new insurance products.
+DNN metamodels are known to suffer from over-fitting when the number of training samples is limited.
+In the next chapter, we will extend our study to transfer learning and show that DNN metamodels trained on a existing VA contract can be transferred to a new VA contract with different market conditions.
+We hypothesize that the DNN metamodel will generalize well to the new VA contract, and the computational savings from transfer learning will be significant.

### 2024-11-14 project2/nnMetamodels.tex
new

@@
 
-We compare our two-stage procedure to a benchmark standard nested simulation procedure that runs $N=\num{1000}$ inner replications for each of the $M=\num{100000}$ outer scenarios.
-In stage 1 of the proposed procedure, we first run inner simulations with $N'=100$ inner replications for each of the $M=\num{100000}$ outer scenarios.
-So, stage 1's simulation budget is $10\%$ of the standard procedure's.
-The resulting feature-label pairs $\{(\bS^{(i)}, \Lhat_i): i=1,\ldots,M\}$ is used for training different  metamodels.
-Specifically, following the convention in machine learning literature, we split this dataset into three parts: The training, validation, and test sets have $\num{90000}$, $\num{5000}$, and $\num{5000}$ data points ($90\%$, $5\%$, and $5\%$ of the dataset), respectively.
-At the end of stage 1, $m$ predicted tail scenarios, are identified by the trained metamodels.
-In stage 2, $N=\num{1000}$ inner replications are run for all predicted tail scenarios.
-This is the same number of replications as the benchmark standard procedure.
-Stage 2's simulation budget is $\frac{m}{M}$ of the benchmark standard procedure's.
-In short, the two-stage procedure uses $15\% - 30\%$ of the benchmark procedure's budget for a safety margin between $0\% - 15\%$.
+In our experiments, the standard nested simulation procedure is mainly used in three ways.
+\begin{enumerate}
+    \item   The true losses and the true $95\%$-CVaR are estimated using a standard nested simulation procedure that runs $N=\num{100000}$ inner replications for each of the $M=\num{100000}$ outer scenarios.
+    \item   A benchmark estimator of the $95\%$-CVaR is generated using $N=\num{1000}$ for each of the $M=\num{100000}$ outer scenarios.
+    \item   The training data for our metamodels is generated using $N=\num{100}$ for $M=\num{100000}$.
+    The value of $M$ and $N$ are subject to change in our other numerical experiments.
+\end{enumerate}
 
@@
 All neural network metamodels are trained by the Adam optimizer~\citep{kingma2014adam} with an initial learning rate of $0.001$ and an exponential learning rate decay schedule.
-FNN is trained with a dropout rate of $20\%$.
-RNN and LSTM are trained with a dropout rate of $10\%$.
+All DNN metamodels are trained with a dropout rate of $10\%$.
 The architectures and training settings are typical choices in the deep learning literature.
@@
 We observe that the three DNN metamodels have orders of magnitudes more trainable parameters than the two traditional regression metamodels.
-In machine learning terminologies, the three DNN models have much higher \textit{model capacities}.
-From another point of view, MLR and QPR are two neural networks with no hidden layers. 
-For a traditional regression model, the numbers of neurons in its input layer equals to the cardinality of its regression bases.
-Treating regression metamodels as shallow neural networks allows for direct comparisons with DNNs.
+In machine learning terminologies, the three DNN metamodels have much higher \textit{model capacities}.
+From a neural network of view, MLR and QPR are two neural networks with no hidden layers. 
+For a traditional regression metamodel, the numbers of neurons in its input layer equals to the cardinality of its regression bases.
+Treating a regression as a shallow neural network allows for direct comparisons with DNNs.
 
+% Fill this table with new results
 \begin{table}[ht!]
@@
     \footnotesize
-    \begin{tabular}{lccccc}
+    \begin{tabular}{lcccc}
     \toprule
-    \textbf{Model} & \textbf{\makecell{Layer size}} & \textbf{\makecell{Capacity}} & \textbf{Training error} & \textbf{Test error} & \textbf{True error}\\
+    \textbf{Metamodel} & \textbf{\makecell{Capacity}} & \textbf{Training error} & \textbf{Test error} & \textbf{True error}\\
     \midrule
-    MLR & $\num{240}$ & $\num{241}$ & $0.707 (\pm 3.6 \times 10^{-4})$ & $0.877 (\pm 0.001)$ & $0.694 (\pm 0.000)$ \\
-    QPR & $\num{480}$ & $\num{481}$ & $0.544 (\pm 0.000)$ & $0.636 (\pm 0.001)$ & $0.531 (\pm 0.000)$ \\
-    FNN & $240, 128, 16$ & $\num{35009}$ & $0.118 (\pm 0.001)$ & $0.247 (\pm 0.002)$ & $0.113 (\pm 0.001)$ \\
-    RNN & $(240, 32), (240, 4), 32$ & $\num{32021}$ & $0.132 (\pm 0.008)$ & $0.137 (\pm 0.008)$ & $0.119 (\pm 0.008)$ \\
-    LSTM & $(240, 32), (240, 4), 32$ & $\num{35729}$ & $0.075 (\pm 0.004)$ & $0.079 (\pm 0.005)$ & $0.063 (\pm 0.004)$ \\
-    RNN$^*$\footnotemark & $(240, 32), (240, 4), 32$ & $\num{32021}$ & $0.109 (\pm 0.005)$ & $0.128 (\pm 0.005)$ & $0.109 (\pm 0.005)$ \\
+    MLR & $\num{241}$ & $0.706 (\pm 8.34\times 10^{-4})$ & $0.713 (\pm 2.67 \times 10^{-2})$ & $0.706 (\pm 3.44 \times 10^{-4})$ \\
+    QPR & $\num{481}$ & $0.543 (\pm 8.27\times 10^{-4})$ & $0.554 (\pm 2.32 \times 10^{-2})$ & $0.544 (\pm 4.12\times 10^{-4})$ \\
+    FNN & $\num{35009}$ & $0.129 (\pm 5.95\times 10^{-3})$ & $0.240 (\pm 9.82 \times 10^{-3})$ & $0.132 (\pm 5.82\times 10^{-3})$ \\
+    RNN & $\num{32021}$ & $0.132 (\pm 0.008)$ & $0.137 (\pm 0.008)$ & $0.119 (\pm 0.008)$ \\
+    LSTM & $\num{35729}$ & $0.075 (\pm 0.004)$ & $0.079 (\pm 0.005)$ & $0.063 (\pm 0.004)$ \\
+    RNN$^*$\footnotemark & $\num{32021}$ & $0.109 (\pm 0.005)$ & $0.128 (\pm 0.005)$ & $0.109 (\pm 0.005)$ \\
     \bottomrule
@@
 
-\footnotetext{This row summarizes the results of the well-trained RNN, where the ones suffers from the vanishing and exploding gradient issue are removed from the averages.}
+\footnotetext{This row summarizes the results of the well-trained RNN, where the ones suffers from the vanishing gradient issue are removed from the averages.}
+
+\textcolor{red}{Need to collect the result for RNN and LSTM}
 
@@
 Given a good initialization, the optimization algorithm is likely to find a solution that generalizes well to unseen data.
+Another explanation is that most existing DNN models have specific architectures that make them less prone to over-fitting.
+For example, a convolutional neural network (CNN) is specifically designed to capture the spatial structure in image data.
+Unlike a FNN, not all neurons are connected to all neurons in the previous layer.
+This architecture serves as prior knowledge and a form of regularization that make CNNs less prone to over-fitting.
 
-There are significant differences among the three DNN models due to having different neural network architectures.
+In our experiments, there are significant differences among the three DNN models due to having different neural network architectures.
 Their model capacities are intentionally set to be similar to each other for a fair comparison.
@@
     These gates decide what information should be kept or discarded.
-    This makes a LSTM network more capcable of learning long-term dependencies. 
+    For detailed discussion on the LSTM network, please refer to Section~\ref{subsec:LSTM}.
+    This gating mechanism makes a LSTM network more capable of learning long-term dependencies. 
     Since the feature in our dynamic hedging problem is a 240-dimensional time series, a LSTM network is more suitable than a crude RNN.
 \end{enumerate}
-In summary, the network depth ensures successful learning of the training dataset, and the network architecture serves as a prior knowledge that guides the optimization algorithm to find a solution that generalizes well to unseen data.
+In summary, the network depth ensures successful learning of the training dataset, and the network architecture serves as 
+\begin{enumerate}
+    \item regularization that prevents over-fitting, and 
+    \item a prior knowledge that guides the optimization algorithm to find a solution that generalizes well to unseen data.
+\end{enumerate}
 They are both crucial for the metamodels' performance.
@@
     \begin{subfigure}{0.48\textwidth}
-        \includegraphics[width=\textwidth]{./project2/figures/qqPlots/rnnGood.png}
+        \includegraphics[width=\textwidth]{./project2/figures/2a_QQ_good_training.png}
         \caption{A good RNN metamodel}
@@
     \begin{subfigure}{0.48\textwidth}
-        \includegraphics[width=\textwidth]{./project2/figures/qqPlots/rnnBad.png}
+        \includegraphics[width=\textwidth]{./project2/figures/2b_QQ_bad_training.png}
         \caption{A bad RNN metamodel}
@@
 However, analyzing the quality of fit on the true labels in a simulation environment offers a unique opportunity to understand the metamodels' true ability of learning.
-Figure~\ref{fig2:QQ_REG} and Figure~\ref{fig2:QQ_NN} shows the QQ plots between the \textbf{true} labels and the predicted losses for the regression metamodels and the neural network metamodels, respectively.
+Figure~\ref{fig2:QQ_REG} and Figure~\ref{fig2:QQ_NN} shows the QQ plots between the \textbf{true} loss labels and the predicted losses for the regression metamodels and the neural network metamodels, respectively.
 
@@
 Comparing with the MSE table in Table~\ref{tab:gmwb_arch} that summarizes the overall fit, QQ plots offer a closer look at the metamodels' performance on different parts of the loss distribution.
-Figure~\ref{fig2:QQ_REG} show that the regression metamodels' predictions are far from the true losses, especially on the tails.
+Figure~\ref{fig2:QQ_REG} show the regression metamodel predictions and the loss labels in the true dataset.
 Between the two regression metamodels, the QPR metamodel has a slightly better fit for larger losses.
@@
 The FNN has a better fit than the regression metamodels, but it still has a poor fit on the tails.
-We observe that the LSTM metamodels' QQ-plots closely follow that 45-degree line.
+We observe that the LSTM metamodels' QQ-plots closely follow the $45$-degree line.
 Again, these metamodels are trained on noisy data, so the good fit to the true data should not be taken for granted.
@@
 The LSTM metamodels' ability to learn the true feature-label relationship is crucial for the two-stage procedure to identify true tail scenarios and produce accurate CVaR estimates.
+Section~\ref{subsec2:noiseTolerance} discusses LSTM metamodels in more details regarding their sensitivity to data quality and quantity.
+We aim to provide numerical evidence and provide insights on the DNN metamodels' noise tolerance.
 
 \subsection{Two-Stage Procedure} \label{subsec:twoStageProcedure}
+
+We compare our two-stage procedure to a benchmark standard nested simulation procedure that runs $N=\num{1000}$ inner replications for each of the $M=\num{100000}$ outer scenarios.
+In stage 1 of the proposed procedure, we first run inner simulations with $N'=100$ inner replications for each of the $M=\num{100000}$ outer scenarios.
+So, stage 1's simulation budget is $10\%$ of the standard procedure's.
+The resulting feature-label pairs $\{(\bS^{(i)}, \Lhat_i): i=1,\ldots,M\}$ is used for training different  metamodels.
+Specifically, following the convention in machine learning literature, we split this dataset into three parts: The training, validation, and test sets have $\num{90000}$, $\num{5000}$, and $\num{5000}$ samples ($90\%$, $5\%$, and $5\%$ of the dataset), respectively.
+At the end of stage 1, $m$ predicted tail scenarios, are identified by the trained metamodels.
+In stage 2, $N=\num{1000}$ inner replications are run for all predicted tail scenarios.
+This is the same number of replications as the benchmark standard procedure.
+Stage 2's simulation budget is $\frac{m}{M}$ of the benchmark standard procedure's.
+In short, the two-stage procedure uses $15\% - 30\%$ of the benchmark procedure's budget for a safety margin between $0\% - 15\%$.
+Analyzing the two stages separately, the simulation budget for stage 1 is $10\%$ of the benchmark procedure's.
+Stage 2 uses $5\%$ to $20\%$ of the simulation budget of the benchmark procedure for a safety margin between $0\% - 15\%$.
 
@@
 
+\textcolor{red}{Need to separate the bad RNN from the good RNN for Figure~\ref{fig2:tailMatches}.}
+
 Figure~\ref{fig2:tailMatches} depicts the average percentage of correctly identified true tail scenarios by different metamodels for increasing safety margins.
@@
 For a fixed safety margin, the percentage of tail matches of the traditional regression metamodels are significantly lower than the ones of the neural networks.
-We see that a poor metamodel like the QPR identifies less than 40\% of the true tail scenario without any safety margin.
-In contrast, a well-suited metamodel like the LSTM identifies more than 75\% of the true tail scenarios without any safety margin and more than the QPR metamodel does with $15\%$ of safety margin\footnote{The metamodel in~\cite{dang2020efficient} identifies $100\%$ of the true tail scenarios on with a $10\%$ safety margin for a GMAB contract.
+We see that a poor metamodel like the QPR identifies less than $40\%$ of the true tail scenario without any safety margin.
+In contrast, a well-suited metamodel like the LSTM identifies more than $75\%$ of the true tail scenarios without any safety margin and more than the QPR metamodel does with $15\%$ of safety margin\footnote{The metamodel in~\cite{dang2020efficient} identifies $100\%$ of the true tail scenarios on with a $10\%$ safety margin for a GMAB contract.
 The GMAB contract is simpler than the GMWB contract, and the true tail scenarios are easier to identify. 
@@
 Otherwise, the two-stage procedure will offer no computational advantage in simulation budget over the standard procedure.
-The LSTM metamodel can reaches similar percentage with a 5\% safety margin.
-This indicates that the LSTM metamodel should be able to reach the same level of accuracy as the standard procedure with only 20\% of the simulation budget.
+The LSTM metamodel can reaches similar percentage with a $5\%$ safety margin.
+This indicates that the LSTM metamodel should be able to reach the same level of accuracy as the standard procedure with only $20\%$ of the simulation budget.
 
@@
         \includegraphics[width=\textwidth]{./project2/figures/CVaR/allLN.png}
-        \caption{Safety margin 0\% - 15\%.}
+        \caption{Safety margin $0\%$ - $15\%$.}
         \label{subfig2:AllSafetyMargin}
@@
         \includegraphics[width=\textwidth]{./project2/figures/CVaR/zoomedLN.png}
-        \caption{Safety margin 7.5\% - 15\%.}
+        \caption{Safety margin $7.5\%$ - $15\%$.}
         \label{subfig2:ZoomedSafetyMargin}
@@
 
+\textcolor{red}{Need to separate the bad RNN from the good RNN for Figure~\ref{fig2:CVaR95}.}
 Lastly, we return to our original goal of estimating the $95\%$-CVaR of the dynamic hedging error.
@@
 The first two rows of Table~\ref{tab:lstm_arch} shows the average squared errors and the half widths of their $95\%$ confidence intervals between the metamodel predictions and the labels in the training dataset and the true dataset.
-The test errors are included as a practical measure of the metamodels' generalization ability.
+The test errors are included as a practical measure of the metamodels' generalization ability to unseen noisy samples.
 For this particular experiment, we are more interested in the true errors, which measure the metamodels' ability to learn the true feature-label relationship from the low-noise, medium-noise, and high-noise datasets.
@@
 They measure the metamodel's overall prediction accuracy.
+Our previous numerical experiments illustrated in Figure~\ref{fig2:tailMatches} have shown that the LSTM metamodel predictions have high \textit{Spearman} correlation with the true labels for the combination $M=\num{100000}$ and $N=\num{100}$.
+We intend to examine if LSTM predictions also have high \textit{Pearson} correlation with the true labels.
+A high \textit{Pearson} correlation suggests the possibility of using LSTM predictions to estimate risk measures directly.
 
@@
 
-Consistent with the results in Table~\ref{tab2:lstm_sens}, the Spearman correlation of the LSTM metamodel predictions with the true losses is insensitive to the number of inner replications, especially when $M$ is large.
+Consistent with our previous numerical experiments, the Spearman correlations of a high-capacity LSTM is high for a moderate simulation budget. 
+For $M= \num{100000}$, the Spearman correlation is insensitive to $N$.
+This finding supports further budget savings for our two-stage procedure.
+In stage 1, we can lower $N$ from $\num{100}$ to $\num{10}$ without compromising on tail scenario preditions. 
+Table
+
+For an entry of Table~\ref{tab2:lstm_corr}, the total simulation budget $\Gamma = M N$. 
+Entries on the same off-diagonal all have the same $\Gamma$.
 The Pearson correlation coefficients are significantly lower for $N=\num{1}$ than the other $N$ values.
@@
 This is a strong evidence that the LSTM metamodel is not only able to effectively rank the scenarios by their true losses, but also able to make accurate loss predictions.
-Instead of using the LSTM metamodel only for ranking in a two-stage procedure, LSTM's ability to cut through a moderate level of noise in training labels encourages us to use its predictions to estimate the CVaR directly.
+Instead of using the LSTM metamodel only for classifying tail scenarios in a two-stage procedure, LSTM's ability to cut through a moderate level of noise in training labels encourages us to use its predictions to estimate the CVaR directly.
 
@@
 \end{figure}
+
+\textcolor{red}{The $N=1$ plot is not valid}
 

### 2024-11-14 uw-ethesis-frontpgs.tex
new

@@
         \Huge
-        {\bf Resilient Machine Learning Approaches to Risk Evaluation and Hedging in Financial Portfolios and Variable Annuities}
+        {\bf Resilient Machine Learning Approaches for Fast Risk Evaluation and Management in Financial Portfolios and Variable Annuities}
 
@@
 
-I would like to thank Professor Mingbin Feng and Professor Tony Wirjanto for their valuable support. They have patiently helped me through my journey as a Ph.D. student.  
+I would like to thank Professor Mingbin Feng and Professor Tony Wirjanto for their valuable support. 
+They have patiently helped me through my research journey.
+I am forever grateful for my true best friends, who have supported me during the most difficult times.
+
 \cleardoublepage

### 2024-11-15 project2/nnMetamodels.tex
new

@@
 Specifically, following the convention in machine learning literature, we split this dataset into three parts: The training, validation, and test sets have $\num{90000}$, $\num{5000}$, and $\num{5000}$ samples ($90\%$, $5\%$, and $5\%$ of the dataset), respectively.
-At the end of stage 1, $m$ predicted tail scenarios, are identified by the trained metamodels.
+At the end of stage 1, $m$ predicted tail scenarios are identified by the trained metamodels.
 In stage 2, $N=\num{1000}$ inner replications are run for all predicted tail scenarios.
@@
 In a two-stage procedure, metamodels' overall prediction errors measured by the MSEs in Table~\ref{tab:gmwb_arch} are not the determining factor, but their ability to effectively rank the scenarios by their \textbf{true} losses is most critical in producing accurate CVaR estimates.
+A metamodel that uses less safety margin to rank can save simulation budget in stage 2.
 
@@
 For a fixed safety margin, the percentage of tail matches of the traditional regression metamodels are significantly lower than the ones of the neural networks.
-We see that a poor metamodel like the QPR identifies less than $40\%$ of the true tail scenario without any safety margin.
+We observe that a poor metamodel like the QPR identifies less than $40\%$ of the true tail scenario without any safety margin.
 In contrast, a well-suited metamodel like the LSTM identifies more than $75\%$ of the true tail scenarios without any safety margin and more than the QPR metamodel does with $15\%$ of safety margin\footnote{The metamodel in~\cite{dang2020efficient} identifies $100\%$ of the true tail scenarios on with a $10\%$ safety margin for a GMAB contract.

### 2024-11-18 project2/nnMetamodels.tex
new figs

@@
     FNN & $\num{35009}$ & $0.129 (\pm 5.95\times 10^{-3})$ & $0.240 (\pm 9.82 \times 10^{-3})$ & $0.132 (\pm 5.82\times 10^{-3})$ \\
-    RNN & $\num{32021}$ & $0.132 (\pm 0.008)$ & $0.137 (\pm 0.008)$ & $0.119 (\pm 0.008)$ \\
-    LSTM & $\num{35729}$ & $0.075 (\pm 0.004)$ & $0.079 (\pm 0.005)$ & $0.063 (\pm 0.004)$ \\
-    RNN$^*$\footnotemark & $\num{32021}$ & $0.109 (\pm 0.005)$ & $0.128 (\pm 0.005)$ & $0.109 (\pm 0.005)$ \\
+    RNN & $\num{32021}$ & $0.132 (\pm 7.53\times 10^{-3})$ & $0.137 (\pm 7.62\times 10^{-3})$ & $0.119 (\pm 7.51\times 10^{-3})$ \\
+    LSTM & $\num{35729}$ & $0.075 (\pm 4.48\times 10^{-3})$  & $0.079 (\pm 5.35\times 10^{-3})$ & $0.063 (\pm 4.43\times 10^{-3})$ \\
+    RNN$^*$\footnotemark & $\num{32021}$ & $0.109 (\pm 5.20\times 10^{-3})$  & $0.128 (\pm 5.22\times 10^{-3})$  & $0.109 (\pm 5.20\times 10^{-3})$ \\
     \bottomrule
@@
 \footnotetext{This row summarizes the results of the well-trained RNN, where the ones suffers from the vanishing gradient issue are removed from the averages.}
-
-\textcolor{red}{Need to collect the result for RNN and LSTM}
 
@@
 In a two-stage procedure, metamodels' overall prediction errors measured by the MSEs in Table~\ref{tab:gmwb_arch} are not the determining factor, but their ability to effectively rank the scenarios by their \textbf{true} losses is most critical in producing accurate CVaR estimates.
-A metamodel that uses less safety margin to rank can save simulation budget in stage 2.
+A metamodel that uses less safety margin to rank can save more simulation budget in stage 2.
 
@@
 \end{figure}
-
-\textcolor{red}{Need to separate the bad RNN from the good RNN for Figure~\ref{fig2:tailMatches}.}
 
@@
 
-\textcolor{red}{Need to separate the bad RNN from the good RNN for Figure~\ref{fig2:CVaR95}.}
 Lastly, we return to our original goal of estimating the $95\%$-CVaR of the dynamic hedging error.
@@
         \toprule
-        \textbf{Model}      & \textbf{Noise level}   & \textbf{Training error}   & \textbf{Test error}   & \textbf{True error}\\
+        \textbf{Model}      & \textbf{$N$}   & \textbf{Training error}   & \textbf{Test error}   & \textbf{True error}\\
         \midrule
-        LSTM                & $N=100$                & $0.075 (\pm0.004)$        & $0.079(\pm0.005)$     & $0.063 (\pm0.004)$ \\ 
-        High-capacity LSTM  & $N=100$                & $0.068 (\pm0.004)$        & $0.102(\pm0.006)$     & $0.060 (\pm0.004)$ \\
-        Difference          & $N=100$                & $-0.007$                  & $0.023$               & $-0.003$ \\
+        LSTM                & $100$                & $0.075 (\pm4.5\times 10^{-3})$        & $0.079(\pm5.4\times 10^{-3})$     & $0.063 (\pm4.4\times 10^{-3})$ \\ 
+        High-capacity LSTM  & $100$                & $0.068 (\pm3.6\times 10^{-3})$        & $0.102(\pm6.1\times 10^{-2})$     & $0.060 (\pm3.6\times 10^{-3})$ \\
+        Difference          & $100$                & $-0.007$                  & $0.023$               & $-0.003$ \\
         \hline
-        LSTM                & $N=10$                 & $0.195 (\pm0.001)$        & $0.193(\pm0.001)$     & $0.070 (\pm0.001)$ \\
-        High-capacity LSTM  & $N=10$                 & $0.157 (\pm0.002)$        & $0.199(\pm0.002)$     & $0.065 (\pm0.001)$ \\
-        Difference          & $N=10$                 & $-0.038$                  & $0.006$               & $-0.005$ \\
+        LSTM                & $10$                 & $0.195 (\pm1.1\times 10^{-3})$        & $0.193(\pm1.7\times 10^{-3})$     & $0.070 (\pm9.1\times 10^{-4})$ \\
+        High-capacity LSTM  & $10$                 & $0.157 (\pm2.0\times 10^{-3})$        & $0.199(\pm1.9\times 10^{-3})$     & $0.065 (\pm1.9\times 10^{-3})$ \\
+        Difference          & $10$                 & $-0.038$                  & $0.006$               & $-0.005$ \\
         \hline
-        LSTM                & $N=1$                  & $1.366 (\pm0.006)$        & $0.781(\pm0.005)$     & $0.129 (\pm0.002)$ \\
-        High-capacity LSTM  & $N=1$                  & $1.354 (\pm0.006)$        & $0.795(\pm0.005)$     & $0.149 (\pm0.002)$ \\
-        Difference          & $N=1$                  & $-0.012$                  & $0.014$               & \textcolor{red}{$0.020$} \\
+        LSTM                & $1$                  & $1.366 (\pm8.6\times 10^{-3})$        & $0.781(\pm6.0\times 10^{-3})$     & $0.129 (\pm5.0\times 10^{-3})$ \\
+        High-capacity LSTM  & $1$                  & $1.354 (\pm2.7\times 10^{-2})$        & $0.795(\pm8.3\times10^{-2})$     & $0.149 (\pm2.7\times 10^{-2})$ \\
+        Difference          & $1$                  & $-0.012$                  & $0.014$               & \textcolor{red}{$0.020$} \\
         \bottomrule
@@
 The first two rows of Table~\ref{tab:lstm_arch} shows the average squared errors and the half widths of their $95\%$ confidence intervals between the metamodel predictions and the labels in the training dataset and the true dataset.
+$N$ indicates the noise level in the training labels, i.e., a simulation dataset with fewer inner replications has a higher noise level.
 The test errors are included as a practical measure of the metamodels' generalization ability to unseen noisy samples.
@@
 
-\textcolor{red}{The $N=1$ plot is not valid}
-
 Figure~\ref{fig2:CVaRsingleStage} shows the boxplots of the 95\%-CVaR estimates of the single-stage procedure with different metamodels and compares them to the two-stage procedure and the standard procedure.

### 2024-11-19 introduction.tex
new

@@
 
-\subsection{Training and Evaluation of Neural Networks}
-
-The training of neural networks involves adjusting the trainable parameters of the network to minimize the loss function, which quantifies the error between the predictions and labels.
-The training process aims to find the optimal parameters that minimize this error.
-The most common approach is to use gradient descent methods with backpropagation, which is an efficient method for computing the gradients of the loss function with respect to the trainable parameters.
-Backpropagation computes the gradients by propagating the error derivatives backward through the network layers.
-This process allows the network to adjust the parameters in the direction of minimizing the loss function.
-The training process is typically performed over a number of epochs, where each epoch is one complete pass through the training dataset.
-
-However, the training of neural networks is non-convex, and the optimization problem is challenging.
-Stochastic gradient descent (SGD) is a popular optimization algorithm for training neural networks.
-It updates the parameters using a single or a small batch of training examples at a time, which makes it much faster than the crude gradient descent.
-However, SGD may oscillate and converge slowly, especially in non-convex problems~\citep{bengio2016}.
-To address these issues, various adaptive learning rate methods have been proposed.
-The most popular approach is Adam, which is a SGD algorithm that adjusts the learning rate during training to improve convergence speed and stability~\citep{kingma2014adam}.
-
-Another common technique to improve the training of neural networks is regularization to prevent overfitting.
-One effective regularization method is dropout, which randomly sets a fraction of neurons to zero during each training iteration~\citep{srivastava2014dropout}.
-This prevents neurons from co-adapting too much, encourages redundancy, and leads to a more robust model that generalizes better to unseen data.
-Early stopping is another regularization method that is relevant to our study.
-It involves monitoring the model's performance on a validation set and stopping training when the performance no longer improves~\citep{prechelt2002early}.
-This helps prevent over-fitting by stopping training before the model begins to fit to noise in the data.
-
-Evaluation of the performance of a neural network is challenging due to the absence of analytical tools.
-Existing machine learning literature addresses this challenge by splitting the data into three parts: training set, validation set, and test set.
-The training set is used to train the model, the validation set is used to tune the model hyper-parameters, and the test set is used to evaluate how well the model generalizes to unseen data.
-The test set is not used during training and is only used for evaluation.
-
-Under-fitting occurs when the training error is high, which means that the neural network fails to capture the underlying patterns in the training data.
-Over-fitting occurs when the neural network fits to noise in the training data and cannot generalize to unseen data.
-In machine learning literature, over-fitting is often quantified as the gap between the training error and the test error~\citep{bishop2006pattern}.
-During training, as the test dataset is not used, this quantity is estimated using the validation set.
-If the validation error is high compared to the training error, the model is likely over-fitting to the training data.
-
-\subsection{Long Short-Term Memory Networks}
+\subsection{Long Short-Term Memory Networks} \label{subsec:LSTM}
 
@@
 By leveraging the memory and sequential modeling capabilities of LSTMs, we aim to improve the accuracy and efficiency of nested simulation procedures for risk management applications.
+
+\subsection{Training and Evaluation of Neural Networks in a Simulation Environment}
+
+The training of neural networks involves adjusting the trainable parameters of the network to minimize the loss function, which quantifies the error between the predictions and labels.
+The training process aims to find the optimal parameters that minimize this error.
+The most common approach is to use gradient descent methods with backpropagation, which is an efficient method for computing the gradients of the loss function with respect to the trainable parameters.
+Backpropagation computes the gradients by propagating the error derivatives backward through the network layers.
+This process allows the network to adjust the parameters in the direction of minimizing the loss function.
+The training process is typically performed over a number of epochs, where each epoch is one complete pass through the training dataset.
+
+However, the training of neural networks is non-convex, and the optimization problem is challenging.
+Stochastic gradient descent (SGD) is a popular optimization algorithm for training neural networks.
+It updates the parameters using a single or a small batch of training examples at a time, which makes it much faster than the crude gradient descent.
+However, SGD may oscillate and converge slowly, especially in non-convex problems~\citep{bengio2016}.
+To address these issues, various adaptive learning rate methods have been proposed.
+The most popular approach is Adam, which is a SGD algorithm that adjusts the learning rate during training to improve convergence speed and stability~\citep{kingma2014adam}.
+
+Another common technique to improve the training of neural networks is regularization to prevent overfitting.
+One effective regularization method is dropout, which randomly sets a fraction of neurons to zero during each training iteration~\citep{srivastava2014dropout}.
+This prevents neurons from co-adapting too much, encourages redundancy, and leads to a more robust model that generalizes better to unseen data.
+Early stopping is another regularization method that is relevant to our study.
+It involves monitoring the model's performance on a validation set and stopping training when the performance no longer improves~\citep{prechelt2002early}.
+This helps prevent over-fitting by stopping training before the model begins to fit to noise in the data.
+
+Evaluation of the performance of a neural network is challenging due to the absence of analytical tools.
+Existing machine learning literature addresses this challenge by splitting the data into three parts: training set, validation set, and test set.
+The training set is used to train the model, the validation set is used to tune the model hyper-parameters, and the test set is used to evaluate how well the model generalizes to unseen data.
+The test set is not used during training and is only used for evaluation.
+
+Under-fitting occurs when the training error is high, which means that the neural network fails to capture the underlying patterns in the training data.
+Over-fitting occurs when the neural network fits to noise in the training data and cannot generalize to unseen data.
+In machine learning literature, over-fitting is often quantified as the gap between the training error and the test error~\citep{bishop2006pattern}.
+During training, as the test dataset is not used, this quantity is estimated using the validation set.
+If the validation error is high compared to the training error, the model is likely over-fitting to the training data.
+
+In practice, the ultimate performance of a neural network is often evalutated based on error metrics on the test dataset and how it compares with the training error. 
+The test error is often thought to be a reliable indicator of the model's generalization capability for most machine learning applications.
+However, real-world datasets often contain noise.
+As the test dataset is separated from the training dataset, it is often contaminated with noise.
+Therefore, the test error may not be robust for evaluating the generalization capability of a neural network.
+In this thesis, we aim to evaluate the generalization capability of neural networks in a simulation environment.
+For a simulation model, we can generate a large number of datasets with different levels of noise.
+The noise level can be controlled by the design parameters of the simulation model, e.g., the number of replications.
+Instead of relying on the noisy test labels, we can generate a less noisy test labels using a higher number of replications, or even the true simulation model.
+In the rest of this thesis, we will use ``test dataset'' or ``test labels'' to refer to the noisy test dataset, and ``true dataset'', ``true labels'', or ``true relationship'' to refer to dataset generated from the true simulation model.
+
+\begin{figure}[ht!] 
+    \centering
+    \includegraphics[width=0.8\textwidth]{./project2/figures/datasets.png}
+    \caption{Different Levels of Noise}
+    \label{fig:datasets}
+\end{figure}
+
+Figure~\ref{fig:datasets} shows datasets with different levels of noise in a typical machine learning setting.
+The left panel illustrates the common practice of using a test dataset that is separate from the training dataset that is contaminated with noise.
+The right panel shows an alternative approach of using \textit{true labels} generated from the true relationship.
+In a simulation context, the true relationship, which is the simulation model that generates the data, is visible to the user.
+Even if the true relationship is unknown, we can approximate it using a large number of replications and use it as the true labels.
+Comparing the errors of a neural network on the true labels can reveal its true generalization capability and robustness.
+Chapter~\ref{chap:project2} provides a detailed study of the generalization capability of LSTM networks in a simulation environment for risk management of VA contracts.
+Viewing the simulation environment as a data-generating process allows us to systematically study and evaluate the performance of neural networks within a controlled setting.
+This approach provides insights into their applicability in real-world risk management applications.
+
+In the subsequent chapters, we dive deeper into these topics.
+Chapter~\ref{chap:project1} provides a comprehensive analysis of the convergence properties of existing nested simulation procedures and their practical implications.
+Chapter~\ref{chap:project2} focuses on the development and evaluation of neural network metamodels, particularly LSTM networks, for enhancing the efficiency of nested simulations in risk management of VA contracts.
+We also examine the robustness and generalization capabilities of these models in the presence of simulation noise.
+Chapter~\ref{chap:project3} explores the use of transfer learning techniques to adapt neural network metamodels to new market conditions and contract specifications.
+Our approach enables rapid deployment in changing environments.
+Finally, Chapter~\ref{chap:conclusion} summarizes the key findings of the thesis and discusses future research directions that involve the robost use of neural networks in quantitative risk management applications.

### 2024-11-20 project2/nnMetamodels.tex
new

@@
 For some macro replications (as shown in Figure~\ref{subfig2:badRNN}), the RNN metamodels' predictions are far from the true losses, especially on the tails.
+Seperating the good training macro replications from the bad ones, the results reconcile with the findings in Table~\ref{tab:gmwb_arch}.
 The FNN metamodel has a better fit than the regression metamodels, but it does not have the same level of accuracy as the LSTM metamodel, which is a specialized network to capture the sequential structure of our time-series features.
@@
 Otherwise, the two-stage procedure will offer no computational advantage in simulation budget over the standard procedure.
-The LSTM metamodel can reaches similar percentage with a $5\%$ safety margin.
+The LSTM metamodel can reach similar percentage with a $5\%$ safety margin.
 This indicates that the LSTM metamodel should be able to reach the same level of accuracy as the standard procedure with only $20\%$ of the simulation budget.
@@
 For practical applications that utilize nerual networks as metamodels, we recommend not simulating the test scenarios.
-Instead, we recommend simulating the true contract losses on a few tail and non-tail training scenarios to evaluate the metamodels' noise tolerance.
+Instead, we recommend simulating the true contract losses on a subset of training scenarios to evaluate the metamodels' generalization ability.
 
@@
         $M = \num{10000}$    & $0.283$ & $0.115$ & $0.099$ & $0.097$ \\
-        $M = \num{100000}$   & $0.126$ & $0.068$ & $0.063$ & $0.063$ \\
+        $M = \num{100000}$   & $0.129$ & $0.070$ & $0.063$ & $0.063$ \\
         \bottomrule
@@
 Another way to interpret the results in Table~\ref{tab2:lstm_sens} is to compare the MSEs for the same budget of $\Gamma = M \times N$. 
-Entries on the same diagonal represents the same simulation budget.
+Table entries on the same off-diagonal have the same simulation budget $\Gamma$.
 For most budgets, the MSEs are also the lowest when $N = 10$.
@@
 Consistent with our previous numerical experiments, the Spearman correlations of a high-capacity LSTM is high for a moderate simulation budget. 
-For $M= \num{100000}$, the Spearman correlation is insensitive to $N$.
+For $M= \num{100000}$, the Spearman correlation is relativelyinsensitive to $N$.
 This finding supports further budget savings for our two-stage procedure.
-In stage 1, we can lower $N$ from $\num{100}$ to $\num{10}$ without compromising on tail scenario preditions. 
-Table
+In stage 1, we can lower $N$ from $\num{100}$ to $\num{10}$ almost without compromising on tail scenario preditions.
 
@@
 In this section, we compare the single-stage procedure to the two-stage procedure and the standard procedure in estimating the $95\%$-CVaR of the hedging losses for GMWB.
-% , and we also examine the single-stage procedure's performance in estimating the standard deviation of the hedging losses. 
 In our numerical experiments, the results for the single-stage procedure is obtained with the same metamodels as in the two-stage procedure.
@@
 The two-stage procedure uses the same simulation budget as the single-stage procedure in stage 1 with extra budget for extensive inner simulation on the predicted tail scenarios in stage 2.
-The metamodel with the best performance in the two-stage procedure is chosen, and the safety margin is set to $0\%$.
+The metamodel with the best performance in the two-stage procedure is selected, and the safety margin is set to $0\%$.
 The standard procedure shown in Figure~\ref{fig2:CVaRsingleStage} uses the noisy loss labels in the training dataset to estimate the CVaR directly, which uses the same simulation budget as the single-stage procedure.
-We observe that the single-stage procedures with the LSTM metamodels consistently produce CVaR estimates that are closer to the true value than the standard procedure's estimate, especially when the noise level is high in the training labels.
-It is another strong evidence that the LSTM metamodel is able to cut through the noise in the noisy training labels and make accurate loss predictions that lead to accurate CVaR estimates.
+We observe that the single-stage procedures with the regular LSTM metamodel consistently produce CVaR estimates that are closer to the true value than the standard procedure's estimate.
+This finding is especially impressive when the noise level in the training labels is high.
+It is another strong evidence that a well-selected LSTM metamodel is able to cut through the noise in the noisy training labels and make accurate loss predictions that lead to accurate CVaR estimates.
 The difference in performance among the metamodels is more pronounced in the single-stage procedure than in the two-stage procedure.
-Trained using low noise and medium noise labels, high-capacity LSTM metamodel consistently produces CVaR estimates that are closer to the true value than the regular LSTM, while the other metamodels produce even worse estimates.
+Trained using medium noise labels, high-capacity LSTM metamodel consistently produces CVaR estimates that are closer to the true value than the regular LSTM, while the other metamodels produce even worse estimates.
+However, with high noise training labels, the high-capacity LSTM suffers from severe overfitting. 
+This is also evident in Table~\ref{tab:lstm_arch}.
 Since we are using the metamodel predictions to estimate the CVaR directly without any safety margin, the metamodel's overall prediction accuracy becomes more important.
@@
 
-A single-stage procedure with a high-capcity LSTM metamodel is particularly superior to the two-stage procedure, as it is able to achieve a similar accuracy as the standard procedure with a much smaller simulation budget.
+A single-stage procedure with a regular LSTM metamodel is particularly superior to the two-stage procedure, as it is able to achieve a higher accuracy as the standard procedure with a much smaller simulation budget.
 Note that the single-stage procedure does not require a safety margin.
@@
 For a two-stage procedure with a $0\%$ safety margin, the extra computational cost is from the extensive inner simulation in stage 2.
-On $4$ $20$-core Intel Xeon Gold $\num{6230}$ processors, stage 2 of the two-stage procedure takes $30$ minutes to run with parallel processing, while the $95\%$ confidence interval of training time of the high-capacity LSTM metamodel is $(19.64 \pm 0.94)$ minutes on a Nvidia RTX $\num{3060}$ Ti GPU.
+On $4$ $20$-core Intel Xeon Gold $\num{6230}$ processors, stage 2 of the two-stage procedure takes $30$ minutes to run with parallel processing, while the $95\%$ confidence band of training time of the high-capacity LSTM metamodel is $(19.64 \pm 0.94)$ minutes on a Nvidia RTX $\num{3060}$ Ti GPU.
 While the accuracy of the two-stage procedure is highly dependent on the safety margin, increasing the safety margin introduces extra computational cost.

### 2024-11-20 project2/nnMetamodels.tex
new

@@
     Even for CVaR, the two-stage procedure become less attactive for an increased level.
-    In our numerical experiments, we will compare the single-stage procedure to the two-stage procedure and the standard procedure in estimating the $\alpha$-CVaR for a lower $\alpha$.
 \end{enumerate}
@@
         High-capacity LSTM  & $100$                & $0.068 (\pm3.6\times 10^{-3})$         & $0.102(\pm6.1\times 10^{-2})$     & $0.060 (\pm3.6\times 10^{-3})$ \\
-        Difference          & $100$                & $-0.007$                  & $0.023$               & $-0.003$ \\
+        Average Difference  & $100$                & $-0.007$                               & $0.023$                           & $-0.003$ \\
         \hline
@@
         High-capacity LSTM  & $10$                 & $0.157 (\pm2.0\times 10^{-3})$         & $0.199(\pm1.9\times 10^{-3})$     & $0.065 (\pm1.9\times 10^{-3})$ \\
-        Difference          & $10$                 & $-0.038$                  & $0.006$               & $-0.005$ \\
+        Average Difference  & $10$                 & $-0.038$                               & $0.006$                           & $-0.005$ \\
         \hline
@@
         High-capacity LSTM  & $1$                  & $1.354 (\pm2.7\times 10^{-2})$         & $0.795(\pm8.3\times10^{-2})$      & $0.149 (\pm2.7\times 10^{-2})$ \\
-        Difference          & $1$                  & $-0.012$                  & $0.014$               & \textcolor{red}{$0.020$} \\
+        Average Difference  & $1$                  & $-0.012$                               & $0.014$                           & \textcolor{red}{$0.020$} \\
         \bottomrule
@@
 The accuracy and robustness of the LSTM metamodels motivate us to propose a single-stage procedure that uses the metamodel predictions to estimate the CVaR directly. 
-Instead of relying on the standard nested simulation procedure in stage 2, the single-stage procedure is more efficient and extends to estimating other risk measures that require knowledge of the entire loss distribution.
+Instead of relying on the standard nested simulation procedure in stage 2, the single-stage procedure can be even more efficient.
 In this section, we compare the single-stage procedure to the two-stage procedure and the standard procedure in estimating the $95\%$-CVaR of the hedging losses for GMWB.

### 2024-11-20 project2/nnMetamodels.tex
new

@@
 Furthermore, our numerical results provide evidences for adopting DNN metamodels in Monte Carlo simulation for risk management tasks.
-Through our systematic empirical study of the noise tolerance of DNN metamodels, we address regulatory concerns by showing that a LSTM metamodel is resilient to a high level of noise in training labels and is able to make accurate predictions.
+Through our systematic empirical study of the noise tolerance of DNN metamodels, we address regulatory concerns by showing that a LSTM metamodel with moderate model capacity is resilient to a high level of noise in training labels and is able to make accurate predictions.
 A possible future research direction is to apply DNN metamodels in other financial risk management tasks that requires complex nested simulation with high-dimensional outer scenarios.

### 2024-11-22 project3/draft.tex
new

@@
 Chapter~\ref{chap:project2} introduces a nested simulation framework for dynamic hedging of VAs, where the inner simulation is approximated by an LSTM metamodel.
-It shows that crude RNN and LSTMs are well-suited for metamodeling Monte Carlo simulation of financial time series and can capture the long-term dependencies in the simulation dataset.
+It shows that crude RNN and LSTMs are well-suited as metamodels for Monte Carlo simulation of financial time series and can capture the long-term dependencies in the simulation dataset.
 
@@
 Retraining neural network metamodels from scratch in response to every change is computationally inefficient and time-consuming.
+The simulation budget is often limited, and the computational cost of retraining a suitable DNN metamodel is high.
 Moreover, financial markets are inherently dynamic with frequent shifts in volatility, interest rates, and other risk factors~\citep{cont2001empirical}.
@@
 Traditional models, such as autoregressive integrated moving average (ARIMA) and generalized autoregressive conditional heteroskedasticity (GARCH), have been widely used in time series modeling.
-However, these models often struggle to capture the complex patterns and nonlinear relationships in financial data.
-DNNs like RNN and LSTM networks have demonstrated significant improvements in modeling temporal dependencies. 
+ARIMA models~\citep{box1970distribution} combine autoregression, differencing, and moving average components to capture linear relationships in time series data.
+GARCH models~\citep{bollerslev1990modelling}, extend ARCH models to better capture volatility clustering, which is a key stylized fact of financial time series~\citep{cont2001empirical}.
+However, these models often struggle to capture complex dynamics, e.g., regime changes~\citep{hamilton1989new} and extreme market events~\citep{embrechts2013modelling} that are prevalent in financial markets.
+In Chapter~\ref{chap:project2}, our numerical experiment uses a regime-switching geometric Brownian motion as the underlying asset model.
+We have shown DNNs like RNN and LSTM networks have demonstrated significant improvements in modeling temporal dependencies. 
 However, training these models from scratch requires extensive data, which may not always be available for specific assets or under certain market conditions.
@@
 In our context of DNNs metamodeling-based simulation procedures for hedging VAs, TL involves pre-training a neural network where the simulation budget is abundant and then fine-tuning it on a smaller dataset of new contracts or market conditions.
-Written on the same underlying asset, different VA contracts may share common features or exhibit similar patterns, especially temporal dependencies in the underlying financial time series.
+Written on the same underlying asset, different VA contracts may share common features or exhibit similar patterns, especially temporal dependencies and regime changes in the underlying financial time series.
 Similarly, two VAs with the same features but based on different underlying assets may have some shared characteristics that can be leveraged to improve the learning performance of the metamodel.
@@
 TL offers an alternative approach to keep the previous knowledge as a foundation, thus accelerates the adaptation of the LSTM metamodel to new conditions.
-Computational savings come in two forms: (1) less training time is required to fine-tune the pre-trained model on the new dataset, and (2) fewer data points are needed to achieve a good LSTM metamodel, which is particularly beneficial when the standard nested simulation procedure is costly.
+Computational savings come in two forms: 
+\begin{equation*}
+    \item   less training time is required to fine-tune the pre-trained model on the new dataset, and
+    \item   fewer data points are needed to achieve a good LSTM metamodel, which is particularly beneficial when the standard nested simulation procedure is costly.
+\end{equation*}
 

### 2024-11-23 project2/nnMetamodels.tex
new

@@
 We present our proposed procedure as a competitor to the standard procedure with $M$ outer scenarios and $N$ inner replications for each outer scenario, as described in Section~\ref{subsec:dynamicHedge}.
-We propose a two-stage procedure with a neural network metamodel that aims to produce a CVaR estimate that's as accurate as that of the standard procedure, but uses fewer computations as than latter.
+We propose a two-stage procedure with a supervised learning metamodel that aims to produce a CVaR estimate that's as accurate as that of the standard procedure, but requires fewer computations than the latter.
 
@@
         Note that $N'$ may be much smaller than $N$, so $\Lhat_i$ are expected to have larger variance.
-        \item Use the simulated data, $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$ to train a neural network.
-Refer to the trained model as a metamodel and denote it by $\Lhat^{PD}(\bS)$.
-Denote the predicted losses for the outer scenarios by $\Lhat^{PD}_i = \Lhat^{PD}(\bS^{(i)})$, $i=1,\ldots,M$.
+        \item Use the simulated data, $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$ to train a supervised learning model. 
+        It is standard practice in supervised learning research to transform the stock prices $\bS^{(i)}$ to log returns $\mathbf{X}^{(i)}$,
+        $$
+        \mathbf{X}^{(i)} = \left(\ln\left(\frac{S_{1}^{(i)}}{S_{0}^{(i)}}\right), \ln\left(\frac{S_{2}^{(i)}}{S_{1}^{(i)}}\right), \ldots, \ln\left(\frac{S_{T}^{(i)}}{S_{T-1}^{(i)}}\right)\right),
+        $$
+        and use $\mathbf{X}^{(i)}$ as features instead of the stock prices $\bS^{(i)}$.
+        Refer to the trained model as a metamodel and denote it by $\Lhat^{PD}(\mathbf{X})$.
+Denote the predicted losses for the outer scenarios by $\Lhat^{PD}_i = \Lhat^{PD}(\mathbf{X}^{(i)})$, $i=1,\ldots,M$.
         \item Sort the predicted losses $\Lhat^{PD}_{(1)}\leq \Lhat^{PD}_{(2)} \leq \cdots\leq \Lhat^{PD}_{(M)}$ to identify a predicted tail scenario set, $\widehat{\tail}_{m}^{PD}$, associated with the largest predicted losses.

### 2024-11-23 project2/nnMetamodels.tex
new

@@
         \item Use the simulated data, $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$ to train a supervised learning model. 
-        It is standard practice in supervised learning research to transform the stock prices $\bS^{(i)}$ to log returns $\mathbf{X}^{(i)}$,
-        $$
-        \mathbf{X}^{(i)} = \left(\ln\left(\frac{S_{1}^{(i)}}{S_{0}^{(i)}}\right), \ln\left(\frac{S_{2}^{(i)}}{S_{1}^{(i)}}\right), \ldots, \ln\left(\frac{S_{T}^{(i)}}{S_{T-1}^{(i)}}\right)\right),
-        $$
+        It is standard practice in supervised learning research to transform the stock prices $\bS^{(i)}$ to returns $\mathbf{X}^{(i)}$,
+        \begin{equation} \label{eq2:return}
+        \mathbf{X}^{(i)} = \left(\frac{S_1^{(i)} - S_0}{S_0}, \frac{S_2^{(i)} - S_1^{(i)}}{S_1^{(i)}}, \ldots, \frac{S_T^{(i)} - S_{T-1}^{(i)}}{S_{T-1}^{(i)}}\right)
+        \end{equation}
         and use $\mathbf{X}^{(i)}$ as features instead of the stock prices $\bS^{(i)}$.

### 2024-11-23 project3/draft.tex
new

@@
 Computational savings come in two forms: 
-\begin{equation*}
+\begin{enumerate}
     \item   less training time is required to fine-tune the pre-trained model on the new dataset, and
     \item   fewer data points are needed to achieve a good LSTM metamodel, which is particularly beneficial when the standard nested simulation procedure is costly.
-\end{equation*}
+\end{enumerate}
 
@@
 \begin{itemize}
-    \item   \textbf{source domain}: $\mathcal{D}_{\text{So}} = \{\mathcal{X}_{\text{So}}, F_{\text{So}}(X)\}$
+    \item   \textbf{source domain}: $\mathcal{D}_{\text{So}} = \{\mathcal{X}_{\text{So}}, F_{\text{So}}(\mathbf{X})\}$
     \item   \textbf{source task}: $\mathcal{T}_{\text{So}} = \{\mathcal{Y}_{\text{So}}, f_{\text{So}}(\cdot)\}$
-    \item   \textbf{target domain}: $\mathcal{D}_{\text{Ta}} = \{\mathcal{X}_{\text{Ta}}, F_{\text{Ta}}(x)\}$
+    \item   \textbf{target domain}: $\mathcal{D}_{\text{Ta}} = \{\mathcal{X}_{\text{Ta}}, F_{\text{Ta}}(\cdot)\}$
     \item   \textbf{target task}: $\mathcal{T}_{\text{Ta}} = \{\mathcal{Y}_{\text{Ta}}, f_{\text{Ta}}(\cdot)\}$
@@
 
-where $\mathcal{X}_{\text{So}}$ and $\mathcal{X}_{\text{Ta}}$ include input features derived from the outer simulation of two different VA contracts or market conditions, and $F_{\text{So}}(X)$ and $F_{\text{Ta}}(x)$ are the marginal probability distributions of the source and target domains, respectively.
-In our numerical experiments, the dataset is generated by running the standard nested simulation procedure in Algorithm~\ref{alg2:standardProcedure} for a large number of VA contracts.
-The input features $X$ are the risk factors, and the output labels $L$ are the contract losses at each time step.
+where $\mathcal{X}_{\text{So}}$ and $\mathcal{X}_{\text{Ta}}$ include input features derived from the outer simulation of two different VA contracts or market conditions, and $F_{\text{So}}$ and $F_{\text{Ta}}$ are the marginal probability distributions of the source and target domains, respectively.
+In our numerical experiments, the dataset is generated by running the standard nested simulation procedure in Algorithm~\ref{alg2:standardProcedure} for a large number of VA contracts.+-
+The input features $\mathbf{X}$ are the return vectors from Equation~\ref{eq2:return}, and the output labels $L$ are the contract losses at each time step.
+The stock price vector $\mathbf{S}$ is not crucial for the discussion of this chapter and is omitted since it can be immediately recovered from $\mathbf{X}$ and the initial stock price $S_0$.
 We keep the number of features to be $240$ for both source and target domains as in Section~\ref{sec2:numerical}.
@@
 $X_{\text{So}}^{(i)} \in \mathcal{X}_{\text{So}}$ and $L_{\text{So}}^{(i)} \in \mathcal{Y}_{\text{So}}$.
-
 The ultimate objective is to learn a metamodel $f_{\text{Ta}}$ that predicts the VA contract losses $L_{\text{So}}$ from the scenarios $X_{\text{Ta}}$ in the form of a financial time series.

### 2024-11-24 project3/draft.tex
1

@@
 In the evolving landscape of financial markets, insurance products such as VAs have gained significant interest due to their ability to provide both investment growth and guaranteed benefits. 
-Managing the risks associated with these products, especially in volatile market conditions, is a complex task that demands sophisticated financial modeling techniques like nested simulation.
-A standard nested simulation procedure involves running a large number of simulations to generate a dataset of scenario-wise contract losses.
-To address the computational burden, metamodeling techniques have been proposed, where a surrogate model approximates the outcomes of a more complex simulation. 
+Managing the risks associated with these products in volatile market conditions is a complex task that demands sophisticated financial modeling techniques like nested simulation.
+A standard nested simulation procedure involves running a large number of simulations to generate a dataset of scenario-wise contract losses with two levels of simulations.
+Practitioners can estimate tail risk measures using the realized losses obtained from these simulations.
+Nested simulation is extremely computationally expensive.
+To address the computational burden, metamodeling techniques have been proposed, where a surrogate model approximates the outcomes of a complex simulation procedure. 
 Traditional machine learning models often struggle to capture the intricate nonlinear relationships and temporal dependencies inherent in financial data.
@@
 
-Despite the advantages of using DNN metamodels, a significant challenge arises when market conditions change or new VA contracts with different features are introduced. 
+Despite the advantages of using DNN metamodels, computational challenges arise when market conditions change or new VA contracts with different features are introduced. 
 Retraining neural network metamodels from scratch in response to every change is computationally inefficient and time-consuming.
-The simulation budget is often limited, and the computational cost of retraining a suitable DNN metamodel is high.
+The simulation budget is often limited, and the computational cost of retraining a suitable DNN metamodel is often much higher than fitting a traditional parametric regression.
 Moreover, financial markets are inherently dynamic with frequent shifts in volatility, interest rates, and other risk factors~\citep{cont2001empirical}.
-Therefore, it is essential to develop methods that can rapidly adapt existing metamodels to new conditions without incurring the full computational cost of retraining.
+Therefore, it is essential to develop methods that can rapidly adapt existing metamodels to new conditions without incurring the full computational cost of retraining and extensive addtional simulations.
 Transfer Learning (TL) offers a compelling solution to this problem by enabling the reuse of a pre-trained model on a new but related task~\citep{pan2009survey}.
@@
 where $\mathcal{X}_{\text{So}}$ and $\mathcal{X}_{\text{Ta}}$ include input features derived from the outer simulation of two different VA contracts or market conditions, and $F_{\text{So}}$ and $F_{\text{Ta}}$ are the marginal probability distributions of the source and target domains, respectively.
-In our numerical experiments, the dataset is generated by running the standard nested simulation procedure in Algorithm~\ref{alg2:standardProcedure} for a large number of VA contracts.+-
+In our numerical experiments, the dataset is generated by running the standard nested simulation procedure in Algorithm~\ref{alg2:standardProcedure} for a large number of VA contracts.
 The input features $\mathbf{X}$ are the return vectors from Equation~\ref{eq2:return}, and the output labels $L$ are the contract losses at each time step.
@@
     \midrule
-    GMMB & GBM & No lapse & 50,000 & N/A \\
-    GMMB & RS-GBM & No lapse & 50,000 & 2,000 \\
-    GMMB & RS-GBM & Static lapse & 50,000 & 2,000 \\
-    GMMB & RS-GBM & Dynamic lapse & 50,000 & 2,000 \\
-    GMWB & RS-GBM & Dynamic lapse & N/A & 2,000 \\
+    GMMB & GBM & No lapse & $\num{50000}$ & N/A \\
+    GMMB & RS-GBM & No lapse & $\num{50000}$ & $\num{2000}$ \\
+    GMMB & RS-GBM & Static lapse & $\num{50000}$ & $\num{2000}$ \\
+    GMMB & RS-GBM & Dynamic lapse & $\num{50000}$ & $\num{2000}$ \\
+    GMWB & RS-GBM & Dynamic lapse & N/A & $\num{2000}$ \\
     \bottomrule
@@
 These contracts include GMMB and GMWB contracts with no lapse, static lapse, and dynamic lapse features.
-Before transferred to the target task, a LSTM metamodel is trained on a source dataset with $M_{\text{So}} = 50,\!000$ samples generated with $N_{\text{So}} = 100$ inner replications\footnotemark.
+Before transferred to the target task, a LSTM metamodel is trained on a source dataset with $M_{\text{So}} = \num{50000}$ samples generated with $N_{\text{So}} = \num{100}$ inner replications\footnotemark.
 \footnotetext{The GMMB contract on the GBM asset model is an exception, where scenario-wise contract losses can be computed analytically.}
 The pre-trained LSTM metamodel is then adapted to a target task that is different from the source task.
-The training dataset for the target task has $M_{\text{Ta}} = 2,\!000$ samples generated with $N_{\text{Ta}} = 100$ inner replications.
+The training dataset for the target task has $M_{\text{Ta}} = \num{2000}$ samples generated with $N_{\text{Ta}} = \num{100}$ inner replications.
 During the training on both the source and target tasks, $10\%$ of the data is split into a validation dataset to monitor the training process and prevent overfitting using early stopping.
@@
 We measure the generalization performance of the LSTM metamodels using the true MSE, which quantifies the accuracy of the LSTM metamodels in approximating the true inner simulation model of VA contracts.
-The true MSE is computed by comparing the metamodel predictions with the true contract losses, which are approximated by the standard nested simulation procedure with $100,\!000$ inner replications.
+The true MSE is computed by comparing the metamodel predictions with the true contract losses, which are approximated by the standard nested simulation procedure with $\num{100000}$ inner replications.
 Hyperparameters and network architectures for the LSTM metamodels are kept the same as the LSTM metamodel in Section~\ref{sec2:numerical}. 
@@
     \midrule
-    No Lapse & N/A & 0.4894 & 0.3361 & N/A \\
-    Static Lapse & N/A & 0.0794 & 0.0763 & N/A \\
-    Dynamic Lapse & 0.0587 &  N/A &  N/A & 0.2950 \\
+    No Lapse & N/A & $0.4894$ & $0.3361$ & N/A \\
+    Static Lapse & N/A & $0.0794$ & $0.0763$ & N/A \\
+    Dynamic Lapse & $0.0587$ &  N/A &  N/A & $0.2950$ \\
     \bottomrule
@@
 Table~\ref{tab3:transfer_learning_results} summarizes the true MSEs of the LSTM metamodels trained using different TL methods across various source tasks.
-The calculations are based on the metamodel predictions and the true contract losses approximated with $100,\!000$ inner replications.
+The calculations are based on the metamodel predictions and the true contract losses approximated with $\num{100000}$ inner replications.
 The first two rows show the performance of transferring knowledge from GMMB contracts with no lapse and static lapse to the target task of GMMB with dynamic lapse.
@@
 
-Figure~\ref{subfig3-4:extensive} presents the performance of an extensively trained LSTM metamodel on the target task using 50,000 samples, serving as a benchmark of best metamodel performance. 
+Figure~\ref{subfig3-4:extensive} presents the performance of an extensively trained LSTM metamodel on the target task using $\num{50000}$ samples, serving as a benchmark of best metamodel performance.
 The extensively trained metamodel achieves a low validation error and demonstrates stable convergence due to having enough training samples. 
-In contrast, Figure~\ref{subfig3-4:without} shows the results of training the metamodel directly on the target task with $2,\!000$ training samples. 
+In contrast, Figure~\ref{subfig3-4:without} shows the results of training the metamodel directly on the target task with $\num{2000}$ training samples. 
 Fewer training samples and no prior knowledge leads to unstable training dynamics. 
@@
         \midrule
-        Without TL & 2,000 & 0.3588 & 0.4188 \\
-        Fine Tuning & 2,000 & 0.1690 & 0.1780 \\
-        Layer Freezing & 2,000 & 0.1828 & 0.2295 \\
-        Extensive Training & 50,000 & 0.0853 & 0.0726 \\
+        Without TL & $\num{2000}$ & $0.3588$ & $0.4188$ \\
+        Fine Tuning & $\num{2000}$ & $0.1690$ & $0.1780$ \\
+        Layer Freezing & $\num{2000}$ & $0.1828$ & $0.2295$ \\
+        Extensive Training & $\num{50000}$ & $0.0853$ & $0.0726$ \\
         \bottomrule

### 2024-11-25 project3/draft.tex
1

@@
 
-In this chapter, we explore the application of TL to the dynamic hedging of VAs using RNN and LSTM metamodels.
-We propose a novel TL framework that accelerates the training of DNN metamodels for nested simulation procecedures in dynamic hedging.
-This setting is particularly relevant for hedging problems, as insurance companies often underwrite new contracts under changing market conditions and actuarial assumptions.
-Fast adaptation of metamodels is necessarily for metamodel-based nested simulation procedures.
+In this chapter, we explore the application of TL to the dynamic hedging of VAs using LSTM metamodels.
+We propose a novel TL framework that accelerates the training of DNN metamodels for nested simulation procedures in dynamic hedging.
+This setting is particularly relevant for dynamic hedging problems, as insurance companies often underwrite new contracts under changing market conditions and actuarial assumptions.
+Fast adaptation of metamodels is necessary for metamodel-based nested simulation procedures.
 Our approach involves pre-training an LSTM network on a large dataset of VA simulations and then fine-tuning it on a smaller dataset of new VA contracts.
 We evaluate the performance of the TL framework on a real-world dataset of VA contracts and compare it with training a LSTM metamodel from scratch.
+More importantly, we show the strengths and weaknesses of different TL techniques for rapid adaptation of LSTM metamodels.
 
@@
 One of the primary applications of TL in finance is asset price prediction. 
-Traditional models, such as autoregressive integrated moving average (ARIMA) and generalized autoregressive conditional heteroskedasticity (GARCH), have been widely used in time series modeling.
+Traditional models, such as geometric Brownian motion (GBM), autoregressive integrated moving average (ARIMA) and generalized autoregressive conditional heteroskedasticity (GARCH), have been widely used in time series modeling.
 ARIMA models~\citep{box1970distribution} combine autoregression, differencing, and moving average components to capture linear relationships in time series data.
@@
 However, these models often struggle to capture complex dynamics, e.g., regime changes~\citep{hamilton1989new} and extreme market events~\citep{embrechts2013modelling} that are prevalent in financial markets.
-In Chapter~\ref{chap:project2}, our numerical experiment uses a regime-switching geometric Brownian motion as the underlying asset model.
-We have shown DNNs like RNN and LSTM networks have demonstrated significant improvements in modeling temporal dependencies. 
-However, training these models from scratch requires extensive data, which may not always be available for specific assets or under certain market conditions.
-TL offers a solution to this problem by leveraging knowledge from related assets or tasks to improve the learning performance of DNNs on the target task.
+In Chapter~\ref{chap:project2}, our numerical experiment uses a regime-switching geometric Brownian motion (RS-GBM) as the underlying asset model.
+For estimating tail risk measures, a metamodel-based nested simulation procedure is proposed to approximate the inner simulation.
+We have shown DNN metamodels like RNN and LSTM networks have demonstrated significant improvements in modeling temporal dependencies, and they save a substantial amount of simulation budget.
+However, training these models from scratch requires extensive simulation data, which may not always be available for specific assets or under certain market conditions.
+TL offers a solution to this problem by leveraging knowledge from related assets or tasks to improve the learning performance of DNN metamodels on the target task.
 In algorithmic trading,~\cite{jeong2019improving} used TL to enhance the performance of a reinforcement learning agent by preventing overfitting from insufficient market data.
@@
 In our work, we focus on the application of TL to accelerate the training of LSTM metamodels for nested simulation in dynamic hedging of VAs.
-The fine-tuned LSTM metamodels can be readily adapted to the two-stage procedure and the single-stage procedure in Chapter~\ref{chap:project2} to predict the contract losses under different market scenarios.
+The fine-tuned LSTM metamodels can be readily adapted to the two-stage procedure and the single-stage procedure in Chapter~\ref{chap:project2} to predict the contract losses under different scenarios.
 
-In our context of DNNs metamodeling-based simulation procedures for hedging VAs, TL involves pre-training a neural network where the simulation budget is abundant and then fine-tuning it on a smaller dataset of new contracts or market conditions.
+In our context of DNNs metamodeling-based simulation procedures for hedging VAs, TL involves pre-training a DNN metamodel where the simulation budget is abundant and then fine-tuning it on a smaller dataset of new contracts or market conditions.
 Written on the same underlying asset, different VA contracts may share common features or exhibit similar patterns, especially temporal dependencies and regime changes in the underlying financial time series.
@@
 
-LSTM networks are well-suited for modeling sequential data due to their ability to capture long-term dependencies.
-For the application of VA risk management using metamodel-based nested simulation, LSTM networks approximate the inner simulation, i.e., the mapping from market scenarios to the scenario-wise contract losses.
+LSTM networks are well-suited for modeling sequential data due to their ability to capture long-term dependencies~\citep{hochreiter1997long}.
+For the application of VA risk management using metamodel-based nested simulation, LSTM networks approximate the inner simulation, i.e., the mapping from scenarios to the scenario-wise contract losses.
 In Chapter~\ref{chap:project2}, we treat metamodeling as a supervised learning problem and demonstrated that LSTM networks can effectively model this complex relationships with extensive training on a large dataset of VA simulations.
 The total computational cost originates from two sources: running the standard nested simulation procedure to generate the training data and training the LSTM network on the generate dataset.
-Given a new of VA contract, the above process needs to be repeated to adapt the LSTM metamodel to the new contract.
+Given a new VA contract, these steps need to be repeated to adapt the LSTM metamodel to new market conditions and contract features.
 For a DNN with a large number of parameters, retraining the LSTM network from scratch can be computationally expensive.
-TL offers an alternative approach to keep the previous knowledge as a foundation, thus accelerates the adaptation of the LSTM metamodel to new conditions.
+Generating a large training dataset using the standard nested simulation procedure is costly, and the computational burden can be prohibitive for certain assets or market conditions.
+TL offers an alternative approach that keeps the previous knowledge, i.e., the pre-trained model, as a foundation.
+Building on the pre-trained model, the LSTM network can be fine-tuned on a smaller dataset of new contracts or market conditions.
+This approach accelerates the adaptation of the LSTM metamodel to new conditions.
 Computational savings come in two forms: 
 \begin{enumerate}
-    \item   less training time is required to fine-tune the pre-trained model on the new dataset, and
-    \item   fewer data points are needed to achieve a good LSTM metamodel, which is particularly beneficial when the standard nested simulation procedure is costly.
+    \item   fine-tuning requires less training time than training LSTM metamodels from scratch, and
+    \item   fewer training data points are needed to achieve a good LSTM metamodel, which is particularly beneficial when the standard nested simulation procedure is costly.
 \end{enumerate}
@@
 where $\mathcal{X}_{\text{So}}$ and $\mathcal{X}_{\text{Ta}}$ include input features derived from the outer simulation of two different VA contracts or market conditions, and $F_{\text{So}}$ and $F_{\text{Ta}}$ are the marginal probability distributions of the source and target domains, respectively.
+Hence, the source domain and task are related to one VA contract for a certain market condition, while the target domain and task are related to new VA contracts and market conditions for which we don't have the simulation budget to run the standard nested simulation procedure extensively.
 In our numerical experiments, the dataset is generated by running the standard nested simulation procedure in Algorithm~\ref{alg2:standardProcedure} for a large number of VA contracts.
-The input features $\mathbf{X}$ are the return vectors from Equation~\ref{eq2:return}, and the output labels $L$ are the contract losses at each time step.
+The input features $\mathbf{X}$ are the return vectors from Equation~\ref{eq2:return}, and the output labels $L$ are the contract losses for different outer scenarios.
 The stock price vector $\mathbf{S}$ is not crucial for the discussion of this chapter and is omitted since it can be immediately recovered from $\mathbf{X}$ and the initial stock price $S_0$.
-We keep the number of features to be $240$ for both source and target domains as in Section~\ref{sec2:numerical}.
-The predictive function $f_{\text{So}}$ and $f_{\text{Ta}}$ are trained to estimate outputs $L_{\text{So}}$ and $L_{\text{Ta}}$ such as contract losses in inner simulations under the source and target tasks, respectively.
+We keep the number of features to be $\num{240}$ for both source and target domains as in Section~\ref{sec2:numerical}.
+The predictive function $f_{\text{So}}$ and $f_{\text{Ta}}$ are trained to estimate outputs $L_{\text{So}}$ and $L_{\text{Ta}}$, i.e., approximating the inner simulations under the source and target tasks, respectively.
 TL seeks to improve the learning of the target predictive function $f_{\text{Ta}}(\cdot)$ in $\mathcal{D}_{\text{Ta}}$ by leveraging the previous training on $\mathcal{D}_{\text{So}}$ and $f_{\text{So}}(\cdot)$, particularly when $\mathcal{D}_{\text{So}} \neq \mathcal{D}_{\text{Ta}}$ or $\mathcal{T}_{\text{So}} \neq \mathcal{T}_{\text{Ta}}$.
@@
 TL starts by training a metamodel $f_{\text{So}}$ on the source domain $\mathcal{D}_{\text{So}}$.
-$f_{\text{So}}$ is approximated by an LSTM network $f_{\text{So}}(\cdot ; \theta_{\text{So}})$, and the parameters of the LSTM network, $\theta_{\text{So}}$ are learned by minimizing a MSE loss function on the source domain.
+For both the two-stage procedure and the single-stage procedure in Chapter~\ref{chap:project2}, $f_{\text{So}}$ is approximated by an LSTM network $f_{\text{So}}(\cdot ; \theta_{\text{So}})$, where the parameters of the LSTM network, $\theta_{\text{So}}$ are learned by minimizing a MSE loss function on the source domain.
 Then the pre-trained parameters $\theta_{\text{So}}$ to inform the learning of $f_{\text{Ta}}(\cdot ; \theta_{\text{Ta}})$ on the target domain $\mathcal{D}_{\text{Ta}}$.
@@
 
-These tasks share similarities in contract features and market dynamics, enabling the shared LSTM layers to learn relevant temporal patterns applicable to the target task.
+These tasks need to share similarities in contract features and market dynamics so that the shared LSTM layers can learn relevant temporal patterns applicable to the target task.
+Training a multi-task LSTM metamodel benefits from having more training data, and the shared layers can learn more generalizable representations of temporal dependencies.
 Furthermore, if a new but similar task is introduced, fine-tuning, layer freezing, and multi-task learning can be combined to leverage the pre-trained model effectively.

### 2024-11-29 project3/draft.tex
1

@@
 The tasks should be related to ensure that the shared layers can capture common features beneficial across tasks. 
-Criteria for selecting simulation schemes include:
+Criteria for selecting tasks with similar simulation schemes include:
 
@@
 These tasks need to share similarities in contract features and market dynamics so that the shared LSTM layers can learn relevant temporal patterns applicable to the target task.
+Otherwise, the shared layers may not be able to learn generalizable representations of temporal dependencies, and the multi-task learning framework may lead to negative transfer.
+Negative transfer refers to the phenomenon where the performance of the target task is worse than that of training directly on the target task without TL.
+It occurs when the tasks are not related or an improper TL technique is used.
+Positive transfer, on the other hand, refers to the phenomenon where the performance of the target task is better than that of training directly on the target task without TL.
 Training a multi-task LSTM metamodel benefits from having more training data, and the shared layers can learn more generalizable representations of temporal dependencies.
@@
 However, despite this improvement, fine-tuning may not fully mitigate the challenges of training with a small dataset.
-The fine-tuned metamodel struggles to achieve a low validation MSE.
+No negative trasfer is observed, but the fine-tuned metamodel struggles to achieve a low validation MSE.
 Lowering the learning rate does not help the fine-tuned metamodel converge, and the validation MSE remains high after increasing the number of training epochs.
@@
 The LSTM layers are critical for capturing general feature representations that are transferable across tasks, and freezing these layers helps prevent overfitting to the target task.
-In addition, the layer freezing approch tunes fewer neural network parameters than crude fine-tuning.
-It allows the transferred metamodelmodel to only focus on learning the lapse features without excessively adjusting the general temporal representations learned from the source task.
-This reduction in trainable parameters also accelerates the convergence process, and it leads to a more stable and efficient training on the target task.
+In addition, the layer freezing approach tunes fewer neural network parameters than crude fine-tuning.
+It allows the transferred metamodel to only focus on learning the lapse features without excessively adjusting the general temporal representations learned from the source task for the target task.
+This reduction in trainable parameters also accelerates the convergence, and it leads to a more stable and efficient training on the target task.
 
@@
 When the source and target contracts are substantially different, the pre-trained metamodels may struggle to adapt to the new conditions, as they may not have learned features relevant to the target task.
+There is no negative transfer observed, but the knowledge transfer is limited.
 
@@
 However, when employing layer freezing (Figure~\ref{subfig3-4:layerFreezing}), the metamodel's performance deteriorates.
+Negative transfer is observed.
 Freezing some layers trained on the GMMB contracts does not allow the metamodel to sufficiently adapt to the complexities of the GMWB contracts. 
@@
 This underscores the need for careful model selection and validation when applying TL techniques to different VA products.
+When the source and target tasks are substantially different, all layers need to be updated, thus freezing some layers may lead to negative transfer.
 
@@
 By sharing representations through the LSTM layers, the model can learn more generalizable features that are beneficial across different VA contracts. 
-The multi-task approach was particularly beneficial when training data for individual tasks was scarce, as it effectively pooled information across tasks to enhance learning efficiency and predictive performance.
+The multi-task approach is particularly beneficial when training data for individual tasks is scarce, as it effectively pools information across tasks to enhance learning efficiency and predictive performance.
+We have extended the idea of pooling in Chapter~\ref{chap:project1} and~\ref{chap:project2} to a higher level.
 Furthermore, a metamodel trained with multi-task learning can serve as a pre-trained model. 
@@
 
-The integration of transfer learning into LSTM metamodeling represents a significant advancement in robust risk management associated with variable annuity contracts.
+The integration of transfer learning in LSTM metamodeling represents a significant advancement in robust risk management associated with variable annuity contracts.
 By effectively leveraging existing knowledge, financial institutions can maintain accurate and responsive risk management practices in a rapidly changing market environment. 

### 2024-12-09 project2/nnMetamodels.tex
ee

@@
 The training labels are normalized to have zero mean and unit standard deviation.
-The architectures and the numbers of trainable parameters are recorded in the first two columns of Table~\ref{tab:gmwb_arch}.
+The numbers of trainable parameters are recorded in the second column of Table~\ref{tab:gmwb_arch}.
 We observe that the three DNN metamodels have orders of magnitudes more trainable parameters than the two traditional regression metamodels.
 In machine learning terminologies, the three DNN metamodels have much higher \textit{model capacities}.
-From a neural network of view, MLR and QPR are two neural networks with no hidden layers. 
-For a traditional regression metamodel, the numbers of neurons in its input layer equals to the cardinality of its regression bases.
-Treating a regression as a shallow neural network allows for direct comparisons with DNNs.
+From a neural network of view, MLR and QPR are two neural networks with no hidden layer. 
+For a traditional regression metamodel, the numbers of neurons in its input layer equals to the cardinality of its regression basis.
+Treating a regression as a shallow neural network, i.e., a neural network with only an input layer and an output layer, allows for direct comparisons with DNNs.
+The capacity of a regression metamodel is the product of the number of neurons in its input layer and its output layer.
+Since our target variable is a scalar, the output layer has only one neuron.
+The capacity of a regression metamodel therefore equals to the size of its regression basis.
+On the other hand, the three DNN metamodels have several hidden layers and are much more complex than the two regression metamodels.
+Our FNN has two hidden layers before the output layer.
+Its last hidden layer serves as an automatic feature extraction layer that transforms the 240-dimension feature vector into a 32-dimension vector that can directly relate to the target variable.
+Our RNN and LSTM networks have three hidden layers.
+They contain similar numbers of neurons as the FNN but have deeper network structures.
+For the RNN, two of its hidden layers are recurrent layers that capture the temporal dependency in the feature, and the last hidden layer is a standard feedforward layer that transforms the previous hidden states into a 32-dimension vector for target prediction.
+Our LSTM has the same architecture as the RNN but with LSTM cells in place of the RNN cells.
 
@@
 
-Comparing the two metamodels with recurrent structures, A LSTM network overcomes two key drawbacks of a crude RNN.
+The intuition behind the RNN and LSTM metamodels is briefly mentioned in~\ref{subsec:LSTM}.
+To overcome the overfitting issue of the FNN, RNN learns a single function that operates across all time steps, and the time $t$ itself is not a variable in the RNN.
+The RNN cells in RNN and LSTM networks share parameters across time and serve as a form of regularization that prevents overfitting.
+However, the price that RNN pays for a reduced number of parameters is the difficulty in its optimization.
+Comparing the two metamodels with recurrent structures, a LSTM network overcomes two key drawbacks of a crude RNN.
 \begin{enumerate}
-    \item It avoids the vanishing gradient problem during training, which makes the LSTM network easier to than the RNN.
+    \item It avoids the vanishing gradient problem during training, which makes the LSTM network easier to train than the RNN.
 Figure~\ref{fig2:QQ_RNN} shows the quantile-quantile (QQ) plots between the \textbf{training} labels and the RNN predictions for two macro replications, where training of the latter is hindered by the vanishing gradient problem.
@@
     The last row of Table~\ref{tab:gmwb_arch} shows the average squared errors of the good RNN metamodels that are successfully trained. 
-    Removing the RNN metamodels that are ill-trained, the average squared errors of the RNN metamodels are lower than those of the FNN, but the half lengths of their $95\%$ confidence bands are larger than those of the FNN.
+    Removing the RNN metamodels that are ill-trained, the average squared errors of the RNN metamodels are lower than those of the FNN.
     This suggests that the RNN is more sensitive to noise in stochastic gradient descent than the FNN.
+    They can capture the temporal dependency but are more difficult to optimize.
     \item A LSTM introduces three gates that regulate the flow of information. 

### 2024-12-23 project3/draft.tex
ee
new

@@
 \begin{itemize}
-    \item whether lapse is present and
+    \item whether lapse is present, and
     \item whether the lapse is dynamic.
 \end{itemize}
-This learning process is more challenging.
+This makes learning more challenging.
 
@@
 Table~\ref{tab3:transfer_learning_results_gmwb} summarizes the true MSEs of the LSTM metamodels on the GMWB contracts.
+Training MSE and true MSE are computed using the training labels and the true contract losses approximated with $\num{100000}$ inner replications, respectively.
+This is consistent with the terminology used in Chapter~\ref{chap:project2}.
 The TL methods are compared to training from scratch.
@@
 The fact that fine-tuning outperforms layer freezing suggests that there are significant differences in the tail behavior of GMMB and GMWB contracts, particularly when dynamic lapse is considered. 
-This underscores the need for careful model selection and validation when applying TL techniques to different VA products.
-When the source and target tasks are substantially different, all layers need to be updated, thus freezing some layers may lead to negative transfer.
+These findings highlight the need for careful model selection and validation when applying TL techniques to different VA products.
+When the source and target tasks are substantially different, all layers need to be updated.
+Freezing some layers may lead to negative transfer.
 
@@
 
+\subsection{}
+
 % \begin{figure}[ht!]

### 2025-01-02 pre_private/pre.tex
ee

\documentclass[9pt,handout]{beamer}

\input{StyleFile.tex}

% \setbeameroption{show notes}
% \setbeameroption{show notes on second screen=right}

\title[\textbf{Resilient Machine Learning Approaches for Fast Risk Evaluation and Management in Financial Portfolios and Variable Annuities}]{Efficient Machine Learning Approaches for Fast Risk Evaluation of VAs}

\author[\textbf{Xintong Li, xintong.li1@uwaterloo.ca}]
{\Large\bfseries
Xintong Li\\\medskip
xintong.li1@uwaterloo.ca
} % Your name

\institute[\textbf{University of Waterloo, Actuarial Science}] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{\large\bfseries
Dept. Statistics and Actuarial Science\\\smallskip
University of Waterloo % Your institution for the title page
}

\jointwork{Supervised by Prof. Tony Wirjanto and Prof. Mingbin Feng}
\conference{Thesis Defense, University of Waterloo}

%\usepackage[backend=bibtex,citestyle=authoryear-icomp,natbib,maxcitenames=1]{biblatex}
%\addbibresource{NestedSim.bib}

% use this so appendices' page numbers do not count
\usepackage{appendixnumberbeamer}
\usepackage{booktabs}
\usepackage{subfigure}
\usepackage[round]{natbib}
\usepackage{mathtools}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{algorithmicx}
\usepackage{multirow}
\usepackage{graphicx}

\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}

\newcommand{\E}{\mathbb{E}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\I}{\mathbbm{1}}

\newcommand{\fracM}{\frac{1}{M}}
\newcommand{\fracMM}{\frac{1}{M^2}}
\newcommand{\sumM}{\sum_{i=1}^M}

\newcommand{\fracN}{\frac{1}{N}}
\newcommand{\fracNN}{\frac{1}{N^2}}
\newcommand{\sumN}{\sum_{j=1}^N}

\newcommand{\rhoh}{\hat{\rho}}
\newcommand{\Lh}{\hat{L}}
\newcommand{\betah}{\hat{\beta}}

\newcommand{\Bias}{\textnormal{Bias}}
\newcommand{\Variance}{\textnormal{Variance}}

\newcommand{\SNS}{\textnormal{SNS}}
\newcommand{\REG}{\textnormal{REG}}
\newcommand{\KS}{\textnormal{KS}}
\newcommand{\LR}{\textnormal{LR}}
\newcommand{\KRR}{\textnormal{KRR}}
\newcommand{\skipv}{\vspace{8pt}}

\newtheorem{assumption}{Assumption}
\newtheorem{proposition}{Proposition}

\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\begin{document}

% Title page, navigation surpressed, no page number
{
\beamertemplatenavigationsymbolsempty
\begin{frame}[plain]
\titlepage
\end{frame}
}

{
\beamertemplatenavigationsymbolsempty
\defbeamertemplate*{headline}{miniframes theme no subsection no content}
{ \begin{beamercolorbox}{section in head/foot}
    \vskip\headheight
  \end{beamercolorbox}}
\begin{frame}{Outline}
\tableofcontents
\end{frame}
}
\addtocounter{framenumber}{-2}

\section{Introduction}

\begin{frame}{Nested Simulation Procedures}

Nested simulation procedures are necessary for \textbf{complex} financial derivatives and insurance products.

$$\rho(L) = \rho(L(X)), \;\;\; L(X) = \mathbb{E}\left[ Y|X=x \right]\vert_{x=X}  $$

Involves two levels of Monte Carlo simulations:
\begin{itemize}
    \item Outer level: generates underlying risk factors (outer scenarios), $X_i \sim F_X$
    \item Inner level: generates scenario-wise samples of portfolio losses (inner replications), $Y_{ij} \sim F_{Y|X_i}$
\end{itemize}

\textbf{Computationally expensive due to its nested structure.}

\end{frame}

\begin{frame}{Common Risk Measures}

\begin{itemize}
    \item Smooth $h$, e.g., quadratic tracking error

    $$ \rho(L) = \mathbb{E} \left[ (L - b)^2 \right] $$

    \item hockey-stick $h$: mean excess loss

    $$ \rho(L) = \mathbb{E} \left[ L \cdot \mathbbm{1}_{\{L \geq u\}} \right] $$

    \item indicator $h$: probability of large loss

    $$ \rho(L) = \mathbb{E} \left[ \mathbbm{1}_{\{L \geq u\}} \right] $$

    \item Value at Risk (VaR)

    $$ \rho_\alpha(L) = Q_\alpha(L) = \inf \{ u: \mathbb{P}(L \leq u) \geq \alpha \} $$

    \item Conditional Value at Risk (CVaR) \footnotemark

    $$ \rho_\alpha(L) = \mathbb{E} \left[ L \vert L \geq Q_\alpha(L) \right] $$

    \end{itemize}

    \footnotetext{Note: If $Q_\alpha(L)$ falls in a probability mass, $\rho(L) = \frac{(\beta - \alpha)Q_\alpha(L) + (1- \beta) \mathbb{E} \left[ L \vert L \geq Q_\alpha(L) \right]}{1-\alpha}$.}

\end{frame}

\section{Nested Simulation Procedures in Financial Engineering: A Selected Review}

\begin{frame}{Standard Nested Simulation}

$$\hat{L}_{N, i} = \frac{1}{N} \sum_{j=1}^N Y_{ij}; ~~~ Y_{ij} \sim F_{Y|X_i} $$

\begin{itemize}
    \item Uses inner sample mean to estimate $L(X_i)$.
    \item Proposed by \citet{gordy2010nested}; finds optimal growth order of $M$ and $N$.
    \item \citet{zhang2021bootstrap} estimate the optimal $M$ and $N$ using a bootstrap method.
    \item Computationally expensive and potentially \textbf{wasteful} use of budget.
\end{itemize}

\end{frame}

\begin{frame}{Other Nested Simulation Procedures}

Subsequent works focus on improving the efficiency of nested simulation:
\begin{itemize}
    \item Regression-based~\citep{broadie2015risk}
    \item Kernel smoothing~\citep{hong2017kernel}
    \item Likelihood ratio~\citep{feng2020optimal}
    \item Kernel ridge regression~\citep{zhang2022sample}
\end{itemize}

Key ideas: 
\begin{itemize}
    \item Pool inner replications from different outer scenarios 
    \item Use metamodeling techniques to approximate the inner simulation model
\end{itemize}

\end{frame}

\begin{frame}{Metamodeling Approach}

In this thesis, we focus on procedures that use \textbf{supervised learning metamodels} to approximate the inner simulation model.

\begin{itemize}
    \item Treat the inner simulation as a black-box function
    \item Approximate $L(\cdot)$ with $\hat{L}^{\text{SL}}_{M, N}(\cdot)$
    \item Train with a set of feature-label pairs generated from the standard procedure:
    $$\{(X_i, \hat{L}_{N, i}) \vert i=1, \ldots, M, j=1, \ldots, N\}$$
    \item Use trained metamodel to make predictions for all $X \in \mathcal{X}$
\end{itemize}

There are \textbf{computational costs} associated with pooling inner replications.

\end{frame}

\begin{frame}{Problem Statement}

Minimize mean squared error (MSE) of the estimator subject to total simulation budget:

\begin{align*}
\min_{M, N} ~~~ \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] \\
\text{ subject to } M \cdot N = \Gamma
\end{align*}

Interested in convergence order as $\Gamma \to \infty$

\end{frame}

\subsection{Theoretical Results}

\begin{frame}{Asymptotic Convergence Rates of Different Procedures}

    \begin{table}
		\centering
		\begin{tabular}{l|c|c|c}
			\toprule
			\textbf{Procedures} & \textbf{Smooth $h$} & \textbf{Hockey-Stick $h$} & \textbf{Indicator $h$}  \\
			\midrule
			Standard Procedure	& \textcolor{red}{$\mathcal{O}(\Gamma^{-2/3})$} & \textcolor{red}{$\mathcal{O}(\Gamma^{-2/3})$} & $\mathcal{O}(\Gamma^{-2/3})$ \\
			\midrule
			Regression  & $\mathcal{O}(\Gamma^{-1})$ & $\mathcal{O}(\Gamma^{-1+\delta})$ & No Result \\
			\midrule
			Kernel Smoothing 	& \multicolumn{3}{c}{$\mathcal{O}(\Gamma^{-\min(1, 4/(d+2))})$}  \\
			\midrule
			Kernel Ridge Regression  		& \multicolumn{3}{c}{$\mathcal{O}(\Gamma^{-1})$} \\
			\midrule
			Likelihood Ratio  			& \multicolumn{3}{c}{$\mathcal{O}(\Gamma^{-1})$} \\
			\bottomrule
		\end{tabular}
	\end{table}
    \vspace{10pt}
    \begin{itemize}
        \item We show the asymptotic convergence rates of the standard procedure for smooth and hockey-stick $h$.
        \item Only kernel smoothing depends on the asset dimension $d$.
    \end{itemize}

\end{frame}

\begin{frame}{Key Theoretical Results}

\textbf{Observations:}
\begin{itemize}
\item Most literature focuses on the MSE of $\hat{\rho}$.
\item \citet{wang2022smooth} analyze convergence of absolute error in probabilistic order.
\end{itemize}

\vspace{10pt}

\textbf{Contribution:} bridging the gap between MSE and absolute error convergence.
\begin{itemize}
    \item Convergence in MSE:
    $$ \mathbb{E} \left[ \left( \hat{\rho}_{\Gamma} - \rho \right)^2 \right] = \mathcal{O} \left( \Gamma^{-\xi} \right) $$
    \item Convergence in Probabilistic Order:
    $$ |\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-\xi}) $$
\end{itemize}

\end{frame}

\begin{frame}{Key Theoretical Results}

\begin{block}{Theorem}
    If $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $\xi$, then $\hat{\rho}_{\Gamma}$ converges in probabilistic order to $\rho$ in order $\frac{\xi}{2}$.
\end{block}

\begin{itemize}
    \item First result to draw connection between MSE and probabilistic order convergence.
    \item Applicable to any nested simulation procedure.
    \item Convergence in MSE implies convergence in probabilistic order.
\end{itemize}

\end{frame}

\subsection{Finite-Sample Analysis}

\begin{frame}{Experiment Design}

We compare 5 nested simulation procedures 
\begin{itemize}
    \item Standard nested simulation
    \item Regression-based
    \item Kernel smoothing
    \item Likelihood ratio
    \item Kernel ridge regression
\end{itemize}

And their empirical convergence stable across different:
\begin{itemize}
    \item Risk measures
    \item Option types
    \item Asset dimensions
    \item Asset models (GBM vs. Heston)
    \item Regression bases (only for the regression-based procedure)
\end{itemize}

\end{frame}

\begin{frame}{Finite-Sample Performance}

\begin{figure}
    \includegraphics[width=\textwidth]{../project1/figures/figure1.png}
    \caption{Empirical convergence rates of different procedures for the base case}
\end{figure}

\end{frame}

\begin{frame}{Sensitivity to Asset Dimension}

\begin{figure}
    \includegraphics[width=\textwidth]{../project1/figures/figure2a.png}
\end{figure}

\begin{itemize}
    \item Standard, KRR, and likelihood ratio procedures are dimension-independent
    \item Kernel smoothing and regression show sensitivity to dimension, but in different ways
\end{itemize}

\end{frame}

\begin{frame}{Sensitivity to Asset Dimension}

    \begin{figure}
        \includegraphics[width=\textwidth]{../project1/figures/figure2b.png}
    \end{figure}

    \begin{itemize}
        \item Standard, KRR, and likelihood ratio procedures are dimension-independent
        \item Kernel smoothing and regression show sensitivity to dimension, but in different ways
    \end{itemize}

\end{frame}

\begin{frame}{Fast Convergence of Regression-based Procedure}

\begin{figure}
    \includegraphics[width=\textwidth]{../project1/figures/figure3.png}
\end{figure}

\begin{itemize}
    \item Higher initial convergence rate
    \item Stabilizes to match asymptotic rate at higher budgets
    \item Consistent across different asset dimensions
\end{itemize}

\end{frame}

\begin{frame}{Sensitivity to Option Type}

\begin{figure}
    \includegraphics[width=\textwidth]{../project1/figures/figure6a.png}
\end{figure}

\begin{itemize}
    \item Similar convergence patterns across different option types
    \item Regression and kernel smoothing show higher empirical rates for barrier options
\end{itemize}

\end{frame}

\begin{frame}{Sensitivity to Risk Measure}

\begin{figure}
    \includegraphics[width=\textwidth]{../project1/figures/figure8a.png}
\end{figure}

\begin{itemize}
    \item Convergence behavior consistent across different risk measures
    \item Regression-based method shows highest empirical convergence rates
\end{itemize}

\end{frame}

\begin{frame}{Sensitivity to VaR/CVaR Level}

\begin{figure}
    \includegraphics[width=\textwidth]{../project1/figures/figure9a.png}
\end{figure}

\begin{itemize}
    \item Regression-based method not sensitive to VaR/CVaR level
    \item Consistent performance across different levels
\end{itemize}

\end{frame}

\begin{frame}{Sensitivity to Asset Model}

\begin{figure}
    \includegraphics[width=\textwidth]{../project1/figures/figure10a.png}
\end{figure}

\begin{itemize}
    \item Regression-based method insensitive to asset model (GBM vs. Heston)
    \item Consistent performance across different asset models
\end{itemize}

\end{frame}

\begin{frame}{Computational Complexity}

    There are \textbf{computational costs} associated with pooling inner replications.

    \begin{itemize}
        \item Standard procedure: cost of estimating the optimal $M$ and $N$
        \item Regression: most efficient among metamodel-based procedures
        \item Kernel smoothing: costly distance calculations and cross-validation
        \item Likelihood ratio: No training, but costly weight calculations
        \item KRR: even more expensive than kernel smoothing
    \end{itemize}

\end{frame}

\begin{frame}{Total Computation Time}

    \begin{figure}
        \includegraphics[width=\textwidth]{../project1/figures/figure11b.png}
        \caption{Total computation time for different procedures}
    \end{figure}

\end{frame}

\begin{frame}{Cost of Hyperparameter Tuning}

    \begin{figure}
        \includegraphics[width=\textwidth]{../project1/figures/figure12a.png}
        \caption{Cost of hyperparameter tuning for different procedures}
    \end{figure}

\end{frame}

\begin{frame}{Cost of Model Fitting and Validation}

    \begin{figure}
        \includegraphics[width=\textwidth]{../project1/figures/figure12b.png}
        \caption{Cost of model fitting and validation for different procedures}
    \end{figure}

\end{frame}

\begin{frame}{Conclusion}
    Regression-based nested simulation procedure:
    \begin{itemize}
        \item Most robust and stable for limited budgets
        \item Efficient to implement
        \item Fast empirical convergence for option portfolios
    \end{itemize}

    \vspace{10pt}

    For high-dimensional or complex payoffs:
    \begin{itemize}
        \item Difficult to find a good regression basis
        \item Neural network-based procedures may be more suitable
    \end{itemize}

    \vspace{10pt}

    Next project: examining performance of metamodel-based simulation procedures for variable annuities

\end{frame}

\section{Using Deep Neural Network Metamodels for High-Dimensional Nested Simulation}

\begin{frame}{Introduction}

    \begin{figure}[H]
        \makebox[\textwidth][c]{
            \subfigure{
                \begin{tikzpicture}[scale=0.7]
                \draw[-latex] (0,0)--(2,0);
                \draw[-latex] (2.2,0)--(4,2) node[right]  {$\blacksquare$};
                \draw[-latex] (2.2,0)--(4,0.5) node[right]  {$\blacksquare$};
                \draw[-latex] (2.2,0)--(4,-2) node[right]  {$\blacksquare$};
                \node at (1.2,-0.3) {$X_i$};
                \node at (3.8,-0.7) {$\vdots$};
                \node at (4.2,-0.7) {$\vdots$};
                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (4.5,2.2) --  (4.5,-2.2);
                \node at (5.3,0) {$\hat L_i$};
                \node at (2,-3.1) {1 Outer Path in standard SPNS};
                \end{tikzpicture}}
            \subfigure{
                \begin{tikzpicture}[scale=0.6]
                \draw[-latex] (0,0)--(10,0);
                \draw[-latex] (0,0)--(-1,1.5) node[above] {$\blacksquare$};
                \draw[-latex] (0,0)--(0,1.5) node[above] {$\blacksquare$};
                \draw[-latex] (0,0)--(1,1.5) node[above] {$\blacksquare$};
                \node at (0.5,1.2) {\small$\dots$};
                \node at (0.5,1.85) {\small$\dots$};

                \draw[-latex] (3,0)--(2,1.5) node[above] {$\blacksquare$};
                \draw[-latex] (3,0)--(3,1.5) node[above] {$\blacksquare$};
                \draw[-latex] (3,0)--(4,1.5) node[above] {$\blacksquare$};
                \node at (3.5,1.2) {\small$\dots$};
                \node at (3.5,1.85) {\small$\dots$};

                \draw[-latex] (6,0)--(5,1.5) node[above] {$\blacksquare$};
                \draw[-latex] (6,0)--(6,1.5) node[above] {$\blacksquare$};
                \draw[-latex] (6,0)--(7,1.5) node[above] {$\blacksquare$};
                \node at (6.5,1.2) {\small$\dots$};
                \node at (6.5,1.85) {\small$\dots$};

                \draw[-latex] (9,0)--(8,1.5) node[above] {$\blacksquare$};
                \draw[-latex] (9,0)--(9,1.5) node[above] {$\blacksquare$};
                \draw[-latex] (9,0)--(10,1.5) node[above] {$\blacksquare$};
                \node at (9.5,1.2) {\small$\dots$};
                \node at (9.5,1.85) {\small$\dots$};

                \node at (7.5,0.7) {\Huge $\dots$};

                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (-1,2) --  (1,2);
                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (2,2) --  (4,2);
                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (5,2) --  (7,2);
                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (8,2) --  (10,2);
                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=12pt}] (0,2.4) --  (9,2.4);
                \node at (4.5,-0.5) {$X_i$};
                \node at (4.5,3.5) {$\hat L_i$};
                \node at (4.5,-1.3) {1 Outer Path in standard MPNS};
                \end{tikzpicture}
                }}
	\end{figure}

    Metamodeling: think of the inner simulation as a black-box function.

\end{frame}

\begin{frame}
    \frametitle{References}
    \bibliographystyle{apa}
    \bibliography{../refP1, ../refP2, ../refP3}
\end{frame}
\end{document}

### 2025-01-03 pre_private/pre.tex
we

@@
 
-Key ideas: 
+\vspace{10pt}
+
+\textbf{Key ideas:} 
 \begin{itemize}
@@
 
-\begin{frame}{Introduction}
+\begin{frame}{From Options to Variable Annuities}
+
+    Variable annuities (VAs) poses a challenge for nested simulation due to its \textbf{high-dimensional} and \textbf{complex payoff structure}.
 
@@
                 \draw[-latex] (2.2,0)--(4,-2) node[right]  {$\blacksquare$};
-                \node at (1.2,-0.3) {$X_i$};
+                \node at (1.2,-0.3) {$S_i$};
                 \node at (3.8,-0.7) {$\vdots$};
@@
                 \node at (5.3,0) {$\hat L_i$};
-                \node at (2,-3.1) {1 Outer Path in standard SPNS};
+                \node at (2,-3.1) {1 Outer Path for Options};
                 \end{tikzpicture}}
@@
                 \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=12pt}] (0,2.4) --  (9,2.4);
-                \node at (4.5,-0.5) {$X_i$};
+                \node at (4.5,-0.5) {$S_i$};
                 \node at (4.5,3.5) {$\hat L_i$};
-                \node at (4.5,-1.3) {1 Outer Path in standard MPNS};
+                \node at (4.5,-1.3) {1 Outer Path for VAs};
                 \end{tikzpicture}
@@
 
-    Metamodeling: think of the inner simulation as a black-box function.
+    \begin{itemize}
+        \item Need to reconstruct a metamodeling-based nested simulation procedure
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Nested Simulation for VAs}
+
+    \begin{figure}[c]
+        \includegraphics[width=\textwidth]{../project2/figures/sns.pdf}
+        \caption{Illustration of nested simulation that estimates the P\&L for one outer scenario}
+    \end{figure}
 

### 2025-01-03 pre_private/pre.tex
11

@@
 
-\begin{frame}{Nested Simulation for VAs}
+\begin{frame}{Nested Simulation for Risk Management of VAs}
 
@@
     \end{figure}
+
+\end{frame}
+
+\begin{frame}{Standard Nested Simulation for VAs}
+
+Standard nested simulation for VAs is similar to the one for options.
+
+\begin{itemize}
+    \item Generate $M$ outer scenarios
+    \item For each outer scenario,
+    \begin{itemize}
+        \item Perform $N$ inner simulations
+        \item Estimate hedging loss $L_i$ with $\hat{L}_i$
+    \end{itemize}
+    \item Use estimated losses to calculate tail risk measures (e.g., $95\%$-CVaR)
+\end{itemize}
+
+\vspace{10pt}
+
+\textbf{Main challenge:}
+\begin{itemize}
+    \item Computational budget is limited.
+    \item Accuracy of the estimation depends on both $M$ and $N$.
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Two-Stage LSTM-based Nested Simulation for VAs}
 

### 2025-01-06 pre_private/pre.tex
new

@@
 
-\input{StyleFile.tex}
+\input{./StyleFile.tex}
 
@@
 \usepackage{algorithm}
-\usepackage{algpseudocode}
-\usepackage{algorithmicx}
+\usepackage{algorithmic}
+\usepackage{graphicx}
+\usepackage{subcaption}
+\usepackage{bm}
 \usepackage{multirow}
@@
 \usepackage{tikz}
-\usetikzlibrary{decorations.pathreplacing}
+\usetikzlibrary{shapes,arrows,positioning, calc, fit, decorations.pathreplacing}
 
@@
 \newcommand{\skipv}{\vspace{8pt}}
+
+\definecolor{color10_2}{HTML}{1F77B4}
+\definecolor{color10_3}{HTML}{FF7F0E}
+\definecolor{color10_4}{HTML}{2CA02C}
+\definecolor{color10_5}{HTML}{D62728}
+\definecolor{color10_6}{HTML}{9467BD}
+\definecolor{color10_7}{HTML}{8C564B}
+\definecolor{color10_8}{HTML}{E377C2}
+\definecolor{color10_9}{HTML}{7F7F7F}
+\definecolor{color10_10}{HTML}{BCBD22}
+\definecolor{color10_11}{HTML}{17BECF}
 
@@
 
-\textbf{Main challenge:}
+\textbf{Observations:}
 \begin{itemize}
-    \item Computational budget is limited.
-    \item Accuracy of the estimation depends on both $M$ and $N$.
+    \item computational budget is limited;
+    \item high-dimensional input space;
+    \item only a \textbf{small} portion of scenarios are relevant when estimating \textbf{tail} risk measures.
 \end{itemize}
@@
 
-\begin{frame}{Two-Stage LSTM-based Nested Simulation for VAs}
+\begin{frame}{Metamodel-based Nested Simulation}
+
+    We use deep neural networks (DNNs) as metamodels 
+    \begin{itemize}
+        \item Use LSTMs for sequential data
+        \item \textbf{Challenge}: lack of transparency and interpretability
+    \end{itemize}
+
+    \vspace{20pt}
+
+    \textbf{Research Contributions:}
+    \vspace{6pt}
+    \begin{enumerate}
+        \item Propose two generic DNN-based nested simulation procedures
+        \begin{itemize}
+            \item   Accurate tail scenario identification
+            \item   Significant computational savings by \textbf{budget concentration}
+        \end{itemize}
+        \vspace{6pt}
+        \item Study noise tolerance of DNNs using simulated data
+        \begin{itemize}
+            \item \textbf{Control noise levels} by adjusting simulation parameters
+            \item Provide direct evidence on transparency and interpretability
+        \end{itemize}
+    \end{enumerate}
+
+\end{frame}
+
+\begin{frame}{Two-Stage Metamodel-based Nested Simulation}
+
+\begin{algorithm}[H]
+    \caption{Two-Stage Metamodel-based Nested Simulation for VAs}
+
+\begin{algorithmic}[1]
+    \STATE{\textbf{Generate training data for metamodels:}}
+    \begin{itemize}
+        \item Use a fraction of the simulation budget to run the standard nested simulation procedure with $M$ outer scenarios and $N'$ inner replications.
+        \item Construct feature-label pairs $\{(X_i, Y_{ij}) : i=1, \ldots, M, j=1, \ldots, N'\}$
+    \end{itemize}
+    \STATE{\textbf{Train metamodels:}}
+    \begin{itemize}
+        \item Use the feature-label pairs to train a metamodel.
+        \item Use the trained metamodel to make predictions for $\{X_i: i=1, \ldots, M\}$.
+        \item Sort the predicted losses to identify a predicted tail scenario set that contains the $m$ largest predicted losses.
+    \end{itemize}
+    \STATE{\textbf{Concentrate simulation on predicted tail scenarios:}}
+    \begin{itemize}
+        \item Run the standard procedure on the predicted tail scenarios.
+        \item Estimate the $\alpha$-CVaR of $L$ using the estimated losses on the predicted tail scenarios.
+    \end{itemize}
+\end{algorithmic}
+\end{algorithm}
+
+\end{frame}
+
+\begin{frame}{Benefits of a Two-Stage Procedure}
+
+Simulation budget can be saved when:
+\begin{itemize}
+    \item the metamodel is accurate (a small $m$ includes most tail scenarios)
+    \item the metamodel can tolerate noise in training labels (a small $N'$)
+\end{itemize}
+
+\vspace{10pt}
+
+\textbf{Key findings:}
+\begin{itemize}
+    \item Substantial computational savings ($70\% - 85\%$ reduction)
+    \item Maintains accuracy comparable to standard procedure
+    \item DNN metamodels can distinguish between tail and non-tail scenarios effectively
+    \item Addresses regulatory concerns by using actual simulations for final estimates
+\end{itemize}
+
+\vspace{10pt}
+\textbf{Another finding:} 
+some DNN metamodels make \textbf{accurate loss predictions} for given scenarios.
+
+\end{frame}
+
+\begin{frame}{Single-Stage Metamodel-based Nested Simulation}
+
+\begin{algorithm}[H]
+\caption{Single-Stage Metamodel-based Nested Simulation for VAs}
+\begin{algorithmic}[1]
+    \STATE{\textbf{Generate training data for metamodels:}}
+    \begin{itemize}
+        \item Use the entire simulation budget to run the standard nested simulation procedure with $M$ outer scenarios and $N$ inner replications.
+        \item Construct feature-label pairs $\{(X_i, Y_{ij}) : i=1, \ldots, M, j=1, \ldots, N\}$
+    \end{itemize}
+    \STATE{\textbf{Train metamodels:}}
+    \begin{itemize}
+        \item Use the feature-label pairs to train a metamodel.
+        \item Use the trained metamodel to make predictions for $\{X_i: i=1, \ldots, M\}$.
+    \end{itemize}
+    \STATE{\textbf{Use metamodel predictions to estimate tail risk measures directly.}}
+\end{algorithmic}
+\end{algorithm}
+
+\textbf{Key advantages:}
+\begin{itemize}
+    \item more efficient than a two-stage procedure;
+    \item avoids specifying $m$;
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Experiment Setting}
+
+    We estimate the $95\%$-CVaR of the hedging loss for a GMWB contract with 20-year maturity.
+
+    \vspace{10pt}
+
+    \textbf{Specifications:}
+    \begin{itemize}
+        \item The underlying asset follows a regime-switching geometric Brownian motion;
+        \item The contract is delta-hedged monthly (240 periods);
+        \item The true $95\%$-CVaR is estimated using 100,000 outer scenarios and 100,000 inner replications.
+        \item The metamodel is trained using 90,000 outer scenarios and 100 inner replications.
+        \item Benchmark: standard nested simulation procedure with 100,000 outer scenarios and 1,000 inner replications.
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Experiment Design}
+
+    \textbf{Research Questions:}
+    \begin{itemize}
+        \item What do DNNs learn from noisy data?
+        \item How well do DNNs learn from noisy data?
+    \end{itemize}
+
+    \begin{figure}[H]
+        \includegraphics[width=\textwidth]{../project2/figures/datasets.png}
+    \end{figure}
+
+    \begin{itemize}
+        \item Our 90,000 training data is noisy, and the test data is also \textbf{noisy}.
+        \item Our evaluation is based on the true (\textbf{noiseless}) feature-label relationship\footnotemark.
+    \end{itemize}
+
+    \footnotetext{Made possible by novel simulation design.}
+
+\end{frame}
+
+\begin{frame}{Experiment Setting}
+
+    We consider the following metamodel architectures:
+
+    \begin{table}[ht!]
+        \centering
+        \begin{tabular}{lcc}
+            \toprule
+            \textbf{Metamodel} & \textbf{Abbreviation} & \textbf{Capacity} \\
+            \midrule
+            Multiple Linear Regression      & MLR       & 241 \\
+            Quadratic Polynomial Regression & QPR       & 481 \\
+            Feedforward Neural Network      & FNN       & 35,009 \\
+            Recurrent Neural Network        & RNN       & 32,021 \\
+            Long Short-Term Memory          & LSTM      & 35,729 \\
+            \bottomrule
+        \end{tabular}
+        \caption{Metamodel architectures for GMWB inner simulation model}
+        \label{tab:arch}
+    \end{table}
+
+    Capacity is defined as the number of parameters in the metamodel.
+    \begin{itemize}
+        \item   Higher capacity metamodels are more flexible and expressive.
+        \item   Lower capacity metamodels are less likely to overfit.
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Traditional Regression Metamodels}
+
+    \begin{figure}[H]
+        \includegraphics[width=0.48\textwidth]{../project2/figures/qqPlots/mlrLN.png}
+        \includegraphics[width=0.48\textwidth]{../project2/figures/qqPlots/qprLN.png}
+        \caption{QQ plots between true and predicted loss labels for MLR and QPR metamodels}
+    \end{figure}
+
+    \begin{itemize}
+        \item   MLR and QPR metamodels make \textbf{inaccurate} loss predictions.
+        \item   Feature engineering is hardly feasible for our 240-dimensional $X$.
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Deep Neural Network Metamodels}
+
+    \begin{figure}[H]
+        \includegraphics[width=0.48\textwidth]{../project2/figures/qqPlots/fnnLN.png}
+        \includegraphics[width=0.48\textwidth]{../project2/figures/qqPlots/lstmLoCapLN.png}
+        \caption{QQ plots between true and predicted loss labelsfor FNN and LSTM metamodels}
+    \end{figure}
+
+    \begin{itemize}
+        \item   DNN metamodels are more flexible.
+        \item   Time series features prefer a LSTM metamodel over FNN.
+        \item   Network architecture serves as prior knowledge that regularizes DNNs.
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Metamodel Performance on Different Datasets}
+
+    \begin{table}[ht!]
+        \centering
+        \small
+        \begin{tabular}{lccc}
+        \toprule
+        \textbf{Metamodel} & \textbf{Training error} & \textbf{Test error} & \textbf{True error}\\
+        \midrule
+        MLR & $0.706 (\pm 8.34\times 10^{-4})$ & $0.713 (\pm 2.67 \times 10^{-2})$ & $0.706 (\pm 3.44 \times 10^{-4})$ \\
+        QPR & $0.543 (\pm 8.27\times 10^{-4})$ & $0.554 (\pm 2.32 \times 10^{-2})$ & $0.544 (\pm 4.12\times 10^{-4})$ \\
+        FNN & $0.129 (\pm 5.95\times 10^{-3})$ & $0.240 (\pm 9.82 \times 10^{-3})$ & $0.132 (\pm 5.82\times 10^{-3})$ \\
+        RNN & $0.132 (\pm 7.53\times 10^{-3})$ & $0.137 (\pm 7.62\times 10^{-3})$ & $0.119 (\pm 7.51\times 10^{-3})$ \\
+        LSTM & $0.075 (\pm 4.48\times 10^{-3})$ & $0.079 (\pm 5.35\times 10^{-3})$ & $0.063 (\pm 4.43\times 10^{-3})$ \\
+        RNN$^*$\footnotemark & $0.109 (\pm 5.20\times 10^{-3})$ & $0.128 (\pm 5.22\times 10^{-3})$ & $0.109 (\pm 5.20\times 10^{-3})$ \\
+        \bottomrule
+        \end{tabular}
+        \caption{MSEs of metamodels for GMWB inner simulation model.}
+        \label{tab:gmwb_arch}
+    \end{table}
+
+    \footnotetext{This row summarizes the results of the well-trained RNNs.}
+
+    \begin{itemize}
+        \item   DNN metamodels with suitable architectures \textbf{cut through the noise} in training labels.
+        \item   
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Issues with RNNs}
+
+    \begin{figure}[H]
+        \includegraphics[width=0.48\textwidth]{../project2/figures/qqPlots/rnnGood_training.png}
+        \includegraphics[width=0.48\textwidth]{../project2/figures/qqPlots/rnnBad_training.png}
+        \caption{QQ plots between training and predicted loss labels for RNN metamodels}
+    \end{figure}
+
+    \begin{itemize}
+        \item   RNN metamodels suffers from \textbf{vanishing gradient problem}.
+        \item   Ease of training (reliability) is a critical factor when choosing a DNN metamodel.
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Safety Margin}
+
+    Consider estimating the $95\%$ CVaR with 100,000 outer scenarios.
+    \begin{figure}
+        \centering
+        \begin{tikzpicture}[scale=1]
+            % Make the height of the solid rectangle half.
+            \draw[line width=1pt, fill=gray, fill opacity=0.40] (0,0) rectangle (3,1); 
+            % Adjust node positions for the new height.
+            \node[above] at (1.5, 0.5) {5\% \textbf{true} tails}; 
+            \node[above] at (1.5, 0) {(5,000 scenarios)};
+            % Adjust the dashed lines for the new height.
+            \draw[dashed, line width=1pt] (3,0) -- (10,0); 
+            \node[above] at (6.5, 0.3) {non-tails};
+            \draw[dashed, line width=1pt] (3,1) -- (10,1); 
+            \node[above] at (9.5, 0.3) {...};
+        \end{tikzpicture}
+    \end{figure}
+    \begin{figure}
+        \centering
+        \begin{tikzpicture}[scale=1]
+            % Make the height of the solid rectangle half.
+            \draw[line width=1pt, fill=gray, fill opacity=0.20] (0,0) rectangle (3,1);
+            % Adjust node positions for the new height.
+            \node[above] at (1.5, 0.5) {5\% \textbf{predicted} tails};
+            \node[above] at (1.5, 0) {(5,000 scenarios)};
+            % Adjust the dashed boxes for the new height.
+            \draw[dashed, line width=1pt, fill=gray, fill opacity=0.10] (3,0) rectangle (5,1);
+            \node[above] at (4, 0.5) {+2\% margin};
+            \node[above] at (4, 0) {(2,000 more)};
+            \draw[dashed, line width=1pt, fill=gray, fill opacity=0.10] (5,0) rectangle (7,1);
+            \node[above] at (6, 0.5) {+2\% margin};
+            \node[above] at (6, 0) {(2,000 more)};
+            % Adjust the dashed lines for the new height.
+            \draw[dashed, line width=1pt] (7,0) -- (10,0);
+            \draw[dashed, line width=1pt] (7,1) -- (10,1);
+            \node[above] at (9.5, 0.3) {...};
+        \end{tikzpicture}
+    \end{figure}
+
+    \vspace{10pt}
+
+    Choosing a safety margin: a trade-off between accuracy and efficiency.
+    \begin{itemize}
+        \item   A lower margin: not enough tail identified.
+        \item   A higher margin: more accurate CVaR estimate, but more budget needed to perform extensive inner simulations.
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Tail Scenario Identification}
+
+    \begin{figure}[H]
+        \includegraphics[width=0.48\textwidth]{../project2/figures/tailMatches/regLN.png}
+        \includegraphics[width=0.48\textwidth]{../project2/figures/tailMatches/nnLN.png}
+        \caption{Tail scenario identification for regression and DNN metamodels}
+    \end{figure}
+
+    \begin{itemize}
+        \item Traditional regression metamodels are \textbf{unable} to accurately identify tail scenarios even with high safety margins.
+        \item LSTM metamodels surpasses the standard procedure with $5\%$ safety margin.
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Estimating CVaR}
+
+    \begin{figure}[H]
+        \includegraphics[width=0.48\textwidth]{../project2/figures/CVaR/allLN.png}
+        \includegraphics[width=0.48\textwidth]{../project2/figures/CVaR/zoomedLN.png}
+        \caption{CVaR estimation for DNN metamodels}
+    \end{figure}
+
+    \begin{itemize}
+        \item Traditional regression metamodels are \textbf{unable} to accurately estimate CVaR even with high safety margins.
+        \item LSTM surpasses the standard procedure with a \textbf{5\% safety margin}.
+        \item With a 95\% safety margin, any two-stage procedure produce the same CVaR estimate as a standard procedure.
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Sensitivity Testing for DNNs}
+
+    In a simulation study, we have control over the \textbf{noise level in training labels} and the \textbf{number of training samples}.
+
+    \vspace{10pt}
+
+    Controling the inner replications $N'$ varies the noise level in training labels.
+
+    \begin{itemize}
+        \item   \textbf{Low noise labels}: $N' = 100$
+        \item   \textbf{Medium noise labels}: $N' = 10$
+        \item   \textbf{High noise labels}: $N' = 1$
+    \end{itemize}
+
+    \vspace{10pt}
+
+    Controling the outer scenarios $M$ varies the number of training samples.
+
+    \begin{itemize}
+        \item $M \in \{10^2, 10^3, 10^4, 10^5\}$
+    \end{itemize}
+
+    \vspace{10pt}
+
+    2 LSTMs of \textbf{different capacities} are examined based on their MSEs.
+
+\end{frame}
+
+\begin{frame}{Noise Tolerance of DNNs}
+
+    \begin{table}[ht!]
+        \centering
+        \begin{tabular}{lccccc}
+            \toprule
+            \textbf{Model}      & \textbf{$N'$}         & \textbf{Training error}                & \textbf{Test error}               & \textbf{True error}\\
+            \midrule
+            LSTM                & $100$                & $0.075$         & $0.079$     & $0.063$ \\ 
+            High-capacity LSTM  & $100$                & $0.068$         & $0.102$     & $0.060$ \\
+            Average Difference  & $100$                & $-0.007$       & $0.023$     & $-0.003$ \\
+            \hline
+            LSTM                & $10$                 & $0.195$         & $0.193$     & $0.070$ \\
+            High-capacity LSTM  & $10$                 & $0.157$         & $0.199$     & $0.065$ \\
+            Average Difference  & $10$                 & $-0.038$       & $0.006$     & $-0.005$ \\
+            \hline
+            LSTM                & $1$                  & $1.366$         & $0.781$     & $0.129$ \\
+            High-capacity LSTM  & $1$                  & $1.354$         & $0.795$     & $0.149$ \\
+            Average Difference  & $1$                  & $-0.012$       & $0.014$     &\textcolor{color10_5}{$0.020$} \\
+            \bottomrule
+        \end{tabular}
+        \caption{MSEs of LSTM metamodels.}
+    \end{table}
+
+    \begin{itemize}
+        \item   Both LSTMs cut through the noise in training labels.
+        \item   Both LSTMs deteriorate dramatically on \textbf{high-noise} labels.
+        \item   High-capacity LSTM can tolerate \textbf{low} and \textbf{medium} label noise.
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Noise Tolerance of DNNs}
+
+    \begin{figure}[ht!]
+        \centering
+        \includegraphics[width=\textwidth]{../project2/figures/qqPlots/lstmAll.png}
+    \end{figure}
+
+\end{frame}
+
+\begin{frame}{Sensitivity of Regular LSTM}
+
+    \begin{table}[ht!]
+        \centering
+        \begin{tabular}{lccccc}
+            \toprule
+                           & $N'=1$   & $N'=10$  & $N'=100$ & $N'=1000$\\
+            \midrule
+            $M = 100$      & \textcolor{color10_2}{$1.139$} & \textcolor{color10_3}{$0.229$} & \textcolor{color10_4}{$0.167$} & \textcolor{color10_5}{$0.158$} \\
+            $M = 1000$     & \textcolor{color10_3}{$0.559$} & \textcolor{color10_4}{$0.173$} & \textcolor{color10_5}{$0.123$} & \textcolor{color10_6}{$0.127$} \\
+            $M = 10000$    & \textcolor{color10_4}{$0.283$} & \textcolor{color10_5}{$0.115$} & \textcolor{color10_6}{$0.099$} & \textcolor{color10_7}{$0.097$} \\
+            $M = 100000$   & \textcolor{color10_5}{$0.129$} & \textcolor{color10_6}{$0.070$} & \textcolor{color10_7}{$0.063$} & \textcolor{color10_8}{$0.063$} \\
+            \bottomrule
+        \end{tabular}
+        \caption{MSE between regular LSTM's predicted losses and true losses.}
+    \end{table}
+
+    \begin{itemize}
+        \item   Same color $\rightarrow$ same total simulation budget.
+        \item   $N = 10$ is a reasonable budget allocation for LSTM metamodels.
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Sensitivity of High-capacity LSTM}
+
+    \begin{table}[ht!]
+        \centering
+        \begin{tabular}{lccccc}
+            \toprule
+            & $N'=1$ & $N'=10$  & $N'=100$ & $N'=1000$\\
+            \midrule
+            $M = 100$      & \textcolor{color10_2}{$0.764$} & \textcolor{color10_3}{$0.408$} & \textcolor{color10_4}{$0.131$} & \textcolor{color10_5}{$0.087$} \\
+            $M = 1000$     & \textcolor{color10_3}{$0.878$} & \textcolor{color10_4}{$0.367$} & \textcolor{color10_5}{$0.156$} & \textcolor{color10_6}{$0.087$} \\
+            $M = 10000$    & \textcolor{color10_4}{$0.351$} & \textcolor{color10_5}{$0.147$} & \textcolor{color10_6}{$0.064$} & \textcolor{color10_7}{$0.063$} \\
+            $M = 100000$   & \textcolor{color10_5}{$0.149$} & \textcolor{color10_6}{$0.065$} & \textcolor{color10_7}{$0.060$} & \textcolor{color10_8}{$0.038$} \\
+            \bottomrule
+        \end{tabular}
+        \caption{MSE between high-capacity LSTM's predicted losses and true losses.}
+    \end{table}
+
+    \begin{itemize}
+        \item   Same color $\rightarrow$ same total simulation budget.
+        \item   $N' = 10$ is a reasonable budget allocation for LSTM metamodels.
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Single-Stage Procedure}
+
+    \begin{figure}[ht!]
+        \centering
+        \includegraphics[width=0.48\textwidth]{../project2/figures/singleStage/CVaRmediumNoise.png}
+        \includegraphics[width=0.48\textwidth]{../project2/figures/singleStage/CVaRhighNoise.png}
+        \caption{CVaR estimates of single-stage procedures (left: $N' = 10$. right: $N' = 1$).}
+    \end{figure}
+
+    \begin{itemize}
+        \item   The single-stage procedure outperforms the two-stage procedure.
+        \item   The single-stage procedure is more efficient than the two-stage procedure.
+        \item   Setting $N' = 10$ is a reasonable budget allocation.
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Convergence Analysis}
+
+    For each $\Gamma$, the best performing metamodel is used.
+
+    \begin{itemize}
+        \item   Maximum number of outer scenarios $M = 10^5$.
+    \end{itemize}
+
+    \begin{figure}[ht!]
+        \centering
+        \includegraphics[width=0.48\textwidth]{../project2/figures/singleStage/MSEConvergence_lstmLoCap.png}
+        \includegraphics[width=0.48\textwidth]{../project2/figures/singleStage/MSEConvergence_lstmHiCap.png}
+        \caption{Empirical convergence of CVaR for single-stage procedures with LSTM metamodels (left: regular LSTM. right: high-capacity LSTM).}
+    \end{figure}
+
+    \begin{itemize}
+        \item   Minimal effect of increasing $N'$ on CVaR estimation.
+        \item   Similar behavior as regression metamodels ($d=20$) in the previous section.
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Convergence Analysis}
+    \begin{figure}[ht!]
+        \centering
+        \includegraphics[width=\textwidth]{../project2/figures/singleStage/MSEConvergence_lstmLoCap_MN.png}
+        \caption{Empirical convergence of the single-stage procedure with a LSTM metamodel.} 
+    \end{figure}
+
+    \begin{itemize}
+        \item   Minimal effect of increasing $N'$ on CVaR estimation.
+        \item   For a given $\Gamma$, set $N'$ constant and allocate budget to outer simulations.
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Conclusion}
+
+    \textbf{Key Findings:}
+    \begin{itemize}
+        \item   LSTMs are \textbf{resilient} to moderate levels of noise in training labels.
+        \item   Deep neural networks can learn \textbf{true} complex dynamic hedging model.
+        \item   Two-stage procedure addresses regulatory concerns by avoiding direct use of metamodel predictions.
+        \item   Single-stage procedure is \textbf{efficient} and \textbf{versatile}.
+        \item   \textbf{Increasing outer scenarios} is more beneficial.
+        \item   High-capacity LSTM requires lower noise training labels.
+    \end{itemize}
+
+    \vspace{10pt}
+
+    \textbf{Future Directions:}
+    \begin{itemize}
+        \item   Apply deep neural network metamodels to other risk management tasks.
+        \item   Investigate impact of label noise on other deep learning models 
+        \item   Explore optimal network architectures for different simulation models.
+    \end{itemize}
+
+\end{frame}
+
+\section{Transfer Learning for Dynamic Hedging}
+\begin{frame}{Transfer Learning for Dynamic Hedging}
 

### 2025-01-07 pre_private/pre.tex
new

@@
 \usepackage{booktabs}
-\usepackage{subfigure}
 \usepackage[round]{natbib}
 \usepackage{mathtools}
+% \usepackage{subfigure}
 
@@
 \usepackage{algorithmic}
+\usepackage{subcaption}
 \usepackage{graphicx}
-\usepackage{subcaption}
 \usepackage{bm}
-\usepackage{multirow}
-\usepackage{graphicx}
 
@@
 \usetikzlibrary{shapes,arrows,positioning, calc, fit, decorations.pathreplacing}
-
-\newcommand{\E}{\mathbb{E}}
-\newcommand{\R}{\mathbb{R}}
-\newcommand{\I}{\mathbbm{1}}
-
-\newcommand{\fracM}{\frac{1}{M}}
-\newcommand{\fracMM}{\frac{1}{M^2}}
-\newcommand{\sumM}{\sum_{i=1}^M}
-
-\newcommand{\fracN}{\frac{1}{N}}
-\newcommand{\fracNN}{\frac{1}{N^2}}
-\newcommand{\sumN}{\sum_{j=1}^N}
-
-\newcommand{\rhoh}{\hat{\rho}}
-\newcommand{\Lh}{\hat{L}}
-\newcommand{\betah}{\hat{\beta}}
-
-\newcommand{\Bias}{\textnormal{Bias}}
-\newcommand{\Variance}{\textnormal{Variance}}
-
-\newcommand{\SNS}{\textnormal{SNS}}
-\newcommand{\REG}{\textnormal{REG}}
-\newcommand{\KS}{\textnormal{KS}}
-\newcommand{\LR}{\textnormal{LR}}
-\newcommand{\KRR}{\textnormal{KRR}}
-\newcommand{\skipv}{\vspace{8pt}}
 
@@
 
+    \vspace{10pt}
+
     \begin{figure}[H]
-        \makebox[\textwidth][c]{
-            \subfigure{
-                \begin{tikzpicture}[scale=0.7]
-                \draw[-latex] (0,0)--(2,0);
-                \draw[-latex] (2.2,0)--(4,2) node[right]  {$\blacksquare$};
-                \draw[-latex] (2.2,0)--(4,0.5) node[right]  {$\blacksquare$};
-                \draw[-latex] (2.2,0)--(4,-2) node[right]  {$\blacksquare$};
-                \node at (1.2,-0.3) {$S_i$};
-                \node at (3.8,-0.7) {$\vdots$};
-                \node at (4.2,-0.7) {$\vdots$};
-                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (4.5,2.2) --  (4.5,-2.2);
-                \node at (5.3,0) {$\hat L_i$};
-                \node at (2,-3.1) {1 Outer Path for Options};
-                \end{tikzpicture}}
-            \subfigure{
-                \begin{tikzpicture}[scale=0.6]
-                \draw[-latex] (0,0)--(10,0);
-                \draw[-latex] (0,0)--(-1,1.5) node[above] {$\blacksquare$};
-                \draw[-latex] (0,0)--(0,1.5) node[above] {$\blacksquare$};
-                \draw[-latex] (0,0)--(1,1.5) node[above] {$\blacksquare$};
-                \node at (0.5,1.2) {\small$\dots$};
-                \node at (0.5,1.85) {\small$\dots$};
-
-                \draw[-latex] (3,0)--(2,1.5) node[above] {$\blacksquare$};
-                \draw[-latex] (3,0)--(3,1.5) node[above] {$\blacksquare$};
-                \draw[-latex] (3,0)--(4,1.5) node[above] {$\blacksquare$};
-                \node at (3.5,1.2) {\small$\dots$};
-                \node at (3.5,1.85) {\small$\dots$};
-
-                \draw[-latex] (6,0)--(5,1.5) node[above] {$\blacksquare$};
-                \draw[-latex] (6,0)--(6,1.5) node[above] {$\blacksquare$};
-                \draw[-latex] (6,0)--(7,1.5) node[above] {$\blacksquare$};
-                \node at (6.5,1.2) {\small$\dots$};
-                \node at (6.5,1.85) {\small$\dots$};
-
-                \draw[-latex] (9,0)--(8,1.5) node[above] {$\blacksquare$};
-                \draw[-latex] (9,0)--(9,1.5) node[above] {$\blacksquare$};
-                \draw[-latex] (9,0)--(10,1.5) node[above] {$\blacksquare$};
-                \node at (9.5,1.2) {\small$\dots$};
-                \node at (9.5,1.85) {\small$\dots$};
-
-                \node at (7.5,0.7) {\Huge $\dots$};
-
-                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (-1,2) --  (1,2);
-                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (2,2) --  (4,2);
-                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (5,2) --  (7,2);
-                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (8,2) --  (10,2);
-                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=12pt}] (0,2.4) --  (9,2.4);
-                \node at (4.5,-0.5) {$S_i$};
-                \node at (4.5,3.5) {$\hat L_i$};
-                \node at (4.5,-1.3) {1 Outer Path for VAs};
-                \end{tikzpicture}
-                }}
-	\end{figure}
+            \includegraphics[width=0.33\textwidth]{./tikz/illustration_spns.pdf}
+            \includegraphics[width=0.62\textwidth]{./tikz/illustration_mpns.pdf}
+	\end{figure}
+
+    \vspace{10pt}
 
@@
     \item more efficient than a two-stage procedure;
-    \item avoids specifying $m$;
+    \item avoids specifying $m$.
 \end{itemize}
@@
         \end{tikzpicture}
-    \end{figure}
-
-    \vspace{10pt}
+        \caption{Illustration: a safety margin of $4\%$ ($m = 9000$)}
+    \end{figure}
 
@@
 
-\section{Transfer Learning for Dynamic Hedging}
-\begin{frame}{Transfer Learning for Dynamic Hedging}
+\section{Transfer Learning for Rapid Adaptation of DNN Metamodels}
+\begin{frame}{Transfer Learning for Rapid Adaptation of DNN Metamodels}
+
+    \textbf{Challenge:} Adapting deep neural network metamodels to changing conditions.
+    \begin{itemize}
+        \item   Retraining from scratch is computationally expensive.
+        \item   Efficient incorporation of new VA contract data.
+        \item   Balancing model accuracy and computational costs.
+    \end{itemize}
+
+    \vspace{10pt}
+
+    \textbf{Solution:} Transfer learning (TL) to develop adaptable, efficient metamodels for VA dynamic hedging.
+
+    \begin{itemize}
+        \item   Pre-train deep neural network on contracts with abundant simulation data.
+        \item   Fine-tune on smaller dataset of new contracts/market conditions.
+        \item   Leverages shared features between VA contracts.
+        \item   Computational savings:
+            \begin{itemize}
+                \item   Reduced training time.
+                \item   Fewer data points needed for good performance.
+            \end{itemize}
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Transfer Learning Framework}
+
+    \textbf{Key Components:}
+    \begin{itemize}
+        \item   \textbf{Domain} $\mathcal{D}$: feature space $\mathcal{X}$ + probability distribution $F$
+        \item   \textbf{Task} $\mathcal{T}$: label space $\mathcal{Y}$ + predictive function $f: \mathcal{X} \rightarrow \mathcal{Y}$
+    \end{itemize}
+
+    \vspace{10pt}
+    \textbf{Source vs. Target:}
+    \begin{itemize}
+        \item   \textbf{Source:} $\mathcal{D}_{\text{So}} = \{\mathcal{X}_{\text{So}}, F_{\text{So}}(X)\}$
+        \item   \textbf{Target:} $\mathcal{D}_{\text{Ta}} = \{\mathcal{X}_{\text{Ta}}, F_{\text{Ta}}(X)\}$
+    \end{itemize}
+
+    \vspace{10pt}
+    \textbf{Our Goal:}
+    \begin{itemize}
+        \item   \textbf{Input features} $X$: risk factors from outer simulation
+        \item   \textbf{Output labels} $L$: contract losses
+        \item   \textbf{Source and target}: from VAs with abundant simulation data to new VAs with limited data
+        \item   \textbf{Goal}: improve $f_{\text{Ta}}(\cdot)$ using knowledge from $\mathcal{D}_{\text{So}}$ and $f_{\text{So}}(\cdot)$
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Transfer Learning Techniques}
+
+    \textbf{Common Techniques:}
+    \begin{itemize}
+        \item   \textbf{Fine-tuning:} a model pre-trained on a source task is used as a starting point for a target task.
+        \item   \textbf{Layer freezing:} only part of the model is fine-tuned.
+        \item   \textbf{Multi-task learning:} perform training on multiple tasks simultaneously.
+    \end{itemize}
+
+    \vspace{10pt}
+
+    \textbf{Key considerations:}
+    \begin{itemize}
+        \item   Similarity between source and target tasks
+        \item   Appropriate learning rate
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Fine-tuning Algorithm for LSTM Metamodels in VA Hedging}
+
+    \begin{algorithm}[H]
+        \caption{Fine-tuning Algorithm for LSTM Metamodels in VA Hedging}
+        \begin{algorithmic}[1]
+            \STATE \textbf{Input:} $\mathcal{D}_{\text{So}} = \{(X_{\text{So}}^{(i)}, L_{\text{So}}^{(i)})\}_{i=1}^{M_{\text{So}}}$ , $\mathcal{D}_{\text{Ta}} = \{(X_{\text{Ta}}^{(i)}, L_{\text{Ta}}^{(i)})\}_{i=1}^{M_{\text{Ta}}}$, $\alpha_{\text{So}}$, and $\alpha_{\text{Ta}}$.
+            \STATE Train a LSTM metamodel $f_{\text{So}}(\cdot; \theta_{\text{So}})$ on $\mathcal{D}_{\text{So}}$:
+            \begin{equation*}
+                \theta_{\text{So}} = \min_{\theta} \frac{1}{M_{\text{So}}} \sum_{i=1}^{M_{\text{So}}} \left( f_{\text{So}}(X_{\text{So}}^{(i)}; \theta) - L_{\text{So}}^{(i)} \right)^2
+            \end{equation*}
+            \STATE Initialize the target metamodel parameters $\theta_{\text{Ta}}$ using the pre-trained metamodel parameters:
+            \begin{equation*}
+                \theta_{\text{Ta}} \gets \theta_{\text{So}}
+            \end{equation*}
+            \STATE Fine-tune the entire LSTM metamodel $f_{\text{Ta}}(\cdot; \theta_{\text{Ta}})$ on the target dataset $\mathcal{D}_{\text{Ta}}$ using a smaller learning rate $\alpha_{\text{Ta}}$:
+            \begin{equation*}
+                \theta_{\text{Ta}} = \min_{\theta} \frac{1}{M_{\text{Ta}}} \sum_{i=1}^{M_{\text{Ta}}} \left( f_{\text{Ta}}(X_{\text{Ta}}^{(i)}; \theta) - L_{\text{Ta}}^{(i)} \right)^2
+            \end{equation*}
+            \STATE \textbf{Output:} Final adapted LSTM metamodel $f_{\text{Ta}}(\cdot; \theta_{\text{Ta}})$ for the target task
+        \end{algorithmic}
+    \end{algorithm}
+
+\end{frame}
+
+\begin{frame}{Layer Freezing Algorithm for LSTM Metamodels in VA Hedging}
+
+    \begin{algorithm}[H]
+        \caption{Layer Freezing Algorithm for LSTM Metamodels in VA Hedging}
+        \begin{algorithmic}[1]
+            \STATE \textbf{Input:} $\mathcal{D}_{\text{So}} = \{(X_{\text{So}}^{(i)}, L_{\text{So}}^{(i)})\}_{i=1}^{M_{\text{So}}}$ , $\mathcal{D}_{\text{Ta}} = \{(X_{\text{Ta}}^{(i)}, L_{\text{Ta}}^{(i)})\}_{i=1}^{M_{\text{Ta}}}$, $\alpha_{\text{So}}$, and $\alpha_{\text{Ta}}$.
+            \STATE Train LSTM model $f_{\text{So}}(\cdot; \theta_{\text{So}})$ on $\mathcal{D}_{\text{So}}$.
+            \STATE Initialize the target model parameters $\theta_{\text{Ta}} = [\theta_0, \theta_1]$ using the pre-trained source model parameters $\theta_{\text{So}}$:
+            \begin{equation*}
+                \theta_{\text{Ta}} \gets \theta_{\text{So}} = [\theta_0, \theta_1]
+            \end{equation*}
+            \STATE Freeze the parameters of the shared layers $\theta_0$ and fine-tune the trainable layers $\theta_1$ on the target dataset $\mathcal{D}_{\text{Ta}}$:
+            \begin{equation*}
+                \theta_{\text{Ta}} = \min_{\theta_1} \frac{1}{M_{\text{Ta}}} \sum_{i=1}^{M_{\text{Ta}}} \left( f_{\text{Ta}}(X_{\text{Ta}}^{(i)}; [\theta_0, \theta_1]) - L_{\text{Ta}}^{(i)} \right)^2
+            \end{equation*}
+            \STATE \textbf{Output:} Adapted model $f_{\text{Ta}}(\cdot; \theta_{\text{Ta}})$ for the target task.
+        \end{algorithmic}
+    \end{algorithm}
+
+\end{frame}
+
+\begin{frame}{Multi-task Learning Algorithm for LSTM Metamodels in VA Hedging}
+
+    \begin{algorithm}[H]
+        \caption{Multi-task Learning Algorithm for LSTM Metamodels in VA Hedging}
+        \begin{algorithmic}[1] \label{alg3:multiTaskLearning}
+            \STATE \textbf{Input:} learning rate $\alpha$, set of $K$ tasks $\{\mathcal{T}_k\}_{k=1}^K$ with datasets $\mathcal{D}_k = \{(X_k^{(i)}, L_k^{(i)})\}_{i=1}^{M_k}$, task-specific parameters $\theta_k$ for each task $k$, and shared parameters $\theta_0$.
+
+            \STATE Train the multi-head LSTM metamodel on all $K$ tasks simultaneously by minimizing the multi-task loss function:
+            \begin{equation} \label{eq3:multiTaskLoss}
+                \min_{\theta_0, \{\theta_k\}_{k=1}^K} \sum_{k=1}^K \frac{1}{M_k} \sum_{i=1}^{M_k} \left( f_i(X_k^{(i)}; \theta_0, \theta_k) - L_k^{(i)} \right)^2
+            \end{equation}
+
+            \STATE Update both the shared parameters $\theta_0$ and task-specific parameters $\{\theta_k\}_{k=1}^K$ simultaneously using backpropagation and gradient descent with learning rate $\alpha$.
+
+            \STATE \textbf{Output:} Trained multi-task metamodel $f(\cdot; \theta_0, \{\theta_k\}_{k=1}^K)$ for all $K$ tasks
+        \end{algorithmic}
+    \end{algorithm}
+
+\end{frame}
+
+\begin{frame}{Experiment Setup}
+
+    \begin{table}[ht!] 
+        \centering
+        \begin{tabular}{lcccc} 
+        \toprule
+        \textbf{Contract} & \textbf{Asset Model} & \textbf{Lapse} & \textbf{$M_{\text{So}}$}  & \textbf{$M_{\text{Ta}}$}\\
+        \midrule
+        GMMB & GBM & No lapse & 50000 & N/A \\
+        GMMB & RS-GBM & No lapse & 50000 & 2000 \\
+        GMMB & RS-GBM & Static lapse & 50000 & 2000 \\
+        GMMB & RS-GBM & Dynamic lapse & 50000 & 2000 \\
+        GMWB & RS-GBM & Dynamic lapse & N/A & 2000 \\
+        \bottomrule
+        \end{tabular}
+        \caption{VA Contracts for Transfer Learning Experiments}
+    \end{table}
+
+    We aim to examine the performance of TL techniques
+    \begin{itemize}
+        \item   learning the lapse features,
+        \item   learning the dynamic lapse, and 
+        \item   transferring to other contract types.
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Learning Lapse Features}
+    \begin{figure}[ht!]
+        \centering
+        \begin{subfigure}{0.48\textwidth}
+            \includegraphics[width=\textwidth]{../project3/figures/figure1a.png}
+            \caption{Extensive Training on Target Task}
+        \end{subfigure}
+        \begin{subfigure}{0.48\textwidth}
+            \includegraphics[width=\textwidth]{../project3/figures/figure1b.png}
+            \caption{Without TL}
+        \end{subfigure}
+        \caption{Direct training on RS-GBM GMMB with static lapse}
+    \end{figure}
+\end{frame}
+
+\begin{frame}{Learning Lapse Features}
+    \begin{figure}[ht!]
+        \centering
+        \begin{subfigure}{0.48\textwidth}
+            \includegraphics[width=\textwidth]{../project3/figures/figure1c.png}
+            \caption{With Fine-tuning}
+        \end{subfigure}
+        \begin{subfigure}{0.48\textwidth}
+            \includegraphics[width=\textwidth]{../project3/figures/figure1d.png}
+            \caption{With Layer Freezing}
+        \end{subfigure}
+        \caption{TL on RS-GBM GMMB with static lapse}
+    \end{figure}
 

### 2025-01-07 pre_private/tikz/illustration_mpns.tex
new

\documentclass[tikz]{standalone}
\usepackage{tikz}
\usepackage{amssymb}

\usetikzlibrary{shapes,arrows,positioning, calc, fit, decorations.pathreplacing}

\begin{document}

\begin{tikzpicture}[scale=1]
        \draw[-latex] (0,0)--(10,0);
        \draw[-latex] (0,0)--(-1,1.5) node[above] {$\blacksquare$};
        \draw[-latex] (0,0)--(0,1.5) node[above] {$\blacksquare$};
        \draw[-latex] (0,0)--(1,1.5) node[above] {$\blacksquare$};
        \node at (0.5,1.2) {\small$\dots$};
        \node at (0.5,1.85) {\small$\dots$};

        \draw[-latex] (3,0)--(2,1.5) node[above] {$\blacksquare$};
        \draw[-latex] (3,0)--(3,1.5) node[above] {$\blacksquare$};
        \draw[-latex] (3,0)--(4,1.5) node[above] {$\blacksquare$};
        \node at (3.5,1.2) {\small$\dots$};
        \node at (3.5,1.85) {\small$\dots$};

        \draw[-latex] (6,0)--(5,1.5) node[above] {$\blacksquare$};
        \draw[-latex] (6,0)--(6,1.5) node[above] {$\blacksquare$};
        \draw[-latex] (6,0)--(7,1.5) node[above] {$\blacksquare$};
        \node at (6.5,1.2) {\small$\dots$};
        \node at (6.5,1.85) {\small$\dots$};

        \draw[-latex] (9,0)--(8,1.5) node[above] {$\blacksquare$};
        \draw[-latex] (9,0)--(9,1.5) node[above] {$\blacksquare$};
        \draw[-latex] (9,0)--(10,1.5) node[above] {$\blacksquare$};
        \node at (9.5,1.2) {\small$\dots$};
        \node at (9.5,1.85) {\small$\dots$};

        \node at (7.5,0.7) {\Huge $\dots$};

        \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (-1,2) --  (1,2);
        \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (2,2) --  (4,2);
        \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (5,2) --  (7,2);
        \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (8,2) --  (10,2);
        \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=12pt}] (0,2.4) --  (9,2.4);
        \node at (4.5,-0.5) {$S_i$};
        \node at (4.5,3.5) {$\hat L_i$};
        \node at (4.5,-1.3) {1 Outer Path for VAs};
\end{tikzpicture}

\end{document}

### 2025-01-27 project3/draft.tex
a

@@
 A standard nested simulation procedure involves running a large number of simulations to generate a dataset of scenario-wise contract losses with two levels of simulations.
-Practitioners can estimate tail risk measures using the realized losses obtained from these simulations.
+Practitioners can estimate tail risk measures using the realized losses for different risk scenarios obtained from these simulations.
 Nested simulation is extremely computationally expensive.
@@
 Traditional machine learning models often struggle to capture the intricate nonlinear relationships and temporal dependencies inherent in financial data.
-In particular, DNNs, and specifically LSTM networks, have been employed as metamodels to predict the outcomes of the inner simulations efficiently
-Chapter~\ref{chap:project2} introduces a nested simulation framework for dynamic hedging of VAs, where the inner simulation is approximated by an LSTM metamodel.
-It shows that crude RNN and LSTMs are well-suited as metamodels for Monte Carlo simulation of financial time series and can capture the long-term dependencies in the simulation dataset.
+In particular, DNNs, and specifically LSTM networks, have been employed as metamodels to predict the outcomes of the inner simulations efficiently.
+Chapter~\ref{chap:project2} introduces a metamodeling-based nested simulation framework for dynamic hedging of VAs that approximates the inner simulation by an LSTM metamodel.
+It shows that LSTMs, as a type of gated RNNs, are well-suited as metamodels for Monte Carlo simulation of financial time series and can capture the long-term dependencies in the simulation dataset.
+This property is crucial for the application of dynamic hedging of VAs.
 
@@
 Retraining neural network metamodels from scratch in response to every change is computationally inefficient and time-consuming.
-The simulation budget is often limited, and the computational cost of retraining a suitable DNN metamodel is often much higher than fitting a traditional parametric regression.
-Moreover, financial markets are inherently dynamic with frequent shifts in volatility, interest rates, and other risk factors~\citep{cont2001empirical}.
+Practitioners with limited resources face several challenges:
+\begin{enumerate}
+    \item The simulation budget is limited, but DNN metamodels require extensive training data to learn the feature-label relationship~\citep{golestaneh2024many}. 
+    \item The computational cost of retraining a suitable DNN metamodel is often much higher than fitting a traditional parametric regression.
+    \item Financial markets are dynamic with frequent shifts in volatility, interest rates, and other risk factors~\citep{cont2001empirical}.
+\end{enumerate}
+
+Constraints on the simulation budget is the most critical challenge for dynamic hedging of VAs.
+Any method that involves nested simulation is computationally expensive, and the computational cost is often prohibitive for changing market conditions.
 Therefore, it is essential to develop methods that can rapidly adapt existing metamodels to new conditions without incurring the full computational cost of retraining and extensive addtional simulations.
@@
 In the context of DNNs, TL involves leveraging the knowledge acquired during training on one dataset to improve learning performance on a different dataset~\citep{yosinski2014transferable}.
-This approach can significantly reduce training time and computational resources while enhancing model generalization.
-Instead of starting from scratch, a new DNN metamodel can be built on top of the pre-trained model and fine-tuned on the new data, allowing it to adapt quickly to changing market conditions and new VA contracts.
+This approach can significantly reduce the amount of training data needed, training time and computational resources while enhancing model generalization.
+Instead of starting from scratch, a new DNN metamodel can be built on top of a pre-trained metamodel and fine-tuned on new data.
+This allows the metamodel to adapt quickly to unseen conditions and new VA contracts.
 
@@
 This setting is particularly relevant for dynamic hedging problems, as insurance companies often underwrite new contracts under changing market conditions and actuarial assumptions.
-Fast adaptation of metamodels is necessary for metamodel-based nested simulation procedures.
+This chapter proposes a TL framework that makes fast adaptation of metamodels possible.
 Our approach involves pre-training an LSTM network on a large dataset of VA simulations and then fine-tuning it on a smaller dataset of new VA contracts.
@@
 TL techniques have also been applied in building fraud detection systems. 
-Financial fraud often exhibits subtle and evolving patterns, making it challenging to develop robust detection models.
+Financial fraud often exhibits subtle and evolving patterns, and it is challenging to develop robust detection models.
 By transferring previous knowledge from detected fraud cases, models can adapt to detect new fraud schemes more effectively~\citep{lebichot2021transfer}.

### 2025-02-02 introduction.tex
1

@@
 Quantitative risk management is a key component of modern financial systems.
-Successful risk management practice ensures the stability and resilience against a variety of risks.
-For financial products like option portfolios and variable annuity (VA) contracts, traditional risk assessment methods often fall short in accurately capturing the complex dynamics of the underlying risk factors.
+Successful risk management practice can ensure the stability and resilience against a variety of risks.
+For financial products such as option portfolios and variable annuity (VA) contracts, traditional risk assessment methods often fall short in accurately capturing the complex dynamics of the underlying risk factors.
 VA contracts are a popular type of complex insurance product that is linked to the performance of underlying assets.
@@
 In this thesis, we focus on building and analyzing nested simulation procedures for risk management applications of financial derivatives and insurance products.
-Nested simulation, also known as nested stochastic modeling and stochastic-on-stochastic modeling, becomes necessary when stochastic simulation of a parameter of interest is contingent on another quantity to be determined stochastically.
+Nested simulation, also known as nested stochastic modeling and stochastic-on-stochastic modeling, becomes a necessary tool when stochastic simulation of a parameter of interest is contingent on another quantity to be determined stochastically.
 In the context of financial engineering, nested simulation is used to model the tail risk of a contract whose payoff depends on a set of underlying risk factors.
-For example, estimating the value of an exotic option at a risk horizon requires simulation given a realization of the underlying assets upto that horizon.
+For example, estimating the value of an exotic option over a risk horizon requires simulation given a realization of the underlying assets over that horizon.
 A standard nested simulation procedure consists of two levels of simulation: the outer-level simulation generates the underlying risk factors, while the inner-level simulation estimates the value of interest with the inner sample mean from another level of Monte Carlo simulation.
 This nested structure allows for accurate estimation given sufficient computational resources, but it also introduces additional complexity in the simulation design and implementation.
-Furthermore, in real-world applications, the computational burden of nested simulation can be prohibitive.
-The number of inner simulations required to achieve a desired level of accuracy for each outer scenario can be infeasibly large.
-Metamodeling techniques that approximate the inner simulation model can be used to reduce the computational burden of nested simulation.
+Furthermore, in real-world applications, the computational burden of a nested simulation can be prohibitive.
+The number of inner simulations required to achieve a desired level of accuracy for each outer scenario can be intractably large.
+Metamodeling techniques that approximate the inner simulation model can be used to reduce the computational burden of a nested simulation.
 Metamodels are statistical models that approximate the output of a complex simulation model as a function of its input parameters.
@@
 Eliminating the inner simulation can lead to more substantial computational savings without affecting estimation quality. 
-In the case of requiring extensive inner simulations for regulatory purposes, effective budget allocations can help achieve higher estimator quality with the same computational budget.
+In the case of requiring extensive inner simulations for regulatory purposes, effective budget allocations can help achieve an improved estimator quality with the same computational budget.
 In practice, underlying assumptions of the simulation model are subject to change, and new VA contracts are issued with different contract specifications.
 Simulation budgets are often scarce for new conditions.
-Chapter~\ref{chap:project3} uses transfer learning techniques for quick adaptation of the neural network metamodel to new market conditions and new VA contracts.
-Our numerical experiments shows that an intelligent use of transfer learning can lead to significantly better metamodels than those trained from scratch.
-Chapter~\ref{chap:futureWork} discusses the application of deep reinforcement learning in the dynamic hedging of VA contracts.
-Chapter \ref{chap:conclusion} concludes the thesis and discusses potential future research directions.
+Chapter~\ref{chap:project3} uses transfer learning techniques for a quick adaptation of the neural network metamodel to new market conditions and new VA contracts.
+Our numerical experiments shows that an judicious use of transfer learning can lead to substantially better metamodels than those trained from the scratch.
+Chapter~\ref{chap:conclusion} concludes the thesis and discusses potential future research directions.
+Chapter~\ref{chap:futureWork} discusses the future directions of applying deep reinforcement learning in the dynamic hedging of VA contracts.
 
@@
 
-VA contracts are index-linked insurance products that offer policyholders the upside potential of equity markets while providing guarantees that protect against downside risk.
-These products have gained significant interest as they address the needs of individuals seeking both wealth accumulation and financial security, especially in the context of retirement planning.
+VA contracts are index-linked insurance products that offer policyholders an upside potential of equity markets while providing guarantees that protect against a downside risk.
+These products have gained a substantial amount of interest as they address the needs of individuals seeking both wealth accumulation and financial security, especially in the context of retirement planning.
 The most interesting feature of VAs is embedded guarantees that ensure a specified minimum benefit regardless of market performance.
@@
 The GMWB allows policyholders to withdraw a specified percentage of their benefit base each period during the contract horizon~\citep{hardy2003investment}.
-While these guarantees enhance the attractiveness of VAs to consumers by offering protection against market downturns and ensuring income stability, they introduce substantial financial risks to insurers.
+While these guarantees enhance the attractiveness of VAs to consumers by offering protection against market downturns and ensuring income stability, they introduce a substantial amount of financial risks to insurers.
 The embedded options within GMMBs and GMWBs expose insurers to market risk, longevity risk, and policyholder behavior risk. 
-Effective management of these risks is crucial for insurers to maintain solvency and meet regulatory capital requirements.
+Therefore, an effective management of these risks is crucial for insurers to maintain solvency and meet regulatory capital requirements.
 
 One of the primary risk management strategies employed by insurers to mitigate the financial risks associated with VAs is dynamic hedging. 
-Dynamic hedging involves frequently adjusting a portfolio of financial instruments to offset changes in the value of the guarantees due to market movements~\citep{hull2016options}. 
-This strategy aims to neutralize the sensitivity of the insurer's liability to market fluctuations by constructing a hedging portfolio that replicates the cash flows of the guarantees.
+Dynamic hedging involves a frequent adjustment of a portfolio of financial instruments to offset changes in the value of the guarantees due to market movements~\citep{hull2016options}. 
+This strategy aims at neutralizing the sensitivity of the insurer's liability to market fluctuations by constructing a hedging portfolio that replicates the cash flows of the guarantees.
 However, dynamic hedging introduces complexity in estimating the insurer's overall risk exposure.
-One of such examples is the estimation of tail risk measures of a VA contract.
+One such example is the estimation of tail risk measures of a VA contract.
 It requires the stochastic modeling of the financial market and the accurate loss estimation of the hedging portfolio under different market scenarios.
@@
 
-Despite its robustness, nested simulation is computationally intensive, often requiring significant computational resources and time. 
+Despite its robustness, nested simulation is computationally intensive, often requiring a substantial amount of computational resources and time. 
 Each scenario in the outer simulation requires numerous inner simulations to accurately estmate contract loss. 
-This computational burden poses practical limitations, especially when high precision in tail risk estimation is required.
+This computational burden poses practical limitations, especially when a high degree of precision in tail risk estimation is required.
 To address this challenge, metamodeling techniques can be employed to approximate the inner simulation model and reduce the computational cost of nested simulation.
@@
 Metamodeling, also known as surrogate modeling, is a technique used to approximate complex simulation models with simpler, computationally efficient models. 
-In the context of Monte Carlo simulations, metamodels are models of models that aim to reduce computational costs by creating an approximate model that can quickly predict simulation outputs based on input variables~\citep{kleijnen2018design}.
-This section introduces metamodeling for Monte Carlo simulation, elaborates on its methodologies, and highlights its importance in practical applications.
+In the context of Monte Carlo simulations, metamodels are models of models that aim at reducing computational costs by creating an approximate model that can quickly predict simulation outputs based on input variables~\citep{kleijnen2018design}.
+This section introduces metamodeling for a Monte Carlo simulation, elaborates on its methodologies, and highlights its importance in practical applications.
 
 Monte Carlo simulations are widely used for modeling and analyzing complex systems that are probabilistic in nature. 
-These simulations often require a significant amount of computational resources, especially when high accuracy or numerous iterations are necessary~\citep{glasserman2004monte}. 
-Metamodeling addresses this challenge by constructing an approximate model (metamodel) that emulates the behavior of the original simulation model with much less computational effort.
+These simulations often require a substantial amount of computational resources, especially when a high degree of accuracy or a high number of iterations is necessary~\citep{glasserman2004monte}. 
+Metamodeling addresses this challenge by constructing an approximate model (known as ametamodel) that emulates the behavior of the original simulation model with much less computational effort.
 The metamodel serves as a predictive model that maps input variables to output responses. 
@@
 Metamodeling is particularly useful when the simulation model is computationally expensive. 
-By replacing the simulation model with a metamodel, the computational cost of evaluating the model can be significantly reduced. 
+By replacing the simulation model with a metamodel, the computational cost of evaluating the model can be substantially reduced. 
 This allows for faster convergence of simulation-based estimators.
 
-The process of metamodeling generally involves:
+The process of metamodeling generally involves the following steps:
 
 \begin{enumerate} 
-    \item \textbf{Design of Experiments}: Selecting input combinations to run the original simulation and collect data. 
-    \item \textbf{Building the Metamodel}: Using the collected data to train a metamodel that approximates the simulation model. 
-    \item \textbf{Validation}: Assessing the metamodel's accuracy and generalization capability.
-    \item \textbf{Application}: Using the metamodel to predict simulation outputs for new input combinations.
+    \item \textbf{Design of Experiments}: Select input combinations to run the original simulation and collect data. 
+    \item \textbf{Building the Metamodel}: Use the collected data to train a metamodel that approximates the simulation model. 
+    \item \textbf{Validation}: Assess the metamodel's accuracy and generalization capability.
+    \item \textbf{Application}: Use the metamodel to predict simulation outputs for new input combinations.
 \end{enumerate}
 
-The development of advanced machine learning models and deep learning techniques has significantly enhanced metamodeling approaches for Monte Carlo simulations, especially in high-dimensional and complex problem settings.
+The development of advanced machine learning models and deep learning techniques has enhanced metamodeling approaches for Monte Carlo simulations, especially in high-dimensional and complex problem settings.
 Example use cases for machine learning include~\cite{jin2020deep}, ~\cite{tang2020deep}, and~\cite{rosen2012metamodeling}.
-These methods offer powerful tools for capturing intricate patterns and nonlinear relationships that traditional metamodeling techniques might struggle to model effectively.
+These methods offer powerful tools for capturing intricate patterns and nonlinear relationships that traditional metamodeling techniques might have to struggle to model them effectively.
 In the following sections, we discuss machine learning algorithms in the context of metamodeling for Monte Carlo simulations and their applications in risk management.
@@
 ML algorithms can be broadly categorized into supervised learning, unsupervised learning, and reinforcement learning.
-This section focuses on three widely used supervised learning models and two reinforcement learning algorithms that are relevant to risk management applications.
+This section focuses on three widely used supervised learning models and two reinforcement learning algorithms that are most relevant to risk management applications.
 
@@
 In this paradigm, a model is trained on a labeled dataset, which means that each training example is associated with an output label or value. 
-The goal is to learn a general rule that maps inputs (also known as features) to outputs (also known as target), enabling the model to make accurate predictions on new, unseen data.
+The goal of a supervised learning paradigm is to learn a general rule that maps inputs (also known as features) to outputs (also known as target), enabling the model to make accurate predictions on new, unseen data.
+Supervised learning can be carried out in two domains of applications.
+These are:
 
 \begin{itemize} 
-    \item \textbf{Classification}: The output variable is categorical, and the task is to assign inputs to one of several predefined categories. 
+    \item \textbf{Classification}: The output variable is categorical, and the task is to assign inputs to one of several predefined categories to produce a qualitative prediction. 
     Common use in finance and actuarial applications are fraud detection and credit scoring.
-    \item \textbf{Regression}: The output variable is continuous, and the task is to predict a real-valued number. 
+    \item \textbf{Regression}: The output variable is continuous, and the task is to predict a real-valued number and produce a quantitative prediction. 
     Examples in actuarial applications include predicting claim amounts, reserve estimates, asset pricing, and estimating tail risk measures of loss distributions.
@@
 This thesis focuses on regression models for risk management applications, where the goal is to predict a continuous target variable based on one or more input features.
-Given a dataset of $n$ observations $\{(x_1, y_1), (x_2, y_2), \ldots, (x_n, y_n)\}$, where $x_i \in \mathbb{R}^d$ is the $d$-dimensional input feature vector, and $y_i \in \mathbb{R}$ is the target variable, a supervised learning algorithm aims to learn a function $f(;\theta): \mathbb{R}^d \rightarrow \mathbb{R}$ that best predicts the target variable $y$ given the input features $x$ with a set of function parameters $\theta$.
+Given a dataset of $n$ observations $\{(x_1, y_1), (x_2, y_2), \ldots, (x_n, y_n)\}$, where $x_i \in \mathbb{R}^d$ is the $d$-dimensional input feature vector, and $y_i \in \mathbb{R}$ is the target variable, a supervised learning algorithm aims to learning a function $f(;\theta): \mathbb{R}^d \rightarrow \mathbb{R}$ that best predicts the target variable $y$ given the input vector of features $x$ with a vector of function parameters $\theta$.
 
@@
 Despite the differences in their functional forms, all supervised learning models can be evaluated on a similar set of metrics.
-The learning process is referred to as training, which involves minimizing a loss function $l(f(x; \theta),y)$ over the training data, which quantifies the difference between the predicted labels and the training labels.
-A common loss function for regression problems is the mean squared error (MSE):
+The learning process is referred to as training, which involves minimizing a loss function $l(f(x; \theta),y)$ over the training data, which quantifies the closeness of the difference between the predicted labels and the training labels.
+A common loss function for regression problems is a quadratic loss function in the form of a mean squared error (MSE):
 
@@
 Another important consideration is the choice of a suitable supervised learning algorithm.
-The choice may vary based on the complexity of the relationship, the interpretability of the model, and the computational resources available.
+The choice may vary based on a trade-off among the complexity of the relationship, the interpretability of the model, and the computational resources available.
 In the following sections, we discuss four widely used supervised learning techniques in risk management applications: parametric regression, kernel regression, and two neural network architectures.
@@
 A regression model predicts a continuous target variable based on one or more input features.
-Linear regression is a simple and interpretable model that attempts to predict a target variable as a linear combination of input features. 
+A multiple linear regression is a simple and interpretable model that attempts to predict a target variable as a linear combination of input features. 
 It assumes a linear relationship between the target output and one or more input features. 
@@
 \citet{bishop2006pattern} provide an extensive treatment of regression techniques in the broader context of machine learning.
-It is known as parametric regression because it assumes a specific functional form for the input-output relationship with a finite set of parameters~\citep{seber2012linear}.
-General form of a parametric regression model is given by:
+It is known as a parametric regression because it assumes a specific functional form for the input-output relationship with a finite set of parameters~\citep{seber2012linear}.
+A general form of a parametric regression model is given by:
 \begin{equation} \label{eq:regression}
@@
 \end{equation}
-where $p$ is the number of features, $\beta_0, \beta_1, \ldots, \beta_p$ are the trainable regression coefficients, and $\phi_j(x)$ are basis functions that transfrom the input $x$ to allow for non-linear modeling.
+where $p$ is a number of features, $\beta_0, \beta_1, \ldots, \beta_p$ are trainable regression coefficients, and $\phi_j(x)$ are basis functions that transfrom the input $x$ to allow for non-linear modeling.
 Basis functions can be any functions of $x$ that are chosen to capture the underlying structure of the data.
@@
 The training of parametric regression refers to the process of estimating the regression coefficients $\beta_0, \beta_1, \ldots, \beta_p$ that minimize the loss function.
-For a MSE loss, the optimal regression coefficients can be obtained by solving the normal equations.
+For a MSE loss metrics, the optimal regression coefficients can be obtained by solving the normal equations.
 Parametric regression is a powerful tool for modeling linear relationships where the basis functions are known from expert knowledge for explicit feature engineering techniques~\citep{hastie2009elements}.
-These techniques utilize predefined functional forms to model the relationship between independent variables and the dependent variable. 
+These techniques utilize predefined functional forms to model the relationship between a set of independent variables and a dependent variable. 
 However, when data exhibits complex, non-linear relationships, linear models fall short. 
@@
 Often, expert knowledge is required to select the appropriate basis functions, which can limit the flexibility of the model.
-Extensions like polynomial regression and generalized linear models (GLMs) have been introduced to capture non-linearity.
-Nevertheless, these models can still be limited in capturing highly complex patterns.
+Extensions like polynomial regression and generalized linear models (GLMs) have been introduced to capture non-linearity in the data.
+Nevertheless, these models can still be limited in capturing highly complex patterns of the data.
 
 \subsection{Non-Parametric Regression Models}
-To overcome some limitations of parametric regression, non-parametric methods such as kernel regression~\citep{hastie2009elements} are often employed. 
+To overcome some of the previously mentioned limitations of the parametric regression, non-parametric methods such as kernel regression~\citep{hastie2009elements} are often employed. 
 Kernel regression estimates the relationship by averaging the values of the target variable over a local neighborhood of the input $x$.
@@
 \end{equation}
-where $K(\cdot)$ is the kernel function, which assigns weights to the data points based on their distance to the input $x$, and $h$ is the bandwidth parameter that controls the smoothness of the estimated function.
-The objective is to estimate the feature-label relationship directly from the data without imposing a specific form.
+where $K(\cdot)$ is a kernel function, which assigns weights to the data points based on their distance to the input $x$, and $h$ is a bandwidth parameter that controls the smoothness of the estimated function.
+The objective of this approach is to estimate a feature-label relationship directly from the data without imposing a specific functional form of the regression function.
 However, they come with several drawbacks that limit their effectiveness, especially in high-dimensional settings or for large datasets. 
-One of the most significant drawbacks of non-parametric regression is the curse of dimensionality \cite{bellman1966dynamic}. 
+One of the most important drawbacks of the non-parametric regression is the curse of dimensionality \cite{bellman1966dynamic}. 
 As the number of features increases, the volume of the input space grows exponentially.
@@
 In addition, the computational cost associated with non-parametric methods often grows rapidly with the number of dimensions.
-Cross validation and distance calculation are two computationally expensive operations that are often required for non-parametric regression.
-These drawbacks make non-parametric regression impractical for modeling high-dimensional large-scale datasets.
+Cross validation and distance calculation are two computationally expensive operations that are often required for a non-parametric regression.
+These drawbacks make the non-parametric regression impractical for modeling high-dimensional large-scale datasets.
 
@@
 \end{equation}
-
-where $\theta = (\theta^{(1)}, \theta^{(2)}, \ldots, \theta^{(k)})$ are the trainable parameters of the neural network, $f^{(i)}$ is the $i$-th layer of the neural network, $x$ is the input feature vector, $f^{(1)}(x;\theta^{(1)}) = x$, $f^{(k)}$ is the output layer, $k$ is the number of layers, and $f^{(i)}$ is the output of the $i$-th layer.
+where $\theta = (\theta^{(1)}, \theta^{(2)}, \ldots, \theta^{(k)})$ are trainable parameters of the neural network, $f^{(i)}$ is an $i$-th layer of the neural network, $x$ is an input feature vector, $f^{(1)}(x;\theta^{(1)}) = x$, $f^{(k)}$ is an output layer, $k$ is a number of layers, and $f^{(i)}$ is an output of the $i$-th layer.
 To move from a lower layer to a higher layer, i.e., from layer $i-1$ to layer $i$,
@@
 \end{equation}
-
-where $a^{(i)}$ are the nonlinear activation functions, $\theta^{(i)} = (\beta_0^{(i)}, \dots, \beta_p^{(i)})$ are the trainable parameters of the $i$-th layer, and $p_i$ is the number of neurons in the previous layer.
+where $a^{(i)}$ are nonlinear activation functions, $\theta^{(i)} = (\beta_0^{(i)}, \dots, \beta_p^{(i)})$ are trainable parameters of the $i$-th layer, and $p_i$ is a number of neurons in the previous layer.
 Equation~\ref{eq:neural} represents a single neuron in a neural network, which applies a linear transformation to the input followed by a non-linear activation function. 
@@
 A typical choice for the activation function is the rectified linear unit (ReLU), which is defined as $a(z) = \max(0, z)$~\citep{nair2010rectified}.
-The choice of activation function also plays a crucial role in the training of neural networks.
+The choice of an activation function also plays a crucial role in the training of neural networks.
 While sigmoid and hyperbolic tangent functions were popular in early neural networks, ReLU has become the default activation function for deep networks due to its ability to mitigate the vanishing gradient problem and promote sparse activations~\citep{lecun2015deep}.
 
-The key advantage of feedforward neural networks (FNNs) lies in their ability to perform automatic feature engineering without direct human intervention. 
+The key advantage of FNNs lies in their ability to perform automatic feature engineering without a direct human intervention. 
 Unlike traditional machine learning models that require manual selection and transformation of input features, neural networks learn to extract and compose features through their hidden layers during the training.
@@
 The last layer of the neural network, known as the output layer, typically performs a linear transformation of the features extracted by the preceding hidden layers. 
-With $a^{k}(z) = z$, the last layer is equivalent to a linear regression with its inputs as transformed, high-level features learned by the hidden layers.
+With $a^{k}(z) = z$, the last layer is equivalent to a multiple linear regression with its inputs as transformed, high-level features learned by the hidden layers.
 We can draw parallels between neural networks and traditional regression models. 
@@
 \end{equation}
-
 where $h_t$ is the hidden state at time $t$, $x_t$ is the input at time $t$, $h_{t-1}$ is the hidden state at time $t-1$, and $f$ is the recurrent function parameterized by $\theta$.
 This architecture enables RNNs to capture temporal dependencies by maintaining a dynamic internal state that reflects the memory of past inputs.
-However, traditional RNNs suffer from the vanishing and explodeing gradient problem, which hinders their ability to capture long-term dependencies that often present in financial time series~\citep{bengio1994learning}.
-During training, gradients propagated backward through time can either diminish exponentially (vanishing gradients) or grow uncontrollably (exploding gradients).
+However, traditional RNNs suffer from the vanishing and exploding gradient problem, which hinders their ability to capture longer-term dependencies that often present in financial time series~\citep{bengio1994learning}.
+During training, gradients propagated backward through time can either diminish exponentially (known as vanishing gradients) or grow uncontrollably (known as exploding gradients).
 This limitation is particularly problematic in modeling long-term financial contracts and insurance guarantees, where patterns may span over extended periods.
@@
 \end{align*}
-
-where $i_t, f_t, o_t, g_t, c_t, h_t$ are the input gate, forget gate, output gate, cell input, cell state, and hidden state at time $t$, respectively.
-$W_i$, $W_f$, $W_o$, $W_g$, $U_i$, $U_f$, $U_o$, $U_g$ are the weight matrices, and $b_i$, $b_f$, $b_o$, $b_g$ are the bias vectors.
+where $i_t, f_t, o_t, g_t, c_t, h_t$ are an input gate, a forget gate, an output gate, a cell input, a cell state, and a hidden state at time $t$, respectively.
+$W_i$, $W_f$, $W_o$, $W_g$, $U_i$, $U_f$, $U_o$, $U_g$ are weight matrices, and $b_i$, $b_f$, $b_o$, $b_g$ are bias vectors.
 $a$ is the activation function, typically the sigmoid function, and $\odot$ denotes element-wise multiplication.
@@
 By effectively modeling complex, non-linear relationships and temporal dependencies, neural networks serve as powerful tools for addressing the computational challenges in estimating risk measures and developing effective risk mitigation strategies.
-This thesis aims to explore the application and noise tolerance of LSTM networks in metamodeling for nested simulation procedures in risk management.
-We investigate the performance of LSTM networks in approximating the inner simulation model in a two-stage nested simulation procedure for index-linked insurance contracts.
+This thesis aims at exploring the application and noise tolerance of LSTM networks in metamodeling for nested simulation procedures in risk management.
+In this thesis, we investigate the performance of LSTM networks in approximating the inner simulation model in a two-stage nested simulation procedure for index-linked insurance contracts.
 By leveraging the memory and sequential modeling capabilities of LSTMs, we aim to improve the accuracy and efficiency of nested simulation procedures for risk management applications.
@@
 
-The training of neural networks involves adjusting the trainable parameters of the network to minimize the loss function, which quantifies the error between the predictions and labels.
-The training process aims to find the optimal parameters that minimize this error.
+The training of neural networks involves adjusting the trainable parameters of the network to minimize the loss function, which quantifies the error between the predictions and the labels.
+The training process aims at finding the optimal parameters that minimize this error.
 The most common approach is to use gradient descent methods with backpropagation, which is an efficient method for computing the gradients of the loss function with respect to the trainable parameters.
@@
 However, SGD may oscillate and converge slowly, especially in non-convex problems~\citep{bengio2016}.
-To address these issues, various adaptive learning rate methods have been proposed.
-The most popular approach is Adam, which is a SGD algorithm that adjusts the learning rate during training to improve convergence speed and stability~\citep{kingma2014adam}.
+To address these issues, various adaptive learning rate methods have been proposed in the literature.
+The most popular approach is Adam optimizer, which is a SGD algorithm that adjusts the learning rate during training to improve convergence speed and stability~\citep{kingma2014adam}.
 
-Another common technique to improve the training of neural networks is regularization to prevent overfitting.
+Another common technique to improve the training of neural networks is a regularization technique to prevent overfitting.
 One effective regularization method is dropout, which randomly sets a fraction of neurons to zero during each training iteration~\citep{srivastava2014dropout}.
@@
 It involves monitoring the model's performance on a validation set and stopping training when the performance no longer improves~\citep{prechelt2002early}.
-This helps prevent over-fitting by stopping training before the model begins to fit to noise in the data.
+This helps prevent over-fitting by stopping training before the model begins to fit to the noise in the data.
 
@@
 The training set is used to train the model, the validation set is used to tune the model hyper-parameters, and the test set is used to evaluate how well the model generalizes to unseen data.
-The test set is not used during training and is only used for evaluation.
+The test set is not used during training and is only used for an evaluation purpose.
 
 Under-fitting occurs when the training error is high, which means that the neural network fails to capture the underlying patterns in the training data.
-Over-fitting occurs when the neural network fits to noise in the training data and cannot generalize to unseen data.
+Over-fitting occurs when the neural network fits to the noise in the training data and cannot generalize results to unseen data.
 In machine learning literature, over-fitting is often quantified as the gap between the training error and the test error~\citep{bishop2006pattern}.
-During training, as the test dataset is not used, this quantity is estimated using the validation set.
+During training, as the test dataset is not used, this quantity is estimated by using the validation set.
 If the validation error is high compared to the training error, the model is likely over-fitting to the training data.

### 2025-02-02 project1/nsSurvey.tex
1

@@
 The term \textit{standard} refers to using a standard MC estimator, the sample mean of the inner replication to estimate a scenario-wise portfolio loss for an outer scenario.
-~\cite{gordy2010nested} investigate the optimal budget allocation for a standard nested simulation procedure with respect to the MSE of the estimated risk measure.
+~\cite{gordy2010nested} investigate an optimal budget allocation for a standard nested simulation procedure with respect to the MSE of the estimated risk measure.
 
@@
 ~\cite{broadie2015risk} propose a regression-based nested simulation procedure, which uses a trained regression metamodel to estimate the scenario-wise portfolio loss for an outer scenario by pooling the inner replications from all outer scenarios.
-For risk measures in certain forms,~\cite{broadie2015risk} show that it is optimal to allocate all simulation budget to the outer level simulation, and the inner replication should be kept to a minimum of $1$.
-Similarly,~\cite{hong2017kernel},~\cite{feng2020optimal}, and~\cite{zhang2022sample} use a kernel smoothing model, a likelihood ratio model, and a kernel ridge regression (KRR) model as metamodels to pool the inner replications from all outer scenarios.
+For certain forms of risk measures,~\cite{broadie2015risk} show that it is optimal to allocate all simulation budget to the outer level simulation, and the inner replication should be kept to a minimum of $1$.
+Similarly,~\cite{hong2017kernel},~\cite{feng2020optimal}, and~\cite{zhang2022sample} use a kernel smoothing model, a likelihood ratio model, and a kernel ridge regression (KRR) model as metamodels to pool the inner replications from all outer scenarios, respectively.
 In simulation studies, this approach of using a model of a simulation model is known as metamodeling, and the models of a simulation model are also referred to as metamodels~\citep{barton1998simulation}.
-Another line of research is the multi-level Monte Carlo (MLMC) method analyzed in~\cite{giles2019multilevel}, which is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest.
+Another line of research is a multi-level Monte Carlo (MLMC) method analyzed in~\cite{giles2019multilevel}, which is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest.
 
 This paper presents a survey study of some popular nested simulation procedures that have both asymptotic convergence analysis and finite-sample performance evaluation.
-Many procedures are proposed in the literature, but they are not directly comparable due to having different error metrics, different assumptions, and different numerical examples.
-Within a common analytical framework, we first summarize and compare their asymptotic rate of convergence.
+Many procedures are proposed in the literature, but they are not directly comparable due to having different error metrics, different assumptions, and different numerical examples used in their studies.
+Within a common analytical framework, we first summarize and compare their asymptotic rates of convergence.
 Their asymptotic convergence results are closely examined for their assumptions that guarantee the convergence.
@@
 
-In terms of finite-sample performance, different studies propose different examples in their numerical experiments, which introduces unfair advantages for certain simulation procedures over others. 
+In terms of finite-sample performance, different studies propose different examples in their numerical experiments, which introduces unfair advantages for certain simulation procedures over the others.
 A fair comparison among popular methods is therefore urgently needed in the literature. 
-Our numerical experiment in this chapter is the first of its kind to subject back all the aforementioned simulation procedures to a complete and unbiased comparison. 
-Extensive numerical experiments are conducted to show, in practical examples, how well the finite-sample performance of a method matches its theoretical convergence behavior. 
+Our numerical experiment in this chapter is the first of its kind to subject all the aforementioned simulation procedures to a fair comparison. 
+As a result, extensive numerical experiments are conducted to show, in practical examples, how well the finite-sample performance of a method matches its theoretical convergence behavior. 
 With our numerical examples, we compare the nested simulation procedures for different payoff complexity, problem dimensions, and risk measures. 
@@
 
-The rest of the paper is organized as follows.
+The rest of this chapter is organized as follows.
 Section~\ref{sec1:problem-formulation} introduces the nested simulation procedure and the standard MC estimator.
@@
 where $X \in \mathcal{X} \subset \mathbb{R}^d$, and $L = L(X)$ is a random variable whose distribution is characterized by $X$.
-$L(X)$ can't be directly evaluated, but it is the output of
+$L(X)$ is not subject to direct evaluation, but it is the output of
 
@@
 
-Some common risk measures are in the nested expectation form, in which 
+Some common risk measures are in the nested expectation form as
 $$\rho(L) = \mathbb{E}\left[ h(L) \right]$$
-
 where $h: \mathbb{R} \rightarrow \mathbb{R}$ is a known nonlinear function. 
@@
 Despite being more advanced than kernel smoothing, the KRR-based procedure requires a less stringent smoothness assumption on $h$.
-It is counterintuitive that a more complex metamodel requires a less stringent smoothness assumption.
-This phenomenon is due to the fact that the convergence analysis for the KRR-based nested simulation procedure is shown in terms of absolute error, which is a less stringent error metric than MSE.
+At first sight, it is counterintuitive that a more complex metamodel requires a less stringent smoothness assumption.
+This phenomenon is due to the fact that the convergence analysis for the KRR-based nested simulation procedure is shown in terms of an absolute error (AE), which is a less stringent error metric than MSE.
 Section~\ref{sec1:connection-mse-absolute-error} discusses the connection between the MSE and the AE of the estimator in the context of nested simulation procedures.
-In Table~\ref{tab1:smoothness}, the standard nested simulation procedure is the only procedure without asymptotic convergence analysis for smooth $h$.
+In Table~\ref{tab1:smoothness}, the standard nested simulation procedure is the only procedure without an asymptotic convergence analysis for smooth $h$.
 Section~\ref{sec1:sns} fills this gap by providing the asymptotic convergence analysis for the standard nested simulation procedure in terms of MSE.
@@
 \begin{definition} \label{def1:lipschitz}
-    A function $h: \mathbb{R} \rightarrow \mathbb{R}$ is Lipschitz continuous with Lipschitz constant $K$ if for all $t_1, t_2 \in \mathbb{R}$, 
+    A function $h: \mathbb{R} \rightarrow \mathbb{R}$ is Lipschitz continuous with a Lipschitz constant $K$ if for all $t_1, t_2 \in \mathbb{R}$, 
     $$|h(t_1) - h(t_2)| \leq K|t_1 - t_2|.$$
@@
 A mean excess loss over a threshold $u$ is defined by setting $h(t) = \max\{t - u, 0\}$, which is a special case of a Lipschitz continuous function.
-The regression-based nested simulation procedure is the only procedure that performs theoretical analysis for Lipschitz continuous $h$.
-The other procedures only provide convergence analysis for the special case, mean excess loss over a threshold $u$.
+The regression-based nested simulation procedure is the only procedure that performs a theoretical analysis for Lipschitz continuous $h$.
+The other procedures only provide a convergence analysis for the special case, mean excess loss over a threshold $u$.
 
@@
 
-Other risk measures of interest that are not in the nested expectation form are the value at risk (VaR) and the conditional value at risk(CVaR)~\citep{hardy2022quantitative}. 
+Other risk measures of interest that are not in the nested expectation form are the Value at Risk (VaR) and the Conditional Value at Risk (CVaR)~\citep{hardy2022quantitative}. 
 The $\alpha$-VaR of $L$ is defined as
@@
 
-The standard nested simulation procedure first simulates $M$ independent and identically distributed (iid) outer scenarios $X_1, \dots, X_M$ from $F_X$, the distribution of $X$.
+The standard nested simulation procedure first simulates $M$ independent and identically distributed (i.i.d.) outer scenarios $X_1, \dots, X_M$ from $F_X$, the distribution of $X$.
 For each $X_i$, again simulate $Y_{ij}$, $j = 1, \dots, N$ from $F_{Y|X_i}$, the conditional distribution of $Y$ given $X_i$.
-Given scenario $i$, the $Y_{ij}$ are conditionally iid.
-Let $\Gamma = M \cdot N$ denote the total simulation budget, $f_X(x)$ denote the density of $X$, and $\mathbf{X} = (X_1, \dots, X_M)$ denote the vector of outer scenarios.
+Given scenario $i$, the $Y_{ij}$ are conditionally i.i.d.
+Let $\Gamma = M \cdot N$ denote a total simulation budget, $f_X(x)$ denote a density of $X$, and $\mathbf{X} = (X_1, \dots, X_M)$ denote a vector of outer scenarios.
 
@@
 \end{equation*}
-
-where $\hat{L}_{N_{-1}}(\cdot) = 0$, $\Upsilon$ is the number of levels, $M_{\upsilon}$ is the number of outer scenarios at level $\upsilon$, and $N_{\upsilon}$ is the number of inner replications at level $\upsilon$.
-Applying the analysis of~\cite{giles2015multilevel} in a nested simulation context,~\cite{giles2019multilevel} show that the MLMC method can achieve a similar level of accuracy as the standard nested simulation procedure with a lower total computational budget.
-The simulation budget $\Gamma$ is the sum of the computational budget at each level, that is, $\Gamma = \sum_{\upsilon=0}^{\Upsilon} M_{\upsilon} \cdot N_{\upsilon}$.
+where $\hat{L}_{N_{-1}}(\cdot) = 0$, $\Upsilon$ is a number of levels, $M_{\upsilon}$ is a number of outer scenarios at level $\upsilon$, and $N_{\upsilon}$ is a number of inner replications at level $\upsilon$.
+Applying the analysis of~\cite{giles2015multilevel} in a nested simulation context,~\cite{giles2019multilevel} show that the MLMC method can achieve a similar degree of accuracy as the standard nested simulation procedure with a lower total computational budget.
+The simulation budget $\Gamma$ is a sum of the computational budget at each level, that is, $\Gamma = \sum_{\upsilon=0}^{\Upsilon} M_{\upsilon} \cdot N_{\upsilon}$.
 Neither the standard nested simulation procedure nor the MLMC method involves pooling the inner replications from all outer scenarios.
@@
 Supervised learning-based nested simulation procedures treat the inner simulation model $L(\cdot)$ as a black-box function, and they approximate $L(\cdot)$ with supervised learning metamodels.
-In this metamodeling approach, $L(\cdot)$ can be approximated by $\hat{L}^{\text{SL}}_{M, N}(\cdot)$, which is based on a chosen function family and observations from the standard nested simulation procedure.
+In this metamodeling approach, $L(\cdot)$ can be approximated by $\hat{L}^{\text{SL}}_{M, N}(\cdot)$, which is based on a family of chosen function and observations from the standard nested simulation procedure.
 Consider the observation pairs $(X_i, \hat{L}_{N, i})$ for $i \in \{1, \dots, M\}$ as training data, we can use supervised learning to approximate $L_i$ by $\hat{L}_{M, N}^{\text{SL}}(X_i)$ and to pool the inner replications from all outer scenarios.
-More specifically, $\hat{L}^{\text{SL}}_{M, N}(\cdot)$ denotes the supervised learning model trained on $(X_i, \hat{L}_{N, i})$ for $i \in \{1, \dots, M\}$, which is the simulation output of the standard nested simulation procedure with $M$ outer scenarios and $N$ inner replications.
+More specifically, $\hat{L}^{\text{SL}}_{M, N}(\cdot)$ denotes a supervised learning model trained on $(X_i, \hat{L}_{N, i})$ for $i \in \{1, \dots, M\}$, which is the simulation output of the standard nested simulation procedure with $M$ outer scenarios and $N$ inner replications.
 To evaluate the convergence of the supervised learning-based nested simulation procedure, we consider the convergence behavior of the supervised learning model $h(\hat{L}^{\text{SL}}_{M, N}(\cdot))$ to the true risk measure $\rho = h(L(\cdot))$.
-More specifically, we want to study the quantity
+More specifically, we want to study the following quantity
 \begin{equation} \label{eq1:sl-E}
@@
 
-After a supervised learning metamodel is trained, it can be used to make predictions for all $X \in \mathcal{X}$.
+After a supervised learning metamodel is trained, it can be used to form predictions for all $X \in \mathcal{X}$.
 Instead of using the same training samples to estimate the risk measure, we can use metamodel predictions for a new set of $M'$ \textit{test} samples of $X$, namely $\tilde{\mathbf{X}} = \tilde{X}_1, \dots, \tilde{X}_{M'}$.
@@
 \end{enumerate}
-where $\hat{L}^{\text{SL}}_{(\lceil \alpha M' \rceil)}$ is the $\lceil \alpha M' \rceil$-th order statistic of $\hat{L}^{\text{SL}}_{M, N}(\tilde{X}_1), \dots, \hat{L}^{\text{SL}}_{M, N}(\tilde{X}_{M'})$.
+where $\hat{L}^{\text{SL}}_{(\lceil \alpha M' \rceil)}$ is an $\lceil \alpha M' \rceil$-th order statistic of $\hat{L}^{\text{SL}}_{M, N}(\tilde{X}_1), \dots, \hat{L}^{\text{SL}}_{M, N}(\tilde{X}_{M'})$.
 Note that $\hat{L}^{\text{SL}}_{M, N}(\cdot)$ is the model preditions of a supervised learning model trained on the training samples $(X_1, \hat{L}_{N, 1}), \dots, (X_M, \hat{L}_{N, M})$.
@@
             $$\hat{L}^{\text{KS}}_{M, N}(X) = \frac{\sum_{i=1}^M \hat{L}_{N, i} K_w(X - X_i)}{\sum_{i=1}^M K_w(X - X_i)}, $$
-            where $K_w$ is the kernel function with bandwidth $w$.
-            ~\cite{nadaraya1964estimating} and ~\cite{watson1964smooth} originally proposed this kernel smoothing method for nonparametric regression, and it is widely known in the literature as Nadaraya-Watson kernel regression.
-            ~\cite{hong2017kernel} provides convergence analysis for metamodel predictions of the training samples (Equation~\ref{eq1:sl-train}), and the convergence analysis is provided for smooth, hockey-stick, and indicator $h$.
+            where $K_w$ is a kernel function with bandwidth $w$.
+            ~\cite{nadaraya1964estimating} and ~\cite{watson1964smooth} originally proposed this kernel smoothing method for a non-parametric regression, and it is widely known in the literature as a Nadaraya-Watson kernel regression.
+            ~\cite{hong2017kernel} provides convergence analysis for metamodel predictions of the training samples (Equation~\ref{eq1:sl-train}), and the convergence analysis is provided for a smooth, a hockey-stick, and an indicator $h$.
 
@@
             \end{equation*}
-            where $R_k$ is the Euclidean distance between $X_i$ and its $k$-th nearest neighbor, and $K:\mathbb{R}^d \rightarrow \mathbb{R}$ is a bounded, nonnegative kernel function satisfying 
+            where $R_k$ is a Euclidean distance between $X_i$ and its $k$-th nearest neighbor, and $K:\mathbb{R}^d \rightarrow \mathbb{R}$ is a bounded, nonnegative kernel function satisfying 
             \begin{align*}
@@
             \end{align*}
-            where $\|\cdot\|$ is the Euclidean norm, and  $k$ is the number of nearest neighbors to consider.
+            where $\|\cdot\|$ is the Euclidean norm, and  $k$ is a number of nearest neighbors to consider.
             The k-nearest neighbor (KNN) method is implemented as a metamodel for numerical experiments in~\cite{hong2017kernel}, but the convergence analysis is not provided.
@@
             $$\hat{L}^{\text{KRR}}_{M, N}(X) = \argmin_{g \in \mathcal{N}_{\Psi}(\Omega)} \left( \frac{1}{M} \sum_{i=1}^M (\hat{L}_{N, i} - L_i)^2 + \lambda \|L\|_{\mathcal{N}_{\Psi}(\Omega)}^2\right),$$
-            where $\mathcal{N}_{\Psi}(\Omega)$ is the reproducing kernel Hilbert space (RKHS) with kernel $\Psi$ defined domain $\Omega$, and $\lambda$ is the regularization parameter as in ridge regression.
-            More specifically, $\Phi$ is a Mat\'ern kernel with smoothness parameter $\nu$ and length scale parameter $\upsilon$.
-            ~\cite{wang2022smooth} provides convergence analysis for the AE (Equation~\ref{eq1:ae}), and the convergence analysis is provided for smooth, Lipschitz continuous, and indicator $h$, VaR, and CVaR.
+            where $\mathcal{N}_{\Psi}(\Omega)$ is a reproducing kernel Hilbert space (RKHS) with a kernel $\Psi$ defined on a domain $\Omega$, and $\lambda$ is a regularization parameter as in a ridge regression.
+            More specifically, $\Phi$ is a Mat\'ern kernel with a smoothness parameter $\nu$ and a length scale parameter $\upsilon$.
+            ~\cite{wang2022smooth} provides a convergence analysis for the AE (Equation~\ref{eq1:ae}), and the convergence analysis is provided for a smooth, a Lipschitz continuous, and an indicator $h$, VaR, and CVaR.
 \end{itemize}
@@
 These supervised learning metamodels approximate the inner simulation model $L(\cdot)$ with functions in the form of $\hat{L}^{\text{SL}}_{M, N}(\cdot)$, and the metamodels are used to pool the inner replications from all outer scenarios to estimate the risk measure $\rho$.
-In simulation literature, using models to approximate simulation is often referred to as the metamodeling approach, or it is referred to as a metamodel in the financial engineering literature.
-Supervised learning models are broadly classified into regression and classification models depending on whether the traget variable is continuous or discrete.
+In the simulation literature, using models to approximate simulation is often referred to as a metamodeling approach, or it is referred to as a metamodel in the financial engineering literature.
+Supervised learning models are broadly classified into regression and classification models depending on whether the target variable is continuous or discrete.
 In our context, the target variable $L$ is continuous, and the supervised learning models refer to regression models.
-Regression models can be further categorized into parametric and non-parametric regression.
-Among our interested supervised learning models, regression is a parametric regression model, while kernel smoothing and kernel ridge regression are non-parametric regression model.
+Regression models can be further categorized into parametric and non-parametric regressions.
+Among our interested supervised learning models, a multiple linear regression is a parametric regression model, while kernel smoothing and kernel ridge regression are non-parametric regression models.
 
@@
 For the more complex metamodels, the convergence analysis of their MSEs is more challenging.
-More specifically, the KRR-based nested simulation~\citep{wang2022smooth} provides a convergence analysis in terms of absolute error (AE).
+More specifically, the KRR-based nested simulation~\citep{wang2022smooth} provides a convergence analysis in terms of AE.
 \begin{align} \label{eq1:ae}
@@
 Instead of using a supervised learning model as a metamodel,~\cite{zhang2022sample} uses the likelihood ratio weights to pool the inner replications from all outer scenarios.
-Here, we restrict our attention to problems in the nested expectation form whose outer scenarios characterize the stochasticity of the inner simulation model. 
+Here, we restrict our attention to problems in the nested expectation form which outer scenarios characterize the stochasticity of the inner simulation model. 
 Specifically,
@@
 \end{align}
-
-where $\Gamma$ is the total simulation budget for a nested simulation procedure.
+where $\Gamma$ is the a simulation budget for a nested simulation procedure.
 A special case is the MLMC method, where the total simulation budget $\Gamma$ is the sum of the simulation budgets at all levels.
@@
 In the first part of this section, we summarize the existing asymptotic convergence results of the nested simulation procedures in the literature, and we compare their critical assumptions that guarantee the convergence.
-The remaining of this section aims to fill the gap in the literature by
+The remaining of this section aims to fill the gap in the literature by offering the following steps:
 \begin{itemize}
-    \item providing the asymptotic convergence results for the standard nested simulation procedure, 
-    \item showing the connections between the convergence in MSE and the convergence in probabilistic order for AE in the context of nested simulation procedures, and
-    \item illustrating the asymptotic rate of convergence of a kNN-based nested simulation procedure.
+    \item provide the asymptotic convergence results for the standard nested simulation procedure, 
+    \item show the connections between the convergence in MSE and the convergence in probabilistic order for AE in the context of nested simulation procedures, and
+    \item illustrate the asymptotic rate of convergence of a kNN-based nested simulation procedure.
 \end{itemize}
@@
 a $\Diamond$ indicates the asymptotic convergence result exists in the literature but in a weaker form.
-~\cite{gordy2010nested} provide the asymptotic convergence results for the standard nested simulation procedure with hockey-stick $h$, indicator $h$ and VaR.
+~\cite{gordy2010nested} provide asymptotic convergence results for the standard nested simulation procedure with a hockey-stick $h$, an indicator $h$ and VaR.
 Their CVaR analysis is incomplete as the VaR is assumed to be known but not estimated in the convergence proof.
 When the VaR is known, the CVaR analysis reduces to the nested expectation form with $h$ being a hockey-stick function.
-~\cite{giles2019multilevel} provide the asymptotic convergence results for the MLMC method with an indicator $h$.
-~\cite{broadie2015risk} provide the asymptotic convergence results for the regression-based nested simulation procedure with smooth $h$ and Lipschitz continuous $h$.
+~\cite{giles2019multilevel} provide asymptotic convergence results for the MLMC method with an indicator $h$.
+~\cite{broadie2015risk} provide asymptotic convergence results for the regression-based nested simulation procedure with a smooth $h$ and a Lipschitz continuous $h$.
 The Lipschitz continuous family includes the hockey-stick function as a special case, thus the convergence result for the hockey-stick function is implied.
-~\cite{hong2017kernel} and~\cite{zhang2022sample} provide the asymptotic convergence results with the nested expectation form for the kernel smoothing-based procedure and likelihood ratio-based nested simulation procedure, respectively.
+~\cite{hong2017kernel} and~\cite{zhang2022sample} provide asymptotic convergence results with the nested expectation form for the kernel smoothing-based procedure and likelihood ratio-based nested simulation procedure, respectively.
 The convergence results for a Lipschitz continuous $h$ cannot be directly inferred from the analysis for a hockey-stick function.
@@
 While most of the literature focuses on the MSE of the estimator of $\rho$,~\cite{wang2022smooth} analyze the asymptotic convergence of the estimator of $\rho$ in terms of AE.
-Let $\hat{\rho}$ be the estimator of $\rho$. Its AE about $\rho$ is defined as
+Let $\hat{\rho}$ be the estimator of $\rho$. 
+Then the AE of $\hat{\rho}$ about $\rho$ is defined as
 
@@
 
-We start by showing the convergence in probabilistic order from the convergence in MSE.
+We start our analysis by showing the convergence in probabilistic order from the convergence in MSE.
 Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-\xi} \right)$.
@@
 $$
-The convergence in probabilistic order can be shown by separating the expectation into two parts: tail and non-tail.
+The convergence in probabilistic order can be shown by separating the expectation into two parts: tail and non-tail components.
 $$
@@
 
-In essence, the above is the definition of convergence in probabilistic order, that is,
+In essence, the above expression is a definition of convergence in probabilistic order, that is,
 
@@
 However, the second term is not always bounded. 
-If the random variable $\hat{\rho}_{\Gamma}$ admits a density function $f$, then the second term can be further decomposed.
+If the random variable $\hat{\rho}_{\Gamma}$ admits a density function $f$, then the second term can be further decomposed as follows.
 
@@
 Hence, the converse of Theorem~\ref{thm1:convergence-mse-prob} is not necessarily true, and the convergence in probabilistic order is a weaker form of convergence than the convergence in MSE.
-The immediate implication is that the results in~\cite{wang2022smooth}, which show the convergence in probabilistic order for the AE, is not necessarily equivalent to the convergence in MSE.
+The immediate implication of this result is that the results in~\cite{wang2022smooth}, which show the convergence in probabilistic order for the AE is not necessarily equivalent to the convergence in MSE.
 
@@
 \begin{assumption} \label{as1:sns-noise}
-    $\hat{L}_N(X) = L(X) + \bar{Z}_N(X)$, where the simulation noise $\bar{Z}_N(X)$ has zero mean and variance $\nu(X) / N$, where the conditional variance $\nu(X)$ is bounded, i.e., 
+    $\hat{L}_N(X) = L(X) + \bar{Z}_N(X)$, where the simulation noise $\bar{Z}_N(X)$ has zero mean and variance $\nu(X) / N$, and the conditional variance $\nu(X)$ is bounded, i.e., 
     $$
@@
 For simplicity, we abbreviate $\hat{L}_N(X)$ as $\hat{L}_N$, $\bar{Z}_N(X)$ as $\bar{Z}_N$, and $\bar{Z}_{N, i}$ as $\bar{Z}_{N, i}$.
-Let $\rho_M = \frac{1}{M} \sum_{i=1}^M h(L_i)$ be the nested MC estimator with the true function $g$.
+Let $\rho_M = \frac{1}{M} \sum_{i=1}^M h(L_i)$ be a nested MC estimator with the true function $g$.
 The MSE of the standard nested simulation procedure can be decomposed into two ways.
@@
 The analysis of the first term is different for smooth and Lipschitz continuous $h$. 
-We will analyze them separately.
-
-Another way to decompose the MSE is the bias-variance decomposition as in~\cite{gordy2010nested}.
+We will analyze them separately below.
+
+Another way to decompose the MSE is a bias-variance decomposition as in~\cite{gordy2010nested}.
 
@@
 \end{align}
-
-where $\text{Var}(\hat{\rho}_{M, N})$ is the variance of the estimator and $\text{Bias}(\hat{\rho}_{M, N})$ is the bias of the estimator about $\rho$.
+where $\text{Var}(\hat{\rho}_{M, N})$ is variance of the estimator and $\text{Bias}(\hat{\rho}_{M, N})$ is bias of the estimator about $\rho$.
 For a smooth function $h$, both ways of decomposing the MSE lead to the same order of convergence.
 However, for a Lipschitz continuous function $h$, Equation~\ref{eq1:mse-sns2} leads to a stronger order of convergence than Equation~\ref{eq1:mse-sns}.
-In the following, we analyze the convergence of the standard nested simulation procedure for smooth and Lipschitz continuous $h$ using following both decompositions.
+In the following, we analyze the convergence of the standard nested simulation procedure for a smooth and a Lipschitz continuous $h$ by using both decompositions.
 Their critical assumptions and convergence results are summarized and compared.
@@
 However, we observe that Equation~\ref{eq1:s1-sns} converges in the order of $\mathcal{O}(M^{-1}N^{-1})$.
-The cross term here is potentially problematic \textcolor{red}{(Why?)}, as setting $N$ as a negative power of $M$ may result in Equation~\ref{eq1:s1-sns} to be divergent.
+The cross term here is potentially problematic, as setting $N$ as a negative power of $M$ may result in Equation~\ref{eq1:s1-sns} to be divergent.
 
@@
 \end{align}
-
 where the last equality follows from the Taylor expansion of the smooth function $h$.
@@
 The analysis in~\cite{gordy2010nested} is based on the differentiablity of the joint density of $Y$ and the average inner simulation noise, which is difficult to verify in practice.
-Instead, we use the Taylor expansion of the smooth function $h$ to analyze the convergence of the standard nested simulation procedure.
+Instead, we use the a Taylor expansion of the smooth function $h$ to analyze the convergence of the standard nested simulation procedure.
 The critical assumption in our derivation is Assumption~\ref{as1:sns-noise-var}, which is necessary to ensure the existence of the fourth moment of the simulation noise and the convergence of $S_2$, the second order term in the Taylor expansion.
@@
 We proceed to analyze the convergence for a Lipschitz continuous function $h$.
-For the CVaR analysis in~\cite{gordy2010nested}, the authors assume the knowing of the corresponding VaR.
+For the CVaR analysis in~\cite{gordy2010nested}, the authors assume the knowledge of the corresponding VaR.
 Hence, the analysis of CVaR is not complete.
-Instead, the quantity that is being analyzed is instead the mean excess loss, which corresponds to $h$ being a hockey-stick function and belongs to the family of the Lipschitz continuous functions. 
+Instead, the quantity that is being analyzed is the mean excess loss, which corresponds to $h$ being a hockey-stick function and belongs to the family of the Lipschitz continuous functions. 
 Here we present the convergence analysis for the whole family of the Lipschitz continuous functions, which includes the hockey-stick function as a special case.
@@
 \end{equation}
-Setting $M = \mathcal{O}(\Gamma^{1/2})$ and $N = \mathcal{O}(\Gamma^{1/2})$, we provide a looser bound than the one obtained for hockey-stick $h$.
-Using the bias-variance decomposition in Equation~\ref{eq1:mse-sns2},
+Setting $M = \mathcal{O}(\Gamma^{1/2})$ and $N = \mathcal{O}(\Gamma^{1/2})$, we provide a looser bound than the one obtained for the hockey-stick $h$.
+Using the bias-variance decomposition in Equation~\ref{eq1:mse-sns2}, we obtain the following bias term.
 
@@
 \end{align}
-
 The variance term in Equation~\ref{eq1:mse-sns2} for Lipschitz continuous $h$ is identical to the one in Equation~\ref{eq1:var-sns-smooth}.
@@
 Nevertheless, the numerical results are derived based on a kNN-based nested simulation procedure.
-In this section, we attempt to fill in the holes in the analysis of~\cite{hong2017kernel} by providing the asymptotic convergence of a kNN-based nested simulation procedure for smooth $h$ in the nested expectation form.
+In this section, we attempt to fill in the holes in the analysis of~\cite{hong2017kernel} by providing asymptotic convergence of a kNN-based nested simulation procedure for smooth $h$ in the nested expectation form.
 Surprisingly, the asymptotic convergence rate of the kNN-based nested simulation procedure is noticeably different from the result obtained in~\cite{hong2017kernel}.
@@
 A kNN regression can be used as a non-parametric metamodel that estimates the conditional expectation of $Y$ given $X$ by averaging the $Y$ values of the $k$ nearest neighbors of $X$.
-Without loss of generality, we assume that $\{(X_i, \bar{Y}_{n, i}), i = 1, \dots, M\}$ are independent and identically distributed (i.i.d.) observations of $(X, Y)$ from the standard nested simulation procedure with an inner simulation budget of $n$, where $X_i$ is the $i^{\text{th}}$ of the outer scenario $X \in \Omega \subset \mathbb{R}^d$, and $\bar{Y}_{n, i}$ is the estimate of $Y|X_i$ with an inner simulation budget of $n$.
-Let $f_{XY}(x, y)$ be the joint density of random vector $(X, Y)$, and $f_X(x) = \int f_{XY}(x, y) dy$ be the marginal density of $X$.
+Without loss of generality, we assume that $\{(X_i, \bar{Y}_{n, i}), i = 1, \dots, M\}$ are i.i.d.
+observations of $(X, Y)$ from the standard nested simulation procedure with an inner simulation budget of $n$, where $X_i$ is the $i^{\text{th}}$ of the outer scenario $X \in \Omega \subset \mathbb{R}^d$, and $\bar{Y}_{n, i}$ is an estimate of $Y|X_i$ with an inner simulation budget of $n$.
+Let $f_{XY}(x, y)$ be a joint density of random vector $(X, Y)$, and $f_X(x) = \int f_{XY}(x, y) dy$ be a marginal density of $X$.
 Let $k$ be a sequence of positive integers $k = k(M)$ such that 
@@
 \end{align*}
-A kNN-based nested simulation procedure with model parameter $k$ estimates the risk measure $\rho = \mathbb{E} \left[ h(L) \right]$ with
+A kNN-based nested simulation procedure with a model parameter $k$ estimates the risk measure $\rho = \mathbb{E} \left[ h(L) \right]$ with
 
@@
     \end{equation*}
-    where $R_k$ is the Euclidean distance between $X_i$ and its $k$-th nearest neighbor, and $K:\mathbb{R}^d \rightarrow \mathbb{R}$ is a bounded, nonnegative kernel function satisfying 
+    where $R_k$ is a Euclidean distance between $X_i$ and its $k$-th nearest neighbor, and $K:\mathbb{R}^d \rightarrow \mathbb{R}$ is a bounded, nonnegative kernel function satisfying 
     \begin{align*}
@@
     \end{align*}
-where $\|\cdot\|$ is the Euclidean norm, and $k$ is the number of nearest neighbors to consider.
+where $\|\cdot\|$ is a Euclidean norm, and $k$ is a number of nearest neighbors to consider.
 For a kNN estimator trained with $M$ i.i.d. observations, denote $B_M(x)$ and $V_M(x)$ as its bias and variance at point $x$, respectively.
@@
 \begin{assumption} \label{as1:knn}
-    $f_X$ is bounded and continuously differentiable up to second order in a neighborhood of $x$ with $f_X(x) > 0$, $f_X$, $\mathbb{E} \left[ Y^2| X = x \right] < \infty$, and the kernel function $K$ satisfies
+    $f_X$ is bounded and continuously differentiable up to a second order in a neighborhood of $x$ with $f_X(x) > 0$, $f_X$, $\mathbb{E} \left[ Y^2| X = x \right] < \infty$, and the kernel function $K$ satisfies
     \begin{align*}
@@
     \end{align*}
-    Suppose $\mathbb{P}(\|x - X\| > r) = \mathcal{O}(r^{-\alpha})$ for some $\alpha > 0$ as $r \rightarrow \infty$.
+    Suppose that $\mathbb{P}(\|x - X\| > r) = \mathcal{O}(r^{-\alpha})$ for some $\alpha > 0$ as $r \rightarrow \infty$.
 \end{assumption}
 
-The following lemma from~\cite{mack1981local} characterizes the pointwise convergence of the kNN estimator in terms of its bias and variance at point $x$.
+The following lemma from~\cite{mack1981local} characterizes pointwise convergence of the kNN estimator in terms of its bias and variance at point $x$.
 
 \begin{lemma}
-    Assume the random vector $(X, Y)$ and the kernel function $K$ satisfies Assumption~\ref{as1:knn}. Then the bias and variance of the kNN estimator at point $x$ are given by
+    Assume that a random vector $(X, Y)$ and a kernel function $K$ satisfies Assumption~\ref{as1:knn}. Then the bias and variance of the kNN estimator at point $x$ are given by
     \begin{align*}
@@
 Let $h$ be a smooth function, i.e., Assumption~\ref{as1:sns-smooth} holds.
-The bias of the estimator of $\rho$ for a kNN-based nested simulation procedure is analyzed following Taylor expansion.
+The bias of the estimator of $\rho$ for a kNN-based nested simulation procedure is analyzed following a Taylor expansion.
 \begin{align} \label{eq1:bias-knn}
@@
 \end{align}
-
 where the second term in Equation~\ref{eq1:bias-knn-2} is of higher order than Equation~\ref{eq1:bias-knn-1}, and it is negligible since $kM^{-1} \rightarrow 0$ as $M \rightarrow \infty$ and $k \rightarrow \infty$,
@@
 ~\cite{gordy2010nested} and~\cite{broadie2015risk} assume that the inner simulation noise has zero mean and variance that is inversely proportional to the inner simulation budget $N$, i.e., Assumption~\ref{as1:sns-noise}.
-The analysis in~\cite{gordy2010nested} further requires assumptions on $f_{Y,\tilde{Z}_N}(y,z_N)$, the joint density of random variable $Y$ and the normalized inner simulation noise $\tilde{Z}_N := \sqrt{N} \cdot\bar{Z}_N(X)$.
+The analysis in~\cite{gordy2010nested} further requires assumptions on $f_{Y,\tilde{Z}_N}(y,z_N)$, a joint density of random variable $Y$ and the normalized inner simulation noise $\tilde{Z}_N := \sqrt{N} \cdot\bar{Z}_N(X)$.
 
@@
 However, Assumption~\ref{as1:sns-joint-density-bound} is hard to be verified in practice.
-Since~\cite{broadie2015risk} only analyze the nested expectation case with smooth and Lipschitz continuous function $h$, the regression-based nested simulation procedure does not require Assumption~\ref{as1:sns-joint-density} and~\ref{as1:sns-joint-density-bound} for the convergence analysis.
-In our analysis of the standard nested simulation procedure for smooth $h$ in the nested expectation form, we make additional assumptions on the fourth moment of the inner simulation noise, i.e., Assumption~\ref{as1:sns-smooth}, so the second-order term in the Taylor expansion can be bounded.
+Since~\cite{broadie2015risk} only analyze the nested expectation case with a smooth and a Lipschitz continuous function $h$, the regression-based nested simulation procedure does not require Assumptions~\ref{as1:sns-joint-density} and~\ref{as1:sns-joint-density-bound} for the convergence analysis.
+In our analysis of the standard nested simulation procedure for a smooth function $h$ in the nested expectation form, we make additional assumptions on the fourth moment of the inner simulation noise, i.e., Assumption~\ref{as1:sns-smooth}, so that the second-order term in the Taylor expansion can be bounded.
 
@@
 \begin{assumption} \label{as1:likelihood-ratio-marginal-density}
-    The marginal density $f_H(y)$ of $H$ exists. $f_H(y)$ can be sampled from and evaluated, and $Y(y, x) f_{H|X}(y|x) = 0$ whenever $f_H(x) = 0$. 
+    The marginal density $f_H(y)$ of $H$ exists. $f_H(y)$ can be sampled and evaluated, and $Y(y, x) f_{H|X}(y|x) = 0$ whenever $f_H(x) = 0$. 
 \end{assumption}
@@
 For the kernel-based nested simulation procedure,~\cite{hong2017kernel} simplifies the analysis by assuming that for each $X_i$, the inner simulation budget $N$ is fixed together with the variance of the inner simulation noise $\bar{Z}_{N, i}$.
-In essence, this fixed variance design treats the $(X_i, \bar{Y}_{N, i})$ as independent and identically distributed observations of $(X, Y)$, and the kernel-based nested simulation procedure is analyzed as a nonparametric regression problem.
+In essence, this fixed variance design treats the $(X_i, \bar{Y}_{N, i})$ as independent and identically distributed observations of $(X, Y)$, and the kernel-based nested simulation procedure is analyzed as a non-parametric regression problem.
 Regularity conditions on $f_X(x)$, the density of $X$, and the conditional second moment of $Y$ are assumed to ensure the convergence of $\hat{L}^{\text{KS}}_{M, N}(X)$, the kernel smoothing estimator of $L$.
@@
 The inner simulation noise is assumed to have lighter tails than the normal distribution, while examples of random variables that satisfy the sub-Gaussian assumption are hard to find.
-In addition, the following assumptions are made on $\Omega$, the domain of the outer scenario $X$:
+In addition, the following assumptions are made on $\Omega$, which is the domain of the outer scenario $X$:
 
@@
 \section{Finite-Sample Experiments} \label{sec1:numerical-experiments}
-The theoretical framework has allowed the comparison of the asymptotic convergence behavior for different nested simulation procedures.
+The theoretical framework has lend itself for a comparison of the asymptotic convergence behavior for different nested simulation procedures.
 However, a simulation budget in practice is almost always finite.
@@
 
-A total of 5 nested simulation procedures are considered, namely the standard nested simulation procedure, the regression-based, kernel smoothing-based, likelihood ratio-based, and kernel ridge regression-based nested simulation procedures.
+A total of 5 nested simulation procedures are considered, namely a standard nested simulation procedure, a  regression-based, a kernel smoothing-based, a likelihood ratio-based, and a kernel ridge regression-based nested simulation procedure.
 For the standard nested simulation procedure, the bootstrap-based budget allocation strategy from~\cite{zhang2021bootstrap} is implemented to estimate the optimal values of outer and inner simulation budgets.
 For the regression metamodel, the Laguerre polynomials up to degree $3$ are used as the default basis functions.
-The kNN metamodel is implemented for the kernel smoothing-based procedure, and a cross-validation with grid search is used to find the optimal number of neighbors.
-The KRR metamodel is implemented with a Mat\'ern kernel, and the smoothness, the length scale, and the regularization hyperparameters are found by a cross-validation with Bayesian search~\citep{frazier2018bayesian}.
-Due to budget constraints, the hyperparameters of the nonparametric regression metamodel are tuned and used across all macro replications of the same experiment.
+The kNN metamodel is implemented for the kernel smoothing-based procedure, and a cross-validation procedure with a grid search is used to find the optimal number of neighbors.
+The KRR metamodel is implemented with a Mat\'ern kernel, and the smoothness, the length scale, and the regularization hyperparameters are found by a cross-validation procedure with a Bayesian search~\citep{frazier2018bayesian}.
+Due to budget constraints, the hyperparameters of the non-parametric regression metamodel are tuned and used across all macro replications of the same experiment.
 
@@
 \end{itemize}
-where the threshold $u$ for the mean excess loss and the probability of a large loss is set to be the 90\% VaR.
+where the threshold $u$ for the mean excess loss and the probability of a large loss is set to be 90\% VaR.
 The procedures are compared for different portfolios consisting of different types of options:
@@
     \item   Portfolio 1 consists of $d$ assets.
-    The portfolio contains 3 European call options written on each asset with strikes $90$, $100$, and $110$, respectively. 
+    This portfolio contains 3 European call options written on each asset with strikes $90$, $100$, and $110$, respectively. 
     \item   Portfolio 2 consists of $d$ assets.
-    The portfolio contains 3 geometric Asian options written on each asset with strikes $90$, $100$, and $110$, respectively. 
+    This portfolio contains 3 geometric Asian options written on each asset with strikes $90$, $100$, and $110$, respectively. 
     \item   Portfolio 3 consists of $d$ assets.
-    The portfolio contains 3 up-and-out barrier call options written on each asset with strikes $90$, $100$, and $110$, respectively. They have a barrier level of $120$.
+    This portfolio contains 3 up-and-out barrier call options written on each asset with strikes $90$, $100$, and $110$, respectively. They have a barrier level of $120$.
     \item   Portfolio 4 considers $d$ assets.
-    The portfolio contains 3 down-and-out barrier call options written on each asset with strikes $90$, $100$, and $110$, respectively. They have a barrier level of $90$.
+    This portfolio contains 3 down-and-out barrier call options written on each asset with strikes $90$, $100$, and $110$, respectively. They have a barrier level of $90$.
     \item   Portfolio 5 contains 1 asset.
-    The portfolio longs 2 down-and-out barrier put options and shorts 1 barrier down-and-out put option. 
+    This portfolio longs 2 down-and-out barrier put options and shorts 1 barrier down-and-out put option. 
 \end{itemize}
-Except for portfolio 5, 5 different asset dimensions are considered, i.e., $d = 1, 2, 5, 10, 20$.
+Except for Portfolio 5, 5 different asset dimensions are considered, i.e., $d = 1, 2, 5, 10, 20$.
 525 experiment settings that arise from an exhaustive combination of the above simulation procedures, risk measures, portfolios, and asset dimensions are generated.
@@
 The empirical convergence results of each estimator are measured and recorded to illustrate their empirical behavior under different risk measures, option types, and asset dimensions.
-We start by examining the empirical convergence results for the most basic case, i.e., the quadratic tracking error risk measure for European call options on Portfolio 1 with $d = 1$.
+We start by examining the empirical convergence results for the most basic case, i.e., a quadratic tracking error risk measure for European call options on Portfolio 1 with $d = 1$.
 
@@
 In the following sections, we examine the empirical convergence of the nested simulation procedures in a similar manner as in Figure~\ref{fig1:compareAll}.
-With a more detailed analysis of different risk measures, option types, and asset dimensions, we aim to provide a comprehensive understanding and comparison of the convergence behavior of the nested simulation procedures in practice.
+With a more detailed analysis of different risk measures, option types, and asset dimensions, we aim at providing a comprehensive understanding and comparison of the convergence behavior of the nested simulation procedures in practice.
 
@@
 The empirical rates of convergence of the standard, the KRR-based, and the likelihood ratio-based procedures closely match their asymptotic rates for both asset dimensions, and they are insensitive to an increase in the asset dimension.
-Conversely, both the kernel smoothing-based and regression-based procedures are greatly affected by the asset dimension.
+In contrast, both the kernel smoothing-based and regression-based procedures are greatly affected by the asset dimension.
 Their sensitivities to the asset dimension differ in finite-sample experiments:
@@
 
-Kernel smoothing is a nonparametric regression metamodel.
+Kernel smoothing is a non-parametric regression metamodel.
 According to the theoretical analysis in Section~\ref{sec1:asymptotic-convergence}, the asymptotic rate of convergence of the kernel smoothing-based nested simulation procedure is highly dependent on the asset dimension $d$.
@@
 
-In Figure~\ref{fig1:kernel_d}, the empirical convergence of the kernel smoothing-based nested simulation procedure for quadratic tracking error is illustrated for different asset dimensions, i.e., $d = 1, 2, 5, 10$.
-The observation finds that the kernel smoothing-based nested simulation procedure is extremely sensitive to the asset dimension and the payoff structure.
+In Figure~\ref{fig1:kernel_d}, the empirical convergence of the kernel smoothing-based nested simulation procedure for a quadratic tracking error is illustrated for different asset dimensions, i.e., $d = 1, 2, 5, 10$.
+The experiment finds that the kernel smoothing-based nested simulation procedure is extremely sensitive to the asset dimension and the payoff structure.
 While the asset dimension is expected to be a critical factor as shown in the theoretical analysis, the payoff structure is an unexpected factor that affects the empirical convergence of the kernel smoothing-based nested simulation procedure.
 For a portfolio with geometric Asian options, the payoff complexity is higher than that of a portfolio with European call options.
-The empirical rate of convergence of the kernel smoothing-based procedure is significantly lower for the portfolio with geometric Asian options than for the portfolio with European call options.
+The empirical rate of convergence of the kernel smoothing-based procedure is substantially lower for the portfolio with geometric Asian options than for the portfolio with European call options.
 For geometric Asian options, the empirical rates of convergence are even lower than the asymptotic rates for all asset dimensions.
@@
 Another phenomenon that is observed in Figure~\ref{fig1:kernel_d} is that the empirical rate of convergence of the kernel smoothing-based procedure does not decrease monotonically as the simulation budget increases.
-This is likely due to the fact that the kernel smoothing-based procedure, as a nonparametric regression procedure, is highly dependent on the cross-validation of the hyperparameters of the metamodel.
+This is likely due to the fact that the kernel smoothing-based procedure, as a non-parametric regression procedure, is highly dependent on the cross-validation of the hyperparameters of the metamodel.
 For the kernel smoothing-based procedure, the kNN metamodel is implemented. 
@@
 For $d = 2$, the optimal value of $k$ is estimated to be between $120$ to $220$ for most replications, and the estimated risk measures are close to the true risk measure of $0.1$.
-For the two replications where $k = 80$ is estimated as the optimal value of $k$, the resulting estimates of risk measures are $0.1187$ and $0.1189$, which are significantly higher than the estimated risk measures for the other replications and far from the true risk measure of $0.1$.
+For the two replications where $k = 80$ is estimated as the optimal value of $k$, the resulting estimates of risk measures are $0.1187$ and $0.1189$, which are substantially higher than the estimated risk measures for the other replications and far from the true risk measure of $0.1$.
 This observation suggests that the empirical convergence of the kernel smoothing-based nested simulation procedure is highly sensitive to the cross-validation of the hyperparameters of the metamodel.
@@
 For dimensions larger than $10$, the MSE of the regression procedure decreases quickly in the beginning, and its rate of decrease stabilizes after a certain budget level.
-In~\ref{fig1:reg_lb} illustrates the empirical convergence of the regression-based procedure in more detail at higher simulation budgets, where the asymptotic level of convergence is reached for $d = 20$.
+In Figure~\ref{fig1:reg_lb} illustrates the empirical convergence of the regression-based procedure in more detail at higher simulation budgets, where the asymptotic level of convergence is reached for $d = 20$.
 
@@
 Slopes of the fitted lines on the left correspond to the empirical rate of convergence of the regression procedure for budget levels between $10^3$ and $10^4$.
-To investigate the convergence behavior for higher budget levels, we conduct additional experiments for the European call option with dimension $20$. 
+To investigate the convergence behavior for higher budget levels, we conduct additional experiments for the European call option with a dimension of $20$. 
 The additional experiments are summarized on the right side of Figure \ref{fig1:reg_lb}.
@@
 \begin{itemize}
-    \item For small budget sizes, the improvement in the bias of the regression metamodel dominates the improvement in simulation variance. 
-    Performing poorly for extremely low simulation budgets, the regression metamodel improves significantly as the simulation budget increases.
+    \item For small budget sizes, the improvement in the bias of the regression metamodel dominates the improvement in the simulation variance. 
+    Performing poorly for extremely low simulation budgets, the regression metamodel improves dramatically as the simulation budget increases.
     \item As the simulation budget gets higher, the improvement of the regression bias becomes negligible compared with that of the simulation variance. 
@@
 \end{itemize}
-Due to high computational costs, we are not able to conduct experiments for even higher budget levels, but we expect the MSE of the regression-based nested simulation procedure to stabilize after $\Gamma = 10^6$, and the empirical rate of convergence to approach its asymptotic rate.
-In the context of nested simulation procedures, a parametric regression metamodel has several advantages over a nonparametric regression metamodel.
+Due to high computational costs, we are not able to conduct experiments for higher budget levels, but we expect the MSE of the regression-based nested simulation procedure to stabilize after $\Gamma = 10^6$, and the empirical rate of convergence to approach its asymptotic rate.
+In the context of nested simulation procedures, a parametric regression metamodel has several advantages over a non-parametric regression metamodel.
 \begin{itemize}
@@
 In our previous numerical experiments, we have examined the empirical convergence behavior of the nested simulation procedures for European call options, which only depends on the asset price at maturity.
-To examine the sensitivity of the empirical convergence behavior to the option type, we consider path-dependent options, i.e., geometric Asian options and barrier options.
+To examine the sensitivity of the empirical convergence behavior to the option type, we consider path-dependent options, which are geometric Asian options and barrier options.
 
@@
 We have incorporated this example as Portfolio 5.
-In Figure~\ref{fig1:5503}, the empirical convergence of the nested simulation procedures for quadratic tracking error and mean excess loss on Portfolio 5 is illustrated for $d = 1$.
+In Figure~\ref{fig1:5503}, the empirical convergence of the nested simulation procedures for a quadratic tracking error and a mean excess loss on Portfolio 5 is illustrated for $d = 1$.
 For all procedures, we observe a similar convergence behavior as in other path-dependent options.
@@
 Our previous numerical experiments have been conducted under the assumption that the underlying asset dynamics follow a multidimensional geometric Brownian motion with $0.3$ pairwise correlation.
-To examine the sensitivity of the empirical convergence behavior to the asset model, we consider a stochastic volatility model, i.e., a Heston model.
+To examine the sensitivity of the empirical convergence behavior to the asset model, we consider a stochastic volatility model of a Heston type~\citep{heston1993stochastic}.
 
@@
 Their faster convergence benefits from the pooling of inner samples through the metamodels. 
-However, pooling itself comes with computational costs, which are usually ignored in most numerical comparisons. 
+However, pooling itself comes with increased computational costs, which are usually ignored in most numerical comparisons. 
 This section summarizes the algorithmic complexity and illustrate the computational time of different nested simulation procedures.
@@
 The simulation cost is omitted from Table~\ref{tab1:complexity}, as all procedures are given the same simulation budget.
-Given $M$ outer samples and the corresponding $M$ inner sample averages, the algorithmic complexity of the additional operations does not involve $N$ thus can be written in terms of $M$ only.
-The training cost includes the cost of fitting the metamodel and the cost of cross-validation for nonparametric regression metamodels.
+Given $M$ outer samples and the corresponding $M$ inner sample averages, the algorithmic complexity of the additional operations does not involve $N$ and thus, can be written in terms of $M$ only. 
+The training cost includes the cost of fitting the metamodel and the cost of cross-validation for non-parametric regression metamodels.
 
@@
           Estimating the coefficients of the regression model involves multiplying the design matrix by its transpose and inverting the resulting matrix, which has complexity $\mathcal{O}(p^2M)$ and $\mathcal{O}(p^3)$, respectively.
-          For a review in the complexity of matrix inversion, see~\cite{stothers2010complexity}.
-          The matrix inversion has complexity $\mathcal{O}(p^3)$ using Gauss-Jordan elimination, but in practice, the complexity can be reduced to $\mathcal{O}(p^{2.807})$ by~\cite{strassen1969gaussian} and $\mathcal{O}(p^{2.376})$ by~\cite{coppersmith1987matrix}.
+          For a review in the complexity of a matrix inversion, see~\cite{stothers2010complexity}.
+          The matrix inversion has complexity $\mathcal{O}(p^3)$ using a Gauss-Jordan elimination, but in practice, the complexity can be reduced to $\mathcal{O}(p^{2.807})$ by~\cite{strassen1969gaussian} and $\mathcal{O}(p^{2.376})$ by~\cite{coppersmith1987matrix}.
           In practice, $p$ is usually much smaller than $M$ and does not grow with the simulation budget $\Gamma$.
@@
 For the kernel smoothing-based procedure, the kNN metamodel is implemented. 
-In practice, the K-D tree algorithm~\citep{bentley1975multidimensional} is often implemented for efficient nearest neighbor search.
+In practice, the K-D tree algorithm~\citep{bentley1975multidimensional} is often implemented for an efficient nearest neighbor search.
 \begin{itemize}
-    \item During training, a tree is constructed to store the distance, which has complexity $\mathcal{O}(M\log(M))$.
+    \item During training, a tree is constructed to store the distance, which has a degree of complexity of $\mathcal{O}(M\log(M))$.
     \item The prediction cost of the kernel smoothing-based procedure is $\mathcal{O}(kM\log(M))$, which comes from a query of the K-D tree for $k$ nearest neighbors for $M$ samples.
-    Conversely, An inefficient algorithm calculates the distance matrix during training and a block sort algorithm to find the $k$ nearest neighbors, which results in a complexity of $\mathcal{O}(M^2)$ and $\mathcal{O}(M^2\log(M))$, respectively.
-    A practical implementation of block sort is provided in~\cite{kim2008ratio}.
+    Conversely, an inefficient algorithm calculates the distance matrix during training and a block sort algorithm to find the $k$ nearest neighbors, which results in a degree of complexity of $\mathcal{O}(M^2)$ and $\mathcal{O}(M^2\log(M))$, respectively.
+    A practical implementation of a block sort is provided in~\cite{kim2008ratio}.
     Hence, an efficient implementation of the kNN metamodel is crucial for the kernel smoothing-based procedure.
@@
 \begin{itemize}
-    \item the main training cost comes from inverting an $M \times M$ kernel matrix~\citep{scholkopf2002learning}, which has complexity $\mathcal{O}(M^3)$ using Gauss-Jordan elimination.
+    \item the main training cost comes from inverting an $M \times M$ kernel matrix~\citep{scholkopf2002learning}, which has a degree of complexity of $\mathcal{O}(M^3)$ using a Gauss-Jordan elimination.
           Similar to the regression-based procedure, this complexity can be reduced to $\mathcal{O}(M^{2.376})$.
@@
 Among the metamodel-based procedures, parametric regression is the most efficient.
-In regression, the number of features is usually much less than the number of data points, i.e., $p<M$. 
+In the multiple linear regression, the number of features is usually much less than the number of data points, i.e., $p<M$. 
 Kernel smoothing and KRR are kernel-based metamodels, and they are more computaional expensive due to distance calculations and cross-validations of hyperparameters. 
-The kNN metamodel has only 1 hyperparameter $k$, while the KRR metamodel requires 3 hyperparameters, namely the smoothness hyperparameter $\nu$, scale hyperparameter $\upsilon$, and the regularization hyperparameter $\lambda$.
+The kNN metamodel has only 1 hyperparameter $k$, while the KRR metamodel requires 3 hyperparameters, namely a smoothness hyperparameter $\nu$, a scale hyperparameter $\upsilon$, and a regularization hyperparameter $\lambda$.
 Calculating the likelihood ratio weights is inevitable for the likelihood ratio-based procedure. 
@@
 
-The cost associated with pooling makes a significant impact on the overall computaional complexity of a metamodel-based nested simulation procedure.
-In our finite-sample experiments, we have indeed observed that the actual computational cost to deviate significantly from the simulation cost.
+The cost associated with pooling makes a major impact on the overall computaional complexity of a metamodel-based nested simulation procedure.
+In our finite-sample experiments, we have indeed observed that the actual computational cost to deviate substantially from the simulation cost.
 In Figure~\ref{fig1:tcc}, the total actual computational time of different nested simulation procedures for European call options and geometric Asian options with $d = 10$ is illustrated in a log-log scale.
@@
 The regression and kernel smoothing-based procedures are the most efficient among the metamodel-based procedures.
-Since the regression-based procedure has a higher empirical rate of convergence, it is preferred over the kNN.
+Since the regression-based procedure has a higher empirical rate of convergence, it is preferred over kNN.
 The likelihood ratio-based and KRR-based procedures are the most computationally expensive among all procedures.
@@
     This cost does not grow with the simulation budget $\Gamma$, as its slope is close to $0$.
-    \item The regression-based procedure does not require hyperparameter tuning, and its total computational time is mainly attributed to the model implementation.
-    The slope of the regression line is close to $1$, resembling the its algorithmic complexity in Table~\ref{tab1:complexity}.
-    \item The kernel smoothing-based and KRR-based procedure requires cross-validation to estimate the optimal hyperparameters. 
-    In our implementaion of kNN, the cross-validation is conducted using a grid search with a search space whose cardinality does not grow with the simulation budget $\Gamma$.
+    \item The regression-based procedure does not require any hyperparameter tuning, and its total computational time is mainly attributed to the model implementation.
+    The slope of the regression line is close to $1$, resembling its algorithmic complexity reported in Table~\ref{tab1:complexity}.
+    \item The kernel smoothing-based and KRR-based procedure requires a cross-validation procedure to estimate the optimal hyperparameters. 
+    In our implementaion of kNN, the cross-validation is conducted by using a grid search with a search space which cardinality does not grow with the simulation budget $\Gamma$.
     However, the cross-validation cost of the kernel smoothing-based procedure grows with the simulation budget $\Gamma$ as more samples are involved.
-    The KRR-based procedure requires Bayesian optimization to estimate the optimal hyperparameters, and the cardinality of the search space also grows with the simulation budget $\Gamma$.
-    The empirical cost of the KRR-based procedure does not resemble its algorithmic complexity in Table~\ref{tab1:complexity}.
+    The KRR-based procedure requires a Bayesian optimization to estimate the optimal hyperparameters, and the cardinality of the search space also grows with the simulation budget $\Gamma$.
+    The empirical cost of the KRR-based procedure does not resemble its algorithmic complexity reported in Table~\ref{tab1:complexity}.
     The efficient implementation of KRR is an active area of research, and the computational cost of KRR can be reduced by using a low-rank approximation of the kernel matrix, e.g., the Nystr\"om method~\citep{nystrom1930praktische}.
-    Our observation for KRR implementation time is in line with the findings in~\cite{scikit-learn}, where the cost of KRR is reported quickly increasing with the number of samples.
+    Our observation for the KRR implementation time is in line with the findings in~\cite{scikit-learn}, where the cost of KRR is reported to be increasing quickly with the number of samples.
     \item The likelihood ratio-based procedure requires no hyperparameter tuning, and its total computational time is mainly attributed to the likelihood weight calculation, which is $\mathcal{O}(M^2)$.
@@
 In summary, for a large simulation budget, the regression-based procedure is the most efficient among all metamodel-based procedures in terms of computational time.
-For moderate simulation budgets, the regression-based procedure should be the preferred choice.
+For moderate simulation budgets, the regression-based procedure is a preferred choice.
 
@@
 Tremendous efforts have been made to improve the efficiency of nested simulation procedures by approximating the inner simulation model with a metamodels. 
-In this study, we review the literature on nested simulation procedures in financial engineering and establish fair comparisons of different metamodels using the same set of numerical examples. 
+In this study, we review the literature on nested simulation procedures in financial engineering and provide fair comparisons of different metamodels by using the same set of numerical examples. 
 Asymptotic properties of estimators for different nested simulation procedures are influenced by their corresponding metamodels.
 To show an asymptotic convergence result, a more complex metamodels requires a more stringent set of assumptions on the distribution of the outer scenario and the inner simulation noise.
-With extensive numerical experiments, we have found the finite-sample performance of a procedure can deviate from its theory. 
+With extensive numerical experiments, we have found that the finite-sample performance of a procedure can deviate from its theory. 
 In theory, supervised learning-based nested simulation procedures often provide higher rates of convergence, but they come at the computational expense of model training and generating predictions from the trained models.
-The likelihood ratio-based procedure requires no training, but it is computationally expensive to compute and store the likelihood weights.
+The likelihood ratio-based procedure requires no training, but it is expensive to compute, and it is also expensive to store the likelihood weights.
 As a result, the total computational budget is not necessarily the same as the simulation budget, which is usually a limiting factor for practical applications.
@@
 For a nested estimation problem with a given computational budget, we suggest the use of the regression-based simulation procedure when the budget size is moderate. 
-It is efficient to implement, and it exhibits fast empirical convergence in estimating risk measures for option portfolios. 
+It is efficient to implement, and it exhibits fast empirical convergence in estimating risk measures for popular option portfolios. 
 However, we have only examined the performance for option portfolios in this study, where finding a suitable set of basis functions for regression is relatively easy.
 In practice, a variable annuity contract is often high-dimensional in time with a complex payoff structure, and it is a challenging problem for nested simulation procedures.
-The time dependence in the feature space leads to multi-collinearity, and the regression-based procedure may not be the best choice.
+The time dependence in the feature space leads to multi-collinearity, and the regression-based procedure may not be the best choice in such instances.
 In such cases, a neural network-based procedure may be more suitable, as it is a data-driven algorithm that finds a suitable set of basis functions automatically.

### 2025-02-02 project2/nnMetamodels.tex
new
1

@@
 Deep neural networks (DNNs) have attracted attentions of researchers and practitioners due to their success~\citep{hastie2009elements,lecun2015deep} in solving real-world machine learning tasks such as AlphaGo~\citep{silver2016mastering} and ChatGPT~\citep{chatgpt}.
-Since the first artificial neural network model~\citep{mcculloch1943logical} and the first algorithm for training a perceptron~\citep{rosenblatt1958perceptron}, especially after the introduction of backpropagation~\citep{rumelhart1985learning} and the growth of high-performance computing, the field of artificial neural network and deep learning in general has grown rapidly.
-Two specialized neural network architectures that are relevant to our study are RNN~\citep{williams1989learning,sutskever2014sequence} and LSTM~\citep{hochreiter1997long,chung2014empirical}, as In the field of actuarial science, a metamodel is commonly referred to as a proxy model.
+Since the first artificial neural network model~\citep{mcculloch1943logical} and the first algorithm for training a perceptron~\citep{rosenblatt1958perceptron}, especially after the introduction of backpropagation~\citep{rumelhart1985learning} and the growth of high-performance computing, the field of artificial neural network and deep learning in general has been growing rapidly.
+Two specialized neural network architectures that are relevant to our study are RNN~\citep{williams1989learning,sutskever2014sequence} and LSTM~\citep{hochreiter1997long,chung2014empirical}.
+In the field of actuarial science, a metamodel is commonly referred to as a proxy model.
 Despite their success, DNN models are often criticized for their lack of transparency and interpretability, which hinders their adoption in financial and actuarial applications.
-Enormous research efforts are spent to test and improve the robustness of DNN models with carefully designed noise injection methods.
+Enormous research efforts have been spent to test and improve the robustness of DNN models with carefully designed noise injection methods.
 ~\cite{poole2014analyzing} show that injecting synthetic noise before and after hidden unit activations during training improves the performance of autoencoders.
@@
 
-The contributions of our study are two-fold:
+The contributions of our study in this chapter are two-fold:
 \begin{enumerate}
@@
     The first procedure uses a metamodel to identify a set of potential tail scenarios on which computations are performed in stage 2, while the second procedure uses metamodel predictions to estimate risk measures directly.
-    Our numerical results show that DNN metamodels can identify the tail scenarios accurately and so the proposed procedures can estimate tail risk measures with similar accuracy while, at the same time, using less simulation budget.
+    Our numerical results show that DNN metamodels can identify the tail scenarios accurately and so the proposed procedures can estimate tail risk measures with a similar degree of accuracy while, at the same time, using less simulation budget.
 \end{enumerate}
 
-We are curious about fundamental questions like ``What do DNNs learn from noisy data?'' and ``How well do neural networks learn from noisy data?''.
+In essence, we are curious about two fundamental questions:
+\begin{enumerate}
+    \item ``What do DNNs learn from noisy data?'' and 
+    \item ``How well do neural networks learn from noisy data?''.
+\end{enumerate}
 Data-driven answers to these questions prevail in the existing literature.
-In supervised learning, DNNs are believed to learn from the given data about the feature-label relationship to predict new labels for unseen features.
-Cross-validation using to assess a subset, i.e., the validation set, of the original data, is a common way to access the quality of learning.
+In supervised learning, DNNs are believed to learn from a given data about the feature-label relationship to predict new labels for unseen features.
+A cross-validation procedure used to assess a subset, i.e., the validation set, of the original data, is a common way to access the quality of learning.
 Generalization error on the test labels is another popular assessment metric.
@@
 
-In nested simulation, a simulation model is used to generate a large number of outer scenarios, and each scenario is then used as an input to another simulation model, referred to as the inner simulation model.
-Borrowing terminologies from machine learning research, we can view a set of simulated outer scenarios and the estimated hedging errors for those scenarios as the \textit{features} and noisy \textit{labels}.
+In a nested simulation, a simulation model is used to generate a large number of outer scenarios, and each scenario is then used as an input to another simulation model, referred to as a inner simulation model.
+Borrowing terminologies from the machine learning community, we can view a set of simulated outer scenarios and estimated hedging errors for those scenarios as \textit{features} and noisy \textit{labels}.
 The noise level of the labels can be controlled by the number of inner replications in the inner simulation model.
@@
 They are then used to replace the time-consuming inner simulations by the trained model.
-We refer to the trained supervised learning models as \textit{metamodels} of the inner simulation, which is also known as the \textit{surrogate models} in simulation literature.
+We refer to the trained supervised learning models as \textit{metamodels} of the inner simulation, which is also known as the \textit{surrogate models} in the simulation literature.
 Metamodeling is a popular approach to reduce the computational burden of simulation-based applications by replacing the time-consuming simulation with a metamodel.
@@
 The study of metamodeling is an active research area in the simulation literature, and using DNNs as metamodels is a relatively new development.
-~\cite{fonseca2003simulation} provide general guidelines for simulation metamodeling with neural networks,~\cite{lieu2022adaptive} use DNNs as metamodels of a simulation model for structural reliability analysis, and~\cite{salle2014efficient} show that neural network metamodels help achieve higher prediction accuracy that other metamodels in approximating agent-based simulation models.
+~\cite{fonseca2003simulation} provide general guidelines for simulation metamodeling with neural networks,~\cite{lieu2022adaptive} use DNNs as metamodels of a simulation model for a structural reliability analysis, and~\cite{salle2014efficient} show that neural network metamodels help achieve higher degree of prediction accuracy that other metamodels in approximating agent-based simulation models.
 A popular metamodel in nested simulation procedures is stochastic kriging.
-~\cite{liu2010stochastic} use stochastic kriging as a metamodel of Monte Carlo simulations to estimate the CVaR of a portfolio of derivative securities, and~\cite{gan2015valuation} use stochastic kriging for an efficient valuation of large portfolios of variable annuity (VA) contracts.
-Other studies, such as ~\cite{broadie2015risk},~\cite{hong2017kernel}, and~\cite{zhang2022sample} use regression, kernel smoothing, and the likelihood ratio method, respectively.
+~\cite{liu2010stochastic} use stochastic kriging as a metamodel of Monte Carlo simulations to estimate the CVaR of a portfolio of derivative securities, and~\cite{gan2015valuation} use a stochastic kriging for an efficient valuation of large portfolios of variable annuity (VA) contracts.
+Other studies, such as ~\cite{broadie2015risk},~\cite{hong2017kernel}, and~\cite{zhang2022sample} use a regression, a kernel smoothing, and a likelihood ratio method, respectively as metamodels.
 Our study has three key distinctions over the existing ones:
@@
 \begin{itemize}
-    \item The discussion of \textit{DNN metamodels} focus more on the aspect of \textit{estimating} the inner simulation.
-    \item Tthe discussion of \textit{DNN models} focus more on \textit{studying the DNN} using simulation data.
+    \item The discussion of \textit{DNN metamodels} focuses more on the aspect of \textit{estimating} the inner simulation.
+    \item The discussion of \textit{DNN models} focuses more on \textit{studying the DNN} using simulation data.
 \end{itemize}
 
-The rest of this chapter is organized as follows: 
+The rest of this chapter is organized as follows.
 Section~\ref{sec2:problem-formulation} presents the problem settings for tail risk measures and dynamic hedging of VAs. 
-Section~\ref{sec2:metamodel2Stage} proposes an efficient two-stage nested simulation procedure that uses DNNs as metamodels to help reduce simulation budget by only performing computations on identified tail scenarios.
+Section~\ref{sec2:metamodel2Stage} proposes an efficient two-stage nested simulation procedure that uses DNNs as metamodels to help reduce a simulation budget by only performing computations on identified tail scenarios.
 Section~\ref{sec2:metamodel1Stage} proposes a single-stage nested simulation procedure that estimates risk measures directly with metamodel predictions.
-Section~\ref{sec2:numerical} demonstrates the efficiency of DNN metamodels and examines error tolerance of two LSTM metamodels with different numbers of trainable parameters. 
-Practical suggestions are provided for the choice of suitable metamodels and simulation settings.
+Section~\ref{sec2:numerical} demonstrates the efficiency of DNN metamodels and examines the error tolerance of two LSTM metamodels with different numbers of trainable parameters. 
+Lastly, practical suggestions are provided for the choice of suitable metamodels and simulation settings.
 
@@
 In this section we present notations, problem settings, and a simulation model for risk estimation for hedging errors of VAs.
-A main goal of the section is to showcase the complexity of the simulation model, which we use as a data generator to train DNN metamodels (Section~\ref{sec2:metamodel2Stage} and Section~\ref{sec2:metamodel1Stage}).
+A main goal of this section is to showcase the complexity of the simulation model, which we use as a data generator to train DNN metamodels (Section~\ref{sec2:metamodel2Stage} and Section~\ref{sec2:metamodel1Stage}).
 For readers who are interested in the examination of a neural network metamodel, it is sufficient to understand that our simulation model generates data with 240 features and 1 real-value label and our metamodels are generally applicable to any simulation model that generates data with similar characteristics.
@@
 \subsection{Tail Risk Measures: VaR and CVaR}
-Measuring and monitoring risks, particularly tail risks, are important risk management tasks for financial institutions like banks and insurance companies.
+Measuring and monitoring risks, particularly tail risks, are important risk management tasks for financial institutions such as banks and insurance companies.
 Two most popular tail risk measures are VaR and CVaR~\citep{hardy2022quantitative, rockafellar2002conditional}.
 
-Consider a loss random variable $L$ whose losses and gains lie in the right and left tails, respectively, of its distribution.
+Consider a loss random variable $L$ which losses and gains lie in the right and left tails, respectively, of its distribution.
 For a given confidence level $\alpha\in [0,1]$, the $\alpha$-VaR and $\alpha$-CVaR are defined in Equation~\eqref{eq1:var} and Equation~\eqref{eq1:cvar}, respectively.
-Tail risk measures like VaR and CVaR are widely used for setting regulatory and economic capital, which is the amount of capital a financial institution holds to cover its risk.
+Tail risk measures such as VaR and CVaR are widely used for setting a regulatory and economic capital, which is the amount of capital a financial institution holds to cover its risk.
 For example, European insurers set regulatory capital at $99.5\%$-VaR according to Solvency II~\cite{eiopa2014underlying}.
@@
 \end{equation}
-Equation \eqref{eq2:cvar-hat} is the same as \eqref{eq1:cvar-hat} except we define a \textit{true tail scenario set} of size $k$ as $\tail_{k} = \{i: L_i > L_{(M-k)}\}$.
+Equation \eqref{eq2:cvar-hat} is the same as \eqref{eq1:cvar-hat} except that we define a \textit{true tail scenario set} of size $k$ as $\tail_{k} = \{i: L_i > L_{(M-k)}\}$.
 In this study, the loss random variable of interest is the hedging error for VA.
@@
 VA contracts offer different types of guarantees.
-Generally speaking, a portion of the VA premium is invested in a sub-account whose return is linked to some stock indices.
+Generally speaking, a portion of the VA premium is invested in a sub-account which return is linked to some stock indices.
 
@@
 Denote the policyholder's (random) time of death by $\tau>0$.
-The contract expires at $T'=\min\{T,\tau\}$, i.e., the earlier of the contract maturity and the death of the policyholder.
-Let $S_t$, $F_t$, and $G_t$ be the indexed stock price, the subaccount value and the guarantee value, respectively, at time $t=1,2,\ldots,T$.
+The contract expires at $T'=\min\{T,\tau\}$, which isthe earlier of the contract maturity and the death of the policyholder.
+Let $S_t$, $F_t$, and $G_t$ be an indexed stock price, the subaccount value and a guarantee value, respectively, at time $t=1,2,\ldots,T$.
 Evolution of the subaccount value and the guarantee value of a VA contract affect the contract payout.
@@
 For clarity, we use $F_t$ and $F_{t_+}$ to denote the sub-account value just before and just after the withdrawal at time $t$, if any.
-Let $\eta_g$ be the gross rate of management fee that is deducted from the fund value at each period and let $\eta_n < \eta_g$ be the net rate of management fee income to the insurer.
-The difference between the gross management fee and the net management fee income represents the incurred investment expenses.
+Let $\eta_g$ be a gross rate of management fee that is deducted from the fund value at each period and let $\eta_n < \eta_g$ be a net rate of management fee income to the insurer.
+The difference between the gross management fee and the net management fee income represents incurred investment expenses.
 
@@
 \end{equation*}
-At each time $t=1,\ldots,T$, the following events take place in the following order:
+At each time $t=1,\ldots,T$, the following events take place in order:
 \begin{enumerate}
-    \item The sub-account value changes according to the growth of the underlying stock and the (gross) management fee is deducted. That is, 
+    \item The sub-account value changes according to the growth of the underlying stock and the (gross) management fee is deducted, which is, 
         \begin{equation*}
@@
         \end{equation*} 
-    where $(x)^+=\max\{x,0\}$ and $F_{(t-1)_+}$ will be defined later. The insurer's income at time $t$ is the net management fee, i.e., $F_t\eta_n$.
+    where $(x)^+=\max\{x,0\}$ and $F_{(t-1)_+}$ will be defined later. The insurer's income at time $t$ is a net management fee, i.e., $F_t\eta_n$.
 
-    \item The guarantee value ratchets up (ratcheting is a common feature in GMWB) if the sub-account value exceeds the previous guarantee value, i.e., 
+    \item The guarantee value ratchets up (ratcheting is a common feature in GMWB) if the sub-account value exceeds the previous guarantee value,
         \begin{equation*}
@@
 
-    \item The withdrawal is made (for GMWB) and is deducted from the sub-account value, i.e., 
+    \item The withdrawal is made (for GMWB) and is deducted from the sub-account value,
         \begin{equation*}
@@
 
-We see from the above modeling steps that the status of a generic VA contract is summarized by a triplet $(S_t,F_t,G_t)$ whose evolution is driven by the stochasticity of $S_t$.
-In practice, the simulation model may also incorporate additional complications like mortality, lapse, and excess withdrawal, etc.
+We see from the above modeling steps that the status of a generic VA contract is summarized by a triplet $(S_t,F_t,G_t)$ which evolution is driven by the stochasticity of $S_t$.
+In practice, the simulation model may also incorporate additional complications such as mortality, lapse, and excess withdrawal, etc.
 
@@
 For example, consider the time-$t$ liability $V_t$ of a GMWB:
-Suppose that given the stock sample path, e.g., an outer path $S_1,\ldots,S_t$, one can simulate future stock prices $\Stilde_{t+1},\ldots,\Stilde_{T}$, e.g., inner sample paths, based on some asset model such as a Black-Scholes model.
+Suppose that given the stock sample path, which is an outer path $S_1,\ldots,S_t$, one can simulate future stock prices $\Stilde_{t+1},\ldots,\Stilde_{T}$, e.g., inner sample paths, based on some asset model such as a Black-Scholes model.
 The tilde symbol ($\sim$) over a quantity denotes its association with the inner simulation.
@@
     \includegraphics[width=0.85\textwidth]{./project2/figures/sns.pdf}
-    \caption{Illustration of multi-period nested simulation that estimates the P\&L for one outer scenario.}
+    \caption{Illustration of a multi-period nested simulation that estimates the P\&L for one outer scenario.}
     \label{fig2:illustration}
@@
 For simplicity, in this study we consider delta hedging for a generic VA liability using one stock and one bond.
-The metamodeling procedures in Section~\ref{sec2:metamodel2Stage} and Section~\ref{sec2:metamodel1Stage} can be trivially adapted to more general hedging strategies.
+The metamodeling procedures presented in Section~\ref{sec2:metamodel2Stage} and Section~\ref{sec2:metamodel1Stage} can be trivially adapted to more general hedging strategies.
 
-Consider a VA contract whose delta hedge portfolio at any time~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at time $T$.
+Consider a VA contract which delta hedge portfolio at any time~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at time $T$.
 The value of the hedge portfolio at time~$(t-1)$ is:
@@
 \end{equation*}
-where $S_t$ is the underlying stock price and any time $t>0$.
+where $S_t$ is an underlying stock price and any time $t>0$.
 This hedge portfolio is brought forward to the next rebalancing time~$t$, when its value becomes:
@@
 \end{equation*}
-Therefore, the time~$t$ hedging error, i.e., the cash flow incurred by the insurer due to rebalancing at time~$t$, is
+Therefore, the time~$t$ hedging error, which is the cash flow incurred by the insurer due to rebalancing at time~$t$, is
 \begin{equation}\label{eq2:hedgingerror}
@@
 \end{equation}
-The P\&L of the VA contract includes the cost of the initial hedge ($H_0$), the hedging errors~\eqref{eq2:hedgingerror}, the unwinding of the hedge at maturity ($H^{bf}_T$), and the unhedged liability ($V_0$).
+The P\&L of the VA contract includes cost of the initial hedge ($H_0$), hedging errors~\eqref{eq2:hedgingerror}, unwinding of the hedge at maturity ($H^{bf}_T$), and unhedged liability ($V_0$).
 Mathematically, the present value of these cash flows is given by
@@
 Recall from Section~\ref{subsec:VApayout} that the stock's sample path, regardless of inner or outer simulation or a combination of both, determines the evolution of the triplet $(S_t,F_t,G_t)$.
-For GMWB, a standard nested simulation procedure to estimate the $\alpha$-CVaR of $L$ is described in Algorithm~\ref{alg2:standardProcedure}.
+For GMWB, a standard nested simulation procedure to estimate the $\alpha$-CVaR of $L$ is described in Algorithm~\ref{alg2:standardProcedure} below.
 
@@
 
-We refer to the collection of experiments needed conditional on one scenario $\bS^{(i)}$ to estimate $L_i$, that is, all upward arrows in Figure~\ref{fig2:illustration}, as one inner simulation.
+We refer to the collection of experiments needed conditional on one scenario $\bS^{(i)}$ to estimate $L_i$, which is all upward arrows in Figure~\ref{fig2:illustration}, as one inner simulation.
 We make four observations:
@@
     \item   Each inner simulation is time-consuming, as it includes $T$ simulation experiments: one at each time $t=0,\ldots,T-1$,
-    \item   After running inner simulations for $M$ scenarios, we obtain simulated dataas feature-label pairs, $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$; the feature vector $\bS$ is $T$ dimensional.
+    \item   After running inner simulations for $M$ scenarios, we obtain simulated data as feature-label pairs, $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$; the feature vector $\bS$ is $T$ dimensional.
     \item   $\Lhat_i^{MC}$ is a standard Monte Carlo estimator of the true loss for scenario $\bS^{(i)}$. 
@@
     As $N$ approaches infinity, $\Lhat_i^{MC}$ converges to the true loss $L_i$, and
-    \item   Most importantly, when estimating tail risk measures such as $\alpha$-CVaR, only a small number of estimated losses, that is, those associated with the set of tail scenarios $\widehat{\tail}_{k}$ are used in the estimator.
+    \item   Most importantly, when estimating tail risk measures such as $\alpha$-CVaR, only a small number of estimated losses, which is those associated with the set of tail scenarios $\widehat{\tail}_{k}$ are used in the estimator.
 \end{itemize}
@@
 
-Based on the three observations above and inspired by~\cite{dang2020efficient}, we propose a two-stage nested simulation procedure which uses a DNN metamodel to identify potential tail scenarios.
+Based on the three observations above and built on the work by~\cite{dang2020efficient}, we propose a two-stage nested simulation procedure which uses a DNN metamodel to identify potential tail scenarios.
 We present our proposed procedure as a competitor to the standard procedure with $M$ outer scenarios and $N$ inner replications for each outer scenario, as described in Section~\ref{subsec:dynamicHedge}.
-We propose a two-stage procedure with a supervised learning metamodel that aims to produce a CVaR estimate that's as accurate as that of the standard procedure, but requires fewer computations than the latter.
+We propose a two-stage procedure with a supervised learning metamodel that aims at producing a CVaR estimate that is as accurate as that of the standard procedure, but requires fewer computations than the latter.
 
@@
 There are two different types of experiment designs for nested simulation procedures: fixed-budget design and fixed-accuracy design.
-In a fixed-budget design, the simulation budget is fixed and the goal is to achieve the highest accuracy possible within the budget.
+In a fixed-budget design, the simulation budget is fixed and the goal is to achieve the highest degree of accuracy possible within the budget.
 Let $\Gamma = MN$ be the simulation budget for the standard procedure, where each scenario receives $\frac{\Gamma}{M}$ inner replications.
-In the proposed two-stage procedure, suppose stage 2 uses $1\%$ of the simulation budget, $\alpha = 95\%$, and $m=(1-\alpha)M$, then $99\%$ of the simulation budget is concentrated on $5\% M$ predicted tail scenarios in stage 2.
+In the proposed two-stage procedure, suppose that stage 1 uses $1\%$ of the simulation budget, $\alpha = 95\%$, and $m=(1-\alpha)M$, then $99\%$ of the simulation budget is concentrated on $5\% M$ predicted tail scenarios in stage 2.
 In other words, each predicted tail scenario receives $\frac{99\% \Gamma}{5\% M}$ inner replications, almost 20 times more than that in the standard procedure.
 This budget concentration is expected to improve the estimation accuracy of the two-stage procedure compared to a standard procedure with the same budget. 
-If the metamodel is accurate in predicting true tail scenarios, the two-stage procedure is expected to achieve higher accuracy than the standard procedure with the same budget.
+If the metamodel is accurate in predicting true tail scenarios, the two-stage procedure is expected to achieve a higher degree of accuracy than the standard procedure with the same budget.
 However, we believe that the goal of designing an efficient simulation procedure is to solve practical problems faster, so a target-accuracy design is more suitable, which refers to obtaining a similar level of accuracy as the standard procedure but with much less simulation budget.
-One other reason for this fixed-accuracy design is to investigate whether DNN metamodels trained with much noisier labels can identify true tail scenarios with similar accuracy as the standard procedure.
+One other reason for recommending this fixed-accuracy design is to investigate whether DNN metamodels trained with much noisier labels can identify true tail scenarios with a similar degree of accuracy as the standard procedure.
 The size of the predicted tail scenario set in stage 1, $m$, is an important experiment design parameter that affects the correct identification of true tail scenarios and ultimately affects the estimation accuracy for CVaR.
@@
 On one hand, large $\epsilon$ is not desirable because it increases computations in stage 2.
-On the other hand, $\epsilon$ should be set reasonably large so more true tail scenarios are included in the the predicted tail scenario set $\widehat{\tail}_{m}^{PD}$ and are ultimately included in $\widehat{\tail}_{(1-\alpha )M}$ at the end of stage 2.
+On the other hand, $\epsilon$ should be set reasonably large so that more true tail scenarios are included in the predicted tail scenario set $\widehat{\tail}_{m}^{PD}$ and are ultimately included in $\widehat{\tail}_{(1-\alpha )M}$ at the end of stage 2.
 The selection of $m$ is highly dependent on the choice of the metamodel.
-Due to the simulation errors and approximation error in the metamodel in stage 1, we do not expect perfect match between the true tail scenario set $\tail_{k}$ and the predicted tail scenario set $\widehat{\tail}_{k}^{PD}$ for any size $k$.
+Due to the simulation errors and approximation error in the metamodel in stage 1, we do not expect a perfect match between the true tail scenario set $\tail_{k}$ and the predicted tail scenario set $\widehat{\tail}_{k}^{PD}$ for any size $k$.
 This means that we should not set $m$ at its lower bound: Some safety margin $\epsilon M$ should be added to the predicted tail scenario set, i.e., $m = (1-\alpha )M + \epsilon M$, to increase the likelihood that $\tail_{k} \subseteq \widehat{\tail}_{m}^{PD}$ and that the true tail scenarios are included in estimating $\alpha$-CVaR at the end of stage 2.
-The choice of safety margin $\epsilon$ is not trivial, and it should be set based on the metamodel's accuracy in identifying true tail scenarios.
+The choice of a safety margin $\epsilon$ is not trivial, and it should be set based on the metamodel's accuracy in identifying true tail scenarios.
 In the numerical experiments, we examine the relationship between the safety margin and the correct identification of true tail scenarios for different metamodels.
@@
 \begin{enumerate}
-    \item The single-stage procedure is expected to be more efficient than the two-stage procedure because it does not require the running the standard procedure in stage 2.
+    \item The single-stage procedure is expected to be more efficient than the two-stage procedure because it does not require us to run the standard procedure described in stage 2.
     \item The safety margin $\epsilon$ is not needed in the single-stage procedure.
     The safety margin is difficult to determine because it depends on the metamodel's accuracy in identifying true tail scenarios.
-    The single-stage procedure does not need a safety margin because it directly estimates the risk measure using the predicted losses.
+    The single-stage procedure does not need a safety margin because it directly estimates the risk measure by using the predicted losses.
     \item Most importantly, the single-stage procedure is not limited to just estimating tail risk measures and can be extended to provide a broader assessment of risk. 
-    It can be naturally adapted to estimate risk measures that require the knowing of the entire loss distribution, such as the standard deviation or the squared tracking error.
-    Even for CVaR, the two-stage procedure become less attactive for an increased level.
+    It can be naturally adapted to estimate risk measures that require the knowledge of the entire loss distribution, such as the standard deviation or the squared tracking error.
+    Even for CVaR, the two-stage procedure becomes less attractive at a higher level of $\alpha$.
 \end{enumerate}
@@
 \end{enumerate}
-The problem settings in our experiments are identical to those in~\cite{dang2020efficient}:
-we consider estimating the $95\%$ CVaR of the hedging loss of a GMWB contract, which is one of the most complex VA contracts in the market.
+The problem settings in our experiments are identical to those in~\cite{dang2020efficient}.
+We consider estimating the $95\%$ CVaR of the hedging loss of a GMWB contract, which is one of the most complex VA contracts in the market.
 The VA contracts have a 20-year maturity and are delta-hedged with monthly rebalancing, i.e., $T=240$ rebalancing periods.
@@
     \end{equation}
-    where ${}_{\frac{1}{12}}q^{base}_{x+\frac{t}{12}}$ is the base monthly mortality rate for a policyholder aged $x + \frac{t}{12}$ at month $t$.
-    where the base monthly lapse rate is defined as:
+    where ${}_{\frac{1}{12}}q^{base}_{x+\frac{t}{12}}$ is a base monthly mortality rate for a policyholder aged $x + \frac{t}{12}$ at month $t$, and the base monthly lapse rate is defined as:
     \begin{equation}
@@
 \begin{enumerate}
-    \item   The true losses and the true $95\%$-CVaR are estimated using a standard nested simulation procedure that runs $N=\num{100000}$ inner replications for each of the $M=\num{100000}$ outer scenarios.
-    \item   A benchmark estimator of the $95\%$-CVaR is generated using $N=\num{1000}$ for each of the $M=\num{100000}$ outer scenarios.
-    \item   The training data for our metamodels is generated using $N=\num{100}$ for $M=\num{100000}$.
+    \item   The true losses and the true $95\%$-CVaR are estimated by using a standard nested simulation procedure that runs $N=\num{100000}$ inner replications for each of the $M=\num{100000}$ outer scenarios.
+    \item   A benchmark estimator of the $95\%$-CVaR is generated by using $N=\num{1000}$ for each of the $M=\num{100000}$ outer scenarios.
+    \item   The training data for our metamodels is generated by using $N=\num{100}$ for $M=\num{100000}$.
     The value of $M$ and $N$ are subject to change in our other numerical experiments.
@@
 The architectures and training settings are typical choices in the deep learning literature.
-The training labels are normalized to have zero mean and unit standard deviation.
+The training labels are normalized to have a zero mean and a unit standard deviation.
 The numbers of trainable parameters are recorded in the second column of Table~\ref{tab:gmwb_arch}.
 We observe that the three DNN metamodels have orders of magnitudes more trainable parameters than the two traditional regression metamodels.
-In machine learning terminologies, the three DNN metamodels have much higher \textit{model capacities}.
-From a neural network of view, MLR and QPR are two neural networks with no hidden layer. 
+Following the convention in machine learning literature, the three DNN metamodels are said to have much higher \textit{model capacities}.
+Treating regression metamodels as shallow neural networks, MLR and QPR are two neural networks with no hidden layer. 
 For a traditional regression metamodel, the numbers of neurons in its input layer equals to the cardinality of its regression basis.
-Treating a regression as a shallow neural network, i.e., a neural network with only an input layer and an output layer, allows for direct comparisons with DNNs.
-The capacity of a regression metamodel is the product of the number of neurons in its input layer and its output layer.
-Since our target variable is a scalar, the output layer has only one neuron.
-The capacity of a regression metamodel therefore equals to the size of its regression basis.
-On the other hand, the three DNN metamodels have several hidden layers and are much more complex than the two regression metamodels.
-Our FNN has two hidden layers before the output layer.
-Its last hidden layer serves as an automatic feature extraction layer that transforms the 240-dimension feature vector into a 32-dimension vector that can directly relate to the target variable.
+On the other hand, the three DNN metamodels have several hidden layers and are more flexible than MLR and QPR.
+Our FNN has two hidden layers prior to its output layer.
+Its hidden layers are feature extraction layers that transform the 240-dimension feature vector into a 32-dimension vector that can directly relate to the target variable.
+This extraction process is automatic and does not require manual feature engineering.
 Our RNN and LSTM networks have three hidden layers.
 They contain similar numbers of neurons as the FNN but have deeper network structures.
-For the RNN, two of its hidden layers are recurrent layers that capture the temporal dependency in the feature, and the last hidden layer is a standard feedforward layer that transforms the previous hidden states into a 32-dimension vector for target prediction.
-Our LSTM has the same architecture as the RNN but with LSTM cells in place of the RNN cells.
+For RNN, two of its hidden layers are recurrent layers that capture the temporal dependency in the feature, and its last hidden layer is a standard feedforward layer that transforms the previous hidden states into a 32-dimension vector for target prediction.
+Our LSTM has the same architecture as the RNN but with LSTM cells in place of RNN cells.
 
@@
 
-\footnotetext{This row summarizes the results of the well-trained RNN, where the ones suffers from the vanishing gradient issue are removed from the averages.}
+\footnotetext{This row summarizes the error metrics of the well-trained RNN, where the ones suffers from a vanishing gradient issue are removed from the averages.}
 
 For each metamodel, \num{100} independent macro replications are run.
-Each macro replication involves simulating a noisy dataset, randomly separating it into training and test data, fitting a metamodel, and making predictions.
+Each macro replication involves simulating a noisy dataset, randomly separating it into training and test data, fitting a metamodel, and forming predictions.
 The last three columns in Table~\ref{tab:gmwb_arch} display the average squared errors between the metamodel predictions and the loss labels for different datasets.
@@
 In neural network literature, the number of trainable parameters is often much larger than the number of training samples.
-AlexNet~\citep{krizhevsky2012imagenet}, a well-known convolutional neural network, has $\num{60}$ million trained parameters and is trained on the ImageNet dataset with only $1.2$ million sample images.
+AlexNet~\citep{krizhevsky2012imagenet}, a well-known CNN, has $\num{60}$ million trained parameters and is trained on the ImageNet dataset with only $1.2$ million sample images.
 Other examples include generative pre-trained transformer models like BERT~\citep{devlin2018bert} and GPT-3~\citep{brown2020language}, which have billions of trainable parameters and are trained on large-scale text corpora.
-The reason for not over-fitting when the number of trainable parameters is much larger than the number of training samples is still an open question in deep learning research.
+The reason for not over-fitting when the number of trainable parameters is much larger than the number of training samples is still an open question in deep learning community.
 One of the explanations in the literature is that the optimization surface of DNNs is highly non-convex and has many local minima.
@@
 Another explanation is that most existing DNN models have specific architectures that make them less prone to over-fitting.
-For example, a convolutional neural network (CNN) is specifically designed to capture the spatial structure in image data.
-Unlike a FNN, not all neurons are connected to all neurons in the previous layer.
+For example, a CNN is specifically designed to capture a spatial structure in image data.
+Unlike the FNN, not all neurons are connected to all neurons in the previous layer.
 This architecture serves as prior knowledge and a form of regularization that make CNNs less prone to over-fitting.
 
-In our experiments, there are significant differences among the three DNN models due to having different neural network architectures.
+In our experiments, there are important differences among the three DNN models due to having different neural network architectures.
 Their model capacities are intentionally set to be similar to each other for a fair comparison.
 The FNN is a generic neural network, its test error is much greater than the training error, which is a sign of over-fitting and poor generalization.
-In contrast, RNN and LSTM networks have recurrent strucutures and are designed to capture temporal relationship in the high-dimensional feature.
-As a result, they have lower training errors, i.e., they fit the data better, and have lower test errors, i.e., they generalize better.
+In contrast, RNN and LSTM networks have recurrent structures and are designed to capture temporal relationship in the high-dimensional feature.
+As a result, they have lower training errors.
+They fit the data better and have lower test errors, i.e., they generalize better.
 Notably, the true errors for the DNN metamodels are lower than the training errors.
@@
     As a result, the half length of the $95\%$ confidence band of the RNN's training error is much larger than all other metamodels. 
-    The last row of Table~\ref{tab:gmwb_arch} shows the average squared errors of the good RNN metamodels that are successfully trained. 
+    The last row of Table~\ref{tab:gmwb_arch} shows the average squared errors of the good RNN metamodels that have been successfully trained. 
     Removing the RNN metamodels that are ill-trained, the average squared errors of the RNN metamodels are lower than those of the FNN.
-    This suggests that the RNN is more sensitive to noise in stochastic gradient descent than the FNN.
+    This suggests that the RNN is more sensitive to noise in the sense of a stochastic gradient descent than the FNN.
     They can capture the temporal dependency but are more difficult to optimize.
@@
 From a unique analytical standpoint, our numerical study offers a methodical exploration into the robustness of DNN models against noise in training labels. 
-By employing the standard nested simulation procedure in Algorithm~\ref{alg2:standardProcedure} as a data generator, we gain the ability to manipulate the noise level through adjusting the number of inner replications while keeping the same simulation procedure.
+By employing the standard nested simulation procedure in Algorithm~\ref{alg2:standardProcedure} as a data generator, we gain the ability to manipulate the noise level by adjusting the number of inner replications while keeping the same simulation procedure.
 This approach provides a controlled environment to examine the impact of label noise on neural network models.
@@
 Section~\ref{subsec2:noiseTolerance} discusses LSTM metamodels in more details regarding their sensitivity to data quality and quantity.
-We aim to provide numerical evidence and provide insights on the DNN metamodels' noise tolerance.
+We aim at providing numerical evidence and insights into the DNN metamodels' noise tolerance.
 
@@
 The resulting feature-label pairs $\{(\bS^{(i)}, \Lhat_i): i=1,\ldots,M\}$ is used for training different  metamodels.
-Specifically, following the convention in machine learning literature, we split this dataset into three parts: The training, validation, and test sets have $\num{90000}$, $\num{5000}$, and $\num{5000}$ samples ($90\%$, $5\%$, and $5\%$ of the dataset), respectively.
+Specifically, following the convention in machine learning literature, we split this dataset into three parts: The training, validation, and test sets have $\num{90000}$, $\num{5000}$, and $\num{5000}$ samples (representing $90\%$, $5\%$, and $5\%$ of the dataset), respectively.
 At the end of stage 1, $m$ predicted tail scenarios are identified by the trained metamodels.
@@
 Each quantity is averaged over $100$ macro replications.
-For a fixed safety margin, the percentage of tail matches of the traditional regression metamodels are significantly lower than the ones of the neural networks.
-We observe that a poor metamodel like the QPR identifies less than $40\%$ of the true tail scenario without any safety margin.
-In contrast, a well-suited metamodel like the LSTM identifies more than $75\%$ of the true tail scenarios without any safety margin and more than the QPR metamodel does with $15\%$ of safety margin\footnote{The metamodel in~\cite{dang2020efficient} identifies $100\%$ of the true tail scenarios on with a $10\%$ safety margin for a GMAB contract.
+For a fixed safety margin, the percentage of tail matches of the traditional regression metamodels are substantially lower than the ones of the neural networks.
+We observe that a poor metamodel such as the QPR identifies less than $40\%$ of the true tail scenario without any safety margin.
+In contrast, a well-suited metamodel such as the LSTM identifies more than $75\%$ of the true tail scenarios without any safety margin and more than the QPR metamodel does with $15\%$ of safety margin\footnote{The metamodel in~\cite{dang2020efficient} identifies $100\%$ of the true tail scenarios on with a $10\%$ safety margin for a GMAB contract.
 The GMAB contract is simpler than the GMWB contract, and the true tail scenarios are easier to identify. 
 For a GMAB, our LSTM metamodel identifies $100\%$ of the true tail scenarios with a $2.5\%$ safety margin}.
-The RNN metamodel suffers from the vanishing gradient problem during training. 
+The RNN metamodel suffers from the vanishing gradient problem during the training stage. 
 For some macro replications (as shown in Figure~\ref{subfig2:badRNN}), the RNN metamodels' predictions are far from the true losses, especially on the tails.
@@
     \end{subfigure}
-    \caption{Average $95\%$-CVaR estimates by different procedures. Right figure is a zoomed-in version of left figure.} 
+    \caption{Average $95\%$-CVaR estimates by different procedures. The right figure is a zoomed-in version of the left figure.} 
     \label{fig2:CVaR95}
@@
 Figure~\ref{subfig2:ZoomedSafetyMargin} is a zoomed version of Figure~\ref{subfig2:AllSafetyMargin}.
-Because the safety margin only affects the two-stage procedure, the true 95\%-CVaR and the one estimated by the standard procedure are horizontal (solid and dotted, respectively) lines in Figure~\ref{fig2:CVaR95}.
+Because the safety margin only affects the two-stage procedure, the true 95\%-CVaR and the one estimated by the standard procedure are horizontal lines (which are the solid and dotted lines, respectively) in Figure~\ref{fig2:CVaR95}.
 We observe that, with reasonable safety margins, the two-stage procedures with a LSTM metamodel consistently produce estimates that are as accurate as the standard procedure's estimate.
@@
 The LSTM is particularly superior to other metamodels as it accurately identifies the true tail scenarios and produces highly accurate CVaR estimates with small safety margins.
-By concentrating the simulation budget on the predicted tail scenarios, the two-stage procedure with the LSTM metamodel is able to achieve a similar accuracy as the standard procedure with a much smaller simulation budget.
+By concentrating the simulation budget on the predicted tail scenarios, the two-stage procedure with the LSTM metamodel is able to achieve a similar degree of accuracy as the standard procedure with a much smaller simulation budget.
 As the percentage of correctly identified tails approaches $100\%$, the two-stage procedure's CVaR estimates does not converge to the true CVaR but to the standard procedure's estimate.
@@
 More specfically, when the quality of the training labels is fixed at $N = \num{10}$, the CVaR estimator of single-stage procedure with a LSTM metamodel converge roughly in the order of $\mathcal{O}(M^{\frac{2}{3}})$.
-This observation resonates with the convergence rate of a regression-based nested simulation procedure in~\cite{broadie2015risk}.
+This observation resonates with the best possible convergence rate of a standard nested simulation procedure in~\cite{gordy2010nested}.
 Hence, in practice, we suggest to run the single-stage procedure with a moderate number of inner replications and a large number of outer scenarios to achieve a high level of accuracy with a reasonable computational cost.

### 2025-02-02 uw-ethesis-frontpgs.tex
1

@@
 A simulation scheme is flexible, and it can easily adapt to changes in model assumptions and market conditions.
-However, as multiple sources of risk are considered for long time horizons, such simulation schemes become expensive to implement. 
-Tremendous research effort is dedicated in the design of computationally efficient machine learning-based procedures that mitigate the computational burden of a standard simulation procedure.
+However, as multiple sources of risk are considered over long time horizons, such simulation schemes become increasingly more expensive to implement. 
+Tremendous research effort has been dedicated in the design of computationally efficient machine learning-based procedures that mitigate the computational burden of a standard simulation procedure.
 In machine learning, model flexibility comes at the expense of model resilience, which is especially crucial for risk management tasks.
 This study considers the management of tail risk for complex financial and actuarial products with resilient machine learning-based nested simulation procedures.
-We propose a novel metamodeling approach that integrates deep neural networks within the nested simulation framework for efficient risk estimation.
-Our approaches offer significant improvements over a standard simulation procedures and illustrate a resilient machine learning model is built by accounting for problem complexity and data structure, quality, and quantity.
-To further enhance adaptability to new VA contracts and changing market conditions, the thesis introduces transfer learning techniques. 
-By reusing and fine-tuning pre-trained metamodels, the approach accelerates the adaptation process to different contract features and evolving market dynamics without the need for retraining models from scratch.
-Transfer learning improves computational efficiency ando enhances the robustness and flexibility neural network metamodels in dynamic hedging of variable annuities.
+We propose a novel metamodeling approach that integrates deep neural networks within a nested simulation framework for efficient risk estimation.
+Our approaches offer substantial improvements over standard simulation procedures associated with and illustrate how a resilient machine learning model is built for problem complexity, data structure, quality, and quantity.
+To further enhance adaptability to new variable annuity contracts and changing market conditions, the thesis introduces transfer learning techniques. 
+By reusing and fine-tuning pre-trained metamodels, the proposed approach accelerates the adaptation process to different contract features and evolving market dynamics without the need for retraining models from the scratch.
+Transfer learning improves computational efficiency and enhances the robustness and flexibility of neural network metamodels in dynamic hedging of variable annuities.
 
-Extensive numerical experiments demonstrate that the proposed method achieves substantial improvements in computational efficiency, reducing simulation times by orders of magnitude compared to standard nested simulation procedures.
+Extensive numerical experiments carried out in this thesis demonstrate that the proposed method achieves substantial improvements in computational efficiency, reducing simulation times by orders of magnitude compared to standard nested simulation procedures.
 The results indicate that the deep neural network metamodels with transfer learning can quickly adapt to new market scenarios and contract specifications.
@@
 By leveraging advanced machine learning techniques, the thesis offers a practical and scalable solution for insurers to perform timely and accurate risk assessments.
-The integration of LSTM metamodels and transfer learning into the nested simulation framework represents a significant step toward more efficient, adaptable, and robust methodologies in actuarial science and quantitative finance.
+The integration of long short-term memory (LSTM) metamodels and transfer learning into a nested simulation framework represents a major step forwardtoward more efficient, adaptable, and robust methodologies in actuarial science and quantitative finance.
 

### 2025-02-04 conclusion.tex
1

@@
 
-In this thesis, we have explored the application of nested simulation procedures in the risk management of financial derivatives and insurance products, with a particular focus on variable annuity contracts featuring Guaranteed Minimum Maturity Benefits and Guaranteed Minimum Withdrawal Benefits.
+In this thesis, we have explored the application of nested simulation procedures in the risk management of financial derivatives and insurance products, with a particular focus on variable annuity contracts featuring the Guaranteed Minimum Maturity Benefits and the Guaranteed Minimum Withdrawal Benefits.
 Recognizing the computational challenges inherent in the standard nested simulation procedure, especially when estimating tail risk measures for complex financial products, we proposed an innovative approach that integrates machine learning-based metamodels into the nested simulation framework.
+
 We have shown that the nested simulation framework can be used to efficiently estimate the risk measures of complex financial products, such as variable annuities, by combining machine learning-based metamodels with nested simulations.
@@
 By employing LSTMs, we effectively approximated the contract losses associated with dynamic hedging strategies under various market scenarios. 
-This approach significantly reduced computational complexity while maintaining high levels of accuracy in risk estimation. 
+This approach substantially reduced the computational complexity while maintaining high levels of accuracy in risk estimation. 
 The LSTM metamodels captured the temporal dependencies and nonlinear relationships present in financial time series data, enabling efficient estimation of tail risk measures.
 
-Through extensive numerical experiments and sensitivity analysis, we demonstrated that our LSTM-based nested simulation procedure provides accurate and computationally efficient estimates of the tail risk associated with VA contracts.
+Through the extensive numerical experiments and sensitivity analysis, we demonstrated that our LSTM-based nested simulation procedure provides accurate and computationally efficient estimates of the tail risk associated with VA contracts.
 The results showed that the metamodels could effectively replace the computationally intensive inner simulations, reducing the overall runtime without compromising the precision of risk assessments.
-This efficiency gain is particularly valuable for insurers and financial institutions that require timely and accurate risk evaluations to meet regulatory requirements and make informed risk management decisions.
+This efficiency gain is particularly valuable for insurers and financial institutions that require timely and accurate risk evaluations to meet regulatory requirements and make informed and timely risk management decisions.
 
 Additionally, we investigated the feasibility of our approach to changing market conditions and different VA contract features. 
-By incorporating transfer learning techniques, we enabled rapid adaptation of the LSTM metamodels to new contracts and evolving market dynamics. 
+By incorporating the transfer learning techniques, we enabled rapid adaptation of the LSTM metamodels to new contracts and evolving market dynamics. 
 This aspect of our research highlights the potential for machine learning models to not only improve computational efficiency but also enhance the flexibility and responsiveness of risk management practices in the face of market volatility.

### 2025-02-04 project2/nnMetamodels.tex
1

@@
 For financial and actuarial applications, regulators and practitioners are often concerned about the robustness of DNN models to noise in training labels, which hinders the adoption of these models in practice.
-Since the true relationship is unknown in real-world applications, most deep learning literature illustrates the impact of noise by artificially injecting noise into real-world datasets, which is already noisy before the injection.
-In our numerical experiments, we are able to use Monte Carlo simulation generate a true dataset that approximates the true hedging losses with a high degree of precision, and, as a result, we are able to explore the crucial question of whether deep learning models are capable of learning the true feature-label relationship from noisy training labels.
-In this section, we treat the standard nested simulation procedure as a data generator and examine the noise tolerance of LSTM metamodels by varying the numbers of outer scenarios ($M$) and inner replications ($N$) used to generate the training samples.
+Since the true relationship is unknown in real-world applications, most deep learning literature illustrates the impact of noise by artificially injecting noise into real-world datasets, which is already noisy prior to the injection.
+In our numerical experiments, we are able to use Monte Carlo simulation to generate a true dataset that approximates the true hedging losses with a high degree of precision, and, as a result, we are able to explore the important question of whether deep learning models are indeed capable of learning the true feature-label relationship from noisy training labels.
+In this section, we treat the standard nested simulation procedure as a data generator and examine the noise tolerance of LSTM metamodels by varying the numbers of the outer scenarios ($M$) and the inner replications ($N$) used to generate the training samples.
+
 The number of outer scenarios corresponds to the number of feature-label pairs in the training dataset, and the number of inner replications controls the noise level in the training labels.
@@
 The maximum number of training samples is set to $M = \num{100000}$.
-The training samples are split into training and test sets with a $90\%$-$10\%$ ratio.
+The training samples are split into training and test sets with a $90\%$-$10\%$ split ratio.
 The true labels are generated by running the standard nested simulation procedure with $N=\num{100000}$ inner replications for each of the $\num{100000}$ outer scenarios.
@@
 Both LSTM metamodels are able to learn the true feature-label relationship from the low-noise and medium-noise datasets.
-However, when the noise level is high, both LSTM metamodels have high true error.
-The diffences in the errors between the LSTM metamodels are also reported in the last rows of Table~\ref{tab:lstm_arch}.
-A positive difference indicates that the high-capacity LSTM has higher errors than the LSTM.
+However, when the noise level is high, both LSTM metamodels have high true errors.
+
+The differences in the errors between the LSTM metamodels are also reported in the last rows of Table~\ref{tab:lstm_arch}.
+A positive difference indicates that the high-capacity LSTM has a higher error than the regular LSTM.
 We observe that both LSTM metamodels have similar errors on the low-noise and medium-noise datasets.
@@
 The test error approximates the true error and is directly observable.
-The difference in test errors of the LSTM metamodels are inconsistent with the differences in true errors.
+The differences in test errors of the LSTM metamodels are inconsistent with the differences in true errors.
 Therefore, test errors are not reliable indicators of the metamodels' noise tolerance.
-For practical applications that utilize nerual networks as metamodels, we recommend not simulating the test scenarios.
-Instead, we recommend simulating the true contract losses on a subset of training scenarios to evaluate the metamodels' generalization ability.
+For practical applications that utilize nerual networks as metamodels, we recommend not to simulate the test scenarios.
+Instead, we recommend to simulate the true contract losses on a subset of training scenarios to evaluate the metamodels' generalization ability.
 
-In summary, our numerical experiments demonstrate that both LSTM metamodels are capable of learning the true inner simulation model from noisy training labels.
-In most cases, a high-capacity metamodel is better.
+In summary, our numerical experiments demonstrate that both LSTM metamodels are capable of learning the true inner simulation model from the noisy training labels.
+In most cases, a high-capacity metamodel is shown to perform better.
 Nevertheless, in extreme circumstances when the noise level is too high, using a high capacity metamodel leads to severe over-fitting and poor generalization.
-Hence, domain knowledge about the right architecture for the task and knowledge about the noise level in the training labels are beneficial for choosing the right metamodel.
+Hence, domain knowledge about the right architecture for the task and knowledge about the noise level in the training labels are beneficial for choosing the correct metamodel.
 
@@
 
-In more details, the QQ-plots depicted in Figure~\ref{fig2:QQ_All} illustrates the fit of the two LSTM metamodels when different noise levels are present in the training labels.
+In further details, the QQ-plots depicted in Figure~\ref{fig2:QQ_All} illustrates the fit of the two LSTM metamodels when different noise levels are present in the training labels.
 They are arranged in a 2-by-3 grid, where the two rows correspond to the two LSTM metamodels with different model capacities, and the three columns correspond to the increasing noise levels.
@@
 The last rows of Table~\ref{tab2:lstm_sens} and Table~\ref{tab2:hicaplstm_sens} show the performance of the regular and high capacity LSTM metamodels trained with $M=\num{100000}$ training labels with different noise levels.
-We observe that an increasing $N$ reduces the MSE, but the reduction is not significant for a regular LSTM when $N$ is larger than $\num{10}$.
-For the high-capacity LSTM, the MSE is significantly reduced when $N$ is increased from $\num{1}$ to $\num{100}$, but the reduction is not significant when $N$ is increased from $\num{100}$ to $\num{1000}$.
+We observe that an increasing $N$ reduces the MSE, but the reduction is not substantial for a regular LSTM when $N$ is larger than $\num{10}$.
+For the high-capacity LSTM, the MSE is substantially reduced when $N$ is increased from $\num{1}$ to $\num{100}$, but the reduction is not substantial when $N$ is increased from $\num{100}$ to $\num{1000}$.
 Another way to interpret the results in Table~\ref{tab2:lstm_sens} is to compare the MSEs for the same budget of $\Gamma = M \times N$.
+
 Table entries on the same off-diagonal have the same simulation budget $\Gamma$.
@@
 Entries on the same off-diagonal all have the same $\Gamma$.
-The Pearson correlation coefficients are significantly lower for $N=\num{1}$ than the other $N$ values.
+The Pearson correlation coefficients are substantially lower for $N=\num{1}$ than the other $N$ values.
 
@@
 The heatmap is generated by subtracting the Pearson correlation coefficients from the Spearman correlation.
-We observe that Spearman correlation coefficients are not significantly different from the Pearson correlation coefficients for any $N$ larger than $\num{10}$. 
+We observe that Spearman correlation coefficients are not substantially different from the Pearson correlation coefficients for any $N$ larger than $\num{10}$. 
 This is a strong evidence that the LSTM metamodel is not only able to effectively rank the scenarios by their true losses, but also able to make accurate loss predictions.
@@
 Figure~\ref{fig2:CVaRsingleStage} shows the boxplots of the 95\%-CVaR estimates of the single-stage procedure with different metamodels and compares them to the two-stage procedure and the standard procedure.
-The two-stage procedure uses the same simulation budget as the single-stage procedure in stage 1 with extra budget for extensive inner simulation on the predicted tail scenarios in stage 2.
+The two-stage procedure uses the same simulation budget as the single-stage procedure in stage 1 with an extra amount of budget for an  extensive inner simulation on the predicted tail scenarios in stage 2.
 The metamodel with the best performance in the two-stage procedure is selected, and the safety margin is set to $0\%$.
@@
 The difference in performance among the metamodels is more pronounced in the single-stage procedure than in the two-stage procedure.
-Trained using medium noise labels, high-capacity LSTM metamodel consistently produces CVaR estimates that are closer to the true value than the regular LSTM, while the other metamodels produce even worse estimates.
-However, with high noise training labels, the high-capacity LSTM suffers from severe overfitting. 
+Trained using medium noise labels, the high-capacity LSTM metamodel consistently produces CVaR estimates that are closer to the true value than the regular LSTM, while the other metamodels produce worse estimates.
+
+However, when the noise level in the training labels is high, the high-capacity LSTM suffers from severe overfitting. 
 This is also evident in Table~\ref{tab:lstm_arch}.
@@
 
-A single-stage procedure with a regular LSTM metamodel is particularly superior to the two-stage procedure, as it is able to achieve a higher accuracy as the standard procedure with a much smaller simulation budget.
+A single-stage procedure with a regular LSTM metamodel is particularly superior to the two-stage procedure, as it is able to achieve a higher accuracy as the standard procedure with a much smaller amount of simulation budget.
 Note that the single-stage procedure does not require a safety margin.
@@
 For an LSTM metamodel, increasing the data quality of the training labels has diminishing returns, which is consistent with the results in Figure~\ref{fig2:mnConvergence}.
-For an increasing number of inner replications with fixed number of outer scenarios, the RRMSE cease to decrease after reaching $N = \num{100}$. 
-More specfically, when the quality of the training labels is fixed at $N = \num{10}$, the CVaR estimator of single-stage procedure with a LSTM metamodel converge roughly in the order of $\mathcal{O}(M^{\frac{2}{3}})$.
+For an increasing number of inner replications with a fixed number of outer scenarios, the RRMSE ceases to decrease after reaching $N = \num{100}$. 
+More specfically, when the quality of the training labels is fixed at $N = \num{10}$, the CVaR estimator of a single-stage procedure with a LSTM metamodel converge roughly in the order of $\mathcal{O}(M^{\frac{2}{3}})$.
 This observation resonates with the best possible convergence rate of a standard nested simulation procedure in~\cite{gordy2010nested}.
@@
 \section{Conclusion} \label{sec2:conclusion}
-The proposed nested simulation procedures with DNN metamodels result in substantial computational savings in estimating CVaR of the hedging loss of a VA contract from accurately predicting the hedging losses and identifying the tail scenarios.
+The proposed nested simulation procedures with DNN metamodels are shown to result in substantial computational savings in estimating CVaR of the hedging loss of a VA contract from accurately predicting the hedging losses and identifying the tail scenarios.
 When new outer scenarios are generated, a trained LSTM metamodel can distinguish between tail and non-tail scenarios and make accurate predictions without the need to run new inner simulations.
+
 Our novel experiment design allows us to examine the impact of label noise on DNN models.
 We find that a DNN with a suitable architecture is able to cut through the noise in training labels and learn the true complex dynamic hedging model.
-By showcasing the resilience of these models, our study aims to influence regulatory bodies towards recognizing the value and applicability of deep learning metamodels in financial risk management, and it provides informed suggestions and guidance for the incorporation and oversight of advanced deep learning metamodel in Monte Carlo Simulation in financial applications.
+By showcasing the resilience of these models, our study aims at encouraging regulatory bodies to recognize the value and applicability of deep learning metamodels in financial risk management, and it provides informed suggestions and guidance for the incorporation and oversight of advanced deep learning metamodel in Monte Carlo Simulation in financial applications.
 Our findings are particularly insightful in this context.
+
 In our numerical experiments, a LSTM metamodel is resilient to a high level of noise in training labels and is able to make accurate predictions. 
-This is a promising evidence that DNN metamodels can be used to improve the efficiency of Monte Carlo simulation for quantitative risk management tasks that require a computational-expensive simulation procedure.
+This is a an encouraging evidence that DNN metamodels can be used to improve the efficiency of Monte Carlo simulation for quantitative risk management tasks that require a computational-expensive simulation procedure.
 We propose two nested simulation procedures that use DNN metamodels to estimate risk measures of the hedging loss of a VA contract.
-For estimating tail risk measures, our two-stage procedure is designed to address regulatory concerns by avoiding the direct use of metamodel predictions but instead use them to identify the potential tail scenarios.
-An extensive inner simulation is performed to achieve a high level of accuracy on the predicted tail scenarios.
+For estimating tail risk measures, our two-stage procedure is designed to address regulatory concerns by avoiding the direct use of metamodel predictions but instead by using them to identify the potential tail scenarios.
+An extensive inner simulation is performed in this chapter to achieve a high level of accuracy on the predicted tail scenarios.
 However, the safety margin in the two-stage procedure is a user's choice and is not easy to determine before running extensive numerical experiments.
@@
 In the next chapter, we will extend our study to transfer learning and show that DNN metamodels trained on a existing VA contract can be transferred to a new VA contract with different market conditions.
-We hypothesize that the DNN metamodel will generalize well to the new VA contract, and the computational savings from transfer learning will be significant.
+We hypothesize that the DNN metamodel will generalize well to the new VA contract, and the computational savings from transfer learning will be substantial.

### 2025-02-04 project3/draft.tex
1

@@
 
-In the evolving landscape of financial markets, insurance products such as VAs have gained significant interest due to their ability to provide both investment growth and guaranteed benefits. 
-Managing the risks associated with these products in volatile market conditions is a complex task that demands sophisticated financial modeling techniques like nested simulation.
+In the evolving landscape of financial markets, insurance products such as VAs have gained a substantial amount of interest due to their ability to provide both investment growth and guaranteed benefits.
+Managing risks associated with these products in volatile market conditions is a complex task that demands sophisticated financial modeling techniques such as nested simulation.
 A standard nested simulation procedure involves running a large number of simulations to generate a dataset of scenario-wise contract losses with two levels of simulations.
@@
 In particular, DNNs, and specifically LSTM networks, have been employed as metamodels to predict the outcomes of the inner simulations efficiently.
-Chapter~\ref{chap:project2} introduces a metamodeling-based nested simulation framework for dynamic hedging of VAs that approximates the inner simulation by an LSTM metamodel.
-It shows that LSTMs, as a type of gated RNNs, are well-suited as metamodels for Monte Carlo simulation of financial time series and can capture the long-term dependencies in the simulation dataset.
+Chapter~\ref{chap:project2} introduced a metamodeling-based nested simulation framework for dynamic hedging of VAs that approximates the inner simulation by an LSTM metamodel.
+It shows that LSTMs, as a type of gated RNNs, were well-suited as metamodels for Monte Carlo simulation of financial time series and could capture the long-term dependencies in the simulation dataset.
 This property is crucial for the application of dynamic hedging of VAs.
@@
 Despite the advantages of using DNN metamodels, computational challenges arise when market conditions change or new VA contracts with different features are introduced. 
-Retraining neural network metamodels from scratch in response to every change is computationally inefficient and time-consuming.
+Retraining neural network metamodels from the scratch in response to every change is computationally inefficient and time-consuming.
 Practitioners with limited resources face several challenges:
@@
 In the context of DNNs, TL involves leveraging the knowledge acquired during training on one dataset to improve learning performance on a different dataset~\citep{yosinski2014transferable}.
-This approach can significantly reduce the amount of training data needed, training time and computational resources while enhancing model generalization.
-Instead of starting from scratch, a new DNN metamodel can be built on top of a pre-trained metamodel and fine-tuned on new data.
+This approach can substantially reduce the amount of training data needed, training time and computational resources while enhancing model generalization.
+Instead of starting from the scratch, a new DNN metamodel can be built on top of a pre-trained metamodel and fine-tuned on new data.
 This allows the metamodel to adapt quickly to unseen conditions and new VA contracts.
@@
 For estimating tail risk measures, a metamodel-based nested simulation procedure is proposed to approximate the inner simulation.
-We have shown DNN metamodels like RNN and LSTM networks have demonstrated significant improvements in modeling temporal dependencies, and they save a substantial amount of simulation budget.
-However, training these models from scratch requires extensive simulation data, which may not always be available for specific assets or under certain market conditions.
+We have shown DNN metamodels like RNN and LSTM networks have demonstrated substantial improvements in modeling temporal dependencies, and they save a substantial amount of simulation budget.
+However, training these models from the scratch requires an extensive amount of simulation data, which may not always be available for specific assets or under certain market conditions.
+
 TL offers a solution to this problem by leveraging knowledge from related assets or tasks to improve the learning performance of DNN metamodels on the target task.
-In algorithmic trading,~\cite{jeong2019improving} used TL to enhance the performance of a reinforcement learning agent by preventing overfitting from insufficient market data.
+In algorithmic trading,~\cite{jeong2019improving} used TL to enhance the performance of a reinforcement learning agent by preventing overfitting from an insufficient amount of market data.
 TL techniques have also been applied in building fraud detection systems. 
@@
 
-Regarding nested simulation of VAs,~\cite{cheng2019fast} is the most relevant study to our work, where they proposed a TL framework for fast valuation of large portfolios of VAs.
+Regarding a nested simulation of VAs,~\cite{cheng2019fast} is the most relevant study to our work, where they proposed a TL framework for fast valuation of large portfolios of VAs.
 Instead of using stochastic kriging~\citep{gan2015valuation}, they employed a pre-trained DNN to select the best representative scenarios from a large portfolio of VAs.
-In our work, we focus on the application of TL to accelerate the training of LSTM metamodels for nested simulation in dynamic hedging of VAs.
+In our work, we focus on the application of TL to accelerate the training of LSTM metamodels for a nested simulation in dynamic hedging of VAs.
 The fine-tuned LSTM metamodels can be readily adapted to the two-stage procedure and the single-stage procedure in Chapter~\ref{chap:project2} to predict the contract losses under different scenarios.
@@
 Similarly, two VAs with the same features but based on different underlying assets may have some shared characteristics that can be leveraged to improve the learning performance of the metamodel.
-By transferring knowledge from a pre-trained model to a new but related task, TL can significantly reduce the computational cost of training the metamodel on the target task.
+By transferring knowledge from a pre-trained model to a new but related task, TL can substantially reduce the computational cost of training the metamodel on the target task.
 
@@
 For the application of VA risk management using metamodel-based nested simulation, LSTM networks approximate the inner simulation, i.e., the mapping from scenarios to the scenario-wise contract losses.
-In Chapter~\ref{chap:project2}, we treat metamodeling as a supervised learning problem and demonstrated that LSTM networks can effectively model this complex relationships with extensive training on a large dataset of VA simulations.
+In Chapter~\ref{chap:project2}, we treat metamodeling as a supervised learning problem and demonstrated that LSTM networks could effectively model this complex relationships with extensive training on a large dataset of VA simulations.
 The total computational cost originates from two sources: running the standard nested simulation procedure to generate the training data and training the LSTM network on the generate dataset.
 Given a new VA contract, these steps need to be repeated to adapt the LSTM metamodel to new market conditions and contract features.
-For a DNN with a large number of parameters, retraining the LSTM network from scratch can be computationally expensive.
+For a DNN with a large number of parameters, retraining the LSTM network from the scratch can be computationally expensive.
 Generating a large training dataset using the standard nested simulation procedure is costly, and the computational burden can be prohibitive for certain assets or market conditions.
@@
     \item   fine-tuning requires less training time than training LSTM metamodels from scratch, and
-    \item   fewer training data points are needed to achieve a good LSTM metamodel, which is particularly beneficial when the standard nested simulation procedure is costly.
+    \item   fewer training data points are needed to achieve a good LSTM metamodel, which is particularly beneficial when the standard nested simulation procedure is costly to implement.
 \end{enumerate}
@@
 \end{itemize}
-
 where $\mathcal{X}_{\text{So}}$ and $\mathcal{X}_{\text{Ta}}$ include input features derived from the outer simulation of two different VA contracts or market conditions, and $F_{\text{So}}$ and $F_{\text{Ta}}$ are the marginal probability distributions of the source and target domains, respectively.
@@
 TL seeks to improve the learning of the target predictive function $f_{\text{Ta}}(\cdot)$ in $\mathcal{D}_{\text{Ta}}$ by leveraging the previous training on $\mathcal{D}_{\text{So}}$ and $f_{\text{So}}(\cdot)$, particularly when $\mathcal{D}_{\text{So}} \neq \mathcal{D}_{\text{Ta}}$ or $\mathcal{T}_{\text{So}} \neq \mathcal{T}_{\text{Ta}}$.
-In Chapter~\ref{chap:project2}, $\mathcal{D}_{\text{So}} = \mathcal{D}_{\text{Ta}}$ and $\mathcal{T}_{\text{So}} = \mathcal{T}_{\text{Ta}}$.
+In Chapter~\ref{chap:project2}, we have $\mathcal{D}_{\text{So}} = \mathcal{D}_{\text{Ta}}$ and $\mathcal{T}_{\text{So}} = \mathcal{T}_{\text{Ta}}$.
 
@@
 We first train the source LSTM metamodel $f_{\text{So}}(\cdot; \theta_{\text{So}})$ on $\mathcal{D}_{\text{So}}$, capturing temporal dependencies and patterns relevant to the source task. 
-For the target task, we initialize $\theta_{\text{Ta}} = \theta_{\text{So}}$ and proceed to fine-tune the entire network on $\mathcal{D}_{\text{Ta}}$ using a smaller learning rate.
+For the target task, we initialize $\theta_{\text{Ta}} = \theta_{\text{So}}$ and proceed to fine-tune the entire network on $\mathcal{D}_{\text{Ta}}$ by using a smaller learning rate.
 
@@
 
-Algorithm~\ref{alg3:fineTuning} assumes that the learned sequential representations are beneficial for the target task.
+Algorithm~\ref{alg3:fineTuning} assumes that learned sequential representations are beneficial for the target task.
 Only minor adjustments are needed to adapt the metamodel to the new task, and the training process is accelerated by the pre-trained parameters.
@@
 Shared representations are learned across tasks, which can improve learning efficiency and predictive performance on each individual task with limited data.
-In contrast to fine-tuning and layer freezing, multi-task learning aims to leverage learned knowledge from multiple tasks, and all tasks are trained simultaneously.
+In contrast to fine-tuning and layer freezing, multi-task learning aims at leveraging learned knowledge from multiple tasks, and all tasks are trained simultaneously.
 
@@
 
-For our metamodeling implementation in Chapter~\ref{chap:project2}, we consider a multi-task learning framework where the LSTM layers are shared across multiple tasks, and each task has its own fully connected layer for prediction.
+For the implementation of our metamodeling studied in Chapter~\ref{chap:project2}, we consider a multi-task learning framework where the LSTM layers are shared across multiple tasks, and each task has its own fully connected layer for prediction.
 The network parameters are divided into shared parameters $\theta_0$ (LSTM layers) and task-specific parameters $\theta_k$ (fully connected layers for task $k$). 
 As opposed to layer freezing, all parameters are trainable.
+
 The objective function for multi-task learning is the sum of the loss functions of all tasks:
@@
 Algorithm~\ref{alg3:multiTaskLearning} outlines the multi-task learning framework for LSTM metamodels for nested simulation procedures.
-In Chapter~\ref{chap:project1} and Chapter~\ref{chap:project2}, we demonstrate that pooling using a metamodel can improve the computation efficiency and estimator accuracy in nested simulation procedures.
-Here, pooling happens at a higher level, where information from multiple metamodels are shared to improve the learning performance on individual tasks.
+In Chapter~\ref{chap:project1} and Chapter~\ref{chap:project2}, we demonstrated that pooling using a metamodel could improve the computation efficiency and estimator accuracy in nested simulation procedures.
+Here, pooling happens at a higher level, where information from multiple metamodels is shared to improve the learning performance on individual tasks.
 The multi-task loss function encourages the shared LSTM layers to learn generalizable representations of temporal dependencies that are beneficial across all tasks.
@@
 
-Suppose we aim to develop an LSTM metamodel for a GMWB contract under a stochastic volatility asset model, but we have limited data for this simulation scheme. 
+Suppose that we aim at developing an LSTM metamodel for a GMWB contract under a stochastic volatility asset model, but we have limited data for this simulation scheme. 
 For multi-task learning, we can select related nested simulation simulation procedures with relatively abundant data, such as:
@@
 \begin{itemize}
-    \item \textbf{Multi-task learning} allows the shared LSTM layers to pool information across related tasks, learning generalizable representations of temporal dependencies.
-    \item \textbf{Layer freezing} ensures that shared features learned from source tasks are retained when adapting to a new task, reducing the risk of overfitting to the target simulation data.
-    \item \textbf{Fine-tuning} enables the task-specific layers to adapt quickly to the new task with minimal simulation cost, leveraging the pre-trained shared layers.
+    \item \textbf{Multi-task learning} allows the shared LSTM layers to pool information across related tasks, and it allows the metamodel to learn generalizable representations of temporal dependencies.
+    \item \textbf{Layer freezing} ensures that shared features learned from the source tasks are retained when adapting to a new task, reducing the risk of overfitting to the target simulation data.
+    \item \textbf{Fine-tuning} enables the task-specific layers to adapt quickly to the new task with a minimum amount of simulation cost, leveraging the pre-trained shared layers.
+
 \end{itemize}
 
-The combination of these techniques aims to significantly reduce the computational cost of training LSTM metamodels for a new but related VA contract.
+The combination of these techniques significantly reduces the computational cost of training LSTM metamodels for a new but related VA contract.
 
@@
 The training dataset for the target task has $M_{\text{Ta}} = \num{2000}$ samples generated with $N_{\text{Ta}} = \num{100}$ inner replications.
-During the training on both the source and target tasks, $10\%$ of the data is split into a validation dataset to monitor the training process and prevent overfitting using early stopping.
-The complexity of the simulation schemes increases from the first task to the last task, and the LSTM metamodels need to adapt to the new conditions with limited training data on the target tasks.
+During the training on both the source and target tasks, $10\%$ of the data is split into a validation dataset to monitor the training process and prevent overfitting by using early stopping.
+The complexity of the simulation schemes increases from the first task to the last task, and the LSTM metamodels need to adapt to the new conditions with a limited amount of training data on the target tasks.
 
@@
 Hyperparameters and network architectures for the LSTM metamodels are kept the same as the LSTM metamodel in Section~\ref{sec2:numerical}. 
-Due to limited computational resources, macro replications are not feasible for the TL experiments.
+Due to a limited amount of computational resources, macro replications are not feasible for the TL experiments.
 
@@
 Learning histories of the LSTM metamodels is shown for the target task of metamodeling GMMB contract losses on the RS-GBM asset model with static lapse.
-The source task is hedging a GMMB contract on RS-GBM with no lapse, and the target task is hedging the same GMMB contract but with static lapse.
+The source task is hedging a GMMB contract on RS-GBM with no lapse, and the target task is hedging the same GMMB contract but with a static lapse.
 The simulation data for the target task is generated with the same nested simulation simulation procedure as the source task, except for the lapse feature.
-Figure~\ref{subfig3-1:extensive} demonstrates the performance of the LSTM metamodel trained extensively only on the target task using $M_{\text{TA}} = 50,\!000$ samples, which serves as a benchmark for this study.
+Figure~\ref{subfig3-1:extensive} demonstrates the performance of the LSTM metamodel trained extensively only on the target task by using $M_{\text{TA}} = 50,\!000$ samples, which serves as a benchmark for this study.
 The metamodel achieves a low validation MSE due to the availability of a large dataset.
@@
 With only $M_{\text{TA}} = 2,\!000$ samples, the LSTM metamodel struggles to learn the temporal dependencies and patterns in the target task.
-It leads to highly unstable training dynamics with substantial fluctuations in the validation MSE.
+It leads to highly unstable training dynamics with a substantial amount of fluctuations in the validation MSE.
 Learning without knowledge transfer leads poor generalization and extreme overfitting. 
-Often, the training data is limited for a new VA contract, and such instability is particularly problematic for quick adaptation of LSTM metamodels.
+Often, the training data is limited for a new VA contract, and such instability is particularly problematic for a quick adaptation of LSTM metamodels.
 TL techniques like fine-tuning and layer freezing can help mitigate these challenges.
@@
 Lowering the learning rate does not help the fine-tuned metamodel converge, and the validation MSE remains high after increasing the number of training epochs.
-It indicates that fine-tuning may not be sufficient for limited training data.
+It indicates that fine-tuning may not be sufficient for a limited amount of training data.
 Figure~\ref{subfig3-1:layerFreezing} presents the performance of layer freezing on the same target task.
@@
 
-\subsection{Transfer to VAs with Dynamic Lapse}
+\subsection{Transfer to VAs with a Dynamic Lapse}
 
@@
     \end{subfigure}
-    \caption{Fine-tuned Metamodel performance on RS-GBM GMMB with dynamic lapse}
+    \caption{Fine-tuned Metamodel performance on RS-GBM GMMB with a dynamic lapse}
     \label{fig3:figure2}
@@
 
-We further investigate the performance of fine-tuning on the target task of metamodeling GMMB contract losses on RS-GBM with dynamic lapse. 
-The source tasks used for pretraining are GMMB contracts on RS-GBM with no lapse and static lapse, respectively. 
+We further investigate the performance of fine-tuning on the target task of metamodeling GMMB contract losses on RS-GBM with a dynamic lapse. 
+The source tasks used for pretraining are GMMB contracts on RS-GBM with no lapse and a static lapse, respectively. 
 Figure~\ref{fig3:figure2} displays the learning curves of the LSTM metamodels fine-tuned from these two distinct source tasks.
 We observe that the performance of the fine-tuned metamodel is highly dependent on the similarity between the source and target tasks.
-Fine-tuning from a source task with static lapse results in faster convergence and lower validation error.
-The metamodel trained on the GMMB with static lapse captures some features that are beneficial for the GMMB with dynamic lapse, which leads to a more stable training process.
+Fine-tuning from a source task with a static lapse results in a faster convergence and a lower validation error.
+The metamodel trained on the GMMB with a static lapse captures some features that are beneficial for the GMMB with a dynamic lapse, which leads to a more stable training process.
 In Figure~\ref{subfig3-2:fromNolapse}, the metamodel needs to learn the effect of
+
 \begin{itemize}
@@
 The observed improvement in transferability when fine-tuning from a static lapse source task highlights the importance of selecting appropriate source tasks in TL. 
-When the source task diverges significantly from the target task, the transferred metamodel may struggle to adapt to the new conditions given the limited amount of of training data.
+When the source task diverges substantially from the target task, the transferred metamodel may struggle to adapt to the new conditions given the limited amount of training data.
 
@@
 
-Figure~\ref{fig3:figure3} continues the investigation of layer freezing in the task of metamodeling GMMB contract losses on RS-GBM with dynamic lapse. 
-When transferring knowledge from the GMMB model with static lapse, the primary adaptation for the target task involves learning the impact of dynamic lapse.
+Figure~\ref{fig3:figure3} continues the investigation of layer freezing in the task of metamodeling GMMB contract losses on RS-GBM with the dynamic lapse. 
+When transferring knowledge from the GMMB model with the static lapse, the primary adaptation for the target task involves learning the impact of the dynamic lapse.
 Freezing the LSTM layers and fine-tuning only the fully connected layer results in a higher validation error, which suggests a tendency of overfitting.
-This indicates that the fully connected layer struggles to adapt to the changes in the temporal dynamics introduced by dynamic lapse, which can be viewed as another source of randomness in the time series.
+This indicates that the fully connected layer struggles to adapt to the changes in the temporal dynamics introduced by a dynamic lapse, which can be viewed as another source of randomness in the time series.
 In contrast, freezing the fully connected layer and fine-tuning the LSTM layers leads to a lower validation error and better generalization. 
-This can be attributed to the fact that the LSTM layers are responsible for capturing the temporal dependencies associated with dynamic lapse, and the fully connected layer predicts the contract losses based on these learned features.
+This can be attributed to the fact that the LSTM layers are responsible for capturing the temporal dependencies associated with the dynamic lapse, and the fully connected layer predicts the contract losses based on these learned features.
 
 This experiment emphasizes the importance of choosing which layers to freeze based on the nature of the source and target tasks. 
-In the case of learning dynamic lapse features, freezing the LSTM layers is not beneficial as they need to adapt to the new temporal patterns.
+In the case of learning the dynamic lapse features, freezing the LSTM layers is not beneficial as they need to adapt to the new temporal patterns.
 
@@
 The calculations are based on the metamodel predictions and the true contract losses approximated with $\num{100000}$ inner replications.
-The first two rows show the performance of transferring knowledge from GMMB contracts with no lapse and static lapse to the target task of GMMB with dynamic lapse.
+The first two rows show the performance of transferring knowledge from GMMB contracts with no lapse and the static lapse to the target task of GMMB with the dynamic lapse.
 The last row shows the performance of training without TL on the target task.
 The results demonstrate the effectiveness of fine-tuning and layer freezing in transferring knowledge from a related source tasks to the target task. 
-When transferring from a source task with static lapse to a target task with dynamic lapse, the MSEs achieved are $0.0794$ for fine-tuning and $0.0763$ for layer freezing.
+When transferring from a source task with the static lapse to a target task with the dynamic lapse, the MSEs achieved are $0.0794$ for fine-tuning and $0.0763$ for layer freezing.
 The benchmark MSE of $0.0587$, obtained from extensive training on the GMMB dynamic lapse task with much more samples.
-While TL from static lapse GMMB do not reach this level of accuracy due to the limited data in the target task, they significantly outperform training without TL. 
+
+While TL from static lapse GMMB do not reach this level of accuracy due to the limited data in the target task, they substantially outperform training without TL. 
 This indicates that the models pre-trained on a static lapse setting are effective in capturing relevant features that are transferable to the dynamic lapse scenario.
@@
 When transferring knowledge from one VA contract type to another, the LSTM metamodel needs to adapt to different contract features and time series dynamics.
-We consider the task of metamodeling GMWB contract losses on RS-GBM asset model with dynamic lapse, with the source tasks being a GMMB contract on RS-GBM also with dynamic lapse.
+We consider the task of metamodeling GMWB contract losses on RS-GBM asset model with the dynamic lapse, with the source tasks being a GMMB contract on RS-GBM also with the dynamic lapse.
 Figure~\ref{fig3:figure4} illustrates the learning history of transferring pre-trained LSTM metamodels from the GMMB contracts to the GMWB contracts.
@@
 Fewer training samples and no prior knowledge leads to unstable training dynamics. 
-The validation MSE fluctuates significantly.
+The validation MSE fluctuates substantially.
 
-When applying fine-tuning from the GMMB source task (Figure~\ref{subfig3-4:fineTuning}), the metamodel exhibits improved performance compared to training without TL. 
+When applying fine-tuning from the GMMB source task (Figure~\ref{subfig3-4:fineTuning}), the metamodel exhibits an improved performance compared to the training without TL. 
 Fine-tuning results in a lower validation error and more stable convergence.
-Despite the differences between GMMB and GMWB contracts, there is still valuable information that can be transferred. 
+Despite the differences between the GMMB and GMWB contracts, there is still valuable information that can be transferred. 
 Both the LSTM layers and the fully connected layers capture general temporal patterns and feature representations that are beneficial for the target task. 
 Fine-tuning allows the metamodel to adjust all its neural network layers. 
-It allows better adaptation to the complexities introduced by the GMWB contract.
+It allows a better adaptation to the complexities introduced by the GMWB contract.
 
@@
 Freezing some layers trained on the GMMB contracts does not allow the metamodel to sufficiently adapt to the complexities of the GMWB contracts. 
-The GMWB contracts are inherently more complex than GMMB contracts due to the guaranteed withdrawal benefits at each time step, and the contract features are significantly different.
-The complexity introduce significant changes in the time series dynamics that the metamodel needs to capture.
-Freezing the LSTM layers or the fully connected layer hinders the metamodel's ability to learn these new patterns, and it leads to poor generalization and unstable error curves.
+The GMWB contracts are inherently more complex than GMMB contracts due to the guaranteed withdrawal benefits at each time step, and the contract features are substantially different.
+The complexity introduced by the GMWB contracts leads to significant changes in the time series dynamics that the metamodel needs to capture.
+Freezing the LSTM layers or the fully connected layer hinders the metamodel's ability to learn these new patterns, and it leads to a poor generalization and unstable error curves.
 
@@
 This is consistent with the terminology used in Chapter~\ref{chap:project2}.
-The TL methods are compared to training from scratch.
+The TL methods are compared to training from the scratch.
 The suboptimal performance of layer freezing in this context indicates that the difference between the source and target tasks is too substantial for this method to be effective. 
-While layer freezing can be advantageous when the source and target tasks are closely related, it may hinder performance when the tasks diverge significantly.
+While layer freezing can be advantageous when the source and target tasks are closely related, it may hinder performance when the tasks diverge substantially.
 In such circumstances, fine-tuning provides a better approach by allowing the metamodel to leverage transferable knowledge while adapting to the new task's specific requirements. 
-Fine-tuning enables both the LSTM and fully connected layers to update their weights, capturing the complex dynamics of the GMWB contracts more effectively.
-This is particularly beneficial when developing metamodels for complex VA contracts with limited simulation data. 
-For instance, transferring information from GMMB contracts can still be valuable when modeling GMWB contracts.
+Fine-tuning enables both the LSTM and the fully connected layers to update their weights, capturing the complex dynamics of the GMWB contracts more effectively.
+This is particularly beneficial when developing metamodels for the complex VA contracts with limited simulation data. 
+For instance, transferring information from the GMMB contracts can still be valuable when modeling the GMWB contracts.
 Both contracts share some common contract features and temporal patterns, which allows a pre-trained LSTM metamodel to capture generalizable features that provide a solid foundation for the target task.
@@
 
-Figure~\ref{fig3:figure4-1} illustrates the performance of the two-stage procedure with TL for GMWB contracts with dynamic lapse in predicting the tail scenarios and the $95\%$-CVaR.
-The graph provides a visual representation of how different TL approaches compare to training from scratch and the standard nested simulation procedure.
-Fine-tuning consistently outperforms both layer freezing and training from scratch across different simulation budgets, particularly in predicting tail scenarios and estimating the 95\%-CVaR. 
+Figure~\ref{fig3:figure4-1} illustrates the performance of the two-stage procedure with TL for GMWB contracts with the dynamic lapse in predicting the tail scenarios and the $95\%$-CVaR.
+The graph provides a visual representation of how different TL approaches compare to training from the scratch and the standard nested simulation procedure.
+Fine-tuning consistently outperforms both layer freezing and training from the scratch across different simulation budgets, particularly in predicting tail scenarios and estimating the 95\%-CVaR.
+
 This finding is consistent with the training history and MSEs in Figure~\ref{fig3:figure4} and Table~\ref{tab3:transfer_learning_results_gmwb}, respectively.
-It's important to note that while these results are promising, they also highlight the complexity of modeling GMWB contracts with dynamic lapse. 
-The fact that fine-tuning outperforms layer freezing suggests that there are significant differences in the tail behavior of GMMB and GMWB contracts, particularly when dynamic lapse is considered. 
-These findings highlight the need for careful model selection and validation when applying TL techniques to different VA products.
+It is important to note that while these results are promising, they also highlight the complexity of modeling the GMWB contracts with the dynamic lapse. 
+The fact that fine-tuning outperforms layer freezing suggests that there are substantial differences in the tail behavior of the GMMB and GMWB contracts, particularly when the dynamic lapse is considered.
+These findings highlight the need for careful model selection and validation when applying the TL techniques to different VA products.
 When the source and target tasks are substantially different, all layers need to be updated.
@@
 Multi-task learning enables the LSTM metamodels to learn shared representations across related VA contracts.
-In this section, we examine the performance of multitask learning applied to two types of VAs, GMMB and GMWB with dynamic lapse rates.
-The simulation datasets contrain $2,\!000$ samples for each contract type, and the LSTM metamodels are trained using multi-task learning. 
+In this section, we examine the performance of multitask learning applied to two types of VAs, GMMB and GMWB with the dynamic lapse rates.
+The simulation datasets contain $2,\!000$ samples for each contract type, and the LSTM metamodels are trained using multi-task learning. 
 In our experiments, Algorithm~\ref{alg3:multiTaskLearning} is used to train the LSTM metamodels simultaneously to minimize the multi-task MSE loss function in Equation~\ref{eq3:multiTaskLoss}.
@@
 
-Figure~\ref{fig3:mtl} illustrates our multi-task learning framework for GMMB and GMWB contracts with dynamic lapse rates.
+Figure~\ref{fig3:mtl} illustrates our multi-task learning framework for GMMB and GMWB contracts with the dynamic lapse rates.
 The outer simulation paths for both contracts are the same, which are generated from the same nested simulation procedure with $100$ inner replications.
 The LSTM metamodels are trained simultaneously on both contracts.
-The LSTM layers are shared, and each contract has its own separate fully connected layers for contract loss predictions.
+The LSTM layers are shared to train for capturing general temporal patterns, and each contract has its own fully connected layers that are trained for contract loss predictions.
 
@@
 
-Figure~\ref{fig3:figure5} compares the learning curves for the training of GMMB and GMWB, with and without multitask learning.
-The comparison between multitask learning (Figure~\ref{subfig3-5:multiTask} and~\ref{subfig3-5:fineTuning}) and individual task training ((Figure~\ref{subfig3-5:gmmb_individual} and~\ref{subfig3-5:gmwb_individual})) demonstrates the benefit of multi-task learning for both products.
-In the case of GMMB, multitask learning allows the model to achieve faster convergence while reducing overfitting.
-For GMWB, the multi-task learning framework helps to stablize the training process.
-The shared LSTM layers in the multitask model are able to capture common temporal patterns and dynamics, which benefits both GMMB and GMWB when training samples is scarce.
-Similar to pooling in Chapter~\ref{chap:project1} and~\ref{chap:project2} but on a higher level, multi-task learning enables the LSTM metamodels to leverage shared representations across related VA contracts.
+Figure~\ref{fig3:figure5} compares the learning curves for the training of the GMMB and the GMWB, with and without the multitask learning.
+The comparison between the multitask learning (Figures~\ref{subfig3-5:multiTask} and~\ref{subfig3-5:fineTuning}) and the individual task training ((Figures~\ref{subfig3-5:gmmb_individual} and~\ref{subfig3-5:gmwb_individual})) demonstrates the benefit of the multi-task learning for both products.
 
-\subsection{}
+In the case of the GMMB, the multi-task learning allows the model to achieve faster convergence while reducing overfitting.
+For the GMWB, the multi-task learning framework helps to stablize the training process.
+The shared LSTM layers in the multitask model are able to capture common temporal patterns and dynamics, which benefits both the GMMB and the GMWB when the training samples are scarce.
+
+Similar to the pooling in Chapters~\ref{chap:project1} and~\ref{chap:project2} but on a higher level, multi-task learning enables the LSTM metamodels to leverage shared representations across related VA contracts.
 
@@
 
-In this chapter, we introduced a transfer learning framework to accelerate the training of LSTM metamodels for dynamic hedging of variable annuity contracts.
+In this chapter, we have introduced a transfer learning framework to accelerate the training of LSTM metamodels for dynamic hedging of variable annuity contracts.
 Traditional nested simulation procedures for VA risk management are computationally intensive.
-LSTM metamodels offer a data-driven approach to approximate the true contract losses, which can significantly reduce the computational cost of hedging a single VA contract.
+LSTM metamodels offer a data-driven approach to approximate the true contract losses, which can substantially reduce the computational cost of hedging a single VA contract.
 However, training LSTM metamodels on new VA contracts can be challenging due to the limited availability of simulation data.
-Our proposed framework leverages pre-trained LSTM networks and transfer learning techniques to adapt quickly metamodels to new but related VA contracts with minimal additional simulation cost.
-Fine-tuning a pre-trained LSTM metamodel on a new target task with limited data significantly improved training stability and predictive accuracy compared to training from scratch. 
+Our proposed framework leverages pre-trained LSTM networks and transfer learning techniques to adapt metamodels quickly to new but related VA contracts with a minimum amount of additional simulation cost.
+Fine-tuning a pre-trained LSTM metamodel on a new target task with a limited amount of data substantially improved training stability and predictive accuracy compared to training from the scratch.
+
 Layer freezing further enhanced performance by retaining transferable temporal representations learned from the source task. 
@@
 When the tasks were closely related, freezing some neural network layers yields substantial benefits. 
-Conversely, when the source and target tasks diverged significantly, fine-tuning the entire network is more effective.
+Conversely, when the source and target tasks diverged substantially, fine-tuning the entire network is more effective.
 
-Multi-task learning offers a robust framework for transferring knowledge across related simulation schemes in LSTM metamodeling for nested simulations. 
+Multi-task learning offers a robust framework for transferring knowledge across related simulation schemes in the LSTM metamodeling for nested simulations. 
 By sharing representations through the LSTM layers, the model can learn more generalizable features that are beneficial across different VA contracts. 
@@
 
-The integration of transfer learning in LSTM metamodeling represents a significant advancement in robust risk management associated with variable annuity contracts.
+The integration of transfer learning in LSTM metamodeling represents an important advancement in robust risk management associated with variable annuity contracts.
 By effectively leveraging existing knowledge, financial institutions can maintain accurate and responsive risk management practices in a rapidly changing market environment. 
-The methodologies presented in this chapter attempt to make a significant contribution to the broader applications of transfer learning in financial modeling and risk assessment.
+The methodologies presented in this chapter attempt to make a contribution to the broader applications of transfer learning in financial modeling and risk assessment.

### 2025-02-04 futureWork/rlHedging.tex
new
w

@@
 
-In the evolving landscape of financial markets, insurance products such as VAs have gained significant interest due to their ability to provide both investment growth and guaranteed benefits. 
+In the evolving landscape of financial markets, insurance products such as VAs have gained a substantial amount of interest due to their ability to provide both investment growth and guaranteed benefits.
 Managing the risks associated with these products, especially in volatile market conditions, is a complex task that demands sophisticated financial modeling techniques. 
@@
 In a dynamic hedging problem, the agent is referred to as the decision-maker that tries to minimize financial risks over time horizon by adjusting the hedging portfolio based on the current environment, which is the current state of the financial markets and actuarial assumptions.
-By intergrating deep neural network, DRL extends this framework by enabling the agent to handle high-dimensional and complex environments. 
+By integrating deep neural network, DRL extends this framework by enabling the agent to handle high-dimensional and complex environments. 
 DRL has shown particular promise in finance because of its ability to process vast amounts of financial data and discover intricate patterns in market dynamics.
@@
 Its most significant drawback is the requirement for extensive data and computational resources.
-Training a DRL agent from scratch requires a large dataset along with considerable computational time for exploration and learning.
-This is especially problematic for variable annuities, which are long-term insurance products that are sensitive to market fluctuations and underlying actuarial assumptions.
-Given that financial markets are highly dynamic, frequent retraining to account for new market regimes becomes necessary, which can lead to prohibitively high costs and computational inefficiency.
+Training a DRL agent from the scratch requires a large dataset along with considerable computational time for the purpose of exploration and learning.
+This is especially problematic for VA contracts, which are long-term insurance products that are sensitive to market fluctuations and underlying actuarial assumptions.
+Given that financial markets are highly dynamic, a frequent retraining to account for new market regimes becomes necessary, which can lead to prohibitively high costs and computational inefficiency.
 Moreover, using historical data leads to overfitting to the past. 
@@
 
-Transfer learning (TL) offers a compelling solution to the challenges posed by existing DRL approaches. 
+TL offers a compelling solution to the challenges posed by existing DRL approaches. 
 Similar to the TL framework proposed in Chapter~\ref{chap:project3}, TL can also be applied to DRL to accelerate the training.
-In the context of financial modeling, instead of training an RL agent from scratch every time underlying assumptions change, the model can utilize the knowledge gained from past market environments to accelerate the learning process under the new environment.
+In the context of financial modeling, instead of training an RL agent from the scratch every time underlying assumptions change, the model can utilize the knowledge gained from past market environments to accelerate the learning process under the new environment.
 TL in financial markets is particularly advantageous for addressing the data scarcity problem. 
@@
 Additionally, TL enhances the robustness of models by allowing continuous learning. 
-Instead of retraining a deep RL model from scratch when market conditions shift, TL enables the reuse of pre-trained models, facilitating faster adaptation to new environments while avoiding overfitting to past conditions.
-In the risk management of variable annuities, transfer learning enables quicker adaptation to changing financial and actuarial assumptions by reusing information obtained from another set of related assumptions, such as the management of similar financial instruments or different market regimes.
+Instead of retraining a deep RL model from the scratch when market conditions shift, TL enables the reuse of pre-trained models, facilitating a faster adaptation to new environments while avoiding overfitting to past conditions.
+In the risk management of VA contracts, transfer learning enables quicker adaptation to changing financial and actuarial assumptions by reusing information obtained from another set of related assumptions, such as the management of similar financial instruments or different market regimes.
 A DRL agent equipped with transfer learning can adjust its strategies in response to new market data, making the model more adaptive and responsive without the need for costly retraining.
-More specifically, a DRL agent trained to manage variable annuities for a GMMB contract can apply its learned strategies to a GMWB contract with the same financial assumptions. 
+More specifically, a DRL agent trained to manage VA contracts for a GMMB contract can apply its learned strategies to a GMWB contract with the same financial assumptions. 
 A DRL agent trained for a VA product on a Black-Scholes asset model can transfer its knowledge to the training of a similar product on a stochastic volatility model.
-This approach significantly reduces the computational costs associated with the training of new VA products with different assumptions and improves the generalization of the model to unseen market conditions.
-By integrating transfer learning with existing DRL frameworks, we can eliminate the inefficiencies of training models from scratch, provide faster adaptability to new market conditions, and enhance the scalability and computational efficiency of financial models.
-This approach offers a more robust and practical solution for managing variable annuities in dynamic and volatile financial markets.
+This approach substantially reduces the computational costs associated with the training of new VA products with different assumptions and improves the generalization of the model to unseen market conditions.
+By integrating the transfer learning with the existing DRL frameworks, we can eliminate the inefficiencies of training models from scratch, provide faster adaptability to new market conditions, and enhance the scalability and computational efficiency of financial models.
+This approach offers a more robust and practical solution for managing VA contracts in dynamic and volatile financial markets.
 
 The rest of the chapter is organized as follows: 
-% Section~\ref{sec:MDP} introduces the mathematical formulation for hedging VAs and defines the key components of the framework.
-% Section~\ref{sec:RLAlgorithms} provides an overview of existing RL algorithms and their limitations in the context of hedging VAs.
-% Section~\ref{sec:PPO} introduces the proximal policy optimization algorithm and its application to the hedging of VAs.
-% Section~\ref{sec:TL} presents the transfer learning framework for accelerating the training of DRL agents in the dynamic hedging of VAs.
-% Section~\ref{sec:experiments} presents the experimental setup and results, comparing the performance of transfer learning with training from scratch.
-% Finally, Section~\ref{sec:FutureDirections} concludes the chapter and discusses future research directions.
+Section~\ref{sec:MDP} introduces the mathematical formulation for hedging VAs and defines the key components of the framework.
+Section~\ref{sec:RLAlgorithms} provides an overview of existing RL algorithms and their limitations in the context of hedging VAs.
+Section~\ref{sec:PPO} introduces the proximal policy optimization algorithm and its application to the hedging of VAs.
+Section~\ref{sec:TL} presents the transfer learning framework for accelerating the training of DRL agents in the dynamic hedging of VAs.
+Section~\ref{sec:experiments} presents the experimental setup and results, comparing the performance of transfer learning with training from scratch.
+Finally, Section~\ref{sec:FutureDirections} concludes the chapter and discusses future research directions.
 
@@
 By formulating the VA hedging problem as an MDP, we can utilize RLalgorithms to learn optimal hedging policies directly from data.
-AnMDP is defined by the tuple $\mathcal{M} = (\mathcal{S}, \mathcal{A}, \mathcal{P}, \mathcal{R}, \gamma)$, where:
+An MDP is defined by the tuple $\mathcal{M} = (\mathcal{S}, \mathcal{A}, \mathcal{P}, \mathcal{R}, \gamma)$, where:
 
@@
 where $R_t$ is the term reward received by the agent at time $t$, and the discount factor $\gamma$ is conveniently inherited from the risk-free rate $r$. 
-In hedging, the term reward $R_t$ should be drived from Equation~\ref{eq3:lossGMMB} and Equation~\ref{eq3:lossGMWB} to represent the performance of the hedging policy, i.e., how closely the hedging portfolio tracks the liability.
-For GMWB, we propose a term reward formulation that encourages the agent to maximize the expected reward with low hedging errors and transaction costs:
+In hedging, the term reward $R_t$ should be derived from Equation~\ref{eq3:lossGMMB} and Equation~\ref{eq3:lossGMWB} to represent the performance of the hedging policy, i.e., how closely the hedging portfolio tracks the liability.
+For the GMWB, we propose a term reward formulation that encourages the agent to maximize the expected reward with low hedging errors and transaction costs:
 \begin{equation} \label{eq3:rewardGMWB}
@@
 \end{equation}
-The reward function of GMWB directly links to the time-$t$ loss of a GMWB contract as in Equation~\ref{eq3:lossGMWB}.
+The reward function of the GMWB directly links to the time-$t$ loss of a GMWB contract as in Equation~\ref{eq3:lossGMWB}.
 The GMMB loss consists of an additional payoff at maturity $T$, thus its term reward is formulated as:
@@
 \end{equation}
-where $f_{\theta}$ is the neural network with parameters $\theta$, $s$ is the current state of the game, $\pi$ is the policy, $v$ is the value of the current state, and $c$ is a regularization parameter.
-$\mathbf{p}$ and $z$ are the probability distribution of the next move and the outcome of the game, respectively.
+where $f_{\theta}$ is a neural network with parameters $\theta$, $s$ is a current state of the game, $\pi$ is a policy, $v$ is a value of the current state, and $c$ is a regularization parameter.
+$\mathbf{p}$ and $z$ are a probability distribution of the next move and an outcome of the game, respectively.
 They are induced by a planning algorithm, i.e., Monte Carlo Tree Search (MCTS).
@@
 
-\begin{algorithm}[H] \label{alg:REINFORCE}
+\begin{algorithm}[H] 
     \caption{Vanilla Policy Gradient (REINFORCE)}
-    \begin{algorithmic}[1]
+    \begin{algorithmic}[1] \label{alg:REINFORCE}
     \STATE \textbf{Initialize} policy parameters $\theta$ arbitrarily.
@@
 \section{Hedging VAs with a PPO Agent} \label{sec:PPO}
-In a hedging problem, an insurer aims to find a policy $\pi$ that maximize the expected reward over time.
+In a hedging problem, an insurer aims at finding a policy $\pi$ that maximizes the expected reward over time.
 In a policy-based RL approach like the PPO, both the policy and the value function are parameterized by deep neural networks.
@@
 \end{align}
-
-where $\theta_{old}$ denotes the policy parameters at the previous iteration, $\epsilon$ is a clip range hyperparameter that controls the size of the policy update, $\text{clip}(x, a, b)$ is a function that clips the value of $x$ to be within the range $[a, b]$, and $\hat{A}^{\pi_{\theta}}(s_t, a_t)$ is the estimated advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi_{\theta_{old}}$.
+where $\theta_{old}$ denotes the policy parameters at the previous iteration, $\epsilon$ is a clip range hyperparameter that controls the size of the policy update, $\text{clip}(x, a, b)$ is a function that clips the value of $x$ to be within the range $[a, b]$, and $\hat{A}^{\pi_{\theta}}(s_t, a_t)$ is an estimated advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi_{\theta_{old}}$.
 In our implementation, the advantage function is estimated following the GAE method proposed by~\cite{schulman2015high}.
@@
 The recurrent PPO algorithm is similar to the standard PPO algorithm, but it includes an LSTM component to capture the temporal dependencies in the data.
-However, the sequantial nature of the LSTM is not suitable for parallel computation, which slows down the training process.
+However, the sequantial nature of the LSTM is not suitable for a parallel computation, which slows down the training process.
 
@@
 In the context of hedging VAs using deep reinforcement learning and transfer learning, reward shaping becomes a crucial technique. 
-It involves modifying the reward function in the target domain to incorporate additional guidance, which often leads to more efficient learning and better performance.
+It involves modifying the reward function in the target domain to incorporate additional guidance, which often leads to more efficient learning and a better performance.
 This technique can be particularly useful for managing the complex risks associated with VAs, as it can guide the learning process towards strategies that are more effective in hedging these products.
@@
 
-Some popular reward shaping techniques include potential-based reward shaping~\citep{ng1999policy}, potential based state-action advice~\citep{wiewiora2003principled}, dynamic value function advice~\citep{harutyunyan2015expressing}.
+Some popular reward shaping techniques include potential-based reward shaping~\citep{ng1999policy}, potential-based state-action advice~\citep{wiewiora2003principled}, dynamic value function advice~\citep{harutyunyan2015expressing}.
 
@@
 This experiment compares the hedging performance of the recurrent PPO agent with LSTM and the deep hedging algorithm proposed by~\cite{buehler2019deep} for hedging VAs with a GMMB rider.
-The experiment is conducted with the same simulation budget.
+The experiment is conducted with the same amount ofsimulation budget.
 
@@
 
-The proposed future work of this thesis aims to investigate how transfer learning can be effectively integrated into the training of PPO agents for dynamic hedging of VA contracts. 
+The proposed future work of this thesis aims at investigating how transfer learning can be effectively integrated into the training of PPO agents for dynamic hedging of VA contracts. 
 The primary goal is to enhance the adaptability and efficiency of hedging strategies in response to new VA products and changing market conditions.
@@
 Policy distillation has been effective in compressing and transferring knowledge between networks, improving learning efficiency in RL settings.
-Another avenue is the use of pre-trained model initialization, wherein the policy network trained on the source task initializes the policy for the target task. 
-This method leverages the shared underlying structures between tasks, potentially accelerating convergence and improving performance 
-The framework will also consider feature representation transfer, aiming to reuse learned representations of market dynamics and policyholder behaviors between tasks. 
+Another avenue for future research is the use of pre-trained model initialization, wherein the policy network trained on the source task initializes the policy for the target task. 
+This method leverages the shared underlying structures between tasks, which can potentially accelerate convergence and improve performance.
+The framework will also consider feature representation transfer, which aims at reusing learned representations of market dynamics and policyholder behaviors between tasks. 
 By capturing common patterns across different contracts and market models, the PPO agent can more effectively generalize to new scenarios~\citep{bengio2012deep}.
 
-By addressing these objectives, the research aims to advance the field of financial risk management through the development of adaptive and efficient hedging strategies for variable annuities.
-The integration of transfer learning into PPO agents has the potential to significantly reduce computational costs and improve the robustness of hedging policies in dynamic market environments.
+By addressing these objectives, the research aims at advancing the field of financial risk management through the development of adaptive and efficient hedging strategies for VA contracts.
+The integration of transfer learning into PPO agents has the potential to substantially reduce computational costs and improve the robustness of hedging policies in dynamic market environments.

### 2025-02-20 introduction.tex
new

@@
 Quantitative risk management is a key component of modern financial systems.
-Successful risk management practice can ensure the stability and resilience against a variety of risks.
+Successful risk management practice can ensure stability and resilience against a variety of risks.
 For financial products such as option portfolios and variable annuity (VA) contracts, traditional risk assessment methods often fall short in accurately capturing the complex dynamics of the underlying risk factors.
 VA contracts are a popular type of complex insurance product that is linked to the performance of underlying assets.
-It provides a guaranteed minimum income benefit to the policyholder regardless of the performance of the underlying assets.
+They provide a guaranteed minimum income benefit to the policyholder regardless of the performance of the underlying assets.
 Advanced Monte Carlo simulation techniques, particularly nested simulation procedures, become indispensable for risk assessment of such products.
@@
 In this thesis, we focus on metamodels of the inner simulation models in nested simulation procedures for risk management applications of financial derivatives and VA contracts.
-Two interesting problems that requires nested simulation are considered in this thesis:  
+Two interesting problems that require nested simulation are considered in this thesis:  
 \begin{itemize}
@@
 Chapter~\ref{chap:project2} also conducts sensitivity testing on the neural network metamodel. 
-We argue that for estimating tail risk measures of VA contact losses, the inner simulation can be replaced entirely by a suitable metamodel. 
+We argue that for estimating tail risk measures of VA contract losses, the inner simulation can be replaced entirely by a suitable metamodel. 
 Eliminating the inner simulation can lead to more substantial computational savings without affecting estimation quality. 
@@
 Dynamic hedging involves a frequent adjustment of a portfolio of financial instruments to offset changes in the value of the guarantees due to market movements~\citep{hull2016options}. 
-This strategy aims at neutralizing the sensitivity of the insurer's liability to market fluctuations by constructing a hedging portfolio that replicates the cash flows of the guarantees.
+This strategy aims to neutralize the sensitivity of the insurer's liability to market fluctuations by constructing a hedging portfolio that replicates the cash flows of the guarantees.
 However, dynamic hedging introduces complexity in estimating the insurer's overall risk exposure.
 One such example is the estimation of tail risk measures of a VA contract.
-It requires the stochastic modeling of the financial market and the accurate loss estimation of the hedging portfolio under different market scenarios.
+It requires a stochastic modeling of the financial market and an accurate loss estimation of the hedging portfolio under different market scenarios.
 Nested simulation has emerged as a robust method for estimating risk measures in such complex settings~\citep{gordy2010nested}.
@@
 Metamodeling, also known as surrogate modeling, is a technique used to approximate complex simulation models with simpler, computationally efficient models. 
-In the context of Monte Carlo simulations, metamodels are models of models that aim at reducing computational costs by creating an approximate model that can quickly predict simulation outputs based on input variables~\citep{kleijnen2018design}.
-This section introduces metamodeling for a Monte Carlo simulation, elaborates on its methodologies, and highlights its importance in practical applications.
+In the context of Monte Carlo simulations, metamodels are models of models that aim to reduce computational costs by creating an approximate model that can quickly predict simulation outputs based on input variables~\citep{kleijnen2018design}.
+This section introduces metamodeling for Monte Carlo simulation, elaborates on its methodologies, and highlights its importance in practical applications.
 
 Monte Carlo simulations are widely used for modeling and analyzing complex systems that are probabilistic in nature. 
-These simulations often require a substantial amount of computational resources, especially when a high degree of accuracy or a high number of iterations is necessary~\citep{glasserman2004monte}. 
-Metamodeling addresses this challenge by constructing an approximate model (known as ametamodel) that emulates the behavior of the original simulation model with much less computational effort.
+These simulations often require substantial computational resources, especially when a high degree of accuracy or a high number of iterations is necessary~\citep{glasserman2004monte}. 
+Metamodeling addresses this challenge by constructing an approximate model (known as a metamodel) that emulates the behavior of the original simulation model with much less computational effort.
 The metamodel serves as a predictive model that maps input variables to output responses. 
@@
 Example use cases for machine learning include~\cite{jin2020deep}, ~\cite{tang2020deep}, and~\cite{rosen2012metamodeling}.
-These methods offer powerful tools for capturing intricate patterns and nonlinear relationships that traditional metamodeling techniques might have to struggle to model them effectively.
+These methods offer powerful tools for capturing intricate patterns and nonlinear relationships that traditional metamodeling techniques might struggle to model effectively.
 In the following sections, we discuss machine learning algorithms in the context of metamodeling for Monte Carlo simulations and their applications in risk management.
@@
 In this paradigm, a model is trained on a labeled dataset, which means that each training example is associated with an output label or value. 
-The goal of a supervised learning paradigm is to learn a general rule that maps inputs (also known as features) to outputs (also known as target), enabling the model to make accurate predictions on new, unseen data.
+The goal of a supervised learning paradigm is to learn a general rule that maps inputs (also known as features) to outputs (also known as targets), enabling the model to make accurate predictions on new, unseen data.
 Supervised learning can be carried out in two domains of applications.
@@
     \item \textbf{Classification}: The output variable is categorical, and the task is to assign inputs to one of several predefined categories to produce a qualitative prediction. 
-    Common use in finance and actuarial applications are fraud detection and credit scoring.
+    Common uses in finance and actuarial applications are fraud detection and credit scoring.
     \item \textbf{Regression}: The output variable is continuous, and the task is to predict a real-valued number and produce a quantitative prediction. 
@@
 This thesis focuses on regression models for risk management applications, where the goal is to predict a continuous target variable based on one or more input features.
-Given a dataset of $n$ observations $\{(x_1, y_1), (x_2, y_2), \ldots, (x_n, y_n)\}$, where $x_i \in \mathbb{R}^d$ is the $d$-dimensional input feature vector, and $y_i \in \mathbb{R}$ is the target variable, a supervised learning algorithm aims to learning a function $f(;\theta): \mathbb{R}^d \rightarrow \mathbb{R}$ that best predicts the target variable $y$ given the input vector of features $x$ with a vector of function parameters $\theta$.
+Given a dataset of $n$ observations $\{(x_1, y_1), (x_2, y_2), \ldots, (x_n, y_n)\}$, where $x_i \in \mathbb{R}^d$ is the $d$-dimensional input feature vector, and $y_i \in \mathbb{R}$ is the target variable, a supervised learning algorithm aims to learn a function $f(;\theta): \mathbb{R}^d \rightarrow \mathbb{R}$ that best predicts the target variable $y$ given the input vector of features $x$ with a vector of function parameters $\theta$.
 
@@
 
-In most risk management applications, a critical task of users of supervised learning models is to design a suitable loss function that aligns with the objectives of the problem.
+In most risk management applications, a critical task for users of supervised learning models is to design a suitable loss function that aligns with the objectives of the problem.
 Another important consideration is the choice of a suitable supervised learning algorithm.
@@
 A regression model predicts a continuous target variable based on one or more input features.
-A multiple linear regression is a simple and interpretable model that attempts to predict a target variable as a linear combination of input features. 
+Multiple linear regression is a simple and interpretable model that attempts to predict a target variable as a linear combination of input features. 
 It assumes a linear relationship between the target output and one or more input features. 
 This method has been thoroughly explored in statistical literature. 
-\citet{bishop2006pattern} provide an extensive treatment of regression techniques in the broader context of machine learning.
-It is known as a parametric regression because it assumes a specific functional form for the input-output relationship with a finite set of parameters~\citep{seber2012linear}.
+\citet{bishop2006pattern} provides an extensive treatment of regression techniques in the broader context of machine learning.
+It is known as parametric regression because it assumes a specific functional form for the input-output relationship with a finite set of parameters~\citep{seber2012linear}.
 A general form of a parametric regression model is given by:
@@
 \end{equation}
-where $p$ is a number of features, $\beta_0, \beta_1, \ldots, \beta_p$ are trainable regression coefficients, and $\phi_j(x)$ are basis functions that transfrom the input $x$ to allow for non-linear modeling.
+where $p$ is the number of features, $\beta_0, \beta_1, \ldots, \beta_p$ are trainable regression coefficients, and $\phi_j(x)$ are basis functions that transform the input $x$ to allow for non-linear modeling.
 Basis functions can be any functions of $x$ that are chosen to capture the underlying structure of the data.
@@
 The training of parametric regression refers to the process of estimating the regression coefficients $\beta_0, \beta_1, \ldots, \beta_p$ that minimize the loss function.
-For a MSE loss metrics, the optimal regression coefficients can be obtained by solving the normal equations.
-Parametric regression is a powerful tool for modeling linear relationships where the basis functions are known from expert knowledge for explicit feature engineering techniques~\citep{hastie2009elements}.
+For an MSE loss metric, the optimal regression coefficients can be obtained by solving the normal equations.
+Parametric regression is a powerful tool for modeling linear relationships where the basis functions are known from expert knowledge or explicit feature engineering techniques~\citep{hastie2009elements}.
 These techniques utilize predefined functional forms to model the relationship between a set of independent variables and a dependent variable. 
@@
 Extensions like polynomial regression and generalized linear models (GLMs) have been introduced to capture non-linearity in the data.
-Nevertheless, these models can still be limited in capturing highly complex patterns of the data.
+Nevertheless, these models can still be limited in capturing highly complex patterns in the data.
 
 \subsection{Non-Parametric Regression Models}
-To overcome some of the previously mentioned limitations of the parametric regression, non-parametric methods such as kernel regression~\citep{hastie2009elements} are often employed. 
+To overcome some of the previously mentioned limitations of parametric regression, non-parametric methods such as kernel regression~\citep{hastie2009elements} are often employed. 
 Kernel regression estimates the relationship by averaging the values of the target variable over a local neighborhood of the input $x$.
@@
 However, they come with several drawbacks that limit their effectiveness, especially in high-dimensional settings or for large datasets. 
-One of the most important drawbacks of the non-parametric regression is the curse of dimensionality \cite{bellman1966dynamic}. 
+One of the most important drawbacks of non-parametric regression is the curse of dimensionality \cite{bellman1966dynamic}. 
 As the number of features increases, the volume of the input space grows exponentially.
@@
 In addition, the computational cost associated with non-parametric methods often grows rapidly with the number of dimensions.
-Cross validation and distance calculation are two computationally expensive operations that are often required for a non-parametric regression.
-These drawbacks make the non-parametric regression impractical for modeling high-dimensional large-scale datasets.
+Cross validation and distance calculation are two computationally expensive operations that are often required for non-parametric regression.
+These drawbacks make non-parametric regression impractical for modeling high-dimensional large-scale datasets.
 
@@
 They can learn complex, non-linear relationships in data without the need for explicit feature engineering.
-The most crude form of a neural network is the feedforward neural network (FNN), which consists of an input layer, one or more hidden layers, and an output layer~\citep{goodfellow2016}.
+The most basic form of a neural network is the feedforward neural network (FNN), which consists of an input layer, one or more hidden layers, and an output layer~\citep{goodfellow2016}.
 
@@
 \end{equation}
-where $\theta = (\theta^{(1)}, \theta^{(2)}, \ldots, \theta^{(k)})$ are trainable parameters of the neural network, $f^{(i)}$ is an $i$-th layer of the neural network, $x$ is an input feature vector, $f^{(1)}(x;\theta^{(1)}) = x$, $f^{(k)}$ is an output layer, $k$ is a number of layers, and $f^{(i)}$ is an output of the $i$-th layer.
+where $\theta = (\theta^{(1)}, \theta^{(2)}, \ldots, \theta^{(k)})$ are trainable parameters of the neural network, $f^{(i)}$ is the $i$-th layer of the neural network, $x$ is an input feature vector, $f^{(1)}(x;\theta^{(1)}) = x$, $f^{(k)}$ is an output layer, $k$ is the number of layers, and $f^{(i)}$ is an output of the $i$-th layer.
 To move from a lower layer to a higher layer, i.e., from layer $i-1$ to layer $i$,
@@
 \end{equation}
-where $a^{(i)}$ are nonlinear activation functions, $\theta^{(i)} = (\beta_0^{(i)}, \dots, \beta_p^{(i)})$ are trainable parameters of the $i$-th layer, and $p_i$ is a number of neurons in the previous layer.
+where $a^{(i)}$ are nonlinear activation functions, $\theta^{(i)} = (\beta_0^{(i)}, \dots, \beta_p^{(i)})$ are trainable parameters of the $i$-th layer, and $p_i$ is the number of neurons in the previous layer.
 Equation~\ref{eq:neural} represents a single neuron in a neural network, which applies a linear transformation to the input followed by a non-linear activation function. 
@@
 
-The key advantage of FNNs lies in their ability to perform automatic feature engineering without a direct human intervention. 
-Unlike traditional machine learning models that require manual selection and transformation of input features, neural networks learn to extract and compose features through their hidden layers during the training.
+The key advantage of FNNs lies in their ability to perform automatic feature engineering without direct human intervention. 
+Unlike traditional machine learning models that require manual selection and transformation of input features, neural networks learn to extract and compose features through their hidden layers during training.
 Each hidden layer in the network captures higher-level abstractions of the input data by transforming the outputs of the previous layer through nonlinear activation functions~\citep{lecun2015deep}.
@@
 The last layer of the neural network, known as the output layer, typically performs a linear transformation of the features extracted by the preceding hidden layers. 
-With $a^{k}(z) = z$, the last layer is equivalent to a multiple linear regression with its inputs as transformed, high-level features learned by the hidden layers.
+With $a^{k}(z) = z$, the last layer is equivalent to multiple linear regression with its inputs as transformed, high-level features learned by the hidden layers.
 We can draw parallels between neural networks and traditional regression models. 
@@
 To overcome the limitations of FNNs in handling sequential input, recurrent neural networks (RNNs) were introduced.
-In a RNN, the hidden state at each time step is a function of both the current input and the hidden state from the previous time period~\citep{elman1990finding}:
+In an RNN, the hidden state at each time step is a function of both the current input and the hidden state from the previous time period~\citep{elman1990finding}:
 
@@
 
-To address these issues, a long short-term memory (LSTM) network was developed by \citet{hochreiter1997long}.
-It is a specialized form of RNNs designed to capture long-term dependencies more effectively with the help of RNN memory cells and gating mechanisms.
+To address these issues, long short-term memory (LSTM) networks were developed by \citet{hochreiter1997long}.
+They are a specialized form of RNNs designed to capture long-term dependencies more effectively with the help of RNN memory cells and gating mechanisms.
 
@@
 By effectively modeling complex, non-linear relationships and temporal dependencies, neural networks serve as powerful tools for addressing the computational challenges in estimating risk measures and developing effective risk mitigation strategies.
-This thesis aims at exploring the application and noise tolerance of LSTM networks in metamodeling for nested simulation procedures in risk management.
+This thesis aims to explore the application and noise tolerance of LSTM networks in metamodeling for nested simulation procedures in risk management.
 In this thesis, we investigate the performance of LSTM networks in approximating the inner simulation model in a two-stage nested simulation procedure for index-linked insurance contracts.
@@
 The training of neural networks involves adjusting the trainable parameters of the network to minimize the loss function, which quantifies the error between the predictions and the labels.
-The training process aims at finding the optimal parameters that minimize this error.
+The training process aims to find the optimal parameters that minimize this error.
 The most common approach is to use gradient descent methods with backpropagation, which is an efficient method for computing the gradients of the loss function with respect to the trainable parameters.
@@
 Stochastic gradient descent (SGD) is a popular optimization algorithm for training neural networks.
-It updates the parameters using a single or a small batch of training examples at a time, which makes it much faster than the crude gradient descent.
+It updates the parameters using a single or a small batch of training examples at a time, which makes it much faster than crude gradient descent.
 However, SGD may oscillate and converge slowly, especially in non-convex problems~\citep{bengio2016}.
 To address these issues, various adaptive learning rate methods have been proposed in the literature.
-The most popular approach is Adam optimizer, which is a SGD algorithm that adjusts the learning rate during training to improve convergence speed and stability~\citep{kingma2014adam}.
+The most popular approach is the Adam optimizer, which is an SGD algorithm that adjusts the learning rate during training to improve convergence speed and stability~\citep{kingma2014adam}.
 
-Another common technique to improve the training of neural networks is a regularization technique to prevent overfitting.
+Another common technique to improve the training of neural networks is regularization to prevent overfitting.
 One effective regularization method is dropout, which randomly sets a fraction of neurons to zero during each training iteration~\citep{srivastava2014dropout}.
@@
 It involves monitoring the model's performance on a validation set and stopping training when the performance no longer improves~\citep{prechelt2002early}.
-This helps prevent over-fitting by stopping training before the model begins to fit to the noise in the data.
+This helps prevent overfitting by stopping training before the model begins to fit to the noise in the data.
 
@@
 Existing machine learning literature addresses this challenge by splitting the data into three parts: training set, validation set, and test set.
-The training set is used to train the model, the validation set is used to tune the model hyper-parameters, and the test set is used to evaluate how well the model generalizes to unseen data.
-The test set is not used during training and is only used for an evaluation purpose.
+The training set is used to train the model, the validation set is used to tune the model hyperparameters, and the test set is used to evaluate how well the model generalizes to unseen data.
+The test set is not used during training and is only used for evaluation purposes.
 
-Under-fitting occurs when the training error is high, which means that the neural network fails to capture the underlying patterns in the training data.
-Over-fitting occurs when the neural network fits to the noise in the training data and cannot generalize results to unseen data.
-In machine learning literature, over-fitting is often quantified as the gap between the training error and the test error~\citep{bishop2006pattern}.
+Underfitting occurs when the training error is high, which means that the neural network fails to capture the underlying patterns in the training data.
+Overfitting occurs when the neural network fits to the noise in the training data and cannot generalize results to unseen data.
+In machine learning literature, overfitting is often quantified as the gap between the training error and the test error~\citep{bishop2006pattern}.
 During training, as the test dataset is not used, this quantity is estimated by using the validation set.
-If the validation error is high compared to the training error, the model is likely over-fitting to the training data.
+If the validation error is high compared to the training error, the model is likely overfitting to the training data.
 
+In practice, the ultimate performance of a neural network is often evaluated based on error metrics on the test dataset and how it compares with the training error. 
 In practice, the ultimate performance of a neural network is often evalutated based on error metrics on the test dataset and how it compares with the training error. 

### 2025-02-20 pre_private/pre.tex
new

@@
         \midrule
-        MLR & $0.706 (\pm 8.34\times 10^{-4})$ & $0.713 (\pm 2.67 \times 10^{-2})$ & $0.706 (\pm 3.44 \times 10^{-4})$ \\
-        QPR & $0.543 (\pm 8.27\times 10^{-4})$ & $0.554 (\pm 2.32 \times 10^{-2})$ & $0.544 (\pm 4.12\times 10^{-4})$ \\
-        FNN & $0.129 (\pm 5.95\times 10^{-3})$ & $0.240 (\pm 9.82 \times 10^{-3})$ & $0.132 (\pm 5.82\times 10^{-3})$ \\
-        RNN & $0.132 (\pm 7.53\times 10^{-3})$ & $0.137 (\pm 7.62\times 10^{-3})$ & $0.119 (\pm 7.51\times 10^{-3})$ \\
-        LSTM & $0.075 (\pm 4.48\times 10^{-3})$ & $0.079 (\pm 5.35\times 10^{-3})$ & $0.063 (\pm 4.43\times 10^{-3})$ \\
-        RNN$^*$\footnotemark & $0.109 (\pm 5.20\times 10^{-3})$ & $0.128 (\pm 5.22\times 10^{-3})$ & $0.109 (\pm 5.20\times 10^{-3})$ \\
+        MLR & $0.706 (\pm 8.3\times 10^{-4})$ & $0.713 (\pm 2.7 \times 10^{-2})$ & $0.706 (\pm 3.4 \times 10^{-4})$ \\
+        QPR & $0.543 (\pm 8.3\times 10^{-4})$ & $0.554 (\pm 2.7 \times 10^{-2})$ & $0.544 (\pm 4.1 \times 10^{-4})$ \\
+        FNN & $0.129 (\pm 6.0\times 10^{-3})$ & $0.240 (\pm 9.8 \times 10^{-3})$ & $0.132 (\pm 5.8 \times 10^{-3})$ \\
+        RNN & $0.132 (\pm 7.5\times 10^{-3})$ & $0.137 (\pm 7.6 \times 10^{-3})$ & $0.119 (\pm 7.5 \times 10^{-3})$ \\
+        LSTM & $0.075 (\pm 4.5\times 10^{-3})$ & $0.079 (\pm 5.4 \times 10^{-3})$ & $0.063 (\pm 4.4 \times 10^{-3})$ \\
+        RNN$^*$\footnotemark & $0.109 (\pm 5.2\times 10^{-3})$ & $0.128 (\pm 5.2 \times 10^{-3})$ & $0.109 (\pm 5.2 \times 10^{-3})$ \\
         \bottomrule
         \end{tabular}
-        \caption{MSEs of metamodels for GMWB inner simulation model.}
+        \caption{Average MSEs and 95\% confidence bands of metamodels for GMWB inner simulation model.}
         \label{tab:gmwb_arch}
@@
     \begin{itemize}
+        \item   RNN-based metamodels have lower true errors than their training errors.
         \item   DNN metamodels with suitable architectures \textbf{cut through the noise} in training labels.
-        \item   
     \end{itemize}
@@
         \item   Same color $\rightarrow$ same total simulation budget.
-        \item   $N = 10$ is a reasonable budget allocation for LSTM metamodels.
+        \item   $N' = 10$ is a reasonable budget allocation for LSTM metamodels.
     \end{itemize}

### 2025-02-20 uw-ethesis-frontpgs.tex
new

@@
 
-        Waterloo, Ontario, Canada, 2024 \\
+        Waterloo, Ontario, Canada, 2025 \\
 
@@
 
-        \copyright\ Xintong Li, 2024 \\
+        \copyright\ Xintong Li, 2025 \\
         \end{center}
@@
 Supervisor(s): \> Mingbin Feng \\
-\> Assistant Professor, Dept. of Statistics and Actuarial Science\\
+\> Associate Professor, Dept. of Statistics and Actuarial Science\\
 \> University of Waterloo \\[1cm]
@@
 
-Quantitative risk management of modern financial derivatives and actuarial products is intricate and often requires modelling the underlying stochasticity with Monte Carlo simulations.
-A simulation scheme is flexible, and it can easily adapt to changes in model assumptions and market conditions.
-However, as multiple sources of risk are considered over long time horizons, such simulation schemes become increasingly more expensive to implement. 
-Tremendous research effort has been dedicated in the design of computationally efficient machine learning-based procedures that mitigate the computational burden of a standard simulation procedure.
-In machine learning, model flexibility comes at the expense of model resilience, which is especially crucial for risk management tasks.
-This study considers the management of tail risk for complex financial and actuarial products with resilient machine learning-based nested simulation procedures.
+Risk management of financial derivatives and actuarial products is intricate and often requires modelling the underlying stochasticity with Monte Carlo simulations.
+Monte Carlo simulation is flexible, and it can easily adapt to changes in model assumptions and market conditions.
+However, as multiple sources of risk are considered over long time horizons, the simulation model becomes complex and time-consuming to run. 
+Tremendous research effort has been dedicated to the design of computationally efficient machine learning-based procedures that mitigate the computational burden of a standard simulation procedure.
+In machine learning, model flexibility comes at the expense of model resilience, which is crucial for risk management tasks.
+This study considers estimating tail risks of complex financial and actuarial products with resilient machine learning-based nested simulation procedures.
 We propose a novel metamodeling approach that integrates deep neural networks within a nested simulation framework for efficient risk estimation.
-Our approaches offer substantial improvements over standard simulation procedures associated with and illustrate how a resilient machine learning model is built for problem complexity, data structure, quality, and quantity.
-To further enhance adaptability to new variable annuity contracts and changing market conditions, the thesis introduces transfer learning techniques. 
-By reusing and fine-tuning pre-trained metamodels, the proposed approach accelerates the adaptation process to different contract features and evolving market dynamics without the need for retraining models from the scratch.
+Our approaches offer substantial improvements over the associated standard simulation procedures.
+This study also illustrates how to build and assess resilient machine learning models for different problem complexities and different data structures, qualities, and quantities.
+To further enhance adaptability to new variable annuity contracts and changing market conditions, this thesis explores transfer learning techniques. 
+By reusing and fine-tuning pre-trained metamodels, the proposed approach accelerates the adaptation process to different contract features and evolving market dynamics without retraining models from scratch.
 Transfer learning improves computational efficiency and enhances the robustness and flexibility of neural network metamodels in dynamic hedging of variable annuities.
 
-Extensive numerical experiments carried out in this thesis demonstrate that the proposed method achieves substantial improvements in computational efficiency, reducing simulation times by orders of magnitude compared to standard nested simulation procedures.
+Extensive numerical experiments in this thesis demonstrate that the proposed methods substantially improve computational efficiency, sometimes shortening runtime by orders of magnitude compared to standard nested simulation procedures.
 The results indicate that the deep neural network metamodels with transfer learning can quickly adapt to new market scenarios and contract specifications.
-The findings of this research contribute to the advancement of risk management practices for complex actuarial products and financial derivatives.
+This research contributes to the advancement of risk management practices for complex actuarial products and financial derivatives.
 By leveraging advanced machine learning techniques, the thesis offers a practical and scalable solution for insurers to perform timely and accurate risk assessments.
-The integration of long short-term memory (LSTM) metamodels and transfer learning into a nested simulation framework represents a major step forwardtoward more efficient, adaptable, and robust methodologies in actuarial science and quantitative finance.
+The integration of long short-term memory metamodels and transfer learning into a nested simulation framework represents a major step forward toward more efficient, adaptable, and robust methodologies in actuarial science and quantitative finance.
 
@@
 
-I would like to thank Professor Mingbin Feng and Professor Tony Wirjanto for their valuable support. 
-They have patiently helped me through my research journey.
-I am forever grateful for my true best friends, who have supported me during the most difficult times.
+I would like to express my deepest gratitude to Professor Mingbin Feng and Professor Tony Wirjanto for their invaluable support and guidance throughout my academic journey. 
+Their unwavering patience and profound wisdom have been instrumental in helping me navigate the complexities of my research. 
+I am deeply grateful for their mentorship, which has not only sharpened my analytical skills but also inspired me to pursue excellence in my work.
+
+Additionally, I extend my sincere thanks to my best friends, who have stood by me during the most challenging times. 
+Their unwavering support and encouragement have been a constant source of strength that helped me overcome obstacles and maintained my motivation throughout this process. 
+Words cannot fully convey how much their presence has meant to me over these years.
+
+I also wish to acknowledge the support of my family, who have always been a source of love and encouragement.
+They have provided me with the emotional stability I needed to focus on my studies and research.
 

### 2025-02-20 introduction.tex
e

--- 2025-02-02 introduction.tex
@@
 
-Quantitative risk management is a key component of modern financial systems.
-Successful risk management practice can ensure the stability and resilience against a variety of risks.
-For financial products such as option portfolios and variable annuity (VA) contracts, traditional risk assessment methods often fall short in accurately capturing the complex dynamics of the underlying risk factors.
-VA contracts are a popular type of complex insurance product that is linked to the performance of underlying assets.
-It provides a guaranteed minimum income benefit to the policyholder regardless of the performance of the underlying assets.
+Risk management is a key component of modern financial systems.
+Successful risk management practice can enhance financial stability and resilience for individual companies and for the financial system too.
+Variable annuity (VA) contracts are a popular type of complex insurance product that is linked to the performance of underlying assets.
+They provide a guaranteed minimum income benefit to the policyholder regardless of the performance of the underlying assets.
 Advanced Monte Carlo simulation techniques, particularly nested simulation procedures, become indispensable for risk assessment of such products.
@@
 Furthermore, in real-world applications, the computational burden of a nested simulation can be prohibitive.
-The number of inner simulations required to achieve a desired level of accuracy for each outer scenario can be intractably large.
+The number of inner simulations required to achieve a desired level of accuracy for each outer scenario can be large.
 Metamodeling techniques that approximate the inner simulation model can be used to reduce the computational burden of a nested simulation.
@@
 \end{itemize}
-The risk management of VAs is a challenging problem due to the complex interactions between the policyholder's behavior, the financial market dynamics, and the insurer's risk management strategies.
+Risk management of VAs is a challenging problem due to the complex interactions between the policyholder's behavior and the financial market dynamics.
 We focus mainly on the estimation of tail risk measures of VA contract losses using metamodel-based nested simulation procedures.
@@
 These simulations often require a substantial amount of computational resources, especially when a high degree of accuracy or a high number of iterations is necessary~\citep{glasserman2004monte}. 
-Metamodeling addresses this challenge by constructing an approximate model (known as ametamodel) that emulates the behavior of the original simulation model with much less computational effort.
+Metamodeling addresses this challenge by constructing an approximate model (known as a metamodel) that emulates the behavior of the original simulation model with much less computational effort.
 The metamodel serves as a predictive model that maps input variables to output responses. 

### 2025-02-20 uw-ethesis-frontpgs.tex
e

@@
 Additionally, I extend my sincere thanks to my best friends, who have stood by me during the most challenging times. 
-Their unwavering support and encouragement have been a constant source of strength that helped me overcome obstacles and maintained my motivation throughout this process. 
+Their unwavering support and encouragement have been a constant source of strength that has helped me overcome obstacles and maintain my motivation throughout this process. 
 Words cannot fully convey how much their presence has meant to me over these years.

### 2025-02-20 introduction.tex
e

@@
 Eliminating the inner simulation can lead to more substantial computational savings without affecting estimation quality. 
-In the case of requiring extensive inner simulations for regulatory purposes, effective budget allocations can help achieve an improved estimator quality with the same computational budget.
+In the case of requiring extensive inner simulations for regulatory purposes, effective budget allocations can help achieve improved estimator quality with the same computational budget.
 In practice, underlying assumptions of the simulation model are subject to change, and new VA contracts are issued with different contract specifications.
@@
 Chapter~\ref{chap:project3} uses transfer learning techniques for a quick adaptation of the neural network metamodel to new market conditions and new VA contracts.
-Our numerical experiments shows that an judicious use of transfer learning can lead to substantially better metamodels than those trained from the scratch.
+Our numerical experiments show that a judicious use of transfer learning can lead to substantially better metamodels than those trained from scratch.
 Chapter~\ref{chap:conclusion} concludes the thesis and discusses potential future research directions.
@@
 Despite its robustness, nested simulation is computationally intensive, often requiring a substantial amount of computational resources and time. 
-Each scenario in the outer simulation requires numerous inner simulations to accurately estmate contract loss. 
+Each scenario in the outer simulation requires numerous inner simulations to accurately estimate contract loss. 
 This computational burden poses practical limitations, especially when a high degree of precision in tail risk estimation is required.
@@
 The development of advanced machine learning models and deep learning techniques has enhanced metamodeling approaches for Monte Carlo simulations, especially in high-dimensional and complex problem settings.
-Example use cases for machine learning include~\cite{jin2020deep}, ~\cite{tang2020deep}, and~\cite{rosen2012metamodeling}.
-These methods offer powerful tools for capturing intricate patterns and nonlinear relationships that traditional metamodeling techniques might have to struggle to model them effectively.
+Example use cases for machine learning include~\cite{jin2020deep},~\cite{tang2020deep}, and~\cite{rosen2012metamodeling}.
+These methods offer powerful tools for capturing intricate patterns and nonlinear relationships that traditional metamodeling techniques might struggle to model effectively.
 In the following sections, we discuss machine learning algorithms in the context of metamodeling for Monte Carlo simulations and their applications in risk management.
@@
 This thesis focuses on regression models for risk management applications, where the goal is to predict a continuous target variable based on one or more input features.
-Given a dataset of $n$ observations $\{(x_1, y_1), (x_2, y_2), \ldots, (x_n, y_n)\}$, where $x_i \in \mathbb{R}^d$ is the $d$-dimensional input feature vector, and $y_i \in \mathbb{R}$ is the target variable, a supervised learning algorithm aims to learning a function $f(;\theta): \mathbb{R}^d \rightarrow \mathbb{R}$ that best predicts the target variable $y$ given the input vector of features $x$ with a vector of function parameters $\theta$.
+Given a dataset of $n$ observations $\{(x_1, y_1), (x_2, y_2), \ldots, (x_n, y_n)\}$, where $x_i \in \mathbb{R}^d$ is the $d$-dimensional input feature vector, and $y_i \in \mathbb{R}$ is the target variable, a supervised learning algorithm aims at learning a function $f(;\theta): \mathbb{R}^d \rightarrow \mathbb{R}$ that best predicts the target variable $y$ given the input vector of features $x$ with a vector of function parameters $\theta$.
 
@@
 \end{equation}
-where $p$ is a number of features, $\beta_0, \beta_1, \ldots, \beta_p$ are trainable regression coefficients, and $\phi_j(x)$ are basis functions that transfrom the input $x$ to allow for non-linear modeling.
+where $p$ is a number of features, $\beta_0, \beta_1, \ldots, \beta_p$ are trainable regression coefficients, and $\phi_j(x)$ are basis functions that transform the input $x$ to allow for non-linear modeling.
 Basis functions can be any functions of $x$ that are chosen to capture the underlying structure of the data.
@@
 The training of parametric regression refers to the process of estimating the regression coefficients $\beta_0, \beta_1, \ldots, \beta_p$ that minimize the loss function.
-For a MSE loss metrics, the optimal regression coefficients can be obtained by solving the normal equations.
+For a MSE loss metric, the optimal regression coefficients can be obtained by solving the normal equations.
 Parametric regression is a powerful tool for modeling linear relationships where the basis functions are known from expert knowledge for explicit feature engineering techniques~\citep{hastie2009elements}.
@@
 \subsection{Non-Parametric Regression Models}
-To overcome some of the previously mentioned limitations of the parametric regression, non-parametric methods such as kernel regression~\citep{hastie2009elements} are often employed. 
+To overcome some of the previously mentioned limitations of parametric regression methods, non-parametric methods such as kernel regression~\citep{hastie2009elements} are often employed. 
 Kernel regression estimates the relationship by averaging the values of the target variable over a local neighborhood of the input $x$.
@@
 However, they come with several drawbacks that limit their effectiveness, especially in high-dimensional settings or for large datasets. 
-One of the most important drawbacks of the non-parametric regression is the curse of dimensionality \cite{bellman1966dynamic}. 
+One of the most important drawbacks of non-parametric regression methods is the curse of dimensionality~\cite{bellman1966dynamic}. 
 As the number of features increases, the volume of the input space grows exponentially.
@@
 Cross validation and distance calculation are two computationally expensive operations that are often required for a non-parametric regression.
-These drawbacks make the non-parametric regression impractical for modeling high-dimensional large-scale datasets.
+These drawbacks make non-parametric regression methods impractical for modeling high-dimensional large-scale datasets.
 
@@
 The key advantage of FNNs lies in their ability to perform automatic feature engineering without a direct human intervention. 
-Unlike traditional machine learning models that require manual selection and transformation of input features, neural networks learn to extract and compose features through their hidden layers during the training.
+Unlike traditional machine learning models that require manual selection and transformation of input features, neural networks learn to extract and compose features through their hidden layers during their training.
 Each hidden layer in the network captures higher-level abstractions of the input data by transforming the outputs of the previous layer through nonlinear activation functions~\citep{lecun2015deep}.
@@
 Stochastic gradient descent (SGD) is a popular optimization algorithm for training neural networks.
-It updates the parameters using a single or a small batch of training examples at a time, which makes it much faster than the crude gradient descent.
+It updates the parameters using a single or a small batch of training examples at a time, which makes it much faster than a crude gradient descent.
 However, SGD may oscillate and converge slowly, especially in non-convex problems~\citep{bengio2016}.
 To address these issues, various adaptive learning rate methods have been proposed in the literature.
-The most popular approach is Adam optimizer, which is a SGD algorithm that adjusts the learning rate during training to improve convergence speed and stability~\citep{kingma2014adam}.
+The most popular approach is Adam optimizer, which is an SGD algorithm that adjusts the learning rate during training to improve convergence speed and stability~\citep{kingma2014adam}.
 
@@
 Existing machine learning literature addresses this challenge by splitting the data into three parts: training set, validation set, and test set.
-The training set is used to train the model, the validation set is used to tune the model hyper-parameters, and the test set is used to evaluate how well the model generalizes to unseen data.
-The test set is not used during training and is only used for an evaluation purpose.
+The training set is used to train the model, the validation set is used to tune the model hyperparameters, and the test set is used to evaluate how well the model generalizes to unseen data.
+The test set is not used during training and is only used for evaluation purposes.
 
-Under-fitting occurs when the training error is high, which means that the neural network fails to capture the underlying patterns in the training data.
-Over-fitting occurs when the neural network fits to the noise in the training data and cannot generalize results to unseen data.
-In machine learning literature, over-fitting is often quantified as the gap between the training error and the test error~\citep{bishop2006pattern}.
+Underfitting occurs when the training error is high, which means that the neural network fails to capture the underlying patterns in the training data.
+Overfitting occurs when the neural network fits to the noise in the training data and cannot generalize results to unseen data.
+In machine learning literature, overfitting is often quantified as the gap between the training error and the test error~\citep{bishop2006pattern}.
 During training, as the test dataset is not used, this quantity is estimated by using the validation set.
-If the validation error is high compared to the training error, the model is likely over-fitting to the training data.
+If the validation error is high compared to the training error, the model is likely overfitting to the training data.
 
-In practice, the ultimate performance of a neural network is often evalutated based on error metrics on the test dataset and how it compares with the training error. 
+In practice, the ultimate performance of a neural network is often evaluated based on error metrics on the test dataset and how it compares with the training error. 
 The test error is often thought to be a reliable indicator of the model's generalization capability for most machine learning applications.

### 2025-02-20 uw-ethesis-frontpgs.tex
e

@@
 
-Risk management of financial derivatives and actuarial products is intricate and often requires modelling the underlying stochasticity with Monte Carlo simulations.
-Monte Carlo simulation is flexible, and it can easily adapt to changes in model assumptions and market conditions.
+Risk management of financial derivatives and actuarial products is intricate and often requires modeling the underlying stochasticity with Monte Carlo simulations.
+Monte Carlo simulation is flexible and can easily adapt to changes in model assumptions and market conditions.
 However, as multiple sources of risk are considered over long time horizons, the simulation model becomes complex and time-consuming to run.
-Tremendous research effort has been dedicated to the design of computationally efficient machine learning-based procedures that mitigate the computational burden of a standard simulation procedure.
+Tremendous research effort has been dedicated to designing computationally efficient machine learning-based procedures that mitigate the computational burden of a standard simulation procedure.
 In machine learning, model flexibility comes at the expense of model resilience, which is crucial for risk management tasks.
@@
 Extensive numerical experiments in this thesis demonstrate that the proposed methods substantially improve computational efficiency, sometimes shortening runtime by orders of magnitude compared to standard nested simulation procedures.
-The results indicate that the deep neural network metamodels with transfer learning can quickly adapt to new market scenarios and contract specifications.
+The results indicate that deep neural network metamodels with transfer learning can quickly adapt to new market scenarios and contract specifications.
 This research contributes to the advancement of risk management practices for complex actuarial products and financial derivatives.

### 2025-02-20 project1/nsSurvey.tex
w

@@
 Nested simulation procedures are commonly used in financial engineering to estimate risk measures for portfolios of complex financial derivatives. 
-The term \textit{nested} is referred to a nested estimation problem, in which the estimation of the risk measure requires two levels of Monte Carlo (MC) simulations.
-In a typical nested simulation procedure, an outer level simulation model generates underlying risk factors, which is referred to as the \textit{outer scenarios}.
-For each outer scenario, an inner level simulation model generates scenario-wise samples of the portfolio losses, which is referred to as the \textit{inner replications}.
+The term \textit{nested} refers to a nested estimation problem, in which the estimation of the risk measure requires two levels of Monte Carlo (MC) simulations.
+In a typical nested simulation procedure, an outer-level simulation model generates underlying risk factors, which are referred to as the \textit{outer scenarios}.
+For each outer scenario, an inner-level simulation model generates scenario-wise samples of the portfolio losses, which are referred to as the \textit{inner replications}.
 
@@
 ~\cite{gordy2010nested} are the first to analyze and propose the optimal budget allocation of a standard nested simulation procedure. 
-The term \textit{standard} refers to using a standard MC estimator, the sample mean of the inner replication to estimate a scenario-wise portfolio loss for an outer scenario.
+The term \textit{standard} refers to using a standard MC estimator, the sample mean of the inner replications to estimate a scenario-wise portfolio loss for an outer scenario.
 ~\cite{gordy2010nested} investigate an optimal budget allocation for a standard nested simulation procedure with respect to the MSE of the estimated risk measure.
@@
 The standard nested simulation procedure is computationally expensive with a somewhat wasteful use of the simulation budget, as only the inner replications from the same outer scenario are used in estimating the scenario-wise portfolio loss for that outer scenario.
-Subsequent research efforts have been made to improve the efficiency of nested simulation procedures by using the inner replications from other outer scenarios. 
+Subsequent research efforts have been made to improve the efficiency of nested simulation procedures by using inner replications from other outer scenarios.
 This is referred to as pooling.
-Different methods pool in different ways, either by a trained supervised learning metamodel or by pre-defined likelihood ratio weights.
+Different methods pool in different ways, either through a trained supervised learning metamodel or through predefined likelihood ratio weights.
 ~\cite{broadie2015risk} propose a regression-based nested simulation procedure, which uses a trained regression metamodel to estimate the scenario-wise portfolio loss for an outer scenario by pooling the inner replications from all outer scenarios.
@@
 This paper presents a survey study of some popular nested simulation procedures that have both asymptotic convergence analysis and finite-sample performance evaluation.
-Many procedures are proposed in the literature, but they are not directly comparable due to having different error metrics, different assumptions, and different numerical examples used in their studies.
+Many procedures have been proposed in the literature, but they are not directly comparable because they use different error metrics, different assumptions, and different numerical examples in their studies.
 Within a common analytical framework, we first summarize and compare their asymptotic rates of convergence.
@@
 
-In terms of finite-sample performance, different studies propose different examples in their numerical experiments, which introduces unfair advantages for certain simulation procedures over the others.
+In terms of finite-sample performance, different studies propose different examples in their numerical experiments, which introduces unfair advantages for certain simulation procedures over others. 
 A fair comparison among popular methods is therefore urgently needed in the literature. 
@@
 As a result, extensive numerical experiments are conducted to show, in practical examples, how well the finite-sample performance of a method matches its theoretical convergence behavior. 
-With our numerical examples, we compare the nested simulation procedures for different payoff complexity, problem dimensions, and risk measures. 
-This chapter also provides a discussion on the computational complexity of different nested simulation procedures, including additional computational costs for training supervised learning metamodels and pooling inner replications.
+Through our numerical examples, we compare the nested simulation procedures for different payoff complexities, problem dimensions, and risk measures. 
+This chapter also provides a discussion of the computational complexity of different nested simulation procedures, including additional computational costs for training supervised learning metamodels and pooling inner replications.
 
@@
 
-$$\rho(L) = \rho(L(X))$$
+$$\rho(L) = \rho(L(X)),$$
 
@@
 Applying the analysis of~\cite{giles2015multilevel} in a nested simulation context,~\cite{giles2019multilevel} show that the MLMC method can achieve a similar degree of accuracy as the standard nested simulation procedure with a lower total computational budget.
-The simulation budget $\Gamma$ is a sum of the computational budget at each level, that is, $\Gamma = \sum_{\upsilon=0}^{\Upsilon} M_{\upsilon} \cdot N_{\upsilon}$.
+The simulation budget $\Gamma$ is a sum of the computational budget at each level, that is to say, $\Gamma = \sum_{\upsilon=0}^{\Upsilon} M_{\upsilon} \cdot N_{\upsilon}$.
 Neither the standard nested simulation procedure nor the MLMC method involves pooling the inner replications from all outer scenarios.
@@
 where $\hat{L}^{\text{SL}}_{(\lceil \alpha M' \rceil)}$ is an $\lceil \alpha M' \rceil$-th order statistic of $\hat{L}^{\text{SL}}_{M, N}(\tilde{X}_1), \dots, \hat{L}^{\text{SL}}_{M, N}(\tilde{X}_{M'})$.
-Note that $\hat{L}^{\text{SL}}_{M, N}(\cdot)$ is the model preditions of a supervised learning model trained on the training samples $(X_1, \hat{L}_{N, 1}), \dots, (X_M, \hat{L}_{N, M})$.
+Note that $\hat{L}^{\text{SL}}_{M, N}(\cdot)$ is the model predictions of a supervised learning model trained on the training samples $(X_1, \hat{L}_{N, 1}), \dots, (X_M, \hat{L}_{N, M})$.
 
@@
             where $\Phi$ is a chosen basis, and $\hat{\beta}$ is estimated from the training samples.
-            In~\cite{broadie2015risk}, the convergence analysis is performed on the expection Equation~\ref{eq1:sl-E} and for smooth and Lipschitz continuous $h$. 
+            In~\cite{broadie2015risk}, the convergence analysis is performed on the expectation (Equation~\ref{eq1:sl-E}) and for smooth and Lipschitz continuous $h$. 
             Connections between the expectation and the MSE are discussed in the Appendix.
@@
 \end{align}
-where $\Gamma$ is the a simulation budget for a nested simulation procedure.
+where $\Gamma$ is a simulation budget for a nested simulation procedure.
 A special case is the MLMC method, where the total simulation budget $\Gamma$ is the sum of the simulation budgets at all levels.
@@
 However, for a Lipschitz continuous function $h$, Equation~\ref{eq1:mse-sns2} leads to a stronger order of convergence than Equation~\ref{eq1:mse-sns}.
-In the following, we analyze the convergence of the standard nested simulation procedure for a smooth and a Lipschitz continuous $h$ by using both decompositions.
+In the following, we analyze the convergence of the standard nested simulation procedure for a smooth and a Lipschitz continuous $h$ by using both decomposition methods.
 Their critical assumptions and convergence results are summarized and compared.
@@
 The analysis in~\cite{gordy2010nested} is based on the differentiablity of the joint density of $Y$ and the average inner simulation noise, which is difficult to verify in practice.
-Instead, we use the a Taylor expansion of the smooth function $h$ to analyze the convergence of the standard nested simulation procedure.
+Instead, we use a Taylor expansion of the smooth function $h$ to analyze the convergence of the standard nested simulation procedure.
 The critical assumption in our derivation is Assumption~\ref{as1:sns-noise-var}, which is necessary to ensure the existence of the fourth moment of the simulation noise and the convergence of $S_2$, the second order term in the Taylor expansion.
@@
 \section{Finite-Sample Experiments} \label{sec1:numerical-experiments}
-The theoretical framework has lend itself for a comparison of the asymptotic convergence behavior for different nested simulation procedures.
+The theoretical framework has lent itself for a comparison of the asymptotic convergence behavior for different nested simulation procedures.
 However, a simulation budget in practice is almost always finite.
@@
 
-In the following sections, we examine the empirical convergence of the nested simulation procedures in a similar manner as in Figure~\ref{fig1:compareAll}.
+In the following sections, we examine the empirical convergence of the nested simulation procedures similarly as in Figure~\ref{fig1:compareAll}.
 With a more detailed analysis of different risk measures, option types, and asset dimensions, we aim at providing a comprehensive understanding and comparison of the convergence behavior of the nested simulation procedures in practice.
@@
 In portfolio risk management, the asset dimension is a critical factor that determines the complexity of the portfolio and the computational cost of the risk measure estimation.
-The theoretical analyses in Section~\ref{sec1:convergence-orders} suggest that the asymptotic rate of convergence of the nested simulation procedures, except for the kernel smoothing-based procedure, is independent from the asset dimension.
+The theoretical analyses in Section~\ref{sec1:convergence-orders} suggest that the asymptotic rate of convergence of the nested simulation procedures, except for the kernel smoothing-based procedure, is independent of the asset dimension.
 However, in practice, their empirical convergence behavior could be different.
@@
 Our previous numerical experiments have been conducted under the assumption that the underlying asset dynamics follow a multidimensional geometric Brownian motion with $0.3$ pairwise correlation.
-To examine the sensitivity of the empirical convergence behavior to the asset model, we consider a stochastic volatility model of a Heston type~\citep{heston1993stochastic}.
+To examine the sensitivity of the empirical convergence behavior to the asset model, we consider a stochastic volatility model of a Heston type~\citep{heston1993closed}.
 
@@
 
-The cost associated with pooling makes a major impact on the overall computaional complexity of a metamodel-based nested simulation procedure.
+The cost associated with pooling makes a major impact on the overall computational complexity of a metamodel-based nested simulation procedure.
 In our finite-sample experiments, we have indeed observed that the actual computational cost to deviate substantially from the simulation cost.
@@
 The $x$-axis shows the total simulation budget $\Gamma$, and the $y$-axis is the total computational time for 1 replication of the numerical experiment, in seconds.
-All procedures are implemented on a machine with an AMD Ryzen 9 7900X processor with 32GB of RAM.
+All procedures are implemented on a machine with an AMD Ryzen 9 7900X processor with 32 GB of RAM.
 8 cores are used for parallel computing, and the total computational time is the sum of the simulation time, the training time, and the prediction time.
@@
     \item The kernel smoothing-based and KRR-based procedure requires a cross-validation procedure to estimate the optimal hyperparameters. 
-    In our implementaion of kNN, the cross-validation is conducted by using a grid search with a search space which cardinality does not grow with the simulation budget $\Gamma$.
+    In our implementation of kNN, the cross-validation is conducted by using a grid search with a search space which cardinality does not grow with the simulation budget $\Gamma$.
     However, the cross-validation cost of the kernel smoothing-based procedure grows with the simulation budget $\Gamma$ as more samples are involved.
@@
 In the task of estimating risk measures for portfolios of complex financial derivatives, nested simulation procedures are commonly required but often computationally expensive. 
-Tremendous efforts have been made to improve the efficiency of nested simulation procedures by approximating the inner simulation model with a metamodels. 
+Tremendous efforts have been made to improve the efficiency of nested simulation procedures by approximating the inner simulation model with a metamodel. 
 In this study, we review the literature on nested simulation procedures in financial engineering and provide fair comparisons of different metamodels by using the same set of numerical examples. 
@@
 As a result, the total computational budget is not necessarily the same as the simulation budget, which is usually a limiting factor for practical applications.
-A kernel-based procedure, e.g., kNN and KRR, requires cross-validation, and its empirical performance depends heavily the choice of hyperparameters.
+A kernel-based procedure, e.g., kNN and KRR, requires cross-validation, and its empirical performance depends heavily on the choice of hyperparameters.
 A kNN-based procedure is sensitive to the asset dimension and the problem complexity.

### 2025-02-20 project2/nnMetamodels.tex
w

@@
 
-In a nested simulation, a simulation model is used to generate a large number of outer scenarios, and each scenario is then used as an input to another simulation model, referred to as a inner simulation model.
+In a nested simulation, a simulation model is used to generate a large number of outer scenarios, and each scenario is then used as an input to another simulation model, referred to as an inner simulation model.
 Borrowing terminologies from the machine learning community, we can view a set of simulated outer scenarios and estimated hedging errors for those scenarios as \textit{features} and noisy \textit{labels}.
@@
 
-Let $L_1,L_2,\ldots,L_M$ be $M$ independent and identically distributed (i.i.d.) simulated losses of $L$ and let $L_{(1)}\leq L_{(2)}\leq \ldots\leq L_{(M)}$ be the corresponding ordered losses.
+Let $L_1,L_2,\ldots,L_M$ be $M$ independent and identically distributed (i.i.d.) simulated losses of $L$ and let $L_{(1)}\leq L_{(2)}\leq \ldots\leq L_{(M)}$ be the ordered losses.
 For a given confidence level $\alpha$ (assume that $\alpha M$ is an integer for simplicity), $\alpha$-VaR can be estimated by the sample quantile $\widehat{\VaR}_\alpha = L_{(\alpha M)}$.
@@
 There are two different types of experiment designs for nested simulation procedures: fixed-budget design and fixed-accuracy design.
-In a fixed-budget design, the simulation budget is fixed and the goal is to achieve the highest degree of accuracy possible within the budget.
+In a fixed-budget design, the simulation budget is fixed, and the goal is to achieve the highest degree of accuracy possible within the budget.
 Let $\Gamma = MN$ be the simulation budget for the standard procedure, where each scenario receives $\frac{\Gamma}{M}$ inner replications.
@@
 The size of the predicted tail scenario set in stage 1, $m$, is an important experiment design parameter that affects the correct identification of true tail scenarios and ultimately affects the estimation accuracy for CVaR.
-Clearly, there is a lower bound $m \geq (1-\alpha)M$ because the $\alpha$-CVaR is estimated by the average of $(1-\alpha)M$ largest losses at the end of stage 2.
+Clearly, there is a lower bound $m \geq (1-\alpha)M$ because the $\alpha$-CVaR is estimated by the average of the largest $(1-\alpha)M$ losses at the end of stage 2.
 For ease of reference, we call the additional percentage of predicted tail scenarios above this lower bound, i.e., $\epsilon = \frac{m - (1-\alpha)M}{M}$, as a \textit{safety margin}.
@@
 
-\footnotetext{This row summarizes the error metrics of the well-trained RNN, where the ones suffers from a vanishing gradient issue are removed from the averages.}
+\footnotetext{This row summarizes the error metrics of the well-trained RNN, where the ones suffer from a vanishing gradient issue are removed from the averages.}
 
@@
 Figure~\ref{fig2:QQ_RNN} shows the quantile-quantile (QQ) plots between the \textbf{training} labels and the RNN predictions for two macro replications, where training of the latter is hindered by the vanishing gradient problem.
-    As a result, the half length of the $95\%$ confidence band of the RNN's training error is much larger than all other metamodels. 
+    As a result, the half-width of the $95\%$ confidence band of the RNN's training error is much larger than all other metamodels. 
     The last row of Table~\ref{tab:gmwb_arch} shows the average squared errors of the good RNN metamodels that have been successfully trained. 
@@
     \item regularization that prevents over-fitting, and 
-    \item a prior knowledge that guides the optimization algorithm to find a solution that generalizes well to unseen data.
+    \item prior knowledge that guides the optimization algorithm to find a solution that generalizes well to unseen data.
 \end{enumerate}
@@
 For practical applications that utilize nerual networks as metamodels, we recommend not to simulate the test scenarios.
-Instead, we recommend to simulate the true contract losses on a subset of training scenarios to evaluate the metamodels' generalization ability.
+Instead, we recommend simulating the true contract losses on a subset of training scenarios to evaluate the metamodels' generalization ability.
 
@@
 For a two-stage procedure with a $0\%$ safety margin, the extra computational cost is from the extensive inner simulation in stage 2.
-On $4$ $20$-core Intel Xeon Gold $\num{6230}$ processors, stage 2 of the two-stage procedure takes $30$ minutes to run with parallel processing, while the $95\%$ confidence band of training time of the high-capacity LSTM metamodel is $(19.64 \pm 0.94)$ minutes on a Nvidia RTX $\num{3060}$ Ti GPU.
+On $4$ $20$-core Intel Xeon Gold $\num{6230}$ processors, stage 2 of the two-stage procedure takes $30$ minutes to run with parallel processing, while the $95\%$ confidence band of training time of the high-capacity LSTM metamodel is $(19.64 \pm 0.94)$ minutes on an Nvidia RTX $\num{3060}$ Ti GPU.
 While the accuracy of the two-stage procedure is highly dependent on the safety margin, increasing the safety margin introduces extra computational cost.
@@
         \includegraphics[width=\textwidth]{./project2/figures/singleStage/MSEConvergence_lstmLoCap.png}
-        \caption{regular LSTM}
+        \caption{Regular LSTM}
         \label{subfig2:convLoCap}
@@
         \includegraphics[width=\textwidth]{./project2/figures/singleStage/MSEConvergence_lstmHiCap.png}
-        \caption{high-capacity LSTM}
+        \caption{High-capacity LSTM}
         \label{subfig2:convHiCap}
@@
 For each budget $\Gamma$, the metamodels are trained for different combinations of $M$ and $N$, and the metamodel with the best RRMSE is plotted.
-While numerical results suggests that the CVaR estimator of the single-stage procedure with LSTM metamodels may have better accuracy than the two-stage procedure and the standard procedure when the number of outer scenarios is further increased, we found it difficult to compare their performance due to insufficient computational resources.
+While numerical results suggest that the CVaR estimator of the single-stage procedure with LSTM metamodels may have better accuracy than the two-stage procedure and the standard procedure when the number of outer scenarios is further increased, we found it difficult to compare their performance due to insufficient computational resources.
 For $\Gamma \leq \num{100000}$, the number of outer scenarios is fixed at $M = \num{100000}$, and only the number of inner replications is varied.
@@
 This observation resonates with the best possible convergence rate of a standard nested simulation procedure in~\cite{gordy2010nested}.
-Hence, in practice, we suggest to run the single-stage procedure with a moderate number of inner replications and a large number of outer scenarios to achieve a high level of accuracy with a reasonable computational cost.
+Hence, in practice, we suggest running the single-stage procedure with a moderate number of inner replications and a large number of outer scenarios to achieve a high level of accuracy with a reasonable computational cost.
 
@@
 In our numerical experiments, a LSTM metamodel is resilient to a high level of noise in training labels and is able to make accurate predictions. 
-This is a an encouraging evidence that DNN metamodels can be used to improve the efficiency of Monte Carlo simulation for quantitative risk management tasks that require a computational-expensive simulation procedure.
+This is an encouraging evidence that DNN metamodels can be used to improve the efficiency of Monte Carlo simulation for quantitative risk management tasks that require a computational-expensive simulation procedure.
 We propose two nested simulation procedures that use DNN metamodels to estimate risk measures of the hedging loss of a VA contract.
@@
 DNN metamodels are known to suffer from over-fitting when the number of training samples is limited.
-In the next chapter, we will extend our study to transfer learning and show that DNN metamodels trained on a existing VA contract can be transferred to a new VA contract with different market conditions.
+In the next chapter, we will extend our study to transfer learning and show that DNN metamodels trained on an existing VA contract can be transferred to a new VA contract with different market conditions.
 We hypothesize that the DNN metamodel will generalize well to the new VA contract, and the computational savings from transfer learning will be substantial.

### 2025-02-20 project3/draft.tex
w

@@
 TL starts by training a metamodel $f_{\text{So}}$ on the source domain $\mathcal{D}_{\text{So}}$.
-For both the two-stage procedure and the single-stage procedure in Chapter~\ref{chap:project2}, $f_{\text{So}}$ is approximated by an LSTM network $f_{\text{So}}(\cdot ; \theta_{\text{So}})$, where the parameters of the LSTM network, $\theta_{\text{So}}$ are learned by minimizing a MSE loss function on the source domain.
+For both the two-stage procedure and the single-stage procedure in Chapter~\ref{chap:project2}, $f_{\text{So}}$ is approximated by an LSTM network $f_{\text{So}}(\cdot ; \theta_{\text{So}})$, where the parameters of the LSTM network, $\theta_{\text{So}}$ are learned by minimizing an MSE loss function on the source domain.
 Then the pre-trained parameters $\theta_{\text{So}}$ to inform the learning of $f_{\text{Ta}}(\cdot ; \theta_{\text{Ta}})$ on the target domain $\mathcal{D}_{\text{Ta}}$.
@@
 \begin{algorithmic}[1] \label{alg3:fineTuning}
-    \STATE \textbf{Input:} source dataset $\mathcal{D}_{\text{So}} = \{(X_{\text{So}}^{(i)}, L_{\text{So}}^{(i)})\}_{i=1}^{M_{\text{So}}}$ , target dataset $\mathcal{D}_{\text{Ta}} = \{(X_{\text{Ta}}^{(i)}, L_{\text{Ta}}^{(i)})\}_{i=1}^{M_{\text{Ta}}}$, learning rate $\alpha_{\text{So}}$ and smaller learning rate $\alpha_{\text{Ta}}$.
+    \STATE \textbf{Input:} source dataset $\mathcal{D}_{\text{So}} = \{(X_{\text{So}}^{(i)}, L_{\text{So}}^{(i)})\}_{i=1}^{M_{\text{So}}}$, target dataset $\mathcal{D}_{\text{Ta}} = \{(X_{\text{Ta}}^{(i)}, L_{\text{Ta}}^{(i)})\}_{i=1}^{M_{\text{Ta}}}$, learning rate $\alpha_{\text{So}}$ and smaller learning rate $\alpha_{\text{Ta}}$.
 
@@
 Suppose that we aim at developing an LSTM metamodel for a GMWB contract under a stochastic volatility asset model, but we have limited data for this simulation scheme. 
-For multi-task learning, we can select related nested simulation simulation procedures with relatively abundant data, such as:
+For multi-task learning, we can select related nested simulation procedures with relatively abundant data, such as:
 
@@
 The source task is hedging a GMMB contract on RS-GBM with no lapse, and the target task is hedging the same GMMB contract but with a static lapse.
-The simulation data for the target task is generated with the same nested simulation simulation procedure as the source task, except for the lapse feature.
+The simulation data for the target task is generated with the same nested simulation procedure as the source task, except for the lapse feature.
 Figure~\ref{subfig3-1:extensive} demonstrates the performance of the LSTM metamodel trained extensively only on the target task by using $M_{\text{TA}} = 50,\!000$ samples, which serves as a benchmark for this study.
@@
 TL techniques like fine-tuning and layer freezing can help mitigate these challenges.
-Figure~\ref{subfig3-1:fineTuning} shows the results of fine-tuning a pretrained metamodel on RS-GBM with no lapse.
+Figure~\ref{subfig3-1:fineTuning} shows the results of fine-tuning a pre-trained metamodel on RS-GBM with no lapse.
 Fine-tuning offers a noticeable improvement over training without TL by reducing the instability in the validation MSE. 
@@
 We further investigate the performance of fine-tuning on the target task of metamodeling GMMB contract losses on RS-GBM with a dynamic lapse. 
-The source tasks used for pretraining are GMMB contracts on RS-GBM with no lapse and a static lapse, respectively. 
+The source tasks used for pre-training are GMMB contracts on RS-GBM with no lapse and a static lapse, respectively. 
 Figure~\ref{fig3:figure2} displays the learning curves of the LSTM metamodels fine-tuned from these two distinct source tasks.
@@
 
-Figure~\ref{subfig3-4:extensive} presents the performance of an extensively trained LSTM metamodel on the target task using $\num{50000}$ samples, serving as a benchmark of best metamodel performance.
+Figure~\ref{subfig3-4:extensive} presents the performance of an extensively trained LSTM metamodel on the target task using $\num{50000}$ samples, serving as a benchmark of the best metamodel performance.
 The extensively trained metamodel achieves a low validation error and demonstrates stable convergence due to having enough training samples. 
@@
         \toprule
-        \textbf{Model} & \textbf{Training Samples} & \textbf{Training MSE} & \textbf{True MSE} \\
+        \textbf{Model} & \textbf{Training samples} & \textbf{Training MSE} & \textbf{True MSE} \\
         \midrule
         Without TL & $\num{2000}$ & $0.3588$ & $0.4188$ \\
-        Fine Tuning & $\num{2000}$ & $0.1690$ & $0.1780$ \\
-        Layer Freezing & $\num{2000}$ & $0.1828$ & $0.2295$ \\
-        Extensive Training & $\num{50000}$ & $0.0853$ & $0.0726$ \\
+        Fine-tuning & $\num{2000}$ & $0.1690$ & $0.1780$ \\
+        Layer freezing & $\num{2000}$ & $0.1828$ & $0.2295$ \\
+        Extensive training & $\num{50000}$ & $0.0853$ & $0.0726$ \\
         \bottomrule
@@
         \includegraphics[width=\textwidth]{./project3/figures/figure4_1.png}
-        \caption{Tail scenarios identification} 
+        \caption{Identifying Tail scenarios} 
         \label{subfig3-4-1:tail}
@@
         \includegraphics[width=\textwidth]{./project3/figures/figure4_2.png}
-        \caption{$95\%$-CVaR prediction}
+        \caption{$95\%$-CVaR predictions}
         \label{subfig3-4-2:CVaR}
@@
 Multi-task learning enables the LSTM metamodels to learn shared representations across related VA contracts.
-In this section, we examine the performance of multitask learning applied to two types of VAs, GMMB and GMWB with the dynamic lapse rates.
+In this section, we examine the performance of multi-task learning applied to two types of VAs, GMMB and GMWB with the dynamic lapse rates.
 The simulation datasets contain $2,\!000$ samples for each contract type, and the LSTM metamodels are trained using multi-task learning. 
@@
 We use individual task training as a baseline for comparison, where the LSTM metamodels are trained separately on the GMMB and GMWB contracts.
-The objective is to assess how multitask learning can improve the training efficiency and performance of both products compared to individual task training.
+The objective is to assess how multi-task learning can improve the training efficiency and performance of both products compared to individual task training.
 
@@
         \includegraphics[width=\textwidth]{./project3/figures/figure5b.png}
-        \caption{Task performance with multitask training}
+        \caption{Task performance with multi-task training}
         \label{subfig3-5:fineTuning}
@@
 
-Figure~\ref{fig3:figure5} compares the learning curves for the training of the GMMB and the GMWB, with and without the multitask learning.
-The comparison between the multitask learning (Figures~\ref{subfig3-5:multiTask} and~\ref{subfig3-5:fineTuning}) and the individual task training ((Figures~\ref{subfig3-5:gmmb_individual} and~\ref{subfig3-5:gmwb_individual})) demonstrates the benefit of the multi-task learning for both products.
+Figure~\ref{fig3:figure5} compares the learning curves for the training of the GMMB and the GMWB, with and without the multi-task learning.
+The comparison between the mult-itask learning (Figures~\ref{subfig3-5:multiTask} and~\ref{subfig3-5:fineTuning}) and the individual task training ((Figures~\ref{subfig3-5:gmmb_individual} and~\ref{subfig3-5:gmwb_individual})) demonstrates the benefit of the multi-task learning for both products.
 
@@
 For the GMWB, the multi-task learning framework helps to stablize the training process.
-The shared LSTM layers in the multitask model are able to capture common temporal patterns and dynamics, which benefits both the GMMB and the GMWB when the training samples are scarce.
+The shared LSTM layers in the multi-task model are able to capture common temporal patterns and dynamics, which benefits both the GMMB and the GMWB when the training samples are scarce.
 
@@
 %         \includegraphics[width=\textwidth]{./project3/figures/figure5b.png}
-%         \caption{Task performance with multitask training}
+%         \caption{Task performance with multi-task training}
 %         \label{subfig3-6:fineTuning}

### 2025-02-20 conclusion.tex
hey

@@
 
-The thesis is an attempt to bridge the gap between traditional simulation schemes and modern machine learning techniques in the context of financial risk management.
+This thesis is an attempt to bridge the gap between traditional simulation schemes and modern machine learning techniques in the context of financial risk management.
 By bridging advanced machine learning techniques with financial risk management practices, this thesis contributes to the development of more efficient, adaptable, and robust methodologies that are essential in the rapidly evolving landscape of quantitative finance and actuarial science.

### 2025-02-20 introduction.tex
hey

@@
 Our numerical experiments show that a judicious use of transfer learning can lead to substantially better metamodels than those trained from scratch.
-Chapter~\ref{chap:conclusion} concludes the thesis and discusses potential future research directions.
+Chapter~\ref{chap:conclusion} concludes this thesis and discusses potential future research directions.
 Chapter~\ref{chap:futureWork} discusses the future directions of applying deep reinforcement learning in the dynamic hedging of VA contracts.
@@
 Our approach enables rapid deployment in changing environments.
-Finally, Chapter~\ref{chap:conclusion} summarizes the key findings of the thesis and discusses future research directions that involve the robost use of neural networks in quantitative risk management applications.
+Finally, Chapter~\ref{chap:conclusion} summarizes the key findings of this thesis and discusses future research directions that involve the robost use of neural networks in quantitative risk management applications.

### 2025-02-21 conclusion.tex
12

@@
 
-In this thesis, we have explored the application of nested simulation procedures in the risk management of financial derivatives and insurance products, with a particular focus on variable annuity contracts featuring the Guaranteed Minimum Maturity Benefits and the Guaranteed Minimum Withdrawal Benefits.
-Recognizing the computational challenges inherent in the standard nested simulation procedure, especially when estimating tail risk measures for complex financial products, we proposed an innovative approach that integrates machine learning-based metamodels into the nested simulation framework.
+In this thesis, we have explored the application of nested simulation procedures in the risk management of financial derivatives and insurance products, with a particular focus on variable annuity contracts featuring Guaranteed Minimum Maturity Benefits and Guaranteed Minimum Withdrawal Benefits.
+Recognizing the computational challenges inherent in the standard nested simulation procedure, especially when estimating tail risk measures for complex financial products, we have proposed an innovative approach that integrates machine learning-based metamodels into the nested simulation framework.
 
-We have shown that the nested simulation framework can be used to efficiently estimate the risk measures of complex financial products, such as variable annuities, by combining machine learning-based metamodels with nested simulations.
+We have shown that the nested simulation framework can be used to efficiently estimate risk measures of complex financial products, such as variable annuities, by combining machine learning-based metamodels with nested simulations.
 
 Our primary contribution lies in the development and implementation of long short-term memory networks as metamodels for the inner simulations within the nested simulation procedure. 
-By employing LSTMs, we effectively approximated the contract losses associated with dynamic hedging strategies under various market scenarios. 
-This approach substantially reduced the computational complexity while maintaining high levels of accuracy in risk estimation. 
-The LSTM metamodels captured the temporal dependencies and nonlinear relationships present in financial time series data, enabling efficient estimation of tail risk measures.
+By employing LSTMs, we have effectively approximated the contract losses associated with dynamic hedging strategies under various market scenarios. 
+This approach has substantially reduced the computational complexity of the standard nested simulation procedure while maintaining high levels of accuracy in risk estimation. 
+The LSTM metamodels have captured the temporal dependencies and nonlinear relationships present in financial time series data, enabling efficient estimation of tail risk measures.
 
-Through the extensive numerical experiments and sensitivity analysis, we demonstrated that our LSTM-based nested simulation procedure provides accurate and computationally efficient estimates of the tail risk associated with VA contracts.
-The results showed that the metamodels could effectively replace the computationally intensive inner simulations, reducing the overall runtime without compromising the precision of risk assessments.
+Through extensive numerical experiments and sensitivity analysis, we have demonstrated that our LSTM-based nested simulation procedure provides accurate and computationally efficient estimates of the tail risk associated with VA contracts.
+The results have shown that the metamodels can effectively replace the computationally intensive inner simulations in the standard nested simulation procedure.
+This approachhas reduced the overall runtime without compromising the precision of risk assessments.
 This efficiency gain is particularly valuable for insurers and financial institutions that require timely and accurate risk evaluations to meet regulatory requirements and make informed and timely risk management decisions.
 
-Additionally, we investigated the feasibility of our approach to changing market conditions and different VA contract features. 
-By incorporating the transfer learning techniques, we enabled rapid adaptation of the LSTM metamodels to new contracts and evolving market dynamics. 
+Additionally, we have investigated the feasibility of our approach under changing market conditions and different VA contract features. 
+By incorporating transfer learning techniques, we have enabled rapid adaptation of the LSTM metamodels to new contracts and evolving market dynamics. 
 This aspect of our research highlights the potential for machine learning models to not only improve computational efficiency but also enhance the flexibility and responsiveness of risk management practices in the face of market volatility.
@@
 This thesis is an attempt to bridge the gap between traditional simulation schemes and modern machine learning techniques in the context of financial risk management.
-By bridging advanced machine learning techniques with financial risk management practices, this thesis contributes to the development of more efficient, adaptable, and robust methodologies that are essential in the rapidly evolving landscape of quantitative finance and actuarial science.
+By combining advanced machine learning techniques with financial risk management practices, this thesis contributes to the development of more efficient, adaptable, and robust methodologies that are essential in the rapidly evolving landscape of quantitative finance and actuarial science.

### 2025-02-21 futureWork/rlHedging.tex
w
edited

@@
 Section~\ref{sec:PPO} introduces the proximal policy optimization algorithm and its application to the hedging of VAs.
-Section~\ref{sec:TL} presents the transfer learning framework for accelerating the training of DRL agents in the dynamic hedging of VAs.
-Section~\ref{sec:experiments} presents the experimental setup and results, comparing the performance of transfer learning with training from scratch.
 Finally, Section~\ref{sec:FutureDirections} concludes the chapter and discusses future research directions.
@@
 The GMWB payout is implicitly included in $F_t\eta_n$.
-Both Equation~\ref{eq3:lossGMMB} and Equation~\ref{eq3:lossGMWB} neglect the transaction cost to liquidate the hedge portfolio at maturity.
+Both Equation~\eqref{eq3:lossGMMB} and Equation~\eqref{eq3:lossGMWB} neglect the transaction cost to liquidate the hedge portfolio at maturity.
 The discrete-time hedging problem of VAs can be conveniently formulated as an MDP, where the states, actions, transition probabilities, policies, and rewards are defined as follows.
@@
 The transition probabilities $\mathcal{P}$ represent the probability of transitioning from one state to another from taking an action.
-In our setup, the transition probabilities are fully determined by Equation~\ref{eq3:lapse}, Equation~\ref{eq3:subaccount}, Equation~\ref{eq3:guarantee}, and Equation~\ref{eq3:withdrawal}.
+In our setup, the transition probabilities are fully determined by Equation~\eqref{eq3:lapse}, Equation~\eqref{eq3:subaccount}, Equation~\eqref{eq3:guarantee}, and Equation~\eqref{eq3:withdrawal}.
 Let $\mathcal{P}(\mathbf{s}_{t+1}|\mathbf{s}_t, a_t)$ be the probability of transitioning from state $\mathbf{s}_t$ to state $\mathbf{s}_{t+1}$ due to action $a_t$.
@@
 where $R_t$ is the term reward received by the agent at time $t$, and the discount factor $\gamma$ is conveniently inherited from the risk-free rate $r$. 
-In hedging, the term reward $R_t$ should be derived from Equation~\ref{eq3:lossGMMB} and Equation~\ref{eq3:lossGMWB} to represent the performance of the hedging policy, i.e., how closely the hedging portfolio tracks the liability.
+In hedging, the term reward $R_t$ should be derived from Equation~\eqref{eq3:lossGMMB} and Equation~\eqref{eq3:lossGMWB} to represent the performance of the hedging policy, i.e., how closely the hedging portfolio tracks the liability.
 For the GMWB, we propose a term reward formulation that encourages the agent to maximize the expected reward with low hedging errors and transaction costs:
@@
 \end{equation}
-The reward function of the GMWB directly links to the time-$t$ loss of a GMWB contract as in Equation~\ref{eq3:lossGMWB}.
+The reward function of the GMWB directly links to the time-$t$ loss of a GMWB contract as in Equation~\eqref{eq3:lossGMWB}.
 The GMMB loss consists of an additional payoff at maturity $T$, thus its term reward is formulated as:
@@
 
-In a recurrent PPO with LSTM, the policy and reward function remain the same but with the new state representation in Equation~\ref{eq3:stateRNN}.
+In a recurrent PPO with LSTM, the policy and reward function remain the same but with the new state representation in Equation~\eqref{eq3:stateRNN}.
 Instead of following the standard PPO algorithm, the agent uses the recurrent PPO algorithm to learn an optimal policy for hedging VAs.

### 2025-02-21 introduction.tex
edited

@@
 The number of inner simulations required to achieve a desired level of accuracy for each outer scenario can be large.
-Metamodeling techniques that approximate the inner simulation model can be used to reduce the computational burden of a nested simulation.
+Metamodeling techniques can reduce the computational burden of nested simulations by approximating the inner simulation model.
 Metamodels are statistical models that approximate the output of a complex simulation model as a function of its input parameters.
 In this thesis, we focus on metamodels of the inner simulation models in nested simulation procedures for risk management applications of financial derivatives and VA contracts.
-Two interesting problems that require nested simulation are considered in this thesis:  
+This thesis addresses two key problems that necessitate nested simulation:
 \begin{itemize}
@@
 In our numerical experiment, the best neural network metamodel surpasses the state-of-the-art metamodels in tail identification, and it leads to substantial computational savings.
-Chapter~\ref{chap:project2} also conducts sensitivity testing on the neural network metamodel. 
+Chapter~\ref{chap:project2 } also includes sensitivity testing of the neural network metamodel.
 We argue that for estimating tail risk measures of VA contract losses, the inner simulation can be replaced entirely by a suitable metamodel.
 Eliminating the inner simulation can lead to more substantial computational savings without affecting estimation quality.
-In the case of requiring extensive inner simulations for regulatory purposes, effective budget allocations can help achieve improved estimator quality with the same computational budget.
+When extensive inner simulations are required for regulatory purposes, effective budget allocation can improve estimator accuracy without increasing the computational budget.
 In practice, underlying assumptions of the simulation model are subject to change, and new VA contracts are issued with different contract specifications.
@@
 Chapter~\ref{chap:conclusion} concludes this thesis and discusses potential future research directions.
-Chapter~\ref{chap:futureWork} discusses the future directions of applying deep reinforcement learning in the dynamic hedging of VA contracts.
+Chapter~\ref{chap:futureWork } explores future applications of deep reinforcement learning in the dynamic hedging of VA contracts.
 
@@
 
-VA contracts are index-linked insurance products that offer policyholders an upside potential of equity markets while providing guarantees that protect against a downside risk.
+VA contracts are index-linked insurance products that offer policyholders the upside potential of equity markets while providing guarantees against downside risk.
 These products have gained a substantial amount of interest as they address the needs of individuals seeking both wealth accumulation and financial security, especially in the context of retirement planning.
-The most interesting feature of VAs is embedded guarantees that ensure a specified minimum benefit regardless of market performance.
+The key feature of VAs is their embedded guarantees, which ensure a specified minimum benefit regardless of market performance.
 Two VA contracts that are most relevant to this thesis are Guaranteed Minimum Maturity Benefit (GMMB) and the Guaranteed Minimum Withdrawal Benefit (GMWB).
@@
 The GMWB allows policyholders to withdraw a specified percentage of their benefit base each period during the contract horizon~\citep{hardy2003investment}.
-While these guarantees enhance the attractiveness of VAs to consumers by offering protection against market downturns and ensuring income stability, they introduce a substantial amount of financial risks to insurers.
+While these guarantees make VAs more attractive to consumers by offering protection against market downturns and ensuring income stability, they also introduce significant financial risks for insurers.
 The embedded options within GMMBs and GMWBs expose insurers to market risk, longevity risk, and policyholder behavior risk.
@@
 One of the primary risk management strategies employed by insurers to mitigate the financial risks associated with VAs is dynamic hedging.
-Dynamic hedging involves a frequent adjustment of a portfolio of financial instruments to offset changes in the value of the guarantees due to market movements~\citep{hull2016options}. 
-This strategy aims to neutralize the sensitivity of the insurer's liability to market fluctuations by constructing a hedging portfolio that replicates the cash flows of the guarantees.
+Dynamic hedging involves frequent adjustments to a portfolio of financial instruments to offset changes in guarantee values due to market movements~\citep{hull2016options}.
+This strategy aims to neutralize the insurer's liability sensitivity to market fluctuations by constructing a hedging portfolio that replicates the guarantees' cash flows.
 However, dynamic hedging introduces complexity in estimating the insurer's overall risk exposure.
@@
 It requires a stochastic modeling of the financial market and an accurate loss estimation of the hedging portfolio under different market scenarios.
-Nested simulation has emerged as a robust method for estimating risk measures in such complex settings~\citep{gordy2010nested}.
+Nested simulation is a robust method for estimating risk measures in complex settings~\citep{gordy2010nested}.
 In nested simulation, an outer simulation generates a set of market scenarios over the contract horizon, while an inner simulation estimates the contract loss in each scenario.
@@
 
-Despite its robustness, nested simulation is computationally intensive, often requiring a substantial amount of computational resources and time. 
-Each scenario in the outer simulation requires numerous inner simulations to accurately estimate contract loss. 
+Despite its robustness, nested simulation is computationally intensive, often demanding significant computational resources and time.
+Each outer simulation scenario requires numerous inner simulations to accurately estimate contract loss.
 This computational burden poses practical limitations, especially when a high degree of precision in tail risk estimation is required.
@@
 
-Metamodeling, also known as surrogate modeling, is a technique used to approximate complex simulation models with simpler, computationally efficient models. 
-In the context of Monte Carlo simulations, metamodels are models of models that aim at reducing computational costs by creating an approximate model that can quickly predict simulation outputs based on input variables~\citep{kleijnen2018design}.
+Metamodeling, or surrogate modeling, approximates complex simulation models with simpler, computationally efficient models.
+In Monte Carlo simulations, metamodels reduce computational costs by approximating simulation outputs based on input variables~\citep{kleijnen2018design}.
 This section introduces metamodeling for a Monte Carlo simulation, elaborates on its methodologies, and highlights its importance in practical applications.
@@
 Learning from a set of simulation runs, the metamodel can generalize and predict outputs for new inputs without running the full simulation.
-Metamodeling is particularly useful when the simulation model is computationally expensive. 
-By replacing the simulation model with a metamodel, the computational cost of evaluating the model can be substantially reduced. 
+Metamodeling is especially useful for computationally expensive simulation models.
+Replacing the simulation model with a metamodel significantly reduces computational costs.
 This allows for faster convergence of simulation-based estimators.
@@
 The development of advanced machine learning models and deep learning techniques has enhanced metamodeling approaches for Monte Carlo simulations, especially in high-dimensional and complex problem settings.
-Example use cases for machine learning include~\cite{jin2020deep},~\cite{tang2020deep}, and~\cite{rosen2012metamodeling}.
+Examples of machine learning applications include~\cite{jin2020deep},~\cite{tang2020deep}, and~\cite{rosen2012metamodeling}.
 These methods offer powerful tools for capturing intricate patterns and nonlinear relationships that traditional metamodeling techniques might struggle to model effectively.
@@
 
-Supervised learning is a fundamental approach in machine learning where the algorithm learns a mapping from inputs to outputs based on example input-output pairs \cite{galton1886regression}. 
+Supervised learning is a fundamental approach in machine learning where the algorithm learns a mapping from inputs to outputs based on example input-output pairs~\cite{galton1886regression}.
 In this paradigm, a model is trained on a labeled dataset, which means that each training example is associated with an output label or value.
 The goal of a supervised learning paradigm is to learn a general rule that maps inputs (also known as features) to outputs (also known as targets), enabling the model to make accurate predictions on new, unseen data.
-Supervised learning can be carried out in two domains of applications.
-These are:
-
+Supervised learning is usually applied in two domains:
 \begin{itemize} 
@@
 This thesis focuses on regression models for risk management applications, where the goal is to predict a continuous target variable based on one or more input features.
-Given a dataset of $n$ observations $\{(x_1, y_1), (x_2, y_2), \ldots, (x_n, y_n)\}$, where $x_i \in \mathbb{R}^d$ is the $d$-dimensional input feature vector, and $y_i \in \mathbb{R}$ is the target variable, a supervised learning algorithm aims at learning a function $f(;\theta): \mathbb{R}^d \rightarrow \mathbb{R}$ that best predicts the target variable $y$ given the input vector of features $x$ with a vector of function parameters $\theta$.
+Given a dataset of $n$ observations $\{(x_1, y_1), (x_2, y_2), \ldots, (x_n, y_n)\}$, where $x_i \in \mathbb{R}^d$ is the $d$-dimensional input feature vector, and $y_i \in \mathbb{R}$ is the target variable, a supervised learning algorithm aims at learning a function $f(x;\theta): \mathbb{R}^d \mapsto \mathbb{R}$ that to predict $y$ from $x$ using parameters $\theta$.
 
@@
 Despite the differences in their functional forms, all supervised learning models can be evaluated on a similar set of metrics.
-The learning process is referred to as training, which involves minimizing a loss function $l(f(x; \theta),y)$ over the training data, which quantifies the closeness of the difference between the predicted labels and the training labels.
+The learning process, called training, minimizes a loss function $l(f(x; \theta),y)$ over the training data, which quantifies the difference between predicted and actual labels.
 A common loss function for regression problems is a quadratic loss function in the form of a mean squared error (MSE):
@@
 For a MSE loss metric, the optimal regression coefficients can be obtained by solving the normal equations.
-Parametric regression is a powerful tool for modeling linear relationships where the basis functions are known from expert knowledge for explicit feature engineering techniques~\citep{hastie2009elements}.
+Parametric regression is powerful for modeling linear relationships when basis functions are known from expert knowledge or feature engineering~\citep{hastie2009elements}.
 These techniques utilize predefined functional forms to model the relationship between a set of independent variables and a dependent variable.
@@
 In addition, the computational cost associated with non-parametric methods often grows rapidly with the number of dimensions.
-Cross validation and distance calculation are two computationally expensive operations that are often required for a non-parametric regression.
-These drawbacks make non-parametric regression methods impractical for modeling high-dimensional large-scale datasets.
+Cross-validation and distance calculations are computationally expensive for non-parametric regression.
+These drawbacks render non-parametric regression impractical for high-dimensional, large-scale datasets.
 
@@
 The progression from traditional parametric and non-parametric regression methods to neural network architectures has been driven by the need to model increasingly complex and high-dimensional data.
-Neural networks have emerged as powerful tools capable of overcoming many limitations of traditional regression methods. 
+Neural networks are powerful tools that overcome many limitations of traditional regression methods.
 They can learn complex, non-linear relationships in data without the need for explicit feature engineering.
@@
 where $\theta = (\theta^{(1)}, \theta^{(2)}, \ldots, \theta^{(k)})$ are trainable parameters of the neural network, $f^{(i)}$ is an $i$-th layer of the neural network, $x$ is an input feature vector, $f^{(1)}(x;\theta^{(1)}) = x$, $f^{(k)}$ is an output layer, $k$ is a number of layers, and $f^{(i)}$ is an output of the $i$-th layer.
-To move from a lower layer to a higher layer, i.e., from layer $i-1$ to layer $i$,
-
+To transition from layer $i-1$ to layer $i$,
 \begin{equation} \label{eq:neural}
@@
 where $a^{(i)}$ are nonlinear activation functions, $\theta^{(i)} = (\beta_0^{(i)}, \dots, \beta_p^{(i)})$ are trainable parameters of the $i$-th layer, and $p_i$ is a number of neurons in the previous layer.
-Equation~\ref{eq:neural} represents a single neuron in a neural network, which applies a linear transformation to the input followed by a non-linear activation function. 
-The linear transformation is similar to the linear regression model in Equation~\ref{eq:regression}, but the non-linear activation function allows the neural network to model complex, non-linear relationships in the data.
+Equation~\eqref{eq:neural} represents a single neuron in a neural network, which applies a linear transformation to the input followed by a non-linear activation function.
+The linear transformation is similar to the linear regression model in Equation~\eqref{eq:regression}, but the non-linear activation function allows the neural network to model complex, non-linear relationships in the data.
 The FNN is tuned by adjusting the trainable parameters $\theta$ while fixing the activation functions $a^{(i)}$.
 A typical choice for the activation function is the rectified linear unit (ReLU), which is defined as $a(z) = \max(0, z)$~\citep{nair2010rectified}.
-The choice of an activation function also plays a crucial role in the training of neural networks.
+The activation function choice is crucial for training neural networks.
 While sigmoid and hyperbolic tangent functions were popular in early neural networks, ReLU has become the default activation function for deep networks due to its ability to mitigate the vanishing gradient problem and promote sparse activations~\citep{lecun2015deep}.
@@
 
-To address these issues, a long short-term memory (LSTM) network was developed by \citet{hochreiter1997long}.
+To address these issues, a long short-term memory (LSTM) network was developed by~\citet{hochreiter1997long}.
 It is a specialized form of RNNs designed to capture long-term dependencies more effectively with the help of RNN memory cells and gating mechanisms.

### 2025-02-21 project1/nsSurvey.tex
edited

@@
 %======================================================================
-\chapter{Nested Simulation Procedures in Financial Engineering: A Selected Review} \label{chap:project1}
+\chapter{Nested Simulation Procedures in Financial Engineering: A Selected Review}\label{chap:project1}
 %======================================================================
@@
 The nested simulation procedure is computationally expensive due to its nested structure. 
-Given a fixed computational budget, the nested simulation procedure has to make a trade-off between the number of outer scenarios and the number of inner replications.
-~\cite{gordy2010nested} are the first to analyze and propose the optimal budget allocation of a standard nested simulation procedure. 
+Given a fixed computational budget, the nested simulation procedure should balance the number of outer scenarios and the number of inner replications to maximize computational efficiency.
+\cite{gordy2010nested} first analyzed and proposed an optimal budget allocation for a standard nested simulation procedure.
 The term \textit{standard} refers to using a standard MC estimator, the sample mean of the inner replications to estimate a scenario-wise portfolio loss for an outer scenario.
-~\cite{gordy2010nested} investigate an optimal budget allocation for a standard nested simulation procedure with respect to the MSE of the estimated risk measure.
-
-The standard nested simulation procedure is computationally expensive with a somewhat wasteful use of the simulation budget, as only the inner replications from the same outer scenario are used in estimating the scenario-wise portfolio loss for that outer scenario.
+\cite{gordy2010nested} investigate an optimal budget allocation for a standard nested simulation procedure with respect to the MSE of the estimated risk measure.
+
+The standard nested simulation procedure is computationally expensive with a wasteful use of the simulation budget, as only the inner replications from the same outer scenario are used in estimating the scenario-wise portfolio loss for that outer scenario.
 Subsequent research efforts have been made to improve the efficiency of nested simulation procedures by using inner replications from other outer scenarios.
 This is referred to as pooling.
-Different methods pool in different ways, either through a trained supervised learning metamodel or through predefined likelihood ratio weights.
-~\cite{broadie2015risk} propose a regression-based nested simulation procedure, which uses a trained regression metamodel to estimate the scenario-wise portfolio loss for an outer scenario by pooling the inner replications from all outer scenarios.
-For certain forms of risk measures,~\cite{broadie2015risk} show that it is optimal to allocate all simulation budget to the outer level simulation, and the inner replication should be kept to a minimum of $1$.
+Different methods pool inner replications differently, using either a trained supervised learning metamodel or predefined likelihood ratio weights.
+\cite{broadie2015risk} propose a regression-based nested simulation procedure, which uses a trained regression metamodel to estimate the scenario-wise portfolio loss for an outer scenario by pooling the inner replications from all outer scenarios.
+For certain risk measures,~\cite{broadie2015risk} show that it’s optimal to allocate the entire simulation budget to outer-level simulations, keeping only 1 inner replication in each outer scenario.
 Similarly,~\cite{hong2017kernel},~\cite{feng2020optimal}, and~\cite{zhang2022sample} use a kernel smoothing model, a likelihood ratio model, and a kernel ridge regression (KRR) model as metamodels to pool the inner replications from all outer scenarios, respectively.
-In simulation studies, this approach of using a model of a simulation model is known as metamodeling, and the models of a simulation model are also referred to as metamodels~\citep{barton1998simulation}.
+In simulation studies, this approach—using a model of a simulation—is called metamodeling, and such models are termed metamodels~\citep{barton1998simulation}.
 Another line of research is a multi-level Monte Carlo (MLMC) method analyzed in~\cite{giles2019multilevel}, which is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest.
@@
 Many procedures have been proposed in the literature, but they are not directly comparable because they use different error metrics, different assumptions, and different numerical examples in their studies.
-Within a common analytical framework, we first summarize and compare their asymptotic rates of convergence.
+Within a common analytical framework, we first summarize and compare the asymptotic convergence rates of these procedures.
 Their asymptotic convergence results are closely examined for their assumptions that guarantee the convergence.
-Furthermore, the existing literature chooses different performance metrics to evaluate the asymptotic convergence of nested simulation procedures.
+Furthermore, the existing literature has chosen different performance metrics to evaluate the asymptotic convergence of nested simulation procedures.
 In this chapter, we discuss the asymptotic convergence in terms of MSE of the estimator, and we provide a comprehensive comparison of their convergence rates and critical assumptions.
@@
 
-\section{Problem Formulation} \label{sec1:problem-formulation}
+\section{Problem Formulation}\label{sec1:problem-formulation}
 
@@
 $$\rho(L) = \mathbb{E}\left[ h(L) \right]$$
-where $h: \mathbb{R} \rightarrow \mathbb{R}$ is a known nonlinear function. 
+where $h: \mathbb{R} \mapsto \mathbb{R}$ is a known nonlinear function. 
 The nested expectation form is a general form that covers many risk measures of interest in financial engineering by varying the function $h$.
@@
 
-\begin{definition} \label{def1:smooth}
-    A function $h: \mathbb{R} \rightarrow \mathbb{R}$ is smooth if it is continuously differentiable up to the $n$-th order for some $n \in \mathbb{N}$, 
+\begin{definition}\label{def1:smooth}
+    A function $h: \mathbb{R} \mapsto \mathbb{R}$ is smooth if it is continuously differentiable up to the $n$-th order for some $n \in \mathbb{N}$, 
     and its $n$-th and $m$-th derivatives are bounded for some $m \in \mathbb{N}$ and $m < n$.
@@
 
-A quadratic tracking error with a benchmark $b$ falls into this category, in which $h(t) = (t - b)^2$.
+A quadratic tracking error with benchmark $b$, where $h(t) = (t - b)^2$, falls into this category.
 In the context of nested estimation for smooth $h$, different procedures require different versions of Definition~\ref{def1:smooth} to specify the smoothness for their convergence analysis.
@@
 
-\begin{definition} \label{def1:lipschitz}
-    A function $h: \mathbb{R} \rightarrow \mathbb{R}$ is Lipschitz continuous with a Lipschitz constant $K$ if for all $t_1, t_2 \in \mathbb{R}$, 
+\begin{definition}\label{def1:lipschitz}
+    A function $h: \mathbb{R} \mapsto \mathbb{R}$ is Lipschitz continuous with a Lipschitz constant $K$ if for all $t_1, t_2 \in \mathbb{R}$, 
     $$|h(t_1) - h(t_2)| \leq K|t_1 - t_2|.$$
@@
 
-A mean excess loss over a threshold $u$ is defined by setting $h(t) = \max\{t - u, 0\}$, which is a special case of a Lipschitz continuous function.
+The mean excess loss over a threshold $u$ is defined by setting $h(t) = \max\{t - u, 0\}$, which is a special case of a Lipschitz continuous function.
 The regression-based nested simulation procedure is the only procedure that performs a theoretical analysis for Lipschitz continuous $h$.
-The other procedures only provide a convergence analysis for the special case, mean excess loss over a threshold $u$.
-
-\begin{definition} \label{def1:indicator}
-    A function $h: \mathbb{R} \rightarrow \mathbb{R}$ is an indicator function if 
+The other procedures only provide a convergence analysis for the special case of mean excess loss over a threshold $u$.
+
+\begin{definition}\label{def1:indicator}
+    A function $h: \mathbb{R} \mapsto \mathbb{R}$ is an indicator function if 
     $$h(t) = \mathbb{I}_{\{t \geq u\}}$$
@@
 
-Other risk measures of interest that are not in the nested expectation form are the Value at Risk (VaR) and the Conditional Value at Risk (CVaR)~\citep{hardy2022quantitative}. 
+Other risk measures of interest not in the nested expectation form include Value at Risk (VaR) and Conditional Value at Risk (CVaR)~\citep{hardy2022quantitative}. 
 The $\alpha$-VaR of $L$ is defined as
-\begin{equation} \label{eq1:var}
+\begin{equation}\label{eq1:var}
     \mbox{VaR}_\alpha(L) = q_\alpha = \inf \left\{ q: \Pr(L\leq q) \geq \alpha \right\}.
@@
 The $\alpha$-CVaR of $L$ is defined as
-\begin{equation} \label{eq1:cvar}
+\begin{equation}\label{eq1:cvar}
     \mbox{CVaR}_\alpha(L) =\frac{1}{1-\alpha} \int_{\alpha}^{1} q_v dv. 
 \end{equation}
-Other names of CVaR include Conditional Tail Expectation (CTE), Tail Value-at-Risk (TailVaR), and Expected Shortfall (ES).
+In the literature, CVaR are also known as Conditional Tail Expectation (CTE), Tail Value-at-Risk (TailVaR), and Expected Shortfall (ES).
 
@@
 Given scenario $i$, the $Y_{ij}$ are conditionally i.i.d.
-Let $\Gamma = M \cdot N$ denote a total simulation budget, $f_X(x)$ denote a density of $X$, and $\mathbf{X} = (X_1, \dots, X_M)$ denote a vector of outer scenarios.
+Let $\Gamma = M \cdot N$ denote the total simulation budget, $f_X(x)$ denote the density of $X$, and $\mathbf{X} = (X_1, \dots, X_M)$ denote the vector of outer scenarios.
 
 The standard nested simulation procedure estimates $L_i = L(X_i)$ with a standard MC estimator 
-
-$$\hat{L}_{N, i} = \frac{1}{N} \sum_{j=1}^N Y_{ij}; ~~~ Y_{ij} \sim F_{Y|X_i} $$
-
-Let $\hat{L}_{(i)}, \dots, \hat{L}_{(M)}$ be the order statistics of $\hat{L}_{N, 1}, \dots \hat{L}_{N, M}$. 
+\begin{equation*}
+  \hat{L}_{N, i} = \frac{1}{N} \sum_{j=1}^N Y_{ij}, \quad Y_{ij} \sim F_{Y|X_i}.  
+\end{equation*}
+
+Let $\hat{L}_{(i)}, \dots, \hat{L}_{(M)}$ be the order statistics of $\hat{L}_{N, 1}, \dots, \hat{L}_{N, M}$. 
 The standard nested simulation estimators for different forms of $\rho$ are as follows:
@@
     \item   Nested expectation form:
-            $$\hat{\rho}_{M, N} = \frac{1}{M} \sum_{i=1}^M h(\hat{L}_{N, i}) = \frac{1}{M} \sum_{i=1}^M h(\bar{Y}_{N, i}); ~~~ X_i \sim F_X$$
+            \begin{equation*}
+                \hat{\rho}_{M, N} = \frac{1}{M} \sum_{i=1}^M h(\hat{L}_{N, i}) = \frac{1}{M} \sum_{i=1}^M h(\bar{Y}_{N, i}), \quad X_i \sim F_X.
+            \end{equation*}
     \item   Value at risk (VaR):
-            $$\hat{\rho}_{M, N} = \hat{L}_{(\lceil \alpha M \rceil)}$$
+            \begin{equation*}
+                \hat{\rho}_{M, N} = \hat{L}_{(\lceil \alpha M \rceil)}.
+            \end{equation*}
+
     \item   CVaR:
-            \begin{equation} \label{eq1:cvar-hat}
-                \hat{\rho}_{M, N} = \hat{L}_{(\lceil \alpha M \rceil)} + \frac{1}{(1-\alpha) M} \sum_{i=1}^M \max \{\hat{L}_{N, i} - \hat{L}_{(\lceil \alpha M \rceil)}, 0 \}
+            \begin{equation}\label{eq1:cvar-hat}
+                \hat{\rho}_{M, N} = \hat{L}_{(\lceil \alpha M \rceil)} + \frac{1}{(1-\alpha) M} \sum_{i=1}^M \max \{\hat{L}_{N, i} - \hat{L}_{(\lceil \alpha M \rceil)}, 0 \}.
             \end{equation}
@@
 The MLMC method is particularly useful when the quantity of interest is expensive to evaluate, and the standard MC estimator has a high variance.
-The MLMC method estimates $\rho$ with a MLMC estimator:
+The MLMC method estimates $\rho$ with an MLMC estimator:
 
 \begin{equation*}
-    \hat{\rho}^{\text{MLMC}}_\Gamma = \sum_{\upsilon=0}^{\Upsilon} \left( \frac{1}{M_{\upsilon}} \sum_{i=1}^{M_{\upsilon}} h(\hat{L}_{N_{\upsilon}}(X_{i, \upsilon})) - \frac{1}{M_{\upsilon-1}} \sum_{i=1}^{M_{\upsilon-1}} h(\hat{L}_{N_{\upsilon-1}}(X_{i, \upsilon-1})) \right), ~~~ X_{i, \upsilon} \sim F_X,
+    \hat{\rho}^{\text{MLMC}}_\Gamma = \sum_{\upsilon=0}^{\Upsilon} \left( \frac{1}{M_{\upsilon}} \sum_{i=1}^{M_{\upsilon}} h(\hat{L}_{N_{\upsilon}}(X_{i, \upsilon})) - \frac{1}{M_{\upsilon-1}} \sum_{i=1}^{M_{\upsilon-1}} h(\hat{L}_{N_{\upsilon-1}}(X_{i, \upsilon-1})) \right), \quad X_{i, \upsilon} \sim F_X,
 \end{equation*}
@@
 Applying the analysis of~\cite{giles2015multilevel} in a nested simulation context,~\cite{giles2019multilevel} show that the MLMC method can achieve a similar degree of accuracy as the standard nested simulation procedure with a lower total computational budget.
-The simulation budget $\Gamma$ is a sum of the computational budget at each level, that is to say, $\Gamma = \sum_{\upsilon=0}^{\Upsilon} M_{\upsilon} \cdot N_{\upsilon}$.
+The simulation budget $\Gamma$ is a sum of the computational budget at each level, i.e., $\Gamma = \sum_{\upsilon=0}^{\Upsilon} M_{\upsilon} \cdot N_{\upsilon}$.
 Neither the standard nested simulation procedure nor the MLMC method involves pooling the inner replications from all outer scenarios.
-Pooling enhances sample efficiency, and it is a key feature that distinguishes the more advanced nested simulation procedures from the standard procedure.
+Pooling enhances sample efficiency and distinguishes advanced nested simulation procedures from the standard procedure.
 
@@
 In this metamodeling approach, $L(\cdot)$ can be approximated by $\hat{L}^{\text{SL}}_{M, N}(\cdot)$, which is based on a family of chosen function and observations from the standard nested simulation procedure.
-Consider the observation pairs $(X_i, \hat{L}_{N, i})$ for $i \in \{1, \dots, M\}$ as training data, we can use supervised learning to approximate $L_i$ by $\hat{L}_{M, N}^{\text{SL}}(X_i)$ and to pool the inner replications from all outer scenarios.
-More specifically, $\hat{L}^{\text{SL}}_{M, N}(\cdot)$ denotes a supervised learning model trained on $(X_i, \hat{L}_{N, i})$ for $i \in \{1, \dots, M\}$, which is the simulation output of the standard nested simulation procedure with $M$ outer scenarios and $N$ inner replications.
+Consider the observation pairs $(X_i, \hat{L}_{N, i})$ for $i \in \{1, \dots, M\}$ as training data.
+We can use supervised learning to approximate $L_i$ by $\hat{L}_{M, N}^{\text{SL}}(X_i)$ and to pool the inner replications from all outer scenarios.
+Specifically, $\hat{L}^{\text{SL}}{M, N}(\cdot)$ denotes a supervised learning model trained on $(X_i, \hat{L}{N, i})$ for $i \in {1, \dots, M}$.
+This is the output of the standard nested simulation procedure with $M$ outer scenarios and $N$ inner replications.
 To evaluate the convergence of the supervised learning-based nested simulation procedure, we consider the convergence behavior of the supervised learning model $h(\hat{L}^{\text{SL}}_{M, N}(\cdot))$ to the true risk measure $\rho = h(L(\cdot))$.
 More specifically, we want to study the following quantity
-\begin{equation} \label{eq1:sl-E}
-    \mathbb{E} \left[ h(\hat{L}^{\text{SL}}_{M, N}(X))   \right] - \rho; ~~~ X \sim F_X.
+\begin{equation}\label{eq1:sl-E}
+    \mathbb{E} \left[ h(\hat{L}^{\text{SL}}_{M, N}(X))   \right] - \rho, \quad X \sim F_X.
 \end{equation}
 
-However, studying the expectation in Equation~\ref{eq1:sl-E} is unrealistic, as in practice the risk measure $\rho$ is estimated with a finite number of samples.
+However, studying the expectation in Equation~\eqref{eq1:sl-E} is unrealistic, as in practice the risk measure $\rho$ is estimated with a finite number of samples.
 Using the $M$ \textit{training} samples, a supervised learning-based nested MC estimator of $\rho$ is given by
@@
     \item   Nested expectation form:
-            \begin{equation} \label{eq1:sl-train}
-                \hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = \frac{1}{M} \sum_{i=1}^M h(\hat{L}^{\text{SL}}_{M, N}(X_i)); ~~~ X_i \sim F_X
+            \begin{equation}\label{eq1:sl-train}
+                \hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = \frac{1}{M} \sum_{i=1}^M h(\hat{L}^{\text{SL}}_{M, N}(X_i)), \quad X_i \sim F_X.
             \end{equation}
     \item   VaR:
-            $$\hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = \hat{L}^{\text{SL}}_{(\lceil \alpha M \rceil)}$$
+            \begin{equation*}
+              \hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = \hat{L}^{\text{SL}}_{(\lceil \alpha M \rceil)}.  
+            \end{equation*}
     \item   CVaR:
-            $$\hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = \hat{L}^{\text{SL}}_{(\lceil \alpha M \rceil)} + \frac{1}{(1-\alpha) M} \sum_{i=1}^M \max \{\hat{L}^{\text{SL}}_{M, N}(X_i) - \hat{L}^{\text{SL}}_{(\lceil \alpha M \rceil)}, 0 \}$$
+            \begin{equation*}
+                \hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = \hat{L}^{\text{SL}}_{(\lceil \alpha M \rceil)} + \frac{1}{(1-\alpha) M} \sum_{i=1}^M \max \{\hat{L}^{\text{SL}}_{M, N}(X_i) - \hat{L}^{\text{SL}}_{(\lceil \alpha M \rceil)}, 0 \}.
+            \end{equation*}
 \end{enumerate}
-where $\hat{L}_{(\lceil \alpha M \rceil)}$ is the $\lceil \alpha M \rceil$-th order statistic of $\hat{L}^{\text{SL}}_{M, N}(X_1), \dots, \hat{L}_{M, N}(X_M)$.
-
-After a supervised learning metamodel is trained, it can be used to form predictions for all $X \in \mathcal{X}$.
-Instead of using the same training samples to estimate the risk measure, we can use metamodel predictions for a new set of $M'$ \textit{test} samples of $X$, namely $\tilde{\mathbf{X}} = \tilde{X}_1, \dots, \tilde{X}_{M'}$.
+where $\hat{L}^{\text{SL}}_{(\lceil \alpha M \rceil)}$ is the $\lceil \alpha M \rceil$-th order statistic of $\hat{L}^{\text{SL}}_{M, N}(X_1), \dots, \hat{L}^{\text{SL}}_{M, N}(X_M)$.
+
+After a supervised learning metamodel is trained, it can be used to make predictions for all $X \in \mathcal{X}$.
+Instead of using the same training samples to estimate the risk measure, we can use metamodel predictions for a new set of $M'$ \textit{test} samples of $X$, namely $\tilde{\mathbf{X}} = \{\tilde{X}_1, \dots, \tilde{X}_{M'}\}$.
 The resulting supervised learning-based estimator of $\rho^{\text{SL}, \text{Test}}$ is given by
@@
     \item   Nested expectation form:
-            \begin{equation} \label{eq1:sl-test}
-            \hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = \frac{1}{M'} \sum_{i=1}^{M'} h(\hat{L}^{\text{SL}}_{M, N}(\tilde{X}_i)); ~~~ \tilde{X}_i \sim F_X.
+            \begin{equation}\label{eq1:sl-test}
+            \hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = \frac{1}{M'} \sum_{i=1}^{M'} h(\hat{L}^{\text{SL}}_{M, N}(\tilde{X}_i)), \quad \tilde{X}_i \sim F_X.
             \end{equation}
     \item   VaR:
-            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = \hat{L}^{\text{SL}}_{(\lceil \alpha M' \rceil)}.$$
+            \begin{equation*}
+              \hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = \hat{L}^{\text{SL}}_{(\lceil \alpha M' \rceil)}.  
+            \end{equation*}
     \item   CVaR:
@@
 where $\hat{L}^{\text{SL}}_{(\lceil \alpha M' \rceil)}$ is an $\lceil \alpha M' \rceil$-th order statistic of $\hat{L}^{\text{SL}}_{M, N}(\tilde{X}_1), \dots, \hat{L}^{\text{SL}}_{M, N}(\tilde{X}_{M'})$.
-Note that $\hat{L}^{\text{SL}}_{M, N}(\cdot)$ is the model predictions of a supervised learning model trained on the training samples $(X_1, \hat{L}_{N, 1}), \dots, (X_M, \hat{L}_{N, M})$.
+Note that $\hat{L}^{\text{SL}}_{M, N}(\cdot)$ represents the predictions of a supervised learning model trained on the samples $(X_1, \hat{L}_{N, 1}), \dots, (X_M, \hat{L}_{N, M})$.
 
@@
             where $\Phi$ is a chosen basis, and $\hat{\beta}$ is estimated from the training samples.
-            In~\cite{broadie2015risk}, the convergence analysis is performed on the expectation (Equation~\ref{eq1:sl-E}) and for smooth and Lipschitz continuous $h$. 
+            In~\cite{broadie2015risk}, the convergence analysis is performed on the expectation (Equation~\eqref{eq1:sl-E}) and for smooth and Lipschitz continuous $h$. 
             Connections between the expectation and the MSE are discussed in the Appendix.
@@
             ~\cite{nadaraya1964estimating} and ~\cite{watson1964smooth} originally proposed this kernel smoothing method for a non-parametric regression, and it is widely known in the literature as a Nadaraya-Watson kernel regression.
-            ~\cite{hong2017kernel} provides convergence analysis for metamodel predictions of the training samples (Equation~\ref{eq1:sl-train}), and the convergence analysis is provided for a smooth, a hockey-stick, and an indicator $h$.
+            ~\cite{hong2017kernel} provides convergence analysis for metamodel predictions of the training samples (Equation~\eqref{eq1:sl-train}), and the convergence analysis is provided for smooth, hockey-stick, and indicator $h$.
 
@@
             \end{equation*}
-            where $R_k$ is a Euclidean distance between $X_i$ and its $k$-th nearest neighbor, and $K:\mathbb{R}^d \rightarrow \mathbb{R}$ is a bounded, nonnegative kernel function satisfying 
+            where $R_k$ is a Euclidean distance between $X_i$ and its $k$-th nearest neighbor, and $K:\mathbb{R}^d \mapsto \mathbb{R}$ is a bounded, nonnegative kernel function satisfying 
             \begin{align*}
                 \int K(u) du & = 1, \\
-                K(u) &= 0 ~~~ ~\text{for}~ \|u\| \geq 1,
+                K(u) &= 0, ~~~ ~\text{for}~ \|u\| \geq 1,
             \end{align*}
             where $\|\cdot\|$ is the Euclidean norm, and  $k$ is a number of nearest neighbors to consider.
-            The k-nearest neighbor (KNN) method is implemented as a metamodel for numerical experiments in~\cite{hong2017kernel}, but the convergence analysis is not provided.
+            The kNN method is implemented as a metamodel for numerical experiments in~\cite{hong2017kernel}, but the convergence analysis is not provided.
 
@@
             More specifically, $\Phi$ is a Mat\'ern kernel with a smoothness parameter $\nu$ and a length scale parameter $\upsilon$.
-            ~\cite{wang2022smooth} provides a convergence analysis for the AE (Equation~\ref{eq1:ae}), and the convergence analysis is provided for a smooth, a Lipschitz continuous, and an indicator $h$, VaR, and CVaR.
+            ~\cite{wang2022smooth} provides a convergence analysis for the AE (Equation~\eqref{eq1:ae}), and the convergence analysis is provided for a smooth, a Lipschitz continuous, and an indicator $h$, VaR, and CVaR.
 \end{itemize}
@@
 These supervised learning metamodels approximate the inner simulation model $L(\cdot)$ with functions in the form of $\hat{L}^{\text{SL}}_{M, N}(\cdot)$, and the metamodels are used to pool the inner replications from all outer scenarios to estimate the risk measure $\rho$.
-In the simulation literature, using models to approximate simulation is often referred to as a metamodeling approach, or it is referred to as a metamodel in the financial engineering literature.
+In the simulation literature, using models to approximate simulation models is often called metamodeling; such models are referred to as metamodels.
 Supervised learning models are broadly classified into regression and classification models depending on whether the target variable is continuous or discrete.
@@
 Regression models can be further categorized into parametric and non-parametric regressions.
-Among our interested supervised learning models, a multiple linear regression is a parametric regression model, while kernel smoothing and kernel ridge regression are non-parametric regression models.
-
-We are interested in minimizing the MSE of the supervised learning-based nested simulation estimator with supervised learning $\hat{\rho}^{\text{SL}, \text{Train}}_{M, N}$ and $\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'}$ subject to the total simulation budget $\Gamma$, and we are interested in the order of convergence of the estimator for all nested simulation procedures when the total simulation budget $\Gamma$ approaches infinity.
+Among the supervised learning models we consider, multiple linear regression is parametric, while kernel smoothing and kernel ridge regression are non-parametric.
+
+We aim to minimize the MSE of the supervised learning-based nested simulation estimators $\hat{\rho}^{\text{SL}, \text{Train}}_{M, N}$ and $\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'}$ subject to the total simulation budget $\Gamma$.
+We are also interested in the order of convergence of the estimator for all nested simulation procedures as the total simulation budget $\Gamma$ approaches infinity.
 
@@
 More specifically, the KRR-based nested simulation~\citep{wang2022smooth} provides a convergence analysis in terms of AE.
-\begin{align} \label{eq1:ae}
+\begin{align}\label{eq1:ae}
     & \min_{M, N}  & \text{AE}(\hat{\rho}^{\text{SL}}_{M, N}) = \mathbb{E} \left[ \left| \hat{\rho}^{\text{KRR}}_{M, N} - \rho \right| \right] \nonumber \\
@@
 where $H_{ij} \sim f_{H|X}(\cdot |X_i)$.
-Suppose that one can generate random variable H from some sampling
+Suppose that one can generate random variable $H$ from some sampling
 distribution $f_H$. Then, the likelihood ratio estimator of $\rho$ is given by
 $$\hat{\rho}^{\text{LR}}_{M,N} = \frac{1}{M} \sum_{i=1}^M h(\hat{L}^{\text{LR}}_{N, i}), $$ where the inner replications are pooled by the likelihood ratio weights with
-$$\hat{L}^{\text{LR}}_{N, i} = \frac{1}{N} \sum_{j=1}^N Y(H_j, X_i) \frac{f_{H|X}(H_{j}|X_i)}{f_H(H_{ij})}, \;\;\; H_j \sim f_H, \;\;\; i=1, \dots, M.$$
+$$\hat{L}^{\text{LR}}_{N, i} = \frac{1}{N} \sum_{j=1}^N Y(H_j, X_i) \frac{f_{H|X}(H_{j}|X_i)}{f_H(H_{j})}, \;\;\; H_j \sim f_H, \;\;\; i=1, \dots, M.$$
 In Section~\ref{sec1:sensitivity-option-type}, we implement the likelihood ratio method and share its fast convergence in finite-sample experiments despite the costly computation of the likelihood ratio weights (Section~\ref{sec1:computational-complexity}).
@@
 
-\section{Asymptotic Analysis} \label{sec1:asymptotic-convergence}
+\section{Asymptotic Analysis}\label{sec1:asymptotic-convergence}
 In the first part of this section, we summarize the existing asymptotic convergence results of the nested simulation procedures in the literature, and we compare their critical assumptions that guarantee the convergence.
-The remaining of this section aims to fill the gap in the literature by offering the following steps:
+The remainder of this section aims to fill the gap in the literature by offering the following steps:
 \begin{itemize}
@@
 a $\star$ indicates an asymptotic result is not available in the literature but is provided in this study, and
-a $\Diamond$ indicates the asymptotic convergence result exists in the literature but in a weaker form.
+a $\Diamond$ indicates that an asymptotic convergence result exists in the literature, though in a weaker form.
 ~\cite{gordy2010nested} provide asymptotic convergence results for the standard nested simulation procedure with a hockey-stick $h$, an indicator $h$ and VaR.
@@
 
-\subsection{Connections between Convergence in MSE and AE} \label{sec1:connection-mse-absolute-error}
+\subsection{Connections between Convergence in MSE and AE}\label{sec1:connection-mse-absolute-error}
 
@@
     Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
-    We write $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-\xi} \right)$, that is, $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $\xi$ if
-    $$
-        \exists C \limsup_{M} \frac{\mathbb{E} \left[\left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-\xi}} \leq C
+    We write $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-\xi} \right)$, that is, $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $\xi$ if there exists a constant $C$ such that
+    $$
+        \limsup_{\Gamma \to \infty} \frac{\mathbb{E} \left[\left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-\xi}} \leq C.
     $$
@@
     Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
-    We write $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-\xi})$, that is $\hat{\rho}_{\Gamma}$ converges in probabilistic order $\xi$ to $\rho$ if for a sufficiently large $\Gamma$,
-    $$
-        \forall \epsilon > 0 \exists C \mathbb{P} \left( \left| \hat{\rho}_{\Gamma} - \rho \right| \geq C \Gamma^{-\xi} \right) \leq \epsilon 
+    We write $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-\xi})$, that is $\hat{\rho}_{\Gamma}$ converges in probabilistic order $\xi$ to $\rho$ if for a sufficiently large $\Gamma$, for all $\epsilon > 0$ there exists a constant $C$ such that
+    $$
+         \mathbb{P} \left( \left| \hat{\rho}_{\Gamma} - \rho \right| \geq C \Gamma^{-\xi} \right) \leq \epsilon.
     $$
@@
 $$
-    \limsup_{M} \frac{\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-\xi}} \leq C.
+    \limsup_{\Gamma} \frac{\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-\xi}} \leq C.
 $$
@@
 & = d^2 \gamma^{2s} \cdot \mathbb{E} \left[ \mathbb{I}\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \} \right] \\
-& = d^2 \gamma^{2s} \cdot \mathbb{P} \left(|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \right)
+& = d^2 \gamma^{2s} \cdot \mathbb{P} \left(|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \right).
 \end{align*}
@@
 
-\begin{theorem} \label{thm1:convergence-mse-prob}
+\begin{theorem}\label{thm1:convergence-mse-prob}
     Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
@@
 
-\subsection{Asymptotic Analysis for the Standard Nested Simulation Procedure} \label{sec1:sns}
+\subsection{Asymptotic Analysis for the Standard Nested Simulation Procedure}\label{sec1:sns}
 In~\cite{gordy2010nested}, the authors analyze the asymptotic convergence of the standard nested simulation procedure in terms of MSE. 
@@
 
-\begin{assumption} \label{as1:sns}
+\begin{assumption}\label{as1:sns}
     $h(L)$ has finite second moment, i.e., $\mathbb{E} \left[ \left( h(L) \right)^2 \right] < \infty$.
@@
 
-\begin{assumption} \label{as1:sns-noise}
+\begin{assumption}\label{as1:sns-noise}
     $\hat{L}_N(X) = L(X) + \bar{Z}_N(X)$, where the simulation noise $\bar{Z}_N(X)$ has zero mean and variance $\nu(X) / N$, and the conditional variance $\nu(X)$ is bounded, i.e., 
@@
 
-\begin{align} \label{eq1:mse-sns}
+\begin{align}\label{eq1:mse-sns}
     & \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] \nonumber \\
@@
 
-In~\ref{eq1:mse-sns}, the last equality follows from Assumption~\ref{as1:sns}.
+In Equation~\eqref{eq1:mse-sns}, the last equality follows from Assumption~\ref{as1:sns}.
 The analysis of the first term is different for smooth and Lipschitz continuous $h$. 
@@
 
-\begin{align} \label{eq1:mse-sns2}
+\begin{align}\label{eq1:mse-sns2}
     \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] 
@@
 For a smooth function $h$, both ways of decomposing the MSE lead to the same order of convergence.
-However, for a Lipschitz continuous function $h$, Equation~\ref{eq1:mse-sns2} leads to a stronger order of convergence than Equation~\ref{eq1:mse-sns}.
+However, for a Lipschitz continuous function $h$, Equation~\eqref{eq1:mse-sns2} leads to a stronger order of convergence than Equation~\eqref{eq1:mse-sns}.
 In the following, we analyze the convergence of the standard nested simulation procedure for a smooth and a Lipschitz continuous $h$ by using both decomposition methods.
@@
 \subsubsection*{A Smooth Function $h$}
-\begin{assumption} \label{as1:sns-smooth}
+\begin{assumption}\label{as1:sns-smooth}
     The function $h$ has bounded first and second order derivative, i.e.,
@@
 Assumption~\ref{as1:sns-smooth} is similar to the smoothness assumption in~\cite{wang2022smooth}.
-Since $h$ is a smooth function, Taylor expansion can be applied to the first term in Equation~\ref{eq1:mse-sns}.
-
-\begin{align} \label{eq1:taylor-sns}
+Since $h$ is a smooth function, Taylor expansion can be applied to the first term in Equation~\eqref{eq1:mse-sns}.
+
+\begin{align}\label{eq1:taylor-sns}
     & \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) -  h\left(L_i \right)  \right)^2\right] \nonumber \\
@@
 where the last inequality is due to $2ab \leq a^2 + b^2$ for any $a, b \in \mathbb{R}$. 
-The two terms on the right-hand side of Equation~\ref{eq1:taylor-sns} are analyzed separately.
+The two terms on the right-hand side of Equation~\eqref{eq1:taylor-sns} are analyzed separately.
 We start with the first term $S_1$.
 
-\begin{align} \label{eq1:s1-sns}
+\begin{align}\label{eq1:s1-sns}
     S_1 
@@
 \end{align}
-where the last inequality in Equation~\ref{eq1:s1-sns} is due to Assumption~\ref{as1:sns-noise}, independence of $X_i$ and $X_j$ for $i \neq j$, and the fact that the inner simulation noise has zero mean, i.e., $\mathbb{E} \left[ \bar{Z}_N \right] = 0$.
+where the last inequality in Equation~\eqref{eq1:s1-sns} is due to Assumption~\ref{as1:sns-noise}, independence of $X_i$ and $X_j$ for $i \neq j$, and the fact that the inner simulation noise has zero mean, i.e., $\mathbb{E} \left[ \bar{Z}_N \right] = 0$.
 It remains to analyze the second term $S_2$, where Assumption \ref{as1:sns-noise-var} is necessary to ensure the existence of the fourth moment of the simulation noise and the convergence of the second term.
 
-\begin{assumption} \label{as1:sns-noise-var}
+\begin{assumption}\label{as1:sns-noise-var}
     The fourth moment of simulation noise $\bar{Z}_N(X)$ follows $\mathbb{E} \left[ \left( \bar{Z}_N(X) \right)^4 \right] = \nu_2(X) / N^2$, where $\nu_2(X)$ is bounded, i.e., there exists $C_{\nu,2} > 0$ such that $\nu_2(X) \leq C_{\nu,2}$ for all $x \in \mathbb{R}$.
@@
 
-\begin{align} \label{eq1:s2-sns}
+\begin{align}\label{eq1:s2-sns}
     S_2 & = \mathbb{E} \left[ \left( \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{L}^{\text{SL}}_{M, N}(X_i) - L_i \right)^2 \right)^2\right] \nonumber \\
@@
 where the second inequality is due to Assumption~\ref{as1:sns-smooth}, and the last inequality follows from Assumption~\ref{as1:sns-noise-var} and the fact that $\hat{L}_N$ is a standard MC estimator of $L$.
-Combining Equation~\ref{eq1:mse-sns},~\ref{eq1:taylor-sns},~\ref{eq1:s1-sns}, and~\ref{eq1:s2-sns}, we have
-
-\begin{equation} \label{eq1:mse-sns-smooth}
+Combining Equation~\eqref{eq1:mse-sns},~\ref{eq1:taylor-sns},~\ref{eq1:s1-sns}, and~\ref{eq1:s2-sns}, we have
+
+\begin{equation}\label{eq1:mse-sns-smooth}
     \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(M^{-1}) + \mathcal{O}(N^{-2})
@@
 Setting $M = \mathcal{O}(\Gamma^{2/3})$ and $N = \mathcal{O}(\Gamma^{1/3})$, we provide the same rate of convergence as obtained for other risk measures in~\cite{gordy2010nested}.
-However, we observe that Equation~\ref{eq1:s1-sns} converges in the order of $\mathcal{O}(M^{-1}N^{-1})$.
-The cross term here is potentially problematic, as setting $N$ as a negative power of $M$ may result in Equation~\ref{eq1:s1-sns} to be divergent.
-
-In order to avoid the cross term, we proceed to follow the bias-variance decomposition in Equation~\ref{eq1:mse-sns2}.
-
-\begin{align} \label{eq1:bias-sns-smooth}
+However, we observe that Equation~\eqref{eq1:s1-sns} converges in the order of $\mathcal{O}(M^{-1}N^{-1})$.
+The cross term here is potentially problematic, as setting $N$ as a negative power of $M$ may result in Equation~\eqref{eq1:s1-sns} to be divergent.
+
+In order to avoid the cross term, we proceed to follow the bias-variance decomposition in Equation~\eqref{eq1:mse-sns2}.
+
+\begin{align}\label{eq1:bias-sns-smooth}
     \text{Bias}(\hat{\rho}_{M, N})
@@
 where the last equality follows from the Taylor expansion of the smooth function $h$.
-The first and second order Taylor expansion terms are analyzed separately in Equation~\ref{eq1:bias-sns-smooth-Taylor1} and Equation~\ref{eq1:bias-sns-smooth-Taylor2}.
-
-\begin{align} \label{eq1:bias-sns-smooth-Taylor1}
+The first and second order Taylor expansion terms are analyzed separately in Equation~\eqref{eq1:bias-sns-smooth-Taylor1} and Equation~\eqref{eq1:bias-sns-smooth-Taylor2}.
+
+\begin{align}\label{eq1:bias-sns-smooth-Taylor1}
     \mathbb{E} \left[ h'\left( L \right) \left( \hat{L}_N - L \right) \right]
@@
 
-\begin{align} \label{eq1:bias-sns-smooth-Taylor2}
+\begin{align}\label{eq1:bias-sns-smooth-Taylor2}
     \mathbb{E} \left[ h''\left( z \right) \left( \hat{L}_N - L \right)^2 \right]
@@
 
-It remains to analyze the variance term in Equation~\ref{eq1:mse-sns2}.
-
-\begin{equation} \label{eq1:var-sns-smooth}
+It remains to analyze the variance term in Equation~\eqref{eq1:mse-sns2}.
+
+\begin{equation}\label{eq1:var-sns-smooth}
     \text{Var}(\hat{\rho}_{M, N}) = \frac{1}{M} \text{Var}(h(\hat{L}_N)) = \mathcal{O}(M^{-1})
@@
 
-Equation~\ref{eq1:var-sns-smooth} directly follows from Assumption~\ref{as1:sns} and the fact that $\hat{L}_N$ is a standard MC estimator of $L$.
-Combining Equation~\ref{eq1:bias-sns-smooth-Taylor1},~\ref{eq1:bias-sns-smooth-Taylor2}, and~\ref{eq1:var-sns-smooth}, we are able to show the convergence order of the standard nested simulation procedure for a smooth function $h$ without the cross term as in Equation~\ref{eq1:s1-sns}.
-
-\begin{theorem} \label{thm1:sns-smooth}
+Equation~\eqref{eq1:var-sns-smooth} directly follows from Assumption~\ref{as1:sns} and the fact that $\hat{L}_N$ is a standard MC estimator of $L$.
+Combining Equation~\eqref{eq1:bias-sns-smooth-Taylor1},~\ref{eq1:bias-sns-smooth-Taylor2}, and~\ref{eq1:var-sns-smooth}, we are able to show the convergence order of the standard nested simulation procedure for a smooth function $h$ without the cross term as in Equation~\eqref{eq1:s1-sns}.
+
+\begin{theorem}\label{thm1:sns-smooth}
     Let $h$ be a smooth function. 
@@
 
-\begin{assumption} \label{as1:sns-lip}
+\begin{assumption}\label{as1:sns-lip}
     The function $h$ is Lipschitz continuous. Hence, $|h(x_1) - h(x_2)| \leq K|x_1 - x_2|$ for some constant $K< \infty$.
@@
 Assumption~\ref{as1:sns-lip} is a standard assumption for analysis involving Lipschitz continuous functions, and it is also used in~\cite{broadie2015risk}.
-For the Lipschitz continuous case, the first term in Equation~\ref{eq1:mse-sns} is analyzed differently.
+For the Lipschitz continuous case, the first term in Equation~\eqref{eq1:mse-sns} is analyzed differently.
 
@@
 Setting $M = \mathcal{O}(\Gamma^{1/2})$ and $N = \mathcal{O}(\Gamma^{1/2})$, we provide a looser bound than the one obtained for the hockey-stick $h$.
-Using the bias-variance decomposition in Equation~\ref{eq1:mse-sns2}, we obtain the following bias term.
-
-\begin{align} \label{eq1:bias-sns-lip}
+Using the bias-variance decomposition in Equation~\eqref{eq1:mse-sns2}, we obtain the following bias term.
+
+\begin{align}\label{eq1:bias-sns-lip}
     \text{Bias}(\hat{\rho}_{M, N})
@@
 \end{align}
-The variance term in Equation~\ref{eq1:mse-sns2} for Lipschitz continuous $h$ is identical to the one in Equation~\ref{eq1:var-sns-smooth}.
+The variance term in Equation~\eqref{eq1:mse-sns2} for Lipschitz continuous $h$ is identical to the one in Equation~\eqref{eq1:var-sns-smooth}.
 
@@
 \begin{align*}
-    k                   & \rightarrow \infty \\
-    \frac{k}{M}         & \rightarrow 0, ~~~ \text{as} ~ M \rightarrow \infty. \\
-    \frac{\log(M)}{k}   & \rightarrow 0, ~~~ \text{as} ~ k \rightarrow \infty.
+    k                   & \to \infty \\
+    \frac{k}{M}         & \to 0, ~~~ \text{as} ~ M \to \infty. \\
+    \frac{\log(M)}{k}   & \to 0, ~~~ \text{as} ~ k \to \infty.
 \end{align*}
@@
     \end{equation*}
-    where $R_k$ is a Euclidean distance between $X_i$ and its $k$-th nearest neighbor, and $K:\mathbb{R}^d \rightarrow \mathbb{R}$ is a bounded, nonnegative kernel function satisfying 
+    where $R_k$ is a Euclidean distance between $X_i$ and its $k$-th nearest neighbor, and $K:\mathbb{R}^d \mapsto \mathbb{R}$ is a bounded, nonnegative kernel function satisfying 
     \begin{align*}
@@
 
-\begin{assumption} \label{as1:knn}
+\begin{assumption}\label{as1:knn}
     $f_X$ is bounded and continuously differentiable up to a second order in a neighborhood of $x$ with $f_X(x) > 0$, $f_X$, $\mathbb{E} \left[ Y^2| X = x \right] < \infty$, and the kernel function $K$ satisfies
@@
     \end{align*}
-    Suppose that $\mathbb{P}(\|x - X\| > r) = \mathcal{O}(r^{-\alpha})$ for some $\alpha > 0$ as $r \rightarrow \infty$.
+    Suppose that $\mathbb{P}(\|x - X\| > r) = \mathcal{O}(r^{-\alpha})$ for some $\alpha > 0$ as $r \to \infty$.
 \end{assumption}
@@
 The bias of the estimator of $\rho$ for a kNN-based nested simulation procedure is analyzed following a Taylor expansion.
-\begin{align} \label{eq1:bias-knn}
+\begin{align}\label{eq1:bias-knn}
     & \mathbb{E} \left[ h(\hat{L}^{\text{kNN}}_{M, n}(X)) - h(L) \right] \nonumber \\
@@
 where the bias is decomposed into two terms, and $z$ is between $\hat{L}^{\text{kNN}}_{M, n}(X)$ and $L$.
-The first term in Equation~\ref{eq1:bias-knn} is 
-\begin{align} \label{eq1:bias-knn-1}
+The first term in Equation~\eqref{eq1:bias-knn} is 
+\begin{align}\label{eq1:bias-knn-1}
     & ~~~~ \mathbb{E} \left[ h'(L) \left( \hat{L}^{\text{kNN}}_{M, n}(X) - L \right) \right]  \nonumber \\
@@
 
-The second term in Equation~\ref{eq1:bias-knn} is 
-\begin{align} \label{eq1:bias-knn-2}
+The second term in Equation~\eqref{eq1:bias-knn} is 
+\begin{align}\label{eq1:bias-knn-2}
     & ~~~~ \mathbb{E} \left[ h''(z) \left( \hat{L}^{\text{kNN}}_{M, n}(X) - L \right)^2 \right]  \nonumber \\
@@
 \end{align}
-where the second term in Equation~\ref{eq1:bias-knn-2} is of higher order than Equation~\ref{eq1:bias-knn-1}, and it is negligible since $kM^{-1} \rightarrow 0$ as $M \rightarrow \infty$ and $k \rightarrow \infty$,
-The first term in Equation~\ref{eq1:bias-knn-2} is $\mathcal{O}\left(\frac{1}{k}\right)$.
+where the second term in Equation~\eqref{eq1:bias-knn-2} is of higher order than Equation~\eqref{eq1:bias-knn-1}, and it is negligible since $kM^{-1} \to 0$ as $M \to \infty$ and $k \to \infty$, 
+The first term in Equation~\eqref{eq1:bias-knn-2} is $\mathcal{O}\left(\frac{1}{k}\right)$.
 Set $k = \mathcal{O}(M^{\frac{2}{2+d}})$ and $M = \mathcal{O}(\Gamma)$, the bias of the kNN-based nested simulation procedure converges in the order of $\Gamma^{-\frac{2}{2+d}}$.
 
-\begin{definition} \label{def:knn-smooth-bias}
+\begin{definition}\label{def:knn-smooth-bias}
     Let $h$ be a smooth function. 
@@
 
-Definition~\ref{def:knn-smooth-bias} is obtained by matching the orders of the bias terms in Equation~\ref{eq1:bias-knn-1} and~\ref{eq1:bias-knn-2}.
+Definition~\ref{def:knn-smooth-bias} is obtained by matching the orders of the bias terms in Equation~\eqref{eq1:bias-knn-1} and~\ref{eq1:bias-knn-2}.
 It is the tightest bound that can be obtained for the convergence of the kNN-based nested simulation procedure with a smooth function $h$.
@@
 
-\begin{assumption} \label{as1:sns-joint-density}
+\begin{assumption}\label{as1:sns-joint-density}
     The joint density $f_{Y,\tilde{Z}_N}(y,z_N)$ and its partial derivatives 
@@
 
-\begin{assumption} \label{as1:sns-joint-density-bound}
+\begin{assumption}\label{as1:sns-joint-density-bound}
     For $N \geq 1$, there exist non-negative functions $p_{0, N}(\cdot)$, $p_{1, N}(\cdot)$, and $p_{2, N}(\cdot)$ such that for all $y$ and $z$,
@@
 
-\begin{assumption} \label{as1:mlmc-q}
+\begin{assumption}\label{as1:mlmc-q}
     $f_Q$, the density of $Q$ exists, and there exist positive constants $q_0$ such that $f_Q(q) \leq q_0$ for all $q \in [0, q_0]$.
@@
 
-\begin{assumption} \label{as1:likelihood-ratio-marginal-density}
+\begin{assumption}\label{as1:likelihood-ratio-marginal-density}
     The marginal density $f_H(y)$ of $H$ exists. $f_H(y)$ can be sampled and evaluated, and $Y(y, x) f_{H|X}(y|x) = 0$ whenever $f_H(x) = 0$. 
@@
 
-\begin{assumption} \label{as1:likelihood-ratio-independence}
+\begin{assumption}\label{as1:likelihood-ratio-independence}
     The inner sample $H \sim f_H(y)$ is independent of $X$. Samples $\{X_i, i=1,\ldots,M\}$ and $\{H_i, i=1,\ldots,N\}$ are i.i.d. samples from $f_X(x)$ and $f_H(y)$, respectively.
@@
 
-\begin{assumption} \label{as1:krr-domain}
+\begin{assumption}\label{as1:krr-domain}
     $\Omega$ is a bounded subset of $\mathbb{R}^d$, and $f_X(x)$ is bounded above and below away from zero.
@@
 
-\section{Finite-Sample Experiments} \label{sec1:numerical-experiments}
+\section{Finite-Sample Experiments}\label{sec1:numerical-experiments}
 The theoretical framework has lent itself for a comparison of the asymptotic convergence behavior for different nested simulation procedures.
@@
 
-\subsection{Sensitivity to the Asset Dimension} \label{sec1:sensitivity-dimension}
+\subsection{Sensitivity to the Asset Dimension}\label{sec1:sensitivity-dimension}
 In portfolio risk management, the asset dimension is a critical factor that determines the complexity of the portfolio and the computational cost of the risk measure estimation.
@@
 
-\subsection{Empirical Convergence of Kernel Smoothing-Based Procedures} \label{sec1:kernel-smoothing-convergence}
+\subsection{Empirical Convergence of Kernel Smoothing-Based Procedures}\label{sec1:kernel-smoothing-convergence}
 
@@
 
-\subsection{Empirical Convergence of Parametric Regression Procedures} \label{sec1:regression-convergence}
+\subsection{Empirical Convergence of Parametric Regression Procedures}\label{sec1:regression-convergence}
 
@@
 
-\subsection{Sensitivity to the Option Types and Risk Measures} \label{sec1:sensitivity-option-type}
+\subsection{Sensitivity to the Option Types and Risk Measures}\label{sec1:sensitivity-option-type}
 
@@
 
-\subsection{Sensitivity to level for VaR and CVaR} \label{sec1:sensitivity-level}
+\subsection{Sensitivity to level for VaR and CVaR}\label{sec1:sensitivity-level}
 
@@
 
-\subsection{Sensitivity to the Asset Model} \label{sec1:sensitivity-assetModel}
+\subsection{Sensitivity to the Asset Model}\label{sec1:sensitivity-assetModel}
 
@@
 
-\subsection{Empirical Convergence of MLMC} \label{sec1:empirical-mlmc}
+\subsection{Empirical Convergence of MLMC}\label{sec1:empirical-mlmc}
 
@@
 
-\section{Computational Complexity} \label{sec1:computational-complexity}
+\section{Computational Complexity}\label{sec1:computational-complexity}
 Compared to the standard procedure, metamodel-based nested simulation procedures often have faster empirical rates of convergence.
@@
 
-\section{Conclusion and Extensions} \label{sec1:conclusion}
+\section{Conclusion and Extensions}\label{sec1:conclusion}
 In the task of estimating risk measures for portfolios of complex financial derivatives, nested simulation procedures are commonly required but often computationally expensive. 

### 2025-02-21 project3/draft.tex
edited

@@
 In our numerical experiments, the dataset is generated by running the standard nested simulation procedure in Algorithm~\ref{alg2:standardProcedure} for a large number of VA contracts.
-The input features $\mathbf{X}$ are the return vectors from Equation~\ref{eq2:return}, and the output labels $L$ are the contract losses for different outer scenarios.
+The input features $\mathbf{X}$ are the return vectors from Equation~\eqref{eq2:return}, and the output labels $L$ are the contract losses for different outer scenarios.
 The stock price vector $\mathbf{S}$ is not crucial for the discussion of this chapter and is omitted since it can be immediately recovered from $\mathbf{X}$ and the initial stock price $S_0$.
@@
 The simulation datasets contain $2,\!000$ samples for each contract type, and the LSTM metamodels are trained using multi-task learning. 
-In our experiments, Algorithm~\ref{alg3:multiTaskLearning} is used to train the LSTM metamodels simultaneously to minimize the multi-task MSE loss function in Equation~\ref{eq3:multiTaskLoss}.
+In our experiments, Algorithm~\ref{alg3:multiTaskLearning} is used to train the LSTM metamodels simultaneously to minimize the multi-task MSE loss function in Equation~\eqref{eq3:multiTaskLoss}.
 We use individual task training as a baseline for comparison, where the LSTM metamodels are trained separately on the GMMB and GMWB contracts.

### 2025-02-21 introduction.tex
new

@@
 Risk management is a key component of modern financial systems.
-Successful risk management practice can enhance financial stability and resilience for individual companies and for the financial system too.
+Successful risk management practice can enhance financial stability and resilience for individual companies and for the financial system as well.
 Variable annuity (VA) contracts are a popular type of complex insurance product that is linked to the performance of underlying assets.
@@
 In our numerical experiment, the best neural network metamodel surpasses the state-of-the-art metamodels in tail identification, and it leads to substantial computational savings.
-Chapter~\ref{chap:project2 } also includes sensitivity testing of the neural network metamodel.
+Chapter~\ref{chap:project2} also includes sensitivity testing of the neural network metamodel.
 We argue that for estimating tail risk measures of VA contract losses, the inner simulation can be replaced entirely by a suitable metamodel.
@@
 Chapter~\ref{chap:conclusion} concludes this thesis and discusses potential future research directions.
-Chapter~\ref{chap:futureWork } explores future applications of deep reinforcement learning in the dynamic hedging of VA contracts.
+Chapter~\ref{chap:futureWork} explores future applications of deep reinforcement learning in the dynamic hedging of VA contracts.
 
-\section{Managing Risk of Variable Annuity with Nested Simulation}
+\section{Risk Management of Variable Annuities with Nested Simulation}
 
@@
 Our approach enables rapid deployment in changing environments.
-Finally, Chapter~\ref{chap:conclusion} summarizes the key findings of this thesis and discusses future research directions that involve the robost use of neural networks in quantitative risk management applications.
+Chapter~\ref{chap:conclusion} summarizes the key findings of this thesis and discusses future research directions that involve the robost use of neural networks in quantitative risk management applications.
+Chapter~\ref{chap:futureWork} explores future applications of transfer learning and deep reinforcement learning in the dynamic hedging of VA contracts.

### 2025-02-21 project1/nsSurvey.tex
new

@@
 $$\rho(L) = \rho(L(X)),$$
-
 where $X \in \mathcal{X} \subset \mathbb{R}^d$, and $L = L(X)$ is a random variable whose distribution is characterized by $X$.
@@
 \end{equation}
+
 In the literature, CVaR are also known as Conditional Tail Expectation (CTE), Tail Value-at-Risk (TailVaR), and Expected Shortfall (ES).
@@
             In~\cite{broadie2015risk}, the convergence analysis is performed on the expectation (Equation~\eqref{eq1:sl-E}) and for smooth and Lipschitz continuous $h$. 
-            Connections between the expectation and the MSE are discussed in the Appendix.
     \item   Kernel smoothing:
@@
             \hat{L}^{\text{kNN}}_{M, N}(x) 
-            = \frac{\frac{1}{M R_M^d} \sum_{i=1}^M \hat{L}_{N, i} K\left(\frac{x - X_i}{R_M}\right)}{\frac{1}{M R_M^d} \sum_{i=1}^M K\left(\frac{x - X_i}{R_M}\right)}
+            = \frac{\frac{1}{M R_M^d} \sum_{i=1}^M \hat{L}_{N, i} K\left(\frac{x - X_i}{R_M}\right)}{\frac{1}{M R_M^d} \sum_{i=1}^M K\left(\frac{x - X_i}{R_M}\right)},
             \end{equation*}
@@
 \begin{align}
-    & \min_{M, N}  & \text{MSE}(\hat{\rho}^{\text{SL}}_{M, N}) = \mathbb{E} \left[ \left( \hat{\rho}^{\text{SL}}_{M, N} - \rho \right)^2 \right] \nonumber \\
-    & \text{subject to} & M \cdot N = \Gamma 
+    & \min_{M, N}  & \text{MSE}(\hat{\rho}^{\text{SL}}_{M, N}) = \mathbb{E} \left[ \left( \hat{\rho}^{\text{SL}}_{M, N} - \rho \right)^2 \right], \nonumber \\
+    & \text{subject to} & M \cdot N = \Gamma.
 \end{align}
@@
 \begin{align}
-    & \min ~~~ \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] \nonumber \\
+    & \min ~~~ \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right], \nonumber \\
     & \text{subject to} ~~~ M \cdot N = \Gamma, 
@@
 $$
-    \mathbb{P} \left( |\hat{\rho}_{\gamma} - \rho| > d\gamma^{-\frac{\xi}{2}} \right) \leq \frac{C}{d^2}
+    \mathbb{P} \left( |\hat{\rho}_{\gamma} - \rho| > d\gamma^{-\frac{\xi}{2}} \right) \leq \frac{C}{d^2}.
 $$
@@
 $$
-    \left| \hat{\rho}_{\gamma} - \rho \right| = \mathcal{O}_\mathbb{P} \left( \Gamma^{-\frac{\xi}{2}} \right)
+    \left| \hat{\rho}_{\gamma} - \rho \right| = \mathcal{O}_\mathbb{P} \left( \Gamma^{-\frac{\xi}{2}} \right).
 $$
@@
     & \leq d^2 \Gamma^{-2\xi} \cdot \mathbb{E} \left[ \mathbb{I}\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s \} \right] \\
-    & = d^2 \Gamma^{-2\xi} \cdot \mathbb{P} \left(|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s \right) \leq d^2 \Gamma^{-2\xi} 
+    & = d^2 \Gamma^{-2\xi} \cdot \mathbb{P} \left(|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s \right) \leq d^2 \Gamma^{-2\xi}.
 \end{align*}
@@
     \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^{-2\xi}\}} \right] 
-    & = \int_{-\infty}^{-d\Gamma^{-2k}} (x - \rho)^2 f(x) dx + \int_{d\Gamma^{-2\xi}}^{\infty} (x - \rho)^2 f(x) dx 
+    & = \int_{-\infty}^{-d\Gamma^{-2k}} (x - \rho)^2 f(x) dx + \int_{d\Gamma^{-2\xi}}^{\infty} (x - \rho)^2 f(x) dx.
 \end{align*}
@@
     & = 2 \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) -  h\left(L_i \right)  \right)^2\right] + \frac{2}{M} \text{Var}(h(L)) \nonumber \\
-    & = 2 \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) -  h\left(L_i \right)  \right)^2\right] + \mathcal{O}(M^{-1}),
+    & = 2 \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) -  h\left(L_i \right)  \right)^2\right] + \mathcal{O}(M^{-1}).
 \end{align}
@@
     & = \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \mathbb{E} \left[ \hat{\rho}_{M, N} \right] \right)^2 \right] + \left( \mathbb{E} \left[ \hat{\rho}_{M, N} \right] - \rho \right)^2 \nonumber \\
-    & = \text{Var}(\hat{\rho}_{M, N}) + \text{Bias}^2(\hat{\rho}_{M, N})
+    & = \text{Var}(\hat{\rho}_{M, N}) + \text{Bias}^2(\hat{\rho}_{M, N}),
 \end{align}
@@
 \end{assumption}
+
 Assumption~\ref{as1:sns-smooth} is similar to the smoothness assumption in~\cite{wang2022smooth}.
@@
     & \leq 2 \underbrace{\mathbb{E} \left[ \left( \frac{1}{M} \sum_{i=1}^M h'\left( L_i \right) \left( \hat{L}_{N, i}- L_i \right) \right)^2\right]}_{S_1} \nonumber \\
-    & ~~~~ + 2 \underbrace{\mathbb{E} \left[ \left( \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{L}_{N, i} - L_i \right)^2 \right)^2\right]}_{S_2}
+    & ~~~~ + 2 \underbrace{\mathbb{E} \left[ \left( \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{L}_{N, i} - L_i \right)^2 \right)^2\right]}_{S_2},
 \end{align}
@@
     & = C_1^2 \mathbb{E} \left[ \frac{1}{M^2} \sum_{i=1}^M \bar{Z}_{N, i}^2 + \frac{1}{M^2} \sum_{i=1}^M \sum_{j \neq i}^M \bar{Z}_{N, i} \bar{Z}_{N, j} \right] \nonumber \\
-    & \leq  \frac{C_1^2 C_{\nu, 1}}{MN} = \mathcal{O}(M^{-1} N^{-1})
+    & \leq  \frac{C_1^2 C_{\nu, 1}}{MN} = \mathcal{O}(M^{-1} N^{-1}),
 \end{align}
@@
     & = C_2^2 \mathbb{E} \left[ \frac{1}{2M^2} \sum_{i=1}^M \bar{Z}_{N, i}^4 + \frac{1}{2M^2} \sum_{i=1}^M \sum_{j \neq i}^M \bar{Z}_N^2(X_i) \bar{Z}_N^2(X_j) \right] \nonumber \\
-    & \leq  C_2^2 \left(\frac{ C_{\nu, 2} M}{2M^2N^2} + \frac{C_{\nu,1}^2M(M-1)}{2M^2N^2}\right) = \mathcal{O}(N^{-2})
+    & \leq  C_2^2 \left(\frac{ C_{\nu, 2} M}{2M^2N^2} + \frac{C_{\nu,1}^2M(M-1)}{2M^2N^2}\right) = \mathcal{O}(N^{-2}),
 \end{align}
@@
 \begin{equation}\label{eq1:mse-sns-smooth}
-    \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(M^{-1}) + \mathcal{O}(N^{-2})
+    \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(M^{-1}) + \mathcal{O}(N^{-2}).
 \end{equation}
+
 Setting $M = \mathcal{O}(\Gamma^{2/3})$ and $N = \mathcal{O}(\Gamma^{1/3})$, we provide the same rate of convergence as obtained for other risk measures in~\cite{gordy2010nested}.
@@
     & = \mathbb{E} \left[ h\left( \hat{L}_N \right) - h\left( L \right) \right] \nonumber \\
-    & = \mathbb{E} \left[h'\left( L \right) \left( \hat{L}_N - L \right) + \frac{1}{2} h''\left( z \right) \left( \hat{L}_N - L \right)^2 \right]
+    & = \mathbb{E} \left[h'\left( L \right) \left( \hat{L}_N - L \right) + \frac{1}{2} h''\left( z \right) \left( \hat{L}_N - L \right)^2 \right],
 \end{align}
@@
     & = \mathbb{E} \left[ \mathbb{E} \left[ h'\left( L \right) \left( \hat{L}_N - L \right)  | X \right] \right] \nonumber \\
-    & = \mathbb{E} \left[ h'\left( L \right) \mathbb{E} \left[ \hat{L}_N - L  | X \right] \right] = 0
+    & = \mathbb{E} \left[ h'\left( L \right) \mathbb{E} \left[ \hat{L}_N - L  | X \right] \right] = 0.
 \end{align}
@@
     & \leq C_{h,2} \mathbb{E} \left[ \left( \hat{L}_N - L \right)^2 \right] \nonumber \\
-    & = C_{h,2} \text{Var}(\hat{L}_N) = \mathcal{O}\left( N^{-1} \right)
+    & = C_{h,2} \text{Var}(\hat{L}_N) = \mathcal{O}\left( N^{-1} \right).
 \end{align}
@@
 \begin{equation}\label{eq1:var-sns-smooth}
-    \text{Var}(\hat{\rho}_{M, N}) = \frac{1}{M} \text{Var}(h(\hat{L}_N)) = \mathcal{O}(M^{-1})
+    \text{Var}(\hat{\rho}_{M, N}) = \frac{1}{M} \text{Var}(h(\hat{L}_N)) = \mathcal{O}(M^{-1}).
 \end{equation}
@@
     & \leq K^2 \mathbb{E} \left[ \left( \hat{L}_N -  L  \right)^2\right] \nonumber \\
-    & = K^2 \mathbb{E} \left[ \left( \bar{Z}_{N}(X) \right)^2\right] = \mathcal{O}(N^{-1})
+    & = K^2 \mathbb{E} \left[ \left( \bar{Z}_{N}(X) \right)^2\right] = \mathcal{O}(N^{-1}),
 \end{align}
@@
     & = K \mathbb{E} \left[ |\bar{Z}_N| \right] \nonumber \\
-    & \leq K \sqrt{\mathbb{E} \left[ \left( \bar{Z}_N \right)^2 \right]} = \mathcal{O}(N^{-1/2})
-\end{align}
+    & \leq K \sqrt{\mathbb{E} \left[ \left( \bar{Z}_N \right)^2 \right]} = \mathcal{O}(N^{-1/2}).
+\end{align}
+
 The variance term in Equation~\eqref{eq1:mse-sns2} for Lipschitz continuous $h$ is identical to the one in Equation~\eqref{eq1:var-sns-smooth}.
@@
 \begin{equation}
-    \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(M^{-1}) + \mathcal{O}(N^{-1})
+    \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(M^{-1}) + \mathcal{O}(N^{-1}).
 \end{equation}
@@
 \begin{align*}
-    k                   & \to \infty \\
-    \frac{k}{M}         & \to 0, ~~~ \text{as} ~ M \to \infty. \\
+    k                   & \to \infty, \\
+    \frac{k}{M}         & \to 0, ~~~ \text{as} ~ M \to \infty, \\
     \frac{\log(M)}{k}   & \to 0, ~~~ \text{as} ~ k \to \infty.
 \end{align*}
+
 A kNN-based nested simulation procedure with a model parameter $k$ estimates the risk measure $\rho = \mathbb{E} \left[ h(L) \right]$ with
@@
     & \mathbb{E} \left[ h(\hat{L}^{\text{kNN}}_{M, n}(X)) - h(L) \right] \nonumber \\
-    & = \mathbb{E} \left[ h'(L) \left( \hat{L}^{\text{kNN}}_{M, n}(X) - L \right) + \frac{1}{2} h''(z) \left( \hat{L}^{\text{kNN}}_{M, n}(X) - L \right)^2 \right] 
+    & = \mathbb{E} \left[ h'(L) \left( \hat{L}^{\text{kNN}}_{M, n}(X) - L \right) + \frac{1}{2} h''(z) \left( \hat{L}^{\text{kNN}}_{M, n}(X) - L \right)^2 \right],
 \end{align}
@@
     & \leq C_2 \int_{\Omega} \left( \frac{C_{\text{kNN}} \cdot \text{Var}[Y| X = x]}{k} \int K^2(u) du + o\left(\frac{1}{k}\right) \right) f_X(x) dx \nonumber \\
-    & + C_2 \int_{\Omega} \left( A_{\text{kNN}}(x) \left(\frac{k}{M}\right)^{2/d} \left(1+o_x(1)\right) + B_{\text{kNN}} \cdot \left(\frac{1}{k} + o_x\left(\frac{1}{k}\right)\right) \right)^2 f_X(x) dx
+    & + C_2 \int_{\Omega} \left( A_{\text{kNN}}(x) \left(\frac{k}{M}\right)^{2/d} \left(1+o_x(1)\right) + B_{\text{kNN}} \cdot \left(\frac{1}{k} + o_x\left(\frac{1}{k}\right)\right) \right)^2 f_X(x) dx,
 \end{align}
@@
 For the kernel-based nested simulation procedure,~\cite{hong2017kernel} simplifies the analysis by assuming that for each $X_i$, the inner simulation budget $N$ is fixed together with the variance of the inner simulation noise $\bar{Z}_{N, i}$.
-In essence, this fixed variance design treats the $(X_i, \bar{Y}_{N, i})$ as independent and identically distributed observations of $(X, Y)$, and the kernel-based nested simulation procedure is analyzed as a non-parametric regression problem.
+In essence, this fixed variance design treats the $(X_i, \bar{Y}_{N, i})$ as i.i.d.
+observations of $(X, Y)$, and the kernel-based nested simulation procedure is analyzed as a non-parametric regression problem.
 Regularity conditions on $f_X(x)$, the density of $X$, and the conditional second moment of $Y$ are assumed to ensure the convergence of $\hat{L}^{\text{KS}}_{M, N}(X)$, the kernel smoothing estimator of $L$.

### 2025-02-21 project2/nnMetamodels.tex
new

@@
 
-Let $L_1,L_2,\ldots,L_M$ be $M$ independent and identically distributed (i.i.d.) simulated losses of $L$ and let $L_{(1)}\leq L_{(2)}\leq \ldots\leq L_{(M)}$ be the ordered losses.
+Let $L_1,L_2,\ldots,L_M$ be $M$ i.i.d. simulated losses of $L$ and let $L_{(1)}\leq L_{(2)}\leq \ldots\leq L_{(M)}$ be the ordered losses.
 For a given confidence level $\alpha$ (assume that $\alpha M$ is an integer for simplicity), $\alpha$-VaR can be estimated by the sample quantile $\widehat{\VaR}_\alpha = L_{(\alpha M)}$.
@@
 \end{equation}
+
 Equation \eqref{eq2:cvar-hat} is the same as \eqref{eq1:cvar-hat} except that we define a \textit{true tail scenario set} of size $k$ as $\tail_{k} = \{i: L_i > L_{(M-k)}\}$.
@@
         \item Estimate the $\alpha$-CVaR of $L$ by 
-        $$\widehat{\CVaR}^{ML}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}\Lhat_{(i)}^{ML} = \frac{1}{(1-\alpha)M} \sum_{i \in \widehat{\tail}_{(1-\alpha )M}^{ML}}\Lhat_{i}^{ML},$$ 
+        $$\widehat{\CVaR}^{ML}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}\Lhat_{(i)}^{ML} = \frac{1}{(1-\alpha)M} \sum_{i \in \widehat{\tail}_{(1-\alpha)M}^{ML}}\Lhat_{i}^{ML},$$ 
         where $\widehat{\tail}_{k}^{ML}$ denotes a predicted tail scenario set associated with the largest $k$ estimated losses.
@@
         \begin{cases}
-            0.00417 & \text{if } t < 84 \\
-            0.00833 & \text{if } t \geq 84
+            0.00417 & \text{if } t < 84, \\
+            0.00833 & \text{if } t \geq 84.
         \end{cases}
@@
         \midrule
-        LSTM                & $100$                & $0.075 (\pm4.5\times 10^{-3})$         & $0.079(\pm5.4\times 10^{-3})$     & $0.063 (\pm4.4\times 10^{-3})$ \\ 
-        High-capacity LSTM  & $100$                & $0.068 (\pm3.6\times 10^{-3})$         & $0.102(\pm6.1\times 10^{-2})$     & $0.060 (\pm3.6\times 10^{-3})$ \\
-        Average Difference  & $100$                & $-0.007$                               & $0.023$                           & $-0.003$ \\
+        LSTM                & $\num{100}$                & $0.075 (\pm4.5\times 10^{-3})$         & $0.079(\pm5.4\times 10^{-3})$     & $0.063 (\pm4.4\times 10^{-3})$ \\ 
+        High-capacity LSTM  & $\num{100}$                & $0.068 (\pm3.6\times 10^{-3})$         & $0.102(\pm6.1\times 10^{-2})$     & $0.060 (\pm3.6\times 10^{-3})$ \\
+        Average Difference  & $\num{100}$                & $-0.007$                               & $0.023$                           & $-0.003$ \\
         \hline
-        LSTM                & $10$                 & $0.195 (\pm1.1\times 10^{-3})$         & $0.193(\pm1.7\times 10^{-3})$     & $0.070 (\pm9.1\times 10^{-4})$ \\
-        High-capacity LSTM  & $10$                 & $0.157 (\pm2.0\times 10^{-3})$         & $0.199(\pm1.9\times 10^{-3})$     & $0.065 (\pm1.9\times 10^{-3})$ \\
-        Average Difference  & $10$                 & $-0.038$                               & $0.006$                           & $-0.005$ \\
+        LSTM                & $\num{10}$                 & $0.195 (\pm1.1\times 10^{-3})$         & $0.193(\pm1.7\times 10^{-3})$     & $0.070 (\pm9.1\times 10^{-4})$ \\
+        High-capacity LSTM  & $\num{10}$                 & $0.157 (\pm2.0\times 10^{-3})$         & $0.199(\pm1.9\times 10^{-3})$     & $0.065 (\pm1.9\times 10^{-3})$ \\
+        Average Difference  & $\num{10}$                 & $-0.038$                               & $0.006$                           & $-0.005$ \\
         \hline
-        LSTM                & $1$                  & $1.366 (\pm8.6\times 10^{-3})$         & $0.781(\pm6.0\times 10^{-3})$     & $0.129 (\pm5.0\times 10^{-3})$ \\
-        High-capacity LSTM  & $1$                  & $1.354 (\pm2.7\times 10^{-2})$         & $0.795(\pm8.3\times10^{-2})$      & $0.149 (\pm2.7\times 10^{-2})$ \\
-        Average Difference  & $1$                  & $-0.012$                               & $0.014$                           & \textcolor{red}{$0.020$} \\
+        LSTM                & $\num{1}$                  & $1.366 (\pm8.6\times 10^{-3})$         & $0.781(\pm6.0\times 10^{-3})$     & $0.129 (\pm5.0\times 10^{-3})$ \\
+        High-capacity LSTM  & $\num{1}$                  & $1.354 (\pm2.7\times 10^{-2})$         & $0.795(\pm8.3\times10^{-2})$      & $0.149 (\pm2.7\times 10^{-2})$ \\
+        Average Difference  & $\num{1}$                  & $-0.012$                               & $0.014$                           & \textcolor{red}{$0.020$} \\
         \bottomrule

### 2025-02-21 project3/draft.tex
new

@@
 \begin{itemize}
-    \item   \textbf{source domain}: $\mathcal{D}_{\text{So}} = \{\mathcal{X}_{\text{So}}, F_{\text{So}}(\mathbf{X})\}$
-    \item   \textbf{source task}: $\mathcal{T}_{\text{So}} = \{\mathcal{Y}_{\text{So}}, f_{\text{So}}(\cdot)\}$
-    \item   \textbf{target domain}: $\mathcal{D}_{\text{Ta}} = \{\mathcal{X}_{\text{Ta}}, F_{\text{Ta}}(\cdot)\}$
-    \item   \textbf{target task}: $\mathcal{T}_{\text{Ta}} = \{\mathcal{Y}_{\text{Ta}}, f_{\text{Ta}}(\cdot)\}$
+    \item   \textbf{source domain}: $\mathcal{D}_{\text{So}} = \{\mathcal{X}_{\text{So}}, F_{\text{So}}(\mathbf{X})\}$,
+    \item   \textbf{source task}: $\mathcal{T}_{\text{So}} = \{\mathcal{Y}_{\text{So}}, f_{\text{So}}(\cdot)\}$,
+    \item   \textbf{target domain}: $\mathcal{D}_{\text{Ta}} = \{\mathcal{X}_{\text{Ta}}, F_{\text{Ta}}(\cdot)\}$,
+    \item   \textbf{target task}: $\mathcal{T}_{\text{Ta}} = \{\mathcal{Y}_{\text{Ta}}, f_{\text{Ta}}(\cdot)\}$,
 \end{itemize}
@@
     \begin{equation}
-        \theta_{\text{So}} = \min_{\theta} \frac{1}{M_{\text{So}}} \sum_{i=1}^{M_{\text{So}}} \left( f_{\text{So}}(X_{\text{So}}^{(i)}; \theta) - L_{\text{So}}^{(i)} \right)^2
+        \theta_{\text{So}} = \min_{\theta} \frac{1}{M_{\text{So}}} \sum_{i=1}^{M_{\text{So}}} \left( f_{\text{So}}(X_{\text{So}}^{(i)}; \theta) - L_{\text{So}}^{(i)} \right)^2.
     \end{equation}
@@
     \[
-    \theta_{\text{Ta}} \gets \theta_{\text{So}}
+    \theta_{\text{Ta}} \gets \theta_{\text{So}}.
     \]
@@
     \begin{equation}
-        \theta_{\text{Ta}} = \min_{\theta} \frac{1}{M_{\text{Ta}}} \sum_{i=1}^{M_{\text{Ta}}} \left( f_{\text{Ta}}(X_{\text{Ta}}^{(i)}; \theta) - L_{\text{Ta}}^{(i)} \right)^2
+        \theta_{\text{Ta}} = \min_{\theta} \frac{1}{M_{\text{Ta}}} \sum_{i=1}^{M_{\text{Ta}}} \left( f_{\text{Ta}}(X_{\text{Ta}}^{(i)}; \theta) - L_{\text{Ta}}^{(i)} \right)^2.
     \end{equation}
 
-    \STATE \textbf{Output:} Final adapted LSTM metamodel $f_{\text{Ta}}(\cdot; \theta_{\text{Ta}})$ for the target task
+    \STATE \textbf{Output:} Final adapted LSTM metamodel $f_{\text{Ta}}(\cdot; \theta_{\text{Ta}})$ for the target task.
 \end{algorithmic}
@@
         \begin{equation}
-            \theta_{\text{So}} = [\theta_0, \theta_1] = \min_{\theta} \frac{1}{M_{\text{So}}} \sum_{i=1}^{M_{\text{So}}} \left( f_{\text{So}}(X_{\text{So}}^{(i)}; \theta) - L_{\text{So}}^{(i)} \right)^2
+            \theta_{\text{So}} = [\theta_0, \theta_1] = \min_{\theta} \frac{1}{M_{\text{So}}} \sum_{i=1}^{M_{\text{So}}} \left( f_{\text{So}}(X_{\text{So}}^{(i)}; \theta) - L_{\text{So}}^{(i)} \right)^2.
         \end{equation}
@@
         \[
-        \theta_{\text{Ta}} \gets \theta_{\text{So}} = [\theta_0, \theta_1]
+        \theta_{\text{Ta}} \gets \theta_{\text{So}} = [\theta_0, \theta_1].
         \]
@@
         \begin{equation}
-            \theta_{\text{Ta}} = \min_{\theta_1} \frac{1}{M_{\text{Ta}}} \sum_{i=1}^{M_{\text{Ta}}} \left( f_{\text{Ta}}(X_{\text{Ta}}^{(i)}; [\theta_0, \theta_1]) - L_{\text{Ta}}^{(i)} \right)^2
+            \theta_{\text{Ta}} = \min_{\theta_1} \frac{1}{M_{\text{Ta}}} \sum_{i=1}^{M_{\text{Ta}}} \left( f_{\text{Ta}}(X_{\text{Ta}}^{(i)}; [\theta_0, \theta_1]) - L_{\text{Ta}}^{(i)} \right)^2.
         \end{equation}
 
-        \STATE \textbf{Output:} Final adapted LSTM metamodel $f_{\text{Ta}}(\cdot; [\theta_0, \theta_1])$ for the target task
+        \STATE \textbf{Output:} Final adapted LSTM metamodel $f_{\text{Ta}}(\cdot; [\theta_0, \theta_1])$ for the target task.
     \end{algorithmic}
@@
 \end{equation}
-
 where MSE loss function is used as the error metric, and $f_i(\cdot; \theta_0, \theta_1, \dots, \theta_K)$ is the output of the network for task $k$.
@@
         \begin{equation} \label{eq3:multiTaskLoss}
-            \min_{\theta_0, \{\theta_k\}_{k=1}^K} \sum_{k=1}^K \frac{1}{M_k} \sum_{i=1}^{M_k} \left( f_i(X_k^{(i)}; \theta_0, \theta_k) - L_k^{(i)} \right)^2
+            \min_{\theta_0, \{\theta_k\}_{k=1}^K} \sum_{k=1}^K \frac{1}{M_k} \sum_{i=1}^{M_k} \left( f_i(X_k^{(i)}; \theta_0, \theta_k) - L_k^{(i)} \right)^2.
         \end{equation}
@@
 
-        \STATE \textbf{Output:} Trained multi-task LSTM metamodel $f(\cdot; \theta_0, \{\theta_k\}_{k=1}^K)$ for all $K$ tasks
+        \STATE \textbf{Output:} Trained multi-task LSTM metamodel $f(\cdot; \theta_0, \{\theta_k\}_{k=1}^K)$ for all $K$ tasks.
     \end{algorithmic}
@@
         \begin{equation}
-            \min_{\theta_0, \{\theta_k\}_{k=1}^K} \sum_{k=1}^K \frac{1}{M_k} \sum_{i=1}^{M_k} \left( f_i(X_k^{(i)}; \theta_0, \theta_k) - L_k^{(i)} \right)^2
+            \min_{\theta_0, \{\theta_k\}_{k=1}^K} \sum_{k=1}^K \frac{1}{M_k} \sum_{i=1}^{M_k} \left( f_i(X_k^{(i)}; \theta_0, \theta_k) - L_k^{(i)} \right)^2.
         \end{equation}
@@
         \begin{equation}
-            \min_{\theta_{\text{Ta}}} \frac{1}{M_{\text{Ta}}} \sum_{i=1}^{M_{\text{Ta}}} \left( f_{\text{Ta}}(X_{\text{Ta}}^{(i)}; \theta_0, \theta_{\text{Ta}}) - L_{\text{Ta}}^{(i)} \right)^2
+            \min_{\theta_{\text{Ta}}} \frac{1}{M_{\text{Ta}}} \sum_{i=1}^{M_{\text{Ta}}} \left( f_{\text{Ta}}(X_{\text{Ta}}^{(i)}; \theta_0, \theta_{\text{Ta}}) - L_{\text{Ta}}^{(i)} \right)^2.
         \end{equation}
@@
     \includegraphics[width=\textwidth]{./project3/tikz/mtl.pdf}
-    \caption{Multi-task Learning Framework for VA Contracts}
+    \caption{Multi-task learning framework for VA contracts}
     \label{fig3:mtl}

### 2025-02-21 uw-ethesis-frontpgs.tex
edited
new

@@
 
-%   \noindent
-% \begin{tabbing}
-% Internal-External Member: \=  \kill % using longest text to define tab length
-% Internal-External Member: \> John Smith \\
-% \> Professor, Dept. of XX, University of ABC \\
-% \end{tabbing}
-%   \bigskip
+  \noindent
+\begin{tabbing}
+Internal-External Member: \=  \kill % using longest text to define tab length
+Internal-External Member: \> Yuying Li \\
+\> Professor, School of Computer Science \\
+\> University of Waterloo \\
+\end{tabbing}
+  \bigskip
 
-%   \noindent
-% \begin{tabbing}
-% Internal-External Member: \=  \kill % using longest text to define tab length
-% Other Member(s): \> John Smith \\
-% \> Professor, Dept. of XX, University of ABC \\
-% \end{tabbing}
+  \noindent
+\begin{tabbing}
+Internal-External Member: \=  \kill % using longest text to define tab length
+Other Member(s): \>  Emiliano Valdez \\
+\> Professor, Dept. of Mathematics \\
+\> University of Connecticut \\
+\end{tabbing}
 
@@
 This research contributes to the advancement of risk management practices for complex actuarial products and financial derivatives.
-By leveraging advanced machine learning techniques, the thesis offers a practical and scalable solution for insurers to perform timely and accurate risk assessments.
+By leveraging advanced machine learning techniques, this thesis offers a practical and scalable solution for insurers to perform timely and accurate risk assessments.
 The integration of long short-term memory metamodels and transfer learning into a nested simulation framework represents a major step forward toward more efficient, adaptable, and robust methodologies in actuarial science and quantitative finance.
@@
 
-Additionally, I extend my sincere thanks to my best friends, who have stood by me during the most challenging times. 
+Additionally, I extend my sincere thanks to my best friends.
 Their unwavering support and encouragement have been a constant source of strength that has helped me overcome obstacles and maintain my motivation throughout this process. 

### 2025-03-17 pre_private/pre.tex
1

@@
 
-$$\rho(L) = \rho(L(X)), \;\;\; L(X) = \mathbb{E}\left[ Y|X=x \right]\vert_{x=X}  $$
+$$\rho(L) = \rho(L(X)), \;\;\; L(X) = \mathbb{E}\left[ Y|X=x \right]\vert_{x=X}.  $$
 
@@
 \begin{itemize}
-    \item Outer level: generates underlying risk factors (outer scenarios), $X_i \sim F_X$
-    \item Inner level: generates scenario-wise samples of portfolio losses (inner replications), $Y_{ij} \sim F_{Y|X_i}$
+    \item Outer level: generates underlying risk factors (outer scenarios), $X_i \sim F_X$.
+    \item Inner level: generates scenario-wise samples of portfolio losses (inner replications), $Y_{ij} \sim F_{Y|X_i}$.
+    \item Total simulation budget: $\Gamma = M \cdot N$.
 \end{itemize}
@@
 
+\note{In the context of quantitative risk management, nested simulation is used for risk evaluation of financial derivatives and insurance products.}
+\note{The nested structure is due to the fact that the loss random variable is in the form of a conditional expectation of the portfolio loss given the underlying risk factors.}
+\note{In our problems, the loss random variable $L$ depends on the risk factors $X$ and is the conditional expectation of the portfolio loss given $X$.}
+\note{Estimating a risk measure, $\rho(L)$, involves two levels of Monte Carlo simulations: outer level generates underlying risk factors, and inner level generates scenario-wise samples of portfolio losses.}
+\note{The nested structure makes the estimation computationally expensive.}
+\note{In this thesis, we focus on examining and improving the efficiency of nested simulation procedures mostly using supervised learning metamodels.}
+
 \end{frame}
@@
 \begin{itemize}
-    \item Smooth $h$, e.g., quadratic tracking error
-
-    $$ \rho(L) = \mathbb{E} \left[ (L - b)^2 \right] $$
-
-    \item hockey-stick $h$: mean excess loss
-
-    $$ \rho(L) = \mathbb{E} \left[ L \cdot \mathbbm{1}_{\{L \geq u\}} \right] $$
-
-    \item indicator $h$: probability of large loss
-
-    $$ \rho(L) = \mathbb{E} \left[ \mathbbm{1}_{\{L \geq u\}} \right] $$
-
-    \item Value at Risk (VaR)
-
-    $$ \rho_\alpha(L) = Q_\alpha(L) = \inf \{ u: \mathbb{P}(L \leq u) \geq \alpha \} $$
-
-    \item Conditional Value at Risk (CVaR) \footnotemark
-
-    $$ \rho_\alpha(L) = \mathbb{E} \left[ L \vert L \geq Q_\alpha(L) \right] $$
+    \item Smooth $h$, e.g., quadratic tracking error,
+
+    $$ \rho(L) = \mathbb{E} \left[ (L - b)^2 \right]; $$
+
+    \item hockey-stick $h$: mean excess loss,
+
+    $$ \rho(L) = \mathbb{E} \left[ L \cdot \mathbbm{1}_{\{L \geq u\}} \right]; $$
+
+    \item indicator $h$: probability of large loss,
+
+    $$ \rho(L) = \mathbb{E} \left[ \mathbbm{1}_{\{L \geq u\}} \right]; $$
+
+    \item Value at Risk (VaR),
+
+    $$ \rho_\alpha(L) = Q_\alpha(L) = \inf \{ u: \mathbb{P}(L \leq u) \geq \alpha \}; $$
+
+    \item Conditional Value at Risk (CVaR) \footnotemark,
+
+    $$ \rho_\alpha(L) = \mathbb{E} \left[ L \vert L \geq Q_\alpha(L) \right]. $$
 
@@
     \footnotetext{Note: If $Q_\alpha(L)$ falls in a probability mass, $\rho(L) = \frac{(\beta - \alpha)Q_\alpha(L) + (1- \beta) \mathbb{E} \left[ L \vert L \geq Q_\alpha(L) \right]}{1-\alpha}$.}
+
+\note{We consider different types of risk measures in this thesis.}
+\note{The first three are in expectation form, and the last two are quantile-based risk measures.}
+\note{The difference between the first three is the choice of the function $h$.}
+\note{$h$ can be a smooth function, a hockey-stick function, or an indicator function.}
+\note{The examples of risk measures are quadratic tracking error, mean excess loss, and probability of large loss.}
+\note{The last two are value at risk and conditional value at risk, which are widely used in practice.}
+\note{Note that the definition of CVaR requires the knowledge of the Value at Risk.}
 
@@
 
+\note{In our first project, we focus on comparing existing nested simulation procedures for different types of risk measures.}
+\note{They differ in the way they estimate $L(X_i)$, the portfolio loss conditional on the risk factors $X_i$.}
+\note{The standard nested simulation procedure uses the inner sample mean under that scenarioto estimate $L(X_i)$.}
+\note{The optimal growth order of $M$ and $N$ is found by \citet{gordy2010nested}.}
+\note{For a growing total simulation budget $\Gamma$, $M$ should grow in the order of $\Gamma^{2/3}$, and $N$ should grow in the order of $\Gamma^{1/3}$.}
+\note{For a finite-sample case, the bootstrap method is used to estimate the optimal $M$ and $N$ by \citet{zhang2021bootstrap}.}
+\note{Since the standard procedure only uses the information from the same scenario, it is potentially \textbf{wasteful} use of budget.}
+\note{Subsequent works focus on improving the efficiency of nested simulation by pooling inner replications from different outer scenarios.}
+
 \end{frame}
@@
 \end{itemize}
+
+\note{Pooling can happen in different ways, and the key idea is to use the information from different outer scenarios to improve the efficiency of nested simulation.}
+\note{There are two main streams of research in this direction.}
+\note{The first stream is to use a supervised learning metamodel to approximate the simulation.}
+\note{A metamodel is a model of model, or a surrogate model for the simulation model.}
+\note{Here, the metamodel is used to approximate the inner simulation model, by treating it as a black-box function.}
+\note{The second stream is to use importance sampling to improve the efficiency of nested simulation.}
+\note{The likelihood ratio weights are used to weight the inner replications from different outer scenarios.}
+\note{This end up improving the efficiency of nested simulation as well.}
 
@@
 
+\note{A supervised learning based nested simulation procedure is implemented following these steps.}
+\note{First, the user runs the standard nested simulation procedure to generate a set of outer scenarios and inner replications.}
+\note{Then, the outer scenarios and inner sample means can be treated as features and labels.}
+\note{Their relationship is then approximated by a supervised learning metamodel.}
+\note{Finally, the trained metamodel is used to make predictions for all $X \in \mathcal{X}$.}
+\note{In other words, instead of using the inner sample mean to estimate $L(X_i)$, we use the trained metamodel to make predictions of the portfolio loss.}
+\note{These loss predictions are then used to calculate the risk measures of interest.}
+\note{For most research in this area, the focus is on the convergence rate of the risk measure estimator in terms of the simulation budget.}
+\note{However, in this thesis, we note that there are other important aspects to consider, such as the cost of pooling that may come from metamodel training and validation.}
+
 \end{frame}
@@
 Interested in convergence order as $\Gamma \to \infty$
+
+\note{For a nested simulation procedure with a given total simulation budget $\Gamma$, the objective is to find the optimal $M$ and $N$ that minimizes the MSE of the estimator.}
+\note{Thus, in this thesis, we compare the asymptotic convergence rates of different nested simulation procedures using their MSE.}
+\note{Here, $\hat{\rho}_{M, N}$ is the risk measure estimator using the nested simulation procedure with $M$ outer scenarios and $N$ inner replications.}
+\note{We also consider the cost of pooling that may come from metamodel training and validation in our numerical experiments.}
 
@@
     \end{itemize}
+
+\note{We start by comparing the asymptotic convergence rates of different nested simulation procedures.}
+\note{}
 
@@
 
-\begin{frame}{Learning Lapse Features}
-    \begin{figure}[ht!]
+\begin{frame}{The Effect of Number of Training Samples}
+    \begin{figure}[ht]
         \centering
@@
             \includegraphics[width=\textwidth]{../project3/figures/figure1a.png}
-            \caption{Extensive Training on Target Task}
+            \caption{50000 samples}
         \end{subfigure}
@@
             \includegraphics[width=\textwidth]{../project3/figures/figure1b.png}
-            \caption{Without TL}
+            \caption{2000 samples}
         \end{subfigure}
-        \caption{Direct training on RS-GBM GMMB with static lapse}
-    \end{figure}
-\end{frame}
-
-\begin{frame}{Learning Lapse Features}
-    \begin{figure}[ht!]
+        \caption{Learning curves of GMMB contracts with static lapse}
+    \end{figure}
+
+\end{frame}
+
+\begin{frame}{Learning Lapse Features using Transfer Learning}
+
+    \begin{figure}[ht]
         \centering
@@
             \includegraphics[width=\textwidth]{../project3/figures/figure1c.png}
-            \caption{With Fine-tuning}
+            \caption{Fine-tuning}
         \end{subfigure}
@@
             \includegraphics[width=\textwidth]{../project3/figures/figure1d.png}
-            \caption{With Layer Freezing}
+            \caption{Layer Freezing}
         \end{subfigure}
-        \caption{TL on RS-GBM GMMB with static lapse}
-    \end{figure}
-
+        \caption{Learning curves of GMMB contracts with static lapse}
+    \end{figure}
+
+\end{frame}
+
+\begin{frame}{Learning Curves: Learning Dynamic Lapse}
+
+    \begin{figure}[ht]
+        \centering
+        \begin{subfigure}{0.48\textwidth}
+            \includegraphics[width=\textwidth]{../project3/figures/figure2a.png}
+            \caption{No Lapse}
+        \end{subfigure}
+        \begin{subfigure}{0.48\textwidth}
+            \includegraphics[width=\textwidth]{../project3/figures/figure2b.png}
+            \caption{Static Lapse}
+        \end{subfigure}
+        \caption{Learning curves of GMMB contracts with dynamic lapse}
+    \end{figure}
+
+\end{frame}
+
+    \begin{frame}{Results: Accuracy Comparison}
+    \begin{table}
+    \begin{tabular}{lcccc}
+    \toprule
+    \textbf{Lapse Type} & \textbf{Extensive} & \textbf{Fine-tuning} & \textbf{Layer Freezing} & \textbf{Without TL} \\
+    \midrule
+    No Lapse & N/A & 0.4894 & \textbf{0.3361} & N/A \\
+    Static Lapse & N/A & 0.0794 & 0.0763 & N/A \\
+    Dynamic Lapse & \textbf{0.0587} & N/A & N/A & \textbf{0.2950} \\
+    \bottomrule
+    \end{tabular}
+    \end{table}
+
+    \textit{Comparison of different TL methods on GMMB contracts (best MSE values)}
+    \end{frame}
+
+    \begin{frame}{Learning Curves: Effect of Similarity}
+    \begin{columns}
+    \column{0.5\textwidth}
+    \includegraphics[height=0.8\textheight]{../project3/figures/figure3a.png}
+    \column{0.5\textwidth}
+    \includegraphics[height=0.8\textheight]{../project3/figures/figure3b.png}
+    \end{columns}
+
+    \textit{The effect of similarity between source and target on the convergence speed}
+    \begin{itemize}
+        \item \textit{Left: from No Lapse; right: from Static Lapse}
+    \end{itemize}
+    \end{frame}
+
+    \begin{frame}{Transfer Knowledge to other Contract Types}
+    \textbf{From GMMB to GMWB Contract}
+    \end{frame}
+
+    \begin{frame}{Learning Curves: Transfer Knowledge to other Contract Types}
+    \begin{columns}
+    \column{0.5\textwidth}
+    \includegraphics[height=0.8\textheight]{../project3/figures/figure4a.png}
+    \column{0.5\textwidth}
+    \includegraphics[height=0.8\textheight]{../project3/figures/figure4b.png}
+    \end{columns}
+
+    \textit{Learning curves of GMWB contracts}
+    \begin{itemize}
+        \item \textit{Left: 50000 samples; right: 2000 samples}
+    \end{itemize}
+    \end{frame}
+
+    \begin{frame}{Learning Curves: Effect of Similarity}
+    \begin{columns}
+    \column{0.5\textwidth}
+    \includegraphics[height=0.8\textheight]{../project3/figures/figure4c.png}
+    \column{0.5\textwidth}
+    \includegraphics[height=0.8\textheight]{../project3/figures/figure4d.png}
+    \end{columns}
+
+    \textit{Comparison of different TL methods on GMWB contracts}
+    \begin{itemize}
+        \item \textit{Left: fine-tuning; right: layer freezing}
+    \end{itemize}
+    \end{frame}
+
+    \begin{frame}{Performance Comparison (GMMB → GMWB)}
+    \begin{table}
+    \begin{tabular}{lcc}
+    \toprule
+    \textbf{Model} & \textbf{Training MSE} & \textbf{True MSE} \\
+    \midrule
+    Without TL & 0.3588 & 0.4188 \\
+    Fine Tuning & 0.1690 & 0.1780 \\
+    Layer Freezing & 0.1828 & 0.2295 \\
+    Extensive Training & 0.0853 & 0.0726 \\
+    \bottomrule
+    \end{tabular}
+    \end{table}
+
+    \begin{itemize}
+        \item Fine-tuning outperforms layer freezing for dissimilar tasks
+        \item Both TL methods better than training from scratch
+        \item Extensive training still superior with abundant data
+    \end{itemize}
+    \end{frame}
+
+    \begin{frame}{Practical Implementation}
+    \begin{itemize}
+        \item \textbf{Framework}: TensorFlow/PyTorch implementation
+        \item \textbf{Workflow}:
+        \begin{enumerate}
+            \item Train base model on source contract
+            \item Freeze early layers
+            \item Fine-tune later layers on target contract
+            \item Deploy for production use
+        \end{enumerate}
+    \end{itemize}
+
+    \textbf{PyTorch} is recommended.
+    \begin{itemize}
+        \item It is more flexible and easier to customize
+        \item It is more intuitive and easier to understand 
+        \item It is more efficient and easier to debug
+    \end{itemize}
+    \end{frame}
+
+    \begin{frame}{Multi-task Learning}
+    \includegraphics[width=0.9\textwidth]{../project3/figures/mtl.png}
+
+    \begin{itemize}
+        \item LSTM layers shared across multiple tasks
+        \item Task-specific fully connected layers
+        \item Objective: Minimize sum of loss functions across all tasks
+    \end{itemize}
+    \end{frame}
+
+    \begin{frame}{Multi-task Learning Framework}
+    \textbf{Input}: Set of $K$ tasks $\{\mathcal{T}_k\}_{k=1}^K$ with datasets $\mathcal{D}_k = \{(X_k^{(i)}, L_k^{(i)})\}_{i=1}^{M_k}$, shared parameters $\theta_0$, and task-specific parameters $\theta_k$ for each task $k$
+
+    \textbf{Algorithm}:
+    \begin{enumerate}
+        \item Train the multi-head LSTM metamodel on all $K$ tasks simultaneously by minimizing the multi-task loss function:
+        \begin{equation}
+            \min_{\theta_0, \{\theta_k\}_{k=1}^K} \sum_{k=1}^K \frac{1}{M_k} \sum_{i=1}^{M_k} \left( f_i(X_k^{(i)}; \theta_0, \theta_k) - L_k^{(i)} \right)^2
+        \end{equation}
+        \item Update both the shared parameters $\theta_0$ and task-specific parameters $\{\theta_k\}_{k=1}^K$ simultaneously using backpropagation and gradient descent with learning rate $\alpha$
+    \end{enumerate}
+
+    \textbf{Output}: Trained multi-task LSTM metamodel $f(\cdot; \theta_0, \{\theta_k\}_{k=1}^K)$ for all $K$ tasks
+    \end{frame}
+
+    \begin{frame}{Multi-task Learning: GMMB and GMWB}
+    \begin{columns}
+    \column{0.5\textwidth}
+    \includegraphics[height=0.8\textheight]{../project3/figures/figure5a.png}
+    \column{0.5\textwidth}
+    \includegraphics[height=0.8\textheight]{../project3/figures/figure5b.png}
+    \end{columns}
+
+    \textit{Multi-task learning of GMMB and GMWB}
+    \begin{itemize}
+        \item \textit{Left: total MSE; right: individual MSE}
+    \end{itemize}
+    \end{frame}
+
+    \begin{frame}{Multi-task Learning: GMMB and GMWB}
+    \begin{columns}
+    \column{0.5\textwidth}
+    \includegraphics[height=0.8\textheight]{../project3/figures/figure5c.png}
+    \column{0.5\textwidth}
+    \includegraphics[height=0.8\textheight]{../project3/figures/figure5d.png}
+    \end{columns}
+
+    \textit{Training without multi-task learning}
+    \begin{itemize}
+        \item \textit{Left: GMMB; right: GMWB}
+    \end{itemize}
+    \end{frame}
+
+    \begin{frame}{Challenges \& Limitations}
+    \begin{itemize}
+        \item Determining optimal layer freezing strategy
+        \item Handling significantly different contract structures
+        \item Quantifying uncertainty in transfer learning predictions
+        \item Regulatory acceptance of black-box approaches
+    \end{itemize}
+    \end{frame}
+
+    \begin{frame}{Conclusions}
+    \begin{itemize}
+        \item Transfer learning significantly improves metamodeling for VA contracts:
+        \begin{itemize}
+            \item Faster training convergence
+            \item Better prediction accuracy
+            \item Reduced computational requirements
+        \end{itemize}
+        \item Enables more frequent risk assessments and faster decision-making
+    \end{itemize}
+    \end{frame}
+
+    \begin{frame}{Future Directions}
+    \begin{itemize}
+        \item Incorporating domain knowledge into transfer process
+        \item Extension to other insurance and financial products
+        \item Multi-task learning with more than two tasks
+    \end{itemize}
     \end{frame}

### 2025-03-18 pre_private/pre.tex
12

--- 2025-02-20 pre_private/pre.tex
@@
 
-% \setbeameroption{show notes}
-% \setbeameroption{show notes on second screen=right}
-
-\title[\textbf{Resilient Machine Learning Approaches for Fast Risk Evaluation and Management in Financial Portfolios and Variable Annuities}]{Efficient Machine Learning Approaches for Fast Risk Evaluation of VAs}
+\setbeameroption{show notes}
+\setbeameroption{show notes on second screen=right}
+
+\title[Resilient ML for Fast Risk Evaluation of VAs]{\textbf{Resilient Machine Learning Approaches \\ for Fast Risk Evaluation and Management \\ of Financial Portfolios and Variable Annuities}}
 
@@
 \jointwork{Supervised by Prof. Tony Wirjanto and Prof. Mingbin Feng}
-\conference{Thesis Defense, University of Waterloo}
+\conference{Thesis Defense, \\ University of Waterloo}
 
@@
 
-$$\rho(L) = \rho(L(X)), \;\;\; L(X) = \mathbb{E}\left[ Y|X=x \right]\vert_{x=X}  $$
+$$\rho(L) = \rho(L(X)), \;\;\; L(X) = \mathbb{E}\left[ Y|X=x \right]\vert_{x=X}.  $$
+
+\vspace{10pt}
 
@@
 \begin{itemize}
-    \item Outer level: generates underlying risk factors (outer scenarios), $X_i \sim F_X$
-    \item Inner level: generates scenario-wise samples of portfolio losses (inner replications), $Y_{ij} \sim F_{Y|X_i}$
-\end{itemize}
-
-\textbf{Computationally expensive due to its nested structure.}
+    \item Outer: underlying risk factors (outer scenarios), $X_i \sim F_X$
+    \item Inner: scenario-wise losses (inner replications), $Y_{ij} \sim F_{Y|X_i}$
+    \item Total simulation budget: $\Gamma = M \cdot N$
+\end{itemize}
+
+\vspace{10pt}
+\textbf{Computationally expensive}
+
+\note{In the context of quantitative risk management, nested simulation is used for risk evaluation of financial derivatives and insurance products. \\}
+\note{The nested structure is due to the fact that the loss random variable is in the form of a conditional expectation of the portfolio loss given the underlying risk factors. \\}
+\note{In our problems, the loss random variable $L$ depends on the risk factors $X$ and is the conditional expectation of the portfolio loss given $X$. \\}
+\note{More specifically, $X$ is $d$-dimensional and $L$ is 1-dimensional. \\}
+\note{Estimating a risk measure, $\rho(L)$, involves two levels of Monte Carlo simulations: outer level generates underlying risk factors, and inner level generates scenario-wise samples of portfolio losses.
+\\}
+\note{The nested structure makes the estimation computationally expensive. \\}
+\note{In this thesis, we focus on examining and improving the efficiency of nested simulation procedures mostly using supervised learning metamodels.}
 
@@
 
-\end{frame}
-
-\section{Nested Simulation Procedures in Financial Engineering: A Selected Review}
+\note{We consider different types of risk measures in this thesis. \\}
+\note{The first three are in expectation form, and the last two are quantile-based risk measures. \\}
+\note{The difference between the first three is the choice of the function $h$. \\}
+\note{$h$ can be a smooth function, a hockey-stick function, or an indicator function. \\}
+\note{The examples of risk measures are quadratic tracking error, mean excess loss, and probability of large loss. \\}
+\note{The last two are value at risk and conditional value at risk, which are widely used in practice. \\}
+\note{Note that the definition of CVaR requires the knowledge of the Value at Risk.}
+
+\end{frame}
+
+\section[Nested Simulation Procedures]{Nested Simulation Procedures in Financial Engineering: A Selected Review}
 
@@
 
-\end{frame}
-
-\begin{frame}{Other Nested Simulation Procedures}
-
-Subsequent works focus on improving the efficiency of nested simulation:
-\begin{itemize}
-    \item Regression-based~\citep{broadie2015risk}
-    \item Kernel smoothing~\citep{hong2017kernel}
-    \item Likelihood ratio~\citep{feng2020optimal}
-    \item Kernel ridge regression~\citep{zhang2022sample}
-\end{itemize}
+\note{In our first project, we focus on comparing existing nested simulation procedures for different types of risk measures. \\}
+\note{They differ in the way they estimate $L(X_i)$, the portfolio loss conditional on the risk factors $X_i$. \\}
+\note{The standard nested simulation procedure uses the inner sample mean under that scenarioto estimate $L(X_i)$. \\}
+\note{The optimal growth order of $M$ and $N$ is found by \citet{gordy2010nested}. \\}
+\note{For a growing total simulation budget $\Gamma$, $M$ should grow in the order of $\Gamma^{2/3}$, and $N$ should grow in the order of $\Gamma^{1/3}$. \\}
+\note{For a finite-sample case, the bootstrap method is used to estimate the optimal $M$ and $N$ by \citet{zhang2021bootstrap}. \\}
+\note{Since the standard procedure only uses the information from the same scenario, it is potentially \textbf{wasteful} use of budget. \\}
+\note{Subsequent works focus on improving the efficiency of nested simulation by pooling inner replications from different outer scenarios.}
+
+\end{frame}
+
+% \begin{frame}{Other Nested Simulation Procedures}
+
+% Subsequent works focus on improving the efficiency of nested simulation:
+% \begin{itemize}
+%     \item Regression-based~\citep{broadie2015risk}
+%     \item Kernel smoothing~\citep{hong2017kernel}
+%     \item Likelihood ratio~\citep{feng2020optimal}
+%     \item Kernel ridge regression~\citep{zhang2022sample}
+% \end{itemize}
+
+% \vspace{10pt}
+
+% \textbf{Key ideas:} 
+% \begin{itemize}
+%     \item Pool inner replications from different outer scenarios 
+%     \item Use metamodels to approximate the inner simulation model
+% \end{itemize}
+
+% \note{Pooling can happen in different ways, and the key idea is to use the information from different outer scenarios to improve the efficiency of nested simulation. \\}
+% \note{There are two main streams of research in this direction. \\}
+% \note{The first stream is to use a supervised learning metamodel to approximate the simulation. \\}
+% \note{A metamodel is a model of model, or a surrogate model for the simulation model. \\}
+% \note{Here, the metamodel is used to approximate the inner simulation model, by treating it as a black-box function. \\}
+% \note{The second stream is to use importance sampling to improve the efficiency of nested simulation. \\}
+% \note{The likelihood ratio weights are used to weight the inner replications from different outer scenarios. \\}
+% \note{This end up improving the efficiency of nested simulation as well.}
+
+% \end{frame}
+
+\begin{frame}{Metamodeling Approach}
+
+We focus on procedures that \textbf{pool} with \textbf{supervised learning metamodels}.
 
@@
 
-\textbf{Key ideas:} 
-\begin{itemize}
-    \item Pool inner replications from different outer scenarios 
-    \item Use metamodeling techniques to approximate the inner simulation model
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Metamodeling Approach}
-
-In this thesis, we focus on procedures that use \textbf{supervised learning metamodels} to approximate the inner simulation model.
-
-\begin{itemize}
-    \item Treat the inner simulation as a black-box function
+\begin{itemize}
+    \item Treat inner simulation as a black-box function
     \item Approximate $L(\cdot)$ with $\hat{L}^{\text{SL}}_{M, N}(\cdot)$
-    \item Train with a set of feature-label pairs generated from the standard procedure:
+    \item Train with feature-label pairs generated by simulation:
     $$\{(X_i, \hat{L}_{N, i}) \vert i=1, \ldots, M, j=1, \ldots, N\}$$
-    \item Use trained metamodel to make predictions for all $X \in \mathcal{X}$
-\end{itemize}
-
+    \item Use metamodel predictions to estimate risk measures
+\end{itemize}
+
+\vspace{10pt}
 There are \textbf{computational costs} associated with pooling inner replications.
 
-\end{frame}
-
-\begin{frame}{Problem Statement}
-
-Minimize mean squared error (MSE) of the estimator subject to total simulation budget:
+\note{A supervised learning based nested simulation procedure is implemented following these steps. \\}
+\note{First, the user runs the standard nested simulation procedure to generate a set of outer scenarios and inner replications. \\}
+\note{Then, the outer scenarios and inner sample means can be treated as features and labels. \\}
+\note{Their relationship is then approximated by a supervised learning metamodel. \\}
+\note{Finally, the trained metamodel is used to make predictions for all $X \in \mathcal{X}$. \\}
+\note{In other words, instead of using the inner sample mean to estimate $L(X_i)$, we use the trained metamodel to make predictions of the portfolio loss. \\}
+\note{These loss predictions are then used to calculate the risk measures of interest. \\}
+\note{For most research in this area, the focus is on the convergence rate of the risk measure estimator in terms of the simulation budget. \\}
+\note{However, in this thesis, we note that there are other important aspects to consider, such as the cost of pooling that may come from metamodel training and validation. }
+
+\end{frame}
+
+% \begin{frame}{Problem Statement}
+
+% Minimize mean squared error (MSE) of the estimator subject to simulation budget $\Gamma$:
+
+% \begin{align*}
+% \min_{M, N} ~~~ \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] \\
+% \text{ subject to } M \cdot N = \Gamma
+% \end{align*}
+
+% Interested in convergence order as $\Gamma \to \infty$
+
+% \note{For a nested simulation procedure with a given total simulation budget $\Gamma$, the objective is to find the optimal $M$ and $N$ that minimizes the MSE of the estimator. \\}
+% \note{Thus, in this thesis, we compare the asymptotic convergence rates of different nested simulation procedures using their MSE. \\}
+% \note{Here, $\hat{\rho}_{M, N}$ is the risk measure estimator using the nested simulation procedure with $M$ outer scenarios and $N$ inner replications. \\}
+% \note{We also consider the cost of pooling that may come from metamodel training and validation in our numerical experiments.}
+
+% \end{frame}
+
+\subsection{Theoretical Results}
+
+\begin{frame}{Asymptotic Convergence Rates of Different Procedures}
 
@@
 
-Interested in convergence order as $\Gamma \to \infty$
-
-\end{frame}
-
-\subsection{Theoretical Results}
-
-\begin{frame}{Asymptotic Convergence Rates of Different Procedures}
+    \vspace{10pt}
 
@@
 			\midrule
-			Standard Procedure	& \textcolor{red}{$\mathcal{O}(\Gamma^{-2/3})$} & \textcolor{red}{$\mathcal{O}(\Gamma^{-2/3})$} & $\mathcal{O}(\Gamma^{-2/3})$ \\
+			Standard Procedure	& \textcolor{color10_5}{$\mathcal{O}(\Gamma^{-2/3})$} & \textcolor{color10_5}{$\mathcal{O}(\Gamma^{-2/3})$} & $\mathcal{O}(\Gamma^{-2/3})$ \\
 			\midrule
@@
 			\midrule
-			Kernel Ridge Regression  		& \multicolumn{3}{c}{$\mathcal{O}(\Gamma^{-1})$} \\
+			Kernel Ridge Regression\footnotemark  		& \multicolumn{3}{c}{\textcolor{color10_3}{$\mathcal{O}(\Gamma^{-1})$}} \\
 			\midrule
@@
     \vspace{10pt}
-    \begin{itemize}
-        \item We show the asymptotic convergence rates of the standard procedure for smooth and hockey-stick $h$.
-        \item Only kernel smoothing depends on the asset dimension $d$.
-    \end{itemize}
+
+\note{We start by comparing the asymptotic convergence rates of different nested simulation procedures. \\}
+\note{These are the convergence rates of the MSE of the risk measure estimator when the total simulation budget $\Gamma$ goes to infinity, and when one follows the optimal growth order of $M$ and $N$.
+\\}
+\note{The standard procedure has the same convergence rate of $\mathcal{O}(\Gamma^{-2/3})$ for all types of $h$ considered.
+The rates in red are not available in the original works but are derived in this thesis.
+\\}
+\note{The regression-based procedure has $\mathcal{O}(\Gamma^{-1})$ convergence rate for smooth and hockey-stick $h$. \\}
+\note{It is achieved by only allowing $M$ to grow in the order of $\Gamma^{1}$. In their experiments, $N$ is set to equal a value of $1$. \\}
+\note{The kernel smoothing procedure is the only procedure that depends on the asset dimension $d$. \\}
+\note{When risk factor $X$ is high-dimensional, the kernel smoothing procedure may converge slower than the standard procedure. \\}
+\note{The kernel ridge regression procedure and likelihood ratio procedure have the same convergence rate as the regression-based procedure. \\}
+\note{However, as we will see in the numerical experiments, their additional cost of pooling inner replications may offset their benefit of fast convergence rate. \\}
+\note{Additionally for KRR, the authors analyze convergence of absolute error in probabilistic order instead of MSE.}
 
@@
 \begin{frame}{Key Theoretical Results}
-
-\textbf{Observations:}
-\begin{itemize}
-\item Most literature focuses on the MSE of $\hat{\rho}$.
-\item \citet{wang2022smooth} analyze convergence of absolute error in probabilistic order.
-\end{itemize}
-
-\vspace{10pt}
 
@@
 
-\end{frame}
-
-\begin{frame}{Key Theoretical Results}
-
 \begin{block}{Theorem}
@@
 
-\begin{itemize}
-    \item First result to draw connection between MSE and probabilistic order convergence.
-    \item Applicable to any nested simulation procedure.
-    \item Convergence in MSE implies convergence in probabilistic order.
-\end{itemize}
-
-\end{frame}
+\note{In most theoretical works, the focus is on the convergence rate of the MSE of the risk measure estimator. \\}
+\note{However, for KRR, the authors analyze convergence of absolute error in probabilistic order. \\}
+\note{One of the contributions of this thesis is to bridge the gap between MSE and absolute error convergence. \\}
+\note{Let's first define the convergence in MSE and the convergence in probabilistic order. \\}
+\note{The convergence in MSE is the convergence of the MSE of the risk measure estimator to the true risk measure, that is, $\hat{\rho}_{\Gamma}$ minus $\rho$ squared. \\}
+\note{The convergence in probabilistic order is the convergence of the absolute error of the risk measure estimator to the true risk measure, that is, $|\hat{\rho}_{\Gamma} - \rho|$ to 0 in probability.
+\\}
+\note{We show that the convergence rate of the MSE of the risk measure estimator implies the convergence rate of the absolute error in probabilistic order. \\}
+\note{We will also show that the converse is not necessarily true.}
+
+\end{frame}
+
+% \begin{frame}{Key Theoretical Results}
+
+% \begin{block}{Theorem}
+%     If $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $\xi$, then $\hat{\rho}_{\Gamma}$ converges in probabilistic order to $\rho$ in order $\frac{\xi}{2}$.
+% \end{block}
+
+% \begin{itemize}
+%     \item First result to draw connection between MSE and probabilistic order convergence.
+%     \item Applicable to any nested simulation procedure.
+%     \item Convergence in MSE implies convergence in probabilistic order.
+% \end{itemize}
+
+% \note{In the thesis, we provide a proof for the theorem above. \\}
+% \note{Here I will give the intuition for the proof. \\}
+% \note{The proof is based on the idea of splitting the expectation into two parts: the tail and the non-tail components. \\}
+% \note{The non-tail component does not impact the type of convergence. \\}
+% \note{Writing the tail component in an integral form shows that the convergence in MSE is stronger than the convergence in probabilistic order. \\}
+% \note{The proof is provided in the thesis. \\}
+% \note{Therefore, we have shown that the result of~\cite{wang2022smooth} is slightly weaker than the results shown in other works. }
+
+% \end{frame}
 
@@
 
-And their empirical convergence stable across different:
+And their empirical convergence across different:
 \begin{itemize}
@@
 
+\note{Previously, we worked on the asymptotic convergence rates of different nested simulation procedures. \\}
+\note{In practice, the total simulation budget is finite.}
+\note{When the budget is finite, the theoretical convergence rate may not be the only thing we should consider. \\}
+\note{We should also consider the cost of pooling itself. \\}
+\note{The additional cost of pooling inner replications is not considered in the theoretical analysis of the previous works. \\}
+\note{Neither it is mentioned in their numerical experiments. \\}
+\note{More specifically, we have found that different research uses different numerical experiments to show the empirical rate of different procedures. \\}
+\note{We aim to provide a fair and comprehensive analysis of the finite-sample performance of different nested simulation procedures. \\}
+\note{The following numerical experiments test the empirical convergence rates of different nested simulation procedures across different risk measures, option types, asset dimensions, and asset models.}
+
 \end{frame}
@@
 
-\end{frame}
-
-\begin{frame}{Sensitivity to Asset Dimension}
-
-\begin{figure}
-    \includegraphics[width=\textwidth]{../project1/figures/figure2a.png}
-\end{figure}
-
-\begin{itemize}
-    \item Standard, KRR, and likelihood ratio procedures are dimension-independent
-    \item Kernel smoothing and regression show sensitivity to dimension, but in different ways
-\end{itemize}
-
-\end{frame}
+\note{This figure shows the performance of all 5 procedures in their estimation of the quadratic tracking error for the portfolio of European call options.}
+\note{It is a log-log plot of the MSE of the estimator versus the total simulation budget $\Gamma$.}
+\note{For each procedure, we run 1000 macro replications of Monte Carlo simulations with different total simulation budgets. \\}
+\note{For each data point on the plot, 1000 independent replications of the procedure are used to estimate the MSE. \\}
+\note{The slopes of the lines estimates the empirical convergence rates of the procedures. \\}
+\note{In the legend records the slopes of the lines and the corresponding asymptotic convergence rates of the procedures. \\}
+\note{In the most basic case, most procedures have their empirical convergence rates match their asymptotic convergence rates. \\}
+\note{However, as we will see after, this is not the case for all experiments. \\}
+\note{The following slides will show the sensitivity of the procedures to different factors. \\}
+
+\end{frame}
+
+% \begin{frame}{Sensitivity to Asset Dimension}
+
+% \begin{figure}
+%     \includegraphics[width=\textwidth]{../project1/figures/figure2a.png}
+% \end{figure}
+
+% \begin{itemize}
+%     \item Standard, KRR, and likelihood ratio procedures are dimension-independent
+%     \item Kernel smoothing and regression show sensitivity to dimension, but in different ways
+% \end{itemize}
+
+% \note{This figure shows the sensitivity of the procedures to the asset dimension. \\}
+% \note{The asset dimension is the dimension of the risk factors $X$. \\}
+% \note{Everything is the same as the previous figure, except that the asset dimension is varied from 1 to 2. \\}
+% \note{The standard, regression, KRR, and likelihood ratio procedures are dimension-independent. \\}
+% \note{The kernel smoothing procedure is sensitive to the asset dimension. \\}
+% \note{Despite the fact that the kernel smoothing procedure has the same asymptotic convergence rate as before, it converges slower in practice. \\}
+
+% \end{frame}
 
@@
 
+\note{This figure shows the same experiment as the previous figure, but we further increase the asset dimension to 20. \\}
+\note{The standard procedure is not affected by the asset dimension. \\}
+\note{The kernel smoothing procedure actually converges faster than what its asymptotic convergence rate suggests. \\}
+\note{The regression-based procedure is the only procedure that actually converges faster when the asset dimension is high. We will do a deeper dive into it in the following experiment. \\}
+\note{It is also worth noting that the likelihood ratio and KRR procedures are dimension-independent. \\}
+\note{While it is not shown in their empirical rate, due to their additional cost of pooling inner replications, we are not able to run these procedures when $\Gamma$ is large. \\}
+
 \end{frame}
@@
 
-\end{frame}
-
-\begin{frame}{Sensitivity to Option Type}
-
-\begin{figure}
-    \includegraphics[width=\textwidth]{../project1/figures/figure6a.png}
-\end{figure}
-
-\begin{itemize}
-    \item Similar convergence patterns across different option types
-    \item Regression and kernel smoothing show higher empirical rates for barrier options
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Sensitivity to Risk Measure}
-
-\begin{figure}
-    \includegraphics[width=\textwidth]{../project1/figures/figure8a.png}
-\end{figure}
-
-\begin{itemize}
-    \item Convergence behavior consistent across different risk measures
-    \item Regression-based method shows highest empirical convergence rates
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Sensitivity to VaR/CVaR Level}
-
-\begin{figure}
-    \includegraphics[width=\textwidth]{../project1/figures/figure9a.png}
-\end{figure}
-
-\begin{itemize}
-    \item Regression-based method not sensitive to VaR/CVaR level
-    \item Consistent performance across different levels
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Sensitivity to Asset Model}
-
-\begin{figure}
-    \includegraphics[width=\textwidth]{../project1/figures/figure10a.png}
-\end{figure}
-
-\begin{itemize}
-    \item Regression-based method insensitive to asset model (GBM vs. Heston)
-    \item Consistent performance across different asset models
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Computational Complexity}
-
-    There are \textbf{computational costs} associated with pooling inner replications.
-
-    \begin{itemize}
-        \item Standard procedure: cost of estimating the optimal $M$ and $N$
-        \item Regression: most efficient among metamodel-based procedures
-        \item Kernel smoothing: costly distance calculations and cross-validation
-        \item Likelihood ratio: No training, but costly weight calculations
-        \item KRR: even more expensive than kernel smoothing
-    \end{itemize}
-
-\end{frame}
+\note{To investigate the regression-based procedure, we further increase the total simulation budget $\Gamma$. \\}
+\note{The figure shows the performance of the regression-based procedure in the estimation of the quadratic tracking error for the portfolio of European call options. \\}
+\note{We separate different values of $\Gamma$ into two different parts. \\}
+\note{The first part is when $\Gamma$ is small. \\}
+\note{The second part is when $\Gamma$ is large. \\}
+\note{The first part is when the regression-based procedure has a higher convergence rate than its asymptotic convergence rate. \\}
+\note{The second part is when the regression-based procedure stabilizes and matches its asymptotic convergence rate. \\}
+\note{In our experiments, we find that the regression-based procedure is very poor when $\Gamma$ is small. \\}
+\note{It means that when we don't have enough data points, the regression-based procedure is particularly bad. \\}
+\note{As we increase the total simulation budget $\Gamma$, the regression-based procedure improves fast, and eventually matches the asymptotic convergence rate. \\}
+
+\end{frame}
+
+% \begin{frame}{Sensitivity to Option Type}
+
+% \begin{figure}
+%     \includegraphics[width=\textwidth]{../project1/figures/figure7b.png}
+% \end{figure}
+
+% \begin{itemize}
+%     \item Similar convergence patterns across different option types
+%     \item Regression and kernel smoothing show higher empirical rates for barrier options
+% \end{itemize}
+
+% \note{This figure shows the performance of the procedures for a portfolio of 3 barrier options with a W-shaped payoff. \\}
+% \note{This example is found in the regression-based procedure paper by broadie. It presents a case of complex payoffs for single asset dimension. \\}
+% \note{Most procedures are not sensitive to the option type. \\}
+% \note{The reason for kernel smoothing's MSE to increase at the right end of the plot is due to error in cross-validation of its bandwidth parameter. \\}
+% \note{Due to the additional cost of cross-validation, we are not able to run it for every macro replication when the kernel smoothing procedure when $\Gamma$ is large. \\}
+% \note{Instead, we use the same bandwidth parameter for all macro replications. \\}
+% \note{A detailed explanation of this phenomenon is provided in the thesis. \\ }
+% \note{We conducted a numerical experiment to show that the kernel smoothing procedure has sensitive cross-validation.}
+
+% \end{frame}
+
+% \begin{frame}{Sensitivity to Risk Measure}
+
+%     \begin{figure}
+%         \includegraphics[width=\textwidth]{../project1/figures/figure8a.png}
+%     \end{figure}
+
+%     \begin{itemize}
+%         \item Convergence behavior consistent across different risk measures
+%     \end{itemize}
+
+% \note{This figure shows the performance of the procedures for estimating the mean excess loss for a portfolio of 10 geometric Asian options on 10 underlying assets. \\}
+% \note{The mean excess loss is a risk measure that involves the tail of the distribution of the portfolio loss. \\}
+% \note{Most procedures are consistent across different risk measures. \\}
+% \note{The kernel smoothing procedure is the only procedure that is sensitive to the risk measure. }
+
+% \end{frame}
+
+% \begin{frame}{Sensitivity to VaR/CVaR Level}
+
+%     \begin{figure}
+%         \includegraphics[width=\textwidth]{../project1/figures/figure9a.png}
+%     \end{figure}
+
+%     \begin{itemize}
+%         \item Regression-based method not sensitive to VaR/CVaR level
+%         \item Consistent performance across different levels
+%     \end{itemize}
+
+%     \note{From our experiments, we find that the regression procedure is cheap to implement, and its performance is consistent across different experiments. \\}
+%     \note{We shift our focus to the sentivity of regression-based procedure. First, we test its sensitivity to the VaR/CVaR level. \\}
+%     \note{This figure shows the performance of the regression-based procedure for different VaR/CVaR levels. \\}
+%     \note{The regression-based procedure is not sensitive to the VaR/CVaR level. \\}
+
+% \end{frame}
+
+% \begin{frame}{Sensitivity to Asset Model}
+
+%     \begin{figure}
+%         \includegraphics[width=\textwidth]{../project1/figures/figure10a.png}
+%     \end{figure}
+
+%     \begin{itemize}
+%         \item Regression-based method insensitive to asset model (GBM vs. Heston)
+%         \item Consistent performance across different asset models
+%     \end{itemize}
+
+%     \note{We further test the sensitivity of the regression-based procedure to the asset model. \\}
+%     \note{This figure shows the performance of the regression-based procedure for different asset models. \\}
+%     \note{The regression-based procedure is insensitive to the asset model. \\}
+
+% \end{frame}
+
+% \begin{frame}{Computational Complexity}
+
+%     There are \textbf{computational costs} associated with pooling inner replications.
+
+%     \begin{itemize}
+%         \item Standard procedure: cost of estimating the optimal $M$ and $N$
+%         \item Regression: most efficient among metamodel-based procedures
+%         \item Kernel smoothing: costly distance calculations and cross-validation
+%         \item Likelihood ratio: No training, but costly weight calculations
+%         \item KRR: even more expensive than kernel smoothing
+%     \end{itemize}
+
+% \note{We have mentioned the cost of pooling inner replications multiple times. \\}
+% \note{We now provide a detailed analysis of the computational complexity of different procedures. \\}
+% \note{The standard procedure cannot be run without estimating the optimal $M$ and $N$. \\}
+% \note{The regression procedure is the most efficient among metamodel-based procedures. \\}
+% \note{The kernel smoothing procedure is costly due to the distance calculations and cross-validation. \\}
+% \note{The likelihood ratio procedure does not require training, but the likelihood ratio weight calculations are costly. \\}
+% \note{The KRR procedure is even more expensive than the kernel smoothing procedure due to the additional cost of the additional steps of ridge regression after the distance calculations.
+It also has more parameters to cross-validate.
+\\}
+
+% \end{frame}
 
@@
 
-\end{frame}
-
-\begin{frame}{Cost of Hyperparameter Tuning}
-
-    \begin{figure}
-        \includegraphics[width=\textwidth]{../project1/figures/figure12a.png}
-        \caption{Cost of hyperparameter tuning for different procedures}
-    \end{figure}
-
-\end{frame}
-
-\begin{frame}{Cost of Model Fitting and Validation}
-
-    \begin{figure}
-        \includegraphics[width=\textwidth]{../project1/figures/figure12b.png}
-        \caption{Cost of model fitting and validation for different procedures}
-    \end{figure}
-
-\end{frame}
+    \note{This figure shows the total computation time for different procedures. \\}
+    \note{It includes the time for both the simulation, training, validation, and everything else. \\}
+    \note{The total computation time of the standard procedure does not increase fast with $\Gamma$. \\}
+    \note{It is because the computation time of estimating the optimal $M$ and $N$ does not increase for larger $\Gamma$. \\}
+    \note{The regression procedure and kernel smoothing procedure are the most efficient among metamodel-based procedures. \\}
+    \note{Our implementation of the kernel smoothing procedure is efficient because we only run the cross-validation once for all macro replications. \\}
+    \note{The likelihood ratio procedure and KRR procedure are more expensive due to their additional costs}
+    \note{The likelihood ratio weight calculations increase quadratically with $\Gamma$. \\}
+    \note{For KRR, the cost of cross-validation is so high that running it once still takes a very long time. \\}
+    \note{In the thesis includes a detailed analysis of the computational complexity of different procedures in terms of $\Gamma$.}
+
+\end{frame}
+
+% \begin{frame}{Cost of Hyperparameter Tuning}
+
+%     \begin{figure}
+%         \includegraphics[width=\textwidth]{../project1/figures/figure12a.png}
+%         \caption{Cost of hyperparameter tuning for different procedures}
+%     \end{figure}
+
+%     \note{We separate the additional computational cost into two parts: the cost of hyperparameter tuning and the cost of model fitting and validation. \\}
+%     \note{The cost of hyperparameter tuning is the cost of running the cross-validation for the kernel smoothing procedure and KRR procedure. \\}
+%     \note{$M$ and $N$ are hyperparameters for the standard procedure, so we also include the cost of estimating the optimal $M$ and $N$ in the figure. \\}
+%     \note{From the figure, we can see that the cost of hyperparameter tuning contributes quite a lot to the total computation time. }
+% \end{frame}
+
+% \begin{frame}{Cost of Model Fitting and Prediction}
+
+%     \begin{figure}
+%         \includegraphics[width=\textwidth]{../project1/figures/figure12b.png}
+%         \caption{Cost of model fitting and prediction for different procedures}
+%     \end{figure}
+
+%     \note{The cost of model fitting and prediction is the cost of fitting and using the metamodel. \\}
+%     \note{We include the likelihood ratio procedure because using the likelihood ratio weights is similar to making predictions with a metamodel with fixed parameters. \\}
+%     \note{We show that the regression-based and kernel-based procedures are very efficient in terms of model fitting and prediction. \\}
+%     \note{Comparing the performance and the associated computational cost of different procedures, we find that the regression-based procedure is most cost-effective. \\}
+
+% \end{frame}
 
@@
 
-\end{frame}
-
-\section{Using Deep Neural Network Metamodels for High-Dimensional Nested Simulation}
-
-\begin{frame}{From Options to Variable Annuities}
-
-    Variable annuities (VAs) poses a challenge for nested simulation due to its \textbf{high-dimensional} and \textbf{complex payoff structure}.
-
-    \vspace{10pt}
-
-    \begin{figure}[H]
-            \includegraphics[width=0.33\textwidth]{./tikz/illustration_spns.pdf}
-            \includegraphics[width=0.62\textwidth]{./tikz/illustration_mpns.pdf}
-	\end{figure}
-
-    \vspace{10pt}
-
-    \begin{itemize}
-        \item Need to reconstruct a metamodeling-based nested simulation procedure
-    \end{itemize}
-
-\end{frame}
+    \note{In our numerical experiemenct, we have shown that the regression-based procedure is the most cost-effective among all the procedures. \\}
+    \note{It is robust and efficient to implement for limited budget sizes, and has fast empirical convergence for option portfolios. \\}
+    \note{However, the regression-based procedure is not suitable for extremely high-dimensional risk factors or complex payoffs. \\}
+    \note{The first reason is that it is hard to find a good regression basis for high-dimensional risk factors. It will involve a lot of feature engineering and expert knowledge. \\}
+    \note{The second reason is that the regression-based procedure is not able to capture the nonlinearity in the payoff. \\}
+    \note{In the next project, we will examine the performance of metamodel-based simulation procedures for variable annuities. \\}
+    \note{This is where a neural network-based procedure can be more suitable as a form of automated feature engineering. }
+
+\end{frame}
+
+\section[Using DNNs for Nested Simulation]{Cutting Through the Noise: Using Deep Neural Network Metamodels for High-Dimensional Nested Simulation}
+
+% \begin{frame}{From Options to Variable Annuities}
+
+%     Variable annuities (VAs) poses a challenge for nested simulation due to its \textbf{high-dimensional} and \textbf{complex payoff structure}.
+
+%     \vspace{10pt}
+
+%     \begin{figure}[H]
+%             \includegraphics[width=0.33\textwidth]{./tikz/illustration_spns.pdf}
+%             \includegraphics[width=0.62\textwidth]{./tikz/illustration_mpns.pdf}
+% 	\end{figure}
+
+%     \vspace{10pt}
+
+%     \begin{itemize}
+%         \item Need to reconstruct a metamodeling-based nested simulation procedure
+%     \end{itemize}
+
+%     \note{Variable annuities poses a challenge for nested simulation due to its high-dimensional and complex payoff structure. \\}
+%     \note{A regression-based procedure is not suitable. We need to reconstruct a metamodeling-based nested simulation procedure for VAs. \\}
+%     \note{On the left is the illustration of our previous nested simulation procedure for options. \\}
+%     \note{On the right is the illustration of the nested simulation procedure for VAs. \\}
+%     \note{The main difference is that the payoff of VAs, when dynamic hedging is present, is a function of the entire path of the underlying asset. \\}
+%     \note{In terms of metamodeling with machine learning, the feature is a time series of the underlying asset, and the label is the payoff of the VA with dynamic hedging. \\}
+
+% \end{frame}
 
@@
 
-\end{frame}
-
-\begin{frame}{Standard Nested Simulation for VAs}
-
-Standard nested simulation for VAs is similar to the one for options.
-
-\begin{itemize}
-    \item Generate $M$ outer scenarios
-    \item For each outer scenario,
-    \begin{itemize}
-        \item Perform $N$ inner simulations
-        \item Estimate hedging loss $L_i$ with $\hat{L}_i$
-    \end{itemize}
-    \item Use estimated losses to calculate tail risk measures (e.g., $95\%$-CVaR)
-\end{itemize}
-
-\vspace{10pt}
-
-\textbf{Observations:}
-\begin{itemize}
-    \item computational budget is limited;
-    \item high-dimensional input space;
-    \item only a \textbf{small} portion of scenarios are relevant when estimating \textbf{tail} risk measures.
-\end{itemize}
-
-\end{frame}
+    \note{The main difference of the standard nested simulation of VAs can be explained by this illustration. \\}
+    \note{This is how the P\&L is estimated for one outer scenario. \\}
+    \note{It starts at $t=0$ with a simulation to estimate the initial value of the VA contract and the initial hedge. Here we are using delta-hedging. \\}
+    \note{This hedge gets carried forward and updated at each time period with another simulation. \\}
+    \note{The P\&L is then estimated by adding up the hedging error at each time period to the initial value of the VA contract. \\}
+    \note{All the simulation mentioned is a single set of inner simulations for one outer scenario. \\}
+    \note{It is very expensive to run this standard nested simulation for VAs. \\}
+
+\end{frame}
+
+% \begin{frame}{Standard Nested Simulation for VAs}
+
+% Standard nested simulation for VAs is similar to the one for options.
+
+% \begin{itemize}
+%     \item Generate $M$ outer scenarios
+%     \item For each outer scenario,
+%     \begin{itemize}
+%         \item Perform $N$ inner simulations
+%         \item Estimate hedging loss $L_i$ with $\hat{L}_i$
+%     \end{itemize}
+%     \item Use estimated losses to calculate tail risk measures (e.g., $95\%$-CVaR)
+% \end{itemize}
+
+% \vspace{10pt}
+
+% \textbf{Observations:}
+% \begin{itemize}
+%     \item computational budget is limited;
+%     \item high-dimensional input space;
+%     \item only a \textbf{small} portion of scenarios are relevant when estimating \textbf{tail} risk measures.
+% \end{itemize}
+
+% \note{The standard nested simulation for VAs is similar to the one for options. \\}
+% \note{First, we generate $M$ outer scenarios. \\}
+% \note{For each outer scenario, we perform $N$ inner simulations to estimate the hedging loss $L_i$ with $\hat{L}_i$. \\}
+% \note{Then, we use the estimated losses to calculate tail risk measures, such as a $95\%$-CVaR. \\}
+% \note{The main difference is that the payoff of VAs, when dynamic hedging is present, is a function of the entire path of the underlying asset. \\}
+% \note{In terms of metamodeling with machine learning, the feature is a time series of the underlying asset, and the label is the payoff of the VA with dynamic hedging. \\}
+% \note{The computational budget is limited, and the input space is high-dimensional. \\}
+% \note{Only a small portion of scenarios are relevant when estimating tail risk measures. \\}
+% \note{In this project, we propose a metamodel-based nested simulation procedures to concentrate the simulation on the relevant scenarios. \\}
+
+% \end{frame}
 
@@
 
+\note{After numerical experiments, we find that the deep neural network metamodels are suitable for this problem. \\}
+\note{We use LSTM for the sequential data. It provides accurate tail scenario identification and significant computational savings by budget concentration. \\}
+\note{However, it is not transparent and interpretable. Many researchers are working on this topic. \\}
+\note{This is where we can contribute to the research. \\}
+\note{By using nested simulation as a data generating process, we can study the noise tolerance of DNNs. \\}
+\note{The noise level in the training labels can be controlled by adjusting the simulation parameters. \\}
+\note{By examining the performance of DNNs with different noise levels, we can provide direct evidence on the transparency and interpretability of DNNs. \\}
+
 \end{frame}
@@
 \begin{algorithmic}[1]
-    \STATE{\textbf{Generate training data for metamodels:}}
-    \begin{itemize}
-        \item Use a fraction of the simulation budget to run the standard nested simulation procedure with $M$ outer scenarios and $N'$ inner replications.
-        \item Construct feature-label pairs $\{(X_i, Y_{ij}) : i=1, \ldots, M, j=1, \ldots, N'\}$
-    \end{itemize}
-    \STATE{\textbf{Train metamodels:}}
-    \begin{itemize}
-        \item Use the feature-label pairs to train a metamodel.
-        \item Use the trained metamodel to make predictions for $\{X_i: i=1, \ldots, M\}$.
-        \item Sort the predicted losses to identify a predicted tail scenario set that contains the $m$ largest predicted losses.
-    \end{itemize}
-    \STATE{\textbf{Concentrate simulation on predicted tail scenarios:}}
-    \begin{itemize}
-        \item Run the standard procedure on the predicted tail scenarios.
-        \item Estimate the $\alpha$-CVaR of $L$ using the estimated losses on the predicted tail scenarios.
+    \STATE{\textbf{Generate training data for metamodels}}
+    % \begin{itemize}
+    %     \item Use a fraction of the simulation budget to run the standard nested simulation procedure with $M$ outer scenarios and $N'$ inner replications.
+    %     \item Construct feature-label pairs $\{(X_i, Y_{ij}) : i=1, \ldots, M, j=1, \ldots, N'\}$
+    % \end{itemize}
+    \STATE{\textbf{Train metamodels}}
+    % \begin{itemize}
+    %     \item Use the feature-label pairs to train a metamodel.
+    %     \item Use the trained metamodel to make predictions for $\{X_i: i=1, \ldots, M\}$.
+    %     \item Sort the predicted losses to identify a predicted tail scenario set that contains the $m$ largest predicted losses.
+    % \end{itemize}
+    \STATE{\textbf{Estimate $\alpha$-CVaR with extensive simulation on \textcolor{color10_5}{predicted tail scenarios}}}
+    \begin{itemize}
+        \item  Concentrate simulation on predicted tails
     \end{itemize}
@@
 
-\end{frame}
-
-\begin{frame}{Benefits of a Two-Stage Procedure}
-
-Simulation budget can be saved when:
-\begin{itemize}
-    \item the metamodel is accurate (a small $m$ includes most tail scenarios)
-    \item the metamodel can tolerate noise in training labels (a small $N'$)
-\end{itemize}
-
 \vspace{10pt}
 
-\textbf{Key findings:}
+\textbf{Key Findings:}
 \begin{itemize}
     \item   Substantial computational savings ($70\% - 85\%$ reduction)
-    \item Maintains accuracy comparable to standard procedure
-    \item DNN metamodels can distinguish between tail and non-tail scenarios effectively
-    \item Addresses regulatory concerns by using actual simulations for final estimates
-\end{itemize}
-
-\vspace{10pt}
-\textbf{Another finding:} 
-some DNN metamodels make \textbf{accurate loss predictions} for given scenarios.
-
-\end{frame}
+    \item   Some DNN metamodels make \textbf{accurate loss predictions}
+\end{itemize}
+
+\note{The two-stage procedure is a two-step process that is based on the idea of budget concentration. \\}
+\note{First, we generate training data for the metamodel. \\}
+\note{We use a fraction of the simulation budget to run the standard nested simulation procedure with $M$ outer scenarios and $N'$ inner replications. \\}
+\note{We then train a metamodel using the feature-label pairs. \\}
+\note{We use the trained metamodel to make predictions for all outer scenarios. \\}
+\note{We then identify the predicted tail scenario set that contains the $m$ largest predicted losses. \\}
+\note{Finally, we run the standard nested simulation procedure on the predicted tail scenarios. \\}
+
+\end{frame}
+
+% \begin{frame}{Benefits of a Two-Stage Procedure}
+
+% Simulation budget can be saved when:
+% \begin{itemize}
+%     \item the metamodel is accurate (a small $m$ includes most tail scenarios)
+%     \item the metamodel can tolerate noise in training labels (a small $N'$)
+% \end{itemize}
+
+% \vspace{10pt}
+
+% \textbf{Key findings:}
+% \begin{itemize}
+%     \item Substantial computational savings ($70\% - 85\%$ reduction)
+%     \item Maintains accuracy comparable to standard procedure
+%     \item DNN metamodels can distinguish between tail and non-tail scenarios effectively
+%     \item Addresses regulatory concerns by using actual simulations for final estimates
+% \end{itemize}
+
+% \vspace{10pt}
+% \textbf{Another finding:} 
+% some DNN metamodels make \textbf{accurate loss predictions} for given scenarios.
+
+% \note{The two-stage procedure can save substantial computational budget when the metamodel is accurate and can tolerate noise in training labels. \\}
+% \note{By concentrating the simulation on the predicted tail scenarios, the two-stage procedure can achieve a comparable accuracy to the standard procedure while using only a fraction of the simulation budget.
+\\}
+% \note{This approach also addresses regulatory concerns by using actual simulations for final estimates. \\}
+% \note{It is also worth noting that we found some DNN metamodels that can make accurate loss predictions for given scenarios. \\}
+% \note{Why don't we use these metamodels to make predictions directly? So, we propose a single-stage procedure to avoid the second stage of the two-stage procedure.}
+
+% \end{frame}
 
@@
         \caption{Single-Stage Metamodel-based Nested Simulation for VAs}
+
     \begin{algorithmic}[1]
-    \STATE{\textbf{Generate training data for metamodels:}}
-    \begin{itemize}
-        \item Use the entire simulation budget to run the standard nested simulation procedure with $M$ outer scenarios and $N$ inner replications.
-        \item Construct feature-label pairs $\{(X_i, Y_{ij}) : i=1, \ldots, M, j=1, \ldots, N\}$
-    \end{itemize}
-    \STATE{\textbf{Train metamodels:}}
-    \begin{itemize}
-        \item Use the feature-label pairs to train a metamodel.
-        \item Use the trained metamodel to make predictions for $\{X_i: i=1, \ldots, M\}$.
-    \end{itemize}
-    \STATE{\textbf{Use metamodel predictions to estimate tail risk measures directly.}}
+        \STATE{\textbf{Generate training data for metamodels}}
+        % \begin{itemize}
+        %     \item Use a fraction of the simulation budget to run the standard nested simulation procedure with $M$ outer scenarios and $N'$ inner replications.
+        %     \item Construct feature-label pairs $\{(X_i, Y_{ij}) : i=1, \ldots, M, j=1, \ldots, N'\}$
+        % \end{itemize}
+        \STATE{\textbf{Train metamodels}}
+        % \begin{itemize}
+        %     \item Use the feature-label pairs to train a metamodel.
+        %     \item Use the trained metamodel to make predictions for $\{X_i: i=1, \ldots, M\}$.
+        %     \item Sort the predicted losses to identify a predicted tail scenario set that contains the $m$ largest predicted losses.
+        % \end{itemize}
+        \STATE{\textbf{Estimate $\alpha$-CVaR with \textcolor{color10_5}{metamodel predictions}}}
+        \begin{itemize}
+            \item  Entirely avoids extensive simulation
+        \end{itemize}
     \end{algorithmic}
@@
 
+\vspace{10pt}
+
 \textbf{Key advantages:}
@@
     \item more efficient than a two-stage procedure;
-    \item avoids specifying $m$.
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Experiment Setting}
-
-    We estimate the $95\%$-CVaR of the hedging loss for a GMWB contract with 20-year maturity.
-
-    \vspace{10pt}
-
-    \textbf{Specifications:}
-    \begin{itemize}
-        \item The underlying asset follows a regime-switching geometric Brownian motion;
-        \item The contract is delta-hedged monthly (240 periods);
-        \item The true $95\%$-CVaR is estimated using 100,000 outer scenarios and 100,000 inner replications.
-        \item The metamodel is trained using 90,000 outer scenarios and 100 inner replications.
-        \item Benchmark: standard nested simulation procedure with 100,000 outer scenarios and 1,000 inner replications.
-    \end{itemize}
-
-\end{frame}
-
-\begin{frame}{Experiment Design}
-
-    \textbf{Research Questions:}
-    \begin{itemize}
-        \item What do DNNs learn from noisy data?
-        \item How well do DNNs learn from noisy data?
-    \end{itemize}
-
-    \begin{figure}[H]
-        \includegraphics[width=\textwidth]{../project2/figures/datasets.png}
-    \end{figure}
-
-    \begin{itemize}
-        \item Our 90,000 training data is noisy, and the test data is also \textbf{noisy}.
-        \item Our evaluation is based on the true (\textbf{noiseless}) feature-label relationship\footnotemark.
-    \end{itemize}
-
-    \footnotetext{Made possible by novel simulation design.}
-
-\end{frame}
+    \item avoids specifying a safety margin $m$.
+\end{itemize}
+
+\note{The single-stage procedure shares the same idea of running the standard nested simulation procedure to generate training data for the metamodel. \\}
+\note{After a metamodel is trained, we use it to make predictions for VA contract losses accross all outer scenarios. \\}
+\note{The risk measure is estimated using the predicted losses of the metamodel. \\}
+\note{It is more efficient than the two-stage procedure because it avoids the second stage of the two-stage procedure. \\}
+\note{It also avoids specifying a safety margin $m$, which is a feature of the two-stage procedure that we will discuss later.}
+
+\end{frame}
+
+% \begin{frame}{Experiment Setting}
+
+%     We estimate the $95\%$-CVaR of the hedging loss for a GMWB contract with 20-year maturity.
+
+%     \vspace{10pt}
+
+%     \textbf{Specifications:}
+%     \begin{itemize}
+%         \item The underlying asset follows a regime-switching geometric Brownian motion;
+%         \item The contract is delta-hedged monthly (240 periods);
+%         \item The true $95\%$-CVaR is estimated using 100,000 outer scenarios and 100,000 inner replications.
+%         \item The metamodel is trained using 90,000 outer scenarios and 100 inner replications.
+%         \item Benchmark: standard nested simulation procedure with 100,000 outer scenarios and 1,000 inner replications.
+%     \end{itemize}
+
+% \note{In our numerical experiments, we consider a GMWB contract with 20-year maturity. \\}
+% \note{The underlying asset follows a regime-switching geometric Brownian motion. \\}
+% \note{The contract is delta-hedged monthly (240 periods). \\}
+% \note{The true $95\%$-CVaR is estimated using 100,000 outer scenarios and 100,000 inner replications. We call this the true data. \\}
+% \note{The metamodel is trained using 90,000 outer scenarios and 100 inner replications, called the training data. \\}
+% \note{Another 10,000 outer scenarios with 100 inner replications are used to evaluate the performance of the metamodel, called the test data. \\}
+% \note{The true data is not available in practice, but it is useful for evaluating the performance of the metamodel. \\}
+% \note{The difference in performance between the training data and the test data, and between the test data and the true data, provides insights into the noise tolerance of the metamodel. \\}
+% \note{And it helps us to understand an important question: what does deep neural networks learn from noisy data? \\}
+% \note{For our experiments, the benchmark is the standard nested simulation procedure with 100,000 outer scenarios and 1,000 inner replications. }
+
+% \end{frame}
 
@@
 
-    Capacity is defined as the number of parameters in the metamodel.
-    \begin{itemize}
-        \item   Higher capacity metamodels are more flexible and expressive.
-        \item   Lower capacity metamodels are less likely to overfit.
-    \end{itemize}
-
-\end{frame}
-
-\begin{frame}{Traditional Regression Metamodels}
+    Three datasets are considered:
+    \begin{itemize}
+        \item   \textcolor{color10_2}{Training}: 90,000 scenarios (100 inner replications).
+        \item   \textcolor{color10_3}{Test}: 10,000 scenarios (100 inner replications).
+        \item   \textcolor{color10_5}{True}: 100,000 scenarios (100,000 inner replications).
+    \end{itemize}
+
+    \note{We consider the following metamodel architectures: \\}
+    \note{Multiple Linear Regression, Quadratic Polynomial Regression, Feedforward Neural Network, Recurrent Neural Network, and Long Short-Term Memory Network. \\}
+    \note{Capacity is defined as the number of parameters in the metamodel. \\}
+    \note{Higher capacity metamodels are more flexible and expressive. \\}
+    \note{Lower capacity metamodels are less likely to overfit. \\}
+    \note{The deep neural network metamodels are more flexible and expressive, but they are said to be more prone to overfitting. \\}
+    \note{We will see whether this is indeed the case in our experiments. \\}
+
+\end{frame}
+
+\begin{frame}{Research Questions}
+
+    \begin{itemize}
+        \item What do DNNs learn from noisy data?
+        \item How well do DNNs learn from noisy data?
+    \end{itemize}
 
     \begin{figure}[H]
-        \includegraphics[width=0.48\textwidth]{../project2/figures/qqPlots/mlrLN.png}
+        \includegraphics[width=\textwidth]{../project2/figures/datasets.png}
+    \end{figure}
+
+    In our experiment:
+    \begin{itemize}
+        \item $95\%$-CVaR of loss for a GMWB with a 240-month maturity
+        \item 240-dimensional feature vector and 1-dimensional loss
+    \end{itemize}
+
+\note{To further clarify our research questions, we consider the following scenario: \\}
+\note{We have a noisy training data and a noisy test data. \\}
+\note{We want to know what the metamodel learns from the noisy data. \\}
+\note{We also want to know how well the metamodel can make accurate loss predictions for given scenarios. \\}
+\note{In a simulation experiment, we can control the noise level in the training data and the test data. \\}
+\note{We also have access to the true feature-label relationship when we increase the number of replications. \\}
+\note{We can use this true feature-label relationship to evaluate the performance of deep neural networks, which is usually not possible in practice. }
+
+\end{frame}
+
+\begin{frame}{Metamodel Performance}
+
+    \begin{figure}[H]
         \includegraphics[width=0.48\textwidth]{../project2/figures/qqPlots/qprLN.png}
-        \caption{QQ plots between true and predicted loss labels for MLR and QPR metamodels}
+        \includegraphics[width=0.48\textwidth]{../project2/figures/qqPlots/lstmLoCapLN.png}
+        \caption{QQ plots between true and predicted loss labels for QPR and LSTM metamodels}
     \end{figure}
@@
     \begin{itemize}
-        \item   MLR and QPR metamodels make \textbf{inaccurate} loss predictions.
-        \item   Feature engineering is hardly feasible for our 240-dimensional $X$.
-    \end{itemize}
-
-\end{frame}
-
-\begin{frame}{Deep Neural Network Metamodels}
-
-    \begin{figure}[H]
-        \includegraphics[width=0.48\textwidth]{../project2/figures/qqPlots/fnnLN.png}
-        \includegraphics[width=0.48\textwidth]{../project2/figures/qqPlots/lstmLoCapLN.png}
-        \caption{QQ plots between true and predicted loss labelsfor FNN and LSTM metamodels}
-    \end{figure}
-
-    \begin{itemize}
+        \item   QPR make \textbf{inaccurate} loss predictions
         \item   DNN metamodels are more flexible.
-        \item   Time series features prefer a LSTM metamodel over FNN.
-        \item   Network architecture serves as prior knowledge that regularizes DNNs.
-    \end{itemize}
-
-\end{frame}
+    \end{itemize}
+
+    \note{We first consider the traditional regression metamodels. \\}
+    \note{On the left is the QQ plot between the true loss labels and the predicted loss labels for MLR, and on the right is the QQ plot for QPR. \\}
+    \note{MLR and QPR metamodels make inaccurate loss predictions. \\}
+    \note{Feature engineering is hardly feasible for our 240-dimensional $X$. \\}
+    \note{We will see whether deep neural networks can make more accurate loss predictions. \\}
+
+\end{frame}
+
+% \begin{frame}{Deep Neural Network Metamodels}
+
+%     \begin{figure}[H]
+%         \includegraphics[width=0.48\textwidth]{../project2/figures/qqPlots/fnnLN.png}
+%         \caption{QQ plots between true and predicted loss labelsfor FNN and LSTM metamodels}
+%     \end{figure}
+
+%     \begin{itemize}
+%         \item   DNN metamodels are more flexible.
+%         \item   Time series features prefer LSTM over FNN.
+%         \item   Network architecture serves as regularization.
+%     \end{itemize}
+
+%     \note{We then consider the deep neural network metamodels. \\}
+%     \note{On the left is the QQ plot between the true loss labels and the predicted loss labels for FNN, and on the right is the QQ plot for LSTM. \\}
+%     \note{DNN metamodels are more flexible. \\}
+%     \note{We find that our time series outer scenarios prefer a LSTM metamodel over FNN. \\}
+%     \note{Network architecture is thought to serve as prior knowledge that regularizes DNNs. \\}
+%     \note{It decides how the individual neurons are connected to each other. \\}
+%     \note{For example, FNN is a fully-connected network, meaning that we don't impose any structure on the connections between neurons. \\}
+%     \note{In contrast, LSTM has a recurrent structure, meaning that the connections between neurons are time-dependent. \\}
+
+% \end{frame}
 
@@
         \toprule
-        \textbf{Metamodel} & \textbf{Training error} & \textbf{Test error} & \textbf{True error}\\
+        \textbf{Metamodel} & \textcolor{color10_2}{\textbf{Training error}} & \textcolor{color10_3}{\textbf{Test error}} & \textcolor{color10_5}{\textbf{True error}}\\
         \midrule
-        MLR & $0.706 (\pm 8.3\times 10^{-4})$ & $0.713 (\pm 2.7 \times 10^{-2})$ & $0.706 (\pm 3.4 \times 10^{-4})$ \\
-        QPR & $0.543 (\pm 8.3\times 10^{-4})$ & $0.554 (\pm 2.7 \times 10^{-2})$ & $0.544 (\pm 4.1 \times 10^{-4})$ \\
-        FNN & $0.129 (\pm 6.0\times 10^{-3})$ & $0.240 (\pm 9.8 \times 10^{-3})$ & $0.132 (\pm 5.8 \times 10^{-3})$ \\
-        RNN & $0.132 (\pm 7.5\times 10^{-3})$ & $0.137 (\pm 7.6 \times 10^{-3})$ & $0.119 (\pm 7.5 \times 10^{-3})$ \\
-        LSTM & $0.075 (\pm 4.5\times 10^{-3})$ & $0.079 (\pm 5.4 \times 10^{-3})$ & $0.063 (\pm 4.4 \times 10^{-3})$ \\
-        RNN$^*$\footnotemark & $0.109 (\pm 5.2\times 10^{-3})$ & $0.128 (\pm 5.2 \times 10^{-3})$ & $0.109 (\pm 5.2 \times 10^{-3})$ \\
+        MLR & $\textcolor{color10_2}{0.706}$ $(\pm 8.3\times 10^{-4})$ & $\textcolor{color10_3}{0.713}$ $(\pm 2.7 \times 10^{-2})$ & $\textcolor{color10_5}{0.706}$ $(\pm 3.4 \times 10^{-4})$ \\
+        QPR & $\textcolor{color10_2}{0.543}$ $(\pm 8.3\times 10^{-4})$ & $\textcolor{color10_3}{0.554}$ $(\pm 2.7 \times 10^{-2})$ & $\textcolor{color10_5}{0.544}$ $(\pm 4.1 \times 10^{-4})$ \\
+        FNN & $\textcolor{color10_2}{0.129}$ $(\pm 6.0\times 10^{-3})$ & $\textcolor{color10_3}{0.240}$ $(\pm 9.8 \times 10^{-3})$ & $\textcolor{color10_5}{0.132}$ $(\pm 5.8 \times 10^{-3})$ \\
+        RNN & $\textcolor{color10_2}{0.132}$ $(\pm 7.5\times 10^{-3})$ & $\textcolor{color10_3}{0.137}$ $(\pm 7.6 \times 10^{-3})$ & $\textcolor{color10_5}{0.119}$ $(\pm 7.5 \times 10^{-3})$ \\
+        LSTM & \textbf{$\textcolor{color10_2}{0.075}$} $(\pm 4.5\times 10^{-3})$ & \textbf{$\textcolor{color10_3}{0.079}$} $(\pm 5.4 \times 10^{-3})$ & \textbf{$\textcolor{color10_5}{0.063}$} $(\pm 4.4 \times 10^{-3})$ \\
+        RNN$^*$\footnotemark & $\textcolor{color10_2}{0.109}$ $(\pm 5.2\times 10^{-3})$ & $\textcolor{color10_3}{0.128}$ $(\pm 5.2 \times 10^{-3})$ & $\textcolor{color10_5}{0.109}$ $(\pm 5.2 \times 10^{-3})$ \\
         \bottomrule
         \end{tabular}
-        \caption{Average MSEs and 95\% confidence bands of metamodels for GMWB inner simulation model.}
+        \caption{Average MSEs and 95\% confidence bands of metamodels for GMWB.}
         \label{tab:gmwb_arch}
@@
 
-\end{frame}
-
-\begin{frame}{Issues with RNNs}
-
-    \begin{figure}[H]
-        \includegraphics[width=0.48\textwidth]{../project2/figures/qqPlots/rnnGood_training.png}
-        \includegraphics[width=0.48\textwidth]{../project2/figures/qqPlots/rnnBad_training.png}
-        \caption{QQ plots between training and predicted loss labels for RNN metamodels}
-    \end{figure}
-
-    \begin{itemize}
-        \item   RNN metamodels suffers from \textbf{vanishing gradient problem}.
-        \item   Ease of training (reliability) is a critical factor when choosing a DNN metamodel.
-    \end{itemize}
-
-\end{frame}
+    \note{This table summarizes the results of our experiments. \\}
+    \note{It is the most interesting finding that DNN metamodels with suitable architectures can \textbf{cut through the noise} in training labels. \\}
+    \note{The average MSEs of metamodels on the training, test, and true data are reported in the three columns, respectively. \\}
+    \note{Note that the training and test labels are noisy. The simulation noise is what makes them noisy, which is less present in the true data. \\}
+    \note{First, we note that DNN metamodels has lower training errors than the traditional regression metamodels. \\}
+    \note{This is expected because DNNs are more flexible and expressive than traditional regression metamodels. \\}
+    \note{What is more interesting is the comparison between the test and true errors. \\}
+    \note{We find that the true errors of RNN-based metamodels are lower than their test errors. \\}
+    \note{This suggests that the RNN and LSTM metamodels are able to cut through the simulation noise and learn the true feature-label relationship. \\}
+    \note{When we take another look at the table, we find that for LSTM, its true error is even lower than its training error. \\}
+    \note{This is another evidence that LSTM metamodels are able to cut through the noise in training labels and fit to the true relationship. \\}
+    \note{We also find that the LSTM metamodel is able to cut through the noise in training labels and fit to the true relationship. \\}
+    \note{We have another finding for RNN. RNN metamodels suffer from the vanishing gradient problem. \\}
+    \note{This is why we make separate rows for well-trained RNNs and poorly-trained RNNs. \\}
+    \note{We will discuss this in the next slide. \\}
+
+\end{frame}
+
+% \begin{frame}{Issues with Crude RNNs}
+
+%     \begin{figure}[H]
+%         \includegraphics[width=0.48\textwidth]{../project2/figures/qqPlots/rnnGood_training.png}
+%         \includegraphics[width=0.48\textwidth]{../project2/figures/qqPlots/rnnBad_training.png}
+%         \caption{QQ plots between training and predicted loss labels for RNN metamodels}
+%     \end{figure}
+
+%     \begin{itemize}
+%         \item   RNN metamodels suffers from \textbf{vanishing gradient problem}.
+%         \item   Ease of training (reliability) is a critical factor when choosing a DNN metamodel.
+%     \end{itemize}
+
+%     \note{The QQ plots on the left show the relationship between the training and predicted loss labels for a well-trained RNN, and on the right is a poorly-trained RNN. \\}
+%     \note{We find that the well-trained RNN has a better relationship between the training and predicted loss labels. \\}
+%     \note{However, the poorly-trained RNN suffers from the vanishing gradient problem. \\}
+%     \note{It is unable to continue learning from the training data. \\}
+%     \note{During our training some RNNs suffer from gradient explosion. \\}
+%     \note{The training process is highly unstable. \\}
+%     \note{This issue can be mitigated by using gradient clipping and other techniques. However, it can not be completely avoided. \\}
+%     \note{Therefore, we recommend using LSTM metamodels over RNN metamodels. \\}
+
+% \end{frame}
 
@@
 
-    Choosing a safety margin: a trade-off between accuracy and efficiency.
-    \begin{itemize}
-        \item   A lower margin: not enough tail identified.
-        \item   A higher margin: more accurate CVaR estimate, but more budget needed to perform extensive inner simulations.
-    \end{itemize}
-
-\end{frame}
-
-\begin{frame}{Tail Scenario Identification}
+    \vspace{10pt}
+    \textbf{Trade-off between accuracy and efficiency}
+    \begin{itemize}
+        \item   Lower margin: not enough tail identified
+        \item   Higher margin: more budget spent on extensive simulation
+    \end{itemize}
+
+    \note{For a two-stage procedure, we need to choose a safety margin $m$ to identify the tail scenarios. \\}
+    \note{Consider estimating the $95\%$ CVaR with 100,000 outer scenarios. \\}
+    \note{On the top is the true tail and non-tail scenarios, and on the bottom is the predicted tail and non-tail scenarios. \\}
+    \note{The 5\% predicted tail scenarios are not guaranteed to contain all the true tail scenarios. \\}
+    \note{Therefore, we need to add a safety margin $m$ to the predicted tail scenarios. \\}
+    \note{On the bottom, we add a 2\% safety margin to the predicted tail scenarios. \\}
+    \note{This adds 2,000 more scenarios to the inner simulations. \\}
+    \note{We may add another 2\% safety margin to be more confident. \\}
+    \note{This introduce a safety margin of $4\%$. $9000$ predicted tail scenarios are used for extensive inner simulations in stage 2. \\}
+    \note{This is a trade-off between accuracy and efficiency. \\}
+    \note{For a good metamodel, we only need a small safety margin to be accurate in tail identification. \\}
+    \note{However, for a bad metamodel, the safety margin needs to be large to identify all the tail scenarios. \\}
+    \note{This comes at the cost of more inner simulations, which is computationally expensive. \\}
+    \note{So, one of the limitations of the two-stage procedure is the choice of safety margin. \\}
+    \note{It can be partially mitigated by using a good metamodel. \\}
+
+\end{frame}
+
+\begin{frame}{Metamodel Performance}
 
     \begin{figure}[H]
-        \includegraphics[width=0.48\textwidth]{../project2/figures/tailMatches/regLN.png}
         \includegraphics[width=0.48\textwidth]{../project2/figures/tailMatches/nnLN.png}
-        \caption{Tail scenario identification for regression and DNN metamodels}
+        \includegraphics[width=0.48\textwidth]{../project2/figures/CVaR/allLN.png}
+        \caption{Tail Matches and CVaR Predictions for DNN Metamodels}
     \end{figure}
@@
 
-\end{frame}
-
-\begin{frame}{Estimating CVaR}
-
-    \begin{figure}[H]
-        \includegraphics[width=0.48\textwidth]{../project2/figures/CVaR/allLN.png}
-        \includegraphics[width=0.48\textwidth]{../project2/figures/CVaR/zoomedLN.png}
-        \caption{CVaR estimation for DNN metamodels}
-    \end{figure}
-
-    \begin{itemize}
-        \item Traditional regression metamodels are \textbf{unable} to accurately estimate CVaR even with high safety margins.
-        \item LSTM surpasses the standard procedure with a \textbf{5\% safety margin}.
-        \item With a 95\% safety margin, any two-stage procedure produce the same CVaR estimate as a standard procedure.
-    \end{itemize}
-
-\end{frame}
+    \note{We now consider the tail scenario identification for the two-stage procedure. \\}
+    \note{On the left is the tail scenario identification for the traditional regression metamodel, and on the right is the tail scenario identification for the LSTM metamodel. \\}
+    \note{We compare the two-stage procedure with the standard procedure. \\}
+    \note{When colored lines cross the grey dashed line, it means that the metamodel is able to identify the tail scenarios as well as the standard procedure. \\}
+    \note{We find that the LSTM metamodel is able to surpass the standard procedure on tail identification with a less than $5\%$ safety margin. \\}
+    \note{However, the traditional regression metamodel is unable to identify the tail scenarios even with a high safety margin. \\}
+    \note{A well-trained RNN is better than a FNN, but the poorly-trained RNN is far worse.}
+    \note{This further motivates the use of LSTM metamodels over RNN metamodels. \\}
+
+\end{frame}
+
+% \begin{frame}{Estimating CVaR}
+
+%     \begin{figure}[H]
+%         \includegraphics[width=0.48\textwidth]{../project2/figures/CVaR/allLN.png}
+%         \includegraphics[width=0.48\textwidth]{../project2/figures/CVaR/zoomedLN.png}
+%         \caption{CVaR estimation for DNN metamodels}
+%     \end{figure}
+
+%     \begin{itemize}
+%         \item Traditional regression metamodels are \textbf{unable} to accurately estimate CVaR even with high safety margins.
+%         \item LSTM surpasses the standard procedure with a \textbf{5\% safety margin}.
+%         \item With a 95\% safety margin, any two-stage procedure produce the same CVaR estimate as a standard procedure.
+%     \end{itemize}
+
+%     \note{We now consider the CVaR estimation for the two-stage procedure. \\}
+%     \note{On the left is the CVaR estimation for the all metamodels, and on the right is the zoomed-in version. \\}
+%     \note{Their performance estimating CVaR is similar to their performance on tail identification. \\}
+%     \note{The LSTM metamodel is able to surpass the standard procedure on CVaR estimation with a less than $5\%$ safety margin. \\}
+%     \note{However, the traditional regression metamodel is unable to estimate the CVaR even with a high safety margin. \\}
+%     \note{For the zoomed-in version, we can see that the LSTM metamodel is approaching CVaR of the standard procedure but not the true CVaR. \\}
+%     \note{This is because in the second stage, the inner simulations are still not noiseless. \\}
+%     \note{We use the same inner simulation for both the standard procedure and the two-stage procedure, which has 1000 inner replications for each outer scenario. \\}
+
+% \end{frame}
 
@@
 
-    In a simulation study, we have control over the \textbf{noise level in training labels} and the \textbf{number of training samples}.
+    Simulation controls \textbf{noise level in training labels} and \textbf{number of training samples}.
 
@@
 
-    Controling the inner replications $N'$ varies the noise level in training labels.
+    $N'$ varies the noise level.
 
@@
 
-    Controling the outer scenarios $M$ varies the number of training samples.
+    $M$ varies the number of training samples.
 
@@
 
-\end{frame}
-
-\begin{frame}{Noise Tolerance of DNNs}
-
-    \begin{table}[ht!]
-        \centering
-        \begin{tabular}{lccccc}
-            \toprule
-            \textbf{Model}      & \textbf{$N'$}         & \textbf{Training error}                & \textbf{Test error}               & \textbf{True error}\\
-            \midrule
-            LSTM                & $100$                & $0.075$         & $0.079$     & $0.063$ \\ 
-            High-capacity LSTM  & $100$                & $0.068$         & $0.102$     & $0.060$ \\
-            Average Difference  & $100$                & $-0.007$       & $0.023$     & $-0.003$ \\
-            \hline
-            LSTM                & $10$                 & $0.195$         & $0.193$     & $0.070$ \\
-            High-capacity LSTM  & $10$                 & $0.157$         & $0.199$     & $0.065$ \\
-            Average Difference  & $10$                 & $-0.038$       & $0.006$     & $-0.005$ \\
-            \hline
-            LSTM                & $1$                  & $1.366$         & $0.781$     & $0.129$ \\
-            High-capacity LSTM  & $1$                  & $1.354$         & $0.795$     & $0.149$ \\
-            Average Difference  & $1$                  & $-0.012$       & $0.014$     &\textcolor{color10_5}{$0.020$} \\
-            \bottomrule
-        \end{tabular}
-        \caption{MSEs of LSTM metamodels.}
-    \end{table}
-
-    \begin{itemize}
-        \item   Both LSTMs cut through the noise in training labels.
-        \item   Both LSTMs deteriorate dramatically on \textbf{high-noise} labels.
-        \item   High-capacity LSTM can tolerate \textbf{low} and \textbf{medium} label noise.
-    \end{itemize}
-
-\end{frame}
+    \note{We now consider the sensitivity testing for the DNN metamodels. \\}
+    \note{We are interested in the sensitivity of the DNN metamodels to the noise level in training labels and the number of training samples. \\}
+    \note{In a simulation experiment, we can vary them to see how the DNN metamodels perform. \\}
+    \note{We consider the noise level in training labels by varying the number of inner replications $N'$. \\}
+    \note{We consider the number of training samples by varying the number of outer scenarios $M$. \\}
+    \note{We consider two LSTM metamodels of different capacities because we want to see if the capacity of the metamodel matters for overfitting. \\}
+    \note{The high-capacity LSTM metamodel has 10 times more parameters than the regular LSTM metamodel}
+
+\end{frame}
+
+% \begin{frame}{Noise Tolerance of DNNs}
+
+%     \begin{table}[ht!]
+%         \centering
+%         \begin{tabular}{lccccc}
+%             \toprule
+%             \textbf{Model}      & \textbf{$N'$}         & \textbf{Training error}                & \textbf{Test error}               & \textbf{True error}\\
+%             \midrule
+%             LSTM                & $100$                & $0.075$         & $0.079$     & $0.063$ \\ 
+%             High-capacity LSTM  & $100$                & $0.068$         & $0.102$     & $0.060$ \\
+%             Average Difference  & $100$                & $-0.007$       & $0.023$     & $-0.003$ \\
+%             \hline
+%             LSTM                & $10$                 & $0.195$         & $0.193$     & $0.070$ \\
+%             High-capacity LSTM  & $10$                 & $0.157$         & $0.199$     & $0.065$ \\
+%             Average Difference  & $10$                 & $-0.038$       & $0.006$     & $-0.005$ \\
+%             \hline
+%             LSTM                & $1$                  & $1.366$         & $0.781$     & $0.129$ \\
+%             High-capacity LSTM  & $1$                  & $1.354$         & $0.795$     & $0.149$ \\
+%             Average Difference  & $1$                  & $-0.012$       & $0.014$     &\textcolor{color10_5}{$0.020$} \\
+%             \bottomrule
+%         \end{tabular}
+%         \caption{MSEs of LSTM metamodels.}
+%     \end{table}
+
+%     \begin{itemize}
+%         \item   Both LSTMs cut through the noise in training labels.
+%         \item   Both LSTMs deteriorate dramatically on \textbf{high-noise} labels.
+%         \item   High-capacity LSTM can tolerate \textbf{low} and \textbf{medium} label noise.
+%     \end{itemize}
+
+%     \note{This table shows the MSEs of the two LSTM metamodels on different datasets. \\}
+%     \note{We also record the average difference in MSEs between the two LSTM metamodels. \\}
+%     \note{Their difference indicates which LSTM is better at different noise levels. \\}
+%     \note{The high-capacity LSTM is better at low and medium noise levels, while the regular LSTM is better at high noise levels. \\}
+%     \note{This is because the high-capacity LSTM has more parameters and is therefore more flexible to fit the training data. \\}
+%     \note{However, the regular LSTM is more robust to high noise levels. \\}
+%     \note{We note that the high-capacity LSTM can tolerate quite a lot of noise in the training labels. \\}
+%     \note{With only 10 inner replications, the high-capacity LSTM can still achieve a true MSE.}
+%     \note{It is only when the labels become extremely noisy that the high-capacity LSTM deteriorates. $N=1$ is the most noise we are able to achieve in a simulation experiment.}
+
+% \end{frame}
 
@@
 
-\end{frame}
-
-\begin{frame}{Sensitivity of Regular LSTM}
-
-    \begin{table}[ht!]
-        \centering
-        \begin{tabular}{lccccc}
-            \toprule
-                           & $N'=1$   & $N'=10$  & $N'=100$ & $N'=1000$\\
-            \midrule
-            $M = 100$      & \textcolor{color10_2}{$1.139$} & \textcolor{color10_3}{$0.229$} & \textcolor{color10_4}{$0.167$} & \textcolor{color10_5}{$0.158$} \\
-            $M = 1000$     & \textcolor{color10_3}{$0.559$} & \textcolor{color10_4}{$0.173$} & \textcolor{color10_5}{$0.123$} & \textcolor{color10_6}{$0.127$} \\
-            $M = 10000$    & \textcolor{color10_4}{$0.283$} & \textcolor{color10_5}{$0.115$} & \textcolor{color10_6}{$0.099$} & \textcolor{color10_7}{$0.097$} \\
-            $M = 100000$   & \textcolor{color10_5}{$0.129$} & \textcolor{color10_6}{$0.070$} & \textcolor{color10_7}{$0.063$} & \textcolor{color10_8}{$0.063$} \\
-            \bottomrule
-        \end{tabular}
-        \caption{MSE between regular LSTM's predicted losses and true losses.}
-    \end{table}
-
-    \begin{itemize}
-        \item   Same color $\rightarrow$ same total simulation budget.
-        \item   $N' = 10$ is a reasonable budget allocation for LSTM metamodels.
-    \end{itemize}
-
-\end{frame}
+    \note{This figure shows the QQ plots of the two LSTM metamodels. \\}
+    \note{We plot the predicted losses versus the true losses for both LSTMs and different noise levels. \\}
+    \note{The closer the points are to the line, the better the model is. \\}
+    \note{The high-capacity LSTM is better at low and medium noise levels, while the regular LSTM is better at high noise levels. \\}
+    \note{We can see on the bottom right that the high-capacity LSTM has very poor performance.}
+
+\end{frame}
+
+% \begin{frame}{Sensitivity of Regular LSTM}
+
+%     \begin{table}[ht!]
+%         \centering
+%         \begin{tabular}{lccccc}
+%             \toprule
+%                            & $N'=1$   & $N'=10$  & $N'=100$ & $N'=1000$\\
+%             \midrule
+%             $M = 100$      & \textcolor{color10_2}{$1.139$} & \textcolor{color10_3}{$0.229$} & \textcolor{color10_4}{$0.167$} & \textcolor{color10_5}{$0.158$} \\
+%             $M = 1000$     & \textcolor{color10_3}{$0.559$} & \textcolor{color10_4}{$0.173$} & \textcolor{color10_5}{$0.123$} & \textcolor{color10_6}{$0.127$} \\
+%             $M = 10000$    & \textcolor{color10_4}{$0.283$} & \textcolor{color10_5}{$0.115$} & \textcolor{color10_6}{$0.099$} & \textcolor{color10_7}{$0.097$} \\
+%             $M = 100000$   & \textcolor{color10_5}{$0.129$} & \textcolor{color10_6}{$0.070$} & \textcolor{color10_7}{$0.063$} & \textcolor{color10_8}{$0.063$} \\
+%             \bottomrule
+%         \end{tabular}
+%         \caption{MSE between regular LSTM's predicted losses and true losses.}
+%     \end{table}
+
+%     \begin{itemize}
+%         \item   Same color $\rightarrow$ same total simulation budget.
+%         \item   $N' = 10$ is a reasonable budget allocation for LSTM metamodels.
+%     \end{itemize}
+
+%     \note{This table shows the MSEs of the two LSTM metamodels on different datasets. \\}
+%     \note{We modify $M$, the number of outer scenarios, and $N'$, the number of inner replications. \\}
+%     \note{$M$ is the number of data points in the training set, and $N'$ is the noise level in the training labels. \\}
+%     \note{We see similar patterns as in the previous table. \\}
+%     \note{Additional findings being that the number of data points, $M$ also matters. \\}
+%     \note{And it matters more for than $N'$ does. \\}
+%     \note{In this table, the entries in the same diagonal represent the same total simulation budget. \\}
+%     \note{It gives us a good indication of how much noise the LSTM metamodel can tolerate. \\}
+%     \note{For a practical application, we almost want to increase $M$ as much as possible. \\}
+%     \note{However, we can see that in the diagonal of red color, we should keep $N'$ at 10 and not lower it to 1. \\}
+%     \note{We don't want the training labels to be too noisy. \\}
+%     \note{If we increase $M$ too much, the performance of the regular LSTM will also deteriorate. \\}
+
+% \end{frame}
 
@@
 
+    \note{The findings are similar for the high-capacity LSTM metamodel. \\}
+    \note{We can find similar patterns as in the previous table. \\}
+    \note{The model is more sensitive to $N'$ than $M$, unless $N'$ is very small. \\}
+    \note{For a practical application, we recommend using the high-capacity LSTM metamodel with $N' = 10$ for almost all simulation budgets. }
+
 \end{frame}
@@
         \centering
-        \includegraphics[width=0.48\textwidth]{../project2/figures/singleStage/CVaRmediumNoise.png}
-        \includegraphics[width=0.48\textwidth]{../project2/figures/singleStage/CVaRhighNoise.png}
-        \caption{CVaR estimates of single-stage procedures (left: $N' = 10$. right: $N' = 1$).}
+        \includegraphics[width=0.6\textwidth]{../project2/figures/singleStage/CVaRmediumNoise.png}
+        % \includegraphics[width=0.48\textwidth]{../project2/figures/singleStage/CVaRhighNoise.png}
+        \caption{CVaR estimates of single-stage procedures with $N' = 10$.}
     \end{figure}
@@
         \item   The single-stage procedure outperforms the two-stage procedure.
-        \item   The single-stage procedure is more efficient than the two-stage procedure.
-        \item   Setting $N' = 10$ is a reasonable budget allocation.
-    \end{itemize}
-
-\end{frame}
-
-\begin{frame}{Convergence Analysis}
-
-    For each $\Gamma$, the best performing metamodel is used.
-
-    \begin{itemize}
-        \item   Maximum number of outer scenarios $M = 10^5$.
-    \end{itemize}
-
-    \begin{figure}[ht!]
-        \centering
-        \includegraphics[width=0.48\textwidth]{../project2/figures/singleStage/MSEConvergence_lstmLoCap.png}
-        \includegraphics[width=0.48\textwidth]{../project2/figures/singleStage/MSEConvergence_lstmHiCap.png}
-        \caption{Empirical convergence of CVaR for single-stage procedures with LSTM metamodels (left: regular LSTM. right: high-capacity LSTM).}
-    \end{figure}
-
-    \begin{itemize}
-        \item   Minimal effect of increasing $N'$ on CVaR estimation.
-        \item   Similar behavior as regression metamodels ($d=20$) in the previous section.
-    \end{itemize}
-
-\end{frame}
+        \item   $N' = 10$ is a reasonable budget allocation.
+    \end{itemize}
+
+    \note{This figure shows the CVaR estimates of the single-stage procedure. \\}
+    \note{We compare it with the two-stage procedure using regular LSTM metamodel with no safety margin.
+So we are using the 5\% metamodel predicted tails to estimate the 95\% CVaR with extensive simulation in stage 2.
+\\}
+    \note{The single-stage procedure with LSTM metamodels outperforms the two-stage procedure when noise level is moderate. \\}
+    \note{Due to its design, the single-stage procedure is more efficient than the two-stage procedure. \\}
+    \note{Setting $N' = 10$ is a reasonable budget allocation for the single-stage procedure. \\}
+    \note{Further decreasing $N'$ to 1 deteriorates the performance of the single-stage procedure.
+But it is worth noting that the 2-stage procedure can overcome this issue by increasing the safety margin.
+\\}
+
+\end{frame}
+
+% \begin{frame}{Convergence Analysis}
+
+%     For each $\Gamma$, the best performing metamodel is used.
+
+%     \begin{itemize}
+%         \item   Maximum number of outer scenarios $M = 10^5$.
+%     \end{itemize}
+
+%     \begin{figure}[ht!]
+%         \centering
+%         \includegraphics[width=0.48\textwidth]{../project2/figures/singleStage/MSEConvergence_lstmLoCap.png}
+%         \includegraphics[width=0.48\textwidth]{../project2/figures/singleStage/MSEConvergence_lstmHiCap.png}
+%         \caption{Empirical convergence of CVaR for single-stage procedures with LSTM metamodels (left: regular LSTM. right: high-capacity LSTM).}
+%     \end{figure}
+
+%     \begin{itemize}
+%         \item   Minimal effect of increasing $N'$ on CVaR estimation.
+%         \item   Similar behavior as regression metamodels ($d=20$) in the previous section.
+%     \end{itemize}
+
+%     \note{This figure shows the empirical convergence of CVaR for the single-stage procedure with LSTM metamodels. \\}
+%     \note{We use the best performing metamodel for each $\Gamma$. \\}
+%     \note{The maxmium number of outer scenarios we can afford is $M = 10^5$. \\}
+%     \note{For budget larger than $10^6$, we uses higher $N'$ and keeping the maximum number of outer scenarios $M$ fixed at $10^5$. \\}
+%     \note{The regular LSTM plot on the left between $10^3$ and $10^6$ offers a good indication of how empirically LSTM-based CVaR estimation converges to the true CVaR. \\}
+%     \note{We can further investigate the convergence rate by plotting the RRMSE for $M$ and $N$ separately. \\}
+
+% \end{frame}
 
@@
 
+    \note{This figure shows the empirical convergence of the single-stage procedure with LSTM metamodels when only $M$ or $N'$ is varied. \\}
+    \note{On the left, we fix $M=10^5$ and vary $N'$. \\}
+    \note{There is no significant difference to further increase $N'$ when $N' \geq 10$. \\}
+    \note{On the right, we fix $N'=10$ and vary $M$. \\}
+    \note{We can see that the convergence rate is around $O(M^{-2/3})$. \\}
+    \note{This finding is consistent with our previous analysis on the sensitivity of LSTM metamodels to data quality and data quantity. \\}
+    \note{Once the quality is good enough, the quantity is more important. \\}
+
 \end{frame}
@@
         \item   LSTMs are \textbf{resilient} to moderate levels of noise in training labels.
-        \item   Deep neural networks can learn \textbf{true} complex dynamic hedging model.
-        \item   Two-stage procedure addresses regulatory concerns by avoiding direct use of metamodel predictions.
-        \item   Single-stage procedure is \textbf{efficient} and \textbf{versatile}.
-        \item   \textbf{Increasing outer scenarios} is more beneficial.
-        \item   High-capacity LSTM requires lower noise training labels.
+        \item   DNNs can learn \textbf{true} complex dynamic hedging model.
+        \item   Two-stage procedure addresses regulatory concerns.
+        \item   Single-stage procedure is \textbf{efficient}.
     \end{itemize}
@@
     \begin{itemize}
-        \item   Apply deep neural network metamodels to other risk management tasks.
-        \item   Investigate impact of label noise on other deep learning models 
-        \item   Explore optimal network architectures for different simulation models.
-    \end{itemize}
-
-\end{frame}
-
-\section{Transfer Learning for Rapid Adaptation of DNN Metamodels}
-\begin{frame}{Transfer Learning for Rapid Adaptation of DNN Metamodels}
-
-    \textbf{Challenge:} Adapting deep neural network metamodels to changing conditions.
-    \begin{itemize}
-        \item   Retraining from scratch is computationally expensive.
-        \item   Efficient incorporation of new VA contract data.
-        \item   Balancing model accuracy and computational costs.
-    \end{itemize}
-
-    \vspace{10pt}
-
-    \textbf{Solution:} Transfer learning (TL) to develop adaptable, efficient metamodels for VA dynamic hedging.
-
-    \begin{itemize}
-        \item   Pre-train deep neural network on contracts with abundant simulation data.
-        \item   Fine-tune on smaller dataset of new contracts/market conditions.
-        \item   Leverages shared features between VA contracts.
-        \item   Computational savings:
-            \begin{itemize}
-                \item   Reduced training time.
-                \item   Fewer data points needed for good performance.
-            \end{itemize}
-    \end{itemize}
-
-\end{frame}
-
-\begin{frame}{Transfer Learning Framework}
-
-    \textbf{Key Components:}
-    \begin{itemize}
-        \item   \textbf{Domain} $\mathcal{D}$: feature space $\mathcal{X}$ + probability distribution $F$
-        \item   \textbf{Task} $\mathcal{T}$: label space $\mathcal{Y}$ + predictive function $f: \mathcal{X} \rightarrow \mathcal{Y}$
-    \end{itemize}
-
-    \vspace{10pt}
-    \textbf{Source vs. Target:}
-    \begin{itemize}
-        \item   \textbf{Source:} $\mathcal{D}_{\text{So}} = \{\mathcal{X}_{\text{So}}, F_{\text{So}}(X)\}$
-        \item   \textbf{Target:} $\mathcal{D}_{\text{Ta}} = \{\mathcal{X}_{\text{Ta}}, F_{\text{Ta}}(X)\}$
-    \end{itemize}
-
-    \vspace{10pt}
-    \textbf{Our Goal:}
-    \begin{itemize}
-        \item   \textbf{Input features} $X$: risk factors from outer simulation
-        \item   \textbf{Output labels} $L$: contract losses
-        \item   \textbf{Source and target}: from VAs with abundant simulation data to new VAs with limited data
-        \item   \textbf{Goal}: improve $f_{\text{Ta}}(\cdot)$ using knowledge from $\mathcal{D}_{\text{So}}$ and $f_{\text{So}}(\cdot)$
-    \end{itemize}
-
-\end{frame}
-
-\begin{frame}{Transfer Learning Techniques}
-
-    \textbf{Common Techniques:}
-    \begin{itemize}
-        \item   \textbf{Fine-tuning:} a model pre-trained on a source task is used as a starting point for a target task.
-        \item   \textbf{Layer freezing:} only part of the model is fine-tuned.
-        \item   \textbf{Multi-task learning:} perform training on multiple tasks simultaneously.
-    \end{itemize}
-
-    \vspace{10pt}
-
-    \textbf{Key considerations:}
-    \begin{itemize}
-        \item   Similarity between source and target tasks
-        \item   Appropriate learning rate
-    \end{itemize}
-
-\end{frame}
-
-\begin{frame}{Fine-tuning Algorithm for LSTM Metamodels in VA Hedging}
-
-    \begin{algorithm}[H]
-        \caption{Fine-tuning Algorithm for LSTM Metamodels in VA Hedging}
-        \begin{algorithmic}[1]
-            \STATE \textbf{Input:} $\mathcal{D}_{\text{So}} = \{(X_{\text{So}}^{(i)}, L_{\text{So}}^{(i)})\}_{i=1}^{M_{\text{So}}}$ , $\mathcal{D}_{\text{Ta}} = \{(X_{\text{Ta}}^{(i)}, L_{\text{Ta}}^{(i)})\}_{i=1}^{M_{\text{Ta}}}$, $\alpha_{\text{So}}$, and $\alpha_{\text{Ta}}$.
-            \STATE Train a LSTM metamodel $f_{\text{So}}(\cdot; \theta_{\text{So}})$ on $\mathcal{D}_{\text{So}}$:
-            \begin{equation*}
-                \theta_{\text{So}} = \min_{\theta} \frac{1}{M_{\text{So}}} \sum_{i=1}^{M_{\text{So}}} \left( f_{\text{So}}(X_{\text{So}}^{(i)}; \theta) - L_{\text{So}}^{(i)} \right)^2
-            \end{equation*}
-            \STATE Initialize the target metamodel parameters $\theta_{\text{Ta}}$ using the pre-trained metamodel parameters:
-            \begin{equation*}
-                \theta_{\text{Ta}} \gets \theta_{\text{So}}
-            \end{equation*}
-            \STATE Fine-tune the entire LSTM metamodel $f_{\text{Ta}}(\cdot; \theta_{\text{Ta}})$ on the target dataset $\mathcal{D}_{\text{Ta}}$ using a smaller learning rate $\alpha_{\text{Ta}}$:
-            \begin{equation*}
-                \theta_{\text{Ta}} = \min_{\theta} \frac{1}{M_{\text{Ta}}} \sum_{i=1}^{M_{\text{Ta}}} \left( f_{\text{Ta}}(X_{\text{Ta}}^{(i)}; \theta) - L_{\text{Ta}}^{(i)} \right)^2
-            \end{equation*}
-            \STATE \textbf{Output:} Final adapted LSTM metamodel $f_{\text{Ta}}(\cdot; \theta_{\text{Ta}})$ for the target task
-        \end{algorithmic}
-    \end{algorithm}
-
-\end{frame}
-
-\begin{frame}{Layer Freezing Algorithm for LSTM Metamodels in VA Hedging}
-
-    \begin{algorithm}[H]
-        \caption{Layer Freezing Algorithm for LSTM Metamodels in VA Hedging}
-        \begin{algorithmic}[1]
-            \STATE \textbf{Input:} $\mathcal{D}_{\text{So}} = \{(X_{\text{So}}^{(i)}, L_{\text{So}}^{(i)})\}_{i=1}^{M_{\text{So}}}$ , $\mathcal{D}_{\text{Ta}} = \{(X_{\text{Ta}}^{(i)}, L_{\text{Ta}}^{(i)})\}_{i=1}^{M_{\text{Ta}}}$, $\alpha_{\text{So}}$, and $\alpha_{\text{Ta}}$.
-            \STATE Train LSTM model $f_{\text{So}}(\cdot; \theta_{\text{So}})$ on $\mathcal{D}_{\text{So}}$.
-            \STATE Initialize the target model parameters $\theta_{\text{Ta}} = [\theta_0, \theta_1]$ using the pre-trained source model parameters $\theta_{\text{So}}$:
-            \begin{equation*}
-                \theta_{\text{Ta}} \gets \theta_{\text{So}} = [\theta_0, \theta_1]
-            \end{equation*}
-            \STATE Freeze the parameters of the shared layers $\theta_0$ and fine-tune the trainable layers $\theta_1$ on the target dataset $\mathcal{D}_{\text{Ta}}$:
-            \begin{equation*}
-                \theta_{\text{Ta}} = \min_{\theta_1} \frac{1}{M_{\text{Ta}}} \sum_{i=1}^{M_{\text{Ta}}} \left( f_{\text{Ta}}(X_{\text{Ta}}^{(i)}; [\theta_0, \theta_1]) - L_{\text{Ta}}^{(i)} \right)^2
-            \end{equation*}
-            \STATE \textbf{Output:} Adapted model $f_{\text{Ta}}(\cdot; \theta_{\text{Ta}})$ for the target task.
-        \end{algorithmic}
-    \end{algorithm}
-
-\end{frame}
-
-\begin{frame}{Multi-task Learning Algorithm for LSTM Metamodels in VA Hedging}
-
-    \begin{algorithm}[H]
-        \caption{Multi-task Learning Algorithm for LSTM Metamodels in VA Hedging}
-        \begin{algorithmic}[1] \label{alg3:multiTaskLearning}
-            \STATE \textbf{Input:} learning rate $\alpha$, set of $K$ tasks $\{\mathcal{T}_k\}_{k=1}^K$ with datasets $\mathcal{D}_k = \{(X_k^{(i)}, L_k^{(i)})\}_{i=1}^{M_k}$, task-specific parameters $\theta_k$ for each task $k$, and shared parameters $\theta_0$.
-
-            \STATE Train the multi-head LSTM metamodel on all $K$ tasks simultaneously by minimizing the multi-task loss function:
-            \begin{equation} \label{eq3:multiTaskLoss}
-                \min_{\theta_0, \{\theta_k\}_{k=1}^K} \sum_{k=1}^K \frac{1}{M_k} \sum_{i=1}^{M_k} \left( f_i(X_k^{(i)}; \theta_0, \theta_k) - L_k^{(i)} \right)^2
-            \end{equation}
-
-            \STATE Update both the shared parameters $\theta_0$ and task-specific parameters $\{\theta_k\}_{k=1}^K$ simultaneously using backpropagation and gradient descent with learning rate $\alpha$.
-
-            \STATE \textbf{Output:} Trained multi-task metamodel $f(\cdot; \theta_0, \{\theta_k\}_{k=1}^K)$ for all $K$ tasks
-        \end{algorithmic}
-    \end{algorithm}
-
-\end{frame}
-
-\begin{frame}{Experiment Setup}
-
-    \begin{table}[ht!] 
-        \centering
-        \begin{tabular}{lcccc} 
-        \toprule
-        \textbf{Contract} & \textbf{Asset Model} & \textbf{Lapse} & \textbf{$M_{\text{So}}$}  & \textbf{$M_{\text{Ta}}$}\\
-        \midrule
-        GMMB & GBM & No lapse & 50000 & N/A \\
-        GMMB & RS-GBM & No lapse & 50000 & 2000 \\
-        GMMB & RS-GBM & Static lapse & 50000 & 2000 \\
-        GMMB & RS-GBM & Dynamic lapse & 50000 & 2000 \\
-        GMWB & RS-GBM & Dynamic lapse & N/A & 2000 \\
-        \bottomrule
-        \end{tabular}
-        \caption{VA Contracts for Transfer Learning Experiments}
-    \end{table}
-
-    We aim to examine the performance of TL techniques
-    \begin{itemize}
-        \item   learning the lapse features,
-        \item   learning the dynamic lapse, and 
-        \item   transferring to other contract types.
-    \end{itemize}
-
-\end{frame}
-
-\begin{frame}{Learning Lapse Features}
-    \begin{figure}[ht!]
-        \centering
-        \begin{subfigure}{0.48\textwidth}
-            \includegraphics[width=\textwidth]{../project3/figures/figure1a.png}
-            \caption{Extensive Training on Target Task}
-        \end{subfigure}
-        \begin{subfigure}{0.48\textwidth}
-            \includegraphics[width=\textwidth]{../project3/figures/figure1b.png}
-            \caption{Without TL}
-        \end{subfigure}
-        \caption{Direct training on RS-GBM GMMB with static lapse}
-    \end{figure}
-\end{frame}
-
-\begin{frame}{Learning Lapse Features}
-    \begin{figure}[ht!]
-        \centering
-        \begin{subfigure}{0.48\textwidth}
-            \includegraphics[width=\textwidth]{../project3/figures/figure1c.png}
-            \caption{With Fine-tuning}
-        \end{subfigure}
-        \begin{subfigure}{0.48\textwidth}
-            \includegraphics[width=\textwidth]{../project3/figures/figure1d.png}
-            \caption{With Layer Freezing}
-        \end{subfigure}
-        \caption{TL on RS-GBM GMMB with static lapse}
-    \end{figure}
-
-\end{frame}
+        \item   Apply DNNs to other risk management tasks.
+        \item   Fast adaptation to new contracts/market conditions.
+    \end{itemize}
+
+    \note{In this project, we present our extensive research into LSTM metamodels in a simulation setting.\\}
+    \note{Our findings demonstrate that LSTMs can effectively learn complex hedging strategies even with noisy training data.\\}
+    \note{The single-stage procedure offers an excellent balance of efficiency and accuracy for practical applications.\\}
+    \note{We've shown that allocating computational budget to increase outer scenarios rather than inner simulations yields better results.\\}
+    \note{These insights provide valuable guidance for implementing machine learning in financial risk management.\\}
+
+    \note{For the research directions. In the future, we can apply deep neural network metamodels to other actuarial applications.\\}
+    \note{In the future, we can also apply transfer learning to speed up the training process for deep neural network metamodels.\\}
+
+\end{frame}
+
+\section[TL for DNN Metamodels]{Transfer Learning for Rapid Adaptation of DNN Metamodels}
+
+% \begin{frame}{Transfer Learning for Rapid Adaptation of DNN Metamodels}
+
+%     \textbf{Challenge:} Adapting deep neural network metamodels to changing conditions.
+%     \begin{itemize}
+%         \item   Retraining from scratch is computationally expensive.
+%         \item   Efficient incorporation of new VA contract data.
+%         \item   Balancing model accuracy and computational costs.
+%     \end{itemize}
+
+%     \vspace{10pt}
+
+%     \textbf{Solution:} Transfer learning (TL) to develop adaptable, efficient metamodels for VA dynamic hedging.
+
+%     \begin{itemize}
+%         \item   Pre-train deep neural network on contracts with abundant simulation data.
+%         \item   Fine-tune on smaller dataset of new contracts/market conditions.
+%         \item   Leverages shared features between VA contracts.
+%         \item   Computational savings:
+%             \begin{itemize}
+%                 \item   Reduced training time.
+%                 \item   Fewer data points needed for good performance.
+%             \end{itemize}
+%     \end{itemize}
+
+%     \note{In this project, we propose a transfer learning framework for rapid adaptation of deep neural network metamodels in VA dynamic hedging.\\ }
+%     \note{The problem is the same as the previous project. We want to use deep neural network metamodels to approximate the complex simulation model that involves dynamic hedging.\\}
+%     \note{The difference is that we want to use transfer learning to speed up the training process.\\}
+%     \note{This can be beneficial for the practical applications.\\}
+%     \note{Firstly, new VA contracts are continuously issued.\\}
+%     \note{Secondly, market conditions are changing.\\}
+%     \note{Thirdly, the computational budget is limited.\\}
+%     \note{Transfer learning can help us to adapt to the new market conditions quickly and efficiently.\\}
+%     \note{We can pre-train the deep neural network metamodel on a large dataset of VA contracts with abundant simulation data.\\}
+%     \note{Then, we can fine-tune the metamodel on a smaller dataset of new VA contracts with limited data.\\}
+%     \note{The data is often limited for new VA contracts as simulation is expensive to run.\\}
+%     \note{The shared features between VA contracts can be leveraged to speed up the training process.\\}
+%     \note{We can also transfer the knowledge to other contract types.\\}
+%     \note{When a new VA contract is issued, we can use transfer learning to adapt the metamodel to the new contract quickly.\\}
+
+% \end{frame}
+
+% \begin{frame}{Transfer Learning Framework}
+
+%     \textbf{Key Components:}
+%     \begin{itemize}
+%         \item   \textbf{Domain} $\mathcal{D}$: feature space $\mathcal{X}$ + probability distribution $F$
+%         \item   \textbf{Task} $\mathcal{T}$: label space $\mathcal{Y}$ + predictive function $f: \mathcal{X} \rightarrow \mathcal{Y}$
+%     \end{itemize}
+
+%     \vspace{10pt}
+%     \textbf{Source vs. Target:}
+%     \begin{itemize}
+%         \item   \textbf{Source:} $\mathcal{D}_{\text{So}} = \{\mathcal{X}_{\text{So}}, F_{\text{So}}(X)\}$
+%         \item   \textbf{Target:} $\mathcal{D}_{\text{Ta}} = \{\mathcal{X}_{\text{Ta}}, F_{\text{Ta}}(X)\}$
+%     \end{itemize}
+
+%     \vspace{10pt}
+%     \textbf{Our Goal:}
+%     \begin{itemize}
+%         \item   \textbf{Input features} $X$: risk factors from outer simulation
+%         \item   \textbf{Output labels} $L$: contract losses
+%         \item   \textbf{Source and target}: from VAs with abundant simulation data to new VAs with limited data
+%         \item   \textbf{Goal}: improve $f_{\text{Ta}}(\cdot)$ using knowledge from $\mathcal{D}_{\text{So}}$ and $f_{\text{So}}(\cdot)$
+%     \end{itemize}
+
+%     \note{Transfer learning provides a formal framework for adapting models from one domain to another.\\}
+%     \note{The domain consists of a feature space and a probability distribution over that space.\\}
+%     \note{In our context, the feature space includes risk factors from the outer simulation.\\}
+%     \note{It is equipped with a probability distribution that describes the joint distribution of the risk factors.\\}
+%     \note{We don't know the exact joint distribution of the risk factors, but we can simulate outer scenarios from it using monte carlo simulation.\\}
+%     \note{The task consists of a label space and a predictive function mapping features to labels.\\}
+%     \note{For VA contracts, our labels are the contract losses under different scenarios.\\}
+%     \note{The source domain typically has abundant data - this could be existing VA contracts with extensive simulation data.\\}
+%     \note{The target domain has limited data - new VA contracts or existing contracts under new market conditions.\\}
+%     \note{Our goal is to leverage knowledge from the source domain to improve prediction in the target domain.\\}
+%     \note{This is particularly valuable when simulation data is expensive to generate for new contracts.\\}
+%     \note{The transfer learning approach allows us to maintain accuracy while significantly reducing computational requirements.\\}
+
+% \end{frame}
+
+% \begin{frame}{Transfer Learning Techniques}
+
+%     \textbf{Common Techniques:}
+%     \begin{itemize}
+%         \item   \textbf{Fine-tuning:} a model pre-trained on a source task is used as a starting point for a target task.
+%         \item   \textbf{Layer freezing:} only part of the model is fine-tuned.
+%         \item   \textbf{Multi-task learning:} perform training on multiple tasks simultaneously.
+%     \end{itemize}
+
+%     \vspace{10pt}
+
+%     \textbf{Key considerations:}
+%     \begin{itemize}
+%         \item   Similarity between source and target tasks
+%         \item   Appropriate learning rate
+%     \end{itemize}
+
+%     \note{Fine-tuning involves using a pre-trained model as a starting point for a new task.\\}
+%     \note{This approach is effective when the source and target tasks are similar.\\}
+%     \note{For VA contracts, we can fine-tune models between different contract types or market conditions.\\}
+%     \note{Layer freezing is a technique where we keep some layers of the pre-trained model fixed.\\}
+%     \note{Typically, early layers capture general features while later layers are more task-specific.\\}
+%     \note{By freezing early layers, we preserve general knowledge while adapting task-specific layers.\\}
+%     \note{Multi-task learning trains a single model to perform multiple related tasks simultaneously.\\}
+%     \note{This approach can improve generalization by leveraging the domain-specific information across tasks.\\}
+%     \note{For VA contracts, we can train a model to handle multiple contract types or features.\\}
+%     \note{The learning rate is a critical hyperparameter in transfer learning.\\}
+%     \note{Typically, we use a smaller learning rate for fine-tuning compared to training from scratch.\\}
+%     \note{The similarity between source and target tasks greatly impacts transfer learning effectiveness.\\}
+%     \note{More similar tasks generally allow for more effective knowledge transfer.\\}
+
+% \end{frame}
+
+% \begin{frame}{Fine-tuning Algorithm for LSTM Metamodels in VA Hedging}
+
+%     \begin{algorithm}[H]
+%         \caption{Fine-tuning Algorithm for LSTM Metamodels in VA Hedging}
+%         \begin{algorithmic}[1]
+%             \STATE \textbf{Input:} $\mathcal{D}_{\text{So}} = \{(X_{\text{So}}^{(i)}, L_{\text{So}}^{(i)})\}_{i=1}^{M_{\text{So}}}$ , $\mathcal{D}_{\text{Ta}} = \{(X_{\text{Ta}}^{(i)}, L_{\text{Ta}}^{(i)})\}_{i=1}^{M_{\text{Ta}}}$, $\alpha_{\text{So}}$, and $\alpha_{\text{Ta}}$.
+%             \STATE Train a LSTM metamodel $f_{\text{So}}(\cdot; \theta_{\text{So}})$ on $\mathcal{D}_{\text{So}}$:
+%             \begin{equation*}
+%                 \theta_{\text{So}} = \min_{\theta} \frac{1}{M_{\text{So}}} \sum_{i=1}^{M_{\text{So}}} \left( f_{\text{So}}(X_{\text{So}}^{(i)}; \theta) - L_{\text{So}}^{(i)} \right)^2
+%             \end{equation*}
+%             \STATE Initialize the target metamodel parameters $\theta_{\text{Ta}}$ using the pre-trained metamodel parameters:
+%             \begin{equation*}
+%                 \theta_{\text{Ta}} \gets \theta_{\text{So}}
+%             \end{equation*}
+%             \STATE Fine-tune the entire LSTM metamodel $f_{\text{Ta}}(\cdot; \theta_{\text{Ta}})$ on the target dataset $\mathcal{D}_{\text{Ta}}$ using a smaller learning rate $\alpha_{\text{Ta}}$:
+%             \begin{equation*}
+%                 \theta_{\text{Ta}} = \min_{\theta} \frac{1}{M_{\text{Ta}}} \sum_{i=1}^{M_{\text{Ta}}} \left( f_{\text{Ta}}(X_{\text{Ta}}^{(i)}; \theta) - L_{\text{Ta}}^{(i)} \right)^2
+%             \end{equation*}
+%             \STATE \textbf{Output:} Final adapted LSTM metamodel $f_{\text{Ta}}(\cdot; \theta_{\text{Ta}})$ for the target task
+%         \end{algorithmic}
+%     \end{algorithm}
+
+%     \note{This algorithm outlines the fine-tuning process for LSTM metamodels in VA hedging. \\}
+%     \note{We start with a source dataset $\mathcal{D}_{\text{So}}$ and a target dataset $\mathcal{D}_{\text{Ta}}$. \\}
+%     \note{First, we train the source model on the larger source dataset. \\}
+%     \note{Then we initialize the target model with the pre-trained weights from the source model. \\}
+%     \note{The key is using a smaller learning rate $\alpha_{\text{Ta}}$ during fine-tuning. \\}
+%     \note{This prevents catastrophic forgetting of useful features learned from the source task. \\}
+%     \note{The entire model is updated during fine-tuning, unlike layer freezing. \\}
+%     \note{This approach works well when source and target tasks are similar. \\}
+%     \note{For VA contracts, this might mean transferring between similar contract types. \\}
+%     \note{The effectiveness depends on the similarity between source and target domains. \\}
+% \end{frame}
+
+% \begin{frame}{Layer Freezing Algorithm for LSTM Metamodels in VA Hedging}
+
+%     \begin{algorithm}[H]
+%         \caption{Layer Freezing Algorithm for LSTM Metamodels in VA Hedging}
+%         \begin{algorithmic}[1]
+%             \STATE \textbf{Input:} $\mathcal{D}_{\text{So}} = \{(X_{\text{So}}^{(i)}, L_{\text{So}}^{(i)})\}_{i=1}^{M_{\text{So}}}$ , $\mathcal{D}_{\text{Ta}} = \{(X_{\text{Ta}}^{(i)}, L_{\text{Ta}}^{(i)})\}_{i=1}^{M_{\text{Ta}}}$, $\alpha_{\text{So}}$, and $\alpha_{\text{Ta}}$.
+%             \STATE Train LSTM model $f_{\text{So}}(\cdot; \theta_{\text{So}})$ on $\mathcal{D}_{\text{So}}$.
+%             \STATE Initialize the target model parameters $\theta_{\text{Ta}} = [\theta_0, \theta_1]$ using the pre-trained source model parameters $\theta_{\text{So}}$:
+%             \begin{equation*}
+%                 \theta_{\text{Ta}} \gets \theta_{\text{So}} = [\theta_0, \theta_1]
+%             \end{equation*}
+%             \STATE Freeze the parameters of the shared layers $\theta_0$ and fine-tune the trainable layers $\theta_1$ on the target dataset $\mathcal{D}_{\text{Ta}}$:
+%             \begin{equation*}
+%                 \theta_{\text{Ta}} = \min_{\theta_1} \frac{1}{M_{\text{Ta}}} \sum_{i=1}^{M_{\text{Ta}}} \left( f_{\text{Ta}}(X_{\text{Ta}}^{(i)}; [\theta_0, \theta_1]) - L_{\text{Ta}}^{(i)} \right)^2
+%             \end{equation*}
+%             \STATE \textbf{Output:} Adapted model $f_{\text{Ta}}(\cdot; \theta_{\text{Ta}})$ for the target task.
+%         \end{algorithmic}
+%     \end{algorithm}
+
+%     \note{The difference between the fine-tuning and layer freezing algorithms is that the parameters of the shared layers are frozen in the layer freezing algorithm. \\}
+%     \note{This allows us to preserve the general knowledge learned from the source task while adapting the task-specific layers. \\}
+%     \note{Layer freezing is particularly effective when the source and target tasks share similar low-level features. \\}
+%     \note{In the context of VA contracts, this might mean transferring between contracts with similar underlying asset dynamics. \\}
+%     \note{The choice of which layers to freeze is critical - typically early layers capture general features. \\}
+%     \note{Later layers tend to be more task-specific and should be fine-tuned. \\}
+%     \note{This approach preserves the feature extraction capabilities learned from the source task. \\}
+%     \note{It's computationally efficient as fewer parameters need to be updated during training. \\}
+%     \note{Layer freezing can help prevent overfitting when the target dataset is small. \\}
+%     \note{The tradeoff is less flexibility compared to full fine-tuning. \\}
+%     \note{For VA contracts with significantly different features, fine-tuning may be more appropriate. \\}
+%     \note{Empirical testing is often needed to determine the optimal freezing strategy. \\}
+
+% \end{frame}
+
+% \begin{frame}{Multi-task Learning Algorithm for LSTM Metamodels in VA Hedging}
+
+%     \begin{algorithm}[H]
+%         \caption{Multi-task Learning Algorithm for LSTM Metamodels in VA Hedging}
+%         \begin{algorithmic}[1] \label{alg3:multiTaskLearning}
+%             \STATE \textbf{Input:} learning rate $\alpha$, set of $K$ tasks $\{\mathcal{T}_k\}_{k=1}^K$ with datasets $\mathcal{D}_k = \{(X_k^{(i)}, L_k^{(i)})\}_{i=1}^{M_k}$, task-specific parameters $\theta_k$ for each task $k$, and shared parameters $\theta_0$.
+
+%             \STATE Train the multi-head LSTM metamodel on all $K$ tasks simultaneously by minimizing the multi-task loss function:
+%             \begin{equation} \label{eq3:multiTaskLoss}
+%                 \min_{\theta_0, \{\theta_k\}_{k=1}^K} \sum_{k=1}^K \frac{1}{M_k} \sum_{i=1}^{M_k} \left( f_i(X_k^{(i)}; \theta_0, \theta_k) - L_k^{(i)} \right)^2
+%             \end{equation}
+
+%             \STATE Update both the shared parameters $\theta_0$ and task-specific parameters $\{\theta_k\}_{k=1}^K$ simultaneously using backpropagation and gradient descent with learning rate $\alpha$.
+
+%             \STATE \textbf{Output:} Trained multi-task metamodel $f(\cdot; \theta_0, \{\theta_k\}_{k=1}^K)$ for all $K$ tasks
+%         \end{algorithmic}
+%     \end{algorithm}
+
+%     \note{Multi-task learning allows simultaneous training on multiple VA contract types. \\}
+%     \note{The algorithm shares parameters across tasks while maintaining task-specific components. \\}
+%     \note{This approach leverages the common underlying financial and mathematical structures. \\}
+%     \note{The shared parameters $\theta_0$ capture general features applicable to all contracts. \\}
+%     \note{Task-specific parameters $\theta_k$ adapt to the unique characteristics of each contract. \\}
+%     \note{The loss function balances performance across all tasks. \\}
+%     \note{This is particularly valuable when data for some contract types is limited. \\}
+%     \note{Multi-task learning can improve generalization compared to single-task models. \\}
+%     \note{It reduces the risk of overfitting on smaller datasets. \\}
+%     \note{For VA contracts, this enables efficient modeling of GMMB and GMWB simultaneously. \\}
+%     \note{The approach is scalable to more than two contract types. \\}
+%     \note{Implementation requires careful balancing of task contributions to prevent domination. \\}
+%     \note{Computational efficiency is achieved through shared feature extraction. \\}
+
+% \end{frame}
+
+% \begin{frame}{Multi-task Learning}
+%     \includegraphics[width=0.9\textwidth]{../project3/figures/mtl.png}
+
+%     \begin{itemize}
+%         \item LSTM layers shared across multiple tasks
+%         \item Task-specific fully connected layers
+%         \item Objective: Minimize sum of loss functions across all tasks
+%     \end{itemize}
+
+%     \note{Multi-task learning offers an alternative approach to transfer learning. \\}
+%     \note{Instead of sequential knowledge transfer, we train on multiple contract types simultaneously. \\}
+%     \note{The shared LSTM layers capture common features across different VA contracts. \\}
+%     \note{Task-specific layers then specialize for each contract type's unique characteristics. \\}
+%     \note{We will examine whether this approach can be more efficient than training separate models for each contract type. \\}
+
+% \end{frame}
+
+% \begin{frame}{Experiment Setup}
+
+%     \begin{table}[ht!] 
+%         \centering
+%         \begin{tabular}{lcccc} 
+%         \toprule
+%         \textbf{Contract} & \textbf{Asset Model} & \textbf{Lapse} & \textbf{$M_{\text{So}}$}  & \textbf{$M_{\text{Ta}}$}\\
+%         \midrule
+%         GMMB & GBM & No lapse & 50000 & N/A \\
+%         GMMB & RS-GBM & No lapse & 50000 & 2000 \\
+%         GMMB & RS-GBM & Static lapse & 50000 & 2000 \\
+%         GMMB & RS-GBM & Dynamic lapse & 50000 & 2000 \\
+%         GMWB & RS-GBM & Dynamic lapse & N/A & 2000 \\
+%         \bottomrule
+%         \end{tabular}
+%         \caption{VA Contracts for Transfer Learning Experiments}
+%     \end{table}
+
+%     We aim to examine the performance of TL techniques
+%     \begin{itemize}
+%         \item   learning the lapse features,
+%         \item   learning the dynamic lapse, and 
+%         \item   transferring to other contract types.
+%     \end{itemize}
+
+%     \note{We use a variety of VA contracts with different features to test transfer learning. \\}
+%     \note{The source model ($M_{\text{So}}$) is trained with 50,000 samples for comprehensive learning. \\}
+%     \note{The target model ($M_{\text{Ta}}$) uses only 2,000 samples to simulate limited data scenarios. \\}
+%     \note{We progress from simpler to more complex models (No lapse → Static → Dynamic). \\}
+%     \note{We examine both within-contract transfer (GMMB to GMMB with different features) and cross-contract transfer (GMMB to GMWB). \\}
+%     \note{The regime-switching GBM (RS-GBM) model captures more realistic market dynamics. \\}
+%     \note{All training data is generated using 100 inner replications for consistency. \\}
+%     \note{We compare fine-tuning and layer freezing as two primary transfer learning approaches. \\}
+%     \note{The experiments are designed to evaluate how similarity between source and target affects transfer efficiency. \\}
+%     \note{This is another attempt to use simulation models as data generating processes to examine deep neural networks. \\}
+%     \note{By examining the transfer learning performance, we can gain insights into which parts of the neural network are transferable, or more generally, which layers of the neural network learn which features of the VA contracts.
+\\}
+
+% \end{frame}
+
+% \begin{frame}{The Effect of Number of Training Samples}
+%     \begin{figure}[ht]
+%         \centering
+%         \begin{subfigure}{0.48\textwidth}
+%             \includegraphics[width=\textwidth]{../project3/figures/figure1a.png}
+%             \caption{50000 samples}
+%         \end{subfigure}
+%         \begin{subfigure}{0.48\textwidth}
+%             \includegraphics[width=\textwidth]{../project3/figures/figure1b.png}
+%             \caption{2000 samples}
+%         \end{subfigure}
+%         \caption{Learning curves of GMMB contracts with static lapse}
+%     \end{figure}
+
+%     \note{We first examine the effect of the number of training samples on the convergence of the model. \\}
+%     \note{There is no transfer learning in this experiment. \\}
+%     \note{With 50,000 training samples, the model converges quickly to a low MSE. \\}
+%     \note{With only 2,000 samples, convergence is slower and less stable. \\}
+%     \note{Limited data scenarios are common in practice due to computational constraints. \\}
+%     \note{The difference in performance highlights the need for transfer learning techniques. \\}
+%     \note{More training data leads to better generalization and lower prediction error. \\}
+%     \note{The figure on the right shows the challenge of training complex models with limited data. \\}
+%     \note{This motivates our exploration of transfer learning to improve performance with limited data. \\}
+
+% \end{frame}
+
+% \begin{frame}{Learning Lapse Features using Transfer Learning}
+
+%     \begin{figure}[ht]
+%         \centering
+%         \begin{subfigure}{0.48\textwidth}
+%             \includegraphics[width=\textwidth]{../project3/figures/figure1c.png}
+%             \caption{Fine-tuning}
+%         \end{subfigure}
+%         \begin{subfigure}{0.48\textwidth}
+%             \includegraphics[width=\textwidth]{../project3/figures/figure1d.png}
+%             \caption{Layer Freezing}
+%         \end{subfigure}
+%         \caption{Learning curves of GMMB contracts with static lapse}
+%     \end{figure}
+
+%     \note{This slide demonstrates the effectiveness of transfer learning techniques. \\}
+%     \note{Fine-tuning (left) allows all model parameters to be updated during training on the target task. \\}
+%     \note{Layer freezing (right) keeps early layers fixed and only updates later layers. \\}
+%     \note{Both transfer learning approaches show significant improvement over training from scratch. \\}
+%     \note{With only 2,000 samples, transfer learning achieves much lower MSE values. \\}
+%     \note{Fine-tuning also converges fast but layer freezing shows more stability. \\}
+%     \note{The knowledge transferred from the source model (no lapse) helps the model learn static lapse features. \\}
+%     \note{Transfer learning reduces overfitting and improves generalization with limited data. \\}
+%     \note{Here, we are only learning the lapse feature. \\}
+%     \note{This demonstrates how knowledge from one VA contract can be leveraged for another when the difference between the source and target is small. \\}
+
+% \end{frame}
+
+% \begin{frame}{Learning Curves: Learning Dynamic Lapse}
+
+%     \begin{figure}[ht]
+%         \centering
+%         \begin{subfigure}{0.48\textwidth}
+%             \includegraphics[width=\textwidth]{../project3/figures/figure2a.png}
+%             \caption{No Lapse}
+%         \end{subfigure}
+%         \begin{subfigure}{0.48\textwidth}
+%             \includegraphics[width=\textwidth]{../project3/figures/figure2b.png}
+%             \caption{Static Lapse}
+%         \end{subfigure}
+%         \caption{Learning curves of GMMB contracts with dynamic lapse}
+%     \end{figure}
+
+%     \note{This slide shows how transfer learning performs when learning dynamic lapse features. \\}
+%     \note{The left figure shows transfer from a model trained on contracts with no lapse. \\}
+%     \note{The right figure shows transfer from a model trained on contracts with static lapse. \\}
+%     \note{We observe that the source model's similarity to the target task significantly impacts transfer learning effectiveness. \\}
+%     \note{Transfer from static lapse (right) performs much better than transfer from no lapse (left). \\}
+%     \note{This demonstrates the importance of task similarity in transfer learning. \\}
+%     \note{When source and target domains are more similar (static to dynamic lapse), knowledge transfer is more effective. \\}
+
+% \end{frame}
+
+%     \begin{frame}{Results: Accuracy Comparison}
+%         \begin{table}
+%             \begin{tabular}{lr}
+%             \toprule
+%             \textbf{Method and Setting} & \textbf{MSE} \\
+%             \midrule
+%             Extensive Training (Dynamic) & \textbf{0.0587} \\
+%             Fine-tuning (Static) & 0.0794 \\
+%             Layer Freezing (Static) & 0.0763 \\
+%             Layer Freezing (No Lapse) & 0.3361 \\
+%             Fine-tuning (No Lapse) & 0.4894 \\
+%             Without TL (Dynamic) & 0.2950 \\
+%             \bottomrule
+%             \end{tabular}
+%             \caption{Comparison of different TL methods on GMMB contracts (best MSE values)}
+%         \end{table}
+
+%     \note{This table summarizes the MSE values for different training methods. \\}
+%     \note{Extensive training with full data achieves the best performance (0.0587 MSE). \\}
+%     \note{Without transfer learning, training from scratch on dynamic lapse data yields mediocre results (0.2950 MSE). \\}
+%     \note{Transfer learning from static lapse models (both fine-tuning and layer freezing) performs well. \\}
+%     \note{Transfer from no lapse models performs poorly, demonstrating that negative transfer can occur. \\}
+%     \note{Negative transfer happens when source and target tasks are substantially different. \\}
+%     \note{In such cases, knowledge from the source model can actually hinder learning on the target task. \\}
+%     \note{This highlights the importance of selecting appropriate source models for transfer learning. \\}
+
+%     \end{frame}
+
+%     \begin{frame}{Learning Curves: Effect of Similarity}
+%     \begin{columns}
+%     \column{0.5\textwidth}
+%     \includegraphics[height=0.48\textheight]{../project3/figures/figure3a.png}
+%     \column{0.5\textwidth}
+%     \includegraphics[height=0.48\textheight]{../project3/figures/figure3b.png}
+%     \end{columns}
+
+%     \textit{The effect of similarity between source and target on the convergence speed}
+%     \begin{itemize}
+%         \item \textit{Left: from No Lapse; right: from Static Lapse}
+%     \end{itemize}
+
+%     \note{These figures further illustrate how source-target similarity affects transfer learning performance. \\}
+%     \note{The left graph shows transfer from no lapse models, which has slower convergence. \\}
+%     \note{The right graph shows transfer from static lapse models, with faster convergence. \\}
+%     \note{This reinforces our finding that greater similarity between source and target domains leads to more effective knowledge transfer. \\}
+%     \end{frame}
+
+%     \begin{frame}{Transfer Knowledge to other Contract Types}
+%     \textbf{From GMMB to GMWB Contract}
+
+%     \note{Now we examine transfer learning between different contract types, not just different features. \\}
+%     \note{This is a more challenging transfer learning scenario as the contract structures differ significantly. \\}
+%     \note{GMMB (Guaranteed Minimum Maturity Benefit) and GMWB (Guaranteed Minimum Withdrawal Benefit) have different risk profiles and valuation approaches. \\}
+%     \end{frame}
+
+%     \begin{frame}{Learning Curves: Transfer Knowledge to other Contract Types}
+%     \begin{figure}[ht]
+%         \centering
+%         \begin{subfigure}{0.48\textwidth}
+%             \includegraphics[width=\textwidth]{../project3/figures/figure4a.png}
+%             \caption{50000 samples}
+%         \end{subfigure}
+%         \begin{subfigure}{0.48\textwidth}
+%             \includegraphics[width=\textwidth]{../project3/figures/figure4b.png}
+%             \caption{2000 samples}
+%         \end{subfigure}
+%         \caption{Learning curves of GMWB contracts}
+%     \end{figure}
+
+%     \note{These graphs show learning curves for GMWB contracts with different training sample sizes. \\}
+%     \note{Left figure (50,000 samples) shows that with abundant data, all methods eventually converge well. \\}
+%     \note{Right figure (2,000 samples) demonstrates the advantage of transfer learning in data-limited scenarios. \\}
+%     \note{With limited data, transfer learning methods significantly outperform training from scratch. \\}
+%     \note{This is particularly relevant for new products or market conditions where historical data is scarce. \\}
+%     \end{frame}
+
+%     \begin{frame}{Learning Curves: Effect of Similarity}
+%     \begin{figure}[ht]
+%         \centering
+%         \begin{subfigure}{0.48\textwidth}
+%             \includegraphics[width=\textwidth]{../project3/figures/figure4c.png}
+%             \caption{Fine-tuning}
+%         \end{subfigure}
+%         \begin{subfigure}{0.48\textwidth}
+%             \includegraphics[width=\textwidth]{../project3/figures/figure4d.png}
+%             \caption{Layer Freezing}
+%         \end{subfigure}
+%         \caption{Comparison of different TL methods on GMWB contracts}
+%     \end{figure}
+
+%     \note{These figures compare fine-tuning vs. layer freezing approaches for GMWB contracts. \\}
+%     \note{Fine-tuning (left) allows all network parameters to be updated during training. \\}
+%     \note{Layer freezing (right) keeps early layers fixed and only updates later layers. \\}
+%     \note{For dissimilar contracts like GMMB to GMWB, fine-tuning generally performs better. \\}
+%     \note{This suggests that when transferring between different contract types, more flexibility in adaptation is beneficial. \\}
+%     \end{frame}
+
+%     \begin{frame}{Performance Comparison (GMMB → GMWB)}
+%     \begin{table}
+%     \begin{tabular}{lcc}
+%     \toprule
+%     \textbf{Model} & \textbf{Training MSE} & \textbf{True MSE} \\
+%     \midrule
+%     Without TL & 0.3588 & 0.4188 \\
+%     Fine Tuning & 0.1690 & 0.1780 \\
+%     Layer Freezing & 0.1828 & 0.2295 \\
+%     Extensive Training & 0.0853 & 0.0726 \\
+%     \bottomrule
+%     \end{tabular}
+%     \end{table}
+
+%     \begin{itemize}
+%         \item Fine-tuning outperforms layer freezing for dissimilar tasks
+%         \item Both TL methods better than training from scratch
+%         \item Extensive training still superior with abundant data
+%     \end{itemize}
+
+%     \note{This table quantifies the performance of different approaches when transferring from GMMB to GMWB. \\}
+%     \note{Fine-tuning (0.1780 MSE) outperforms layer freezing (0.2295 MSE) for these dissimilar contracts. \\}
+%     \note{Both transfer learning methods significantly outperform training from scratch (0.4188 MSE). \\}
+%     \note{With unlimited data and computational resources, extensive training (0.0726 MSE) remains the gold standard. \\}
+%     \note{In practice, the trade-off between computational cost and accuracy often favors transfer learning. \\}
+%     \end{frame}
+
+%     \begin{frame}{Multi-task Learning}
+%     \includegraphics[width=0.9\textwidth]{../project3/figures/mtl.png}
+
+%     \begin{itemize}
+%         \item LSTM layers shared across multiple tasks
+%         \item Task-specific fully connected layers
+%         \item Objective: Minimize sum of loss functions across all tasks
+%     \end{itemize}
+
+%     \note{Multi-task learning offers an alternative approach to transfer learning. \\}
+%     \note{Instead of sequential knowledge transfer, we train on multiple contract types simultaneously. \\}
+%     \note{The shared LSTM layers capture common features across different VA contracts. \\}
+%     \note{Task-specific layers then specialize for each contract type's unique characteristics. \\}
+%     \note{This approach can be more efficient than training separate models for each contract type. \\}
+%     \end{frame}
+
+%     \begin{frame}{Multi-task Learning Framework}
+%     \textbf{Input}: Set of $K$ tasks $\{\mathcal{T}_k\}_{k=1}^K$ with datasets $\mathcal{D}_k = \{(X_k^{(i)}, L_k^{(i)})\}_{i=1}^{M_k}$, shared parameters $\theta_0$, and task-specific parameters $\theta_k$ for each task $k$
+
+%     \textbf{Algorithm}:
+%     \begin{enumerate}
+%         \item Train the multi-head LSTM metamodel on all $K$ tasks simultaneously by minimizing the multi-task loss function:
+%         \begin{equation}
+%             \min_{\theta_0, \{\theta_k\}_{k=1}^K} \sum_{k=1}^K \frac{1}{M_k} \sum_{i=1}^{M_k} \left( f_i(X_k^{(i)}; \theta_0, \theta_k) - L_k^{(i)} \right)^2
+%         \end{equation}
+%         \item Update both the shared parameters $\theta_0$ and task-specific parameters $\{\theta_k\}_{k=1}^K$ simultaneously using backpropagation and gradient descent with learning rate $\alpha$
+%     \end{enumerate}
+
+%     \textbf{Output}: Trained multi-task LSTM metamodel $f(\cdot; \theta_0, \{\theta_k\}_{k=1}^K)$ for all $K$ tasks
+
+%     \note{This slide formalizes the multi-task learning framework mathematically. \\}
+%     \note{We have $K$ different tasks (contract types) with their respective datasets. \\}
+%     \note{The objective function minimizes the combined MSE across all tasks. \\}
+%     \note{Parameters are divided into shared parameters $\theta_0$ and task-specific parameters $\theta_k$. \\}
+%     \note{This approach encourages the model to learn generalizable features across different contract types. \\}
+%     \end{frame}
+
+%     \begin{frame}{Multi-task Learning: GMMB and GMWB}
+%     \begin{figure}[ht]
+%         \centering
+%         \begin{subfigure}{0.48\textwidth}
+%             \includegraphics[width=\textwidth]{../project3/figures/figure5a.png}
+%             \caption{Total MSE}
+%         \end{subfigure}
+%         \begin{subfigure}{0.48\textwidth}
+%             \includegraphics[width=\textwidth]{../project3/figures/figure5b.png}
+%             \caption{Individual MSE}
+%         \end{subfigure}
+%         \caption{Multi-task learning of GMMB and GMWB}
+%     \end{figure}
+
+%     \note{These figures show the performance of multi-task learning for GMMB and GMWB contracts. \\}
+%     \note{The left graph shows the total MSE across both tasks decreasing with training. \\}
+%     \note{The right graph breaks down performance by individual contract type. \\}
+%     \note{Multi-task learning allows knowledge sharing between contract types during training. \\}
+%     \note{This can lead to better generalization, especially for the more complex contract type. \\}
+%     \end{frame}
+
+%     \begin{frame}{Multi-task Learning: GMMB and GMWB}
+%     \begin{figure}[ht]
+%         \centering
+%         \begin{subfigure}{0.48\textwidth}
+%             \includegraphics[width=\textwidth]{../project3/figures/figure5c.png}
+%             \caption{GMMB}
+%         \end{subfigure}
+%         \begin{subfigure}{0.48\textwidth}
+%             \includegraphics[width=\textwidth]{../project3/figures/figure5d.png}
+%             \caption{GMWB}
+%         \end{subfigure}
+%         \caption{Training without multi-task learning}
+%     \end{figure}
+
+%     \note{For comparison, these figures show training curves when each contract is trained separately. \\}
+%     \note{The left graph shows GMMB training alone, and the right shows GMWB training alone. \\}
+%     \note{Compared to multi-task learning, individual training may converge more slowly or to higher error rates. \\}
+%     \note{This demonstrates how learning multiple related tasks simultaneously can improve performance. \\}
+%     \note{The shared representation forces the model to learn more robust features applicable to both contract types. \\}
+%     \end{frame}
+
+%     \begin{frame}{Challenges \& Limitations}
+%     \begin{itemize}
+%         \item Determining optimal layer freezing strategy
+%         \item Handling significantly different contract structures
+%         \item Quantifying uncertainty in transfer learning predictions
+%         \item Regulatory acceptance of black-box approaches
+%     \end{itemize}
+
+%     \note{Despite promising results, several challenges remain in applying these techniques. \\}
+%     \note{Finding the optimal layer freezing strategy often requires experimentation. \\}
+%     \note{Very different contract structures may limit effective knowledge transfer. \\}
+%     \note{Uncertainty quantification is crucial for risk management but challenging with complex models. \\}
+%     \note{Regulatory concerns about model interpretability may limit practical implementation. \\}
+%     \note{These challenges represent important areas for future research. \\}
+%     \end{frame}
+
+%     \begin{frame}{Conclusions}
+%     \begin{itemize}
+%         \item Transfer learning significantly improves metamodeling for VA contracts:
+%         \begin{itemize}
+%             \item Faster training convergence
+%             \item Better prediction accuracy
+%             \item Reduced computational requirements
+%         \end{itemize}
+%         \item Enables more frequent risk assessments and faster decision-making
+%     \end{itemize}
+
+%     \note{Our research demonstrates that transfer learning significantly enhances VA contract metamodeling. \\}
+%     \note{The benefits include faster convergence, better accuracy with limited data, and reduced computational needs. \\}
+%     \note{These improvements enable more frequent and timely risk assessments. \\}
+%     \note{This is particularly valuable in volatile markets where rapid decision-making is essential. \\}
+%     \note{The approach bridges the gap between traditional actuarial methods and modern machine learning techniques. \\}
+%     \end{frame}
+
+% \begin{frame}{Future Directions}
+%     \begin{itemize}
+%         \item Incorporating domain knowledge into transfer process
+%         \item Extension to other insurance and financial products
+%         \item Multi-task learning with more than two tasks
+%     \end{itemize}
+
+%     \note{Several promising directions exist for extending this research. \\}
+%     \note{Incorporating actuarial domain knowledge could further improve transfer learning effectiveness. \\}
+%     \note{The approach could be extended to other insurance products and financial derivatives. \\}
+%     \note{Multi-task learning could be expanded to handle more than two contract types simultaneously. \\}
+%     \note{Integration with existing risk management systems would facilitate practical adoption. \\}
+%     \note{Ultimately, these techniques could transform how financial institutions manage complex product portfolios. \\}
+% \end{frame}
 

### 2025-03-18 project1/nsSurvey.tex
12

@@
 \cite{broadie2015risk} propose a regression-based nested simulation procedure, which uses a trained regression metamodel to estimate the scenario-wise portfolio loss for an outer scenario by pooling the inner replications from all outer scenarios.
-For certain risk measures,~\cite{broadie2015risk} show that it’s optimal to allocate the entire simulation budget to outer-level simulations, keeping only 1 inner replication in each outer scenario.
+For certain risk measures,~\cite{broadie2015risk} show that it's optimal to allocate the entire simulation budget to outer-level simulations, keeping only 1 inner replication in each outer scenario.
 Similarly,~\cite{hong2017kernel},~\cite{feng2020optimal}, and~\cite{zhang2022sample} use a kernel smoothing model, a likelihood ratio model, and a kernel ridge regression (KRR) model as metamodels to pool the inner replications from all outer scenarios, respectively.

### 2025-03-19 pre_private/pre.tex
1

@@
 
-    Three datasets are considered:
-    \begin{itemize}
-        \item   \textcolor{color10_2}{Training}: 90,000 scenarios (100 inner replications).
-        \item   \textcolor{color10_3}{Test}: 10,000 scenarios (100 inner replications).
-        \item   \textcolor{color10_5}{True}: 100,000 scenarios (100,000 inner replications).
+    In our experiment:
+    \begin{itemize}
+        \item $95\%$-CVaR of loss for a GMWB with a 240-month maturity
+        \item 240-dimensional feature vector and 1-dimensional loss
     \end{itemize}
@@
 
-    In our experiment:
-    \begin{itemize}
-        \item $95\%$-CVaR of loss for a GMWB with a 240-month maturity
-        \item 240-dimensional feature vector and 1-dimensional loss
+    Three datasets are considered:
+    \begin{itemize}
+        \item   \textcolor{color10_2}{Training}: 90,000 scenarios (100 inner replications).
+        \item   \textcolor{color10_3}{Test}: 10,000 scenarios (100 inner replications).
+        \item   \textcolor{color10_5}{True}: 100,000 scenarios (100,000 inner replications).
     \end{itemize}
@@
 
-% \begin{frame}{Transfer Learning for Rapid Adaptation of DNN Metamodels}
-
-%     \textbf{Challenge:} Adapting deep neural network metamodels to changing conditions.
-%     \begin{itemize}
-%         \item   Retraining from scratch is computationally expensive.
-%         \item   Efficient incorporation of new VA contract data.
-%         \item   Balancing model accuracy and computational costs.
-%     \end{itemize}
-
-%     \vspace{10pt}
-
-%     \textbf{Solution:} Transfer learning (TL) to develop adaptable, efficient metamodels for VA dynamic hedging.
-
-%     \begin{itemize}
-%         \item   Pre-train deep neural network on contracts with abundant simulation data.
-%         \item   Fine-tune on smaller dataset of new contracts/market conditions.
-%         \item   Leverages shared features between VA contracts.
-%         \item   Computational savings:
-%             \begin{itemize}
-%                 \item   Reduced training time.
-%                 \item   Fewer data points needed for good performance.
-%             \end{itemize}
-%     \end{itemize}
-
-%     \note{In this project, we propose a transfer learning framework for rapid adaptation of deep neural network metamodels in VA dynamic hedging.\\ }
-%     \note{The problem is the same as the previous project. We want to use deep neural network metamodels to approximate the complex simulation model that involves dynamic hedging.\\}
-%     \note{The difference is that we want to use transfer learning to speed up the training process.\\}
-%     \note{This can be beneficial for the practical applications.\\}
-%     \note{Firstly, new VA contracts are continuously issued.\\}
-%     \note{Secondly, market conditions are changing.\\}
-%     \note{Thirdly, the computational budget is limited.\\}
-%     \note{Transfer learning can help us to adapt to the new market conditions quickly and efficiently.\\}
-%     \note{We can pre-train the deep neural network metamodel on a large dataset of VA contracts with abundant simulation data.\\}
-%     \note{Then, we can fine-tune the metamodel on a smaller dataset of new VA contracts with limited data.\\}
-%     \note{The data is often limited for new VA contracts as simulation is expensive to run.\\}
-%     \note{The shared features between VA contracts can be leveraged to speed up the training process.\\}
-%     \note{We can also transfer the knowledge to other contract types.\\}
-%     \note{When a new VA contract is issued, we can use transfer learning to adapt the metamodel to the new contract quickly.\\}
-
-% \end{frame}
+\begin{frame}{Transfer Learning for Rapid Adaptation of DNN Metamodels}
+
+    \textbf{Use Case:} Adapting deep neural network metamodels to changing conditions.
+    \begin{itemize}
+        \item   Retraining from scratch is computationally expensive.
+        \item   Efficient incorporation of new VA contract data.
+        \item   Balancing model accuracy and computational costs.
+    \end{itemize}
+
+    \vspace{10pt}
+
+    \textbf{Solution:} Transfer learning (TL) to develop adaptable, efficient metamodels for VA dynamic hedging.
+
+    \begin{itemize}
+        \item   Pre-train deep neural network on contracts with abundant simulation data.
+        \item   Fine-tune on smaller dataset of new contracts/market conditions.
+        \item   Leverages shared features between VA contracts.
+        \item   Computational savings:
+            \begin{itemize}
+                \item   Reduced training time.
+                \item   Fewer data points needed for good performance.
+            \end{itemize}
+    \end{itemize}
+
+    \note{In this project, we propose a transfer learning framework for rapid adaptation of deep neural network metamodels in VA dynamic hedging.\\ }
+    \note{The problem is the same as the previous project. We want to use deep neural network metamodels to approximate the complex simulation model that involves dynamic hedging.\\}
+    \note{The difference is that we want to use transfer learning to speed up the training process.\\}
+    \note{This can be beneficial for the practical applications.\\}
+    \note{Firstly, new VA contracts are continuously issued.\\}
+    \note{Secondly, market conditions are changing.\\}
+    \note{Thirdly, the computational budget is limited.\\}
+    \note{Transfer learning can help us to adapt to the new market conditions quickly and efficiently.\\}
+    \note{We can pre-train the deep neural network metamodel on a large dataset of VA contracts with abundant simulation data.\\}
+    \note{Then, we can fine-tune the metamodel on a smaller dataset of new VA contracts with limited data.\\}
+    \note{The data is often limited for new VA contracts as simulation is expensive to run.\\}
+    \note{The shared features between VA contracts can be leveraged to speed up the training process.\\}
+    \note{We can also transfer the knowledge to other contract types.\\}
+    \note{When a new VA contract is issued, we can use transfer learning to adapt the metamodel to the new contract quickly.\\}
+
+\end{frame}
 

### 2025-03-22 pre_private/pre.tex
w

@@
 
-    \textbf{Use Case:} Adapting deep neural network metamodels to changing conditions.
-    \begin{itemize}
-        \item   Retraining from scratch is computationally expensive.
-        \item   Efficient incorporation of new VA contract data.
-        \item   Balancing model accuracy and computational costs.
+    \textbf{Problem:} Updating models for new conditions is expensive.
+    \begin{itemize}
+        \item   Full retraining takes too much time.
+        \item   New VA contracts need quick model updates.
+        \item   Need balance between speed and accuracy.
     \end{itemize}
@@
 
-    \textbf{Solution:} Transfer learning (TL) to develop adaptable, efficient metamodels for VA dynamic hedging.
-
-    \begin{itemize}
-        \item   Pre-train deep neural network on contracts with abundant simulation data.
-        \item   Fine-tune on smaller dataset of new contracts/market conditions.
-        \item   Leverages shared features between VA contracts.
-        \item   Computational savings:
-            \begin{itemize}
-                \item   Reduced training time.
-                \item   Fewer data points needed for good performance.
+    \textbf{Solution:} Transfer learning for faster model adaptation.
+
+    \begin{itemize}
+        \item   Train first on existing contract data.
+        \item   Update with small amount of new contract data.
+        \item   Reuse knowledge between similar contracts.
+        \item   Benefits:
+            \begin{itemize}
+                \item   Faster training.
+                \item   Less data needed.
             \end{itemize}
@@
 
-% \begin{frame}{Transfer Learning Framework}
-
-%     \textbf{Key Components:}
-%     \begin{itemize}
-%         \item   \textbf{Domain} $\mathcal{D}$: feature space $\mathcal{X}$ + probability distribution $F$
-%         \item   \textbf{Task} $\mathcal{T}$: label space $\mathcal{Y}$ + predictive function $f: \mathcal{X} \rightarrow \mathcal{Y}$
-%     \end{itemize}
-
-%     \vspace{10pt}
-%     \textbf{Source vs. Target:}
-%     \begin{itemize}
-%         \item   \textbf{Source:} $\mathcal{D}_{\text{So}} = \{\mathcal{X}_{\text{So}}, F_{\text{So}}(X)\}$
-%         \item   \textbf{Target:} $\mathcal{D}_{\text{Ta}} = \{\mathcal{X}_{\text{Ta}}, F_{\text{Ta}}(X)\}$
-%     \end{itemize}
-
-%     \vspace{10pt}
-%     \textbf{Our Goal:}
-%     \begin{itemize}
-%         \item   \textbf{Input features} $X$: risk factors from outer simulation
-%         \item   \textbf{Output labels} $L$: contract losses
-%         \item   \textbf{Source and target}: from VAs with abundant simulation data to new VAs with limited data
-%         \item   \textbf{Goal}: improve $f_{\text{Ta}}(\cdot)$ using knowledge from $\mathcal{D}_{\text{So}}$ and $f_{\text{So}}(\cdot)$
-%     \end{itemize}
-
-%     \note{Transfer learning provides a formal framework for adapting models from one domain to another.\\}
-%     \note{The domain consists of a feature space and a probability distribution over that space.\\}
-%     \note{In our context, the feature space includes risk factors from the outer simulation.\\}
-%     \note{It is equipped with a probability distribution that describes the joint distribution of the risk factors.\\}
-%     \note{We don't know the exact joint distribution of the risk factors, but we can simulate outer scenarios from it using monte carlo simulation.\\}
-%     \note{The task consists of a label space and a predictive function mapping features to labels.\\}
-%     \note{For VA contracts, our labels are the contract losses under different scenarios.\\}
-%     \note{The source domain typically has abundant data - this could be existing VA contracts with extensive simulation data.\\}
-%     \note{The target domain has limited data - new VA contracts or existing contracts under new market conditions.\\}
-%     \note{Our goal is to leverage knowledge from the source domain to improve prediction in the target domain.\\}
-%     \note{This is particularly valuable when simulation data is expensive to generate for new contracts.\\}
-%     \note{The transfer learning approach allows us to maintain accuracy while significantly reducing computational requirements.\\}
-
-% \end{frame}
-
-% \begin{frame}{Transfer Learning Techniques}
-
-%     \textbf{Common Techniques:}
-%     \begin{itemize}
-%         \item   \textbf{Fine-tuning:} a model pre-trained on a source task is used as a starting point for a target task.
-%         \item   \textbf{Layer freezing:} only part of the model is fine-tuned.
-%         \item   \textbf{Multi-task learning:} perform training on multiple tasks simultaneously.
-%     \end{itemize}
-
-%     \vspace{10pt}
-
-%     \textbf{Key considerations:}
-%     \begin{itemize}
-%         \item   Similarity between source and target tasks
-%         \item   Appropriate learning rate
-%     \end{itemize}
-
-%     \note{Fine-tuning involves using a pre-trained model as a starting point for a new task.\\}
-%     \note{This approach is effective when the source and target tasks are similar.\\}
-%     \note{For VA contracts, we can fine-tune models between different contract types or market conditions.\\}
-%     \note{Layer freezing is a technique where we keep some layers of the pre-trained model fixed.\\}
-%     \note{Typically, early layers capture general features while later layers are more task-specific.\\}
-%     \note{By freezing early layers, we preserve general knowledge while adapting task-specific layers.\\}
-%     \note{Multi-task learning trains a single model to perform multiple related tasks simultaneously.\\}
-%     \note{This approach can improve generalization by leveraging the domain-specific information across tasks.\\}
-%     \note{For VA contracts, we can train a model to handle multiple contract types or features.\\}
-%     \note{The learning rate is a critical hyperparameter in transfer learning.\\}
-%     \note{Typically, we use a smaller learning rate for fine-tuning compared to training from scratch.\\}
-%     \note{The similarity between source and target tasks greatly impacts transfer learning effectiveness.\\}
-%     \note{More similar tasks generally allow for more effective knowledge transfer.\\}
-
-% \end{frame}
+\begin{frame}{Transfer Learning Framework}
+
+    \textbf{Key Components:}
+    \begin{itemize}
+        \item   \textbf{Domain} $\mathcal{D}$: feature space $\mathcal{X}$ + probability distribution $F$
+        \item   \textbf{Task} $\mathcal{T}$: label space $\mathcal{Y}$ + predictive function $f: \mathcal{X} \rightarrow \mathcal{Y}$
+    \end{itemize}
+
+    \vspace{10pt}
+    \textbf{Source vs. Target:}
+    \begin{itemize}
+        \item   \textbf{Source:} $\mathcal{D}_{\text{So}} = \{\mathcal{X}_{\text{So}}, F_{\text{So}}(X)\}$
+        \item   \textbf{Target:} $\mathcal{D}_{\text{Ta}} = \{\mathcal{X}_{\text{Ta}}, F_{\text{Ta}}(X)\}$
+    \end{itemize}
+
+    \vspace{10pt}
+    \textbf{Our Goal:}
+    \begin{itemize}
+        \item   \textbf{Input features} $X$: risk factors from outer simulation
+        \item   \textbf{Output labels} $L$: contract losses
+        \item   \textbf{Source and target}: from VAs with abundant simulation data to new VAs with limited data
+        \item   \textbf{Goal}: improve $f_{\text{Ta}}(\cdot)$ using knowledge from $\mathcal{D}_{\text{So}}$ and $f_{\text{So}}(\cdot)$
+    \end{itemize}
+
+    \note{Transfer learning provides a formal framework for adapting models from one domain to another.\\}
+    \note{The domain consists of a feature space and a probability distribution over that space.\\}
+    \note{In our context, the feature space includes risk factors from the outer simulation.\\}
+    \note{It is equipped with a probability distribution that describes the joint distribution of the risk factors.\\}
+    \note{We don't know the exact joint distribution of the risk factors, but we can simulate outer scenarios from it using monte carlo simulation.\\}
+    \note{The task consists of a label space and a predictive function mapping features to labels.\\}
+    \note{For VA contracts, our labels are the contract losses under different scenarios.\\}
+    \note{The source domain typically has abundant data - this could be existing VA contracts with extensive simulation data.\\}
+    \note{The target domain has limited data - new VA contracts or existing contracts under new market conditions.\\}
+    \note{Our goal is to leverage knowledge from the source domain to improve prediction in the target domain.\\}
+    \note{This is particularly valuable when simulation data is expensive to generate for new contracts.\\}
+    \note{The transfer learning approach allows us to maintain accuracy while significantly reducing computational requirements.\\}
+
+\end{frame}
+
+\begin{frame}{Transfer Learning Techniques}
+
+    \textbf{Common Techniques:}
+    \begin{itemize}
+        \item   \textbf{Fine-tuning:} a model pre-trained on a source task is used as a starting point for a target task.
+        \item   \textbf{Layer freezing:} only part of the model is fine-tuned.
+        \item   \textbf{Multi-task learning:} perform training on multiple tasks simultaneously.
+    \end{itemize}
+
+    \vspace{10pt}
+
+    \textbf{Key considerations:}
+    \begin{itemize}
+        \item   Similarity between source and target tasks
+        \item   Appropriate learning rate
+    \end{itemize}
+
+    \note{Fine-tuning involves using a pre-trained model as a starting point for a new task.\\}
+    \note{This approach is effective when the source and target tasks are similar.\\}
+    \note{For VA contracts, we can fine-tune models between different contract types or market conditions.\\}
+    \note{Layer freezing is a technique where we keep some layers of the pre-trained model fixed.\\}
+    \note{Typically, early layers capture general features while later layers are more task-specific.\\}
+    \note{By freezing early layers, we preserve general knowledge while adapting task-specific layers.\\}
+    \note{Multi-task learning trains a single model to perform multiple related tasks simultaneously.\\}
+    \note{This approach can improve generalization by leveraging the domain-specific information across tasks.\\}
+    \note{For VA contracts, we can train a model to handle multiple contract types or features.\\}
+    \note{The learning rate is a critical hyperparameter in transfer learning.\\}
+    \note{Typically, we use a smaller learning rate for fine-tuning compared to training from scratch.\\}
+    \note{The similarity between source and target tasks greatly impacts transfer learning effectiveness.\\}
+    \note{More similar tasks generally allow for more effective knowledge transfer.\\}
+
+\end{frame}
 
@@
 
-% \begin{frame}{Multi-task Learning}
-%     \includegraphics[width=0.9\textwidth]{../project3/figures/mtl.png}
-
-%     \begin{itemize}
-%         \item LSTM layers shared across multiple tasks
-%         \item Task-specific fully connected layers
-%         \item Objective: Minimize sum of loss functions across all tasks
-%     \end{itemize}
-
-%     \note{Multi-task learning offers an alternative approach to transfer learning. \\}
-%     \note{Instead of sequential knowledge transfer, we train on multiple contract types simultaneously. \\}
-%     \note{The shared LSTM layers capture common features across different VA contracts. \\}
-%     \note{Task-specific layers then specialize for each contract type's unique characteristics. \\}
-%     \note{We will examine whether this approach can be more efficient than training separate models for each contract type. \\}
-
-% \end{frame}
-
-% \begin{frame}{Experiment Setup}
-
-%     \begin{table}[ht!] 
-%         \centering
-%         \begin{tabular}{lcccc} 
-%         \toprule
-%         \textbf{Contract} & \textbf{Asset Model} & \textbf{Lapse} & \textbf{$M_{\text{So}}$}  & \textbf{$M_{\text{Ta}}$}\\
-%         \midrule
-%         GMMB & GBM & No lapse & 50000 & N/A \\
-%         GMMB & RS-GBM & No lapse & 50000 & 2000 \\
-%         GMMB & RS-GBM & Static lapse & 50000 & 2000 \\
-%         GMMB & RS-GBM & Dynamic lapse & 50000 & 2000 \\
-%         GMWB & RS-GBM & Dynamic lapse & N/A & 2000 \\
-%         \bottomrule
-%         \end{tabular}
-%         \caption{VA Contracts for Transfer Learning Experiments}
-%     \end{table}
-
-%     We aim to examine the performance of TL techniques
-%     \begin{itemize}
-%         \item   learning the lapse features,
-%         \item   learning the dynamic lapse, and 
-%         \item   transferring to other contract types.
-%     \end{itemize}
-
-%     \note{We use a variety of VA contracts with different features to test transfer learning. \\}
-%     \note{The source model ($M_{\text{So}}$) is trained with 50,000 samples for comprehensive learning. \\}
-%     \note{The target model ($M_{\text{Ta}}$) uses only 2,000 samples to simulate limited data scenarios. \\}
-%     \note{We progress from simpler to more complex models (No lapse → Static → Dynamic). \\}
-%     \note{We examine both within-contract transfer (GMMB to GMMB with different features) and cross-contract transfer (GMMB to GMWB). \\}
-%     \note{The regime-switching GBM (RS-GBM) model captures more realistic market dynamics. \\}
-%     \note{All training data is generated using 100 inner replications for consistency. \\}
-%     \note{We compare fine-tuning and layer freezing as two primary transfer learning approaches. \\}
-%     \note{The experiments are designed to evaluate how similarity between source and target affects transfer efficiency. \\}
-%     \note{This is another attempt to use simulation models as data generating processes to examine deep neural networks. \\}
-%     \note{By examining the transfer learning performance, we can gain insights into which parts of the neural network are transferable, or more generally, which layers of the neural network learn which features of the VA contracts.
+\begin{frame}{Multi-task Learning}
+    \includegraphics[width=0.9\textwidth]{../project3/figures/mtl.png}
+
+    \begin{itemize}
+        \item LSTM layers shared across multiple tasks
+        \item Task-specific fully connected layers
+        \item Objective: Minimize sum of loss functions across all tasks
+    \end{itemize}
+
+    \note{Multi-task learning offers an alternative approach to transfer learning. \\}
+    \note{Instead of sequential knowledge transfer, we train on multiple contract types simultaneously. \\}
+    \note{The shared LSTM layers capture common features across different VA contracts. \\}
+    \note{Task-specific layers then specialize for each contract type's unique characteristics. \\}
+    \note{We will examine whether this approach can be more efficient than training separate models for each contract type. \\}
+
+\end{frame}
+
+\begin{frame}{Experiment Setup}
+
+    \begin{table}[ht!] 
+        \centering
+        \begin{tabular}{lcccc} 
+        \toprule
+        \textbf{Contract} & \textbf{Asset Model} & \textbf{Lapse} & \textbf{$M_{\text{So}}$}  & \textbf{$M_{\text{Ta}}$}\\
+        \midrule
+        GMMB & GBM & No lapse & 50000 & N/A \\
+        GMMB & RS-GBM & No lapse & 50000 & 2000 \\
+        GMMB & RS-GBM & Static lapse & 50000 & 2000 \\
+        GMMB & RS-GBM & Dynamic lapse & 50000 & 2000 \\
+        GMWB & RS-GBM & Dynamic lapse & N/A & 2000 \\
+        \bottomrule
+        \end{tabular}
+        \caption{VA Contracts for Transfer Learning Experiments}
+    \end{table}
+
+    We aim to examine the performance of TL techniques
+    \begin{itemize}
+        \item   learning the lapse features,
+        \item   learning the dynamic lapse, and 
+        \item   transferring to other contract types.
+    \end{itemize}
+
+    \note{We use a variety of VA contracts with different features to test transfer learning. \\}
+    \note{The source model ($M_{\text{So}}$) is trained with 50,000 samples for comprehensive learning. \\}
+    \note{The target model ($M_{\text{Ta}}$) uses only 2,000 samples to simulate limited data scenarios. \\}
+    \note{We progress from simpler to more complex models (No lapse → Static → Dynamic). \\}
+    \note{We examine both within-contract transfer (GMMB to GMMB with different features) and cross-contract transfer (GMMB to GMWB). \\}
+    \note{The regime-switching GBM (RS-GBM) model captures more realistic market dynamics. \\}
+    \note{All training data is generated using 100 inner replications for consistency. \\}
+    \note{We compare fine-tuning and layer freezing as two primary transfer learning approaches. \\}
+    \note{The experiments are designed to evaluate how similarity between source and target affects transfer efficiency. \\}
+    \note{This is another attempt to use simulation models as data generating processes to examine deep neural networks. \\}
+    \note{By examining the transfer learning performance, we can gain insights into which parts of the neural network are transferable, or more generally, which layers of the neural network learn which features of the VA contracts.
 \\}
 
-% \end{frame}
+\end{frame}
 
@@
 
-%     \begin{frame}{Results: Accuracy Comparison}
-%         \begin{table}
-%             \begin{tabular}{lr}
-%             \toprule
-%             \textbf{Method and Setting} & \textbf{MSE} \\
-%             \midrule
-%             Extensive Training (Dynamic) & \textbf{0.0587} \\
-%             Fine-tuning (Static) & 0.0794 \\
-%             Layer Freezing (Static) & 0.0763 \\
-%             Layer Freezing (No Lapse) & 0.3361 \\
-%             Fine-tuning (No Lapse) & 0.4894 \\
-%             Without TL (Dynamic) & 0.2950 \\
-%             \bottomrule
-%             \end{tabular}
-%             \caption{Comparison of different TL methods on GMMB contracts (best MSE values)}
-%         \end{table}
-
-%     \note{This table summarizes the MSE values for different training methods. \\}
-%     \note{Extensive training with full data achieves the best performance (0.0587 MSE). \\}
-%     \note{Without transfer learning, training from scratch on dynamic lapse data yields mediocre results (0.2950 MSE). \\}
-%     \note{Transfer learning from static lapse models (both fine-tuning and layer freezing) performs well. \\}
-%     \note{Transfer from no lapse models performs poorly, demonstrating that negative transfer can occur. \\}
-%     \note{Negative transfer happens when source and target tasks are substantially different. \\}
-%     \note{In such cases, knowledge from the source model can actually hinder learning on the target task. \\}
-%     \note{This highlights the importance of selecting appropriate source models for transfer learning. \\}
-
-%     \end{frame}
-
-%     \begin{frame}{Learning Curves: Effect of Similarity}
-%     \begin{columns}
-%     \column{0.5\textwidth}
-%     \includegraphics[height=0.48\textheight]{../project3/figures/figure3a.png}
-%     \column{0.5\textwidth}
-%     \includegraphics[height=0.48\textheight]{../project3/figures/figure3b.png}
-%     \end{columns}
-
-%     \textit{The effect of similarity between source and target on the convergence speed}
-%     \begin{itemize}
-%         \item \textit{Left: from No Lapse; right: from Static Lapse}
-%     \end{itemize}
-
-%     \note{These figures further illustrate how source-target similarity affects transfer learning performance. \\}
-%     \note{The left graph shows transfer from no lapse models, which has slower convergence. \\}
-%     \note{The right graph shows transfer from static lapse models, with faster convergence. \\}
-%     \note{This reinforces our finding that greater similarity between source and target domains leads to more effective knowledge transfer. \\}
-%     \end{frame}
-
-%     \begin{frame}{Transfer Knowledge to other Contract Types}
-%     \textbf{From GMMB to GMWB Contract}
-
-%     \note{Now we examine transfer learning between different contract types, not just different features. \\}
-%     \note{This is a more challenging transfer learning scenario as the contract structures differ significantly. \\}
-%     \note{GMMB (Guaranteed Minimum Maturity Benefit) and GMWB (Guaranteed Minimum Withdrawal Benefit) have different risk profiles and valuation approaches. \\}
-%     \end{frame}
-
-%     \begin{frame}{Learning Curves: Transfer Knowledge to other Contract Types}
-%     \begin{figure}[ht]
-%         \centering
-%         \begin{subfigure}{0.48\textwidth}
-%             \includegraphics[width=\textwidth]{../project3/figures/figure4a.png}
-%             \caption{50000 samples}
-%         \end{subfigure}
-%         \begin{subfigure}{0.48\textwidth}
-%             \includegraphics[width=\textwidth]{../project3/figures/figure4b.png}
-%             \caption{2000 samples}
-%         \end{subfigure}
-%         \caption{Learning curves of GMWB contracts}
-%     \end{figure}
-
-%     \note{These graphs show learning curves for GMWB contracts with different training sample sizes. \\}
-%     \note{Left figure (50,000 samples) shows that with abundant data, all methods eventually converge well. \\}
-%     \note{Right figure (2,000 samples) demonstrates the advantage of transfer learning in data-limited scenarios. \\}
-%     \note{With limited data, transfer learning methods significantly outperform training from scratch. \\}
-%     \note{This is particularly relevant for new products or market conditions where historical data is scarce. \\}
-%     \end{frame}
-
-%     \begin{frame}{Learning Curves: Effect of Similarity}
-%     \begin{figure}[ht]
-%         \centering
-%         \begin{subfigure}{0.48\textwidth}
-%             \includegraphics[width=\textwidth]{../project3/figures/figure4c.png}
-%             \caption{Fine-tuning}
-%         \end{subfigure}
-%         \begin{subfigure}{0.48\textwidth}
-%             \includegraphics[width=\textwidth]{../project3/figures/figure4d.png}
-%             \caption{Layer Freezing}
-%         \end{subfigure}
-%         \caption{Comparison of different TL methods on GMWB contracts}
-%     \end{figure}
-
-%     \note{These figures compare fine-tuning vs. layer freezing approaches for GMWB contracts. \\}
-%     \note{Fine-tuning (left) allows all network parameters to be updated during training. \\}
-%     \note{Layer freezing (right) keeps early layers fixed and only updates later layers. \\}
-%     \note{For dissimilar contracts like GMMB to GMWB, fine-tuning generally performs better. \\}
-%     \note{This suggests that when transferring between different contract types, more flexibility in adaptation is beneficial. \\}
-%     \end{frame}
+\begin{frame}{Results: Accuracy Comparison}
+        \begin{table}
+            \begin{tabular}{lr}
+            \toprule
+            \textbf{Method and Setting} & \textbf{MSE} \\
+            \midrule
+            Extensive Training (Dynamic) & \textbf{0.0587} \\
+            Fine-tuning (Static) & 0.0794 \\
+            Layer Freezing (Static) & 0.0763 \\
+            Layer Freezing (No Lapse) & 0.3361 \\
+            Fine-tuning (No Lapse) & 0.4894 \\
+            Without TL (Dynamic) & 0.2950 \\
+            \bottomrule
+            \end{tabular}
+            \caption{Comparison of different TL methods on GMMB contracts (best MSE values)}
+        \end{table}
+
+    \note{This table summarizes the MSE values for different training methods. \\}
+    \note{Extensive training with full data achieves the best performance (0.0587 MSE). \\}
+    \note{Without transfer learning, training from scratch on dynamic lapse data yields mediocre results (0.2950 MSE). \\}
+    \note{Transfer learning from static lapse models (both fine-tuning and layer freezing) performs well. \\}
+    \note{Transfer from no lapse models performs poorly, demonstrating that negative transfer can occur. \\}
+    \note{Negative transfer happens when source and target tasks are substantially different. \\}
+    \note{In such cases, knowledge from the source model can actually hinder learning on the target task. \\}
+    \note{This highlights the importance of selecting appropriate source models for transfer learning. \\}
+
+\end{frame}
+
+\begin{frame}{Learning Curves: Effect of Similarity}
+    \begin{columns}
+    \column{0.5\textwidth}
+    \includegraphics[height=0.48\textheight]{../project3/figures/figure3a.png}
+    \column{0.5\textwidth}
+    \includegraphics[height=0.48\textheight]{../project3/figures/figure3b.png}
+    \end{columns}
+
+    \textit{The effect of similarity between source and target on the convergence speed}
+    \begin{itemize}
+        \item \textit{Left: from No Lapse; right: from Static Lapse}
+    \end{itemize}
+
+    \note{These figures further illustrate how source-target similarity affects transfer learning performance. \\}
+    \note{The left graph shows transfer from no lapse models, which has slower convergence. \\}
+    \note{The right graph shows transfer from static lapse models, with faster convergence. \\}
+    \note{This reinforces our finding that greater similarity between source and target domains leads to more effective knowledge transfer. \\}
+\end{frame}
+
+    \begin{frame}{Learning Curves: Transfer Knowledge to other Contract Types}
+    \begin{figure}[ht]
+        \centering
+        \begin{subfigure}{0.48\textwidth}
+            \includegraphics[width=\textwidth]{../project3/figures/figure4a.png}
+            \caption{50000 samples}
+        \end{subfigure}
+        \begin{subfigure}{0.48\textwidth}
+            \includegraphics[width=\textwidth]{../project3/figures/figure4b.png}
+            \caption{2000 samples}
+        \end{subfigure}
+        \caption{Learning curves of GMWB contracts}
+    \end{figure}
+
+    \note{These graphs show learning curves for GMWB contracts with different training sample sizes. \\}
+    \note{Left figure (50,000 samples) shows that with abundant data, all methods eventually converge well. \\}
+    \note{Right figure (2,000 samples) demonstrates the advantage of transfer learning in data-limited scenarios. \\}
+    \note{With limited data, transfer learning methods significantly outperform training from scratch. \\}
+    \note{This is particularly relevant for new products or market conditions where historical data is scarce. \\}
+    \end{frame}
+
+    \begin{frame}{Learning Curves: Effect of Similarity}
+    \begin{figure}[ht]
+        \centering
+        \begin{subfigure}{0.48\textwidth}
+            \includegraphics[width=\textwidth]{../project3/figures/figure4c.png}
+            \caption{Fine-tuning}
+        \end{subfigure}
+        \begin{subfigure}{0.48\textwidth}
+            \includegraphics[width=\textwidth]{../project3/figures/figure4d.png}
+            \caption{Layer Freezing}
+        \end{subfigure}
+        \caption{Comparison of different TL methods on GMWB contracts}
+    \end{figure}
+
+    \note{These figures compare fine-tuning vs. layer freezing approaches for GMWB contracts. \\}
+    \note{Fine-tuning (left) allows all network parameters to be updated during training. \\}
+    \note{Layer freezing (right) keeps early layers fixed and only updates later layers. \\}
+    \note{For dissimilar contracts like GMMB to GMWB, fine-tuning generally performs better. \\}
+    \note{This suggests that when transferring between different contract types, more flexibility in adaptation is beneficial. \\}
+    \end{frame}
 
@@
 
-%     \begin{frame}{Conclusions}
-%     \begin{itemize}
-%         \item Transfer learning significantly improves metamodeling for VA contracts:
-%         \begin{itemize}
-%             \item Faster training convergence
-%             \item Better prediction accuracy
-%             \item Reduced computational requirements
-%         \end{itemize}
-%         \item Enables more frequent risk assessments and faster decision-making
-%     \end{itemize}
-
-%     \note{Our research demonstrates that transfer learning significantly enhances VA contract metamodeling. \\}
-%     \note{The benefits include faster convergence, better accuracy with limited data, and reduced computational needs. \\}
-%     \note{These improvements enable more frequent and timely risk assessments. \\}
-%     \note{This is particularly valuable in volatile markets where rapid decision-making is essential. \\}
-%     \note{The approach bridges the gap between traditional actuarial methods and modern machine learning techniques. \\}
-%     \end{frame}
-
-% \begin{frame}{Future Directions}
-%     \begin{itemize}
-%         \item Incorporating domain knowledge into transfer process
-%         \item Extension to other insurance and financial products
-%         \item Multi-task learning with more than two tasks
-%     \end{itemize}
-
-%     \note{Several promising directions exist for extending this research. \\}
-%     \note{Incorporating actuarial domain knowledge could further improve transfer learning effectiveness. \\}
-%     \note{The approach could be extended to other insurance products and financial derivatives. \\}
-%     \note{Multi-task learning could be expanded to handle more than two contract types simultaneously. \\}
-%     \note{Integration with existing risk management systems would facilitate practical adoption. \\}
-%     \note{Ultimately, these techniques could transform how financial institutions manage complex product portfolios. \\}
-% \end{frame}
+    \begin{frame}{Conclusions}
+    \begin{itemize}
+        \item Transfer learning significantly improves metamodeling for VA contracts:
+        \begin{itemize}
+            \item Faster training convergence
+            \item Better prediction accuracy
+            \item Reduced computational requirements
+        \end{itemize}
+        \item Enables more frequent risk assessments and faster decision-making
+    \end{itemize}
+
+    \note{Our research demonstrates that transfer learning significantly enhances VA contract metamodeling. \\}
+    \note{The benefits include faster convergence, better accuracy with limited data, and reduced computational needs. \\}
+    \note{These improvements enable more frequent and timely risk assessments. \\}
+    \note{This is particularly valuable in volatile markets where rapid decision-making is essential. \\}
+    \note{The approach bridges the gap between traditional actuarial methods and modern machine learning techniques. \\}
+
+    \textbf{Future Work:}
+    \begin{itemize}
+        \item Incorporating domain knowledge into transfer process
+        \item Extension to other insurance and financial products
+        \item Multi-task learning with more than two tasks
+    \end{itemize}
+
+    \note{Several promising directions exist for extending this research. \\}
+    \note{Incorporating actuarial domain knowledge could further improve transfer learning effectiveness. \\}
+    \note{The approach could be extended to other insurance products and financial derivatives. \\}
+    \note{Multi-task learning could be expanded to handle more than two contract types simultaneously. \\}
+    \note{Integration with existing risk management systems would facilitate practical adoption. \\}
+    \note{Ultimately, these techniques could transform how financial institutions manage complex product portfolios. \\}
+
+\end{frame}
 

### 2025-03-24 pre_private/pre.tex
new

@@
 \jointwork{Supervised by Prof. Tony Wirjanto and Prof. Mingbin Feng}
-\conference{Thesis Defense, \\ University of Waterloo}
+\conference{Thesis Defense \\ University of Waterloo \\ 2025}
 
@@
 \titlepage
+
+\note{Thank you for attending my thesis defense. \\}
+\note{Today, I will present my work on resilient machine learning approaches for fast risk evaluation and management of financial portfolios and variable annuities. \\}
+\note{I am supervised by Prof. Tony Wirjanto and Prof. Mingbin Feng. \\}
+
 \end{frame}
@@
 \tableofcontents
+
+\note{My thesis focuses on improving nested simulation with supervised learning metamodels. It consists of three parts. \\}
+\note{In the first part, I focus on comparing different nested simulation procedures for risk evaluation of financial derivatives. \\}
+\note{In the second part, I examine deep neural network based nested simulation procedures for risk management of variable annuities. \\}
+\note{In the third part, I propose a transfer learning based nested simulation procedure for fast adaptation to new variable annuity contracts.}
 \end{frame}
@@
 \begin{itemize}
-    \item Outer: underlying risk factors (outer scenarios), $X_i \sim F_X$
-    \item Inner: scenario-wise losses (inner replications), $Y_{ij} \sim F_{Y|X_i}$
-    \item Total simulation budget: $\Gamma = M \cdot N$
+    \item Outer: underlying risk factors, $X_i \sim F_X$
+    \item Inner: scenario-wise losses, $Y_{ij} \sim F_{Y|X_i}$
 \end{itemize}
@@
 \vspace{10pt}
-\textbf{Computationally expensive}
+
+With an expensive total simulation budget $\Gamma = M \cdot N$:
+$$\hat{L}_{N, i} = \frac{1}{N} \sum_{j=1}^N Y_{ij}; ~~~ Y_{ij} \sim F_{Y|X_i} $$
+
+\begin{itemize}
+    \item Uses inner sample mean to estimate $L(X_i)$.
+\end{itemize}
 
 \note{In the context of quantitative risk management, nested simulation is used for risk evaluation of financial derivatives and insurance products. \\}
-\note{The nested structure is due to the fact that the loss random variable is in the form of a conditional expectation of the portfolio loss given the underlying risk factors. \\}
-\note{In our problems, the loss random variable $L$ depends on the risk factors $X$ and is the conditional expectation of the portfolio loss given $X$. \\}
+\note{The nested structure is due to the loss random variable being a conditional expectation of the portfolio loss given the underlying risk factors. \\}
+\note{In our problems, the loss $L$ depends on the risk factors $X$ and is the conditional expectation of the portfolio loss given the risk factors. \\}
 \note{More specifically, $X$ is $d$-dimensional and $L$ is 1-dimensional. \\}
-\note{Estimating a risk measure, $\rho(L)$, involves two levels of Monte Carlo simulations: outer level generates underlying risk factors, and inner level generates scenario-wise samples of portfolio losses.
+\note{Estimating a risk measure, $\rho(L)$, involves two levels of Monte Carlo simulations: a outer level generates underlying risk factors, and a inner level generates scenario-wise samples of portfolio losses.
 \\}
+\note{The standard nested simulation procedure uses the inner sample mean under that scenarioto estimate $L(X_i)$. \\}
 \note{The nested structure makes the estimation computationally expensive. \\}
-\note{In this thesis, we focus on examining and improving the efficiency of nested simulation procedures mostly using supervised learning metamodels.}
-
-\end{frame}
-
-\begin{frame}{Common Risk Measures}
-
-\begin{itemize}
-    \item Smooth $h$, e.g., quadratic tracking error,
-
-    $$ \rho(L) = \mathbb{E} \left[ (L - b)^2 \right]; $$
-
-    \item hockey-stick $h$: mean excess loss,
-
-    $$ \rho(L) = \mathbb{E} \left[ L \cdot \mathbbm{1}_{\{L \geq u\}} \right]; $$
-
-    \item indicator $h$: probability of large loss,
-
-    $$ \rho(L) = \mathbb{E} \left[ \mathbbm{1}_{\{L \geq u\}} \right]; $$
-
-    \item Value at Risk (VaR),
-
-    $$ \rho_\alpha(L) = Q_\alpha(L) = \inf \{ u: \mathbb{P}(L \leq u) \geq \alpha \}; $$
-
-    \item Conditional Value at Risk (CVaR) \footnotemark,
-
-    $$ \rho_\alpha(L) = \mathbb{E} \left[ L \vert L \geq Q_\alpha(L) \right]. $$
-
-    \end{itemize}
-
-    \footnotetext{Note: If $Q_\alpha(L)$ falls in a probability mass, $\rho(L) = \frac{(\beta - \alpha)Q_\alpha(L) + (1- \beta) \mathbb{E} \left[ L \vert L \geq Q_\alpha(L) \right]}{1-\alpha}$.}
-
-\note{We consider different types of risk measures in this thesis. \\}
-\note{The first three are in expectation form, and the last two are quantile-based risk measures. \\}
-\note{The difference between the first three is the choice of the function $h$. \\}
-\note{$h$ can be a smooth function, a hockey-stick function, or an indicator function. \\}
-\note{The examples of risk measures are quadratic tracking error, mean excess loss, and probability of large loss. \\}
-\note{The last two are value at risk and conditional value at risk, which are widely used in practice. \\}
-\note{Note that the definition of CVaR requires the knowledge of the Value at Risk.}
-
-\end{frame}
+\note{In this thesis, we focus on examining and improving the efficiency of nested simulation procedures mostly by pooling with supervised learning metamodels.}
+
+\end{frame}
+
+% \begin{frame}{Common Risk Measures}
+
+% \begin{itemize}
+%     \item Smooth $h$, e.g., quadratic tracking error,
+
+%     $$ \rho(L) = \mathbb{E} \left[ (L - b)^2 \right]; $$
+
+%     \item hockey-stick $h$: mean excess loss,
+
+%     $$ \rho(L) = \mathbb{E} \left[ L \cdot \mathbbm{1}_{\{L \geq u\}} \right]; $$
+
+%     \item indicator $h$: probability of large loss,
+
+%     $$ \rho(L) = \mathbb{E} \left[ \mathbbm{1}_{\{L \geq u\}} \right]; $$
+
+%     \item Value at Risk (VaR),
+
+%     $$ \rho_\alpha(L) = Q_\alpha(L) = \inf \{ u: \mathbb{P}(L \leq u) \geq \alpha \}; $$
+
+%     \item Conditional Value at Risk (CVaR) \footnotemark,
+
+%     $$ \rho_\alpha(L) = \mathbb{E} \left[ L \vert L \geq Q_\alpha(L) \right]. $$
+
+%     \end{itemize}
+
+%     \footnotetext{Note: If $Q_\alpha(L)$ falls in a probability mass, $\rho(L) = \frac{(\beta - \alpha)Q_\alpha(L) + (1- \beta) \mathbb{E} \left[ L \vert L \geq Q_\alpha(L) \right]}{1-\alpha}$.}
+
+% \note{We consider different types of risk measures in this thesis. \\}
+% \note{The first three are in expectation form, and the last two are quantile-based risk measures. \\}
+% \note{The difference between the first three is the choice of the function $h$. \\}
+% \note{$h$ can be a smooth function, a hockey-stick function, or an indicator function. \\}
+% \note{The examples of risk measures are quadratic tracking error, mean excess loss, and probability of large loss. \\}
+% \note{The last two are value at risk and conditional value at risk, which are widely used in practice. \\}
+% \note{Note that the definition of CVaR requires the knowledge of the Value at Risk.}
+
+% \end{frame}
 
@@
 
-\begin{frame}{Standard Nested Simulation}
-
-$$\hat{L}_{N, i} = \frac{1}{N} \sum_{j=1}^N Y_{ij}; ~~~ Y_{ij} \sim F_{Y|X_i} $$
-
-\begin{itemize}
-    \item Uses inner sample mean to estimate $L(X_i)$.
-    \item Proposed by \citet{gordy2010nested}; finds optimal growth order of $M$ and $N$.
-    \item \citet{zhang2021bootstrap} estimate the optimal $M$ and $N$ using a bootstrap method.
-    \item Computationally expensive and potentially \textbf{wasteful} use of budget.
-\end{itemize}
-
-\note{In our first project, we focus on comparing existing nested simulation procedures for different types of risk measures. \\}
-\note{They differ in the way they estimate $L(X_i)$, the portfolio loss conditional on the risk factors $X_i$. \\}
-\note{The standard nested simulation procedure uses the inner sample mean under that scenarioto estimate $L(X_i)$. \\}
-\note{The optimal growth order of $M$ and $N$ is found by \citet{gordy2010nested}. \\}
-\note{For a growing total simulation budget $\Gamma$, $M$ should grow in the order of $\Gamma^{2/3}$, and $N$ should grow in the order of $\Gamma^{1/3}$. \\}
-\note{For a finite-sample case, the bootstrap method is used to estimate the optimal $M$ and $N$ by \citet{zhang2021bootstrap}. \\}
-\note{Since the standard procedure only uses the information from the same scenario, it is potentially \textbf{wasteful} use of budget. \\}
-\note{Subsequent works focus on improving the efficiency of nested simulation by pooling inner replications from different outer scenarios.}
-
-\end{frame}
+% \begin{frame}{Standard Nested Simulation}
+
+% $$\hat{L}_{N, i} = \frac{1}{N} \sum_{j=1}^N Y_{ij}; ~~~ Y_{ij} \sim F_{Y|X_i} $$
+
+% \begin{itemize}
+%     \item Uses inner sample mean to estimate $L(X_i)$.
+%     \item Proposed by \citet{gordy2010nested}; finds optimal growth order of $M$ and $N$.
+%     \item \citet{zhang2021bootstrap} estimate the optimal $M$ and $N$ using a bootstrap method.
+%     \item Computationally expensive and potentially \textbf{wasteful} use of budget.
+% \end{itemize}
+
+% \note{In our first project, we focus on comparing existing nested simulation procedures for different types of risk measures. \\}
+% \note{They differ in the way they estimate $L(X_i)$, the portfolio loss conditional on the risk factors $X_i$. \\}
+% \note{The standard nested simulation procedure uses the inner sample mean under that scenarioto estimate $L(X_i)$. \\}
+% \note{The optimal growth order of $M$ and $N$ is found by \citet{gordy2010nested}. \\}
+% \note{For a growing total simulation budget $\Gamma$, $M$ should grow in the order of $\Gamma^{2/3}$, and $N$ should grow in the order of $\Gamma^{1/3}$. \\}
+% \note{For a finite-sample case, the bootstrap method is used to estimate the optimal $M$ and $N$ by \citet{zhang2021bootstrap}. \\}
+% \note{Since the standard procedure only uses the information from the same scenario, it is potentially \textbf{wasteful} use of budget. \\}
+% \note{Subsequent works focus on improving the efficiency of nested simulation by pooling inner replications from different outer scenarios.}
+
+% \end{frame}
 
@@
 
-\note{A supervised learning based nested simulation procedure is implemented following these steps. \\}
+\note{Pooling can happen in different ways, and the key idea is to use the information from different outer scenarios to improve the efficiency of nested simulation. \\}
+\note{A supervised learning based nested simulation procedure pools with these steps. \\}
 \note{First, the user runs the standard nested simulation procedure to generate a set of outer scenarios and inner replications. \\}
-\note{Then, the outer scenarios and inner sample means can be treated as features and labels. \\}
-\note{Their relationship is then approximated by a supervised learning metamodel. \\}
-\note{Finally, the trained metamodel is used to make predictions for all $X \in \mathcal{X}$. \\}
-\note{In other words, instead of using the inner sample mean to estimate $L(X_i)$, we use the trained metamodel to make predictions of the portfolio loss. \\}
-\note{These loss predictions are then used to calculate the risk measures of interest. \\}
-\note{For most research in this area, the focus is on the convergence rate of the risk measure estimator in terms of the simulation budget. \\}
-\note{However, in this thesis, we note that there are other important aspects to consider, such as the cost of pooling that may come from metamodel training and validation. }
+\note{Then, the outer scenarios and inner sample means can be treated as features and labels for metamodel training. \\}
+\note{Finally, instead of the inner sample mean from the standard procedure, the metamodel predictions estimate the portfolio loss and the risk measures. \\}
+\note{Most existing works focus on the convergence rate of their estimators in terms of the simulation budget. \\}
+\note{However, we find that there is a cost of pooling that comes from metamodel training, validation, and prediction. }
 
@@
 
-\note{We start by comparing the asymptotic convergence rates of different nested simulation procedures. \\}
-\note{These are the convergence rates of the MSE of the risk measure estimator when the total simulation budget $\Gamma$ goes to infinity, and when one follows the optimal growth order of $M$ and $N$.
-\\}
+\note{We start by comparing the asymptotic rates of different nested simulation procedures. \\}
+\note{These are the convergence rates of the MSE of the risk measure estimator when the total simulation budget $\Gamma$ goes to infinity. \\}
 \note{The standard procedure has the same convergence rate of $\mathcal{O}(\Gamma^{-2/3})$ for all types of $h$ considered.
@@
 \note{The regression-based procedure has $\mathcal{O}(\Gamma^{-1})$ convergence rate for smooth and hockey-stick $h$. \\}
-\note{It is achieved by only allowing $M$ to grow in the order of $\Gamma^{1}$. In their experiments, $N$ is set to equal a value of $1$. \\}
+\note{It is achieved by only allowing $M$ to grow. In their experiments, $N$ is set to equal a constant. \\}
 \note{The kernel smoothing procedure is the only procedure that depends on the asset dimension $d$. \\}
@@
 \note{The kernel ridge regression procedure and likelihood ratio procedure have the same convergence rate as the regression-based procedure. \\}
-\note{However, as we will see in the numerical experiments, their additional cost of pooling inner replications may offset their benefit of fast convergence rate. \\}
+\note{However, in our numerical experiments, we find that their additional cost of pooling may offset their benefit of fast asymptotic rates. \\}
 \note{Additionally for KRR, the authors analyze convergence of absolute error in probabilistic order instead of MSE.}
@@
 \note{One of the contributions of this thesis is to bridge the gap between MSE and absolute error convergence. \\}
-\note{Let's first define the convergence in MSE and the convergence in probabilistic order. \\}
-\note{The convergence in MSE is the convergence of the MSE of the risk measure estimator to the true risk measure, that is, $\hat{\rho}_{\Gamma}$ minus $\rho$ squared. \\}
-\note{The convergence in probabilistic order is the convergence of the absolute error of the risk measure estimator to the true risk measure, that is, $|\hat{\rho}_{\Gamma} - \rho|$ to 0 in probability.
-\\}
-\note{We show that the convergence rate of the MSE of the risk measure estimator implies the convergence rate of the absolute error in probabilistic order. \\}
-\note{We will also show that the converse is not necessarily true.}
+\note{We first define the convergence in MSE and the convergence in probabilistic order. \\}
+\note{And we show that the convergence rate of $\Gamma^{-\xi}$ in MSE of the risk measure estimator implies the convergence rate of $\Gamma^{-\frac{\xi}{2}}$ in probabilistic order. \\}
+\note{We also show that the converse is not necessarily true.}
 
@@
 
-\begin{frame}{Experiment Design}
-
-We compare 5 nested simulation procedures 
-\begin{itemize}
-    \item Standard nested simulation
-    \item Regression-based
-    \item Kernel smoothing
-    \item Likelihood ratio
-    \item Kernel ridge regression
-\end{itemize}
-
-And their empirical convergence across different:
-\begin{itemize}
-    \item Risk measures
-    \item Option types
-    \item Asset dimensions
-    \item Asset models (GBM vs. Heston)
-    \item Regression bases (only for the regression-based procedure)
+% \begin{frame}{Experiment Design}
+
+% We compare 5 nested simulation procedures 
+% \begin{itemize}
+%     \item Standard nested simulation
+%     \item Regression-based
+%     \item Kernel smoothing
+%     \item Likelihood ratio
+%     \item Kernel ridge regression
+% \end{itemize}
+
+% And their empirical convergence across different:
+% \begin{itemize}
+%     \item Risk measures
+%     \item Option types
+%     \item Asset dimensions
+%     \item Asset models (GBM vs. Heston)
+%     \item Regression bases (only for the regression-based procedure)
+% \end{itemize}
+
+% \note{Previously, we worked on the asymptotic convergence rates of different nested simulation procedures. \\}
+% \note{In practice, the total simulation budget is finite.}
+% \note{When the budget is finite, the theoretical convergence rate may not be the only thing we should consider. \\}
+% \note{We should also consider the cost of pooling itself. \\}
+% \note{The additional cost of pooling inner replications is not considered in the theoretical analysis of the previous works. \\}
+% \note{Neither it is mentioned in their numerical experiments. \\}
+% \note{More specifically, we have found that different research uses different numerical experiments to show the empirical rate of different procedures. \\}
+% \note{We aim to provide a fair and comprehensive analysis of the finite-sample performance of different nested simulation procedures. \\}
+% \note{Our numerical experiments test the empirical convergence rates of different nested simulation procedures across different risk measures, option types, asset dimensions, and asset models.}
+
+% \end{frame}
+
+\begin{frame}{Finite-Sample Performance}
+
+\begin{figure}
+    \includegraphics[width=0.9\textwidth]{../project1/figures/figure2a.png}
+\end{figure}
+
+\begin{itemize}
+    \item Standard, KRR, and likelihood ratio procedures are dimension-independent
+    \item Kernel smoothing and regression show sensitivity to dimension, but in different ways
 \end{itemize}
@@
 \note{When the budget is finite, the theoretical convergence rate may not be the only thing we should consider. \\}
-\note{We should also consider the cost of pooling itself. \\}
-\note{The additional cost of pooling inner replications is not considered in the theoretical analysis of the previous works. \\}
-\note{Neither it is mentioned in their numerical experiments. \\}
-\note{More specifically, we have found that different research uses different numerical experiments to show the empirical rate of different procedures. \\}
-\note{We aim to provide a fair and comprehensive analysis of the finite-sample performance of different nested simulation procedures. \\}
-\note{The following numerical experiments test the empirical convergence rates of different nested simulation procedures across different risk measures, option types, asset dimensions, and asset models.}
-
-\end{frame}
-
-\begin{frame}{Finite-Sample Performance}
-
-\begin{figure}
-    \includegraphics[width=\textwidth]{../project1/figures/figure1.png}
-    \caption{Empirical convergence rates of different procedures for the base case}
-\end{figure}
-
 \note{This figure shows the performance of all 5 procedures in their estimation of the quadratic tracking error for the portfolio of European call options.}
@@
 \note{In the most basic case, most procedures have their empirical convergence rates match their asymptotic convergence rates. \\}
-\note{However, as we will see after, this is not the case for all experiments. \\}
-\note{The following slides will show the sensitivity of the procedures to different factors. \\}
-
-\end{frame}
-
-% \begin{frame}{Sensitivity to Asset Dimension}
-
-% \begin{figure}
-%     \includegraphics[width=\textwidth]{../project1/figures/figure2a.png}
-% \end{figure}
-
-% \begin{itemize}
-%     \item Standard, KRR, and likelihood ratio procedures are dimension-independent
-%     \item Kernel smoothing and regression show sensitivity to dimension, but in different ways
-% \end{itemize}
-
-% \note{This figure shows the sensitivity of the procedures to the asset dimension. \\}
-% \note{The asset dimension is the dimension of the risk factors $X$. \\}
-% \note{Everything is the same as the previous figure, except that the asset dimension is varied from 1 to 2. \\}
-% \note{The standard, regression, KRR, and likelihood ratio procedures are dimension-independent. \\}
-% \note{The kernel smoothing procedure is sensitive to the asset dimension. \\}
-% \note{Despite the fact that the kernel smoothing procedure has the same asymptotic convergence rate as before, it converges slower in practice. \\}
-
-% \end{frame}
+\note{However, as we will see after, this is not the case for all experiments. }
+
+\end{frame}
 
@@
     \begin{figure}
-        \includegraphics[width=\textwidth]{../project1/figures/figure2b.png}
+        \includegraphics[width=0.9\textwidth]{../project1/figures/figure2b.png}
     \end{figure}
@@
     \begin{itemize}
-        \item Standard, KRR, and likelihood ratio procedures are dimension-independent
-        \item Kernel smoothing and regression show sensitivity to dimension, but in different ways
+        \item Regression and kernel converge faster than their asymptotic rates
+        \item Results of other experiments are in the thesis (Figure 2.3 - Figure 2.11)
     \end{itemize}
@@
 \note{While it is not shown in their empirical rate, due to their additional cost of pooling inner replications, we are not able to run these procedures when $\Gamma$ is large. \\}
-
-\end{frame}
-
-\begin{frame}{Fast Convergence of Regression-based Procedure}
-
-\begin{figure}
-    \includegraphics[width=\textwidth]{../project1/figures/figure3.png}
-\end{figure}
-
-\begin{itemize}
-    \item Higher initial convergence rate
-    \item Stabilizes to match asymptotic rate at higher budgets
-    \item Consistent across different asset dimensions
-\end{itemize}
-
-\note{To investigate the regression-based procedure, we further increase the total simulation budget $\Gamma$. \\}
-\note{The figure shows the performance of the regression-based procedure in the estimation of the quadratic tracking error for the portfolio of European call options. \\}
-\note{We separate different values of $\Gamma$ into two different parts. \\}
-\note{The first part is when $\Gamma$ is small. \\}
-\note{The second part is when $\Gamma$ is large. \\}
-\note{The first part is when the regression-based procedure has a higher convergence rate than its asymptotic convergence rate. \\}
-\note{The second part is when the regression-based procedure stabilizes and matches its asymptotic convergence rate. \\}
-\note{In our experiments, we find that the regression-based procedure is very poor when $\Gamma$ is small. \\}
-\note{It means that when we don't have enough data points, the regression-based procedure is particularly bad. \\}
-\note{As we increase the total simulation budget $\Gamma$, the regression-based procedure improves fast, and eventually matches the asymptotic convergence rate. \\}
-
-\end{frame}
+\note{In the thesis, we provide a detailed analysis of the sensitivity for all 5 procedures with more than 500 experiments. }
+
+\end{frame}
+
+% \begin{frame}{Fast Convergence of Regression-based Procedure}
+
+% \begin{figure}
+%     \includegraphics[width=\textwidth]{../project1/figures/figure3.png}
+% \end{figure}
+
+% \begin{itemize}
+%     \item Higher initial convergence rate
+%     \item Stabilizes to match asymptotic rate at higher budgets
+%     \item Consistent across different asset dimensions
+% \end{itemize}
+
+% \note{To investigate the regression-based procedure, we further increase the total simulation budget $\Gamma$. \\}
+% \note{The figure shows the performance of the regression-based procedure in the estimation of the quadratic tracking error for the portfolio of European call options. \\}
+% \note{We separate different values of $\Gamma$ into two different parts. \\}
+% \note{The first part is when $\Gamma$ is small. \\}
+% \note{The second part is when $\Gamma$ is large. \\}
+% \note{The first part is when the regression-based procedure has a higher convergence rate than its asymptotic convergence rate. \\}
+% \note{The second part is when the regression-based procedure stabilizes and matches its asymptotic convergence rate. \\}
+% \note{In our experiments, we find that the regression-based procedure is very poor when $\Gamma$ is small. \\}
+% \note{It means that when we don't have enough data points, the regression-based procedure is particularly bad. \\}
+% \note{As we increase the total simulation budget $\Gamma$, the regression-based procedure improves fast, and eventually matches the asymptotic convergence rate. \\}
+
+% \end{frame}
 
@@
 
-\begin{frame}{Total Computation Time}
+\begin{frame}{Additional Computational Costs}
 
     \begin{figure}
-        \includegraphics[width=\textwidth]{../project1/figures/figure11b.png}
-        \caption{Total computation time for different procedures}
+        \includegraphics[width=\textwidth]{./time_comparison.png}
+        \caption{Additional computation time for different procedures}
     \end{figure}
 
-    \note{This figure shows the total computation time for different procedures. \\}
-    \note{It includes the time for both the simulation, training, validation, and everything else. \\}
+    \note{This figure shows the additional computation time for different procedures. \\}
+    \note{It includes the time for training, validation, and everything else. \\}
     \note{The total computation time of the standard procedure does not increase fast with $\Gamma$. \\}
     \note{It is because the computation time of estimating the optimal $M$ and $N$ does not increase for larger $\Gamma$. \\}
-    \note{The regression procedure and kernel smoothing procedure are the most efficient among metamodel-based procedures. \\}
-    \note{Our implementation of the kernel smoothing procedure is efficient because we only run the cross-validation once for all macro replications. \\}
-    \note{The likelihood ratio procedure and KRR procedure are more expensive due to their additional costs}
+    \note{Regression is the most efficient among metamodel-based procedures. \\}
+    \note{The likelihood ratio and KRR are more expensive due to their additional costs. \\}
     \note{The likelihood ratio weight calculations increase quadratically with $\Gamma$. \\}
-    \note{For KRR, the cost of cross-validation is so high that running it once still takes a very long time. \\}
+    \note{For KRR, the cost of cross-validation is too high. \\}
     \note{In the thesis includes a detailed analysis of the computational complexity of different procedures in terms of $\Gamma$.}
@@
 
-\begin{frame}{Research Questions}
-
-    \begin{itemize}
-        \item What do DNNs learn from noisy data?
-        \item How well do DNNs learn from noisy data?
-    \end{itemize}
-
-    \begin{figure}[H]
-        \includegraphics[width=\textwidth]{../project2/figures/datasets.png}
-    \end{figure}
-
-    Three datasets are considered:
-    \begin{itemize}
-        \item   \textcolor{color10_2}{Training}: 90,000 scenarios (100 inner replications).
-        \item   \textcolor{color10_3}{Test}: 10,000 scenarios (100 inner replications).
-        \item   \textcolor{color10_5}{True}: 100,000 scenarios (100,000 inner replications).
-    \end{itemize}
-
-\note{To further clarify our research questions, we consider the following scenario: \\}
-\note{We have a noisy training data and a noisy test data. \\}
-\note{We want to know what the metamodel learns from the noisy data. \\}
-\note{We also want to know how well the metamodel can make accurate loss predictions for given scenarios. \\}
-\note{In a simulation experiment, we can control the noise level in the training data and the test data. \\}
-\note{We also have access to the true feature-label relationship when we increase the number of replications. \\}
-\note{We can use this true feature-label relationship to evaluate the performance of deep neural networks, which is usually not possible in practice. }
-
-\end{frame}
-
 \begin{frame}{Metamodel Performance}
@@
 
-    \note{We first consider the traditional regression metamodels. \\}
-    \note{On the left is the QQ plot between the true loss labels and the predicted loss labels for MLR, and on the right is the QQ plot for QPR. \\}
-    \note{MLR and QPR metamodels make inaccurate loss predictions. \\}
-    \note{Feature engineering is hardly feasible for our 240-dimensional $X$. \\}
-    \note{We will see whether deep neural networks can make more accurate loss predictions. \\}
+    \note{We first take a look at their performance with QQ plots. \\}
+    \note{On the left is the QQ plot between the true loss labels and the predicted loss labels for QPR, and on the right is the QQ plot for LSTM. \\}
+    \note{Feature engineering for QPR is hardly feasible for our 240-dimensional $X$. Its poor performance is expected. \\}
+    \note{DNN metamodels are more flexible, and they can make more accurate loss predictions. \\}
 
@@
 % \end{frame}
+
+\begin{frame}{Research Questions}
+
+    \begin{itemize}
+        \item What do DNNs learn from noisy data?
+        \item How well do DNNs learn from noisy data?
+    \end{itemize}
+
+    \begin{figure}[H]
+        \includegraphics[width=\textwidth]{../project2/figures/datasets.png}
+    \end{figure}
+
+    Three datasets are considered:
+    \begin{itemize}
+        \item   \textcolor{color10_2}{Training}: 90,000 scenarios (100 inner replications).
+        \item   \textcolor{color10_3}{Test}: 10,000 scenarios (100 inner replications).
+        \item   \textcolor{color10_5}{True}: 100,000 scenarios (100,000 inner replications).
+    \end{itemize}
+
+\note{To further clarify our research questions, we consider the following scenario: \\}
+\note{We have a noisy training data and a noisy test data. \\}
+\note{We want to know what the metamodel learns from the noisy data. \\}
+\note{We also want to know how well the metamodel can make accurate loss predictions for given scenarios. \\}
+\note{In a simulation experiment, we can control the noise level in the training data and the test data. \\}
+\note{We also have access to the true feature-label relationship when we increase the number of replications. \\}
+\note{We can use this true feature-label relationship to evaluate the performance of deep neural networks, which is usually not possible in practice. }
+
+\end{frame}
 
@@
     \note{We find that the true errors of RNN-based metamodels are lower than their test errors. \\}
-    \note{This suggests that the RNN and LSTM metamodels are able to cut through the simulation noise and learn the true feature-label relationship. \\}
+    \note{This suggests that the RNN and LSTM metamodels can learn the true feature-label relationship. \\}
     \note{When we take another look at the table, we find that for LSTM, its true error is even lower than its training error. \\}
     \note{This is another evidence that LSTM metamodels are able to cut through the noise in training labels and fit to the true relationship. \\}
-    \note{We also find that the LSTM metamodel is able to cut through the noise in training labels and fit to the true relationship. \\}
-    \note{We have another finding for RNN. RNN metamodels suffer from the vanishing gradient problem. \\}
-    \note{This is why we make separate rows for well-trained RNNs and poorly-trained RNNs. \\}
-    \note{We will discuss this in the next slide. \\}
+    \note{RNN metamodels suffer from the vanishing gradient problem. This is why we make separate rows for well-trained RNNs and poorly-trained RNNs. }
 
@@
 
-    \note{We now consider the tail scenario identification for the two-stage procedure. \\}
-    \note{On the left is the tail scenario identification for the traditional regression metamodel, and on the right is the tail scenario identification for the LSTM metamodel. \\}
+    \note{We now consider the tail scenario identification and the CVaR estimation for the two-stage procedure. \\}
+    \note{On the left is the tail scenario identification plot, and on the right is the plot of CVaR. \\}
     \note{We compare the two-stage procedure with the standard procedure. \\}
     \note{When colored lines cross the grey dashed line, it means that the metamodel is able to identify the tail scenarios as well as the standard procedure. \\}
+    \note{And it should be able to estimate the CVaR as accurately as the standard procedure. \\}
     \note{We find that the LSTM metamodel is able to surpass the standard procedure on tail identification with a less than $5\%$ safety margin. \\}
@@
     \note{A well-trained RNN is better than a FNN, but the poorly-trained RNN is far worse.}
-    \note{This further motivates the use of LSTM metamodels over RNN metamodels. \\}
+    \note{The CVaR estimation plot shows similar results.}
 
@@
 
-    \note{We now consider the sensitivity testing for the DNN metamodels. \\}
-    \note{We are interested in the sensitivity of the DNN metamodels to the noise level in training labels and the number of training samples. \\}
+    \note{We now dig deeper into the research questions asked: how well do deep learning metamodels learn from noisy data? \\}
+    \note{We study this phenomenon by considering the sensitivity testing for the DNN metamodels. \\}
+    \note{The sensitivity of the DNN metamodels to the noise level in training labels and the number of training samples. \\}
     \note{In a simulation experiment, we can vary them to see how the DNN metamodels perform. \\}
-    \note{We consider the noise level in training labels by varying the number of inner replications $N'$. \\}
-    \note{We consider the number of training samples by varying the number of outer scenarios $M$. \\}
+    \note{We control the noise level in training labels by varying the number of inner replications $N'$. \\}
+    \note{We control the number of training samples by varying the number of outer scenarios $M$. \\}
     \note{We consider two LSTM metamodels of different capacities because we want to see if the capacity of the metamodel matters for overfitting. \\}
@@
     \note{We plot the predicted losses versus the true losses for both LSTMs and different noise levels. \\}
-    \note{The closer the points are to the line, the better the model is. \\}
     \note{The high-capacity LSTM is better at low and medium noise levels, while the regular LSTM is better at high noise levels. \\}
@@
 
-    \note{The findings are similar for the high-capacity LSTM metamodel. \\}
-    \note{We can find similar patterns as in the previous table. \\}
-    \note{The model is more sensitive to $N'$ than $M$, unless $N'$ is very small. \\}
-    \note{For a practical application, we recommend using the high-capacity LSTM metamodel with $N' = 10$ for almost all simulation budgets. }
+    \note{This table shows the MSEs of the two LSTM metamodels on different datasets. \\}
+    \note{We modify $M$, the number of outer scenarios, and $N'$, the number of inner replications. \\}
+    \note{$M$ is the number of data points in the training set, and $N'$ is the noise level in the training labels. \\}
+    \note{We have additional findings that the number of data points, $M$ also matters. \\}
+    \note{And it matters more for than $N'$ does. \\}
+    \note{In this table, the entries in the same diagonal represent the same total simulation budget. \\}
+    \note{It gives us a good indication of how much noise the LSTM metamodel can tolerate. \\}
+    \note{For a practical application, we almost want to increase $M$ as much as possible. \\}
+    \note{However, we can see that in the diagonal of red color, we should keep $N'$ at 10 and not lower it to 1. \\}
+    \note{We don't want the training labels to be too noisy.}
 
@@
     \note{These insights provide valuable guidance for implementing machine learning in financial risk management.\\}
-
-    \note{For the research directions. In the future, we can apply deep neural network metamodels to other actuarial applications.\\}
-    \note{In the future, we can also apply transfer learning to speed up the training process for deep neural network metamodels.\\}
+    \note{For the research directions, we can apply deep neural network metamodels to other actuarial applications.\\}
+    \note{We can also apply transfer learning to speed up the training process for deep neural network metamodels.\\}
 
@@
     \note{This is particularly valuable when simulation data is expensive to generate for new contracts.\\}
-    \note{The transfer learning approach allows us to maintain accuracy while significantly reducing computational requirements.\\}
+    \note{The transfer learning approach allows us to maintain accuracy while significantly reducing computational requirements.}
 
@@
         \item   \textbf{Layer freezing:} only part of the model is fine-tuned.
-        \item   \textbf{Multi-task learning:} perform training on multiple tasks simultaneously.
     \end{itemize}
@@
 
-    \textbf{Key considerations:}
-    \begin{itemize}
-        \item   Similarity between source and target tasks
-        \item   Appropriate learning rate
+    \textbf{Key considerations:} similarity between source and target tasks
+
+    \vspace{10pt}
+
+    \textbf{Experiment Design:}
+    \begin{itemize}
+        \item   Source domain (50000 samples): GMMB with no lapse and GMMB with static lapse
+        \item   Target domain (2000 samples): GMMB with dynamic lapse
     \end{itemize}
@@
     \note{Fine-tuning involves using a pre-trained model as a starting point for a new task.\\}
-    \note{This approach is effective when the source and target tasks are similar.\\}
     \note{For VA contracts, we can fine-tune models between different contract types or market conditions.\\}
@@
     \note{By freezing early layers, we preserve general knowledge while adapting task-specific layers.\\}
-    \note{Multi-task learning trains a single model to perform multiple related tasks simultaneously.\\}
-    \note{This approach can improve generalization by leveraging the domain-specific information across tasks.\\}
-    \note{For VA contracts, we can train a model to handle multiple contract types or features.\\}
-    \note{The learning rate is a critical hyperparameter in transfer learning.\\}
-    \note{Typically, we use a smaller learning rate for fine-tuning compared to training from scratch.\\}
-    \note{The similarity between source and target tasks greatly impacts transfer learning effectiveness.\\}
-    \note{More similar tasks generally allow for more effective knowledge transfer.\\}
+    \note{In our experiment, we use the same model architecture for all tasks. \\}
+    \note{Metamodels are trained with 50,000 samples on the source domain before transferring to the target domain with only 2000 samples. \\}
+    \note{We progress from simpler to more complex models (No lapse → Static → Dynamic). \\}
+    \note{The experiments are designed to evaluate how similarity between source and target affects transfer efficiency. \\}
+    \note{This is another attempt to use simulation models as data generating processes to examine deep neural networks. \\}
+    \note{By examining the transfer learning performance, we can gain insights into which parts of the neural network are transferable, or more generally, which layers of the neural network learn which features of the VA contracts.
+}
 
@@
 
-\begin{frame}{Multi-task Learning}
-    \includegraphics[width=0.9\textwidth]{../project3/figures/mtl.png}
-
-    \begin{itemize}
-        \item LSTM layers shared across multiple tasks
-        \item Task-specific fully connected layers
-        \item Objective: Minimize sum of loss functions across all tasks
-    \end{itemize}
-
-    \note{Multi-task learning offers an alternative approach to transfer learning. \\}
-    \note{Instead of sequential knowledge transfer, we train on multiple contract types simultaneously. \\}
-    \note{The shared LSTM layers capture common features across different VA contracts. \\}
-    \note{Task-specific layers then specialize for each contract type's unique characteristics. \\}
-    \note{We will examine whether this approach can be more efficient than training separate models for each contract type. \\}
-
-\end{frame}
-
-\begin{frame}{Experiment Setup}
-
-    \begin{table}[ht!] 
-        \centering
-        \begin{tabular}{lcccc} 
-        \toprule
-        \textbf{Contract} & \textbf{Asset Model} & \textbf{Lapse} & \textbf{$M_{\text{So}}$}  & \textbf{$M_{\text{Ta}}$}\\
-        \midrule
-        GMMB & GBM & No lapse & 50000 & N/A \\
-        GMMB & RS-GBM & No lapse & 50000 & 2000 \\
-        GMMB & RS-GBM & Static lapse & 50000 & 2000 \\
-        GMMB & RS-GBM & Dynamic lapse & 50000 & 2000 \\
-        GMWB & RS-GBM & Dynamic lapse & N/A & 2000 \\
-        \bottomrule
-        \end{tabular}
-        \caption{VA Contracts for Transfer Learning Experiments}
-    \end{table}
-
-    We aim to examine the performance of TL techniques
-    \begin{itemize}
-        \item   learning the lapse features,
-        \item   learning the dynamic lapse, and 
-        \item   transferring to other contract types.
-    \end{itemize}
-
-    \note{We use a variety of VA contracts with different features to test transfer learning. \\}
-    \note{The source model ($M_{\text{So}}$) is trained with 50,000 samples for comprehensive learning. \\}
-    \note{The target model ($M_{\text{Ta}}$) uses only 2,000 samples to simulate limited data scenarios. \\}
-    \note{We progress from simpler to more complex models (No lapse → Static → Dynamic). \\}
-    \note{We examine both within-contract transfer (GMMB to GMMB with different features) and cross-contract transfer (GMMB to GMWB). \\}
-    \note{The regime-switching GBM (RS-GBM) model captures more realistic market dynamics. \\}
-    \note{All training data is generated using 100 inner replications for consistency. \\}
-    \note{We compare fine-tuning and layer freezing as two primary transfer learning approaches. \\}
-    \note{The experiments are designed to evaluate how similarity between source and target affects transfer efficiency. \\}
-    \note{This is another attempt to use simulation models as data generating processes to examine deep neural networks. \\}
-    \note{By examining the transfer learning performance, we can gain insights into which parts of the neural network are transferable, or more generally, which layers of the neural network learn which features of the VA contracts.
+% \begin{frame}{Multi-task Learning}
+%     \includegraphics[width=0.9\textwidth]{../project3/figures/mtl.png}
+
+%     \begin{itemize}
+%         \item LSTM layers shared across multiple tasks
+%         \item Task-specific fully connected layers
+%         \item Objective: Minimize sum of loss functions across all tasks
+%     \end{itemize}
+
+%     \note{Multi-task learning offers an alternative approach to transfer learning. \\}
+%     \note{Instead of sequential knowledge transfer, we train on multiple contract types simultaneously. \\}
+%     \note{The shared LSTM layers capture common features across different VA contracts. \\}
+%     \note{Task-specific layers then specialize for each contract type's unique characteristics. \\}
+%     \note{We will examine whether this approach can be more efficient than training separate models for each contract type. \\}
+
+% \end{frame}
+
+% \begin{frame}{Experiment Setup}
+
+%     \begin{table}[ht!] 
+%         \centering
+%         \begin{tabular}{lcccc} 
+%         \toprule
+%         \textbf{Contract} & \textbf{Asset Model} & \textbf{Lapse} & \textbf{$M_{\text{So}}$}  & \textbf{$M_{\text{Ta}}$}\\
+%         \midrule
+%         GMMB & GBM & No lapse & 50000 & N/A \\
+%         GMMB & RS-GBM & No lapse & 50000 & 2000 \\
+%         GMMB & RS-GBM & Static lapse & 50000 & 2000 \\
+%         GMMB & RS-GBM & Dynamic lapse & 50000 & 2000 \\
+%         GMWB & RS-GBM & Dynamic lapse & N/A & 2000 \\
+%         \bottomrule
+%         \end{tabular}
+%         \caption{VA Contracts for Transfer Learning Experiments}
+%     \end{table}
+
+%     We aim to examine the performance of TL techniques
+%     \begin{itemize}
+%         \item   learning the lapse features,
+%         \item   learning the dynamic lapse, and 
+%         \item   transferring to other contract types.
+%     \end{itemize}
+
+%     \note{We use a variety of VA contracts with different features to test transfer learning. \\}
+%     \note{The source model ($M_{\text{So}}$) is trained with 50,000 samples for comprehensive learning. \\}
+%     \note{The target model ($M_{\text{Ta}}$) uses only 2,000 samples to simulate limited data scenarios. \\}
+%     \note{We progress from simpler to more complex models (No lapse → Static → Dynamic). \\}
+%     \note{We examine both within-contract transfer (GMMB to GMMB with different features) and cross-contract transfer (GMMB to GMWB). \\}
+%     \note{All training data is generated using 100 inner replications for consistency. \\}
+%     \note{We compare fine-tuning and layer freezing as two primary transfer learning approaches. \\}
+%     \note{The experiments are designed to evaluate how similarity between source and target affects transfer efficiency. \\}
+%     \note{This is another attempt to use simulation models as data generating processes to examine deep neural networks. \\}
+%     \note{By examining the transfer learning performance, we can gain insights into which parts of the neural network are transferable, or more generally, which layers of the neural network learn which features of the VA contracts.
 \\}
 
-\end{frame}
+% \end{frame}
 

### 2025-03-24 pre_private/bs_ec_knn_time.py

@@ -1,0 +1,168 @@
+import numpy as np
+import pandas as pd
+import methods
+from sklearn.neighbors import KNeighborsRegressor
+from sklearn.model_selection import KFold
+from joblib import Parallel, delayed
+import time
+
+def knn_Euro_Call(n_front, n_back, d, S_0, K, mu, sigma, r, tau, T, k_opt=-1):
+
+    cor_mat = np.ones((d, d)) * 0.3 + np.identity(d) * 0.7
+    cov_mat = cor_mat * sigma**2
+
+    start = time.time()
+    sample_outer_train = methods.GBM_front(n_front = n_front, d = d, S_0 = S_0,
+                                           drift_vec = mu, diffusion_mat = cov_mat, tau = tau)
+    sample_inner = methods.GBM_back(n_front = n_front, n_back = n_back, d = d, S_tau = sample_outer_train,
+                                    drift = r, diffusion = cov_mat, T = T - tau)
+
+    payoff = np.zeros([d, n_front])
+    for j in range(len(K)):
+        price = np.mean(np.maximum(sample_inner - K[j], 0), axis=2) * np.exp(-r * (T - tau))
+        payoff = payoff + price
+
+    portfolio_value_0 = 0
+    for j in range(len(K)):
+        portfolio_value_0 = portfolio_value_0 + methods.price_CP(S_0, T, sigma, r, K[j], 0, "C", "long")
+
+    X_train = methods.generate_basis(sample_outer_train, option_type = "Vanilla", basis_function = "None")
+    y_train = np.sum(payoff, axis=0)
+
+    if k_opt <= 0:
+        cv_kf = KFold(n_splits=3)
+        k_range = np.arange(100, 301, 50)
+        n_k = k_range.shape[0]
+        cv_score = np.zeros(n_k)
+
+        for k in range(n_k):
+
+            for train_ind, val_ind in cv_kf.split(X_train, y_train):
+
+                X = X_train[train_ind]
+                X_val = X_train[val_ind]
+                y = y_train[train_ind]
+                y_val = y_train[val_ind]
+
+                y_hat = KNeighborsRegressor(n_neighbors = k_range[k]).fit(X, y).predict(X_val)
+                cv_score[k] = cv_score[k] + np.sum((y_hat - y_val) ** 2)
+
+        k_opt = k_range[np.argmin(cv_score)]
+
[…]

### 2025-03-24 pre_private/bs_ec_reg_time.py

@@ -1,0 +1,105 @@
+import numpy as np
+import pandas as pd
+import methods
+from sklearn.linear_model import LinearRegression
+from joblib import Parallel, delayed
+import time
+
+
+def reg_Euro_Call(n_front, n_back, d, S_0, K, mu, sigma, r, tau, T):
+
+    cor_mat = np.ones((d, d)) * 0.3 + np.identity(d) * 0.7
+    cov_mat = cor_mat * sigma**2
+
+    start = time.time()
+    sample_outer_train = methods.GBM_front(n_front = n_front, d = d, S_0 = S_0,
+                                           drift_vec = mu, diffusion_mat = cov_mat, tau = tau)
+    sample_inner = methods.GBM_back(n_front = n_front, n_back = n_back, d = d, S_tau = sample_outer_train,
+                                    drift = r, diffusion = cov_mat, T = T - tau)
+
+    payoff = np.zeros([d, n_front])
+    for j in range(len(K)):
+        price = np.mean(np.maximum(sample_inner - K[j], 0), axis=2) * np.exp(-r * (T - tau))
+        payoff = payoff + price
+
+    portfolio_value_0 = 0
+    for j in range(len(K)):
+        portfolio_value_0 = portfolio_value_0 + methods.price_CP(S_0, T, sigma, r, K[j], 0, "C", "long")
+
+    X_train = methods.generate_basis(sample_outer_train)
+    y_train = np.sum(payoff, axis=0)
+
+    reg = LinearRegression().fit(X_train, y_train)
+
+    sample_outer_test = methods.GBM_front(n_front=n_front, d=d, S_0=S_0,
+                                          drift_vec=mu, diffusion_mat=cov_mat, tau=tau)
+
+    X_test = methods.generate_basis(sample_outer_test)
+    y_test = reg.predict(X_test)
+
+    loss_reg = d * portfolio_value_0 - y_test
+
+    total_time = time.time() - start
+
+    return loss_reg, total_time
+
+
+def cal_RRMSE(n_front, n_back, d, S_0, K, mu, sigma, r, tau, T, alpha, L0):
+
+    loss, total_time = reg_Euro_Call(n_front, n_back, d, S_0, K, mu, sigma, r, tau, T)
+
+    # indicator = np.mean((loss > L0))
+    # hockey = np.mean(np.maximum(loss - L0, 0))
+    # quadratic = np.mean((loss - L0) ** 2)
+
[…]

### 2025-03-24 pre_private/simTrue.py

@@ -1,0 +1,74 @@
+import numpy as np
+import methods
+import pandas as pd
+from joblib import Parallel, delayed
+
+
+def ComputeTrueLoss(n_front, d, S_0, K, mu, sigma, r, tau, T, alpha=0.1):
+
+    rho = 0.3
+    cor_mat = methods.generate_cor_mat(d, rho)
+    cov_mat_call = cor_mat * sigma ** 2
+
+    print("European Call: Simulating Front Paths...")
+    sample_outer_call = methods.GBM_front(n_front=n_front, d=d, S_0=S_0,
+                                          drift_vec=mu, diffusion_mat=cov_mat_call, tau=tau)
+
+    print("Calculating Value...")
+    call_tau = np.zeros(n_front)
+    for j in range(len(K)):
+        call_tau_vec = Parallel(n_jobs=d, verbose=10)(
+            delayed(methods.price_CP)(sample_outer_call[k, :], T - tau, sigma, r, K[j], 0, "C", "long")
+            for k in range(d))
+        call_tau = call_tau + np.sum(call_tau_vec, axis=0)
+    print("End of European Call.")
+
+    portfolio_value_0 = 0
+
+    for j in range(len(K)):
+        portfolio_value_0 = portfolio_value_0 + methods.price_CP(S_0, T, sigma, r, K[j], 0, "C", "long")
+
+    loss_true = d * portfolio_value_0 - call_tau
+
+    loss_true.sort()
+
+    L0 = loss_true[int(np.ceil((1 - alpha) * n_front))]
+
+    indicator_true = alpha
+    hockey_true = np.mean(np.maximum(loss_true - L0, 0))
+    quadratic_true = np.mean((loss_true - L0) ** 2)
+    CVaR = np.mean(loss_true[loss_true > L0])
+
+    return L0, indicator_true, hockey_true, quadratic_true, CVaR
+
+
+d = 2
+sigma = 0.1
+n_cmc = 10**7
+S_0 = 100
+K = [90, 100, 110]
+mu = 0.08
+r = 0.05
+tau = 3/50
+T = 1
+
+L0, indicator_true, hockey_true, quadratic_true, CVaR = ComputeTrueLoss(n_front=n_cmc,
+                                                                                       d=d,
+                                                                                       S_0=S_0,
+                                                                                       K=K,
+                                                                                       mu=mu,
+                                                                                       sigma=sigma,
+                                                                                       r=r,
+                                                                                       tau=tau,
+                                                                                       T=T,
[…]

### 2025-03-24 pre_private/summarize.py

@@ -1,0 +1,32 @@
+import numpy as np
+
+import matplotlib.pyplot as plt
+
+
+methods = ["snsbs", "reg", "knn", "lr", "krr"]
+methods_name = ["Standard with Bootstrap", "Regression", "Kernel Smoothing", "Likelihood Ratio", "Kernel Ridge Regression"]
+Gammas = [1000, 2000, 4000, 8000, 16000, 32000]
+
+plt.figure(figsize=(8, 4.5))
+
+for method, name in zip(methods, methods_name):
+    data = np.load(f"./result_2_time_{method}.npy")
+
+    plt.loglog(Gammas, data, label=name, marker="o", linestyle="--")
+
+plt.legend(loc="upper left")
+plt.xlabel("Simulation Budget $\Gamma$")
+plt.ylabel("Time (s)")
+plt.title("European Call - d = 2")
+plt.savefig("time_comparison.png", dpi=300)
+
+
+
+
+
+
+
+
+
+
+

### 2025-03-24 pre_private/pre.tex
123

@@
 
-\setbeameroption{show notes}
-\setbeameroption{show notes on second screen=right}
+% \setbeameroption{show notes}
+% \setbeameroption{show notes on second screen=right}
 
@@
         \item   Source domain (50000 samples): GMMB with no lapse and GMMB with static lapse
-        \item   Target domain (2000 samples): GMMB with dynamic lapse
+        \item   Target domain (2000 samples): GMMB and GMWB with dynamic lapse 
     \end{itemize}
@@
     \note{This highlights the importance of selecting appropriate source models for transfer learning. \\}
-
-\end{frame}
-
-\begin{frame}{Learning Curves: Effect of Similarity}
-    \begin{columns}
-    \column{0.5\textwidth}
-    \includegraphics[height=0.48\textheight]{../project3/figures/figure3a.png}
-    \column{0.5\textwidth}
-    \includegraphics[height=0.48\textheight]{../project3/figures/figure3b.png}
-    \end{columns}
-
-    \textit{The effect of similarity between source and target on the convergence speed}
-    \begin{itemize}
-        \item \textit{Left: from No Lapse; right: from Static Lapse}
-    \end{itemize}
-
-    \note{These figures further illustrate how source-target similarity affects transfer learning performance. \\}
-    \note{The left graph shows transfer from no lapse models, which has slower convergence. \\}
-    \note{The right graph shows transfer from static lapse models, with faster convergence. \\}
-    \note{This reinforces our finding that greater similarity between source and target domains leads to more effective knowledge transfer. \\}
-\end{frame}
-
-    \begin{frame}{Learning Curves: Transfer Knowledge to other Contract Types}
-    \begin{figure}[ht]
-        \centering
-        \begin{subfigure}{0.48\textwidth}
-            \includegraphics[width=\textwidth]{../project3/figures/figure4a.png}
-            \caption{50000 samples}
-        \end{subfigure}
-        \begin{subfigure}{0.48\textwidth}
-            \includegraphics[width=\textwidth]{../project3/figures/figure4b.png}
-            \caption{2000 samples}
-        \end{subfigure}
-        \caption{Learning curves of GMWB contracts}
-    \end{figure}
-
-    \note{These graphs show learning curves for GMWB contracts with different training sample sizes. \\}
-    \note{Left figure (50,000 samples) shows that with abundant data, all methods eventually converge well. \\}
-    \note{Right figure (2,000 samples) demonstrates the advantage of transfer learning in data-limited scenarios. \\}
-    \note{With limited data, transfer learning methods significantly outperform training from scratch. \\}
-    \note{This is particularly relevant for new products or market conditions where historical data is scarce. \\}
+    \note{Note that for layer-freezing, freezing the LSTM layers lead to better performance. }
+
 \end{frame}
@@
         \begin{subfigure}{0.48\textwidth}
-            \includegraphics[width=\textwidth]{../project3/figures/figure4c.png}
-            \caption{Fine-tuning}
+            \includegraphics[width=\textwidth]{../project3/figures/figure2a.png}
         \end{subfigure}
         \begin{subfigure}{0.48\textwidth}
-            \includegraphics[width=\textwidth]{../project3/figures/figure4d.png}
-            \caption{Layer Freezing}
+            \includegraphics[width=\textwidth]{../project3/figures/figure2b.png}
         \end{subfigure}
-        \caption{Comparison of different TL methods on GMWB contracts}
+        \caption{Fine-tuning performance on GMMB with dynamic lapse}
     \end{figure}
 
-    \note{These figures compare fine-tuning vs. layer freezing approaches for GMWB contracts. \\}
-    \note{Fine-tuning (left) allows all network parameters to be updated during training. \\}
-    \note{Layer freezing (right) keeps early layers fixed and only updates later layers. \\}
+    \begin{itemize}
+        \item Similarity between source and target domain matters
+        \item Negative transfer can happen for dissimilar tasks
+    \end{itemize}
+
+    \note{These figures further illustrate how source-target similarity affects transfer learning performance. \\}
+    \note{The left graph shows transfer from no lapse models, which has slower convergence. \\}
+    \note{The right graph shows transfer from static lapse models, with faster convergence. \\}
+    \note{This reinforces our finding that greater similarity between source and target domains leads to more effective knowledge transfer. }
+
+\end{frame}
+
+\begin{frame}{Learning Curves: Effect of Freezing Layers}
+    \begin{figure}[ht]
+        \centering
+        \begin{subfigure}{0.48\textwidth}
+            \includegraphics[width=\textwidth]{../project3/figures/figure3a.png}
+            \caption{Freezing LSTM layers}
+        \end{subfigure}
+        \begin{subfigure}{0.48\textwidth}
+            \includegraphics[width=\textwidth]{../project3/figures/figure3b.png}
+            \caption{Freezing fully connected layers}
+        \end{subfigure}
+        \caption{Learning dynamic lapse from a GMMB with static lapse}
+    \end{figure}
+
+    \begin{itemize}
+        \item   When learning dynamic lapse, freezing the LSTM layers is suboptimal.
+        \item   Freezing the fully connected layers leads to better performance.
+    \end{itemize}
+
+    \note{These figures show the effect of freezing layers on the convergence of the model. \\}
+    \note{When learning dynamic lapse, freezing the LSTM layers leads to poor performance. \\}
+    \note{Freezing the fully connected layers is better since we are learning a dynamic lapse feature that introduces another source of stochasticity. \\}
+    \note{We suspect that the LSTM layers capture the time series component of the data, and the fully connected layers use the output of the LSTM layers to learn the VA contract losses.}
+
+\end{frame}
+
+\begin{frame}{Metamodel Performance}
+    \begin{figure}[ht]
+        \centering
+        \begin{subfigure}{0.48\textwidth}
+            \includegraphics[width=\textwidth]{../project3/figures/figure4_1.png}
+            \caption{Identifying tail scenarios}
+        \end{subfigure}
+        \begin{subfigure}{0.48\textwidth}
+            \includegraphics[width=\textwidth]{../project3/figures/figure4_2.png}
+            \caption{CVaR estimation}
+        \end{subfigure}
+        \caption{Comparison of different TL methods on transferring to GMWB contracts}
+    \end{figure}
+
+    \note{These figures examine the performance of transfer learning to GMWB contracts. \\}
+    \note{The source task is a GMMB, and the target task is a GMWB with dynamic lapse. \\}
     \note{For dissimilar contracts like GMMB to GMWB, fine-tuning generally performs better. \\}
     \note{This suggests that when transferring between different contract types, more flexibility in adaptation is beneficial. \\}
+    \note{When combined with a 2-stage procedure, we are able to reach reasonable performance for GMWB contracts with limited data. }
+
 \end{frame}
@@
 
+    \vspace{10pt}
+
+    \textbf{Future Work:}
+    \begin{itemize}
+        \item Incorporating domain knowledge into transfer process
+        \item Extension to other insurance and financial products
+        \item Multi-task learning
+    \end{itemize}
+
     \note{Our research demonstrates that transfer learning significantly enhances VA contract metamodeling. \\}
@@
     \note{This is particularly valuable in volatile markets where rapid decision-making is essential. \\}
-    \note{The approach bridges the gap between traditional actuarial methods and modern machine learning techniques. \\}
-
-    \textbf{Future Work:}
-    \begin{itemize}
-        \item Incorporating domain knowledge into transfer process
-        \item Extension to other insurance and financial products
-        \item Multi-task learning with more than two tasks
-    \end{itemize}
+    \note{The approach enables pooling on a higher level, that is, pooling across different contracts. \\}
 
@@
     \note{The approach could be extended to other insurance products and financial derivatives. \\}
-    \note{Multi-task learning could be expanded to handle more than two contract types simultaneously. \\}
-    \note{Integration with existing risk management systems would facilitate practical adoption. \\}
-    \note{Ultimately, these techniques could transform how financial institutions manage complex product portfolios. \\}
-
-\end{frame}
-
-\begin{frame}
+    \note{In the future, we can also consider multi-task learning to handle multiple contracts simultaneously. }
+
+\end{frame}
+
+\begin{frame}[t,allowframebreaks]
     \frametitle{References}
     \bibliographystyle{apa}
-    \bibliography{../refP1, ../refP2, ../refP3}
+    \nocite{*}
+    \bibliography{../ref_pre}
 \end{frame}

### 2025-04-02 pre_private/pre.tex
1

@@
 \note{The nested structure is due to the loss random variable being a conditional expectation of the portfolio loss given the underlying risk factors. \\}
-\note{In our problems, the loss $L$ depends on the risk factors $X$ and is the conditional expectation of the portfolio loss given the risk factors. \\}
-\note{More specifically, $X$ is $d$-dimensional and $L$ is 1-dimensional. \\}
+\note{In our problems, the 1-dimensional loss $L$ depends on the $d$-dimensional risk factors $X$. \\}
 \note{Estimating a risk measure, $\rho(L)$, involves two levels of Monte Carlo simulations: a outer level generates underlying risk factors, and a inner level generates scenario-wise samples of portfolio losses.
 \\}
-\note{The standard nested simulation procedure uses the inner sample mean under that scenarioto estimate $L(X_i)$. \\}
+\note{The standard nested simulation procedure uses the inner sample mean under that scenario to estimate $L(X_i)$. \\}
 \note{The nested structure makes the estimation computationally expensive. \\}
@@
 \note{Pooling can happen in different ways, and the key idea is to use the information from different outer scenarios to improve the efficiency of nested simulation. \\}
-\note{A supervised learning based nested simulation procedure pools with these steps. \\}
-\note{First, the user runs the standard nested simulation procedure to generate a set of outer scenarios and inner replications. \\}
-\note{Then, the outer scenarios and inner sample means can be treated as features and labels for metamodel training. \\}
-\note{Finally, instead of the inner sample mean from the standard procedure, the metamodel predictions estimate the portfolio loss and the risk measures. \\}
+\note{A supervised learning based procedure pools with these steps. \\}
+\note{First, the user runs the standard procedure to generate a set of outer scenarios and inner sample means. \\}
+\note{Then, they are treated as features and labels that train a metamodel. \\}
+\note{Instead of using the inner sample mean, risk measures are estimated with the metamodel predictions. \\}
 \note{Most existing works focus on the convergence rate of their estimators in terms of the simulation budget. \\}
@@
 \note{We start by comparing the asymptotic rates of different nested simulation procedures. \\}
-\note{These are the convergence rates of the MSE of the risk measure estimator when the total simulation budget $\Gamma$ goes to infinity. \\}
+\note{These are the convergence rates of the MSE when the total simulation budget $\Gamma$ goes to infinity. \\}
 \note{The standard procedure has the same convergence rate of $\mathcal{O}(\Gamma^{-2/3})$ for all types of $h$ considered.
@@
 \note{The kernel ridge regression procedure and likelihood ratio procedure have the same convergence rate as the regression-based procedure. \\}
-\note{However, in our numerical experiments, we find that their additional cost of pooling may offset their benefit of fast asymptotic rates. \\}
+\note{However, in our numerical experiments, we find that their additional cost of pooling is too high, which may offset their benefit of high asymptotic rates. \\}
 \note{Additionally for KRR, the authors analyze convergence of absolute error in probabilistic order instead of MSE.}
@@
 \note{In most theoretical works, the focus is on the convergence rate of the MSE of the risk measure estimator. \\}
-\note{However, for KRR, the authors analyze convergence of absolute error in probabilistic order. \\}
+\note{However, the analysis of KRR is different. \\}
 \note{One of the contributions of this thesis is to bridge the gap between MSE and absolute error convergence. \\}
 \note{We first define the convergence in MSE and the convergence in probabilistic order. \\}
-\note{And we show that the convergence rate of $\Gamma^{-\xi}$ in MSE of the risk measure estimator implies the convergence rate of $\Gamma^{-\frac{\xi}{2}}$ in probabilistic order. \\}
+\note{And we show that the convergence rate of $\Gamma^{-\xi}$ in MSE implies the convergence rate of $\Gamma^{-\frac{\xi}{2}}$ in probabilistic order. \\}
 \note{We also show that the converse is not necessarily true.}
@@
 \note{In practice, the total simulation budget is finite.}
-\note{When the budget is finite, the theoretical convergence rate may not be the only thing we should consider. \\}
+\note{When the budget is finite, these theoretical rates may not be the only thing we should consider. \\}
 \note{This figure shows the performance of all 5 procedures in their estimation of the quadratic tracking error for the portfolio of European call options.}
 \note{It is a log-log plot of the MSE of the estimator versus the total simulation budget $\Gamma$.}
-\note{For each procedure, we run 1000 macro replications of Monte Carlo simulations with different total simulation budgets. \\}
 \note{For each data point on the plot, 1000 independent replications of the procedure are used to estimate the MSE. \\}
 \note{The slopes of the lines estimates the empirical convergence rates of the procedures. \\}
-\note{In the legend records the slopes of the lines and the corresponding asymptotic convergence rates of the procedures. \\}
-\note{In the most basic case, most procedures have their empirical convergence rates match their asymptotic convergence rates. \\}
+\note{In the legend records the slopes of the lines and the corresponding asymptotic rates. \\}
+\note{In this case, most procedures have their empirical convergence rates matching their asymptotic rates. \\}
 \note{However, as we will see after, this is not the case for all experiments. }
@@
 
-\note{This figure shows the same experiment as the previous figure, but we further increase the asset dimension to 20. \\}
+\note{This figure shows the same experiment as the previous one, but we increase the asset dimension to 20. \\}
 \note{The standard procedure is not affected by the asset dimension. \\}
 \note{The kernel smoothing procedure actually converges faster than what its asymptotic convergence rate suggests. \\}
-\note{The regression-based procedure is the only procedure that actually converges faster when the asset dimension is high. We will do a deeper dive into it in the following experiment. \\}
-\note{It is also worth noting that the likelihood ratio and KRR procedures are dimension-independent. \\}
-\note{While it is not shown in their empirical rate, due to their additional cost of pooling inner replications, we are not able to run these procedures when $\Gamma$ is large. \\}
+\note{The regression-based procedure is the only procedure that converges faster when the asset dimension is high.
+The reason is the regression-based procedure is particularly bad when we don't have enough data points at low $\Gamma$.
+We did a follow-up experiment to show regression converges in its asymptotic rate at high $\Gamma$.
+\\}
+\note{Counter to what's on the graph, the likelihood ratio and KRR procedures are also sensitive to dimension. \\}
+\note{While it is not shown in their empirical rate, due to their additional cost of pooling, we are not able to run these procedures when $\Gamma$ is large. \\}
 \note{In the thesis, we provide a detailed analysis of the sensitivity for all 5 procedures with more than 500 experiments. }
@@
 
-\begin{frame}{Conclusion}
+\begin{frame}{Future Work}
     Regression-based nested simulation procedure:
@@
 
-    \note{In our numerical experiemenct, we have shown that the regression-based procedure is the most cost-effective among all the procedures. \\}
+    \note{Before here, we have shown that the regression-based procedure is the most cost-effective among all the procedures. \\}
     \note{It is robust and efficient to implement for limited budget sizes, and has fast empirical convergence for option portfolios. \\}
-    \note{However, the regression-based procedure is not suitable for extremely high-dimensional risk factors or complex payoffs. \\}
-    \note{The first reason is that it is hard to find a good regression basis for high-dimensional risk factors. It will involve a lot of feature engineering and expert knowledge. \\}
-    \note{The second reason is that the regression-based procedure is not able to capture the nonlinearity in the payoff. \\}
-    \note{In the next project, we will examine the performance of metamodel-based simulation procedures for variable annuities. \\}
+    \note{However, the it is not suitable for modeling variable annuities. \\}
+    \note{It is hard to find a good regression basis for high-dimensional risk factors. It will involve a lot of feature engineering and expert knowledge. \\}
+    \note{In the next project, we will design a metamodel-based simulation procedures for variable annuities. \\}
     \note{This is where a neural network-based procedure can be more suitable as a form of automated feature engineering. }
@@
     \note{All the simulation mentioned is a single set of inner simulations for one outer scenario. \\}
-    \note{It is very expensive to run this standard nested simulation for VAs. \\}
+    \note{It is more expensive to run the standard nested for VAs. \\}
 
@@
 
-\note{After numerical experiments, we find that the deep neural network metamodels are suitable for this problem. \\}
-\note{We use LSTM for the sequential data. It provides accurate tail scenario identification and significant computational savings by budget concentration. \\}
-\note{However, it is not transparent and interpretable. Many researchers are working on this topic. \\}
-\note{This is where we can contribute to the research. \\}
+\note{After some numerical experiments, we found that the deep neural network metamodels are suitable for this problem. \\}
+\note{We use LSTM for the sequential data. It can predict tail scenarios accurately, so we can use it to concentrate simulation budget on the tail scenarios. \\}
+\note{However, it is not transparent. Many researchers are working on this topic. \\}
+\note{This is where we can contribute to the field. \\}
 \note{By using nested simulation as a data generating process, we can study the noise tolerance of DNNs. \\}
-\note{The noise level in the training labels can be controlled by adjusting the simulation parameters. \\}
-\note{By examining the performance of DNNs with different noise levels, we can provide direct evidence on the transparency and interpretability of DNNs. \\}
+\note{We can control data quality and quantity by adjusting the simulation parameters. \\}
+\note{By examining the performance of DNNs, we can provide direct evidence on the transparency of DNNs. }
 
@@
 
-\note{The two-stage procedure is a two-step process that is based on the idea of budget concentration. \\}
-\note{First, we generate training data for the metamodel. \\}
-\note{We use a fraction of the simulation budget to run the standard nested simulation procedure with $M$ outer scenarios and $N'$ inner replications. \\}
-\note{We then train a metamodel using the feature-label pairs. \\}
-\note{We use the trained metamodel to make predictions for all outer scenarios. \\}
-\note{We then identify the predicted tail scenario set that contains the $m$ largest predicted losses. \\}
-\note{Finally, we run the standard nested simulation procedure on the predicted tail scenarios. \\}
+\note{Our two-stage procedure is based on the idea of budget concentration. \\}
+\note{In stage 1, we use a fraction of the simulation budget to run the standard nested simulation procedure. \\}
+\note{We then train a metamodel using the scenarios and the inner sample means. \\}
+\note{We use metamodel predictions to identify the tail scenario set that contains the $m$ largest predicted losses. \\}
+\note{In stage 2, we run the standard nested simulation procedure on these predicted tail scenarios. \\}
 
@@
 
-\note{The single-stage procedure shares the same idea of running the standard nested simulation procedure to generate training data for the metamodel. \\}
-\note{After a metamodel is trained, we use it to make predictions for VA contract losses accross all outer scenarios. \\}
-\note{The risk measure is estimated using the predicted losses of the metamodel. \\}
-\note{It is more efficient than the two-stage procedure because it avoids the second stage of the two-stage procedure. \\}
+    \note{In our experiments, we found some DNN metamodels that can make accurate loss predictions, so we propose a single-stage procedure. \\}
+    \note{It shares the same idea of running the standard nested to get training data. \\}
+    \note{After a metamodel is trained, the risk measure is estimated using the metamodel predictions directly. \\}
+    \note{It is more efficient than the two-stage procedure because it avoids the stage 2 of the two-stage procedure. \\}
     \note{It also avoids specifying a safety margin $m$, which is a feature of the two-stage procedure that we will discuss later.}
@@
     \note{Capacity is defined as the number of parameters in the metamodel. \\}
-    \note{Higher capacity metamodels are more flexible and expressive. \\}
     \note{Lower capacity metamodels are less likely to overfit. \\}
-    \note{The deep neural network metamodels are more flexible and expressive, but they are said to be more prone to overfitting. \\}
+    \note{The deep neural network metamodels are higher in capacity, but they are said to be more prone to overfitting. \\}
     \note{We will see whether this is indeed the case in our experiments. \\}
@@
     \note{Feature engineering for QPR is hardly feasible for our 240-dimensional $X$. Its poor performance is expected. \\}
-    \note{DNN metamodels are more flexible, and they can make more accurate loss predictions. \\}
+    \note{DNN metamodels are more flexible, and they can make more accurate predictions. \\}
 
@@
 \note{To further clarify our research questions, we consider the following scenario: \\}
-\note{We have a noisy training data and a noisy test data. \\}
+\note{We have noisy training data and noisy test data. \\}
 \note{We want to know what the metamodel learns from the noisy data. \\}
-\note{We also want to know how well the metamodel can make accurate loss predictions for given scenarios. \\}
-\note{In a simulation experiment, we can control the noise level in the training data and the test data. \\}
-\note{We also have access to the true feature-label relationship when we increase the number of replications. \\}
-\note{We can use this true feature-label relationship to evaluate the performance of deep neural networks, which is usually not possible in practice. }
+\note{We also want to know how well the metamodel can make accurate predictions. \\}
+\note{In a simulation experiment, we have control over the noise level in the training data and the test data. \\}
+\note{We also have access to the true relationship when we increase the number of replications. \\}
+\note{We can use this true relationship to evaluate the performance of deep neural networks, which is usually not possible in practice. \\ }
+\note{Instead of measuring the distance between the blue line and the orange dots, we can measure the distance between the blue line and the red line. }
 
@@
     \note{It is the most interesting finding that DNN metamodels with suitable architectures can \textbf{cut through the noise} in training labels. \\}
-    \note{The average MSEs of metamodels on the training, test, and true data are reported in the three columns, respectively. \\}
-    \note{Note that the training and test labels are noisy. The simulation noise is what makes them noisy, which is less present in the true data. \\}
+    \note{The average MSEs of metamodels on the training, test, and true data are reported in different colors. \\}
+    \note{Note that the training and test labels are noisy due to simulation noise. This noise is less present in the true labels. \\}
     \note{First, we note that DNN metamodels has lower training errors than the traditional regression metamodels. \\}
-    \note{This is expected because DNNs are more flexible and expressive than traditional regression metamodels. \\}
+    \note{This is expected because DNNs are more flexible. \\}
     \note{What is more interesting is the comparison between the test and true errors. \\}
@@
 
-    \note{For a two-stage procedure, we need to choose a safety margin $m$ to identify the tail scenarios. \\}
+    \note{Coming back to the two-stage procedure, we need to choose a safety margin $m$ to identify the tail scenarios. \\}
     \note{Consider estimating the $95\%$ CVaR with 100,000 outer scenarios. \\}
-    \note{On the top is the true tail and non-tail scenarios, and on the bottom is the predicted tail and non-tail scenarios. \\}
-    \note{The 5\% predicted tail scenarios are not guaranteed to contain all the true tail scenarios. \\}
-    \note{Therefore, we need to add a safety margin $m$ to the predicted tail scenarios. \\}
-    \note{On the bottom, we add a 2\% safety margin to the predicted tail scenarios. \\}
+    \note{On the top is the true tail and non-tail scenarios, and on the bottom is the predicted tail and non-tail. \\}
+    \note{The 5\% predicted tails are not guaranteed to contain all the true tails. \\}
+    \note{Therefore, we need to add a safety margin $m$. \\}
+    \note{On the bottom, we add a 2\% safety margin. \\}
     \note{This adds 2,000 more scenarios to the inner simulations. \\}
     \note{We may add another 2\% safety margin to be more confident. \\}
-    \note{This introduce a safety margin of $4\%$. $9000$ predicted tail scenarios are used for extensive inner simulations in stage 2. \\}
+    \note{This introduce a safety margin of $4\%$. In total, $9000$ predicted tails are used for extensive inner simulations in stage 2. \\}
     \note{This is a trade-off between accuracy and efficiency. \\}
-    \note{For a good metamodel, we only need a small safety margin to be accurate in tail identification. \\}
-    \note{However, for a bad metamodel, the safety margin needs to be large to identify all the tail scenarios. \\}
+    \note{For a regression metamodel, the safety margin needs to be large to identify all the tail scenarios. \\}
     \note{This comes at the cost of more inner simulations, which is computationally expensive. \\}
@@
 
-    \note{We now consider the tail scenario identification and the CVaR estimation for the two-stage procedure. \\}
-    \note{On the left is the tail scenario identification plot, and on the right is the plot of CVaR. \\}
+    \note{We now consider the precentage of tail match and the CVaR estimates for the two-stage procedure. \\}
+    \note{On the left is the tail match plot, and on the right is the plot for CVaR. \\}
     \note{We compare the two-stage procedure with the standard procedure. \\}
-    \note{When colored lines cross the grey dashed line, it means that the metamodel is able to identify the tail scenarios as well as the standard procedure. \\}
-    \note{And it should be able to estimate the CVaR as accurately as the standard procedure. \\}
+    \note{When colored lines cross the grey dashed line, it means that the metamodel is able to identify the true tails as well as the standard procedure. \\}
+    \note{And it should be able to estimate the CVaR as accurately. \\}
     \note{We find that the LSTM metamodel is able to surpass the standard procedure on tail identification with a less than $5\%$ safety margin. \\}
     \note{However, the traditional regression metamodel is unable to identify the tail scenarios even with a high safety margin. \\}
+    \note{They are not even in the first plot. \\}
     \note{A well-trained RNN is better than a FNN, but the poorly-trained RNN is far worse.}
-    \note{The CVaR estimation plot shows similar results.}
+    \note{The CVaR plot shows similar results.}
 
@@
     \note{We now dig deeper into the research questions asked: how well do deep learning metamodels learn from noisy data? \\}
-    \note{We study this phenomenon by considering the sensitivity testing for the DNN metamodels. \\}
-    \note{The sensitivity of the DNN metamodels to the noise level in training labels and the number of training samples. \\}
-    \note{In a simulation experiment, we can vary them to see how the DNN metamodels perform. \\}
-    \note{We control the noise level in training labels by varying the number of inner replications $N'$. \\}
-    \note{We control the number of training samples by varying the number of outer scenarios $M$. \\}
-    \note{We consider two LSTM metamodels of different capacities because we want to see if the capacity of the metamodel matters for overfitting. \\}
-    \note{The high-capacity LSTM metamodel has 10 times more parameters than the regular LSTM metamodel}
+    \note{We study this phenomenon by testing the sensitivity of the DNN metamodels to the noise level in training labels and the number of training samples. \\}
+    \note{In a simulation experiment, we have the flexibility to vary them. \\}
+    \note{Data quality is controlled by $N'$, and data quantity is controlled by $M$. \\}
+    \note{We consider two LSTM metamodels of different capacities. \\}
+    \note{The high-capacity LSTM has 10 times more parameters than the regular LSTM.}
 
@@
     \note{This figure shows the CVaR estimates of the single-stage procedure. \\}
-    \note{We compare it with the two-stage procedure using regular LSTM metamodel with no safety margin.
-So we are using the 5\% metamodel predicted tails to estimate the 95\% CVaR with extensive simulation in stage 2.
-\\}
+    \note{We compare it with the two-stage procedure using regular LSTM metamodel with no safety margin. So we are using the 5\% metamodel predicted tails to run extensive simulation in stage 2. \\}
     \note{The single-stage procedure with LSTM metamodels outperforms the two-stage procedure when noise level is moderate. \\}
@@
     \note{This finding is consistent with our previous analysis on the sensitivity of LSTM metamodels to data quality and data quantity. \\}
-    \note{Once the quality is good enough, the quantity is more important. \\}
-
-\end{frame}
-
-\begin{frame}{Conclusion}
-
-    \textbf{Key Findings:}
-    \begin{itemize}
-        \item   LSTMs are \textbf{resilient} to moderate levels of noise in training labels.
+    \note{Once the quality is good enough, the quantity is more important. }
+
+\end{frame}
+
+\begin{frame}{Future Directions}
+
+    \textbf{We have found that:}
+    \begin{itemize}
         \item   DNNs can learn \textbf{true} complex dynamic hedging model.
-        \item   Two-stage procedure addresses regulatory concerns.
-        \item   Single-stage procedure is \textbf{efficient}.
     \end{itemize}
@@
 
-    \note{In this project, we present our extensive research into LSTM metamodels in a simulation setting.\\}
-    \note{Our findings demonstrate that LSTMs can effectively learn complex hedging strategies even with noisy training data.\\}
-    \note{The single-stage procedure offers an excellent balance of efficiency and accuracy for practical applications.\\}
-    \note{We've shown that allocating computational budget to increase outer scenarios rather than inner simulations yields better results.\\}
-    \note{These insights provide valuable guidance for implementing machine learning in financial risk management.\\}
-    \note{For the research directions, we can apply deep neural network metamodels to other actuarial applications.\\}
-    \note{We can also apply transfer learning to speed up the training process for deep neural network metamodels.\\}
+    \note{In this project, we demonstrate that LSTMs can effectively learn complex hedging strategies even with noisy training data.\\}
+    \note{We can apply deep neural network metamodels to other actuarial products.\\}
+    \note{However, DNNs are data-hungry. We may not have enough time to simulate enough data for new products.\\}
+    \note{That's where transfer learning can help us to speed up the training process for contracts with not enough data.}
 
@@
     \note{The problem is the same as the previous project. We want to use deep neural network metamodels to approximate the complex simulation model that involves dynamic hedging.\\}
-    \note{The difference is that we want to use transfer learning to speed up the training process.\\}
+    \note{The difference is that we want to use transfer learning to speed up the training process when the amount of data is limited.\\}
     \note{This can be beneficial for the practical applications.\\}
     \note{Firstly, new VA contracts are continuously issued.\\}
-    \note{Secondly, market conditions are changing.\\}
-    \note{Thirdly, the computational budget is limited.\\}
-    \note{Transfer learning can help us to adapt to the new market conditions quickly and efficiently.\\}
-    \note{We can pre-train the deep neural network metamodel on a large dataset of VA contracts with abundant simulation data.\\}
-    \note{Then, we can fine-tune the metamodel on a smaller dataset of new VA contracts with limited data.\\}
-    \note{The data is often limited for new VA contracts as simulation is expensive to run.\\}
+    \note{Secondly, the computational budget is limited for simulation.\\}
+    \note{With transfer learning, we can pre-train the deep neural network metamodel on a large dataset of VA contracts with abundant simulation data.\\}
+    \note{Then, we can fine-tune the metamodel on new VA contracts with limited data.\\}
     \note{The shared features between VA contracts can be leveraged to speed up the training process.\\}
-    \note{We can also transfer the knowledge to other contract types.\\}
-    \note{When a new VA contract is issued, we can use transfer learning to adapt the metamodel to the new contract quickly.\\}
+    \note{We can also try transferring knowledge to other contract types.}
 
@@
     \note{In our context, the feature space includes risk factors from the outer simulation.\\}
-    \note{It is equipped with a probability distribution that describes the joint distribution of the risk factors.\\}
+    % \note{It is equipped with a probability distribution that describes the joint distribution of the risk factors.\\}
     \note{We don't know the exact joint distribution of the risk factors, but we can simulate outer scenarios from it using monte carlo simulation.\\}
     \note{The task consists of a label space and a predictive function mapping features to labels.\\}
-    \note{For VA contracts, our labels are the contract losses under different scenarios.\\}
-    \note{The source domain typically has abundant data - this could be existing VA contracts with extensive simulation data.\\}
-    \note{The target domain has limited data - new VA contracts or existing contracts under new market conditions.\\}
-    \note{Our goal is to leverage knowledge from the source domain to improve prediction in the target domain.\\}
+    \note{For a VA dynamic hedging problem, our labels are the contract losses for different scenarios.\\}
+    \note{The source domain typically has abundant data - this could be existing VA contracts with extensive simulation done already.\\}
+    \note{The target domain, new VA contracts may have limited data.\\}
+    \note{Our goal is to leverage knowledge from the source domain to improve performance in the target domain.\\}
     \note{This is particularly valuable when simulation data is expensive to generate for new contracts.\\}
-    \note{The transfer learning approach allows us to maintain accuracy while significantly reducing computational requirements.}
+    \note{It allows us to maintain accuracy while significantly reducing computational requirements.}
 
@@
 
+    \note{There are several ways to transfer knowledge.}
     \note{Fine-tuning involves using a pre-trained model as a starting point for a new task.\\}
@@
     \note{The experiments are designed to evaluate how similarity between source and target affects transfer efficiency. \\}
-    \note{This is another attempt to use simulation models as data generating processes to examine deep neural networks. \\}
-    \note{By examining the transfer learning performance, we can gain insights into which parts of the neural network are transferable, or more generally, which layers of the neural network learn which features of the VA contracts.
-}
+    \note{This is another attempt to use simulation as data generating processes to examine deep neural networks. \\}
+    \note{By examining the transfer learning performance, we can gain insights into which parts of the neural network are transferable.\\}
+    \note{Or more generally, which layers of the neural network learn which features of the VA contracts. }
 
@@
     \note{This table summarizes the MSE values for different training methods. \\}
-    \note{Extensive training with full data achieves the best performance (0.0587 MSE). \\}
-    \note{Without transfer learning, training from scratch on dynamic lapse data yields mediocre results (0.2950 MSE). \\}
-    \note{Transfer learning from static lapse models (both fine-tuning and layer freezing) performs well. \\}
-    \note{Transfer from no lapse models performs poorly, demonstrating that negative transfer can occur. \\}
+    \note{Extensive training with full data achieves the best performance. \\}
+    \note{Without transfer learning, training from scratch on dynamic lapse data yields mediocre results. \\}
+    \note{Transfer learning from static lapse models performs well. \\}
+    \note{Transfer from no lapse models performs poorly. It demonstrates that negative transfer can occur. \\}
     \note{Negative transfer happens when source and target tasks are substantially different. \\}
     \note{In such cases, knowledge from the source model can actually hinder learning on the target task. \\}
-    \note{This highlights the importance of selecting appropriate source models for transfer learning. \\}
-    \note{Note that for layer-freezing, freezing the LSTM layers lead to better performance. }
+    \note{This highlights the importance of selecting appropriate source models for transfer learning. }
 
@@
         \begin{subfigure}{0.48\textwidth}
-            \includegraphics[width=\textwidth]{../project3/figures/figure2a.png}
+            \includegraphics[width=\textwidth]{./figure2a.png}
+            \caption{From no lapse}
         \end{subfigure}
         \begin{subfigure}{0.48\textwidth}
-            \includegraphics[width=\textwidth]{../project3/figures/figure2b.png}
+            \includegraphics[width=\textwidth]{./figure2b.png}
+            \caption{From static lapse}
         \end{subfigure}
@@
 
-    \note{These figures further illustrate how source-target similarity affects transfer learning performance. \\}
+    \note{These figures further illustrate the same idea. \\}
     \note{The left graph shows transfer from no lapse models, which has slower convergence. \\}
@@
         \begin{subfigure}{0.48\textwidth}
-            \includegraphics[width=\textwidth]{../project3/figures/figure3a.png}
+            \includegraphics[width=\textwidth]{./figure3a.png}
             \caption{Freezing LSTM layers}
@@
         \begin{subfigure}{0.48\textwidth}
-            \includegraphics[width=\textwidth]{../project3/figures/figure3b.png}
+            \includegraphics[width=\textwidth]{./figure3b.png}
             \caption{Freezing fully connected layers}
@@
     \note{Freezing the fully connected layers is better since we are learning a dynamic lapse feature that introduces another source of stochasticity. \\}
-    \note{We suspect that the LSTM layers capture the time series component of the data, and the fully connected layers use the output of the LSTM layers to learn the VA contract losses.}
+    \note{This counters the previous assumption that the early layers learn general features and should be freezed. \\}
+    \note{We suspect that the LSTM layers capture the time series component of the data, and the fully connected layers learn to model contract losses. \\}
+    \note{When new source of stochasticity is introduced, the LSTM layers are not able to capture it. \\}
+    \note{But static lapse and dynamic lapse, they are essentially the same contract with different lapse rates. \\}
+    \note{Also, I want to mention when transferring from no lapse to static lapse, freezing the LSTM layers is better.}
 
@@
 
-    \note{These figures examine the performance of transfer learning to GMWB contracts. \\}
-    \note{The source task is a GMMB, and the target task is a GMWB with dynamic lapse. \\}
+    \note{These figures examine the performance of transfer learning from GMMB to GMWB contracts. \\}
+    \note{The source task is a GMMB, and the target task is a GMWB. Both with dynamic lapse. \\}
     \note{For dissimilar contracts like GMMB to GMWB, fine-tuning generally performs better. \\}
@@
 \begin{frame}{Conclusions}
-    \begin{itemize}
-        \item Transfer learning significantly improves metamodeling for VA contracts:
-        \begin{itemize}
-            \item Faster training convergence
-            \item Better prediction accuracy
-            \item Reduced computational requirements
-        \end{itemize}
-        \item Enables more frequent risk assessments and faster decision-making
+
+    We study supervised learning models with simulation data.
+
+    \begin{itemize}
+        \item   Additional cost of pooling may overweight benefits.
+        \item   DNNs cut through the simulation noise.
+        \item   Data quantity is more important once quality is good enough.
+        \item   Transferable features in different layers.
     \end{itemize}
@@
     \begin{itemize}
-        \item Incorporating domain knowledge into transfer process
-        \item Extension to other insurance and financial products
-        \item Multi-task learning
-    \end{itemize}
-
-    \note{Our research demonstrates that transfer learning significantly enhances VA contract metamodeling. \\}
-    \note{The benefits include faster convergence, better accuracy with limited data, and reduced computational needs. \\}
-    \note{These improvements enable more frequent and timely risk assessments. \\}
-    \note{This is particularly valuable in volatile markets where rapid decision-making is essential. \\}
-    \note{The approach enables pooling on a higher level, that is, pooling across different contracts. \\}
-
-    \note{Several promising directions exist for extending this research. \\}
-    \note{Incorporating actuarial domain knowledge could further improve transfer learning effectiveness. \\}
-    \note{The approach could be extended to other insurance products and financial derivatives. \\}
-    \note{In the future, we can also consider multi-task learning to handle multiple contracts simultaneously. }
+        \item Examine other types of DNNs.
+        \item Try multi-task learning.
+    \end{itemize}
+
+    \note{Our study of supervised learning models with simulation data revealed several key insights. \\}
+    \note{We found that while pooling data can be beneficial, the additional computational costs may sometimes outweigh the advantages. \\}
+    \note{Deep neural networks demonstrated remarkable ability to cut through the simulation noise. \\}
+    \note{Our results suggest that once data quality reaches a certain threshold, increasing quantity becomes more beneficial. \\}
+    \note{We also identified that different neural network layers contain different features that can be transferred between contract types. \\}
+    \note{For future work, we plan to explore other types of DNN architectures in other actuarial applications. \\}
+    \note{We also aim to implement multi-task learning approaches to simultaneously model multiple similar actuarial products. \\}
 

### 2025-04-08 project1/nsSurvey.tex
w

@@
 The nested simulation procedure is computationally expensive due to its nested structure. 
-Given a fixed computational budget, the nested simulation procedure should balance the number of outer scenarios and the number of inner replications to maximize computational efficiency.
+Given a fixed computational budget, the nestzed simulation procedure should balance the number of outer scenarios and the number of inner replications to maximize computational efficiency.
 \cite{gordy2010nested} first analyzed and proposed an optimal budget allocation for a standard nested simulation procedure.
@@
 The MLMC method is particularly useful when the quantity of interest is expensive to evaluate, and the standard MC estimator has a high variance.
-The MLMC method estimates $\rho$ with an MLMC estimator:
+\textcolor{red}{For the nested expectation form $\rho = \mathbb{E}[h(L)]$, the MLMC method selects an approximation level $L$ with sufficient accuracy, and it uses the difference between the approximations to reduce the variance of the estimator.}
+\textcolor{red}{\sout{The MLMC method estimates $\rho$ with an MLMC estimator:}}
 
@@
 Numerical experiments are conducted on portfolios that consist of options on $d$ underlying assets, whose dynamics follow a multidimensional geometric Brownian motion with $0.3$ pairwise correlation.
+\textcolor{red}{The initial values of the assets are set to be $100$.}
+\textcolor{red}{The drifts are set to be $0.08$, and the risk free rate is set to be $0.05$.}
 
@@
 Except for Portfolio 5, 5 different asset dimensions are considered, i.e., $d = 1, 2, 5, 10, 20$.
+\textcolor{red}{All options have a maturity of $1$ year, and we are interested in the value of the portfolio at time $3/50$ year from now.}
 525 experiment settings that arise from an exhaustive combination of the above simulation procedures, risk measures, portfolios, and asset dimensions are generated.
@@
 The empirical convergence results of each estimator are measured and recorded to illustrate their empirical behavior under different risk measures, option types, and asset dimensions.
+\textcolor{red}{All numerical experiments are conducted on a linux server with four Intel Xeon Gold 6230 20-core 2.1 GHz CPU with 768 GB RAM.}
+
 We start by examining the empirical convergence results for the most basic case, i.e., a quadratic tracking error risk measure for European call options on Portfolio 1 with $d = 1$.
@@
 The theoretical analysis in~\cite{giles2019multilevel} shows that the MLMC procedure has a faster empirical rate of convergence than the standard nested simulation procedure when the risk measure of interest is the probability of a large loss over a threshold $u$, i.e., the nested expectation case with $h$ being an indicator function.
+\textcolor{red}{In this numerical experiment, the initial number of inner replications, the refinement factor, the r-value for adaptive algorithm are set to be $4$, $4$, and $1.5$, respectively.}
+\textcolor{red}{We note that the MLMC procedure focuses on adaptive allocation of the simulation budget and is fundamentally different from supervised learning-based nested simulation procedures.
+And their results are not directly comparable.}
 

### 2025-04-13 conclusion.tex
1
11

@@
 
-In this thesis, we have explored the application of nested simulation procedures in the risk management of financial derivatives and insurance products, with a particular focus on variable annuity contracts featuring Guaranteed Minimum Maturity Benefits and Guaranteed Minimum Withdrawal Benefits.
+In this thesis, we have explored the application of nested simulation procedures in the risk management of financial derivatives and insurance products, with a particular focus on variable annuity contracts featuring \gls{gmmb} and \gls{gmwb}.
 Recognizing the computational challenges inherent in the standard nested simulation procedure, especially when estimating tail risk measures for complex financial products, we have proposed an innovative approach that integrates machine learning-based metamodels into the nested simulation framework.
 
-We have shown that the nested simulation framework can be used to efficiently estimate risk measures of complex financial products, such as variable annuities, by combining machine learning-based metamodels with nested simulations.
+We have shown that the nested simulation framework can be used to efficiently estimate risk measures of complex financial products, such as \gls{va}s, by combining machine learning-based metamodels with nested simulations.
 
-Our primary contribution lies in the development and implementation of long short-term memory networks as metamodels for the inner simulations within the nested simulation procedure. 
-By employing LSTMs, we have effectively approximated the contract losses associated with dynamic hedging strategies under various market scenarios. 
+Our primary contribution lies in the development and implementation of \gls{lstm}s as metamodels for the inner simulations within the nested simulation procedure. 
+By employing \gls{lstm}s, we have effectively approximated the contract losses associated with dynamic hedging strategies under various market scenarios. 
 This approach has substantially reduced the computational complexity of the standard nested simulation procedure while maintaining high levels of accuracy in risk estimation. 
-The LSTM metamodels have captured the temporal dependencies and nonlinear relationships present in financial time series data, enabling efficient estimation of tail risk measures.
+The \gls{lstm} metamodels have captured the temporal dependencies and nonlinear relationships present in financial time series data, enabling efficient estimation of tail risk measures.
 
-Through extensive numerical experiments and sensitivity analysis, we have demonstrated that our LSTM-based nested simulation procedure provides accurate and computationally efficient estimates of the tail risk associated with VA contracts.
+Through extensive numerical experiments and sensitivity analysis, we have demonstrated that our \gls{lstm}-based nested simulation procedure provides accurate and computationally efficient estimates of the tail risk associated with \gls{va} contracts.
 The results have shown that the metamodels can effectively replace the computationally intensive inner simulations in the standard nested simulation procedure.
@@
 
-Additionally, we have investigated the feasibility of our approach under changing market conditions and different VA contract features. 
-By incorporating transfer learning techniques, we have enabled rapid adaptation of the LSTM metamodels to new contracts and evolving market dynamics. 
+Additionally, we have investigated the feasibility of our approach under changing market conditions and different \gls{va} contract features. 
+By incorporating \gls{tl} techniques, we have enabled rapid adaptation of the \gls{lstm} metamodels to new contracts and evolving market dynamics. 
 This aspect of our research highlights the potential for machine learning models to not only improve computational efficiency but also enhance the flexibility and responsiveness of risk management practices in the face of market volatility.

### 2025-04-13 futureWork/rlHedging.tex
11

@@
 Managing the risks associated with these products, especially in volatile market conditions, is a complex task that demands sophisticated financial modeling techniques. 
-Reinforcement Learning (RL) has emerged as a powerful tool for addressing such complexities.
-With the recent advancement in deep learning, DNN architectures have been successfully applied to RL problems, leading to the development of deep reinforcement learning (DRL) algorithms.
+\gls{rl} has emerged as a powerful tool for addressing such complexities.
+With the recent advancement in deep learning, \gls{dnn} architectures have been successfully applied to \gls{rl} problems, leading to the development of deep reinforcement learning (\gls{drl}) algorithms.
 These algorithms have demonstrated remarkable success decision-making tasks that must be optimized over time. 
-In the context of managing VAs, DRL has shown promise in optimizing hedging strategies where long-term financial and policyholder decisions interact dynamically with changing market conditions.
+In the context of managing VAs, \gls{drl} has shown promise in optimizing hedging strategies where long-term financial and policyholder decisions interact dynamically with changing market conditions.
 
@@
 Through trial and error, the agent receives feedback in the form of rewards or penalties, allowing it to learn an optimal policy for achieving long-term goals. 
-In financial and actuarial contexts, RL has been applied to portfolio optimization, asset allocation, and risk management. 
+In financial and actuarial contexts, \gls{rl} has been applied to portfolio optimization, asset allocation, and risk management. 
 In a dynamic hedging problem, the agent is referred to as the decision-maker that tries to minimize financial risks over time horizon by adjusting the hedging portfolio based on the current environment, which is the current state of the financial markets and actuarial assumptions.
-By integrating deep neural network, DRL extends this framework by enabling the agent to handle high-dimensional and complex environments. 
-DRL has shown particular promise in finance because of its ability to process vast amounts of financial data and discover intricate patterns in market dynamics.
-Despite their success, DRL faces practical limitations when applied to real-world financial markets.
+By integrating deep neural network, \gls{drl} extends this framework by enabling the agent to handle high-dimensional and complex environments. 
+\gls{drl} has shown particular promise in finance because of its ability to process vast amounts of financial data and discover intricate patterns in market dynamics.
+Despite their success, \gls{drl} faces practical limitations when applied to real-world financial markets.
 Its most significant drawback is the requirement for extensive data and computational resources.
-Training a DRL agent from the scratch requires a large dataset along with considerable computational time for the purpose of exploration and learning.
-This is especially problematic for VA contracts, which are long-term insurance products that are sensitive to market fluctuations and underlying actuarial assumptions.
+Training a \gls{drl} agent from the scratch requires a large dataset along with considerable computational time for the purpose of exploration and learning.
+This is especially problematic for \gls{va} contracts, which are long-term insurance products that are sensitive to market fluctuations and underlying actuarial assumptions.
 Given that financial markets are highly dynamic, a frequent retraining to account for new market regimes becomes necessary, which can lead to prohibitively high costs and computational inefficiency.
@@
 
-TL offers a compelling solution to the challenges posed by existing DRL approaches. 
-Similar to the TL framework proposed in Chapter~\ref{chap:project3}, TL can also be applied to DRL to accelerate the training.
-In the context of financial modeling, instead of training an RL agent from the scratch every time underlying assumptions change, the model can utilize the knowledge gained from past market environments to accelerate the learning process under the new environment.
-TL in financial markets is particularly advantageous for addressing the data scarcity problem. 
-By transferring existing knowledge from similar environments, TL improves model performance in situations where historical data is limited or noisy. 
-This allows models using TL to be both more accurate and computationally efficient. 
-Additionally, TL enhances the robustness of models by allowing continuous learning. 
-Instead of retraining a deep RL model from the scratch when market conditions shift, TL enables the reuse of pre-trained models, facilitating a faster adaptation to new environments while avoiding overfitting to past conditions.
-In the risk management of VA contracts, transfer learning enables quicker adaptation to changing financial and actuarial assumptions by reusing information obtained from another set of related assumptions, such as the management of similar financial instruments or different market regimes.
-A DRL agent equipped with transfer learning can adjust its strategies in response to new market data, making the model more adaptive and responsive without the need for costly retraining.
-More specifically, a DRL agent trained to manage VA contracts for a GMMB contract can apply its learned strategies to a GMWB contract with the same financial assumptions. 
-A DRL agent trained for a VA product on a Black-Scholes asset model can transfer its knowledge to the training of a similar product on a stochastic volatility model.
-This approach substantially reduces the computational costs associated with the training of new VA products with different assumptions and improves the generalization of the model to unseen market conditions.
-By integrating the transfer learning with the existing DRL frameworks, we can eliminate the inefficiencies of training models from scratch, provide faster adaptability to new market conditions, and enhance the scalability and computational efficiency of financial models.
-This approach offers a more robust and practical solution for managing VA contracts in dynamic and volatile financial markets.
+\gls{tl} offers a compelling solution to the challenges posed by existing \gls{drl} approaches. 
+Similar to the \gls{tl} framework proposed in Chapter~\ref{chap:project3}, \gls{tl} can also be applied to \gls{drl} to accelerate the training.
+In the context of financial modeling, instead of training an \gls{rl} agent from the scratch every time underlying assumptions change, the model can utilize the knowledge gained from past market environments to accelerate the learning process under the new environment.
+\gls{tl} in financial markets is particularly advantageous for addressing the data scarcity problem. 
+By transferring existing knowledge from similar environments, \gls{tl} improves model performance in situations where historical data is limited or noisy. 
+This allows models using \gls{tl} to be both more accurate and computationally efficient. 
+Additionally, \gls{tl} enhances the robustness of models by allowing continuous learning. 
+Instead of retraining a deep \gls{rl} model from the scratch when market conditions shift, \gls{tl} enables the reuse of pre-trained models, facilitating a faster adaptation to new environments while avoiding overfitting to past conditions.
+In the risk management of \gls{va} contracts, transfer learning enables quicker adaptation to changing financial and actuarial assumptions by reusing information obtained from another set of related assumptions, such as the management of similar financial instruments or different market regimes.
+A \gls{drl} agent equipped with transfer learning can adjust its strategies in response to new market data, making the model more adaptive and responsive without the need for costly retraining.
+More specifically, a \gls{drl} agent trained to manage \gls{va} contracts for a \gls{gmmb} contract can apply its learned strategies to a \gls{gmwb} contract with the same financial assumptions. 
+A \gls{drl} agent trained for a \gls{va} product on a Black-Scholes asset model can transfer its knowledge to the training of a similar product on a stochastic volatility model.
+This approach substantially reduces the computational costs associated with the training of new \gls{va} products with different assumptions and improves the generalization of the model to unseen market conditions.
+By integrating the transfer learning with the existing \gls{drl} frameworks, we can eliminate the inefficiencies of training models from scratch, provide faster adaptability to new market conditions, and enhance the scalability and computational efficiency of financial models.
+This approach offers a more robust and practical solution for managing \gls{va} contracts in dynamic and volatile financial markets.
 
@@
 Section~\ref{sec:MDP} introduces the mathematical formulation for hedging VAs and defines the key components of the framework.
-Section~\ref{sec:RLAlgorithms} provides an overview of existing RL algorithms and their limitations in the context of hedging VAs.
+Section~\ref{sec:RLAlgorithms} provides an overview of existing \gls{rl} algorithms and their limitations in the context of hedging VAs.
 Section~\ref{sec:PPO} introduces the proximal policy optimization algorithm and its application to the hedging of VAs.
@@
 
-A Markov Decision Process (MDP) provides a mathematical framework for modeling decision-making in stochastic environments over time. 
-By formulating the VA hedging problem as an MDP, we can utilize RLalgorithms to learn optimal hedging policies directly from data.
-An MDP is defined by the tuple $\mathcal{M} = (\mathcal{S}, \mathcal{A}, \mathcal{P}, \mathcal{R}, \gamma)$, where:
+A \gls{mdp} provides a mathematical framework for modeling decision-making in stochastic environments over time. 
+By formulating the \gls{va} hedging problem as an \gls{mdp}, we can utilize RLalgorithms to learn optimal hedging policies directly from data.
+An \gls{mdp} is defined by the tuple $\mathcal{M} = (\mathcal{S}, \mathcal{A}, \mathcal{P}, \mathcal{R}, \gamma)$, where:
 
@@
 
-The objective in an MDP is to find a policy, $\pi: \mathcal{S} \rightarrow \mathbb{P}(\mathcal{A})$, that maximizes the cumulative reward over time.
-A MDP provides a mathematical framework for solving sequential decision-making tasks in an enviornment where outcomes are partly random and partly under the control of a hedging agent. 
+The objective in an \gls{mdp} is to find a policy, $\pi: \mathcal{S} \rightarrow \mathbb{P}(\mathcal{A})$, that maximizes the cumulative reward over time.
+A \gls{mdp} provides a mathematical framework for solving sequential decision-making tasks in an enviornment where outcomes are partly random and partly under the control of a hedging agent. 
 For hedging VAs, the asset dynamics and the mortality model are not controlled by the agent, but the agent controls the cumulative reward by deciding on the hedging weights.
-In this section, we reformulate the hedging enviornment of VAs from Section~\ref{subsec:VApayout} as an MDP and define the key components of the MDP.
+In this section, we reformulate the hedging enviornment of VAs from Section~\ref{subsec:VApayout} as an \gls{mdp} and define the key components of the \gls{mdp}.
 
@@
 
-Consider a generic VA contract with maturity $T>0$ periods, e.g., $T=240$ months.
+Consider a generic \gls{va} contract with maturity $T>0$ periods, e.g., $T=240$ months.
 Then the contract expires at $T'=\min\{T,\tau\}$, i.e., the earlier of the contract maturity and the death of the policyholder.
 Let $S_t$, $F_t$, and $G_t$ be the indexed stock price, the subaccount value and the guarantee value, respectively, at time $t=1,2,\ldots,T$.
-Evolution of the subaccount value and the guarantee value of a VA contract affect the contract payout.
+Evolution of the subaccount value and the guarantee value of a \gls{va} contract affect the contract payout.
 For clarity, we use $F_t$ and $F_{t_+}$ to denote the sub-account value just before and just after the withdrawal at time $t$, if any.
@@
 
-    \item The guarantee value ratchets up (ratcheting is a common feature in GMWB) if the sub-account value exceeds the previous guarantee value, i.e., 
+    \item The guarantee value ratchets up (ratcheting is a common feature in \gls{gmwb}) if the sub-account value exceeds the previous guarantee value, i.e., 
         \begin{equation} \label{eq3:guarantee}
@@
         \end{equation} 
-    A GMMB can be modeled with $G_t = G_{t-1}\cdot(1-q_t)$.
+    A \gls{gmmb} can be modeled with $G_t = G_{t-1}\cdot(1-q_t)$.
 
-    \item The withdrawal is made (for GMWB) and is deducted from the sub-account value, i.e., 
+    \item The withdrawal is made (for \gls{gmwb}) and is deducted from the sub-account value, i.e., 
         \begin{equation} \label{eq3:withdrawal}
@@
         \end{equation} 
-    where $I_t = \xi G_t$. A GMMB can be modeled with $\xi = 0$.
+    where $I_t = \xi G_t$. A \gls{gmmb} can be modeled with $\xi = 0$.
 \end{enumerate}
 
-Consider a VA contract whose delta hedge portfolio at any time~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at time $T$.
+Consider a \gls{va} contract whose delta hedge portfolio at any time~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at time $T$.
 The value of the hedge portfolio at time~$(t-1)$ is:
@@
 \end{equation}
-The P\&L of the VA contract includes the cost of the initial hedge ($H_0$), the hedging errors~\eqref{eq2:hedgingerror}, the unwinding of the hedge at maturity ($H^{bf}_T$), and the contract payout at time~$t\in \{0,\ldots,T\}$.
-Mathematically, the present value of the liability for a GMMB contract is 
+The P\&L of the \gls{va} contract includes the cost of the initial hedge ($H_0$), the hedging errors~\eqref{eq2:hedgingerror}, the unwinding of the hedge at maturity ($H^{bf}_T$), and the contract payout at time~$t\in \{0,\ldots,T\}$.
+Mathematically, the present value of the liability for a \gls{gmmb} contract is 
 \begin{align} \label{eq3:lossGMMB}
@@
 Hence, the present liability consist of the hedging errors, the transaction costs, the net management fees, and the contract payouts.
-Similarly, the present value of the liability for a GMWB contract is
+Similarly, the present value of the liability for a \gls{gmwb} contract is
 \begin{equation} \label{eq3:lossGMWB}
@@
 \end{equation}
-The GMWB payout is implicitly included in $F_t\eta_n$.
+The \gls{gmwb} payout is implicitly included in $F_t\eta_n$.
 Both Equation~\eqref{eq3:lossGMMB} and Equation~\eqref{eq3:lossGMWB} neglect the transaction cost to liquidate the hedge portfolio at maturity.
-The discrete-time hedging problem of VAs can be conveniently formulated as an MDP, where the states, actions, transition probabilities, policies, and rewards are defined as follows.
+The discrete-time hedging problem of VAs can be conveniently formulated as an \gls{mdp}, where the states, actions, transition probabilities, policies, and rewards are defined as follows.
 
@@
 The state space $\mathcal{S}$ represents all the information needed to characterize the hedging environment.
-In a VA hedging problem, $\mathbf{s}_t$, the information available to a hedging agent at each time $t$ is 
+In a \gls{va} hedging problem, $\mathbf{s}_t$, the information available to a hedging agent at each time $t$ is 
 $$\mathbf{s}_t := (S_t, F_t, G_t, \tau, \Delta_{t-1}) \in \mathcal{S}.$$
@@
 The action space $\mathcal{A}$ represents the set of actions that the agent can take at each time $t$.
-In a VA hedging problem, the action space only includes the hedging weight $\Delta_t$.
+In a \gls{va} hedging problem, the action space only includes the hedging weight $\Delta_t$.
 
@@
 $$a_t \sim \pi(\cdot|\mathbf{s}_t).$$
-In a VA hedging problem the policy outputs the hedging weight $a_t = \Delta_t$ given the observed state $\mathbf{s}_t$.
+In a \gls{va} hedging problem the policy outputs the hedging weight $a_t = \Delta_t$ given the observed state $\mathbf{s}_t$.
 In the following sections, we will refer to $\Delta_t$ as the policy.
@@
 Aside from the previous hedging weight $\Delta_{t-1}$, the transition probabilities are independent from the actions.
-Paths simulated from the transition probabilities are called trajectories (or episodes) of the MDP.
+Paths simulated from the transition probabilities are called trajectories (or episodes) of the \gls{mdp}.
 
 \subsection{Reward and Discount Factor}
-The reward function $\mathcal{R}$ and discount factor $\gamma$ in a typical RL problem are defined as follows:
+The reward function $\mathcal{R}$ and discount factor $\gamma$ in a typical \gls{rl} problem are defined as follows:
 \begin{align}
@@
 In hedging, the term reward $R_t$ should be derived from Equation~\eqref{eq3:lossGMMB} and Equation~\eqref{eq3:lossGMWB} to represent the performance of the hedging policy, i.e., how closely the hedging portfolio tracks the liability.
-For the GMWB, we propose a term reward formulation that encourages the agent to maximize the expected reward with low hedging errors and transaction costs:
+For the \gls{gmwb}, we propose a term reward formulation that encourages the agent to maximize the expected reward with low hedging errors and transaction costs:
 \begin{equation} \label{eq3:rewardGMWB}
@@
 \end{equation}
-The reward function of the GMWB directly links to the time-$t$ loss of a GMWB contract as in Equation~\eqref{eq3:lossGMWB}.
-The GMMB loss consists of an additional payoff at maturity $T$, thus its term reward is formulated as:
+The reward function of the \gls{gmwb} directly links to the time-$t$ loss of a \gls{gmwb} contract as in Equation~\eqref{eq3:lossGMWB}.
+The \gls{gmmb} loss consists of an additional payoff at maturity $T$, thus its term reward is formulated as:
 \begin{equation} \label{eq3:rewardGMMB}
@@
 
-This section introduces some critical concepts in RL, i.e., the value function and the advantage function.
-They are essential for understanding the performance of the hedging policy and the learning process of the RL agent.
+This section introduces some critical concepts in \gls{rl}, i.e., the value function and the advantage function.
+They are essential for understanding the performance of the hedging policy and the learning process of the \gls{rl} agent.
 
@@
 Deep reinforcement learning first attacted attentions when AlphaGo~\citep{silver2016mastering} surpasses human in playing Go. 
-Soon after, AlphaZero~\citep{silver2016mastering} emerged as a model-based RL algorithm that improves over self-plays.
+Soon after, AlphaZero~\citep{silver2016mastering} emerged as a model-based \gls{rl} algorithm that improves over self-plays.
 It quickly extended beyond Go to other games like Chess and Shogi.
@@
 It stores a global solution that predicts the outcome of the game and the next move before they are actually observed.
-This is known as model-based RL~\citep{sutton2018reinforcement}.
+This is known as model-based \gls{rl}~\citep{sutton2018reinforcement}.
 Using a model allows for planning, i.e., decision-making take place using future situations that have not been experienced by the agent.
@@
 Consequently, the learned policy is inherently tailored to the characteristics of the model used in the simulations.
-The ability to know the future outcomes of the hedging policy before they are actually observed and the use of a risk measure to guide the training of the neural network are the key features of model-based RL.
+The ability to know the future outcomes of the hedging policy before they are actually observed and the use of a risk measure to guide the training of the neural network are the key features of model-based \gls{rl}.
 These models describe how asset prices evolve over time, and more importantly, they are used to predict future states based on current information.
@@
 
-For hedging VAs,~\cite{xu2020variable} propose a deep hedging algorithm that falls into this category of model-based RL.
+For hedging VAs,~\cite{xu2020variable} propose a deep hedging algorithm that falls into this category of model-based \gls{rl}.
 A cost function is defined to minimize the expected shortfall of the total present liability.
 ~\cite{carbonneau2021deep} extends the model-based approach to hedging long-term financial derivatives and compares the performance of deep hedging strategies trained with different cost functions.
-In deep hedging~\citep{buehler2019deep} the state space of the MDP contains the previous hedging weight.
+In deep hedging~\citep{buehler2019deep} the state space of the \gls{mdp} contains the previous hedging weight.
 A more recent paper by~\cite{imaki2021no} proposes a new network architecture that removes the previous hedging weight from the state space by introducing a no-transaction band.
@@
 
-Despite the success of model-based RL in hedging, most studies focus on hedging different types of contracts on classical asset models, e.g., Black-Scholes model and Heston model.
+Despite the success of model-based \gls{rl} in hedging, most studies focus on hedging different types of contracts on classical asset models, e.g., Black-Scholes model and Heston model.
 Motivated by the seminal work by~\cite{gatheral2022volatility}, there are a many subsequent works focusing on roughening the classical stochastic volatility models. 
@@
 Among these rough volatility models, notable examples are rough Heston model and the rough Bergomi model. 
-Model-based RL struggles in a rough volatility model due to difficulties in designing a suitable cost function.~\cite{horvath2021deep} shows that a standard implementation of deep hedging can lead to suboptimal hedging performance in a discretized rough Bergomi model.
+Model-based \gls{rl} struggles in a rough volatility model due to difficulties in designing a suitable cost function.~\cite{horvath2021deep} shows that a standard implementation of deep hedging can lead to suboptimal hedging performance in a discretized rough Bergomi model.
 
@@
 
-Model-free RL algorithms gain its popularity in robotics tasks, where transition probabilities in the environment are unknown and can be affected by the agent's actions.
+Model-free \gls{rl} algorithms gain its popularity in robotics tasks, where transition probabilities in the environment are unknown and can be affected by the agent's actions.
 In the context of hedging, existing studies use transaction costs as a function of the hedging weights, which makes the transition probabilities independent on the actions.
@@
 
-Boardly speaking, model-free RL can be categorized into two types: value-based RL and policy-based RL.
+Boardly speaking, model-free \gls{rl} can be categorized into two types: value-based \gls{rl} and policy-based \gls{rl}.
 Value-based approaches learn the value function directly from the data and derive the policy from the learned value function. 
-The value function is learned by training a DNN to approximate the value function, which quantifies the expected cumulative reward over time. 
+The value function is learned by training a \gls{dnn} to approximate the value function, which quantifies the expected cumulative reward over time. 
 The policy is then derived from the learned value function by selecting the action that maximizes the value function at each state. 
 ~\cite{mnih2015human} is the first paper to demonstrate the effectiveness of value-based deep reinforcement learning in training agents to play Atari games.
-To update the value function, the DNN is trained to minimize the difference between the current value function and the target value function, which is updated based on the maximum expected reward from the previous iteration.
-When trained to approximate the value function, the DNN benefits from the use of experience replay buffers, which is proposed by~\cite{lin1992self} to store and sample historical transitions and uniformly sampled during training to enhance the sample efficiency and stability of the learning process.
-~\cite{kolm2019dynamic} uses a value-based deep reinforcement learning approach to hedge European options under the Black-Scholes framework.
+To update the value function, the \gls{dnn} is trained to minimize the difference between the current value function and the target value function, which is updated based on the maximum expected reward from the previous iteration.
+When trained to approximate the value function, the \gls{dnn} benefits from the use of experience replay buffers, which is proposed by~\cite{lin1992self} to store and sample historical transitions and uniformly sampled during training to enhance the sample efficiency and stability of the learning process.
+~\cite{kolm2019dynamic} uses a value-based deep reinforcement learning approach to hedge European options under the \gls{gbm} asset model.
 
 In valued-based approaches, the value function is updated iteratively with the maximum expected reward of all possible actions, which can be computationally expensive for continuous action spaces.
-To overcome this difficulty, a policy-based approach estimates the value function before realization of the final payoff of the hedging portfolio, which is particularly useful for hedging long-term financial derivatives or VA contracts.
+To overcome this difficulty, a policy-based approach estimates the value function before realization of the final payoff of the hedging portfolio, which is particularly useful for hedging long-term financial derivatives or \gls{va} contracts.
 Two types of policy-based approaches prevail in the literature: actor-critic and policy gradient methods.
@@
 The actor network learns the policy by directly outputting the action based on the current state, while the critic network learns the value of an action by approximating the expected cumulative reward over time following the actor's policy.
-A popular actor-critic algorithm is the Deep Deterministic Policy Gradient (DDPG) algorithm proposed by~\cite{lillicrap2015continuous}, which is implemented by~\cite{xu2022delta} in hedging financial derivatives in S\&P 500 and DJIA index options.
+A popular actor-critic algorithm is the \gls{ddpg} algorithm proposed by~\cite{lillicrap2015continuous}, which is implemented by~\cite{xu2022delta} in hedging financial derivatives in S\&P 500 and DJIA index options.
 
@@
 
-Representative algorithms include the Trust Region Policy Optimization (TRPO) algorithm proposed by~\cite{schulman2015trust} and the Proximal Policy Optimization (PPO) algorithm proposed by~\cite{schulman2017proximal}.
-~\cite{du2020deep} show that the PPO algorithm is more sample efficient and stable than the value-based approaches in training agents to hedge financial derivatives.
-The most relevant paper to our study is~\cite{chong2023pseudo}, which uses the PPO algorithm to hedge GMMB with a GMDB rider under the Black-Scholes framework.
+Representative algorithms include the \gls{trpo} algorithm proposed by~\cite{schulman2015trust} and the \gls{ppo} algorithm proposed by~\cite{schulman2017proximal}.
+~\cite{du2020deep} show that the \gls{ppo} algorithm is more sample efficient and stable than the value-based approaches in training agents to hedge financial derivatives.
+The most relevant paper to our study is~\cite{chong2023pseudo}, which uses the \gls{ppo} algorithm to hedge \gls{gmmb} with a GMDB rider under the Black-Scholes framework.
 However, information of the underlying risk factors is leaked to the agent, which makes their study pseudo-model-free.
@@
 In a hedging problem, an insurer aims at finding a policy $\pi$ that maximizes the expected reward over time.
-In a policy-based RL approach like the PPO, both the policy and the value function are parameterized by deep neural networks.
+In a policy-based \gls{rl} approach like the \gls{ppo}, both the policy and the value function are parameterized by deep neural networks.
 We denote the policy by $\pi_{\theta}$ and the value function by $V_{\phi}$, where $\theta$ and $\phi$ are the parameters of the value network and the policy network, respectively.
@@
 The first component in the objective function, $\Lambda_t(\theta) \hat{A}^{\pi_{\theta}}(s_t, a_t)$, is a surrogate objective function that approximates the advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi_{\theta_{old}}$, and the second component, $\text{clip}(\Lambda_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(s_t, a_t)$, is a clipped surrogate objective function that prevents large policy updates and ensures more stable training.
-The TRPO algorithm proposed by~\cite{schulman2015trust} uses a similar clipped surrogate objective function to ensure that the policy update does not deviate too far from the old policy, but PPO simplifies the optimization problem by using a clipped surrogate objective function instead of a hard-coded constraint on the policy update.
-Compared to TRPO, PPO is more computationally efficient and easier to implement, making it a popular choice for training deep reinforcement learning agents.
-For a in-depth discussion on the implementation details of both TRPO and PPO, we refer the reader to~\cite{engstrom2020implementation}.
+The \gls{trpo} algorithm proposed by~\cite{schulman2015trust} uses a similar clipped surrogate objective function to ensure that the policy update does not deviate too far from the old policy, but \gls{ppo} simplifies the optimization problem by using a clipped surrogate objective function instead of a hard-coded constraint on the policy update.
+Compared to \gls{trpo}, \gls{ppo} is more computationally efficient and easier to implement, making it a popular choice for training deep reinforcement learning agents.
+For a in-depth discussion on the implementation details of both \gls{trpo} and \gls{ppo}, we refer the reader to~\cite{engstrom2020implementation}.
 
@@
 
-Algorithm~\ref{alg3:ppoHedging} outlines the PPO algorithm for training an agent to hedge VAs.
+Algorithm~\ref{alg3:ppoHedging} outlines the \gls{ppo} algorithm for training an agent to hedge VAs.
 At each iteration $k$, the agent collects a set of trajectories $\mathcal{D}_k$ by interacting with the environment (Section~\ref{subsec:VASimulation}) with the current policy $\pi_{\theta_k}$.
@@
 Furthermore, a rough volatility model introduces non-Markovian dynamics, i.e., the future state of the system depends on the entire history of the system.
-To address the non-Markovian dynamics, an LSTM component is added to the state representation $\mathbf{s}_t$ to capture the temporal dependencies in the data.
-This approach is known as recurrent PPO~\citep{ni2021recurrent}.
-Let $h_t$ be the hidden state of the LSTM at time $t$.
-The state representation $\mathbf{s}_t$ is fed into the LSTM at each time step to update the hidden state $h_t$.
+To address the non-Markovian dynamics, an \gls{lstm} component is added to the state representation $\mathbf{s}_t$ to capture the temporal dependencies in the data.
+This approach is known as recurrent \gls{ppo}~\citep{ni2021recurrent}.
+Let $h_t$ be the hidden state of the \gls{lstm} at time $t$.
+The state representation $\mathbf{s}_t$ is fed into the \gls{lstm} at each time step to update the hidden state $h_t$.
 \begin{equation} \label{eq3:stateRNN}
-    \mathbf{s}_t = (S_t, F_t, G_t, \tau, \Delta_{t-1}), \quad h_t = \text{LSTM}(\mathbf{s}_t, h_{t-1})
+    \mathbf{s}_t = (S_t, F_t, G_t, \tau, \Delta_{t-1}), \quad h_t = \text{\gls{lstm}}(\mathbf{s}_t, h_{t-1})
 \end{equation}
 
-In a LSTM, the cell state $c_t$ stores a representation of historical information up to time $t$.
+In a \gls{lstm}, the cell state $c_t$ stores a representation of historical information up to time $t$.
 It is updated at each time step by a forget gate $f_t$, an input gate $i_t$, and an output gate $o_t$.
 
-In a recurrent PPO with LSTM, the policy and reward function remain the same but with the new state representation in Equation~\eqref{eq3:stateRNN}.
-Instead of following the standard PPO algorithm, the agent uses the recurrent PPO algorithm to learn an optimal policy for hedging VAs.
-Figure~\ref{fig3:architecturePPO} illustrates the network architecture of the standard PPO and the recurrent PPO with LSTM, and Algorithm~\ref{alg3:ppoHedging-rnn} outlines the recurrent PPO algorithm and for training an agent to hedge VAs with non-Markovian dynamics.
+In a recurrent \gls{ppo} with \gls{lstm}, the policy and reward function remain the same but with the new state representation in Equation~\eqref{eq3:stateRNN}.
+Instead of following the standard \gls{ppo} algorithm, the agent uses the recurrent \gls{ppo} algorithm to learn an optimal policy for hedging VAs.
+Figure~\ref{fig3:architecturePPO} illustrates the network architecture of the standard \gls{ppo} and the recurrent \gls{ppo} with \gls{lstm}, and Algorithm~\ref{alg3:ppoHedging-rnn} outlines the recurrent \gls{ppo} algorithm and for training an agent to hedge VAs with non-Markovian dynamics.
 
 \begin{algorithm}
-    \caption{Recurrent PPO with LSTM for Hedging Variable Annuities} 
+    \caption{Recurrent \gls{ppo} with \gls{lstm} for Hedging Variable Annuities} 
     \begin{algorithmic}[1] \label{alg3:ppoHedging-rnn}
         \STATE  Initialize policy parameters $\theta_0$ and value function parameters $\phi_0$.
-        \STATE  Initialize the LSTM layers with random weights, and set the hidden state $h_0$ to zeros.
+        \STATE  Initialize the \gls{lstm} layers with random weights, and set the hidden state $h_0$ to zeros.
         \STATE  \textbf{For} {iteration $k=0, 1,2,\ldots$} \textbf{do}
         \STATE  \quad Collect a set of trajectories $\mathcal{D}_k$ by sampling from the environment with policy $\pi_{\theta_{k}}$.
-        \STATE  \quad Reset the LSTM hidden state $h_0$ to zeros at the beginning of each trajectory.
+        \STATE  \quad Reset the \gls{lstm} hidden state $h_0$ to zeros at the beginning of each trajectory.
         \STATE  \quad Compute the rewards $\hat{R}_t$ for each trajectory in $\mathcal{D}_k$.
@@
         \includegraphics[width=\textwidth]{./futureWork/tikz/ppo_diagram.pdf}
-        \caption{regular PPO}
+        \caption{regular \gls{ppo}}
         \label{subfig3:architecturePPO}
@@
         \includegraphics[width=\textwidth]{./futureWork/tikz/recurrentppo_diagram.pdf}
-        \caption{Recurrent PPO with LSTM}
+        \caption{Recurrent \gls{ppo} with \gls{lstm}}
         \label{subfig3:architectureLSTMPPO}
     \end{subfigure}
-    \caption{PPO Network Architectures} 
+    \caption{\gls{ppo} Network Architectures} 
     \label{fig3:architecturePPO}
@@
 
-The recurrent PPO algorithm is similar to the standard PPO algorithm, but it includes an LSTM component to capture the temporal dependencies in the data.
-However, the sequantial nature of the LSTM is not suitable for a parallel computation, which slows down the training process.
+The recurrent \gls{ppo} algorithm is similar to the standard \gls{ppo} algorithm, but it includes an \gls{lstm} component to capture the temporal dependencies in the data.
+However, the sequantial nature of the \gls{lstm} is not suitable for a parallel computation, which slows down the training process.
 
@@
 
-We present a numerical experiment to demonstrate the effectiveness of the model-free PPO algorithm for hedging VAs with transaction costs.
-We consider a VA contract with a maturity of $T=240$ months and a GMMB rider with a simulation environment described in Section~\ref{subsec:VASimulation}.
+We present a numerical experiment to demonstrate the effectiveness of the model-free \gls{ppo} algorithm for hedging VAs with transaction costs.
+We consider a \gls{va} contract with a maturity of $T=240$ months and a \gls{gmmb} rider with a simulation environment described in Section~\ref{subsec:VASimulation}.
 The simulation enviornment is implemented in Python using the OpenAI Gym framework~\citep{brockman2016openai}, and the neural networks are programmed using the PyTorch library~\citep{paszke2019pytorch}.
-The environment is designed to simulate the dynamics of the VA contract and provide the agent with the current state of the VA with the contract specifications and the financial market information described in Table~\ref{tab3:hyperparameters}.
+The environment is designed to simulate the dynamics of the \gls{va} contract and provide the agent with the current state of the \gls{va} with the contract specifications and the financial market information described in Table~\ref{tab3:hyperparameters}.
 
@@
     \end{tabular}
-    \caption{PPO Hyperparameters and GMMB Contract Specifications} 
+    \caption{\gls{ppo} Hyperparameters and \gls{gmmb} Contract Specifications} 
     \label{tab3:hyperparameters}
@@
 
-The underlying asset price $S_t$ is modeled as a geometric Brownian motion (GBM) with a drift rate $\mu$ and a volatility $\sigma$.
+The underlying asset price $S_t$ is modeled as a \gls{gbm} with a drift rate $\mu$ and a volatility $\sigma$.
 
@@
 
-Figure~\ref{fig3:dh-transfers} illustrates the hedging performance of the deep hedging algorithm with transfer learning for hedging VAs with a GMMB rider.
-The first deep hedging agent is directly trained on the Heston asset model, and the second deep hedging agent is trained with transfer learning from the GBM model.
+Figure~\ref{fig3:dh-transfers} illustrates the hedging performance of the deep hedging algorithm with transfer learning for hedging VAs with a \gls{gmmb} rider.
+The first deep hedging agent is directly trained on the Heston asset model, and the second deep hedging agent is trained with transfer learning from the \gls{gbm} model.
 The figure plot the 95\%-CVaR of hedging errors against training epochs for both agents.
@@
 
-For the PPO agent, we use a regular PPO and a recurrent PPO with an LSTM component to capture the temporal dependencies in the data.
+For the \gls{ppo} agent, we use a regular \gls{ppo} and a recurrent \gls{ppo} with an \gls{lstm} component to capture the temporal dependencies in the data.
 The weights of the value network and the policy network are initialized with orthogonal initialization~\citep{engstrom2020implementation} with scaling $\sqrt{2}$ and the bias terms set to zero.
@@
 At each timestep, the observations are normalized and cliped between $-10$ and $10$ before being fed into the neural networks to stabilize the training process.
-For PPO, we follow the suggestions in~\cite{schulman2017proximal} and set the clipping hyperparameter $\epsilon$ to $0.2$ to prevent large policy updates. 
-More specifically, our implementation of the PPO uses a generalized advantage estimation~\citep{schulman2015high} to estimate the advantage function.
+For \gls{ppo}, we follow the suggestions in~\cite{schulman2017proximal} and set the clipping hyperparameter $\epsilon$ to $0.2$ to prevent large policy updates. 
+More specifically, our implementation of the \gls{ppo} uses a generalized advantage estimation~\citep{schulman2015high} to estimate the advantage function.
 The agent interacts with the environment for $10^5$ episodes, and the policy and value networks are evaluated every $1000$ episodes.
@@
     \includegraphics[width=0.5\textwidth]{./futureWork/figures/PPO_DH.png}
-    \caption{Hedging performance of recurrent PPO and deep hedging}
+    \caption{Hedging performance of recurrent \gls{ppo} and deep hedging}
     \label{fig3:ppo_dh}
@@
 
-This experiment compares the hedging performance of the recurrent PPO agent with LSTM and the deep hedging algorithm proposed by~\cite{buehler2019deep} for hedging VAs with a GMMB rider.
+This experiment compares the hedging performance of the recurrent \gls{ppo} agent with \gls{lstm} and the deep hedging algorithm proposed by~\cite{buehler2019deep} for hedging VAs with a \gls{gmmb} rider.
 The experiment is conducted with the same amount ofsimulation budget.
@@
     \end{subfigure}
-    \caption{Hedging performance of standard PPO and recurrent PPO} 
+    \caption{Hedging performance of standard \gls{ppo} and recurrent \gls{ppo}} 
     \label{fig3:ppo_result}
@@
 
-Figure~\ref{fig3:ppo_result} illustrates the hedging performance of the standard PPO and the recurrent PPO with LSTM for hedging VAs with transaction costs $C=0.005$.
-The figures show the distributions of the hedging errors incurred by the agents over the $10^3$ test episodes for the GBM and the regime-switching GBM asset models.
-For both asset models, the recurrent PPO outperforms the standard PPO in terms of hedging performance.
-For the regime-switching GBM, the 95\%-VaR of hedging errors of the recurrent PPO and the standard PPO are $136.24$ and $147.14$, respectively.
-The hedging errors of the recurrent PPO are more concentrated around zero, indicating that historical information captured by the LSTM component helps the agent make better hedging decisions even in the enviornment is Markovian.
+Figure~\ref{fig3:ppo_result} illustrates the hedging performance of the standard \gls{ppo} and the recurrent \gls{ppo} with \gls{lstm} for hedging VAs with transaction costs $C=0.005$.
+The figures show the distributions of the hedging errors incurred by the agents over the $10^3$ test episodes for the \gls{gbm} and the \gls{rsgbm} asset models.
+For both asset models, the recurrent \gls{ppo} outperforms the standard \gls{ppo} in terms of hedging performance.
+For the regime-switching \gls{gbm}, the 95\%-VaR of hedging errors of the recurrent \gls{ppo} and the standard \gls{ppo} are $136.24$ and $147.14$, respectively.
+The hedging errors of the recurrent \gls{ppo} are more concentrated around zero, indicating that historical information captured by the \gls{lstm} component helps the agent make better hedging decisions even in the enviornment is Markovian.
 
@@
     \end{subfigure}
-    \caption{Hedging performance of recurrent PPO and delta hedging with different transaction costs} 
+    \caption{Hedging performance of recurrent \gls{ppo} and delta hedging with different transaction costs} 
     \label{fig3:ppo_cost}
@@
 
-Figure~\ref{fig3:ppo_cost} shows the hedging performance of the recurrent PPO agent and the delta hedging strategy with different transaction costs when the asset model is a GBM.
+Figure~\ref{fig3:ppo_cost} shows the hedging performance of the recurrent \gls{ppo} agent and the delta hedging strategy with different transaction costs when the asset model is a \gls{gbm}.
 The experiment is conducted with transaction costs of $C=0.001$ and $C=0.02$.
 The delta hedging strategy is implemented with the Black-Scholes delta.
-When the transaction cost is low, the delta hedging strategy outperforms the recurrent PPO agent.
-However, as the transaction cost increases, delta hedging becomes less effective, and the recurrent PPO agent is able to learn from the environment and adapt its hedging strategy to minimize the hedging errors.
+When the transaction cost is low, the delta hedging strategy outperforms the recurrent \gls{ppo} agent.
+However, as the transaction cost increases, delta hedging becomes less effective, and the recurrent \gls{ppo} agent is able to learn from the environment and adapt its hedging strategy to minimize the hedging errors.
 
@@
     \includegraphics[width=\textwidth]{./futureWork/figures/PPO_anchor.png}
-    \caption{Hedging performance of recurrent PPO with or without anchor}
+    \caption{Hedging performance of recurrent \gls{ppo} with or without anchor}
     \label{fig3:ppo_anchor}
@@
 
-Figure~\ref{fig3:ppo_anchor} illustrates the hedging performance of the recurrent PPO agent with and without the model information of the underlying asset model and the current value of the liability.
-The experiment is conducted for the GBM asset model with transaction costs of $C=0.005$.
+Figure~\ref{fig3:ppo_anchor} illustrates the hedging performance of the recurrent \gls{ppo} agent with and without the model information of the underlying asset model and the current value of the liability.
+The experiment is conducted for the \gls{gbm} asset model with transaction costs of $C=0.005$.
 The results show that the agent with the model information does not outperform the agent without the model information.
@@
     \includegraphics[width=\textwidth]{./futureWork/figures/PPO_GMWB.png}
-    \caption{Hedging performance of recurrent PPO with GMWB}
+    \caption{Hedging performance of recurrent \gls{ppo} with \gls{gmwb}}
     \label{fig3:ppo_GMWB}
@@
 
-Figure~\ref{fig3:ppo_GMWB} illustrates the hedging performance of the recurrent PPO agent for hedging VAs with a GMWB rider.
-The experiment is conducted with the same hyperparameters as the experiment with the GMMB rider.
-Unlike the GMMB rider, the PPO agent struggles to learn an optimal hedging strategy for the VA with a GMWB rider.
-The hedging errors of the PPO agent are more dispersed, indicating that more training episodes are needed to achieve a satisfactory hedging performance.
-The results suggest that the GMWB rider introduces additional complexity to the hedging problem, and the model-free RL algorithm is not sample efficient.
+Figure~\ref{fig3:ppo_GMWB} illustrates the hedging performance of the recurrent \gls{ppo} agent for hedging VAs with a \gls{gmwb} rider.
+The experiment is conducted with the same hyperparameters as the experiment with the \gls{gmmb} rider.
+Unlike the \gls{gmmb} rider, the \gls{ppo} agent struggles to learn an optimal hedging strategy for the \gls{va} with a \gls{gmwb} rider.
+The hedging errors of the \gls{ppo} agent are more dispersed, indicating that more training episodes are needed to achieve a satisfactory hedging performance.
+The results suggest that the \gls{gmwb} rider introduces additional complexity to the hedging problem, and the model-free \gls{rl} algorithm is not sample efficient.
 
@@
 
-The proposed future work of this thesis aims at investigating how transfer learning can be effectively integrated into the training of PPO agents for dynamic hedging of VA contracts. 
-The primary goal is to enhance the adaptability and efficiency of hedging strategies in response to new VA products and changing market conditions.
+The proposed future work of this thesis aims at investigating how transfer learning can be effectively integrated into the training of \gls{ppo} agents for dynamic hedging of \gls{va} contracts. 
+The primary goal is to enhance the adaptability and efficiency of hedging strategies in response to new \gls{va} products and changing market conditions.
 
-The first objective is to establish a systematic approach for transferring policies learned by PPO agents from source tasks to target tasks in the context of dynamic hedging. 
-Source tasks may involve hedging a GMMB under a specific market model, while target tasks could entail hedging a GMWB under a different market model.
+The first objective is to establish a systematic approach for transferring policies learned by \gls{ppo} agents from source tasks to target tasks in the context of dynamic hedging. 
+Source tasks may involve hedging a \gls{gmmb} under a specific market model, while target tasks could entail hedging a \gls{gmwb} under a different market model.
 
 To achieve this, the research will explore methodologies such as policy distillation, where knowledge from a pre-trained "teacher" policy is transferred to a "student" policy~\citep{rusu2015policy}.
-Policy distillation has been effective in compressing and transferring knowledge between networks, improving learning efficiency in RL settings.
+Policy distillation has been effective in compressing and transferring knowledge between networks, improving learning efficiency in \gls{rl} settings.
 Another avenue for future research is the use of pre-trained model initialization, wherein the policy network trained on the source task initializes the policy for the target task. 
@@
 The framework will also consider feature representation transfer, which aims at reusing learned representations of market dynamics and policyholder behaviors between tasks. 
-By capturing common patterns across different contracts and market models, the PPO agent can more effectively generalize to new scenarios~\citep{bengio2012deep}.
+By capturing common patterns across different contracts and market models, the \gls{ppo} agent can more effectively generalize to new scenarios~\citep{bengio2012deep}.
 
-By addressing these objectives, the research aims at advancing the field of financial risk management through the development of adaptive and efficient hedging strategies for VA contracts.
-The integration of transfer learning into PPO agents has the potential to substantially reduce computational costs and improve the robustness of hedging policies in dynamic market environments.
+By addressing these objectives, the research aims at advancing the field of financial risk management through the development of adaptive and efficient hedging strategies for \gls{va} contracts.
+The integration of transfer learning into \gls{ppo} agents has the potential to substantially reduce computational costs and improve the robustness of hedging policies in dynamic market environments.

### 2025-04-13 introduction.tex
11

@@
 Successful risk management practice can enhance financial stability and resilience for individual companies and for the financial system as well.
-Variable annuity (VA) contracts are a popular type of complex insurance product that is linked to the performance of underlying assets.
+\gls{va} contracts are a popular type of complex insurance product that is linked to the performance of underlying assets.
 They provide a guaranteed minimum income benefit to the policyholder regardless of the performance of the underlying assets.
@@
 Metamodels are statistical models that approximate the output of a complex simulation model as a function of its input parameters.
-In this thesis, we focus on metamodels of the inner simulation models in nested simulation procedures for risk management applications of financial derivatives and VA contracts.
+In this thesis, we focus on metamodels of the inner simulation models in nested simulation procedures for risk management applications of financial derivatives and \gls{va} contracts.
 This thesis addresses two key problems that necessitate nested simulation:
@@
     \item estimating the risk of a portfolio of financial options and 
-    \item dynamic hedging of VA contracts with a delta hedging strategy.
+    \item dynamic hedging of \gls{va} contracts with a delta hedging strategy.
 \end{itemize}
 Risk management of VAs is a challenging problem due to the complex interactions between the policyholder's behavior and the financial market dynamics.
-We focus mainly on the estimation of tail risk measures of VA contract losses using metamodel-based nested simulation procedures.
+We focus mainly on the estimation of tail risk measures of \gls{va} contract losses using metamodel-based nested simulation procedures.
 This thesis consists of four chapters.
@@
 Numerical experiments are conducted to test their empirical convergence behavior under finite budget sizes.
-Chapter~\ref{chap:project2} proposes the use of neural network models as metamodels for a two-stage multi-period nested simulation procedure on VA contracts.
+Chapter~\ref{chap:project2} proposes the use of neural network models as metamodels for a two-stage multi-period nested simulation procedure on \gls{va} contracts.
 In our numerical experiment, the best neural network metamodel surpasses the state-of-the-art metamodels in tail identification, and it leads to substantial computational savings.
 Chapter~\ref{chap:project2} also includes sensitivity testing of the neural network metamodel.
-We argue that for estimating tail risk measures of VA contract losses, the inner simulation can be replaced entirely by a suitable metamodel.
+We argue that for estimating tail risk measures of \gls{va} contract losses, the inner simulation can be replaced entirely by a suitable metamodel.
 Eliminating the inner simulation can lead to more substantial computational savings without affecting estimation quality.
 When extensive inner simulations are required for regulatory purposes, effective budget allocation can improve estimator accuracy without increasing the computational budget.
-In practice, underlying assumptions of the simulation model are subject to change, and new VA contracts are issued with different contract specifications.
+In practice, underlying assumptions of the simulation model are subject to change, and new \gls{va} contracts are issued with different contract specifications.
 Simulation budgets are often scarce for new conditions.
-Chapter~\ref{chap:project3} uses transfer learning techniques for a quick adaptation of the neural network metamodel to new market conditions and new VA contracts.
+Chapter~\ref{chap:project3} uses transfer learning techniques for a quick adaptation of the neural network metamodel to new market conditions and new \gls{va} contracts.
 Our numerical experiments show that a judicious use of transfer learning can lead to substantially better metamodels than those trained from scratch.
 Chapter~\ref{chap:conclusion} concludes this thesis and discusses potential future research directions.
-Chapter~\ref{chap:futureWork} explores future applications of deep reinforcement learning in the dynamic hedging of VA contracts.
+Chapter~\ref{chap:futureWork} explores future applications of deep reinforcement learning in the dynamic hedging of \gls{va} contracts.
 
@@
 
-VA contracts are index-linked insurance products that offer policyholders the upside potential of equity markets while providing guarantees against downside risk.
+\gls{va} contracts are index-linked insurance products that offer policyholders the upside potential of equity markets while providing guarantees against downside risk.
 These products have gained a substantial amount of interest as they address the needs of individuals seeking both wealth accumulation and financial security, especially in the context of retirement planning.
 The key feature of VAs is their embedded guarantees, which ensure a specified minimum benefit regardless of market performance.
-Two VA contracts that are most relevant to this thesis are Guaranteed Minimum Maturity Benefit (GMMB) and the Guaranteed Minimum Withdrawal Benefit (GMWB).
-The GMMB guarantees that at the maturity of the contract, the policyholder will receive no less than the initial investment or a predetermined minimum amount.
-The GMWB allows policyholders to withdraw a specified percentage of their benefit base each period during the contract horizon~\citep{hardy2003investment}.
+Two \gls{va} contracts that are most relevant to this thesis are \gls{gmmb} and \gls{gmwb}.
+The \gls{gmmb} guarantees that at the maturity of the contract, the policyholder will receive no less than the initial investment or a predetermined minimum amount.
+The \gls{gmwb} allows policyholders to withdraw a specified percentage of their benefit base each period during the contract horizon~\citep{hardy2003investment}.
 While these guarantees make VAs more attractive to consumers by offering protection against market downturns and ensuring income stability, they also introduce significant financial risks for insurers.
-The embedded options within GMMBs and GMWBs expose insurers to market risk, longevity risk, and policyholder behavior risk.
+The embedded options within \gls{gmmb} and \gls{gmwb} expose insurers to market risk, longevity risk, and policyholder behavior risk.
 Therefore, an effective management of these risks is crucial for insurers to maintain solvency and meet regulatory capital requirements.
@@
 However, dynamic hedging introduces complexity in estimating the insurer's overall risk exposure.
-One such example is the estimation of tail risk measures of a VA contract.
+One such example is the estimation of tail risk measures of a \gls{va} contract.
 It requires a stochastic modeling of the financial market and an accurate loss estimation of the hedging portfolio under different market scenarios.
@@
 In nested simulation, an outer simulation generates a set of market scenarios over the contract horizon, while an inner simulation estimates the contract loss in each scenario.
-By combining the results of the inner simulations across the outer scenarios, nested simulation provides an accurate estimate of the tail risk of the VA contract.
+By combining the results of the inner simulations across the outer scenarios, nested simulation provides an accurate estimate of the tail risk of the \gls{va} contract.
 
@@
 The learning process, called training, minimizes a loss function $l(f(x; \theta),y)$ over the training data, which quantifies the difference between predicted and actual labels.
-A common loss function for regression problems is a quadratic loss function in the form of a mean squared error (MSE):
+A common loss function for regression problems is a quadratic loss function in the form of a \gls{mse}:
 
@@
 The training of parametric regression refers to the process of estimating the regression coefficients $\beta_0, \beta_1, \ldots, \beta_p$ that minimize the loss function.
-For a MSE loss metric, the optimal regression coefficients can be obtained by solving the normal equations.
+For a \gls{mse} loss metric, the optimal regression coefficients can be obtained by solving the normal equations.
 Parametric regression is powerful for modeling linear relationships when basis functions are known from expert knowledge or feature engineering~\citep{hastie2009elements}.
@@
 Often, expert knowledge is required to select the appropriate basis functions, which can limit the flexibility of the model.
-Extensions like polynomial regression and generalized linear models (GLMs) have been introduced to capture non-linearity in the data.
+Extensions like polynomial regression and \gls{glm} have been introduced to capture non-linearity in the data.
 Nevertheless, these models can still be limited in capturing highly complex patterns of the data.
@@
 They can learn complex, non-linear relationships in data without the need for explicit feature engineering.
-The most basic form of a neural network is the feedforward neural network (FNN), which consists of an input layer, one or more hidden layers, and an output layer~\citep{goodfellow2016}.
+The most basic form of a neural network is the \gls{fnn}, which consists of an input layer, one or more hidden layers, and an output layer~\citep{goodfellow2016}.
 
@@
         \includegraphics[width=\textwidth]{./project3/tikz/fnn.pdf}
-        \caption{FNN}
+        \caption{\gls{fnn}}
         \label{subfig:fnn}
@@
         \includegraphics[width=\textwidth]{./project3/tikz/lstm.pdf}
-        \caption{LSTM}
+        \caption{\gls{lstm}}
         \label{subfig:lstm}
@@
 
-Figure~\ref{subfig:fnn} shows a feedforward neural network (FNN) architecture with one hidden layer.
+Figure~\ref{subfig:fnn} shows a \gls{fnn} architecture with one hidden layer.
 The input layer receives the input features, which are then passed through the hidden layer(s) to the output layer.
@@
 The linear transformation is similar to the linear regression model in Equation~\eqref{eq:regression}, but the non-linear activation function allows the neural network to model complex, non-linear relationships in the data.
-The FNN is tuned by adjusting the trainable parameters $\theta$ while fixing the activation functions $a^{(i)}$.
-A typical choice for the activation function is the rectified linear unit (ReLU), which is defined as $a(z) = \max(0, z)$~\citep{nair2010rectified}.
+The \gls{fnn} is tuned by adjusting the trainable parameters $\theta$ while fixing the activation functions $a^{(i)}$.
+A typical choice for the activation function is the \gls{relu}, which is defined as $a(z) = \max(0, z)$~\citep{nair2010rectified}.
 The activation function choice is crucial for training neural networks.
@@
 
-The key advantage of FNNs lies in their ability to perform automatic feature engineering without a direct human intervention.
+The key advantage of \gls{fnn}s lies in their ability to perform automatic feature engineering without a direct human intervention.
 Unlike traditional machine learning models that require manual selection and transformation of input features, neural networks learn to extract and compose features through their hidden layers during their training.
@@
 It states that given appropriate activation functions $a$, a feedforward neural network with a single hidden layer containing a finite number of neurons can approximate any continuous function on a compact subset of $\mathbb{R}^n$ to arbitrary accuracy.
-Despite this theoretical guarantee for single-layer neural networks, in practice, deep neural networks (DNN) with multiple hidden layers have been shown to be more effective at capturing complex patterns and relationships in data~\citep{lecun2015deep}.
+Despite this theoretical guarantee for single-layer neural networks, in practice, \gls{dnn} with multiple hidden layers have been shown to be more effective at capturing complex patterns and relationships in data~\citep{lecun2015deep}.
 Examples include AlexNet~\citep{krizhevsky2012imagenet}, VGG~\citep{simonyan2014very}, and ResNet~\citep{he2016deep}, which have achieved state-of-the-art performance on image classification tasks.
-In this thesis, we focus on the application of deep neural networks, specifically long short-term memory (LSTM) networks, as metamodels for nested simulation procedures in risk management applications.
+In this thesis, we focus on the application of deep neural networks, specifically \gls{lstm}, as metamodels for nested simulation procedures in risk management applications.
 
@@
 
-Building upon the capabilities of FNNs, we recognize that while FNNs are successful at capturing complex, nonlinear relationships through automatic feature learning, they are inherently limited when it comes to modeling sequential data or time-dependent patterns.
+Building upon the capabilities of \gls{fnn}s, we recognize that while \gls{fnn}s are successful at capturing complex, nonlinear relationships through automatic feature learning, they are inherently limited when it comes to modeling sequential data or time-dependent patterns.
 This independence assumption limits their effectiveness in modeling financial time series, where temporal dependencies play a critical role.
-The stylized facts of financial time series, such as volatility clustering, fat tails, and autocorrelation, are challenging to capture with traditional FNNs due to the absence of memory in the model~\citep{cont2001empirical}.
+The stylized facts of financial time series, such as volatility clustering, fat tails, and autocorrelation, are challenging to capture with traditional \gls{fnn}s due to the absence of memory in the model~\citep{cont2001empirical}.
 
-To overcome the limitations of FNNs in handling sequential input, recurrent neural networks (RNNs) were introduced.
-In an RNN, the hidden state at each time step is a function of both the current input and the hidden state from the previous time period~\citep{elman1990finding}:
+To overcome the limitations of \gls{fnn}s in handling sequential input, \gls{rnn}s were introduced.
+In an \gls{rnn}, the hidden state at each time step is a function of both the current input and the hidden state from the previous time period~\citep{elman1990finding}:
 
@@
 where $h_t$ is the hidden state at time $t$, $x_t$ is the input at time $t$, $h_{t-1}$ is the hidden state at time $t-1$, and $f$ is the recurrent function parameterized by $\theta$.
-This architecture enables RNNs to capture temporal dependencies by maintaining a dynamic internal state that reflects the memory of past inputs.
-However, traditional RNNs suffer from the vanishing and exploding gradient problem, which hinders their ability to capture longer-term dependencies that often present in financial time series~\citep{bengio1994learning}.
+This architecture enables \gls{rnn} to capture temporal dependencies by maintaining a dynamic internal state that reflects the memory of past inputs.
+However, traditional \gls{rnn} suffer from the vanishing and exploding gradient problem, which hinders their ability to capture longer-term dependencies that often present in financial time series~\citep{bengio1994learning}.
 During training, gradients propagated backward through time can either diminish exponentially (known as vanishing gradients) or grow uncontrollably (known as exploding gradients).
@@
 
-To address these issues, a long short-term memory (LSTM) network was developed by~\citet{hochreiter1997long}.
-It is a specialized form of RNNs designed to capture long-term dependencies more effectively with the help of RNN memory cells and gating mechanisms.
+To address these issues, a \gls{lstm} network was developed by~\citet{hochreiter1997long}.
+It is a specialized form of RNNs designed to capture long-term dependencies more effectively with the help of \gls{rnn} memory cells and gating mechanisms.
 
@@
 
-Figure~\ref{subfig:lstm} shows the architecture of an LSTM network.
-The gating mechanisms in LSTM networks effectively mitigate the vanishing and exploding gradient problem by regulating the flow of information through the network.
+Figure~\ref{subfig:lstm} shows the architecture of an \gls{lstm} network.
+The gating mechanisms in \gls{lstm} networks effectively mitigate the vanishing and exploding gradient problem by regulating the flow of information through the network.
 The input gate $i_t$ controls the flow of information into the cell state $c_t$, the forget gate $f_t$ regulates the retention of information in the cell state, and the output gate $o_t$ determines the information passed to the hidden state $h_t$.
@@
 The cell state $c_t$ acts as a memory unit that stores information over time, while the hidden state $h_t$ captures the relevant information for the current time step.
-By incorporating memory cells and gating mechanisms, LSTMs can effectively model long-term dependencies in sequential data in finance and actuarial applications.
+By incorporating memory cells and gating mechanisms, \gls{lstm} can effectively model long-term dependencies in sequential data in finance and actuarial applications.
 
@@
 By effectively modeling complex, non-linear relationships and temporal dependencies, neural networks serve as powerful tools for addressing the computational challenges in estimating risk measures and developing effective risk mitigation strategies.
-This thesis aims at exploring the application and noise tolerance of LSTM networks in metamodeling for nested simulation procedures in risk management.
-In this thesis, we investigate the performance of LSTM networks in approximating the inner simulation model in a two-stage nested simulation procedure for index-linked insurance contracts.
-By leveraging the memory and sequential modeling capabilities of LSTMs, we aim to improve the accuracy and efficiency of nested simulation procedures for risk management applications.
+This thesis aims at exploring the application and noise tolerance of \gls{lstm} networks in metamodeling for nested simulation procedures in risk management.
+In this thesis, we investigate the performance of \gls{lstm} networks in approximating the inner simulation model in a two-stage nested simulation procedure for index-linked insurance contracts.
+By leveraging the memory and sequential modeling capabilities of \gls{lstm}, we aim to improve the accuracy and efficiency of nested simulation procedures for risk management applications.
 
@@
 However, the training of neural networks is non-convex, and the optimization problem is challenging.
-Stochastic gradient descent (SGD) is a popular optimization algorithm for training neural networks.
+\gls{sgd} is a popular optimization algorithm for training neural networks.
 It updates the parameters using a single or a small batch of training examples at a time, which makes it much faster than a crude gradient descent.
-However, SGD may oscillate and converge slowly, especially in non-convex problems~\citep{bengio2016}.
+However, \gls{sgd} may oscillate and converge slowly, especially in non-convex problems~\citep{bengio2016}.
 To address these issues, various adaptive learning rate methods have been proposed in the literature.
@@
 Comparing the errors of a neural network on the true labels can reveal its true generalization capability and robustness.
-Chapter~\ref{chap:project2} provides a detailed study of the generalization capability of LSTM networks in a simulation environment for risk management of VA contracts.
+Chapter~\ref{chap:project2} provides a detailed study of the generalization capability of \gls{lstm} networks in a simulation environment for risk management of \gls{va} contracts.
 Viewing the simulation environment as a data-generating process allows us to systematically study and evaluate the performance of neural networks within a controlled setting.
@@
 Chapter~\ref{chap:project1} provides a comprehensive analysis of the convergence properties of existing nested simulation procedures and their practical implications.
-Chapter~\ref{chap:project2} focuses on the development and evaluation of neural network metamodels, particularly LSTM networks, for enhancing the efficiency of nested simulations in risk management of VA contracts.
+Chapter~\ref{chap:project2} focuses on the development and evaluation of neural network metamodels, particularly \gls{lstm} networks, for enhancing the efficiency of nested simulations in risk management of \gls{va} contracts.
 We also examine the robustness and generalization capabilities of these models in the presence of simulation noise.
@@
 Chapter~\ref{chap:conclusion} summarizes the key findings of this thesis and discusses future research directions that involve the robost use of neural networks in quantitative risk management applications.
-Chapter~\ref{chap:futureWork} explores future applications of transfer learning and deep reinforcement learning in the dynamic hedging of VA contracts.
+Chapter~\ref{chap:futureWork} explores future applications of transfer learning and deep reinforcement learning in the dynamic hedging of \gls{va} contracts.

### 2025-04-13 project1/nsSurvey.tex
11

@@
 Nested simulation procedures are commonly used in financial engineering to estimate risk measures for portfolios of complex financial derivatives. 
-The term \textit{nested} refers to a nested estimation problem, in which the estimation of the risk measure requires two levels of Monte Carlo (MC) simulations.
+The term \textit{nested} refers to a nested estimation problem, in which the estimation of the risk measure requires two levels of \gls{mc} simulations.
 In a typical nested simulation procedure, an outer-level simulation model generates underlying risk factors, which are referred to as the \textit{outer scenarios}.
@@
 The nested simulation procedure is computationally expensive due to its nested structure. 
-Given a fixed computational budget, the nestzed simulation procedure should balance the number of outer scenarios and the number of inner replications to maximize computational efficiency.
+Given a fixed computational budget, the nested simulation procedure should balance the number of outer scenarios and the number of inner replications to maximize computational efficiency.
 \cite{gordy2010nested} first analyzed and proposed an optimal budget allocation for a standard nested simulation procedure.
-The term \textit{standard} refers to using a standard MC estimator, the sample mean of the inner replications to estimate a scenario-wise portfolio loss for an outer scenario.
-\cite{gordy2010nested} investigate an optimal budget allocation for a standard nested simulation procedure with respect to the MSE of the estimated risk measure.
+The term \textit{standard} refers to using a standard \gls{mc} estimator, the sample mean of the inner replications to estimate a scenario-wise portfolio loss for an outer scenario.
+\cite{gordy2010nested} investigate an optimal budget allocation for a standard nested simulation procedure with respect to the \gls{mse} of the estimated risk measure.
 
@@
 For certain risk measures,~\cite{broadie2015risk} show that it's optimal to allocate the entire simulation budget to outer-level simulations, keeping only 1 inner replication in each outer scenario.
-Similarly,~\cite{hong2017kernel},~\cite{feng2020optimal}, and~\cite{zhang2022sample} use a kernel smoothing model, a likelihood ratio model, and a kernel ridge regression (KRR) model as metamodels to pool the inner replications from all outer scenarios, respectively.
+Similarly,~\cite{hong2017kernel},~\cite{feng2020optimal}, and~\cite{zhang2022sample} use a kernel smoothing model, a likelihood ratio model, and a \gls{krr} model as metamodels to pool the inner replications from all outer scenarios, respectively.
 In simulation studies, this approach—using a model of a simulation—is called metamodeling, and such models are termed metamodels~\citep{barton1998simulation}.
-Another line of research is a multi-level Monte Carlo (MLMC) method analyzed in~\cite{giles2019multilevel}, which is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest.
+Another line of research is a \gls{mlmc} method analyzed in~\cite{giles2019multilevel}, which is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest.
 
@@
 Furthermore, the existing literature has chosen different performance metrics to evaluate the asymptotic convergence of nested simulation procedures.
-In this chapter, we discuss the asymptotic convergence in terms of MSE of the estimator, and we provide a comprehensive comparison of their convergence rates and critical assumptions.
-We also discuss the connection between the MSE and the absolute error of the estimator in the context of nested simulation procedures.
+In this chapter, we discuss the asymptotic convergence in terms of \gls{mse} of the estimator, and we provide a comprehensive comparison of their convergence rates and critical assumptions.
+We also discuss the connection between the \gls{mse} and the absolute error of the estimator in the context of nested simulation procedures.
 
@@
 The rest of this chapter is organized as follows.
-Section~\ref{sec1:problem-formulation} introduces the nested simulation procedure and the standard MC estimator.
+Section~\ref{sec1:problem-formulation} introduces the nested simulation procedure and the standard \gls{mc} estimator.
 Section~\ref{sec1:asymptotic-convergence} provides new theoretical results on the convergence of existing nested simulation procedures.
@@
 In general, a more complex metamodel requires a higher-order smoothness for $h$ for its convergence analysis.
-Despite being more advanced than kernel smoothing, the KRR-based procedure requires a less stringent smoothness assumption on $h$.
+Despite being more advanced than kernel smoothing, the \gls{var}-based procedure requires a less stringent smoothness assumption on $h$.
 At first sight, it is counterintuitive that a more complex metamodel requires a less stringent smoothness assumption.
-This phenomenon is due to the fact that the convergence analysis for the KRR-based nested simulation procedure is shown in terms of an absolute error (AE), which is a less stringent error metric than MSE.
-Section~\ref{sec1:connection-mse-absolute-error} discusses the connection between the MSE and the AE of the estimator in the context of nested simulation procedures.
+This phenomenon is due to the fact that the convergence analysis for the \gls{var}-based nested simulation procedure is shown in terms of an \gls{ae}, which is a less stringent error metric than \gls{mse}.
+Section~\ref{sec1:connection-mse-absolute-error} discusses the connection between the \gls{mse} and the \gls{ae} of the estimator in the context of nested simulation procedures.
 In Table~\ref{tab1:smoothness}, the standard nested simulation procedure is the only procedure without an asymptotic convergence analysis for smooth $h$.
-Section~\ref{sec1:sns} fills this gap by providing the asymptotic convergence analysis for the standard nested simulation procedure in terms of MSE.
+Section~\ref{sec1:sns} fills this gap by providing the asymptotic convergence analysis for the standard nested simulation procedure in terms of \gls{mse}.
 
@@
 
-Other risk measures of interest not in the nested expectation form include Value at Risk (VaR) and Conditional Value at Risk (CVaR)~\citep{hardy2022quantitative}. 
-The $\alpha$-VaR of $L$ is defined as
+Other risk measures of interest not in the nested expectation form include \gls{var} and \gls{cvar}~\citep{hardy2022quantitative}. 
+The $\alpha$-\gls{var} of $L$ is defined as
 \begin{equation}\label{eq1:var}
@@
 
-The $\alpha$-CVaR of $L$ is defined as
+The $\alpha$-\gls{cvar} of $L$ is defined as
 \begin{equation}\label{eq1:cvar}
@@
 
-In the literature, CVaR are also known as Conditional Tail Expectation (CTE), Tail Value-at-Risk (TailVaR), and Expected Shortfall (ES).
+In the literature, \gls{cvar} are also known as Conditional Tail Expectation (CTE), Tail Value-at-Risk (TailVaR), and Expected Shortfall (ES).
 
@@
 
-The standard nested simulation procedure estimates $L_i = L(X_i)$ with a standard MC estimator 
+The standard nested simulation procedure estimates $L_i = L(X_i)$ with a standard \gls{mc} estimator 
 \begin{equation*}
@@
             \end{equation*}
-    \item   Value at risk (VaR):
+    \item   Value at risk (\gls{var}):
             \begin{equation*}
@@
 
-    \item   CVaR:
+    \item   \gls{cvar}:
             \begin{equation}\label{eq1:cvar-hat}
@@
 
-~\cite{gordy2010nested} analyze the optimal budget allocation of the standard nested simulation procedure with respect to the MSE of the estimator $\hat{\rho}_{M, N}$ for hockey-stick $h$, indicator $h$, and VaR.
+~\cite{gordy2010nested} analyze the optimal budget allocation of the standard nested simulation procedure with respect to the \gls{mse} of the estimator $\hat{\rho}_{M, N}$ for hockey-stick $h$, indicator $h$, and \gls{var}.
 
@@
 
-The MLMC method is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest, and it uses the difference between the approximations to reduce the variance of the estimator.
-The MLMC method is particularly useful when the quantity of interest is expensive to evaluate, and the standard MC estimator has a high variance.
-\textcolor{red}{For the nested expectation form $\rho = \mathbb{E}[h(L)]$, the MLMC method selects an approximation level $L$ with sufficient accuracy, and it uses the difference between the approximations to reduce the variance of the estimator.}
-\textcolor{red}{\sout{The MLMC method estimates $\rho$ with an MLMC estimator:}}
+The \gls{mlmc} method is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest, and it uses the difference between the approximations to reduce the variance of the estimator.
+The \gls{mlmc} method is particularly useful when the quantity of interest is expensive to evaluate, and the standard \gls{mc} estimator has a high variance.
+\textcolor{red}{For the nested expectation form $\rho = \mathbb{E}[h(L)]$, the \gls{mlmc} method selects an approximation level $L$ with sufficient accuracy, and it uses the difference between the approximations to reduce the variance of the estimator.}
+\textcolor{red}{\sout{The \gls{mlmc} method estimates $\rho$ with an \gls{mlmc} estimator:}}
 
 \begin{equation*}
-    \hat{\rho}^{\text{MLMC}}_\Gamma = \sum_{\upsilon=0}^{\Upsilon} \left( \frac{1}{M_{\upsilon}} \sum_{i=1}^{M_{\upsilon}} h(\hat{L}_{N_{\upsilon}}(X_{i, \upsilon})) - \frac{1}{M_{\upsilon-1}} \sum_{i=1}^{M_{\upsilon-1}} h(\hat{L}_{N_{\upsilon-1}}(X_{i, \upsilon-1})) \right), \quad X_{i, \upsilon} \sim F_X,
+    \hat{\rho}^{\text{MLMC}}_\Gamma = h(\hat{L}_{N_{0}}(X_{i, 0})) + \sum_{\upsilon=1}^{\Upsilon}  \frac{1}{M_{\upsilon}} \sum_{i=1}^{M_{\upsilon}} h(\hat{L}_{N_{\upsilon}}(X_{i, \upsilon})) -  h(\hat{L}_{N_{\upsilon-1}}(X_{i, \upsilon-1}))  , \quad X_{i, \upsilon} \sim F_X,
 \end{equation*}
-where $\hat{L}_{N_{-1}}(\cdot) = 0$, $\Upsilon$ is a number of levels, $M_{\upsilon}$ is a number of outer scenarios at level $\upsilon$, and $N_{\upsilon}$ is a number of inner replications at level $\upsilon$.
-Applying the analysis of~\cite{giles2015multilevel} in a nested simulation context,~\cite{giles2019multilevel} show that the MLMC method can achieve a similar degree of accuracy as the standard nested simulation procedure with a lower total computational budget.
+where $X_{i, \nu}$ is the outer scenarios at level $\nu$, $\Upsilon$ is a number of levels, $M_{\upsilon}$ is a number of outer scenarios at level $\upsilon$, and $N_{\upsilon}$ is a number of inner replications at level $\upsilon$.
+Applying the analysis of~\cite{giles2015multilevel} in a nested simulation context,~\cite{giles2019multilevel} show that the \gls{mlmc} method can achieve a similar degree of accuracy as the standard nested simulation procedure with a lower total computational budget.
 The simulation budget $\Gamma$ is a sum of the computational budget at each level, i.e., $\Gamma = \sum_{\upsilon=0}^{\Upsilon} M_{\upsilon} \cdot N_{\upsilon}$.
-Neither the standard nested simulation procedure nor the MLMC method involves pooling the inner replications from all outer scenarios.
+Neither the standard nested simulation procedure nor the \gls{mlmc} method involves pooling the inner replications from all outer scenarios.
 Pooling enhances sample efficiency and distinguishes advanced nested simulation procedures from the standard procedure.
@@
 However, studying the expectation in Equation~\eqref{eq1:sl-E} is unrealistic, as in practice the risk measure $\rho$ is estimated with a finite number of samples.
-Using the $M$ \textit{training} samples, a supervised learning-based nested MC estimator of $\rho$ is given by
+Using the $M$ \textit{training} samples, a supervised learning-based nested \gls{mc} estimator of $\rho$ is given by
 
@@
             \end{equation}
-    \item   VaR:
+    \item   \gls{var}:
             \begin{equation*}
@@
             \end{equation*}
-    \item   CVaR:
+    \item   \gls{var}:
+            \begin{equation*}
+              \hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = \hat{L}^{\text{SL}}_{(\lceil \alpha M \rceil)}.  
+            \end{equation*}
+    \item   \gls{cvar}:
             \begin{equation*}
@@
             \end{equation*}
-    \item   CVaR:
+    \item   \gls{var}:
+            \begin{equation*}
+              \hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = \hat{L}^{\text{SL}}_{(\lceil \alpha M' \rceil)}.  
+            \end{equation*}
+    \item   \gls{cvar}:
             \begin{equation*}
@@
 In this study, we focus on the metamodeling approaches that include theoretical convergence results.
-Methods that include theoretical convergence results are regression~\citep{broadie2015risk}, kernel smoothing~\citep{hong2017kernel}, and KRR~\citep{wang2022smooth}.
+Methods that include theoretical convergence results are regression~\citep{broadie2015risk}, kernel smoothing~\citep{hong2017kernel}, and \gls{krr}~\citep{wang2022smooth}.
 Their estimators of $L(\cdot)$ are given by $\hat{L}^{\text{REG}}_{M, N}(\cdot)$, $\hat{L}^{\text{KS}}_{M, N}(\cdot)$, and $\hat{L}^{\text{KRR}}_{M, N}(\cdot)$, respectively.
@@
 
-    \item   kNN~\citep{mack1981local}:
+    \item   \gls{knn}~\citep{mack1981local}:
             \begin{equation*}
@@
             where $\|\cdot\|$ is the Euclidean norm, and  $k$ is a number of nearest neighbors to consider.
-            The kNN method is implemented as a metamodel for numerical experiments in~\cite{hong2017kernel}, but the convergence analysis is not provided.
-
-    \item   KRR:
+            The \gls{knn} method is implemented as a metamodel for numerical experiments in~\cite{hong2017kernel}, but the convergence analysis is not provided.
+
+    \item   \gls{var}:
             $$\hat{L}^{\text{KRR}}_{M, N}(X) = \argmin_{g \in \mathcal{N}_{\Psi}(\Omega)} \left( \frac{1}{M} \sum_{i=1}^M (\hat{L}_{N, i} - L_i)^2 + \lambda \|L\|_{\mathcal{N}_{\Psi}(\Omega)}^2\right),$$
-            where $\mathcal{N}_{\Psi}(\Omega)$ is a reproducing kernel Hilbert space (RKHS) with a kernel $\Psi$ defined on a domain $\Omega$, and $\lambda$ is a regularization parameter as in a ridge regression.
+            where $\mathcal{N}_{\Psi}(\Omega)$ is a \gls{rkhs} with a kernel $\Psi$ defined on a domain $\Omega$, and $\lambda$ is a regularization parameter as in a ridge regression. 
             More specifically, $\Phi$ is a Mat\'ern kernel with a smoothness parameter $\nu$ and a length scale parameter $\upsilon$.
-            ~\cite{wang2022smooth} provides a convergence analysis for the AE (Equation~\eqref{eq1:ae}), and the convergence analysis is provided for a smooth, a Lipschitz continuous, and an indicator $h$, VaR, and CVaR.
+            ~\cite{wang2022smooth} provides a convergence analysis for the \gls{ae} (Equation~\eqref{eq1:ae}), and the convergence analysis is provided for a smooth, a Lipschitz continuous, and an indicator $h$, \gls{var}, and \gls{cvar}.
 \end{itemize}
@@
 Regression models can be further categorized into parametric and non-parametric regressions.
-Among the supervised learning models we consider, multiple linear regression is parametric, while kernel smoothing and kernel ridge regression are non-parametric.
-
-We aim to minimize the MSE of the supervised learning-based nested simulation estimators $\hat{\rho}^{\text{SL}, \text{Train}}_{M, N}$ and $\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'}$ subject to the total simulation budget $\Gamma$.
+Among the supervised learning models we consider, multiple linear regression is parametric, while kernel smoothing and \gls{krr} are non-parametric.
+
+We aim to minimize the \gls{mse} of the supervised learning-based nested simulation estimators $\hat{\rho}^{\text{SL}, \text{Train}}_{M, N}$ and $\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'}$ subject to the total simulation budget $\Gamma$.
 We are also interested in the order of convergence of the estimator for all nested simulation procedures as the total simulation budget $\Gamma$ approaches infinity.
@@
 
-For the more complex metamodels, the convergence analysis of their MSEs is more challenging.
-More specifically, the KRR-based nested simulation~\citep{wang2022smooth} provides a convergence analysis in terms of AE.
+For the more complex metamodels, the convergence analysis of their \gls{mse}s is more challenging.
+More specifically, the \gls{var}-based nested simulation~\citep{wang2022smooth} provides a convergence analysis in terms of \gls{ae}.
 \begin{align}\label{eq1:ae}
@@
 \end{align}
-Section~\ref{sec1:connection-mse-absolute-error} draws the connection between the MSE and the AE of the estimator in the context of nested simulation procedures.
+Section~\ref{sec1:connection-mse-absolute-error} draws the connection between the \gls{mse} and the \gls{ae} of the estimator in the context of nested simulation procedures.
 
@@
 
-With a total simulation budget $\Gamma$, we are interested in the orders of convergence of estimators for all nested simulation procedures, which are measured by their MSE about the risk measure $\rho$.
+With a total simulation budget $\Gamma$, we are interested in the orders of convergence of estimators for all nested simulation procedures, which are measured by their \gls{mse} about the risk measure $\rho$.
 
@@
 where $\Gamma$ is a simulation budget for a nested simulation procedure.
-A special case is the MLMC method, where the total simulation budget $\Gamma$ is the sum of the simulation budgets at all levels.
+A special case is the \gls{mlmc} method, where the total simulation budget $\Gamma$ is the sum of the simulation budgets at all levels.
 
@@
     \item provide the asymptotic convergence results for the standard nested simulation procedure, 
-    \item show the connections between the convergence in MSE and the convergence in probabilistic order for AE in the context of nested simulation procedures, and
-    \item illustrate the asymptotic rate of convergence of a kNN-based nested simulation procedure.
+    \item show the connections between the convergence in \gls{mse} and the convergence in probabilistic order for \gls{ae} in the context of nested simulation procedures, and
+    \item illustrate the asymptotic rate of convergence of a \gls{knn}-based nested simulation procedure.
 \end{itemize}
@@
     \hline
-    \textbf{Estimator for} $L$ & \textbf{Smooth} $h$ & \textbf{Lipschitz}(\textbf{hockey-stick} $h$) & \textbf{Indicator} $h$ & \textbf{VaR} & \textbf{CVaR} \\
+    \textbf{Estimator for} $L$ & \textbf{Smooth} $h$ & \textbf{Lipschitz}(\textbf{hockey-stick} $h$) & \textbf{Indicator} $h$ & \textbf{\gls{var}} & \textbf{\gls{cvar}} \\
     \hline
@@
 
-Table~\ref{tab1:asymConv-mse} summarizes the existing asymptotic convergence results of nested simulation procedures for MSE in the literature.
+Table~\ref{tab1:asymConv-mse} summarizes the existing asymptotic convergence results of nested simulation procedures for \gls{mse} in the literature.
 A $\checkmark$ indicates there exists an asymptotic convergence result for the corresponding estimator,
@@
 a $\Diamond$ indicates that an asymptotic convergence result exists in the literature, though in a weaker form.
-~\cite{gordy2010nested} provide asymptotic convergence results for the standard nested simulation procedure with a hockey-stick $h$, an indicator $h$ and VaR.
-Their CVaR analysis is incomplete as the VaR is assumed to be known but not estimated in the convergence proof.
-When the VaR is known, the CVaR analysis reduces to the nested expectation form with $h$ being a hockey-stick function.
-~\cite{giles2019multilevel} provide asymptotic convergence results for the MLMC method with an indicator $h$.
+~\cite{gordy2010nested} provide asymptotic convergence results for the standard nested simulation procedure with a hockey-stick $h$, an indicator $h$ and \gls{var}.
+Their \gls{cvar} analysis is incomplete as the \gls{var} is assumed to be known but not estimated in the convergence proof.
+When the \gls{var} is known, the \gls{cvar} analysis reduces to the nested expectation form with $h$ being a hockey-stick function.
+~\cite{giles2019multilevel} provide asymptotic convergence results for the \gls{mlmc} method with an indicator $h$.
 ~\cite{broadie2015risk} provide asymptotic convergence results for the regression-based nested simulation procedure with a smooth $h$ and a Lipschitz continuous $h$.
@@
 
-While most of the literature focuses on the MSE of the estimator of $\rho$,~\cite{wang2022smooth} analyze the asymptotic convergence of the estimator of $\rho$ in terms of AE.
+While most of the literature focuses on the \gls{mse} of the estimator of $\rho$,~\cite{wang2022smooth} analyze the asymptotic convergence of the estimator of $\rho$ in terms of \gls{ae}.
 Let $\hat{\rho}$ be the estimator of $\rho$. 
-Then the AE of $\hat{\rho}$ about $\rho$ is defined as
+Then the \gls{ae} of $\hat{\rho}$ about $\rho$ is defined as
 
@@
 
-In~\cite{wang2022smooth}, the authors of the KRR-based nested simulation procedures claim to have bridged the gap between the cubic and square root convergence rates of nested simulation procedures.
-However, they analyze convergence in probabilistic order, and it is only applicable in terms of AE.
-Instead of showing the convergence of the KRR-based estimator in terms of MSE as in~\cite{gordy2010nested}, we show the connections between the convergence in MSE and the convergence in probabilistic order for AE.
-Our findings in Section~\ref{sec1:connection-mse-absolute-error} show that the analysis of ~\cite{wang2022smooth} indeed bridges the gap, but only in terms of convergence in probabilistic order for AE.
-
-\subsection{Connections between Convergence in MSE and AE}\label{sec1:connection-mse-absolute-error}
-
-This section establishes the connections between the convergence in MSE and the convergence in probabilistic order for AE in the context of nested simulation procedures.
-In order to show the connections between the convergence in MSE and the convergence in probabilistic order for AE, we first need to state the definition for a sequence of random variables to converge in those two forms.
+In~\cite{wang2022smooth}, the authors of the \gls{var}-based nested simulation procedures claim to have bridged the gap between the cubic and square root convergence rates of nested simulation procedures.
+However, they analyze convergence in probabilistic order, and it is only applicable in terms of \gls{ae}.
+Instead of showing the convergence of the \gls{var}-based estimator in terms of \gls{mse} as in~\cite{gordy2010nested}, we show the connections between the convergence in \gls{mse} and the convergence in probabilistic order for \gls{ae}.
+Our findings in Section~\ref{sec1:connection-mse-absolute-error} show that the analysis of ~\cite{wang2022smooth} indeed bridges the gap, but only in terms of convergence in probabilistic order for \gls{ae}.
+
+\subsection{Connections between Convergence in \gls{mse} and AE}\label{sec1:connection-mse-absolute-error}
+
+This section establishes the connections between the convergence in \gls{mse} and the convergence in probabilistic order for \gls{ae} in the context of nested simulation procedures.
+In order to show the connections between the convergence in \gls{mse} and the convergence in probabilistic order for \gls{ae}, we first need to state the definition for a sequence of random variables to converge in those two forms.
 
@@
     Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
-    We write $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-\xi} \right)$, that is, $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $\xi$ if there exists a constant $C$ such that
+    We write $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-\xi} \right)$, that is, $\hat{\rho}_{\Gamma}$ converges in \gls{mse} to $\rho$ in order $\xi$ if there exists a constant $C$ such that
     $$
@@
 
-We start our analysis by showing the convergence in probabilistic order from the convergence in MSE.
+We start our analysis by showing the convergence in probabilistic order from the convergence in \gls{mse}.
 Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-\xi} \right)$.
-Then, from the definition of convergence in MSE, there exists a constant $C$ such that 
+Then, from the definition of convergence in \gls{mse}, there exists a constant $C$ such that 
 $$
@@
 To the best of our knowledge, Theorem~\ref{thm1:convergence-mse-prob} has not been explicitly stated in the literature.
-It is the first result that shows the connections between the convergence in MSE and the convergence in probabilistic order for AE in the context of nested simulation.
-Theorem~\ref{thm1:convergence-mse-prob} is a general result that can be applied to any nested simulation procedure that converges in MSE to $\rho$ in order $\xi$.
-If the estimator converges in MSE to $\rho$ in order $\xi$, then it converges in probabilistic order to $\rho$ in order $\frac{\xi}{2}$.
-
-While the convergence in MSE implies the convergence in probabilistic order, the converse is not necessarily true.
+It is the first result that shows the connections between the convergence in \gls{mse} and the convergence in probabilistic order for \gls{ae} in the context of nested simulation.
+Theorem~\ref{thm1:convergence-mse-prob} is a general result that can be applied to any nested simulation procedure that converges in \gls{mse} to $\rho$ in order $\xi$.
+If the estimator converges in \gls{mse} to $\rho$ in order $\xi$, then it converges in probabilistic order to $\rho$ in order $\frac{\xi}{2}$.
+
+While the convergence in \gls{mse} implies the convergence in probabilistic order, the converse is not necessarily true.
 Similarly, the above argument is applied in reverse.
 Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-\xi})$.
-The MSE of $\hat{\rho}_{\Gamma}$ can be separated into the same two parts.
+The \gls{mse} of $\hat{\rho}_{\Gamma}$ can be separated into the same two parts.
 
@@
 \end{align*}
-Hence, $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $2\xi$ if and only if both integrals converge in order higher than $2\xi$. 
-The above argument shows that the convergence in probabilistic order does not necessarily imply the convergence in MSE.
-Hence, the converse of Theorem~\ref{thm1:convergence-mse-prob} is not necessarily true, and the convergence in probabilistic order is a weaker form of convergence than the convergence in MSE.
-The immediate implication of this result is that the results in~\cite{wang2022smooth}, which show the convergence in probabilistic order for the AE is not necessarily equivalent to the convergence in MSE.
+Hence, $\hat{\rho}_{\Gamma}$ converges in \gls{mse} to $\rho$ in order $2\xi$ if and only if both integrals converge in order higher than $2\xi$. 
+The above argument shows that the convergence in probabilistic order does not necessarily imply the convergence in \gls{mse}.
+Hence, the converse of Theorem~\ref{thm1:convergence-mse-prob} is not necessarily true, and the convergence in probabilistic order is a weaker form of convergence than the convergence in \gls{mse}.
+The immediate implication of this result is that the results in~\cite{wang2022smooth}, which show the convergence in probabilistic order for the \gls{ae} is not necessarily equivalent to the convergence in \gls{mse}.
 
 \subsection{Asymptotic Analysis for the Standard Nested Simulation Procedure}\label{sec1:sns}
-In~\cite{gordy2010nested}, the authors analyze the asymptotic convergence of the standard nested simulation procedure in terms of MSE. 
-The analysis is complete for the nested expectation form where $h$ is either an indicator function or a hockey-stick function and VaR. 
+In~\cite{gordy2010nested}, the authors analyze the asymptotic convergence of the standard nested simulation procedure in terms of \gls{mse}. 
+The analysis is complete for the nested expectation form where $h$ is either an indicator function or a hockey-stick function and \gls{var}. 
 For the nested expectation form where $h$ is a smooth function or a Lipschitz continuous function, the analysis is incomplete.
@@
 For simplicity, we abbreviate $\hat{L}_N(X)$ as $\hat{L}_N$, $\bar{Z}_N(X)$ as $\bar{Z}_N$, and $\bar{Z}_{N, i}$ as $\bar{Z}_{N, i}$.
-Let $\rho_M = \frac{1}{M} \sum_{i=1}^M h(L_i)$ be a nested MC estimator with the true function $g$.
-The MSE of the standard nested simulation procedure can be decomposed into two ways.
+Let $\rho_M = \frac{1}{M} \sum_{i=1}^M h(L_i)$ be a nested \gls{mc} estimator with the true function $g$.
+The \gls{mse} of the standard nested simulation procedure can be decomposed into two ways.
 
@@
 
-Another way to decompose the MSE is a bias-variance decomposition as in~\cite{gordy2010nested}.
+Another way to decompose the \gls{mse} is a bias-variance decomposition as in~\cite{gordy2010nested}.
 
@@
 where $\text{Var}(\hat{\rho}_{M, N})$ is variance of the estimator and $\text{Bias}(\hat{\rho}_{M, N})$ is bias of the estimator about $\rho$.
-For a smooth function $h$, both ways of decomposing the MSE lead to the same order of convergence.
+For a smooth function $h$, both ways of decomposing the \gls{mse} lead to the same order of convergence.
 However, for a Lipschitz continuous function $h$, Equation~\eqref{eq1:mse-sns2} leads to a stronger order of convergence than Equation~\eqref{eq1:mse-sns}.
@@
 \end{align}
-where the last inequality is due to $2ab \leq a^2 + b^2$ for any $a, b \in \mathbb{R}$. 
+where \textcolor{red}{$z_i$ is between $L_i$ and $\hat{L}_{N,i}$, and} the last inequality is due to $2ab \leq a^2 + b^2$ for any $a, b \in \mathbb{R}$. 
 The two terms on the right-hand side of Equation~\eqref{eq1:taylor-sns} are analyzed separately.
@@
 \end{align}
-where the second inequality is due to Assumption~\ref{as1:sns-smooth}, and the last inequality follows from Assumption~\ref{as1:sns-noise-var} and the fact that $\hat{L}_N$ is a standard MC estimator of $L$.
+where the second inequality is due to Assumption~\ref{as1:sns-smooth}, and the last inequality follows from Assumption~\ref{as1:sns-noise-var} and the fact that $\hat{L}_N$ is a standard \gls{mc} estimator of $L$.
 Combining Equation~\eqref{eq1:mse-sns},~\ref{eq1:taylor-sns},~\ref{eq1:s1-sns}, and~\ref{eq1:s2-sns}, we have
@@
 \end{align}
-where the last equality follows from the Taylor expansion of the smooth function $h$.
+where \textcolor{red}{$z_i$ is between $L_i$ and $\hat{L}_{N,i}$, and} the last equality follows from the Taylor expansion of the smooth function $h$.
 The first and second order Taylor expansion terms are analyzed separately in Equation~\eqref{eq1:bias-sns-smooth-Taylor1} and Equation~\eqref{eq1:bias-sns-smooth-Taylor2}.
@@
 
-Equation~\eqref{eq1:var-sns-smooth} directly follows from Assumption~\ref{as1:sns} and the fact that $\hat{L}_N$ is a standard MC estimator of $L$.
+Equation~\eqref{eq1:var-sns-smooth} directly follows from Assumption~\ref{as1:sns} and the fact that $\hat{L}_N$ is a standard \gls{mc} estimator of $L$.
 Combining Equation~\eqref{eq1:bias-sns-smooth-Taylor1},~\ref{eq1:bias-sns-smooth-Taylor2}, and~\ref{eq1:var-sns-smooth}, we are able to show the convergence order of the standard nested simulation procedure for a smooth function $h$ without the cross term as in Equation~\eqref{eq1:s1-sns}.
@@
 Assumption~\ref{as1:sns-noise-var} is a moment condition that is easier to verify in practice than conditions on the joint density.
-As stated in Theorem~\ref{thm1:convergence-mse-prob}, the convergence in MSE automatically implies the convergence in probabilistic order.
+As stated in Theorem~\ref{thm1:convergence-mse-prob}, the convergence in \gls{mse} automatically implies the convergence in probabilistic order.
 
@@
 We proceed to analyze the convergence for a Lipschitz continuous function $h$.
-For the CVaR analysis in~\cite{gordy2010nested}, the authors assume the knowledge of the corresponding VaR.
-Hence, the analysis of CVaR is not complete.
+For the \gls{cvar} analysis in~\cite{gordy2010nested}, the authors assume the knowledge of the corresponding \gls{var}.
+Hence, the analysis of \gls{cvar} is not complete.
 Instead, the quantity that is being analyzed is the mean excess loss, which corresponds to $h$ being a hockey-stick function and belongs to the family of the Lipschitz continuous functions. 
@@
 
-Immediately from Theorem~\ref{thm1:convergence-mse-prob}, the convergence in MSE automatically implies the convergence in probabilistic order.
+Immediately from Theorem~\ref{thm1:convergence-mse-prob}, the convergence in \gls{mse} automatically implies the convergence in probabilistic order.
 
@@
 
-In~\cite{hong2017kernel}, the authors analyze the asymptotic convergence in terms of MSE for a kernel smoothing-based nested simulation procedure.
+In~\cite{hong2017kernel}, the authors analyze the asymptotic convergence in terms of \gls{mse} for a kernel smoothing-based nested simulation procedure.
 The analysis is complete for the nested expectation form where $h$ is either a smooth function, an indicator function, or a hockey-stick function.
 The kernel function of interest in the asymptotic analysis is the Nadaraya-Watson kernel.
-Nevertheless, the numerical results are derived based on a kNN-based nested simulation procedure.
-In this section, we attempt to fill in the holes in the analysis of~\cite{hong2017kernel} by providing asymptotic convergence of a kNN-based nested simulation procedure for smooth $h$ in the nested expectation form.
-Surprisingly, the asymptotic convergence rate of the kNN-based nested simulation procedure is noticeably different from the result obtained in~\cite{hong2017kernel}.
-
-A kNN regression can be used as a non-parametric metamodel that estimates the conditional expectation of $Y$ given $X$ by averaging the $Y$ values of the $k$ nearest neighbors of $X$.
+Nevertheless, the numerical results are derived based on a \gls{knn}-based nested simulation procedure.
+In this section, we attempt to fill in the holes in the analysis of~\cite{hong2017kernel} by providing asymptotic convergence of a \gls{knn}-based nested simulation procedure for smooth $h$ in the nested expectation form.
+Surprisingly, the asymptotic convergence rate of the \gls{knn}-based nested simulation procedure is noticeably different from the result obtained in~\cite{hong2017kernel}.
+
+A \gls{knn} regression can be used as a non-parametric metamodel that estimates the conditional expectation of $Y$ given $X$ by averaging the $Y$ values of the $k$ nearest neighbors of $X$.
 Without loss of generality, we assume that $\{(X_i, \bar{Y}_{n, i}), i = 1, \dots, M\}$ are i.i.d.
@@
 
-A kNN-based nested simulation procedure with a model parameter $k$ estimates the risk measure $\rho = \mathbb{E} \left[ h(L) \right]$ with
+A \gls{knn}-based nested simulation procedure with a model parameter $k$ estimates the risk measure $\rho = \mathbb{E} \left[ h(L) \right]$ with
 
@@
 where $\|\cdot\|$ is a Euclidean norm, and $k$ is a number of nearest neighbors to consider.
-For a kNN estimator trained with $M$ i.i.d. observations, denote $B_M(x)$ and $V_M(x)$ as its bias and variance at point $x$, respectively.
+For a \gls{knn} estimator trained with $M$ i.i.d. observations, denote $B_M(x)$ and $V_M(x)$ as its bias and variance at point $x$, respectively.
 
@@
 
-The following lemma from~\cite{mack1981local} characterizes pointwise convergence of the kNN estimator in terms of its bias and variance at point $x$.
+The following lemma from~\cite{mack1981local} characterizes pointwise convergence of the \gls{knn} estimator in terms of its bias and variance at point $x$.
 
@@
 Let $h$ be a smooth function, i.e., Assumption~\ref{as1:sns-smooth} holds.
-The bias of the estimator of $\rho$ for a kNN-based nested simulation procedure is analyzed following a Taylor expansion.
+The bias of the estimator of $\rho$ for a \gls{knn}-based nested simulation procedure is analyzed following a Taylor expansion.
 \begin{align}\label{eq1:bias-knn}
@@
 The first term in Equation~\eqref{eq1:bias-knn-2} is $\mathcal{O}\left(\frac{1}{k}\right)$.
-Set $k = \mathcal{O}(M^{\frac{2}{2+d}})$ and $M = \mathcal{O}(\Gamma)$, the bias of the kNN-based nested simulation procedure converges in the order of $\Gamma^{-\frac{2}{2+d}}$.
+Set $k = \mathcal{O}(M^{\frac{2}{2+d}})$ and $M = \mathcal{O}(\Gamma)$, the bias of the \gls{knn}-based nested simulation procedure converges in the order of $\Gamma^{-\frac{2}{2+d}}$.
 
@@
 Definition~\ref{def:knn-smooth-bias} is obtained by matching the orders of the bias terms in Equation~\eqref{eq1:bias-knn-1} and~\ref{eq1:bias-knn-2}.
-It is the tightest bound that can be obtained for the convergence of the kNN-based nested simulation procedure with a smooth function $h$.
+It is the tightest bound that can be obtained for the convergence of the \gls{knn}-based nested simulation procedure with a smooth function $h$.
 The variance is left for future work.
-It implies that the kNN-based nested simulation procedure converges at most in the order of $\Gamma^{-\frac{2}{3}}$ for $d = 1$ and has slower convergence than the standard procedure for $d \geq 2$.
+It implies that the \gls{knn}-based nested simulation procedure converges at most in the order of $\Gamma^{-\frac{2}{3}}$ for $d = 1$ and has slower convergence than the standard procedure for $d \geq 2$.
 Asymptotically, it has slower convergence than the result obtained in~\cite{hong2017kernel} for the Nadaraya-Watson kernel.
 This discrepancy underscores the critical importance of aligning theoretical analysis with numerical illustrations.
-The slower convergence rate observed with the kNN approach not only challenges the robustness of empirical findings derived under differing assumptions but also signals a cautionary note for practitioners.
+The slower convergence rate observed with the \gls{knn} approach not only challenges the robustness of empirical findings derived under differing assumptions but also signals a cautionary note for practitioners.
 This alignment is crucial for ensuring the reliability and validity of conclusions drawn from such procedures, especially in the context of risk management and financial decision-making.
@@
     \hline
-    \textbf{Estimator for} $L$ & \textbf{Smooth} $h$ & \textbf{Lipschitz} / \textbf{hockey-stick} $h$ & \textbf{Indicator} $h$ & \textbf{VaR} & \textbf{CVaR} \\
-    \hline
-    Standard MC & $\mathcal{O}(\Gamma^{-2/3})$ & $\mathcal{O}(\Gamma^{-1/2})$ / $\mathcal{O}(\Gamma^{-2/3})$ & $\mathcal{O}(\Gamma^{-2/3})$ & $\mathcal{O}(\Gamma^{-2/3})$ & $\times$ \\
-    \hline
-    Multi-level MC & $\times$ & $\times$ / $\times$ & $\mathcal{O}(\Gamma^{-1}|\log(\Gamma)|
+    \textbf{Estimator for} $L$ & \textbf{Smooth} $h$ & \textbf{Lipschitz} / \textbf{hockey-stick} $h$ & \textbf{Indicator} $h$ & \textbf{\gls{var}} & \textbf{\gls{cvar}} \\
+    \hline
+    Standard \gls{mc} & $\mathcal{O}(\Gamma^{-2/3})$ & $\mathcal{O}(\Gamma^{-1/2})$ / $\mathcal{O}(\Gamma^{-2/3})$ & $\mathcal{O}(\Gamma^{-2/3})$ & $\mathcal{O}(\Gamma^{-2/3})$ & $\times$ \\
+    \hline
+    Multi-level \gls{mc} & $\times$ & $\times$ / $\times$ & $\mathcal{O}(\Gamma^{-1}|\log(\Gamma)|
     )$ & $\times$ & $\times$ \\
@@
     \end{tabular}
-    \caption{Asymptotic rate of convergence of nested simulation procedures in MSE}
+    \caption{Asymptotic rate of convergence of nested simulation procedures in \gls{mse}}
 \label{tab1:asymConv-order}
@@
 \subsection{Assumptions for the MLMC Procedure}
-In addition to Assumption~\ref{as1:sns-joint-density-bound}, the MLMC procedure requires assumptions on the random variable $Q:= \frac{|\mathbb{E} \left[ Y | X \right]|}{\text{Var}[Y|X]}$.
+In addition to Assumption~\ref{as1:sns-joint-density-bound}, the \gls{mlmc} procedure requires assumptions on the random variable $Q:= \frac{|\mathbb{E} \left[ Y | X \right]|}{\text{Var}[Y|X]}$.
 
@@
 \subsection{Assumptions for the KRR-Based Procedure}
-For the KRR-based nested simulation procedure, the convergence is guaranteed only when $\bar{Z}_N(X)$ is the sum of $N$ i.i.d. zero-mean sub-Gaussian random variables.
+For the \gls{var}-based nested simulation procedure, the convergence is guaranteed only when $\bar{Z}_N(X)$ is the sum of $N$ i.i.d. zero-mean sub-Gaussian random variables.
 The sub-Gaussian assumption imposes a stronger condition on the inner simulation noise than all the other nested simulation procedures.
@@
 Assumption~\ref{as1:krr-domain} rules out the possibility of the outer scenario $X$ being a normal random variable, which is a common assumption in the literature.
-Furthermore, the convergence analysis of the KRR-based nested simulation procedure is shown in terms of AE rather than in MSE, which is due to the complexity of the KRR metatmodel.
+Furthermore, the convergence analysis of the \gls{var}-based nested simulation procedure is shown in terms of \gls{ae} rather than in \gls{mse}, which is due to the complexity of the KRR metatmodel.
 
@@
 
-A total of 5 nested simulation procedures are considered, namely a standard nested simulation procedure, a  regression-based, a kernel smoothing-based, a likelihood ratio-based, and a kernel ridge regression-based nested simulation procedure.
+A total of 5 nested simulation procedures are considered, namely a standard nested simulation procedure, a  regression-based, a kernel smoothing-based, a likelihood ratio-based, and a \gls{krr}-based nested simulation procedure.
 For the standard nested simulation procedure, the bootstrap-based budget allocation strategy from~\cite{zhang2021bootstrap} is implemented to estimate the optimal values of outer and inner simulation budgets.
 For the regression metamodel, the Laguerre polynomials up to degree $3$ are used as the default basis functions.
-The kNN metamodel is implemented for the kernel smoothing-based procedure, and a cross-validation procedure with a grid search is used to find the optimal number of neighbors.
-The KRR metamodel is implemented with a Mat\'ern kernel, and the smoothness, the length scale, and the regularization hyperparameters are found by a cross-validation procedure with a Bayesian search~\citep{frazier2018bayesian}.
+The \gls{knn} metamodel is implemented for the kernel smoothing-based procedure, and a cross-validation procedure with a grid search is used to find the optimal number of neighbors.
+The \gls{var} metamodel is implemented with a Mat\'ern kernel, and the smoothness, the length scale, and the regularization hyperparameters are found by a cross-validation procedure with a Bayesian search~\citep{frazier2018bayesian}.
 Due to budget constraints, the hyperparameters of the non-parametric regression metamodel are tuned and used across all macro replications of the same experiment.
@@
     \item a probability of a large loss over a threshold $u$,
-    \item the VaR, and
-    \item the CVaR,
+    \item the \gls{var}, and
+    \item the \gls{cvar},
 \end{itemize}
-where the threshold $u$ for the mean excess loss and the probability of a large loss is set to be 90\% VaR.
+where the threshold $u$ for the mean excess loss and the probability of a large loss is set to be 90\% \gls{var}.
 The procedures are compared for different portfolios consisting of different types of options:
@@
 525 experiment settings that arise from an exhaustive combination of the above simulation procedures, risk measures, portfolios, and asset dimensions are generated.
-For each experiment setting, the estimation of the risk measure is repeated \num{1000} times to obtain the empirical MSE of the corresponding estimator under a range of simulation budgets.
+For each experiment setting, the estimation of the risk measure is repeated \num{1000} times to obtain the empirical \gls{mse} of the corresponding estimator under a range of simulation budgets.
 The total simulation budget $\Gamma$ ranges from $\num{10000}$ to $\num{10240000}$ in a geometric progression with a common ratio of $2$.
@@
 \end{figure}
-In Figure~\ref{fig1:compareAll}, the MSEs of the nested simulation procedures are plotted against the total simulation budget $\Gamma$ in a log-log scale, where each point represents the average MSE of the corresponding estimator over \num{1000} macro replications of the same experiment.
-Due to the difficulty of fixing $\Gamma$ for the MLMC procedure, the empirical rate of convergence of the MLMC procedure is not reported here, but a detailed analysis of the empirical convergence of the MLMC procedure is provided in Section~\ref{sec1:empirical-mlmc}.
-
-A regression line is fitted to the MSEs of each nested simulation procedure against the simulation budget $\Gamma$ in a log-log scale, and the slope of the fitted line is reported.
+In Figure~\ref{fig1:compareAll}, the \gls{mse}s of the nested simulation procedures are plotted against the total simulation budget $\Gamma$ in a log-log scale, where each point represents the average \gls{mse} of the corresponding estimator over \num{1000} macro replications of the same experiment.
+Due to the difficulty of fixing $\Gamma$ for the \gls{mlmc} procedure, the empirical rate of convergence of the \gls{mlmc} procedure is not reported here, but a detailed analysis of the empirical convergence of the \gls{mlmc} procedure is provided in Section~\ref{sec1:empirical-mlmc}.
+
+A regression line is fitted to the \gls{mse}s of each nested simulation procedure against the simulation budget $\Gamma$ in a log-log scale, and the slope of the fitted line is reported.
 The slopes of the fitted lines can be interpreted as the empirical rates of convergence.
@@
 However, pooling also introduces additional computational cost that is not reflected in the simulation budget $\Gamma$.
-Due to the computational complexity of the likelihood ratio-based and the KRR-based procedures, their MSEs are not reported for $\Gamma$ larger than $\num{16000}$ and $\num{64000}$, respectively.
+Due to the computational complexity of the likelihood ratio-based and the \gls{var}-based procedures, their \gls{mse}s are not reported for $\Gamma$ larger than $\num{16000}$ and $\num{64000}$, respectively.
 Detailed discussion of the additional computational cost of pooling is provided in Section~\ref{sec1:computational-complexity}.
@@
 In Figure~\ref{fig1:assetDimension}, the empirical convergence of the nested simulation procedures for a quadratic tracking error on Portfolio 1 is illustrated for different asset dimensions, i.e., $d = 2$ and $d = 20$.
-The empirical rates of convergence of the standard, the KRR-based, and the likelihood ratio-based procedures closely match their asymptotic rates for both asset dimensions, and they are insensitive to an increase in the asset dimension.
+The empirical rates of convergence of the standard, the \gls{var}-based, and the likelihood ratio-based procedures closely match their asymptotic rates for both asset dimensions, and they are insensitive to an increase in the asset dimension.
 In contrast, both the kernel smoothing-based and regression-based procedures are greatly affected by the asset dimension.
@@
 According to the theoretical analysis in Section~\ref{sec1:asymptotic-convergence}, the asymptotic rate of convergence of the kernel smoothing-based nested simulation procedure is highly dependent on the asset dimension $d$.
-In this section, we use a kNN metamodel for the kernel smoothing-based nested simulation procedure, and we examine its empirical convergence for different asset dimensions.
+In this section, we use a \gls{knn} metamodel for the kernel smoothing-based nested simulation procedure, and we examine its empirical convergence for different asset dimensions.
 
@@
 This is likely due to the fact that the kernel smoothing-based procedure, as a non-parametric regression procedure, is highly dependent on the cross-validation of the hyperparameters of the metamodel.
-For the kernel smoothing-based procedure, the kNN metamodel is implemented. 
+For the kernel smoothing-based procedure, the \gls{knn} metamodel is implemented. 
 Hence, the hyperparameter of interest is the number of nearest neighbors $k$.
 In our numerical experiment, cross-validation is conducted once to select the optimal value of $k$ for each simulation budget, and the selected value of $k$ is fixed for all $\num{1000}$ replications.
-Therefore, a suboptimal selection of the optimal value of $k$ can lead to a poor metamodel estimate, and the MSE of the kRR-based procedure will be dominated by the model error of the metamodel.
+Therefore, a suboptimal selection of the optimal value of $k$ can lead to a poor metamodel estimate, and the \gls{mse} of the kRR-based procedure will be dominated by the model error of the metamodel.
 
@@
 This observation suggests that the empirical convergence of the kernel smoothing-based nested simulation procedure is highly sensitive to the cross-validation of the hyperparameters of the metamodel.
-A KRR-based nested simulation procedure suffers from the same problem. 
+A \gls{var}-based nested simulation procedure suffers from the same problem. 
 The fluctuation in Figure~\ref{fig1:kernel_d} is likely due to poor cross-validation of the hyperparameters of the metamodel.
@@
 When simulation budgets are low, the metamodels trained to approximate the true inner simulation are inadequate.
-The MSEs for these procedures are dominated by the model errors of the metamodels.
+The \gls{mse}s for these procedures are dominated by the model errors of the metamodels.
 In other words, they have not yet reached their asymptotic convergence regimes.
@@
 In our previous numerical experiments, the empirical rate of convergence of the regression procedure is observed to be much larger than its asymptotic rate of convergence.
-For dimensions larger than $10$, the MSE of the regression procedure decreases quickly in the beginning, and its rate of decrease stabilizes after a certain budget level.
+For dimensions larger than $10$, the \gls{mse} of the regression procedure decreases quickly in the beginning, and its rate of decrease stabilizes after a certain budget level.
 In Figure~\ref{fig1:reg_lb} illustrates the empirical convergence of the regression-based procedure in more detail at higher simulation budgets, where the asymptotic level of convergence is reached for $d = 20$.
@@
 
-The left part of Figure \ref{fig1:reg_lb} contains the MSEs of the regression procedure for budget sizes that are smaller than $10^3$. 
+The left part of Figure \ref{fig1:reg_lb} contains the \gls{mse}s of the regression procedure for budget sizes that are smaller than $10^3$. 
 Slopes of the fitted lines on the left correspond to the empirical rate of convergence of the regression procedure for budget levels between $10^3$ and $10^4$.
@@
 For nested simulation procedures with a biased metamodel, the metamodel estimates of the true inner simulation are poor, especially for smaller budget sizes. 
-We are able to clearly observe this phenomenon for the regression metamodel, and it can be explained by dividing the MSE into metamodeling bias and simulation variance.
+We are able to clearly observe this phenomenon for the regression metamodel, and it can be explained by dividing the \gls{mse} into metamodeling bias and simulation variance.
 \begin{itemize}
@@
 \end{itemize}
-Due to high computational costs, we are not able to conduct experiments for higher budget levels, but we expect the MSE of the regression-based nested simulation procedure to stabilize after $\Gamma = 10^6$, and the empirical rate of convergence to approach its asymptotic rate.
+Due to high computational costs, we are not able to conduct experiments for higher budget levels, but we expect the \gls{mse} of the regression-based nested simulation procedure to stabilize after $\Gamma = 10^6$, and the empirical rate of convergence to approach its asymptotic rate.
 In the context of nested simulation procedures, a parametric regression metamodel has several advantages over a non-parametric regression metamodel.
@@
 However, parametric regression suffers from the model misspecification risk.
-More specifically, selecting a wrong regression basis can lead to a poor metamodel estimate, where the MSE of the nested simulation procedure is dominated by the model error of the metamodel~\citep{broadie2015risk}.
+More specifically, selecting a wrong regression basis can lead to a poor metamodel estimate, where the \gls{mse} of the nested simulation procedure is dominated by the model error of the metamodel~\citep{broadie2015risk}.
 
@@
 
-In Figure~\ref{fig1:sens_basis}, the empirical convergence results of the regression-based nested simulation procedure for a quadratic tracking error and a 90\%-CVaR are illustrated for the two different regression bases.
+In Figure~\ref{fig1:sens_basis}, the empirical convergence results of the regression-based nested simulation procedure for a quadratic tracking error and a 90\%-\gls{cvar} are illustrated for the two different regression bases.
 The empirical rates of convergence of the regression-based nested simulation procedure are observed to be insensitive to the chosen regression basis.
@@
 In Figure~\ref{fig1:1x03}, the empirical convergence of the nested simulation procedures for the quadratic tracking errors of Portfolio 1 and Portfolio 4 is illustrated for $d = 20$.
-The empirical rates of standard, likelihood ratio-based, and KRR-based nested simulation procedures closely ensemble their asymptotic rates for path-dependent options.
+The empirical rates of standard, likelihood ratio-based, and \gls{var}-based nested simulation procedures closely ensemble their asymptotic rates for path-dependent options.
 The empirical rate of convergence of the regression-based and kernel smoothing-based procedures is much higher than their asymptotic rates for barrier options. 
@@
 For all procedures, we observe a similar convergence behavior as in other path-dependent options.
-The MSEs of the kernel smoothing-based and KRR-based procedures do not decrease monotonically as the simulation budget increases.
+The \gls{mse}s of the kernel smoothing-based and \gls{var}-based procedures do not decrease monotonically as the simulation budget increases.
 This fluctuating behavior is observed and analyzed in Section~\ref{sec1:kernel-smoothing-convergence}.
@@
 Furthermore, the regression-based procedure is stable across different payoff structures and risk measures. 
-Its MSEs decrease quickly in the beginning, and after reaching a certain level of $\Gamma$, the rate of decrease stabilizes to match its asymptotic rate of convergence.
+Its \gls{mse}s decrease quickly in the beginning, and after reaching a certain level of $\Gamma$, the rate of decrease stabilizes to match its asymptotic rate of convergence.
 Parametric regression is the most attractive metamodel for nested simulation procedures due to its fast empirical convergence behavior, stability across different payoff structures and risk measures, and ease of implementation.
@@
 
-The level of VaR and CVaR is a critical factor that determines the complexity of the risk measure estimation.
-In our previous numerical experiments, the level of VaR and CVaR is set to be the $90\%$ quantile of the distribution of the inner simulation noise.
-In this section, we examine the empirical convergence of the regression-based nested simulation procedures for other levels of VaR and CVaR, i.e., $80\%$, $95\%$, $99\%$, and $99.6\%$.
+The level of \gls{var} and \gls{cvar} is a critical factor that determines the complexity of the risk measure estimation.
+In our previous numerical experiments, the level of \gls{var} and \gls{cvar} is set to be the $90\%$ quantile of the distribution of the inner simulation noise.
+In this section, we examine the empirical convergence of the regression-based nested simulation procedures for other levels of \gls{var} and \gls{cvar}, i.e., $80\%$, $95\%$, $99\%$, and $99.6\%$.
 
@@
 
-In Figure~\ref{fig1:sens_level}, the empirical convergence of the regression-based nested simulation procedure for different levels of VaR and CVaR is illustrated for up-and-out barrier call options.
-The empirical rates of convergence of the regression-based nested simulation procedure are not sensitive to the level of VaR and CVaR.
+In Figure~\ref{fig1:sens_level}, the empirical convergence of the regression-based nested simulation procedure for different levels of \gls{var} and \gls{cvar} is illustrated for up-and-out barrier call options.
+The empirical rates of convergence of the regression-based nested simulation procedure are not sensitive to the level of \gls{var} and \gls{cvar}.
 
@@
 To examine the sensitivity of the empirical convergence behavior to the asset model, we consider a stochastic volatility model of a Heston type~\citep{heston1993closed}.
+\textcolor{red}{In a Heston model, the asset price and the volatility are correlated, and the volatility is a stochastic process.}
+
+\begin{align*}
+    dS_t &= \mu S_t dt + \sqrt{v_t} S_t dW_{1,t}, \\
+    dv_t &= \kappa (\theta - v_t) dt + \xi \sqrt{v_t} dW_{2,t},
+\end{align*}
+where $W_{1,t}$ and $W_{2,t}$ are two independent Brownian motions.
+
+\textcolor{red}{In this experiment, the initial asset price and the volatility are set to be $100$ and $0.2$, respectively.
+The parameters are set to be $\mu = 0.08$, $\kappa = 2$, $\theta = 0.04$, $\xi = 0.1$.}
 
@@
 
-In Figure~\ref{fig1:sens_model}, the empirical convergence results of the regression-based nested simulation procedure for a quadratic tracking error and a 90\%-CVaR are illustrated for different asset models, i.e., a geometric Brownian motion and a Heston model.
+In Figure~\ref{fig1:sens_model}, the empirical convergence results of the regression-based nested simulation procedure for a quadratic tracking error and a 90\%-\gls{cvar} are illustrated for different asset models, i.e., a geometric Brownian motion and a Heston model.
 The empirical rates of convergence of the regression-based nested simulation procedure are observed to be insensitive to the asset model.
 
-In summary, we find the empirical convergence behavior of the regression-based nested simulation procedure to be stable across different risk measures, option types, asset dimensions, levels of VaR and CVaR, asset models, and regression bases.
+In summary, we find the empirical convergence behavior of the regression-based nested simulation procedure to be stable across different risk measures, option types, asset dimensions, levels of \gls{var} and \gls{cvar}, asset models, and regression bases.
 With a limited total budget, the regression-based nested simulation procedure is the most robust and stable among all nested simulation procedures.
@@
 
-The MLMC procedure is a variance reduction technique that is designed to reduce the computational cost of nested simulation procedures.
-The theoretical analysis in~\cite{giles2019multilevel} shows that the MLMC procedure has a faster empirical rate of convergence than the standard nested simulation procedure when the risk measure of interest is the probability of a large loss over a threshold $u$, i.e., the nested expectation case with $h$ being an indicator function.
+The \gls{mlmc} procedure is a variance reduction technique that is designed to reduce the computational cost of nested simulation procedures.
+The theoretical analysis in~\cite{giles2019multilevel} shows that the \gls{mlmc} procedure has a faster empirical rate of convergence than the standard nested simulation procedure when the risk measure of interest is the probability of a large loss over a threshold $u$, i.e., the nested expectation case with $h$ being an indicator function.
 \textcolor{red}{In this numerical experiment, the initial number of inner replications, the refinement factor, the r-value for adaptive algorithm are set to be $4$, $4$, and $1.5$, respectively.}
-\textcolor{red}{We note that the MLMC procedure focuses on adaptive allocation of the simulation budget and is fundamentally different from supervised learning-based nested simulation procedures.
+\textcolor{red}{We note that the \gls{mlmc} procedure focuses on adaptive allocation of the simulation budget and is fundamentally different from supervised learning-based nested simulation procedures.
 And their results are not directly comparable.}
@@
 
-We provide a summary of the empirical convergence results of the MLMC procedure with a decomposition table of the MSEs in Table~\ref{tab1:mlmc-mse}.
-The MSEs of the MLMC procedure are decomposed into the bias and the variance of the estimator.
-The MSEs of the standard nested simulation procedure with a similar total simulation budget are also provided for comparison.
-Since the MLMC procedure is designed with a fixed number of outer simulation paths, the benefit of the MLMC procedure is minimal when the total simulation budget is large.
-More specifically, when $\Gamma$ is large, the standard nested simulation procedure with a bootstrap-based budget allocation strategy benefits from having a larger number of outer simulation paths, and the MSE of the standard nested simulation procedure is lower than that of the MLMC procedure with a fixed number of outer simulation paths.
+We provide a summary of the empirical convergence results of the \gls{mlmc} procedure with a decomposition table of the \gls{mse}s in Table~\ref{tab1:mlmc-mse}.
+The \gls{mse}s of the \gls{mlmc} procedure are decomposed into the bias and the variance of the estimator.
+The \gls{mse}s of the standard nested simulation procedure with a similar total simulation budget are also provided for comparison.
+Since the \gls{mlmc} procedure is designed with a fixed number of outer simulation paths, the benefit of the \gls{mlmc} procedure is minimal when the total simulation budget is large.
+More specifically, when $\Gamma$ is large, the standard nested simulation procedure with a bootstrap-based budget allocation strategy benefits from having a larger number of outer simulation paths, and the \gls{mse} of the standard nested simulation procedure is lower than that of the \gls{mlmc} procedure with a fixed number of outer simulation paths.
 
@@
 \end{itemize}
-For the kernel smoothing-based procedure, the kNN metamodel is implemented. 
+For the kernel smoothing-based procedure, the \gls{knn} metamodel is implemented. 
 In practice, the K-D tree algorithm~\citep{bentley1975multidimensional} is often implemented for an efficient nearest neighbor search.
@@
     A practical implementation of a block sort is provided in~\cite{kim2008ratio}.
-    Hence, an efficient implementation of the kNN metamodel is crucial for the kernel smoothing-based procedure.
+    Hence, an efficient implementation of the \gls{knn} metamodel is crucial for the kernel smoothing-based procedure.
 \end{itemize}
@@
 \end{itemize}
-For the KRR-based procedure, 
+For the \gls{var}-based procedure, 
 \begin{itemize}
@@
           Similar to the regression-based procedure, this complexity can be reduced to $\mathcal{O}(M^{2.376})$.
-    \item The prediction cost of the KRR-based procedure is $\mathcal{O}(M^2)$, which comes from the multiplication of the kernel matrix by the estimated coefficients.
+    \item The prediction cost of the \gls{var}-based procedure is $\mathcal{O}(M^2)$, which comes from the multiplication of the kernel matrix by the estimated coefficients.
 \end{itemize}
@@
 In the multiple linear regression, the number of features is usually much less than the number of data points, i.e., $p<M$. 
-Kernel smoothing and KRR are kernel-based metamodels, and they are more computaional expensive due to distance calculations and cross-validations of hyperparameters. 
-The kNN metamodel has only 1 hyperparameter $k$, while the KRR metamodel requires 3 hyperparameters, namely a smoothness hyperparameter $\nu$, a scale hyperparameter $\upsilon$, and a regularization hyperparameter $\lambda$.
+Kernel smoothing and \gls{var} are kernel-based metamodels, and they are more computaional expensive due to distance calculations and cross-validations of hyperparameters. 
+The \gls{knn} metamodel has only 1 hyperparameter $k$, while the \gls{var} metamodel requires 3 hyperparameters, namely a smoothness hyperparameter $\nu$, a scale hyperparameter $\upsilon$, and a regularization hyperparameter $\lambda$.
 Calculating the likelihood ratio weights is inevitable for the likelihood ratio-based procedure. 
-While a k-fold cross-validation is used to estimate the hyperparameter for kNN, the KRR requires Bayesian optimization~\citep{shahriari2015taking} to estimate the hyperparameters due to having a high-dimensional search space.
+While a k-fold cross-validation is used to estimate the hyperparameter for \gls{knn}, the \gls{var} requires Bayesian optimization~\citep{shahriari2015taking} to estimate the hyperparameters due to having a high-dimensional search space.
 The likelihood ratio-based procedure requires no training, but the cost of calculating the likelihood weights is $\mathcal{O}(M^2)$.
@@
 The regression and kernel smoothing-based procedures are the most efficient among the metamodel-based procedures.
-Since the regression-based procedure has a higher empirical rate of convergence, it is preferred over kNN.
-The likelihood ratio-based and KRR-based procedures are the most computationally expensive among all procedures.
+Since the regression-based procedure has a higher empirical rate of convergence, it is preferred over \gls{knn}.
+The likelihood ratio-based and \gls{var}-based procedures are the most computationally expensive among all procedures.
 They are also demanding in terms of memory.
 For budgets larger than $10^5$, the likelihood ratio-based procedure becomes impractical as storage of the likelihood weights becomes a bottleneck.
-The KRR-based procedure suffers from both cross-validation and inverting a kernel matrix of size $M \times M$.
+The \gls{var}-based procedure suffers from both cross-validation and inverting a kernel matrix of size $M \times M$.
 To separate the total computational time into different attributes, we provide a detailed analysis of the total computational time in the remainder of this section.
@@
     The slope of the regression line is close to $1$, resembling its algorithmic complexity reported in Table~\ref{tab1:complexity}.
-    \item The kernel smoothing-based and KRR-based procedure requires a cross-validation procedure to estimate the optimal hyperparameters. 
-    In our implementation of kNN, the cross-validation is conducted by using a grid search with a search space which cardinality does not grow with the simulation budget $\Gamma$.
+    \item The kernel smoothing-based and \gls{var}-based procedure requires a cross-validation procedure to estimate the optimal hyperparameters. 
+    In our implementation of \gls{knn}, the cross-validation is conducted by using a grid search with a search space which cardinality does not grow with the simulation budget $\Gamma$.
     However, the cross-validation cost of the kernel smoothing-based procedure grows with the simulation budget $\Gamma$ as more samples are involved.
-    The KRR-based procedure requires a Bayesian optimization to estimate the optimal hyperparameters, and the cardinality of the search space also grows with the simulation budget $\Gamma$.
-    The empirical cost of the KRR-based procedure does not resemble its algorithmic complexity reported in Table~\ref{tab1:complexity}.
-    The efficient implementation of KRR is an active area of research, and the computational cost of KRR can be reduced by using a low-rank approximation of the kernel matrix, e.g., the Nystr\"om method~\citep{nystrom1930praktische}.
-    Our observation for the KRR implementation time is in line with the findings in~\cite{scikit-learn}, where the cost of KRR is reported to be increasing quickly with the number of samples.
+    The \gls{var}-based procedure requires a Bayesian optimization to estimate the optimal hyperparameters, and the cardinality of the search space also grows with the simulation budget $\Gamma$.
+    The empirical cost of the \gls{var}-based procedure does not resemble its algorithmic complexity reported in Table~\ref{tab1:complexity}.
+    The efficient implementation of \gls{var} is an active area of research, and the computational cost of \gls{var} can be reduced by using a low-rank approximation of the kernel matrix, e.g., the Nystr\"om method~\citep{nystrom1930praktische}.
+    Our observation for the \gls{var} implementation time is in line with the findings in~\cite{scikit-learn}, where the cost of \gls{var} is reported to be increasing quickly with the number of samples.
     \item The likelihood ratio-based procedure requires no hyperparameter tuning, and its total computational time is mainly attributed to the likelihood weight calculation, which is $\mathcal{O}(M^2)$.
@@
 As a result, the total computational budget is not necessarily the same as the simulation budget, which is usually a limiting factor for practical applications.
-A kernel-based procedure, e.g., kNN and KRR, requires cross-validation, and its empirical performance depends heavily on the choice of hyperparameters.
-A kNN-based procedure is sensitive to the asset dimension and the problem complexity.
-A KRR-based procedure is computationally expensive, and its cost grows quickly with the simulation budget.
+A kernel-based procedure, e.g., \gls{knn} and \gls{var}, requires cross-validation, and its empirical performance depends heavily on the choice of hyperparameters.
+A \gls{knn}-based procedure is sensitive to the asset dimension and the problem complexity.
+A \gls{var}-based procedure is computationally expensive, and its cost grows quickly with the simulation budget.
 For kernel-based procedures, the computational cost is heavily dependent on the efficient implementation of the associated algorithms.

### 2025-04-13 project2/nnMetamodels.tex
11

@@
 
-Deep neural networks (DNNs) have attracted attentions of researchers and practitioners due to their success~\citep{hastie2009elements,lecun2015deep} in solving real-world machine learning tasks such as AlphaGo~\citep{silver2016mastering} and ChatGPT~\citep{chatgpt}.
+\gls{dnn} have attracted attentions of researchers and practitioners due to their success~\citep{hastie2009elements,lecun2015deep} in solving real-world machine learning tasks such as AlphaGo~\citep{silver2016mastering} and ChatGPT~\citep{chatgpt}.
 Since the first artificial neural network model~\citep{mcculloch1943logical} and the first algorithm for training a perceptron~\citep{rosenblatt1958perceptron}, especially after the introduction of backpropagation~\citep{rumelhart1985learning} and the growth of high-performance computing, the field of artificial neural network and deep learning in general has been growing rapidly.
-Two specialized neural network architectures that are relevant to our study are RNN~\citep{williams1989learning,sutskever2014sequence} and LSTM~\citep{hochreiter1997long,chung2014empirical}.
+Two specialized neural network architectures that are relevant to our study are \gls{rnn}~\citep{williams1989learning,sutskever2014sequence} and \gls{lstm}~\citep{hochreiter1997long,chung2014empirical}.
 In the field of actuarial science, a metamodel is commonly referred to as a proxy model.
-Despite their success, DNN models are often criticized for their lack of transparency and interpretability, which hinders their adoption in financial and actuarial applications.
-Enormous research efforts have been spent to test and improve the robustness of DNN models with carefully designed noise injection methods.
+Despite their success, \gls{dnn} models are often criticized for their lack of transparency and interpretability, which hinders their adoption in financial and actuarial applications.
+Enormous research efforts have been spent to test and improve the robustness of \gls{dnn} models with carefully designed noise injection methods.
 ~\cite{poole2014analyzing} show that injecting synthetic noise before and after hidden unit activations during training improves the performance of autoencoders.
-~\cite{neelakantan2015adding} improve learning for DNNs by injecting synthetic noise to the gradients during backpropagations.
+~\cite{neelakantan2015adding} improve learning for \gls{dnn}s by injecting synthetic noise to the gradients during backpropagations.
 A branch of research has been devoted to understanding the resilience of neural network models to noise in training labels.
-For example,~\cite{luo2016understanding} show that adding synthetic label noise to the convolutional neural network (CNN) can improve its ability to capture global features. 
+For example,~\cite{luo2016understanding} show that adding synthetic label noise to the convolutional neural network (\gls{cnn}) can improve its ability to capture global features. 
 ~\cite{srivastava2014dropout} quantify the error tolerance by injecting synthetic label noise with a custom Boltzmann machine hardware.
@@
 Users of real-world data have little control over the noise level of the original training labels and usually examine the effect of noisy data by injecting noise, but it is unclear whether a neural network model trained on noisy data actually learns the real, i.e., noiseless, feature-label relationship.
-Due to their lack of transparency and interpretability, the adoption of DNNs in financial and actuarial applications has been received by regulators with some skepticism.
+Due to their lack of transparency and interpretability, the adoption of \gls{dnn}s in financial and actuarial applications has been received by regulators with some skepticism.
 
@@
 \begin{enumerate}
-    \item We study what DNNs learn from noisy data by training them using simulated data based on well-designed simulation experiments.
+    \item We study what \gls{dnn}s learn from noisy data by training them using simulated data based on well-designed simulation experiments.
     This is a novel way to study the effect of noisy data and error tolerance of neural network models as one can \textit{reduce noise} in the data by increasing the number of replications in a simulation model.
     This new way of studying neural network models can provide more direct evidence on their transparency and interpretability. 
-    \item We propose two generic nested simulation procedures that uses DNNs as metamodels to improve its efficiency while maintaining transparency. 
+    \item We propose two generic nested simulation procedures that uses \gls{dnn}s as metamodels to improve its efficiency while maintaining transparency. 
     In essence, a pilot stage simulation is used to generate a large number of noisy data, which are then used to train a metamodel.
@@
     The first procedure uses a metamodel to identify a set of potential tail scenarios on which computations are performed in stage 2, while the second procedure uses metamodel predictions to estimate risk measures directly.
-    Our numerical results show that DNN metamodels can identify the tail scenarios accurately and so the proposed procedures can estimate tail risk measures with a similar degree of accuracy while, at the same time, using less simulation budget.
+    Our numerical results show that \gls{dnn} metamodels can identify the tail scenarios accurately and so the proposed procedures can estimate tail risk measures with a similar degree of accuracy while, at the same time, using less simulation budget.
 \end{enumerate}
@@
 \begin{enumerate}
-    \item ``What do DNNs learn from noisy data?'' and 
+    \item ``What do \gls{dnn}s learn from noisy data?'' and 
     \item ``How well do neural networks learn from noisy data?''.
@@
 Data-driven answers to these questions prevail in the existing literature.
-In supervised learning, DNNs are believed to learn from a given data about the feature-label relationship to predict new labels for unseen features.
+In supervised learning, \gls{dnn}s are believed to learn from a given data about the feature-label relationship to predict new labels for unseen features.
 A cross-validation procedure used to assess a subset, i.e., the validation set, of the original data, is a common way to access the quality of learning.
@@
 In this study, we revisit these questions in a simulation context and propose an alternative approach to answer them.
-Instead of relying solely on real-data and splitting it into multiple subsets, we propose using stochastic simulation outputs as training labels for DNNs.
+Instead of relying solely on real-data and splitting it into multiple subsets, we propose using stochastic simulation outputs as training labels for \gls{dnn}s.
 By controlling the simulation design parameters, such as the number of independent replications, we can control the quality and also the quantity of the training labels fed into the neural networks.
@@
 The metamodel is trained using a set of simulated data, and it is used to predict the simulation output for new inputs.
-The study of metamodeling is an active research area in the simulation literature, and using DNNs as metamodels is a relatively new development.
-~\cite{fonseca2003simulation} provide general guidelines for simulation metamodeling with neural networks,~\cite{lieu2022adaptive} use DNNs as metamodels of a simulation model for a structural reliability analysis, and~\cite{salle2014efficient} show that neural network metamodels help achieve higher degree of prediction accuracy that other metamodels in approximating agent-based simulation models.
+The study of metamodeling is an active research area in the simulation literature, and using \gls{dnn}s as metamodels is a relatively new development.
+~\cite{fonseca2003simulation} provide general guidelines for simulation metamodeling with neural networks,~\cite{lieu2022adaptive} use \gls{dnn}s as metamodels of a simulation model for a structural reliability analysis, and~\cite{salle2014efficient} show that neural network metamodels help achieve higher degree of prediction accuracy that other metamodels in approximating agent-based simulation models.
 A popular metamodel in nested simulation procedures is stochastic kriging.
-~\cite{liu2010stochastic} use stochastic kriging as a metamodel of Monte Carlo simulations to estimate the CVaR of a portfolio of derivative securities, and~\cite{gan2015valuation} use a stochastic kriging for an efficient valuation of large portfolios of variable annuity (VA) contracts.
+~\cite{liu2010stochastic} use stochastic kriging as a metamodel of Monte Carlo simulations to estimate the \gls{cvar} of a portfolio of derivative securities, and~\cite{gan2015valuation} use a stochastic kriging for an efficient valuation of large portfolios of \gls{va} contracts.
 Other studies, such as ~\cite{broadie2015risk},~\cite{hong2017kernel}, and~\cite{zhang2022sample} use a regression, a kernel smoothing, and a likelihood ratio method, respectively as metamodels.
@@
     \item  our metamodel has high-dimensional inputs. In machine learning terminology, the features are high-dimensional vectors.
-    To estimate the hedging error of a typical VA contract, the number of features is in the order of hundreds, which is at least one order of magnitude larger than the number of features in the aforementioned studies,
+    To estimate the hedging error of a typical \gls{va} contract, the number of features is in the order of hundreds, which is at least one order of magnitude larger than the number of features in the aforementioned studies,
     \item  for estimating tail risk measures, our metamodel is only used for tail scenario identification but is \textit{not} used in the estimation of the tail risk measures.
@@
     \item  using simulation models as data generators, we can decrease the noise level and get arbitrarily close to the true labels by increasing the number of replications in the simulation model.
-    This design allows a systematic study of the effect of noisy training labels on the performance of DNN models in predicting the noiseless labels.
+    This design allows a systematic study of the effect of noisy training labels on the performance of \gls{dnn} models in predicting the noiseless labels.
 \end{enumerate}
 
-In this chapter, DNN metamodels and DNN models are used almost interchangeably despite one distinction.
+In this chapter, \gls{dnn} metamodels and \gls{dnn} models are used almost interchangeably despite one distinction.
 \begin{itemize}
-    \item The discussion of \textit{DNN metamodels} focuses more on the aspect of \textit{estimating} the inner simulation.
-    \item The discussion of \textit{DNN models} focuses more on \textit{studying the DNN} using simulation data.
+    \item The discussion of \textit{\gls{dnn} metamodels} focuses more on the aspect of \textit{estimating} the inner simulation.
+    \item The discussion of \textit{\gls{dnn} models} focuses more on \textit{studying the \gls{dnn}} using simulation data.
 \end{itemize}
@@
 The rest of this chapter is organized as follows.
-Section~\ref{sec2:problem-formulation} presents the problem settings for tail risk measures and dynamic hedging of VAs. 
-Section~\ref{sec2:metamodel2Stage} proposes an efficient two-stage nested simulation procedure that uses DNNs as metamodels to help reduce a simulation budget by only performing computations on identified tail scenarios.
+Section~\ref{sec2:problem-formulation} presents the problem settings for tail risk measures and dynamic hedging of \gls{va}s. 
+Section~\ref{sec2:metamodel2Stage} proposes an efficient two-stage nested simulation procedure that uses \gls{dnn}s as metamodels to help reduce a simulation budget by only performing computations on identified tail scenarios.
 Section~\ref{sec2:metamodel1Stage} proposes a single-stage nested simulation procedure that estimates risk measures directly with metamodel predictions.
-Section~\ref{sec2:numerical} demonstrates the efficiency of DNN metamodels and examines the error tolerance of two LSTM metamodels with different numbers of trainable parameters. 
+Section~\ref{sec2:numerical} demonstrates the efficiency of \gls{dnn} metamodels and examines the error tolerance of two \gls{lstm} metamodels with different numbers of trainable parameters. 
 Lastly, practical suggestions are provided for the choice of suitable metamodels and simulation settings.
@@
 
-In this section we present notations, problem settings, and a simulation model for risk estimation for hedging errors of VAs.
-A main goal of this section is to showcase the complexity of the simulation model, which we use as a data generator to train DNN metamodels (Section~\ref{sec2:metamodel2Stage} and Section~\ref{sec2:metamodel1Stage}).
+In this section we present notations, problem settings, and a simulation model for risk estimation for hedging errors of \gls{va}s.
+A main goal of this section is to showcase the complexity of the simulation model, which we use as a data generator to train \gls{dnn} metamodels (Section~\ref{sec2:metamodel2Stage} and Section~\ref{sec2:metamodel1Stage}).
 For readers who are interested in the examination of a neural network metamodel, it is sufficient to understand that our simulation model generates data with 240 features and 1 real-value label and our metamodels are generally applicable to any simulation model that generates data with similar characteristics.
 
-\subsection{Tail Risk Measures: VaR and CVaR}
+\subsection{Tail Risk Measures}
 Measuring and monitoring risks, particularly tail risks, are important risk management tasks for financial institutions such as banks and insurance companies.
-Two most popular tail risk measures are VaR and CVaR~\citep{hardy2022quantitative, rockafellar2002conditional}.
+Two most popular tail risk measures are \gls{var} and \gls{cvar}~\citep{hardy2022quantitative, rockafellar2002conditional}.
 
 Consider a loss random variable $L$ which losses and gains lie in the right and left tails, respectively, of its distribution.
-For a given confidence level $\alpha\in [0,1]$, the $\alpha$-VaR and $\alpha$-CVaR are defined in Equation~\eqref{eq1:var} and Equation~\eqref{eq1:cvar}, respectively.
-Tail risk measures such as VaR and CVaR are widely used for setting a regulatory and economic capital, which is the amount of capital a financial institution holds to cover its risk.
-For example, European insurers set regulatory capital at $99.5\%$-VaR according to Solvency II~\cite{eiopa2014underlying}.
-In Canada, the regulatory capital requirement for VAs is set based on CVaRs as prescribed in~\cite{osfi2017life}.
+For a given confidence level $\alpha\in [0,1]$, the $\alpha$-\gls{var} and $\alpha$-\gls{cvar} are defined in Equation~\eqref{eq1:var} and Equation~\eqref{eq1:cvar}, respectively.
+Tail risk measures such as \gls{var} and \gls{cvar} are widely used for setting a regulatory and economic capital, which is the amount of capital a financial institution holds to cover its risk.
+For example, European insurers set regulatory capital at $99.5\%$-\gls{var} according to Solvency II~\cite{eiopa2014underlying}.
+In Canada, the regulatory capital requirement for \gls{va}s is set based on \gls{cvar}s as prescribed in~\cite{osfi2017life}.
 
 Let $L_1,L_2,\ldots,L_M$ be $M$ i.i.d. simulated losses of $L$ and let $L_{(1)}\leq L_{(2)}\leq \ldots\leq L_{(M)}$ be the ordered losses.
-For a given confidence level $\alpha$ (assume that $\alpha M$ is an integer for simplicity), $\alpha$-VaR can be estimated by the sample quantile $\widehat{\VaR}_\alpha = L_{(\alpha M)}$.
-Also, $\alpha$-CVaR can be estimated by
+For a given confidence level $\alpha$ (assume that $\alpha M$ is an integer for simplicity), $\alpha$-\gls{var} can be estimated by the sample quantile $\widehat{\VaR}_\alpha = L_{(\alpha M)}$.
+Also, $\alpha$-\gls{cvar} can be estimated by
 \begin{equation} \label{eq2:cvar-hat}
@@
 Equation \eqref{eq2:cvar-hat} is the same as \eqref{eq1:cvar-hat} except that we define a \textit{true tail scenario set} of size $k$ as $\tail_{k} = \{i: L_i > L_{(M-k)}\}$.
-In this study, the loss random variable of interest is the hedging error for VA.
+In this study, the loss random variable of interest is the hedging error for \gls{va}.
 
@@
 
-VA contracts offer different types of guarantees.
-Generally speaking, a portion of the VA premium is invested in a sub-account which return is linked to some stock indices.
+\gls{va} contracts offer different types of guarantees.
+Generally speaking, a portion of the \gls{va} premium is invested in a sub-account which return is linked to some stock indices.
 
@@
 \begin{itemize}[noitemsep]
-    \item \textbf{Guaranteed Minimum Maturity Benefit (GMMB)}: A GMMB contract pays a maturity benefit equal to the greater of the sub-account value and a fixed guarantee value.
+    \item \textbf{\gls{gmmb}}: A \gls{gmmb} contract pays a maturity benefit equal to the greater of the sub-account value and a fixed guarantee value.
     The guarantee value is often set as a percentage, e.g., 75\% or 100\%, of the initial premium.
 
-    \item \textbf{Guaranteed Minimum Withdrawal Benefit (GMWB)}: A GMWB contract guarantees the minimum amount of periodic withdrawal the policyholder can take from the sub-account until maturity, even if the sub-account value reduces to zero.
+    \item \textbf{\gls{gmwb}}: A \gls{gmwb} contract guarantees the minimum amount of periodic withdrawal the policyholder can take from the sub-account until maturity, even if the sub-account value reduces to zero.
     The minimum withdrawal benefit is typically a fixed percentage of the guarantee value.
     The guarantee value will decrease if the withdrawal exceeds the guaranteed minimum.
-The GMWB is typically offered with an accumulation period, during which no withdrawals are made but a GMDB is usually offered.
-Additional features offered with the GMWB include roll-up, ratchet, and reset~\citep{geneva2013variable}.
+The \gls{gmwb} is typically offered with an accumulation period, during which no withdrawals are made but a \gls{gmab} is usually offered.
+Additional features offered with the \gls{gmwb} include roll-up, ratchet, and reset~\citep{geneva2013variable}.
 \end{itemize}
-For a comprehensive review of other types of VA contracts such as Guaranteed Minimum Death Benefit (GMDB), Guaranteed Minimum Accumulation Benefit (GMAB) and Guaranteed Lifetime Withdrawal Benefit (GLWB), we refer readers to~\cite{hardy2003investment}.
-Next we present a summary of dynamic hedging for VA contracts.
-We refer readers to~\cite{dang2021efficient} for detailed modeling of insurer liabilities in different VA contracts and Greek estimation.
+For a comprehensive review of other types of \gls{va} contracts such as \gls{gmab}, \gls{gmdb}, and \gls{glwb}, we refer readers to~\cite{hardy2003investment}.
+Next we present a summary of dynamic hedging for \gls{va} contracts.
+We refer readers to~\cite{dang2021efficient} for detailed modeling of insurer liabilities in different \gls{va} contracts and Greek estimation.
 
-Consider a generic VA contract with maturity $T>0$ periods, e.g., $T=240$ months.
+Consider a generic \gls{va} contract with maturity $T>0$ periods, e.g., $T=240$ months.
 Denote the policyholder's (random) time of death by $\tau>0$.
@@
 Let $S_t$, $F_t$, and $G_t$ be an indexed stock price, the subaccount value and a guarantee value, respectively, at time $t=1,2,\ldots,T$.
-Evolution of the subaccount value and the guarantee value of a VA contract affect the contract payout.
-Note that the policyholder's (random) time of death also affects the timing of the benefit payout for certain types of VA such as GMDB, but this is not considered in our study for simplicity.
+Evolution of the subaccount value and the guarantee value of a \gls{va} contract affect the contract payout.
+Note that the policyholder's (random) time of death also affects the timing of the benefit payout for certain types of \gls{va} such as \gls{gmab}, but this is not considered in our study for simplicity.
 For clarity, we use $F_t$ and $F_{t_+}$ to denote the sub-account value just before and just after the withdrawal at time $t$, if any.
@@
 
-    \item The guarantee value ratchets up (ratcheting is a common feature in GMWB) if the sub-account value exceeds the previous guarantee value,
+    \item The guarantee value ratchets up (ratcheting is a common feature in \gls{gmwb}) if the sub-account value exceeds the previous guarantee value,
         \begin{equation*}
@@
 
-    \item The withdrawal is made (for GMWB) and is deducted from the sub-account value,
+    \item The withdrawal is made (for \gls{gmwb}) and is deducted from the sub-account value,
         \begin{equation*}
@@
         \end{equation*} 
-    where $I_t = \gamma G_t$. A GMMB can be modeled with $\gamma = 0$.
+    where $I_t = \gamma G_t$. A \gls{gmmb} can be modeled with $\gamma = 0$.
 \end{enumerate}
 
-We see from the above modeling steps that the status of a generic VA contract is summarized by a triplet $(S_t,F_t,G_t)$ which evolution is driven by the stochasticity of $S_t$.
+We see from the above modeling steps that the status of a generic \gls{va} contract is summarized by a triplet $(S_t,F_t,G_t)$ which evolution is driven by the stochasticity of $S_t$.
 In practice, the simulation model may also incorporate additional complications such as mortality, lapse, and excess withdrawal, etc.
 
-At any time $t=1,\ldots,T$, the insurer's liability in a VA contract is the present value of all payments, net of the fee income.
+At any time $t=1,\ldots,T$, the insurer's liability in a \gls{va} contract is the present value of all payments, net of the fee income.
 For example, suppose that the per-period risk-free rate is $r$, then
-the insurer's time-$t$ liability for a GMMB contract is $V_t = e^{-r(T-t)}\cdot (G_T - F_T)^+ - \sum_{s=t+1}^{T} e^{-r(T-s)} F_s \eta_n$.
-Also, the insurer's time-$t$ liability for a GMWB contract is $V_t = \sum_{s=t+1}^{T} e^{-r(T-s)} [(I_s - F_s)^+- \eta_n F_s] $.
+the insurer's time-$t$ liability for a \gls{gmmb} contract is $V_t = e^{-r(T-t)}\cdot (G_T - F_T)^+ - \sum_{s=t+1}^{T} e^{-r(T-s)} F_s \eta_n$.
+Also, the insurer's time-$t$ liability for a \gls{gmwb} contract is $V_t = \sum_{s=t+1}^{T} e^{-r(T-s)} [(I_s - F_s)^+- \eta_n F_s] $.
 
-For example, consider the time-$t$ liability $V_t$ of a GMWB:
+For example, consider the time-$t$ liability $V_t$ of a \gls{gmwb}:
 Suppose that given the stock sample path, which is an outer path $S_1,\ldots,S_t$, one can simulate future stock prices $\Stilde_{t+1},\ldots,\Stilde_{T}$, e.g., inner sample paths, based on some asset model such as a Black-Scholes model.
@@
 
-Insurers commonly use dynamic hedging to mitigate a market risk exposure in VA contract's embedded options.
-In a dynamic hedging program, a hedge portfolio is set up and periodically rebalanced for a portfolio of VA contracts using stocks, bonds, futures, and other derivatives.
-For simplicity, in this study we consider delta hedging for a generic VA liability using one stock and one bond.
+Insurers commonly use dynamic hedging to mitigate a market risk exposure in \gls{va} contract's embedded options.
+In a dynamic hedging program, a hedge portfolio is set up and periodically rebalanced for a portfolio of \gls{va} contracts using stocks, bonds, futures, and other derivatives.
+For simplicity, in this study we consider delta hedging for a generic \gls{va} liability using one stock and one bond.
 The metamodeling procedures presented in Section~\ref{sec2:metamodel2Stage} and Section~\ref{sec2:metamodel1Stage} can be trivially adapted to more general hedging strategies.
 
-Consider a VA contract which delta hedge portfolio at any time~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at time $T$.
+Consider a \gls{va} contract which delta hedge portfolio at any time~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at time $T$.
 The value of the hedge portfolio at time~$(t-1)$ is:
@@
 \end{equation}
-The P\&L of the VA contract includes cost of the initial hedge ($H_0$), hedging errors~\eqref{eq2:hedgingerror}, unwinding of the hedge at maturity ($H^{bf}_T$), and unhedged liability ($V_0$).
+The P\&L of the \gls{va} contract includes cost of the initial hedge ($H_0$), hedging errors~\eqref{eq2:hedgingerror}, unwinding of the hedge at maturity ($H^{bf}_T$), and unhedged liability ($V_0$).
 Mathematically, the present value of these cash flows is given by
@@
 Recall from Section~\ref{subsec:VApayout} that the stock's sample path, regardless of inner or outer simulation or a combination of both, determines the evolution of the triplet $(S_t,F_t,G_t)$.
-For GMWB, a standard nested simulation procedure to estimate the $\alpha$-CVaR of $L$ is described in Algorithm~\ref{alg2:standardProcedure} below.
+For \gls{gmwb}, a standard nested simulation procedure to estimate the $\alpha$-\gls{cvar} of $L$ is described in Algorithm~\ref{alg2:standardProcedure} below.
 
@@
     As $N$ approaches infinity, $\Lhat_i^{MC}$ converges to the true loss $L_i$, and
-    \item   Most importantly, when estimating tail risk measures such as $\alpha$-CVaR, only a small number of estimated losses, which is those associated with the set of tail scenarios $\widehat{\tail}_{k}$ are used in the estimator.
+    \item   Most importantly, when estimating tail risk measures such as $\alpha$-\gls{cvar}, only a small number of estimated losses, which is those associated with the set of tail scenarios $\widehat{\tail}_{k}$ are used in the estimator.
 \end{itemize}
@@
 
-Based on the three observations above and built on the work by~\cite{dang2020efficient}, we propose a two-stage nested simulation procedure which uses a DNN metamodel to identify potential tail scenarios.
+Based on the three observations above and built on the work by~\cite{dang2020efficient}, we propose a two-stage nested simulation procedure which uses a \gls{dnn} metamodel to identify potential tail scenarios.
 We present our proposed procedure as a competitor to the standard procedure with $M$ outer scenarios and $N$ inner replications for each outer scenario, as described in Section~\ref{subsec:dynamicHedge}.
-We propose a two-stage procedure with a supervised learning metamodel that aims at producing a CVaR estimate that is as accurate as that of the standard procedure, but requires fewer computations than the latter.
+We propose a two-stage procedure with a supervised learning metamodel that aims at producing a \gls{cvar} estimate that is as accurate as that of the standard procedure, but requires fewer computations than the latter.
 
@@
 However, we believe that the goal of designing an efficient simulation procedure is to solve practical problems faster, so a target-accuracy design is more suitable, which refers to obtaining a similar level of accuracy as the standard procedure but with much less simulation budget.
-One other reason for recommending this fixed-accuracy design is to investigate whether DNN metamodels trained with much noisier labels can identify true tail scenarios with a similar degree of accuracy as the standard procedure.
-The size of the predicted tail scenario set in stage 1, $m$, is an important experiment design parameter that affects the correct identification of true tail scenarios and ultimately affects the estimation accuracy for CVaR.
-Clearly, there is a lower bound $m \geq (1-\alpha)M$ because the $\alpha$-CVaR is estimated by the average of the largest $(1-\alpha)M$ losses at the end of stage 2.
+One other reason for recommending this fixed-accuracy design is to investigate whether \gls{dnn} metamodels trained with much noisier labels can identify true tail scenarios with a similar degree of accuracy as the standard procedure.
+The size of the predicted tail scenario set in stage 1, $m$, is an important experiment design parameter that affects the correct identification of true tail scenarios and ultimately affects the estimation accuracy for \gls{cvar}.
+Clearly, there is a lower bound $m \geq (1-\alpha)M$ because the $\alpha$-\gls{cvar} is estimated by the average of the largest $(1-\alpha)M$ losses at the end of stage 2.
 For ease of reference, we call the additional percentage of predicted tail scenarios above this lower bound, i.e., $\epsilon = \frac{m - (1-\alpha)M}{M}$, as a \textit{safety margin}.
@@
 Due to the simulation errors and approximation error in the metamodel in stage 1, we do not expect a perfect match between the true tail scenario set $\tail_{k}$ and the predicted tail scenario set $\widehat{\tail}_{k}^{PD}$ for any size $k$.
-This means that we should not set $m$ at its lower bound: Some safety margin $\epsilon M$ should be added to the predicted tail scenario set, i.e., $m = (1-\alpha )M + \epsilon M$, to increase the likelihood that $\tail_{k} \subseteq \widehat{\tail}_{m}^{PD}$ and that the true tail scenarios are included in estimating $\alpha$-CVaR at the end of stage 2.
+This means that we should not set $m$ at its lower bound: Some safety margin $\epsilon M$ should be added to the predicted tail scenario set, i.e., $m = (1-\alpha )M + \epsilon M$, to increase the likelihood that $\tail_{k} \subseteq \widehat{\tail}_{m}^{PD}$ and that the true tail scenarios are included in estimating $\alpha$-\gls{cvar} at the end of stage 2.
 The choice of a safety margin $\epsilon$ is not trivial, and it should be set based on the metamodel's accuracy in identifying true tail scenarios.
@@
 In our exploratory experiment with the two-stage procedure, we observe that a suitable metamodel trained with noisy labels is accurate enough to identify true tail scenarios with a relatively small safety margin.
-This observation motivates us to propose a single-stage procedure that uses the identical neural network metamodel, not for the purpose of differentiating between tail and non-tail scenarios, but rater to estimate the CVaR directly using the predicted losses.
+This observation motivates us to propose a single-stage procedure that uses the identical neural network metamodel, not for the purpose of differentiating between tail and non-tail scenarios, but rater to estimate the \gls{cvar} directly using the predicted losses.
 
@@
     It can be naturally adapted to estimate risk measures that require the knowledge of the entire loss distribution, such as the standard deviation or the squared tracking error.
-    Even for CVaR, the two-stage procedure becomes less attractive at a higher level of $\alpha$.
+    Even for \gls{cvar}, the two-stage procedure becomes less attractive at a higher level of $\alpha$.
 \end{enumerate}
@@
 The problem settings in our experiments are identical to those in~\cite{dang2020efficient}.
-We consider estimating the $95\%$ CVaR of the hedging loss of a GMWB contract, which is one of the most complex VA contracts in the market.
-The VA contracts have a 20-year maturity and are delta-hedged with monthly rebalancing, i.e., $T=240$ rebalancing periods.
+We consider estimating the $95\%$ \gls{cvar} of the hedging loss of a \gls{gmwb} contract, which is one of the most complex \gls{va} contracts in the market.
+The \gls{va} contracts have a 20-year maturity and are delta-hedged with monthly rebalancing, i.e., $T=240$ rebalancing periods.
 The gross and net management fees are $\eta_g = 0.2\%$ and $\eta_n=0.1\%$, respectively.
-The withdrawal rate for GMWB is $0.375\%$ per month.
-To make our examples more realistic, the VAs are also subject to a dynamic lapse model with the following key features~\citep{naic2021}:
+The withdrawal rate for \gls{gmwb} is $0.375\%$ per month.
+To make our examples more realistic, the \gls{va}s are also subject to a dynamic lapse model with the following key features~\citep{naic2021}:
 \begin{enumerate}
@@
     \item The monthly lapse rate from time $t$ to $t + 1$, denoted as ${}_{\frac{1}{12}}q^l_{x+\frac{t}{12}}$, is given by:
-    \begin{equation}
+    \begin{equation} \label{eq:dynamic_lapse_rate}
         {}_{\frac{1}{12}}q^l_{x+\frac{t}{12}} = \min\left\{1, \max\left\{0.5, 1 - 1.25 \times \left(\frac{G_t}{F_t} - 1.1\right)\right\} \times {}_{\frac{1}{12}}q^{base}_{x+\frac{t}{12}}\right\}
@@
     where ${}_{\frac{1}{12}}q^{base}_{x+\frac{t}{12}}$ is a base monthly mortality rate for a policyholder aged $x + \frac{t}{12}$ at month $t$, and the base monthly lapse rate is defined as:
-    \begin{equation}
+    \begin{equation} \label{eq:lapse_rate}
         {}_{\frac{1}{12}}q^{base}_{x+\frac{t}{12}} = 
@@
 \begin{enumerate}
-    \item   The true losses and the true $95\%$-CVaR are estimated by using a standard nested simulation procedure that runs $N=\num{100000}$ inner replications for each of the $M=\num{100000}$ outer scenarios.
-    \item   A benchmark estimator of the $95\%$-CVaR is generated by using $N=\num{1000}$ for each of the $M=\num{100000}$ outer scenarios.
+    \item   The true losses and the true $95\%$-\gls{cvar} are estimated by using a standard nested simulation procedure that runs $N=\num{100000}$ inner replications for each of the $M=\num{100000}$ outer scenarios.
+    \item   A benchmark estimator of the $95\%$-\gls{cvar} is generated by using $N=\num{1000}$ for each of the $M=\num{100000}$ outer scenarios.
     \item   The training data for our metamodels is generated by using $N=\num{100}$ for $M=\num{100000}$.
@@
 
-Five metamodels are considered in this experiment: multiple linear regression (MLR), quadratic polynomial regression (QPR) without interaction terms, FNN, RNN, and LSTM network.
-MLR and QPR are two common metamodels in the simulation literature, and their implemention is straightfoward in our simulation setting.
-FNN is a generic neural network while RNN and LSTM are specialized models to accommodate the sequential structure of our time-series features.
-A $\tanh$ activation function is used for RNN and LSTM layers, and a ReLU activation function is used for the fully-connected layers.
+Five metamodels are considered in this experiment: \gls{mlr}, \gls{qpr} without interaction terms, \gls{fnn}, \gls{rnn}, and \gls{lstm} network.
+\gls{mlr} and \gls{qpr} are two common metamodels in the simulation literature, and their implemention is straightfoward in our simulation setting.
+\gls{fnn} is a generic neural network while \gls{rnn} and \gls{lstm} are specialized models to accommodate the sequential structure of our time-series features.
+A $\tanh$ activation function is used for \gls{rnn} and \gls{lstm} layers, and a ReLU activation function is used for the fully-connected layers.
 All neural network metamodels are trained by the Adam optimizer~\citep{kingma2014adam} with an initial learning rate of $0.001$ and an exponential learning rate decay schedule.
-All DNN metamodels are trained with a dropout rate of $10\%$.
+All \gls{dnn} metamodels are trained with a dropout rate of $10\%$.
 The architectures and training settings are typical choices in the deep learning literature.
@@
 The numbers of trainable parameters are recorded in the second column of Table~\ref{tab:gmwb_arch}.
-We observe that the three DNN metamodels have orders of magnitudes more trainable parameters than the two traditional regression metamodels.
-Following the convention in machine learning literature, the three DNN metamodels are said to have much higher \textit{model capacities}.
-Treating regression metamodels as shallow neural networks, MLR and QPR are two neural networks with no hidden layer. 
+We observe that the three \gls{dnn} metamodels have orders of magnitudes more trainable parameters than the two traditional regression metamodels.
+Following the convention in machine learning literature, the three \gls{dnn} metamodels are said to have much higher \textit{model capacities}.
+Treating regression metamodels as shallow neural networks, \gls{mlr} and \gls{qpr} are two neural networks with no hidden layer. 
 For a traditional regression metamodel, the numbers of neurons in its input layer equals to the cardinality of its regression basis.
-On the other hand, the three DNN metamodels have several hidden layers and are more flexible than MLR and QPR.
-Our FNN has two hidden layers prior to its output layer.
+On the other hand, the three \gls{dnn} metamodels have several hidden layers and are more flexible than \gls{mlr} and \gls{qpr}.
+Our \gls{fnn} has two hidden layers prior to its output layer.
 Its hidden layers are feature extraction layers that transform the 240-dimension feature vector into a 32-dimension vector that can directly relate to the target variable.
 This extraction process is automatic and does not require manual feature engineering.
-Our RNN and LSTM networks have three hidden layers.
-They contain similar numbers of neurons as the FNN but have deeper network structures.
-For RNN, two of its hidden layers are recurrent layers that capture the temporal dependency in the feature, and its last hidden layer is a standard feedforward layer that transforms the previous hidden states into a 32-dimension vector for target prediction.
-Our LSTM has the same architecture as the RNN but with LSTM cells in place of RNN cells.
+Our \gls{rnn} and \gls{lstm} networks have three hidden layers.
+They contain similar numbers of neurons as the \gls{fnn} but have deeper network structures.
+For \gls{rnn}, two of its hidden layers are recurrent layers that capture the temporal dependency in the feature, and its last hidden layer is a standard feedforward layer that transforms the previous hidden states into a 32-dimension vector for target prediction.
+Our \gls{lstm} has the same architecture as the \gls{rnn} but with \gls{lstm} cells in place of \gls{rnn} cells.
 
@@
     \midrule
-    MLR & $\num{241}$ & $0.706 (\pm 8.34\times 10^{-4})$ & $0.713 (\pm 2.67 \times 10^{-2})$ & $0.706 (\pm 3.44 \times 10^{-4})$ \\
-    QPR & $\num{481}$ & $0.543 (\pm 8.27\times 10^{-4})$ & $0.554 (\pm 2.32 \times 10^{-2})$ & $0.544 (\pm 4.12\times 10^{-4})$ \\
-    FNN & $\num{35009}$ & $0.129 (\pm 5.95\times 10^{-3})$ & $0.240 (\pm 9.82 \times 10^{-3})$ & $0.132 (\pm 5.82\times 10^{-3})$ \\
-    RNN & $\num{32021}$ & $0.132 (\pm 7.53\times 10^{-3})$ & $0.137 (\pm 7.62\times 10^{-3})$ & $0.119 (\pm 7.51\times 10^{-3})$ \\
-    LSTM & $\num{35729}$ & $0.075 (\pm 4.48\times 10^{-3})$  & $0.079 (\pm 5.35\times 10^{-3})$ & $0.063 (\pm 4.43\times 10^{-3})$ \\
-    RNN$^*$\footnotemark & $\num{32021}$ & $0.109 (\pm 5.20\times 10^{-3})$  & $0.128 (\pm 5.22\times 10^{-3})$  & $0.109 (\pm 5.20\times 10^{-3})$ \\
+    \gls{mlr} & $\num{241}$ & $0.706 (\pm 8.34\times 10^{-4})$ & $0.713 (\pm 2.67 \times 10^{-2})$ & $0.706 (\pm 3.44 \times 10^{-4})$ \\
+    \gls{qpr} & $\num{481}$ & $0.543 (\pm 8.27\times 10^{-4})$ & $0.554 (\pm 2.32 \times 10^{-2})$ & $0.544 (\pm 4.12\times 10^{-4})$ \\
+    \gls{fnn} & $\num{35009}$ & $0.129 (\pm 5.95\times 10^{-3})$ & $0.240 (\pm 9.82 \times 10^{-3})$ & $0.132 (\pm 5.82\times 10^{-3})$ \\
+    \gls{rnn} & $\num{32021}$ & $0.132 (\pm 7.53\times 10^{-3})$ & $0.137 (\pm 7.62\times 10^{-3})$ & $0.119 (\pm 7.51\times 10^{-3})$ \\
+    \gls{lstm} & $\num{35729}$ & $0.075 (\pm 4.48\times 10^{-3})$  & $0.079 (\pm 5.35\times 10^{-3})$ & $0.063 (\pm 4.43\times 10^{-3})$ \\
+    \gls{rnn}$^*$\footnotemark & $\num{32021}$ & $0.109 (\pm 5.20\times 10^{-3})$  & $0.128 (\pm 5.22\times 10^{-3})$  & $0.109 (\pm 5.20\times 10^{-3})$ \\
     \bottomrule
     \end{tabular}
-    \caption{Architectures and MSEs of metamodels for GMWB inner simulation model.}
+    \caption{Architectures and \gls{mse}s of metamodels for \gls{gmwb} inner simulation model.}
     \label{tab:gmwb_arch}
@@
 
-\footnotetext{This row summarizes the error metrics of the well-trained RNN, where the ones suffer from a vanishing gradient issue are removed from the averages.}
+\footnotetext{This row summarizes the error metrics of the well-trained \gls{rnn}, where the ones suffer from a vanishing gradient issue are removed from the averages.}
 
@@
 All neural network metamodels have high model capcities comparing with the number of data points in the training set, i.e., $\num{90000}$.
-Empirically, this is not a huge concern for the DNNs.
+Empirically, this is not a huge concern for the \gls{dnn}s.
 In neural network literature, the number of trainable parameters is often much larger than the number of training samples.
@@
 The reason for not over-fitting when the number of trainable parameters is much larger than the number of training samples is still an open question in deep learning community.
-One of the explanations in the literature is that the optimization surface of DNNs is highly non-convex and has many local minima.
+One of the explanations in the literature is that the optimization surface of \gls{dnn}s is highly non-convex and has many local minima.
 Given a good initialization, the optimization algorithm is likely to find a solution that generalizes well to unseen data.
-Another explanation is that most existing DNN models have specific architectures that make them less prone to over-fitting.
-For example, a CNN is specifically designed to capture a spatial structure in image data.
-Unlike the FNN, not all neurons are connected to all neurons in the previous layer.
-This architecture serves as prior knowledge and a form of regularization that make CNNs less prone to over-fitting.
+Another explanation is that most existing \gls{dnn} models have specific architectures that make them less prone to over-fitting.
+For example, a \gls{cnn} is specifically designed to capture a spatial structure in image data.
+Unlike the \gls{fnn}, not all neurons are connected to all neurons in the previous layer.
+This architecture serves as prior knowledge and a form of regularization that make \gls{cnn}s less prone to over-fitting.
 
-In our experiments, there are important differences among the three DNN models due to having different neural network architectures.
+In our experiments, there are important differences among the three \gls{dnn} models due to having different neural network architectures.
 Their model capacities are intentionally set to be similar to each other for a fair comparison.
-The FNN is a generic neural network, its test error is much greater than the training error, which is a sign of over-fitting and poor generalization.
-In contrast, RNN and LSTM networks have recurrent structures and are designed to capture temporal relationship in the high-dimensional feature.
+The \gls{fnn} is a generic neural network, its test error is much greater than the training error, which is a sign of over-fitting and poor generalization.
+In contrast, \gls{rnn} and \gls{lstm} networks have recurrent structures and are designed to capture temporal relationship in the high-dimensional feature.
 As a result, they have lower training errors.
 They fit the data better and have lower test errors, i.e., they generalize better.
-Notably, the true errors for the DNN metamodels are lower than the training errors.
+Notably, the true errors for the \gls{dnn} metamodels are lower than the training errors.
 This is a sign of the metamodels' ability to learn the true feature-label relationship with noisy training labels. 
@@
 
-The intuition behind the RNN and LSTM metamodels is briefly mentioned in~\ref{subsec:LSTM}.
-To overcome the overfitting issue of the FNN, RNN learns a single function that operates across all time steps, and the time $t$ itself is not a variable in the RNN.
-The RNN cells in RNN and LSTM networks share parameters across time and serve as a form of regularization that prevents overfitting.
-However, the price that RNN pays for a reduced number of parameters is the difficulty in its optimization.
-Comparing the two metamodels with recurrent structures, a LSTM network overcomes two key drawbacks of a crude RNN.
+The intuition behind the \gls{rnn} and \gls{lstm} metamodels is briefly mentioned in~\ref{subsec:LSTM}.
+To overcome the overfitting issue of the \gls{fnn}, \gls{rnn} learns a single function that operates across all time steps, and the time $t$ itself is not a variable in the \gls{rnn}.
+The \gls{rnn} cells in \gls{rnn} and \gls{lstm} networks share parameters across time and serve as a form of regularization that prevents overfitting.
+However, the price that \gls{rnn} pays for a reduced number of parameters is the difficulty in its optimization.
+Comparing the two metamodels with recurrent structures, a \gls{lstm} network overcomes two key drawbacks of a crude \gls{rnn}.
 \begin{enumerate}
-    \item It avoids the vanishing gradient problem during training, which makes the LSTM network easier to train than the RNN.
-Figure~\ref{fig2:QQ_RNN} shows the quantile-quantile (QQ) plots between the \textbf{training} labels and the RNN predictions for two macro replications, where training of the latter is hindered by the vanishing gradient problem.
-    As a result, the half-width of the $95\%$ confidence band of the RNN's training error is much larger than all other metamodels. 
-    The last row of Table~\ref{tab:gmwb_arch} shows the average squared errors of the good RNN metamodels that have been successfully trained. 
-    Removing the RNN metamodels that are ill-trained, the average squared errors of the RNN metamodels are lower than those of the FNN.
-    This suggests that the RNN is more sensitive to noise in the sense of a stochastic gradient descent than the FNN.
+    \item It avoids the vanishing gradient problem during training, which makes the \gls{lstm} network easier to train than the \gls{rnn}.
+Figure~\ref{fig2:QQ_RNN} shows the quantile-quantile (QQ) plots between the \textbf{training} labels and the \gls{rnn} predictions for two macro replications, where training of the latter is hindered by the vanishing gradient problem.
+    As a result, the half-width of the $95\%$ confidence band of the \gls{rnn}'s training error is much larger than all other metamodels. 
+    The last row of Table~\ref{tab:gmwb_arch} shows the average squared errors of the good \gls{rnn} metamodels that have been successfully trained. 
+    Removing the \gls{rnn} metamodels that are ill-trained, the average squared errors of the \gls{rnn} metamodels are lower than those of the \gls{fnn}.
+    This suggests that the \gls{rnn} is more sensitive to noise in the sense of a stochastic gradient descent than the \gls{fnn}.
     They can capture the temporal dependency but are more difficult to optimize.
-    \item A LSTM introduces three gates that regulate the flow of information. 
+    \item A \gls{lstm} introduces three gates that regulate the flow of information. 
     These gates decide what information should be kept or discarded.
-    For detailed discussion on the LSTM network, please refer to Section~\ref{subsec:LSTM}.
-    This gating mechanism makes a LSTM network more capable of learning long-term dependencies. 
-    Since the feature in our dynamic hedging problem is a 240-dimensional time series, a LSTM network is more suitable than a crude RNN.
+    For detailed discussion on the \gls{lstm} network, please refer to Section~\ref{subsec:LSTM}.
+    This gating mechanism makes a \gls{lstm} network more capable of learning long-term dependencies. 
+    Since the feature in our dynamic hedging problem is a 240-dimensional time series, a \gls{lstm} network is more suitable than a crude \gls{rnn}.
+\end{enumerate}
+In summary, the network depth ensures successful learning of the training dataset, and the network architecture serves as 
+The intuition behind the \gls{rnn} and \gls{lstm} metamodels is briefly mentioned in~\ref{subsec:LSTM}.
+To overcome the overfitting issue of the \gls{fnn}, \gls{rnn} learns a single function that operates across all time steps, and the time $t$ itself is not a variable in the \gls{rnn}.
+The \gls{rnn} cells in \gls{rnn} and \gls{lstm} networks share parameters across time and serve as a form of regularization that prevents overfitting.
+However, the price that \gls{rnn} pays for a reduced number of parameters is the difficulty in its optimization.
+Comparing the two metamodels with recurrent structures, a \gls{lstm} network overcomes two key drawbacks of a crude \gls{rnn}.
+\begin{enumerate}
+    \item It avoids the vanishing gradient problem during training, which makes the \gls{lstm} network easier to train than the \gls{rnn}.
+Figure~\ref{fig2:QQ_RNN} shows the quantile-quantile (QQ) plots between the \textbf{training} labels and the \gls{rnn} predictions for two macro replications, where training of the latter is hindered by the vanishing gradient problem.
+    As a result, the half-width of the $95\%$ confidence band of the \gls{rnn}'s training error is much larger than all other metamodels. 
+    The last row of Table~\ref{tab:gmwb_arch} shows the average squared errors of the good \gls{rnn} metamodels that have been successfully trained. 
+    Removing the \gls{rnn} metamodels that are ill-trained, the average squared errors of the \gls{rnn} metamodels are lower than those of the \gls{fnn}.
+    This suggests that the \gls{rnn} is more sensitive to noise in the sense of a stochastic gradient descent than the \gls{fnn}.
+    They can capture the temporal dependency but are more difficult to optimize.
+    \item A \gls{lstm} introduces three gates that regulate the flow of information. 
+    These gates decide what information should be kept or discarded.
+    For detailed discussion on the \gls{lstm} network, please refer to Section~\ref{subsec:LSTM}.
+    This gating mechanism makes a \gls{lstm} network more capable of learning long-term dependencies. 
+    Since the feature in our dynamic hedging problem is a 240-dimensional time series, a \gls{lstm} network is more suitable than a crude \gls{rnn}.
 \end{enumerate}
@@
 They also have low test and true errors, which indicates poor generalization.
-In contrast, the DNN metamodels have lower errors.
+In contrast, the \gls{dnn} metamodels have lower errors.
 More specifically, they generalize better to the true labels than to the test labels.
@@
 Figure~\ref{fig2:QQ_REG} show the regression metamodel predictions and the loss labels in the true dataset.
-Between the two regression metamodels, the QPR metamodel has a slightly better fit for larger losses.
+Between the two regression metamodels, the \gls{qpr} metamodel has a slightly better fit for larger losses.
 Nevertheless, the predictions of both regression metamodels are far from the true labels, and their fit on the tail is particularly undesirable.
-The poor fit on the tail hinders the regression metamodels' ability to identify true tail scenarios and ultimately leads to poor CVaR estimates.
-Adding the quadratic terms, our QPR metamodel is considered as a natural extension of the MLR.
+The poor fit on the tail hinders the regression metamodels' ability to identify true tail scenarios and ultimately leads to poor \gls{cvar} estimates.
+Adding the quadratic terms, our \gls{qpr} metamodel is considered as a natural extension of the \gls{mlr}.
 Attempts to further improve the regression metamodels by adding interaction terms or higher-order terms do not improve the fit.
@@
 In Figure~\ref{fig2:QQ_NN}, we illustrate the fit of the neural network metamodels.
-The FNN has a better fit than the regression metamodels, but it still has a poor fit on the tails.
-We observe that the LSTM metamodels' QQ-plots closely follow the $45$-degree line.
+The \gls{fnn} has a better fit than the regression metamodels, but it still has a poor fit on the tails.
+We observe that the \gls{lstm} metamodels' QQ-plots closely follow the $45$-degree line.
 Again, these metamodels are trained on noisy data, so the good fit to the true data should not be taken for granted.
@@
 
-From a unique analytical standpoint, our numerical study offers a methodical exploration into the robustness of DNN models against noise in training labels. 
+From a unique analytical standpoint, our numerical study offers a methodical exploration into the robustness of \gls{dnn} models against noise in training labels. 
 By employing the standard nested simulation procedure in Algorithm~\ref{alg2:standardProcedure} as a data generator, we gain the ability to manipulate the noise level by adjusting the number of inner replications while keeping the same simulation procedure.
@@
 It allows us to generate our true dataset that approximates the true hedging losses with a high degree of precision, and, as a result, it enables us to explore the crucial question of whether deep learning models are capable of learning the true feature-label relationship from noisy training labels.
-Our numerical results in Table~\ref{tab:gmwb_arch} and the QQ plots provide direct evidence that DNN models are indeed able to cut through the noise in the training labels and learn the true feature-label relationship.
-The LSTM metamodels' ability to learn the true feature-label relationship is crucial for the two-stage procedure to identify true tail scenarios and produce accurate CVaR estimates.
-Section~\ref{subsec2:noiseTolerance} discusses LSTM metamodels in more details regarding their sensitivity to data quality and quantity.
-We aim at providing numerical evidence and insights into the DNN metamodels' noise tolerance.
+Our numerical results in Table~\ref{tab:gmwb_arch} and the QQ plots provide direct evidence that \gls{dnn} models are indeed able to cut through the noise in the training labels and learn the true feature-label relationship.
+The \gls{lstm} metamodels' ability to learn the true feature-label relationship is crucial for the two-stage procedure to identify true tail scenarios and produce accurate \gls{cvar} estimates.
+Section~\ref{subsec2:noiseTolerance} discusses \gls{lstm} metamodels in more details regarding their sensitivity to data quality and quantity.
+We aim at providing numerical evidence and insights into the \gls{dnn} metamodels' noise tolerance.
 
@@
 
-In our proposed two-stage procedure, the metamodel is used to identify the predicted tail scenario set, on which the standard nested simulation procedure is run in stage 2 to estimate the $95\%$-CVaR.
+In our proposed two-stage procedure, the metamodel is used to identify the predicted tail scenario set, on which the standard nested simulation procedure is run in stage 2 to estimate the $95\%$-\gls{cvar}.
 An accurate identification of the true tail scenarios is crucial.
-In a two-stage procedure, metamodels' overall prediction errors measured by the MSEs in Table~\ref{tab:gmwb_arch} are not the determining factor, but their ability to effectively rank the scenarios by their \textbf{true} losses is most critical in producing accurate CVaR estimates.
+In a two-stage procedure, metamodels' overall prediction errors measured by the MSEs in Table~\ref{tab:gmwb_arch} are not the determining factor, but their ability to effectively rank the scenarios by their \textbf{true} losses is most critical in producing accurate \gls{cvar} estimates.
 A metamodel that uses less safety margin to rank can save more simulation budget in stage 2.
@@
 For a fixed safety margin, the percentage of tail matches of the traditional regression metamodels are substantially lower than the ones of the neural networks.
-We observe that a poor metamodel such as the QPR identifies less than $40\%$ of the true tail scenario without any safety margin.
-In contrast, a well-suited metamodel such as the LSTM identifies more than $75\%$ of the true tail scenarios without any safety margin and more than the QPR metamodel does with $15\%$ of safety margin\footnote{The metamodel in~\cite{dang2020efficient} identifies $100\%$ of the true tail scenarios on with a $10\%$ safety margin for a GMAB contract.
-The GMAB contract is simpler than the GMWB contract, and the true tail scenarios are easier to identify. 
-For a GMAB, our LSTM metamodel identifies $100\%$ of the true tail scenarios with a $2.5\%$ safety margin}.
-The RNN metamodel suffers from the vanishing gradient problem during the training stage. 
-For some macro replications (as shown in Figure~\ref{subfig2:badRNN}), the RNN metamodels' predictions are far from the true losses, especially on the tails.
+We observe that a poor metamodel such as the \gls{qpr} identifies less than $40\%$ of the true tail scenario without any safety margin.
+In contrast, a well-suited metamodel such as the \gls{lstm} identifies more than $75\%$ of the true tail scenarios without any safety margin and more than the QPR metamodel does with $15\%$ of safety margin\footnote{The metamodel in~\cite{dang2020efficient} identifies $100\%$ of the true tail scenarios on with a $10\%$ safety margin for a \gls{gmab} contract.
+The \gls{gmab} contract is simpler than the \gls{gmwb} contract, and the true tail scenarios are easier to identify. 
+For a \gls{gmab}, our \gls{lstm} metamodel identifies $100\%$ of the true tail scenarios with a $2.5\%$ safety margin}.
+The \gls{rnn} metamodel suffers from the vanishing gradient problem during the training stage. 
+For some macro replications (as shown in Figure~\ref{subfig2:badRNN}), the \gls{rnn} metamodels' predictions are far from the true losses, especially on the tails.
 Seperating the good training macro replications from the bad ones, the results reconcile with the findings in Table~\ref{tab:gmwb_arch}.
-The FNN metamodel has a better fit than the regression metamodels, but it does not have the same level of accuracy as the LSTM metamodel, which is a specialized network to capture the sequential structure of our time-series features.
+The \gls{fnn} metamodel has a better fit than the regression metamodels, but it does not have the same level of accuracy as the \gls{lstm} metamodel, which is a specialized network to capture the sequential structure of our time-series features.
 For comparison, the horizontal dotted line shows the percentage of correctly identified true tails for the standard nested simulation procedure.
@@
 Otherwise, the two-stage procedure will offer no computational advantage in simulation budget over the standard procedure.
-The LSTM metamodel can reach similar percentage with a $5\%$ safety margin.
-This indicates that the LSTM metamodel should be able to reach the same level of accuracy as the standard procedure with only $20\%$ of the simulation budget.
+The \gls{lstm} metamodel can reach similar percentage with a $5\%$ safety margin.
+This indicates that the \gls{lstm} metamodel should be able to reach the same level of accuracy as the standard procedure with only $20\%$ of the simulation budget.
 
@@
 
-Lastly, we return to our original goal of estimating the $95\%$-CVaR of the dynamic hedging error.
-Figure~\ref{fig2:CVaR95} shows the $95\%$-CVaR estimates for all five metamodels with different safety margins, averaged over $100$ macro replications.
+Lastly, we return to our original goal of estimating the $95\%$-\gls{cvar} of the dynamic hedging error.
+Figure~\ref{fig2:CVaR95} shows the $95\%$-\gls{cvar} estimates for all five metamodels with different safety margins, averaged over $100$ macro replications.
 Figure~\ref{subfig2:ZoomedSafetyMargin} is a zoomed version of Figure~\ref{subfig2:AllSafetyMargin}.
-Because the safety margin only affects the two-stage procedure, the true 95\%-CVaR and the one estimated by the standard procedure are horizontal lines (which are the solid and dotted lines, respectively) in Figure~\ref{fig2:CVaR95}.
-We observe that, with reasonable safety margins, the two-stage procedures with a LSTM metamodel consistently produce estimates that are as accurate as the standard procedure's estimate.
+Because the safety margin only affects the two-stage procedure, the true 95\%-\gls{cvar} and the one estimated by the standard procedure are horizontal lines (which are the solid and dotted lines, respectively) in Figure~\ref{fig2:CVaR95}.
+We observe that, with reasonable safety margins, the two-stage procedures with a \gls{lstm} metamodel consistently produce estimates that are as accurate as the standard procedure's estimate.
 The amount of computational savings is substantial.
-The LSTM is particularly superior to other metamodels as it accurately identifies the true tail scenarios and produces highly accurate CVaR estimates with small safety margins.
-By concentrating the simulation budget on the predicted tail scenarios, the two-stage procedure with the LSTM metamodel is able to achieve a similar degree of accuracy as the standard procedure with a much smaller simulation budget.
-As the percentage of correctly identified tails approaches $100\%$, the two-stage procedure's CVaR estimates does not converge to the true CVaR but to the standard procedure's estimate.
-This is because the two-stage procedure's CVaR estimates are based on the standard procedure's estimates on the predicted tail scenarios, and the standard procedure's estimates themselves are also noisy.
+The \gls{lstm} is particularly superior to other metamodels as it accurately identifies the true tail scenarios and produces highly accurate \gls{cvar} estimates with small safety margins.
+By concentrating the simulation budget on the predicted tail scenarios, the two-stage procedure with the \gls{lstm} metamodel is able to achieve a similar degree of accuracy as the standard procedure with a much smaller simulation budget.
+As the percentage of correctly identified tails approaches $100\%$, the two-stage procedure's \gls{cvar} estimates does not converge to the true \gls{cvar} but to the standard procedure's estimate.
+This is because the two-stage procedure's \gls{cvar} estimates are based on the standard procedure's estimates on the predicted tail scenarios, and the standard procedure's estimates themselves are also noisy.
 
@@
 
-For financial and actuarial applications, regulators and practitioners are often concerned about the robustness of DNN models to noise in training labels, which hinders the adoption of these models in practice.
+For financial and actuarial applications, regulators and practitioners are often concerned about the robustness of \gls{dnn} models to noise in training labels, which hinders the adoption of these models in practice.
 Since the true relationship is unknown in real-world applications, most deep learning literature illustrates the impact of noise by artificially injecting noise into real-world datasets, which is already noisy prior to the injection.
 In our numerical experiments, we are able to use Monte Carlo simulation to generate a true dataset that approximates the true hedging losses with a high degree of precision, and, as a result, we are able to explore the important question of whether deep learning models are indeed capable of learning the true feature-label relationship from noisy training labels.
-In this section, we treat the standard nested simulation procedure as a data generator and examine the noise tolerance of LSTM metamodels by varying the numbers of the outer scenarios ($M$) and the inner replications ($N$) used to generate the training samples.
+In this section, we treat the standard nested simulation procedure as a data generator and examine the noise tolerance of \gls{lstm} metamodels by varying the numbers of the outer scenarios ($M$) and the inner replications ($N$) used to generate the training samples.
 
@@
 We also generate a \textit{medium-noise dataset} and a \textit{high-noise dataset} by running the standard nested simulation procedure with $N=10$ and $N=1$ inner replications, respectively.
-By altering the data quantity and quality, we conduct a sensitivity analysis on the LSTM metamodels' noise tolerance.
-We study the impact of noisy data on two LSTM metamodels with different model capacities, i.e., different numbers of trainable parameters.
-The two LSTM metamodels has the same number of layers, but their numbers of hidden units in each layer are different.
-More specfically, the high-capacity LSTM metamodel has $128$ and $16$ hidden units in the first and second LSTM layers, respectively, while the low-capacity LSTM metamodel has $32$ and $4$.
+By altering the data quantity and quality, we conduct a sensitivity analysis on the \gls{lstm} metamodels' noise tolerance.
+We study the impact of noisy data on two \gls{lstm} metamodels with different model capacities, i.e., different numbers of trainable parameters.
+The two \gls{lstm} metamodels has the same number of layers, but their numbers of hidden units in each layer are different.
+More specfically, the high-capacity \gls{lstm} metamodel has $128$ and $16$ hidden units in the first and second \gls{lstm} layers, respectively, while the low-capacity \gls{lstm} metamodel has $32$ and $4$.
 
@@
 The reason for using a maximum of $\num{100000}$ data points is precisely due to the computational cost of running the standard nested simulation procedure.
-For consistency, the LSTM metamodels are trained with the same architecture and training settings as in the previous experiments.
+For consistency, the \gls{lstm} metamodels are trained with the same architecture and training settings as in the previous experiments.
 
@@
         \midrule
-        LSTM                & $\num{100}$                & $0.075 (\pm4.5\times 10^{-3})$         & $0.079(\pm5.4\times 10^{-3})$     & $0.063 (\pm4.4\times 10^{-3})$ \\ 
-        High-capacity LSTM  & $\num{100}$                & $0.068 (\pm3.6\times 10^{-3})$         & $0.102(\pm6.1\times 10^{-2})$     & $0.060 (\pm3.6\times 10^{-3})$ \\
+        \gls{lstm}                & $\num{100}$                & $0.075 (\pm4.5\times 10^{-3})$         & $0.079(\pm5.4\times 10^{-3})$     & $0.063 (\pm4.4\times 10^{-3})$ \\ 
+        High-capacity \gls{lstm}  & $\num{100}$                & $0.068 (\pm3.6\times 10^{-3})$         & $0.102(\pm6.1\times 10^{-2})$     & $0.060 (\pm3.6\times 10^{-3})$ \\
         Average Difference  & $\num{100}$                & $-0.007$                               & $0.023$                           & $-0.003$ \\
         \hline
-        LSTM                & $\num{10}$                 & $0.195 (\pm1.1\times 10^{-3})$         & $0.193(\pm1.7\times 10^{-3})$     & $0.070 (\pm9.1\times 10^{-4})$ \\
-        High-capacity LSTM  & $\num{10}$                 & $0.157 (\pm2.0\times 10^{-3})$         & $0.199(\pm1.9\times 10^{-3})$     & $0.065 (\pm1.9\times 10^{-3})$ \\
+        \gls{lstm}                & $\num{10}$                 & $0.195 (\pm1.1\times 10^{-3})$         & $0.193(\pm1.7\times 10^{-3})$     & $0.070 (\pm9.1\times 10^{-4})$ \\
+        High-capacity \gls{lstm}  & $\num{10}$                 & $0.157 (\pm2.0\times 10^{-3})$         & $0.199(\pm1.9\times 10^{-3})$     & $0.065 (\pm1.9\times 10^{-3})$ \\
         Average Difference  & $\num{10}$                 & $-0.038$                               & $0.006$                           & $-0.005$ \\
         \hline
-        LSTM                & $\num{1}$                  & $1.366 (\pm8.6\times 10^{-3})$         & $0.781(\pm6.0\times 10^{-3})$     & $0.129 (\pm5.0\times 10^{-3})$ \\
-        High-capacity LSTM  & $\num{1}$                  & $1.354 (\pm2.7\times 10^{-2})$         & $0.795(\pm8.3\times10^{-2})$      & $0.149 (\pm2.7\times 10^{-2})$ \\
+        \gls{lstm}                & $\num{1}$                  & $1.366 (\pm8.6\times 10^{-3})$         & $0.781(\pm6.0\times 10^{-3})$     & $0.129 (\pm5.0\times 10^{-3})$ \\
+        High-capacity \gls{lstm}  & $\num{1}$                  & $1.354 (\pm2.7\times 10^{-2})$         & $0.795(\pm8.3\times10^{-2})$      & $0.149 (\pm2.7\times 10^{-2})$ \\
         Average Difference  & $\num{1}$                  & $-0.012$                               & $0.014$                           & \textcolor{red}{$0.020$} \\
@@
 For this particular experiment, we are more interested in the true errors, which measure the metamodels' ability to learn the true feature-label relationship from the low-noise, medium-noise, and high-noise datasets.
-We first observe that all the true errors are lower than the training errors, indicating that the LSTM metamodels generalize well to predicting the true losses.
-Both LSTM metamodels are able to learn the true feature-label relationship from the low-noise and medium-noise datasets.
-However, when the noise level is high, both LSTM metamodels have high true errors.
+We first observe that all the true errors are lower than the training errors, indicating that the \gls{lstm} metamodels generalize well to predicting the true losses.
+Both \gls{lstm} metamodels are able to learn the true feature-label relationship from the low-noise and medium-noise datasets.
+However, when the noise level is high, both \gls{lstm} metamodels have high true errors.
 
-The differences in the errors between the LSTM metamodels are also reported in the last rows of Table~\ref{tab:lstm_arch}.
-A positive difference indicates that the high-capacity LSTM has a higher error than the regular LSTM.
-We observe that both LSTM metamodels have similar errors on the low-noise and medium-noise datasets.
-However, when the noise level is high, the high-capacity LSTM has higher errors than the regular LSTM.
-This is because the high-capacity LSTM has more trainable parameters and is more prone to over-fitting to the noise in the training labels.
-In contrast, the LSTM metamodel is more robust to label noise and is able to learn the true feature-label relationship better from the high-noise dataset.
+The differences in the errors between the \gls{lstm} metamodels are also reported in the last rows of Table~\ref{tab:lstm_arch}.
+A positive difference indicates that the high-capacity \gls{lstm} has a higher error than the regular \gls{lstm}.
+We observe that both \gls{lstm} metamodels have similar errors on the low-noise and medium-noise datasets.
+However, when the noise level is high, the high-capacity \gls{lstm} has higher errors than the regular \gls{lstm}.
+This is because the high-capacity \gls{lstm} has more trainable parameters and is more prone to over-fitting to the noise in the training labels.
+In contrast, the \gls{lstm} metamodel is more robust to label noise and is able to learn the true feature-label relationship better from the high-noise dataset.
 In practice, since the true relationship is unknown, the true error is not readily available.
 The test error approximates the true error and is directly observable.
-The differences in test errors of the LSTM metamodels are inconsistent with the differences in true errors.
+The differences in test errors of the \gls{lstm} metamodels are inconsistent with the differences in true errors.
 Therefore, test errors are not reliable indicators of the metamodels' noise tolerance.
@@
 
-In summary, our numerical experiments demonstrate that both LSTM metamodels are capable of learning the true inner simulation model from the noisy training labels.
+In summary, our numerical experiments demonstrate that both \gls{lstm} metamodels are capable of learning the true inner simulation model from the noisy training labels.
 In most cases, a high-capacity metamodel is shown to perform better.
@@
 
-In further details, the QQ-plots depicted in Figure~\ref{fig2:QQ_All} illustrates the fit of the two LSTM metamodels when different noise levels are present in the training labels.
-They are arranged in a 2-by-3 grid, where the two rows correspond to the two LSTM metamodels with different model capacities, and the three columns correspond to the increasing noise levels.
+In further details, the QQ-plots depicted in Figure~\ref{fig2:QQ_All} illustrates the fit of the two \gls{lstm} metamodels when different noise levels are present in the training labels.
+They are arranged in a 2-by-3 grid, where the two rows correspond to the two \gls{lstm} metamodels with different model capacities, and the three columns correspond to the increasing noise levels.
 The Pearson correlation coefficient between the true losses and the predicted losses is labeled in each subplot.
@@
 \begin{enumerate}
-    \item   When trained on the low-noise dataset, the metamodel predictions of high-capacity LSTM align more closely with the true labels than the regular LSTM.
-    This is expected because the high-capacity LSTM has more trainable parameters and is able to learn more complex relationships better when the noise level is low.
-    \item   When the noise level is medium or high, the high-capacity LSTM is more affected than the regular LSTM.
-    This is because the high-capacity LSTM has more trainable parameters and is more prone to over-fitting to the noise in the training labels.
-    In contrast, the regular LSTM is more robust to label noise.
+    \item   When trained on the low-noise dataset, the metamodel predictions of high-capacity \gls{lstm} align more closely with the true labels than the regular \gls{lstm}.
+    This is expected because the high-capacity \gls{lstm} has more trainable parameters and is able to learn more complex relationships better when the noise level is low.
+    \item   When the noise level is medium or high, the high-capacity \gls{lstm} is more affected than the regular \gls{lstm}.
+    This is because the high-capacity \gls{lstm} has more trainable parameters and is more prone to over-fitting to the noise in the training labels.
+    In contrast, the regular \gls{lstm} is more robust to label noise.
 \end{enumerate}
 
-To further test the sensitivity of a LSTM metamodel and provide a more comprehensive view of the noise tolerance of DNN models, we conduct a sensitivity analysis on the noise tolerance of the regular LSTM metamodel by varying the numbers of outer scenarios ($M$) and inner replications ($N$) used to generate the training dataset.
+To further test the sensitivity of a \gls{lstm} metamodel and provide a more comprehensive view of the noise tolerance of \gls{dnn} models, we conduct a sensitivity analysis on the noise tolerance of the regular \gls{lstm} metamodel by varying the numbers of outer scenarios ($M$) and inner replications ($N$) used to generate the training dataset.
 The number of outer scenarios corresponds to the number of data points in the training dataset, and the number of inner replications controls the noise level in the training labels.
@@
 
-Table~\ref{tab2:lstm_sens} and~\ref{tab2:hicaplstm_sens} show the average squared errors between the LSTM predictions and the true losses for increasing $M$ and $N$.
-The last rows of Table~\ref{tab2:lstm_sens} and Table~\ref{tab2:hicaplstm_sens} show the performance of the regular and high capacity LSTM metamodels trained with $M=\num{100000}$ training labels with different noise levels.
-We observe that an increasing $N$ reduces the MSE, but the reduction is not substantial for a regular LSTM when $N$ is larger than $\num{10}$.
-For the high-capacity LSTM, the MSE is substantially reduced when $N$ is increased from $\num{1}$ to $\num{100}$, but the reduction is not substantial when $N$ is increased from $\num{100}$ to $\num{1000}$.
+Table~\ref{tab2:lstm_sens} and~\ref{tab2:hicaplstm_sens} show the average squared errors between the \gls{lstm} predictions and the true losses for increasing $M$ and $N$.
+The last rows of Table~\ref{tab2:lstm_sens} and Table~\ref{tab2:hicaplstm_sens} show the performance of the regular and high capacity \gls{lstm} metamodels trained with $M=\num{100000}$ training labels with different noise levels.
+We observe that an increasing $N$ reduces the MSE, but the reduction is not substantial for a regular \gls{lstm} when $N$ is larger than $\num{10}$.
+For the high-capacity \gls{lstm}, the MSE is substantially reduced when $N$ is increased from $\num{1}$ to $\num{100}$, but the reduction is not substantial when $N$ is increased from $\num{100}$ to $\num{1000}$.
 Another way to interpret the results in Table~\ref{tab2:lstm_sens} is to compare the MSEs for the same budget of $\Gamma = M \times N$.
@@
 For most budgets, the MSEs are also the lowest when $N = 10$.
-The results in Table~\ref{tab2:lstm_sens} suggest that the performance of the LSTM metamodel is more sensitive to the number of outer scenarios than the number of inner replications.
+The results in Table~\ref{tab2:lstm_sens} suggest that the performance of the \gls{lstm} metamodel is more sensitive to the number of outer scenarios than the number of inner replications.
 Treating the neural network as an advanced regression metamodel, we find this pheonomenon to be consistent with the results in~\cite{broadie2015risk}, where the authors show that the performance of a regression-based nested simulation procedure is more affected by the number of outer scenarios.
-The last row in Table~\ref{tab2:lstm_sens} and ~\ref{tab2:hicaplstm_sens} show that the high-capacity LSTM metamodel is relatively insensitive to the number of inner replications.
+The last row in Table~\ref{tab2:lstm_sens} and ~\ref{tab2:hicaplstm_sens} show that the high-capacity \gls{lstm} metamodel is relatively insensitive to the number of inner replications.
 To make the most efficient use of a fixed simulation budget, the number of inner replication should be set constant around $N=10$ while increasing the number of outer scenarios to the maximum.
 
-To further investigate the LSTM metamodels' sensitivity to data quantity and quality ($M$ and $N$, respectively), we report the Spearman rank correlation coefficients Table~\ref{tab2:lstm_corr}, which measure the ability to rank the scenarios by their true losses.
-It is an appropriate measure of the metamodel's performance in the two-stage procedure, where the metamodel is used to identify the predicted tail scenario set, on which extensive simulations are run in stage 2 to estimate the $95\%$-CVaR.
+To further investigate the \gls{lstm} metamodels' sensitivity to data quantity and quality ($M$ and $N$, respectively), we report the Spearman rank correlation coefficients Table~\ref{tab2:lstm_corr}, which measure the ability to rank the scenarios by their true losses.
+It is an appropriate measure of the metamodel's performance in the two-stage procedure, where the metamodel is used to identify the predicted tail scenario set, on which extensive simulations are run in stage 2 to estimate the $95\%$-\gls{cvar}.
 The Pearson correlation coefficients are also included in the parentheses to illustrate the linear correlation between the predicted losses and the true losses.
 They measure the metamodel's overall prediction accuracy.
-Our previous numerical experiments illustrated in Figure~\ref{fig2:tailMatches} have shown that the LSTM metamodel predictions have high \textit{Spearman} correlation with the true labels for the combination $M=\num{100000}$ and $N=\num{100}$.
-We intend to examine if LSTM predictions also have high \textit{Pearson} correlation with the true labels.
-A high \textit{Pearson} correlation suggests the possibility of using LSTM predictions to estimate risk measures directly.
+Our previous numerical experiments illustrated in Figure~\ref{fig2:tailMatches} have shown that the \gls{lstm} metamodel predictions have high \textit{Spearman} correlation with the true labels for the combination $M=\num{100000}$ and $N=\num{100}$.
+We intend to examine if \gls{lstm} predictions also have high \textit{Pearson} correlation with the true labels.
+A high \textit{Pearson} correlation suggests the possibility of using \gls{lstm} predictions to estimate risk measures directly.
 
@@
 
-Consistent with our previous numerical experiments, the Spearman correlations of a high-capacity LSTM is high for a moderate simulation budget. 
+Consistent with our previous numerical experiments, the Spearman correlations of a high-capacity \gls{lstm} is high for a moderate simulation budget. 
 For $M= \num{100000}$, the Spearman correlation is relativelyinsensitive to $N$.
@@
 
-Figure~\ref{fig2:cor-heatmap} shows the difference between the Spearman and Pearson correlation coefficients for the high-capacity LSTM metamodel.
+Figure~\ref{fig2:cor-heatmap} shows the difference between the Spearman and Pearson correlation coefficients for the high-capacity \gls{lstm} metamodel.
 The heatmap is generated by subtracting the Pearson correlation coefficients from the Spearman correlation.
 We observe that Spearman correlation coefficients are not substantially different from the Pearson correlation coefficients for any $N$ larger than $\num{10}$. 
-This is a strong evidence that the LSTM metamodel is not only able to effectively rank the scenarios by their true losses, but also able to make accurate loss predictions.
-Instead of using the LSTM metamodel only for classifying tail scenarios in a two-stage procedure, LSTM's ability to cut through a moderate level of noise in training labels encourages us to use its predictions to estimate the CVaR directly.
+This is a strong evidence that the \gls{lstm} metamodel is not only able to effectively rank the scenarios by their true losses, but also able to make accurate loss predictions.
+Instead of using the \gls{lstm} metamodel only for classifying tail scenarios in a two-stage procedure, \gls{lstm}'s ability to cut through a moderate level of noise in training labels encourages us to use its predictions to estimate the \gls{cvar} directly.
 
@@
 
-The accuracy and robustness of the LSTM metamodels motivate us to propose a single-stage procedure that uses the metamodel predictions to estimate the CVaR directly. 
+The accuracy and robustness of the \gls{lstm} metamodels motivate us to propose a single-stage procedure that uses the metamodel predictions to estimate the \gls{cvar} directly. 
 Instead of relying on the standard nested simulation procedure in stage 2, the single-stage procedure can be even more efficient.
-In this section, we compare the single-stage procedure to the two-stage procedure and the standard procedure in estimating the $95\%$-CVaR of the hedging losses for GMWB.
+In this section, we compare the single-stage procedure to the two-stage procedure and the standard procedure in estimating the $95\%$-\gls{cvar} of the hedging losses for \gls{gmwb}.
 In our numerical experiments, the results for the single-stage procedure is obtained with the same metamodels as in the two-stage procedure.
@@
 
-Figure~\ref{fig2:CVaRsingleStage} shows the boxplots of the 95\%-CVaR estimates of the single-stage procedure with different metamodels and compares them to the two-stage procedure and the standard procedure.
+Figure~\ref{fig2:CVaRsingleStage} shows the boxplots of the 95\%-\gls{cvar} estimates of the single-stage procedure with different metamodels and compares them to the two-stage procedure and the standard procedure.
 The two-stage procedure uses the same simulation budget as the single-stage procedure in stage 1 with an extra amount of budget for an  extensive inner simulation on the predicted tail scenarios in stage 2.
 The metamodel with the best performance in the two-stage procedure is selected, and the safety margin is set to $0\%$.
-The standard procedure shown in Figure~\ref{fig2:CVaRsingleStage} uses the noisy loss labels in the training dataset to estimate the CVaR directly, which uses the same simulation budget as the single-stage procedure.
-We observe that the single-stage procedures with the regular LSTM metamodel consistently produce CVaR estimates that are closer to the true value than the standard procedure's estimate.
+The standard procedure shown in Figure~\ref{fig2:CVaRsingleStage} uses the noisy loss labels in the training dataset to estimate the \gls{cvar} directly, which uses the same simulation budget as the single-stage procedure.
+We observe that the single-stage procedures with the regular \gls{lstm} metamodel consistently produce \gls{cvar} estimates that are closer to the true value than the standard procedure's estimate.
 This finding is especially impressive when the noise level in the training labels is high.
-It is another strong evidence that a well-selected LSTM metamodel is able to cut through the noise in the noisy training labels and make accurate loss predictions that lead to accurate CVaR estimates.
+It is another strong evidence that a well-selected \gls{lstm} metamodel is able to cut through the noise in the noisy training labels and make accurate loss predictions that lead to accurate \gls{cvar} estimates.
 The difference in performance among the metamodels is more pronounced in the single-stage procedure than in the two-stage procedure.
-Trained using medium noise labels, the high-capacity LSTM metamodel consistently produces CVaR estimates that are closer to the true value than the regular LSTM, while the other metamodels produce worse estimates.
+Trained using medium noise labels, the high-capacity \gls{lstm} metamodel consistently produces \gls{cvar} estimates that are closer to the true value than the regular \gls{lstm}, while the other metamodels produce worse estimates.
 
-However, when the noise level in the training labels is high, the high-capacity LSTM suffers from severe overfitting. 
+However, when the noise level in the training labels is high, the high-capacity \gls{lstm} suffers from severe overfitting. 
 This is also evident in Table~\ref{tab:lstm_arch}.
-Since we are using the metamodel predictions to estimate the CVaR directly without any safety margin, the metamodel's overall prediction accuracy becomes more important.
+Since we are using the metamodel predictions to estimate the \gls{cvar} directly without any safety margin, the metamodel's overall prediction accuracy becomes more important.
 In other words, the single-stage procedure is more sensitive to the metamodel's ability to make accurate loss predictions than the two-stage procedure.
-Previously, a generic FNN metamodel performs well in the two-stage procedure. 
-However, results in Figure~\ref{fig2:CVaRsingleStage} suggest that the FNN metamodel should not be used in the single-stage procedure.
+Previously, a generic \gls{fnn} metamodel performs well in the two-stage procedure. 
+However, results in Figure~\ref{fig2:CVaRsingleStage} suggest that the \gls{fnn} metamodel should not be used in the single-stage procedure.
 
-A single-stage procedure with a regular LSTM metamodel is particularly superior to the two-stage procedure, as it is able to achieve a higher accuracy as the standard procedure with a much smaller amount of simulation budget.
+A single-stage procedure with a regular \gls{lstm} metamodel is particularly superior to the two-stage procedure, as it is able to achieve a higher accuracy as the standard procedure with a much smaller amount of simulation budget.
 Note that the single-stage procedure does not require a safety margin.
@@
 For a two-stage procedure with a $0\%$ safety margin, the extra computational cost is from the extensive inner simulation in stage 2.
-On $4$ $20$-core Intel Xeon Gold $\num{6230}$ processors, stage 2 of the two-stage procedure takes $30$ minutes to run with parallel processing, while the $95\%$ confidence band of training time of the high-capacity LSTM metamodel is $(19.64 \pm 0.94)$ minutes on an Nvidia RTX $\num{3060}$ Ti GPU.
+On $4$ $20$-core Intel Xeon Gold $\num{6230}$ processors, stage 2 of the two-stage procedure takes $30$ minutes to run with parallel processing, while the $95\%$ confidence band of training time of the high-capacity \gls{lstm} metamodel is $(19.64 \pm 0.94)$ minutes on an Nvidia RTX $\num{3060}$ Ti GPU.
 While the accuracy of the two-stage procedure is highly dependent on the safety margin, increasing the safety margin introduces extra computational cost.
-Therefore, while achieving a higher accuracy in estimating the CVaR, the single-stage procedure requires only $60\%$ computation time of the two-stage procedure.
+Therefore, while achieving a higher accuracy in estimating the \gls{cvar}, the single-stage procedure requires only $60\%$ computation time of the two-stage procedure.
 
@@
 
-To further investigate the single-stage procedure's performance, we conduct a convergence analysis on the LSTM metamodels.
-Figure~\ref{fig2:gammaConvergence} shows the log-log plots of the relative root mean square errors (RRMSE) between the LSTM metamodel CVaR predictions and the true CVaR against the total simulation budget $\Gamma$.
+To further investigate the single-stage procedure's performance, we conduct a convergence analysis on the \gls{lstm} metamodels.
+Figure~\ref{fig2:gammaConvergence} shows the log-log plots of the relative root mean square errors (RRMSE) between the \gls{lstm} metamodel \gls{cvar} predictions and the true \gls{cvar} against the total simulation budget $\Gamma$.
 For each budget $\Gamma$, the metamodels are trained for different combinations of $M$ and $N$, and the metamodel with the best RRMSE is plotted.
-While numerical results suggest that the CVaR estimator of the single-stage procedure with LSTM metamodels may have better accuracy than the two-stage procedure and the standard procedure when the number of outer scenarios is further increased, we found it difficult to compare their performance due to insufficient computational resources.
+While numerical results suggest that the \gls{cvar} estimator of the single-stage procedure with \gls{lstm} metamodels may have better accuracy than the two-stage procedure and the standard procedure when the number of outer scenarios is further increased, we found it difficult to compare their performance due to insufficient computational resources.
 For $\Gamma \leq \num{100000}$, the number of outer scenarios is fixed at $M = \num{100000}$, and only the number of inner replications is varied.
@@
 
-Figure~\ref{fig2:mnConvergence} shows the log-log plots of the RRMSE between the LSTM metamodel CVaR predictions and the true CVaR against the simulation budget.
+Figure~\ref{fig2:mnConvergence} shows the log-log plots of the RRMSE between the \gls{lstm} metamodel \gls{cvar} predictions and the true \gls{cvar} against the simulation budget.
 The left figure shows the empirical convergence of the RRMSE for increasing inner replications with a fixed number of outer scenarios ($M=\num{100000}$), and the right figure shows the empirical convergence of the RRMSE for increasing outer scenarios with a fixed number of inner replications ($N=\num{10}$).
@@
 We observe that the RRMSE decreases as the simulation budget increases, and the rate of convergence is higher when the quantity of the data increases.
-For an LSTM metamodel, increasing the data quality of the training labels has diminishing returns, which is consistent with the results in Figure~\ref{fig2:mnConvergence}.
+For an \gls{lstm} metamodel, increasing the data quality of the training labels has diminishing returns, which is consistent with the results in Figure~\ref{fig2:mnConvergence}.
 For an increasing number of inner replications with a fixed number of outer scenarios, the RRMSE ceases to decrease after reaching $N = \num{100}$. 
-More specfically, when the quality of the training labels is fixed at $N = \num{10}$, the CVaR estimator of a single-stage procedure with a LSTM metamodel converge roughly in the order of $\mathcal{O}(M^{\frac{2}{3}})$.
+More specfically, when the quality of the training labels is fixed at $N = \num{10}$, the \gls{cvar} estimator of a single-stage procedure with a \gls{lstm} metamodel converge roughly in the order of $\mathcal{O}(M^{\frac{2}{3}})$.
 This observation resonates with the best possible convergence rate of a standard nested simulation procedure in~\cite{gordy2010nested}.
@@
 \section{Conclusion} \label{sec2:conclusion}
-The proposed nested simulation procedures with DNN metamodels are shown to result in substantial computational savings in estimating CVaR of the hedging loss of a VA contract from accurately predicting the hedging losses and identifying the tail scenarios.
-When new outer scenarios are generated, a trained LSTM metamodel can distinguish between tail and non-tail scenarios and make accurate predictions without the need to run new inner simulations.
+The proposed nested simulation procedures with \gls{dnn} metamodels are shown to result in substantial computational savings in estimating \gls{cvar} of the hedging loss of a \gls{va} contract from accurately predicting the hedging losses and identifying the tail scenarios.
+When new outer scenarios are generated, a trained \gls{lstm} metamodel can distinguish between tail and non-tail scenarios and make accurate predictions without the need to run new inner simulations.
 
-Our novel experiment design allows us to examine the impact of label noise on DNN models.
-We find that a DNN with a suitable architecture is able to cut through the noise in training labels and learn the true complex dynamic hedging model.
+Our novel experiment design allows us to examine the impact of label noise on \gls{dnn} models.
+We find that a \gls{dnn} with a suitable architecture is able to cut through the noise in training labels and learn the true complex dynamic hedging model.
 By showcasing the resilience of these models, our study aims at encouraging regulatory bodies to recognize the value and applicability of deep learning metamodels in financial risk management, and it provides informed suggestions and guidance for the incorporation and oversight of advanced deep learning metamodel in Monte Carlo Simulation in financial applications.
@@
 
-In our numerical experiments, a LSTM metamodel is resilient to a high level of noise in training labels and is able to make accurate predictions. 
-This is an encouraging evidence that DNN metamodels can be used to improve the efficiency of Monte Carlo simulation for quantitative risk management tasks that require a computational-expensive simulation procedure.
-We propose two nested simulation procedures that use DNN metamodels to estimate risk measures of the hedging loss of a VA contract.
+In our numerical experiments, a \gls{lstm} metamodel is resilient to a high level of noise in training labels and is able to make accurate predictions. 
+This is an encouraging evidence that \gls{dnn} metamodels can be used to improve the efficiency of Monte Carlo simulation for quantitative risk management tasks that require a computational-expensive simulation procedure.
+We propose two nested simulation procedures that use \gls{dnn} metamodels to estimate risk measures of the hedging loss of a \gls{va} contract.
 For estimating tail risk measures, our two-stage procedure is designed to address regulatory concerns by avoiding the direct use of metamodel predictions but instead by using them to identify the potential tail scenarios.
@@
 It is more efficient and can be extended to estimate risk measures that require knowledge of the entire loss distribution.
-Our numerical experiments demonstrate that the proposed single-stage procedure with DNN metamodels result in further computational savings over our two-stage procedure. 
-Furthermore, our numerical results provide evidences for adopting DNN metamodels in Monte Carlo simulation for risk management tasks.
-Through our systematic empirical study of the noise tolerance of DNN metamodels, we address regulatory concerns by showing that a LSTM metamodel with moderate model capacity is resilient to a high level of noise in training labels and is able to make accurate predictions.
-A possible future research direction is to apply DNN metamodels in other financial risk management tasks that requires complex nested simulation with high-dimensional outer scenarios.
-Another future research direction is to investigate the impact of label noise on other deep learning models, such as convolutional neural networks and transformer models, and to compare their performance with LSTM metamodels in nested simulation procedures.
-From a practical standpoint, the choice of a suitable DNN architecture is crucial for the success of a deep learning metamodel in nested simulation procedures.
-We find that a LSTM metamodel is the most suitable for our dynamic hedging simulation model with time series features, but the optimal network architecture may vary for different simulation models.
-Exploring DNN metamodels in other complex risk management tasks presents a promising avenue for research, especially as these tasks often involve complex, high-dimensional scenarios where traditional methods are insufficient.
+Our numerical experiments demonstrate that the proposed single-stage procedure with \gls{dnn} metamodels result in further computational savings over our two-stage procedure. 
+Furthermore, our numerical results provide evidences for adopting \gls{dnn} metamodels in Monte Carlo simulation for risk management tasks.
+Through our systematic empirical study of the noise tolerance of \gls{dnn} metamodels, we address regulatory concerns by showing that a \gls{lstm} metamodel with moderate model capacity is resilient to a high level of noise in training labels and is able to make accurate predictions.
+A possible future research direction is to apply \gls{dnn} metamodels in other financial risk management tasks that requires complex nested simulation with high-dimensional outer scenarios.
+Another future research direction is to investigate the impact of label noise on other deep learning models, such as convolutional neural networks and transformer models, and to compare their performance with \gls{lstm} metamodels in nested simulation procedures.
+From a practical standpoint, the choice of a suitable \gls{dnn} architecture is crucial for the success of a deep learning metamodel in nested simulation procedures.
+We find that a \gls{lstm} metamodel is the most suitable for our dynamic hedging simulation model with time series features, but the optimal network architecture may vary for different simulation models.
+Exploring \gls{dnn} metamodels in other complex risk management tasks presents a promising avenue for research, especially as these tasks often involve complex, high-dimensional scenarios where traditional methods are insufficient.
 The versatility of neural networks could unlock new insights across a broad spectrum of financial and actuarial applications.
 
-In this chapter, we have demonstrated the potential of DNN metamodels to estimate risk measures with high accuracy and efficiency when simulation data is abundant.
+In this chapter, we have demonstrated the potential of \gls{dnn} metamodels to estimate risk measures with high accuracy and efficiency when simulation data is abundant.
 In practice, simulation data is often scarce for new market conditions and new insurance products.
-DNN metamodels are known to suffer from over-fitting when the number of training samples is limited.
-In the next chapter, we will extend our study to transfer learning and show that DNN metamodels trained on an existing VA contract can be transferred to a new VA contract with different market conditions.
-We hypothesize that the DNN metamodel will generalize well to the new VA contract, and the computational savings from transfer learning will be substantial.
+\gls{dnn} metamodels are known to suffer from over-fitting when the number of training samples is limited.
+In the next chapter, we will extend our study to transfer learning and show that \gls{dnn} metamodels trained on an existing \gls{va} contract can be transferred to a new \gls{va} contract with different market conditions.
+We hypothesize that the \gls{dnn} metamodel will generalize well to the new \gls{va} contract, and the computational savings from transfer learning will be substantial.

### 2025-04-13 project3/draft.tex
11

@@
 
-In the evolving landscape of financial markets, insurance products such as VAs have gained a substantial amount of interest due to their ability to provide both investment growth and guaranteed benefits.
+In the evolving landscape of financial markets, insurance products such as \gls{va}s have gained a substantial amount of interest due to their ability to provide both investment growth and guaranteed benefits.
 Managing risks associated with these products in volatile market conditions is a complex task that demands sophisticated financial modeling techniques such as nested simulation.
@@
 To address the computational burden, metamodeling techniques have been proposed, where a surrogate model approximates the outcomes of a complex simulation procedure. 
-Traditional machine learning models often struggle to capture the intricate nonlinear relationships and temporal dependencies inherent in financial data.
-In particular, DNNs, and specifically LSTM networks, have been employed as metamodels to predict the outcomes of the inner simulations efficiently.
-Chapter~\ref{chap:project2} introduced a metamodeling-based nested simulation framework for dynamic hedging of VAs that approximates the inner simulation by an LSTM metamodel.
-It shows that LSTMs, as a type of gated RNNs, were well-suited as metamodels for Monte Carlo simulation of financial time series and could capture the long-term dependencies in the simulation dataset.
-This property is crucial for the application of dynamic hedging of VAs.
+Traditional \gls{ml} models often struggle to capture the intricate nonlinear relationships and temporal dependencies inherent in financial data.
+In particular, \gls{dnn}s, and specifically \gls{lstm} networks, have been employed as metamodels to predict the outcomes of the inner simulations efficiently.
+Chapter~\ref{chap:project2} introduced a metamodeling-based nested simulation framework for dynamic hedging of \gls{va}s that approximates the inner simulation by an \gls{lstm} metamodel.
+It shows that \gls{lstm}s, as a type of gated \gls{rnn}s, were well-suited as metamodels for \gls{mc} simulation of financial time series and could capture the long-term dependencies in the simulation dataset.
+This property is crucial for the application of dynamic hedging of \gls{va}s.
 
-Despite the advantages of using DNN metamodels, computational challenges arise when market conditions change or new VA contracts with different features are introduced. 
+Despite the advantages of using \gls{dnn} metamodels, computational challenges arise when market conditions change or new \gls{va} contracts with different features are introduced. 
 Retraining neural network metamodels from the scratch in response to every change is computationally inefficient and time-consuming.
@@
 \begin{enumerate}
-    \item The simulation budget is limited, but DNN metamodels require extensive training data to learn the feature-label relationship~\citep{golestaneh2024many}. 
-    \item The computational cost of retraining a suitable DNN metamodel is often much higher than fitting a traditional parametric regression.
+    \item The simulation budget is limited, but \gls{dnn} metamodels require extensive training data to learn the feature-label relationship~\citep{golestaneh2024many}. 
+    \item The computational cost of retraining a suitable \gls{dnn} metamodel is often much higher than fitting a traditional parametric regression.
     \item Financial markets are dynamic with frequent shifts in volatility, interest rates, and other risk factors~\citep{cont2001empirical}.
@@
 
-Constraints on the simulation budget is the most critical challenge for dynamic hedging of VAs.
+Constraints on the simulation budget is the most critical challenge for dynamic hedging of \gls{va}s.
 Any method that involves nested simulation is computationally expensive, and the computational cost is often prohibitive for changing market conditions.
 Therefore, it is essential to develop methods that can rapidly adapt existing metamodels to new conditions without incurring the full computational cost of retraining and extensive addtional simulations.
-Transfer Learning (TL) offers a compelling solution to this problem by enabling the reuse of a pre-trained model on a new but related task~\citep{pan2009survey}.
-In the context of DNNs, TL involves leveraging the knowledge acquired during training on one dataset to improve learning performance on a different dataset~\citep{yosinski2014transferable}.
+Transfer Learning (\gls{tl}) offers a compelling solution to this problem by enabling the reuse of a pre-trained model on a new but related task~\citep{pan2009survey}.
+In the context of \gls{dnn}s, \gls{tl} involves leveraging the knowledge acquired during training on one dataset to improve learning performance on a different dataset~\citep{yosinski2014transferable}.
 This approach can substantially reduce the amount of training data needed, training time and computational resources while enhancing model generalization.
-Instead of starting from the scratch, a new DNN metamodel can be built on top of a pre-trained metamodel and fine-tuned on new data.
-This allows the metamodel to adapt quickly to unseen conditions and new VA contracts.
+Instead of starting from the scratch, a new \gls{dnn} metamodel can be built on top of a pre-trained metamodel and fine-tuned on new data.
+This allows the metamodel to adapt quickly to unseen conditions and new \gls{va} contracts.
 
-In this chapter, we explore the application of TL to the dynamic hedging of VAs using LSTM metamodels.
-We propose a novel TL framework that accelerates the training of DNN metamodels for nested simulation procedures in dynamic hedging.
+In this chapter, we explore the application of \gls{tl} to the dynamic hedging of \gls{va}s using \gls{lstm} metamodels.
+We propose a novel \gls{tl} framework that accelerates the training of \gls{dnn} metamodels for nested simulation procedures in dynamic hedging.
 This setting is particularly relevant for dynamic hedging problems, as insurance companies often underwrite new contracts under changing market conditions and actuarial assumptions.
-This chapter proposes a TL framework that makes fast adaptation of metamodels possible.
-Our approach involves pre-training an LSTM network on a large dataset of VA simulations and then fine-tuning it on a smaller dataset of new VA contracts.
-We evaluate the performance of the TL framework on a real-world dataset of VA contracts and compare it with training a LSTM metamodel from scratch.
-More importantly, we show the strengths and weaknesses of different TL techniques for rapid adaptation of LSTM metamodels.
+This chapter proposes a \gls{tl} framework that makes fast adaptation of metamodels possible.
+Our approach involves pre-training an \gls{lstm} network on a large dataset of \gls{va} simulations and then fine-tuning it on a smaller dataset of new \gls{va} contracts.
+We evaluate the performance of the \gls{tl} framework on a real-world dataset of \gls{va} contracts and compare it with training a \gls{lstm} metamodel from scratch.
+More importantly, we show the strengths and weaknesses of different \gls{tl} techniques for rapid adaptation of \gls{lstm} metamodels.
 
 The rest of this chapter is organized as follows.
-Section~\ref{sec3:background} provides an overview of the dynamic hedging problem for VAs and the use of LSTM networks as metamodels in a nested simulation procedure.
-Section~\ref{sec3:transfer_learning} introduces the TL framework for rapid adaptation of LSTM metamodels in dynamic hedging.
-Section~\ref{sec3:experiments} presents the experimental setup and results, comparing the performance of TL with training from scratch.
+Section~\ref{sec3:background} provides an overview of the dynamic hedging problem for \gls{va}s and the use of \gls{lstm} networks as metamodels in a nested simulation procedure.
+Section~\ref{sec3:transfer_learning} introduces the \gls{tl} framework for rapid adaptation of \gls{lstm} metamodels in dynamic hedging.
+Section~\ref{sec3:experiments} presents the experimental setup and results, comparing the performance of \gls{tl} with training from scratch.
 Finally, Section~\ref{sec3:conclusion} concludes the chapter and discusses future research directions.
@@
 
-TL is a machine learning paradigm where knowledge acquired from a source task is utilized to improve learning performance on a related target task.
-One of the primary applications of TL in finance is asset price prediction. 
-Traditional models, such as geometric Brownian motion (GBM), autoregressive integrated moving average (ARIMA) and generalized autoregressive conditional heteroskedasticity (GARCH), have been widely used in time series modeling.
-ARIMA models~\citep{box1970distribution} combine autoregression, differencing, and moving average components to capture linear relationships in time series data.
-GARCH models~\citep{bollerslev1990modelling}, extend ARCH models to better capture volatility clustering, which is a key stylized fact of financial time series~\citep{cont2001empirical}.
+\gls{tl} is a machine learning paradigm where knowledge acquired from a source task is utilized to improve learning performance on a related target task.
+One of the primary applications of \gls{tl} in finance is asset price prediction. 
+Traditional models, such as geometric Brownian motion (\gls{gbm}), autoregressive integrated moving average (\gls{arima}) and generalized autoregressive conditional heteroskedasticity (\gls{garch}), have been widely used in time series modeling.
+\gls{arima} models~\citep{box1970distribution} combine autoregression, differencing, and moving average components to capture linear relationships in time series data.
+\gls{garch} models~\citep{bollerslev1990modelling}, extend \gls{arch} models to better capture volatility clustering, which is a key stylized fact of financial time series~\citep{cont2001empirical}.
 However, these models often struggle to capture complex dynamics, e.g., regime changes~\citep{hamilton1989new} and extreme market events~\citep{embrechts2013modelling} that are prevalent in financial markets.
-In Chapter~\ref{chap:project2}, our numerical experiment uses a regime-switching geometric Brownian motion (RS-GBM) as the underlying asset model.
+In Chapter~\ref{chap:project2}, our numerical experiment uses a regime-switching geometric Brownian motion (\gls{rsgbm}) as the underlying asset model.
 For estimating tail risk measures, a metamodel-based nested simulation procedure is proposed to approximate the inner simulation.
-We have shown DNN metamodels like RNN and LSTM networks have demonstrated substantial improvements in modeling temporal dependencies, and they save a substantial amount of simulation budget.
+We have shown \gls{dnn} metamodels like \gls{rnn} and \gls{lstm} networks have demonstrated substantial improvements in modeling temporal dependencies, and they save a substantial amount of simulation budget.
 However, training these models from the scratch requires an extensive amount of simulation data, which may not always be available for specific assets or under certain market conditions.
 
-TL offers a solution to this problem by leveraging knowledge from related assets or tasks to improve the learning performance of DNN metamodels on the target task.
-In algorithmic trading,~\cite{jeong2019improving} used TL to enhance the performance of a reinforcement learning agent by preventing overfitting from an insufficient amount of market data.
-TL techniques have also been applied in building fraud detection systems. 
+\gls{tl} offers a solution to this problem by leveraging knowledge from related assets or tasks to improve the learning performance of \gls{dnn} metamodels on the target task.
+In algorithmic trading,~\cite{jeong2019improving} used \gls{tl} to enhance the performance of a reinforcement learning agent by preventing overfitting from an insufficient amount of market data.
+\gls{tl} techniques have also been applied in building fraud detection systems. 
 Financial fraud often exhibits subtle and evolving patterns, and it is challenging to develop robust detection models.
 By transferring previous knowledge from detected fraud cases, models can adapt to detect new fraud schemes more effectively~\citep{lebichot2021transfer}.
-\cite{yan2024comprehensive} conduct a comprehensive survey study of current TL techniques in financial applications, and they find almost all applications of TL only employ parameter transfer, where the pre-trained model is fine-tuned on the target task.
+\cite{yan2024comprehensive} conduct a comprehensive survey study of current \gls{tl} techniques in financial applications, and they find almost all applications of \gls{tl} only employ parameter transfer, where the pre-trained model is fine-tuned on the target task.
 Our multi-task learning framework in Section~\ref{sec3:transfer_learning} extends beyond parameter transfer to shared representation learning across multiple tasks.
 
-Regarding a nested simulation of VAs,~\cite{cheng2019fast} is the most relevant study to our work, where they proposed a TL framework for fast valuation of large portfolios of VAs.
-Instead of using stochastic kriging~\citep{gan2015valuation}, they employed a pre-trained DNN to select the best representative scenarios from a large portfolio of VAs.
-In our work, we focus on the application of TL to accelerate the training of LSTM metamodels for a nested simulation in dynamic hedging of VAs.
-The fine-tuned LSTM metamodels can be readily adapted to the two-stage procedure and the single-stage procedure in Chapter~\ref{chap:project2} to predict the contract losses under different scenarios.
+Regarding a nested simulation of \gls{va}s,~\cite{cheng2019fast} is the most relevant study to our work, where they proposed a \gls{tl} framework for fast valuation of large portfolios of \gls{va}s.
+Instead of using stochastic kriging~\citep{gan2015valuation}, they employed a pre-trained \gls{dnn} to select the best representative scenarios from a large portfolio of \gls{va}s.
+In our work, we focus on the application of \gls{tl} to accelerate the training of \gls{lstm} metamodels for a nested simulation in dynamic hedging of \gls{va}s.
+The fine-tuned \gls{lstm} metamodels can be readily adapted to the two-stage procedure and the single-stage procedure in Chapter~\ref{chap:project2} to predict the contract losses under different scenarios.
 
-In our context of DNNs metamodeling-based simulation procedures for hedging VAs, TL involves pre-training a DNN metamodel where the simulation budget is abundant and then fine-tuning it on a smaller dataset of new contracts or market conditions.
-Written on the same underlying asset, different VA contracts may share common features or exhibit similar patterns, especially temporal dependencies and regime changes in the underlying financial time series.
-Similarly, two VAs with the same features but based on different underlying assets may have some shared characteristics that can be leveraged to improve the learning performance of the metamodel.
-By transferring knowledge from a pre-trained model to a new but related task, TL can substantially reduce the computational cost of training the metamodel on the target task.
+In our context of \gls{dnn}s metamodeling-based simulation procedures for hedging \gls{va}s, \gls{tl} involves pre-training a \gls{dnn} metamodel where the simulation budget is abundant and then fine-tuning it on a smaller dataset of new contracts or market conditions.
+Written on the same underlying asset, different \gls{va} contracts may share common features or exhibit similar patterns, especially temporal dependencies and regime changes in the underlying financial time series.
+Similarly, two \gls{va}s with the same features but based on different underlying assets may have some shared characteristics that can be leveraged to improve the learning performance of the metamodel.
+By transferring knowledge from a pre-trained model to a new but related task, \gls{tl} can substantially reduce the computational cost of training the metamodel on the target task.
 
-LSTM networks are well-suited for modeling sequential data due to their ability to capture long-term dependencies~\citep{hochreiter1997long}.
-For the application of VA risk management using metamodel-based nested simulation, LSTM networks approximate the inner simulation, i.e., the mapping from scenarios to the scenario-wise contract losses.
-In Chapter~\ref{chap:project2}, we treat metamodeling as a supervised learning problem and demonstrated that LSTM networks could effectively model this complex relationships with extensive training on a large dataset of VA simulations.
-The total computational cost originates from two sources: running the standard nested simulation procedure to generate the training data and training the LSTM network on the generate dataset.
-Given a new VA contract, these steps need to be repeated to adapt the LSTM metamodel to new market conditions and contract features.
-For a DNN with a large number of parameters, retraining the LSTM network from the scratch can be computationally expensive.
+\gls{lstm} networks are well-suited for modeling sequential data due to their ability to capture long-term dependencies~\citep{hochreiter1997long}.
+For the application of \gls{va} risk management using metamodel-based nested simulation, \gls{lstm} networks approximate the inner simulation, i.e., the mapping from scenarios to the scenario-wise contract losses.
+In Chapter~\ref{chap:project2}, we treat metamodeling as a supervised learning problem and demonstrated that \gls{lstm} networks could effectively model this complex relationships with extensive training on a large dataset of \gls{va} simulations.
+The total computational cost originates from two sources: running the standard nested simulation procedure to generate the training data and training the \gls{lstm} network on the generate dataset.
+Given a new \gls{va} contract, these steps need to be repeated to adapt the \gls{lstm} metamodel to new market conditions and contract features.
+For a \gls{dnn} with a large number of parameters, retraining the \gls{lstm} network from the scratch can be computationally expensive.
 Generating a large training dataset using the standard nested simulation procedure is costly, and the computational burden can be prohibitive for certain assets or market conditions.
-TL offers an alternative approach that keeps the previous knowledge, i.e., the pre-trained model, as a foundation.
-Building on the pre-trained model, the LSTM network can be fine-tuned on a smaller dataset of new contracts or market conditions.
-This approach accelerates the adaptation of the LSTM metamodel to new conditions.
+\gls{tl} offers an alternative approach that keeps the previous knowledge, i.e., the pre-trained model, as a foundation.
+Building on the pre-trained model, the \gls{lstm} network can be fine-tuned on a smaller dataset of new contracts or market conditions.
+This approach accelerates the adaptation of the \gls{lstm} metamodel to new conditions.
 Computational savings come in two forms: 
 \begin{enumerate}
-    \item   fine-tuning requires less training time than training LSTM metamodels from scratch, and
-    \item   fewer training data points are needed to achieve a good LSTM metamodel, which is particularly beneficial when the standard nested simulation procedure is costly to implement.
+    \item   fine-tuning requires less training time than training \gls{lstm} metamodels from scratch, and
+    \item   fewer training data points are needed to achieve a good \gls{lstm} metamodel, which is particularly beneficial when the standard nested simulation procedure is costly to implement.
 \end{enumerate}
@@
 
-A typical TL framework for supervised learning consists of the following:
+A typical \gls{tl} framework for supervised learning consists of the following:
 \begin{itemize}
@@
 \end{itemize}
-where $\mathcal{X}_{\text{So}}$ and $\mathcal{X}_{\text{Ta}}$ include input features derived from the outer simulation of two different VA contracts or market conditions, and $F_{\text{So}}$ and $F_{\text{Ta}}$ are the marginal probability distributions of the source and target domains, respectively.
-Hence, the source domain and task are related to one VA contract for a certain market condition, while the target domain and task are related to new VA contracts and market conditions for which we don't have the simulation budget to run the standard nested simulation procedure extensively.
-In our numerical experiments, the dataset is generated by running the standard nested simulation procedure in Algorithm~\ref{alg2:standardProcedure} for a large number of VA contracts.
+where $\mathcal{X}_{\text{So}}$ and $\mathcal{X}_{\text{Ta}}$ include input features derived from the outer simulation of two different \gls{va} contracts or market conditions, and $F_{\text{So}}$ and $F_{\text{Ta}}$ are the marginal probability distributions of the source and target domains, respectively.
+Hence, the source domain and task are related to one \gls{va} contract for a certain market condition, while the target domain and task are related to new \gls{va} contracts and market conditions for which we don't have the simulation budget to run the standard nested simulation procedure extensively.
+In our numerical experiments, the dataset is generated by running the standard nested simulation procedure in Algorithm~\ref{alg2:standardProcedure} for a large number of \gls{va} contracts.
 The input features $\mathbf{X}$ are the return vectors from Equation~\eqref{eq2:return}, and the output labels $L$ are the contract losses for different outer scenarios.
@@
 The predictive function $f_{\text{So}}$ and $f_{\text{Ta}}$ are trained to estimate outputs $L_{\text{So}}$ and $L_{\text{Ta}}$, i.e., approximating the inner simulations under the source and target tasks, respectively.
-TL seeks to improve the learning of the target predictive function $f_{\text{Ta}}(\cdot)$ in $\mathcal{D}_{\text{Ta}}$ by leveraging the previous training on $\mathcal{D}_{\text{So}}$ and $f_{\text{So}}(\cdot)$, particularly when $\mathcal{D}_{\text{So}} \neq \mathcal{D}_{\text{Ta}}$ or $\mathcal{T}_{\text{So}} \neq \mathcal{T}_{\text{Ta}}$.
+\gls{tl} seeks to improve the learning of the target predictive function $f_{\text{Ta}}(\cdot)$ in $\mathcal{D}_{\text{Ta}}$ by leveraging the previous training on $\mathcal{D}_{\text{So}}$ and $f_{\text{So}}(\cdot)$, particularly when $\mathcal{D}_{\text{So}} \neq \mathcal{D}_{\text{Ta}}$ or $\mathcal{T}_{\text{So}} \neq \mathcal{T}_{\text{Ta}}$.
 In Chapter~\ref{chap:project2}, we have $\mathcal{D}_{\text{So}} = \mathcal{D}_{\text{Ta}}$ and $\mathcal{T}_{\text{So}} = \mathcal{T}_{\text{Ta}}$.
 
-In our TL setting, both the source and target tasks involve learning a mapping from the risk factors to the VA contract losses.
+In our \gls{tl} setting, both the source and target tasks involve learning a mapping from the risk factors to the \gls{va} contract losses.
 For the source task, we have a dataset $\mathcal{D}_{\text{So}} = { (X_{\text{So}}^{(i)}, L_{\text{So}}^{(i)}) }_{i=1}^{M_{\text{So}}}$, where $M_{\text{So}}$ is the number of training samples, i.e., the number of outer simulation paths used to generate the dataset with a standard nested simulation procedure.
 $X_{\text{So}}^{(i)} \in \mathcal{X}_{\text{So}}$ and $L_{\text{So}}^{(i)} \in \mathcal{Y}_{\text{So}}$.
-The ultimate objective is to learn a metamodel $f_{\text{Ta}}$ that predicts the VA contract losses $L_{\text{So}}$ from the scenarios $X_{\text{Ta}}$ in the form of a financial time series.
-TL starts by training a metamodel $f_{\text{So}}$ on the source domain $\mathcal{D}_{\text{So}}$.
-For both the two-stage procedure and the single-stage procedure in Chapter~\ref{chap:project2}, $f_{\text{So}}$ is approximated by an LSTM network $f_{\text{So}}(\cdot ; \theta_{\text{So}})$, where the parameters of the LSTM network, $\theta_{\text{So}}$ are learned by minimizing an MSE loss function on the source domain.
+The ultimate objective is to learn a metamodel $f_{\text{Ta}}$ that predicts the \gls{va} contract losses $L_{\text{So}}$ from the scenarios $X_{\text{Ta}}$ in the form of a financial time series.
+\gls{tl} starts by training a metamodel $f_{\text{So}}$ on the source domain $\mathcal{D}_{\text{So}}$.
+For both the two-stage procedure and the single-stage procedure in Chapter~\ref{chap:project2}, $f_{\text{So}}$ is approximated by an \gls{lstm} network $f_{\text{So}}(\cdot ; \theta_{\text{So}})$, where the parameters of the \gls{lstm} network, $\theta_{\text{So}}$ are learned by minimizing an \gls{mse} loss function on the source domain.
 Then the pre-trained parameters $\theta_{\text{So}}$ to inform the learning of $f_{\text{Ta}}(\cdot ; \theta_{\text{Ta}})$ on the target domain $\mathcal{D}_{\text{Ta}}$.
@@
 
-The most common TL techniques for supervised learning include fine-tuning, layer freezing, and multi-task learning. 
+The most common \gls{tl} techniques for supervised learning include fine-tuning, layer freezing, and multi-task learning. 
 These techniques can be categorized based on how they leverage pre-trained metamodels and how they encourage the similarity between $f_{\text{So}}(\cdot ; \theta_{\text{So}})$ and $f_{\text{Ta}}(\cdot ; \theta_{\text{Ta}})$.
@@
 
-Fine-tuning is a commonly used TL technique that uses the \textbf{same neural network architecture} for both the source and target tasks.
-We first train the source LSTM metamodel $f_{\text{So}}(\cdot; \theta_{\text{So}})$ on $\mathcal{D}_{\text{So}}$, capturing temporal dependencies and patterns relevant to the source task. 
+Fine-tuning is a commonly used \gls{tl} technique that uses the \textbf{same neural network architecture} for both the source and target tasks.
+We first train the source \gls{lstm} metamodel $f_{\text{So}}(\cdot; \theta_{\text{So}})$ on $\mathcal{D}_{\text{So}}$, capturing temporal dependencies and patterns relevant to the source task. 
 For the target task, we initialize $\theta_{\text{Ta}} = \theta_{\text{So}}$ and proceed to fine-tune the entire network on $\mathcal{D}_{\text{Ta}}$ by using a smaller learning rate.
@@
 
-    \STATE Train a LSTM metamodel $f_{\text{So}}(\cdot; \theta_{\text{So}})$ on $\mathcal{D}_{\text{So}}$:
+    \STATE Train a \gls{lstm} metamodel $f_{\text{So}}(\cdot; \theta_{\text{So}})$ on $\mathcal{D}_{\text{So}}$:
     \begin{equation}
@@
 
-    \STATE Fine-tune the entire LSTM model $f_{\text{Ta}}(\cdot; \theta_{\text{Ta}})$ on the target dataset $\mathcal{D}_{\text{Ta}}$ using a smaller learning rate $\alpha_{\text{Ta}}$:
+    \STATE Fine-tune the entire \gls{lstm} model $f_{\text{Ta}}(\cdot; \theta_{\text{Ta}})$ on the target dataset $\mathcal{D}_{\text{Ta}}$ using a smaller learning rate $\alpha_{\text{Ta}}$:
     \begin{equation}
@@
 
-    \STATE \textbf{Output:} Final adapted LSTM metamodel $f_{\text{Ta}}(\cdot; \theta_{\text{Ta}})$ for the target task.
+    \STATE \textbf{Output:} Final adapted \gls{lstm} metamodel $f_{\text{Ta}}(\cdot; \theta_{\text{Ta}})$ for the target task.
 \end{algorithmic}
@@
 Only minor adjustments are needed to adapt the metamodel to the new task, and the training process is accelerated by the pre-trained parameters.
-Fine-tuning is particularly useful when the nested simulation procedures for the two VA contracts are closely related.
-Only minor adjustments are needed to adapt the LSTM metamodel to the new domain.
+Fine-tuning is particularly useful when the nested simulation procedures for the two \gls{va} contracts are closely related.
+Only minor adjustments are needed to adapt the \gls{lstm} metamodel to the new domain.
 
@@
 
-        \STATE Train LSTM model $f_{\text{So}}(\cdot; \theta_{\text{So}})$ on $\mathcal{D}_{\text{So}}$:
+        \STATE Train \gls{lstm} model $f_{\text{So}}(\cdot; \theta_{\text{So}})$ on $\mathcal{D}_{\text{So}}$:
         \begin{equation}
@@
 
-        \STATE \textbf{Output:} Final adapted LSTM metamodel $f_{\text{Ta}}(\cdot; [\theta_0, \theta_1])$ for the target task.
+        \STATE \textbf{Output:} Final adapted \gls{lstm} metamodel $f_{\text{Ta}}(\cdot; [\theta_0, \theta_1])$ for the target task.
     \end{algorithmic}
@@
 
-For the implementation of our metamodeling studied in Chapter~\ref{chap:project2}, we consider a multi-task learning framework where the LSTM layers are shared across multiple tasks, and each task has its own fully connected layer for prediction.
-The network parameters are divided into shared parameters $\theta_0$ (LSTM layers) and task-specific parameters $\theta_k$ (fully connected layers for task $k$). 
+For the implementation of our metamodeling studied in Chapter~\ref{chap:project2}, we consider a multi-task learning framework where the \gls{lstm} layers are shared across multiple tasks, and each task has its own fully connected layer for prediction.
+The network parameters are divided into shared parameters $\theta_0$ (\gls{lstm} layers) and task-specific parameters $\theta_k$ (fully connected layers for task $k$). 
 As opposed to layer freezing, all parameters are trainable.
@@
 \end{equation}
-where MSE loss function is used as the error metric, and $f_i(\cdot; \theta_0, \theta_1, \dots, \theta_K)$ is the output of the network for task $k$.
-In essence, multi-task learning uses a multi-head architecture, where each task has its own output head, but the shared LSTM layers learn a common representation across tasks.
-Transfer occurs through the shared LSTM layers $\theta_0$. 
+where \gls{mse} loss function is used as the error metric, and $f_i(\cdot; \theta_0, \theta_1, \dots, \theta_K)$ is the output of the network for task $k$.
+In essence, multi-task learning uses a multi-head architecture, where each task has its own output head, but the shared \gls{lstm} layers learn a common representation across tasks.
+Transfer occurs through the shared \gls{lstm} layers $\theta_0$. 
 These layers learn representations of temporal patterns and dependencies common to all tasks, effectively \textbf{pooling} information from multiple simulation schemes. 
@@
 \begin{algorithm}
-    \caption{Multi-task Learning Framework for LSTM Metamodels}
+    \caption{Multi-task Learning Framework for \gls{lstm} Metamodels}
     \begin{algorithmic}[1] \label{alg3:multiTaskLearning}
@@
 
-        \STATE Train the multi-head LSTM metamodel on all $K$ tasks simultaneously by minimizing the multi-task loss function:
+        \STATE Train the multi-head \gls{lstm} metamodel on all $K$ tasks simultaneously by minimizing the multi-task loss function:
         \begin{equation} \label{eq3:multiTaskLoss}
@@
 
-        \STATE \textbf{Output:} Trained multi-task LSTM metamodel $f(\cdot; \theta_0, \{\theta_k\}_{k=1}^K)$ for all $K$ tasks.
+        \STATE \textbf{Output:} Trained multi-task \gls{lstm} metamodel $f(\cdot; \theta_0, \{\theta_k\}_{k=1}^K)$ for all $K$ tasks.
     \end{algorithmic}
@@
 
-Algorithm~\ref{alg3:multiTaskLearning} outlines the multi-task learning framework for LSTM metamodels for nested simulation procedures.
+Algorithm~\ref{alg3:multiTaskLearning} outlines the multi-task learning framework for \gls{lstm} metamodels for nested simulation procedures.
 In Chapter~\ref{chap:project1} and Chapter~\ref{chap:project2}, we demonstrated that pooling using a metamodel could improve the computation efficiency and estimator accuracy in nested simulation procedures.
 Here, pooling happens at a higher level, where information from multiple metamodels is shared to improve the learning performance on individual tasks.
-The multi-task loss function encourages the shared LSTM layers to learn generalizable representations of temporal dependencies that are beneficial across all tasks.
+The multi-task loss function encourages the shared \gls{lstm} layers to learn generalizable representations of temporal dependencies that are beneficial across all tasks.
 
@@
     \item   \textbf{Similarity in contract specifications:} 
-            simulations involving VA contracts with similar features are likely to share underlying risk factors and policyholder behaviors. 
+            simulations involving \gls{va} contracts with similar features are likely to share underlying risk factors and policyholder behaviors. 
     \item   \textbf{Similarity in underlying assets:} 
@@
     \item   \textbf{Temporal Dynamics:} 
-            VA contracts with comparable maturity and rebalance frequency can help the shared layers learn temporal dependencies consistent across tasks. 
+            \gls{va} contracts with comparable maturity and rebalance frequency can help the shared layers learn temporal dependencies consistent across tasks. 
 \end{itemize}
 
-Suppose that we aim at developing an LSTM metamodel for a GMWB contract under a stochastic volatility asset model, but we have limited data for this simulation scheme. 
+Suppose that we aim at developing an \gls{lstm} metamodel for a \gls{gmwb} contract under a stochastic volatility asset model, but we have limited data for this simulation scheme. 
 For multi-task learning, we can select related nested simulation procedures with relatively abundant data, such as:
@@
 \begin{itemize} 
-    \item GMMB contracts under a stochastic volatility asset model. 
-    \item GMWB contracts under a Black-Scholes asset model. 
-    \item GMWB contracts under a stochastic volatility model with different simulation parameters.
+    \item \gls{gmmb} contracts under a stochastic volatility asset model. 
+    \item \gls{gmwb} contracts under a Black-Scholes asset model. 
+    \item \gls{gmwb} contracts under a stochastic volatility model with different simulation parameters.
 \end{itemize}
 
-These tasks need to share similarities in contract features and market dynamics so that the shared LSTM layers can learn relevant temporal patterns applicable to the target task.
+These tasks need to share similarities in contract features and market dynamics so that the shared \gls{lstm} layers can learn relevant temporal patterns applicable to the target task.
 Otherwise, the shared layers may not be able to learn generalizable representations of temporal dependencies, and the multi-task learning framework may lead to negative transfer.
-Negative transfer refers to the phenomenon where the performance of the target task is worse than that of training directly on the target task without TL.
-It occurs when the tasks are not related or an improper TL technique is used.
-Positive transfer, on the other hand, refers to the phenomenon where the performance of the target task is better than that of training directly on the target task without TL.
-Training a multi-task LSTM metamodel benefits from having more training data, and the shared layers can learn more generalizable representations of temporal dependencies.
+Negative transfer refers to the phenomenon where the performance of the target task is worse than that of training directly on the target task without \gls{tl}.
+It occurs when the tasks are not related or an improper \gls{tl} technique is used.
+Positive transfer, on the other hand, refers to the phenomenon where the performance of the target task is better than that of training directly on the target task without \gls{tl}.
+Training a multi-task \gls{lstm} metamodel benefits from having more training data, and the shared layers can learn more generalizable representations of temporal dependencies.
 Furthermore, if a new but similar task is introduced, fine-tuning, layer freezing, and multi-task learning can be combined to leverage the pre-trained model effectively.
 More specfically, the shared layers can be frozen, and the task-specific layers for a similar task in the training set can be fine-tuned on the new task.
-This shared knowledge helps the model generalize better on a target task, as the LSTM layers have been exposed to a wider variety of patterns and dynamics.
+This shared knowledge helps the model generalize better on a target task, as the \gls{lstm} layers have been exposed to a wider variety of patterns and dynamics.
 
-\subsection{Rapid Adaptation of LSTM Metamodels} \label{sec3:transfer_learning}
+\subsection{Rapid Adaptation of \gls{lstm} Metamodels} \label{sec3:transfer_learning}
 
-In this section, we propose a TL framework for rapid adaptation of LSTM metamodels in dynamic hedging of VAs.
-The goal is to leverage the knowledge acquired during training on a large dataset of VA simulations to improve the learning performance on a smaller dataset of new VA contracts.
+In this section, we propose a \gls{tl} framework for rapid adaptation of \gls{lstm} metamodels in dynamic hedging of \gls{va}s.
+The goal is to leverage the knowledge acquired during training on a large dataset of \gls{va} simulations to improve the learning performance on a smaller dataset of new \gls{va} contracts.
 
 \begin{algorithm}
-    \caption{Transfer Learning Framework for LSTM Metamodels: Combining Fine-tuning, Layer Freezing, and Multi-task Learning}
+    \caption{Transfer Learning Framework for \gls{lstm} Metamodels: Combining Fine-tuning, Layer Freezing, and Multi-task Learning}
     \begin{algorithmic}[1] \label{alg3:combined}
@@
 
-        \STATE Train the multi-task LSTM metamodel on all $K$ tasks simultaneously:
+        \STATE Train the multi-task \gls{lstm} metamodel on all $K$ tasks simultaneously:
         \begin{equation}
@@
 
-        \STATE For a related task of hedging a new VA contract, combine fine-tuning and layer freezing:
+        \STATE For a related task of hedging a new \gls{va} contract, combine fine-tuning and layer freezing:
 
@@
 
-        \STATE \textbf{Output:} Final adapted LSTM metamodel $f_{\text{Ta}}(\cdot; \theta_0, \theta_{\text{Ta}})$ for the new VA contracts in the target task.
+        \STATE \textbf{Output:} Final adapted \gls{lstm} metamodel $f_{\text{Ta}}(\cdot; \theta_0, \theta_{\text{Ta}})$ for the new \gls{va} contracts in the target task.
     \end{algorithmic}
@@
 
-Algorithm~\ref{alg3:combined} combines the strengths of Multi-task learning, layer freezing, and fine-tuning to accelerate the training of LSTM metamodels.
+Algorithm~\ref{alg3:combined} combines the strengths of Multi-task learning, layer freezing, and fine-tuning to accelerate the training of \gls{lstm} metamodels.
 
 \begin{itemize}
-    \item \textbf{Multi-task learning} allows the shared LSTM layers to pool information across related tasks, and it allows the metamodel to learn generalizable representations of temporal dependencies.
+    \item \textbf{Multi-task learning} allows the shared \gls{lstm} layers to pool information across related tasks, and it allows the metamodel to learn generalizable representations of temporal dependencies.
     \item \textbf{Layer freezing} ensures that shared features learned from the source tasks are retained when adapting to a new task, reducing the risk of overfitting to the target simulation data.
@@
 
-The combination of these techniques significantly reduces the computational cost of training LSTM metamodels for a new but related VA contract.
+The combination of these techniques significantly reduces the computational cost of training \gls{lstm} metamodels for a new but related \gls{va} contract.
 
@@
 
-In this section, we evaluate the performance of the TL framework for rapid adaptation of LSTM metamodels in dynamic hedging of VAs.
-The low noise dataset generated by the standard nested simulation procedure in Section~\ref{sec2:numerical} is used to train the source LSTM metamodels.
-We consider TL to two types of target tasks: 
+In this section, we evaluate the performance of the \gls{tl} framework for rapid adaptation of \gls{lstm} metamodels in dynamic hedging of \gls{va}s.
+The low noise dataset generated by the standard nested simulation procedure in Section~\ref{sec2:numerical} is used to train the source \gls{lstm} metamodels.
+We consider \gls{tl} to two types of target tasks: 
 \begin{itemize}
@@
 Similar to Section~\ref{sec2:numerical}, we use the standard nested simulation procedure to generate the dataset for the source and target tasks.
-Serveral VA datasets generated with the standard nested simulation procedures under geometric Brownian motion (GBM) and regime-switching GBM (RS-GBM) asset models.
+Serveral \gls{va} datasets generated with the standard nested simulation procedures under geometric Brownian motion (\gls{gbm}) and regime-switching \gls{gbm} (\gls{rsgbm}) asset models.
+\textcolor{red}{In this experiment, we use the same \gls{rsgbm} asset model as Chapter~\ref{chap:project2} to generate the dataset for the source and target tasks.}
+\textcolor{red}{When following a static lapse model and a dynamic lapse model, the monthly lapse rate is given by Equation~\ref{eq:lapse_rate} and Equation~\ref{eq:dynamic_lapse_rate}, respectively.}
+\textcolor{red}{The experiments are run on a machine with a AMD Ryzen 9 7900X processor with 32 GB of RAM and a Nvidia RTX $\num{3060}$ Ti GPU}
 
@@
     \midrule
-    GMMB & GBM & No lapse & $\num{50000}$ & N/A \\
-    GMMB & RS-GBM & No lapse & $\num{50000}$ & $\num{2000}$ \\
-    GMMB & RS-GBM & Static lapse & $\num{50000}$ & $\num{2000}$ \\
-    GMMB & RS-GBM & Dynamic lapse & $\num{50000}$ & $\num{2000}$ \\
-    GMWB & RS-GBM & Dynamic lapse & N/A & $\num{2000}$ \\
+    \gls{gmmb} & \gls{rsgbm} & No lapse & $\num{50000}$ & N/A \\
+    \gls{gmmb} & \gls{rsgbm} & Static lapse & $\num{50000}$ & $\num{2000}$ \\
+    \gls{gmmb} & \gls{rsgbm} & Dynamic lapse & $\num{50000}$ & $\num{2000}$ \\
+    \gls{gmwb} & \gls{rsgbm} & Dynamic lapse & N/A & $\num{2000}$ \\
     \bottomrule
     \end{tabular}
-    \caption{VA Contracts for Transfer Learning Experiments}
+    \caption{\gls{va} Contracts for Transfer Learning Experiments}
     \label{tab3:contracts}
@@
 
-Table~\ref{tab3:contracts} lists the VA contracts used in the TL experiments.
-These contracts include GMMB and GMWB contracts with no lapse, static lapse, and dynamic lapse features.
-Before transferred to the target task, a LSTM metamodel is trained on a source dataset with $M_{\text{So}} = \num{50000}$ samples generated with $N_{\text{So}} = \num{100}$ inner replications\footnotemark.
-\footnotetext{The GMMB contract on the GBM asset model is an exception, where scenario-wise contract losses can be computed analytically.}
-The pre-trained LSTM metamodel is then adapted to a target task that is different from the source task.
+Table~\ref{tab3:contracts} lists the \gls{va} contracts used in the \gls{tl} experiments.
+These contracts include \gls{gmmb} and \gls{gmwb} contracts with no lapse, static lapse, and dynamic lapse features.
+These contracts include \gls{gmmb} and \gls{gmwb} contracts with no lapse, static lapse, and dynamic lapse features.
+Before transferred to the target task, a \gls{lstm} metamodel is trained on a source dataset with $M_{\text{So}} = \num{50000}$ samples generated with $N_{\text{So}} = \num{100}$ inner replications\footnotemark.
+\footnotetext{The GMMB contract on the \gls{gbm} asset model is an exception, where scenario-wise contract losses can be computed analytically.}
+The pre-trained \gls{lstm} metamodel is then adapted to a target task that is different from the source task.
 The training dataset for the target task has $M_{\text{Ta}} = \num{2000}$ samples generated with $N_{\text{Ta}} = \num{100}$ inner replications.
 During the training on both the source and target tasks, $10\%$ of the data is split into a validation dataset to monitor the training process and prevent overfitting by using early stopping.
-The complexity of the simulation schemes increases from the first task to the last task, and the LSTM metamodels need to adapt to the new conditions with a limited amount of training data on the target tasks.
+The complexity of the simulation schemes increases from the first task to the last task, and the \gls{lstm} metamodels need to adapt to the new conditions with a limited amount of training data on the target tasks.
 
-All LSTM metamodels are evaluated based on their training history graphs for the target task, which plot training and validation MSE against the number of training epochs.
-The training history graphs visualize the learning curves of the LSTM metamodels, which provide insights into stability and convergence behavior the metamodels.
-We measure the generalization performance of the LSTM metamodels using the true MSE, which quantifies the accuracy of the LSTM metamodels in approximating the true inner simulation model of VA contracts.
+All \gls{lstm} metamodels are evaluated based on their training history graphs for the target task, which plot training and validation MSE against the number of training epochs.
+The training history graphs visualize the learning curves of the \gls{lstm} metamodels, which provide insights into stability and convergence behavior the metamodels.
+We measure the generalization performance of the \gls{lstm} metamodels using the true MSE, which quantifies the accuracy of the \gls{lstm} metamodels in approximating the true inner simulation model of \gls{va} contracts.
 The true MSE is computed by comparing the metamodel predictions with the true contract losses, which are approximated by the standard nested simulation procedure with $\num{100000}$ inner replications.
-Hyperparameters and network architectures for the LSTM metamodels are kept the same as the LSTM metamodel in Section~\ref{sec2:numerical}. 
-Due to a limited amount of computational resources, macro replications are not feasible for the TL experiments.
+Hyperparameters and network architectures for the \gls{lstm} metamodels are kept the same as the \gls{lstm} metamodel in Section~\ref{sec2:numerical}. 
+Due to a limited amount of computational resources, macro replications are not feasible for the \gls{tl} experiments.
 
@@
         \includegraphics[width=\textwidth]{./project3/figures/figure1b.png}
-        \caption{Without TL}
+        \caption{Without \gls{tl}}
         \label{subfig3-1:without}
@@
     \end{subfigure}
-    \caption{Metamodel performance on RS-GBM GMMB with static lapse}
+    \caption{Metamodel performance on \gls{rsgbm} \gls{gmmb} with static lapse}
     \label{fig3:figure1}
@@
 
-We first examine the performance of fine-tuning and layer freezing in adapting LSTM metamodels to new VA contracts with lapse features.
-Figure~\ref{fig3:figure1} compares the performance of LSTM metamodels on the target tasks with and without TL.
-Learning histories of the LSTM metamodels is shown for the target task of metamodeling GMMB contract losses on the RS-GBM asset model with static lapse.
-The source task is hedging a GMMB contract on RS-GBM with no lapse, and the target task is hedging the same GMMB contract but with a static lapse.
+We first examine the performance of fine-tuning and layer freezing in adapting \gls{lstm} metamodels to new \gls{va} contracts with lapse features.
+Figure~\ref{fig3:figure1} compares the performance of \gls{lstm} metamodels on the target tasks with and without \gls{tl}.
+Learning histories of the \gls{lstm} metamodels is shown for the target task of metamodeling \gls{gmmb} contract losses on the \gls{rsgbm} asset model with static lapse.
+The source task is hedging a \gls{gmmb} contract on \gls{rsgbm} with no lapse, and the target task is hedging the same \gls{gmmb} contract but with a static lapse.
 The simulation data for the target task is generated with the same nested simulation procedure as the source task, except for the lapse feature.
-Figure~\ref{subfig3-1:extensive} demonstrates the performance of the LSTM metamodel trained extensively only on the target task by using $M_{\text{TA}} = 50,\!000$ samples, which serves as a benchmark for this study.
-The metamodel achieves a low validation MSE due to the availability of a large dataset.
+Figure~\ref{subfig3-1:extensive} demonstrates the performance of the \gls{lstm} metamodel trained extensively only on the target task by using $M_{\text{TA}} = 50,\!000$ samples, which serves as a benchmark for this study.
+The metamodel achieves a low validation \gls{mse} due to the availability of a large dataset.
 In contrast, Figure~\ref{subfig3-1:without} presents the results of training directly on the target task without pre-training on the source task.
-With only $M_{\text{TA}} = 2,\!000$ samples, the LSTM metamodel struggles to learn the temporal dependencies and patterns in the target task.
-It leads to highly unstable training dynamics with a substantial amount of fluctuations in the validation MSE.
+With only $M_{\text{TA}} = 2,\!000$ samples, the \gls{lstm} metamodel struggles to learn the temporal dependencies and patterns in the target task.
+It leads to highly unstable training dynamics with a substantial amount of fluctuations in the validation \gls{mse}.
 Learning without knowledge transfer leads poor generalization and extreme overfitting. 
-Often, the training data is limited for a new VA contract, and such instability is particularly problematic for a quick adaptation of LSTM metamodels.
-TL techniques like fine-tuning and layer freezing can help mitigate these challenges.
-Figure~\ref{subfig3-1:fineTuning} shows the results of fine-tuning a pre-trained metamodel on RS-GBM with no lapse.
-Fine-tuning offers a noticeable improvement over training without TL by reducing the instability in the validation MSE. 
+Often, the training data is limited for a new \gls{va} contract, and such instability is particularly problematic for a quick adaptation of \gls{lstm} metamodels.
+\gls{tl} techniques like fine-tuning and layer freezing can help mitigate these challenges.
+Figure~\ref{subfig3-1:fineTuning} shows the results of fine-tuning a pre-trained metamodel on \gls{rsgbm} with no lapse.
+Fine-tuning offers a noticeable improvement over training without \gls{tl} by reducing the instability in the validation \gls{mse}. 
 However, despite this improvement, fine-tuning may not fully mitigate the challenges of training with a small dataset.
-No negative trasfer is observed, but the fine-tuned metamodel struggles to achieve a low validation MSE.
-Lowering the learning rate does not help the fine-tuned metamodel converge, and the validation MSE remains high after increasing the number of training epochs.
+No negative trasfer is observed, but the fine-tuned metamodel struggles to achieve a low validation \gls{mse}.
+Lowering the learning rate does not help the fine-tuned metamodel converge, and the validation \gls{mse} remains high after increasing the number of training epochs.
 It indicates that fine-tuning may not be sufficient for a limited amount of training data.
@@
 Layer freezing offers a more stable training process compared to fine-tuning, with a lower validation error and reduced fluctuations during its training.
-The LSTM layers are critical for capturing general feature representations that are transferable across tasks, and freezing these layers helps prevent overfitting to the target task.
+The \gls{lstm} layers are critical for capturing general feature representations that are transferable across tasks, and freezing these layers helps prevent overfitting to the target task.
 In addition, the layer freezing approach tunes fewer neural network parameters than crude fine-tuning.
@@
     \end{subfigure}
-    \caption{Fine-tuned Metamodel performance on RS-GBM GMMB with a dynamic lapse}
+    \caption{Fine-tuned Metamodel performance on \gls{rsgbm} \gls{gmmb} with a dynamic lapse}
     \label{fig3:figure2}
@@
 
-We further investigate the performance of fine-tuning on the target task of metamodeling GMMB contract losses on RS-GBM with a dynamic lapse. 
-The source tasks used for pre-training are GMMB contracts on RS-GBM with no lapse and a static lapse, respectively. 
-Figure~\ref{fig3:figure2} displays the learning curves of the LSTM metamodels fine-tuned from these two distinct source tasks.
+We further investigate the performance of fine-tuning on the target task of metamodeling \gls{gmmb} contract losses on \gls{rsgbm} with a dynamic lapse. 
+The source tasks used for pre-training are \gls{gmmb} contracts on \gls{rsgbm} with no lapse and a static lapse, respectively. 
+Figure~\ref{fig3:figure2} displays the learning curves of the \gls{lstm} metamodels fine-tuned from these two distinct source tasks.
 We observe that the performance of the fine-tuned metamodel is highly dependent on the similarity between the source and target tasks.
 Fine-tuning from a source task with a static lapse results in a faster convergence and a lower validation error.
-The metamodel trained on the GMMB with a static lapse captures some features that are beneficial for the GMMB with a dynamic lapse, which leads to a more stable training process.
+The metamodel trained on the \gls{gmmb} with a static lapse captures some features that are beneficial for the \gls{gmmb} with a dynamic lapse, which leads to a more stable training process.
 In Figure~\ref{subfig3-2:fromNolapse}, the metamodel needs to learn the effect of
@@
 
-The observed improvement in transferability when fine-tuning from a static lapse source task highlights the importance of selecting appropriate source tasks in TL. 
+The observed improvement in transferability when fine-tuning from a static lapse source task highlights the importance of selecting appropriate source tasks in \gls{tl}. 
 When the source task diverges substantially from the target task, the transferred metamodel may struggle to adapt to the new conditions given the limited amount of training data.
@@
     \end{subfigure}
-    \caption{Layer Freezing on RS-GBM GMMB with dynamic lapse}
+    \caption{Layer Freezing on \gls{rsgbm} \gls{gmmb} with dynamic lapse}
     \label{fig3:figure3}
@@
 
-Figure~\ref{fig3:figure3} continues the investigation of layer freezing in the task of metamodeling GMMB contract losses on RS-GBM with the dynamic lapse. 
-When transferring knowledge from the GMMB model with the static lapse, the primary adaptation for the target task involves learning the impact of the dynamic lapse.
-Freezing the LSTM layers and fine-tuning only the fully connected layer results in a higher validation error, which suggests a tendency of overfitting.
+Figure~\ref{fig3:figure3} continues the investigation of layer freezing in the task of metamodeling \gls{gmmb} contract losses on \gls{rsgbm} with the dynamic lapse. 
+When transferring knowledge from the \gls{gmmb} model with the static lapse, the primary adaptation for the target task involves learning the impact of the dynamic lapse.
+Freezing the \gls{lstm} layers and fine-tuning only the fully connected layer results in a higher validation error, which suggests a tendency of overfitting.
 This indicates that the fully connected layer struggles to adapt to the changes in the temporal dynamics introduced by a dynamic lapse, which can be viewed as another source of randomness in the time series.
-In contrast, freezing the fully connected layer and fine-tuning the LSTM layers leads to a lower validation error and better generalization. 
-This can be attributed to the fact that the LSTM layers are responsible for capturing the temporal dependencies associated with the dynamic lapse, and the fully connected layer predicts the contract losses based on these learned features.
+In contrast, freezing the fully connected layer and fine-tuning the \gls{lstm} layers leads to a lower validation error and better generalization. 
+This can be attributed to the fact that the \gls{lstm} layers are responsible for capturing the temporal dependencies associated with the dynamic lapse, and the fully connected layer predicts the contract losses based on these learned features.
 
 This experiment emphasizes the importance of choosing which layers to freeze based on the nature of the source and target tasks. 
-In the case of learning the dynamic lapse features, freezing the LSTM layers is not beneficial as they need to adapt to the new temporal patterns.
+In the case of learning the dynamic lapse features, freezing the \gls{lstm} layers is not beneficial as they need to adapt to the new temporal patterns.
 
@@
     \toprule
-    \textbf{Lapse Type} & \textbf{Extensive} & \textbf{Fine-tuning} & \textbf{Layer Freezing} & \textbf{Without TL} \\
+    \textbf{Lapse Type} & \textbf{Extensive} & \textbf{Fine-tuning} & \textbf{Layer Freezing} & \textbf{Without \gls{tl}} \\
     \midrule
@@
     \end{tabular}
-    \caption{Comparison of different TL methods on GMMB contracts}
+    \caption{Comparison of different \gls{tl} methods on \gls{gmmb} contracts}
     \label{tab3:transfer_learning_results}
@@
 
-Table~\ref{tab3:transfer_learning_results} summarizes the true MSEs of the LSTM metamodels trained using different TL methods across various source tasks.
+Table~\ref{tab3:transfer_learning_results} summarizes the true \gls{mse}s of the \gls{lstm} metamodels trained using different \gls{tl} methods across various source tasks.
 The calculations are based on the metamodel predictions and the true contract losses approximated with $\num{100000}$ inner replications.
-The first two rows show the performance of transferring knowledge from GMMB contracts with no lapse and the static lapse to the target task of GMMB with the dynamic lapse.
-The last row shows the performance of training without TL on the target task.
+The first two rows show the performance of transferring knowledge from \gls{gmmb} contracts with no lapse and the static lapse to the target task of \gls{gmmb} with the dynamic lapse.
+The last row shows the performance of training without \gls{tl} on the target task.
 The results demonstrate the effectiveness of fine-tuning and layer freezing in transferring knowledge from a related source tasks to the target task. 
 When transferring from a source task with the static lapse to a target task with the dynamic lapse, the MSEs achieved are $0.0794$ for fine-tuning and $0.0763$ for layer freezing.
-The benchmark MSE of $0.0587$, obtained from extensive training on the GMMB dynamic lapse task with much more samples.
+The benchmark MSE of $0.0587$, obtained from extensive training on the \gls{gmmb} dynamic lapse task with much more samples.
 
-While TL from static lapse GMMB do not reach this level of accuracy due to the limited data in the target task, they substantially outperform training without TL. 
+While \gls{tl} from static lapse \gls{gmmb} do not reach this level of accuracy due to the limited data in the target task, they substantially outperform training without \gls{tl}. 
 This indicates that the models pre-trained on a static lapse setting are effective in capturing relevant features that are transferable to the dynamic lapse scenario.
 
-However, when the source task is less similar to the target task, the benefits of TL are less pronounced.
+However, when the source task is less similar to the target task, the benefits of \gls{tl} are less pronounced.
 The MSEs in this case are higher, with fine-tuning resulting in $0.4894$ and layer freezing achieving $0.3361$.
 This suggests that the divergence between the source and target tasks can lead to negative transfer.
-These results highlight the importance of selecting source tasks that share significant similarities with the target task to maximize the effectiveness of TL. 
+These results highlight the importance of selecting source tasks that share significant similarities with the target task to maximize the effectiveness of \gls{tl}. 
 When the source and target contracts are substantially different, the pre-trained metamodels may struggle to adapt to the new conditions, as they may not have learned features relevant to the target task.
@@
 
-When transferring knowledge from one VA contract type to another, the LSTM metamodel needs to adapt to different contract features and time series dynamics.
-We consider the task of metamodeling GMWB contract losses on RS-GBM asset model with the dynamic lapse, with the source tasks being a GMMB contract on RS-GBM also with the dynamic lapse.
-Figure~\ref{fig3:figure4} illustrates the learning history of transferring pre-trained LSTM metamodels from the GMMB contracts to the GMWB contracts.
+When transferring knowledge from one \gls{va} contract type to another, the \gls{lstm} metamodel needs to adapt to different contract features and time series dynamics.
+We consider the task of metamodeling \gls{gmwb} contract losses on \gls{rsgbm} asset model with the dynamic lapse, with the source tasks being a \gls{gmmb} contract on \gls{rsgbm} also with the dynamic lapse.
+Figure~\ref{fig3:figure4} illustrates the learning history of transferring pre-trained \gls{lstm} metamodels from the \gls{gmmb} contracts to the \gls{gmwb} contracts.
 
@@
         \includegraphics[width=\textwidth]{./project3/figures/figure4b.png}
-        \caption{Without TL}
+        \caption{Without \gls{tl}}
         \label{subfig3-4:without}
@@
 
-Figure~\ref{subfig3-4:extensive} presents the performance of an extensively trained LSTM metamodel on the target task using $\num{50000}$ samples, serving as a benchmark of the best metamodel performance.
+Figure~\ref{subfig3-4:extensive} presents the performance of an extensively trained \gls{lstm} metamodel on the target task using $\num{50000}$ samples, serving as a benchmark of the best metamodel performance.
 The extensively trained metamodel achieves a low validation error and demonstrates stable convergence due to having enough training samples. 
@@
 
-When applying fine-tuning from the GMMB source task (Figure~\ref{subfig3-4:fineTuning}), the metamodel exhibits an improved performance compared to the training without TL. 
+When applying fine-tuning from the \gls{gmmb} source task (Figure~\ref{subfig3-4:fineTuning}), the metamodel exhibits an improved performance compared to the training without \gls{tl}. 
 Fine-tuning results in a lower validation error and more stable convergence.
-Despite the differences between the GMMB and GMWB contracts, there is still valuable information that can be transferred. 
-Both the LSTM layers and the fully connected layers capture general temporal patterns and feature representations that are beneficial for the target task. 
+Despite the differences between the \gls{gmmb} and \gls{gmwb} contracts, there is still valuable information that can be transferred. 
+Both the \gls{lstm} layers and the fully connected layers capture general temporal patterns and feature representations that are beneficial for the target task. 
 Fine-tuning allows the metamodel to adjust all its neural network layers. 
-It allows a better adaptation to the complexities introduced by the GMWB contract.
+It allows a better adaptation to the complexities introduced by the \gls{gmwb} contract.
 
@@
 Negative transfer is observed.
-Freezing some layers trained on the GMMB contracts does not allow the metamodel to sufficiently adapt to the complexities of the GMWB contracts. 
-The GMWB contracts are inherently more complex than GMMB contracts due to the guaranteed withdrawal benefits at each time step, and the contract features are substantially different.
-The complexity introduced by the GMWB contracts leads to significant changes in the time series dynamics that the metamodel needs to capture.
-Freezing the LSTM layers or the fully connected layer hinders the metamodel's ability to learn these new patterns, and it leads to a poor generalization and unstable error curves.
+Freezing some layers trained on the \gls{gmmb} contracts does not allow the metamodel to sufficiently adapt to the complexities of the \gls{gmwb} contracts. 
+The \gls{gmwb} contracts are inherently more complex than \gls{gmmb} contracts due to the guaranteed withdrawal benefits at each time step, and the contract features are substantially different.
+The complexity introduced by the \gls{gmwb} contracts leads to significant changes in the time series dynamics that the metamodel needs to capture.
+Freezing the \gls{lstm} layers or the fully connected layer hinders the metamodel's ability to learn these new patterns, and it leads to a poor generalization and unstable error curves.
 
@@
         \midrule
-        Without TL & $\num{2000}$ & $0.3588$ & $0.4188$ \\
+        Without \gls{tl} & $\num{2000}$ & $0.3588$ & $0.4188$ \\
         Fine-tuning & $\num{2000}$ & $0.1690$ & $0.1780$ \\
@@
 
-Table~\ref{tab3:transfer_learning_results_gmwb} summarizes the true MSEs of the LSTM metamodels on the GMWB contracts.
+Table~\ref{tab3:transfer_learning_results_gmwb} summarizes the true MSEs of the \gls{lstm} metamodels on the \gls{gmwb} contracts.
 Training MSE and true MSE are computed using the training labels and the true contract losses approximated with $\num{100000}$ inner replications, respectively.
 This is consistent with the terminology used in Chapter~\ref{chap:project2}.
-The TL methods are compared to training from the scratch.
+The \gls{tl} methods are compared to training from the scratch.
 The suboptimal performance of layer freezing in this context indicates that the difference between the source and target tasks is too substantial for this method to be effective. 
@@
 In such circumstances, fine-tuning provides a better approach by allowing the metamodel to leverage transferable knowledge while adapting to the new task's specific requirements. 
-Fine-tuning enables both the LSTM and the fully connected layers to update their weights, capturing the complex dynamics of the GMWB contracts more effectively.
-This is particularly beneficial when developing metamodels for the complex VA contracts with limited simulation data. 
-For instance, transferring information from the GMMB contracts can still be valuable when modeling the GMWB contracts.
-Both contracts share some common contract features and temporal patterns, which allows a pre-trained LSTM metamodel to capture generalizable features that provide a solid foundation for the target task.
+Fine-tuning enables both the \gls{lstm} and the fully connected layers to update their weights, capturing the complex dynamics of the \gls{gmwb} contracts more effectively.
+This is particularly beneficial when developing metamodels for the complex \gls{va} contracts with limited simulation data. 
+For instance, transferring information from the \gls{gmmb} contracts can still be valuable when modeling the \gls{gmwb} contracts.
+Both contracts share some common contract features and temporal patterns, which allows a pre-trained \gls{lstm} metamodel to capture generalizable features that provide a solid foundation for the target task.
 
@@
     \end{subfigure}
-    \caption{TL performance on RS-GBM GMWB with dynamic lapse}
+    \caption{TL performance on \gls{rsgbm} GMWB with dynamic lapse}
     \label{fig3:figure4-1}
@@
 
-Figure~\ref{fig3:figure4-1} illustrates the performance of the two-stage procedure with TL for GMWB contracts with the dynamic lapse in predicting the tail scenarios and the $95\%$-CVaR.
-The graph provides a visual representation of how different TL approaches compare to training from the scratch and the standard nested simulation procedure.
+Figure~\ref{fig3:figure4-1} illustrates the performance of the two-stage procedure with \gls{tl} for \gls{gmwb} contracts with the dynamic lapse in predicting the tail scenarios and the $95\%$-CVaR.
+The graph provides a visual representation of how different \gls{tl} approaches compare to training from the scratch and the standard nested simulation procedure.
 Fine-tuning consistently outperforms both layer freezing and training from the scratch across different simulation budgets, particularly in predicting tail scenarios and estimating the 95\%-CVaR.
@@
 This finding is consistent with the training history and MSEs in Figure~\ref{fig3:figure4} and Table~\ref{tab3:transfer_learning_results_gmwb}, respectively.
-It is important to note that while these results are promising, they also highlight the complexity of modeling the GMWB contracts with the dynamic lapse. 
-The fact that fine-tuning outperforms layer freezing suggests that there are substantial differences in the tail behavior of the GMMB and GMWB contracts, particularly when the dynamic lapse is considered.
-These findings highlight the need for careful model selection and validation when applying the TL techniques to different VA products.
+It is important to note that while these results are promising, they also highlight the complexity of modeling the \gls{gmwb} contracts with the dynamic lapse. 
+The fact that fine-tuning outperforms layer freezing suggests that there are substantial differences in the tail behavior of the \gls{gmmb} and \gls{gmwb} contracts, particularly when the dynamic lapse is considered.
+These findings highlight the need for careful model selection and validation when applying the \gls{tl} techniques to different \gls{va} products.
 When the source and target tasks are substantially different, all layers need to be updated.
@@
 
-Multi-task learning enables the LSTM metamodels to learn shared representations across related VA contracts.
-In this section, we examine the performance of multi-task learning applied to two types of VAs, GMMB and GMWB with the dynamic lapse rates.
-The simulation datasets contain $2,\!000$ samples for each contract type, and the LSTM metamodels are trained using multi-task learning. 
-In our experiments, Algorithm~\ref{alg3:multiTaskLearning} is used to train the LSTM metamodels simultaneously to minimize the multi-task MSE loss function in Equation~\eqref{eq3:multiTaskLoss}.
-We use individual task training as a baseline for comparison, where the LSTM metamodels are trained separately on the GMMB and GMWB contracts.
+Multi-task learning enables the \gls{lstm} metamodels to learn shared representations across related \gls{va} contracts.
+In this section, we examine the performance of multi-task learning applied to two types of \gls{va}s, \gls{gmmb} and \gls{gmwb} with the dynamic lapse rates.
+The simulation datasets contain $2,\!000$ samples for each contract type, and the \gls{lstm} metamodels are trained using multi-task learning. 
+In our experiments, Algorithm~\ref{alg3:multiTaskLearning} is used to train the \gls{lstm} metamodels simultaneously to minimize the multi-task MSE loss function in Equation~\eqref{eq3:multiTaskLoss}.
+We use individual task training as a baseline for comparison, where the \gls{lstm} metamodels are trained separately on the \gls{gmmb} and \gls{gmwb} contracts.
 The objective is to assess how multi-task learning can improve the training efficiency and performance of both products compared to individual task training.
@@
 
-Figure~\ref{fig3:mtl} illustrates our multi-task learning framework for GMMB and GMWB contracts with the dynamic lapse rates.
+Figure~\ref{fig3:mtl} illustrates our multi-task learning framework for \gls{gmmb} and \gls{gmwb} contracts with the dynamic lapse rates.
 The outer simulation paths for both contracts are the same, which are generated from the same nested simulation procedure with $100$ inner replications.
-The LSTM metamodels are trained simultaneously on both contracts.
-The LSTM layers are shared to train for capturing general temporal patterns, and each contract has its own fully connected layers that are trained for contract loss predictions.
+The \gls{lstm} metamodels are trained simultaneously on both contracts.
+The \gls{lstm} layers are shared to train for capturing general temporal patterns, and each contract has its own fully connected layers that are trained for contract loss predictions.
 
@@
     \end{subfigure}
-    \caption{Multi-task Learning on RS-GBM GMMB and GMWB with dynamic lapse}
+    \caption{Multi-task Learning on \gls{rsgbm} GMMB and GMWB with dynamic lapse}
     \label{fig3:figure5}
@@
 
-Figure~\ref{fig3:figure5} compares the learning curves for the training of the GMMB and the GMWB, with and without the multi-task learning.
+Figure~\ref{fig3:figure5} compares the learning curves for the training of the \gls{gmmb} and the \gls{gmwb}, with and without the multi-task learning.
 The comparison between the mult-itask learning (Figures~\ref{subfig3-5:multiTask} and~\ref{subfig3-5:fineTuning}) and the individual task training ((Figures~\ref{subfig3-5:gmmb_individual} and~\ref{subfig3-5:gmwb_individual})) demonstrates the benefit of the multi-task learning for both products.
 
-In the case of the GMMB, the multi-task learning allows the model to achieve faster convergence while reducing overfitting.
-For the GMWB, the multi-task learning framework helps to stablize the training process.
-The shared LSTM layers in the multi-task model are able to capture common temporal patterns and dynamics, which benefits both the GMMB and the GMWB when the training samples are scarce.
+In the case of the \gls{gmmb}, the multi-task learning allows the model to achieve faster convergence while reducing overfitting.
+For the \gls{gmwb}, the multi-task learning framework helps to stablize the training process.
+The shared \gls{lstm} layers in the multi-task model are able to capture common temporal patterns and dynamics, which benefits both the \gls{gmmb} and the \gls{gmwb} when the training samples are scarce.
 
-Similar to the pooling in Chapters~\ref{chap:project1} and~\ref{chap:project2} but on a higher level, multi-task learning enables the LSTM metamodels to leverage shared representations across related VA contracts.
+Similar to the pooling in Chapters~\ref{chap:project1} and~\ref{chap:project2} but on a higher level, multi-task learning enables the \gls{lstm} metamodels to leverage shared representations across related \gls{va} contracts.
 
@@
 
-% Even when data is abundant, multi-task learning can improve the training efficiency and predictive performance of LSTM metamodels for nested simulations.
-% The shared LSTM layers learn generalizable features that are beneficial across different VA contracts.
+% Even when data is abundant, multi-task learning can improve the training efficiency and predictive performance of \gls{lstm} metamodels for nested simulations.
+% The shared LSTM layers learn generalizable features that are beneficial across different \gls{va} contracts.
 % Figure~\ref{fig3:figure6} demonstrates the performance of multi-task learning on GMMB and GMWB contracts with dynamic lapse rates.
@@
 
-In this chapter, we have introduced a transfer learning framework to accelerate the training of LSTM metamodels for dynamic hedging of variable annuity contracts.
-Traditional nested simulation procedures for VA risk management are computationally intensive.
-LSTM metamodels offer a data-driven approach to approximate the true contract losses, which can substantially reduce the computational cost of hedging a single VA contract.
-However, training LSTM metamodels on new VA contracts can be challenging due to the limited availability of simulation data.
-Our proposed framework leverages pre-trained LSTM networks and transfer learning techniques to adapt metamodels quickly to new but related VA contracts with a minimum amount of additional simulation cost.
-Fine-tuning a pre-trained LSTM metamodel on a new target task with a limited amount of data substantially improved training stability and predictive accuracy compared to training from the scratch.
+In this chapter, we have introduced a \gls{tl} framework to accelerate the training of \gls{lstm} metamodels for dynamic hedging of variable annuity contracts.
+Traditional nested simulation procedures for \gls{va} risk management are computationally intensive.
+\gls{lstm} metamodels offer a data-driven approach to approximate the true contract losses, which can substantially reduce the computational cost of hedging a single \gls{va} contract.
+However, training \gls{lstm} metamodels on new \gls{va} contracts can be challenging due to the limited availability of simulation data.
+Our proposed framework leverages pre-trained \gls{lstm} networks and \gls{tl} techniques to adapt metamodels quickly to new but related \gls{va} contracts with a minimum amount of additional simulation cost.
+Fine-tuning a pre-trained \gls{lstm} metamodel on a new target task with a limited amount of data substantially improved training stability and predictive accuracy compared to training from the scratch.
 
@@
 
-Multi-task learning offers a robust framework for transferring knowledge across related simulation schemes in the LSTM metamodeling for nested simulations. 
-By sharing representations through the LSTM layers, the model can learn more generalizable features that are beneficial across different VA contracts. 
+Multi-task learning offers a robust framework for transferring knowledge across related simulation schemes in the \gls{lstm} metamodeling for nested simulations. 
+By sharing representations through the \gls{lstm} layers, the model can learn more generalizable features that are beneficial across different \gls{va} contracts. 
 The multi-task approach is particularly beneficial when training data for individual tasks is scarce, as it effectively pools information across tasks to enhance learning efficiency and predictive performance.
@@
 Furthermore, a metamodel trained with multi-task learning can serve as a pre-trained model. 
-It is adaptable to various VA contracts and asset models, and it is a versatile tool for practical applications in dynamic hedging of VAs.
+It is adaptable to various \gls{va} contracts and asset models, and it is a versatile tool for practical applications in dynamic hedging of \gls{va}s.
 
-The integration of transfer learning in LSTM metamodeling represents an important advancement in robust risk management associated with variable annuity contracts.
+The integration of \gls{tl} in \gls{lstm} metamodeling represents an important advancement in robust risk management associated with \gls{va} contracts.
 By effectively leveraging existing knowledge, financial institutions can maintain accurate and responsive risk management practices in a rapidly changing market environment. 
-The methodologies presented in this chapter attempt to make a contribution to the broader applications of transfer learning in financial modeling and risk assessment.
+The methodologies presented in this chapter attempt to make a contribution to the broader applications of \gls{tl} in financial modeling and risk assessment.

### 2025-04-13 project1/nsSurvey.tex
new

@@
 
-\subsection{Connections between Convergence in \gls{mse} and AE}\label{sec1:connection-mse-absolute-error}
+\subsection{Connections between Convergence in MSE and AE}\label{sec1:connection-mse-absolute-error}
 
@@
     Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
-    We write $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-\xi})$, that is $\hat{\rho}_{\Gamma}$ converges in probabilistic order $\xi$ to $\rho$ if for a sufficiently large $\Gamma$, for all $\epsilon > 0$ there exists a constant $C$ such that
-    $$
-         \mathbb{P} \left( \left| \hat{\rho}_{\Gamma} - \rho \right| \geq C \Gamma^{-\xi} \right) \leq \epsilon.
+    We write $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-\xi})$, that is $\hat{\rho}_{\Gamma}$ converges in probabilistic order $\xi$ to $\rho$ if for a sufficiently large $\Gamma$, \textcolor{red}{for any $\epsilon > 0$ there exists a $C_\epsilon$ such that}
+    $$
+         \mathbb{P} \left( \left| \hat{\rho}_{\Gamma} - \rho \right| \geq C_\epsilon \Gamma^{-\xi} \right) \leq \epsilon.
     $$

### 2025-04-13 project2/nnMetamodels.tex
new

@@
 
-Below we provide a scheme used to perform a multi-period nested simulation in estimating (profit and loss) P\&L for one outer scenario.
+Below we provide a scheme used to perform a multi-period nested simulation in estimating \gls{pl} for one outer scenario.
 
@@
 \end{equation}
-The P\&L of the \gls{va} contract includes cost of the initial hedge ($H_0$), hedging errors~\eqref{eq2:hedgingerror}, unwinding of the hedge at maturity ($H^{bf}_T$), and unhedged liability ($V_0$).
+The \gls{pl} of the \gls{va} contract includes cost of the initial hedge ($H_0$), hedging errors~\eqref{eq2:hedgingerror}, unwinding of the hedge at maturity ($H^{bf}_T$), and unhedged liability ($V_0$).
 Mathematically, the present value of these cash flows is given by
@@
 
-Comparing with the MSE table in Table~\ref{tab:gmwb_arch} that summarizes the overall fit, QQ plots offer a closer look at the metamodels' performance on different parts of the loss distribution.
+Comparing with the \gls{mse} table in Table~\ref{tab:gmwb_arch} that summarizes the overall fit, QQ plots offer a closer look at the metamodels' performance on different parts of the loss distribution.
 Figure~\ref{fig2:QQ_REG} show the regression metamodel predictions and the loss labels in the true dataset.
@@
 We observe that a poor metamodel such as the \gls{qpr} identifies less than $40\%$ of the true tail scenario without any safety margin.
-In contrast, a well-suited metamodel such as the \gls{lstm} identifies more than $75\%$ of the true tail scenarios without any safety margin and more than the QPR metamodel does with $15\%$ of safety margin\footnote{The metamodel in~\cite{dang2020efficient} identifies $100\%$ of the true tail scenarios on with a $10\%$ safety margin for a \gls{gmab} contract.
+In contrast, a well-suited metamodel such as the \gls{lstm} identifies more than $75\%$ of the true tail scenarios without any safety margin and more than the \gls{qpr} metamodel does with $15\%$ of safety margin\footnote{The metamodel in~\cite{dang2020efficient} identifies $100\%$ of the true tail scenarios on with a $10\%$ safety margin for a \gls{gmab} contract.
 The \gls{gmab} contract is simpler than the \gls{gmwb} contract, and the true tail scenarios are easier to identify. 
@@
 Otherwise, the two-stage procedure will offer no computational advantage in simulation budget over the standard procedure.
-The \gls{lstm} metamodel can reach similar percentage with a $5\%$ safety margin.
+The \gls{lstm} metamodel can reach similar percentage \textcolor{red}{of correctly identified true tail scenarios} with a $5\%$ safety margin.
 This indicates that the \gls{lstm} metamodel should be able to reach the same level of accuracy as the standard procedure with only $20\%$ of the simulation budget.
@@
 The last rows of Table~\ref{tab2:lstm_sens} and Table~\ref{tab2:hicaplstm_sens} show the performance of the regular and high capacity \gls{lstm} metamodels trained with $M=\num{100000}$ training labels with different noise levels.
-We observe that an increasing $N$ reduces the MSE, but the reduction is not substantial for a regular \gls{lstm} when $N$ is larger than $\num{10}$.
-For the high-capacity \gls{lstm}, the MSE is substantially reduced when $N$ is increased from $\num{1}$ to $\num{100}$, but the reduction is not substantial when $N$ is increased from $\num{100}$ to $\num{1000}$.
+We observe that an increasing $N$ reduces the \gls{mse}, but the reduction is not substantial for a regular \gls{lstm} when $N$ is larger than $\num{10}$.
+For the high-capacity \gls{lstm}, the \gls{mse} is substantially reduced when $N$ is increased from $\num{1}$ to $\num{100}$, but the reduction is not substantial when $N$ is increased from $\num{100}$ to $\num{1000}$.
 Another way to interpret the results in Table~\ref{tab2:lstm_sens} is to compare the MSEs for the same budget of $\Gamma = M \times N$.
@@
 To further investigate the single-stage procedure's performance, we conduct a convergence analysis on the \gls{lstm} metamodels.
-Figure~\ref{fig2:gammaConvergence} shows the log-log plots of the relative root mean square errors (RRMSE) between the \gls{lstm} metamodel \gls{cvar} predictions and the true \gls{cvar} against the total simulation budget $\Gamma$.
-For each budget $\Gamma$, the metamodels are trained for different combinations of $M$ and $N$, and the metamodel with the best RRMSE is plotted.
+Figure~\ref{fig2:gammaConvergence} shows the log-log plots of the \gls{rrmse} between the \gls{lstm} metamodel \gls{cvar} predictions and the true \gls{cvar} against the total simulation budget $\Gamma$.
+For each budget $\Gamma$, the metamodels are trained for different combinations of $M$ and $N$, and the metamodel with the best \gls{rrmse} is plotted.
 While numerical results suggest that the \gls{cvar} estimator of the single-stage procedure with \gls{lstm} metamodels may have better accuracy than the two-stage procedure and the standard procedure when the number of outer scenarios is further increased, we found it difficult to compare their performance due to insufficient computational resources.
@@
 
-Figure~\ref{fig2:mnConvergence} shows the log-log plots of the RRMSE between the \gls{lstm} metamodel \gls{cvar} predictions and the true \gls{cvar} against the simulation budget.
-The left figure shows the empirical convergence of the RRMSE for increasing inner replications with a fixed number of outer scenarios ($M=\num{100000}$), and the right figure shows the empirical convergence of the RRMSE for increasing outer scenarios with a fixed number of inner replications ($N=\num{10}$).
+Figure~\ref{fig2:mnConvergence} shows the log-log plots of the \gls{rrmse} between the \gls{lstm} metamodel \gls{cvar} predictions and the true \gls{cvar} against the simulation budget.
+The left figure shows the empirical convergence of the \gls{rrmse} for increasing inner replications with a fixed number of outer scenarios ($M=\num{100000}$), and the right figure shows the empirical convergence of the \gls{rrmse} for increasing outer scenarios with a fixed number of inner replications ($N=\num{10}$).
 Due to computational constraints, we are not able to run the two-stage procedure and the standard procedure with more outer scenarios or more inner replications, therefore the comparison between the single-stage procedure is only available up to $M = \num{100000}$ and $N = \num{1000}$.
-We observe that the RRMSE decreases as the simulation budget increases, and the rate of convergence is higher when the quantity of the data increases.
+We observe that the \gls{rrmse} decreases as the simulation budget increases, and the rate of convergence is higher when the quantity of the data increases.
 For an \gls{lstm} metamodel, increasing the data quality of the training labels has diminishing returns, which is consistent with the results in Figure~\ref{fig2:mnConvergence}.
-For an increasing number of inner replications with a fixed number of outer scenarios, the RRMSE ceases to decrease after reaching $N = \num{100}$. 
+For an increasing number of inner replications with a fixed number of outer scenarios, the \gls{rrmse} ceases to decrease after reaching $N = \num{100}$. 
 More specfically, when the quality of the training labels is fixed at $N = \num{10}$, the \gls{cvar} estimator of a single-stage procedure with a \gls{lstm} metamodel converge roughly in the order of $\mathcal{O}(M^{\frac{2}{3}})$.

### 2025-04-13 proof/aeProof.tex
new

--- 2025-04-08 project1/nsSurvey.tex
@@
-%======================================================================
-\chapter{Nested Simulation Procedures in Financial Engineering: A Selected Review}\label{chap:project1}
-%======================================================================
+\documentclass{article}
 
-\section{Introduction}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{graphicx}
+\usepackage{geometry}
 
-Nested simulation procedures are commonly used in financial engineering to estimate risk measures for portfolios of complex financial derivatives. 
-The term \textit{nested} refers to a nested estimation problem, in which the estimation of the risk measure requires two levels of Monte Carlo (MC) simulations.
-In a typical nested simulation procedure, an outer-level simulation model generates underlying risk factors, which are referred to as the \textit{outer scenarios}.
-For each outer scenario, an inner-level simulation model generates scenario-wise samples of the portfolio losses, which are referred to as the \textit{inner replications}.
+\newtheorem{theorem}{Theorem}
+\newtheorem{assumption}{Assumption}
+\newtheorem{proposition}{Proposition}
+\newtheorem{lemma}{Lemma}
+\newtheorem{corollary}{Corollary}
+\newtheorem{definition}{Definition}
 
-The nested simulation procedure is computationally expensive due to its nested structure. 
-Given a fixed computational budget, the nestzed simulation procedure should balance the number of outer scenarios and the number of inner replications to maximize computational efficiency.
-\cite{gordy2010nested} first analyzed and proposed an optimal budget allocation for a standard nested simulation procedure.
-The term \textit{standard} refers to using a standard MC estimator, the sample mean of the inner replications to estimate a scenario-wise portfolio loss for an outer scenario.
-\cite{gordy2010nested} investigate an optimal budget allocation for a standard nested simulation procedure with respect to the MSE of the estimated risk measure.
+\geometry{a4paper, margin=1in}
 
-The standard nested simulation procedure is computationally expensive with a wasteful use of the simulation budget, as only the inner replications from the same outer scenario are used in estimating the scenario-wise portfolio loss for that outer scenario.
-Subsequent research efforts have been made to improve the efficiency of nested simulation procedures by using inner replications from other outer scenarios.
-This is referred to as pooling.
-Different methods pool inner replications differently, using either a trained supervised learning metamodel or predefined likelihood ratio weights.
-\cite{broadie2015risk} propose a regression-based nested simulation procedure, which uses a trained regression metamodel to estimate the scenario-wise portfolio loss for an outer scenario by pooling the inner replications from all outer scenarios.
-For certain risk measures,~\cite{broadie2015risk} show that it's optimal to allocate the entire simulation budget to outer-level simulations, keeping only 1 inner replication in each outer scenario.
-Similarly,~\cite{hong2017kernel},~\cite{feng2020optimal}, and~\cite{zhang2022sample} use a kernel smoothing model, a likelihood ratio model, and a kernel ridge regression (KRR) model as metamodels to pool the inner replications from all outer scenarios, respectively.
-In simulation studies, this approach—using a model of a simulation—is called metamodeling, and such models are termed metamodels~\citep{barton1998simulation}.
-Another line of research is a multi-level Monte Carlo (MLMC) method analyzed in~\cite{giles2019multilevel}, which is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest.
+\title{Connections between Convergence in MSE and AE}
+\author{Xintong Li}
+\date{\today}
 
-This paper presents a survey study of some popular nested simulation procedures that have both asymptotic convergence analysis and finite-sample performance evaluation.
-Many procedures have been proposed in the literature, but they are not directly comparable because they use different error metrics, different assumptions, and different numerical examples in their studies.
-Within a common analytical framework, we first summarize and compare the asymptotic convergence rates of these procedures.
-Their asymptotic convergence results are closely examined for their assumptions that guarantee the convergence.
-Furthermore, the existing literature has chosen different performance metrics to evaluate the asymptotic convergence of nested simulation procedures.
-In this chapter, we discuss the asymptotic convergence in terms of MSE of the estimator, and we provide a comprehensive comparison of their convergence rates and critical assumptions.
-We also discuss the connection between the MSE and the absolute error of the estimator in the context of nested simulation procedures.
-
-In terms of finite-sample performance, different studies propose different examples in their numerical experiments, which introduces unfair advantages for certain simulation procedures over others. 
-A fair comparison among popular methods is therefore urgently needed in the literature. 
-Our numerical experiment in this chapter is the first of its kind to subject all the aforementioned simulation procedures to a fair comparison. 
-As a result, extensive numerical experiments are conducted to show, in practical examples, how well the finite-sample performance of a method matches its theoretical convergence behavior. 
-Through our numerical examples, we compare the nested simulation procedures for different payoff complexities, problem dimensions, and risk measures. 
-This chapter also provides a discussion of the computational complexity of different nested simulation procedures, including additional computational costs for training supervised learning metamodels and pooling inner replications.
-
-The rest of this chapter is organized as follows.
-Section~\ref{sec1:problem-formulation} introduces the nested simulation procedure and the standard MC estimator.
-Section~\ref{sec1:asymptotic-convergence} provides new theoretical results on the convergence of existing nested simulation procedures.
-Section~\ref{sec1:convergence-orders} summarizes the asymptotic convergence orders and the critical assumptions of nested simulation procedures in the literature.
-Section~\ref{sec1:numerical-experiments} presents the numerical experiments and the comparisons of different nested simulation procedures with respect to different risk measures, problem dimensions, and payoff complexities.
-Section~\ref{sec1:computational-complexity} discusses the computational complexity of different nested simulation procedures.
-Section~\ref{sec1:conclusion} concludes this chapter.
-
-\section{Problem Formulation}\label{sec1:problem-formulation}
-
-In a nested estimation problem, we are interested in estimating the quantity
-
-$$\rho(L) = \rho(L(X)),$$
-where $X \in \mathcal{X} \subset \mathbb{R}^d$, and $L = L(X)$ is a random variable whose distribution is characterized by $X$.
-$L(X)$ is not subject to direct evaluation, but it is the output of
-
-$$ L(X) = \mathbb{E}\left[ Y|X=x \right]\vert_{x=X} $$
-
-Some common risk measures are in the nested expectation form as
-$$\rho(L) = \mathbb{E}\left[ h(L) \right]$$
-where $h: \mathbb{R} \mapsto \mathbb{R}$ is a known nonlinear function. 
-The nested expectation form is a general form that covers many risk measures of interest in financial engineering by varying the function $h$.
-Common forms of $h$ in the literature include smooth functions, Lipschitz continuous functions, and indicator functions.
-
-\begin{definition}\label{def1:smooth}
-    A function $h: \mathbb{R} \mapsto \mathbb{R}$ is smooth if it is continuously differentiable up to the $n$-th order for some $n \in \mathbb{N}$, 
-    and its $n$-th and $m$-th derivatives are bounded for some $m \in \mathbb{N}$ and $m < n$.
-\end{definition}
-
-A quadratic tracking error with benchmark $b$, where $h(t) = (t - b)^2$, falls into this category.
-In the context of nested estimation for smooth $h$, different procedures require different versions of Definition~\ref{def1:smooth} to specify the smoothness for their convergence analysis.
-Table~\ref{tab1:smoothness} summarizes the smoothness assumption of $h$ for different nested simulation procedures in the literature.
-
-\begin{table}[ht!]
-    \centering
-    \begin{tabular}{lcc}
-    \toprule
-    \textbf{Nested Simulation Procedures} & $n$ & $m$ \\
-    \midrule
-    Regression & $2$ & not required \\
-    Kernel smoothing & $3$ & $2$ \\
-    Kernel ridge regression & $2$ & $1$ \\
-    Likelihood ratio & $2$ & $1$ \\
-    \bottomrule
-    \end{tabular}
-    \caption{Smoothness assumption of $h$ for different nested simulation procedures}
-\label{tab1:smoothness}
-\end{table}
-
-The regression-based nested simulation procedure has the least stringent smoothness assumption.
-In general, a more complex metamodel requires a higher-order smoothness for $h$ for its convergence analysis.
-Despite being more advanced than kernel smoothing, the KRR-based procedure requires a less stringent smoothness assumption on $h$.
-At first sight, it is counterintuitive that a more complex metamodel requires a less stringent smoothness assumption.
-This phenomenon is due to the fact that the convergence analysis for the KRR-based nested simulation procedure is shown in terms of an absolute error (AE), which is a less stringent error metric than MSE.
-Section~\ref{sec1:connection-mse-absolute-error} discusses the connection between the MSE and the AE of the estimator in the context of nested simulation procedures.
-In Table~\ref{tab1:smoothness}, the standard nested simulation procedure is the only procedure without an asymptotic convergence analysis for smooth $h$.
-Section~\ref{sec1:sns} fills this gap by providing the asymptotic convergence analysis for the standard nested simulation procedure in terms of MSE.
-
-\begin{definition}\label{def1:lipschitz}
-    A function $h: \mathbb{R} \mapsto \mathbb{R}$ is Lipschitz continuous with a Lipschitz constant $K$ if for all $t_1, t_2 \in \mathbb{R}$, 
-    $$|h(t_1) - h(t_2)| \leq K|t_1 - t_2|.$$
-\end{definition}
-
-The mean excess loss over a threshold $u$ is defined by setting $h(t) = \max\{t - u, 0\}$, which is a special case of a Lipschitz continuous function.
-The regression-based nested simulation procedure is the only procedure that performs a theoretical analysis for Lipschitz continuous $h$.
-The other procedures only provide a convergence analysis for the special case of mean excess loss over a threshold $u$.
-
-\begin{definition}\label{def1:indicator}
-    A function $h: \mathbb{R} \mapsto \mathbb{R}$ is an indicator function if 
-    $$h(t) = \mathbb{I}_{\{t \geq u\}}$$
-    for some $u \in \mathbb{R}$.
-\end{definition}
-
-The probability of a large loss over a threshold $u$ is obtained by setting $h(t) = \mathbb{I}_{\{t \geq u\}}$.
-
-Other risk measures of interest not in the nested expectation form include Value at Risk (VaR) and Conditional Value at Risk (CVaR)~\citep{hardy2022quantitative}. 
-The $\alpha$-VaR of $L$ is defined as
-\begin{equation}\label{eq1:var}
-    \mbox{VaR}_\alpha(L) = q_\alpha = \inf \left\{ q: \Pr(L\leq q) \geq \alpha \right\}.
-\end{equation}
-
-The $\alpha$-CVaR of $L$ is defined as
-\begin{equation}\label{eq1:cvar}
-    \mbox{CVaR}_\alpha(L) =\frac{1}{1-\alpha} \int_{\alpha}^{1} q_v dv. 
-\end{equation}
-
-In the literature, CVaR are also known as Conditional Tail Expectation (CTE), Tail Value-at-Risk (TailVaR), and Expected Shortfall (ES).
-
-The rest of this section reviews the existing nested simulation procedures in the literature.
-We unify their notations and provide a comprehensive comparison of how inner replications are generated and pooled for different procedures.
-
-\subsection{The Standard Nested Simulation Procedure}
-
-The standard nested simulation procedure first simulates $M$ independent and identically distributed (i.i.d.) outer scenarios $X_1, \dots, X_M$ from $F_X$, the distribution of $X$.
-For each $X_i$, again simulate $Y_{ij}$, $j = 1, \dots, N$ from $F_{Y|X_i}$, the conditional distribution of $Y$ given $X_i$.
-Given scenario $i$, the $Y_{ij}$ are conditionally i.i.d.
-Let $\Gamma = M \cdot N$ denote the total simulation budget, $f_X(x)$ denote the density of $X$, and $\mathbf{X} = (X_1, \dots, X_M)$ denote the vector of outer scenarios.
-
-The standard nested simulation procedure estimates $L_i = L(X_i)$ with a standard MC estimator 
-\begin{equation*}
-  \hat{L}_{N, i} = \frac{1}{N} \sum_{j=1}^N Y_{ij}, \quad Y_{ij} \sim F_{Y|X_i}.  
-\end{equation*}
-
-Let $\hat{L}_{(i)}, \dots, \hat{L}_{(M)}$ be the order statistics of $\hat{L}_{N, 1}, \dots, \hat{L}_{N, M}$. 
-The standard nested simulation estimators for different forms of $\rho$ are as follows:
-
-\begin{enumerate}
-    \item   Nested expectation form:
-            \begin{equation*}
-                \hat{\rho}_{M, N} = \frac{1}{M} \sum_{i=1}^M h(\hat{L}_{N, i}) = \frac{1}{M} \sum_{i=1}^M h(\bar{Y}_{N, i}), \quad X_i \sim F_X.
-            \end{equation*}
-    \item   Value at risk (VaR):
-            \begin{equation*}
-                \hat{\rho}_{M, N} = \hat{L}_{(\lceil \alpha M \rceil)}.
-            \end{equation*}
-
-    \item   CVaR:
-            \begin{equation}\label{eq1:cvar-hat}
-                \hat{\rho}_{M, N} = \hat{L}_{(\lceil \alpha M \rceil)} + \frac{1}{(1-\alpha) M} \sum_{i=1}^M \max \{\hat{L}_{N, i} - \hat{L}_{(\lceil \alpha M \rceil)}, 0 \}.
-            \end{equation}
-\end{enumerate}
-
-~\cite{gordy2010nested} analyze the optimal budget allocation of the standard nested simulation procedure with respect to the MSE of the estimator $\hat{\rho}_{M, N}$ for hockey-stick $h$, indicator $h$, and VaR.
-
-\subsection{Multi-level Monte Carlo}
-
-The MLMC method is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest, and it uses the difference between the approximations to reduce the variance of the estimator.
-The MLMC method is particularly useful when the quantity of interest is expensive to evaluate, and the standard MC estimator has a high variance.
-\textcolor{red}{For the nested expectation form $\rho = \mathbb{E}[h(L)]$, the MLMC method selects an approximation level $L$ with sufficient accuracy, and it uses the difference between the approximations to reduce the variance of the estimator.}
-\textcolor{red}{\sout{The MLMC method estimates $\rho$ with an MLMC estimator:}}
-
-\begin{equation*}
-    \hat{\rho}^{\text{MLMC}}_\Gamma = \sum_{\upsilon=0}^{\Upsilon} \left( \frac{1}{M_{\upsilon}} \sum_{i=1}^{M_{\upsilon}} h(\hat{L}_{N_{\upsilon}}(X_{i, \upsilon})) - \frac{1}{M_{\upsilon-1}} \sum_{i=1}^{M_{\upsilon-1}} h(\hat{L}_{N_{\upsilon-1}}(X_{i, \upsilon-1})) \right), \quad X_{i, \upsilon} \sim F_X,
-\end{equation*}
-where $\hat{L}_{N_{-1}}(\cdot) = 0$, $\Upsilon$ is a number of levels, $M_{\upsilon}$ is a number of outer scenarios at level $\upsilon$, and $N_{\upsilon}$ is a number of inner replications at level $\upsilon$.
-Applying the analysis of~\cite{giles2015multilevel} in a nested simulation context,~\cite{giles2019multilevel} show that the MLMC method can achieve a similar degree of accuracy as the standard nested simulation procedure with a lower total computational budget.
-The simulation budget $\Gamma$ is a sum of the computational budget at each level, i.e., $\Gamma = \sum_{\upsilon=0}^{\Upsilon} M_{\upsilon} \cdot N_{\upsilon}$.
-Neither the standard nested simulation procedure nor the MLMC method involves pooling the inner replications from all outer scenarios.
-Pooling enhances sample efficiency and distinguishes advanced nested simulation procedures from the standard procedure.
-
-\subsection{Supervised Learning Metamodels}
-
-Supervised learning-based nested simulation procedures treat the inner simulation model $L(\cdot)$ as a black-box function, and they approximate $L(\cdot)$ with supervised learning metamodels.
-In this metamodeling approach, $L(\cdot)$ can be approximated by $\hat{L}^{\text{SL}}_{M, N}(\cdot)$, which is based on a family of chosen function and observations from the standard nested simulation procedure.
-Consider the observation pairs $(X_i, \hat{L}_{N, i})$ for $i \in \{1, \dots, M\}$ as training data.
-We can use supervised learning to approximate $L_i$ by $\hat{L}_{M, N}^{\text{SL}}(X_i)$ and to pool the inner replications from all outer scenarios.
-Specifically, $\hat{L}^{\text{SL}}{M, N}(\cdot)$ denotes a supervised learning model trained on $(X_i, \hat{L}{N, i})$ for $i \in {1, \dots, M}$.
-This is the output of the standard nested simulation procedure with $M$ outer scenarios and $N$ inner replications.
-To evaluate the convergence of the supervised learning-based nested simulation procedure, we consider the convergence behavior of the supervised learning model $h(\hat{L}^{\text{SL}}_{M, N}(\cdot))$ to the true risk measure $\rho = h(L(\cdot))$.
-More specifically, we want to study the following quantity
-\begin{equation}\label{eq1:sl-E}
-    \mathbb{E} \left[ h(\hat{L}^{\text{SL}}_{M, N}(X))   \right] - \rho, \quad X \sim F_X.
-\end{equation}
-
-However, studying the expectation in Equation~\eqref{eq1:sl-E} is unrealistic, as in practice the risk measure $\rho$ is estimated with a finite number of samples.
-Using the $M$ \textit{training} samples, a supervised learning-based nested MC estimator of $\rho$ is given by
-
-\begin{enumerate}
-    \item   Nested expectation form:
-            \begin{equation}\label{eq1:sl-train}
-                \hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = \frac{1}{M} \sum_{i=1}^M h(\hat{L}^{\text{SL}}_{M, N}(X_i)), \quad X_i \sim F_X.
-            \end{equation}
-    \item   VaR:
-            \begin{equation*}
-              \hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = \hat{L}^{\text{SL}}_{(\lceil \alpha M \rceil)}.  
-            \end{equation*}
-    \item   CVaR:
-            \begin{equation*}
-                \hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = \hat{L}^{\text{SL}}_{(\lceil \alpha M \rceil)} + \frac{1}{(1-\alpha) M} \sum_{i=1}^M \max \{\hat{L}^{\text{SL}}_{M, N}(X_i) - \hat{L}^{\text{SL}}_{(\lceil \alpha M \rceil)}, 0 \}.
-            \end{equation*}
-\end{enumerate}
-where $\hat{L}^{\text{SL}}_{(\lceil \alpha M \rceil)}$ is the $\lceil \alpha M \rceil$-th order statistic of $\hat{L}^{\text{SL}}_{M, N}(X_1), \dots, \hat{L}^{\text{SL}}_{M, N}(X_M)$.
-
-After a supervised learning metamodel is trained, it can be used to make predictions for all $X \in \mathcal{X}$.
-Instead of using the same training samples to estimate the risk measure, we can use metamodel predictions for a new set of $M'$ \textit{test} samples of $X$, namely $\tilde{\mathbf{X}} = \{\tilde{X}_1, \dots, \tilde{X}_{M'}\}$.
-The resulting supervised learning-based estimator of $\rho^{\text{SL}, \text{Test}}$ is given by
-
-\begin{enumerate}
-    \item   Nested expectation form:
-            \begin{equation}\label{eq1:sl-test}
-            \hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = \frac{1}{M'} \sum_{i=1}^{M'} h(\hat{L}^{\text{SL}}_{M, N}(\tilde{X}_i)), \quad \tilde{X}_i \sim F_X.
-            \end{equation}
-    \item   VaR:
-            \begin{equation*}
-              \hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = \hat{L}^{\text{SL}}_{(\lceil \alpha M' \rceil)}.  
-            \end{equation*}
-    \item   CVaR:
-            \begin{equation*}
-                \hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} 
-                = \hat{L}^{\text{SL}}_{(\lceil \alpha M' \rceil)} 
-                + \frac{1}{(1-\alpha) M'} \sum_{i=1}^{M'} \max \{\hat{L}^{\text{SL}}_{M, N}(\tilde{X}_i) - \hat{L}^{\text{SL}}_{(\lceil \alpha M' \rceil)}, 0 \}, 
-            \end{equation*}
-\end{enumerate}
-where $\hat{L}^{\text{SL}}_{(\lceil \alpha M' \rceil)}$ is an $\lceil \alpha M' \rceil$-th order statistic of $\hat{L}^{\text{SL}}_{M, N}(\tilde{X}_1), \dots, \hat{L}^{\text{SL}}_{M, N}(\tilde{X}_{M'})$.
-Note that $\hat{L}^{\text{SL}}_{M, N}(\cdot)$ represents the predictions of a supervised learning model trained on the samples $(X_1, \hat{L}_{N, 1}), \dots, (X_M, \hat{L}_{N, M})$.
-
-Existing literature on nested simulation procedures has proposed different supervised learning metamodels to approximate the true function $L(\cdot)$.
-In this study, we focus on the metamodeling approaches that include theoretical convergence results.
-Methods that include theoretical convergence results are regression~\citep{broadie2015risk}, kernel smoothing~\citep{hong2017kernel}, and KRR~\citep{wang2022smooth}.
-Their estimators of $L(\cdot)$ are given by $\hat{L}^{\text{REG}}_{M, N}(\cdot)$, $\hat{L}^{\text{KS}}_{M, N}(\cdot)$, and $\hat{L}^{\text{KRR}}_{M, N}(\cdot)$, respectively.
-
-\begin{itemize}
-    \item   Regression:
-            $$\hat{L}^{\text{REG}}_{M, N}(X) = \Phi(X) \hat{\beta},$$
-            where $\Phi$ is a chosen basis, and $\hat{\beta}$ is estimated from the training samples.
-            In~\cite{broadie2015risk}, the convergence analysis is performed on the expectation (Equation~\eqref{eq1:sl-E}) and for smooth and Lipschitz continuous $h$. 
-    \item   Kernel smoothing:
-            $$\hat{L}^{\text{KS}}_{M, N}(X) = \frac{\sum_{i=1}^M \hat{L}_{N, i} K_w(X - X_i)}{\sum_{i=1}^M K_w(X - X_i)}, $$
-            where $K_w$ is a kernel function with bandwidth $w$.
-            ~\cite{nadaraya1964estimating} and ~\cite{watson1964smooth} originally proposed this kernel smoothing method for a non-parametric regression, and it is widely known in the literature as a Nadaraya-Watson kernel regression.
-            ~\cite{hong2017kernel} provides convergence analysis for metamodel predictions of the training samples (Equation~\eqref{eq1:sl-train}), and the convergence analysis is provided for smooth, hockey-stick, and indicator $h$.
-
-    \item   kNN~\citep{mack1981local}:
-            \begin{equation*}
-            \hat{L}^{\text{kNN}}_{M, N}(x) 
-            = \frac{\frac{1}{M R_M^d} \sum_{i=1}^M \hat{L}_{N, i} K\left(\frac{x - X_i}{R_M}\right)}{\frac{1}{M R_M^d} \sum_{i=1}^M K\left(\frac{x - X_i}{R_M}\right)},
-            \end{equation*}
-            where $R_k$ is a Euclidean distance between $X_i$ and its $k$-th nearest neighbor, and $K:\mathbb{R}^d \mapsto \mathbb{R}$ is a bounded, nonnegative kernel function satisfying 
-            \begin{align*}
-                \int K(u) du & = 1, \\
-                K(u) &= 0, ~~~ ~\text{for}~ \|u\| \geq 1,
-            \end{align*}
-            where $\|\cdot\|$ is the Euclidean norm, and  $k$ is a number of nearest neighbors to consider.
-            The kNN method is implemented as a metamodel for numerical experiments in~\cite{hong2017kernel}, but the convergence analysis is not provided.
-
-    \item   KRR:
-            $$\hat{L}^{\text{KRR}}_{M, N}(X) = \argmin_{g \in \mathcal{N}_{\Psi}(\Omega)} \left( \frac{1}{M} \sum_{i=1}^M (\hat{L}_{N, i} - L_i)^2 + \lambda \|L\|_{\mathcal{N}_{\Psi}(\Omega)}^2\right),$$
-            where $\mathcal{N}_{\Psi}(\Omega)$ is a reproducing kernel Hilbert space (RKHS) with a kernel $\Psi$ defined on a domain $\Omega$, and $\lambda$ is a regularization parameter as in a ridge regression.
-            More specifically, $\Phi$ is a Mat\'ern kernel with a smoothness parameter $\nu$ and a length scale parameter $\upsilon$.
-            ~\cite{wang2022smooth} provides a convergence analysis for the AE (Equation~\eqref{eq1:ae}), and the convergence analysis is provided for a smooth, a Lipschitz continuous, and an indicator $h$, VaR, and CVaR.
-\end{itemize}
-
-These supervised learning metamodels approximate the inner simulation model $L(\cdot)$ with functions in the form of $\hat{L}^{\text{SL}}_{M, N}(\cdot)$, and the metamodels are used to pool the inner replications from all outer scenarios to estimate the risk measure $\rho$.
-In the simulation literature, using models to approximate simulation models is often called metamodeling; such models are referred to as metamodels.
-Supervised learning models are broadly classified into regression and classification models depending on whether the target variable is continuous or discrete.
-In our context, the target variable $L$ is continuous, and the supervised learning models refer to regression models.
-Regression models can be further categorized into parametric and non-parametric regressions.
-Among the supervised learning models we consider, multiple linear regression is parametric, while kernel smoothing and kernel ridge regression are non-parametric.
-
-We aim to minimize the MSE of the supervised learning-based nested simulation estimators $\hat{\rho}^{\text{SL}, \text{Train}}_{M, N}$ and $\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'}$ subject to the total simulation budget $\Gamma$.
-We are also interested in the order of convergence of the estimator for all nested simulation procedures as the total simulation budget $\Gamma$ approaches infinity.
-
-\begin{align}
-    & \min_{M, N}  & \text{MSE}(\hat{\rho}^{\text{SL}}_{M, N}) = \mathbb{E} \left[ \left( \hat{\rho}^{\text{SL}}_{M, N} - \rho \right)^2 \right], \nonumber \\
-    & \text{subject to} & M \cdot N = \Gamma.
-\end{align}
-
-For the more complex metamodels, the convergence analysis of their MSEs is more challenging.
-More specifically, the KRR-based nested simulation~\citep{wang2022smooth} provides a convergence analysis in terms of AE.
-\begin{align}\label{eq1:ae}
-    & \min_{M, N}  & \text{AE}(\hat{\rho}^{\text{SL}}_{M, N}) = \mathbb{E} \left[ \left| \hat{\rho}^{\text{KRR}}_{M, N} - \rho \right| \right] \nonumber \\
-    & \text{subject to} & M \cdot N = \Gamma
-\end{align}
-Section~\ref{sec1:connection-mse-absolute-error} draws the connection between the MSE and the AE of the estimator in the context of nested simulation procedures.
-
-\subsection{Likelihood Ratio Method}
-
-Instead of using a supervised learning model as a metamodel,~\cite{zhang2022sample} uses the likelihood ratio weights to pool the inner replications from all outer scenarios.
-Here, we restrict our attention to problems in the nested expectation form which outer scenarios characterize the stochasticity of the inner simulation model. 
-Specifically,
-$$ Y = Y(H, X), $$
-where $H$ is a random variable whose distribution is specified by the outer scenarios $X$. 
-We denote the conditional distribution of $H|X$ by $f_{H|X}$. 
-For a specific scenario $X_i$, we write $f_{H|X}(\cdot |X_i)$. 
-To reconcile with previously established notations, we note that inner simulation outputs $Y_{ij}$ can be written as
-$$ Y_{ij} = Y(H_{ij}, X_i), $$
-where $H_{ij} \sim f_{H|X}(\cdot |X_i)$.
-Suppose that one can generate random variable $H$ from some sampling
-distribution $f_H$. Then, the likelihood ratio estimator of $\rho$ is given by
-$$\hat{\rho}^{\text{LR}}_{M,N} = \frac{1}{M} \sum_{i=1}^M h(\hat{L}^{\text{LR}}_{N, i}), $$ where the inner replications are pooled by the likelihood ratio weights with
-$$\hat{L}^{\text{LR}}_{N, i} = \frac{1}{N} \sum_{j=1}^N Y(H_j, X_i) \frac{f_{H|X}(H_{j}|X_i)}{f_H(H_{j})}, \;\;\; H_j \sim f_H, \;\;\; i=1, \dots, M.$$
-In Section~\ref{sec1:sensitivity-option-type}, we implement the likelihood ratio method and share its fast convergence in finite-sample experiments despite the costly computation of the likelihood ratio weights (Section~\ref{sec1:computational-complexity}).
-
-\subsection{Problem Statement}
-
-With a total simulation budget $\Gamma$, we are interested in the orders of convergence of estimators for all nested simulation procedures, which are measured by their MSE about the risk measure $\rho$.
-
-\begin{align}
-    & \min ~~~ \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right], \nonumber \\
-    & \text{subject to} ~~~ M \cdot N = \Gamma, 
-\end{align}
-where $\Gamma$ is a simulation budget for a nested simulation procedure.
-A special case is the MLMC method, where the total simulation budget $\Gamma$ is the sum of the simulation budgets at all levels.
-
-\section{Asymptotic Analysis}\label{sec1:asymptotic-convergence}
-In the first part of this section, we summarize the existing asymptotic convergence results of the nested simulation procedures in the literature, and we compare their critical assumptions that guarantee the convergence.
-The remainder of this section aims to fill the gap in the literature by offering the following steps:
-\begin{itemize}
-    \item provide the asymptotic convergence results for the standard nested simulation procedure, 
-    \item show the connections between the convergence in MSE and the convergence in probabilistic order for AE in the context of nested simulation procedures, and
-    \item illustrate the asymptotic rate of convergence of a kNN-based nested simulation procedure.
-\end{itemize}
-
-\begin{table}[ht]
-    \centering
-    \footnotesize
-    \begin{tabular}{|l|c|c|c|c|c|}
-    \hline
-    \textbf{Estimator for} $L$ & \textbf{Smooth} $h$ & \textbf{Lipschitz}(\textbf{hockey-stick} $h$) & \textbf{Indicator} $h$ & \textbf{VaR} & \textbf{CVaR} \\
-    \hline
-    Standard MC & $\star$ & $\star$($\checkmark$) & $\checkmark$ & $\checkmark$ & $\times$ \\
-    \hline
-    Multi-level MC & $\times$ & $\times$($\times$) & $\checkmark$ & $\times$ & $\times$ \\
-    \hline
-    Regression & $\checkmark$ & $\checkmark$($\checkmark$) & $\times$ & $\times$ & $\times$ \\
-    \hline
-    Kernel smoothing & $\checkmark$ & $\times$($\checkmark$) & $\checkmark$ & $\times$ & $\times$ \\
-    \hline
-    Kernel ridge regression & $\Diamond$ & $\times$($\Diamond$) & $\Diamond$ & $\Diamond$ & $\Diamond$ \\
-    \hline
-    Likelihood ratio & $\checkmark$ & $\times$($\checkmark$) & $\checkmark$ & $\times$ & $\times$ \\
-    \hline
-    \end{tabular}
-    \caption{Existing asymptotic convergence results of nested simulation procedures for MSE}
-\label{tab1:asymConv-mse}
-\end{table}
-
-Table~\ref{tab1:asymConv-mse} summarizes the existing asymptotic convergence results of nested simulation procedures for MSE in the literature.
-A $\checkmark$ indicates there exists an asymptotic convergence result for the corresponding estimator,
-a $\times$ indicates there does not exist an asymptotic convergence result, 
-a $\star$ indicates an asymptotic result is not available in the literature but is provided in this study, and
-a $\Diamond$ indicates that an asymptotic convergence result exists in the literature, though in a weaker form.
-~\cite{gordy2010nested} provide asymptotic convergence results for the standard nested simulation procedure with a hockey-stick $h$, an indicator $h$ and VaR.
-Their CVaR analysis is incomplete as the VaR is assumed to be known but not estimated in the convergence proof.
-When the VaR is known, the CVaR analysis reduces to the nested expectation form with $h$ being a hockey-stick function.
-~\cite{giles2019multilevel} provide asymptotic convergence results for the MLMC method with an indicator $h$.
-~\cite{broadie2015risk} provide asymptotic convergence results for the regression-based nested simulation procedure with a smooth $h$ and a Lipschitz continuous $h$.
-The Lipschitz continuous family includes the hockey-stick function as a special case, thus the convergence result for the hockey-stick function is implied.
-~\cite{hong2017kernel} and~\cite{zhang2022sample} provide asymptotic convergence results with the nested expectation form for the kernel smoothing-based procedure and likelihood ratio-based nested simulation procedure, respectively.
-The convergence results for a Lipschitz continuous $h$ cannot be directly inferred from the analysis for a hockey-stick function.
-
-While most of the literature focuses on the MSE of the estimator of $\rho$,~\cite{wang2022smooth} analyze the asymptotic convergence of the estimator of $\rho$ in terms of AE.
-Let $\hat{\rho}$ be the estimator of $\rho$. 
-Then the AE of $\hat{\rho}$ about $\rho$ is defined as
-
-$$
-\mbox{AE}\left(\hat{\rho}\right) = \left| \hat{\rho} - \rho \right|.
-$$
-
-In~\cite{wang2022smooth}, the authors of the KRR-based nested simulation procedures claim to have bridged the gap between the cubic and square root convergence rates of nested simulation procedures.
-However, they analyze convergence in probabilistic order, and it is only applicable in terms of AE.
-Instead of showing the convergence of the KRR-based estimator in terms of MSE as in~\cite{gordy2010nested}, we show the connections between the convergence in MSE and the convergence in probabilistic order for AE.
-Our findings in Section~\ref{sec1:connection-mse-absolute-error} show that the analysis of ~\cite{wang2022smooth} indeed bridges the gap, but only in terms of convergence in probabilistic order for AE.
-
-\subsection{Connections between Convergence in MSE and AE}\label{sec1:connection-mse-absolute-error}
+\begin{document}
+\maketitle
 
@@
 Hence, the converse of Theorem~\ref{thm1:convergence-mse-prob} is not necessarily true, and the convergence in probabilistic order is a weaker form of convergence than the convergence in MSE.
-The immediate implication of this result is that the results in~\cite{wang2022smooth}, which show the convergence in probabilistic order for the AE is not necessarily equivalent to the convergence in MSE.
 
-\subsection{Asymptotic Analysis for the Standard Nested Simulation Procedure}\label{sec1:sns}
-In~\cite{gordy2010nested}, the authors analyze the asymptotic convergence of the standard nested simulation procedure in terms of MSE. 
-The analysis is complete for the nested expectation form where $h$ is either an indicator function or a hockey-stick function and VaR. 
-For the nested expectation form where $h$ is a smooth function or a Lipschitz continuous function, the analysis is incomplete.
-In this section, we fill in the holes for the analysis of~\cite{gordy2010nested}.
-
-\begin{assumption}\label{as1:sns}
-    $h(L)$ has finite second moment, i.e., $\mathbb{E} \left[ \left( h(L) \right)^2 \right] < \infty$.
-\end{assumption}
-
-Assumption~\ref{as1:sns} is a standard assumption in the literature~\citep{hong2017kernel} for the analysis of nested simulation procedures to analyze the convergence of the variance of $\hat{\rho}_{M, N}$.
-
-\begin{assumption}\label{as1:sns-noise}
-    $\hat{L}_N(X) = L(X) + \bar{Z}_N(X)$, where the simulation noise $\bar{Z}_N(X)$ has zero mean and variance $\nu(X) / N$, and the conditional variance $\nu(X)$ is bounded, i.e., 
-    $$
-        \sup_{x \in \mathcal{X}} \nu(x) \leq C_{\nu, 1} < \infty.
-    $$
-\end{assumption}
-
-For simplicity, we abbreviate $\hat{L}_N(X)$ as $\hat{L}_N$, $\bar{Z}_N(X)$ as $\bar{Z}_N$, and $\bar{Z}_{N, i}$ as $\bar{Z}_{N, i}$.
-Let $\rho_M = \frac{1}{M} \sum_{i=1}^M h(L_i)$ be a nested MC estimator with the true function $g$.
-The MSE of the standard nested simulation procedure can be decomposed into two ways.
-
-\begin{align}\label{eq1:mse-sns}
-    & \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] \nonumber \\
-    & \leq 2 \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho_M \right)^2 \right] 
-            + 2  \mathbb{E} \left[ \left(\rho_M - \rho \right)^2 \right]  \nonumber \\
-    & = 2 \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) -  \frac{1}{M} \sum_{i=1}^M h\left(L_i \right)  \right)^2\right] \nonumber \\
-    & ~~~~ + 2  \mathbb{E} \left[ \left(\frac{1}{M} \sum_{i=1}^M h\left(L_i \right) - \mathbb{E}\left[ h(L)\right] \right)^2 \right]  \nonumber \\
-    & = 2 \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) -  h\left(L_i \right)  \right)^2\right] + \frac{2}{M} \text{Var}(h(L)) \nonumber \\
-    & = 2 \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) -  h\left(L_i \right)  \right)^2\right] + \mathcal{O}(M^{-1}).
-\end{align}
-
-In Equation~\eqref{eq1:mse-sns}, the last equality follows from Assumption~\ref{as1:sns}.
-The analysis of the first term is different for smooth and Lipschitz continuous $h$. 
-We will analyze them separately below.
-
-Another way to decompose the MSE is a bias-variance decomposition as in~\cite{gordy2010nested}.
-
-\begin{align}\label{eq1:mse-sns2}
-    \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] 
-    & = \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \mathbb{E} \left[ \hat{\rho}_{M, N} \right] \right)^2 \right] + \left( \mathbb{E} \left[ \hat{\rho}_{M, N} \right] - \rho \right)^2 \nonumber \\
-    & = \text{Var}(\hat{\rho}_{M, N}) + \text{Bias}^2(\hat{\rho}_{M, N}),
-\end{align}
-where $\text{Var}(\hat{\rho}_{M, N})$ is variance of the estimator and $\text{Bias}(\hat{\rho}_{M, N})$ is bias of the estimator about $\rho$.
-For a smooth function $h$, both ways of decomposing the MSE lead to the same order of convergence.
-However, for a Lipschitz continuous function $h$, Equation~\eqref{eq1:mse-sns2} leads to a stronger order of convergence than Equation~\eqref{eq1:mse-sns}.
-In the following, we analyze the convergence of the standard nested simulation procedure for a smooth and a Lipschitz continuous $h$ by using both decomposition methods.
-Their critical assumptions and convergence results are summarized and compared.
-
-\subsubsection*{A Smooth Function $h$}
-\begin{assumption}\label{as1:sns-smooth}
-    The function $h$ has bounded first and second order derivative, i.e.,
-    \begin{align*}
-        \sup_{x \in \mathcal{X}} |h'(x)|  & \leq C_{h, 1} < \infty, \\
-        \sup_{x \in \mathcal{X}} |h''(x)| & \leq C_{h, 2} < \infty.
-    \end{align*}
-\end{assumption}
-
-Assumption~\ref{as1:sns-smooth} is similar to the smoothness assumption in~\cite{wang2022smooth}.
-Since $h$ is a smooth function, Taylor expansion can be applied to the first term in Equation~\eqref{eq1:mse-sns}.
-
-\begin{align}\label{eq1:taylor-sns}
-    & \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) -  h\left(L_i \right)  \right)^2\right] \nonumber \\
-    & = \mathbb{E} \left[ \left( \frac{1}{M} \sum_{i=1}^M h'\left( L_i \right) \left( \hat{L}_{N, i} - L_i \right) +  \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{L}_{N, i} - L_i \right)^2 \right)^2\right] \nonumber \\
-    & \leq 2 \underbrace{\mathbb{E} \left[ \left( \frac{1}{M} \sum_{i=1}^M h'\left( L_i \right) \left( \hat{L}_{N, i}- L_i \right) \right)^2\right]}_{S_1} \nonumber \\
-    & ~~~~ + 2 \underbrace{\mathbb{E} \left[ \left( \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{L}_{N, i} - L_i \right)^2 \right)^2\right]}_{S_2},
-\end{align}
-where the last inequality is due to $2ab \leq a^2 + b^2$ for any $a, b \in \mathbb{R}$. 
-The two terms on the right-hand side of Equation~\eqref{eq1:taylor-sns} are analyzed separately.
-We start with the first term $S_1$.
-
-\begin{align}\label{eq1:s1-sns}
-    S_1 
-    & = \mathbb{E} \left[ \left(\frac{1}{M} \sum_{i=1}^M h'\left( L_i \right) \left( \hat{L}_{N, i} - L_i \right) \right)^2 \right] \nonumber \\
-    & = \mathbb{E} \left[ \left(\frac{1}{M} \sum_{i=1}^M h'\left( L_i \right) \bar{Z}_{N, i} \right)^2 \right] \nonumber \\
-    & \leq C_1^2 \mathbb{E} \left[ \left(\frac{1}{M} \sum_{i=1}^M \bar{Z}_{N, i} \right)^2 \right] \nonumber \\
-    & = C_1^2 \mathbb{E} \left[ \frac{1}{M^2} \sum_{i=1}^M \sum_{j=1}^M \bar{Z}_{N, i} \bar{Z}_{N, j} \right] \nonumber \\
-    & = C_1^2 \mathbb{E} \left[ \frac{1}{M^2} \sum_{i=1}^M \bar{Z}_{N, i}^2 + \frac{1}{M^2} \sum_{i=1}^M \sum_{j \neq i}^M \bar{Z}_{N, i} \bar{Z}_{N, j} \right] \nonumber \\
-    & \leq  \frac{C_1^2 C_{\nu, 1}}{MN} = \mathcal{O}(M^{-1} N^{-1}),
-\end{align}
-where the last inequality in Equation~\eqref{eq1:s1-sns} is due to Assumption~\ref{as1:sns-noise}, independence of $X_i$ and $X_j$ for $i \neq j$, and the fact that the inner simulation noise has zero mean, i.e., $\mathbb{E} \left[ \bar{Z}_N \right] = 0$.
-It remains to analyze the second term $S_2$, where Assumption \ref{as1:sns-noise-var} is necessary to ensure the existence of the fourth moment of the simulation noise and the convergence of the second term.
-
-\begin{assumption}\label{as1:sns-noise-var}
-    The fourth moment of simulation noise $\bar{Z}_N(X)$ follows $\mathbb{E} \left[ \left( \bar{Z}_N(X) \right)^4 \right] = \nu_2(X) / N^2$, where $\nu_2(X)$ is bounded, i.e., there exists $C_{\nu,2} > 0$ such that $\nu_2(X) \leq C_{\nu,2}$ for all $x \in \mathbb{R}$.
-\end{assumption}
-
-\begin{align}\label{eq1:s2-sns}
-    S_2 & = \mathbb{E} \left[ \left( \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{L}^{\text{SL}}_{M, N}(X_i) - L_i \right)^2 \right)^2\right] \nonumber \\
-    & = \mathbb{E} \left[ \left(\frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \bar{Z}_{N, i}^2 \right)^2 \right] \nonumber \\
-    & \leq C_2^2 \mathbb{E} \left[ \left(\frac{1}{2M} \sum_{i=1}^M \bar{Z}_{N, i}^2 \right)^2 \right] \nonumber \\
-    & = C_2^2 \mathbb{E} \left[ \frac{1}{2M^2} \sum_{i=1}^M \sum_{j=1}^M \bar{Z}_{N, i}^2 \bar{Z}_{N, j}^2 \right] \nonumber \\
-    & = C_2^2 \mathbb{E} \left[ \frac{1}{2M^2} \sum_{i=1}^M \bar{Z}_{N, i}^4 + \frac{1}{2M^2} \sum_{i=1}^M \sum_{j \neq i}^M \bar{Z}_N^2(X_i) \bar{Z}_N^2(X_j) \right] \nonumber \\
-    & \leq  C_2^2 \left(\frac{ C_{\nu, 2} M}{2M^2N^2} + \frac{C_{\nu,1}^2M(M-1)}{2M^2N^2}\right) = \mathcal{O}(N^{-2}),
-\end{align}
-where the second inequality is due to Assumption~\ref{as1:sns-smooth}, and the last inequality follows from Assumption~\ref{as1:sns-noise-var} and the fact that $\hat{L}_N$ is a standard MC estimator of $L$.
-Combining Equation~\eqref{eq1:mse-sns},~\ref{eq1:taylor-sns},~\ref{eq1:s1-sns}, and~\ref{eq1:s2-sns}, we have
-
-\begin{equation}\label{eq1:mse-sns-smooth}
-    \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(M^{-1}) + \mathcal{O}(N^{-2}).
-\end{equation}
-
-Setting $M = \mathcal{O}(\Gamma^{2/3})$ and $N = \mathcal{O}(\Gamma^{1/3})$, we provide the same rate of convergence as obtained for other risk measures in~\cite{gordy2010nested}.
-However, we observe that Equation~\eqref{eq1:s1-sns} converges in the order of $\mathcal{O}(M^{-1}N^{-1})$.
-The cross term here is potentially problematic, as setting $N$ as a negative power of $M$ may result in Equation~\eqref{eq1:s1-sns} to be divergent.
-
-In order to avoid the cross term, we proceed to follow the bias-variance decomposition in Equation~\eqref{eq1:mse-sns2}.
-
-\begin{align}\label{eq1:bias-sns-smooth}
-    \text{Bias}(\hat{\rho}_{M, N})
-    & = \mathbb{E} \left[ \hat{\rho}_{M, N} \right] - \rho \nonumber \\
-    & = \mathbb{E} \left[ \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) \right] - \mathbb{E} \left[ h\left(L \right) \right]  \nonumber \\
-    & = \mathbb{E} \left[ h\left( \hat{L}_N \right) - h\left( L \right) \right] \nonumber \\
-    & = \mathbb{E} \left[h'\left( L \right) \left( \hat{L}_N - L \right) + \frac{1}{2} h''\left( z \right) \left( \hat{L}_N - L \right)^2 \right],
-\end{align}
-where the last equality follows from the Taylor expansion of the smooth function $h$.
-The first and second order Taylor expansion terms are analyzed separately in Equation~\eqref{eq1:bias-sns-smooth-Taylor1} and Equation~\eqref{eq1:bias-sns-smooth-Taylor2}.
-
-\begin{align}\label{eq1:bias-sns-smooth-Taylor1}
-    \mathbb{E} \left[ h'\left( L \right) \left( \hat{L}_N - L \right) \right]
-    & = \mathbb{E} \left[ h'\left( L \right) \left( \hat{L}_N - L \right) \right] \nonumber \\
-    & = \mathbb{E} \left[ \mathbb{E} \left[ h'\left( L \right) \left( \hat{L}_N - L \right)  | X \right] \right] \nonumber \\
-    & = \mathbb{E} \left[ h'\left( L \right) \mathbb{E} \left[ \hat{L}_N - L  | X \right] \right] = 0.
-\end{align}
-
-\begin{align}\label{eq1:bias-sns-smooth-Taylor2}
-    \mathbb{E} \left[ h''\left( z \right) \left( \hat{L}_N - L \right)^2 \right]
-    & \leq \mathbb{E} \left[ |h''\left( z \right)| \left( \hat{L}_N - L \right)^2 \right] \nonumber \\
-    & \leq C_{h,2} \mathbb{E} \left[ \left( \hat{L}_N - L \right)^2 \right] \nonumber \\
-    & = C_{h,2} \text{Var}(\hat{L}_N) = \mathcal{O}\left( N^{-1} \right).
-\end{align}
-
-It remains to analyze the variance term in Equation~\eqref{eq1:mse-sns2}.
-
-\begin{equation}\label{eq1:var-sns-smooth}
-    \text{Var}(\hat{\rho}_{M, N}) = \frac{1}{M} \text{Var}(h(\hat{L}_N)) = \mathcal{O}(M^{-1}).
-\end{equation}
-
-Equation~\eqref{eq1:var-sns-smooth} directly follows from Assumption~\ref{as1:sns} and the fact that $\hat{L}_N$ is a standard MC estimator of $L$.
-Combining Equation~\eqref{eq1:bias-sns-smooth-Taylor1},~\ref{eq1:bias-sns-smooth-Taylor2}, and~\ref{eq1:var-sns-smooth}, we are able to show the convergence order of the standard nested simulation procedure for a smooth function $h$ without the cross term as in Equation~\eqref{eq1:s1-sns}.
-
-\begin{theorem}\label{thm1:sns-smooth}
-    Let $h$ be a smooth function. 
-    MSE of the standard nested simulation procedure converges in order $\Gamma^{2/3}$, that is,
-    $$\mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(\Gamma^{-2/3}).$$
-\end{theorem}
-
-The proof techniques used in deriving Theorem~\ref{thm1:sns-smooth} is completely different from the one used in~\cite{gordy2010nested}.
-The analysis in~\cite{gordy2010nested} is based on the differentiablity of the joint density of $Y$ and the average inner simulation noise, which is difficult to verify in practice.
-Instead, we use a Taylor expansion of the smooth function $h$ to analyze the convergence of the standard nested simulation procedure.
-The critical assumption in our derivation is Assumption~\ref{as1:sns-noise-var}, which is necessary to ensure the existence of the fourth moment of the simulation noise and the convergence of $S_2$, the second order term in the Taylor expansion.
-Assumption~\ref{as1:sns-noise-var} is a moment condition that is easier to verify in practice than conditions on the joint density.
-As stated in Theorem~\ref{thm1:convergence-mse-prob}, the convergence in MSE automatically implies the convergence in probabilistic order.
-
-\begin{corollary}
-    Let $h$ be a smooth function. 
-    The AE of the standard nested simulation procedure converges in probabilistic order $\Gamma^{-1/3}$, that is,
-    $$\left| \hat{\rho}_{M, N} - \rho \right| = \mathcal{O}_\mathbb{P}(\Gamma^{-1/3}).$$
-\end{corollary}
-
-\subsubsection*{A Lipschitz Continuous Function $h$}
-We proceed to analyze the convergence for a Lipschitz continuous function $h$.
-For the CVaR analysis in~\cite{gordy2010nested}, the authors assume the knowledge of the corresponding VaR.
-Hence, the analysis of CVaR is not complete.
-Instead, the quantity that is being analyzed is the mean excess loss, which corresponds to $h$ being a hockey-stick function and belongs to the family of the Lipschitz continuous functions. 
-Here we present the convergence analysis for the whole family of the Lipschitz continuous functions, which includes the hockey-stick function as a special case.
-
-\begin{assumption}\label{as1:sns-lip}
-    The function $h$ is Lipschitz continuous. Hence, $|h(x_1) - h(x_2)| \leq K|x_1 - x_2|$ for some constant $K< \infty$.
-\end{assumption}
-Assumption~\ref{as1:sns-lip} is a standard assumption for analysis involving Lipschitz continuous functions, and it is also used in~\cite{broadie2015risk}.
-For the Lipschitz continuous case, the first term in Equation~\eqref{eq1:mse-sns} is analyzed differently.
-
-\begin{align}
-    \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) -  h\left(L_i \right)  \right)^2\right]    
-    & \leq \mathbb{E} \left[ \left( h\left( \hat{L}_N \right) -  h\left(L \right)  \right)^2\right]  \nonumber \\
-    & \leq K^2 \mathbb{E} \left[ \left( \hat{L}_N -  L  \right)^2\right] \nonumber \\
-    & = K^2 \mathbb{E} \left[ \left( \bar{Z}_{N}(X) \right)^2\right] = \mathcal{O}(N^{-1}),
-\end{align}
-where the first inequality follows from Cauchy-Schwarz inequality, the second equality follows from Assumption~\ref{as1:sns-lip}, and the last equality follows from Assumption~\ref{as1:sns-noise}.
-
-\begin{equation}
-    \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(M^{-1}) + \mathcal{O}(N^{-1})
-\end{equation}
-Setting $M = \mathcal{O}(\Gamma^{1/2})$ and $N = \mathcal{O}(\Gamma^{1/2})$, we provide a looser bound than the one obtained for the hockey-stick $h$.
-Using the bias-variance decomposition in Equation~\eqref{eq1:mse-sns2}, we obtain the following bias term.
-
-\begin{align}\label{eq1:bias-sns-lip}
-    \text{Bias}(\hat{\rho}_{M, N})
-    & = \mathbb{E} \left[ \hat{\rho}_{M, N} \right] - \rho \nonumber \\
-    & = \mathbb{E} \left[ \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) \right] - \mathbb{E} \left[ h\left(L \right) \right]  \nonumber \\
-    & = \mathbb{E} \left[ h\left( \hat{L}_N \right) - h\left( L \right) \right] \nonumber \\
-    & \leq \mathbb{E} \left[ |h\left( \hat{L}_N \right) - h\left( L \right) | \right] \nonumber \\
-    & \leq K \mathbb{E} \left[ |\hat{L}_N - L| \right] \nonumber \\
-    & = K \mathbb{E} \left[ |\bar{Z}_N| \right] \nonumber \\
-    & \leq K \sqrt{\mathbb{E} \left[ \left( \bar{Z}_N \right)^2 \right]} = \mathcal{O}(N^{-1/2}).
-\end{align}
-
-The variance term in Equation~\eqref{eq1:mse-sns2} for Lipschitz continuous $h$ is identical to the one in Equation~\eqref{eq1:var-sns-smooth}.
-
-\begin{equation}
-    \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(M^{-1}) + \mathcal{O}(N^{-1}).
-\end{equation}
-
-Setting $M = \mathcal{O}(\Gamma^{2/3})$ and $N = \mathcal{O}(\Gamma^{1/3})$, we provide the same rate of convergence as obtained for other risk measures in~\cite{gordy2010nested}.
-
-\begin{theorem}
-    Let $h$ be a Lipschitz continuous function. 
-    MSE of the standard nested simulation procedure converges in order $\Gamma^{2/3}$, that is,
-    $$\mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(\Gamma^{-1/2}).$$
-\end{theorem}
-
-Immediately from Theorem~\ref{thm1:convergence-mse-prob}, the convergence in MSE automatically implies the convergence in probabilistic order.
-
-\begin{corollary}
-    Let $h$ be a Lipschitz continuous function. AE of the standard nested simulation procedure converges in probabilistic order $\Gamma^{-1/3}$, that is,
-    $$\left| \hat{\rho}_{M, N} - \rho \right| = \mathcal{O}_\mathbb{P}(\Gamma^{-1/4}).$$
-\end{corollary}
-
-\subsection{Asymptotic Analysis of a kNN-based Nested Simulation Procedure for a Smooth Function}
-
-In~\cite{hong2017kernel}, the authors analyze the asymptotic convergence in terms of MSE for a kernel smoothing-based nested simulation procedure.
-The analysis is complete for the nested expectation form where $h$ is either a smooth function, an indicator function, or a hockey-stick function.
-The kernel function of interest in the asymptotic analysis is the Nadaraya-Watson kernel.
-Nevertheless, the numerical results are derived based on a kNN-based nested simulation procedure.
-In this section, we attempt to fill in the holes in the analysis of~\cite{hong2017kernel} by providing asymptotic convergence of a kNN-based nested simulation procedure for smooth $h$ in the nested expectation form.
-Surprisingly, the asymptotic convergence rate of the kNN-based nested simulation procedure is noticeably different from the result obtained in~\cite{hong2017kernel}.
-
-A kNN regression can be used as a non-parametric metamodel that estimates the conditional expectation of $Y$ given $X$ by averaging the $Y$ values of the $k$ nearest neighbors of $X$.
-Without loss of generality, we assume that $\{(X_i, \bar{Y}_{n, i}), i = 1, \dots, M\}$ are i.i.d.
-observations of $(X, Y)$ from the standard nested simulation procedure with an inner simulation budget of $n$, where $X_i$ is the $i^{\text{th}}$ of the outer scenario $X \in \Omega \subset \mathbb{R}^d$, and $\bar{Y}_{n, i}$ is an estimate of $Y|X_i$ with an inner simulation budget of $n$.
-Let $f_{XY}(x, y)$ be a joint density of random vector $(X, Y)$, and $f_X(x) = \int f_{XY}(x, y) dy$ be a marginal density of $X$.
-Let $k$ be a sequence of positive integers $k = k(M)$ such that 
-\begin{align*}
-    k                   & \to \infty, \\
-    \frac{k}{M}         & \to 0, ~~~ \text{as} ~ M \to \infty, \\
-    \frac{\log(M)}{k}   & \to 0, ~~~ \text{as} ~ k \to \infty.
-\end{align*}
-
-A kNN-based nested simulation procedure with a model parameter $k$ estimates the risk measure $\rho = \mathbb{E} \left[ h(L) \right]$ with
-
-\begin{equation*}
-    \hat{L}^{\text{kNN}}_{M, N}(x) 
-    = \frac{\frac{1}{M R_M^d} \sum_{i=1}^M \hat{L}_{N, i} K\left(\frac{x - X_i}{R_M}\right)}{\frac{1}{M R_M^d} \sum_{i=1}^M K\left(\frac{x - X_i}{R_M}\right)}
-    \end{equation*}
-    where $R_k$ is a Euclidean distance between $X_i$ and its $k$-th nearest neighbor, and $K:\mathbb{R}^d \mapsto \mathbb{R}$ is a bounded, nonnegative kernel function satisfying 
-    \begin{align*}
-        \int K(u) du & = 1, \\
-        K(u) &= 0 ~~~ ~\text{for}~ \|u\| \geq 1,
-    \end{align*}
-where $\|\cdot\|$ is a Euclidean norm, and $k$ is a number of nearest neighbors to consider.
-For a kNN estimator trained with $M$ i.i.d. observations, denote $B_M(x)$ and $V_M(x)$ as its bias and variance at point $x$, respectively.
-
-\begin{assumption}\label{as1:knn}
-    $f_X$ is bounded and continuously differentiable up to a second order in a neighborhood of $x$ with $f_X(x) > 0$, $f_X$, $\mathbb{E} \left[ Y^2| X = x \right] < \infty$, and the kernel function $K$ satisfies
-    \begin{align*}
-        \int \|u\|^2  |K(u)| du & < \infty, \\
-        \int \nu_\alpha K(u) du & = 0, ~~~ \text{for}~ \alpha = 1, \dots, d.
-    \end{align*}
-    Suppose that $\mathbb{P}(\|x - X\| > r) = \mathcal{O}(r^{-\alpha})$ for some $\alpha > 0$ as $r \to \infty$.
-\end{assumption}
-
-The following lemma from~\cite{mack1981local} characterizes pointwise convergence of the kNN estimator in terms of its bias and variance at point $x$.
-
-\begin{lemma}
-    Assume that a random vector $(X, Y)$ and a kernel function $K$ satisfies Assumption~\ref{as1:knn}. Then the bias and variance of the kNN estimator at point $x$ are given by
-    \begin{align*}
-        B_M(x) & = A_{\text{kNN}}(x) \cdot \left( \left( \frac{k}{M} \right)^\frac{2}{d} + o \left( \frac{k}{M} \right)^\frac{2}{d} \right) + B_{\text{kNN}} \cdot \left(\frac{1}{k} + o\left(\frac{1}{k}\right)\right), \\
-        V_M(x) & = \frac{C_{kNN} \cdot \text{Var}[Y| X = x]}{k} \int K^2(u) du + o\left(\frac{1}{k}\right).
-    \end{align*}
-\end{lemma}
-
-Let $h$ be a smooth function, i.e., Assumption~\ref{as1:sns-smooth} holds.
-The bias of the estimator of $\rho$ for a kNN-based nested simulation procedure is analyzed following a Taylor expansion.
-\begin{align}\label{eq1:bias-knn}
-    & \mathbb{E} \left[ h(\hat{L}^{\text{kNN}}_{M, n}(X)) - h(L) \right] \nonumber \\
-    & = \mathbb{E} \left[ h'(L) \left( \hat{L}^{\text{kNN}}_{M, n}(X) - L \right) + \frac{1}{2} h''(z) \left( \hat{L}^{\text{kNN}}_{M, n}(X) - L \right)^2 \right],
-\end{align}
-where the bias is decomposed into two terms, and $z$ is between $\hat{L}^{\text{kNN}}_{M, n}(X)$ and $L$.
-The first term in Equation~\eqref{eq1:bias-knn} is 
-\begin{align}\label{eq1:bias-knn-1}
-    & ~~~~ \mathbb{E} \left[ h'(L) \left( \hat{L}^{\text{kNN}}_{M, n}(X) - L \right) \right]  \nonumber \\
-    & = \mathbb{E} \left[ h'(L) \mathbb{E}\left[ \hat{L}^{\text{kNN}}_{M, n}(X) - L |X\right] \right] \nonumber \\
-    & = \int_{\Omega} h'(L) B_M(x) f_X(x) dx \nonumber \\
-    & = \int_{\Omega} h'(L) \left( A_{\text{kNN}}(x) \left(\frac{k}{M}\right)^{2/d} \left(1+o_x(1)\right) + B_{\text{kNN}} \cdot \left(\frac{1}{k} + o_x\left(\frac{1}{k}\right)\right) \right) f_X(x) dx \nonumber \\
-    & = \left(\frac{k}{M}\right)^{2/d} \mathbb{E} \left[ h'(L) A_{\text{kNN}}(X) \right] (1+ o(1)) + \frac{B_{\text{kNN}}}{k} \mathbb{E} \left[ h'(L) \right] (1+ o(1)).
-\end{align}
-
-The second term in Equation~\eqref{eq1:bias-knn} is 
-\begin{align}\label{eq1:bias-knn-2}
-    & ~~~~ \mathbb{E} \left[ h''(z) \left( \hat{L}^{\text{kNN}}_{M, n}(X) - L \right)^2 \right]  \nonumber \\
-    & = \int_{\Omega} h''(z) \left(B_M^2(X) + V_M(x)\right) f_X(x) dx \nonumber \\
-    & \leq C_2 \int_{\Omega} \left( \frac{C_{\text{kNN}} \cdot \text{Var}[Y| X = x]}{k} \int K^2(u) du + o\left(\frac{1}{k}\right) \right) f_X(x) dx \nonumber \\
-    & + C_2 \int_{\Omega} \left( A_{\text{kNN}}(x) \left(\frac{k}{M}\right)^{2/d} \left(1+o_x(1)\right) + B_{\text{kNN}} \cdot \left(\frac{1}{k} + o_x\left(\frac{1}{k}\right)\right) \right)^2 f_X(x) dx,
-\end{align}
-where the second term in Equation~\eqref{eq1:bias-knn-2} is of higher order than Equation~\eqref{eq1:bias-knn-1}, and it is negligible since $kM^{-1} \to 0$ as $M \to \infty$ and $k \to \infty$, 
-The first term in Equation~\eqref{eq1:bias-knn-2} is $\mathcal{O}\left(\frac{1}{k}\right)$.
-Set $k = \mathcal{O}(M^{\frac{2}{2+d}})$ and $M = \mathcal{O}(\Gamma)$, the bias of the kNN-based nested simulation procedure converges in the order of $\Gamma^{-\frac{2}{2+d}}$.
-
-\begin{definition}\label{def:knn-smooth-bias}
-    Let $h$ be a smooth function. 
-    The bias of the kNN-based nested simulation procedure converges in the order of $\Gamma^{-\frac{2}{2+d}}$, that is,
-    $$ \mathbb{E} \left[ h(\hat{L}^{\text{kNN}}_{M, n}(X)) - h(L) \right]  = \mathcal{O}(\Gamma^{-\frac{2}{2+d}}).$$
-\end{definition}
-
-Definition~\ref{def:knn-smooth-bias} is obtained by matching the orders of the bias terms in Equation~\eqref{eq1:bias-knn-1} and~\ref{eq1:bias-knn-2}.
-It is the tightest bound that can be obtained for the convergence of the kNN-based nested simulation procedure with a smooth function $h$.
-The variance is left for future work.
-It implies that the kNN-based nested simulation procedure converges at most in the order of $\Gamma^{-\frac{2}{3}}$ for $d = 1$ and has slower convergence than the standard procedure for $d \geq 2$.
-Asymptotically, it has slower convergence than the result obtained in~\cite{hong2017kernel} for the Nadaraya-Watson kernel.
-This discrepancy underscores the critical importance of aligning theoretical analysis with numerical illustrations.
-The slower convergence rate observed with the kNN approach not only challenges the robustness of empirical findings derived under differing assumptions but also signals a cautionary note for practitioners.
-This alignment is crucial for ensuring the reliability and validity of conclusions drawn from such procedures, especially in the context of risk management and financial decision-making.
-
-\section{Convergence Orders and Critical Assumptions of Nested Simulation Procedures}
-\label{sec1:convergence-orders}
-
-In this section, we summarize the convergence orders and the critical assumptions of the nested simulation procedures.
-The results are summarized in~\ref{tab1:asymConv-order}, where the orders of convergence are presented in the order of the total simulation budget $\Gamma$.
-
-\begin{table}[ht]
-    \centering
-    \tiny
-    \begin{tabular}{|l|c|c|c|c|c|}
-    \hline
-    \textbf{Estimator for} $L$ & \textbf{Smooth} $h$ & \textbf{Lipschitz} / \textbf{hockey-stick} $h$ & \textbf{Indicator} $h$ & \textbf{VaR} & \textbf{CVaR} \\
-    \hline
-    Standard MC & $\mathcal{O}(\Gamma^{-2/3})$ & $\mathcal{O}(\Gamma^{-1/2})$ / $\mathcal{O}(\Gamma^{-2/3})$ & $\mathcal{O}(\Gamma^{-2/3})$ & $\mathcal{O}(\Gamma^{-2/3})$ & $\times$ \\
-    \hline
-    Multi-level MC & $\times$ & $\times$ / $\times$ & $\mathcal{O}(\Gamma^{-1}|\log(\Gamma)|
-    )$ & $\times$ & $\times$ \\
-    \hline
-    Regression & $\mathcal{O}(\Gamma^{-1})$ & $\mathcal{O}(\Gamma^{-1})$/$\mathcal{O}(\Gamma^{-1})$ & $\times$ & $\times$ & $\times$ \\
-    \hline
-    Kernel smoothing & $\mathcal{O}(\Gamma^{-\min\{1, \frac{4}{d+2}\}})$ & $\times$ / $\mathcal{O}(\Gamma^{-\min\{1, \frac{4}{d+2}\}})$ & $\mathcal{O}(\Gamma^{-\min\{1, \frac{4}{d+2}\}})$ & $\times$ & $\times$ \\
-    \hline
-    Kernel ridge regression & $\mathcal{O}(\Gamma^{-1})$ & $\times$ / $\mathcal{O}(\Gamma^{-1})$ & $\mathcal{O}(\Gamma^{-1})$ & $\mathcal{O}(\Gamma^{-1})$ & $\mathcal{O}(\Gamma^{-1})$ \\
-    \hline
-    Likelihood ratio & $\mathcal{O}(\Gamma^{-1})$ & $\times$ / $\mathcal{O}(\Gamma^{-1})$ & $\mathcal{O}(\Gamma^{-1})$ & $\times$ & $\times$ \\
-    \hline
-    \end{tabular}
-    \caption{Asymptotic rate of convergence of nested simulation procedures in MSE}
-\label{tab1:asymConv-order}
-\end{table}
-
-The asymptotic convergence rate of the nested simulation procedures is highly dependent on the assumptions on the random variable $X$, $Y$, and the inner simulation noise.
-As more advanced supervised learning techniques are used to estimate the function $g$, a more restrictive set of assumptions is required to ensure the asymptotic convergence of the inner estimators.
-In this section, we summarize the pivotal assumptions regarding the random variables and the inner simulation noise for all nested simulation procedures. 
-They are presented in an order reflecting their relative ease in satisfying the assumptions.
-
-\subsection{Standard Assumptions}
-~\cite{gordy2010nested} and~\cite{broadie2015risk} assume that the inner simulation noise has zero mean and variance that is inversely proportional to the inner simulation budget $N$, i.e., Assumption~\ref{as1:sns-noise}.
-The analysis in~\cite{gordy2010nested} further requires assumptions on $f_{Y,\tilde{Z}_N}(y,z_N)$, a joint density of random variable $Y$ and the normalized inner simulation noise $\tilde{Z}_N := \sqrt{N} \cdot\bar{Z}_N(X)$.
-
-\subsection{Assumptions on Joint Density}
-
-\begin{assumption}\label{as1:sns-joint-density}
-    The joint density $f_{Y,\tilde{Z}_N}(y,z_N)$ and its partial derivatives 
-    $\frac{\partial f_{Y,\tilde{Z}_N}(y,z_N)}{\partial y}$ and $\frac{\partial^2 f_{Y,\tilde{Z}_N}(y,z)}{\partial y^2}$ exist.
-\end{assumption}
-
-\begin{assumption}\label{as1:sns-joint-density-bound}
-    For $N \geq 1$, there exist non-negative functions $p_{0, N}(\cdot)$, $p_{1, N}(\cdot)$, and $p_{2, N}(\cdot)$ such that for all $y$ and $z$,
-    \begin{align*}
-        f_{Y,\tilde{Z}_N}(y,z) & \leq p_{0, N}(z) \\
-        \left| \frac{\partial f_{Y,\tilde{Z}_N}(y,z)}{\partial y} \right| & \leq p_{1, N}(z) \\
-        \left| \frac{\partial^2 f_{Y,\tilde{Z}_N}(y,z)}{\partial y^2} \right| & \leq p_{2, N}(z).
-    \end{align*}
-    In addition, 
-    \begin{equation}
-        \sup_N \int_{-\infty}^{\infty} |z|^r p_{i, N}(z) dz < \infty
-    \end{equation}
-    for $i = 0, 1, 2$ and $r \in [0, 4]$.
-\end{assumption}
-
-Assumption~\ref{as1:sns-joint-density} and~\ref{as1:sns-joint-density-bound} are necessary for the Taylor expansion up to the second order on the joint density $f_{Y,\tilde{Z}_N}(y,z_N)$, and they can easily be satisfied by perturbing $Y$ and $\tilde{Z}_N$ with a zero-mean normal random variable with a small variance.
-However, Assumption~\ref{as1:sns-joint-density-bound} is hard to be verified in practice.
-Since~\cite{broadie2015risk} only analyze the nested expectation case with a smooth and a Lipschitz continuous function $h$, the regression-based nested simulation procedure does not require Assumptions~\ref{as1:sns-joint-density} and~\ref{as1:sns-joint-density-bound} for the convergence analysis.
-In our analysis of the standard nested simulation procedure for a smooth function $h$ in the nested expectation form, we make additional assumptions on the fourth moment of the inner simulation noise, i.e., Assumption~\ref{as1:sns-smooth}, so that the second-order term in the Taylor expansion can be bounded.
-
-\subsection{Assumptions for the MLMC Procedure}
-In addition to Assumption~\ref{as1:sns-joint-density-bound}, the MLMC procedure requires assumptions on the random variable $Q:= \frac{|\mathbb{E} \left[ Y | X \right]|}{\text{Var}[Y|X]}$.
-
-\begin{assumption}\label{as1:mlmc-q}
-    $f_Q$, the density of $Q$ exists, and there exist positive constants $q_0$ such that $f_Q(q) \leq q_0$ for all $q \in [0, q_0]$.
-\end{assumption}
-
-Assumption~\ref{as1:mlmc-q} ensures that the conditional expectation of $Y$ given $X$ is not concentrated around zero, as ~\cite{giles2019multilevel} show the asymptotic convergence of the MLMC procedure only when $\rho$ is in the nested expectation form with $h$ being an indicator function, i.e., $h(x) = \mathbb{I}_{\{x \geq 0\}}$.
-
-\subsection{Assumptions for the Likelihood Ratio-Based Procedure}
-In addition to Assumption~\ref{as1:sns-joint-density-bound}, the likelihood ratio-based nested simulation procedure requires assumptions on the marginal density of $H$, the random variable that characterizes the stochasticity of the inner simulation model.
-More specifically, for the likelihood ratio-based nested simulation procedure, the random variable $H$ is introduced to represent the inner simulation noise, and $Y$ can be directly expressed as a function of $H$ and $X$, i.e., $Y = Y(H, X)$.
-Instead of simulating $Y$ directly, the random variable $H$ is simulated from the conditional distribution $f_{H|X}(y|x)$, and $Y$ is then obtained by evaluating $Y(H, X)$.
-
-\begin{assumption}\label{as1:likelihood-ratio-marginal-density}
-    The marginal density $f_H(y)$ of $H$ exists. $f_H(y)$ can be sampled and evaluated, and $Y(y, x) f_{H|X}(y|x) = 0$ whenever $f_H(x) = 0$. 
-\end{assumption}
-
-Furthermore, the likelihood ratio-based nested simulation procedure requires the samples of $H$ to be independent with the outer scenario $X$.
-
-\begin{assumption}\label{as1:likelihood-ratio-independence}
-    The inner sample $H \sim f_H(y)$ is independent of $X$. Samples $\{X_i, i=1,\ldots,M\}$ and $\{H_i, i=1,\ldots,N\}$ are i.i.d. samples from $f_X(x)$ and $f_H(y)$, respectively.
-\end{assumption}
-
-Assumption~\ref{as1:likelihood-ratio-independence} is necessary for $\hat{L}^{\text{LR}}_N(X_i)$ to be an unbiased and strongly consistent estimator of $L_i$, which is a necessary condition for the convergence of $\hat{\rho}^{\text{LR}}_{M,N}$, the likelihood ratio-based nested simulation estimator of $\rho$.
-Assumption~\ref{as1:likelihood-ratio-marginal-density} and Assumption~\ref{as1:likelihood-ratio-independence} are likely to be satisfied in practice, as one can simulate $H$ separately from $X$ and evaluate $Y(H, X)$ for each pair of $(H, X)$.
-
-\subsection{Assumptions for the Kernel-Based Procedure}
-For the kernel-based nested simulation procedure,~\cite{hong2017kernel} simplifies the analysis by assuming that for each $X_i$, the inner simulation budget $N$ is fixed together with the variance of the inner simulation noise $\bar{Z}_{N, i}$.
-In essence, this fixed variance design treats the $(X_i, \bar{Y}_{N, i})$ as i.i.d.
-observations of $(X, Y)$, and the kernel-based nested simulation procedure is analyzed as a non-parametric regression problem.
-Regularity conditions on $f_X(x)$, the density of $X$, and the conditional second moment of $Y$ are assumed to ensure the convergence of $\hat{L}^{\text{KS}}_{M, N}(X)$, the kernel smoothing estimator of $L$.
-
-\begin{assumption}
-    $f_X(x)$ and $\mathbb{E} \left[ Y^2 | X = x \right]$ exist, $f(x) > 0$, and $f(x)$ is thrice continuously differentiable at $x$ with bounded third-order derivative.
-\end{assumption}
-
-Further assumptions are made on the kernel function $K_w$ and the bandwidth $w$ to ensure the convergence of the kernel smoothing estimator $\hat{L}^{\text{KS}}_{M, N}(X)$.
-A similar set of assumptions is made in~\cite{jennen1988unifying} for the convergence analysis of a kernel smoothing estimator with kernel functions of higher orders.
-
-\subsection{Assumptions for the KRR-Based Procedure}
-For the KRR-based nested simulation procedure, the convergence is guaranteed only when $\bar{Z}_N(X)$ is the sum of $N$ i.i.d. zero-mean sub-Gaussian random variables.
-The sub-Gaussian assumption imposes a stronger condition on the inner simulation noise than all the other nested simulation procedures.
-The inner simulation noise is assumed to have lighter tails than the normal distribution, while examples of random variables that satisfy the sub-Gaussian assumption are hard to find.
-In addition, the following assumptions are made on $\Omega$, which is the domain of the outer scenario $X$:
-
-\begin{assumption}\label{as1:krr-domain}
-    $\Omega$ is a bounded subset of $\mathbb{R}^d$, and $f_X(x)$ is bounded above and below away from zero.
-\end{assumption}
-
-Assumption~\ref{as1:krr-domain} rules out the possibility of the outer scenario $X$ being a normal random variable, which is a common assumption in the literature.
-Furthermore, the convergence analysis of the KRR-based nested simulation procedure is shown in terms of AE rather than in MSE, which is due to the complexity of the KRR metatmodel.
-
-\section{Finite-Sample Experiments}\label{sec1:numerical-experiments}
-The theoretical framework has lent itself for a comparison of the asymptotic convergence behavior for different nested simulation procedures.
-However, a simulation budget in practice is almost always finite.
-In this section, we conduct a series of numerical experiments to compare the empirical convergence of the nested simulation procedures for different risk measures, option types, and asset dimensions.
-Numerical experiments are conducted on portfolios that consist of options on $d$ underlying assets, whose dynamics follow a multidimensional geometric Brownian motion with $0.3$ pairwise correlation.
-\textcolor{red}{The initial values of the assets are set to be $100$.}
-\textcolor{red}{The drifts are set to be $0.08$, and the risk free rate is set to be $0.05$.}
-
-A total of 5 nested simulation procedures are considered, namely a standard nested simulation procedure, a  regression-based, a kernel smoothing-based, a likelihood ratio-based, and a kernel ridge regression-based nested simulation procedure.
-For the standard nested simulation procedure, the bootstrap-based budget allocation strategy from~\cite{zhang2021bootstrap} is implemented to estimate the optimal values of outer and inner simulation budgets.
-For the regression metamodel, the Laguerre polynomials up to degree $3$ are used as the default basis functions.
-The kNN metamodel is implemented for the kernel smoothing-based procedure, and a cross-validation procedure with a grid search is used to find the optimal number of neighbors.
-The KRR metamodel is implemented with a Mat\'ern kernel, and the smoothness, the length scale, and the regularization hyperparameters are found by a cross-validation procedure with a Bayesian search~\citep{frazier2018bayesian}.
-Due to budget constraints, the hyperparameters of the non-parametric regression metamodel are tuned and used across all macro replications of the same experiment.
-
-The procedures are compared for 5 types of risk measures:
-\begin{itemize}
-    \item a quadratic tracking error,
-    \item a mean excess loss over a threshold $u$,
-    \item a probability of a large loss over a threshold $u$,
-    \item the VaR, and
-    \item the CVaR,
-\end{itemize}
-where the threshold $u$ for the mean excess loss and the probability of a large loss is set to be 90\% VaR.
-The procedures are compared for different portfolios consisting of different types of options:
-\begin{itemize}
-    \item   Portfolio 1 consists of $d$ assets.
-    This portfolio contains 3 European call options written on each asset with strikes $90$, $100$, and $110$, respectively. 
-    \item   Portfolio 2 consists of $d$ assets.
-    This portfolio contains 3 geometric Asian options written on each asset with strikes $90$, $100$, and $110$, respectively. 
-    \item   Portfolio 3 consists of $d$ assets.
-    This portfolio contains 3 up-and-out barrier call options written on each asset with strikes $90$, $100$, and $110$, respectively. They have a barrier level of $120$.
-    \item   Portfolio 4 considers $d$ assets.
-    This portfolio contains 3 down-and-out barrier call options written on each asset with strikes $90$, $100$, and $110$, respectively. They have a barrier level of $90$.
-    \item   Portfolio 5 contains 1 asset.
-    This portfolio longs 2 down-and-out barrier put options and shorts 1 barrier down-and-out put option. 
-\end{itemize}
-Except for Portfolio 5, 5 different asset dimensions are considered, i.e., $d = 1, 2, 5, 10, 20$.
-\textcolor{red}{All options have a maturity of $1$ year, and we are interested in the value of the portfolio at time $3/50$ year from now.}
-525 experiment settings that arise from an exhaustive combination of the above simulation procedures, risk measures, portfolios, and asset dimensions are generated.
-For each experiment setting, the estimation of the risk measure is repeated \num{1000} times to obtain the empirical MSE of the corresponding estimator under a range of simulation budgets.
-The total simulation budget $\Gamma$ ranges from $\num{10000}$ to $\num{10240000}$ in a geometric progression with a common ratio of $2$.
-The empirical convergence results of each estimator are measured and recorded to illustrate their empirical behavior under different risk measures, option types, and asset dimensions.
-\textcolor{red}{All numerical experiments are conducted on a linux server with four Intel Xeon Gold 6230 20-core 2.1 GHz CPU with 768 GB RAM.}
-
-We start by examining the empirical convergence results for the most basic case, i.e., a quadratic tracking error risk measure for European call options on Portfolio 1 with $d = 1$.
-
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=0.7\textwidth]{./project1/figures/figure1.png}
-    \caption{Empirical convergence of nested simulation procedures for quadratic tracking error on Portfolio 1 with $d=1$}
-\label{fig1:compareAll} 
-\end{figure}
-In Figure~\ref{fig1:compareAll}, the MSEs of the nested simulation procedures are plotted against the total simulation budget $\Gamma$ in a log-log scale, where each point represents the average MSE of the corresponding estimator over \num{1000} macro replications of the same experiment.
-Due to the difficulty of fixing $\Gamma$ for the MLMC procedure, the empirical rate of convergence of the MLMC procedure is not reported here, but a detailed analysis of the empirical convergence of the MLMC procedure is provided in Section~\ref{sec1:empirical-mlmc}.
-
-A regression line is fitted to the MSEs of each nested simulation procedure against the simulation budget $\Gamma$ in a log-log scale, and the slope of the fitted line is reported.
-The slopes of the fitted lines can be interpreted as the empirical rates of convergence.
-Alongside in the parentheses are the asymptotic rates of convergence obtained by the theoretical analysis in Section~\ref{sec1:asymptotic-convergence}.
-By comparing the empirical rates of convergence with the asymptotic rates, we can observe how well the empirical rates of convergence match their asymptotic rates.
-In the case illustrated in Figure~\ref{fig1:compareAll}, the empirical rates of all procedures closely match their asymptotic rates.
-
-Except for the standard nested simulation procedure, the empirical rates of convergence of the other procedures are close to $\Gamma^{-1}$, i.e., all of them achieve similar finite-sample performance that is better than the standard procedure.
-Pooling of inner simulation samples across different outer scenarios is the key reason behind their higher empirical rates of convergence.
-However, pooling also introduces additional computational cost that is not reflected in the simulation budget $\Gamma$.
-Due to the computational complexity of the likelihood ratio-based and the KRR-based procedures, their MSEs are not reported for $\Gamma$ larger than $\num{16000}$ and $\num{64000}$, respectively.
-Detailed discussion of the additional computational cost of pooling is provided in Section~\ref{sec1:computational-complexity}.
-
-In the following sections, we examine the empirical convergence of the nested simulation procedures similarly as in Figure~\ref{fig1:compareAll}.
-With a more detailed analysis of different risk measures, option types, and asset dimensions, we aim at providing a comprehensive understanding and comparison of the convergence behavior of the nested simulation procedures in practice.
-
-\subsection{Sensitivity to the Asset Dimension}\label{sec1:sensitivity-dimension}
-In portfolio risk management, the asset dimension is a critical factor that determines the complexity of the portfolio and the computational cost of the risk measure estimation.
-The theoretical analyses in Section~\ref{sec1:convergence-orders} suggest that the asymptotic rate of convergence of the nested simulation procedures, except for the kernel smoothing-based procedure, is independent of the asset dimension.
-However, in practice, their empirical convergence behavior could be different.
-In this section, we examine the sensitivity to the asset dimension of the empirical convergence of the nested simulation procedures.
-
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure2a.png}
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure2b.png}
-    \caption{Empirical convergence of nested simulation procedures for quadratic tracking error on Portfolio 1 with different asset dimensions}
-\label{fig1:assetDimension} 
-\end{figure}
-
-In Figure~\ref{fig1:assetDimension}, the empirical convergence of the nested simulation procedures for a quadratic tracking error on Portfolio 1 is illustrated for different asset dimensions, i.e., $d = 2$ and $d = 20$.
-The empirical rates of convergence of the standard, the KRR-based, and the likelihood ratio-based procedures closely match their asymptotic rates for both asset dimensions, and they are insensitive to an increase in the asset dimension.
-In contrast, both the kernel smoothing-based and regression-based procedures are greatly affected by the asset dimension.
-Their sensitivities to the asset dimension differ in finite-sample experiments:
-\begin{itemize}    
-    \item For the kernel smoothing-based procedure, the empirical rate of convergence decreases as the asset dimension increases. 
-    This observation aligns with the theoretical analysis in Section~\ref{sec1:asymptotic-convergence}, which demonstrates that the asymptotic rate of convergence of the kernel smoothing-based procedure is sensitive to the asset dimension.
-    Nevertheless, even for $d = 2$ and $d = 20$, the empirical rate remains higher than its asymptotic rate.
-    \item For the regression-based procedure, the asymptotic rate is not affected by the asset dimension, but the empirical rates of convergence are higher than the asymptotic rates for both asset dimensions, and the empirical rate is higher for $d = 20$ than for $d = 2$.
-\end{itemize}
-In the following sections, we provide detailed explanations for the discrepancy between their empirical rates of convergence and their asymptotic rates.
-
-\subsection{Empirical Convergence of Kernel Smoothing-Based Procedures}\label{sec1:kernel-smoothing-convergence}
-
-Kernel smoothing is a non-parametric regression metamodel.
-According to the theoretical analysis in Section~\ref{sec1:asymptotic-convergence}, the asymptotic rate of convergence of the kernel smoothing-based nested simulation procedure is highly dependent on the asset dimension $d$.
-In this section, we use a kNN metamodel for the kernel smoothing-based nested simulation procedure, and we examine its empirical convergence for different asset dimensions.
-
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure4a.png}
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure4b.png}
-    \caption{Empirical convergence of kernel smoothing procedure for different values of $d$}
-\label{fig1:kernel_d} 
-\end{figure}
-
-In Figure~\ref{fig1:kernel_d}, the empirical convergence of the kernel smoothing-based nested simulation procedure for a quadratic tracking error is illustrated for different asset dimensions, i.e., $d = 1, 2, 5, 10$.
-The experiment finds that the kernel smoothing-based nested simulation procedure is extremely sensitive to the asset dimension and the payoff structure.
-While the asset dimension is expected to be a critical factor as shown in the theoretical analysis, the payoff structure is an unexpected factor that affects the empirical convergence of the kernel smoothing-based nested simulation procedure.
-For a portfolio with geometric Asian options, the payoff complexity is higher than that of a portfolio with European call options.
-The empirical rate of convergence of the kernel smoothing-based procedure is substantially lower for the portfolio with geometric Asian options than for the portfolio with European call options.
-For geometric Asian options, the empirical rates of convergence are even lower than the asymptotic rates for all asset dimensions.
-
-Due to the computational cost of the kernel smoothing-based nested simulation procedure, we are not able to conduct experiments for higher budget levels.
-However, we are able to conduct additional experiments to examine the effects of cross-validation on the empirical convergence of the kernel smoothing-based procedure.
-Another phenomenon that is observed in Figure~\ref{fig1:kernel_d} is that the empirical rate of convergence of the kernel smoothing-based procedure does not decrease monotonically as the simulation budget increases.
-This is likely due to the fact that the kernel smoothing-based procedure, as a non-parametric regression procedure, is highly dependent on the cross-validation of the hyperparameters of the metamodel.
-For the kernel smoothing-based procedure, the kNN metamodel is implemented. 
-Hence, the hyperparameter of interest is the number of nearest neighbors $k$.
-In our numerical experiment, cross-validation is conducted once to select the optimal value of $k$ for each simulation budget, and the selected value of $k$ is fixed for all $\num{1000}$ replications.
-Therefore, a suboptimal selection of the optimal value of $k$ can lead to a poor metamodel estimate, and the MSE of the kRR-based procedure will be dominated by the model error of the metamodel.
-
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure5a.png}
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure5b.png}
-    \caption{Cross-validation for the kernel smoothing-based procedure with $\Gamma=\num{100000}$}
-\label{fig1:kernel_cv} 
-\end{figure}
-
-In Figure~\ref{fig1:kernel_cv}, the empirical convergence of the kernel smoothing-based nested simulation procedure for the probability of large loss is illustrated for different values of $k$ with $\Gamma = \num{100000}$.
-The observation is that the value of optimal $k$ estimated by cross-validation is highly variable across different replications.
-For $d = 2$, the optimal value of $k$ is estimated to be between $120$ to $220$ for most replications, and the estimated risk measures are close to the true risk measure of $0.1$.
-For the two replications where $k = 80$ is estimated as the optimal value of $k$, the resulting estimates of risk measures are $0.1187$ and $0.1189$, which are substantially higher than the estimated risk measures for the other replications and far from the true risk measure of $0.1$.
-This observation suggests that the empirical convergence of the kernel smoothing-based nested simulation procedure is highly sensitive to the cross-validation of the hyperparameters of the metamodel.
-A KRR-based nested simulation procedure suffers from the same problem. 
-The fluctuation in Figure~\ref{fig1:kernel_d} is likely due to poor cross-validation of the hyperparameters of the metamodel.
-
-\subsection{Empirical Convergence of Parametric Regression Procedures}\label{sec1:regression-convergence}
-
-For both the regression-based and kernel smoothing-based procedures, the observed higher empirical rates of convergence can be explained by the poor performance of their metamodels at low simulation budgets.
-When simulation budgets are low, the metamodels trained to approximate the true inner simulation are inadequate.
-The MSEs for these procedures are dominated by the model errors of the metamodels.
-In other words, they have not yet reached their asymptotic convergence regimes.
-
-Due to computation constraints, we are not able to conduct experiments for kernel smoothing-based nested simulation procedures for higher budget levels, but we are able to conduct additional experiments for the regression-based nested simulation procedure.
-In our previous numerical experiments, the empirical rate of convergence of the regression procedure is observed to be much larger than its asymptotic rate of convergence.
-For dimensions larger than $10$, the MSE of the regression procedure decreases quickly in the beginning, and its rate of decrease stabilizes after a certain budget level.
-In Figure~\ref{fig1:reg_lb} illustrates the empirical convergence of the regression-based procedure in more detail at higher simulation budgets, where the asymptotic level of convergence is reached for $d = 20$.
-
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.7\textwidth]{./project1/figures/figure3.png}
-    \caption{Empirical convergence of regression procedure for European call options and $d=20$}
-\label{fig1:reg_lb} 
-\end{figure}
-
-The left part of Figure \ref{fig1:reg_lb} contains the MSEs of the regression procedure for budget sizes that are smaller than $10^3$. 
-Slopes of the fitted lines on the left correspond to the empirical rate of convergence of the regression procedure for budget levels between $10^3$ and $10^4$.
-To investigate the convergence behavior for higher budget levels, we conduct additional experiments for the European call option with a dimension of $20$. 
-The additional experiments are summarized on the right side of Figure \ref{fig1:reg_lb}.
-After reaching a certain budget level, i.e., $\Gamma = 10^6$ in our case, the empirical rate of convergence for the regression-based nested simulation procedure approaches its asymptotic rate. 
-For nested simulation procedures with a biased metamodel, the metamodel estimates of the true inner simulation are poor, especially for smaller budget sizes. 
-We are able to clearly observe this phenomenon for the regression metamodel, and it can be explained by dividing the MSE into metamodeling bias and simulation variance.
-\begin{itemize}
-    \item For small budget sizes, the improvement in the bias of the regression metamodel dominates the improvement in the simulation variance. 
-    Performing poorly for extremely low simulation budgets, the regression metamodel improves dramatically as the simulation budget increases.
-    \item As the simulation budget gets higher, the improvement of the regression bias becomes negligible compared with that of the simulation variance. 
-    The regression metamodel ceases to improve after reaching a certain level ($\Gamma = 10^6$ in our case), and the improvement of simulation variance dominates.
-\end{itemize}
-Due to high computational costs, we are not able to conduct experiments for higher budget levels, but we expect the MSE of the regression-based nested simulation procedure to stabilize after $\Gamma = 10^6$, and the empirical rate of convergence to approach its asymptotic rate.
-In the context of nested simulation procedures, a parametric regression metamodel has several advantages over a non-parametric regression metamodel.
-\begin{itemize}
-    \item Parametric regression achieves a good empirical convergence behavior for a moderate simulation budget.
-    \item Parametric regression is insensitive to changes in the asset dimension.
-    \item Parametric regression is easier to implement.
-    It does not require cross-validation to select the hyperparameters of the metamodel.
-\end{itemize}
-However, parametric regression suffers from the model misspecification risk.
-More specifically, selecting a wrong regression basis can lead to a poor metamodel estimate, where the MSE of the nested simulation procedure is dominated by the model error of the metamodel~\citep{broadie2015risk}.
-
-In our previous numerical experiments, the regression-based nested simulation procedure is implemented with Laguerre polynomials up to degree $3$ as the basis functions.
-It is a standard choice in the literature.
-To examine the sensitivity of the empirical convergence behavior to the regression basis, we consider different basis functions, i.e., regular polynomial regression up to degree $3$.
-
-\begin{figure}[ht!] 
-    \centering
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure13a.png}
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure13b.png}
-    \caption{Empirical convergence of regression-based nested simulation procedures for different regression bases}
-\label{fig1:sens_basis}
-\end{figure}
-
-In Figure~\ref{fig1:sens_basis}, the empirical convergence results of the regression-based nested simulation procedure for a quadratic tracking error and a 90\%-CVaR are illustrated for the two different regression bases.
-The empirical rates of convergence of the regression-based nested simulation procedure are observed to be insensitive to the chosen regression basis.
-
-\subsection{Sensitivity to the Option Types and Risk Measures}\label{sec1:sensitivity-option-type}
-
-In our previous numerical experiments, we have examined the empirical convergence behavior of the nested simulation procedures for European call options, which only depends on the asset price at maturity.
-To examine the sensitivity of the empirical convergence behavior to the option type, we consider path-dependent options, which are geometric Asian options and barrier options.
-
-\begin{figure}[ht!] 
-    \centering
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure6a.png}
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure6b.png}
-    \caption{Empirical convergence of nested simulation procedures for quadratic tracking error on different portfolios with $d=20$}
-\label{fig1:1x03} 
-\end{figure}
-
-In Figure~\ref{fig1:1x03}, the empirical convergence of the nested simulation procedures for the quadratic tracking errors of Portfolio 1 and Portfolio 4 is illustrated for $d = 20$.
-The empirical rates of standard, likelihood ratio-based, and KRR-based nested simulation procedures closely ensemble their asymptotic rates for path-dependent options.
-The empirical rate of convergence of the regression-based and kernel smoothing-based procedures is much higher than their asymptotic rates for barrier options. 
-The reasons are explained in Section~\ref{sec1:regression-convergence} and Section~\ref{sec1:kernel-smoothing-convergence}.
-
-\begin{figure}[ht!] 
-    \centering
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure7a.png}
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure7b.png}
-    \caption{Empirical convergence of nested simulation procedures for a W-shaped payoff}
-\label{fig1:5503} 
-\end{figure}
-
-In~\cite{broadie2015risk}, the authors propose a numerical example where the payoff has a W-shape with respect to the asset price at maturity.
-We have incorporated this example as Portfolio 5.
-In Figure~\ref{fig1:5503}, the empirical convergence of the nested simulation procedures for a quadratic tracking error and a mean excess loss on Portfolio 5 is illustrated for $d = 1$.
-For all procedures, we observe a similar convergence behavior as in other path-dependent options.
-The MSEs of the kernel smoothing-based and KRR-based procedures do not decrease monotonically as the simulation budget increases.
-This fluctuating behavior is observed and analyzed in Section~\ref{sec1:kernel-smoothing-convergence}.
-
-\begin{figure}[ht!] 
-    \centering
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure8a.png}
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure8b.png}
-    \caption{Empirical convergence of nested simulation procedures for different risk measures on Portfolio 1 with $d=20$}
-\label{fig1:110x}
-\end{figure}
-
-Figure~\ref{fig1:110x} illustrates similar observations for sensitivity to different risk measures.
-A change in the risk measure of interest does not affect the empirical convergence behavior of all nested simulation procedures.
-From the empirical convergence results, we observe that the empirical rates of convergence of the regression-based nested simulation procedure are the highest among all nested simulation procedures for all risk measures and option types.
-Furthermore, the regression-based procedure is stable across different payoff structures and risk measures. 
-Its MSEs decrease quickly in the beginning, and after reaching a certain level of $\Gamma$, the rate of decrease stabilizes to match its asymptotic rate of convergence.
-Parametric regression is the most attractive metamodel for nested simulation procedures due to its fast empirical convergence behavior, stability across different payoff structures and risk measures, and ease of implementation.
-The following sections focus on the regression-based nested simulation procedure for the rest of the numerical experiments.
-
-\subsection{Sensitivity to level for VaR and CVaR}\label{sec1:sensitivity-level}
-
-The level of VaR and CVaR is a critical factor that determines the complexity of the risk measure estimation.
-In our previous numerical experiments, the level of VaR and CVaR is set to be the $90\%$ quantile of the distribution of the inner simulation noise.
-In this section, we examine the empirical convergence of the regression-based nested simulation procedures for other levels of VaR and CVaR, i.e., $80\%$, $95\%$, $99\%$, and $99.6\%$.
-
-\begin{figure}[ht!] 
-    \centering
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure9a.png}
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure9b.png}
-    \caption{Empirical convergence of regression-based procedures for different levels of VaR and CVaR for Up and Out Barrier Call Options}
-\label{fig1:sens_level}
-\end{figure}
-
-In Figure~\ref{fig1:sens_level}, the empirical convergence of the regression-based nested simulation procedure for different levels of VaR and CVaR is illustrated for up-and-out barrier call options.
-The empirical rates of convergence of the regression-based nested simulation procedure are not sensitive to the level of VaR and CVaR.
-
-\subsection{Sensitivity to the Asset Model}\label{sec1:sensitivity-assetModel}
-
-Our previous numerical experiments have been conducted under the assumption that the underlying asset dynamics follow a multidimensional geometric Brownian motion with $0.3$ pairwise correlation.
-To examine the sensitivity of the empirical convergence behavior to the asset model, we consider a stochastic volatility model of a Heston type~\citep{heston1993closed}.
-
-\begin{figure}[ht!] 
-    \centering
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure10a.png}
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure10b.png}
-    \caption{Empirical convergence of regression-based nested simulation procedures for different asset models}
-\label{fig1:sens_model}
-\end{figure}
-
-In Figure~\ref{fig1:sens_model}, the empirical convergence results of the regression-based nested simulation procedure for a quadratic tracking error and a 90\%-CVaR are illustrated for different asset models, i.e., a geometric Brownian motion and a Heston model.
-The empirical rates of convergence of the regression-based nested simulation procedure are observed to be insensitive to the asset model.
-
-In summary, we find the empirical convergence behavior of the regression-based nested simulation procedure to be stable across different risk measures, option types, asset dimensions, levels of VaR and CVaR, asset models, and regression bases.
-With a limited total budget, the regression-based nested simulation procedure is the most robust and stable among all nested simulation procedures.
-
-\subsection{Empirical Convergence of MLMC}\label{sec1:empirical-mlmc}
-
-The MLMC procedure is a variance reduction technique that is designed to reduce the computational cost of nested simulation procedures.
-The theoretical analysis in~\cite{giles2019multilevel} shows that the MLMC procedure has a faster empirical rate of convergence than the standard nested simulation procedure when the risk measure of interest is the probability of a large loss over a threshold $u$, i.e., the nested expectation case with $h$ being an indicator function.
-\textcolor{red}{In this numerical experiment, the initial number of inner replications, the refinement factor, the r-value for adaptive algorithm are set to be $4$, $4$, and $1.5$, respectively.}
-\textcolor{red}{We note that the MLMC procedure focuses on adaptive allocation of the simulation budget and is fundamentally different from supervised learning-based nested simulation procedures.
-And their results are not directly comparable.}
-
-\begin{table}[ht]
-    \centering
-    \begin{tabular}{rrrrrr}
-    \toprule
-    \textbf{Level} & \textbf{Bias} & \textbf{Variance} & \textbf{MSE} & $\Gamma$ & \textbf{MSE of SNS} \\ 
-    \hline\hline
-    0 & 0.118  & 0.104  & 0.1364 & 6400     & 0.1660    \\
-    1 & 0.102  & 0.0916 & 0.1020 & 27600    & 0.1305    \\
-    2 & 0.0870 & 0.0794 & 0.0870 & 76600    & 0.0954    \\
-    3 & 0.0815 & 0.0746 & 0.0812 & 175600   & 0.0744    \\
-    4 & 0.0893 & 0.0805 & 0.0884 & 348100   & 0.0460    \\
-    5 & 0.0750 & 0.0694 & 0.0750 & 640000   & 0.0366    \\
-    \bottomrule
-    \end{tabular}
-    \caption{MSEs of the MLMC procedure for different levels}
-\label{tab1:mlmc-mse}
-\end{table}
-
-We provide a summary of the empirical convergence results of the MLMC procedure with a decomposition table of the MSEs in Table~\ref{tab1:mlmc-mse}.
-The MSEs of the MLMC procedure are decomposed into the bias and the variance of the estimator.
-The MSEs of the standard nested simulation procedure with a similar total simulation budget are also provided for comparison.
-Since the MLMC procedure is designed with a fixed number of outer simulation paths, the benefit of the MLMC procedure is minimal when the total simulation budget is large.
-More specifically, when $\Gamma$ is large, the standard nested simulation procedure with a bootstrap-based budget allocation strategy benefits from having a larger number of outer simulation paths, and the MSE of the standard nested simulation procedure is lower than that of the MLMC procedure with a fixed number of outer simulation paths.
-
-\section{Computational Complexity}\label{sec1:computational-complexity}
-Compared to the standard procedure, metamodel-based nested simulation procedures often have faster empirical rates of convergence.
-Their faster convergence benefits from the pooling of inner samples through the metamodels. 
-However, pooling itself comes with increased computational costs, which are usually ignored in most numerical comparisons. 
-This section summarizes the algorithmic complexity and illustrate the computational time of different nested simulation procedures.
-The findings can provide some further guidance on the choice of a proper nested simulation procedure given a nested estimation problem.
-Define basic operations to be basic mathematical operators, that is, arithmetic with individual elements has complexity $\mathcal{O}(1)$.
-
-\begin{table}[ht]
-    \centering  
-    \small
-    \begin{tabular}{llll}
-    \hline
-    \textbf{Procedures}      & \textbf{Training cost}                    &  \textbf{Prediction cost}    & \textbf{Total additional cost} \\ \hline \hline
-    Standard procedure       &  $0$                                      &  $\mathcal{O}(M)$            & $\mathcal{O}(M)$ \\ 
-    Regression               &  $\mathcal{O}(p^2M) + \mathcal{O}(p^3)$   &  $\mathcal{O}(pM)$           & $\mathcal{O}(p^2M) + \mathcal{O}(p^3)$ \\
-    Kernel smoothing         &  $\mathcal{O}(M\log(M))$                  &  $\mathcal{O}(k\log(M))$     & $\mathcal{O}(M\log(M))$ \\
-    Kernel ridge regression  &  $\mathcal{O}(M^3)$                       &  $\mathcal{O}(M^2)$          & $\mathcal{O}(M^3)$ \\
-    Likelihood ratio         &  $0$                                      &  $\mathcal{O}(M^2)$          & $\mathcal{O}(M^2)$ \\
-    \hline
-    \end{tabular} 
-    \caption{Additional computational costs of nested simulation procedures aside from simulation}
-\label{tab1:complexity}
-\end{table}
-
-Table~\ref{tab1:complexity} shows the algorithmic complexity of the nested simulation procedures.
-For a $d$-dimensional nested estimation problem, the simulation cost for all procedures is $\mathcal{O}(dMN)$.
-The simulation cost is omitted from Table~\ref{tab1:complexity}, as all procedures are given the same simulation budget.
-Given $M$ outer samples and the corresponding $M$ inner sample averages, the algorithmic complexity of the additional operations does not involve $N$ and thus, can be written in terms of $M$ only. 
-The training cost includes the cost of fitting the metamodel and the cost of cross-validation for non-parametric regression metamodels.
-
-For the standard procedure, 
-\begin{itemize}
-    \item the training cost is $0$ due to the absence of a metamodel. 
-    \item Its prediction cost $\mathcal{O}(M)$ comes from the evaluation of the function $h$ for $M$ samples.
-\end{itemize}
-For the regression-based procedure, a linear regression model is fitted with $p$ predictors.
-\begin{itemize}
-    \item The training cost is $\mathcal{O}(p^2M) + \mathcal{O}(p^3)$.
-          Estimating the coefficients of the regression model involves multiplying the design matrix by its transpose and inverting the resulting matrix, which has complexity $\mathcal{O}(p^2M)$ and $\mathcal{O}(p^3)$, respectively.
-          For a review in the complexity of a matrix inversion, see~\cite{stothers2010complexity}.
-          The matrix inversion has complexity $\mathcal{O}(p^3)$ using a Gauss-Jordan elimination, but in practice, the complexity can be reduced to $\mathcal{O}(p^{2.807})$ by~\cite{strassen1969gaussian} and $\mathcal{O}(p^{2.376})$ by~\cite{coppersmith1987matrix}.
-          In practice, $p$ is usually much smaller than $M$ and does not grow with the simulation budget $\Gamma$.
-          $p$ is fixed by the basis function, which is selected based on the complexity of the payoff function.
-    \item The prediction cost of the regression-based procedure is $\mathcal{O}(pM)$, which comes from the multiplication of the design matrix by the estimated coefficients.
-\end{itemize}
-For the kernel smoothing-based procedure, the kNN metamodel is implemented. 
-In practice, the K-D tree algorithm~\citep{bentley1975multidimensional} is often implemented for an efficient nearest neighbor search.
-\begin{itemize}
-    \item During training, a tree is constructed to store the distance, which has a degree of complexity of $\mathcal{O}(M\log(M))$.
-    \item The prediction cost of the kernel smoothing-based procedure is $\mathcal{O}(kM\log(M))$, which comes from a query of the K-D tree for $k$ nearest neighbors for $M$ samples.
-    Conversely, an inefficient algorithm calculates the distance matrix during training and a block sort algorithm to find the $k$ nearest neighbors, which results in a degree of complexity of $\mathcal{O}(M^2)$ and $\mathcal{O}(M^2\log(M))$, respectively.
-    A practical implementation of a block sort is provided in~\cite{kim2008ratio}.
-    Hence, an efficient implementation of the kNN metamodel is crucial for the kernel smoothing-based procedure.
-\end{itemize}
-For the likelihood ratio-based procedure, 
-\begin{itemize}
-    \item the training cost is $0$ as no training is required.
-    \item The prediction cost of the likelihood ratio-based procedure is $\mathcal{O}(M^2)$, which comes from the calculation of the likelihood weights for $M$ samples.
-\end{itemize}
-For the KRR-based procedure, 
-\begin{itemize}
-    \item the main training cost comes from inverting an $M \times M$ kernel matrix~\citep{scholkopf2002learning}, which has a degree of complexity of $\mathcal{O}(M^3)$ using a Gauss-Jordan elimination.
-          Similar to the regression-based procedure, this complexity can be reduced to $\mathcal{O}(M^{2.376})$.
-    \item The prediction cost of the KRR-based procedure is $\mathcal{O}(M^2)$, which comes from the multiplication of the kernel matrix by the estimated coefficients.
-\end{itemize}
-Among the metamodel-based procedures, parametric regression is the most efficient.
-In the multiple linear regression, the number of features is usually much less than the number of data points, i.e., $p<M$. 
-Kernel smoothing and KRR are kernel-based metamodels, and they are more computaional expensive due to distance calculations and cross-validations of hyperparameters. 
-The kNN metamodel has only 1 hyperparameter $k$, while the KRR metamodel requires 3 hyperparameters, namely a smoothness hyperparameter $\nu$, a scale hyperparameter $\upsilon$, and a regularization hyperparameter $\lambda$.
-Calculating the likelihood ratio weights is inevitable for the likelihood ratio-based procedure. 
-While a k-fold cross-validation is used to estimate the hyperparameter for kNN, the KRR requires Bayesian optimization~\citep{shahriari2015taking} to estimate the hyperparameters due to having a high-dimensional search space.
-The likelihood ratio-based procedure requires no training, but the cost of calculating the likelihood weights is $\mathcal{O}(M^2)$.
-Comparing the algorithmic complexity of the nested simulation procedures, the regression-based procedure is the most efficient among the metamodel-based procedures.
-For a fixed $p$, the total additional cost of a regression-based procedure is $\mathcal{O}(M)$, which is the same as the standard procedure's.
-
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure11a.png}
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure11b.png}
-    \caption{Total computational cost for different procedures with $d=10$}
-\label{fig1:tcc}
-\end{figure}
-
-The cost associated with pooling makes a major impact on the overall computational complexity of a metamodel-based nested simulation procedure.
-In our finite-sample experiments, we have indeed observed that the actual computational cost to deviate substantially from the simulation cost.
-In Figure~\ref{fig1:tcc}, the total actual computational time of different nested simulation procedures for European call options and geometric Asian options with $d = 10$ is illustrated in a log-log scale.
-The $x$-axis shows the total simulation budget $\Gamma$, and the $y$-axis is the total computational time for 1 replication of the numerical experiment, in seconds.
-All procedures are implemented on a machine with an AMD Ryzen 9 7900X processor with 32 GB of RAM.
-8 cores are used for parallel computing, and the total computational time is the sum of the simulation time, the training time, and the prediction time.
-The regression and kernel smoothing-based procedures are the most efficient among the metamodel-based procedures.
-Since the regression-based procedure has a higher empirical rate of convergence, it is preferred over kNN.
-The likelihood ratio-based and KRR-based procedures are the most computationally expensive among all procedures.
-They are also demanding in terms of memory.
-For budgets larger than $10^5$, the likelihood ratio-based procedure becomes impractical as storage of the likelihood weights becomes a bottleneck.
-The KRR-based procedure suffers from both cross-validation and inverting a kernel matrix of size $M \times M$.
-To separate the total computational time into different attributes, we provide a detailed analysis of the total computational time in the remainder of this section.
-
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure12a.png}
-    \includegraphics[width=0.48\textwidth]{./project1/figures/figure12b.png}
-    \caption{Computational cost for implementing nested simulation procedures with $d=10$, excluding simulation time}
-\label{fig1:c_model}
-\end{figure}
-
-Figure~\ref{fig1:c_model} illustrates the computational time of implementing different nested simulation procedures for the portfolio of geometric Asian options with $d = 10$.
-The simulation time is omitted as it is the same for all procedures.
-The remaining computations can be decomposed into two parts: hyperparameter tuning and model implementation.
-The hyperparameter tuning cost is the cost of estimating the optimal hyperparameters for the metamodels, and the model implementation cost is the cost of fitting the metamodels and generating predictions from the trained metamodels.
-For each procedure, each point in Figure~\ref{fig1:c_model} represents the average computational time for a given simulation budget $\Gamma$.
-A regression model is fitted to each model respectively, and its slope can be viewed as the growth rate of the computational time with respect to $\Gamma$.
-\begin{itemize}
-    \item The total computational time of the standard procedure is mostly attributed to finding the optimal $M$ and $N$ using the bootstrap-based budget allocation strategy from~\cite{zhang2021bootstrap}.
-    This cost does not grow with the simulation budget $\Gamma$, as its slope is close to $0$.
-    \item The regression-based procedure does not require any hyperparameter tuning, and its total computational time is mainly attributed to the model implementation.
-    The slope of the regression line is close to $1$, resembling its algorithmic complexity reported in Table~\ref{tab1:complexity}.
-    \item The kernel smoothing-based and KRR-based procedure requires a cross-validation procedure to estimate the optimal hyperparameters. 
-    In our implementation of kNN, the cross-validation is conducted by using a grid search with a search space which cardinality does not grow with the simulation budget $\Gamma$.
-    However, the cross-validation cost of the kernel smoothing-based procedure grows with the simulation budget $\Gamma$ as more samples are involved.
-    The KRR-based procedure requires a Bayesian optimization to estimate the optimal hyperparameters, and the cardinality of the search space also grows with the simulation budget $\Gamma$.
-    The empirical cost of the KRR-based procedure does not resemble its algorithmic complexity reported in Table~\ref{tab1:complexity}.
-    The efficient implementation of KRR is an active area of research, and the computational cost of KRR can be reduced by using a low-rank approximation of the kernel matrix, e.g., the Nystr\"om method~\citep{nystrom1930praktische}.
-    Our observation for the KRR implementation time is in line with the findings in~\cite{scikit-learn}, where the cost of KRR is reported to be increasing quickly with the number of samples.
-    \item The likelihood ratio-based procedure requires no hyperparameter tuning, and its total computational time is mainly attributed to the likelihood weight calculation, which is $\mathcal{O}(M^2)$.
-\end{itemize}
-In summary, for a large simulation budget, the regression-based procedure is the most efficient among all metamodel-based procedures in terms of computational time.
-For moderate simulation budgets, the regression-based procedure is a preferred choice.
-
-\section{Conclusion and Extensions}\label{sec1:conclusion}
-In the task of estimating risk measures for portfolios of complex financial derivatives, nested simulation procedures are commonly required but often computationally expensive. 
-Tremendous efforts have been made to improve the efficiency of nested simulation procedures by approximating the inner simulation model with a metamodel. 
-In this study, we review the literature on nested simulation procedures in financial engineering and provide fair comparisons of different metamodels by using the same set of numerical examples. 
-Asymptotic properties of estimators for different nested simulation procedures are influenced by their corresponding metamodels.
-To show an asymptotic convergence result, a more complex metamodels requires a more stringent set of assumptions on the distribution of the outer scenario and the inner simulation noise.
-With extensive numerical experiments, we have found that the finite-sample performance of a procedure can deviate from its theory. 
-In theory, supervised learning-based nested simulation procedures often provide higher rates of convergence, but they come at the computational expense of model training and generating predictions from the trained models.
-The likelihood ratio-based procedure requires no training, but it is expensive to compute, and it is also expensive to store the likelihood weights.
-As a result, the total computational budget is not necessarily the same as the simulation budget, which is usually a limiting factor for practical applications.
-A kernel-based procedure, e.g., kNN and KRR, requires cross-validation, and its empirical performance depends heavily on the choice of hyperparameters.
-A kNN-based procedure is sensitive to the asset dimension and the problem complexity.
-A KRR-based procedure is computationally expensive, and its cost grows quickly with the simulation budget.
-For kernel-based procedures, the computational cost is heavily dependent on the efficient implementation of the associated algorithms.
-For a nested estimation problem with a given computational budget, we suggest the use of the regression-based simulation procedure when the budget size is moderate. 
-It is efficient to implement, and it exhibits fast empirical convergence in estimating risk measures for popular option portfolios. 
-However, we have only examined the performance for option portfolios in this study, where finding a suitable set of basis functions for regression is relatively easy.
-In practice, a variable annuity contract is often high-dimensional in time with a complex payoff structure, and it is a challenging problem for nested simulation procedures.
-The time dependence in the feature space leads to multi-collinearity, and the regression-based procedure may not be the best choice in such instances.
-In such cases, a neural network-based procedure may be more suitable, as it is a data-driven algorithm that finds a suitable set of basis functions automatically.
-In Chapter~\ref{chap:project2}, we examine the performance of regression-based and neural network-based nested simulation procedures for estimating risk measures for variable annuities.
+\end{document}

### 2025-04-14 project1/nsSurvey.tex
21

@@
 
-To the best of our knowledge, Theorem~\ref{thm1:convergence-mse-prob} has not been explicitly stated in the literature.
-It is the first result that shows the connections between the convergence in \gls{mse} and the convergence in probabilistic order for \gls{ae} in the context of nested simulation.
-Theorem~\ref{thm1:convergence-mse-prob} is a general result that can be applied to any nested simulation procedure that converges in \gls{mse} to $\rho$ in order $\xi$.
+Theorem~\ref{thm1:convergence-mse-prob} provides a formal connection between the \textcolor{red}{rate of convergence} in \gls{mse} and that in probabilistic order for \gls{ae} in the context of nested simulation.
+It is a general result that can be applied to any nested simulation procedure that converges in \gls{mse} to $\rho$ in order $\xi$.
 If the estimator converges in \gls{mse} to $\rho$ in order $\xi$, then it converges in probabilistic order to $\rho$ in order $\frac{\xi}{2}$.

### 2025-04-14 project2/nnMetamodels.tex
21

@@
 Evolution of the subaccount value and the guarantee value of a \gls{va} contract affect the contract payout.
+Let the triplet $X_t = (S_t, F_t, G_t)$ be the state of the \gls{va} contract at time $t$.
 Note that the policyholder's (random) time of death also affects the timing of the benefit payout for certain types of \gls{va} such as \gls{gmab}, but this is not considered in our study for simplicity.
@@
 For example, suppose that the per-period risk-free rate is $r$, then
-the insurer's time-$t$ liability for a \gls{gmmb} contract is $V_t = e^{-r(T-t)}\cdot (G_T - F_T)^+ - \sum_{s=t+1}^{T} e^{-r(T-s)} F_s \eta_n$.
-Also, the insurer's time-$t$ liability for a \gls{gmwb} contract is $V_t = \sum_{s=t+1}^{T} e^{-r(T-s)} [(I_s - F_s)^+- \eta_n F_s] $.
-
-For example, consider the time-$t$ liability $V_t$ of a \gls{gmwb}:
-Suppose that given the stock sample path, which is an outer path $S_1,\ldots,S_t$, one can simulate future stock prices $\Stilde_{t+1},\ldots,\Stilde_{T}$, e.g., inner sample paths, based on some asset model such as a Black-Scholes model.
+\textcolor{red}{the insurer's time-$t$ liability for a \gls{gmwb} contract is}
+
+\begin{equation} \label{eq2:liability-gmwb}
+    V_t = V(\mathbf{S}_t) = \mathbb{E} \left[ e^{-r(T-t)}\cdot (G_T - F_T)^+ - \sum_{s=t+1}^{T} e^{-r(T-s)} F_s \eta_n \big\vert \mathbf{S}_t \right],
+\end{equation}
+
+where $\mathbf{S}_t = (S_0, S_1, \ldots, S_t)$ is the (outer) sample path up to time $t$, and the conditional expectation is taken with respect to the inner sample paths $\Stilde_{t+1},\ldots,\Stilde_{T}$ given the outer path $\mathbf{S}_t$.
 The tilde symbol ($\sim$) over a quantity denotes its association with the inner simulation.
+In practice, given the stock sample path, which is an outer path $S_1,\ldots,S_t$, one can simulate these future stock prices $\Stilde_{t+1},\ldots,\Stilde_{T}$ with an inner simulation model that is based on some asset model such as \gls{gbm} or \gls{rsgbm}.
 Given the time~$t$ state $(S_t,F_t,G_t)$, following~\cite{cathcart2015calculating} the sensitivity of $V_t$ with respect to $S_t$ can be estimated by a pathwise estimator~\citep{glasserman2004monte}:
 \begin{align}\label{eq2:delta}
-    \Delta_t(\Stilde_{t+1},\ldots,\Stilde_{T} | S_t) = \frac{\partial V_t}{\partial S_t} = \sum_{s=t+1}^{T} e^{-r(T-s)} \left[\bm{1}\{\Itilde_s > \Ftilde_s\} \cdot \left( \frac{\partial \Itilde_s}{ \partial S_t} - \frac{\partial \Ftilde_s}{ \partial S_t}\right)- \eta_n \frac{\partial \Ftilde_s}{ \partial S_t}\right], \nonumber \\
+    \Delta_t(\Stilde_{t+1},\ldots,\Stilde_{T} | \mathbf{S}_t) 
+    & = \frac{\partial V_t}{\partial S_t} \nonumber \\
+    & = \frac{\partial}{\partial S_t} \mathbb{E} \left[ e^{-r(T-t)}\cdot (G_T - F_T)^+ - \sum_{s=t+1}^{T} e^{-r(T-s)} F_s \eta_n \big\vert \mathbf{S}_t \right] \nonumber \\
+    & = \mathbb{E} \left[ \frac{\partial}{\partial S_t} \left( e^{-r(T-t)}\cdot (G_T - F_T)^+ - \sum_{s=t+1}^{T} e^{-r(T-s)} F_s \eta_n \right) \big\vert \mathbf{S}_t \right] 
+\end{align}
+
+For an inner simulation path $\Stilde_{t+1},\ldots,\Stilde_{T}$ of the \gls{gmwb} contract, the sensitivity of $V_t$ can be calculated by the following recursion:
+\begin{equation}
+    \sum_{s=t+1}^{T} e^{-r(T-s)} \left[\bm{1}\{\Itilde_{t,s} > \Ftilde_{t,s}\} \cdot \left( \frac{\partial \Itilde_{t,s}}{ \partial S_t} - \frac{\partial \Ftilde_{t,s}}{ \partial S_t}\right)- \eta_n \frac{\partial \Ftilde_{t,s}}{ \partial S_t}\right], \nonumber \\
     t=0,\ldots,T-1, 
+\end{equation}
+where $\bm{1}\{\cdot\}$ is an indicator function, $\Stilde_t = (S_{t, t+1},\ldots,S_{t, T})$, $\Ftilde_t = (F_{t, t+1},\ldots,F_{t, T})$, $\Gtilde_t = (G_{t, t+1},\ldots,G_{t, T})$, $\Itilde_t = (I_{t, t+1},\ldots,I_{t, T})$, and
+\begin{align} \label{eq2:partial-derivatives}
+    \frac{\partial \Ftilde_{t, s}}{ \partial S_t} &= \bm{1}\{\Itilde_{t, s-1} < \Ftilde_{t, s-1}\}\cdot\left( \frac{\partial \Ftilde_{t, s-1}}{ \partial S_t} - \frac{\partial \Itilde_{t, s-1}}{ \partial S_t}\right) \cdot \frac{\Stilde_{t, s}}{\Stilde_{t, s-1}}\cdot (1-\eta_g),\nonumber \\
+    \frac{\partial \Gtilde_{t, s}}{ \partial S_t} &= \bm{1}\{\Gtilde_{t, s-1} < \Ftilde_{t, s}\}\cdot\frac{\partial \Ftilde_{t, s}}{ \partial S_t} + \bm{1}\{\Gtilde_{t, s-1} \geq \Ftilde_{t, s}\}\cdot\frac{\partial \Gtilde_{t, s-1}}{ \partial S_t},\nonumber \\
+    \frac{\partial \Itilde_{t, s}}{ \partial S_t} &= \gamma \frac{\partial \Gtilde_{t, s}}{ \partial S_t}.
 \end{align}
-where $\bm{1}\{\cdot\}$ is an indicator function and
-\begin{align*}
-    \frac{\partial \Ftilde_s}{ \partial S_t} &= \bm{1}\{\Itilde_{s-1} < \Ftilde_{s-1}\}\cdot\left( \frac{\partial \Ftilde_{s-1}}{ \partial S_t} - \frac{\partial \Itilde_{s-1}}{ \partial S_t}\right) \cdot \frac{\Stilde_s}{\Stilde_{s-1}}\cdot (1-\eta_g),\\
-    \frac{\partial \Gtilde_s}{ \partial S_t} &= \bm{1}\{\Gtilde_{s-1} < \Ftilde_{s}\}\cdot\frac{\partial \Ftilde_{s}}{ \partial S_t} + \bm{1}\{\Gtilde_{s-1} \geq \Ftilde_{s}\}\cdot\frac{\partial \Gtilde_{s-1}}{ \partial S_t},\\
-    \frac{\partial \Itilde_s}{ \partial S_t} &= \gamma \frac{\partial \Gtilde_s}{ \partial S_t}.
-\end{align*}
-The recursion is initialized with $(\Stilde_t,\Ftilde_t,\Gtilde_t) = (S_t,F_t,G_t)$, $\frac{\partial \Ftilde_s}{ \partial S_t} = \frac{\Ftilde_t}{S_t}$, and $\frac{\partial \Gtilde_s}{ \partial S_t} = \frac{\partial \Itilde_s}{ \partial S_t} = 0$.
+At each inner simulation, the sample path at $t$ is initialized as:
+\begin{equation}
+    (\tilde{X}_{t, t}) = (\tilde{S}_{t, t}, \tilde{F}_{t, t}, \tilde{G}_{t, t}) = (S_t, F_t, G_t) = (X_t)
+\end{equation}
+W
+Before withdrawal at $t$, the partial derivatives are initialized. $\tilde{F}_{t, t}$ is set to be proportional to $\tilde{S}_{t}$, such that:
+\begin{equation}
+    \frac{\partial \Ftilde_{t, t}}{ \partial S_t} = \frac{\partial F_t}{ \partial S_t} = \frac{F_t}{S_t}.
+\end{equation}
+$\tilde{G}_{t, t}$ and $\tilde{I}_{t, t}$ are fixed as constants, such that:
+\begin{equation}
+    \frac{\partial \Gtilde_{t, t}}{ \partial S_t} = \frac{\partial G_{t}}{ \partial S_t} = 0, \quad \frac{\partial \Itilde_{t, t}}{ \partial S_t} = \gamma \frac{\partial I_{t}}{ \partial S_t} = 0.
+\end{equation}
+
+Note that in \eqref{eq2:partial-derivatives}, no calculation is needed for $F_t < I_t$. 
+In this case, the sub-account is already depleted at time $t$ and withdrawals are not allowed.
+Therefore, \gls{gmwb}'s future liabilities beyond time $t$ are no longer affected by the stock price $S_t$, so no hedging is necessary.
+In other words, when $F_t < I_t$, the inner simulation can be skipped and set $\Delta_t = 0$.
 

### 2025-04-15 project2/nnMetamodels.tex
s

@@
 \end{equation}
-W
 Before withdrawal at $t$, the partial derivatives are initialized. $\tilde{F}_{t, t}$ is set to be proportional to $\tilde{S}_{t}$, such that:
 \begin{equation}
-    \frac{\partial \Ftilde_{t, t}}{ \partial S_t} = \frac{\partial F_t}{ \partial S_t} = \frac{F_t}{S_t}.
+    \frac{\partial \Ftilde_{t, t}}{ \partial S_t} = \frac{\partial F_t}{ \partial S_t} = \frac{F_t}{S_t},
 \end{equation}
-$\tilde{G}_{t, t}$ and $\tilde{I}_{t, t}$ are fixed as constants, such that:
+and $\tilde{G}_{t, t}$ and $\tilde{I}_{t, t}$ are fixed as constants, such that:
 \begin{equation}
@@
 \end{equation}
-
-Note that in \eqref{eq2:partial-derivatives}, no calculation is needed for $F_t < I_t$. 
+Note that in Equation~\ref{eq2:partial-derivatives}, no calculation is needed for $F_t \leq I_t$. 
 In this case, the sub-account is already depleted at time $t$ and withdrawals are not allowed.
@@
 
-Consider a \gls{va} contract which delta hedge portfolio at any time~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at time $T$.
-The value of the hedge portfolio at time~$(t-1)$ is:
+Consider hedging a \gls{va} contract whose sub-account is invested in a stock, and the hedging portfolio is rebalanced monthly.
+At $t \leq T$, a dynamic equation can be specified for the sub-account value $F_t$, in the absence of withdrawals, as:
+\begin{equation*}
+    F_t = F_{t-1} \cdot \frac{S_t}{S_{t-1}} \cdot (1-\eta_g)
+\end{equation*}
+where $\eta_g> \eta_n$ is the gross rate of management fee that is deducted from the sub-account value at the end of each month.
+The delta hedge portfolio at any month~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at $T$ months.
+The value of the hedge portfolio at month~$(t-1)$ is:
 \begin{equation*}
@@
 \end{equation*}
-where $S_t$ is an underlying stock price and any time $t>0$.
-This hedge portfolio is brought forward to the next rebalancing time~$t$, when its value becomes:
+where $S_t$ is an underlying stock price and any month $t>0$.
+Assuming there is no rebalacing between $t-1$ and $t$, this hedge portfolio is brought forward to month~$t$,.
+Its value at month~$t$ becomes:
 \begin{equation*}
-    H_{t}^{bf} = \Delta_{t-1} S_{t} + B_{t-1}e^{r}.
+    H_{t}^{bf} = \Delta_{t-1} S_{t} + B_{t-1}e^{-rt}.
 \end{equation*}

### 2025-04-15 project2/nnMetamodels.tex
Update nnMetamodels.tex

@@
 Two specialized neural network architectures that are relevant to our study are \gls{rnn}~\citep{williams1989learning,sutskever2014sequence} and \gls{lstm}~\citep{hochreiter1997long,chung2014empirical}.
-In the field of actuarial science, a metamodel is commonly referred to as a proxy model.
 Despite their success, \gls{dnn} models are often criticized for their lack of transparency and interpretability, which hinders their adoption in financial and actuarial applications.
@@
 
-In a nested simulation, a simulation model is used to generate a large number of outer scenarios, and each scenario is then used as an input to another simulation model, referred to as an inner simulation model.
+Estimating tail risk measures of portfolios of complex \gls{va}s usually requires nested simulation.
+In the nested simulation, the outer simulation involves projecting scenarios of key risk factors under a $\mathbb{P}$ measure, while the inner simulations are used to value payoffs uder guarantees of varying complexity, under a $\mathbb{Q}$ measure.
+
+For insurers, large-scale nested simulations for assessing \gls{va} losses are generally computationally intensive; i.e., a large number of outer level simulations are needed to estimate extreme tails for calculations of tail risk measures, and a large number of inner simulations are also needed at each time step, because the embedded options are out of money.
+In addition, the required calculations need to be repeated for each \gls{va} contract, or cluster of \gls{va} contracts.
+Consequently, insurers are interested in techniques for nested simulation models that produce accurate results within the confines of a finite computational budget.
+
+There are two main approaches that can be used to improve the efficiency of inner simulations.
+The first one uses a dynamic, non-uniform allocation of the inner simulation budget, and the second uses a proxy model to replace the inner simulation step.
+Some work uses a combination of both approaches.
+
+In Chapter~\ref{chap:project1}, the likelihood ratio approach is used to allocate the inner simulation budget using likelihood ratio weights, i.e., importance sampling.
+Proxy models are tractable analytic functions or flexible empirical functions that are used to replace the inner simulation stage of a nested simulation.
+Empirical proxies may be intrinsic or extrinsic to the simulation process.
+Extrinsic proxy functions are selected to be close to the inner simulation values and therefore require detailed information about the payoffs that are evaluated in the inner simulation step.
+Empirical proxies are constructed by using an initial pilot simulation to develop factors or functionals that can subsequently be used in place of the inner simulation. 
+A prominent expirical proxy method discussed in the literature is the least squares Monte Carlo method~\citep{longstaff2001valuing}.
+In Chapter~\ref{chap:project1}, supervised learning models, including linear regression, \gls{knn}, and \gls{krr}, are used as proxy models for inner simulations.
+This chapter introduces a proxy model to reduce the computational requirements of inner simulations of \gls{va}s by replacing the inner simulation step of a nested simulation procedure. 
+This proxy model is chosen to be a flexible empirical function, i.e., a \gls{dnn} metamodel.
+
+In our study, supervised learning metamodels are trained using data simulated from an initial pilot simulation.
+They are then used to replace the time-consuming inner simulations by the trained model.
 Borrowing terminologies from the machine learning community, we can view a set of simulated outer scenarios and estimated hedging errors for those scenarios as \textit{features} and noisy \textit{labels}.
 The noise level of the labels can be controlled by the number of inner replications in the inner simulation model.
-One can train supervised learning models using these simulated features and labels.
-They are then used to replace the time-consuming inner simulations by the trained model.
-We refer to the trained supervised learning models as \textit{metamodels} of the inner simulation, which is also known as the \textit{surrogate models} in the simulation literature.
+We refer to the trained supervised learning proxy models as \textit{metamodels} of the inner simulation, which is also known as the \textit{surrogate models} in the simulation literature.
 Metamodeling is a popular approach to reduce the computational burden of simulation-based applications by replacing the time-consuming simulation with a metamodel.
@@
 \end{equation}
-The \gls{pl} of the \gls{va} contract includes cost of the initial hedge ($H_0$), hedging errors~\eqref{eq2:hedgingerror}, unwinding of the hedge at maturity ($H^{bf}_T$), and unhedged liability ($V_0$).
-Mathematically, the present value of these cash flows is given by
+The \gls{pl} of the \gls{va} contract includes cost of the initial hedge ($H_0$), the periodic hedging gains and losses due to rebalancing at each time $t=1,\ldots,T-1$ (Equation~\ref{eq2:hedgingerror}), unwinding of the hedge at maturity ($H^{bf}_T$), the payment of guaranteed benefit, and the management fee income.
+The present value of these cash flows, discounted at the risk-free rate, is the insurer's overall \gls{pl} from the \gls{va} contract.
+At $t=0$, the insurer's overall \gls{pl}, i.e., the loss random variable $L$ to which a risk measure is applied, is given by
+\begin{align}\label{eq2:lossrvtw}
+L & = H_0 + \sum_{t=1}^{T-1} e^{-rt} HE_t - e^{-rT} H^{bf}_T + V_0  \nonumber \\
+  & = H_0 + \sum_{t=1}^{T-1} e^{-rt} (H_t - H_t^{bf}) - e^{-rT} H^{bf}_T + V_0  \nonumber \\
+  & = B_0 + S_0 V_0 + \sum_{t=1}^{T-1} e^{-rt} \left( B_t + S_t \Delta_t - B_{t-1} \frac{e^{-r(t-1)}}{e^{-rt}} - S_{t-1} \Delta_{t-1}  \right) - e^{-rT} S_T \Delta_{T-1} + V_0,  \nonumber 
+\end{align}
+where $V_0$ can be thought of as a discounted payoff of the \gls{va} contract at $t=0$, net of fee income in the absense of any hedging.
+The terms $H_0 + \sum_{t=1}^{T-1} e^{-rt} HE_t - e^{-rT} H^{bf}_T$ is the gain or loss from hedging.
+It consists of three components:
+\begin{itemize}
+    \item   $H_0$ is the initial cost of the hedging portfolio, 
+    \item   $\sum_{t=1}^{T-1} e^{-rt} HE_t$ is the gain or loss from all rebalacing trades at time $t=1,\ldots,T-1$, and
+    \item   $-e^{-rT} H^{bf}_T$ is the proceeds from unwinding the hedge at maturity $T$.
+\end{itemize}
+Rearranging the terms in Equation~\ref{eq2:lossrvtw}, the loss random variable $L$ can be simplified as
 \begin{equation}\label{eq2:lossrv}
-L = H_0 + \sum_{t=1}^{T-1} e^{-rt} HE_t - e^{-rT} H^{bf}_T + V_0 = \sum_{t=0}^{T-1}\Delta_t (e^{-rt}S_t - e^{-r(t+1)}S_{t+1}) + V_0,
+    L = \sum_{t=0}^{T-1}\Delta_t (e^{-rt}S_t - e^{-r(t+1)}S_{t+1}) + V_0.
 \end{equation}
-where the second equality holds by a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$.
-
+Equation~\ref{eq2:lossrv} shows that in bond holdings of hedging portfolio, all intermediate bond transactions cancel out since the interest rate $r$ at which bond value accumulates is the same as rate at which \gls{pl}s from bond transactions are discounted.
+In the stock holdings of the hedging portfolio, the gain or loss arises from the inital set-up of stock future holdings and the \gls{pl} from each rebalancing trade.
 In~\eqref{eq2:lossrv}, $\Delta_t$ and $V_0$ are determined by using a risk-neutral measure $\mathbb{Q}$ while the distribution of $L$ is under a real-world measure $\mathbb{P}$.
 If $\Delta_t$ and $V_0$ cannot be calculated analytically, a nested simulation is required to estimate the tail risk measure of $L$.
-Recall from Section~\ref{subsec:VApayout} that the stock sample path, regardless of the inner or outer simulation or a combination of both, determines the evolution of the triplet $(S_t,F_t,G_t)$.
-Specifically, the outer scenarios $\bS^{(i)} = (S_{1}^{(i)},\ldots,S_{T}^{(i)})$, $i=1,\ldots,M$ are generated under $\mathbb{P}$.
+Specifically, the outer scenarios $\bS^{(i)} = (S_{1}^{(i)},\ldots,S_{T}^{(i)})$, $i=1,\ldots,M$ are generated under $\mathbb{P}$ measures to estimate the loss distribution.
 At each time~$t=1,\ldots,T-1$ of a given outer scenario $\bS^{(i)}$, inner sample paths $\bStilde_{t}^{(j)} = (\Stilde_{t+1}^{(j)},\ldots,\Stilde_{T}^{(j)})$, $j=1,\ldots,N$ are generated under $\mathbb{Q}$ to estimate $\Delta_t^{(i)}$, $i=1,\ldots,M$.

### 2025-04-19 futureWork/rlHedging.tex
asd

@@
 \begin{equation*}
-    H_{t}^{bf} = \Delta_{t-1} S_{t} + B_{t-1}e^{r}.
+    H_{t}^{bf} = \Delta_{t-1} S_{t} + B_{t-1}e^{-rt}.
 \end{equation*}
@@
 The discrete-time hedging problem of VAs can be conveniently formulated as an \gls{mdp}, where the states, actions, transition probabilities, policies, and rewards are defined as follows.
+\textcolor{red}{Different from the formulation in Chapter~\ref{chap:project2}, the hedging weight $\Delta_0, \ldots, \Delta_{T-1}$ are not estimated from inner simulation steps but are directly controlled by a \gls{drl} agent.
+Thus, the hedging weight $\Delta_t$ at time $t$ is estimated using a neural network whose input is the state $\mathbf{s}_t$ and output is $\Delta_t$.}
 
 \subsection{State Space}
-
 The state space $\mathcal{S}$ represents all the information needed to characterize the hedging environment.

### 2025-04-19 project1/nsSurvey.tex
asd

@@
 
-In Equation~\eqref{eq1:mse-sns}, the last equality follows from Assumption~\ref{as1:sns}.
+\textcolor{red}{In Equation~\eqref{eq1:mse-sns}, the first inequality follows from Cauchy-Schwarz inequality.
+One way to express the Cauchy-Schwarz inequality is 
+$(x_1y_1 + x_2y_2)^2 \leq (x_1^2 + x_2^2)(y_1^2 + y_2^2)$.
+Let $\mathbf{x} = (x_1, x_2)$ and $\mathbf{y} = (y_1, y_2)$.
+The Cauchy-Schwarz inequality can be written as}
+\begin{equation*}
+    \langle \mathbf{x}, \mathbf{y} \rangle^2  = \left( \Vert \mathbf{x} \Vert \cdot \Vert \mathbf{y} \Vert \cdot \cos a \right)^2 \leq \Vert \mathbf{x} \Vert^2 \cdot \Vert \mathbf{y} \Vert^2.
+\end{equation*}
+\textcolor{red}{By setting $x_1 = \rho_{M,N}- \rho_M$, $x_2 = \rho_M - \rho$, $y_1 = y_2 = 1$, we have }
+\begin{align*}
+    \left( \rho_{M,N} - \rho_M + \rho_M - \rho \right)^2 
+    & \leq \left( (\rho_{M,N} - \rho_M)^2 + (\rho_M - \rho)^2 \right) \left( 1^2 + 1^2 \right) \\
+    & = 2 \left( (\rho_{M,N} - \rho_M)^2 + (\rho_M - \rho)^2 \right) \\
+    & = 2  (\rho_{M,N} - \rho_M)^2 + 2 (\rho_M - \rho)^2.
+\end{align*}
+The last equality follows from Assumption~\ref{as1:sns}.
 The analysis of the first term is different for smooth and Lipschitz continuous $h$. 
@@
 Due to high computational costs, we are not able to conduct experiments for higher budget levels, but we expect the \gls{mse} of the regression-based nested simulation procedure to stabilize after $\Gamma = 10^6$, and the empirical rate of convergence to approach its asymptotic rate.
+\textcolor{red}{The empirical convergence rates reported in the graph legends are higher than the actual rates after regression-based nested simulation procedure reaches the asymptotic convergence regime.}
 In the context of nested simulation procedures, a parametric regression metamodel has several advantages over a non-parametric regression metamodel.

### 2025-04-19 project2/nnMetamodels.tex
asd

@@
 
-Estimating tail risk measures of portfolios of complex \gls{va}s usually requires nested simulation.
-In the nested simulation, the outer simulation involves projecting scenarios of key risk factors under a $\mathbb{P}$ measure, while the inner simulations are used to value payoffs uder guarantees of varying complexity, under a $\mathbb{Q}$ measure.
-
-For insurers, large-scale nested simulations for assessing \gls{va} losses are generally computationally intensive; i.e., a large number of outer level simulations are needed to estimate extreme tails for calculations of tail risk measures, and a large number of inner simulations are also needed at each time step, because the embedded options are out of money.
+\textcolor{red}{Estimating tail risk measures of portfolios of complex \gls{va}s usually requires nested simulation.
+In the nested simulation, the outer simulation involves projecting scenarios of key risk factors under a $\mathbb{P}$ measure, while the inner simulations are used to value payoffs uder guarantees of varying complexity, under a $\mathbb{Q}$ measure.}
+
+\textcolor{red}{For insurers, large-scale nested simulations for assessing \gls{va} losses are generally computationally intensive; i.e., a large number of outer level simulations are needed to estimate extreme tails for calculations of tail risk measures, and a large number of inner simulations are also needed at each time step, because the embedded options are out of money.
 In addition, the required calculations need to be repeated for each \gls{va} contract, or cluster of \gls{va} contracts.
-Consequently, insurers are interested in techniques for nested simulation models that produce accurate results within the confines of a finite computational budget.
-
-There are two main approaches that can be used to improve the efficiency of inner simulations.
+Consequently, insurers are interested in techniques for nested simulation models that produce accurate results within the confines of a finite computational budget.}
+
+\textcolor{red}{There are two main approaches that can be used to improve the efficiency of inner simulations.
 The first one uses a dynamic, non-uniform allocation of the inner simulation budget, and the second uses a proxy model to replace the inner simulation step.
-Some work uses a combination of both approaches.
-
-In Chapter~\ref{chap:project1}, the likelihood ratio approach is used to allocate the inner simulation budget using likelihood ratio weights, i.e., importance sampling.
+Some work uses a combination of both approaches.}
+
+\textcolor{red}{In Chapter~\ref{chap:project1}, the likelihood ratio approach is used to allocate the inner simulation budget using likelihood ratio weights, i.e., importance sampling.
 Proxy models are tractable analytic functions or flexible empirical functions that are used to replace the inner simulation stage of a nested simulation.
@@
 This chapter introduces a proxy model to reduce the computational requirements of inner simulations of \gls{va}s by replacing the inner simulation step of a nested simulation procedure. 
-This proxy model is chosen to be a flexible empirical function, i.e., a \gls{dnn} metamodel.
+This proxy model is chosen to be a flexible empirical function, i.e., a \gls{dnn} metamodel.}
 
@@
 \begin{equation}
-    (\tilde{X}_{t, t}) = (\tilde{S}_{t, t}, \tilde{F}_{t, t}, \tilde{G}_{t, t}) = (S_t, F_t, G_t) = (X_t)
+    (\tilde{S}_{t, t}, \tilde{F}_{t, t}, \tilde{G}_{t, t}) = (S_t, F_t, G_t) 
 \end{equation}
@@
   & = H_0 + \sum_{t=1}^{T-1} e^{-rt} (H_t - H_t^{bf}) - e^{-rT} H^{bf}_T + V_0  \nonumber \\
-  & = B_0 + S_0 V_0 + \sum_{t=1}^{T-1} e^{-rt} \left( B_t + S_t \Delta_t - B_{t-1} \frac{e^{-r(t-1)}}{e^{-rt}} - S_{t-1} \Delta_{t-1}  \right) - e^{-rT} S_T \Delta_{T-1} + V_0,  \nonumber 
+  & = B_0 + S_0 V_0 + \sum_{t=1}^{T-1} e^{-rt} \left( B_t + S_t \Delta_t - B_{t-1} \frac{e^{-r(t-1)}}{e^{-rt}} - S_{t-1} \Delta_{t-1}  \right) - e^{-rT} S_T \Delta_{T-1} + V_0,  
 \end{align}
@@
 \end{algorithm}
+
+\textcolor{red}{In the two-stage procedure, the neural network metamodel approximates $L$ in Equation~\ref{eq2:lossrv}, where }
+\begin{equation}
+    L = L(\mathbf{S}_T) = L(\Delta_0, \ldots, \Delta_{T-1}, S_0, \ldots, S_T)
+\end{equation}
+\textcolor{red}{The loss $L$ depends on all the hedging weights $\Delta_0, \ldots, \Delta_{T-1}$, which are determined by the stock prices $S_t$, $t=0,\ldots,T-1$.}
+\textcolor{red}{In addition, $L$ also depends on all the stock prices $S_0, \ldots, S_T$ directly.}
+\textcolor{red}{Therefore, the loss $L(\mathbf{S}_T)$ is a complex function of the entire stock price path $\mathbf{S}_T$, and the neural network metamodel $\Lhat^{PD}(\mathbf{X})$ approximates $L(\mathbf{S}_T)$ by mapping the stock returns $\mathbf{X}_T$ to the loss $L(\mathbf{S}_T)$.}
+\textcolor{red}{Statistically speaking, $L(\mathbf{S}_T)$ is a random variable whose stochasticity solely depends on the stock price path $\mathbf{S}_T$. }
+\textcolor{red}{Nevertheless, $L(\mathbf{S}_T)$ can be viewed as a function of the underlying stock returns $\mathbf{X}_T$ and can be approximated by a neural network metamodel.}
 

### 2025-04-26 project1/nsSurvey.tex
qwe

@@
     Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
-    We write $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-\xi})$, that is $\hat{\rho}_{\Gamma}$ converges in probabilistic order $\xi$ to $\rho$ if for a sufficiently large $\Gamma$, \textcolor{red}{for any $\epsilon > 0$ there exists a $C_\epsilon$ such that}
-    $$
-         \mathbb{P} \left( \left| \hat{\rho}_{\Gamma} - \rho \right| \geq C_\epsilon \Gamma^{-\xi} \right) \leq \epsilon.
+    We write $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-\xi})$, that is $\hat{\rho}_{\Gamma}$ converges in probabilistic order $\xi$ to $\rho$ if for a sufficiently large $\Gamma$, for any $\epsilon > 0$ there exists a $C$ such that
+    $$
+         \mathbb{P} \left( \left| \hat{\rho}_{\Gamma} - \rho \right| \geq C \Gamma^{-\xi} \right) \leq \epsilon.
     $$
@@
 We start our analysis by showing the convergence in probabilistic order from the convergence in \gls{mse}.
-Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-\xi} \right)$.
-Then, from the definition of convergence in \gls{mse}, there exists a constant $C$ such that 
-$$
-    \limsup_{\Gamma} \frac{\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-\xi}} \leq C.
-$$
-Hence, there exists some $\Gamma$ such that for all $\gamma \geq \Gamma$,
-$$
-\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \right] \leq C\gamma^{-\xi}.
-$$
-The convergence in probabilistic order can be shown by separating the expectation into two parts: tail and non-tail components.
-$$
-\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| \leq d\gamma^s\}} \right] + \mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\}} \right] \leq C\gamma^{-\xi}.
-$$
-The first term is always positive, and the second term can be bounded from below by the indicator function.
-\begin{align*}
-\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\}} \right] 
-& \geq \mathbb{E} \left[ d^2 \gamma^{2s} \cdot \mathbb{I}\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\} \right] \\
-& = d^2 \gamma^{2s} \cdot \mathbb{E} \left[ \mathbb{I}\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \} \right] \\
-& = d^2 \gamma^{2s} \cdot \mathbb{P} \left(|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \right).
-\end{align*}
-
-Combining bounds on the two terms, we have
-
-$$
-    d^2 \gamma^{2s} \mathbb{P} \left(|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \right) \leq C \gamma^{-\xi}.
-$$
-
-Let $s = -\frac{\xi}{2}$. Arranging the terms, we have
-
-$$
-    \mathbb{P} \left( |\hat{\rho}_{\gamma} - \rho| > d\gamma^{-\frac{\xi}{2}} \right) \leq \frac{C}{d^2}.
-$$
-
-Hence, for all $\epsilon >0$, there exist $C^* = \sqrt{\frac{C}{\epsilon}}$ such that for all $\gamma \geq \Gamma$,
-
-$$
-    \mathbb{P} \left( |\hat{\rho}_{\gamma} - \rho| > C^*\gamma^{-\frac{\xi}{2}} \right) \leq \epsilon
-$$
-
-In essence, the above expression is a definition of convergence in probabilistic order, that is,
-
-$$
-    \left| \hat{\rho}_{\gamma} - \rho \right| = \mathcal{O}_\mathbb{P} \left( \Gamma^{-\frac{\xi}{2}} \right).
-$$
-
-\begin{theorem}\label{thm1:convergence-mse-prob}
-    Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
-    If $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $\xi$, then $\hat{\rho}_{\Gamma}$ converges in probabilistic order to $\rho$ in order $\frac{\xi}{2}$.
-\end{theorem}
-
-Theorem~\ref{thm1:convergence-mse-prob} provides a formal connection between the \textcolor{red}{rate of convergence} in \gls{mse} and that in probabilistic order for \gls{ae} in the context of nested simulation.
-It is a general result that can be applied to any nested simulation procedure that converges in \gls{mse} to $\rho$ in order $\xi$.
-If the estimator converges in \gls{mse} to $\rho$ in order $\xi$, then it converges in probabilistic order to $\rho$ in order $\frac{\xi}{2}$.
-
-While the convergence in \gls{mse} implies the convergence in probabilistic order, the converse is not necessarily true.
-Similarly, the above argument is applied in reverse.
-Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-\xi})$.
-The \gls{mse} of $\hat{\rho}_{\Gamma}$ can be separated into the same two parts.
-
-$$
-    \mathbb{E}\left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| \leq d\Gamma^{-2\xi}\}} \right] + \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^{-2\xi}\}} \right],
-$$
-where the first term can be bounded from above.
-
-\begin{align*}
-    \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s\}} \right] 
-    & \leq d^2 \Gamma^{-2\xi} \cdot \mathbb{E} \left[ \mathbb{I}\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s \} \right] \\
-    & = d^2 \Gamma^{-2\xi} \cdot \mathbb{P} \left(|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s \right) \leq d^2 \Gamma^{-2\xi}.
-\end{align*}
-However, the second term is not always bounded. 
-If the random variable $\hat{\rho}_{\Gamma}$ admits a density function $f$, then the second term can be further decomposed as follows.
-
-\begin{align*}
-    \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^{-2\xi}\}} \right] 
-    & = \int_{-\infty}^{-d\Gamma^{-2k}} (x - \rho)^2 f(x) dx + \int_{d\Gamma^{-2\xi}}^{\infty} (x - \rho)^2 f(x) dx.
-\end{align*}
-Hence, $\hat{\rho}_{\Gamma}$ converges in \gls{mse} to $\rho$ in order $2\xi$ if and only if both integrals converge in order higher than $2\xi$. 
-The above argument shows that the convergence in probabilistic order does not necessarily imply the convergence in \gls{mse}.
-Hence, the converse of Theorem~\ref{thm1:convergence-mse-prob} is not necessarily true, and the convergence in probabilistic order is a weaker form of convergence than the convergence in \gls{mse}.
-The immediate implication of this result is that the results in~\cite{wang2022smooth}, which show the convergence in probabilistic order for the \gls{ae} is not necessarily equivalent to the convergence in \gls{mse}.
+\textcolor{red}{Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-\xi-\delta} \right)$ for an arbitrarily small $\delta > 0$.}
+\textcolor{red}{Then, from the definition of convergence in \gls{mse}, }
+$$
+    \limsup_{\Gamma \to \infty} \frac{\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-\xi-\delta}} \leq C.
+$$
+\textcolor{red}{for a constant $C > 0$.}
+
+\textcolor{red}{The above inequality implies that}
+$$
+\limsup_{\Gamma \to \infty} \frac{\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-\xi}} =0.
+$$
+
+\textcolor{red}{Therefore, by Chebyshev's inequality, for any $\epsilon > 0$, we have}
+$$
+\mathbb{P} \left( \left| \hat{\rho}_{\Gamma} - \rho \right| \Gamma^{\xi/2} > C  \right) \leq \frac{\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \Gamma^{\xi} \right]}{C^2 } \rightarrow 0
+$$
+\textcolor{red}{as $\Gamma \to \infty$.}
+
+\textcolor{red}{Therefore, $\hat{\rho}_{\Gamma}$ converges in probabilistic order $\xi/2$ to $\rho$ as $\Gamma \to \infty$, that is,}
+$$
+\left| \hat{\rho}_{\Gamma} - \rho \right| = \mathcal{O}_{\mathbb{P}} \left( \Gamma^{-\xi/2} \right).
+$$
+
+% Hence, there exists some $\Gamma$ such that for all $\gamma \geq \Gamma$,
+% $$
+% \mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \right] \leq C\gamma^{-\xi-\delta}.
+% $$
+% The convergence in probabilistic order can be shown by separating the expectation into two parts: tail and non-tail components.
+% $$
+% \mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| \leq d\gamma^s\}} \right] + \mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\}} \right] \leq C\gamma^{-\xi}.
+% $$
+% The first term is always positive, and the second term can be bounded from below by the indicator function.
+% \begin{align*}
+% \mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\}} \right] 
+% & \geq \mathbb{E} \left[ d^2 \gamma^{2s} \cdot \mathbb{I}\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\} \right] \\
+% & = d^2 \gamma^{2s} \cdot \mathbb{E} \left[ \mathbb{I}\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \} \right] \\
+% & = d^2 \gamma^{2s} \cdot \mathbb{P} \left(|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \right).
+% \end{align*}
+
+% Combining bounds on the two terms, we have
+
+% $$
+%     d^2 \gamma^{2s} \mathbb{P} \left(|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \right) \leq C \gamma^{-\xi}.
+% $$
+
+% Let $s = -\frac{\xi}{2}$. Arranging the terms, we have
+
+% $$
+%     \mathbb{P} \left( |\hat{\rho}_{\gamma} - \rho| > d\gamma^{-\frac{\xi}{2}} \right) \leq \frac{C}{d^2}.
+% $$
+
+% Hence, for all $\epsilon >0$, there exist $C^* = \sqrt{\frac{C}{\epsilon}}$ such that for all $\gamma \geq \Gamma$,
+
+% $$
+%     \mathbb{P} \left( |\hat{\rho}_{\gamma} - \rho| > C^*\gamma^{-\frac{\xi}{2}} \right) \leq \epsilon
+% $$
+
+% In essence, the above expression is a definition of convergence in probabilistic order, that is,
+
+% $$
+%     \left| \hat{\rho}_{\gamma} - \rho \right| = \mathcal{O}_\mathbb{P} \left( \Gamma^{-\frac{\xi}{2}} \right).
+% $$
+
+% \begin{theorem}\label{thm1:convergence-mse-prob}
+%     Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
+%     If $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $\xi$, then $\hat{\rho}_{\Gamma}$ converges in probabilistic order to $\rho$ in order $\frac{\xi}{2}$.
+% \end{theorem}
+
+% Theorem~\ref{thm1:convergence-mse-prob} provides a formal connection between the \textcolor{red}{rate of convergence} in \gls{mse} and that in probabilistic order for \gls{ae} in the context of nested simulation.
+% It is a general result that can be applied to any nested simulation procedure that converges in \gls{mse} to $\rho$ in order $\xi$.
+% If the estimator converges in \gls{mse} to $\rho$ in order $\xi$, then it converges in probabilistic order to $\rho$ in order $\frac{\xi}{2}$.
+
+% While the convergence in \gls{mse} implies the convergence in probabilistic order, the converse is not necessarily true.
+% Similarly, the above argument is applied in reverse.
+% Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-\xi})$.
+% The \gls{mse} of $\hat{\rho}_{\Gamma}$ can be separated into the same two parts.
+
+% $$
+%     \mathbb{E}\left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| \leq d\Gamma^{-2\xi}\}} \right] + \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^{-2\xi}\}} \right],
+% $$
+% where the first term can be bounded from above.
+
+% \begin{align*}
+%     \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s\}} \right] 
+%     & \leq d^2 \Gamma^{-2\xi} \cdot \mathbb{E} \left[ \mathbb{I}\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s \} \right] \\
+%     & = d^2 \Gamma^{-2\xi} \cdot \mathbb{P} \left(|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s \right) \leq d^2 \Gamma^{-2\xi}.
+% \end{align*}
+% However, the second term is not always bounded. 
+% If the random variable $\hat{\rho}_{\Gamma}$ admits a density function $f$, then the second term can be further decomposed as follows.
+
+% \begin{align*}
+%     \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^{-2\xi}\}} \right] 
+%     & = \int_{-\infty}^{-d\Gamma^{-2k}} (x - \rho)^2 f(x) dx + \int_{d\Gamma^{-2\xi}}^{\infty} (x - \rho)^2 f(x) dx.
+% \end{align*}
+% Hence, $\hat{\rho}_{\Gamma}$ converges in \gls{mse} to $\rho$ in order $2\xi$ if and only if both integrals converge in order higher than $2\xi$. 
+% The above argument shows that the convergence in probabilistic order does not necessarily imply the convergence in \gls{mse}.
+% Hence, the converse of Theorem~\ref{thm1:convergence-mse-prob} is not necessarily true, and the convergence in probabilistic order is a weaker form of convergence than the convergence in \gls{mse}.
+% The immediate implication of this result is that the results in~\cite{wang2022smooth}, which show the convergence in probabilistic order for the \gls{ae} is not necessarily equivalent to the convergence in \gls{mse}.
 

### 2025-04-30 project1/nsSurvey.tex
1

--- 2025-04-19 project1/nsSurvey.tex
@@
 This paper presents a survey study of some popular nested simulation procedures that have both asymptotic convergence analysis and finite-sample performance evaluation.
-Many procedures have been proposed in the literature, but they are not directly comparable because they use different error metrics, different assumptions, and different numerical examples in their studies.
+Many procedures have been proposed in the literature, but they are not directly comparable because they use \textcolor{red}{\sout{different error metrics,}} different assumptions and different numerical examples in their studies.
 Within a common analytical framework, we first summarize and compare the asymptotic convergence rates of these procedures.
 Their asymptotic convergence results are closely examined for their assumptions that guarantee the convergence.
-Furthermore, the existing literature has chosen different performance metrics to evaluate the asymptotic convergence of nested simulation procedures.
+\textcolor{red}{\sout{Furthermore, the existing literature has chosen different performance metrics to evaluate the asymptotic convergence of nested simulation procedures.
 In this chapter, we discuss the asymptotic convergence in terms of \gls{mse} of the estimator, and we provide a comprehensive comparison of their convergence rates and critical assumptions.
-We also discuss the connection between the \gls{mse} and the absolute error of the estimator in the context of nested simulation procedures.
+We also discuss the connection between the \gls{mse} and the absolute error of the estimator in the context of nested simulation procedures.}}
 
@@
 In general, a more complex metamodel requires a higher-order smoothness for $h$ for its convergence analysis.
-Despite being more advanced than kernel smoothing, the \gls{var}-based procedure requires a less stringent smoothness assumption on $h$.
+Despite being more advanced than kernel smoothing, the \gls{krr}-based procedure requires a less stringent smoothness assumption on $h$.
 At first sight, it is counterintuitive that a more complex metamodel requires a less stringent smoothness assumption.
-This phenomenon is due to the fact that the convergence analysis for the \gls{var}-based nested simulation procedure is shown in terms of an \gls{ae}, which is a less stringent error metric than \gls{mse}.
-Section~\ref{sec1:connection-mse-absolute-error} discusses the connection between the \gls{mse} and the \gls{ae} of the estimator in the context of nested simulation procedures.
+This phenomenon is due to the fact that the convergence analysis for the \gls{krr}-based nested simulation procedure is shown in terms of \textcolor{red}{\gls{ae}, a different error metric than \gls{mse}.}
+\textcolor{red}{In the appendix,} Section~\ref{appendix:connection-mse-absolute-error} includes a discussion of the connection between the \gls{mse} and the \gls{ae} of the estimator in the context of nested simulation procedures.
 In Table~\ref{tab1:smoothness}, the standard nested simulation procedure is the only procedure without an asymptotic convergence analysis for smooth $h$.
@@
 
-    \item   \gls{var}:
+    \item   \gls{krr}:
             $$\hat{L}^{\text{KRR}}_{M, N}(X) = \argmin_{g \in \mathcal{N}_{\Psi}(\Omega)} \left( \frac{1}{M} \sum_{i=1}^M (\hat{L}_{N, i} - L_i)^2 + \lambda \|L\|_{\mathcal{N}_{\Psi}(\Omega)}^2\right),$$
@@
 
-For the more complex metamodels, the convergence analysis of their \gls{mse}s is more challenging.
-More specifically, the \gls{var}-based nested simulation~\citep{wang2022smooth} provides a convergence analysis in terms of \gls{ae}.
+\textcolor{red}{Theoretical properties of different metamodels lead to different convergence results.}
+More specifically, the \gls{krr}-based nested simulation~\citep{wang2022smooth} provides a convergence analysis in terms of \gls{ae}.
 \begin{align}\label{eq1:ae}
@@
 \end{align}
-Section~\ref{sec1:connection-mse-absolute-error} draws the connection between the \gls{mse} and the \gls{ae} of the estimator in the context of nested simulation procedures.
+Section~\ref{appendix:connection-mse-absolute-error} draws the connection between the \gls{mse} and the \gls{ae} of the estimator in the context of nested simulation procedures.
 
@@
 \begin{itemize}
-    \item provide the asymptotic convergence results for the standard nested simulation procedure, 
-    \item show the connections between the convergence in \gls{mse} and the convergence in probabilistic order for \gls{ae} in the context of nested simulation procedures, and
+    \item provide the asymptotic convergence results for the standard nested simulation procedure, \textcolor{red}{and}
+    \item \textcolor{red}{\sout{show the connections between the convergence in \gls{mse} and the convergence in probabilistic order for \gls{ae} in the context of nested simulation procedures, and}}
     \item illustrate the asymptotic rate of convergence of a \gls{knn}-based nested simulation procedure.
@@
 
-In~\cite{wang2022smooth}, the authors of the \gls{var}-based nested simulation procedures claim to have bridged the gap between the cubic and square root convergence rates of nested simulation procedures.
+In~\cite{wang2022smooth}, the authors of the \gls{krr}-based nested simulation procedures claim to have bridged the gap between the cubic and square root convergence rates of nested simulation procedures.
 However, they analyze convergence in probabilistic order, and it is only applicable in terms of \gls{ae}.
-Instead of showing the convergence of the \gls{var}-based estimator in terms of \gls{mse} as in~\cite{gordy2010nested}, we show the connections between the convergence in \gls{mse} and the convergence in probabilistic order for \gls{ae}.
-Our findings in Section~\ref{sec1:connection-mse-absolute-error} show that the analysis of ~\cite{wang2022smooth} indeed bridges the gap, but only in terms of convergence in probabilistic order for \gls{ae}.
-
-\subsection{Connections between Convergence in MSE and AE}\label{sec1:connection-mse-absolute-error}
-
-This section establishes the connections between the convergence in \gls{mse} and the convergence in probabilistic order for \gls{ae} in the context of nested simulation procedures.
-In order to show the connections between the convergence in \gls{mse} and the convergence in probabilistic order for \gls{ae}, we first need to state the definition for a sequence of random variables to converge in those two forms.
-
-\begin{definition}
-    Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
-    We write $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-\xi} \right)$, that is, $\hat{\rho}_{\Gamma}$ converges in \gls{mse} to $\rho$ in order $\xi$ if there exists a constant $C$ such that
-    $$
-        \limsup_{\Gamma \to \infty} \frac{\mathbb{E} \left[\left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-\xi}} \leq C.
-    $$
-\end{definition}
-
-\begin{definition}
-    Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
-    We write $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-\xi})$, that is $\hat{\rho}_{\Gamma}$ converges in probabilistic order $\xi$ to $\rho$ if for a sufficiently large $\Gamma$, \textcolor{red}{for any $\epsilon > 0$ there exists a $C_\epsilon$ such that}
-    $$
-         \mathbb{P} \left( \left| \hat{\rho}_{\Gamma} - \rho \right| \geq C_\epsilon \Gamma^{-\xi} \right) \leq \epsilon.
-    $$
-\end{definition}
-
-We start our analysis by showing the convergence in probabilistic order from the convergence in \gls{mse}.
-Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-\xi} \right)$.
-Then, from the definition of convergence in \gls{mse}, there exists a constant $C$ such that 
-$$
-    \limsup_{\Gamma} \frac{\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-\xi}} \leq C.
-$$
-Hence, there exists some $\Gamma$ such that for all $\gamma \geq \Gamma$,
-$$
-\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \right] \leq C\gamma^{-\xi}.
-$$
-The convergence in probabilistic order can be shown by separating the expectation into two parts: tail and non-tail components.
-$$
-\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| \leq d\gamma^s\}} \right] + \mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\}} \right] \leq C\gamma^{-\xi}.
-$$
-The first term is always positive, and the second term can be bounded from below by the indicator function.
-\begin{align*}
-\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\}} \right] 
-& \geq \mathbb{E} \left[ d^2 \gamma^{2s} \cdot \mathbb{I}\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\} \right] \\
-& = d^2 \gamma^{2s} \cdot \mathbb{E} \left[ \mathbb{I}\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \} \right] \\
-& = d^2 \gamma^{2s} \cdot \mathbb{P} \left(|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \right).
-\end{align*}
-
-Combining bounds on the two terms, we have
-
-$$
-    d^2 \gamma^{2s} \mathbb{P} \left(|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \right) \leq C \gamma^{-\xi}.
-$$
-
-Let $s = -\frac{\xi}{2}$. Arranging the terms, we have
-
-$$
-    \mathbb{P} \left( |\hat{\rho}_{\gamma} - \rho| > d\gamma^{-\frac{\xi}{2}} \right) \leq \frac{C}{d^2}.
-$$
-
-Hence, for all $\epsilon >0$, there exist $C^* = \sqrt{\frac{C}{\epsilon}}$ such that for all $\gamma \geq \Gamma$,
-
-$$
-    \mathbb{P} \left( |\hat{\rho}_{\gamma} - \rho| > C^*\gamma^{-\frac{\xi}{2}} \right) \leq \epsilon
-$$
-
-In essence, the above expression is a definition of convergence in probabilistic order, that is,
-
-$$
-    \left| \hat{\rho}_{\gamma} - \rho \right| = \mathcal{O}_\mathbb{P} \left( \Gamma^{-\frac{\xi}{2}} \right).
-$$
-
-\begin{theorem}\label{thm1:convergence-mse-prob}
-    Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
-    If $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $\xi$, then $\hat{\rho}_{\Gamma}$ converges in probabilistic order to $\rho$ in order $\frac{\xi}{2}$.
-\end{theorem}
-
-Theorem~\ref{thm1:convergence-mse-prob} provides a formal connection between the \textcolor{red}{rate of convergence} in \gls{mse} and that in probabilistic order for \gls{ae} in the context of nested simulation.
-It is a general result that can be applied to any nested simulation procedure that converges in \gls{mse} to $\rho$ in order $\xi$.
-If the estimator converges in \gls{mse} to $\rho$ in order $\xi$, then it converges in probabilistic order to $\rho$ in order $\frac{\xi}{2}$.
-
-While the convergence in \gls{mse} implies the convergence in probabilistic order, the converse is not necessarily true.
-Similarly, the above argument is applied in reverse.
-Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-\xi})$.
-The \gls{mse} of $\hat{\rho}_{\Gamma}$ can be separated into the same two parts.
-
-$$
-    \mathbb{E}\left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| \leq d\Gamma^{-2\xi}\}} \right] + \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^{-2\xi}\}} \right],
-$$
-where the first term can be bounded from above.
-
-\begin{align*}
-    \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s\}} \right] 
-    & \leq d^2 \Gamma^{-2\xi} \cdot \mathbb{E} \left[ \mathbb{I}\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s \} \right] \\
-    & = d^2 \Gamma^{-2\xi} \cdot \mathbb{P} \left(|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s \right) \leq d^2 \Gamma^{-2\xi}.
-\end{align*}
-However, the second term is not always bounded. 
-If the random variable $\hat{\rho}_{\Gamma}$ admits a density function $f$, then the second term can be further decomposed as follows.
-
-\begin{align*}
-    \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^{-2\xi}\}} \right] 
-    & = \int_{-\infty}^{-d\Gamma^{-2k}} (x - \rho)^2 f(x) dx + \int_{d\Gamma^{-2\xi}}^{\infty} (x - \rho)^2 f(x) dx.
-\end{align*}
-Hence, $\hat{\rho}_{\Gamma}$ converges in \gls{mse} to $\rho$ in order $2\xi$ if and only if both integrals converge in order higher than $2\xi$. 
-The above argument shows that the convergence in probabilistic order does not necessarily imply the convergence in \gls{mse}.
-Hence, the converse of Theorem~\ref{thm1:convergence-mse-prob} is not necessarily true, and the convergence in probabilistic order is a weaker form of convergence than the convergence in \gls{mse}.
-The immediate implication of this result is that the results in~\cite{wang2022smooth}, which show the convergence in probabilistic order for the \gls{ae} is not necessarily equivalent to the convergence in \gls{mse}.
+\textcolor{red}{In Section~\ref{appendix:connection-mse-absolute-error}, we illustrate the connection between the convergence in \gls{mse} and the convergence in \gls{ae}.}
 
@@
 Assumption~\ref{as1:sns-noise-var} is a moment condition that is easier to verify in practice than conditions on the joint density.
-As stated in Theorem~\ref{thm1:convergence-mse-prob}, the convergence in \gls{mse} automatically implies the convergence in probabilistic order.
-
-\begin{corollary}
-    Let $h$ be a smooth function. 
-    The AE of the standard nested simulation procedure converges in probabilistic order $\Gamma^{-1/3}$, that is,
-    $$\left| \hat{\rho}_{M, N} - \rho \right| = \mathcal{O}_\mathbb{P}(\Gamma^{-1/3}).$$
-\end{corollary}
+\textcolor{red}{\sout{As stated in Theorem, the convergence in \gls{mse} automatically implies the convergence in probabilistic order.}}
+
+% \begin{corollary}
+%     Let $h$ be a smooth function. 
+%     The AE of the standard nested simulation procedure converges in probabilistic order $\Gamma^{-1/3}$, that is,
+%     $$\left| \hat{\rho}_{M, N} - \rho \right| = \mathcal{O}_\mathbb{P}(\Gamma^{-1/3}).$$
+% \end{corollary}
 
@@
 
-Immediately from Theorem~\ref{thm1:convergence-mse-prob}, the convergence in \gls{mse} automatically implies the convergence in probabilistic order.
-
-\begin{corollary}
-    Let $h$ be a Lipschitz continuous function. AE of the standard nested simulation procedure converges in probabilistic order $\Gamma^{-1/3}$, that is,
-    $$\left| \hat{\rho}_{M, N} - \rho \right| = \mathcal{O}_\mathbb{P}(\Gamma^{-1/4}).$$
-\end{corollary}
+\textcolor{red}{\sout{Immediately from Theorem, the convergence in \gls{mse} automatically implies the convergence in probabilistic order.}}
+
+% \begin{corollary}
+%     Let $h$ be a Lipschitz continuous function. AE of the standard nested simulation procedure converges in probabilistic order $\Gamma^{-1/3}$, that is,
+%     $$\left| \hat{\rho}_{M, N} - \rho \right| = \mathcal{O}_\mathbb{P}(\Gamma^{-1/4}).$$
+% \end{corollary}
 
@@
 \subsection{Assumptions for the KRR-Based Procedure}
-For the \gls{var}-based nested simulation procedure, the convergence is guaranteed only when $\bar{Z}_N(X)$ is the sum of $N$ i.i.d. zero-mean sub-Gaussian random variables.
+For the \gls{krr}-based nested simulation procedure, the convergence is guaranteed only when $\bar{Z}_N(X)$ is the sum of $N$ i.i.d. zero-mean sub-Gaussian random variables.
 The sub-Gaussian assumption imposes a stronger condition on the inner simulation noise than all the other nested simulation procedures.
@@
 Assumption~\ref{as1:krr-domain} rules out the possibility of the outer scenario $X$ being a normal random variable, which is a common assumption in the literature.
-Furthermore, the convergence analysis of the \gls{var}-based nested simulation procedure is shown in terms of \gls{ae} rather than in \gls{mse}, which is due to the complexity of the KRR metatmodel.
+Furthermore, the convergence analysis of the \gls{krr}-based nested simulation procedure is shown in terms of \gls{ae} rather than in \gls{mse}, which is due to the \textcolor{red}{analytical properties} of the KRR metatmodel.
 
@@
 However, pooling also introduces additional computational cost that is not reflected in the simulation budget $\Gamma$.
-Due to the computational complexity of the likelihood ratio-based and the \gls{var}-based procedures, their \gls{mse}s are not reported for $\Gamma$ larger than $\num{16000}$ and $\num{64000}$, respectively.
+Due to the computational complexity of the likelihood ratio-based and the \gls{krr}-based procedures, their \gls{mse}s are not reported for $\Gamma$ larger than $\num{16000}$ and $\num{64000}$, respectively.
 Detailed discussion of the additional computational cost of pooling is provided in Section~\ref{sec1:computational-complexity}.
@@
 In Figure~\ref{fig1:assetDimension}, the empirical convergence of the nested simulation procedures for a quadratic tracking error on Portfolio 1 is illustrated for different asset dimensions, i.e., $d = 2$ and $d = 20$.
-The empirical rates of convergence of the standard, the \gls{var}-based, and the likelihood ratio-based procedures closely match their asymptotic rates for both asset dimensions, and they are insensitive to an increase in the asset dimension.
+The empirical rates of convergence of the standard, the \gls{krr}-based, and the likelihood ratio-based procedures closely match their asymptotic rates for both asset dimensions, and they are insensitive to an increase in the asset dimension.
 In contrast, both the kernel smoothing-based and regression-based procedures are greatly affected by the asset dimension.
@@
 This observation suggests that the empirical convergence of the kernel smoothing-based nested simulation procedure is highly sensitive to the cross-validation of the hyperparameters of the metamodel.
-A \gls{var}-based nested simulation procedure suffers from the same problem. 
+A \gls{krr}-based nested simulation procedure suffers from the same problem. 
 The fluctuation in Figure~\ref{fig1:kernel_d} is likely due to poor cross-validation of the hyperparameters of the metamodel.
@@
 In Figure~\ref{fig1:1x03}, the empirical convergence of the nested simulation procedures for the quadratic tracking errors of Portfolio 1 and Portfolio 4 is illustrated for $d = 20$.
-The empirical rates of standard, likelihood ratio-based, and \gls{var}-based nested simulation procedures closely ensemble their asymptotic rates for path-dependent options.
+The empirical rates of standard, likelihood ratio-based, and \gls{krr}-based nested simulation procedures closely ensemble their asymptotic rates for path-dependent options.
 The empirical rate of convergence of the regression-based and kernel smoothing-based procedures is much higher than their asymptotic rates for barrier options. 
@@
 For all procedures, we observe a similar convergence behavior as in other path-dependent options.
-The \gls{mse}s of the kernel smoothing-based and \gls{var}-based procedures do not decrease monotonically as the simulation budget increases.
+The \gls{mse}s of the kernel smoothing-based and \gls{krr}-based procedures do not decrease monotonically as the simulation budget increases.
 This fluctuating behavior is observed and analyzed in Section~\ref{sec1:kernel-smoothing-convergence}.
@@
 \end{itemize}
-For the \gls{var}-based procedure, 
+For the \gls{krr}-based procedure, 
 \begin{itemize}
@@
           Similar to the regression-based procedure, this complexity can be reduced to $\mathcal{O}(M^{2.376})$.
-    \item The prediction cost of the \gls{var}-based procedure is $\mathcal{O}(M^2)$, which comes from the multiplication of the kernel matrix by the estimated coefficients.
+    \item The prediction cost of the \gls{krr}-based procedure is $\mathcal{O}(M^2)$, which comes from the multiplication of the kernel matrix by the estimated coefficients.
 \end{itemize}
@@
 Since the regression-based procedure has a higher empirical rate of convergence, it is preferred over \gls{knn}.
-The likelihood ratio-based and \gls{var}-based procedures are the most computationally expensive among all procedures.
+The likelihood ratio-based and \gls{krr}-based procedures are the most computationally expensive among all procedures.
 They are also demanding in terms of memory.
 For budgets larger than $10^5$, the likelihood ratio-based procedure becomes impractical as storage of the likelihood weights becomes a bottleneck.
-The \gls{var}-based procedure suffers from both cross-validation and inverting a kernel matrix of size $M \times M$.
+The \gls{krr}-based procedure suffers from both cross-validation and inverting a kernel matrix of size $M \times M$.
 To separate the total computational time into different attributes, we provide a detailed analysis of the total computational time in the remainder of this section.
@@
     The slope of the regression line is close to $1$, resembling its algorithmic complexity reported in Table~\ref{tab1:complexity}.
-    \item The kernel smoothing-based and \gls{var}-based procedure requires a cross-validation procedure to estimate the optimal hyperparameters. 
+    \item The kernel smoothing-based and \gls{krr}-based procedure requires a cross-validation procedure to estimate the optimal hyperparameters. 
     In our implementation of \gls{knn}, the cross-validation is conducted by using a grid search with a search space which cardinality does not grow with the simulation budget $\Gamma$.
     However, the cross-validation cost of the kernel smoothing-based procedure grows with the simulation budget $\Gamma$ as more samples are involved.
-    The \gls{var}-based procedure requires a Bayesian optimization to estimate the optimal hyperparameters, and the cardinality of the search space also grows with the simulation budget $\Gamma$.
-    The empirical cost of the \gls{var}-based procedure does not resemble its algorithmic complexity reported in Table~\ref{tab1:complexity}.
+    The \gls{krr}-based procedure requires a Bayesian optimization to estimate the optimal hyperparameters, and the cardinality of the search space also grows with the simulation budget $\Gamma$.
+    The empirical cost of the \gls{krr}-based procedure does not resemble its algorithmic complexity reported in Table~\ref{tab1:complexity}.
     The efficient implementation of \gls{var} is an active area of research, and the computational cost of \gls{var} can be reduced by using a low-rank approximation of the kernel matrix, e.g., the Nystr\"om method~\citep{nystrom1930praktische}.
@@
 To show an asymptotic convergence result, a more complex metamodels requires a more stringent set of assumptions on the distribution of the outer scenario and the inner simulation noise.
+\textcolor{red}{In terms of finite-sample behavior, this study provides a comprehensive comparison of different nested simulation procedures, and the findings can be used to guide the choice of a proper nested simulation procedure for a given nested estimation problem.}
 With extensive numerical experiments, we have found that the finite-sample performance of a procedure can deviate from its theory. 
@@
 A \gls{knn}-based procedure is sensitive to the asset dimension and the problem complexity.
-A \gls{var}-based procedure is computationally expensive, and its cost grows quickly with the simulation budget.
+A \gls{krr}-based procedure is computationally expensive, and its cost grows quickly with the simulation budget.
 For kernel-based procedures, the computational cost is heavily dependent on the efficient implementation of the associated algorithms.

### 2025-04-30 WorkToBeDone_ThesisRevision/ThesisRevision.tex
Updates from Overleaf

\documentclass[letterpaper]{article}

\usepackage{mathtools}
\usepackage{amsthm}
\usepackage{thmtools}
\usepackage{xcolor}
\usepackage{bm}

\usepackage[margin=1in]{geometry}

\begin{document}

\begin{center}
\large
    Revisions needed for Xintong's thesis (Ben's notes)
\end{center}

\begin{enumerate}
    \item Add sufficient details to \textbf{every} numerical experiments. (suggested by Emil)
    \begin{enumerate}
        \item Dynamic asset model (e.g., Black-Scholes, regime-switching, etc.)
        \item All model parameters (i.e., risk-free rates, volatilities, correlations in all regimes, etc.).
        \item Computing platforms, if applicable (i.e., personal laptop, desktop, university servers, etc.)
    \end{enumerate}

    \item Add an appendix to summarize all acronyms (suggested by Emil)
    \begin{enumerate}
        \item I think at least two summary tables are needed: One for different variable annuity riders (i.e., GMWB, GMMB, GLWB, etc.) and one for different machine learning models (i.e., QPR, RNN, LSTM, etc.).

        \item You might want to add a third table to summarize other acronyms that don't fall into the above two categories.
    \end{enumerate}

    \item Clarify expected values, sample average as an estimator of the expected value, and pathwise sample of an expected value. (suggested by Yuying). This is \textbf{a major issue and a high-priority item} that must be properly addressed. Tony has offered some helpful insights in his notes. I give mine too below.

    \begin{enumerate}
        \item Use GMMB as an example to explain the missing expectation that Yuying had in mind: An insurer's time-$t$ liability for a GMMB contract
        \begin{align*}
            V_t = V(\bm{S}_t) = E[e^{-r(T-t)}(G_T-F_T)^+ - \sum_{s=t+1}^T e^-r(T-s) F_s \eta_n | \bm{S}_t]
        \end{align*}
    where
    \begin{enumerate}
        \item $\bm{S}_t$ is the (outer) stock path up to time $t$
        \item The (conditional) expectation is taken with respect to the inner sample path $\widetilde{S}_{t+1},\ldots,\widetilde{S}_T$ given the outer path $\bm{S}_t$
    \end{enumerate}
    By removing the (conditional) expectation, I believe you meant the time-$t$ liability for one simulate inner path. But the value for one simulated path does not equal to the (conditional) expected value.

    Please do a global check. When revising the thesis, please try to understand readers' perspective. A reader who has not gone through this project would easily be confused. So your writing needs to be very clear in every detail.

    \item Similar idea for the pathwise delta
    \begin{align*}
        \Delta_t(\widetilde{S}_{t+1},\ldots,\widetilde{S}_T | \bm{S}_t) &= \frac{\partial V_t}{\partial S_t} \\
        &= \frac{\partial }{\partial S_t} V(\bm{S}_t)\\
        &=\frac{\partial }{\partial S_t} E[e^{-r(T-t)}(G_T-F_T)^+ - \sum_{s=t+1}^T e^-r(T-s) F_s \eta_n | \bm{S}_t]\\
        &\stackrel{*}{=} E[\frac{\partial }{\partial S_t}e^{-r(T-t)}(G_T-F_T)^+ - \sum_{s=t+1}^T e^-r(T-s) F_s \eta_n | \bm{S}_t]\\
    \end{align*}
    A few things needs to be clarified
    \begin{enumerate}
        \item The value $V(\bm{S}_t)$ is a function of $\bm{S}_t=(S_1,\ldots,S_t)$, but you are only taking derivative with respect to the last value $S_t$

        \item You are passing through the partial derivative inside the expectation. This is the technique called infinitesimal perturbation analysis (IPA). This technique allows you to take derivative for each inner sample path first (i.e., the pathwise derivative) then use the sample average of the pathwise derivative to approximate the (conditional) expected value.
    \end{enumerate}

    \item In my opinions, you should also clarify how the recursive pathwise derivatives (on page 73) are derived, i.e., based on the account evolution on page 72.
    \end{enumerate}

    \item Clarify "What is the neural network approximating?" (suggested by Yuying).
    \begin{enumerate}
        \item The neural network approximates  $L$ in Equation (3.4), where
        \begin{align*}
            L=L(\bm{S}_T) = L(\Delta_0,\ldots,\Delta_{T-1}, S_0,\ldots,S_T).
        \end{align*}
        \item The loss $L$ depends on all $\Delta_0,\ldots,\Delta_{T-1}$ and each $\Delta_t$ depends on $\bm{S}_t$, as discussed above.

        \item The loss also depends on all $S_0,\ldots,S_T$ directly, too.

        \item Since $L(\bm{S}_T)$ is a function of the \textbf{entire} outer path, the neural network $\widehat{L}(\bm{S}_T)$ approximates $L$ and is also a function of the entire outer path.

        \item Statistically speaking, $L(\bm{S}_T)$ is a random variable because $\bm{S}_T$ is random. Nonetheless, we can see $L(\bm{S}_T)$ as a function of the underlying random path $\bm{S}_T$ and approximate this function.

        \item You should revise not only the math equations, but also paragraphs leading up to the equations and those after the equations.

        \item Please do a careful global revision rather than only the two places mentioned above.
        \end{enumerate}

    \item Remove reference for regression or use a different reference. (suggested by Mary Hardy). 
    \begin{enumerate}
        \item WILL ADD MORE DETAILS LATER. I do not remember which specific reference she was referring to. 
    \end{enumerate}

    \item Rewrite the Multi-level Monte Carlo sections (suggested by Mary Hardy)
    \begin{enumerate}
        \item Clarify the descriptions for multi-level Monte Carlo
        \item Add more details in the numerical experiments for readers to replicate the results
    \end{enumerate}

    \item Add a line between the following inequality explaining the use of Cauchy-Schwarz inequality:
    \begin{align*}
        E[(\hat{\rho}_{M,N}-\rho)^2] \leq 2E[(\hat{\rho}_{M,N}-\rho_M)^2] + 2E[(\rho_M-\rho)^2].
    \end{align*}

    One way to express the Cauchy-Schwarz inequality is (you will need some reference)
    \begin{align*}
        (x_1y_1 + x_2y_2)^2 \leq (x_1^2 +x_2^2)(y_1^2 +y_2^2)
    \end{align*}
    So setting $x_1 = \hat{\rho}_{M,N}-\rho_M$, $x_2 = \rho_M-\rho$, $y_1=y_2=1$, we get
    \begin{align*}
        (\hat{\rho}_{M,N}-\rho)^2 &= [(\hat{\rho}_{M,N}-\rho_M) + (\rho_M-\rho)]^2\\
        &= (x_1y_1 + x_2y_2)^2 \\
        &\leq (x_1^2+x_2^2)(y_1^2+y_2^2)\\
        &=2(\hat{\rho}_{M,N}-\rho_M)^2 + 2(\rho_M-\rho)^2
    \end{align*}

    \item Variable $z$ needs to be clearly defined when applying Taylor expansion. (suggested by Chengguo)
    \begin{enumerate}
        \item Chengguo mentioned Equation (2.16), but you should do a global check to make sure all Taylor expansions are clearly explained.
    \end{enumerate}

    \item Rewrite section 2.3.1 and re-evaluate the contributions of Theorem 1, specially in light of the well-know statistical property that L2-convergence implies convergence in probability. This was a main issue raised by Chengguo during the defence. Questions about this part were not answered well. Thus this is a \textbf{high-priority item}. 
    \begin{enumerate}
        \item Chengguo suggested (1) clarifying the definitions (4 \& 5), (2) cleaning up the proof by applying existing statistical results when possible, (3) re-evaluating the theoretical contributions of Theorem 1 and reposition it (i.e., tone down) if appropriate.
    \end{enumerate}

    \item Minor items
    \begin{enumerate}
        \item Move copyright to first page.
        \item Add a paragraph under the "sole-author" declaration that part of this thesis has been published in a WSC proceeding.
    \end{enumerate}
\end{enumerate}

\end{document}

### 2025-05-07 futureWork/rlHedging.tex
final draft

@@
 The discrete-time hedging problem of VAs can be conveniently formulated as an \gls{mdp}, where the states, actions, transition probabilities, policies, and rewards are defined as follows.
-\textcolor{red}{Different from the formulation in Chapter~\ref{chap:project2}, the hedging weight $\Delta_0, \ldots, \Delta_{T-1}$ are not estimated from inner simulation steps but are directly controlled by a \gls{drl} agent.
-Thus, the hedging weight $\Delta_t$ at time $t$ is estimated using a neural network whose input is the state $\mathbf{s}_t$ and output is $\Delta_t$.}
+Different from the formulation in Chapter~\ref{chap:project2}, the hedging weight $\Delta_0, \ldots, \Delta_{T-1}$ are not estimated from inner simulation steps but are directly controlled by a \gls{drl} agent.
+Thus, the hedging weight $\Delta_t$ at time $t$ is estimated using a neural network whose input is the state $\mathbf{s}_t$ and output is $\Delta_t$.
 

### 2025-05-07 project1/nsSurvey.tex
final draft

@@
 This paper presents a survey study of some popular nested simulation procedures that have both asymptotic convergence analysis and finite-sample performance evaluation.
-Many procedures have been proposed in the literature, but they are not directly comparable because they use \textcolor{red}{\sout{different error metrics,}} different assumptions and different numerical examples in their studies.
+Many procedures have been proposed in the literature, but they are not directly comparable because they use different assumptions and different numerical examples in their studies.
 Within a common analytical framework, we first summarize and compare the asymptotic convergence rates of these procedures.
 Their asymptotic convergence results are closely examined for their assumptions that guarantee the convergence.
-\textcolor{red}{\sout{Furthermore, the existing literature has chosen different performance metrics to evaluate the asymptotic convergence of nested simulation procedures.
-In this chapter, we discuss the asymptotic convergence in terms of \gls{mse} of the estimator, and we provide a comprehensive comparison of their convergence rates and critical assumptions.
-We also discuss the connection between the \gls{mse} and the absolute error of the estimator in the context of nested simulation procedures.}}
 
@@
 At first sight, it is counterintuitive that a more complex metamodel requires a less stringent smoothness assumption.
-This phenomenon is due to the fact that the convergence analysis for the \gls{krr}-based nested simulation procedure is shown in terms of \textcolor{red}{\gls{ae}, a different error metric than \gls{mse}.}
-\textcolor{red}{In the appendix,} Section~\ref{appendix:connection-mse-absolute-error} includes a discussion of the connection between the \gls{mse} and the \gls{ae} of the estimator in the context of nested simulation procedures.
+This phenomenon is due to the fact that the convergence analysis for the \gls{krr}-based nested simulation procedure is shown in terms of \gls{ae}, a different error metric than \gls{mse}.
+In the appendix, Section~\ref{appendix:connection-mse-absolute-error} includes a discussion of the connection between the \gls{mse} and the \gls{ae} of the estimator in the context of nested simulation procedures.
 In Table~\ref{tab1:smoothness}, the standard nested simulation procedure is the only procedure without an asymptotic convergence analysis for smooth $h$.
@@
 The \gls{mlmc} method is particularly useful when the quantity of interest is expensive to evaluate, and the standard \gls{mc} estimator has a high variance.
-\textcolor{red}{For the nested expectation form $\rho = \mathbb{E}[h(L)]$, the \gls{mlmc} method selects an approximation level $L$ with sufficient accuracy, and it uses the difference between the approximations to reduce the variance of the estimator.}
-\textcolor{red}{\sout{The \gls{mlmc} method estimates $\rho$ with an \gls{mlmc} estimator:}}
+For the nested expectation form $\rho = \mathbb{E}[h(L)]$, the \gls{mlmc} method selects an approximation level $L$ with sufficient accuracy, and it uses the difference between the approximations to reduce the variance of the estimator.
 
@@
     \item   Regression:
-            $$\hat{L}^{\text{REG}}_{M, N}(X) = \Phi(X) \hat{\beta},$$
+            \begin{equation*}
+            \hat{L}^{\text{REG}}_{M, N}(X) = \Phi(X) \hat{\beta},
+            \end{equation*}
             where $\Phi$ is a chosen basis, and $\hat{\beta}$ is estimated from the training samples.
@@
 
-\textcolor{red}{Theoretical properties of different metamodels lead to different convergence results.}
+Theoretical properties of different metamodels lead to different convergence results.
 More specifically, the \gls{krr}-based nested simulation~\citep{wang2022smooth} provides a convergence analysis in terms of \gls{ae}.
@@
 \begin{itemize}
-    \item provide the asymptotic convergence results for the standard nested simulation procedure, \textcolor{red}{and}
-    \item \textcolor{red}{\sout{show the connections between the convergence in \gls{mse} and the convergence in probabilistic order for \gls{ae} in the context of nested simulation procedures, and}}
+    \item provide the asymptotic convergence results for the standard nested simulation procedure, and
     \item illustrate the asymptotic rate of convergence of a \gls{knn}-based nested simulation procedure.
@@
 However, they analyze convergence in probabilistic order, and it is only applicable in terms of \gls{ae}.
-\textcolor{red}{In Section~\ref{appendix:connection-mse-absolute-error}, we illustrate the connection between the convergence in \gls{mse} and the convergence in \gls{ae}.}
+In Section~\ref{appendix:connection-mse-absolute-error}, we illustrate the connection between the convergence in \gls{mse} and the convergence in \gls{ae}.
 
@@
 
-\textcolor{red}{In Equation~\eqref{eq1:mse-sns}, the first inequality follows from Cauchy-Schwarz inequality.
+In Equation~\eqref{eq1:mse-sns}, the first inequality follows from Cauchy-Schwarz inequality.
 One way to express the Cauchy-Schwarz inequality is 
@@
 Let $\mathbf{x} = (x_1, x_2)$ and $\mathbf{y} = (y_1, y_2)$.
-The Cauchy-Schwarz inequality can be written as}
+The Cauchy-Schwarz inequality can be written as
 \begin{equation*}
@@
 \end{equation*}
-\textcolor{red}{By setting $x_1 = \rho_{M,N}- \rho_M$, $x_2 = \rho_M - \rho$, $y_1 = y_2 = 1$, we have }
+By setting $x_1 = \rho_{M,N}- \rho_M$, $x_2 = \rho_M - \rho$, $y_1 = y_2 = 1$, we have 
 \begin{align*}
@@
 \end{align}
-where \textcolor{red}{$z_i$ is between $L_i$ and $\hat{L}_{N,i}$, and} the last inequality is due to $2ab \leq a^2 + b^2$ for any $a, b \in \mathbb{R}$. 
+where $z_i$ is between $L_i$ and $\hat{L}_{N,i}$, and the last inequality is due to $2ab \leq a^2 + b^2$ for any $a, b \in \mathbb{R}$. 
 The two terms on the right-hand side of Equation~\eqref{eq1:taylor-sns} are analyzed separately.
@@
 \end{align}
-where \textcolor{red}{$z_i$ is between $L_i$ and $\hat{L}_{N,i}$, and} the last equality follows from the Taylor expansion of the smooth function $h$.
+where $z_i$ is between $L_i$ and $\hat{L}_{N,i}$, and the last equality follows from the Taylor expansion of the smooth function $h$.
 The first and second order Taylor expansion terms are analyzed separately in Equation~\eqref{eq1:bias-sns-smooth-Taylor1} and Equation~\eqref{eq1:bias-sns-smooth-Taylor2}.
@@
 Assumption~\ref{as1:sns-noise-var} is a moment condition that is easier to verify in practice than conditions on the joint density.
-\textcolor{red}{\sout{As stated in Theorem, the convergence in \gls{mse} automatically implies the convergence in probabilistic order.}}
-
-% \begin{corollary}
-%     Let $h$ be a smooth function. 
-%     The AE of the standard nested simulation procedure converges in probabilistic order $\Gamma^{-1/3}$, that is,
-%     $$\left| \hat{\rho}_{M, N} - \rho \right| = \mathcal{O}_\mathbb{P}(\Gamma^{-1/3}).$$
-% \end{corollary}
 
@@
 \end{theorem}
-
-\textcolor{red}{\sout{Immediately from Theorem, the convergence in \gls{mse} automatically implies the convergence in probabilistic order.}}
-
-% \begin{corollary}
-%     Let $h$ be a Lipschitz continuous function. AE of the standard nested simulation procedure converges in probabilistic order $\Gamma^{-1/3}$, that is,
-%     $$\left| \hat{\rho}_{M, N} - \rho \right| = \mathcal{O}_\mathbb{P}(\Gamma^{-1/4}).$$
-% \end{corollary}
 
@@
 Assumption~\ref{as1:krr-domain} rules out the possibility of the outer scenario $X$ being a normal random variable, which is a common assumption in the literature.
-Furthermore, the convergence analysis of the \gls{krr}-based nested simulation procedure is shown in terms of \gls{ae} rather than in \gls{mse}, which is due to the \textcolor{red}{analytical properties} of the KRR metatmodel.
+Furthermore, the convergence analysis of the \gls{krr}-based nested simulation procedure is shown in terms of \gls{ae} rather than in \gls{mse}, which is due to the analytical properties of the \gls{krr} metatmodel.
 
@@
 Numerical experiments are conducted on portfolios that consist of options on $d$ underlying assets, whose dynamics follow a multidimensional geometric Brownian motion with $0.3$ pairwise correlation.
-\textcolor{red}{The initial values of the assets are set to be $100$.}
-\textcolor{red}{The drifts are set to be $0.08$, and the risk free rate is set to be $0.05$.}
+The initial values of the assets are set to be $100$.
+The drifts are set to be $0.08$, and the risk free rate is set to be $0.05$.
 
@@
 Except for Portfolio 5, 5 different asset dimensions are considered, i.e., $d = 1, 2, 5, 10, 20$.
-\textcolor{red}{All options have a maturity of $1$ year, and we are interested in the value of the portfolio at time $3/50$ year from now.}
+All options have a maturity of $1$ year, and we are interested in the value of the portfolio at time $3/50$ year from now.
 525 experiment settings that arise from an exhaustive combination of the above simulation procedures, risk measures, portfolios, and asset dimensions are generated.
@@
 The empirical convergence results of each estimator are measured and recorded to illustrate their empirical behavior under different risk measures, option types, and asset dimensions.
-\textcolor{red}{All numerical experiments are conducted on a linux server with four Intel Xeon Gold 6230 20-core 2.1 GHz CPU with 768 GB RAM.}
+All numerical experiments are conducted on a linux server with four Intel Xeon Gold 6230 20-core 2.1 GHz CPU with 768 GB RAM.
 
@@
 Due to high computational costs, we are not able to conduct experiments for higher budget levels, but we expect the \gls{mse} of the regression-based nested simulation procedure to stabilize after $\Gamma = 10^6$, and the empirical rate of convergence to approach its asymptotic rate.
-\textcolor{red}{The empirical convergence rates reported in the graph legends are higher than the actual rates after regression-based nested simulation procedure reaches the asymptotic convergence regime.}
+The empirical convergence rates reported in the graph legends are higher than the actual rates after regression-based nested simulation procedure reaches the asymptotic convergence regime.
 In the context of nested simulation procedures, a parametric regression metamodel has several advantages over a non-parametric regression metamodel.
@@
 To examine the sensitivity of the empirical convergence behavior to the asset model, we consider a stochastic volatility model of a Heston type~\citep{heston1993closed}.
-\textcolor{red}{In a Heston model, the asset price and the volatility are correlated, and the volatility is a stochastic process.}
+In a Heston model, the asset price and the volatility are correlated, and the volatility is a stochastic process.
 
@@
 
-\textcolor{red}{In this experiment, the initial asset price and the volatility are set to be $100$ and $0.2$, respectively.
-The parameters are set to be $\mu = 0.08$, $\kappa = 2$, $\theta = 0.04$, $\xi = 0.1$.}
+In this experiment, the initial asset price and the volatility are set to be $100$ and $0.2$, respectively. The parameters are set to be $\mu = 0.08$, $\kappa = 2$, $\theta = 0.04$, $\xi = 0.1$.
 
@@
 The theoretical analysis in~\cite{giles2019multilevel} shows that the \gls{mlmc} procedure has a faster empirical rate of convergence than the standard nested simulation procedure when the risk measure of interest is the probability of a large loss over a threshold $u$, i.e., the nested expectation case with $h$ being an indicator function.
-\textcolor{red}{In this numerical experiment, the initial number of inner replications, the refinement factor, the r-value for adaptive algorithm are set to be $4$, $4$, and $1.5$, respectively.}
-\textcolor{red}{We note that the \gls{mlmc} procedure focuses on adaptive allocation of the simulation budget and is fundamentally different from supervised learning-based nested simulation procedures.
-And their results are not directly comparable.}
+In this numerical experiment, the initial number of inner replications, the refinement factor, the r-value for adaptive algorithm are set to be $4$, $4$, and $1.5$, respectively.
+We note that the \gls{mlmc} procedure focuses on adaptive allocation of the simulation budget and is fundamentally different from supervised learning-based nested simulation procedures.
+And their results are not directly comparable.
 
@@
 To show an asymptotic convergence result, a more complex metamodels requires a more stringent set of assumptions on the distribution of the outer scenario and the inner simulation noise.
-\textcolor{red}{In terms of finite-sample behavior, this study provides a comprehensive comparison of different nested simulation procedures, and the findings can be used to guide the choice of a proper nested simulation procedure for a given nested estimation problem.}
+In terms of finite-sample behavior, this study provides a comprehensive comparison of different nested simulation procedures, and the findings can be used to guide the choice of a proper nested simulation procedure for a given nested estimation problem.
 With extensive numerical experiments, we have found that the finite-sample performance of a procedure can deviate from its theory. 

### 2025-05-07 project2/nnMetamodels.tex
final draft

--- 2025-04-15 project2/nnMetamodels.tex
@@
 For example, suppose that the per-period risk-free rate is $r$, then
-\textcolor{red}{the insurer's time-$t$ liability for a \gls{gmwb} contract is}
+the insurer's time-$t$ liability for a \gls{gmwb} contract is
 
@@
 \end{algorithm}
+
+In the two-stage procedure, the neural network metamodel approximates $L$ in Equation~\ref{eq2:lossrv}, where 
+\begin{equation}
+    L = L(\mathbf{S}_T) = L(\Delta_0, \ldots, \Delta_{T-1}, S_0, \ldots, S_T)
+\end{equation}
+The loss $L$ depends on all the hedging weights $\Delta_0, \ldots, \Delta_{T-1}$, which are determined by the stock prices $S_t$, $t=0,\ldots,T-1$.
+In addition, $L$ also depends on all the stock prices $S_0, \ldots, S_T$ directly.
+Therefore, the loss $L(\mathbf{S}_T)$ is a complex function of the entire stock price path $\mathbf{S}_T$, and the neural network metamodel $\Lhat^{PD}(\mathbf{X})$ approximates $L(\mathbf{S}_T)$ by mapping the stock returns $\mathbf{X}_T$ to the loss $L(\mathbf{S}_T)$.
+Statistically speaking, $L(\mathbf{S}_T)$ is a random variable whose stochasticity solely depends on the stock price path $\mathbf{S}_T$. 
+Nevertheless, $L(\mathbf{S}_T)$ can be viewed as a function of the underlying stock returns $\mathbf{X}_T$ and can be approximated by a neural network metamodel.
 
@@
 Otherwise, the two-stage procedure will offer no computational advantage in simulation budget over the standard procedure.
-The \gls{lstm} metamodel can reach similar percentage \textcolor{red}{of correctly identified true tail scenarios} with a $5\%$ safety margin.
+The \gls{lstm} metamodel can reach similar percentage of correctly identified true tail scenarios with a $5\%$ safety margin.
 This indicates that the \gls{lstm} metamodel should be able to reach the same level of accuracy as the standard procedure with only $20\%$ of the simulation budget.

### 2025-05-07 project3/draft.tex
asd
final draft

@@
 
-\subsection{Rapid Adaptation of \gls{lstm} Metamodels} \label{sec3:transfer_learning}
+\subsection{Rapid Adaptation of LSTM Metamodels} \label{sec3:transfer_learning}
 
@@
 Serveral \gls{va} datasets generated with the standard nested simulation procedures under geometric Brownian motion (\gls{gbm}) and regime-switching \gls{gbm} (\gls{rsgbm}) asset models.
-\textcolor{red}{In this experiment, we use the same \gls{rsgbm} asset model as Chapter~\ref{chap:project2} to generate the dataset for the source and target tasks.}
-\textcolor{red}{When following a static lapse model and a dynamic lapse model, the monthly lapse rate is given by Equation~\ref{eq:lapse_rate} and Equation~\ref{eq:dynamic_lapse_rate}, respectively.}
-\textcolor{red}{The experiments are run on a machine with a AMD Ryzen 9 7900X processor with 32 GB of RAM and a Nvidia RTX $\num{3060}$ Ti GPU}
+In this experiment, we use the same \gls{rsgbm} asset model as Chapter~\ref{chap:project2} to generate the dataset for the source and target tasks.
+When following a static lapse model and a dynamic lapse model, the monthly lapse rate is given by Equation~\ref{eq:lapse_rate} and Equation~\ref{eq:dynamic_lapse_rate}, respectively.
+The experiments are run on a machine with a AMD Ryzen 9 7900X processor with 32 GB of RAM and a Nvidia RTX $\num{3060}$ Ti GPU.
 

### 2025-05-08 futureWork/rlHedging.tex
new

@@
 
-In the evolving landscape of financial markets, insurance products such as VAs have gained a substantial amount of interest due to their ability to provide both investment growth and guaranteed benefits.
+In the evolving landscape of financial markets, insurance products such as \gls{va} contracts have gained a substantial amount of interest due to their ability to provide both investment growth and guaranteed benefits.
 Managing the risks associated with these products, especially in volatile market conditions, is a complex task that demands sophisticated financial modeling techniques. 
 \gls{rl} has emerged as a powerful tool for addressing such complexities.
-With the recent advancement in deep learning, \gls{dnn} architectures have been successfully applied to \gls{rl} problems, leading to the development of deep reinforcement learning (\gls{drl}) algorithms.
+With the recent advancement in deep learning, \gls{dnn} architectures have been successfully applied to \gls{rl} problems, leading to the development of \gls{drl} algorithms.
 These algorithms have demonstrated remarkable success decision-making tasks that must be optimized over time. 
-In the context of managing VAs, \gls{drl} has shown promise in optimizing hedging strategies where long-term financial and policyholder decisions interact dynamically with changing market conditions.
+In the context of managing \gls{va} contracts, \gls{drl} has shown promise in optimizing hedging strategies where long-term financial and policyholder decisions interact dynamically with changing market conditions.
 
@@
 The rest of the chapter is organized as follows: 
-Section~\ref{sec:MDP} introduces the mathematical formulation for hedging VAs and defines the key components of the framework.
-Section~\ref{sec:RLAlgorithms} provides an overview of existing \gls{rl} algorithms and their limitations in the context of hedging VAs.
-Section~\ref{sec:PPO} introduces the proximal policy optimization algorithm and its application to the hedging of VAs.
+Section~\ref{sec:MDP} introduces the mathematical formulation for hedging \gls{va} contracts and defines the key components of the framework.
+Section~\ref{sec:RLAlgorithms} provides an overview of existing \gls{rl} algorithms and their limitations in the context of hedging \gls{va} contracts.
+Section~\ref{sec:PPO} introduces the proximal policy optimization algorithm and its application to the hedging of \gls{va} contracts.
 Finally, Section~\ref{sec:FutureDirections} concludes the chapter and discusses future research directions.
 
-\section{Markov Decision Process for Hedging VAs} \label{sec:MDP}
+\section{Markov Decision Process for Hedging VA Contracts} \label{sec:MDP}
 
@@
 A \gls{mdp} provides a mathematical framework for solving sequential decision-making tasks in an enviornment where outcomes are partly random and partly under the control of a hedging agent. 
-For hedging VAs, the asset dynamics and the mortality model are not controlled by the agent, but the agent controls the cumulative reward by deciding on the hedging weights.
-In this section, we reformulate the hedging enviornment of VAs from Section~\ref{subsec:VApayout} as an \gls{mdp} and define the key components of the \gls{mdp}.
+For hedging \gls{va} contracts, the asset dynamics and the mortality model are not controlled by the agent, but the agent controls the cumulative reward by deciding on the hedging weights.
+In this section, we reformulate the hedging enviornment of \gls{va} contracts from Section~\ref{subsec:VApayout} as an \gls{mdp} and define the key components of the \gls{mdp}.
 
@@
         \end{equation}
-    where $q_t^B$ is the base lapse rate, $\text{clip}(x, a, b)$ is a function that clips the value of $x$ to be within the range $[a, b]$, and $M_q$, $D_q$, $L_q$, and $U_q$ are the model parameters taken from National Association of Insurance Commissioners’ (NAIC) Valuation Manual 21~\citep{naic2021}.
+    where $q_t^B$ is the base lapse rate, $\text{clip}(x, a, b)$ is a function that clips the value of $x$ to be within the range $[a, b]$, i.e.,
+    $$
+    \text{clip}(x, a, b) = \begin{cases}
+        a, & \text{if } x < a \\
+        x, & \text{if } a \leq x \leq b \\
+        b, & \text{if } x > b,
+    \end{cases}
+    $$
+    and $M_q$, $D_q$, $L_q$, and $U_q$ are the model parameters taken from National Association of Insurance Commissioners’ (NAIC) Valuation Manual 21~\citep{naic2021}.
     \item The sub-account value changes according to the growth of the underlying stock and the (gross) management fee is deducted. That is, 
@@
 Both Equation~\eqref{eq3:lossGMMB} and Equation~\eqref{eq3:lossGMWB} neglect the transaction cost to liquidate the hedge portfolio at maturity.
-The discrete-time hedging problem of VAs can be conveniently formulated as an \gls{mdp}, where the states, actions, transition probabilities, policies, and rewards are defined as follows.
+The discrete-time hedging problem of \gls{va} contracts can be conveniently formulated as an \gls{mdp}, where the states, actions, transition probabilities, policies, and rewards are defined as follows.
 Different from the formulation in Chapter~\ref{chap:project2}, the hedging weight $\Delta_0, \ldots, \Delta_{T-1}$ are not estimated from inner simulation steps but are directly controlled by a \gls{drl} agent.
@@
 
-For hedging VAs,~\cite{xu2020variable} propose a deep hedging algorithm that falls into this category of model-based \gls{rl}.
+For hedging \gls{va} contracts,~\cite{xu2020variable} propose a deep hedging algorithm that falls into this category of model-based \gls{rl}.
 A cost function is defined to minimize the expected shortfall of the total present liability.
@@
 In a model-free reinforcement learning approach, the agent is a trial-and-error learner that interacts with the environment to learn the optimal policy by iteratively updating the policy and the value function based on the observed states, actions, and rewards.
-For hedging VAs, the agent does not have access to a planning algorithm or the underlying stochastic asset model, and it must learn the optimal policy by directly interacting with the environment.
+For hedging \gls{va} contracts, the agent does not have access to a planning algorithm or the underlying stochastic asset model, and it must learn the optimal policy by directly interacting with the environment.
 
@@
 In the context of hedging, existing studies use transaction costs as a function of the hedging weights, which makes the transition probabilities independent on the actions.
-However, the trade size can affect the asset price in a real environment~\citep{hasbrouck1991measuring}, which makes the model-free approach a promising direction for hedging VAs in the real market.
+However, the trade size can affect the asset price in a real environment~\citep{hasbrouck1991measuring}, which makes the model-free approach a promising direction for hedging \gls{va} contracts in the real market.
 
@@
 ~\cite{du2020deep} show that the \gls{ppo} algorithm is more sample efficient and stable than the value-based approaches in training agents to hedge financial derivatives.
-The most relevant paper to our study is~\cite{chong2023pseudo}, which uses the \gls{ppo} algorithm to hedge \gls{gmmb} with a GMDB rider under the Black-Scholes framework.
+The most relevant paper to our study is~\cite{chong2023pseudo}, which uses the \gls{ppo} algorithm to hedge \gls{gmmb} with a \gls{gmdb} rider under the Black-Scholes framework.
 However, information of the underlying risk factors is leaked to the agent, which makes their study pseudo-model-free.
-To further improve the risk management of VAs under rough volatility models, we propose a model-free deep reinforcement learning approach to hedge VAs without explicit or implicit knowledge of the underlying risk factors.
+To further improve the risk management of \gls{va} contracts under rough volatility models, we propose a model-free deep reinforcement learning approach to hedge \gls{va} contracts without explicit or implicit knowledge of the underlying risk factors.
 
-\section{Hedging VAs with a PPO Agent} \label{sec:PPO}
+\section{Hedging VA contracts with a PPO Agent} \label{sec:PPO}
 In a hedging problem, an insurer aims at finding a policy $\pi$ that maximizes the expected reward over time.
@@
 
-Algorithm~\ref{alg3:ppoHedging} outlines the \gls{ppo} algorithm for training an agent to hedge VAs.
+Algorithm~\ref{alg3:ppoHedging} outlines the \gls{ppo} algorithm for training an agent to hedge \gls{va} contracts.
 At each iteration $k$, the agent collects a set of trajectories $\mathcal{D}_k$ by interacting with the environment (Section~\ref{subsec:VASimulation}) with the current policy $\pi_{\theta_k}$.
@@
 The value function parameters $\phi_{k+1}$ are updated by minimizing the mean squared error between the predicted value and the actual collected reward.
-The agent iterates this process until convergence to learn an optimal policy for hedging VAs.
+The agent iterates this process until convergence to learn an optimal policy for hedging \gls{va} contracts.
 
@@
 
-In the context of hedging VAs, the state space is partially observed.
+In the context of hedging \gls{va} contracts, the state space is partially observed.
 The agent does not have access to the contract specifications and the underlying risk factors.
@@
 \begin{equation} \label{eq3:stateRNN}
-    \mathbf{s}_t = (S_t, F_t, G_t, \tau, \Delta_{t-1}), \quad h_t = \text{\gls{lstm}}(\mathbf{s}_t, h_{t-1})
+    \mathbf{s}_t = (S_t, F_t, G_t, \tau, \Delta_{t-1}), \quad h_t = \text{LSTM}(\mathbf{s}_t, h_{t-1}),
 \end{equation}
-
+where 
+\begin{align} 
+    h_t &= o_t \odot \tanh(c_t), \nonumber \\
+    c_t &= f_t \odot c_{t-1} + i_t \odot g_t, \nonumber \\
+    i_t &= a(W_i \mathbf{s}_t + U_i h_{t-1} + b_i), \nonumber \\
+    f_t &= a(W_f \mathbf{s}_t + U_f h_{t-1} + b_f), \nonumber \\
+    o_t &= a(W_o \mathbf{s}_t + U_o h_{t-1} + b_o), \nonumber \\
+    g_t &= a(W_g \mathbf{s}_t + U_g h_{t-1} + b_g), 
+\end{align}
 In a \gls{lstm}, the cell state $c_t$ stores a representation of historical information up to time $t$.
 It is updated at each time step by a forget gate $f_t$, an input gate $i_t$, and an output gate $o_t$.
+Equation~\ref{eq:lstm} provides a general intoduction to \gls{lstm} for a generic time series input $x_t$.
 
 In a recurrent \gls{ppo} with \gls{lstm}, the policy and reward function remain the same but with the new state representation in Equation~\eqref{eq3:stateRNN}.
-Instead of following the standard \gls{ppo} algorithm, the agent uses the recurrent \gls{ppo} algorithm to learn an optimal policy for hedging VAs.
-Figure~\ref{fig3:architecturePPO} illustrates the network architecture of the standard \gls{ppo} and the recurrent \gls{ppo} with \gls{lstm}, and Algorithm~\ref{alg3:ppoHedging-rnn} outlines the recurrent \gls{ppo} algorithm and for training an agent to hedge VAs with non-Markovian dynamics.
+Instead of following the standard \gls{ppo} algorithm, the agent uses the recurrent \gls{ppo} algorithm to learn an optimal policy for hedging \gls{va} contracts.
+Figure~\ref{fig3:architecturePPO} illustrates the network architecture of the standard \gls{ppo} and the recurrent \gls{ppo} with \gls{lstm}, and Algorithm~\ref{alg3:ppoHedging-rnn} outlines the recurrent \gls{ppo} algorithm and for training an agent to hedge \gls{va} contracts with non-Markovian dynamics.
 
@@
 
-\section{Transfer Learning for Hedging VAs} \label{sec:TransferLearning}
+\section{Transfer Learning for Hedging VA contracts} \label{sec:TransferLearning}
 
@@
 To the best of our knowledge, no research has been conducted to improve the hedging strategies with the state-of-the-art transfer learning techniques.
-This section introduces some transfer learning techniques that are relevant to our task of hedging VAs.
+This section introduces some transfer learning techniques that are relevant to our task of hedging \gls{va} contracts.
 
@@
 
-In the context of hedging VAs using deep reinforcement learning and transfer learning, reward shaping becomes a crucial technique. 
+In the context of hedging \gls{va} contracts using deep reinforcement learning and transfer learning, reward shaping becomes a crucial technique. 
 It involves modifying the reward function in the target domain to incorporate additional guidance, which often leads to more efficient learning and a better performance.
-This technique can be particularly useful for managing the complex risks associated with VAs, as it can guide the learning process towards strategies that are more effective in hedging these products.
+This technique can be particularly useful for managing the complex risks associated with \gls{va} contracts, as it can guide the learning process towards strategies that are more effective in hedging these products.
 
@@
 
-We present a numerical experiment to demonstrate the effectiveness of the model-free \gls{ppo} algorithm for hedging VAs with transaction costs.
+We present a numerical experiment to demonstrate the effectiveness of the model-free \gls{ppo} algorithm for hedging \gls{va} contracts with transaction costs.
 We consider a \gls{va} contract with a maturity of $T=240$ months and a \gls{gmmb} rider with a simulation environment described in Section~\ref{subsec:VASimulation}.
@@
 
-Figure~\ref{fig3:dh-transfers} illustrates the hedging performance of the deep hedging algorithm with transfer learning for hedging VAs with a \gls{gmmb} rider.
+Figure~\ref{fig3:dh-transfers} illustrates the hedging performance of the deep hedging algorithm with transfer learning for hedging \gls{va} contracts with a \gls{gmmb} rider.
 The first deep hedging agent is directly trained on the Heston asset model, and the second deep hedging agent is trained with transfer learning from the \gls{gbm} model.
@@
 
-This experiment compares the hedging performance of the recurrent \gls{ppo} agent with \gls{lstm} and the deep hedging algorithm proposed by~\cite{buehler2019deep} for hedging VAs with a \gls{gmmb} rider.
+This experiment compares the hedging performance of the recurrent \gls{ppo} agent with \gls{lstm} and the deep hedging algorithm proposed by~\cite{buehler2019deep} for hedging \gls{va} contracts with a \gls{gmmb} rider.
 The experiment is conducted with the same amount ofsimulation budget.
@@
 
-Figure~\ref{fig3:ppo_result} illustrates the hedging performance of the standard \gls{ppo} and the recurrent \gls{ppo} with \gls{lstm} for hedging VAs with transaction costs $C=0.005$.
+Figure~\ref{fig3:ppo_result} illustrates the hedging performance of the standard \gls{ppo} and the recurrent \gls{ppo} with \gls{lstm} for hedging \gls{va} contracts with transaction costs $C=0.005$.
 The figures show the distributions of the hedging errors incurred by the agents over the $10^3$ test episodes for the \gls{gbm} and the \gls{rsgbm} asset models.
@@
 
-Figure~\ref{fig3:ppo_GMWB} illustrates the hedging performance of the recurrent \gls{ppo} agent for hedging VAs with a \gls{gmwb} rider.
+Figure~\ref{fig3:ppo_GMWB} illustrates the hedging performance of the recurrent \gls{ppo} agent for hedging \gls{va} contracts with a \gls{gmwb} rider.
 The experiment is conducted with the same hyperparameters as the experiment with the \gls{gmmb} rider.

### 2025-05-08 introduction.tex
final draft
new

@@
 They provide a guaranteed minimum income benefit to the policyholder regardless of the performance of the underlying assets.
-Advanced Monte Carlo simulation techniques, particularly nested simulation procedures, become indispensable for risk assessment of such products.
-In contrast to finite-difference methods, a Monte Carlo simulation scheme is more flexible and can be easily adapted to model tail risk with a rule-based design.
-~\cite{glasserman2004monte} provide a comprehensive overview of Monte Carlo simulation methods in financial engineering and risk management applications.
+Advanced \gls{mc} simulation techniques, particularly nested simulation procedures, become indispensable for risk assessment of such products.
+In contrast to finite-difference methods, a \gls{mc} simulation scheme is more flexible and can be easily adapted to model tail risk with a rule-based design.
+~\cite{glasserman2004monte} provide a comprehensive overview of \gls{mc} simulation methods in financial engineering and risk management applications.
 In this thesis, we focus on building and analyzing nested simulation procedures for risk management applications of financial derivatives and insurance products.
@@
 For example, estimating the value of an exotic option over a risk horizon requires simulation given a realization of the underlying assets over that horizon.
-A standard nested simulation procedure consists of two levels of simulation: the outer-level simulation generates the underlying risk factors, while the inner-level simulation estimates the value of interest with the inner sample mean from another level of Monte Carlo simulation.
+A standard nested simulation procedure consists of two levels of simulation: the outer-level simulation generates the underlying risk factors, while the inner-level simulation estimates the value of interest with the inner sample mean from another level of \gls{mc} simulation.
 This nested structure allows for accurate estimation given sufficient computational resources, but it also introduces additional complexity in the simulation design and implementation.
@@
 \end{itemize}
-Risk management of VAs is a challenging problem due to the complex interactions between the policyholder's behavior and the financial market dynamics.
+Risk management of \gls{va} contracts is a challenging problem due to the complex interactions between the policyholder's behavior and the financial market dynamics.
 We focus mainly on the estimation of tail risk measures of \gls{va} contract losses using metamodel-based nested simulation procedures.
@@
 
-\section{Risk Management of Variable Annuities with Nested Simulation}
+\section{Risk Management of VAs with Nested Simulation}
 
@@
 These products have gained a substantial amount of interest as they address the needs of individuals seeking both wealth accumulation and financial security, especially in the context of retirement planning.
-The key feature of VAs is their embedded guarantees, which ensure a specified minimum benefit regardless of market performance.
+The key feature of \gls{va} contracts is their embedded guarantees, which ensure a specified minimum benefit regardless of market performance.
 Two \gls{va} contracts that are most relevant to this thesis are \gls{gmmb} and \gls{gmwb}.
@@
 The \gls{gmwb} allows policyholders to withdraw a specified percentage of their benefit base each period during the contract horizon~\citep{hardy2003investment}.
-While these guarantees make VAs more attractive to consumers by offering protection against market downturns and ensuring income stability, they also introduce significant financial risks for insurers.
+While these guarantees make \gls{va} contracts more attractive to consumers by offering protection against market downturns and ensuring income stability, they also introduce significant financial risks for insurers.
 The embedded options within \gls{gmmb} and \gls{gmwb} expose insurers to market risk, longevity risk, and policyholder behavior risk.
@@
 
-One of the primary risk management strategies employed by insurers to mitigate the financial risks associated with VAs is dynamic hedging.
+One of the primary risk management strategies employed by insurers to mitigate the financial risks associated with \gls{va} contracts is dynamic hedging.
 Dynamic hedging involves frequent adjustments to a portfolio of financial instruments to offset changes in guarantee values due to market movements~\citep{hull2016options}.
@@
 Metamodeling, or surrogate modeling, approximates complex simulation models with simpler, computationally efficient models.
-In Monte Carlo simulations, metamodels reduce computational costs by approximating simulation outputs based on input variables~\citep{kleijnen2018design}.
-This section introduces metamodeling for a Monte Carlo simulation, elaborates on its methodologies, and highlights its importance in practical applications.
+In \gls{mc} simulations, metamodels reduce computational costs by approximating simulation outputs based on input variables~\citep{kleijnen2018design}.
+This section introduces metamodeling for a \gls{mc} simulation, elaborates on its methodologies, and highlights its importance in practical applications.
 
-Monte Carlo simulations are widely used for modeling and analyzing complex systems that are probabilistic in nature.
+\gls{mc} simulations are widely used for modeling and analyzing complex systems that are probabilistic in nature.
 These simulations often require a substantial amount of computational resources, especially when a high degree of accuracy or a high number of iterations is necessary~\citep{glasserman2004monte}.
@@
 
-The development of advanced machine learning models and deep learning techniques has enhanced metamodeling approaches for Monte Carlo simulations, especially in high-dimensional and complex problem settings.
+The development of advanced machine learning models and deep learning techniques has enhanced metamodeling approaches for \gls{mc} simulations, especially in high-dimensional and complex problem settings.
 Examples of machine learning applications include~\cite{jin2020deep},~\cite{tang2020deep}, and~\cite{rosen2012metamodeling}.
 These methods offer powerful tools for capturing intricate patterns and nonlinear relationships that traditional metamodeling techniques might struggle to model effectively.
-In the following sections, we discuss machine learning algorithms in the context of metamodeling for Monte Carlo simulations and their applications in risk management.
+In the following sections, we discuss machine learning algorithms in the context of metamodeling for \gls{mc} simulations and their applications in risk management.
 
@@
 
-\begin{equation}
+\begin{equation} \label{eq:fnn}
     f(x; \theta) = f^{(k)}(f^{(k-1)} \cdots (f^{(2)}(f^{(1)}(x;\theta^{(1)});\theta^{(2)} )\cdots ;\theta^{(k-1)});\theta^{(k)}),
@@
 Despite this theoretical guarantee for single-layer neural networks, in practice, \gls{dnn} with multiple hidden layers have been shown to be more effective at capturing complex patterns and relationships in data~\citep{lecun2015deep}.
-Examples include AlexNet~\citep{krizhevsky2012imagenet}, VGG~\citep{simonyan2014very}, and ResNet~\citep{he2016deep}, which have achieved state-of-the-art performance on image classification tasks.
+Examples include AlexNet~\citep{krizhevsky2012imagenet}, Visual Geometic Group~\citep{simonyan2014very}, and ResNet~\citep{he2016deep}, which have achieved state-of-the-art performance on image classification tasks.
 In this thesis, we focus on the application of deep neural networks, specifically \gls{lstm}, as metamodels for nested simulation procedures in risk management applications.
@@
 
-To overcome the limitations of \gls{fnn}s in handling sequential input, \gls{rnn}s were introduced.
+To overcome the limitations of \gls{fnn}s in handling sequential input, A \gls{rnn} was introduced.
 In an \gls{rnn}, the hidden state at each time step is a function of both the current input and the hidden state from the previous time period~\citep{elman1990finding}:
 
-\begin{equation}
+\begin{equation} \label{eq:rnn}
     h_t = f(x_t, h_{t-1}; \theta),
@@
 To address these issues, a \gls{lstm} network was developed by~\citet{hochreiter1997long}.
-It is a specialized form of RNNs designed to capture long-term dependencies more effectively with the help of \gls{rnn} memory cells and gating mechanisms.
+It is a specialized form of \gls{rnn}s designed to capture long-term dependencies more effectively with the help of \gls{rnn} memory cells and gating mechanisms.
 
-\begin{align*}
-    i_t &= a(W_i x_t + U_i h_{t-1} + b_i), \\
-    f_t &= a(W_f x_t + U_f h_{t-1} + b_f), \\
-    o_t &= a(W_o x_t + U_o h_{t-1} + b_o), \\
-    g_t &= a(W_g x_t + U_g h_{t-1} + b_g), \\
-    c_t &= f_t \odot c_{t-1} + i_t \odot g_t, \\
+\begin{align} \label{eq:lstm}
+    i_t &= a(W_i x_t + U_i h_{t-1} + b_i), \nonumber \\
+    f_t &= a(W_f x_t + U_f h_{t-1} + b_f), \nonumber \\
+    o_t &= a(W_o x_t + U_o h_{t-1} + b_o), \nonumber \\
+    g_t &= a(W_g x_t + U_g h_{t-1} + b_g), \nonumber \\
+    c_t &= f_t \odot c_{t-1} + i_t \odot g_t, \nonumber \\
     h_t &= o_t \odot \tanh(c_t),
-\end{align*}
+\end{align}
 where $i_t, f_t, o_t, g_t, c_t, h_t$ are an input gate, a forget gate, an output gate, a cell input, a cell state, and a hidden state at time $t$, respectively.
 $W_i$, $W_f$, $W_o$, $W_g$, $U_i$, $U_f$, $U_o$, $U_g$ are weight matrices, and $b_i$, $b_f$, $b_o$, $b_g$ are bias vectors.
-$a$ is the activation function, typically the sigmoid function, and $\odot$ denotes element-wise multiplication.
+$a$ is the activation function, typically the sigmoid function, and $\odot$ denotes an element-wise multiplication.
 
@@
 To address these issues, various adaptive learning rate methods have been proposed in the literature.
-The most popular approach is Adam optimizer, which is an SGD algorithm that adjusts the learning rate during training to improve convergence speed and stability~\citep{kingma2014adam}.
+The most popular approach is the Adam optimizer, which is an \gls{sgd} algorithm that adjusts the learning rate during training to improve convergence speed and stability~\citep{kingma2014adam}.
 

### 2025-05-08 project1/nsSurvey.tex
new

@@
             \end{equation*}
-    \item   Value at risk (\gls{var}):
+    \item   \gls{var}:
             \begin{equation*}
@@
 We can use supervised learning to approximate $L_i$ by $\hat{L}_{M, N}^{\text{SL}}(X_i)$ and to pool the inner replications from all outer scenarios.
-Specifically, $\hat{L}^{\text{SL}}{M, N}(\cdot)$ denotes a supervised learning model trained on $(X_i, \hat{L}{N, i})$ for $i \in {1, \dots, M}$.
+Specifically, $\hat{L}^{\text{SL}}{M, N}(\cdot)$ denotes a supervised learning model trained on $(X_i, \hat{L}_{N, i})$ for $i \in {1, \dots, M}$.
 This is the output of the standard nested simulation procedure with $M$ outer scenarios and $N$ inner replications.
@@
 However, we have only examined the performance for option portfolios in this study, where finding a suitable set of basis functions for regression is relatively easy.
-In practice, a variable annuity contract is often high-dimensional in time with a complex payoff structure, and it is a challenging problem for nested simulation procedures.
+In practice, a \gls{va} contract is often high-dimensional in time with a complex payoff structure, and it is a challenging problem for nested simulation procedures.
 The time dependence in the feature space leads to multi-collinearity, and the regression-based procedure may not be the best choice in such instances.
 In such cases, a neural network-based procedure may be more suitable, as it is a data-driven algorithm that finds a suitable set of basis functions automatically.
-In Chapter~\ref{chap:project2}, we examine the performance of regression-based and neural network-based nested simulation procedures for estimating risk measures for variable annuities.
+In Chapter~\ref{chap:project2}, we examine the performance of regression-based and neural network-based nested simulation procedures for estimating risk measures for \gls{va} contracts.

### 2025-05-08 project2/nnMetamodels.tex
new

@@
 A branch of research has been devoted to understanding the resilience of neural network models to noise in training labels.
-For example,~\cite{luo2016understanding} show that adding synthetic label noise to the convolutional neural network (\gls{cnn}) can improve its ability to capture global features. 
+For example,~\cite{luo2016understanding} show that adding synthetic label noise to the \gls{cnn} can improve its ability to capture global features. 
 ~\cite{srivastava2014dropout} quantify the error tolerance by injecting synthetic label noise with a custom Boltzmann machine hardware.
@@
 
-Estimating tail risk measures of portfolios of complex \gls{va}s usually requires nested simulation.
+Estimating tail risk measures of portfolios of complex \gls{va} contracts usually requires nested simulation.
 In the nested simulation, the outer simulation involves projecting scenarios of key risk factors under a $\mathbb{P}$ measure, while the inner simulations are used to value payoffs uder guarantees of varying complexity, under a $\mathbb{Q}$ measure.
@@
 Empirical proxies are constructed by using an initial pilot simulation to develop factors or functionals that can subsequently be used in place of the inner simulation. 
-A prominent expirical proxy method discussed in the literature is the least squares Monte Carlo method~\citep{longstaff2001valuing}.
+A prominent expirical proxy method discussed in the literature is the least squares \gls{mc} method~\citep{longstaff2001valuing}.
 In Chapter~\ref{chap:project1}, supervised learning models, including linear regression, \gls{knn}, and \gls{krr}, are used as proxy models for inner simulations.
-This chapter introduces a proxy model to reduce the computational requirements of inner simulations of \gls{va}s by replacing the inner simulation step of a nested simulation procedure. 
+This chapter introduces a proxy model to reduce the computational requirements of inner simulations of \gls{va} contracts by replacing the inner simulation step of a nested simulation procedure. 
 This proxy model is chosen to be a flexible empirical function, i.e., a \gls{dnn} metamodel.
@@
 A popular metamodel in nested simulation procedures is stochastic kriging.
-~\cite{liu2010stochastic} use stochastic kriging as a metamodel of Monte Carlo simulations to estimate the \gls{cvar} of a portfolio of derivative securities, and~\cite{gan2015valuation} use a stochastic kriging for an efficient valuation of large portfolios of \gls{va} contracts.
+~\cite{liu2010stochastic} use stochastic kriging as a metamodel of \gls{mc} simulations to estimate the \gls{cvar} of a portfolio of derivative securities, and~\cite{gan2015valuation} use a stochastic kriging for an efficient valuation of large portfolios of \gls{va} contracts.
 Other studies, such as ~\cite{broadie2015risk},~\cite{hong2017kernel}, and~\cite{zhang2022sample} use a regression, a kernel smoothing, and a likelihood ratio method, respectively as metamodels.
@@
 The rest of this chapter is organized as follows.
-Section~\ref{sec2:problem-formulation} presents the problem settings for tail risk measures and dynamic hedging of \gls{va}s. 
+Section~\ref{sec2:problem-formulation} presents the problem settings for tail risk measures and dynamic hedging of \gls{va} contracts. 
 Section~\ref{sec2:metamodel2Stage} proposes an efficient two-stage nested simulation procedure that uses \gls{dnn}s as metamodels to help reduce a simulation budget by only performing computations on identified tail scenarios.
@@
 
-In this section we present notations, problem settings, and a simulation model for risk estimation for hedging errors of \gls{va}s.
+In this section we present notations, problem settings, and a simulation model for risk estimation for hedging errors of \gls{va} contracts.
 A main goal of this section is to showcase the complexity of the simulation model, which we use as a data generator to train \gls{dnn} metamodels (Section~\ref{sec2:metamodel2Stage} and Section~\ref{sec2:metamodel1Stage}).
@@
 For example, European insurers set regulatory capital at $99.5\%$-\gls{var} according to Solvency II~\cite{eiopa2014underlying}.
-In Canada, the regulatory capital requirement for \gls{va}s is set based on \gls{cvar}s as prescribed in~\cite{osfi2017life}.
+In Canada, the regulatory capital requirement for \gls{va} contracts is set based on \gls{cvar}s as prescribed in~\cite{osfi2017life}.
 
@@
 \begin{algorithm} 
-\caption{Standard Nested Simulation Procedure for Estimating CVaR for GMWB Hedging Losses}
+\caption{Standard Nested Simulation Procedure for Estimating CVaR for \gls{gmwb} Hedging Losses}
 \begin{algorithmic}[1] \label{alg2:standardProcedure}
@@
     \item   After running inner simulations for $M$ scenarios, we obtain simulated data as feature-label pairs, $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$; the feature vector $\bS$ is $T$ dimensional.
-    \item   $\Lhat_i^{MC}$ is a standard Monte Carlo estimator of the true loss for scenario $\bS^{(i)}$. 
+    \item   $\Lhat_i^{MC}$ is a standard \gls{mc} estimator of the true loss for scenario $\bS^{(i)}$. 
     It is an unbiased estimator and its variance is inversely proportional to the number of inner replications $N$. 
@@
 The withdrawal rate for \gls{gmwb} is $0.375\%$ per month.
-To make our examples more realistic, the \gls{va}s are also subject to a dynamic lapse model with the following key features~\citep{naic2021}:
+To make our examples more realistic, the \gls{va} contracts are also subject to a dynamic lapse model with the following key features~\citep{naic2021}:
 \begin{enumerate}
@@
 \gls{mlr} and \gls{qpr} are two common metamodels in the simulation literature, and their implemention is straightfoward in our simulation setting.
-\gls{fnn} is a generic neural network while \gls{rnn} and \gls{lstm} are specialized models to accommodate the sequential structure of our time-series features.
+\gls{fnn} (Equation~\refeq{eq:fnn}) is a generic neural network while \gls{rnn} (Equation~\refeq{eq:rnn}) and \gls{lstm} (Equation~\refeq{eq:lstm}) are specialized models to accommodate the sequential structure of our time-series features.
 A $\tanh$ activation function is used for \gls{rnn} and \gls{lstm} layers, and a ReLU activation function is used for the fully-connected layers.
@@
 Our \gls{lstm} has the same architecture as the \gls{rnn} but with \gls{lstm} cells in place of \gls{rnn} cells.
+.
 
@@
 Since the true relationship is unknown in real-world applications, most deep learning literature illustrates the impact of noise by artificially injecting noise into real-world datasets, which is already noisy prior to the injection.
-In our numerical experiments, we are able to use Monte Carlo simulation to generate a true dataset that approximates the true hedging losses with a high degree of precision, and, as a result, we are able to explore the important question of whether deep learning models are indeed capable of learning the true feature-label relationship from noisy training labels.
+In our numerical experiments, we are able to use \gls{mc} simulation to generate a true dataset that approximates the true hedging losses with a high degree of precision, and, as a result, we are able to explore the important question of whether deep learning models are indeed capable of learning the true feature-label relationship from noisy training labels.
 In this section, we treat the standard nested simulation procedure as a data generator and examine the noise tolerance of \gls{lstm} metamodels by varying the numbers of the outer scenarios ($M$) and the inner replications ($N$) used to generate the training samples.
@@
 We find that a \gls{dnn} with a suitable architecture is able to cut through the noise in training labels and learn the true complex dynamic hedging model.
-By showcasing the resilience of these models, our study aims at encouraging regulatory bodies to recognize the value and applicability of deep learning metamodels in financial risk management, and it provides informed suggestions and guidance for the incorporation and oversight of advanced deep learning metamodel in Monte Carlo Simulation in financial applications.
+By showcasing the resilience of these models, our study aims at encouraging regulatory bodies to recognize the value and applicability of deep learning metamodels in financial risk management, and it provides informed suggestions and guidance for the incorporation and oversight of advanced deep learning metamodel in \gls{mc} Simulation in financial applications.
 Our findings are particularly insightful in this context.
 
-In our numerical experiments, a \gls{lstm} metamodel is resilient to a high level of noise in training labels and is able to make accurate predictions. 
-This is an encouraging evidence that \gls{dnn} metamodels can be used to improve the efficiency of Monte Carlo simulation for quantitative risk management tasks that require a computational-expensive simulation procedure.
+In our numerical experiments, a \gls{lstm} metamodel is resilient to a moderate level of noise in training labels and is able to make accurate predictions. 
+This is an encouraging evidence that \gls{dnn} metamodels can be used to improve the efficiency of \gls{mc} simulation for quantitative risk management tasks that require a computational-expensive simulation procedure.
 We propose two nested simulation procedures that use \gls{dnn} metamodels to estimate risk measures of the hedging loss of a \gls{va} contract.
@@
 Our numerical experiments demonstrate that the proposed single-stage procedure with \gls{dnn} metamodels result in further computational savings over our two-stage procedure. 
-Furthermore, our numerical results provide evidences for adopting \gls{dnn} metamodels in Monte Carlo simulation for risk management tasks.
+Furthermore, our numerical results provide evidences for adopting \gls{dnn} metamodels in \gls{mc} simulation for risk management tasks.
 Through our systematic empirical study of the noise tolerance of \gls{dnn} metamodels, we address regulatory concerns by showing that a \gls{lstm} metamodel with moderate model capacity is resilient to a high level of noise in training labels and is able to make accurate predictions.

### 2025-05-08 project3/draft.tex
new

@@
 
-In the evolving landscape of financial markets, insurance products such as \gls{va}s have gained a substantial amount of interest due to their ability to provide both investment growth and guaranteed benefits.
+In the evolving landscape of financial markets, insurance products such as \gls{va} contracts have gained a substantial amount of interest due to their ability to provide both investment growth and guaranteed benefits.
 Managing risks associated with these products in volatile market conditions is a complex task that demands sophisticated financial modeling techniques such as nested simulation.
@@
 In particular, \gls{dnn}s, and specifically \gls{lstm} networks, have been employed as metamodels to predict the outcomes of the inner simulations efficiently.
-Chapter~\ref{chap:project2} introduced a metamodeling-based nested simulation framework for dynamic hedging of \gls{va}s that approximates the inner simulation by an \gls{lstm} metamodel.
+Chapter~\ref{chap:project2} introduced a metamodeling-based nested simulation framework for dynamic hedging of \gls{va} contracts that approximates the inner simulation by an \gls{lstm} metamodel.
 It shows that \gls{lstm}s, as a type of gated \gls{rnn}s, were well-suited as metamodels for \gls{mc} simulation of financial time series and could capture the long-term dependencies in the simulation dataset.
-This property is crucial for the application of dynamic hedging of \gls{va}s.
+This property is crucial for the application of dynamic hedging of \gls{va} contracts.
 
@@
 
-Constraints on the simulation budget is the most critical challenge for dynamic hedging of \gls{va}s.
+Constraints on the simulation budget is the most critical challenge for dynamic hedging of \gls{va} contracts.
 Any method that involves nested simulation is computationally expensive, and the computational cost is often prohibitive for changing market conditions.
 Therefore, it is essential to develop methods that can rapidly adapt existing metamodels to new conditions without incurring the full computational cost of retraining and extensive addtional simulations.
-Transfer Learning (\gls{tl}) offers a compelling solution to this problem by enabling the reuse of a pre-trained model on a new but related task~\citep{pan2009survey}.
+\gls{tl} offers a compelling solution to this problem by enabling the reuse of a pre-trained model on a new but related task~\citep{pan2009survey}.
 In the context of \gls{dnn}s, \gls{tl} involves leveraging the knowledge acquired during training on one dataset to improve learning performance on a different dataset~\citep{yosinski2014transferable}.
@@
 
-In this chapter, we explore the application of \gls{tl} to the dynamic hedging of \gls{va}s using \gls{lstm} metamodels.
+In this chapter, we explore the application of \gls{tl} to the dynamic hedging of \gls{va} contracts using \gls{lstm} metamodels.
 We propose a novel \gls{tl} framework that accelerates the training of \gls{dnn} metamodels for nested simulation procedures in dynamic hedging.
@@
 The rest of this chapter is organized as follows.
-Section~\ref{sec3:background} provides an overview of the dynamic hedging problem for \gls{va}s and the use of \gls{lstm} networks as metamodels in a nested simulation procedure.
+Section~\ref{sec3:background} provides an overview of the dynamic hedging problem for \gls{va} contracts and the use of \gls{lstm} networks as metamodels in a nested simulation procedure.
 Section~\ref{sec3:transfer_learning} introduces the \gls{tl} framework for rapid adaptation of \gls{lstm} metamodels in dynamic hedging.
@@
 One of the primary applications of \gls{tl} in finance is asset price prediction. 
-Traditional models, such as geometric Brownian motion (\gls{gbm}), autoregressive integrated moving average (\gls{arima}) and generalized autoregressive conditional heteroskedasticity (\gls{garch}), have been widely used in time series modeling.
+Traditional models, such as \gls{gbm}, \gls{arima} and \gls{garch}, have been widely used in time series modeling.
 \gls{arima} models~\citep{box1970distribution} combine autoregression, differencing, and moving average components to capture linear relationships in time series data.
@@
 However, these models often struggle to capture complex dynamics, e.g., regime changes~\citep{hamilton1989new} and extreme market events~\citep{embrechts2013modelling} that are prevalent in financial markets.
-In Chapter~\ref{chap:project2}, our numerical experiment uses a regime-switching geometric Brownian motion (\gls{rsgbm}) as the underlying asset model.
+In Chapter~\ref{chap:project2}, our numerical experiment uses a \gls{rsgbm} as the underlying asset model.
 For estimating tail risk measures, a metamodel-based nested simulation procedure is proposed to approximate the inner simulation.
@@
 
-Regarding a nested simulation of \gls{va}s,~\cite{cheng2019fast} is the most relevant study to our work, where they proposed a \gls{tl} framework for fast valuation of large portfolios of \gls{va}s.
-Instead of using stochastic kriging~\citep{gan2015valuation}, they employed a pre-trained \gls{dnn} to select the best representative scenarios from a large portfolio of \gls{va}s.
-In our work, we focus on the application of \gls{tl} to accelerate the training of \gls{lstm} metamodels for a nested simulation in dynamic hedging of \gls{va}s.
+Regarding a nested simulation of \gls{va} contracts,~\cite{cheng2019fast} is the most relevant study to our work, where they proposed a \gls{tl} framework for fast valuation of large portfolios of \gls{va} contracts.
+Instead of using stochastic kriging~\citep{gan2015valuation}, they employed a pre-trained \gls{dnn} to select the best representative scenarios from a large portfolio of \gls{va} contracts.
+In our work, we focus on the application of \gls{tl} to accelerate the training of \gls{lstm} metamodels for a nested simulation in dynamic hedging of \gls{va} contracts.
 The fine-tuned \gls{lstm} metamodels can be readily adapted to the two-stage procedure and the single-stage procedure in Chapter~\ref{chap:project2} to predict the contract losses under different scenarios.
 
-In our context of \gls{dnn}s metamodeling-based simulation procedures for hedging \gls{va}s, \gls{tl} involves pre-training a \gls{dnn} metamodel where the simulation budget is abundant and then fine-tuning it on a smaller dataset of new contracts or market conditions.
+In our context of \gls{dnn}s metamodeling-based simulation procedures for hedging \gls{va} contracts, \gls{tl} involves pre-training a \gls{dnn} metamodel where the simulation budget is abundant and then fine-tuning it on a smaller dataset of new contracts or market conditions.
 Written on the same underlying asset, different \gls{va} contracts may share common features or exhibit similar patterns, especially temporal dependencies and regime changes in the underlying financial time series.
-Similarly, two \gls{va}s with the same features but based on different underlying assets may have some shared characteristics that can be leveraged to improve the learning performance of the metamodel.
+Similarly, two \gls{va} contracts with the same features but based on different underlying assets may have some shared characteristics that can be leveraged to improve the learning performance of the metamodel.
 By transferring knowledge from a pre-trained model to a new but related task, \gls{tl} can substantially reduce the computational cost of training the metamodel on the target task.
@@
 
-In this section, we propose a \gls{tl} framework for rapid adaptation of \gls{lstm} metamodels in dynamic hedging of \gls{va}s.
+In this section, we propose a \gls{tl} framework for rapid adaptation of \gls{lstm} metamodels in dynamic hedging of \gls{va} contracts.
 The goal is to leverage the knowledge acquired during training on a large dataset of \gls{va} simulations to improve the learning performance on a smaller dataset of new \gls{va} contracts.
@@
 
-        \STATE \textbf{Multi-task learning:} define shared LSTM layers $\theta_0$ and task-specific fully connected layers $\theta_k$ for each task $k$.
-The LSTM layers are shared across all tasks $\{\mathcal{T}_k\}_{k=1}^K$.
+        \STATE \textbf{Multi-task learning:} define shared \gls{lstm} layers $\theta_0$ and task-specific fully connected layers $\theta_k$ for each task $k$.
+The \gls{lstm} layers are shared across all tasks $\{\mathcal{T}_k\}_{k=1}^K$.
 
@@
 
-        \STATE \textbf{Layer freezing:} once the multi-task metamodel is trained, freeze the parameters of the shared LSTM layers $\theta_0$.
+        \STATE \textbf{Layer freezing:} once the multi-task metamodel is trained, freeze the parameters of the shared \gls{lstm} layers $\theta_0$.
 
@@
 
-In this section, we evaluate the performance of the \gls{tl} framework for rapid adaptation of \gls{lstm} metamodels in dynamic hedging of \gls{va}s.
+In this section, we evaluate the performance of the \gls{tl} framework for rapid adaptation of \gls{lstm} metamodels in dynamic hedging of \gls{va} contracts.
 The low noise dataset generated by the standard nested simulation procedure in Section~\ref{sec2:numerical} is used to train the source \gls{lstm} metamodels.
@@
 Similar to Section~\ref{sec2:numerical}, we use the standard nested simulation procedure to generate the dataset for the source and target tasks.
-Serveral \gls{va} datasets generated with the standard nested simulation procedures under geometric Brownian motion (\gls{gbm}) and regime-switching \gls{gbm} (\gls{rsgbm}) asset models.
+Serveral \gls{va} datasets generated with the standard nested simulation procedures under \gls{gbm} and \gls{rsgbm} asset models.
 In this experiment, we use the same \gls{rsgbm} asset model as Chapter~\ref{chap:project2} to generate the dataset for the source and target tasks.
@@
 Multi-task learning enables the \gls{lstm} metamodels to learn shared representations across related \gls{va} contracts.
-In this section, we examine the performance of multi-task learning applied to two types of \gls{va}s, \gls{gmmb} and \gls{gmwb} with the dynamic lapse rates.
+In this section, we examine the performance of multi-task learning applied to two types of \gls{va} contracts, \gls{gmmb} and \gls{gmwb} with the dynamic lapse rates.
 The simulation datasets contain $2,\!000$ samples for each contract type, and the \gls{lstm} metamodels are trained using multi-task learning. 
@@
 Furthermore, a metamodel trained with multi-task learning can serve as a pre-trained model. 
-It is adaptable to various \gls{va} contracts and asset models, and it is a versatile tool for practical applications in dynamic hedging of \gls{va}s.
+It is adaptable to various \gls{va} contracts and asset models, and it is a versatile tool for practical applications in dynamic hedging of \gls{va} contracts.
 

### 2025-05-08 futureWork/rlHedging.tex
new

@@
 
-Reinforcement learning is a branch of machine learning in which an agent learns to make sequential decisions by interacting with its environment. 
+\gls{rl} is a branch of machine learning in which an agent learns to make sequential decisions by interacting with its environment. 
 Through trial and error, the agent receives feedback in the form of rewards or penalties, allowing it to learn an optimal policy for achieving long-term goals. 
@@
 Instead of retraining a deep \gls{rl} model from the scratch when market conditions shift, \gls{tl} enables the reuse of pre-trained models, facilitating a faster adaptation to new environments while avoiding overfitting to past conditions.
-In the risk management of \gls{va} contracts, transfer learning enables quicker adaptation to changing financial and actuarial assumptions by reusing information obtained from another set of related assumptions, such as the management of similar financial instruments or different market regimes.
-A \gls{drl} agent equipped with transfer learning can adjust its strategies in response to new market data, making the model more adaptive and responsive without the need for costly retraining.
+In the risk management of \gls{va} contracts, \gls{tl} enables quicker adaptation to changing financial and actuarial assumptions by reusing information obtained from another set of related assumptions, such as the management of similar financial instruments or different market regimes.
+A \gls{drl} agent equipped with \gls{tl} can adjust its strategies in response to new market data, making the model more adaptive and responsive without the need for costly retraining.
 More specifically, a \gls{drl} agent trained to manage \gls{va} contracts for a \gls{gmmb} contract can apply its learned strategies to a \gls{gmwb} contract with the same financial assumptions. 
@@
 This approach substantially reduces the computational costs associated with the training of new \gls{va} products with different assumptions and improves the generalization of the model to unseen market conditions.
-By integrating the transfer learning with the existing \gls{drl} frameworks, we can eliminate the inefficiencies of training models from scratch, provide faster adaptability to new market conditions, and enhance the scalability and computational efficiency of financial models.
+By integrating the \gls{tl} with the existing \gls{drl} frameworks, we can eliminate the inefficiencies of training models from scratch, provide faster adaptability to new market conditions, and enhance the scalability and computational efficiency of financial models.
 This approach offers a more robust and practical solution for managing \gls{va} contracts in dynamic and volatile financial markets.
@@
 \end{equation}
-The P\&L of the \gls{va} contract includes the cost of the initial hedge ($H_0$), the hedging errors~\eqref{eq2:hedgingerror}, the unwinding of the hedge at maturity ($H^{bf}_T$), and the contract payout at time~$t\in \{0,\ldots,T\}$.
+The \gls{pl} of the \gls{va} contract includes the cost of the initial hedge ($H_0$), the hedging errors~\eqref{eq2:hedgingerror}, the unwinding of the hedge at maturity ($H^{bf}_T$), and the contract payout at time~$t\in \{0,\ldots,T\}$.
 Mathematically, the present value of the liability for a \gls{gmmb} contract is 
@@
 \subsection{Model-Based RL: From AlphaZero to Deep Hedging}
-Deep reinforcement learning first attacted attentions when AlphaGo~\citep{silver2016mastering} surpasses human in playing Go. 
+\gls{drl} first attacted attentions when AlphaGo~\citep{silver2016mastering} surpasses human in playing Go. 
 Soon after, AlphaZero~\citep{silver2016mastering} emerged as a model-based \gls{rl} algorithm that improves over self-plays.
@@
 
-In a model-free reinforcement learning approach, the agent is a trial-and-error learner that interacts with the environment to learn the optimal policy by iteratively updating the policy and the value function based on the observed states, actions, and rewards.
+In a model-free \gls{rl} approach, the agent is a trial-and-error learner that interacts with the environment to learn the optimal policy by iteratively updating the policy and the value function based on the observed states, actions, and rewards.
 For hedging \gls{va} contracts, the agent does not have access to a planning algorithm or the underlying stochastic asset model, and it must learn the optimal policy by directly interacting with the environment.
@@
 The policy is then derived from the learned value function by selecting the action that maximizes the value function at each state. 
-~\cite{mnih2015human} is the first paper to demonstrate the effectiveness of value-based deep reinforcement learning in training agents to play Atari games.
+~\cite{mnih2015human} is the first paper to demonstrate the effectiveness of value-based \gls{drl} in training agents to play Atari games.
 To update the value function, the \gls{dnn} is trained to minimize the difference between the current value function and the target value function, which is updated based on the maximum expected reward from the previous iteration.
 When trained to approximate the value function, the \gls{dnn} benefits from the use of experience replay buffers, which is proposed by~\cite{lin1992self} to store and sample historical transitions and uniformly sampled during training to enhance the sample efficiency and stability of the learning process.
-~\cite{kolm2019dynamic} uses a value-based deep reinforcement learning approach to hedge European options under the \gls{gbm} asset model.
+~\cite{kolm2019dynamic} uses a value-based \gls{drl} approach to hedge European options under the \gls{gbm} asset model.
 
@@
 However, information of the underlying risk factors is leaked to the agent, which makes their study pseudo-model-free.
-To further improve the risk management of \gls{va} contracts under rough volatility models, we propose a model-free deep reinforcement learning approach to hedge \gls{va} contracts without explicit or implicit knowledge of the underlying risk factors.
+To further improve the risk management of \gls{va} contracts under rough volatility models, we propose a model-free \gls{drl} approach to hedge \gls{va} contracts without explicit or implicit knowledge of the underlying risk factors.
 
@@
 The \gls{trpo} algorithm proposed by~\cite{schulman2015trust} uses a similar clipped surrogate objective function to ensure that the policy update does not deviate too far from the old policy, but \gls{ppo} simplifies the optimization problem by using a clipped surrogate objective function instead of a hard-coded constraint on the policy update.
-Compared to \gls{trpo}, \gls{ppo} is more computationally efficient and easier to implement, making it a popular choice for training deep reinforcement learning agents.
+Compared to \gls{trpo}, \gls{ppo} is more computationally efficient and easier to implement, making it a popular choice for training \gls{drl} agents.
 For a in-depth discussion on the implementation details of both \gls{trpo} and \gls{ppo}, we refer the reader to~\cite{engstrom2020implementation}.
@@
 The most relevant paper to our study is~\cite{xiao2021optimal}, which use policy gradient algorithms to train hedging strategies for European options with simulation data from Heston model and then updated in real-time hedging S\&P 500 index options.
-To the best of our knowledge, no research has been conducted to improve the hedging strategies with the state-of-the-art transfer learning techniques.
-This section introduces some transfer learning techniques that are relevant to our task of hedging \gls{va} contracts.
+To the best of our knowledge, no research has been conducted to improve the hedging strategies with the state-of-the-art \gls{tl} techniques.
+This section introduces some \gls{tl} techniques that are relevant to our task of hedging \gls{va} contracts.
 
@@
 
-In the context of hedging \gls{va} contracts using deep reinforcement learning and transfer learning, reward shaping becomes a crucial technique. 
+In the context of hedging \gls{va} contracts using \gls{drl} and \gls{tl}, reward shaping becomes a crucial technique. 
 It involves modifying the reward function in the target domain to incorporate additional guidance, which often leads to more efficient learning and a better performance.
@@
 
-The most straightforward approach to transfer learning is to directly transfer the policy learned from the source domains to the target domain via policy distillation.
+The most straightforward approach to \gls{tl} is to directly transfer the policy learned from the source domains to the target domain via policy distillation.
 Policy distillation is a technique that transfers the knowledge from a teacher policy to a student policy by training the student policy to mimic the teacher policy up to a certain extent.
@@
 
-The metrics discussed for evaluating transfer learning approaches focus on two key aspects: mastery and generalization. 
+The metrics discussed for evaluating \gls{tl} approaches focus on two key aspects: mastery and generalization. 
 Mastery assesses the agent's final performance level in the target domain, indicating how effectively it has learned a specific task from previous knowledge. 
@@
     \includegraphics[width=0.9\textwidth]{./futureWork/figures/CVaR_histories.png}
-    \caption{Hedging performance of deep hedging with transfer learning}
+    \caption{Hedging performance of deep hedging with \gls{tl}}
     \label{fig3:dh-transfers}
@@
 
-Figure~\ref{fig3:dh-transfers} illustrates the hedging performance of the deep hedging algorithm with transfer learning for hedging \gls{va} contracts with a \gls{gmmb} rider.
-The first deep hedging agent is directly trained on the Heston asset model, and the second deep hedging agent is trained with transfer learning from the \gls{gbm} model.
+Figure~\ref{fig3:dh-transfers} illustrates the hedging performance of the deep hedging algorithm with \gls{tl} for hedging \gls{va} contracts with a \gls{gmmb} rider.
+The first deep hedging agent is directly trained on the Heston asset model, and the second deep hedging agent is trained with \gls{tl} from the \gls{gbm} model.
 The figure plot the 95\%-CVaR of hedging errors against training epochs for both agents.
-The deep hedging agent with transfer learning outperforms the deep hedging agent trained on the Heston model in both mastery and generalization.
-The agent with transfer learning achieves a lower loss in the target domain and adapts more quickly to the new environment, indicating that the agent has learned a more robust hedging strategy that can be effectively applied to a more complex environment.
+The deep hedging agent with \gls{tl} outperforms the deep hedging agent trained on the Heston model in both mastery and generalization.
+The agent with \gls{tl} achieves a lower loss in the target domain and adapts more quickly to the new environment, indicating that the agent has learned a more robust hedging strategy that can be effectively applied to a more complex environment.
 
@@
         \includegraphics[width=\textwidth]{./futureWork/figures/PPOs_GBM.png}
-        \caption{GBM}
+        \caption{\gls{gbm}}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{./futureWork/figures/PPOs_GBMRS.png}
-        \caption{Regime-switching GBM}
+        \caption{\gls{rsgbm}}
     \end{subfigure}
@@
 For both asset models, the recurrent \gls{ppo} outperforms the standard \gls{ppo} in terms of hedging performance.
-For the regime-switching \gls{gbm}, the 95\%-VaR of hedging errors of the recurrent \gls{ppo} and the standard \gls{ppo} are $136.24$ and $147.14$, respectively.
+For the \gls{rsgbm}, the 95\%-VaR of hedging errors of the recurrent \gls{ppo} and the standard \gls{ppo} are $136.24$ and $147.14$, respectively.
 The hedging errors of the recurrent \gls{ppo} are more concentrated around zero, indicating that historical information captured by the \gls{lstm} component helps the agent make better hedging decisions even in the enviornment is Markovian.
@@
 
-The proposed future work of this thesis aims at investigating how transfer learning can be effectively integrated into the training of \gls{ppo} agents for dynamic hedging of \gls{va} contracts. 
+The proposed future work of this thesis aims at investigating how \gls{tl} can be effectively integrated into the training of \gls{ppo} agents for dynamic hedging of \gls{va} contracts. 
 The primary goal is to enhance the adaptability and efficiency of hedging strategies in response to new \gls{va} products and changing market conditions.
@@
 By addressing these objectives, the research aims at advancing the field of financial risk management through the development of adaptive and efficient hedging strategies for \gls{va} contracts.
-The integration of transfer learning into \gls{ppo} agents has the potential to substantially reduce computational costs and improve the robustness of hedging policies in dynamic market environments.
+The integration of \gls{tl} into \gls{ppo} agents has the potential to substantially reduce computational costs and improve the robustness of hedging policies in dynamic market environments.

### 2025-05-08 introduction.tex
new

@@
 The activation function choice is crucial for training neural networks.
-While sigmoid and hyperbolic tangent functions were popular in early neural networks, ReLU has become the default activation function for deep networks due to its ability to mitigate the vanishing gradient problem and promote sparse activations~\citep{lecun2015deep}.
+While sigmoid and hyperbolic tangent functions were popular in early neural networks, \gls{relu} has become the default activation function for deep networks due to its ability to mitigate the vanishing gradient problem and promote sparse activations~\citep{lecun2015deep}.
 

### 2025-05-08 project1/nsSurvey.tex
new

@@
 In this section, we conduct a series of numerical experiments to compare the empirical convergence of the nested simulation procedures for different risk measures, option types, and asset dimensions.
-Numerical experiments are conducted on portfolios that consist of options on $d$ underlying assets, whose dynamics follow a multidimensional geometric Brownian motion with $0.3$ pairwise correlation.
+Numerical experiments are conducted on portfolios that consist of options on $d$ underlying assets, whose dynamics follow a multidimensional \gls{gbm} with $0.3$ pairwise correlation.
 The initial values of the assets are set to be $100$.
@@
 
-Our previous numerical experiments have been conducted under the assumption that the underlying asset dynamics follow a multidimensional geometric Brownian motion with $0.3$ pairwise correlation.
+Our previous numerical experiments have been conducted under the assumption that the underlying asset dynamics follow a multidimensional \gls{gbm} with $0.3$ pairwise correlation.
 To examine the sensitivity of the empirical convergence behavior to the asset model, we consider a stochastic volatility model of a Heston type~\citep{heston1993closed}.
@@
 
-In Figure~\ref{fig1:sens_model}, the empirical convergence results of the regression-based nested simulation procedure for a quadratic tracking error and a 90\%-\gls{cvar} are illustrated for different asset models, i.e., a geometric Brownian motion and a Heston model.
+In Figure~\ref{fig1:sens_model}, the empirical convergence results of the regression-based nested simulation procedure for a quadratic tracking error and a 90\%-\gls{cvar} are illustrated for different asset models, i.e., a \gls{gbm} and a Heston model.
 The empirical rates of convergence of the regression-based nested simulation procedure are observed to be insensitive to the asset model.

### 2025-05-08 project2/nnMetamodels.tex
new

@@
 
-The risk-free rate is $0.2\%$ per month and the underlying asset $S_t$ is modeled by a regime-switching geometric Brownian motion with parameters specified in Table~\ref{tab:regime_params}.
+The risk-free rate is $0.2\%$ per month and the underlying asset $S_t$ is modeled by a \gls{rsgbm} with parameters specified in Table~\ref{tab:regime_params}.
 
@@
     \end{tabular}
-    \caption{Real-world parameters for the regime-switching model (monthly rates)}
+    \caption{Real-world parameters for the \gls{rsgbm} model (monthly rates)}
     \label{tab:regime_params}
@@
 \gls{fnn} (Equation~\refeq{eq:fnn}) is a generic neural network while \gls{rnn} (Equation~\refeq{eq:rnn}) and \gls{lstm} (Equation~\refeq{eq:lstm}) are specialized models to accommodate the sequential structure of our time-series features.
-A $\tanh$ activation function is used for \gls{rnn} and \gls{lstm} layers, and a ReLU activation function is used for the fully-connected layers.
+A $\tanh$ activation function is used for \gls{rnn} and \gls{lstm} layers, and a \gls{relu} activation function is used for the fully-connected layers.
 All neural network metamodels are trained by the Adam optimizer~\citep{kingma2014adam} with an initial learning rate of $0.001$ and an exponential learning rate decay schedule.

### 2025-05-08 futureWork/rlHedging.tex
new

@@
 In a \gls{lstm}, the cell state $c_t$ stores a representation of historical information up to time $t$.
-It is updated at each time step by a forget gate $f_t$, an input gate $i_t$, and an output gate $o_t$.
-Equation~\ref{eq:lstm} provides a general intoduction to \gls{lstm} for a generic time series input $x_t$.
+The variables $i_t, f_t, o_t, g_t, c_t, h_t$ are an input gate, a forget gate, an output gate, a cell input, a cell state, and a hidden state at time $t$, respectively.
+$W_i$, $W_f$, $W_o$, $W_g$, $U_i$, $U_f$, $U_o$, $U_g$ are weight matrices, and $b_i$, $b_f$, $b_o$, $b_g$ are bias vectors.
+$a$ is the activation function, typically a sigmoid function 
+\begin{equation} \label{eq3:sigmoid}
+    a(x) = \frac{1}{1 + e^{-x}}.
+\end{equation}
+$\odot$ denotes an element-wise multiplication.
+Section~\ref{subsec:LSTM} provides a general intoduction to \gls{lstm} for a generic time series input $x_t$.
 

### 2025-05-08 futureWork/rlHedging.tex
final draft

@@
 Additionally, \gls{tl} enhances the robustness of models by allowing continuous learning. 
-Instead of retraining a deep \gls{rl} model from the scratch when market conditions shift, \gls{tl} enables the reuse of pre-trained models, facilitating a faster adaptation to new environments while avoiding overfitting to past conditions.
+Instead of retraining a \gls{drl} model from the scratch when market conditions shift, \gls{tl} enables the reuse of pre-trained models, facilitating a faster adaptation to new environments while avoiding overfitting to past conditions.
 In the risk management of \gls{va} contracts, \gls{tl} enables quicker adaptation to changing financial and actuarial assumptions by reusing information obtained from another set of related assumptions, such as the management of similar financial instruments or different market regimes.
@@
 Section~\ref{sec:RLAlgorithms} provides an overview of existing \gls{rl} algorithms and their limitations in the context of hedging \gls{va} contracts.
-Section~\ref{sec:PPO} introduces the proximal policy optimization algorithm and its application to the hedging of \gls{va} contracts.
+Section~\ref{sec:PPO} introduces the \gls{ppo} algorithm and its application to the hedging of \gls{va} contracts.
 Finally, Section~\ref{sec:FutureDirections} concludes the chapter and discusses future research directions.
@@
 A \gls{mdp} provides a mathematical framework for modeling decision-making in stochastic environments over time. 
-By formulating the \gls{va} hedging problem as an \gls{mdp}, we can utilize RLalgorithms to learn optimal hedging policies directly from data.
+By formulating the \gls{va} hedging problem as an \gls{mdp}, we can utilize \gls{rl} algorithms to learn optimal hedging policies directly from data.
 An \gls{mdp} is defined by the tuple $\mathcal{M} = (\mathcal{S}, \mathcal{A}, \mathcal{P}, \mathcal{R}, \gamma)$, where:
@@
     $$
-    and $M_q$, $D_q$, $L_q$, and $U_q$ are the model parameters taken from National Association of Insurance Commissioners’ (NAIC) Valuation Manual 21~\citep{naic2021}.
+    and $M_q$, $D_q$, $L_q$, and $U_q$ are the model parameters taken from National Association of Insurance Commissioners’ Valuation Manual 21~\citep{naic2021}.
     \item The sub-account value changes according to the growth of the underlying stock and the (gross) management fee is deducted. That is, 
@@
 $\mathbf{p}$ and $z$ are a probability distribution of the next move and an outcome of the game, respectively.
-They are induced by a planning algorithm, i.e., Monte Carlo Tree Search (MCTS).
+They are induced by a planning algorithm, i.e., \gls{mcts}.
 Since it is infeasible to efficiently simulate trajectories in the game of Go, a planning algorithm is necessary to generate expected outcomes.
@@
 The last term penalizes large neural network weights.
-Its first two terms measure the similarity between $f_{\theta}(s)$, the learned policy and value function, with the action and game outcome planned by the MCTS.
+Its first two terms measure the similarity between $f_{\theta}(s)$, the learned policy and value function, with the action and game outcome planned by the \gls{mcts}.
 The neural network is trained to fit the planned outcomes of the game.
@@
 
-A common choice of $\rho$ is a CVaR.
-In practice, the neural network $f_{\theta}$ is trained to minimize the empirical CVaR over a batch of trajectories.
+A common choice of $\rho$ is a \gls{cvar}.
+In practice, the neural network $f_{\theta}$ is trained to minimize the empirical \gls{cvar} over a batch of trajectories.
 In other words, planning is done through $\rho$, which measures the performance of a hedging policy over a batch of complete trajectories.
@@
 where $\theta_{old}$ denotes the policy parameters at the previous iteration, $\epsilon$ is a clip range hyperparameter that controls the size of the policy update, $\text{clip}(x, a, b)$ is a function that clips the value of $x$ to be within the range $[a, b]$, and $\hat{A}^{\pi_{\theta}}(s_t, a_t)$ is an estimated advantage of taking action $a_t$ in state $s_t$ over following the policy $\pi_{\theta_{old}}$.
-In our implementation, the advantage function is estimated following the GAE method proposed by~\cite{schulman2015high}.
+In our implementation, the advantage function is estimated following the Generalized Advantage Estimation method proposed by~\cite{schulman2015high}.
 The policy is updated by performing gradient ascent with respect to the policy parameters $\theta$ to maximize the objective function, which is estimated by sampling from the environment and computing the empirical average of the objective function over the sampled trajectories.
@@
     \end{tabular}
-    \caption{\gls{ppo} Hyperparameters and \gls{gmmb} Contract Specifications} 
+    \caption{Model hyperparameters and \gls{gmmb} contract specifications} 
     \label{tab3:hyperparameters}
@@
 The first deep hedging agent is directly trained on the Heston asset model, and the second deep hedging agent is trained with \gls{tl} from the \gls{gbm} model.
-The figure plot the 95\%-CVaR of hedging errors against training epochs for both agents.
+The figure plot the 95\%-\gls{cvar} of hedging errors against training epochs for both agents.
 The deep hedging agent with \gls{tl} outperforms the deep hedging agent trained on the Heston model in both mastery and generalization.

### 2025-05-08 futureWork/rlHedging.tex
final draft

@@
 The objective in an \gls{mdp} is to find a policy, $\pi: \mathcal{S} \rightarrow \mathbb{P}(\mathcal{A})$, that maximizes the cumulative reward over time.
-A \gls{mdp} provides a mathematical framework for solving sequential decision-making tasks in an enviornment where outcomes are partly random and partly under the control of a hedging agent. 
+A \gls{mdp} provides a mathematical framework for solving sequential decision-making tasks in an environment where outcomes are partly random and partly under the control of a hedging agent. 
 For hedging \gls{va} contracts, the asset dynamics and the mortality model are not controlled by the agent, but the agent controls the cumulative reward by deciding on the hedging weights.
-In this section, we reformulate the hedging enviornment of \gls{va} contracts from Section~\ref{subsec:VApayout} as an \gls{mdp} and define the key components of the \gls{mdp}.
+In this section, we reformulate the hedging environment of \gls{va} contracts from Section~\ref{subsec:VApayout} as an \gls{mdp} and define the key components of the \gls{mdp}.
 
@@
     $$
-    and $M_q$, $D_q$, $L_q$, and $U_q$ are the model parameters taken from National Association of Insurance Commissioners’ Valuation Manual 21~\citep{naic2021}.
+    and $M_q$, $D_q$, $L_q$, and $U_q$ are the model parameters taken from National Association of Insurance Commissioners' Valuation Manual 21~\citep{naic2021}.
     \item The sub-account value changes according to the growth of the underlying stock and the (gross) management fee is deducted. That is, 
@@
 \end{align}
-where the equality holds by a rearrangement of terms and a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$, and $C_t := C \cdot S_{t-1} \cdot |\Delta_t - \Delta_{t-1}|$ is the tranaction cost at time $t$~\citep{garleanu2013dynamic}.
+where the equality holds by a rearrangement of terms and a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$, and $C_t := C \cdot S_{t-1} \cdot |\Delta_t - \Delta_{t-1}|$ is the transaction cost at time $t$~\citep{garleanu2013dynamic}.
 Hence, the present liability consist of the hedging errors, the transaction costs, the net management fees, and the contract payouts.
@@
 
-\section{Exising RL Algorithms and Their Limitations} \label{sec:RLAlgorithms}
+\section{Existing RL Algorithms and Their Limitations} \label{sec:RLAlgorithms}
 
 \subsection{Model-Based RL: From AlphaZero to Deep Hedging}
-\gls{drl} first attacted attentions when AlphaGo~\citep{silver2016mastering} surpasses human in playing Go. 
+\gls{drl} first attracted attention when AlphaGo~\citep{silver2016mastering} surpasses human in playing Go. 
 Soon after, AlphaZero~\citep{silver2016mastering} emerged as a model-based \gls{rl} algorithm that improves over self-plays.
 It quickly extended beyond Go to other games like Chess and Shogi.
-In essence, the AlphaZero agent use a neural network to paramaterize the policy and the value function.
+In essence, the AlphaZero agent use a neural network to parameterize the policy and the value function.
 The neural network takes the current state of the game as input and outputs the probability distribution of the next move and a value of the current state.
@@
 This simplifies the planning as complete trajectories can be simulated without the need of a planning algorithm.
-In contrast to AlphaZero, deep hedging~\citep{buehler2019deep} uses monte carlo simulations to generate sample paths of asset dynamics.
+In contrast to AlphaZero, deep hedging~\citep{buehler2019deep} uses \gls{mc} simulations to generate sample paths of asset dynamics.
 These simulations are conducted based on predefined stochastic asset models. 
@@
 
-Boardly speaking, model-free \gls{rl} can be categorized into two types: value-based \gls{rl} and policy-based \gls{rl}.
+Broadly speaking, model-free \gls{rl} can be categorized into two types: value-based \gls{rl} and policy-based \gls{rl}.
 Value-based approaches learn the value function directly from the data and derive the policy from the learned value function. 
@@
 \begin{algorithm}
-    \caption{Recurrent \gls{ppo} with \gls{lstm} for Hedging Variable Annuities} 
+    \caption{Recurrent PPO with LSTM for Hedging Variable Annuities} 
     \begin{algorithmic}[1] \label{alg3:ppoHedging-rnn}
@@
         \includegraphics[width=\textwidth]{./futureWork/tikz/ppo_diagram.pdf}
-        \caption{regular \gls{ppo}}
+        \caption{Regular PPO}
         \label{subfig3:architecturePPO}
@@
         \includegraphics[width=\textwidth]{./futureWork/tikz/recurrentppo_diagram.pdf}
-        \caption{Recurrent \gls{ppo} with \gls{lstm}}
+        \caption{Recurrent PPO with LSTM}
         \label{subfig3:architectureLSTMPPO}
     \end{subfigure}
-    \caption{\gls{ppo} Network Architectures} 
+    \caption{PPO Network Architectures} 
     \label{fig3:architecturePPO}
@@
     \end{tabular}
-    \caption{Model hyperparameters and \gls{gmmb} contract specifications} 
+    \caption{Model hyperparameters and GMMB contract specifications} 
     \label{tab3:hyperparameters}
@@
     \includegraphics[width=0.9\textwidth]{./futureWork/figures/CVaR_histories.png}
-    \caption{Hedging performance of deep hedging with \gls{tl}}
+    \caption{Hedging performance of deep hedging with TL}
     \label{fig3:dh-transfers}
@@
     \includegraphics[width=0.5\textwidth]{./futureWork/figures/PPO_DH.png}
-    \caption{Hedging performance of recurrent \gls{ppo} and deep hedging}
+    \caption{Hedging performance of recurrent PPO and deep hedging}
     \label{fig3:ppo_dh}
@@
         \includegraphics[width=\textwidth]{./futureWork/figures/PPOs_GBM.png}
-        \caption{\gls{gbm}}
+        \caption{GBM}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{./futureWork/figures/PPOs_GBMRS.png}
-        \caption{\gls{rsgbm}}
+        \caption{RS-GBM}
     \end{subfigure}
-    \caption{Hedging performance of standard \gls{ppo} and recurrent \gls{ppo}} 
+    \caption{Hedging performance of standard PPO and recurrent PPO} 
     \label{fig3:ppo_result}
@@
     \end{subfigure}
-    \caption{Hedging performance of recurrent \gls{ppo} and delta hedging with different transaction costs} 
+    \caption{Hedging performance of recurrent PPO and delta hedging with different transaction costs} 
     \label{fig3:ppo_cost}
@@
     \includegraphics[width=\textwidth]{./futureWork/figures/PPO_anchor.png}
-    \caption{Hedging performance of recurrent \gls{ppo} with or without anchor}
+    \caption{Hedging performance of recurrent PPO with or without anchor}
     \label{fig3:ppo_anchor}
@@
     \includegraphics[width=\textwidth]{./futureWork/figures/PPO_GMWB.png}
-    \caption{Hedging performance of recurrent \gls{ppo} with \gls{gmwb}}
+    \caption{Hedging performance of recurrent PPO with GMWB}
     \label{fig3:ppo_GMWB}

### 2025-05-08 introduction.tex
final draft

@@
 
-The development of advanced machine learning models and deep learning techniques has enhanced metamodeling approaches for \gls{mc} simulations, especially in high-dimensional and complex problem settings.
-Examples of machine learning applications include~\cite{jin2020deep},~\cite{tang2020deep}, and~\cite{rosen2012metamodeling}.
+The development of advanced \gls{ml} models and deep learning techniques has enhanced metamodeling approaches for \gls{mc} simulations, especially in high-dimensional and complex problem settings.
+Examples of \gls{ml} applications include~\cite{jin2020deep},~\cite{tang2020deep}, and~\cite{rosen2012metamodeling}.
 These methods offer powerful tools for capturing intricate patterns and nonlinear relationships that traditional metamodeling techniques might struggle to model effectively.
-In the following sections, we discuss machine learning algorithms in the context of metamodeling for \gls{mc} simulations and their applications in risk management.
+In the following sections, we discuss \gls{ml} algorithms in the context of metamodeling for \gls{mc} simulations and their applications in risk management.
 
@@
 
-Machine learning (ML) algorithms are essential tools for identifying complex patterns and relationships in data.
+\gls{ml} algorithms are essential tools for identifying complex patterns and relationships in data.
 In particular, they are well-suited for handling non-linearities and large-scale data structures, which are challenging for traditional statistical methods.
-In the context of risk management, ML algorithms have been widely used for predicting financial time series, estimating risk measures, and optimizing trading strategies.
-ML algorithms can be broadly categorized into supervised learning, unsupervised learning, and reinforcement learning.
+In the context of risk management, \gls{ml} algorithms have been widely used for predicting financial time series, estimating risk measures, and optimizing trading strategies.
+\gls{ml} algorithms can be broadly categorized into supervised learning, unsupervised learning, and reinforcement learning.
 This section focuses on three widely used supervised learning models and two reinforcement learning algorithms that are most relevant to risk management applications.
@@
 
-Supervised learning is a fundamental approach in machine learning where the algorithm learns a mapping from inputs to outputs based on example input-output pairs~\cite{galton1886regression}.
+Supervised learning is a fundamental approach in \gls{ml} where the algorithm learns a mapping from inputs to outputs based on example input-output pairs~\cite{galton1886regression}.
 In this paradigm, a model is trained on a labeled dataset, which means that each training example is associated with an output label or value.
@@
 This method has been thoroughly explored in statistical literature.
-\citet{bishop2006pattern} provide an extensive treatment of regression techniques in the broader context of machine learning.
+\citet{bishop2006pattern} provide an extensive treatment of regression techniques in the broader context of \gls{ml}.
 It is known as a parametric regression because it assumes a specific functional form for the input-output relationship with a finite set of parameters~\citep{seber2012linear}.
@@
 The key advantage of \gls{fnn}s lies in their ability to perform automatic feature engineering without a direct human intervention.
-Unlike traditional machine learning models that require manual selection and transformation of input features, neural networks learn to extract and compose features through their hidden layers during their training.
+Unlike traditional \gls{ml} models that require manual selection and transformation of input features, neural networks learn to extract and compose features through their hidden layers during their training.
 Each hidden layer in the network captures higher-level abstractions of the input data by transforming the outputs of the previous layer through nonlinear activation functions~\citep{lecun2015deep}.
@@
 Evaluation of the performance of a neural network is challenging due to the absence of analytical tools.
-Existing machine learning literature addresses this challenge by splitting the data into three parts: training set, validation set, and test set.
+Existing \gls{ml} literature addresses this challenge by splitting the data into three parts: training set, validation set, and test set.
 The training set is used to train the model, the validation set is used to tune the model hyperparameters, and the test set is used to evaluate how well the model generalizes to unseen data.
@@
 Overfitting occurs when the neural network fits to the noise in the training data and cannot generalize results to unseen data.
-In machine learning literature, overfitting is often quantified as the gap between the training error and the test error~\citep{bishop2006pattern}.
+In \gls{ml} literature, overfitting is often quantified as the gap between the training error and the test error~\citep{bishop2006pattern}.
 During training, as the test dataset is not used, this quantity is estimated by using the validation set.
@@
 In practice, the ultimate performance of a neural network is often evaluated based on error metrics on the test dataset and how it compares with the training error.
-The test error is often thought to be a reliable indicator of the model's generalization capability for most machine learning applications.
+The test error is often thought to be a reliable indicator of the model's generalization capability for most \gls{ml} applications.
 However, real-world datasets often contain noise.
@@
 
-Figure~\ref{fig:datasets} shows datasets with different levels of noise in a typical machine learning setting.
+Figure~\ref{fig:datasets} shows datasets with different levels of noise in a typical \gls{ml} setting.
 The left panel illustrates the common practice of using a test dataset that is separate from the training dataset that is contaminated with noise.

### 2025-05-08 pre/oh.tex
final draft

\begin{frame}{Learning Curves: With Transfer Learning}
    \begin{columns}
    \column{0.5\textwidth}
    \includegraphics[height=0.8\textheight]{../project3/figures/figure1c.png}
    \column{0.5\textwidth}
    \includegraphics[height=0.8\textheight]{../project3/figures/figure1d.png}
    \end{columns}

    \textit{The effect of transfer learning on limited training samples}
    \begin{itemize}
        \item \textit{Left: fine-tuning; right: layer freezing}
    \end{itemize}
    \end{frame}

    \begin{frame}{Experimental Setup}
    \begin{itemize}
        \item \textbf{Source domain}: VA contract with specific features/parameters
        \item \textbf{Target domain}: New VA contract or same contract with different features
        \item \textbf{Architecture}: LSTM-based metamodel
        \item \textbf{Transfer approach}: Pre-trained weights from source model
    \end{itemize}
    \end{frame}

    \begin{frame}{Learning Dynamic Lapse}
    \textbf{The Effect of Similarity between Source and Target}
    \end{frame}

    \begin{frame}{Learning Curves: Learning Dynamic Lapse}
    \begin{columns}
    \column{0.5\textwidth}
    \includegraphics[height=0.8\textheight]{../project3/figures/figure2a.png}
    \column{0.5\textwidth}
    \includegraphics[height=0.8\textheight]{../project3/figures/figure2b.png}
    \end{columns}

    \textit{The effect of similarity between source and target on the convergence speed}
    \begin{itemize}
        \item \textit{Left: from No Lapse; right: from Static Lapse}
    \end{itemize}
    \end{frame}

    \begin{frame}{Results: Accuracy Comparison}
    \begin{table}
    \begin{tabular}{lcccc}
    \toprule
    \textbf{Lapse Type} & \textbf{Extensive} & \textbf{Fine-tuning} & \textbf{Layer Freezing} & \textbf{Without TL} \\
    \midrule
    No Lapse & N/A & 0.4894 & \textbf{0.3361} & N/A \\
    Static Lapse & N/A & 0.0794 & 0.0763 & N/A \\
    Dynamic Lapse & \textbf{0.0587} & N/A & N/A & \textbf{0.2950} \\
    \bottomrule
    \end{tabular}
    \end{table}

    \textit{Comparison of different TL methods on GMMB contracts (best MSE values)}
    \end{frame}

    \begin{frame}{Learning Curves: Effect of Similarity}
    \begin{columns}
    \column{0.5\textwidth}
    \includegraphics[height=0.8\textheight]{../project3/figures/figure3a.png}
    \column{0.5\textwidth}
    \includegraphics[height=0.8\textheight]{../project3/figures/figure3b.png}
    \end{columns}

    \textit{The effect of similarity between source and target on the convergence speed}
    \begin{itemize}
        \item \textit{Left: from No Lapse; right: from Static Lapse}
    \end{itemize}
    \end{frame}

    \begin{frame}{Transfer Knowledge to other Contract Types}
    \textbf{From GMMB to GMWB Contract}
    \end{frame}

    \begin{frame}{Learning Curves: Transfer Knowledge to other Contract Types}
    \begin{columns}
    \column{0.5\textwidth}
    \includegraphics[height=0.8\textheight]{../project3/figures/figure4a.png}
    \column{0.5\textwidth}
    \includegraphics[height=0.8\textheight]{../project3/figures/figure4b.png}
    \end{columns}

    \textit{Learning curves of GMWB contracts}
    \begin{itemize}
        \item \textit{Left: 50000 samples; right: 2000 samples}
    \end{itemize}
    \end{frame}

    \begin{frame}{Learning Curves: Effect of Similarity}
    \begin{columns}
    \column{0.5\textwidth}
    \includegraphics[height=0.8\textheight]{../project3/figures/figure4c.png}
    \column{0.5\textwidth}
    \includegraphics[height=0.8\textheight]{../project3/figures/figure4d.png}
    \end{columns}

    \textit{Comparison of different TL methods on GMWB contracts}
    \begin{itemize}
        \item \textit{Left: fine-tuning; right: layer freezing}
    \end{itemize}
    \end{frame}

    \begin{frame}{Performance Comparison (GMMB → GMWB)}
    \begin{table}
    \begin{tabular}{lcc}
    \toprule
    \textbf{Model} & \textbf{Training MSE} & \textbf{True MSE} \\
    \midrule
    Without TL & 0.3588 & 0.4188 \\
    Fine Tuning & 0.1690 & 0.1780 \\
    Layer Freezing & 0.1828 & 0.2295 \\
    Extensive Training & 0.0853 & 0.0726 \\
    \bottomrule
    \end{tabular}
    \end{table}

    \begin{itemize}
        \item Fine-tuning outperforms layer freezing for dissimilar tasks
        \item Both TL methods better than training from scratch
        \item Extensive training still superior with abundant data
    \end{itemize}
    \end{frame}

    \begin{frame}{Practical Implementation}
    \begin{itemize}
        \item \textbf{Framework}: TensorFlow/PyTorch implementation
        \item \textbf{Workflow}:
        \begin{enumerate}
            \item Train base model on source contract
            \item Freeze early layers
            \item Fine-tune later layers on target contract
            \item Deploy for production use
        \end{enumerate}
    \end{itemize}

    \textbf{PyTorch} is recommended.
    \begin{itemize}
        \item It is more flexible and easier to customize
        \item It is more intuitive and easier to understand 
        \item It is more efficient and easier to debug
    \end{itemize}
    \end{frame}

    \begin{frame}{Multi-task Learning}
    \includegraphics[width=0.9\textwidth]{../project3/figures/mtl.png}

    \begin{itemize}
        \item LSTM layers shared across multiple tasks
        \item Task-specific fully connected layers
        \item Objective: Minimize sum of loss functions across all tasks
    \end{itemize}
    \end{frame}

    \begin{frame}{Multi-task Learning Framework}
    \textbf{Input}: Set of $K$ tasks $\{\mathcal{T}_k\}_{k=1}^K$ with datasets $\mathcal{D}_k = \{(X_k^{(i)}, L_k^{(i)})\}_{i=1}^{M_k}$, shared parameters $\theta_0$, and task-specific parameters $\theta_k$ for each task $k$

    \textbf{Algorithm}:
    \begin{enumerate}
        \item Train the multi-head LSTM metamodel on all $K$ tasks simultaneously by minimizing the multi-task loss function:
        \begin{equation}
            \min_{\theta_0, \{\theta_k\}_{k=1}^K} \sum_{k=1}^K \frac{1}{M_k} \sum_{i=1}^{M_k} \left( f_i(X_k^{(i)}; \theta_0, \theta_k) - L_k^{(i)} \right)^2
        \end{equation}
        \item Update both the shared parameters $\theta_0$ and task-specific parameters $\{\theta_k\}_{k=1}^K$ simultaneously using backpropagation and gradient descent with learning rate $\alpha$
    \end{enumerate}

    \textbf{Output}: Trained multi-task LSTM metamodel $f(\cdot; \theta_0, \{\theta_k\}_{k=1}^K)$ for all $K$ tasks
    \end{frame}

    \begin{frame}{Multi-task Learning: GMMB and GMWB}
    \begin{columns}
    \column{0.5\textwidth}
    \includegraphics[height=0.8\textheight]{../project3/figures/figure5a.png}
    \column{0.5\textwidth}
    \includegraphics[height=0.8\textheight]{../project3/figures/figure5b.png}
    \end{columns}

    \textit{Multi-task learning of GMMB and GMWB}
    \begin{itemize}
        \item \textit{Left: total MSE; right: individual MSE}
    \end{itemize}
    \end{frame}

    \begin{frame}{Multi-task Learning: GMMB and GMWB}
    \begin{columns}
    \column{0.5\textwidth}
    \includegraphics[height=0.8\textheight]{../project3/figures/figure5c.png}
    \column{0.5\textwidth}
    \includegraphics[height=0.8\textheight]{../project3/figures/figure5d.png}
    \end{columns}

    \textit{Training without multi-task learning}
    \begin{itemize}
        \item \textit{Left: GMMB; right: GMWB}
    \end{itemize}
    \end{frame}

    \begin{frame}{Challenges \& Limitations}
    \begin{itemize}
        \item Determining optimal layer freezing strategy
        \item Handling significantly different contract structures
        \item Quantifying uncertainty in transfer learning predictions
        \item Regulatory acceptance of black-box approaches
    \end{itemize}
    \end{frame}

    \begin{frame}{Conclusions}
    \begin{itemize}
        \item Transfer learning significantly improves metamodeling for VA contracts:
        \begin{itemize}
            \item Faster training convergence
            \item Better prediction accuracy
            \item Reduced computational requirements
        \end{itemize}
        \item Enables more frequent risk assessments and faster decision-making
    \end{itemize}
    \end{frame}

    \begin{frame}{Future Directions}
    \begin{itemize}
        \item Incorporating domain knowledge into transfer process
        \item Extension to other insurance and financial products
        \item Multi-task learning with more than two tasks
    \end{itemize}
    \end{frame}

### 2025-05-08 project1/nsSurvey.tex
final draft

@@
 Section~\ref{sec1:conclusion} concludes this chapter.
+In appendix, we briefly sketch out connections between two modes of convergence for nested simulation procedures.
 
@@
 This phenomenon is due to the fact that the convergence analysis for the \gls{krr}-based nested simulation procedure is shown in terms of \gls{ae}, a different error metric than \gls{mse}.
-In the appendix, Section~\ref{appendix:connection-mse-absolute-error} includes a discussion of the connection between the \gls{mse} and the \gls{ae} of the estimator in the context of nested simulation procedures.
+In appendix, we include a discussion of the connection between the \gls{mse} and the \gls{ae} of the estimator in the context of nested simulation procedures.
 In Table~\ref{tab1:smoothness}, the standard nested simulation procedure is the only procedure without an asymptotic convergence analysis for smooth $h$.
@@
 \end{align}
-Section~\ref{appendix:connection-mse-absolute-error} draws the connection between the \gls{mse} and the \gls{ae} of the estimator in the context of nested simulation procedures.
+In appendix, we sketch out the connection between the \gls{mse} and the \gls{ae} of the estimator in the context of nested simulation procedures.
 
@@
     \hline
-    Standard MC & $\star$ & $\star$($\checkmark$) & $\checkmark$ & $\checkmark$ & $\times$ \\
-    \hline
-    Multi-level MC & $\times$ & $\times$($\times$) & $\checkmark$ & $\times$ & $\times$ \\
+    Standard \gls{mc} & $\star$ & $\star$($\checkmark$) & $\checkmark$ & $\checkmark$ & $\times$ \\
+    \hline
+    \gls{mlmc} & $\times$ & $\times$($\times$) & $\checkmark$ & $\times$ & $\times$ \\
     \hline
@@
 However, they analyze convergence in probabilistic order, and it is only applicable in terms of \gls{ae}.
-In Section~\ref{appendix:connection-mse-absolute-error}, we illustrate the connection between the convergence in \gls{mse} and the convergence in \gls{ae}.
+In appendix, we sketch out the connection between the convergence in \gls{mse} and the convergence in \gls{ae}.
 
@@
     Let $h$ be a smooth function. 
-    MSE of the standard nested simulation procedure converges in order $\Gamma^{2/3}$, that is,
+    \gls{mse} of the standard nested simulation procedure converges in order $\Gamma^{2/3}$, that is,
     $$\mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(\Gamma^{-2/3}).$$
@@
     Let $h$ be a Lipschitz continuous function. 
-    MSE of the standard nested simulation procedure converges in order $\Gamma^{2/3}$, that is,
+    \gls{mse} of the standard nested simulation procedure converges in order $\Gamma^{2/3}$, that is,
     $$\mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] = \mathcal{O}(\Gamma^{-1/2}).$$
@@
     \end{tabular}
-    \caption{Asymptotic rate of convergence of nested simulation procedures in \gls{mse}}
+    \caption{Asymptotic rate of convergence of nested simulation procedures in MSE}
 \label{tab1:asymConv-order}
@@
 
-Assumption~\ref{as1:mlmc-q} ensures that the conditional expectation of $Y$ given $X$ is not concentrated around zero, as ~\cite{giles2019multilevel} show the asymptotic convergence of the MLMC procedure only when $\rho$ is in the nested expectation form with $h$ being an indicator function, i.e., $h(x) = \mathbb{I}_{\{x \geq 0\}}$.
+Assumption~\ref{as1:mlmc-q} ensures that the conditional expectation of $Y$ given $X$ is not concentrated around zero, as ~\cite{giles2019multilevel} show the asymptotic convergence of the \gls{mlmc} procedure only when $\rho$ is in the nested expectation form with $h$ being an indicator function, i.e., $h(x) = \mathbb{I}_{\{x \geq 0\}}$.
 
@@
 The empirical convergence results of each estimator are measured and recorded to illustrate their empirical behavior under different risk measures, option types, and asset dimensions.
-All numerical experiments are conducted on a linux server with four Intel Xeon Gold 6230 20-core 2.1 GHz CPU with 768 GB RAM.
+All numerical experiments are conducted on a Linux server with four Intel Xeon Gold 6230 20-core 2.1 GHz CPU with 768 GB RAM.
 
@@
 In Figure~\ref{fig1:sens_basis}, the empirical convergence results of the regression-based nested simulation procedure for a quadratic tracking error and a 90\%-\gls{cvar} are illustrated for the two different regression bases.
-The empirical rates of convergence of the regression-based nested simulation procedure are observed to be insensitive to the chosen regression basis.
+The empirical rates of convergence of the regression-based nested simulation procedure are observed to be insensitive to the chosen type of regression basis.
 
@@
     \toprule
-    \textbf{Level} & \textbf{Bias} & \textbf{Variance} & \textbf{MSE} & $\Gamma$ & \textbf{MSE of SNS} \\ 
+    \textbf{Level} & \textbf{Bias} & \textbf{Variance} & \textbf{\gls{mse}} & $\Gamma$ & \textbf{\gls{mse} of SNS} \\ 
     \hline\hline

### 2025-05-08 project2/nnMetamodels.tex
final draft

@@
 
-\gls{dnn} have attracted attentions of researchers and practitioners due to their success~\citep{hastie2009elements,lecun2015deep} in solving real-world machine learning tasks such as AlphaGo~\citep{silver2016mastering} and ChatGPT~\citep{chatgpt}.
+\gls{dnn} have attracted attentions of researchers and practitioners due to their success~\citep{hastie2009elements,lecun2015deep} in solving real-world \gls{ml} tasks such as AlphaGo~\citep{silver2016mastering} and ChatGPT~\citep{chatgpt}.
 Since the first artificial neural network model~\citep{mcculloch1943logical} and the first algorithm for training a perceptron~\citep{rosenblatt1958perceptron}, especially after the introduction of backpropagation~\citep{rumelhart1985learning} and the growth of high-performance computing, the field of artificial neural network and deep learning in general has been growing rapidly.
@@
 They are then used to replace the time-consuming inner simulations by the trained model.
-Borrowing terminologies from the machine learning community, we can view a set of simulated outer scenarios and estimated hedging errors for those scenarios as \textit{features} and noisy \textit{labels}.
+Borrowing terminologies from the \gls{ml} community, we can view a set of simulated outer scenarios and estimated hedging errors for those scenarios as \textit{features} and noisy \textit{labels}.
 The noise level of the labels can be controlled by the number of inner replications in the inner simulation model.
@@
 \begin{enumerate}
-    \item  our metamodel has high-dimensional inputs. In machine learning terminology, the features are high-dimensional vectors.
+    \item  our metamodel has high-dimensional inputs. In \gls{ml} terminology, the features are high-dimensional vectors.
     To estimate the hedging error of a typical \gls{va} contract, the number of features is in the order of hundreds, which is at least one order of magnitude larger than the number of features in the aforementioned studies,
@@
 \begin{algorithm} 
-\caption{Standard Nested Simulation Procedure for Estimating CVaR for \gls{gmwb} Hedging Losses}
+\caption{Standard Nested Simulation Procedure for Estimating CVaR for GMWB Hedging Losses}
 \begin{algorithmic}[1] \label{alg2:standardProcedure}
@@
     \end{tabular}
-    \caption{Real-world parameters for the \gls{rsgbm} model (monthly rates)}
+    \caption{Real-world parameters for the RS-GBM model (monthly rates)}
     \label{tab:regime_params}
@@
 We observe that the three \gls{dnn} metamodels have orders of magnitudes more trainable parameters than the two traditional regression metamodels.
-Following the convention in machine learning literature, the three \gls{dnn} metamodels are said to have much higher \textit{model capacities}.
+Following the convention in \gls{ml} literature, the three \gls{dnn} metamodels are said to have much higher \textit{model capacities}.
 Treating regression metamodels as shallow neural networks, \gls{mlr} and \gls{qpr} are two neural networks with no hidden layer. 
@@
     \end{tabular}
-    \caption{Architectures and \gls{mse}s of metamodels for \gls{gmwb} inner simulation model.}
+    \caption{Architectures and MSEs of metamodels for GMWB inner simulation model.}
     \label{tab:gmwb_arch}
@@
 The resulting feature-label pairs $\{(\bS^{(i)}, \Lhat_i): i=1,\ldots,M\}$ is used for training different  metamodels.
-Specifically, following the convention in machine learning literature, we split this dataset into three parts: The training, validation, and test sets have $\num{90000}$, $\num{5000}$, and $\num{5000}$ samples (representing $90\%$, $5\%$, and $5\%$ of the dataset), respectively.
+Specifically, following the convention in \gls{ml} literature, we split this dataset into three parts: The training, validation, and test sets have $\num{90000}$, $\num{5000}$, and $\num{5000}$ samples (representing $90\%$, $5\%$, and $5\%$ of the dataset), respectively.
 At the end of stage 1, $m$ predicted tail scenarios are identified by the trained metamodels.

### 2025-05-08 project3/draft.tex
final draft

@@
 \begin{algorithm}
-    \caption{Multi-task Learning Framework for \gls{lstm} Metamodels}
+    \caption{Multi-task Learning Framework for LSTM Metamodels}
     \begin{algorithmic}[1] \label{alg3:multiTaskLearning}
@@
 \begin{algorithm}
-    \caption{Transfer Learning Framework for \gls{lstm} Metamodels: Combining Fine-tuning, Layer Freezing, and Multi-task Learning}
+    \caption{TL Framework for LSTM Metamodels: Combining Fine-tuning, Layer Freezing, and Multi-task Learning}
     \begin{algorithmic}[1] \label{alg3:combined}
@@
     \toprule
-    \textbf{Contract} & \textbf{Asset Model} & \textbf{Lapse} & \textbf{$M_{\text{So}}$}  & \textbf{$M_{\text{Ta}}$}\\
+    \textbf{Contract} & \textbf{Asset model} & \textbf{Lapse} & \textbf{$M_{\text{So}}$}  & \textbf{$M_{\text{Ta}}$}\\
     \midrule
@@
     \end{tabular}
-    \caption{\gls{va} Contracts for Transfer Learning Experiments}
+    \caption{VA contracts for TL experiments}
     \label{tab3:contracts}
@@
 
-All \gls{lstm} metamodels are evaluated based on their training history graphs for the target task, which plot training and validation MSE against the number of training epochs.
+All \gls{lstm} metamodels are evaluated based on their training history graphs for the target task, which plot training and validation \gls{mse} against the number of training epochs.
 The training history graphs visualize the learning curves of the \gls{lstm} metamodels, which provide insights into stability and convergence behavior the metamodels.
-We measure the generalization performance of the \gls{lstm} metamodels using the true MSE, which quantifies the accuracy of the \gls{lstm} metamodels in approximating the true inner simulation model of \gls{va} contracts.
-The true MSE is computed by comparing the metamodel predictions with the true contract losses, which are approximated by the standard nested simulation procedure with $\num{100000}$ inner replications.
+We measure the generalization performance of the \gls{lstm} metamodels using the true \gls{mse}, which quantifies the accuracy of the \gls{lstm} metamodels in approximating the true inner simulation model of \gls{va} contracts.
+The true \gls{mse} is computed by comparing the metamodel predictions with the true contract losses, which are approximated by the standard nested simulation procedure with $\num{100000}$ inner replications.
 Hyperparameters and network architectures for the \gls{lstm} metamodels are kept the same as the \gls{lstm} metamodel in Section~\ref{sec2:numerical}. 
@@
         \includegraphics[width=\textwidth]{./project3/figures/figure1a.png}
-        \caption{Extensive Training on Target Task} 
+        \caption{Extensive training on target task} 
         \label{subfig3-1:extensive}
@@
         \includegraphics[width=\textwidth]{./project3/figures/figure1b.png}
-        \caption{Without \gls{tl}}
+        \caption{Without TL}
         \label{subfig3-1:without}
@@
         \includegraphics[width=\textwidth]{./project3/figures/figure1c.png}
-        \caption{With Fine-tuning}
+        \caption{With fine-tuning}
         \label{subfig3-1:fineTuning}
@@
         \includegraphics[width=\textwidth]{./project3/figures/figure1d.png}
-        \caption{With Layer Freezing}
+        \caption{With layer freezing}
         \label{subfig3-1:layerFreezing}
     \end{subfigure}
-    \caption{Metamodel performance on \gls{rsgbm} \gls{gmmb} with static lapse}
+    \caption{Metamodel performance on GMMB with RS-GBM and static lapse}
     \label{fig3:figure1}
@@
         \includegraphics[width=\textwidth]{./project3/figures/figure2a.png}
-        \caption{Fine-tuning from No Lapse} 
+        \caption{Fine-tuning from no lapse} 
         \label{subfig3-2:fromNolapse}
@@
         \includegraphics[width=\textwidth]{./project3/figures/figure2b.png}
-        \caption{Fine-tuning from Static Lapse}
+        \caption{Fine-tuning from static lapse}
         \label{subfig3-2:fromLapse}
     \end{subfigure}
-    \caption{Fine-tuned Metamodel performance on \gls{rsgbm} \gls{gmmb} with a dynamic lapse}
+    \caption{Fine-tuned metamodel performance on GMMB with RS-GBM and dynamic lapse}
     \label{fig3:figure2}
@@
         \includegraphics[width=\textwidth]{./project3/figures/figure3b.png}
-        \caption{Freezing the Fully Connected Layer}
+        \caption{Freezing the fully connected layer}
         \label{subfig3-3:freezeFC}
     \end{subfigure}
-    \caption{Layer Freezing on \gls{rsgbm} \gls{gmmb} with dynamic lapse}
+    \caption{Layer freezing on GMMB with RS-GBM and dynamic lapse}
     \label{fig3:figure3}
@@
     \toprule
-    \textbf{Lapse Type} & \textbf{Extensive} & \textbf{Fine-tuning} & \textbf{Layer Freezing} & \textbf{Without \gls{tl}} \\
+    \textbf{Lapse type} & \textbf{Extensive} & \textbf{Fine-tuning} & \textbf{Layer freezing} & \textbf{Without \gls{tl}} \\
     \midrule
@@
     \end{tabular}
-    \caption{Comparison of different \gls{tl} methods on \gls{gmmb} contracts}
+    \caption{Comparison of different TL methods on GMMB contracts}
     \label{tab3:transfer_learning_results}
@@
 The results demonstrate the effectiveness of fine-tuning and layer freezing in transferring knowledge from a related source tasks to the target task. 
-When transferring from a source task with the static lapse to a target task with the dynamic lapse, the MSEs achieved are $0.0794$ for fine-tuning and $0.0763$ for layer freezing.
-The benchmark MSE of $0.0587$, obtained from extensive training on the \gls{gmmb} dynamic lapse task with much more samples.
+When transferring from a source task with the static lapse to a target task with the dynamic lapse, the \gls{mse}s achieved are $0.0794$ for fine-tuning and $0.0763$ for layer freezing.
+The benchmark \gls{mse} of $0.0587$, obtained from extensive training on the \gls{gmmb} dynamic lapse task with much more samples.
 
@@
 However, when the source task is less similar to the target task, the benefits of \gls{tl} are less pronounced.
-The MSEs in this case are higher, with fine-tuning resulting in $0.4894$ and layer freezing achieving $0.3361$.
+The \gls{mse}s in this case are higher, with fine-tuning resulting in $0.4894$ and layer freezing achieving $0.3361$.
 This suggests that the divergence between the source and target tasks can lead to negative transfer.
@@
 
-\subsection{Transfer Knowledge to other Contract Types}
+\subsection{Transfer Knowledge to Other Contract Types}
 
@@
         \includegraphics[width=\textwidth]{./project3/figures/figure4a.png}
-        \caption{Extensive Training on Target Task} 
+        \caption{Extensive training on target task} 
         \label{subfig3-4:extensive}
@@
         \includegraphics[width=\textwidth]{./project3/figures/figure4b.png}
-        \caption{Without \gls{tl}}
+        \caption{Without TL}
         \label{subfig3-4:without}
@@
         \includegraphics[width=\textwidth]{./project3/figures/figure4c.png}
-        \caption{With Fine-tuning}
+        \caption{With fine-tuning}
         \label{subfig3-4:fineTuning}
@@
         \includegraphics[width=\textwidth]{./project3/figures/figure4d.png}
-        \caption{With Layer Freezing}
+        \caption{With layer freezing}
         \label{subfig3-4:layerFreezing}
     \end{subfigure}
-    \caption{TL performance on RS-GBM GMWB with dynamic lapse}
+    \caption{TL performance on GMWB with RS-GBM and dynamic lapse}
     \label{fig3:figure4}
@@
 Fewer training samples and no prior knowledge leads to unstable training dynamics. 
-The validation MSE fluctuates substantially.
+The validation \gls{mse} fluctuates substantially.
 
@@
         \toprule
-        \textbf{Model} & \textbf{Training samples} & \textbf{Training MSE} & \textbf{True MSE} \\
+        \textbf{Model} & \textbf{Training samples} & \textbf{Training \gls{mse}} & \textbf{True \gls{mse}} \\
         \midrule
@@
 
-Table~\ref{tab3:transfer_learning_results_gmwb} summarizes the true MSEs of the \gls{lstm} metamodels on the \gls{gmwb} contracts.
-Training MSE and true MSE are computed using the training labels and the true contract losses approximated with $\num{100000}$ inner replications, respectively.
+Table~\ref{tab3:transfer_learning_results_gmwb} summarizes the true \gls{mse}s of the \gls{lstm} metamodels on the \gls{gmwb} contracts.
+Training \gls{mse} and true \gls{mse} are computed using the training labels and the true contract losses approximated with $\num{100000}$ inner replications, respectively.
 This is consistent with the terminology used in Chapter~\ref{chap:project2}.
@@
         \includegraphics[width=\textwidth]{./project3/figures/figure4_1.png}
-        \caption{Identifying Tail scenarios} 
+        \caption{Identifying tail scenarios} 
         \label{subfig3-4-1:tail}
@@
     \end{subfigure}
-    \caption{TL performance on \gls{rsgbm} GMWB with dynamic lapse}
+    \caption{TL performance on GMWB with RS-GBM and dynamic lapse}
     \label{fig3:figure4-1}
@@
 
-This finding is consistent with the training history and MSEs in Figure~\ref{fig3:figure4} and Table~\ref{tab3:transfer_learning_results_gmwb}, respectively.
+This finding is consistent with the training history and \gls{mse}s in Figure~\ref{fig3:figure4} and Table~\ref{tab3:transfer_learning_results_gmwb}, respectively.
 It is important to note that while these results are promising, they also highlight the complexity of modeling the \gls{gmwb} contracts with the dynamic lapse. 
@@
 The simulation datasets contain $2,\!000$ samples for each contract type, and the \gls{lstm} metamodels are trained using multi-task learning. 
-In our experiments, Algorithm~\ref{alg3:multiTaskLearning} is used to train the \gls{lstm} metamodels simultaneously to minimize the multi-task MSE loss function in Equation~\eqref{eq3:multiTaskLoss}.
+In our experiments, Algorithm~\ref{alg3:multiTaskLearning} is used to train the \gls{lstm} metamodels simultaneously to minimize the multi-task \gls{mse} loss function in Equation~\eqref{eq3:multiTaskLoss}.
 We use individual task training as a baseline for comparison, where the \gls{lstm} metamodels are trained separately on the \gls{gmmb} and \gls{gmwb} contracts.
@@
     \end{subfigure}
-    \caption{Multi-task Learning on \gls{rsgbm} GMMB and GMWB with dynamic lapse}
+    \caption{Multi-task learning on GMMB and GMWB with RS-GBM and dynamic lapse}
     \label{fig3:figure5}

### 2025-05-08 pre/bs_ec_krr_time.py

@@ -1,0 +1,181 @@
+import numpy as np
+import pandas as pd
+import methods
+from sklearn.kernel_ridge import KernelRidge
+from sklearn.gaussian_process.kernels import Matern
+from joblib import Parallel, delayed
+from sklearn.model_selection import KFold
+from skopt import BayesSearchCV
+from skopt.space import Real
+import time
+
+
+def krr_Euro_Call(n_front, n_back, d, S_0, K, mu, sigma, r, tau, T, alpha_opt, l_opt, nu_opt):
+
+    cor_mat = np.ones((d, d)) * 0.3 + np.identity(d) * 0.7
+    cov_mat = cor_mat * sigma ** 2
+
+    start = time.time()
+    sample_outer_train = methods.GBM_front(n_front=n_front, d=d, S_0=S_0,
+                                           drift_vec=mu, diffusion_mat=cov_mat, tau=tau)
+    sample_inner = methods.GBM_back(n_front=n_front, n_back=n_back, d=d, S_tau=sample_outer_train,
+                                    drift=r, diffusion=cov_mat, T=T - tau)
+
+    payoff = np.zeros([d, n_front])
+    for j in range(len(K)):
+        price = np.mean(np.maximum(sample_inner - K[j], 0), axis=2) * np.exp(-r * (T - tau))
+        payoff = payoff + price
+
+    portfolio_value_0 = 0
+    for j in range(len(K)):
+        portfolio_value_0 = portfolio_value_0 + methods.price_CP(S_0, T, sigma, r, K[j], 0, "C", "long")
+
+    X_train = methods.generate_basis(sample_outer_train, option_type="Vanilla", basis_function="None")
+    y_train = np.sum(payoff, axis=0)
+
+    kernel = 1.0 * Matern(length_scale=l_opt, nu=nu_opt)
+    krr = KernelRidge(alpha=alpha_opt, kernel=kernel).fit(X_train, y_train)
+
+    sample_outer_test = methods.GBM_front(n_front=n_front, d=d, S_0=S_0,
+                                          drift_vec=mu, diffusion_mat=cov_mat, tau=tau)
+
+    X_test = methods.generate_basis(sample_outer_test, option_type="Vanilla", basis_function="None")
+
+    y_test = krr.predict(X_test)
+
+    loss_krr = d * portfolio_value_0 - y_test
+
[…]

### 2025-05-08 pre/bs_ec_lr_time.py

@@ -1,0 +1,113 @@
+import numpy as np
+import pandas as pd
+import methods
+from joblib import Parallel, delayed
+import time
+
+
+def lr_Euro_Call(n_front, n, d, S_0, K, mu, sigma, r, tau, T, h):
+
+    cor_mat = np.ones((d, d)) * 0.3 + np.identity(d) * 0.7
+    cov_mat = cor_mat * sigma**2
+
+    start = time.time()
+    sample_outer_train = methods.GBM_front(n_front=n_front, d=d,
+                                   S_0=S_0, drift_vec=mu, diffusion_mat=cov_mat, tau=tau)
+    sample_inner_tau = methods.GBM_back(n_front=n_front, n_back=1, d=d,
+                                S_tau=sample_outer_train, drift=r, diffusion=cov_mat, T=h)[:, :, 0]
+    sample_inner_T = methods.GBM_back(n_front=n_front, n_back=1, d=d,
+                              S_tau=sample_inner_tau, drift=r, diffusion=cov_mat, T=T-tau-h)
+    
+    sample_outer_test = methods.GBM_front(n_front=n_front, d=d,
+                                          S_0=S_0, drift_vec=mu, diffusion_mat=cov_mat, tau=tau)
+
+    portfolio_value_0 = 0
+    for j in range(len(K)):
+        portfolio_value_0 = portfolio_value_0 + methods.price_CP(S_0, T, sigma, r, K[j], 0, "C", "long")
+
+    payoff = np.zeros([d, n_front])
+    for j in range(len(K)):
+        price = np.mean(np.maximum(sample_inner_T - K[j], 0), axis=2) * np.exp(-r * (T - tau))
+        payoff = payoff + price
+
+    diff = portfolio_value_0 - payoff
+    Loss_LR = np.zeros(n_front)
+
+    Weight_D = methods.compute_Weight_D(S_0, mu, r, sigma, h, tau, sample_inner_tau)
+
+    n_partition = int(n_front // n)
+
+    for i in range(n_partition):
+
+        LR_Loss_Matrix = np.zeros([n_front, n])
+
+        for j in range(d):
+
+            Weight_U = methods.compute_Weight_U(sample_inner_tau[j, :], sample_outer_test[j, i * n:(i + 1) * n],
+                                                r, sigma, h)
+
[…]

### 2025-05-08 pre/bs_ec_simTrue.py

@@ -1,0 +1,74 @@
+import numpy as np
+import methods
+import pandas as pd
+from joblib import Parallel, delayed
+
+
+def ComputeTrueLoss(n_front, d, S_0, K, mu, sigma, r, tau, T, alpha=0.1):
+
+    rho = 0.3
+    cor_mat = methods.generate_cor_mat(d, rho)
+    cov_mat_call = cor_mat * sigma ** 2
+
+    print("European Call: Simulating Front Paths...")
+    sample_outer_call = methods.GBM_front(n_front=n_front, d=d, S_0=S_0,
+                                          drift_vec=mu, diffusion_mat=cov_mat_call, tau=tau)
+
+    print("Calculating Value...")
+    call_tau = np.zeros(n_front)
+    for j in range(len(K)):
+        call_tau_vec = Parallel(n_jobs=d, verbose=10)(
+            delayed(methods.price_CP)(sample_outer_call[k, :], T - tau, sigma, r, K[j], 0, "C", "long")
+            for k in range(d))
+        call_tau = call_tau + np.sum(call_tau_vec, axis=0)
+    print("End of European Call.")
+
+    portfolio_value_0 = 0
+
+    for j in range(len(K)):
+        portfolio_value_0 = portfolio_value_0 + methods.price_CP(S_0, T, sigma, r, K[j], 0, "C", "long")
+
+    loss_true = d * portfolio_value_0 - call_tau
+
+    loss_true.sort()
+
+    L0 = loss_true[int(np.ceil((1 - alpha) * n_front))]
+
+    indicator_true = alpha
+    hockey_true = np.mean(np.maximum(loss_true - L0, 0))
+    quadratic_true = np.mean((loss_true - L0) ** 2)
+    CVaR = np.mean(loss_true[loss_true > L0])
+
+    return L0, indicator_true, hockey_true, quadratic_true, CVaR
+
+
+d_11 = 20
+sigma_11 = 0.1
+n_cmc = 10**7
+S_0_11 = 100
+K_11 = [90, 100, 110]
+mu_11 = 0.08
+r_11 = 0.05
+tau_11 = 3/50
+T_11 = 1
+
+L0_11, indicator_true_11, hockey_true_11, quadratic_true_11, CVaR_11 = ComputeTrueLoss(n_front=n_cmc,
+                                                                                       d=d_11,
+                                                                                       S_0=S_0_11,
+                                                                                       K=K_11,
+                                                                                       mu=mu_11,
+                                                                                       sigma=sigma_11,
[…]

### 2025-05-08 pre/bs_ec_snsbs_time.py

@@ -1,0 +1,192 @@
+import numpy as np
+import pandas as pd
+import methods
+from sklearn.linear_model import LinearRegression
+from joblib import Parallel, delayed
+import time
+
+
+def SNS_Euro_Call(n_front, n_back, d, S_0, K, mu, sigma, r, tau, T):
+
+    cor_mat = np.ones((d, d)) * 0.3 + np.identity(d) * 0.7
+    cov_mat = cor_mat * sigma**2
+
+    start = time.time()
+    sample_outer = methods.GBM_front(n_front = n_front, d = d, S_0 = S_0,
+                                     drift_vec = mu, diffusion_mat = cov_mat, tau = tau)
+    sample_inner = methods.GBM_back(n_front = n_front, n_back = n_back, d = d, S_tau = sample_outer,
+                                    drift = r, diffusion = cov_mat, T = T - tau)
+
+    payoff = np.zeros([d, n_front])
+    for j in range(len(K)):
+        price = np.mean(np.maximum(sample_inner - K[j], 0), axis=2) * np.exp(-r * (T - tau))
+        payoff = payoff + price
+
+    portfolio_value_0 = 0
+    for j in range(len(K)):
+        portfolio_value_0 = portfolio_value_0 + methods.price_CP(S_0, T, sigma, r, K[j], 0, "C", "long")
+
+    loss_SNS = d * portfolio_value_0 - np.sum(payoff, axis=0)
+
+    total_time = time.time() - start
+
+    return loss_SNS, total_time
+
+
+def SNS_Euro_Call_BootStrap(Gamma, n_front_vec, n_back_vec, d, S_0, K, mu, sigma, r, tau, T,
+                            L0, I=500, alpha=0.1):
+    cor_mat = np.ones((d, d)) * 0.3 + np.identity(d) * 0.7
+    cov_mat = cor_mat * sigma ** 2
+
+    portfolio_value_0 = 0
+    for j in range(len(K)):
+        portfolio_value_0 = portfolio_value_0 + methods.price_CP(S_0, T, sigma, r, K[j], 0, "C", "long")
+
+    n_front_0 = n_front_vec[-1]
+    n_back_0 = n_back_vec[-1]
+
+    sample_outer_0 = methods.GBM_front(n_front=n_front_0, d=d, S_0=S_0,
+                                       drift_vec=mu, diffusion_mat=cov_mat, tau=tau)
+
[…]

### 2025-05-08 pre/methods.py

@@ -1,0 +1,444 @@
+import numpy as np
+from scipy.stats.distributions import norm
+
+
+def generate_cor_mat(d, rho):
+    return np.ones((d, d)) * rho + np.identity(d) * (1 - rho)
+
+
+def Heston_front(n_front, S_0, V_0, mu, rho, kappa, theta, sigma, tau, step_size=1/253):
+
+    n_step = int(tau // step_size) + 1
+    mu_Z = np.array([0, 0])
+    cov_Z = np.array([[1, rho], [rho, 1]])
+    
+    S_front = np.zeros([n_front, n_step + 1])
+    S_front[:, 0] = np.array(S_0)
+    V = np.zeros([n_front, n_step + 1])
+    V[:, 0] = np.array(V_0)
+
+    Z = np.random.multivariate_normal(mu_Z, cov_Z, [n_front, n_step])
+
+    for k in range(1, n_step + 1):
+        S_front[:, k] = S_front[:, k - 1] * np.exp((mu - (1/2) * V[:, k-1]) * step_size 
+                                                   + np.sqrt(V[:, k-1] * step_size) 
+                                                   * Z[:, k-1, 0])
+        V[:, k] = np.maximum(V[:, k - 1] 
+                             + kappa * (theta - V[:, k - 1]) * step_size 
+                             + sigma * np.sqrt(V[:, k - 1] * step_size) * Z[:, k-1, 1], 0)
+
+    return S_front, V
+
+
+def Heston_back(n_front, n_back, S_tau, V_tau, r, rho, kappa, theta, sigma, T, step_size=1/253):
+
+    n_step = int(T // step_size) + 1
+    mu_Z = np.array([0, 0])
+    cov_Z = np.array([[1, rho], [rho, 1]])
+
+    S_back = np.zeros([n_front, n_back, n_step + 1])
+    V = np.zeros([n_front, n_back, n_step + 1])
+    for j in range(n_back):
+        S_back[:, j, 0] = S_tau[:, -1]
+        V[:, j, 0] = V_tau[:, -1]
+    
+    Z = np.random.multivariate_normal(mu_Z, cov_Z, [n_front, n_back, n_step])
+
+    for k in range(1, n_step + 1):
+
+        S_back[:, :, k] = S_back[:, :, k - 1] * np.exp((r - (1/2) * V[:, :, k-1]) * step_size 
+                                                        + np.sqrt(V[:, :, k-1] * step_size) 
[…]

### 2025-05-08 pre_private/bs_ec_knn_time.py

@@ -1,168 +1,0 @@
-import numpy as np
-import pandas as pd
-import methods
-from sklearn.neighbors import KNeighborsRegressor
-from sklearn.model_selection import KFold
-from joblib import Parallel, delayed
-import time
-
-def knn_Euro_Call(n_front, n_back, d, S_0, K, mu, sigma, r, tau, T, k_opt=-1):
-
-    cor_mat = np.ones((d, d)) * 0.3 + np.identity(d) * 0.7
-    cov_mat = cor_mat * sigma**2
-
-    start = time.time()
-    sample_outer_train = methods.GBM_front(n_front = n_front, d = d, S_0 = S_0,
-                                           drift_vec = mu, diffusion_mat = cov_mat, tau = tau)
-    sample_inner = methods.GBM_back(n_front = n_front, n_back = n_back, d = d, S_tau = sample_outer_train,
-                                    drift = r, diffusion = cov_mat, T = T - tau)
-
-    payoff = np.zeros([d, n_front])
-    for j in range(len(K)):
-        price = np.mean(np.maximum(sample_inner - K[j], 0), axis=2) * np.exp(-r * (T - tau))
-        payoff = payoff + price
-
-    portfolio_value_0 = 0
-    for j in range(len(K)):
-        portfolio_value_0 = portfolio_value_0 + methods.price_CP(S_0, T, sigma, r, K[j], 0, "C", "long")
-
-    X_train = methods.generate_basis(sample_outer_train, option_type = "Vanilla", basis_function = "None")
-    y_train = np.sum(payoff, axis=0)
-
-    if k_opt <= 0:
-        cv_kf = KFold(n_splits=3)
-        k_range = np.arange(100, 301, 50)
-        n_k = k_range.shape[0]
-        cv_score = np.zeros(n_k)
-
-        for k in range(n_k):
-
-            for train_ind, val_ind in cv_kf.split(X_train, y_train):
-
-                X = X_train[train_ind]
-                X_val = X_train[val_ind]
-                y = y_train[train_ind]
-                y_val = y_train[val_ind]
-
-                y_hat = KNeighborsRegressor(n_neighbors = k_range[k]).fit(X, y).predict(X_val)
-                cv_score[k] = cv_score[k] + np.sum((y_hat - y_val) ** 2)
-
-        k_opt = k_range[np.argmin(cv_score)]
-
[…]

### 2025-05-08 pre_private/bs_ec_krr_time.py

@@ -1,181 +1,0 @@
-import numpy as np
-import pandas as pd
-import methods
-from sklearn.kernel_ridge import KernelRidge
-from sklearn.gaussian_process.kernels import Matern
-from joblib import Parallel, delayed
-from sklearn.model_selection import KFold
-from skopt import BayesSearchCV
-from skopt.space import Real
-import time
-
-
-def krr_Euro_Call(n_front, n_back, d, S_0, K, mu, sigma, r, tau, T, alpha_opt, l_opt, nu_opt):
-
-    cor_mat = np.ones((d, d)) * 0.3 + np.identity(d) * 0.7
-    cov_mat = cor_mat * sigma ** 2
-
-    start = time.time()
-    sample_outer_train = methods.GBM_front(n_front=n_front, d=d, S_0=S_0,
-                                           drift_vec=mu, diffusion_mat=cov_mat, tau=tau)
-    sample_inner = methods.GBM_back(n_front=n_front, n_back=n_back, d=d, S_tau=sample_outer_train,
-                                    drift=r, diffusion=cov_mat, T=T - tau)
-
-    payoff = np.zeros([d, n_front])
-    for j in range(len(K)):
-        price = np.mean(np.maximum(sample_inner - K[j], 0), axis=2) * np.exp(-r * (T - tau))
-        payoff = payoff + price
-
-    portfolio_value_0 = 0
-    for j in range(len(K)):
-        portfolio_value_0 = portfolio_value_0 + methods.price_CP(S_0, T, sigma, r, K[j], 0, "C", "long")
-
-    X_train = methods.generate_basis(sample_outer_train, option_type="Vanilla", basis_function="None")
-    y_train = np.sum(payoff, axis=0)
-
-    kernel = 1.0 * Matern(length_scale=l_opt, nu=nu_opt)
-    krr = KernelRidge(alpha=alpha_opt, kernel=kernel).fit(X_train, y_train)
-
-    sample_outer_test = methods.GBM_front(n_front=n_front, d=d, S_0=S_0,
-                                          drift_vec=mu, diffusion_mat=cov_mat, tau=tau)
-
-    X_test = methods.generate_basis(sample_outer_test, option_type="Vanilla", basis_function="None")
-
-    y_test = krr.predict(X_test)
-
-    loss_krr = d * portfolio_value_0 - y_test
-
[…]

### 2025-05-08 pre_private/bs_ec_lr_time.py

@@ -1,113 +1,0 @@
-import numpy as np
-import pandas as pd
-import methods
-from joblib import Parallel, delayed
-import time
-
-
-def lr_Euro_Call(n_front, n, d, S_0, K, mu, sigma, r, tau, T, h):
-
-    cor_mat = np.ones((d, d)) * 0.3 + np.identity(d) * 0.7
-    cov_mat = cor_mat * sigma**2
-
-    start = time.time()
-    sample_outer_train = methods.GBM_front(n_front=n_front, d=d,
-                                   S_0=S_0, drift_vec=mu, diffusion_mat=cov_mat, tau=tau)
-    sample_inner_tau = methods.GBM_back(n_front=n_front, n_back=1, d=d,
-                                S_tau=sample_outer_train, drift=r, diffusion=cov_mat, T=h)[:, :, 0]
-    sample_inner_T = methods.GBM_back(n_front=n_front, n_back=1, d=d,
-                              S_tau=sample_inner_tau, drift=r, diffusion=cov_mat, T=T-tau-h)
-    
-    sample_outer_test = methods.GBM_front(n_front=n_front, d=d,
-                                          S_0=S_0, drift_vec=mu, diffusion_mat=cov_mat, tau=tau)
-
-    portfolio_value_0 = 0
-    for j in range(len(K)):
-        portfolio_value_0 = portfolio_value_0 + methods.price_CP(S_0, T, sigma, r, K[j], 0, "C", "long")
-
-    payoff = np.zeros([d, n_front])
-    for j in range(len(K)):
-        price = np.mean(np.maximum(sample_inner_T - K[j], 0), axis=2) * np.exp(-r * (T - tau))
-        payoff = payoff + price
-
-    diff = portfolio_value_0 - payoff
-    Loss_LR = np.zeros(n_front)
-
-    Weight_D = methods.compute_Weight_D(S_0, mu, r, sigma, h, tau, sample_inner_tau)
-
-    n_partition = int(n_front // n)
-
-    for i in range(n_partition):
-
-        LR_Loss_Matrix = np.zeros([n_front, n])
-
-        for j in range(d):
-
-            Weight_U = methods.compute_Weight_U(sample_inner_tau[j, :], sample_outer_test[j, i * n:(i + 1) * n],
-                                                r, sigma, h)
-
[…]

### 2025-05-08 pre_private/bs_ec_reg_time.py

@@ -1,105 +1,0 @@
-import numpy as np
-import pandas as pd
-import methods
-from sklearn.linear_model import LinearRegression
-from joblib import Parallel, delayed
-import time
-
-
-def reg_Euro_Call(n_front, n_back, d, S_0, K, mu, sigma, r, tau, T):
-
-    cor_mat = np.ones((d, d)) * 0.3 + np.identity(d) * 0.7
-    cov_mat = cor_mat * sigma**2
-
-    start = time.time()
-    sample_outer_train = methods.GBM_front(n_front = n_front, d = d, S_0 = S_0,
-                                           drift_vec = mu, diffusion_mat = cov_mat, tau = tau)
-    sample_inner = methods.GBM_back(n_front = n_front, n_back = n_back, d = d, S_tau = sample_outer_train,
-                                    drift = r, diffusion = cov_mat, T = T - tau)
-
-    payoff = np.zeros([d, n_front])
-    for j in range(len(K)):
-        price = np.mean(np.maximum(sample_inner - K[j], 0), axis=2) * np.exp(-r * (T - tau))
-        payoff = payoff + price
-
-    portfolio_value_0 = 0
-    for j in range(len(K)):
-        portfolio_value_0 = portfolio_value_0 + methods.price_CP(S_0, T, sigma, r, K[j], 0, "C", "long")
-
-    X_train = methods.generate_basis(sample_outer_train)
-    y_train = np.sum(payoff, axis=0)
-
-    reg = LinearRegression().fit(X_train, y_train)
-
-    sample_outer_test = methods.GBM_front(n_front=n_front, d=d, S_0=S_0,
-                                          drift_vec=mu, diffusion_mat=cov_mat, tau=tau)
-
-    X_test = methods.generate_basis(sample_outer_test)
-    y_test = reg.predict(X_test)
-
-    loss_reg = d * portfolio_value_0 - y_test
-
-    total_time = time.time() - start
-
-    return loss_reg, total_time
-
-
-def cal_RRMSE(n_front, n_back, d, S_0, K, mu, sigma, r, tau, T, alpha, L0):
-
-    loss, total_time = reg_Euro_Call(n_front, n_back, d, S_0, K, mu, sigma, r, tau, T)
-
-    # indicator = np.mean((loss > L0))
-    # hockey = np.mean(np.maximum(loss - L0, 0))
-    # quadratic = np.mean((loss - L0) ** 2)
-
[…]

### 2025-05-08 pre_private/bs_ec_simTrue.py

@@ -1,74 +1,0 @@
-import numpy as np
-import methods
-import pandas as pd
-from joblib import Parallel, delayed
-
-
-def ComputeTrueLoss(n_front, d, S_0, K, mu, sigma, r, tau, T, alpha=0.1):
-
-    rho = 0.3
-    cor_mat = methods.generate_cor_mat(d, rho)
-    cov_mat_call = cor_mat * sigma ** 2
-
-    print("European Call: Simulating Front Paths...")
-    sample_outer_call = methods.GBM_front(n_front=n_front, d=d, S_0=S_0,
-                                          drift_vec=mu, diffusion_mat=cov_mat_call, tau=tau)
-
-    print("Calculating Value...")
-    call_tau = np.zeros(n_front)
-    for j in range(len(K)):
-        call_tau_vec = Parallel(n_jobs=d, verbose=10)(
-            delayed(methods.price_CP)(sample_outer_call[k, :], T - tau, sigma, r, K[j], 0, "C", "long")
-            for k in range(d))
-        call_tau = call_tau + np.sum(call_tau_vec, axis=0)
-    print("End of European Call.")
-
-    portfolio_value_0 = 0
-
-    for j in range(len(K)):
-        portfolio_value_0 = portfolio_value_0 + methods.price_CP(S_0, T, sigma, r, K[j], 0, "C", "long")
-
-    loss_true = d * portfolio_value_0 - call_tau
-
-    loss_true.sort()
-
-    L0 = loss_true[int(np.ceil((1 - alpha) * n_front))]
-
-    indicator_true = alpha
-    hockey_true = np.mean(np.maximum(loss_true - L0, 0))
-    quadratic_true = np.mean((loss_true - L0) ** 2)
-    CVaR = np.mean(loss_true[loss_true > L0])
-
-    return L0, indicator_true, hockey_true, quadratic_true, CVaR
-
-
-d_11 = 20
-sigma_11 = 0.1
-n_cmc = 10**7
-S_0_11 = 100
-K_11 = [90, 100, 110]
-mu_11 = 0.08
-r_11 = 0.05
-tau_11 = 3/50
-T_11 = 1
-
-L0_11, indicator_true_11, hockey_true_11, quadratic_true_11, CVaR_11 = ComputeTrueLoss(n_front=n_cmc,
-                                                                                       d=d_11,
-                                                                                       S_0=S_0_11,
-                                                                                       K=K_11,
-                                                                                       mu=mu_11,
-                                                                                       sigma=sigma_11,
[…]

### 2025-05-08 pre_private/bs_ec_snsbs_time.py

@@ -1,192 +1,0 @@
-import numpy as np
-import pandas as pd
-import methods
-from sklearn.linear_model import LinearRegression
-from joblib import Parallel, delayed
-import time
-
-
-def SNS_Euro_Call(n_front, n_back, d, S_0, K, mu, sigma, r, tau, T):
-
-    cor_mat = np.ones((d, d)) * 0.3 + np.identity(d) * 0.7
-    cov_mat = cor_mat * sigma**2
-
-    start = time.time()
-    sample_outer = methods.GBM_front(n_front = n_front, d = d, S_0 = S_0,
-                                     drift_vec = mu, diffusion_mat = cov_mat, tau = tau)
-    sample_inner = methods.GBM_back(n_front = n_front, n_back = n_back, d = d, S_tau = sample_outer,
-                                    drift = r, diffusion = cov_mat, T = T - tau)
-
-    payoff = np.zeros([d, n_front])
-    for j in range(len(K)):
-        price = np.mean(np.maximum(sample_inner - K[j], 0), axis=2) * np.exp(-r * (T - tau))
-        payoff = payoff + price
-
-    portfolio_value_0 = 0
-    for j in range(len(K)):
-        portfolio_value_0 = portfolio_value_0 + methods.price_CP(S_0, T, sigma, r, K[j], 0, "C", "long")
-
-    loss_SNS = d * portfolio_value_0 - np.sum(payoff, axis=0)
-
-    total_time = time.time() - start
-
-    return loss_SNS, total_time
-
-
-def SNS_Euro_Call_BootStrap(Gamma, n_front_vec, n_back_vec, d, S_0, K, mu, sigma, r, tau, T,
-                            L0, I=500, alpha=0.1):
-    cor_mat = np.ones((d, d)) * 0.3 + np.identity(d) * 0.7
-    cov_mat = cor_mat * sigma ** 2
-
-    portfolio_value_0 = 0
-    for j in range(len(K)):
-        portfolio_value_0 = portfolio_value_0 + methods.price_CP(S_0, T, sigma, r, K[j], 0, "C", "long")
-
-    n_front_0 = n_front_vec[-1]
-    n_back_0 = n_back_vec[-1]
-
-    sample_outer_0 = methods.GBM_front(n_front=n_front_0, d=d, S_0=S_0,
-                                       drift_vec=mu, diffusion_mat=cov_mat, tau=tau)
-
[…]

### 2025-05-08 pre_private/methods.py

@@ -1,444 +1,0 @@
-import numpy as np
-from scipy.stats.distributions import norm
-
-
-def generate_cor_mat(d, rho):
-    return np.ones((d, d)) * rho + np.identity(d) * (1 - rho)
-
-
-def Heston_front(n_front, S_0, V_0, mu, rho, kappa, theta, sigma, tau, step_size=1/253):
-
-    n_step = int(tau // step_size) + 1
-    mu_Z = np.array([0, 0])
-    cov_Z = np.array([[1, rho], [rho, 1]])
-    
-    S_front = np.zeros([n_front, n_step + 1])
-    S_front[:, 0] = np.array(S_0)
-    V = np.zeros([n_front, n_step + 1])
-    V[:, 0] = np.array(V_0)
-
-    Z = np.random.multivariate_normal(mu_Z, cov_Z, [n_front, n_step])
-
-    for k in range(1, n_step + 1):
-        S_front[:, k] = S_front[:, k - 1] * np.exp((mu - (1/2) * V[:, k-1]) * step_size 
-                                                   + np.sqrt(V[:, k-1] * step_size) 
-                                                   * Z[:, k-1, 0])
-        V[:, k] = np.maximum(V[:, k - 1] 
-                             + kappa * (theta - V[:, k - 1]) * step_size 
-                             + sigma * np.sqrt(V[:, k - 1] * step_size) * Z[:, k-1, 1], 0)
-
-    return S_front, V
-
-
-def Heston_back(n_front, n_back, S_tau, V_tau, r, rho, kappa, theta, sigma, T, step_size=1/253):
-
-    n_step = int(T // step_size) + 1
-    mu_Z = np.array([0, 0])
-    cov_Z = np.array([[1, rho], [rho, 1]])
-
-    S_back = np.zeros([n_front, n_back, n_step + 1])
-    V = np.zeros([n_front, n_back, n_step + 1])
-    for j in range(n_back):
-        S_back[:, j, 0] = S_tau[:, -1]
-        V[:, j, 0] = V_tau[:, -1]
-    
-    Z = np.random.multivariate_normal(mu_Z, cov_Z, [n_front, n_back, n_step])
-
-    for k in range(1, n_step + 1):
-
-        S_back[:, :, k] = S_back[:, :, k - 1] * np.exp((r - (1/2) * V[:, :, k-1]) * step_size 
-                                                        + np.sqrt(V[:, :, k-1] * step_size) 
[…]

### 2025-05-08 pre_private/simTrue.py

@@ -1,74 +1,0 @@
-import numpy as np
-import methods
-import pandas as pd
-from joblib import Parallel, delayed
-
-
-def ComputeTrueLoss(n_front, d, S_0, K, mu, sigma, r, tau, T, alpha=0.1):
-
-    rho = 0.3
-    cor_mat = methods.generate_cor_mat(d, rho)
-    cov_mat_call = cor_mat * sigma ** 2
-
-    print("European Call: Simulating Front Paths...")
-    sample_outer_call = methods.GBM_front(n_front=n_front, d=d, S_0=S_0,
-                                          drift_vec=mu, diffusion_mat=cov_mat_call, tau=tau)
-
-    print("Calculating Value...")
-    call_tau = np.zeros(n_front)
-    for j in range(len(K)):
-        call_tau_vec = Parallel(n_jobs=d, verbose=10)(
-            delayed(methods.price_CP)(sample_outer_call[k, :], T - tau, sigma, r, K[j], 0, "C", "long")
-            for k in range(d))
-        call_tau = call_tau + np.sum(call_tau_vec, axis=0)
-    print("End of European Call.")
-
-    portfolio_value_0 = 0
-
-    for j in range(len(K)):
-        portfolio_value_0 = portfolio_value_0 + methods.price_CP(S_0, T, sigma, r, K[j], 0, "C", "long")
-
-    loss_true = d * portfolio_value_0 - call_tau
-
-    loss_true.sort()
-
-    L0 = loss_true[int(np.ceil((1 - alpha) * n_front))]
-
-    indicator_true = alpha
-    hockey_true = np.mean(np.maximum(loss_true - L0, 0))
-    quadratic_true = np.mean((loss_true - L0) ** 2)
-    CVaR = np.mean(loss_true[loss_true > L0])
-
-    return L0, indicator_true, hockey_true, quadratic_true, CVaR
-
-
-d = 2
-sigma = 0.1
-n_cmc = 10**7
-S_0 = 100
-K = [90, 100, 110]
-mu = 0.08
-r = 0.05
-tau = 3/50
-T = 1
-
-L0, indicator_true, hockey_true, quadratic_true, CVaR = ComputeTrueLoss(n_front=n_cmc,
-                                                                                       d=d,
-                                                                                       S_0=S_0,
-                                                                                       K=K,
-                                                                                       mu=mu,
-                                                                                       sigma=sigma,
-                                                                                       r=r,
-                                                                                       tau=tau,
-                                                                                       T=T,
[…]

### 2025-05-08 pre_private/summarize.py

@@ -1,32 +1,0 @@
-import numpy as np
-
-import matplotlib.pyplot as plt
-
-
-methods = ["snsbs", "reg", "knn", "lr", "krr"]
-methods_name = ["Standard with Bootstrap", "Regression", "Kernel Smoothing", "Likelihood Ratio", "Kernel Ridge Regression"]
-Gammas = [1000, 2000, 4000, 8000, 16000, 32000]
-
-plt.figure(figsize=(8, 4.5))
-
-for method, name in zip(methods, methods_name):
-    data = np.load(f"./result_2_time_{method}.npy")
-
-    plt.loglog(Gammas, data, label=name, marker="o", linestyle="--")
-
-plt.legend(loc="upper left")
-plt.xlabel("Simulation Budget $\Gamma$")
-plt.ylabel("Time (s)")
-plt.title("European Call - d = 2")
-plt.savefig("time_comparison.png", dpi=300)
-
-
-
-
-
-
-
-
-
-
-
